### 2013-03-01 0_frontmatter/abstract.tex
201303_Mar01

% Thesis Abstract -----------------------------------------------------

%\begin{abstractslong}    %uncommenting this line, gives a different abstract heading
\begin{abstracts}        %this creates the heading for the abstract page

Put your abstract or summary in 0\_frontmatter/abstract.tex.

\end{abstracts}
%\end{abstractlongs}

% ----------------------------------------------------------------------

### 2013-03-01 0_frontmatter/acknowledgement.tex
201303_Mar01

% Thesis Acknowledgements ------------------------------------------------

%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
%\begin{acknowledgements}      %this creates the heading for the acknowlegments

\section*{Acknowledgement} %this results in an overhead bar,  
\pagestyle{empty} %this removes the bar
%\addcontentsline{toc}{chapter}{Acknowledgement}

\epigraph{\textit{``Not many appreciate the ultimate power and potential usefulness of basic knowledge accumulated by obscure, unseen investigators who, in a lifetime of intensive study, may never see any practical use for their findings but who go on seeking answers to the unknown without thought of financial or practical gain.''}}%
{\textit{}\\ \textsc{Eugenie Clark}}

\onehalfspacing

Before anything, I would like to express my gratitude towards my family, specifically my wife, my parents and my kids,
  whose constant love and unconditional support I have greatly relied upon. 
Their immeasurable sacrifices together with their continous encouragement have always been the motivation for me to follow this academic pursuit.
%venture further. 
%It is ultimately to them that this work is dedicated.
They are the first and foremost people that this work is dedicated upon.

This thesis would also not have been possible without the patient and helpful guidance of Assoc. Prof. Ian McLoughlin and Assoc Prof. Nicholas Vun Chan Hua, 
	under whose supervision I am gratefully being under. 
The supervisors have been providing firm support, as well as spot-on guidance. 
During all the stages of my research work, 
	be it conceptualization or result analysis, be it writing, presentation or publishing ..
	their kind attention and wise advices command my utmost respect and admiration.

%The author also wish to thank Dr. Timo Brestchneider and Dr. Lee Ken Yoong, whose suggestions and knowledgable feedbacks have always been greatly appreciated. 
%Their continued efforts, together with EADS's various other contributions have greatly enhanced the quality of this research.

Special thanks go to my friends and colleagues, whose friendship and companion have made the journey a truly enjoyable one. 
They include but not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...

Last but not least I would like to give my appreciations to all NTU staffs at PDCC, SCE and GSO whose quiet but continous supporting efforts played a very important role in any measure of success this dissertation may be associated with.

\begin{flushright}
	\parbox[t]{1\textwidth}{%b
	\begin{flushright}
		\emph{{}``The roots of education are bitter, but the fruit is sweet.''}\\
		\emph{--} Aristotle\\
	\par\end{flushright}%
	}	
\par\end{flushright}

%\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

### 2013-03-01 0_frontmatter/glossary.tex
201303_Mar01

% this file is called up by thesis.tex
% content in this file will be fed into the main document

% Glossary entries are defined with the command \nomenclature{1}{2}
% 1 = Entry name, e.g. abbreviation; 2 = Explanation
% You can place all explanations in this separate file or declare them in the middle of the text. Either way they will be collected in the glossary.

% required to print nomenclature name to page header
\markboth{\MakeUppercase{\nomname}}{\MakeUppercase{\nomname}}

% ----------------------- contents from here ------------------------

\nomenclature{SAR}{Synthetic Aperture Radar} 
% chemicals
\nomenclature{DAPI}{4',6-diamidino-2-phenylindole; a fluorescent stain that binds strongly to DNA and serves to marks the nucleus in fluorescence microscopy} 
\nomenclature{DEPC}{diethyl-pyro-carbonate; used to remove RNA-degrading enzymes (RNAases) from water and laboratory utensils}
\nomenclature{DMSO}{dimethyl sulfoxide; organic solvent, readily passes through skin, cryoprotectant in cell culture}
\nomenclature{EDTA}{Ethylene-diamine-tetraacetic acid; a chelating (two-pronged) molecule used to sequester most divalent (or trivalent) metal ions, such as calcium (Ca$^{2+}$) and magnesium (Mg$^{2+}$), copper (Cu$^{2+}$), or iron (Fe$^{2+}$ / Fe$^{3+}$)}

### 2013-03-01 1_introduction/introduction.tex
201303_Mar01

%: ----------------------- introduction file header -----------------------
\chapter{Introducing The Research Question}

% the code below specifies where the figures are stored
%\ifpdf
%    \graphicspath{{1_introduction/figures/PNG/}{1_introduction/figures/PDF/}{1_introduction/figures/}}
%\else
%    \graphicspath{{1_introduction/figures/EPS/}{1_introduction/figures/}}
%\fi

% ----------------------------------------------------------------------
%: ----------------------- introduction content ----------------------- 
% ----------------------------------------------------------------------

Univariate SAR and multi-variate POLSAR data are multiplicative and heteroskedastic.
By definition, heteroskedastic noised data has its variance, and correspondingly its substractive distances,
  dependent on the main signal.
In another line of research, log transformation has been shown
  to convert the multiplicative nature of SAR data into a more familiar additive nature.
We hypothesize that   
  log-transformation also offers several consistent measures of distance in heteroskedastic SAR and POLSAR data.
This thesis aims to investigate and validate that hypothesis.

In this chapter: the main research problem and the corresponding hypothesis are explicitly stated.
The methodology section explains how the results are obtained and analyzed.
Contributions to advance theoretical knowledge are illustrated.
Towards the end of the thesis, an application illustrate how the theoretical results can be applied in future research and development activities.

%: ----------------------- HELP: latex document organisation
% the commands below help you to subdivide and organise your thesis
%    \chapter{}       = level 1, top level
%    \section{}       = level 2
%    \subsection{}    = level 3
%    \subsubsection{} = level 4
% note that everything after the percentage sign is hidden from output

	\section{Background Context and the Motivation to Study}

%Advantages of SAR in remote sensing paragraph (page 3)
Synthetic Aperture Radar can soon become the preferred choice for
  continous and autonomous large-scale remote surveillance solutions.
Compared to optical remote sensors, which is passive,
  active SAR sensors provides weather independent and night-inclusive operational capabilities.
Compared to other radar based active sensors, for example Real Aperture Radar (RAR),
  SAR provides a much better resolution, and larger coverage solution.
The once-limiting drawback of SAR is the high-demanding signal processing procedures,
  which is needed to process SAR images, has become obsolete,
  due to recent and quick advances in computational power  \citep{Cumming_2005_Artech}.

EM wave polarization and polarimetric SAR paragraph (page 3)

A paragraph about partial polsar and the extension from (page 3)

Problem: speckle in SAR and POLSAR, especially its heteroskedastic nature. (new)

The motivation then is to provide a probably better understanding about the statistics of speckle. (new)

For SAR data (page 4)

For partial POLSAR data (new)

For full polsar data (new)

The purpose of this section is to illustrate the importance of a computational framework needed in the interpretation and processing targets' stochastic polarimetry signatures. 
%This section start by describing the recent focus of space technology in earth observational remote sensing.
As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
Recent advances in computational power has made the once-limiting high-demanding signal-processing procedures, which are needed to process SAR images, obsolete \cite{Cumming_2005_Artech}.
Thus we believe, SAR will soon come to be the preferred choice for continuous and autonomous large-scale remote surveillance solutions.

Electromagnetic waves have the intrinsic nature of polarization.
Polarimetric SAR, i.e. POLSAR, extends the SAR acquisition information from the traditional single SAR channel to multi-channel polarimetric SAR data, corresponding to different combination of transmitted and received polarizations.
Early works from the radar community had focused on the theoretical introduction of scattering matrix, i.e. Sinclair matrix or Mueller matrices, for full, i.e. quad, polarimetric measurements \cite{Sinclair_1950_ProcsIRE}.
%(Sinclair, 1950), (TODO) 
These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \cite{Zebker_1991_ProcsIEEE}.

Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR, and so on, were launched.
However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes apparently as a compromise between theoretical polarimetric requirements and practical limitations.
Initially to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.
Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
In his pioneer paper in 2005, Souyris\cite{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode with the suggestion that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
Raney\cite{Raney_2006_IGARSS} showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave, via Stokes parameters, but also capable of detecting the basic target's polarimetric characters, i.e. odd or even bounce phenomena.

The extensions from single-channel SAR to multi-channel polarimetry can be considered as analogous to the advancement towards colour TV from the black-and-white days.
While the future is promising, both SAR and POLSAR suffer from speckle phenomena, which hampers the human capabilities to understand SAR images.
Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.

%%TODO: SWITCH IMAGES: 24 lines
%\begin{figure}[h!]
%\centering
%	\subfloat[Optical Colour Image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		 \epsffile{images/20100502_mris_clipped.eps} 	
%		 \label{Original}
%	} 
%	\hfill
%	\subfloat[Optical Gray level image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		\epsffile{images/20100502_mris_clipped_gray.eps}
%		 \label{}
%	}
%	\hfill
%	\subfloat[Speckled SAR image]{
%		 \epsfxsize=1.75in
%		 \epsfysize=1.75in
%		 \epsffile{images/20100502_sar.eps} 	
%		 \label{Original}
%	} 
%\caption{Speckle phenomena in SAR data}
%\label{fig:sar_speckle_wrt_optical}
%\end{figure}

The motivation for this research then is to reconstruct high-quality grey-scale images from speckled single channel SAR data, and to visualise as colourful images the despeckled multi-channel POLSAR data.
In order to do so, the speckle effects need to be removed as much as possible from original (POL)SAR data.

Due to the random nature of speckle, speckle filtering has been put into the context of statistical estimation theory, which comprises statistical modelling and validation, estimator design and development as well as evaluation of different estimators' accuracy.
This proposed research project focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
The benefits of such a framework are many fold.
Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for a real expensive satellite imagery.
Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.

For single-channel SAR images, our initial observations and experiences indicate that the community has been oblivious to many of the negative effects of statistical heteroskedasticity manifested in the original intensity and amplitude data.
In Chapter 4, it is shown that logarithmic transformation can convert SAR's multiplicative stochastic process into a better-understood additive noise model.
Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.
As the additive noise PDF in log-domain has been worked out, we hypothesize that the true back-scattering coefficient PDF, also in log-domain, can be estimated through regularized deconvolution algorithms.
If an algorithm could be designed to estimate such PDF, we believe this would present an improvement for a whole class of speckle filters, namely the Maximum-A-Priori (MAP) class, which up to now, still assumes the true PDF will follow certain known fixed distributions.
%It is hoped that with the true PDF now being estimatable from the data itself, a better speckle filtering algorithm, in log-transformed domain, can be developed.

For multi-channel SAR data, as reviewed in Chapter 2, speckle filtering for the off-diagonal element $S_hS_v^*$ of the covariance matrix is still an open question.
Our observation has been that these elements are also available in dual-polarization SAR data, they specifically are part of Stokes parameters.
As mentioned earlier, Stokes parameters have been largely ignored in polarimetric literature, until recently asserted again by Raney in 2006 \cite{Raney_2006_IGARSS}.
Mathematically, Stokes parameters can be written as:
\begin{equation}
S = 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		2 \Re{(S_hS_v^*)} \\
		2 \Im{(S_hS_v^*)}
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		S_+S_+ - S_-S_- \\
		S_lS_l - S_rS_r
	\end{array}
\right)
\end{equation}
We have evidence, and hypothesize that $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ will have the same physical and statistical properties as the normal $S_hS_h$, $S_vS_v$.
If our hypothesis can be proven rigorously, it may then be possible to build and validate a statistical model for all elements in the covariance matrix of Polarimetric SAR data, namely $S_hS_h$, $S_vS_v$, $\Re{( S_hS_v^*)}$, $\Im{( S_hS_v^* )}$.
Also, speckle filtering on off-diagonal elements can be carried out using techniques, that were originally developed for single-channel SAR data, and up to now is only applicable to the diagonal elements of the covariance matrix.

For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
%Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.

	\section{Objectives, Methodology and Contributions}

Copy the objectives (page 6)

copy the benefits (page 6)

\subsection{Objectives and Contributions}

The purpose of this section is to illustrate the objectives in developing computational frameworks for Stochastic Polarimetric Data. 
Assuming the framework will be implemented successfully, this section also describes its academic contributions as well as its projected practical benefits.
% for the industry.
%Also the academic contribution as well as practical benefits, assuming the frameworks is developed that meet the requirements, is to be described.

%Even though the research topics appears segmentable into different sub-fields, the fact is that all of them can be considered as an application of statistical estimators.
Even though the research topic spreads across different sub-fields, a common thread that bind them all together is the application and development of statistical estimators.
For single channel SAR, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
In the case of multi-channel SAR, it is the estimation of a target's polarimetric signature, being measured in multiple channels simultaneously and stochastically.
And for the problem of target detection or classification, it is the likelihood estimation that the target belongs to a certain category.
% which is then fed into a decision rule to make a last judgement.

Thus, the main objective of this research is to derive effective statistical estimators for the reconstruction and classification of the underlying target information in speckled SAR and POLSAR data.

In order to design and evaluate effective estimators, we centre our effort on developing a good computational framework. 
The objective of such framework being:
\begin{enumerate}
\item To build, develop and validate statistical models for different stochastics processes that are inherent within the polarimetric SAR domain.
\item To allow easy, fast and repeatable simulations and experiments of various stochastic processes in designed, focused, as well as broad-based scenarios.
\item To allow easy application of different existing estimators as well as various transformations into focused and simulated scenarios as well as into practical real measured data.
\item To allow development and calculation of good performance indices for estimators. 
\item To allow visualization and analysis of the performance of different stochastic estimators.
\item Ultimately, to allow development of better and more accurate estimators, whose results can be verified: not only qualitatively on real life images, but also quantitatively through rigorous simulations.
%quantitatively in rigorious simulations and qualititatively in real measured data.
\end{enumerate}

The possible benefits of the research project are:
\begin{enumerate}
\item Practical benefits
\begin{enumerate}
\item The computational frameworks allow for faster, quicker and more focused experiments. 
Often, a statistical hypothesis can be observed or rejected by designing and implementing an appropriate computational experiment.
\item The framework allows for easier analysis, and thus more insight to be gained, on the performance of an estimator. 
This, in turn, allows for design and development of better estimators.
\item Our research to find evidence, and hopefully rigorous proofs, supporting the advantages of (partial) polarimetric SAR implementations over conventional SAR data also yields high practical interest.
%Our research to find evidence, and hopefully rigorious proofs, supporting the advantanges of A over B also yields high practical interests.
%Our intended research to address a pressing practical trade-off, between a choice of better resolution and an option of complete polarimetric information, also yields high practical interests.
Apparently the topic has also received a fair share of attention and supports from EADS \footnote{This PhD research project is run in conjunction with EADS and has an EADS co-supervisor}.
\item The investigative research of ship monitoring using polarimetric SAR satellites is also apparently of high interest to EADS, as evidenced by their own in-house investigations.
\end{enumerate}
\item Academic benefits
\begin{enumerate}
\item The computational framework allows for quantitative evaluation and comparison of estimators.
With fast and repeated experiments, the framework allows one to not only compute a single performance value on a single experiment, but also to analyze the whole behaviour of such performance measures over repeated stochastic simulations.
\item For the sub-topic of single-channel SAR imagery, we believe an estimate for the PDF of the true underlying coefficient will be an unique research result.%is the first of such kind.
\item For the multi-channel POLSAR sub-field, we believe our proposed approach in speckle filtering of the off-diagonal elements in the polarimetry covariance matrix is also a novelty.
\item For the specific application of ship detection and classification, we believe our approach of evaluating the performance of higher-resolution and partial polarimetry modes using ground truth from AIS data is also unique.
\end{enumerate}
\end{enumerate}

As a testament on the effectiveness of this research, the work discussed in this report was published as two separate papers in 2010, at ISCCSP\cite{Le_2010_ISCCSP} and ACRS\cite{Le_2010_ACRS}.

\subsection{The Research Questions}

Figure 
	\ref{fig:residual_as_noise} 
shows that: when compared with optical remote sensing images, SAR data suffers from serious degradation.
%SAR data suffers from stochastic speckle phenomena, which poses numerous challenges in human capabilities of understanding SAR images.
%Years of research in SAR signal processing has resulted in various speckle filters, all of which aims to produce better visually de-speckled gray images from the degraded SAR data.
The degraded SAR data almost invariably requires a treatment of speckle filtering to yield more comprehensible images.
Recent advances in Polarimetric SAR (POLSAR) have produced multiple channels of SAR data, which are conceptually similar to the multiple channels found in colourful optical images.
However, the stochastic effects of speckle on multivariate and correlated data is ever more eminent.
The key proposed research question is how to reconstruct clean, colorful visualization of Polarimetric Information from the new but speckled PolSAR satellites.
Towards the end of the research project, an optional extended question shall be how this extra de-speckled polarimetric information may help in the tasks of target detection and classification.

The main research question is conceptually divided into the following subsidiary questions to investigate:
% and project phases include. 
%1. How to simulate SAR and Polarimetric SAR data (quick pass, no lit review)
\begin{enumerate}
\item For single channel SAR data, the main aim would be how best to produce and quantitatively evaluate the de-speckled gray images. 
The main contributions could be that: for the first time, the PDF for the underlying back-scattering coefficient appears to be estimate-able, at least in the log-transformed domain. 
It is hoped this new knowledge may help in developing better speckle filters, especially those filters of \textit{Maximum a Posteriori} (MAP) nature.
Another possible contribution could be: how the homoskedasticity in the log-transformed domain could help to consistently evaluate the performance of different speckle-filters being applied on heterogeneous spatial variations.
%2. how the PDF of underlying back-scattering coefficient, in the log-domain, could be estimated and how this could help in improving the performance of the Maximum A Posteriori class of speckle-filters.
%The topic and the concept itself is a new topic
\item For multi-channel SAR data, the main aim would be to produce a smoothed and colourful visualisation of Polarimetric information. 
The main contributions would be a methodology to extends the results of single-channel SAR speckle filtering towards the issue of estimating the off-diagonal elements in polarimetric covariance matrix. 
Another fundamental contribution could be: how to model, simulate and visualize the multivariate and correlated channels in POLSAR data.
\item The third portion of this project is to investigate how full polarimetric information could be reconstructed from partial polarimetry modes. 
The main aim of this section is to fill the gap between practical dual-polarimetric implementations and theoretical established full polarimetric results. 
%The practical application is synchronized with current satellite hardware deployments and trade-offs.
\item An optional collaborative portion is to investigate how the extra information in different polarimetric modes may help in the task of target detection and classification. 
The main aim of this stage is to demonstrate the capability of (partial) polarimetric information over traditional single-channel SAR data.
%and also to evaluate the trade-off between higher resolution offered by partial polarimetric architecture and the more complete full polarimetric mode.
%Algorithms may have been and will also be proposed to tackle these issues, but the need to evaluate the algorithms requires rigorious ground-truthed data.
\end{enumerate}

\subsection{Research Methodology}

As the speckle phenomena is stochastic in nature, speckle filtering has been put into the framework of statistical estimation.
This project's research methodology will be based extensively on a statistical estimation framework. 
The framework consists of three stages:

\begin{enumerate}
\item Stage 1: data statistical analysis. 
We aim to propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
The statistical models built after such a transformation are validated against real-life data.
\item Stage 2: predictor and estimator development.
Various statistics based computational intelligence and/or signal processing methods are intended to be applied. 
\item Stage 3: results analysis and performance evaluation.
Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
%Stochastic simulation based experiments with evaluation being both through consistent quantitative measures and visual qualititative comparisions from real captured imagery. 
\end{enumerate}

\subsubsection{Data Collection}

We have used, and plan to keep using simulated data extensively. 
There appears to have a number of advantages in using simulated experiments:
\begin{enumerate}
\item Once the model is validated against real-life data, simulated experiments can be carried out on more focused scenarios.
This allows smaller data sets to be generated and analysis can become faster and more accurate.
%Experiments can be carried out on smaller scale data, with validation from real images to come later
\item Contrary to real-life images where underlying coefficients are to be estimated, ground truth is readily available in simulated experiments.
\item Quantitative evaluation is possible not only via a single experiment on a single real-image but via repeated stochastic runs. 
\item Thus not only single values of mean or mean-squared-error is to be evaluated. 
As the whole response PDF is available, statistical bias or heteroskedasticity can also be reported.
%But also statistical bias or heteroskedasticity can be estimated as the whole pdf distributions are available. 
\end{enumerate}

Besides simulated  data, we have gathered a large amount of real-life data.
The table below lists data made available to us, courtesy of EADS Innovation Works Singapore. %(TODO:RECOLLECT)

\begin{table}
\centering
\begin{tabular}{|c|c|c|}
\hline
Radar Platform & Polarization Mode & Data Capture Time \\
\hline
RadarSat 2 & Full Quad Pol & 29 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 05 Apr 2009 \\
RadarSat 2 & Full Quad Pol & 12 Mar 2009 \\
RadarSat 2 & Full Quad Pol & 23 Jan 2009 \\
RadarSat 2 & Full Quad Pol & 30 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 06 Dec 2008 \\
RadarSat 2 & Full Quad Pol & 19 Oct 2008 \\
RadarSat 2 & Full Quad Pol & 12 Nov 2008 \\
RadarSat 2 & Full Quad Pol & 25 Sep 2008 \\
TerraSar-X & Dual Pol (HH-VV) & 18 Apr 2008 \\
NASA-JPL AirSar & Full Quad Pol & 2001 \\
\hline
\end{tabular}

\label{tbl:collected_data}
\caption{Collected imagery data}
\end{table}

Furthermore, for the task of ship detection and classification using polarimetric data, we intended to capture ship's location using readily available Automatic Identification System (AIS) systems. 
The data collection strategy will be synchronized tasks of satellite imagery and AIS data capture.
AIS data, in a close-to-port environment, will be used as ultimate ground truth to evaluate different target detection and classification algorithms.

\subsubsection{Result Interpretation and Evaluation}

Simulated experiments allows evaluation of estimators against ground-truth.
Errors can be quantitatively analyzed and methods to reduce such errors can be developed.
Thus simulated experiments could produce quick results, which may provide faster analysis and further insights for developing more accurate estimators.

Practically in the end, all estimators would always need to be applied on real images.
Contrary to experiments on simulated data, experiments on real images can only be compared qualitatively.
This however, is critical and will always be used in our investigations.
The reason is that this helps to guard against any systematic errors in the used assumptions and approximations made in developing the theoretical models.
Towards that end, real-data can help to build and validate statistical models.

\subsubsection{Theory Development and Research Strategy}
For single channel SAR data, we propose the use of a log transform to evaluate speckle filter's performance. 
We have proved that homoskedasticity property is indeed manifested in the log-domain.
The traditional performance index in comparing speckle filters, i.e. the Equivalent Number of Looks (ENL), has also been shown to be related and calculable from the standard Mean Squared Error (MSE) inside the log-domain.
We are working to prove that, with the homoskedastic property asserted, the universal Mean Squared Error can be a good performance indicator, even on heterogeneous spatial variations.

Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able. 
In figure 
	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
the underlying single channel gray image histogram is presented along with the noise PDF, in the log-transformed domain. 
As the noise is additive, it is expected that the noise PDF will act as a point spread function.
This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
This fact is evidenced in figure 
	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
We hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods.
We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.

\begin{figure}[h!]
\centering
	\subfloat[Original image's histogram and PSF]{
		 \epsfxsize=3in
		 \epsfysize=3in
 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
		 \label{fig:noise_pdf_as_psf:conv_inputs}
	} 
	\hfill
	\subfloat[Convoluted and speckled image histogram]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
		 \label{fig:noise_pdf_as_psf:conv_output_observable}
	}
\caption{Observable convolution of PSF}
\label{fig:noise_pdf_as_psf}
\end{figure}

For multi-channel SAR data, we focus on partial polarimetric SAR satellite data.
Attempts have been made to model the data, especially the off-diagonal covariance matrix elements, i.e. $S_hS_v^*$.
However, the models are overly complicated which made proposed PolSAR speckle suppression algorithms became overly complex (see polarimetric data modelling section in Chapter 2).
We preferred an alternative approach.
We propose to transform the polarization basis of dual-polarized SAR data to help estimate this element.

We first pick up a recent revelation by Raney, 2006 \cite{Raney_2006_IGARSS}, that the back scattering waves' polarization captured in dual-pol data can be completely described using Stokes parameters.
%From the usually given pairs of $S_h$ and $S_v$, Raney has shown that Stokes parameters can be computed.
Furthermore, Stokes parameters can be measured in multiple polarization basis, which can also be synthesized from the given data (see polarization basis transform section in Chapter 2).
%Both transformations, i.e. from $\{h,v\}$ to circular basis $\{l,r\}$ and from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ modes, are special cases of the transformation formula.
That is:
	the measured signal at $\pi/4$ linear polarizer as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.

The Stokes vectors, when aligned at these transformed projections are given by the following well-known equation:
\begin{equation}
S_t = \left(
\begin{array}{c}
 |\xi_h|^2 + |\xi_v|^2 \\
 |\xi_h|^2 - |\xi_v|^2 \\
 2 \Re( \xi_h \xi_v^* ) \\
 2 \Im( \xi_h \xi_v^* ) 
\end{array}
\right)
= \left(
\begin{array}{c}
 |\xi_+|^2 + |\xi_-|^2 \\
 -2 \Re( \xi_+^* \xi_- ) \\
 |\xi_+|^2 - |\xi_-|^2 \\
 2 \Im( \xi_+^* \xi_- ) 
\end{array}
\right)
= \left(
\begin{array}{c}
 |\xi_l|^2 + |\xi_r|^2 \\
 2 \Re( \xi_l^* \xi_r ) \\
 -2 \Im( \xi_l^* \xi_r ) \\ 
 |\xi_l|^2 - |\xi_r|^2 
\end{array}
\right)  
\end{equation}

Evidently, the real and imaginary parts of $S_hS_v^*$ is closely related to Stokes Parameters.
Specifically they may be considered as the subtraction of two random SAR intensity variables, e.g., $|S_l|^2 - |S_r|^2$. 
%Since ShSh is exponential this can be calculated through convolutions, if each channels are independent. 
%Laplace distribution is the difference between two identical exponential distributions. 
For the same traditional reasoning of $|S_h|^2$ and $|S_v|^2$, we hypothesize that all the four intensities calculated from the transformation of polarization basis, i.e., $|S_+|^2$, $|S_-|^2$, $|S_l|^2$, $|S_r|^2$, follow negative exponential distributions. 
The hypothesis is supported by our preliminary experiment results, where we synthesize the basis transformed intensity from real-measured polarimetric data.
It then follows that $S_hS_v^*$ can be despeckled by independently de-speckling the four synthesized intensities.
Read chapter 4 for our work in progress in single-channel SAR speckle filtering.
We hope to go further speculating that: the speckle-filtering methodologies in dual-polarization SAR data is extensible to full polarimetric SAR data.

%In fact, we could build and validate statistical model for all elements of POLSAR data.
%One steps further and we could demonstrate the methodology for target detection and classification in dual-pol data.
%The original results in reconstruction from CP to FP could be revised and evaluation may be on estimates of Entropy, Polarization angle, Anisotropy (Cloude).

%We could also go further and build a model for simulation of POLSAR images.
%Stokes matrix can uniquely describe covariance matrix (CP). Thus dual-pol data could be visualized as a color image, and a color image could be used to simulate CP data? (Simulation). Math: stokes vector to degree of polarization, and two angles! map that to HSV colors.
%This study would also help to identify pdf() rules for polarized light parameters being: degree of polarization, polarization angles. On way to remove speckle is multi-look processing. The effects of multi-look as biased estimation of these parameters will be discussed. The advanced way is bias-correction. Biasness can be investigated by simulation. A more prolonged study is to see the simulate pdf() (additive!) and match that with real data for model identification (ignore this!). Alternatively statistical analysis of off-diagonal Covariance matrix elements. Speckle suppression algorithms can be developed. Evaluation is hard at this point.
%Should a review of target decomposition is needed see (Unal,2009,PIER).
%One can change polarization basis to circular polarizations (see Boulbry,2007,ProcSPIE). 
%decomposition and compact polarimetric target decomposistion

To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).

\subsection{Theoretical and Practical Contributions}

For SAR data, the main focus is on niches areas like evaluation of filters, estimate of PDF, new filter?
For PolSAR data, the main focus is more fundamental: investigation and modelling of PolSAR data channels. 
The approach is to start from simulation and ENL estimation in multi-variate extension of Gauss Markov theorem, 
new filters can be developed, initially with limited assumptions in modelling, and is evaluated against an evaluation protocol.
Assumptions are made and tested in the process of evaluation of PolSAR speckle filter. 
Valid assumptions are then checked against mathematical formula and transformations.

The methodology in analysing multi-channel Polarimetric SAR data is to based on target decompositions.
The multi-variate data is decomposed into conceptually and physically independent quantities and analysis is conducted on them individually!
Another possibility is to find a consistent distance measure from the multi variate, multi-dimensional SAR data.
This distance measure would be useful in the task of target detection from a randomized background.
It could also be useful in land cover classification as well as change detection fields of PolSAR

We believe that the main focus of this research, partial polarimetric speckle filtering, has the following advantages:
\begin{enumerate}
\item The topic and the concept itself are newly developed and have just recently being introduced into the community.
\item Compared to full polarimetric data, partial polarimetry is much more compact.
Yet it still exhibits the same multi-variate correctional statistics properties. 
\item The practical application is synchronized with current satellite hardware deployments and trade-offs.
\end{enumerate}

The possible benefits of our proposed research project are:
\begin{enumerate}
\item Practical benefits
\begin{enumerate}
\item The computational frameworks allow for faster, quicker and more focused experiments. Often a point can be proven or rejected by designing and implementing an appropriate computational experiment.
\item The framework allows for easier analysis and allows for more insight to be gained in an estimator's performance. This in turn allows for the development of better estimators.
\item Our research topic for partial polarimetric SAR has high practical interest, addressing a pressing practical trade-off between the better resolution in partial modes versus the more complete but coarser resolution in theoretical full polarimetry.
Apparently the topic also generated practical interest from industry, i.e. from EADS.
\item The investigative research of ship monitoring using polarimetric SAR satellites is also apparently of high interest to EADS, as they are themselves working in this area.
\end{enumerate}
\item Academic benefits
\begin{enumerate}
\item The computational framework allows for quantitative evaluation of estimators.
And with fast and repeated experiments, the framework allows the computation of not only a single performance counter value on a single experiment, but also allow the full distribution of such performance over repeated stochastic simulations to be inspected.
\item For our research topic in the SAR community, we believe that obtaining an estimate of the true underlying PDF is a first of such systems.
\item For multi-channel POLSAR, we believe our approach to tackle speckle filtering of off-diagonal elements in polarimetric covariance matrix is also a novelty.
\item In the topic of target (ship) detection and classification, we believe our approach of evaluating the trade off between higher-resolution and partial polarimetry using AIS as ground truth is also unique.
\end{enumerate}
\end{enumerate}

	\section{Organisation of the Thesis}
The rest of this thesis is organized into 5 chapters, as follows:
The next chapter will survey the related publications
  and state-of-the-art techniques in modeling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
Through these discussion, the need for a homoskedatic and scalar model for the multivariate and heteroskedastic polsar is brought forward.

The heart of the thesis lies in chapters \ref{chap:sar} and \ref{chap:polsar}.
While chapter \ref{chap:sar} presents the initial homoskedastic model for SAR data, 
chapter \ref{chap:polsar} illustrates the more recent and more generic model for POLSAR.
Chapter \ref{chap:polsar} also specifically describes how the initial model for SAR can be considered as a special case of the POLSAR model.

Chapter \ref{chap:applications} presents several of our published techniques in handling both SAR and POLSAR data.
Theses techniques can all be considered as applications of the theoretical model presented in chapters \ref{chap:sar} and \ref{chap:polsar}.
Demonstrated applications include, but the possibilities are not limited to: clustering algorithms, speckle filtering techniques or a novel methodology to evaluate (POL)SAR speckle filters.
Finally, the contribution of the thesis is discussed in the conclusional chapter \ref{chap:conclusions}.

### 2013-03-01 2/literature_review.tex
201303_Mar01

\chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2

\section{The nature of Polarimetric SAR: EM Wave Polarization}

Remote sensing introduction paragraph (section 2.1.1)

SAR introduction paragraph (section 2.1.2)

EM Wave polarization (Maxwell law leads to wave equations section 2.1.3.1, choice of origin which leads to polarization basis change eq 2.22)

SAR Polarimetry: and SAR as a special case of POLSAR (send and receive polarizations: 2.1.3.5)

Full Polarimetric SAR and target polarimetric response (also 2.1.3.5)

Partial Polarimetric SAR and EM wave polarization (2.1.3.4)

SAR stochastics nature (new)

\subsection{Representations of EM Wave Polarizations (Linear, Circular ...)}

\subsubsection{Plane wave and solutions to the EM Wave equations}

The general solution to the PDE EM wave equation is a linear superposition of waves each having the form
\begin{equation}
\vec{E}(\vec{r},t)=g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{equation} 
and
\begin{equation}
\vec{B}(\vec{r},t)=g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
\end{equation}
where
	$g$ is any well-behaved function of a dimensionless argument $\phi$,
	%for virtually any well-behaved function g of dimensionless argument φ, where
	$\omega$ is the angular frequency (in radians per second), and
	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).

%Although the function $g$ can be, and often is, a monochromatic sine wave, it does not have to be. 
%In practice, $g$ cannot have infinite periodicity because any real electromagnetic wave must always have a finite extent in time and space. 
%Thus based on the theory of Fourier decomposition, a real wave must consist of the superposition of an infinite set of sinusoidal frequencies.
In addition to the relations above, the wave vector and the angular frequency are not independent; they must adhere to the dispersion relation:
\begin{equation}
k = |\vec{k}| = \frac{\omega}{c} = \frac{2\pi}{\lambda}
\end{equation}
where 
	$k$ is the wave number and $\lambda$ is the wavelength.

Since any real wave can be considered as a superpositions of several sinusoidal waves, the simplest solution to consider for the EM Wave equations is:
\begin{equation}
\vec{E}(\vec{r},t)= \Re \left( \vec{E}(\vec{r}) e^{i \omega t} \right)
\end{equation}
where
	$\omega = 2 \pi f$ is the angular frequency,
	$f$ is the wave frequency.
Assuming the most common case of EM waves travelling in a planar fashion, which is a good approximation of most light waves. 
For plane waves Maxwell's equations, specifically Gauss's laws, imposes a transversality requirement that the electric and magnetic field be perpendicular to the direction of propagation and to each other. 
Conventionally, when considering polarization, the electric field vector  is described and the magnetic field is ignored since it is perpendicular  to the electric field and proportional to it. 
%Since the magnetic field is dependent on the electric field, 
Thus it is sufficient to just consider electric field, which equals:
\begin{equation}
\vec{E}(\vec{r}) = \vec{E^0} e^{-i \vec{k} \cdot \vec{r}} %= \vec{E^0} e^{-ikz}
\end{equation}

Combining the two equations we have:
\begin{equation}
\vec{E}(\vec{r},t) 
	= \vec{E^0} \Re \left( e^{i (\omega t - \vec{k} \cdot \vec{r})} \right)
	= \vec{E^0} \cos(wt - \vec{k} \cdot \vec{r}) %\vec{E^0} \cos{ \left( wt - kz + \phi_0 \right)}
\end{equation}

If we define the $z$ direction as the travelling direction of the EM wave,
%	and x direction is the direction of $\vec{E}$,
%	then by Faraday's Law, the magentic field $\vec{B}$ lies in y direction, 
%		and is related to the electric vector by $c^2 \frac{\partial B}{\partial z} = \frac{\partial E}{\partial t}$
	and the electric field is fluctuating in the $(x,y)$ plane,
	because the divergence of the electric and magnetic fields are zero, 
		there will be no fields in the direction of propagation.
Project this into $x$ and $y$ directions:
\begin{equation}
\vec{E}(z,t) 
= 
\left(
	\begin{array} {c}
		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
		0
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		\xi_x(t) \\
		\xi_y(t) \\
		0
	\end{array}
\right)
\end{equation}
where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.

\subsubsection{Linear, Circular and Elliptical Polarization}

The shape traced out in a fixed projective plane by the electric vector as the plane wave passes over it is a description of the polarization state. 
This shape is characterized by the formula
\begin{equation}
 \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
\end{equation}
where
	$\Delta \phi = \phi_y^0 - \phi_x^0$
The formula characterizes what is termed as the polarization ellipse.

%In the leftmost figure above, 
When the two orthogonal components are in phase, i.e. $\phi_x^0 = \phi_y^0$, the ratio of the strengths of the two components is constant.
Thus the direction of the electric vector (the vector sum of these two components) is constant. 
Since the tip of the vector traces out a single line in the plane, this special case is called linear polarization. 
The direction of this line depends on the relative amplitudes of the two components.
%In the middle figure,

When the two orthogonal components have exactly the same amplitude and are exactly ninety degrees out of phase, i.e. $E_x^0=E_y^0$ and $ | \phi_x^0 - \phi_y^0 | = \pi/2$. 
%There are two possible phase relationships that satisfy this requirement: the x component can be ninety degrees ahead of the y  component or it can be ninety degrees behind the y component. 
In this special case the electric vector traces out a circle in the plane, so this special case is called circular polarization. 
The direction the field's rotation depends on the signed of the difference between the two phases. 
These cases are called right-hand circular polarization and left-hand circular polarization, 
	depending on which way the electric vector rotates and the chosen convention.

The general case is when the two components are not in phase 
	and either do not have the same amplitude or are not ninety degrees out of phase, 
	though their phase offset and their amplitude ratio are constant.
This kind of polarization is called elliptical polarization because the electric vector traces out an ellipse in the plane (the polarization ellipse). 
%This is shown in the above figure on the right.

The parameters that describe the polarization ellipse are:
\begin{equation}
\tan (\theta ) = \frac{E_y^0}{E_x^0}
\end{equation}
with
	$0 \leq \theta \leq \pi/2$. 
The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
\begin{equation}
\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
\end{equation}
with
	$0 \leq \Psi < \pi$. 
The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
\begin{equation}
\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
\end{equation}
with
	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$

Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.

%The choice of basis vector used to represent horizontal and vertical directions are evidently arbitrary.
%In general, any pair of orthogonal polarization states can be used.
%Formally orthogonal vector pair is defined as one having a zero inner product.
%Another common choice is left and right circular.
%In anyway, implicit in the representations above is the orientation of the coordination frame.
%Of the two angles frequently used in polarization ellipse analysis, one $\Psi$ is dependent on the coordination frame and the other may not $\chi$

%To recap $\chi = \tan^{-1} (1/\epsilon)$, with $\epsilon$ being the ellipse's ellipticity.
%In polarization ellipse, $\epsilon=1$ indicates circular polarization, while $\epsilon=0$ or $\epsilon=\infty$ corresponds to linear polarizations.
%An alternative to ellipticity angle $\chi$ is the eccentricity angle.
%However, the use of ecccentricity angle has not been widely used, as it has no obvious geometrical interpretation in Poincare Spheres.

%The polarization of light can be measured with a polarimeter.

\subsubsection{Mathematical representations of wave polarizations}

\paragraph{ Complex polarization ratio }
This ratio is important in explaining polarization basis changes.

It is defined as:
\begin{equation}
\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
\end{equation}

\paragraph{Jones Vector}

%Let the total wave power:
%\begin{equation}
%|E|^2 = (E_x^0)^2  + (E_y^0)^2
%\end{equation}
%and phase 
%\begin{equation}
%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
%\end{equation}

The Jones vector is defined as 
\begin{equation}
J = 
\left(
\begin{array}{c}
	\xi_x(t) \\
	\xi_y(t) 
\end{array}
\right)
= \xi_x(t)
\left(
\begin{array}{c}
	1 \\
	\rho
\end{array}
\right)
\end{equation}

Thus the normalized Jones vector can be given as:
\begin{equation}
J = 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
=
\left(
\begin{array}{c}
	1\\
	\tan(\theta) \cdot e^{i \Delta \phi}
\end{array}
\right)
=
\left(
\begin{array}{c}
	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
\end{array}
\right)
\end{equation}

The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
Its bra-ket notation formula, which is normally used in quantum computation contexts is:
\begin{equation}
J = | \Psi \rangle 
= 
\left(
\begin{array}{c}
	\cos(\theta) \cdot e^{i \phi_x^0} \\
	\sin(\theta) \cdot e^{i \phi_y^0}
\end{array}
\right)
\end{equation}

By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
\begin{array}{c}
 1 \\
 0
\end{array}
\right)$, similarly the vertical linear polarized wave: $J_v = \left(
\begin{array}{c}
 0 \\
 1
\end{array}
\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 1
\end{array}
\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 -i
\end{array}
\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
\begin{array}{c}
 1 \\
 i
\end{array}
\right)$

%Then any arbitrary state, written in R-L basis is given by:
%\begin{equation}
%| \Psi \rangle 
%= 
%a_R e^{i \phi_x - i \theta} | R \rangle 
%+ 
%a_L e^{i \phi_x + i \theta} | L \rangle 
%\end{equation}

\paragraph{ Stokes Vector }

Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
The wave coherency matrix is defined as:
\begin{equation}
W_c = \left<
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)^{\dagger}
\right>
= \left<
\left(
\begin{array}{c c}
 \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
 \xi_y \xi_x^* 	& \xi_y \xi_y^* 
\end{array}
\right)
\right>
= \left<
\left(
\begin{array}{c c}
 |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
 |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
\end{array}
\right)
\right>
\end{equation}

The Stokes vector is then defined as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_1 \\
 S_2 \\
 S_3
\end{array}
\right)
=
\left(
\begin{array}{c}
 |\xi_x|^2 + |\xi_y|^2 \\
 |\xi_x|^2 - |\xi_y|^2 \\
 2\Re(\xi_x \xi_y^*) \\
 2\Im(\xi_x \xi_y^*)
\end{array}
\right)
\end{equation}

In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 S_0 \\
 S_0 \cos(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\Psi) \cos(2\chi) \\
 S_0 \sin(2\chi)
\end{array}
\right)
\end{equation}

%It should be noted that: the factor of two before the polarization ellipse's angles indicate the fact that
%	any polarization ellipse is practical indistinguishable from on rotated by $180^o$ 
%	or with on with the axis lengths swapped accompanied by a $90^o$ rotation.

At this point, a distinction needs to be highlighted. %explaination is warranted.
%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
In comparison to the two-element Jones vector, Stokes vectors have more data, four elements. 
Jones vector can completely describe the polarization states of an elementary wave, which formulation is based on the assumption that the wave is very well behaved.
In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
As such, the polarization of the waves are normally not fully polarized.
One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
The phenomena can be loosely called wave depolarization.

The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wave length.
In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.

\paragraph{Degree of polarization}

Degree of polarization $p$ is a quantity used to describe the portion of an EM wave, which is polarized.
A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
Thus $0 \leq p \leq 1$.

In fully polarized wave, the following equation holds:
\begin{equation}
S_0^2 = S_1^2 + S_2^2 + S_3^2
\end{equation}

In depolarized wave, it becomes an in-equation
\begin{equation}
S_0^2 > S_1^2 + S_2^2 + S_3^2
\end{equation}

Then the degree of polarization is defined as
\begin{equation}
p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
\end{equation}

In such general case, the Stokes Vector is written as:
\begin{equation}
S_t = 
\left(
\begin{array}{c}
 I \\
 I p \cos(2\Psi) \cos(2\chi) \\
 I p \sin(2\Psi) \cos(2\chi) \\
 I p \sin(2\chi)
\end{array}
\right)
 = I (1 - p)
\left(
\begin{array}{c}
 1 \\
 0 \\
 0 \\
 0
\end{array}
\right) 
+ I p
\left(
\begin{array}{c}
 1\\
 \cos(2\Psi) \cos(2\chi) \\
 \sin(2\Psi) \cos(2\chi) \\
 \sin(2\chi)
\end{array}
\right)
\end{equation}

Or alternatively, if Stokes vector is measured and given, then the polarization characteristics of a wave is given as:
$I$, the total power of the measured beam is $I=S_0$,
$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.

Depolarization phenomena is explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.

\subsection{Different Modes of Polarimetric SAR}

\subsubsection{Full Polarimetry and the Polarimetric Signatures}

This section describes the core concept of POLSAR, i.e. the target's polarimetric signature, 
	and illustrates why research into partial polarimetry is warranted.

POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
\begin{equation}
 E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
\end{equation}

Normally, horizontal and vertical linear polarization are used, thus the scattering matrix, i.e. $S$, normally have the following expanded form:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c c}
 S_{HH} & S_{HV} \\
 S_{VH} & S_{VV}
\end{array}
 \right) 
\left( 
\begin{array}{c}
 E_h^{Tx} \\
 E_v^{Tx}
\end{array}
 \right) 
\end{equation}

The scattering matrix can be called the Jones matrix (relating the Jones vector) in the forward scattering alignment.
The matrix is normally called Sinclair matrix in SAR literature, as normally backward scattering alignment are normally used in SAR \cite{Sinclair_1950_ProcsIRE}.
In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.

The matrix can also be "stratified" to define the target scattering vector as: 
\begin{equation}
T_{cv} = \left( 
\begin{array}{c}
 S_{HH} \\
 \sqrt{2} S_{HV} \\
 S_{VV}
\end{array}
 \right) 
\end{equation}
or 
\begin{equation}
T_{ch} = \frac{1}{\sqrt{2}} \left( 
\begin{array}{c}
 S_{HH} + S_{VV}\\
 S_{HH} - S_{VV} \\
 S_{HV}
\end{array}
 \right) 
\end{equation}

Similar to the reason that Stokes vector are preferred to Jones vector in wave polarization, 
	second order statistics of target scattering matrix are normally preferred.
The covariance matrix is defined as:
\begin{equation}
\small{
C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
\left( 
\begin{array}{c c c}
 S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
 \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
 S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
\end{array}
 \right) 
}
\end{equation}
while the coherency matrix is defined as:
\begin{equation}
\small{
C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
\left( 
\begin{array}{c c c}
 (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
 (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
\end{array}
 \right) 
}
\end{equation}

Evidently the two matrices are related:
\begin{equation}
C_h = N C_v N^T
\end{equation}
where
	$N = \frac{1}{\sqrt{2}}
\left( 
\begin{array}{c c c}
 1 & 0		& 1\\
 1 & 0		& -1\\
 0 & \sqrt{2}	& 0
\end{array}
\right)$

The off-diagonal values in both covariance and coherence matrices are normally complex. 
The equivalent all real-valued matrices which carries the same information are called Mueller matrix and Kennaugh matrix which are to be used in forward and backward scattering alignment respectively \cite{Guissard_1994_TGRS}. 
They are defined as the matrix that relates the Stokes matrix of sent and received signals.
\begin{equation}
S_t^{Rx} = K S_t^{Tx}
\end{equation}

Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related and is given by:
\begin{equation}
K = 1/2 Q^* S \otimes S^* Q^{T*}
\end{equation}
where
	$\otimes$ denotes the Kronecker product, and
	$Q = 
\left( 
\begin{array}{c c c c}
 1 & 0 & 0 &  1 \\
 1 & 0 & 0 & -1\\
 0 & 1 & 1 &  0\\
 0 & i & i &  0
\end{array}
\right)$

POLSAR aims to measure target's polarimetric response.
%Depending on the satellite instrument and processing, either Sinclair matrix or Kennaugh matrix elements are provided.
Typically, the radar will separately send different horizontal and vertical polarized waves, and measure the response also in horizontal and vertical polarizations.
The full polarimetric data, will then have four channels, i.e. $\{ S_{HH}, S_{VV}, S_{HV}, S_{VH} \}$. 
The four channel, or quad-pol data, is considered full polarimetric data since it allows one to synthesize the target's response for any given pair of transmitted and received polarization.
Such a process is called polarization synthesis.
The formula is given as:
\begin{equation}
I^{Rx} = 
\left( 
\begin{array}{c }
 1 \\
 \cos(2\chi^{Rx}) \cos(2\Psi^{Rx}) \\
 \cos(2\chi^{Rx}) \sin(2\Psi^{Rx}) \\
 \sin(2\chi^{Rx}) 
\end{array}
\right)^T
K
\left( 
\begin{array}{c }
 1 \\
 \cos(2\chi^{Tx}) \cos(2\Psi^{Tx}) \\
 \cos(2\chi^{Tx}) \sin(2\Psi^{Tx}) \\
 \sin(2\chi^{Tx}) 
\end{array}
\right)
\end{equation}
where $I^{Rx}$ is the intensity of the target's response in a given combination of sent and receive polarizations.

In full polarimetric implementation, normally an alternate pulsing scheme is used to share a single time slot for transmitting two different polarizations' pulses.
In partial polarimetry modes only a single polarization is sent.
Since the transmitting time-slot no longer needs to be shared, a higher frequency become possible which leads to better (almost double) resolution or coverage.
Clearly in such cases only two out of four data channels is available, i.e. either $\{S_{HH},S_{HV}\}$ or $\{S_{VH},S_{VV}\}$.
%The limitation in payload is expected to be around for years to come, with new polarimetric projects being planned by various space agencies.
This trade-off is based on limitations of physics, and hence is expected to be around for years to come.

\subsubsection{The Polarization Basis Transformation}

Assume that the polarization states are known, the wave representation can be given as:
\begin{equation}
\left( 
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right) 
= A_0 e^{-i \phi_0} \left(
\begin{array}{c c}
 \cos(\Psi) & -\sin(\Psi) \\
 \sin(\Psi) & \cos(\Psi)
\end{array}
\right) 
\left(
\begin{array}{c}
 \cos(\chi) \\
 i \sin(\chi)
\end{array}
\right) 
\end{equation}
The representation of a wave, however, depends on the choice of orthogonal reference frame basis.

Consider two different orthogonal basis, $\{ x,y \}$ and $\{ h,v \}$.
A given Jones vector can be measured in both basis as:
$J_{xy}= 
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right) $ and 
$J_{hv}
= \left(
\begin{array}{c}
 \xi_h \\
 \xi_v
\end{array}
\right)$
The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by an unitary transformation matrix $U_2$.
The transformation formula is given as:
\begin{equation}
\left(
\begin{array}{c}
 \xi_x \\
 \xi_y
\end{array}
\right)
= U_2
\left(
\begin{array}{c}
 \xi_h \\
 \xi_v
\end{array}
\right)
\end{equation}

Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
\begin{equation}
U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
\left(
\begin{array}{c c}
 1 & -\rho^* \\
 \rho & 1
\end{array}
\right)
\left(
\begin{array}{c c}
 e^{-i\delta} & 0 \\
 0 & e^{i\delta}
\end{array}
\right)
\end{equation}
where
	$\rho$ is the complex polarisation ratio of the Jones vector for the first new basis, and
	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
	and is required for the determination of the initial phase of the Jones vector in the new reference basis.

In the same vein, Ferro-Famil, 2000 gives
\begin{equation}
U_2 = \left(
\begin{array}{c c}
 \cos(\Psi) & -\sin(\Psi) \\
 \sin(\Psi) & \cos(\Psi)
\end{array}
\right)
\left(
\begin{array}{c c}
 \cos(\chi) & i\sin(\chi) \\
 i\sin(\chi) & \cos(\chi)
\end{array}
\right)
\left(
\begin{array}{c c}
 e^{-i \phi_0} & 0 \\
 0 & e^{i \phi_0}
\end{array}
\right)    
\end{equation}

From these results, it is then possible to derive equations for the transformation of the scattering matrix.
Noting that be definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
and that $J_{xy}^*= U_2 J_{hv}^*$. 
Noting further that $(U_2)^{-1} = (U_2)^T$.
It is then trivial to show that:
\begin{equation}
S_{xy} = U_2 S_{hv} U_2^T
\end{equation}.

Using the result above, we then have:
\begin{equation}
S_{xx} = \frac{1}{1+\rho \rho^*} 
\left( 
S_{HH} e^{-2i\delta} - \rho^* (S_{HV}+S_{VH}) + (\rho^*)^2 S_{VV} e^{2i\delta}
\right)
\end{equation}
\begin{equation}
S_{xy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} + S_{HV} -\rho \rho^* S_{VH} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation}
\begin{equation}
S_{yx} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} - \rho \rho^* S_{HV} + S_{VH} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation}
\begin{equation}
S_{yy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho^2 S_{HH} e^{-2i\delta} + \rho (S_{HV} + S_{VH}) + S_{VV} e^{2i\delta}
\right)
\end{equation}

In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
\begin{equation}
S_{xx} = \frac{1}{1+\rho \rho^*} 
\left( 
S_{HH} e^{-2i\delta} - 2 \rho^* S_{XX} + (\rho^*)^2 S_{VV} e^{2i\delta}
\right)
\end{equation}
\begin{equation}
S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
\left( 
\rho S_{HH} e^{-2i\delta} + (1-\rho \rho^*) S_{XX} - \rho^* S_{VV} e^{2i\delta}
\right)
\end{equation}
\begin{equation}
S_{yy} = \frac{1}{1+\rho \rho^*} 
\left( 
\rho^2 S_{HH} e^{-2i\delta} + 2 \rho S_{XX} +  S_{VV} e^{2i\delta}
\right)
\end{equation}

The results here, together with Stokes Vector's formula, can be used to prove the following identity, which form the basis of our approach:
\begin{equation}
S_t = 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		2 \Re{(S_hS_v^*)} \\
		2 \Im{(S_hS_v^*)}
	\end{array}
\right)
= 
\left(
	\begin{array} {c}
		S_hS_h + S_vS_v \\
		S_hS_h - S_vS_v \\
		S_+S_+ - S_-S_- \\
		S_lS_l - S_rS_r
	\end{array}
\right)
\end{equation}
where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.

%The transformation from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ as well as from $\{h,v\}$ to circular basis $\{l,r\}$ are special cases of the above formula.
%Ignoring the determination of initial phases, we have: 
%	the measured signal at $\pi/4$ linear polarizer / projection as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
%	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
%	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
%	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
%
%The Stokes vectors, when aligned at these transformed projections are given by the following well-known equations
%\begin{equation}
%S_t = \left(
%\begin{array}{c}
% |\xi_h|^2 + |\xi_v|^2 \\
% |\xi_h|^2 - |\xi_v|^2 \\
% 2 \Re( \xi_h \xi_v^* ) \\
% 2 \Im( \xi_h \xi_v^* ) 
%\end{array}
%\right)
%= \left(
%\begin{array}{c}
% |\xi_+|^2 + |\xi_-|^2 \\
% -2 \Re( \xi_+^* \xi_- ) \\
% |\xi_+|^2 - |\xi_-|^2 \\
% 2 \Im( \xi_+^* \xi_- ) 
%\end{array}
%\right)
%= \left(
%\begin{array}{c}
% |\xi_l|^2 + |\xi_r|^2 \\
% 2 \Re( \xi_l^* \xi_r ) \\
% -2 \Im( \xi_l^* \xi_r ) \\ 
% |\xi_l|^2 - |\xi_r|^2 
%\end{array}
%\right)  
%\end{equation}

\subsubsection{ Partial Polarimetry and the traditional SAR}

The dual-polarization modes has been practically and operationally available for quite some time.
However, partial polarimetry has only recently been investigated in the scientific community. 
By comparison, 
	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
	while full polarimetry measures the same response for two (most of the time orthogonal) polarisation channels.
Mathematically, the process is modelled as:
\begin{equation}
 \left( 
\begin{array}{c}
 E_h^{Rx} \\
 E_v^{Rx}
\end{array}
 \right) = \frac{e^{ikr}}{r} 
\left( 
\begin{array}{c}
 S_{H} \\
 S_{V}
\end{array}
 \right) E^{Tx}
\end{equation}

Souyris \cite{Souyris_2005_TGRS} pioneered the field with his paper on compact polarimetry.
Compact polarimetry is essentially a partial polarimetry mode in which the incoming pulse is of linear polarization, 
	but is neither of the usual horizontal nor vertical angle.
%	rather it is of an odd angle of 
Instead its incoming polarization of linear polarisation with an odd angle of $\pi/4$.
%The $\pi/4$ mode has not been implemented in real-hardware, but only been simulated using polarization basis change principles.
The partial polarimetric covariance matrix then is given as
\begin{equation}
J = 
\left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
\end{array}
\right)
\end{equation}

Raney \cite{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
The important parameter to choose is the use of which polarisation for the incoming pulse.
His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
The partial covariance matrix then become:
\begin{equation}
J = \frac{1}{2} \left(	
\begin{array}{c c}
	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
\end{array}
\right)
\end{equation}

The benefits of this hybrid architecture, according to Raney being:
	this partial polarimetric measurements can measures certain physical polarimetric phenomena like odd and even bounce phenomena.
The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
\begin{equation}
\Gamma_{tri} = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right)
\end{equation}
Then the response will be reversed as it can be calculated as:
\begin{equation}
J_r = \left(
\begin{array}{c c}
1 & 0 \\
0 & -1
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
i
\end{array}
\right) 
\end{equation}
with
	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.

For a dihedral target, whose main axis at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
\begin{equation}
\Gamma_{dih} = 
\left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right)
\end{equation}
The even bounce phenomena is detectable as its polarimetric response is then:
\begin{equation}
J_r = \left(
\begin{array}{c c}
\cos(2\theta) & \sin(2\theta) \\
\sin(2\theta) & \cos(2\theta)
\end{array}
\right) \cdot
\left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) = \left(
\begin{array}{c}
1 \\
-i
\end{array}
\right) 
\end{equation}
In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conviniences to hardware calibration.
Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrate the classification power of hybrid polarimetry.
Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
Notably, the hybrid architectural concepts has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.

The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformation described above.
Hardware realisation may not be needed until the final physical prototype stages.
This methodology has been demonstrated and is widely used in the community.
We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
The focus into partial polarimetry allow analysis into a smaller matrix, while its implication can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
Besides that, a number of research questions in this new field are still open, relevant and exciting.

Souyris, in 2005, published a paper \cite{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
The algorithm is claimed to work on natural surfaces.
In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
Chapter 3 reviews of this sub-topic further and introduces our work on expanding the reconstruction to urban man-made structures and surfaces.

For the tasks of target detection and classification, we believe that partial dual polarization provides a unique offer.
Compared with single-channel, dual channel provide extra polarimetric information. 
Compared with full polarimetric data, the better spatial resolution could makes up for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.

In fact, this project is intended to provide help for a new project at EADS Innovation Works Singapore to investigate the use of polarimertic data in ship monitoring over the oceans.
It is hypothesized that using polarimetric information would improve the possibilities of detecting ships travelling in the open seas.
Evidently partial polarimetric modes are good candidates for better detection rates.

The scientific application of POLSAR include: 
	oil slick detection \cite{Nunziata_2009_IGARSS, Gambardella_2007_ESASP}, 
	ship monitoring \cite{Kozai_2004_OCEANS}, 
	sea ice monitoring \cite{Wakabayashi_2004_TGRS, Nakamura_2005_IGARSS}, 
	volcano lava-flow monitoring \cite{Dierking_1998_IGARSS}, 
	agricultural crop monitoring \cite{Bouvet_2009_TGRS, Hajnsek_2008_IGARSS}, 
	planetary exploration \cite{Rosenbush_2009_JQuantSpecRadTransfer} 
	and other surface parameter estimations \cite{TruongLoi_2009_TGRS, Touzi_2009_TGRS, Hajnsek_Thesis_2001}. 
The remaining text of this chapter briefly look at recent literature in the context of ship detection and monitoring.
The topic of ship detection and monitoring has already been tackled quite extensively for single channel SAR data \cite{Tello_2005_IGARSS, Tello_2006_ISPRSJPhotogrammetryRemoteSensing}.
In fact, a number of countries have reported to implement such systems, and some uses them in everyday operations.
The countries includes: USA \cite{Montgomery_1998_IGARSS}, Canada \cite{Vachon_2000_JHUApplPhysics}, France \cite{Losekoot_2005_IGARSS}, Norway \cite{weydahl_2007_RemoteSenseGISGeology} and Spain \cite{Margarit_2009_RemoteSensing}.
The common scenarios in use are normally: 
	a designated area is continuously monitored through the use of some automatic ship detection algorithm.
If an unknown ship is detected, some manual intervention is to be applied, normally in the form of a navy ship being sent to further investigate.
The reports however did not elaborate about the accuracy of the detection algorithms.

A recent trend that is reported in the literature is the use of AIS (Automatic Identification System).
In 2007, Vachon \cite{Vachon_2007_IGARSS} reported his study in Canada, which aimed to match ships detectable in SAR images with AIS reported locations.
In 2009, Grasso \cite{Grasso_2009_ISDA} evaluated the performance of ship detection algorithms using AIS as ground truth.
In our planned approach, we are prepared to study the performance improvement through using partial polarimetry data in comparison to normal single-channel SAR approaches.
Ground truth for such study will also be using synchronized AIS data.

\section{The Stochastics and Multivariate Nature of (POL)SAR data}

%\subsection{The Stochastics Nature of SAR and POLSAR}
\subsection{The Stochastic nature of SAR  and SAR speckle filtering }

This section starts with a description of the stochastic nature of SAR data. 
SAR speckle filtering is then reviewed within a statistical estimation theory framework. 
Various different approaches to SAR speckle filtering are reviewed, 
	ranging from Generalized Least Squared Error algorithms
	%ranging from a discrete cartoon like algorithm 
	to the more convoluted Maximum A Posteriori (MAP) approaches.
	%to recent more continous multi-resolution wavelet or partial differental equations based algorithms.

Although speckle has been extensively studied for decades, speckle reduction remains one of the major issue in SAR imaging process. 
Many reconstruction filters have been proposed and they can be classified into two main categories: 
	minimum mean-square error (MMSE) de-speckling using the speckle model; 
	and maximum a posteriori (MAP) de-speckling using the product model. 
%The famous Lee, Kuan, and Frost ﬁlters in the ﬁrst category provide MMSE reconstructions based on measured local statistics.
%In the second category, diﬀerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.

In the first category the speckle random process is assumed to be stationary over the whole image. 
Then speckle models are proposed, the multiplicative speckle model is first approximated by a linear model, then a speckle reduction filter is formulated
The formula is as follows: 
\begin{equation}
\hat{R}(t) = I(t) \cdot W(t) + \bar{I}(t) \cdot (1 - W(t)) 
\end{equation}
where
	$\hat{R}(t)$ is the filter response,
	$I(t)$ is the intensity at the center of the moving window,
	$\bar{I}(t)$ is the averaged intensity for the whole processing window,
	$W(t)$ is the weight function,

For the Lee filter \cite{Lee_PAMI_1980}, the weight function is proposed to be:
\begin{equation}
W(t) = 1 - \frac{C_u^2}{C_I^2} 
\end{equation}
where
	$C_u$ is the variational coefficient of noise, i.e. $C_u=std(u)/avg(u)$, and
	$C_I$ is the variational coefficient of the true image, i.e. $C_I=std(I)/avg(I)$.

In the approach of the Kuan filter \cite{Kuan_1985_PAMI}, the multiplicative speckle model is first transformed into a single-dependent additive noise model, and then the MMSE criterion is applied. 
The speckle filter has the same form as the Lee filter but with a different weighting function 
\begin{equation}
W(t) = \frac{1 - \frac{C_u^2}{C_I^2} }{1+ C_u^2} 
\end{equation} 
The Kuan filter takes into account the dependency of noise into signal. 
In the special case of noise being independent of the underlying signal, the Kuan filter would be exactly the same as the Lee filter.
From this point of view, it can be considered to be superior to the Lee filter.

The Frost filter \cite{Frost_PAMI_1982} is different from the Lee and Kuan filters with respect that the scene reflectivity is estimated by convolving the observed image with the impulse response of the SAR system. 
The impulse response of the SAR system is obtained by minimizing the mean square error between the observed image and the scene reflectivity model which is assumed to be an autoregressive process. 
The filter impulse response can, after some simplification, be written as:
\begin{equation}
H(t) = K_1 e^{-K_2 C_I^2(t)}
\end{equation}
where
	$K_1$ is some normalizing coefficient to allow preservation of signal mean values,
	$K_2$ is a user chosen filter parameter.

As can be seen from all the three most recognized algorithms in this field, they share the same principles:
When the variation coefficient $C_I$ is small, the filter behaves like an low pass filter smoothing out the speckles. 
When $C_I$ is large, it has a tendency to preserve the original observed image.
The choice of functions relating speckle suppression power to local variations may be different, 
	the weighted average as well as the weighted least square principles are apparently common.

As discussed at length in Chapter 4, SAR data is heteroskedastic.
Our literature search yielded only a single article \cite{Amirmazlaghani_2009_TIP} tackling SAR data's heteroskedastic feature, suggesting a lack of appropriate attention within the research community about such characteristic and its effects.
%However, the community appears to be oblivious of the fact, evidenced by the fact that we could only find very few researcher \cite{Amirmazlaghani_2009_TIP} tackling heteroskedasticity in SAR data
Under such conditions, Ordinary Least Square methods may not provide optimal results \cite{Woods_PAMI_1984}. 
In fact as is shown by the mathematical formula above, weighted average formula were being used.
This is consistent with the knowledge that, when variance of heteroskedastic data is available, weighted least squares is an optimal estimator.
As is a fact in SAR data, this variance however is not available directly and can only be estimated (note the concept of variation coefficient).
Our analysis then shows that estimating variance is as hard as estimating the un-speckled signal itself!
We believe that log transformation could help to break through this circle of ambiguity.

In the second approach, the filters assume that speckle is not stationary globally but is only stationary locally within the moving processing window.
The filters operate based on MAP principle, which is given as:
\begin{equation}
f(x|z) = \frac{f(z|x) f(x)}{f(z)}
\end{equation}
where
	$x$ is the underlying signal that need to be estimated, and
	$z$ is the observed signal.
The underlying signal is found by
\begin{equation}
x = argmax \{ \log(f(z|x)) + \log(f(x))  \} 
\end{equation}

As evidenced, these classes of filter require the knowledge of the \textit{a-priori} PDF $f(x)$. 
Various PDFs for the underlying back-scattering coefficient have been assumed.

In case Normal distribution is assumed \cite{Medeiros_1998_IAI}
\begin{equation}
f(x) = \frac{1}{\sigma_x \sqrt{2 \pi} } e^{\frac{1}{2} \left( \frac{x-\mu}{\sigma_x} \right)^2 }
\end{equation}
the underlying signal is found by solving the equation
\begin{equation}
x^4 \Gamma^2(N) - x^3 \Gamma^2(N) \mu_x + x^2 \Gamma^2(N) 2N \sigma^2_x - 2 \sigma^2_x z^2 \Gamma^2(N+1/2) = 0
\end{equation}

In the case of Gamma distribution is assumed \cite{Lopes_1990_IGARSS} 
\begin{equation}
f(x) = \frac{\sigma_x}{\Gamma(\lambda)} (x \sigma_x )^{\lambda-1} e^{-x \sigma_x}
\end{equation}
For $\lambda=1$, the Gamma distribution is identical to the exponential distribution. 
For $\lambda=n/2$ and $\sigma=1/2$ Gamma distribution is equivalent to the chi-square distribution.
The underlying signal is found by solving the equation:
\begin{equation}
x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) (2N - \lambda + 1) - 2 z^2 \Gamma^2(N+1/2) = 0
\end{equation}

In case exponential distribution is assumed 
\begin{equation}
 f(x) = \sigma_x e^{-x \sigma_x}
\end{equation}
then the underlying signal is found by solving the equations
\begin{equation}
 x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) 2N - 2 z^2 \Gamma^2(N+1/2) = 0
\end{equation}

In case Chi square distribution is assumed 
\begin{equation}
 f(x)=\frac{1}{2^{n/2} \Gamma(n/2)} x^{n/2-1} e^{(-x/2)}
\end{equation}
then the true signal is found by solving the equation
\begin{equation}
 x^3 \Gamma^2(N) + x^2 \Gamma^2(N) (4N-n+2) - 4 z^2 \Gamma^2(N+1/2) = 0
\end{equation}

If log-normal distribution is assumed \cite{Medeiros_2003_IntJRemoteSens}
\begin{equation}
 f(x) = \frac{1}{\sigma_x \sqrt{2 \pi}} x^{-1} e^{\frac{-1}{2 \sigma_x} (\ln(x) - \mu_x)^2}
\end{equation}
\begin{equation}
 x^2 \Gamma^2(N) (-2N \sigma^2_x - \sigma^2_x -\log(x) + \mu_x) + 2 z^2 \Gamma^2(N+1/2)=0
\end{equation}
%Some of them being: Gaussian PDF, Gamma PDF, chi square, Rayleigh, beta, log-normal ...

%Clearly should such PDF being estimatable from the data it-self, that would potentially presents an good opportunity for this class of speckle filters.
Other distributions that has been assumed include: heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation} \dots 
Evidently, the performance of these filters are dependent on the underlying distribution of the back-scattering coefficient on the particular surface being imaged. 
In this context, the community appears to focus on using Bayesian inference to choose the most suitable distributions \cite{Walessa_2000_TGRS}.
We hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in log-transformed domain.

Other approaches, that recently has been actively pursuit in the community include: 
	%recently there has been an increase publications about the applicability of 
	wavelet \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
	curvelet \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
	contourlet \cite{Foucher_2006_IGARSS}, 
	ridgelet \cite{Saevarsson_2004_IGARSS},
	fuzzy logic \cite{Cheng_ETCS_2009}, 
	anisotropic kernels \cite{DHondt_2006_TGRS}, 
	and autoregressive conditional heteroskedasticity \cite{Amirmazlaghani_2009_DSPWorkshop}. %techniques into SAR filtering.
Central to wavelet techniques is the discoveries of a consistent and optimal choice for the wavelet coefficients.
Similarly the development of kernel methods depends strongly on the discoveries of consistent predictive kernels.
Evidently the choice of such coefficients are dependent on the underlying statistical characteristics of SAR signals.
This further emphasizes the importance of investigating consistent statistical properties of SAR signals.
Note only that statistical analysis is important in speckle filtering, the technique is also important in the development of information extraction \cite{Oliver_1991_JPhysDApplPhys}, target detection \cite{Luttrell_1986_JPhysDApplPhys}, classification \cite{Nyoungui_2002_IntlJRemoteSense} techniques.

With different speckle filtering approaches presented, it is crucial to have a framework for 
	(a) modelling and simulation which provide the ground-truth data in different scenarios of underlying distribution, and
	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.

\subsection{The Multivariate Nature and The Observables in POLSAR data}

\section{Current methods in SAR and POLSAR speckle filtering}

\subsection{Current Statistical Models for SAR and POLSAR data}

\subsection{Current Methods for SAR speckle filtering}
(2.2.1)

\subsection{Current Methods for POLSAR speckle filtering }

Compared to SAR technologies, most POLSAR techniques have only recently been developed. 
The state of POLSAR speckle filtering is reviewed and filtering the covariance matrix off-diagonal elements is shown to be an open problem.
The problem can be traced back to the lack of a statistical model for the covariance matrix in polarimetry.
%This has the consequences that very few methodologies to statistically simulate POLSAR is porposed in literature and validations for such proposals are pretty primatives.
%is the application of such framework is shown to be beneficial academically.

In the first systems that captured POLSAR data, multi-look processing was used as a method of choice for speckle filtering, at the cost of spatial resolution.
Novak \cite{Novak_1990_TAES} pioneered the area of speckle reduction and proposed the polarimetric whitening filter (PWF) to produce a single speckle reduced intensity image. 
The disadvantages of PWF filter is that the polarimetric information is not well-preserved.
Multi-look processing's polarimetric result also exhibits bias and distortion \cite{Lee_2008_TGRS}.

Lee \cite{Lee_1991_TGRS} proposed a new filtering algorithm which does suppress speckle for the diagonal elements, the off-diagonal elements however remain un-filtered.
Later, Touzi \cite{Touzi_1994_TGRS} drew out the principles of speckle filtering of POLSAR data. 
They are
\begin{enumerate}
	\item Speckle can be filtered if ALL elements of its covariance matrix are filtered.
	\item Single-channel SAR speckle filtering is only applicable to diagonal elements of the covariance matrix
	\item Speckle filtering need to be performed also on off-diagonal elements, as correlation among the elements need to be exploited and the elements do not exists independently.
\end{enumerate}

In 1999, Lee \cite{Lee_1999_TGRS} extended his refined-Lee filters on POLSAR data, and argues that all covariance matrix elements should be filtered by the same amount to preserve polarimetric properties. 
He then proposed to apply the weighted averaging on the full covariance matrix instead of single-channel intensities values. 
\begin{equation}
C_{out} = C_{avg} + w (C_{curr} - C_{avg})
\end{equation}
where
	$C_{out}$ is the filtered covariance matrix output,
	$C_{avg}$ is the average covariance matrix using an edge-aligned window,
	$C_{curr}$ is the covariance matrix of the current processing pixel.
The weight $w$ is computed within the edge aligned window from the total power image $y$ as:
\begin{equation}
w = \frac{\sigma^2_y - \mu^2_y \sigma^2_v}{\sigma^2_y - \sigma^2_y \sigma^2_n}
\end{equation}
where 
	$\sigma^2_y$ and $\mu_y$ are the variance and mean computed within the edge aligned window, respectively,
	$\sigma^2_n$ is the user specified noise variance.

Further attempts has been made towards statistical modelling the off-diagonal elements but the applications of these results towards the problem of speckle suppression for off-diagonal element have been non-conclusive.
Based on his 2003 paper \cite{Lopez_2003_TGRS} on POLSAR statistical analysis, in 2008, Martinez \cite{Lopez_2008_TGRS} proposed a model based polarimetric filter.
He first proposed to model $S_hS_v^*$ as having both additive and multiplicative components. 
\begin{equation}
S_pS_q^* = \psi |\rho | e^{i \theta} + \psi \bar{z}_n N_c (1-n_m) e^{i \theta} + \psi (n_{ar} + i n_{ai}) 
\end{equation}
where
	$\psi = \sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }$ represents the average joint power in the two channels, 
	$\rho = |\rho| e^{i \theta} = \frac{E \left( S_pS_q^* \right)}{ \sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) } }$ is the complex correlation coefficient that characterize the correlation among the channels,
	$N_c = \frac{\pi}{4} |\rho| F_{1,2} ( 1/2,1/2,2,|\rho|^2 )$ basically contains the same information as the complex correlation coefficient, and 
	$F_{1,2} ( a,b,c,d )$ is the Gauss hyper-geometric function,
	$n_m$ is the first speckle noise component that is multiplicative with $E(n_m)=1$ and $var(n_m)=1$,
	$n_{ar} + i n_{ai}$ is the second additive speckle noise component with $E(n_{ar}) = E(n_{ai}) = 0$ and $var(n_{ar}) = var(n_{ai}) = \frac{1}{2} (1-|\rho|^2)^{1.32}$.
The model is overly complicated and to do speckle filtering, various approximations has to be used.

In 2009, Lee \cite{Lee_CRCPress_2009} proposed to model $S_hS_v^*$ in a different approach.
The phase difference is defined as:
\begin{equation}
\phi = \arg{ \left( S_pS_q^* \right) }
\end{equation}
Lee gives the PDF for the phase difference as:
\begin{equation}
pdf(\phi) = \frac{\Gamma(3/2) (1-|\rho|^2) \beta}{2 \sqrt{\pi} \Gamma(1) (1-\beta^2)} + \frac{(1-|\rho|^2)}{2 \pi} F_{1,2}(1,1,1/2,\beta^2)
\end{equation}
with
	$\beta = |\rho| cos(\phi-\theta)$ and
	$F_{1,2} ( a,b,c,d )$ is the Gauss hyper-geometric function.

The normalized magnitude which is defined as
\begin{equation}
\xi = \frac{E \left( S_pS_q^* \right)}{\sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }}
\end{equation}
and the PDF is given as
\begin{equation}
pdf(\xi) = \frac{4\xi}{\Gamma(1)(1-|\rho|^2)} I_0 \left( \frac{2 |\rho| \xi}{1-|\rho|^2} \right) K_0 \left(  \frac{2 \xi}{1-|\rho|^2} \right)
\end{equation}
with
	$I_0$ and $K_0$ are modified Bessel functions.
Again the equations looks overwhelmingly complex, and as admitted by the authors themselves:
	this do not allow for easy speckle filtering as the model is too complex and 
	the complex correlation coefficient $\rho$ is not easy to be estimated \cite{Lee_CRCPress_2009}

There are several other attempts to filter POLSAR data.
Vasile, 2006 proposed to region growing adaptive neighborhood approach, where averaging is performed on an adaptive homogenous neighbor.
The draw back of the approach is that only the intensity was used to determine homogeneity and primitivev averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
%J.S. Lee is also very active in POLSAR speckle filtering.
In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogenous pixels based on their underlying scattering model. 
While the work is interesting, it is believed that pixels having similar underlying model, says volume scattering, can still be of very different nature.
Similar to Lee's previous work, simple weighted average filtering is applied on both diagonal and off-diagonal elements.
Vasile, 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
While polarimetric information is estimated independently from the power span, its output results no longer follow established Wishart distribution.

%In summary, it is evident that further research into designing speckle filters for POLSAR data, especially for off-diagonal elements is warranted. 
%We will discuss our approach in the next section.
In summary, while off-diagonal elements, which carries phase information, is important in intepreting POLSAR data \cite{Rodionova_2009_ESASP}, their estimation and filtering is under-developed.
We will discuss our approach based on polarization basis transformation in the next section.

%\subsection{ Simulating Compact Polarimetry data and the reconstruction of POLSAR signature }

%\subsection{ Target Detection and Classification using SAR-based images }

\subsection{Current Methods to Evaluate (POL)SAR Speckle Filters}

It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
	homogeneous and heterogeneous region evaluation.
Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
	output (a.k.a the speckle suppression power).
In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
	due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
	to be measured and compared.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
Furthermore, the application of any speckle filter in a SAR processing framework
   should enable an improvement in the measurement, 
	detection or classification of the underlying radiometric features.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
	preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
	and variance error of the output.
As the MSE evaluation is a combination of bias and variance error, it is therefore capable of evaluating 
	the general requirements of speckle filtering.

For homogeneous scenes where the underlying radiometry is assumed to be constant, 
	the filtered results are considered, statistically speaking, to be samples of 
	a single but complex stochastic process.
From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
	of speckle filters can be judged using the familiar bias and variance evaluation.

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent criteria for evaluation could be performed by a simple subtraction.
In other words, it is clear that the bias evaluation in the log-transformed domain 
	can be used to evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters preserve
	not only the expected radiometric values
	but also a number of subtractive and consistent measures of distance exhibited in the log-transformed domain.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is mathematically related to variance in the 
	log-transformed domain.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
	which is the primary criteria used to evaluate speckle filters over homogeneous area.

Real-life and practical images, however, are not homogeneous.
Thus there are a number of associated difficulties in evaluating speckle filters over heterogeneous scenes.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparison. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
	real-life images.
And hence, the need for speckle filters estimation is warranted.

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise solely of
    the noise being removed (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
However, when displaying such images for visual evaluation, the ratios that are smaller than unity are much 
harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}. 
We therefore propose to adopt a log-transformed domain perspective 
  where the multiplicative noise would then be transformed into a more familiar additive model.
More importantly, the ratio image would then become a simple subtraction image.
The evaluation methodology for such adoption would not change. 
Only that the residual image would become linear and additive.
And thus it would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; examples of those that have been used are the 
	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
	and edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
of these methodologies.
This is because feature extraction algorithms are only approximations,
	whose accuracy is not only dependent upon the characteristics of the original image 
		but also heavily affected by 
		the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
	how to interpret the results, especially its accuracy.

Since SAR statistical models are quite well understood, 
	simulation experiments with known ground-truth can be employed 
		to evaluate speckle filters.
In this paper, we also make use of a methodology similar to the ones discussed above with two important changes.
Firstly, our simulated experiments offer absolute ground-truth.
Secondly, our threshold-based feature extraction algorithm is extremely simple.
More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
This performance can be 
	conveniently visualized by plotting the Receiver Operating Characteristics Curve (ROC).   
It can also be objectively quantified by measuring the Area Under this Curve (AUC). 
As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
	feature preservation capabilities for different speckle filters.

%There are two main ways that ground truths are used in evaluating speckle filters.
%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
%Normally the image is large, with a number of different features and test conducted in once. 
%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
%
%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
%Since the structure is repeated many times, the combined results become more representative. Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
%The drawback is that only a single type of target can be tested per image. These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
	normally at local or regional levels.
In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
	is likely to perform poorly in terms of preserving underlying radiometric differences 
	(e.g. causing excessive blurring).
Furthermore, we have not found many published articles combining the evaluation
  of these two seemingly contradicting requirements.

Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
	subjective in nature.

%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
%	where $E()$ denotes expectation operator.

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
	the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

%Thus we propose the use of MSE in the homoskedastic log-transformed domain to evaluate eps. 
%This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean). We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss-Markov theorem becomes applicable in this transformed domain, 
	the use of MSE is shown to be again relevant for evaluating statistical estimators (i.e. speckle filters).
Intuitively, each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is presented and discussed, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

\section{Existing Measures of Distance for (POL)SAR data and their applications}

to detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
  which have $L_x$ and $L_y$ as the corresponding number of looks,
  come from the same underlying stochastic process,
Conradsen considered \cite{Conradsen_2003_TGRS_4} the following POLSAR statistics
\begin{equation}
  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
\end{equation}

Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then we have
\begin{eqnarray}
  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
\end{eqnarray}

Since both $Z_x$ and $Z_y$ follow complex wishart distribution with $L_x$ and $L_y$ degrees of freedom,
  $Z_x+Z_y$ also follows the complex wishart distribution with $L_x + L_y$ degrees of freedom.
In view of the models denoted in Eqn. \ref{eqn:log_determinant_distribution},
  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
  but the whole statistical distribution for it can be simulated as well:
\begin{eqnarray}
%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
  \ln{Q} &\sim&  q + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
  Q &\sim& e^q \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
\end{eqnarray}
where $q = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.

In the special case of $L_x = L_y$, the Conradsen statistics become
$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
%Our approach suggest a slightly simpler statistics which probably will work just as well: the contrast
The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should, under exactly the same assumptions, provides another consistent and equivalent approach,
  with probably simpler conceptual model and computational derivations. 
%a slightly simpler statistics.
The details application of this in edge-detection however is outside the scope of this paper.

\section{The need for Scalar Consistent Measures of Distance}
	We will show our originality and significance here!

This section surveys recent developments in the research landscape. 
First, the stochastic nature of SAR speckle phenomena is explained. 
Then, the topic of SAR speckle is reviewed from the perspective of statistical estimation theory. 
An opportunity for contribution in proposing a stochastic simulation and evaluation framework is identified. 
Next, the applications of such a framework into the problem of POLSAR speckle filtering is described. 
Recently, the practicality of Partial Polarimetry has been noticed and studied. 
The need for reconstruction of Full Polarimetric signatures is highlighted and the possible application of the proposed framework is described. 
Last but not least will be an illustration on the applicability of such a framework to the topic of target detection and classification.

%\subsection{POLSAR speckle filter}

	%\section{The Need for Scalar Consistent Measures of Distance}

	%\section{Research Framework: Originality and Significance}

### 2013-03-01 3/sar.tex
201303_Mar01

\chapter{Consistent Measures of Distance for Univariate SAR Data} %chapter 3
\label{chap:sar}

%\section{SAR speckle statistic model}
%\label{sec:heteroskdastic_model}

Useful and robust statistical estimators require un-assuming models. 
In this chapter a homoskedastic model for the usually heteroskedastic SAR is proposed. %speckle filtering.
In the first section the heteroskedastic nature of original amplitude and intensity SAR data will be explained. 
Relying solely on statistical principles,
  log-transformed SAR data is shown to be homoskedastic.
Together with the consistent sense of variance, a few consistent measures of distance are proposed for the traditional SAR data.

\section{Original Heteroskedastic Model of SAR data}

SAR speckle phenomena are explained as the interference of many coherent but dephased back-scaterring components;
  each reflecting from different and distributed elementary scaterers \citep{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
The random nature of the SAR data arises
  due to the unknown and varying location, height and thus distance of each elementary scaterer;
  which, in turn, generates random phases in their back-scattering responses.
Assuming the number of these elementary back scatterers is sufficiently large,
  then the Central Limit Theorem is applicable \citep{Goodman_Springer_1975}.
Consequently the interference of these randomly phased responses can be considered as
  a random walk on the 2D complex plane \citep{Goodman_JOptSocAm_76}.  
Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \citep{Lee_CRCPress_2009}. 
Their probability density functions (PDF) are given as:

\begin{equation}
\label{eqn:SAR Real and Imaginary Components PDF}
\caption{eqn:SAR Real and Imaginary Components PDF}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It can then be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution
  and subsequently the SAR intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of a negative exponentially distributed random process.
That is:

\begin{eqnarray}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
\end{eqnarray}

From a statistical viewpoint, the multiplicative nature of amplitude and intensity data can be explained as follows. 
Let us consider two fixed, independent to $\sigma$ unit distributions given below:

\begin{eqnarray}
pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
pdf(I_1) &=& e^{ \left( -I_1 \right) }
\end{eqnarray}

Using the variable change theorem,
%  it is then trivial to show that:
    it can be shown that:
    the SAR amplitude and intensity are equal to %are simply
    a scaled version of these unit variables,
    specifically $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a mutiplicative nature. 
In fact, the condition has long been noted,
  but from different perspectives,
  in various proposed SAR models (e.g. \cite{Jakeman_1980_JPhysAMathGen}).

Let us now consder the population expected mean and variance of the four distributions.
They are given in Table \ref{tbl:orginal_sar_avg_var}. 
If spatial homogeneity is defined as an imaging areas having the same back-scattering coefficient $\sigma$,
  then over a homogeneous scene, the measured values can then be considered as samples coming from a single stochastic process.
However, over heterogeneous areas where $\sigma$ varies significantly,
  it is then evidently clear that: the amplitude ($A$) as well as the intensity ($I$) of SAR data suffer from hetoroskedastic phenomena,
  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean. 
In the context of speckle filtering which aims to estimate the unknown parameter $\sigma$,
  Table \ref{tbl:orginal_sar_avg_var} also clearly indicates the ambiguous circle.
That is, in the original domain, estimating variance is equal to estimating the mean
  and is as hard as the main problem itself.
  %, i.e. estimating the unknown parameter $\sigma$

\begin{table}[!h]
\normalsize
\centering
\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = \frac{ \sqrt{\pi}}{2}$ & $var(A_1) = \frac{(4-\pi)}{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ & $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline
\end{tabular}
\caption{ Mean and Variance of Original SAR data }
\label{tbl:orginal_sar_avg_var}
\end{table}

The formulas above have long been noted in this research field. 
In fact while pioneering the estimation of the equivalent number of look (ENL) index, 
 it has been noted that the ratio of expected standard deviation to mean is a constant in both cases (i.e. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$) \cite{Lee_1992_IMA_298}.
Here we just offer a different perspective,
  one that avoids the negative effects of heteroskedasticity in SAR data processing.
%Here, we just offer a different interpretation, which sets the stage for the discussion of logarithmic transformation.

\section{The Effects of Heteroskedasticity in SAR Data Processing}

%\subsection{Statistical Heteroskedasticity of SAR data}

The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously. 
Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily \cite{Lee_TGRS_2009}. 
%That is because
And while the statistical model within individual resolution cells is well established,
  the applicability of these models, however, are restricted to homogeneous areas. 
Practical images, nevertheless, are heterogeneous. 
Crucially it is this spatial variation that is of high interest. 
This fact gives rise to the question that seemed obvious:
  %how to call an analysis area heterogeneous and subsequently
  what to do in the case of heterogeneity.

Various statistical models for heterogeneous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
Unfortunately, while most of the models highlight the multiplicative nature of sub-pixel or homogeneous original SAR data, in extending the model to heterogeneous images, virtually none has noted that spatial variation also gives rise to heteroskedasticity phenomena. 
Heteroskedasticity, as explained later, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean or equivalently its underlying back-scattering coefficient $(\sigma)$.

Speckle filtering, by and large, are estimators attempting to estimate the unknown coefficient $\sigma$ from the observable SAR signal $(A)$. 
Thus, SAR speckle-filtering can be and has been positioned within the context of estimation theory \cite{Touzi_2002_TGRS}. 
The statistical framework attempts to estimate unknown statistical parameters from the observable data. 
The stages consist of statistical modelling, estimator development and evaluating the performance of the statistical estimators. 
%In this section, the negative effects of heteroskedasticity on speckle filtering is analysed.
It is believed that heteroskedasticity, in its turn, give rise to serious negative impacts on various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences in the central question of homogeneity or heterogeneity. 
In optical images, the contrast or variance among neighboring pixels have been used to measure homogeneity. 
Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
In SAR images, both of these measures are dependent on the underlying signal $(\sigma)$. 
This make the problem of estimating variance equal to the problem of estimating the mean and is the same as the main problem: estimating $\sigma$. 
The fact give rise to the ambiguity circle in SAR speckle filtering.

A case in point can be found in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
The technique determines outlying points as being too far away from the standard deviation. 
However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of the mean is required and used. 
It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter \cite{Lee_PAMI_1980}.

Heteroskedasticity also poses numerous challenges in designing an efficient estimator. Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt. 
If the variance is known \textit{a priori}, it has been proven \cite{Aitken_1934_ProcsRoyalSocEdinburg}, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations. 
The caveat however is that in SAR speckle filtering, variance is not known \textit{a priori}. 
And even though variance can be estimated from observable values, as the ambiguity circle goes, estimating the variance is as hard as estimating the underlying coefficient $\sigma$ itself.

Heteroskedasticity also affects the performance evaluation stage of such a framework.
Statistical estimators are routinely evaluated using their bias and variance performance,
  which when combined normally results in MSE evaluation.
Unfortunately, under heteroskedastic conditions, Least Squared Error estimation may not be optimal.   
In other words, Minimal Squared Error can no longer serves as a reliable evaluation metric.
A number of different evaluation metrics have been proposed for SAR speckle filters,
  however, none have appeared capable of taking on the MSE's previous role.

%Heteroskedasticity also decrease the effectiveness of estimators by increasing the variance of even the best possible estimations. 
%This fact makes it tricky to evaluate the performance of different estimators, even if quantitative experimental results are reported.
%In fact several quantitative simulated experiments has been carried out to compare the performance of different estimators\cite{Lee_TGRS_2009}. 
%However only results of single experiments were reported. 
%Due to the stochastic nature of the simulated experiment process, more experiments should be done to report the effectiveness, i.e. variance, of each estimators' results.

Last but certainly not least, is the bad impact of heteroskedasticity on SAR image interpretation. 
Most of the task to be carried out in interpreting SAR images almost invariably involve target detection, target segmentation and/or target classification. 
All of these tasks require good discriminant functions. 
Foundational to all of these is the need for a consistence sense of distance. 
Unfortunately, by definition, heteroskedasticity provides inconsistent measures of distance. 
This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to have caused a large class of artificial neural networks as well as a number of other computational intelligence methods to under-perform on SAR data.

%In our work, we aim to neutralize these various negative impacts. 
%The paper is organized as follows. 
%Section \ref{sec:heteroskdastic_model} will be devoted to discussion of the heteroskedastic phenomena in the original per-pixel SAR amplitude and intensity model. 
%Logarithmic transformation is extended to the model and the homoskedastic property of it is asserted. 
%Section \ref{sec:variance_in_log_domain} will discuss how sampling distribution of variance in the log-transformed domain can be used to model various degrees of homogeneity. 
%Section \ref{sec:k_mle} will presents a novel speckle filtering algorithm developed from heterogenous inference made possible by statistical testing of sample variances.
%Section \ref{sec:k_mle_result} will present evaluation of our estimator both quantitatively through simulated experiments and qualitatively on real-life images.

\section{The Homoskedastic Effect of Logarithmic Transformation}

%\subsection{Homoskedastic effect of Logarithmic Transformation }

In this chapter, a base-2 logarithmic transformtion is proposed for SAR data. 
The choice of base-2 is due to implementation reasons
  since base-2 logarithm can be computed faster on digital computer than either natural or decimal logarithms,
  and yet the ability to transform heterskedactic speckle into a homoskedastic relationship is still maintained.
Under base-2 log-transformation, the original variables become:

\begin{eqnarray}
L_{1}^{A} &=& \log_2(A_1) = L_{1}^{I} / 2 \\
L_A &=& \log_2(A) 	= L_{1}^{A} + \log_2\sigma \\
L_{1}^{I} &=& \log_2(I_1) = 2 L_{1}^{A} \\
L_I &=& \log_2(I) 	= L_{1}^{I} + 2 \log_2\sigma
\end{eqnarray}

The equations above highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formulae. 
Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation
is clearly manifested. 
Now, bearing the relationship among the random variables in mind, it is then trivial to 
show that the probability distribution of these log-transformed variables are related as follows:

\begin{eqnarray}
pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left( 2 L_{1}^{A} \right)}e^{-2^{\left( 2 L_{1}^{A} \right) }} \\
pdf(L_A) &=& 2 \cdot 2^{\left( 2 L_A - 2 \log_2 \sigma \right)}e^{-2^{\left( 2 L_A - 2 \log_2 \sigma \right)}} \\ 
pdf(L_{1}^{I}) &=& 2^{L_1^I} e^{-2^{L_1^I}}  \\
pdf(L_I) &=& 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
%pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left[ 2 L_{1}^{A} - 2^{2 L_{1}^{A}} \right]} \\
%pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
%pdf(L_{1}^{I}) &=& 2^{\left[ L_{1}^{I} - 2^{L_{1}^{I}} \right]} \\
%pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} \label{eqn:log_intensity_base_2_dist}
\end{eqnarray}

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances 
are obtained and presented in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma \approx 0.577$ being the Euler-Mascheroni constant. 
Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

\begin{table}[h]
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = - \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = - \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}

\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
\label{tbl:sar_log_domain_avg_var}
%\end{center}
\end{table}

Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  
defined as the independence of the conditional expected variance on the conditional expectation of the mean. 
This result is consistent with findings in \cite{Arsenault_JOptSocAm_1976}. 
The main difference would be the use of base-2 logarithm which is preferred here for more efficient computation.

Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
It can be seen that while the original data, especially intensity values, should be preferred for 
multi-look processing, the log-transformed domain with its homoskedastic distribution offers consistent sense of variance.

\begin{table*}[t]
%\normalsize
%\footnotesize -2
\scriptsize
\centering

\begin{tabular}{|l|l|l|l|}
\hline
 RV & Relationships  & Variance (skedasticity) & Mean (biasness) \\
\hline
$A$ 
	& $A=\sigma A_1 $ 
	& Heteroskedastic $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ 
	& Unbiased $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ \\
$I$ 
	& $I=A^2=\sigma^2 I_1 $ 
	& Heteroskedastic $ var(I) = \sigma^4$ 
	& Unbiased $avg(I) = \sigma^2 $\\
$L_A$ 
	& $L_A=\ln(A)=L_{1^A} + \log_2{\sigma}$ 
	& Homoskedastic $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ 
	& Biased $avg(L_A) = \frac{ - \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ \\
$L_I$ 
	& $L_I=\ln(I)=L_{1^I} + 2 \log_2{\sigma}$  
	& Homoskedastic $var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ 
	& Biased $avg(L_I) = - \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ \\
\hline
\end{tabular}

\caption{ The properties of observable SAR random variables }
\label{tbl:sar_variables_properties}

\end{table*}

To experimentally validate this theoretical discussion, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a 
known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
An excellent agreement is observable in the graph which validate the log-transformed model. 
%In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
%through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[!h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/intensity_histogram.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

\section{Consistent Measures of Distance in the Log-Transformed Domain}

%\subsection{Consistent measures of distance in Log-Transformed domain}

The consistent feature is explored and illustrated in this section from two different perspectives. 
First, the back-scattering coefficient $\sigma$ is assumed to be \textit{known a priori}.
With that, let us consider the dispersion random 
variable defined as the distance between an observable sample and its expected value:

\begin{eqnarray}
D_A &=& A - avg(A) \\
D_I &=& I - avg(I) \\
D_{L^A} &=& L_A - avg(L_A) \\
D_{L^I} &=& L_I - avg(L_I) 
\end{eqnarray}

Noting the results from the previous section, the PDF for these variable can be derived as follows:

\begin{eqnarray}
pdf(D_A) &=& 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] } \\
pdf(D_I) &=& \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
pdf(D_{L^A}) &=& 2 \cdot 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} e^{-2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)}}\\
pdf(D_{L^I}) &=& 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} e^{-2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)}}
%pdf(D_{L^A}) &=& 2 \cdot 2^{\left[ \left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
%pdf(D_{L^I}) &=& 2^{\left[ \left( D_{L^I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} \right]}
\end{eqnarray}

From these equations, it is clear that these distributions, which are dependent on $\sigma$ in the original domain, 
are now independent of it when processed in the log-domain.

Let us investigate SAR data from the second perspective,
  where two adjacent resolution cells are known to have \textit{an identical but unknown} back-scattering coefficient $\sigma$.
Now, the contrast random variable is defined, also in the log-transformed domain, as the distance between two measured samples.

%From a second perspective, given two adjacent resolution cells that are known to have \textit{identical but unknown} back-scattering coefficient $\sigma$,
%  consider the contrast random variable defined, also in the log-transformed domain, as the distance between two 
%measured samples:

\begin{eqnarray}
C_A &=& A_1^\sigma - A_2^\sigma \\
C_I &=& I_1^\sigma - I_2^\sigma \\
C_{L^A} &=& L_1^{A_\sigma} - L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
C_{L^I} &=& L_1^{I_\sigma} - L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
\end{eqnarray}

Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is also consistent in the 
log-domain but inconsistent in the original domain. The PDF of the log-transformed variables can be expressed as:

\begin{eqnarray}
pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{\left[ 1+2^{\left( 2 C_{L^A} \right)} \right]^2} \ln2  \\
pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{\left[ 1+2^{\left( C_{L^I} \right)} \right]^2} \ln2 
%pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
%pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
\end{eqnarray}

Evidently these distributions are also consistent, i.e. they are independent of $\sigma$.
To illustrate this property, Fig. \ref{fig:residual_as_noise} is generated using the data extracted from a homogeneous area in a RADARSAT-2 image.
As can be seen, it shows excellent agreement between the analytical PDF and the observable histogram of dispersion and contrast computed from an homogeneous area in the image. 
%To illustrate this property, Fig. \ref{fig:residual_as_noise} is generated by using data from the RADARSAT-2 
%image. As can be seen, it shows excellent agreement between the analytical pdf and the observable histogram of dispersion
%and contrast of an homogeneous area in the image. 
%Distance is calculated as the difference between each value point and the average value of that region, 
%while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[dispersion]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_dispersion_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[contrast]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_contrast_histogram.eps} 	
		 \label{intensity}
	}
\end{tabular}
\caption{Observed and modelled pdf of dispersion 
and contrast in homogenous log-transformed intensity images.}
\label{fig:residual_as_noise}
\end{figure}

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that 
the measure of observable contrast in original SAR data differs, i.e. is inconsistent, across different homogenous 
areas. On the other hand, the observable contrast in the log-transformed domain is consistently the same across 
different homogenous areas. As such, one possible benefit is that should the sigma filter \cite{Lee_TGRS_2009} be 
designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.

\subsection{Sampling distribution of Variance in Log-Transformed domain}

From the previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as

\begin{eqnarray}
pdf(V_{L^I}) &=& 
	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)\\
pdf(V_{L^A}) &=&
	\frac{\ln2}{4} \frac{1}{\sqrt{V_{L^A}}} \left( \frac{2^{\sqrt{4 V_{L^A}}}}{\left( 1+2^{\sqrt{4 V_{L^A}}} \right)^2} + \frac{2^{-\sqrt{4 V_{L^A}}}}{\left( 1+2^{-2\sqrt{V_{L^A}}} \right)^2} \right)
\end{eqnarray}

It could be seen that, in the log-transformed domain, not only the expected value (mean) of the observable variance is constant, its distribution is also independent of $\sigma$. 
%We have seen this analytically
The above analysis is applicable for two sample variances. 
For larger number of samples $n > 2$, Monte-Carlo simulation is used to visualise the distribution of sample variances. 
The simulation is described as follows:

\begin{enumerate}
\item A large number of input samples are generated ($n \cdot 10^6$ in the figure \ref{fig:variance}) from the PDF given in Eqn. \ref{eqn:log_intensity_base_2_dist}.
\item The input samples are the divided into $10^6$ independent sets, each set consists of $n$ samples.
\item For each input set, the sample variance is calculated.
\item For all input sets, a histogram of the calculated values is then plotted.
\item The consistent variance property is observable when the same plots are obtained, regardless of the value $\sigma$ used in simulations.
\end{enumerate}

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[simulation match analysis]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_variance_hist_model_cdf_scene1.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[simulation for different number of samples]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/log_intensity_variance_no_of_samples_cdf.eps} 	
		 \label{intensity}
	}
\end{tabular}
\caption{ Sample Variance: Observable and Modelled CDF Response }
\label{fig:variance}
\end{figure}

Fig. \ref{fig:variance} not only provides evidence for the validity of the simulation process,
  it also visualizes the shapes of the CDF for sample variance distribution of different look numbers.

\subsection{Sample variance as a statistical measure of homogenity}

The discussion in the previous sub-section is based on the assumption of single stochastic processes, and thus homogeneity.  
In a real given analysis area in SAR images, such condition is unknown. 
The principle of SAR speckle filtering however is to group pixels into homogeneous areas, allowing stochastic components to be removed. 
In order to do that, a methodology is required to assert a partitioned area as being homogeneous. 
Fortunately the sampling distribution of log-variance provides a consistent method for testing this homo/hetero-geneity condition.

Under the null hypothesis that the given analysis area is homogeneous,
  the theoretical distribution of sample variance has been given earlier. 
The PDF, and equivalently the CDF, of this distribution can be visualized from Monte-Carlo simulations, as shown in Fig. \ref{fig:variance}. 
Thus, given a computed value of the sample variance in the log-transformed domain,
  the notion that a given analysis area is heterogeneous or homogeneous can be put to test. 
%This forms the basis of the statistical homogeneity hypothesis testing. 
%The test statistic to be used is the sample variance. 
%Figure \ref{fig:variance} shows the simulated CDF for sampling distribution of variance. 
%It is clear that,
Specifically given a pre-determined threshold-value and number of samples,
  if the observable sample variance is higher than a cut-off value, the null hypothesis can be rejected. 
%The collection of cut-off values for a certain threshold-value (a column in table \ref{tab:var_cut_off_values}) form a threshold-vector.

The steps for finding these cut-off values are given below:

\begin{enumerate}
\item For each number of samples, a CDF plot is derived using the Monte-Carlo simulation described earlier.
  \item Intrapolating from the CDF plot, a corresponding cut-off value is derived for each threshold-level.
  \item The combined results form a table, similar in structure to Table \ref{tab:var_cut_off_values}.
  \item The first 3 steps are repeated a few times,
     and the summary statistics (i.e. mean and variance) of the cut-off values for each combination of threshold-value and look-number is reported.  
\end{enumerate}

Table \ref{tab:var_cut_off_values} gives the result of one such such experiment for an arbitrarily chosen set of threshold values.
The table is useful in cases when an area is to be tested for homogeneity,
  for example in the kMLE speckle filter \cite{Le_2010_ACRS}

\begin{table}
\centering

%awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
\begin{tabular}{c|c|c|c|c|c}
No  & 70\%            &75\%             &80\%             &85\%             &90\%\\
\hline
2   &2.9024 (0.0252)  &3.7088 (0.0261)  &4.7960 (0.0327)  &6.3488 (0.0242)  &8.7974 (0.0370)\\
3   &3.4698 (0.0141)  &4.1308 (0.0177)  &4.9585 (0.0245)  &6.1176 (0.0136)  &7.9207 (0.0316)\\
4   &3.6505 (0.0225)  &4.2096 (0.0386)  &4.9392 (0.0347)  &5.9195 (0.0341)  &7.4209 (0.0162)\\
5   &3.7421 (0.0134)  &4.2513 (0.0165)  &4.8967 (0.0297)  &5.7729 (0.0170)  &7.0725 (0.0250)\\
6   &3.7850 (0.0149)  &4.2588 (0.0242)  &4.8611 (0.0160)  &5.6449 (0.0162)  &6.8062 (0.0282)\\
7   &3.8274 (0.0119)  &4.2686 (0.0102)  &4.8179 (0.0117)  &5.5447 (0.0114)  &6.6049 (0.0158)\\
8   &3.8468 (0.0110)  &4.2591 (0.0124)  &4.7747 (0.0176)  &5.4519 (0.0087)  &6.4370 (0.0085)\\
9   &3.8610 (0.0081)  &4.2503 (0.0125)  &4.7430 (0.0120)  &5.3688 (0.0085)  &6.2829 (0.0112)\\
10  &3.8663 (0.0089)  &4.2423 (0.0126)  &4.6967 (0.0102)  &5.3015 (0.0103)  &6.1574 (0.0116)\\
11  &3.8707 (0.0089)  &4.2284 (0.0109)  &4.6693 (0.0078)  &5.2387 (0.0111)  &6.0473 (0.0122)\\
12  &3.8763 (0.0063)  &4.2228 (0.0072)  &4.6370 (0.0139)  &5.1805 (0.0050)  &5.9502 (0.0044)\\
13  &3.8808 (0.0048)  &4.2089 (0.0083)  &4.6096 (0.0055)  &5.1315 (0.0092)  &5.8654 (0.0070)\\
14  &3.8761 (0.0048)  &4.1920 (0.0112)  &4.5816 (0.0069)  &5.0845 (0.0058)  &5.7870 (0.0106)\\
15  &3.8806 (0.0048)  &4.1901 (0.0063)  &4.5592 (0.0088)  &5.0372 (0.0076)  &5.7158 (0.0119)\\
16  &3.8774 (0.0032)  &4.1778 (0.0060)  &4.5397 (0.0049)  &4.9985 (0.0087)  &5.6483 (0.0083)\\
17  &3.8760 (0.0043)  &4.1682 (0.0035)  &4.5149 (0.0060)  &4.9652 (0.0051)  &5.5919 (0.0078)\\
18  &3.8708 (0.0083)  &4.1584 (0.0026)  &4.4951 (0.0030)  &4.9273 (0.0043)  &5.5319 (0.0083)\\
19  &3.8694 (0.0055)  &4.1464 (0.0037)  &4.4755 (0.0039)  &4.8961 (0.0027)  &5.4838 (0.0031)\\
20  &3.8687 (0.0051)  &4.1364 (0.0041)  &4.4555 (0.0072)  &4.8673 (0.0042)  &5.4371 (0.0076)\\
21  &3.8672 (0.0064)  &4.1268 (0.0049)  &4.4401 (0.0052)  &4.8360 (0.0045)  &5.3927 (0.0027)\\
22  &3.8637 (0.0046)  &4.1215 (0.0037)  &4.4253 (0.0050)  &4.8136 (0.0043)  &5.3499 (0.0060)\\
23  &3.8610 (0.0032)  &4.1110 (0.0039)  &4.4093 (0.0057)  &4.7870 (0.0059)  &5.3118 (0.0056)\\
24  &3.8571 (0.0033)  &4.1015 (0.0051)  &4.3942 (0.0060)  &4.7650 (0.0026)  &5.2732 (0.0054)\\
25  &3.8541 (0.0054)  &4.0931 (0.0052)  &4.3803 (0.0032)  &4.7416 (0.0024)  &5.2453 (0.0045)
\end{tabular}

\caption{Cut off values}
\label{tab:var_cut_off_values}
\end{table}

%\section{Chapter Conclusion}

%It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance 
%constant, the sampling distribution of this random variable is also independent of $\sigma$. 
%While we have observed this analytically for variances based on two samples, for a larger number of samples, 
%Monte-Carlo simulation can be used to visualise the PDF of samples' variances.

\textbf{In summary}, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
The dispersion measurement can be used to test 
if a pixel belongs to a ``known'' class of physical scatterer \cite{Le_2010_ACRS}.
The consistent sense of contrast can be used to test if any pair of measured data points belong to  the same homogeneous class.
An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
%It may also explain why, in the original SAR domain, the ratio based 
%  detector / classifier is preferred to differential measures, which are not consistent. 
The consistent sense 
of contrast also gives rise to consistent measures of sample variances, which for example, can be used to test 
if a group of pixels can form a homogenous area.
This was applied in a clustering algorithm described in  \cite{Le_2010_ACRS}.

%\section{Original Heteroskedastic Model}

%\section{The effects of Heteroskedasticity}

%\section{The Homoskedastic effect of Logarithmic Transformation}

%\section{Consistent Measures of Distance in Log-transformed domain}

%\section{Consistent Measures of Variance in Log-Transformed Domain}

### 2013-03-01 4/polsar.tex
201303_Mar01

\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
\label{chap:polsar}

In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
Then log-transformation is shown converting these into an additive and homoskedastic model.
Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
Finally the last section strengthens our model showing the matching between simulation and real-life captured data
  not only for a few dimensionally-collapsed single-dimensional measures
  but also for all elements of the multi-dimensional POLSAR covariance matrix.

\section{POLSAR statistical analysis}

In this section, the POLSAR scattering vector is denoted as $s$.
In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
  the vector is two-dimensional ($d=2$) and is normally written as: 
\begin{equation}
s_{part}=\begin{bmatrix}
S_h\\ 
S_v
\end{bmatrix}
\end{equation}
In the case of full and monostatic POLSAR data,
  the vector is three-dimensional ($d=3$) and is presented as:
\begin{equation}
s_{full}=\begin{bmatrix}
S_{hh}\\
\sqrt{2}S_{hv}\\
S_{vv}
\end{bmatrix}
\end{equation}

Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
Assuming all the elements in $s$ are independent
  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
  then the probably density function (PDF) of $s$ can be written as:
\begin{equation}
  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
\end{equation}
where $|M|$ denotes the determinant of the matrix $M$.

As covariance matrix is only defined on multiple data points,
  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
They are formed as the mean of Hermitian outer product of single-look scattering vectors
\begin{equation}
  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
\end{equation}
with $s_i$ denotes the single-look scattering vector,
  which equals $s_{part}$ in the case of partial POLSAR and
  $s_{full}$ in the case of full polarimetry,
and $L$ is the number of looks.

Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
$Z=LC_v$, whose PDF is given as:
\begin{equation}
  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
\end{equation}
with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
and $d$ is the dimensional number of the POLSAR covariance matrix.

Our approach differs by applying the homoskedastic log transformation
  on a less-than-well-known result for the deterimant of the covarinace matrix.
  %under the assumption of circular complex Gaussian distribution
  %applicable for POLSAR data.
In \cite{Goodman_1963_AMS_178}, %Goodman
it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
\begin{equation}
\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
\label{eqn:prod_chi_squared_rv}  
\end{equation}

Its log-transformed variable consequently 
  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
\begin{equation}
\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
\label{eqn:sum_log_chi_squared_rv}
\end{equation}
with
  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$

\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
\label{sec:polsar_heterosked_model_and_log_transform}

In this section the multiplicative nature of POLSAR data is illustrated.
Log-transformation is shown converting this into a more familiar additive model.
Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
  is proved to be the case for the original POLSAR data.
In log-transformed domain, the case for a homoskedastic model,
  where  variance is fixed and be independent of the underlying mean,
  is demonstrated.
To keep the section flowing, the mathematical derivation is only presented here in major sketches.
For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.

From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
we have:
\begin{eqnarray}
  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
\label{eqn:log_determinant_distribution}  
\end{eqnarray}

In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
  the logarithmic transformation converts this into a more familiar additive noise.

Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
\begin{equation}
pdf(x;k) =
  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
\label{eqn:chi_squared_dist_pdf:chap4}
\end{equation}
Applying the variable change theorem, 
  its log-transformed variable follows the PDF of:
\begin{equation}
  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
\end{equation}

Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
  can be written as:
  \begin{eqnarray}
    CF_\chi(t) &=& (1-2it)^{−L} \\ 
    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
  \end{eqnarray}
Subsequently their means and variances can be computed from the given characteristic functions as:
  \begin{eqnarray}
    avg \left[ \chi(2L) \right]&=&2L \\
var \left[ \chi(2L) \right]&=&4L \\
avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
var \left[ \Lambda(2L) \right] &=& \psi^1(L)
  \end{eqnarray}
  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma function respectively.

Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
  the product and summation of these random variables also has fixed summary statistics.
Specifically:
\begin{eqnarray*}
  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
\end{eqnarray*}

Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
\begin{eqnarray}
  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
\end{eqnarray}

Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
  the underlying $\Sigma_v$ is expected to differ from one region to the next.
Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
  %and it is clear that 
  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.

\section{Consistent Measures of Distance for POLSAR data}

Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
  this section introduces the consistent sense of distance in a few different perspective.
First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
the following random variables,
  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
  are observable according to their definitions:
%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :

\begin{eqnarray}
  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
\end{eqnarray}
From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
\begin{eqnarray}
  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
\end{eqnarray}

Taking the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
\begin{eqnarray}
\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
\label{eqn:log_determinant_distance_distribution} \\ 
 \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
\label{eqn:dispersion_distribution} \\ 
 \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
\label{eqn:contrast_distribution}  
\end{eqnarray}
with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$

Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
  Appendix \ref{sec:appendix_b} derives the characteristic functions for the summative random variables as:
\begin{align}
  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
\end{align}

Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
  it is natural that these variables also follow fixed distributions.
Moreover, they are independent to $\Sigma_v$.
This serves as conclusive evidence that
  these random variables follows consistent and fixed distributions,
  regardless of the underlying signal $\Sigma_v$.

\section{SAR as the Special Case of Polarimetric SAR}
\label{sec:sar_special_case_of_polsar}

The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
Mathmatically, the sample covariance matrix is reduced to the sample variance
  and the determinant equates the scalar value.
On another hand, it is well known that for SAR data, variance equals intensity.
Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
This can be thought of 
  either as a cross-validation evidence for the proposed POLSAR models
  or alternatively as having SAR as the special case of POLSAR. 
%  with well known results for SAR intensity is presented.

The results so far for our models can be summarized as:
\begin{align}
  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
\end{align}

Upon setting $d=1$ into the above models,
  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
\begin{align*}
  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{align*}
but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
  \end{eqnarray}
Furthermore, the following results for multi-look SAR data,
  which can be thought of 
    either as extensions of the corresponding single-look SAR results
    or as simple cases of the POLSAR results
  are also derived as:
  \begin{align*}
    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
  \end{align*}

This newly derived models for multi-look SAR data can also be validated against real-life data.
Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
The ENL is set to the nominal number of 4.
And good visual match is apparent in the final results.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[verify multi-look SAR log-distance]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[verify multi-look SAR contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
		 \label{multi_look_contrast}
	}
\end{tabular}
\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
\end{figure}

\section{Validating the models against real-life data}
\label{sec:polsar_models_validation}

\subsection{Explaining practical data with the given Number-of-Looks}

This section describes an experiment to validate the models above against real-life captured data.
The validation procedure is quite straightforward.
Given that the stochastic models have been derived in the previous sections, 
  they can be graphically visualized by the histogram plots of the simulated data.
At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
Therefore, the theoretical models can be validated 
  if for the same parameters 
  the two plots match each other reasonably well.

As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
Then theoretical models are employed in an attempt to explain the data.
The validating models include:
  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.

The models are closely related.
Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
Thus ideally speaking
  if one model is validated all the other models will also be,
  assuming that all the parameters of the image are known exactly.
Still in this section, all the models will be made subject to investigation.

Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
Then their histograms are traced out.

At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
The nominal value of 4 was taken as the dataset's number of look,
 while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
		 \label{contrast_2x2}
	} \\
	\subfloat[full-pol (3x3) dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
		 \label{dispersion_3x3}
	} 
	\hfill	
	\subfloat[full-pol (3x3) contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
		 \label{contrast_3x3}
	}
\end{tabular}
\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
\end{figure}

Apart from dispersion and contrast,
the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
There are two ways to estimate this quantity over an homogeneous area.
The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
Both approaches will be explored in this section.
However, given that the log-determinant average has already been computed earlier, 
  the second approach is used first for the validation of determinant-ratio and log-distance.

Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
Again a reasonable match is observed which validates the models for log-distance and determinant ratio.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[part-pol (2x2) determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
		 \label{determinant_ratio_2x2}
	} 
	\hfill	
	\subfloat[part-pol (2x2) log distance]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
		 \label{log_distance_2x2}
	} \\
	\subfloat[full-pol 3x3 determinant ratio]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
		 \label{determinant_ratio_3x3}
	} 
	\hfill	
	\subfloat[full-pol 3x3 log distance]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
		 \label{log_distance_3x3}
	}
\end{tabular}
\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
\end{figure}

Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.

However, a more interesting  phenomena is to be described.
It happens in the validation process for determinant and its log-transformed model,
  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
%For such simulation, an estimation of  the true signal is needed.
The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.

Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
The differences are easier to observe in the log-determinant plots, 
  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[verify polsar 2x2: determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
		 \label{determinant_2x2}
	} 
	\hfill	
	\subfloat[verify polsar 2x2: log-determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
		 \label{log_det_2x2}
	} \\ 
	\subfloat[verify polsar 3x3: determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
		 \label{determinant_3x3}
	} 
	\hfill	
	\subfloat[verify polsar 3x3: log-determinant]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
		 \label{log_det_3x3}
	} 
\end{tabular}
\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
\label{fig:verify_polsar_2x2_simulation_det}
\end{figure}

In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
  if the underlying parameters can be estimated reasonably well for the given image.   
However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
  depending on which estimation method was being used.
The discrepancy suggests that at least one parameter for the models was wrongly employed.

But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
  where not only the look number is shown to be misused
  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
For now, let us contend that:
  using appropriate estimation of the parameters, 
  the proposed models match reasonably well with the practical data.

\subsection{Comparing Theoretical Assumptions and Practical Implementations}
\label{sec:improve_the_match_bw_theory_practice}

Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
  like all other similar models, the proposed model in this paper is built upon certain presumptions.
Practical conditions however may not always satisfy these prerequisites.
In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.

There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
Practically however high correlation is routinely observable between the POLSAR data components,
  specifically between $S_{hh}$ and $S_{vv}$.
This phenomena also presents in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
Despite the mismatch,
  astute reader would probably notice that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs. \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
This suggests that the proposed model is also applicable on correlated POLSAR components,
  eventhough a full explaination for this, however, is outside the scope of this paper.

Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent to each other.
This is a reasonable assumption given that 
  the transmission and receipt of analog signals are done independently for each radar pulse, i.e. for each resolution cell.
Thus theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.

However, the actual imaging mechanism of a real-life (POL)SAR processor is that of digital nature,
where the analog signal is to be converted into a digital data-set. 
Specifically, the analog signal in SAR 
  which is characterized by the pulse bandwidth measurement,
  is fed into an analog-to-digital sampling and conversion process 
  which is characterized by its sampling rate.
Theoretically it is possible to define a sampling rate to ensure that each digital pixel correspond exactly to an analog physical cell resolution.
Practically however, to ensure ``perfect reconstruction'' of the analog signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
This results in a higher number of samples / pixels than the number of physical cells available in the scene.

Stated differently, in practical data each physical radar cell is spread to more than one pixel
  and each pixel now contains less than one physical analog cell.
This high sampling rate also results in 
  a significantly higher correlation between pairs of pixels that maybe related within a single physical cell resolution 
  than the correlation found between pairs of pixels that are further away and hence having less physical relation to each other.
It also results in reduced effective number of look, 
  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
  while the later is experimental observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
The oversampling practice is also documented by the producers of SAR processors.
For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
While for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}

The proposed model can handle this imperfection that is available in pratical data.
The trick is that instead of using the nominal Number of Look given by the SAR processor,
  an ENL estimation procedure is employed. %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
The first part of this section details a simple ENL estimation technique for POLSAR data.
While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved,
  by using ENL estimation.

\subsection{Estimating the Effect Number-of-Looks (ENL)}

This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
The common approach in tackling this problem is by investigating the summary statistics of an known homogeneous area in the given data
  before making inferences about the inherent ENL.
The summary statistics for $|C_v|$ and $\ln|C_v|$ has been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
In fact Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
Recall that in carrying out validation process for AIRSAR Flevoland data using the nominal look number of 4, this relationship was broken.
The reason for such broken relationship is believed to be an inexact look number was taken.
In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ is known,
  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensure the above relationship is valid.

In fact, this approach was taken in \cite{Anfinsen_2009_TGRS_3795},
  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
Instead of relying on the equations for statistical mean to find ENL,
  our approach make used variance statistics in the homoskedastic log-domain to find ENL.
Since the determinant of POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
  this approach can be considered as the generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} towards POLSAR data.
Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
\begin{equation}
  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
  \label{eqn:expected_sample_var_log_as_function_of_enl}
\end{equation}
where $\psi^1()$ denotes tri-gamma function.

Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
Interestingly that would also require some iterative computations.
Practically however, the shape of the right-hand-side can be pre-computed
  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph.
And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
  \begin{equation}
    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
    \label{eqn:enl_estimation_formula}
  \end{equation}
Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
  not only shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
  but also illustrates the approximation power of the simplified formula (Eqn. \ref{eqn:enl_estimation_formula}).

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[ENL and variance log-intensity relations for SAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
		 \label{plot_enl_var_relation_1x1}
	} 
	\hfill	
	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
		 \label{plot_enl_var_relation_2x2}
	} 
\end{tabular}
\caption{The relationships between ENL and the sample variance of log-determinant and log-intensity}
\label{fig:plot_enl_var_relation_1x1_and_2x2}
\end{figure}

\subsection{Using the estimated ENL to better explain pratical data}

For this experiment an example RADARSAT2 dataset was used.
The dataset is in its Fine-Quad mode Single-Look format,
  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
  against the theoretical model for the nominal ENL value of 9.
The match however is not very good.

A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
  and the theoretical model is simulated for the estimated ENL
Then the new sample histogram is plotted in the same figure,
  which indicated a much better consistency.
This procedure can always be carried out for any given dataset,
  as long as an area of homogeneous area can be extracted.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics. Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
\label{fig:handling_radarsat2_oversampling_practice}
\end{figure}

Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
The mis-match problem appears to depend on how much over-sampling were used in the dataset
  as well as the dimension of the data.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
		 \label{sar}
	} 
	\hfill	
	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
		 \label{part_pol}
	}   
\end{tabular}
\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
\label{fig:handling_airsar_oversampling_practice_full_pol}
\end{figure}

\section{Details of Mathematical Derivations}

\subsection{The Log-Chi-Square Distribution}
\label{sec:appendix_a}

This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.

Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
\begin{equation}
pdf(\chi;\,k) =
  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
\label{eqn:chi_squared_dist_pdf:appdixA}
\end{equation}

Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
\begin{equation}
pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
\end{equation}

Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
\begin{equation}
 \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
\end{equation}
into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
\begin{eqnarray*}
  d\chi &=& e^\Lambda d\Lambda \\
  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
\end{eqnarray*}
In other words, we have:
\begin{equation}
pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
\label{eqn:log_chi_square_dist_pdf}
\end{equation}

From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, characteristics function can be computed.
By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
\begin{eqnarray*}
\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
\end{eqnarray*}
with $\varphi_x(t)$ is the characteristic function,
     $F_X(x)$ is the CDF function of X and
     $f_X(x)$ is the PDF function of X.
Thus the characteristic function for log-chi-squared distribution is defined as: 
\begin{equation}
\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
\end{equation}

Gamma function is defined over complex domain as:
$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
%  \begin{eqnarray*}
%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
%  \end{eqnarray*}

%Thus the characteristic function becomes
That is:
\begin{equation}
\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
\end{equation}

Consequently, the first and second derivative of log-chi-squared distribution can be computed.
The first derivative is given as:
\begin{equation}
  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
\end{equation}
due to
\begin{eqnarray*}
  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
\end{eqnarray*}
where $\psi^0()$ denotes di-gamma function.

Meanwhile, the second derivative can be written as:
\begin{equation}
  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
\end{equation}
due to:
\begin{eqnarray*}
  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
\end{eqnarray*}
with $\psi^1()$ denotes tri-gamma function.

The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
\begin{equation}
\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
\end{equation}

Thus
\begin{eqnarray*}
 \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
\end{eqnarray*}
That is
\begin{equation}
  avg(\Lambda) = \psi^0(L) + ln(2)
\end{equation}

Similarly,
\begin{eqnarray*}
 \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
\end{eqnarray*}
That is:
\begin{equation}
  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
\end{equation}
%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.

Thus
\begin{equation}
var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
\end{equation}

\subsection{Summary Statistics of Some POLSAR Observables}

In this section, the expected value and variance value of these mixture of random variables is derived
\begin{eqnarray}
\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
\end{eqnarray}
given the averages and variances of individual components.
\begin{eqnarray}
avg \left[ \chi(2L) \right]&=&2L \\
var \left[ \chi(2L) \right]&=&4L \\
avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
var \left[ \Lambda(2L) \right] &=& \psi^1(L)
\end{eqnarray}

Making use of the mutual indepent property of each component $X_i$,
  the variance and expectation of the sumation and product of random variables can be written as:
\begin{eqnarray*}
avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
\end{eqnarray*}

Thus they can be computed as:
\begin{eqnarray*}
  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
\end{eqnarray*}

\subsection{The characteristic function of some dissimilarity measures for polsar}

Given characteristic function (CF) of the elementary log-chi square distributions can be written as:
\begin{eqnarray}
 CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
\end{eqnarray}
  the CF for the following random variables,
  which are combinations of the above elementary random variables, can be derived
\begin{eqnarray*}
   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
\end{eqnarray*}

Since
\begin{eqnarray*}
 CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
 CF_{x+k}(t) &=& e^{itk}CF_x(t)
\end{eqnarray*}
we have:
\begin{eqnarray}
  CF_{\chi^d_L}(t) &=& \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
   CF_{\mathbb{L}} &=& \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
   CF_{\mathbb{D}} &=& \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
\end{eqnarray}

%The CF for the contrast random variable can also be written as
Also due to
\begin{eqnarray*}
  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
\end{eqnarray*}
we arrive at:
\begin{eqnarray}
  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
\end{eqnarray}
with $\Gamma()$ and $B()$ denotes Gamma and Beta functions respectively.

\subsection{SAR intensity as the special case of the POLSAR cov-matrix determinant}
\label{sec:appendix_sar_special_case_of_polsar}

In this appendix, the following results for SAR intensity $I$ is shown to be special cases of the results given in this paper for the determinant of POLSAR's covariance matrix $det|C_v|$.
Specifically, not only the following results from the our previous works on single-look SAR (TODO:CITE), i.e. $d=L=1$, is reviewed:
\begin{eqnarray}
  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{eqnarray}
but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$ is also considered:
  \begin{eqnarray}
I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
  \end{eqnarray}
It will be shown that all of these results are special cases of the result derived previously and rewritten below:
\begin{eqnarray}
  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
\end{eqnarray}
\begin{eqnarray}
  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
\end{eqnarray}
\begin{eqnarray}
  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
\end{eqnarray}

This appendix also derives new results for multi-look SAR data,
  which can be thought of 
    either as extensions of the corresponding single-look SAR results
    or as simple cases of the POLSAR results presented above.
They are:
  \begin{eqnarray}
    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
    var(\mathbb{D}) &=& \psi^1(L) \\
    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
  \end{eqnarray}

The derivation process detailed below consists of two-phases.
The first phase collapse the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
Mathematically this means setting the dimensional number in POLSAR to  $d=1$
  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.

The output of the first phase, in the general case is applicable to multi-look SAR data, where $d=1$ but $L>1$.
The second phase simplify the multi-look results into single-look results, presented in our previous work (TODO:CITE).
Mathematically, that means setting $L=1$ in the multi-look result
  and converting from natural logarithmic domain used in this paper to the base-2 logarithm used in (TODO:CITE).

\subsubsection{Original Domain: SAR Intensity and its ratio}

Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
we have:
\begin{eqnarray*}
  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
\end{eqnarray*}
Or in PDF forms, and applying variable change theorem we have:
\begin{eqnarray*}
    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
\end{eqnarray*}

Thus we have the following results for multi-look SAR
\begin{eqnarray}
    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
\end{eqnarray}

Now setting $L=1$, these results become:
\begin{eqnarray}
    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
\end{eqnarray}
which is the same as in (TODO:CITE).

\subsubsection{Log-transformed domain: SAR log-intensity and the log-distance}

The result for multi-look SAR data written in log-transformed domain can be derived from two different approaches.
The first is to follow the simplification method, where the results for log-transformed POLSAR data is simplified into log-transformed multi-look SAR result.

The second approach is to apply log-transformation into the results derived in the previous section.
In this section, it is shown that both approaches would results into identical results.

Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
we have
\begin{eqnarray*}
  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
\end{eqnarray*}

Or in PDF form, and applying variable change theorem we have:
\begin{eqnarray*}
  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
 &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
\end{eqnarray*}
with $\bar{N} = \ln{\bar{I}}$.

Thus the first approach arrives at
\begin{eqnarray}
   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
\end{eqnarray}

In the second approach, log-transformation is applied on previous result for multi-look SAR intensity and its ratio in the original domain (Eqns. \ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
The also arrives at the same results as above, the details working however is omitted here for brevity.

%\begin{eqnarray*}
%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
%\end{eqnarray*}
%Thus
%\begin{eqnarray*}
%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
%\end{eqnarray*}
%
%Thus the second approach also arrives at
%\begin{eqnarray}
%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
%\end{eqnarray}

To compute summary statistics for the multi-look SAR dispersion,
  set $d=1$ into the Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
we have:
  \begin{eqnarray*}
    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
    var(\mathbb{L}) &=& \psi^1(L) \\
    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
\end{eqnarray*}

This completes the first phase of the derivation process.
The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
  and converting natural logarithm into base-2 logarithm.
First, setting $L=1$ makes the above results become
\begin{eqnarray*}
   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
\end{eqnarray*}
with $\gamma$ denotes the Euler-Mascharoni constant.
Then to convert to base-2 logarithm from natural logarithmic transformation,
  variable change theorem is invoked.
  That is:
  \begin{eqnarray*}
   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
  \end{eqnarray*}
\begin{eqnarray*}
   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
\end{eqnarray*}
\begin{eqnarray*}
  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
\end{eqnarray*}

\subsubsection{Deriving the PDF for SAR dispersion and contrast}

The PDF for SAR dispersion can be easily derived from
  the PDF for the Log-distance given above as:
  \begin{equation}
   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
  \end{equation}
due to $d=1$ and
\begin{eqnarray*}
  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
\end{eqnarray*}.

Setting $L=1$ for Single-Look SAR we have
\begin{equation}
  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
\end{equation}
due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
with $\gamma$ being the Euler Mascheroni Constant which equals $0.5772$. 
In base-2 logarithm, variable change theorem is invoked
\begin{eqnarray*}
  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
\end{eqnarray*}
Thus we have
\begin{equation}
  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
\end{equation}
which is consistent to the result in our previous work (TODO:CITE).

Setting $d=1$ into Eqn. for contrast result in
\begin{equation}
  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
\end{equation}
The characteristic function would then be
\begin{equation}
  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
\end{equation}
Thus PDF can be written as
\begin{equation}
  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
\end{equation}
due to
\begin{eqnarray*}
  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
\end{eqnarray*}

Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
we have the PDF for contrast of single-look SAR:
\begin{equation}
  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
\end{equation}

Converting to base-2 logarithm we have
\begin{eqnarray*}
  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
\end{eqnarray*}
which is also consistent to the result in our previous work (TODO:CITE).

%\section{Simulating All Elements of POLSAR Covariance Matrix}
%
%Jong sen lee simulation procedures is applied and verified in 2x2 partial polsar AIRSAR Flevoland image.
%Pipia method explicitly indicates cholesky decomposition,
%  while the exponential notion in Lee's book appear to suggest svd decomposition
%
%\begin{figure}[h]
%\centering
%\begin{tabular}{c}
%	\subfloat[verify polsar 2x2 simulation: S11]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%                 \epsffile{images/verify_polsar_2x2_simulation.S11.eps} 
%		 \label{S11}
%	} 
%	\hfill	
%	\subfloat[verify polsar 2x2 simulation: S22]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{images/verify_polsar_2x2_simulation.S22.eps} 	
%		 \label{S22}
%	} \\
%	\subfloat[verify polsar 2x2 simulation: S12r]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%                 \epsffile{images/verify_polsar_2x2_simulation.S12r.eps} 
%		 \label{S12r}
%	} 
%	\hfill	
%	\subfloat[verify polsar 2x2 simulation: S12i]{
%		 \epsfxsize=3in
%		 \epsfysize=3in
%		 \epsffile{images/verify_polsar_2x2_simulation.S12i.eps} 	
%		 \label{S12i}
%	}        
%\end{tabular}
%\caption{verifying polsar 2x2 simulation: the components}
%\label{fig:verify_polsar_2x2_simulation_components}
%\end{figure}
%
%The same procedure does not appear to work on 3x3 full polarimetric POLSAR image.
%Despite all other elements match nicely, the ShhSvv* element does not appear to match.
%However, the log-det still appears to be consistent
%  and more importantly all dis-similarity measures still match.
%  
%\begin{figure}[h!]
%\centering
%\epsfxsize=6.0cm
%\epsffile{images/verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation.eps} 
%\caption{3x3 svd simulation: 13 element mismatch}
%\label{fig:verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation}
%\end{figure}
%
%\begin{figure}[h]
%\centering
%\begin{tabular}{c}
%	\subfloat[C11]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.11.eps} 
%		 \label{11}
%	} 
%	\hfill	
%	\subfloat[C22]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.22.eps} 
%		 \label{22}
%	} 
%	\hfill	
%	\subfloat[C33]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.33.eps} 
%		 \label{33}
%	} \\
%	\subfloat[C12r]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.12r.eps} 
%		 \label{12r}
%	} 
%	\hfill	
%	\subfloat[C13r]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.13r.eps} 
%		 \label{13r}
%	} 
%	\hfill	
%	\subfloat[C23r]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.23r.eps} 
%		 \label{23r}
%	}  \\
%	\subfloat[C12i]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.12i.eps} 
%		 \label{12i}
%	} 
%	\hfill	
%	\subfloat[C13i]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.13i.eps} 
%		 \label{13i}
%	} 
%	\hfill	
%	\subfloat[C23i]{
%		 \epsfxsize=2in
%		 \epsfysize=2in
%                 \epsffile{images/verify_polsar_simulation_3x3.23i.eps} 
%		 \label{23i}
%	}
%\end{tabular}
%\caption{verify polsar 3x3 simulation with polarization basis change}
%\label{fig:verify_polsar_svd_3x3_simulation_polarization_basis_change}
%\end{figure}
%

### 2013-03-01 5/applications.tex
201303_Mar01

\chapter{Using the Consistent Measures of Distance} %chapter 5
\label{chap:applications}

\section{Clustering SAR images using the consistent measures}
%\section{SAR Image Clustering using the consistent measures}

%\section{Proposed SAR speckle filter using Homoskedastic features}
\label{sec:k_mle}

Given an area of analysis, 
  the question of whether it is homogeneous or not can be investigated using
%its non-homogeneity can be detected by 
the statistical hypothesis test described above. 
If that is decided to be the case, clustering algorithm can be applied to partition the area into smaller regions. 
Thus an image can be segmented into homogeneous areas by applying the process repeatedly.

%Given an area of analysis, its non-homogeneity can be detected by the statistical hypothesis test described above. 
%If that is likely to be the case, clustering algorithm can be applied to partition the area into smaller regions. 
%The process can be applied iteratively until all partitions can be considered homogeneous (accepting the null hypothesis). 
%This forms the basis of our proposed speckle filtering technique.

\subsection{Developing kMLE clustering Algorithm}

\subsubsection{Homogeneous Maximum Likelihood Estimation}

In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given earlier. 
Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the aim then is to estimate $\sigma$. 
This section will show how $\sigma$ can be estimated in log-transformed domain.

It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$. 
Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
The PDF given in Eqn. \ref{eqn:conditional_prob} then can be interpreted as
  the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.

\begin{eqnarray}
\label{eqn:conditional_prob}
P(x^l_i | \mu ) 
	&=& \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} P(x^l_i | \mu )  }
%	&=& - \ln^2{2} \frac{ 2^{x^l_i - \mu} (2^{x^l_i - \mu}-1) }{ e^{2^{ x^l_i -\mu }} } 
\end{eqnarray}

Since log-transformed variables are biased, an MLE approach is used to estimate $\mu$. 
The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of value X found in the area, given the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in equation \ref{eqn:conditional_prob}.   
%$P(x^l_i | \mu ) = \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }$. 
Maximize $P(X^e | \mu )$ also maximizes $\ln[P(X^l | \mu )]$, which can be written as:

\begin{eqnarray}
\ln[P(X^l | \mu )] 
	= \displaystyle{\sum^n_{i=1}{ \ln(P(x^l_i | \mu )) }} 
	= \displaystyle{\sum^n_{i=1}{ \ln \left[ \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} } \right] }} 
%	&=& n \ln \ln 2 +  \displaystyle{\sum^n_{i=1}{ \ln \left( 2^{x^l_i - \mu} \right) - \ln \left( e^{2^{ x^l_i -\mu }} \right) }} 
\end{eqnarray}

The parameter $\mu$ which maximizes the likelihood is found by setting its derivatives to zero:
\begin{eqnarray}
\displaystyle{ \frac{ \partial{ \ln[P( X^l | \mu )] }  }{\partial{ \mu }} }
	&=& 0 \\
\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) - \ln( e^{2^{ x^l_i -\mu }} ) } }
	&=& 0 
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( 2^{x^l_i - \mu}) } }
%	&=& - n \cdot \ln2  \\
%\displaystyle{ \frac{ \partial }{\partial{ \mu }} \sum^n_{i=1}{ \ln( e^{2^{ x^l_i -\mu }} )i } }
%	&=& - \ln2 \cdot \sum^n_{i=1}{ 2^{ x^l_i -\mu } } \\
%	&=& - \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  
\end{eqnarray}

Thus $\mu$ can be found by:
\begin{eqnarray}
%n \cdot \ln2	
%	&=& \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  \\
2^\mu 
	&=& \frac{ \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }} }{n}  
\label{eqn:mle_log_transform}
\end{eqnarray}

This result in the log-transformed domain is consistent with the analysis result in the original domain where $\sigma^2 = \frac{\sum^n_{i=1}{x^e_i}}{n} $, with $x^e_i = 2^{x^l_i}$

\subsubsection{Heterogeneous k-MLE Clustering}

In order to apply MLE into a given analysis window ($L^w$), one would need to partition the area into groups of homogeneous pixels ($G$). 
Assuming for now that the number of homogeneous groups ($c=size(C)$) is known \textit{a priori}, this section will describe the proposed clustering algorithm. 
The basic template is similar to the k-means clustering algorithms (Listing \ref{lst:k_mle_algo_template})

\begin{enumerate}
\item Initialize the cluster centres
\item Assign each sample to a centre $C_i$ that has the highest probability $P(x|C_i)$ (as in equation \ref{eqn:conditional_prob})
%(winner take all)
\item Recalculate cluster centres for each $C_i$ (as in equation \ref{eqn:mle_log_transform})
\item Iterate above 2 steps until there is no more changes in cluster centres' locations
\end{enumerate}

%The pseudo code for the algorithm is provided in Listing \ref{lst:k_mle_algo_cluster_centers}

\lstset{language=Matlab,caption=k-MLE Clustering Algorithm Template,label=lst:k_mle_algo_template}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
\begin{lstlisting}[frame=tb]
function optimized_clusters = k_mle_clustering(l, c_init) 
  c_prev = c_init;
  c_new = find_new_centers(l, c_prev);

  while (c_new != c_prev) do
    c_prev = c_new;
    c_new = find_new_centers(l, c_prev);
  end while

  return optimized_clusters = c_new
end function
\end{lstlisting}

Due to the special characteristics of the log-transformed domain, we have adopted
an MLE estimator in lieu of a standard averaging estimation for cluster centers. 
Consequently the kMLE algorithm is presented in Listing \ref{lst:k_mle_algo_cluster_centers}.
%a standard k-means algorithm transformed into k-mle algorithm given in Listing \ref{lst:k_mle_algo_cluster_centers}.

\lstset{language=Matlab,caption=Iteratively find better cluster centers,label=lst:k_mle_algo_cluster_centers}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
%\begin{figure}
%\begin{verbatimtab}
\begin{lstlisting}[frame=tb]
function c_new = find_new_centers(l, c)
  for (i = 1 to size_of(l))
    for (j = 1 to size_of(c))
      m[i,j] = 0; %reset memberships
      p[i,j] = conditional_probability_of( l[i]|c[j] );
    end for

    j_0 = argmax( p[i,:] );
    m[j_0] = 1; %assign membership to a cluster
  end for

  for ( j = 1 to size(c) )
    c_new[j] = maximum_likelyhood_of( l[i] with m[i,j]==1 );
  end for

  return c_new;
end function
\end{lstlisting}
%\end{verbatimtab}
%\caption{Iteratively find better cluster centers}
%\label{src:k_mle_algo}
%\end{figure}

When compared with standard k-means the following differences are evident:
\begin{enumerate}
  \item In k-means, data points are grouped into clusters with minimum distance. 
In our specific situation, as the dispersion PDF is non-symmetric around the cluster center, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
  \item The calculation of new cluster centers is different also. 
In k-means, new cluster centres are estimated as the average of all membered data points. 
Here, due to the bias of the PDF, maximum likelihood estimations are preferred.
  \item All the design decisions are made possible by the knowledge of the statistical PDF in the log-transformed domain!
\end{enumerate}

\subsubsection{Determining number of clusters}

In the previous section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
In practice, this is not the case. This section will describe how the issue is to be tackled.

The basic idea is to start with an assumption that the whole area is homogeneous.
Then such an assumption is put to test using the hypothesis testing procedure described earlier. 
If the assumption appears to be violated, the area is broken down by introducing a new cluster center. 
The clustering algorithm is again performed and the new clusters are again assumed to be homogeneous, and tested. 
The process iterates until all partitions are confirmed to be homogeneous. 
The pseudo code for such a procedure is given in Listing \ref{lst:k_mle_algo_partition_number}

\lstset{language=Matlab,caption=Homogenous partitions number growing,label=lst:k_mle_algo_partition_number}
\definecolor{darkgray}{rgb}{0.95,0.95,0.95}
\lstset{backgroundcolor=\color{darkgray}}
%\begin{figure}
%\begin{verbatimtab}
\begin{lstlisting}[frame=tb]
function centers = partition_into_homogenous_groups(l, threshold)
  c_init = maximum_likelyhood_of(l);
  [further_partition_needed, c_new] = 
          check_homogeneity_status(l, c_init, threshold);

  while (further_partition_needed) do
    c_prev = c_new;
    c_new = k_mle_cluster(l, c_prev);
    [further_partition_needed, c_new] = 
            check_homogeneity_status(l, c_prev, threshold);    
  end while
  %after this: all paritions are homogenous

  return centers = c_new; 
end function

function [further_partition_needed, c_new] 
              = check_homogeneity_status(l, c, threshold_vector);

  m[i,j] = get_membership_assigments(l, c);
  all_partitions_homogenous = true;
  c_new = c;
  for (j = 1 to size_of(c)) 
    g = {L[i] with m[i,j]==1};
    this_partition_homogenous = 
      (variance(g) < threshold_vector[size_of(g)]);

    if (NOT this_partition_homogenous) then
      % split non-homogenous partition
      c_new[j] = min(g);
      c_new[size_of(c_new) + 1] = max(g);

      all_partitions_homogenous = false;
    end if
  end for

  further_partition_needed = NOT all_partitions_homogenous;
end function
\end{lstlisting}

%\section{Experiment Results and Discussions}%describe analysis and compare
\subsection{Evaluating the kMLE algorithm}
\label{sec:k_mle_result}

\subsubsection{Using the kMLE clustering algorithm for speckle filtering}

It should be noted there is a difference between accepting the null hypothesis and simply failing to reject it. 
However, in the section that follows, the decision rule in use is that if the sample variance is lower than the cut-off value, the null hypothesis is accepted. 
The next analysis shows that for the purpose of speckle-filtering the difference is negligible.

The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastics noise can be removed.
This allows the kMLE clustering algorithm to form the basis of a speckle filtering technique,
  where the results of the clustering algorithm can be transformed into answers for the problem of speckle filter.
Specifically the clustered areas directly serves as the grouping of pixels into homogeneous areas, and the cluster centers serves as the estimated backscattering coefficient for the analysis window.

Let us now consider some extreme threshold-values used as the homogeneous criteria for grouping pixels in the kMLE speckle filter.
If threshold-value is set to a very high value (close to 100\%), then a given partition would almost never be broken down.
The kMLE speckle filter effect would then equals to a box-car filter. 
Conversely, if the threshold-value is set to a very low value (close to 0\%), then a given partition would almost always be broken down to a single value.
The kMLE speckle filtering effect then would be virtually negligible.

Figure \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
Using the same moving window size, here $3\times3$, the effect of filtering is apparently proportional to the threshold values employed:
  with sub-figures \ref{fig:k_mle_threshold_original} to \ref{fig:boxcar_filter} visualise qualitatively the effects of the kMLE speckle filter when the threshold is set at 0\% (or left untouched), 25\%, 80\% and 100\% (or equals to the boxcar filter) respectively.

%	Fig. \ref{fig:k_mle_threshold_original} shows the original intensity image the speckle left untouched (0\%), 
%	Fig. \ref{fig:k_mle_threshold_25pc} and Fig. \ref{fig:k_mle_threshold_80pc} visualise qualitatively the effects of the k-MLE filter when the threshold is set at 25\% and 80\% respectively, 
%	while Fig. \ref{fig:boxcar_filter} shows that too much filtering (boxcar, i.e. 100\%) may lead to blurring effects.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[intensity image]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/scene2_intensity.eps}
		 %\epsffile{images/scene2_log_intensity.eps} 	
		 \label{fig:k_mle_threshold_original}
	}
	\hfill
	\subfloat[3x3 25\% k-MLE filter]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_04.eps}
		 %\epsffile{images/scene2_log_intensity.eps} 	
		 \label{fig:k_mle_threshold_25pc}
	}  \\
	\subfloat[3x3 80\% k-MLE filter]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_03.eps}
		 %\epsffile{images/scene2_filtered_LTH_config_02.eps} 	5x5 k-MLE blur
		 \label{fig:k_mle_threshold_80pc}
	}
	\hfill
	\subfloat[3x3 boxcar filter]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/boxcar_3x3.eps} %images/boxcar_5_blur.eps}
		 \label{fig:boxcar_filter}
	} 
\end{tabular}
\caption{Speckle filtering effects by various threshold-value}
\label{fig:k_mle_diff_threshold}
\end{figure}

One way to improve the speckle suppression effect is by working on a larger window size. 
To reduce the associated blurring effect,
  a lower threshold-value than 100\% compared to the box-car filter would help
    by providing an adaptive partitioning of the analysis window.
Figure \ref{fig:k_mle_iterative_vs_boxcar} shows the visual performance of k-MLE filtering on $5 \times 5$ window.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[5x5 boxcar]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/boxcar_5x5.eps}
		 %\epsffile{images/scene2_log_intensity.eps} 	
		 \label{fig:boxcar_5x5}
	} 
	\hfill
	\subfloat[5x5 k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_02.eps} 	
		 \label{variance}
	} 
\end{tabular}
\caption{Blur effects of larger window size}
\label{fig:k_mle_iterative_vs_boxcar}
\end{figure}

%\subsubsection{Quantitative Evaluation in Log-Transformed domain}

Another way to improve the raw kMLE speckle filter is to apply it iteratively.
As can be seen in figure \ref{fig:k_mle_diff_threshold}, a normal 3x3 k-mle filter would not filter as much noise as a similar boxcar filter would. 
At the same time, a 5x5 boxcar filter while having better speckle suppression power, would lose out by the blurring effects (see Fig. \ref{fig:boxcar_5x5}). 
To improve k-MLE filtering power while avoiding the blurring effect, the kMLE speckle filter can be used iteratively. 
Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a 3x3 window with 25\% threshold-value, being applied iteratively for four times. 
%The filtering power is illustrated and the plot shows similar performance with a 5x5 boxcar filter, while the filtered image is rendered with much less blurring effect.
From the plot, the $3 \times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5 \times 5$ boxcar filter,
  while its visual imagary output appears much sharper, qualititatively speaking.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[3x3 25\% 4 iteration k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_01.eps}
		 \label{variance}
	} 
	\hfill
	\subfloat[Homogenous Error in log-domain]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/k_mle_filter_homogenous_performance.eps}
		 %\epsffile{images/scene2_filtered_LTH_ENL.eps} 
		 \label{variance}
	} 
\end{tabular}
\caption{Improving Homogenous error with iterative k-MLE filter}
\label{fig:k_mle_filtering_power}
\end{figure}

\subsubsection{Evaluation of the kMLE speckle filter on Simulated targets}

A number of point targets were simulated on a homogeneous background clutter. 
The ground truth SNR between the target and background clutter is fixed at 9dB. 
The original, speckled images are presented in Figure \ref{fig:sar_point_target_test_boxcar_k_mle}.
Subsequently, the kMLE speckle filter is to be benchmarked against the standard boxcar filters.
%Both qualitative and quantitative comparisons is done between boxcar filters and the proposed iterative k-MLE filter.
Qualitatively speaking, it is apparent that the kMLE speckle filter delivers
a resultant image with both sharper edges than the 5x5 boxcar filter and a stronger visual contrast  than the 3x3 boxcar filter.
%a sharper image than the 5x5 boxcar filter, at the same time its result has better contrast than the 3x3 boxcar filter.
Quantitatively, the k-MLE also appears to have the best histogram response, of all the 3 filters compared.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[5x5 boxcar filter]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/point_target_5x5_boxcar_filtered.eps}
		 \label{intensity}
	}
	\hfill
	\subfloat[iterative k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/point_target_iterative_k_mle_filtered.enhanced.eps}
		 \label{variance}
	} \\ 
	\subfloat[3x3 boxcar filter]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/point_target_3x3_boxcar_filtered.eps}
		 \label{intensity}
	}
	\hfill
	\subfloat[histogram response]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/point_target_histogram_preservation.eps}
		 \label{variance}
	} 
\end{tabular}
\caption{Qualitative evaluation on point targets }
\label{fig:sar_point_target_test_boxcar_k_mle}
\end{figure}

\subsubsection{Evaluation of the kMLE speckle filter on Real Images}

The filters are applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
Apparently the kMLE speckle filter delivers a significantly ``better'' image than the original data.

\begin{figure}[h!]
\centering
\begin{tabular}{c}
	\subfloat[urban: intensity image]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/scene2_intensity.eps}		  	
		 \label{intensity}
	}
	\hfill
	\subfloat[urban: 3x3 iterative k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene2_filtered_LTH_config_01.eps}
		 \label{variance}
	} \\ 
	\subfloat[natural: intensity image]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		  \epsffile{images/scene_natural_intensity_image.eps}
		 \label{intensity}
	}
	\hfill
	\subfloat[natural: 3x3 iterative k-MLE]{
		 \epsfxsize=2.5in
		 \epsfysize=2.5in
		 \epsffile{images/scene_natural_iterative_k_mle_filtered_image.eps}
		 \label{variance}
	} 
\end{tabular}
\caption{Qualitative evaluation on urban and agricultural areas}
\label{fig:k_mle_on_RADARSAT2_data}
\end{figure}

\section{SAR Speckle filtering using the consistent measures}

\begin{tabular}{c c}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:boxcar}
f_{boxcar} = \displaystyle{\sum_{i=1}^n{I_i}} / n 
\end{equation}
\end{minipage}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:kmle}
f_{kMLE }= \displaystyle{\sum_{i=1}^k{I_i} } / k 
\end{equation}
\end{minipage}
\end{tabular}

\subsection{The FMLE SAR Speckle Filters}

SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
The principle of many speckle filters in removing stochastic noise is to group data into homogeneous areas.
In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$n$ is the total number of pixel in the surrounding areas.
The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
In a filter previously proposed by the authors \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
where 
	$I_i$ is the intensity value of pixel \textit{i} and
	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.

\begin{tabular}{c c}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:boxcar}
f_{boxcar} = \displaystyle{\sum_{i=1}^n{I_i}} / n 
\end{equation}
\end{minipage}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:kmle}
f_{kMLE }= \displaystyle{\sum_{i=1}^k{I_i} } / k 
\end{equation}
\end{minipage}
\end{tabular}

By and large, while it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
  the concept of ``homogeneous area'' lacks precise definition and boundaries.
This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.

This paper presents a different approach, that of fuzzy logic.
Fuzzy logic embraces truth values that range from 1 to 0, 
	instead of fixing on a rigid two-member set of logical values (i.e. true and false).
Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability, in contrast to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.

The idea presented in this paper is structured as follows:
Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
Finally, Section \ref{sec:conclusion} concludes this paper.
%The last section will offers some conclusion and finalizes the paper.

The foundation of the approach is the consistent sense of distance found in the log-transformed domain.
It is shown in \cite{Le_2010_ACRS} that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.

Log transformation is defined as:
${L_I}^i = \log_2{(I^i)}$ 
where 
	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
	$L_I^I$ is the value of that sample in the log-transformed domain.
%Distance in log-transformed domain is defined as:
Log domain distance is defined as:
$D= L_I^1 - L_I^2$. 
Assumming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
  then distance will follow the distribution 
$pdf(D)= \frac{2^D}{(1+2^D)^2} \ln2$,
  which is consistent.
The analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.

\subsubsection{FMLE Estimation}

Using a fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
$p_i = pdf(D_i)$, with $D_i=log_2(I_i) - log_2(I_0)$.
We then propose a new approximation given in Eqn. \ref{eqn:fmle_incl}

%We will see how this works in an homogeneous simulated area.
%The figures demonstrate speckle being filtering effects.
In implementating this estimator, we noticed there are visible black dots in the filtered image.
These dots can be explained as the long-tailed nature of the intensity PDF, 
  which manifests itself in the significant existence of very small values in the population.
In the all-inclusive scheme, this will results in 
	a single $D_0=0$ (at $I_0$) and other very large $D_{i, (i > 0)}$, hence
	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
This marginalises the filtering power of surrounding pixels.
An option is to exclude the centre point $I_0$ from its estimation (see Eqn. \ref{eqn:fmle_excl})

\begin{tabular}{c c}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:fmle_incl}
FMLE_{incl}= \frac{\displaystyle{\sum_{i=0}^n{p_i * I_i} } }{\displaystyle{\sum_{i=0}^n{p_i } } }
\end{equation}
\end{minipage}
\begin{minipage}[c]{0.45\textwidth}
\begin{equation}
\label{eqn:fmle_excl}
FMLE_{excl}= \frac{\displaystyle{\sum_{i=1}^n{p_i * I_i} } }{\displaystyle{\sum_{i=1}^n{p_i } } } 
\end{equation}
\end{minipage}
\end{tabular}

%\subsection{Comparing the two schemes}
Both filters are applied to an simulated single-look homogeneous scene 
and the histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original}.
The filtering power is clearly visible.
%demonstrated in Figure \ref{fig:compare_filters_histograms:Original}. 
In comparing the two schemes' histogram in the same figure, it appears that 
	the filtering power of ignoring centre point scheme is at least as powerful as that of centre point included scheme and
	the skewness in the histogram of the ignoring scheme is also appearing less than that of the included scheme.

\begin{figure}[H]
\centering
\subfloat[Intensity histogram]{
  \epsfxsize=6cm
  \epsfysize=6cm
  \epsffile{images/consistent_contrast_log_domain.made.eps}
\label{fig:consistent_contrast_log_domain}
  }
\caption{Consistent Distance Property and the FMLE Estimations}
\end{figure}

\begin{figure}[H]
\centering
\begin{tabular}{c}
\subfloat[Intensity histogram]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/compare_filters_histograms.3.made.eps} 
\label{fig:compare_filters_histograms:Original}
	}
        \hfill 
	\subfloat[Distance histogram]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/compare_filters_distance_histograms.3.made.eps} 
\label{fig:compare_filters_distance_histograms:Original}
	}\\ 
 	\subfloat[FMLE (incl) outputs\label{fig:compare_filters_distance_histograms:Filtered:incl}]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/consistency_preservation.d_incl.made.eps} 
	} \hfill
	\subfloat[FMLE (excl) outputs\label{fig:compare_filters_distance_histograms:Filtered:excl}]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/consistency_preservation.d_excl.made.eps} 
	} 
\end{tabular}
\caption{Consistent Distance Property and the FMLE Estimations}
\label{fig:Consistent_Distance_Property_and_the_FMLE_Estimations}
\end{figure}

\subsubsection{Preservation of Distance Histogram Consistency}

Fig. \ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the distance histograms found in the outputs of applying FMLE filters on the inputs depicted in Fig. \ref{fig:compare_filters_histograms:Original}.
They clearly demonstrate that the filtering treatment described above preserves the consistent sense of distance.
This can be explained from the consistent histogram of the fuzzy possbilistic probabilities.
Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
This renders the task of giving analytical PDF impractical.
However, large scale computer simulations can provide a practical histogram, from which the PDF can estimated.
%from large scale simulations. 
%Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
Given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.

\subsubsection{Recursively Applying Fuzzy MLE Filter}

The preservation of consistent distance property is the enabling factor that allows the recursive use of FMLE filters.
Additional applications of the filtering process can be expected to reduce the random noise variance even further.
In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.

In the subsequent application of the filtering algorithm, the main different when compared with the filters in initial iteration is the way the new fuzzy probabilities being calculated.
This subsequent computation of fuzzy probabilities is based on the derived distance PDF, being computed in the previous section.
This process is iterated iteratively, with the histogram obtained from the previous iteration serves as probabilistic distance PDF input of the subsequent application of the filter.
This scheme allows speckle to be further depressed, as illustrated in Fig. \ref{fig:plot_incl_distance_pdf_by_iterations}

\begin{figure}[h!]
\centering
	\subfloat[FMLE (incl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (incl): 456]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
	} 
	\subfloat[FMLE (excl): 123]{
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.123}
	}
	\subfloat[FMLE (excl): 456]{          
		 \epsfxsize=3.5cm
		 \epsfysize=3.5cm
		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
		 \label{fig:plot_excl_distance_pdf_by_iterations.345}
	}
\caption{Iteratively Improving in Distance Histograms}
\label{fig:plot_incl_distance_pdf_by_iterations}
\end{figure}

The log-transformed domain provides a consistent sense of distance.
By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available scene and computational power, is sufficiently large.
For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
They also exhibit good correlation between the MSE and the AUC index.

\subsection{Evaluating the FMLE SAR speckle filters}

Estimators are evaluated based on the bias and variance properties of their estimates. 
The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.

The nature of SAR speckle is that
	it is stochastic even if the underlying radiometry is constant. 
And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
Estimators are typically evaluated based on the bias and variance properties of their estimates:
  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, our survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
	performance. 
As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
Some papers do present quantitative measurements. 
However, due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

The performance of speckle filters are normally evaluated based on a few criteria \citep{Nyoungui_2002_IntlJRemoteSense}.
The most widely used criteria is speckle suppression, 
  which is often evaluated over homogeneous area.
The other important criteria include radiometric preservation, something undeniably desirable in the filtered output.
In practical terms, the most common usage of speckle filtered imagery include target and feature detection and classification.
We highlight the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs.
We then show that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
%As is customary, we start by an visual evaluation of the filter on real-life images.
We start with visual evaluation of the filters on real-life images.

\subsubsection{Qualititative Evaluation on Real Images}

The filters are applied to a SLC RadarSat 2 image covering the Muda Merbok area of Malaysia.
Fig. \ref{fig:fmle.real.images} shows the patches of original and filtered images of both natural and urban landscape.
The filtering effects are clearly visible.
Apparently the second iteration outputs appears much better than the initial iteration, and offer roughly the same level of performance in comparision to that of boxcar filter.

\begin{figure}[h!]
\centering  
      \begin{tabular}[h]{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter0.made.eps} 
		 \label{fig:fmle.natural.incl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.natural.3x3.made.eps} 
		 \label{fig:boxcar.natural}
	}\\
	\subfloat[FMLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter1.made.eps} 
		 \label{fig:fmle.natural.incl.iter1}
	} \hfill
	\subfloat[FMLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.incl.iter2.made.eps} 
		 \label{fig:fmle.natural.incl.iter2}
	} \\
	\subfloat[FMLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter1.made.eps} 
		 \label{fig:fmle.natural.excl.iter1}
	} \hfill
	\subfloat[FMLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.natural.excl.iter2.made.eps} 
		 \label{fig:fmle.natural.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Natural Surface}
\label{fig:fmle.real.images}
\end{figure}

\begin{figure}[h!]
\centering  
      \begin{tabular}{c}
	\subfloat[Original]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter0.made.eps} 
		 \label{fig:fmle.urban.excl.iter0}
	} \hfill
	\subfloat[Boxcar]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/boxcar.urban.3x3.made.eps} 
		 \label{fig:boxcar.urban}
	} \\
	\subfloat[FMLE incl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.incl.iter1.made.eps} 
		 \label{fig:fmle.urban.incl.iter1}
	} \hfill
	\subfloat[FMLE incl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.incl.iter2.made.eps} 
		 \label{fig:fmle.urban.incl.iter2}
	} \\ 
	\subfloat[FMLE excl, iter 1]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter1.made.eps} 
		 \label{fig:fmle.urban.excl.iter1}
	} \hfill
	\subfloat[FMLE excl, iter 2]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/fmle.urban.excl.iter2.made.eps} 
		 \label{fig:fmle.urban.excl.iter2}
	} 
	\end{tabular}
\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Urban Landscape}
\label{fig:fmle.real.images}
\end{figure}

\subsubsection{Evaluating Speckle Suppression Effects}

We have found that MSE in the log-transformed domain is related to the standard Equivalent Number of Look value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing MSE, as plotted in Fig. \ref{fig:Homogeneous_Area}

\begin{figure}[h]
\centering
 \epsfxsize=6cm
 \epsfysize=6cm
 \epsffile{images/verify_MSE_as_perf_index.made.eps} 
\end{figure}

\begin{figure}[h]
\centering
      \begin{tabular}[h]{c}
	\subfloat[MSE (incl, 3x3)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.incl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.incl}  
	} \hfill
	\subfloat[MSE (excl, 3x3)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.excl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.excl}
	} \\
	\subfloat[MSE (incl, 5x5)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.5x5.incl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.incl.5x5}
	} \hfill
	\subfloat[MSE (excl, 5x5)]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/distance_pdf_simulation_iterative.5x5.excl.made.eps} 
		 \label{fig:distance_pdf_simulation_iterative.excl.5x5}
	}
     \end{tabular}
\caption{Homogeneous Area: MSE criteria and speckle suppression power of FMLE filters}
\label{fig:Homogeneous_Area}
\end{figure}

\subsubsection{Evaluating Target Detection Performance}

The normal application after applying filters on SAR images is to detect the existence of certain target within its surrounding clutters.
%Assume the 
The most common type of detector (or classifier) employs a threshold based approach in determing whether an abnormal value signifies the existence of a target.
The Receiver Characteristic Curve (ROC) and the area under it (AUC) is typically used to evaluate the detectability of target features \citep{Mazurowski_2009_IJCNN}.

It is normally claimed that applying speckle filters increases the performance of subsequent target detection tasks.
The following experiment illustrates this point.
In this experiment, we apply a simple 3x3 boxcar filter to two different homogeneous and SLC noise corrupted scenes that are known to be 3dB apart.
And then the histograms as well as the resulting ROC curve are plotted between the pairs of target and background histogram in the two cases of unfiltered and filtered data.
We noted that the ROC curve for the histograms in original domain matches perfectly with ROC for the histograms in the log-transformed domain (see Fig. \ref{fig:PDF_Discriminality}), as expected from theory.

\begin{figure}[h]
\centering
      \begin{tabular}[h]{c}
 	\subfloat[SLC Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look Intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:illustrate_ROC_curve.pdf.m.made.eps}
	} \\
 	\subfloat[SLC log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.s.made.eps}
	} \hfill
	\subfloat[9-Look log-intensity]{
		 \epsfxsize=6cm
		 \epsfysize=6cm
		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
		 \label{fig:log_illustrate_ROC_curve.pdf.m.made.eps}
	}
   \end{tabular}
\caption{Histogram Discriminality and the ROC Curve}
\label{fig:PDF_Discriminality}
\end{figure}

%\subfloat[Invariant ROC Curve]{
\begin{figure}
 \epsfxsize=6cm
 \epsfysize=6cm
     		 \epsffile{images/log_illustrate_ROC_curve.made.eps} 
		 \label{fig:illustrate_ROC_curve.roc}
  \caption{Invariant ROC Curve}
\end{figure}

The most common types of target to be detected in image processing are point targets, line targets, and edge targets.
The detectability of the targets are measured using the AUC index which is tabulated against the MSE.
Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of FMLE filters for heterogenous regions.
Even though the relationship is probably not linear,
  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
Also FMLE filters apparently have better performance than boxcar filters.

\begin{figure}[h!]
\begin{minipage}[c]{0.5\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{figure}
%\centering
	\subfloat[Point Target]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/641bcaad-f54b-4bb6-8d10-77784da522a5.made.eps} 
		 \label{fig:point_target_pattern}
	}
	\subfloat[Edge]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/c5124949-1228-4749-a99e-caf9430e400a.made.eps} 
		 \label{fig:edge_pattern}
	}\\
	\subfloat[Line]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/a2e330a8-3deb-4328-94d8-d18c43e4f7a1.made.eps} 
		 \label{fig:line_pattern}
	}
	\subfloat[Dotted Pattern]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/38e79d4c-af61-4b1f-acc2-528ecedb96a7.made.eps} 
		 \label{fig:dotted_pattern}
	}
%\caption{Simulated Heterogeneous Patterns}
%\label{fig:distance_pdf_simulation_iterative}
%\end{figure}
\end{minipage}
%} & 
\begin{minipage}[c]{0.38\textwidth}
%\captionsetup[subfigure]{labelformat=empty}
%\subfloat[]{%
%\captionsetup[subfigure]{labelformat=parens}
%\begin{table}
%\centering
\begin{tabular}{|l|l|l|l|}
\hline
Scene 				& Filter 						& MSE 	& AUC \\
\hline
Point Target 	& FMLE (incl, 3x3) 	& 1.38	& 0.901 \\
Point Target 	& FMLE (excl, 3x3) 	& 1.47	& 0.893 \\
Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
Point Target 	& boxcar (5x5) 			& 2.67	& 0.502 \\
\hline
Edge 	& FMLE (incl, 3x3) 	& 0.68	& 0.969 \\
Edge 	& FMLE (excl, 3x3) 	& 0.73	& 0.964 \\
Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
Edge 	& boxcar (5x5) 			& 1.51	& 0.934 \\
\hline
Line 	& FMLE (incl, 3x3) 	& 1.89	& 0.791 \\
Line 	& FMLE (excl, 3x3) 	& 2.02	& 0.767 \\
Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
Line 	& boxcar (5x5) 			& 2.88	& 0.375 \\
\hline
Dotted 			& FMLE (incl, 3x3) 	& 2.28	& 0.639 \\
Dotted 			& FMLE (excl, 3x3) 	& 2.32	& 0.621 \\
Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
Dotted 			& boxcar (5x5) 			& 3.35	& 0.382 \\
\hline
\end{tabular}
%\caption{The MSE \& ROC indices are correlated}
%\end{table}
\end{minipage}
%}
%\end{tabular}
\caption{Heterogeneous Patterns: MSE criteria and FMLE performance}
\label{fig:Heterogeneous_Patterns}
\end{figure}

\subsubsection{Contribution and Conclusions}

The nature of SAR speckle is stochastic. 
The speckle filtering problem has been casted into a statistical estimation theory framework. 
Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
Various negative effects of heteroskedasticity are discussed. 
Log-transformation is shown to provide homoskedasticity in statistical models. 
Using speckle filtering as an applicative example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.

The speckle filtering technique proposed here has been shown to work for single-look SAR images. 
Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
The filter is developed from an easy to understand winner-take-all clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
Should the fuzziness be taken to a new level, an optimal fuzzy probabilistic filter which requires no clustering may be specified and designed.

\section{Evaluating SAR Speckle Filters using the consistent measures}

To do quantitative evaluation of different speckle filters, it is necessary to compare a filtered image with a ground-truth one. 
Furthermore, it is desirable that the error, i.e. the distance between the filtered output and the original input, should be consistent and independent to the particular simulated scenario. 
Normally, the measure of choice is in the original SAR intensity or amplitude domain. 
However owing to the homoskedastic effects of the log-transformation, the error in log-transformed domain is preferred.

Homoskedasticity makes ordinary least square (OLS) approaches becomes valuable again. 
Synonymous to OLS is the use of standard Mean Squared Error as a performance index.

\begin{equation}
\Psi = \displaystyle{ \frac{ \sum^N_{i=1}{(Y^L_i - X^L_i)^2} }{N} }
\end{equation}
where $Y^L_i$ indicates filtered output values and $X^L_i$ denotes the original input as ground-truth values, $N$ is the number of data points available

This section will shows that in a homogeneous area, this performance index is similar to the standard Equivalent Number of Looks (ENL) measures, while investigating the value in heterogeneous areas shows how well the filter adapts to underlying spatial variations.

%\section{Using MSE to evaluate SAR speckle filters}

The nature of SAR speckle is that
	it is stochastic even if the underlying radiometry is constant. 
And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
Estimators are typically evaluated based on the bias and variance properties of their estimates:
  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	prompting alternative evaluation criteria to be proposed.
In fact, our survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
	performance. 
As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
Some papers do present quantitative measurements. 
However, due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

\subsection{ Speckle Filtering Process And The Homoskedastic Log-transformed Domain}
\label{sec:schema_log_images}

\begin{figure}[h]
 \centering
 \epsfxsize=2.4in
 \epsfysize=1.2in
 \epsffile{images/simulation_schema.eps} 	
\caption{SAR simulation, processing and filtering schema}
\label{fig:simul_process_filter_schema}
\end{figure}

Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and 
SAR speckle filtering process.
The ``SAR processor'' block indicates that either one of the following processes can occur.
First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded 
in $\tilde{X}$. Second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known 
ground-truth pattern $X$.
%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.

The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
	which takes the noisy speckled SAR data $\tilde{X}$ as input
	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
The speckle filters used in this paper are: 
	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter 
	and PDE filter \cite{You_TIP_2000}.
Evidently for the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
%Thus $MSE_{residual}^{none} = MSE_{base}$

Logarithmic transformation offers several consistent measures of distance, which is hypothised to be 
significant in evaluating speckle filters.
	A case in point is in visual evaluation of filtered results obtained from real captured SAR images.
Since the radiometric ground-truth is not available, %the most common 
%In real SAR captured images, the radiometric ground-truth normally is not available.
	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
A conventional method is to investigate the ratio images between the filtered output and the noisy input images.
Since logarithmic transformation converts these ratio into substractive residual which are consistent, residual 
analysis can be used to analyse and evaluate the performance of speckle filters.
%To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, 
For visual comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
and the ratio images in the original domain, where a simple boxcar filter has been applied to data obtained from a 
real RADARSAT SAR image.
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in 
the ratio images, although this conclusion is of course itself a subjective one.

%Our qualititative conclusion is that
%	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
%	b. even so, the above conclusion is at best quite subjective.
%Thus to compare the filters against each other, 
%	quantitative measures are preferred.

\begin{figure}
\centering  
\begin{tabular}{c}
	\subfloat[Original Patch]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Filtered Result]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.boxcar.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Ratio: Filtered / Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.ratio2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Ratio: Original / Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.ratio1.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[Log Residual: Filtered - Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.residual2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Log Residual: Original - Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_real.residual1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
\caption{Visualising Removed ``Noise'': Ratio images in the original domain vs. Residual images in the log-transformed domain}
\label{fig:real_image_ratio_vs_residual}
\end{figure}

\begin{subequations} \label{eqn:eval_metric}
\begin{align}
MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
\end{align}
\end{subequations}
%\begin{eqnarray}
%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
%\end{eqnarray}

As qualititative visual evaluation is subjective by nature,
	quantitative metrics and measurements are preferred, if relevant and possible.
Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, 
are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
When ground-truth is available, 
	either in simulated experiments or over homogeneous area where it can be reasonably estimated, 
	true MSE is the expected squared error between the estimated and true values.

However, in real captured SAR images where such ground truth is unknown, the evaluation can then be carried out 
through a benchmarked MSE. 
The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ 
can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be 
estimated reasonably well.
Thus the base MSE level, which is also a measure of the speckle noise level, can also be estimated.
Naturally, the speckle filter should remove as much noise as possible, 
	while it also should not remove more variations than that caused by the speckle noise.
%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base

\subsection{Evaluating SAR Speckle Filters Over Homogeneous Areas}

%\subsubsection{Evaluating Speckle Filters on Homogeneous Areas}
%\label{sec:eval_homo}

In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is 
illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is 
probably insignificant in comparison to the other components, namely, variance evaluation. 
Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance 
methods of evaluation are shown to be mathematically related to the ENL index.
The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
over homogeneous areas.

\subsubsection{ Estimating ENL from MSE index in homogeneous areas }
\label{sec:homogeneous_theoretical}

In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL 
index. Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
	then the MSE evaluation is reducced to variance evaluation.
That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered 
output in the log-transformed domain.

Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
variables as: 
\begin{equation}
var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
\label{eqn:perf_index_theoretical}
\end{equation}

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus the ENL, i.e. $L$, can be estimated as:
\begin{equation}
\hat{L}_{est} = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and 
corrupted with single look SAR-speckle PDF. 
Different multi-look processing filters are then applied to the image patch. 
The observable variance in the log-transformed domain is recorded, and 
	 ENL is then estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms 
of mean and standard deviation.
The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
	together with the analytical values from Eqn. \ref{eqn:perf_index_analytic}.
These experimental results evidently validate the analysis given above.
They also shows that 
	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect, 
	since ENL is supposed to be an integer, the value obtained actually corresponds very closely with the 
	nearest correct integer result.

\begin{table}[h]
\centering
\begin{tabular}{r|c|c|c|c}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

The finding here may also help to explain other seemingly unrelated results. For example, 
	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ 
	to evaluate scene heterogeneity.

\subsubsection{Using log-variance to evaluate speckle filters}

Fig. \ref{fig:log_consistency_model} plots the histograms of homogenous SAR data over different radiometric values.
Both single-look simulated and multi-look processed/box-car filtered data is displayed.
Specifically the plots show that the log-transformed domain is consistent while the plots from the original 
domain are not.

\begin{figure}[h]
\centering  
\begin{tabular}{c}
	\subfloat[Single Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/orig_inconsistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/orig_inconsistency_boxcar.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Single-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_boxcar.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{The Inconsistency evident in the original SAR domain and the Emerged Consistency demonstrated in the log-transformed domain}
\label{fig:log_consistency_model}
\end{figure}

Fig. \ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) 
preserve this consistency in their filtered output. Intuitively, as the boxcar filter is actually similar to 
multi-look processing, thus its output also does exhibit the this consistency.
This consistency will also lead to the consistent sense of distance described earlier, which is significant 
because it is the tell-tale indicator of the consistent contrast and variance.
This ensures applicability of various target detection/classification algorithms 
which employ statistical properties in the un-filtered data, such as the ratio based discriminator 
in the original domain or the differential based discriminator in the log-transformed domain.

\begin{figure}
\centering  
\begin{tabular}{c}
	\subfloat[Lee filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_lee.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_kuan.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_frost.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Gamma MAP filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/log_consistency_map.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Filtered results: consistency in log-transformed domain}
\label{fig:log_consistency_filters}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|c|r|c|r}
Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
\hline
none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
\hline
none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
\hline
none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
\end{tabular}
\caption{ Filters' Performance: Homogeneous Area }
\label{tab:homogeneous_performance_filters}
\end{table}

Table \ref{tab:homogeneous_performance_filters} provides a quantitative comparison among the filters.
It shows that the filters can all preserve the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard ENL index.

\subsubsection{ Estimating ENL from MSE index in homogeneous areas }

Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
Assuming the filters are unbiased, or the bias is already compensated, i.e. $E(Y^L)=X^L$, then the MSE becomes $\Psi = \frac{ \sum^N_{i=1}{ (Y^L_i - E(Y^L)) } }{N} = var(Y^L)$.
That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in log-transformed domain.

Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variable as: $var(Y^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right)$.

Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $\Psi= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  \Psi = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
\begin{equation}
ENL = \frac{1}{\Psi \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

From the section above, it can be shown that logarithmic transformation of single-look intensity, i.e. $X^L_1$, has a speckle power MSE of $\Psi_1 = var(X^L_1)=\frac{1}{\ln2^2} \frac{\pi^2}{6}$. 
With each additional 1-look in SAR multi-look processing, the speckle power will reduce by:  
\begin{equation}
 \Psi_n = \Psi_{n-1} - \left( \frac{1}{\ln2(n-1)} \right)^2 
\end{equation}
with $n$ being the number of look being averaged.

To verify the above analysis an experiment is carried out.
In the experiment, a known $256\times256$ homogeneous area is generated and is corrupted with SAR-speckle PDF. 
Different multi-look processing filters are repeatedly applied to the patch. 
A performance index is calculated for each simulation with their mean and variances reported. 
The analysis values are calculated from Equation \ref{eqn:perf_index_analytic}, together with estimated ENL from Equation \ref{eqn:enl_analytic}

\begin{table}
\centering

\begin{tabular}{c|c|c|c|c}
No  & Simulation                      &Analysis   &Est ENL       & Perf Index Improved \\% &85\%             &90\%\\
\hline
2   &1.3397 ($0.1036 \cdot 10^{-03}$) &1.3423	 &2.0536	& - \\
3   &0.8201 ($0.0188 \cdot 10^{-03}$) &0.8220	 &3.0379	& 0.5196\\
4   &0.5898 ($0.0217 \cdot 10^{-03}$) &0.5907	 &4.0287	& 0.2303\\
5   &0.4595 ($0.0067 \cdot 10^{-03}$) &0.4607	 &5.0292	& 0.1303\\
6   &0.3764 ($0.0013 \cdot 10^{-03}$) &0.3774	 &6.0291	& 0.0831\\
7   &0.3195 ($0.0073 \cdot 10^{-03}$) &0.3196	 &7.0149	& 0.0569\\
8   &0.2773 ($0.0043 \cdot 10^{-03}$) &0.2771	 &8.0056	& 0.0422\\
9   &0.2448 ($0.0016 \cdot 10^{-03}$) &0.2446	 &9.0010	& 0.0325\\
10  &0.2193 ($0.0015 \cdot 10^{-03}$) &0.2189	 &9.9908	& 0.0255\\
11  &0.1975 ($0.0024 \cdot 10^{-03}$) &0.1981	 &11.0400	& 0.0218\\
12  &0.1807 ($0.0013 \cdot 10^{-03}$) &0.1809	 &12.0157	& 0.0168\\
13  &0.1663 ($0.0004 \cdot 10^{-03}$) &0.1664	 &13.0121	& 0.0144\\
14  &0.1544 ($0.0004 \cdot 10^{-03}$) &0.1541	 &13.9783	& 0.0119\\
15  &0.1435 ($0.0003 \cdot 10^{-03}$) &0.1435	 &15.0075	& 0.0109\\
16  &0.1342 ($0.0003 \cdot 10^{-03}$) &0.1342	 &16.0071	& 0.0093\\
17  &0.1263 ($0.0003 \cdot 10^{-03}$) &0.1261	 &16.9765	& 0.0079\\
18  &0.1189 ($0.0004 \cdot 10^{-03}$) &0.1189	 &18.0085	& 0.0074\\
19  &0.1126 ($0.0006 \cdot 10^{-03}$) &0.1125	 &18.9777	& 0.0063\\
20  &0.1070 ($0.0004 \cdot 10^{-03}$) &0.1067	 &19.9528	& 0.0056\\
21  &0.1016 ($0.0003 \cdot 10^{-03}$) &0.1015	 &20.9847	& 0.0054\\
22  &0.0969 ($0.0004 \cdot 10^{-03}$) &0.0968	 &21.9806	& 0.0047\\
23  &0.0924 ($0.0005 \cdot 10^{-03}$) &0.0925	 &23.0188	& 0.0045\\
24  &0.0885 ($0.0002 \cdot 10^{-03}$) &0.0886	 &24.0214	& 0.0039\\
25  &0.0850 ($0.0001 \cdot 10^{-03}$) &0.0849	 &24.9942	& 0.0035
\end{tabular}

\caption{ ENL: Boxcar Filter's Speckle Suppression Power }
\label{tab:enl_in_log_domain}
\end{table}

%To evaluate the effects of number of looks on performance index, the performance index values for each ENL is computed and listed in table \ref{tab:enl_in_log_domain}. 
%To compare our filter with boxcar filters, the error is reported not only as a single performance index value but also as the whole distribution, depicted as the histogram of error in log-domain, see figure ???. Homoskedastic effects should also make it possible to evaluate performance speckle filter in heterogenous scenes, however such evaluation is outside the scope of current paper.

\subsection{ Evaluating SAR Speckle Filters over Heterogeneous Scenes }
\label{sec:eval_hetero}

Similar to the drop in variance allowing one to estimate the effect of each extra look averages being used over homogeneous areas, rises in the error variance can also be used to gauge the effects of underlying spatial variation on speckle filtering effectiveness. 
In original SAR domain, evaluating speckle filters' response to different heterogeneous areas are difficult, due to heteroskedastic conditions.
In log-transformed domain, thanks to homoskedastic property, MSE will be shown to be relevant in evaluating speckle response to heterogeneous scenes (To be continued).
%An simple 4x4 edge is added into the 256x256 area above, filters are applied and MSE reported.

%\section{Evaluating Speckle Filters on Heterogenous Area}

%For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
%First, several test patterns is created to simulate and determine the performance of various speckle filters.
%Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
%As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.

In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
From a statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
Experimentally, on clear-cut simple target-background patterns, the results that follow will indicate that
	the lower the MSE achievable by a speckle filter,
	the better the feature preservation performance recorded for its output.

%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
%log-transformed domain. 
The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
down into the requirements of radiometric preservation and speckle suppression.
In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
statistical estimators.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.

Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
multiple times, the histograms of the target and background areas can be reliably obtained.
%They are expected to be consistent in log-transformed domain.
The target and background can then be seperated using a simple threshold based classification model.
The separability of the two stochastic populations are judged by the standard ROC, 
	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.

The types of test pattern used in this paper include the followings:
  point targets, line targets, edge targets and a heterogeneous checker board. 
These test patterns could of course be concatenated into a larger composite test image, 
although we will consider them as separate images to allow easier analysis of the results.
%However we would prefer to highlight the results separately for each individual area.
Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention used in the 
radar community where the target is signified by the brighter area of the image. 
Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Line: each line is 2 pixels wide, separated by 6 pixels background]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/pattern_line2.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Edge: each stripe is 4 pixels in width]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/pattern_edge.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Point: each point is a $2 \times 2$ square spacing 6 pixels apart]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/pattern_point.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Checker board: the squares are 4 pixels wide each side]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/pattern_checker.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\centering
\caption{Example windows of ground truth patterns, each $32 \times 32$ pixels in size.}
\label{fig:hetero_patterns}
\end{figure}

Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle. The 
filters are then applied onto these noised images.
From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
evaluated by examining the separability of the two background and target populations.
Subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
	allows visual evaluation of target and clutter histograms and their separability.
Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
respectively, and is measured by computing the Area Under these Curves (AUC).

%visualizes the two histograms
%The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
%	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
%	and is measured by computing the Area Under these Curves (AUC).

\clearpage

\begin{figure}
\centering  
\begin{tabular}{c}
	\subfloat[Simulated Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.edge.none.fi.jpg.eps} 	
		 \label{fig:hetero_patterns_roc_auc:amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filtered Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
		 \label{fig:hetero_patterns_roc_auc:intensity}
	} \\
	\subfloat[Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:hist_unfiltered}
	} 
	\hfill	
	\subfloat[Histograms: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:hist_kuan_filtered}
	}  \\
	\subfloat[ROC: Unfiltered, AUC=0.738]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:roc_unfiltered}
	} 
	\hfill	
	\subfloat[ROC: Kuan Filtered, AUC=0.885]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:roc_kuan_filtered}
	} 
\end{tabular}
\caption{Target and Clutter Separability: Histograms and resulting ROC Curve visualisation}
\label{fig:hetero_patterns_roc_auc}
\end{figure}

Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' separation capability.
In pre-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the seperability of clutter and target populations depends only on the variance of the additive noise. 
This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance), 
the better the separation capability.

In post-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

%Also the speckle suppression is related to the measured variance.
Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
evaluate the separability of the two histograms. 
Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and 
patterns.
It shows that the MSE is inversely correlated to this separability index.
The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
The results suggest that the lower MSE achievable by the filters would, in general, lead to better feature preservation.

\begin{figure}
\centering  
\begin{tabular}{c}
	\subfloat[Error Image: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.edge.none.gt.jpg.eps} 	
		 \label{fig:hetero_patterns_mse:amplitude}
	} 
	\hfill	
	\subfloat[Error Image: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
		 \label{fig:hetero_patterns_mse:intensity}
	} \\
	\subfloat[Error Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
		 \label{fig:hetero_patterns_mse:unfiltered}
	} 
	\hfill	
	\subfloat[Error Histograms: Kuan-filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
		 \label{fig:hetero_patterns_mse:kuan_filtered}
	}  
\end{tabular}
\caption{Bias Error Investigation: Image and Histogram Visualisation}
\label{fig:hetero_patterns_mse}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline
\end{tabular}

\caption{Lower MSE suggest better feature detection, measured by the AUC index}
\label{tab:mse_auc_in_log_domain}
\end{table}

\begin{table}
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
\label{tab:mse_auc_corr_coeff}
\end{table}

\subsection{Using MSE to find the most suitable speckle filter for practical SAR images}
\label{sec:practical_conjecture}

In this section, our conjecture
%(??? you want to emphasize this is a proposal that can't be proven mathematically ?)
%ans: it is true that the conclusion cannot be proved, due to lack of absolute ground truth in real SAR images
%our conclusion however is 1. extended from a simulations which is believed to be in agreement with realities.
of using MSE in the log-transformed domain to find the most suitable speckle filter 
for practical real-captured SAR images is described.
In these scenarios, the ground-truth, and hence the true MSE, is not available.
Therefore, only the residential MSE is computable.
Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark 
MSE is also measurable.	
Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters 
for a captured SAR image, where the ground-truth and hence true MSE is not available.
Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its 
removed variation being closest to the inherent speckle noise.

Experimental results are presented as empirical evidence supporting the conjecture.
The experiments in the previous sections are repeated on single-look SAR images 
	which are simulated from given ground-truth aerial images. 
%The a heuristic rule is that 
%	if the best filtered results are those with minimal MSE 
%	then just by observing the residual MSE, 
%	the observable measure of these results will also achieve 
%		being the closest to the MSE of the inherent noise.
%Besides using visual evaluation to validate the conjecture, 
%	the full justification of this conjecture is outside the scope of this paper.
%Real images however are more complex than the patterns illustrated above. 
Then the filters are applied onto the simulated SAR images. 
Fig. \ref{fig:real_simulated_images} illustrates some of the images used for our experiments.

\begin{figure}
\centering  
\begin{tabular}{c}
	\subfloat[A Rural Area in Vietnam]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[A Suburb of Ha Noi]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/simulated_images.hanoi_suburb.gt.jpg.eps} 	
		 \label{intensity}
	} %\\
%	\subfloat[NTU Campus]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/Aerialcampus.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[Chu Thap Island of Vietnam]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/fiery.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
\caption{Ground Truth Images for simulation}
\label{fig:real_simulated_images}
\end{figure}

With the use of MSE being validated from previous experiments, 
	the most suitable filter can be considered as the one with the lowest true MSE.
Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
	the most suitable filter is also the filter that 
		has its observable residual MSE value being closest to the noise MSE (4.1167 in the case of this example).
%We validate the idea by qualititative evaluation, an example of 
The conjecture is also validated using visual evaluation, an example of
	which is presented in Fig. \ref{fig:real_simulated_image_results}.

\begin{table}
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
Vietnam rural	& none		& 4.1174	& 4e-35\\
Vietnam rural	& pde			& 3.8022	& 0.0368\\
Vietnam rural	& lee			& 0.4984	& 3.2555\\
Vietnam rural	& frost		& 0.3490	& 4.6856\\
Vietnam rural	& kuan		& 0.3396	& 3.6877\\
Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
Hanoi suburb	& none		& 4.1321	& 4e-35\\
Hanoi suburb	& pde			& 3.8004	& 0.0391\\
Hanoi suburb	& lee			& 0.5261	& 3.2598\\
Hanoi suburb	& frost		& 0.3811	& 4.7427\\
Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
\label{tab:mse_true_noise_log_domain}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[Ground-Truth Image ]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{images/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Simulated Real Images: Qualititative Validation}
\label{fig:real_simulated_image_results}
\end{center}
\end{figure}
%\end{figure*}

The results from the experiments in previous sections can also be used to validate the use of residual and 
benchmark MSE.
The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly 
correlated with feature classification capability, measured by the standard AUC index.

The conjecture is also validated in real SAR images.
Different speckle filters are applied onto a real RADARSAT-2 image.
In this case, since the ground-truth is not available, 
	only visual evaluation can be used to validate our conjecture.
Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE 
would probably suggest a more suitable filter.
Fig. \ref{fig:real_image_results} tends to confirm this visually.
%IVMThe conclusion in this can be found through further experiments with more images, 
%IVM	which cannot be shown here due to space limitation.

\begin{table}
\centering
\begin{tabular}{c|r|r}
Filter & $MSE_{residual}$ & $MSE_{benchmark}$\\
\hline
pde & 0.2583 & 3.8584 \\
map & 2.6936 & 1.4231 \\
kuan & 3.3924 & 0.7243 \\
lee & 3.4172 & 0.6995 \\
boxcar & 3.6918 & 0.4249 \\
frost & 4.1191 & 0.0024 \\
\hline
none & $MSE_{base}$ & 4.1167 
\end{tabular}
\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
\label{tab:mse_in_real_image}
\end{table}

\begin{figure}
\begin{tabular}{c}
	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/heterogenous_real.log.image.pde.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/heterogenous_real.log.image.map.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/heterogenous_real.log.image.lee.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
		 \epsfxsize=3cm
		 \epsfysize=3cm
		 \epsffile{images/heterogenous_real.log.image.frost.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}
\caption{Filtering Real Images: Smaller $MSE_{benchmark}$ suggests visually better images}
\label{fig:real_image_results}
\end{figure}

\subsection{Discussion and Conclusions}

\subsubsection{Discussion}

Although it is widely known that log transformation transforms multiplicative SAR speckle into additive noise, 
	one should note that the noise is not Gaussian. In fact, figures presented in the previous sections show that 
	they are not even centered around the origin. 
This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
	work very well in practice.
To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
	is suggested \cite{Le_2011_ACRS}. Interestingly, averaging is also the MLE operator in the SAR's original domain.

Log transformation also brings about a few consistent measures of dissimilarity.
	This consistency can be found in single-look or multi-look SAR data, 
	as well as in filtered outputs of various ``standard'' speckle filters.
This allows a variety of target detection/classification algorithms
  - which exploit these consistent statistical properties -
  to not only perform brilliantly on pre-filtered data,
  but also be found practically working on post-filtered data.

These consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
For example, in the subsequent tasks of designing target detectors or classifiers,
  it is normally desirable for the solution to work on both unfiltered and post-filtered SAR data.
In such cases, these consistent dissimilarity measures found in the log-transformed domain could provide a sound theoretical
	basis. In fact, a number of proposed solutions have already appeared to exploit this feature. 
A case in point is the simple ratio based discriminator in the original SAR domain.
Looking backwards, in designing new speckle filters,
  by ensuring that the filtered output preserves these consistent properties,
	the newly designed filters would be eligible to be employed as pre-processing step for properly designed classifiers / detector.
From a higher level perspective, the applicability of Gauss-Markov theorem and consequently a meaningful MSE 
  predict fruitful applications for a variety of least-squared-error algorithms in the homoskedastic log-transformed domain.

Of course, there are other speckle filters that do not preserve such consistency 
	(e.g. the PDE filter \cite{You_TIP_2000}). One could argue that it would not be fair to judge such filters 
	using the MSE criteria, which tend to favour the ``standard'' filters.
While we respect any other criteria that have been used, we reiterate the two salient points of our approach. 
Firstly, our MSE criteria is closely related to the basic ENL criteria.
As shown in previous sections, experimental results indicated that
  the ENL measures for such filter (i.e. the PDE filter) differ depending  on the radiometric values. 
Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
The MSE criteria is shown to be related to feature preservation requirements.
Thus it is relevant towards subsequent target detection / classification processing, 
	believed to be a common subsequent processing step. 
For these two reasons, the MSE criteria is advocated.

In the experiments above, speckle filters with a $3 \times 3$ sliding window were used 
	even though we are aware that the normal window size employed is much larger. 
The reasons for maintaining such a small window is that 
	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk 
	among adjacent targets.
In addition, we focused on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
	and do not wish to advocate any particular ``best'' filter. 
In other words, we addressed the methodology of evaluating speckle filters, 
	and did not directly address the design of speckle filters.
However, interested filter designers are invited to download the open Matlab source code used in this paper 
for evaluating their own designs
  \footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.

In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators 
(i.e. speckle filters).
The use of small and simple patterns allows detailed analysis
  which can then be done repeatedly and reliably against the 
stochastic nature of SAR data.
This also helps in mapping qualitative requirements for the speckle removal process into specific and quantitative 
requirements in the design of speckle filters.
Its use also provides an absolute ground-truth as a solid base for comparison of results across different papers.

The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.
Thus the result extension towards real images is only analogical.
While the proposed rule is heuristic, 
	the experimental results presented in this paper are shown empirically to be valid.

We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
While perfect homogeneous ground truth can be defined, 
	different heterogeneous patterns exhibits different levels of heterogeneity. 
As such, different measures have been proposed to evaluate heterogeneity levels.
Unfortunately, for real captured images, where the absolute ground-truth is not available, 
	there is no known and certain way to assert a given image as being perfectly homogeneous or 
	absolutely heterogeneous.
Thus while the distinction helps in clarifying the concepts, 
	it is probably a leaky abstraction.

The patterns used are chosen based on our experience, which may affects evaluation results. 
As different patterns result in different homogeneity/heterogeneity degrees, 
	they also appear to affect the performance and ranking of each speckle filters.
One extreme example is that of perfect homogeneity, where boxcar filters would exhibit a respectable performance.
While, at the other end of the spectrum: that of high heterogeneity, it is common knowledge that the boxcar filter 
	would not perform that well.

The current scheme of finding the most suitable speckle filter requires the application of all filters before 
a decision is made, which probably demands excessive processing. 
A possibly better alternative would be to predict the choice, escaping such massive requirements of computational power.
This, however, is outside the scope of this paper.

\subsubsection{Conclusion}

To summarise, speckle filters are generally evaluated using many different qualitative criteria.
To compare the filters against each other, a methodology is needed
  to quantify these qualitative requirements,
  and subsequently to measure, compare and evaluate these quantities in the filtered results.
Central to all these is the need for a consistent sense of distance.

Logarithmic transformation has been shown 
  not only to convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values,
  but also to offer a few consistent measures of distance.
With the Gauss-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the 
log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.

Our contribution is mainly centered around a few points. 
Firstly, a mathematical equation is established to link the ENL index to the variance in the log-transformed domain. 
We also illustrate the use of log-variance evaluation -
  which is shown to be equivalent to the standard ENL evaluation -
  in evaluating the speckle suppression effect of different speckle filters.
Secondly we show that MSE is inversely correlated to the AUC index for simulated heterogeneous areas.
The result suggests that the smaller MSE a filter could achieve, the better it would
be at discriminating between the underlying radiometric features.
%The result suggests that the smaller MSE a filter could achieve, the easier it would be discriminating the underlying radiometric features.
Thirdly, the practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
the most suitable speckle filter for any given scene. 
Combined, we propose the use of MSE in log-transformed domain in evaluating the performance of different speckle filters in a variety of evaluation scenarios, and suggest several evaluation methodologies that may be useful in this regard.

It should also be noted that similar consistent measures of distance also exist in polarimetric SAR (POLSAR) data. 
Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.

%\section{FMLE POLSAR Speckle Filter using the consistent measures}

%This section describes the application of one consistent measure of distance,
%  namely contrast, in establishing a new POLSAR speckle filter.
%The first sub-section illuminates how the principles of fuzzy logic and Maximum Liklyhood Estimation (MLE) can be employed.
%The second sub-section illustrates that FMLE estimation preserves the consistency of contrast,
%  and hence consistent variance and ENL can be expected.
%The third sub-section introduces the recursive FMLE POLSAR speckle filter.

%\subsection{Fuzzy MLE estimation of POLSAR covariance matrix}
%\subsection{Preservation of the Consistency Properties in the FMLE outputs}
%\subsection{Recursive FMLE Speckle Filters}
%Compare increasing size FMLE vs decreasing size FMLE

\section{Evaluating POLSAR Speckle Filters using the consistent measures}

This section describes how POLSAR filters can be evaluated
  using the consistent measures of distance found in the homoskedastic log-transformed domain.
The first sub-section theoretically illustrates how the consistent variance is linked to the ENL index.
The second sub-section then demonstrate how the POLSAR speckle filters can be pratically and quantitatively evaluated over homogeneous areas by measuring the observable consistent variance after the log-transformation.
The third sub-section finally illlustrates how POLSAR speckle filters can be visually evaluated on heterogeneous areas.

\subsection{POLSAR ENL Estimation using the Homoskedastic Property}

While Anfinsen solves the above equation to find ENL,
  we took variance approach.
Since we can ignore the constants $d\ln2 + d\ln{L} -ln|\Sigma|$ this approach might be simpler.

\begin{equation}
  var \left[ ln|C_v| \right] = \sum^{d-1}_{i=0} \psi^1(L-i)
\end{equation}

For SAR, d=1 and $C_v=I$ then
$var(\ln{I}) = \psi^1(L)=\sum^{\infty}_{i=L}1/i^2$.
Since $1/L < \sum^{\infty}_{i=L}1/i^2 < 1/(L-1)$ Then an approximation is made to compute L as
$var(\ln{I}) = 1/(L-0.5)$ or $L=1/var(\ln{I}) + 0.5 $

For partial POLSAR, d=2, then
\begin{equation}
  var \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) \\
    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 \\    
\end{equation}
That is $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
Thus an approximation is made $var_d \left[ \ln |C_v| \right] = 2/(L-1)$
or $L = 2/var_d \left[ \ln |C_v| \right] + 1$

For full POLSAR, d=3, then
\begin{equation}
  var \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2) \\
    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 \\    
\end{equation}
That is $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
With L>3, it is trivial to prove that $3/(L-1.5)$ also is bounded by the above thresholds.
Thus an approximation is made $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$

$L_{det}^2 = \ln{|Cv|}$
$var(L_{det}^2)= \frac{2}{ENL-1}$
$L_{est}=\frac{2}{var(L_{det}^2)} + 1$

\begin{table}[h!]
\centering
\begin{tabular}{r|c|c}
 ENL & log-var(std)    & L est (enl)      \\
\hline
   2 & 2.2962 (0.1415) & 1.8734 (0.0509)  \\
   3 & 1.0597 (0.0453) & 2.8899 (0.0812)  \\
   4 & 0.6543 (0.0369) & 4.0646 (0.1831)  \\
   5 & 0.4837 (0.0142) & 5.1373 (0.1239)  \\
   6 & 0.3945 (0.0159) & 6.0755 (0.2129)  \\
   7 & 0.3229 (0.0086) & 7.1966 (0.1640)  \\
   8 & 0.2942 (0.0187) & 7.8209 (0.4616)  \\
   9 & 0.2550 (0.0106) & 8.8517 (0.3200)  \\
  10 & 0.2339 (0.0178) & 9.5867 (0.6273)  \\
  11 & 0.2076 (0.0119) & 10.6565 (0.5543) \\
  12 & 0.1839 (0.0112) & 11.9082 (0.6603) \\
  13 & 0.1734 (0.0181) & 12.6228 (1.1593) \\
  14 & 0.1555 (0.0085) & 13.8911 (0.6963) \\
  15 & 0.1453 (0.0086) & 14.7963 (0.7803) \\
  16 & 0.1316 (0.0083) & 16.2468 (0.9562) \\
  17 & 0.1250 (0.0079) & 17.0421 (1.0042) \\
  18 & 0.1146 (0.0035) & 18.4593 (0.5275) \\
  19 & 0.1087 (0.0032) & 19.4153 (0.5420) \\
  20 & 0.1056 (0.0060) & 19.9855 (1.1097) \\
  21 & 0.0983 (0.0017) & 21.3548 (0.3492) \\
  22 & 0.0945 (0.0056) & 22.2248 (1.2513) \\
  23 & 0.0918 (0.0048) & 22.8346 (1.1785) \\
  24 & 0.0845 (0.0043) & 24.7050 (1.2327) \\
  25 & 0.0874 (0.0039) & 24.9125 (1.0243) \\
\end{tabular}
\caption{ POLSAR Speckle Suppression Power: ENL and Variance Log-Determinant }
\label{tab:enl_in_log_domain}
\end{table}

Other fields in variance log-det table can include: var theory, and variance analysis

\subsection{Evaluating POLSAR Speckle Filters over Homogeneous Areas}

\begin{figure}
	\subfloat[preserving consistency property: boxcar filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/AIRSAR_Flevoland.preserve_consistency.boxcar.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[preserving consistency property: fmle filter]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/AIRSAR_Flevoland.preserve_consistency.fmle.eps} 	
		 \label{contrast_2x2}
	}      
  \caption{Checking the preservation of the consistency property for POLSAR speckle filters}  
\end{figure}

This section describes how POLSAR filters can be evaluated
  using the consistent measures of distance found in the homoskedastic log-transformed domain.
The previous section has illustrated theoretically how the variance of sample log-determinant is linked to the ENL index.
This form the basis for evaluating POLSAR speckle filters over homogeneous areas.
The procedure is simple.
To evaluate a given POLSAR speckle filter over homogeneous areas,
  the filter is applied over any known homogeneous areas and the sample variance of log-determinant is measured.
The Equivant Number of Look (ENL) is then estimated
  either by referencing the prepared graphs given by Eqn. ???
  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. ???.

In order for such a procedure to generic enough, it is important that the given POLSAR speckle filter to preserve the consistency property.
That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the dis-similarity measures presented above.
Fig. ??? presents two example plots for such a test.
Experiment is carried out for the 3x3 POLSAR boxcar filter to show that it preserves the consistency property.
The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
Log-determinant and the contrast measure is computed for the inputs and outputs filtered POLSAR data,
  and their plots are presented in Fig. ???

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinants histograms of boxcar 3x3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
		 \label{log_determinant}
	} 
	\hfill	
	\subfloat[Contrast histograms of boxcar 3x3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
		 \label{contrast}
	}   
\end{tabular}
\caption{POLSAR 3x3 boxcar filter preserves the consistency property. Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
\label{fig:boxcar_3x3_preserves_consistency}
\end{figure}

Apparently for log-determinant histograms,
  while the location of the filtered plots differs depending on the underlysing signal $\Sigma_v$,
  the shape of the plots, for both pre-filtered and post-filtered data, is invariant to that underlying signal.
Contrast, and similarly dispersion, measures of distance have its location independent of $\Sigma_v$,
  thus the contrast plots for the filtered output should overlap each other to show consistency.

The consistency property of POLSAR speckle filter is important
  not only to make the estimation of ENL become general enough
  but also to ensure that any classification / detection algorithm
    which is based on the scalar and consistent measures of distance would work on both pre-filtered and post-filtered data.

\subsection{Evaluating POLSAR Speckle Filters over Heterogeneous Areas}

Over heterogeneous area, the consistent measures of distance may also be valuable tools in helping to evaluate POLSAR speckle filters.
For a start, since the model for log-determinant is additive and homoskedastic,
  log-determinant images may be better naturally suited for gray-level digital images.
Especially for evaluation of statistical estimators,
  the estimators' error / residual plays an important role.
Ideally speaking, under the context of additive model,
  the perfect estimators' residual should be consists of only and wholly random noise.
And Gauss-Markov theorem, which works under the assumption of homoskedasticity, states that the optimal estimator should have minimal Mean Squared Error.
When the underlying signal is not known apriori,
  the second best gauge is possibly having the MSE of residual being equals or being as close as possible to the MSE of the inherent noise.

Our previous work TODO:CITE explored the hypothesis context of SAR data.
Here an experiment is carried out to illustrate the use of the consistent and homoskedastic measures of distance in evaluating the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial POLSAR data (HH-HV).
A square 740x740 portion of the AIRSAR dataset is extracted, and the two POLSAR speckle filters is applied.
The log-determinant images of outputs are display in Fig. ???.
For future further analysis, the residual defined as the distance between the log-determinants of the outputs and the original input is computed for both cases and the images are also displayed in the same figure.
Assumming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
  the Mean Squared Error (MSE) of the filters are computed.
Using the value of 4 as the ENL for the AIRSAR Flevoland dataset,
  the ``optimal'' value is computed as
%  \begin{equation}
%    %avg(\mathbb{L})^2 + var(\mathbb{L}) = mse(\mathbb{L}) =
%    \left[ \psi^0(4) + \psi^0(3) - 2\ln4 \right]^2 + \left[ \psi^1(4) + \psi^1(3) \right] = 1.0312 
%  \end{equation}
by setting $d=2,L=4$ into Eqn. (TODO:REF) making the expected MSE being $mse(\mathbb{L})=1.0132$.

\begin{figure}[h]
\centering
\begin{tabular}{c}
	\subfloat[Log-determinant Image of boxcar 3x3 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Log-determinant Image of boxcar 5x5 speckle filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
		 \label{multi_look_contrast}
	} \\
	\subfloat[Image of Log-determinant Residual for 3x3 filter (MSE=1.5594)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
		 \label{multi_look_dispersion}
	} 
	\hfill	
	\subfloat[Image of Log-determinant Residual for 5x5 filter (MSE=2.1420)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
		 \label{multi_look_contrast}
	} 
\end{tabular}
\caption{Visually Evaluating POLSAR Boxcar 3x3 vs. 5x5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
\end{figure}
%Note if the picture does not look convincing enough
%another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
Visually speaking, while the worse blurring effects of the boxcar 5x5 speckle filter is quite hard to be observed in the final image of the filtered output,
  such detection can be made relatively easier by just by visually investigating the residual image.
And when quantified number is taken out and compared with the expected level of noise to be removed,
  the excessive blurring effects of the 5x5 filter become crystally clear.
In fact, even the 3x3 boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.% of the 3x3 boxcar filter suggests that   
But a full explaination for that is outside the scope of this paper.

\begin{figure}
 	\subfloat[boxcar filter: log-determinant image]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/AIRSAR_Flevoland.boxcar.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[boxcar filter: residual image]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/AIRSAR_Flevoland.boxcar.residual.eps} 	
		 \label{contrast_2x2}
	}  \\
 	\subfloat[fmle filter: log-determinant image]{
		 \epsfxsize=3in
		 \epsfysize=3in
                 \epsffile{images/AIRSAR_Flevoland.fmle.eps} 
		 \label{dispersion_2x2}
	} 
	\hfill	
	\subfloat[fmle filter: residual image]{
		 \epsfxsize=3in
		 \epsfysize=3in
		 \epsffile{images/AIRSAR_Flevoland.fmle.residual.eps} 	
		 \label{contrast_2x2}
	}   
  \caption{AIRSAR image in log-determinant format and its variance as an edge-indicator}  
\end{figure}

### 2013-03-01 6/conclusional_discussion.tex
201303_Mar01

\chapter{Discussion and Conclusions} %chapter 7
\label{chap:conclusions}

%This section summarize 
%	the exciting overview and research motivations
%	the works that has been done
%	the significant contribution of the work 
%	the intrigue and feasible of future research project to extend the current work.

\section{Result Evaluation and Discussion}

In this thesis, a new model is developed for POLSAR data.
The theory development is based in the principles of statistical mathematic and is visualized using computer simulations.
The theory has shown its capabilities through a number of applications, though further studies should unearth even more interesting results.

The main assumption used in this paper is the independent and circular complex Gaussian model for POLSAR data.
While the model may not be perfectly matched with practical data,
  it is apparently the most-widely accepted model.
In the following paragraphs, the imperfect practice of over-sampling   data in SAR and POLSAR processing is discussed.

The practice of over-sampling in SAR (and hence POLSAR) data processing may affects the choice of nominal ENL for showing the match between real-life data and the proposed model.
Specifically, the over-sampling practice would normally be indicated a reduction of the ENL number.
This is for example evidenced in our experiment for the RADARSAT2 dataset.
The RADARSAT2 given to us is in its Single-Look format,
  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig ???
  against the theoretical model for the nominal ENL value of 9.
Even though the shapes of the histograms do look similar, the match however is not very good.
A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
  and the theoretical model for the estimated ENL indicated a much better consistency.
This procedure can always be carried out for any given dataset,
  since the sample variance of the log-determinant can always be measured
  and hence the effective ENL can always be estimated using Eqn. ???.

The use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the second order statsitics POLSAR matrices.
In fact, the log-determinant can also be computed as the sum of log-eigen values.
Specifically:
\begin{eqnarray}
  \ln{|M|} = \sum \ln{\lambda_M}
\end{eqnarray}
where $\lambda_M$ denotes all the eigen-values of M.
Similar to other eigen-value based approach (e.g. Entropy/Anisotropy, ...),
  the models presented here is roll-invariant.

The methodology presented in this paper call for the reduction of the multi-dimensional POLSAR data into a scalar value.
While this is probably desirable for a wide range of application where a one-dimensional number is required to represents the complex multi-dimensional data,
  such reduction is probably not lossless.
Thus similar to the way the Wishart Classifier is employed,
  the use of this technique should be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g. Freeman Durden or entropy/anisotropy TODO:REF ...)

\section{Contributions of the Thesis}

%\subsection{POLSAR Consistent Measures of Distance}

%\subsubsection{Conclusion}

In conclusion, several scalar and consistent measures-of-distance for multi-variate POLSAR data were proposed in this paper.
The dis-similarity measures are computed for the determinant of the POLSAR covariance matrix,
  which when converted into one-dimensional data
  is gracefully transformed into the traditional SAR intensity.
Consequently, these measures of dis-similarity may be employed in a wide range of application
  where a scalar number is required to represent the complex multi-dimensional POLSAR data.
Just like it is shown for the simpler case of SAR data processing\cite{Le_2010_ACRS},
  when these distances are computed in the log-transformed domain,
  their theoretical statistic models become additive and homoskedastic.
The models are shown to be theoretically powerful.
Not only they can provide alternative and sometimes simpler explainations to a range of theoretical concepts:
  i.e. change detection test statistics or ENL estimation
but also a number of results for one-dimensional SAR can be shown as special cases of the POLSAR models.
They are also pratically versatile enough
  capable of explaining the imperfect over-sampling practice evident in RADARSAT2 data.
Finally, to extend our previous work in evaluating SAR speckle filters,
  the applicaton of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored
  with promising results reported.

\section{Possible Future Work and Conclusion}

\subsection{Possibilities for Future Work}

A fair amount of work has been carried out, published in two conference papers in 2010.
Still, as described in this report, the opportunities for further investigation are abundant.

In the field of single channel SAR, further exploitation from the results of log-transformation should be achievable and publishable.
An immediate opportunity is identified as the estimation of the PDF of the underlying signal in SAR images. 
The mathematical construction and conceptualization was presented earlier, with implementation under-way.
In the medium term, a possible protocol for evaluation using homoskedastic mean squared error under various scenarios, made possible through simulation of different ground-truth PDFs is being conceptualized.

On the POLSAR front, the short term focus is to implement speckle filtering for the off-diagonal element in the target's covariance matrix.
The mathematical conceptualization has been given earlier, with a presentation planned as a paper for IGARSS 2011.
In a longer time frame, we are hoping to be able to apply log-transformation's homoskedastic features into POLSAR data to find a consistent measure of distance for one of the matrices representing the target's polarimetry signature.
We are also prepared to render help toward EADS's in-house project investigating the problem of ship identification / classification, ground-truth using AIS data.

\subsection{Conclusion}

In conclusion, recent advances in computational power have made SAR and multiple-channel SAR become the preferred choice for continuous and autonomous global-scale earth observation and monitoring.
Some primitive systems have been implemented and become operational for such purposes, e.g. ship monitoring, which have show-cased the capability of the technology.
Recent advances in multi-channels polarimetric SAR have captured attention, not only within the academic community, but also from industrial players.

There are however certain issues need to be resolved to ensure the extra-information available in POLSAR data leads to better practical implementations.
%Our pilot study have exposed the trade off between higher-resolution in partial polarimetry modes and lower-resolution in images of full polarimetry, which apparently will continue to be around for many years to come.
%More importantly it exposed the need of a computational framework, to simulate, experiment and objectively evaluate the performance of different POLSAR processing techniques.
Our studies have exposed the need for a computation framework, to simulate, experiment, carry out statistical analysis, modelling, validation and evaluation of various SAR and POLSAR processing techniques, most of which can be put within the framework of statistical estimations.
Our work thus far has developed one such framework for the processing of single-channel SAR data.
In the next phase of the project, we aim to develop a more elaborated framework for multi-channel POLSAR data processing.

With the availability of such fundamental research, we can probably afford to follow a wider range of subsidiary research questions.
For the traditional single channel SAR, one sub-topic is our hypothesis that it is possible to estimate the PDF of the true, underlying back-scattering coefficient, at least in the log-transformed domain. 
Should we succeed in such a task, the technique could be an invaluable contributions to the whole class of MAP speckle filters.

Compared to single-channel SAR, the field of multi-channel POLSAR is much less mature. 
Thus the application of our intended framework can be expected to bring even better impact publications.
The first sub-topic that we aim for immediate experiment is the hypothesis that off-diagonal element in the polarimetric covariance matrix element can be speckle filtered through the application of standard SAR techniques on transformed polarization basis intensities.
In the longer term, we hope to investigate the extension of our homoskedastic log-transformation techniques towards finding a consistent measure for the multi-variate and stochastic POLSAR data.
%Should the experiments proved successful, an alternative and simpler way to statistically model off-diagonal element can be proposed.

%The previous chapter just elaborated a few of them, which showed the greatest potential and
%One of such key issues is the filtering of speckle, especially on off-diagonal covariance matrix elements, which also available in partial polarimetric data.

Presented here, and in the previous chapter, are just a few of a whole range of possibilities. 
With such a diversity available, one of our priorities is to be focused to achieve tangible results.
We merely choose to present only the sub-topics which showed the greatest potential and which we believe would provide the most impact and leverage for our future work.
For such tasks, a snap-shot of the project status and the amount of remaining activities is planned and presented in the previous section.
With continued assistance from EADS Innovation Works Singapore, who is a collaborator of this project and has provided us numerous valuable data and discussion, we believe that the remaining tasks are highly feasible.
The academic contribution was discussed earlier while the endorsement of EADS speaks volumes about the practical contributions of our research.
%We believe we have chosen a reasonable group of subsidiary research questions to focus, however we will be delighted to receive any feedback and suggestion from the readers.

%This project, in fact, is part of a collaboration with EADS on the field.

### 2013-03-01 7/discussion.tex
201303_Mar01

% this file is called up by thesis.tex
% content in this file will be fed into the main document

\chapter{Discussion} % top level followed by section, subsection

% ----------------------- paths to graphics ------------------------

% change according to folder and file names
\ifpdf
    \graphicspath{{7/figures/PNG/}{7/figures/PDF/}{7/figures/}}
\else
    \graphicspath{{7/figures/EPS/}{7/figures/}}
\fi

% ----------------------- contents from here ------------------------

Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, 
additive, least squared error regression signal processing (e.g. wavelets) and computational inteliggence
(e.g. artificial neural network) techniques on SAR data.

% ---------------------------------------------------------------------------
% ----------------------- end of thesis sub-document ------------------------
% ---------------------------------------------------------------------------

### 2013-03-01 9_backmatter/appendix.tex
201303_Mar01

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
+\appendix
 
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
-In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
-  the vector is two-dimensional ($d=2$) and is normally written as: 
-\begin{equation}
-s_{part}=\begin{bmatrix}
-S_h\\ 
-S_v
-\end{bmatrix}
-\end{equation}
-In the case of full and monostatic POLSAR data,
-  the vector is three-dimensional ($d=3$) and is presented as:
-\begin{equation}
-s_{full}=\begin{bmatrix}
-S_{hh}\\
-\sqrt{2}S_{hv}\\
-S_{vv}
-\end{bmatrix}
-\end{equation}
-
-Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
-  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
-Assuming all the elements in $s$ are independent
-  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
-  then the probably density function (PDF) of $s$ can be written as:
-\begin{equation}
-  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-\end{equation}
-where $|M|$ denotes the determinant of the matrix $M$.
-
-As covariance matrix is only defined on multiple data points,
-  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
-They are formed as the mean of Hermitian outer product of single-look scattering vectors
-\begin{equation}
-  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
-\end{equation}
-with $s_i$ denotes the single-look scattering vector,
-  which equals $s_{part}$ in the case of partial POLSAR and
-  $s_{full}$ in the case of full polarimetry,
-and $L$ is the number of looks.
-
-Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
-$Z=LC_v$, whose PDF is given as:
-\begin{equation}
-  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
-\end{equation}
-with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
-and $d$ is the dimensional number of the POLSAR covariance matrix.
-
-Our approach differs by applying the homoskedastic log transformation
-  on a less-than-well-known result for the deterimant of the covarinace matrix.
-  %under the assumption of circular complex Gaussian distribution
-  %applicable for POLSAR data.
-In \cite{Goodman_1963_AMS_178}, %Goodman
-it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
-  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
-\begin{equation}
-\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
-\label{eqn:prod_chi_squared_rv}  
-\end{equation}
-
-Its log-transformed variable consequently 
-  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
-\begin{equation}
-\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
-\label{eqn:sum_log_chi_squared_rv}
-\end{equation}
-with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
-
-\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
-\label{sec:polsar_heterosked_model_and_log_transform}
-
-In this section the multiplicative nature of POLSAR data is illustrated.
-Log-transformation is shown converting this into a more familiar additive model.
-Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
-  is proved to be the case for the original POLSAR data.
-In log-transformed domain, the case for a homoskedastic model,
-  where  variance is fixed and be independent of the underlying mean,
-  is demonstrated.
-To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.
-
-From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
-we have:
-\begin{eqnarray}
-  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
-  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
-\label{eqn:log_determinant_distribution}  
-\end{eqnarray}
-
-In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
-Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
-  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
-At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
-  the logarithmic transformation converts this into a more familiar additive noise.
-
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
-\begin{equation}
-pdf(x;k) =
-  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
-\label{eqn:chi_squared_dist_pdf:chap4}
-\end{equation}
-Applying the variable change theorem, 
-  its log-transformed variable follows the PDF of:
-\begin{equation}
-  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
-\end{equation}
-
-Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
-  can be written as:
-  \begin{eqnarray}
-    CF_\chi(t) &=& (1-2it)^{−L} \\ 
-    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
-  \end{eqnarray}
-Subsequently their means and variances can be computed from the given characteristic functions as:
-  \begin{eqnarray}
-    avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-  \end{eqnarray}
-  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma function respectively.
-
-Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
-  the product and summation of these random variables also has fixed summary statistics.
-Specifically:
-\begin{eqnarray*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
-
-Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
-\begin{eqnarray}
-  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
-\end{eqnarray}
-
-Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
-  the underlying $\Sigma_v$ is expected to differ from one region to the next.
-Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
-  %and it is clear that 
-  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
-In such context, Eqn.
-\ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
-At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.
-
-\section{Consistent Measures of Distance for POLSAR data}
-
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
-  this section introduces the consistent sense of distance in a few different perspective.
-First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-the following random variables,
-  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
-  are observable according to their definitions:
-%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
-
-\begin{eqnarray}
-  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
-  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
-\end{eqnarray}
-From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
-\begin{eqnarray}
-  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
-  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
-\end{eqnarray}
-
-Taking the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
-\begin{eqnarray}
-\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
-\label{eqn:log_determinant_distance_distribution} \\ 
- \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
-\label{eqn:dispersion_distribution} \\ 
- \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\label{eqn:contrast_distribution}  
-\end{eqnarray}
-with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
-and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
-
-Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
-  Appendix \ref{sec:appendix_b} derives the characteristic functions for the summative random variables as:
-\begin{align}
-  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
-  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
-\end{align}
-
-Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
-  it is natural that these variables also follow fixed distributions.
-Moreover, they are independent to $\Sigma_v$.
-This serves as conclusive evidence that
-  these random variables follows consistent and fixed distributions,
-  regardless of the underlying signal $\Sigma_v$.
-
-\section{SAR as the Special Case of Polarimetric SAR}
-\label{sec:sar_special_case_of_polsar}
-
-The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
-In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
-Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
-Mathmatically, the sample covariance matrix is reduced to the sample variance
-  and the determinant equates the scalar value.
-On another hand, it is well known that for SAR data, variance equals intensity.
-Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
-This can be thought of 
-  either as a cross-validation evidence for the proposed POLSAR models
-  or alternatively as having SAR as the special case of POLSAR. 
-%  with well known results for SAR intensity is presented.
-
-The results so far for our models can be summarized as:
-\begin{align}
-  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
-  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
-  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
-  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
-  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
-  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align}
-
-Upon setting $d=1$ into the above models,
-  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
-\begin{align*}
-  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
-  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
-  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
-  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
-  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
-  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
-  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{align*}
-but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
-  \begin{eqnarray}
-I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
-  \end{eqnarray}
-Furthermore, the following results for multi-look SAR data,
-  which can be thought of 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results
-  are also derived as:
-  \begin{align*}
-    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
-    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
-    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
-    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
-    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
-    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{align*}
-
-This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
-In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[verify multi-look SAR log-distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[verify multi-look SAR contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
-	}
-\end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
-\end{figure}
-
-\section{Validating the models against real-life data}
-\label{sec:polsar_models_validation}
-
-\subsection{Explaining practical data with the given Number-of-Looks}
-
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
-  assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
-
-Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
-	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
-	}
-\end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
-\end{figure}
-
-Apart from dispersion and contrast,
-the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
-	} \\
-	\subfloat[full-pol 3x3 determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol 3x3 log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
-	}
-\end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
-\end{figure}
-
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
-  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[verify polsar 2x2: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[verify polsar 3x3: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[verify polsar 3x3: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy suggests that at least one parameter for the models was wrongly employed.
-
-But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  where not only the look number is shown to be misused
-  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-For now, let us contend that:
-  using appropriate estimation of the parameters, 
-  the proposed models match reasonably well with the practical data.
-
-\subsection{Comparing Theoretical Assumptions and Practical Implementations}
-\label{sec:improve_the_match_bw_theory_practice}
-
-Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
-  like all other similar models, the proposed model in this paper is built upon certain presumptions.
-Practical conditions however may not always satisfy these prerequisites.
-In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
-And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
-
-There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
-The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
-Practically however high correlation is routinely observable between the POLSAR data components,
-  specifically between $S_{hh}$ and $S_{vv}$.
-This phenomena also presents in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
-Despite the mismatch,
-  astute reader would probably notice that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
-\ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
-This suggests that the proposed model is also applicable on correlated POLSAR components,
-  eventhough a full explaination for this, however, is outside the scope of this paper.
-
-Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent to each other.
-This is a reasonable assumption given that 
-  the transmission and receipt of analog signals are done independently for each radar pulse, i.e. for each resolution cell.
-Thus theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
-
-However, the actual imaging mechanism of a real-life (POL)SAR processor is that of digital nature,
-where the analog signal is to be converted into a digital data-set. 
-Specifically, the analog signal in SAR 
-  which is characterized by the pulse bandwidth measurement,
-  is fed into an analog-to-digital sampling and conversion process 
-  which is characterized by its sampling rate.
-Theoretically it is possible to define a sampling rate to ensure that each digital pixel correspond exactly to an analog physical cell resolution.
-Practically however, to ensure ``perfect reconstruction'' of the analog signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
-This results in a higher number of samples / pixels than the number of physical cells available in the scene.
-
-Stated differently, in practical data each physical radar cell is spread to more than one pixel
-  and each pixel now contains less than one physical analog cell.
-This high sampling rate also results in 
-  a significantly higher correlation between pairs of pixels that maybe related within a single physical cell resolution 
-  than the correlation found between pairs of pixels that are further away and hence having less physical relation to each other.
-It also results in reduced effective number of look, 
-  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
-The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
-  while the later is experimental observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
-The oversampling practice is also documented by the producers of SAR processors.
-For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}
-
-The proposed model can handle this imperfection that is available in pratical data.
-The trick is that instead of using the nominal Number of Look given by the SAR processor,
-  an ENL estimation procedure is employed. %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
-The first part of this section details a simple ENL estimation technique for POLSAR data.
-While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
-It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved,
-  by using ENL estimation.
-
-\subsection{Estimating the Effect Number-of-Looks (ENL)}
-
-This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
-The common approach in tackling this problem is by investigating the summary statistics of an known homogeneous area in the given data
-  before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ has been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
-In fact Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-Recall that in carrying out validation process for AIRSAR Flevoland data using the nominal look number of 4, this relationship was broken.
-The reason for such broken relationship is believed to be an inexact look number was taken.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ is known,
-  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensure the above relationship is valid.
-
-In fact, this approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
-Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
-Instead of relying on the equations for statistical mean to find ENL,
-  our approach make used variance statistics in the homoskedastic log-domain to find ENL.
-Since the determinant of POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
-  this approach can be considered as the generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} towards POLSAR data.
-Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation}
-  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-  \label{eqn:expected_sample_var_log_as_function_of_enl}
-\end{equation}
-where $\psi^1()$ denotes tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
-Interestingly that would also require some iterative computations.
-Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph.
-And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
-  \begin{equation}
-    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
-    \label{eqn:enl_estimation_formula}
-  \end{equation}
-Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  not only shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  but also illustrates the approximation power of the simplified formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relationships between ENL and the sample variance of log-determinant and log-intensity}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
-The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
-Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
+\chapter{Log-Chi-Square Distribution}
+\label{chap:appendix_a}
 
@@
 
-\subsection{Summary Statistics of Some POLSAR Observables}
+\section{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
 
@@
 
-\subsection{The characteristic function of some dissimilarity measures for polsar}
+\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
 
@@
   \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
+  \Gamma(L-it) \Gamm(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
    CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
@@
 
-\subsection{SAR intensity as the special case of the POLSAR cov-matrix determinant}
+\section{SAR intensity as the special case of POLSAR covariance matrix determinant}
 \label{sec:appendix_sar_special_case_of_polsar}
@@
 
-\subsubsection{Original Domain: SAR Intensity and its ratio}
+\section{Original Domain: SAR Intensity and its ratio}
 
@@
 
-\subsubsection{Log-transformed domain: SAR log-intensity and the log-distance}
+\section{Log-transformed domain: SAR log-intensity and the log-distance}
 
@@
 
-\subsubsection{Deriving the PDF for SAR dispersion and contrast}
+\section{Deriving the PDF for SAR dispersion and contrast}
 
@@
 which is also consistent to the result in our previous work (TODO:CITE).
-
-%\section{Simulating All Elements of POLSAR Covariance Matrix}
-%
-%Jong sen lee simulation procedures is applied and verified in 2x2 partial polsar AIRSAR Flevoland image.
-%Pipia method explicitly indicates cholesky decomposition,
-%  while the exponential notion in Lee's book appear to suggest svd decomposition
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[verify polsar 2x2 simulation: S11]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S11.eps} 
-%		 \label{S11}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S22]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S22.eps} 	
-%		 \label{S22}
-%	} \\
-%	\subfloat[verify polsar 2x2 simulation: S12r]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S12r.eps} 
-%		 \label{S12r}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S12i]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S12i.eps} 	
-%		 \label{S12i}
-%	}        
-%\end{tabular}
-%\caption{verifying polsar 2x2 simulation: the components}
-%\label{fig:verify_polsar_2x2_simulation_components}
-%\end{figure}
-%
-%The same procedure does not appear to work on 3x3 full polarimetric POLSAR image.
-%Despite all other elements match nicely, the ShhSvv* element does not appear to match.
-%However, the log-det still appears to be consistent
-%  and more importantly all dis-similarity measures still match.
-%  
-%\begin{figure}[h!]
-%\centering
-%\epsfxsize=6.0cm
-%\epsffile{images/verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation.eps} 
-%\caption{3x3 svd simulation: 13 element mismatch}
-%\label{fig:verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation}
-%\end{figure}
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[C11]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.11.eps} 
-%		 \label{11}
-%	} 
-%	\hfill	
-%	\subfloat[C22]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.22.eps} 
-%		 \label{22}
-%	} 
-%	\hfill	
-%	\subfloat[C33]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.33.eps} 
-%		 \label{33}
-%	} \\
-%	\subfloat[C12r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12r.eps} 
-%		 \label{12r}
-%	} 
-%	\hfill	
-%	\subfloat[C13r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13r.eps} 
-%		 \label{13r}
-%	} 
-%	\hfill	
-%	\subfloat[C23r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23r.eps} 
-%		 \label{23r}
-%	}  \\
-%	\subfloat[C12i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12i.eps} 
-%		 \label{12i}
-%	} 
-%	\hfill	
-%	\subfloat[C13i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13i.eps} 
-%		 \label{13i}
-%	} 
-%	\hfill	
-%	\subfloat[C23i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23i.eps} 
-%		 \label{23i}
-%	}
-%\end{tabular}
-%\caption{verify polsar 3x3 simulation with polarization basis change}
-%\label{fig:verify_polsar_svd_3x3_simulation_polarization_basis_change}
-%\end{figure}
-%

### 2013-03-01 paper_dev/201302_Feb11.article.tex
201303_Mar01

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
-
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
+%\documentclass[a4paper,10pt]{article}
+\documentclass[journal]{IEEEtran}
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{cite} %for citations
+\usepackage{url}
+
+ %this is for math typing (eg: cases)
+\usepackage{amsmath}
+   \usepackage{amsfonts}   % if you want the fonts
+   \usepackage{amssymb}    % if you want extra symbols
+\usepackage{epsfig} %for figures
+
+\usepackage[center]{caption}%for captions
+\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+
+%\nonstopmode
+
+%opening
+\title{
+  Statistically Consistent Measures of Distance for POLSAR Data
+%Scalar Homoskedastic Models for POLSAR data
+}
+
+%\author{Thanh-Hai Le, Ian McLoughlin}
+\author{Thanh-Hai~Le,
+        Ian~McLoughlin, 
+	and Chan-Hua~Vun%
+\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+%	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2013; revised ?.}}
+
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Statistically Consistent Measures of Distance for POLSAR Data}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+In this paper, a homoskedastic and additive model for polarimetric SAR (POLSAR) data is introduced. 
+The statistical properties of this model subsequently lead to a few different consistent measures of distance for the POLSAR covariance matrix.
+The dis-similarity measurements are initially developed for both partial (2x2) and full (3x3 monostatic case) polarimetric SAR data.
+They are computed from the determinant of the POLSAR covariance matrix.
+Interestingly, when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
+Thus the SAR intensity statistics can now be considered as a special case of the theoretical model for POLSAR.
+While powerful theoretically, the statistical model is also robust in handling practical data.
+It can be validated and match reasonably well with practical data,
+ even  when  the supposedly independent polarimetric components are actually highly correlated (e.g. between $S_{hh}$ and $S_{vv}$).
+Moreover, the match can be further improved, as better match is shown achievable, 
+  if the model validation process include an estimation of the dataset's Effective Number of Looks (ENL) 
+  instead of blind employment of the look number given by the SAR processor.
+Towards the end, the practical application of these dissimilarity measures is briefly demonstrated in the context of evaluating POLSAR speckle filters.  
+\end{abstract}
+
+\begin{IEEEkeywords}
+Polarimetric, Synthetic aperture radar, speckle-filtering, homoskedasticity
+\end{IEEEkeywords}
+
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+%\section{POLSAR data: statistical analysis and logarithmic transformation}
+
+In this paper, the POLSAR scattering vector is denoted as $s$.
 In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
@@
 
-\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
+In this paper, the above results are further explored in the context of POLSAR data processing
+  and a few scalar, consistent and homoskedastic measures of distance is proposed.
+The paper is structured as follows:
+  after the preceding introduction to the basics of POLSAR statiscal analysis,
+  the second section presents conclusive evidence for two related points.
+The first is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second: log-transformation converts it into an additive and homoskedastic model.
+Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+After the model is validated against both partial and full polarimetric SAR data in Section \ref{sec:polsar_models_validation},
+  section \ref{sec:sar_special_case_of_polsar} discusses
+    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
+Besides being theoretically powerful, 
+  the model is shown, in section \ref{sec:improve_the_match_bw_theory_practice}, to be robust in handling a few practical imperfections that violate conventional assumptions. 
+As an example application of the consistent and homoskedastic dis-similarity measures, 
+  section \ref{sec:evaluating_polsar_filters} explores how they can be used in evaluating POLSAR speckle filters.   
+Finally, section \ref{sec:discussion_conclusion} critically reviews related works in literature 
+  before providing some conclusional discussion.
+
+\section{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
@@
 In log-transformed domain, the case for a homoskedastic model,
-  where  variance is fixed and be independent of the underlying mean,
+  where sample variance is fixed and thus independent of the underlying signal,
   is demonstrated.
@@
 In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
-Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
+Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that: 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
@@
 
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
-\begin{equation}
-pdf(x;k) =
-  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
+Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows a known PDF:
+\begin{equation}
+pdf(x;2L) =
+  \frac{x^{L-1} e^{-x/2}}{2^L \Gamma\left(L\right)}
 \label{eqn:chi_squared_dist_pdf:chap4}
@@
 
-Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
+As the PDFs become available, the characteristic functions (CF) of both the chi-squared and log-chi-squared random variables
   can be written as:
@@
   \end{eqnarray}
-Subsequently their means and variances can be computed from the given characteristic functions as:
+Subsequently their means and variances can be computed from the given characteristic functions.
+They are:
   \begin{eqnarray}
@@
 Specifically:
-\begin{eqnarray*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
+\begin{align*}
+  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
+  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+\end{align*}
 
 Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
-\begin{eqnarray}
-  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
-\end{eqnarray}
+%\begin{eqnarray}
+%\end{eqnarray}
+\begin{align}
+  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
+  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+\end{align}
 
@@
 Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
-  %and it is clear that 
-  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
 In such context, Eqn.
-\ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
+\ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
 At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
@@
 
-\section{Consistent Measures of Distance for POLSAR data}
+\section{Consistent Measures of Distance for POLSAR}
+\label{sec:distance_measure}
 
@@
 
+\section{Validating the models against real-life data}
+\label{sec:polsar_models_validation}
+
+This section describes an experiment to validate the models above against real-life captured data.
+The validation procedure is quite straightforward.
+Given that the stochastic models have been derived in the previous sections, 
+  they can be graphically visualized by the histogram plots of the simulated data.
+At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
+Therefore, the theoretical models can be validated 
+  if for the same parameters 
+  the two plots match each other reasonably well.
+
+As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+Then theoretical models are employed in an attempt to explain the data.
+The validating models include:
+  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
+
+The models are closely related.
+Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
+Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
+Thus ideally speaking
+  if one model is validated all the other models will also be,
+  assuming that all the parameters of the image are known exactly.
+Still in this section, all the models will be made subject to investigation.
+
+Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
+For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
+Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
+Then their histograms are traced out.
+
+At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
+The nominal value of 4 was taken as the dataset's number of look,
+ while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
+All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
+Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) dispersion]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
+		 \label{dispersion_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) contrast]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
+		 \label{contrast_2x2}
+	} \\
+	\subfloat[full-pol (3x3) dispersion]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
+		 \label{dispersion_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) contrast]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
+		 \label{contrast_3x3}
+	}
+\end{tabular}
+\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
+\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\end{figure}
+
+Apart from dispersion and contrast,
+the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
+There are two ways to estimate this quantity over an homogeneous area.
+The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
+Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+Both approaches will be explored in this section.
+However, given that the log-determinant average has already been computed earlier, 
+  the second approach is used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
+In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
+  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
+Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) log distance]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
+		 \label{log_distance_2x2}
+	} \\
+	\subfloat[full-pol 3x3 determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol 3x3 log distance]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
+		 \label{log_distance_3x3}
+	}
+\end{tabular}
+\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
+\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\end{figure}
+
+Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
+
+However, a more interesting  phenomena is to be described.
+It happens in the validation process for determinant and its log-transformed model,
+  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
+%For such simulation, an estimation of  the true signal is needed.
+The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
+Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
+
+Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
+The differences are easier to observe in the log-determinant plots, 
+  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[verify polsar 2x2: determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
+		 \label{determinant_2x2}
+	} 
+	\hfill	
+	\subfloat[verify polsar 2x2: log-determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
+		 \label{log_det_2x2}
+	} \\ 
+	\subfloat[verify polsar 3x3: determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
+		 \label{determinant_3x3}
+	} 
+	\hfill	
+	\subfloat[verify polsar 3x3: log-determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
+		 \label{log_det_3x3}
+	} 
+\end{tabular}
+\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
+\label{fig:verify_polsar_2x2_simulation_det}
+\end{figure}
+
+In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
+The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
+  if the underlying parameters can be estimated reasonably well for the given image.   
+However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
+  depending on which estimation method was being used.
+The discrepancy suggests that at least one parameter for the models was wrongly employed.
+
+But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
+The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+  where not only the look number is shown to be misused
+  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
+For now, let us contend that:
+  using appropriate estimation of the parameters, 
+  the proposed models match reasonably well with the practical data.
+
 \section{SAR as the Special Case of Polarimetric SAR}
@@
 
-The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
-In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
+The prevous section has validated the use of our models for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+In this section, the focus is on the case where the dimensional number is reduced to 1 $d=1$.
 Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
@@
 Upon setting $d=1$ into the above models,
-  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
+  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
 not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
@@
 
-\section{Validating the models against real-life data}
-\label{sec:polsar_models_validation}
-
-\subsection{Explaining practical data with the given Number-of-Looks}
-
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
-  assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
-
-Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
-	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
-	}
-\end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
-\end{figure}
-
-Apart from dispersion and contrast,
-the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
-	} \\
-	\subfloat[full-pol 3x3 determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol 3x3 log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
-	}
-\end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
-\end{figure}
-
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
-  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[verify polsar 2x2: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[verify polsar 3x3: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[verify polsar 3x3: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy suggests that at least one parameter for the models was wrongly employed.
-
-But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  where not only the look number is shown to be misused
-  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-For now, let us contend that:
-  using appropriate estimation of the parameters, 
-  the proposed models match reasonably well with the practical data.
-
-\subsection{Comparing Theoretical Assumptions and Practical Implementations}
+\section{Handling certain discrepancy between the theoretical model and pratical data}
 \label{sec:improve_the_match_bw_theory_practice}
@@
 
-\subsection{Estimating the Effect Number-of-Looks (ENL)}
+\subsection{ENL Estimation}
 
@@
 \end{tabular}
-\caption{The relationships between ENL and the sample variance of log-determinant and log-intensity}
+\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
 \label{fig:plot_enl_var_relation_1x1_and_2x2}
@@
 
-\subsection{Using the estimated ENL to better explain pratical data}
+\subsection{Using estimated ENL to better explain pratical data}
 
@@
 \caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
+Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then explain the data reasonably well.}
 \label{fig:handling_radarsat2_oversampling_practice}
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}
@@
 
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
+\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+%\section{Visually Evaluating POLSAR Speckle Filters over Heterogeneous Areas}
+\label{sec:evaluating_polsar_filters}
+
+Previous sections have developed a model for polsar, which is also shown to be applicable to sar,
+  in this section, the use of consistent measures of distance in the context of polsar speckle filtering is briefly explored.
+It has been found \cite{Rignot_1993_TGRS_896} that for sar data set that in its original domain: 
+   ratio is a better evaluation than standard substractive residual. 
+However, ratio residual is argued as not being natural for digital display \cite{Medeiros_2003_IJRS}.
+Our previous work in the context of sar speckle filtering found that
+  in log-transformed domains, this ratio is transformed into a subtractive residual that is homoskedastic.
+
+The variance of sample log-determinant is shown linked to the ENL index.
+This form the basis for evaluating POLSAR speckle filters over homogeneous areas.
+The procedure is simple.
+To evaluate a given POLSAR speckle filter over homogeneous areas,
+  the filter is applied over any known homogeneous areas and the sample variance of log-determinant is measured.
+The Equivant Number of Look (ENL) is then estimated
+  either by referencing the prepared graphs given by Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} 
+  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. \ref{eqn:enl_estimation_formula}.
+
+In order for such a procedure to be generic enough, it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
+That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the dis-similarity measures presented above.
+Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that:
+  the 3x3 POLSAR boxcar filter preserves the consistency property.
+The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
+Log-determinant and the contrast measure is computed for the inputs and outputs filtered POLSAR data,
+  and their plots are presented.
+In fact, the test procedure can be applied on any of the models presented above.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinants histograms of boxcar 3x3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+		 \label{log_determinant}
+	} 
+	\hfill	
+	\subfloat[Contrast histograms of boxcar 3x3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+		 \label{contrast}
+	}   
+\end{tabular}
+\caption{POLSAR 3x3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
+\label{fig:boxcar_3x3_preserves_consistency}
+\end{figure}
+
+The consistency property of POLSAR speckle filter is important
+  not only to make the estimation of ENL become general enough
+  but also to ensure that any classification / detection algorithm
+    which is based on the scalar and consistent measures of distance would work on both pre-filtered and post-filtered data.
+Otherwise if a polsar speckle filter gives different plots for different homogeneous areas, then not only its enl estimation will be dependent on the underlying signal, 
+But its output also shall not follow the statistical distribution family that characterize multi-look polsar.
+Thus the preservation of this consistency is believed to be an important consideration for polsar speckle filter if he want a host of detection and classification algorithms to work on his filtered data output.
+
+In evaluation over heterogeneous area, the consistent measures of distance may also be an invaluable tool.
+ %in helping to evaluate POLSAR speckle filters.
+For a start, since the model for log-determinant is additive and homoskedastic,
+  log-determinant images may be better naturally suited for gray-level digital images.
+specifically for evaluation of statistical estimators,
+  It is both important and convinient to investigate the estimators' error / residual image. %plays an important role.
+
+For future further analysis, the residual is defined here as the distance between the log-determinants of the filtered outputs and the original input. 
+Ideally speaking, under the context of additive model,
+  a perfect estimator's residual should be consists only of random noise.
+And under the assumption of homoskedasticity, 
+  the Gauss Markov theorem becomes applicable.
+Thus the optimal estimator is expected to exhibits minimal Mean Squared Error.
+In homogeneous scene, this is reflected in the expectation of minimal bias and variance (hence maximal ENL).
+Over heterogeneous scene, where the underlying signal is not known apriori,
+  the second best gauge is possibly to have the residual mse being as close as possible to the MSE of the inherent noise.
+
+To illustrate the above analysis, an experiment is carried out to evaluate the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+A square 700x700 portion of the AIRSAR dataset is extracted, and the two POLSAR speckle filters is applied on to the patch.
+Then the log-determinant images of the filtered outputs are display in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time the residual is computed for both cases filters and the images are also displayed in the same figure.
+Assumming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+This value is computed   
+by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3x3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5x5 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3x3 filter (MSE=1.5594)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5x5 filter (MSE=2.1420)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3x3 vs. 5x5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%Note if the picture does not look convincing enough
+%another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only the log-determinant image can offer a nice visualization of the scene, 
+  but also the distortion impact of the filter can also be made visible by the residual image.
+In visual evaluation, while it is quite hard to observe the worsening blurring-effects of the boxcar 5x5 speckle filter as compared to the 3x3 filter
+in the additive log-determinant image of the filtered output 
+  such a conclusion can be made relatively easier by visually investigating the residual image.
+
+And when quantified evaluation is carried out
+  where the residual mse is compared with the expected level of noise to be removed,
+  the excessive blurring effects of the 5x5 filter become crystally clear.
+In fact, even the 3x3 boxcar filter itself might be also a bit blurry.%,  as suggested by its relatively high residual values.
+A conclusion which is hard to make just by looking at the filtered imagery.
+However, by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer conclusive evidence.
+
+Much more detailed discussion on this topic, 
+  under the context of evaluating sar speckle filter is published in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+Unfortunately, due to space restriction, only a brief and critical exploration is explored here for polsar speckle filters.
+This section serves more as an illustration of how the proposed theoretical model can be applied on practical scenario,
+  as it is not as a full proposal for such an evaluation procedure for polsar speckle filters.
+
+\section{Discussion and Conclusion}
+\label{sec:discussion_conclusion}
+
+\subsection{Related Work in Literature}
+This sub-section reviews some relevant and published works on proposing different measures of distance for POLSAR data. 
+specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+
+The common used measure of distance for matrices are either the Euclidean or the manhattan distance.
+They are defined in the following equations, respectively 
+The Manhattan distance is
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+In the context of polsar covariance matrix, however, they are not widely used 
+  probably because of the multiplicative nature of the data.
+
+In the field of POLSAR, the Wishart Distance is probably the most widely used as part of the well-known Wishart Classifier \cite{Lee_1999_TGRS}.
+The distance is defined as \cite{Lee_1994_IJRS_2299}
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, it main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dis-similarity measures.
+They are: the asymmetric and the symmetric refined wishart distance\cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance\cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance\cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance\cite{Cao_2007_TGRS_3454}
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+.
+
+In comparision to these formula, the distance measure for two covariance matrix proposed in this paper can be written as:
+\begin{equation}
+  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
+\end{equation}
+At the first glance, while the propose formula may be a lot simpler, it is still very similar to others in making use of the log-determinant.
+
+Closer investigation of these dissimilarity measures reveals that most of them are related to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered as the special case of the Wishart Statistical Test distance, where the two data set have the same number of look $L_x=L_y$.
+And it is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper have fixed statistical behaviour just by comparing the symmetric and asymmetric versions of the Refined Wishart distance, assuming that they are shown to follow fixed distributions.
+
+The close relation among these is further supported by the fact that
+In fact, in their proposal, all of the work referenced the statistical model developed in todocite as their foundation.
+Interestingly, the change detection model also make use of determinant ratio and log determinant in its derivation.  
+The next sub-section will illustrate how the log-determinant model studied in this paper can an alternative and simple derivation for the change-detection statistics.
+
+%which intuitively should have its statistics bouded
+%  as evidentally $tr(V_xV_y^{-1}) - p$ is bounded.
+
+%The Wishart test statistics given by Cao where $V = \frac{\sum^{N_x+N_y}_{i=1}V_i}{N_x + N_y}$
+%and $N_i$ is the number of pixel in cluster $V_i$.
+
+%Note that all Barlett distance, Anfinsen Revised Wishart distance and Cao Wishart test statistics are derived from Conradesen statistical model.
+%\cite{Kersten_2005_TGRS_519} reviewed the distances
+%  and stated $\ln{Q}$ is proportional to Bhattacharyya distance
+%  which is defined for multi-variate Gaussian distribution $p_i=N(m_i,P_i)$ as
+%  \begin{equation}
+%    D_B={1\over 8}(m_1-m_2)^T P^{-1}(m_1-m_2)+{1\over 2}\ln \,\left({\det |P| \over \sqrt{\det |P_1| \, \det |P_2|} }\right)
+%  \end{equation}
+%where $m_i,P_i$ is the mean and covariances of the distributions
+%and $P=(P_1+P_2)/2$.
+%Lee KY gives \cite{Lee_2011_IGARSS_3740} Bhattacharyya distance for POLSAR as
+%\begin{equation}
+%  r(V_x,V_y) = \frac{|V_x|^{1/2} |V_y|^{1/2}}{|(V_x+V_y)/2|}
+%\end{equation}.
+%\cite{Lee_2011_IGARSS_3740}  also derive the revised Wishart distance from the log-likelyhood distance. 
+%
+%
+%Wishart Chernoff distance given by Dabboor \cite{Dabboor_Thesis_2010}
+%\begin{equation}
+%  d(V_x,V_y) = \left[ \beta \ln|V_x| + (1-\beta) \ln|V_y| \right] - \ln | \beta V_x^{-1} + (1-\beta) V_y^{-1} |
+%\end{equation}
+%where $0<\beta<1$ is a parameter that minimizes $f(\beta)=e^{-d(V_x,V_y)}$ which ensure classification error is minimized.
+%Minimal classification error is ensured by Chernoff bound
+% which gives exponentially decreasing bounds on tail distributions of sums of independent random variables.
+%For the complex Wishart distribution, the Chernoff bound is given by: $P(error) < p^\beta(C \in C_1) p^{1-\beta}(C \in C_2) e^{-f(\beta)}$
+%Apparently, while the given methodology is a bit contrived,
+%  it also used $\ln|C|$ as the base for comparision. 
+%
+%In conclusion, the Manhattan distance and Euclidian distance is probably suffers from heteroskedastic problem and hence is probably inconsistent.
+%The other dis-similarity measures are
+%  the Wishart test statistics\cite{Cao_2007_TGRS_3454}, %given by Cao [Cao et al., 2007]
+%  the Barlett distance \cite{Kersten_2005_TGRS_519}, %reviewed by Kersten [Kersten et al., 2005]
+%  and the revised Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR}.% proposed by Anfinsen [Anfinsen et al., 2007].
+%%Our friends in EADS, LKY and Timo [Lee and Bretschneider, 2011] shows derivations
+%It has been shown that\cite{Lee_2011_IGARSS_3740} all these measures of distance are related.
+%Specifically the Barlett distance is porportional to Bhattacharyya distance.
+%At the same time the Revised Wishart distance also can be derived using the Conradsen statistics.
+
+\subsection{The Likelyhood Statistics for POLSAR}
+
+To detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelyhood ratio statistics for POLSAR covariance matrix is considered \cite{Conradsen_2003_TGRS_4} 
+\begin{equation}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation}
+
+Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
+\end{eqnarray}
+
+To detect changes, a test statistics is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, originally in the proposed work, only an asymptotic distribution is derived.
+In this sub-section, a statistical model is developed for this measure of distance.
+
+Since both $Z_x$ and $Z_y$ follow complex wishart distribution with $L_x$ and $L_y$ degrees of freedom,
+  $Z_x+Z_y$ also follows the complex wishart distribution with $L_x + L_y$ degrees of freedom.
+In view of the models denoted in Eqn. \ref{eqn:log_determinant_distribution},
+  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+  but the whole statistical distribution for it can be simulated as well:
+\begin{eqnarray}
+%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+  \ln{Q} &\sim&  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim& e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
+\end{eqnarray}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+In the common case of $L_x = L_y$, the test statistics become
+$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
+This and the barlett distance introduced earlier are closely related, in fact they are just shifted versions of each other.
+under exactly the same assumptions, 
+The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should provides another consistent and equivalent approach,
+  with probably simpler conceptual model and computational derivations. 
+%a slightly simpler statistics.
+The details application of this in edge-detection however is outside the scope of this paper.
+
+\subsection{Discussion}
+
+Let us start the discussion by noting a few theoretical properties of the proposed statistical model
+First, The use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the second order statsitics POLSAR matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigen values.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigen-values of M.
+Thus similar to other eigen-value based approach (e.g. Entropy/Anisotropy, ...),
+  the models presented here is invariant to polarization basis transformations.
+
+Second, the model is developed for the polsar covariance matrix.
+However, since the polsar coherent matrix is related with the covariance matrix via an unitary transformation, which preserves the determinant as invariant,
+The model should also be applicable on the coherency matrix.
+
+The model is far from complete.
+ It calls for the reduction of the multi-dimensional POLSAR data into a scalar value.
+While this is probably desirable for a wide range of application where a one-dimensional number is required to represents the complex multi-dimensional data,
+  such a reduction is probably not lossless.
+Thus similar to the way the Wishart Classifier is employed, to better understand polsar data
+  the use of this technique should be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g. Freeman Durden or entropy/anisotropy TODO:CITE ...)
+
+But at the same time, the model is also promising.
+The models presented in this paper are first developed for partial and monostatic POLSAR data,
+It is then shown to be also applicable to the traditional sar data.
+Since the model's assumptions are quite minimal, It may also work on bi-static and intererometric data,
+  though that requires further investigations.
+Other interesting phenomena which may warrant more study include the applicability of the model on correlated polsar channels ($S_{hh},S_{vv}$) as well as a better explanation in the use of mse to evaluate polsar speckle filters.
+
+Many practical applications may also be developed using the model and its derivatives.
+First, The model allow for the estimation and simulation of non-natural equivalent number of look.
+This come in especially handy when some real-life data is given,
+  where the effective number of look may not be equals to the nominal stated number-of-look after multi-look-processing.
+In such case, better-match models can be derived
+  by roughly estimating the effective ENL 
+  which usually results in a number with fractions.
+
+Similar to the way other measures of distance can be used to derive POLSAR classifier \cite{Lee_1999_TGRS}, change detector \cite{Conradsen_2003_TGRS_4}, edge detector \cite{Schou_2003_TGRS_20} or other clustering cite and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}
+new detection / classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+And since extensive evidence have been shown supporting the use of MSE for SAR data,
+  it is reasonable to expect the relevant of MSE for POLSAR data.
+If that is the case, a large number of existing algorithms can become applicable to the POLSAR model in log-transformed domain,
+  which has been shown to be both additive and homoskedastic.
+
+\subsection{Conclusion}
+\label{sec:conclusion}
+
+In conclusion, an additive and homoskedastic model, 
+  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+  were proposed in this paper.
+The theoretical model is shown to be powerful.
+Not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts:
+  i.e. POLSAR test statistics or ENL estimation 
+but it also puts several well-known models for the traditional SAR within its natural coverage. %as its natural special case.
+The statistical model is based on the determinant of the POLSAR covariance matrix,
+  which when converted into one-dimensional data
+  is gracefully transformed into the traditional SAR intensity.
+Consequently, the derived dis-similarity measures may be employed in a wide range of application
+  where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+The model is also shown to be practically versatile. 
+It is capable of handling a few imperfect conditions found in practical data.   
+As both an application of the model,
+  as well as an extension of our previous work in evaluating SAR speckle filters\cite{Le_2010_ACRS},
+  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored.
+And intially promising results are reported.
+
+%Just like it is shown for the simpler case of SAR data processing\cite{Le_2010_ACRS},
+%  when these distances are computed in the log-transformed domain,
+%  their theoretical statistic models become additive and homoskedastic.
+%The models are shown to be theoretically powerful.
+%Not only they can provide alternative and sometimes simpler explainations to a range of theoretical concepts:
+%  i.e. change detection test statistics or ENL estimation
+%but also a number of results for one-dimensional SAR can be shown as special cases of the POLSAR models.
+%They are also pratically versatile enough
+%  capable of explaining the imperfect over-sampling practice evident in RADARSAT2 data.
+%Finally, to extend our previous work in evaluating SAR speckle filters,
+%  the applicaton of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored
+%  with promising results reported.
+
+\appendices
+\section{Homoskedastic Model for the Log-Determinant}
+\label{chap:appendix_a}
+
+\subsection{Log-Chi-Square Distribution and its Derivatives}
+%\section{Log-Chi-Square Distribution}
+\renewcommand{\theequation}{\thesection.\arabic{equation}}
+\setcounter{equation}{0}
+
+This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
 
@@
 
-\subsection{Summary Statistics of Some POLSAR Observables}
+\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
 
@@
 
-\subsection{The characteristic function of some dissimilarity measures for polsar}
+\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
+\label{sec:appendix_b}
 
@@
   the CF for the following random variables,
-  which are combinations of the above elementary random variables, can be derived
+  which are combinations of the above elementary random variables, are to be derived
 \begin{eqnarray*}
@@
 we have:
-\begin{eqnarray}
-  CF_{\chi^d_L}(t) &=& \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{L}} &=& \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{D}} &=& \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-\end{eqnarray}
+%\begin{eqnarray}
+%\end{eqnarray}
+\begin{align}
+  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
+\end{align}
 
@@
 we arrive at:
-\begin{eqnarray}
+\begin{align}
   CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-\end{eqnarray}
+\end{align}
 with $\Gamma()$ and $B()$ denotes Gamma and Beta functions respectively.
 
-\subsection{SAR intensity as the special case of the POLSAR cov-matrix determinant}
+\section{SAR intensity as the special case of POLSAR covariance matrix determinant}
 \label{sec:appendix_sar_special_case_of_polsar}
@@
 
-\subsubsection{Original Domain: SAR Intensity and its ratio}
+\subsection{Original Domain: SAR Intensity and its ratio}
 
@@
 
-\subsubsection{Log-transformed domain: SAR log-intensity and the log-distance}
+\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
 
@@
 
-\subsubsection{Deriving the PDF for SAR dispersion and contrast}
+\subsection{Deriving the PDF for SAR dispersion and contrast}
 
@@
 
-%\section{Simulating All Elements of POLSAR Covariance Matrix}
-%
-%Jong sen lee simulation procedures is applied and verified in 2x2 partial polsar AIRSAR Flevoland image.
-%Pipia method explicitly indicates cholesky decomposition,
-%  while the exponential notion in Lee's book appear to suggest svd decomposition
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[verify polsar 2x2 simulation: S11]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S11.eps} 
-%		 \label{S11}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S22]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S22.eps} 	
-%		 \label{S22}
-%	} \\
-%	\subfloat[verify polsar 2x2 simulation: S12r]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S12r.eps} 
-%		 \label{S12r}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S12i]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S12i.eps} 	
-%		 \label{S12i}
-%	}        
-%\end{tabular}
-%\caption{verifying polsar 2x2 simulation: the components}
-%\label{fig:verify_polsar_2x2_simulation_components}
-%\end{figure}
-%
-%The same procedure does not appear to work on 3x3 full polarimetric POLSAR image.
-%Despite all other elements match nicely, the ShhSvv* element does not appear to match.
-%However, the log-det still appears to be consistent
-%  and more importantly all dis-similarity measures still match.
-%  
-%\begin{figure}[h!]
-%\centering
-%\epsfxsize=6.0cm
-%\epsffile{images/verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation.eps} 
-%\caption{3x3 svd simulation: 13 element mismatch}
-%\label{fig:verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation}
-%\end{figure}
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[C11]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.11.eps} 
-%		 \label{11}
-%	} 
-%	\hfill	
-%	\subfloat[C22]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.22.eps} 
-%		 \label{22}
-%	} 
-%	\hfill	
-%	\subfloat[C33]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.33.eps} 
-%		 \label{33}
-%	} \\
-%	\subfloat[C12r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12r.eps} 
-%		 \label{12r}
-%	} 
-%	\hfill	
-%	\subfloat[C13r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13r.eps} 
-%		 \label{13r}
-%	} 
-%	\hfill	
-%	\subfloat[C23r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23r.eps} 
-%		 \label{23r}
-%	}  \\
-%	\subfloat[C12i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12i.eps} 
-%		 \label{12i}
-%	} 
-%	\hfill	
-%	\subfloat[C13i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13i.eps} 
-%		 \label{13i}
-%	} 
-%	\hfill	
-%	\subfloat[C23i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23i.eps} 
-%		 \label{23i}
-%	}
-%\end{tabular}
-%\caption{verify polsar 3x3 simulation with polarization basis change}
-%\label{fig:verify_polsar_svd_3x3_simulation_polarization_basis_change}
-%\end{figure}
-%
+% references section
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,article}
+
+\end{document}

### 2013-03-01 paper_dev/article_ivm.tex
201303_Mar01

%\documentclass[a4paper,10pt]{article}
\documentclass[journal]{IEEEtran}
%\documentclass[a4paper, 10pt, conference]{ieeeconf}

\usepackage{cite} %for citations

 %this is for math typing (eg: cases)
\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{epsfig} %for figures

\usepackage[center]{caption}%for captions
\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures

%opening
\title{ 
	Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.
}

%\author{Thanh-Hai Le, Ian McLoughlin}
\author{Thanh-Hai~Le,
        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
	Brian~Quang-Huy~Nguyen,
	Nicholas~Chan-Hua~Vun%
	%Ken-Yoong~Lee, 
	%and Timo~Brestchneider % <-this % stops a space
\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen, Nicholas~Chan-Hua~Vun, and Ian~McLoughlin are with School of Computer Engineering, 
Nanyang Technological University, Singapore,}% <-this % stops a space
%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
\thanks{Manuscript received ?, 2012; revised ?.}}

\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, Jul~2012}%
{ Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }

\begin{document}

\maketitle

\begin{abstract}

Logarithmic transformation has the potential to convert 
	the multiplicative and heteroskedastic statistical distribution of SAR speckle noise into 
	a simpler additive and homoskedastic distribution model.
From this homoskedastic model, within the log-transformed domain, 
	a few consistent measures of distance emerge.
With these, subtractive differences become consistent and predictable. 
We show, through experiments and analysis, that 
	the familiar mean squared error (MSE) criteria can reliably serve 
		as a single unifying performance indicator to evaluate SAR speckle filters. 
In homogeneous areas, we determine a mathematical relationship that links the variance of log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
	is shown to be equivalent to the ratio-based radiometric preservation criteria usually assessed in the original domain. 
Through experiments, and analysis, we show that lower MSE suggests better feature detection and classification ability, an important requirement for subsequent post-filtering steps in practical SAR data processing.
Combined, we propose and describe the use of log-transformed MSE to evaluate SAR speckle filters.

\end{abstract}

\begin{IEEEkeywords}
Synthetic aperture radar, speckle-filtering, homoskedasticity, mean-squared-error
\end{IEEEkeywords}

\IEEEpeerreviewmaketitle

\section{Introduction}

The nature of SAR speckle is that
	it is stochastic even when the underlying radiometry is constant, 
	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
Then speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.

SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
Estimators are typically evaluated based on the bias and variance properties of their estimates; 
	with lower bias and / or lower variance (hence lower MSE) being indicative of better accuracy.
Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
Also, due to the stochastic nature of SAR processing, as well as simulating process, 
	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.

Our survey of SAR speckle filter research, however, indicates 
	a different picture from the standard practice of the statistical framework, 
	specifically, in the stage of performance evaluation. 
Due to the multiplicative and heteroskedastic nature of speckle noise, 
	bias and variance evaluation may not be the most useful measures. 
Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
	so alternative evaluation criteria are proposed.
In fact, a survey of relevant literature fails to reveal 
	a single universally agreed quantitative metric for the performance of speckle filters.

The common theme is that each newly proposed speckle filter tends to be published along with a methodology for evaluating its performance.
Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
Some papers do present quantitative measurements, 
	however  due to the lack of a standardized performance criteria, 
	the evaluation metrics can change significantly from one paper to the next.

In this paper, we propose and evaluate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
The paper is structured as follows.
Section \ref{sec:lit_review} briefly surveys related work in the published literature, Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
%And the last section provides our discussion together with our concluding remarks.
Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.

\section{Related Work in Literature}
\label{sec:lit_review}

%Addressing this issue, 
%There have been a few published articles dedicated to the topic of evaluating speckle filters.
%However, our survey of SAR speckle filtering research indicates 
%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
%In this section, we briefly review published work 
%	related to the topic of evaluating SAR speckle filters.	
It is customary to divide the evaluation of speckle filters into their performance across the two classes of 
	homogeneous and heterogeneous regions.
Across homogeneous areas,
	speckle filters are expected to estimate with negligible radiometric bias.
Thus evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
By contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, due in part to the following difficulties.
The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
The second challenge is then to define a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.

In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters. Furthermore, its application in a SAR processing framework should allow an improvement in the measurement, detection or classification of the underlying radiometric features.
%As shown in the subsequent section, 
%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
As shown in the subsequent sections, by applying log-transformation, 
	this overall requirement of speckle filtering can be broken down into two smaller requirements.
On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
The MSE evaluation is a combined evaluation of bias and variance error, and is therefore capable of evaluating the general requirement of speckle filtering.
%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.

For homogeneous scenes where the underlying radiometry is assumed to be constant, 
	the filtered results, statistically speaking, are considered to be samples of 
		a single but complex stochastic process.
%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
	%are expected to estimate with no radiometry bias. 
%The best filters achieve maximum speckle suppression power in such areas.

One metric that can be used to detect radiometric distortion is the ratio between the estimated and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.

Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
In this paper, we will also show that all of these standard filters 
	not only preserves the expected radiometric values, 
	but in the log-transformed domain they also preserve a few subtractive and consistent measures of distance.

Several metrics have been developed to evaluate speckle suppression power.
The most common measure is the Equivalent Number of Looks (ENL) index 
$ENL=avg(I)^2/var(I)$
that was proposed by Lee \cite{Lee_1981_CGIP}.
Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
%	which is a component of MSE evaluation, 
%	can be and practically has been used to evaluate speckle filters.
%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.

Real-life and practical images, however, are not homogeneous.
Thus there are a few associated difficulties in evaluating speckle filters over heterogenous scenes.
%and there are many proposed methods of evaluating speckle filters in such areas. 
%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous
However, without simulation or access to solid ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters estimation).

Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
Being random, this should display as little ``visible'' structure as possible. 
%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
The ratio image then becomes a simple subtraction image.
The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).

Another way to evaluate speckle filters is by assessing the feature preservation characteristics of the original noised data and those of the filtered image. 
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation would then determine how closely related the two feature maps are. 
Various methods may be applied to extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
While significant effort has been spent on these evaluations, serious doubts remain concerning the precision of this methodology.
This is because feature extraction algorithms are only approximations 
	whose accuracy is 
		not only dependent upon the characteristics of the original image 
		but also heavily reliant on the inherent noise.
Unfortunately, speckle filters invariably alter the noise characteristics.
Thus, without a clear understanding of these dependencies and no absolute ground truth, 
	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results, especially its accuracy.
%is just too imprecise for us.

Since SAR statistical models are quite well understood, 
	simulation experiments with known ground-truth can be employed 
		to evaluate speckle filters.
		%without the need to apply feature detection. 
In this paper, we also make use of a similar methodology discussed above with two important changes.
Firstly, our simulated experiments offer absolute ground-truth.
Secondly, our threshold-based feature extraction algorithm is extremely simple.
More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
This performance can be 
	conveniently visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
	as well as objectively quantified by measuring the Area Under this Curve (AUC). 
As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of feature preservation capabilities for different speckle filters.

%There are two main ways that ground truths are used in evaluating speckle filters.
%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
%Normally the image is large, with a number of different features and test conducted in once. 
%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
%
%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
%Since the structure is repeated many times, the combined results become more representative. Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
%The drawback is that only a single type of target can be tested per image. These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).

Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
This is the second difficulty in evaluating speckle filters for heterogenous scenes.
Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional levels.
In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa. 
%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.

Overall, many different methods and metrics have been proposed to evaluate varios aspects of speckle filters. 
However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and is still subjective in nature.

%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
%	where $E()$ denotes expectation operator.

Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, the use of MSE is not straightforward. 
Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.

%Thus we propose the use of MSE in the homoskedastic log-transformed domain to evaluate eps. 
%This is similar to the investigation of residual image in log-transformed domain and also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters have no problem preserving the mean). We also show experimentally that this MSE measure is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability can be.

In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
As the important Gauss Markov theorem becomes applicable again, 
	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
Initial intitution suggests that each components of the MSE measure, 
	namely bias and variance evaluation, can be mapped into 
	the requirements of radiometric preservation and speckle suppression for speckle filters.
Before the details of our evaluation methodology is discussed and presented, 
	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.

\section{Logarithmic Transformation}
\label{sec:log_transform}

In the first portion of this section,
    the SAR speckle model in the original domain is shown to be multiplicative and heteroskedastic.
Next the impacts of heteroskedasticity on speckle filtering is discussed.
Then logarithmic transformation is shown to convert original speckle data into an homoskedastic model, where the noise is not only additive, but also independent of the underlying radiometric signal.
From the consistent and additive noise in log-transformed domain,
    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and variance ($var(ln(I))$) are described.

\subsection{Original Heteroskedastic Model}

SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components, each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:

\begin{equation}
\label{eqn:component_signal_pdf}
pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
\end{equation}

It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.

\begin{IEEEeqnarray}{l l l}
pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -{A^2}/{\sigma^2} \right) }\\
pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -{I}/{\sigma^2} \right) }
\end{IEEEeqnarray}

From a statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to $\sigma$ unit distributions given below:

\begin{IEEEeqnarray}{l l l}
pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
pdf(I_1) &=& e^{ \left( -I_1 \right) }
\end{IEEEeqnarray}

It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
These relationships evidently manifest a multiplicative nature. 
In fact, this condition has long been noted, but from different perspectives, in various SAR models including the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.

\begin{table}[!h]
\caption{Both the mean and the variance of noisy SAR image data are related to the scale factor $\sigma$.}
\label{tbl:orginal_sar_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(A_1) = { \sqrt{\pi}}/{2}$ & $var(A_1) = {(4-\pi)}/{4}$ \\
$avg(I_1) = 1$ & $var(I_1) = 1$ \\
$avg(A) = {\sigma \cdot \sqrt{\pi}}/{2} $ & $var(A) = \sigma^2 \cdot {(4-\pi)}/{4} $ \\
$avg(I) = \sigma^2 $ & $ var(I) = \sigma^4$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean. 
In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; estimating variance is equal to estimating the mean and is equivalent to the main problem, ie. estimating the unknown parameter $\sigma$.

The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.

\subsection{The effects of Heteroskedasticity on Speckle Filters}

%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily. 
%That is because: 
Even though the statistical model within individual resolution cells is well established, the applicability of its models is restricted to homogenous areas. 
Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial varition also gives rise to the heteroskedasticity phenomena. 
Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying back-scattering coefficient $(\sigma)$.
It is believed that this heteroskedasticity give rise to serious negative impacts at various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences to the central question of homogeneity or heterogeneity. 
In normal images, the contrast or variance among neighboring pixels is often used to measure homogeneity. 
Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent to estimating $\sigma$).
%The fact give rise to the vicious circle in SAR speckle filtering.

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, together with the normal Mean Squared Error evaluation criteria in serious doubt. 
If the variance is known \textit{a priori}, it has been proven, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
The caveat however is that in SAR speckle filtering, variance is not known a priori. 
And eventhough variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.

Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
The technique determines outlying points as being too far away from the standard deviation. 
However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required and used. 
It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. 
Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. 
Each of these tasks require good similarity or discriminant functions. 
Foundational to these is the need of a consistent measures of distance. 
Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. 
This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are
 believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.

\subsection{ Homoskedastic effect of Logarithmic Transformation }

In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet maintains an ability to transform heterskedactic speckle into a homoskedastic relationship. Thus the original variables become:

\begin{IEEEeqnarray}{l l l l l}
L_{1}^{A} &=& \log_2(A_1) &=& L_{1}^{I} / 2 \\
L_A &=& \log_2(A) 	&=& L_{1}^{A} + \log_2\sigma \\
L_{1}^{I} &=& \log_2(I_1) &=& 2 L_{1}^{A} \\
L_I &=& \log_2(I) 	&=& L_{1}^{I} + 2 \log_2\sigma
\end{IEEEeqnarray}

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variables as follows:

\begin{IEEEeqnarray}{l l l}
pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left[ 2 L_{1}^{A} - 2^{2 L_{1}^{A}} \right]} \\
pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
pdf(L_{1}^{I}) &=& 2^{\left[ L_{1}^{I} - 2^{L_{1}^{I}} \right]} \\
pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} 
\end{IEEEeqnarray}

Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$

\begin{table}[!h]
\caption{ Mean and Variance of Log Transformed SAR values. }
\label{tbl:sar_log_domain_avg_var}
\normalsize
\centering
%\begin{center}

\begin{tabular}{|l|l|}
\hline
Mean & Variance \\
\hline
$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
\hline
\end{tabular}

%\end{center}
\end{table}

The equations above also highlight the relationships among random variables in the log-transformed domain. 
Two conclusions become evident from these formula. 
Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation is clearly manifested. 
Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  defined as the independence of the conditional expected variance on the conditional expectation of the mean.

This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. The main difference would be the use of base-2 logarithm which is prefered here for faster computation.

Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
It can be seen that while the original data, especially intensity values, should be preferred for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast. 
Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (including wavelets) and computational (including artificial neural network) techniques into SAR data.

\begin{table*}[t]
\normalsize
%\hrulefill

%\begin{center}
\centering
\caption{ The properties of observable SAR random variables }
\label{tbl:sar_variables_properties}

\begin{tabular}{|l|l|l|l|}
\hline
 RV & Relationships  & Variance (skedasticity) & Mean (biasness) \\
\hline
$A$ & $A=\sigma A_1 $ & Heteroskedastic $var(A) = \frac{(4-\pi)}{4} \cdot \sigma^2 $ & Unbiased $avg(A) = \frac{\sqrt{\pi}}{2} \cdot \sigma $ \\
$I$ & $I=A^2=\sigma^2 I_1 $ & Heteroskedastic $ var(I) = \sigma^4$ & Unbiased $avg(I) = \sigma^2 $\\
$L_A$ & $L_A=\ln(A)=L_{1^A} + \log_2{\sigma}$ & Homoskedastic $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ \\
$L_I$ & $L_I=\ln(I)=L_{1^I} + 2 \log_2{\sigma}$  & Homoskedastic $var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ & Biased $avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ \\
\hline
\end{tabular}

%\end{center}
\end{table*}

In order to explore this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
The excellent agreement is self-evident in the graph which confirmed the log-transformed model. 
In fact, this modelling has been used successful in explaining speckle phenomena, also verified through scientific experiments \cite{Ulaby_TGRS_1988}.

\begin{figure}[h]
\centering
%\centerline{
\begin{tabular}{c}
	\subfloat[amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/intensity_histogram.eps} 	
		 \label{intensity}
	} \\
	\subfloat[log amplitude]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_amplitude_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[log intensity]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_histogram.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Observed histogram in homogenous area and modelled pdf response}
\label{fig:modelled_response}
\end{figure}

\subsection{Consistent measures of distance in Log-Transformed domain}

The consistent sense is explored and illustrated in this section from two different perspectives. 
First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random variable deviation defined as the distance between an observable sample and its expected value:

\begin{IEEEeqnarray}{l l l l l}
D_A &=& A &-& avg(A) \\
D_I &=& I &-& avg(I) \\
D_{L^A} &=& L_A &-& avg(L_A) = log_2{ \left( \frac{A}{avg(A)} \right)}\\
D_{L^I} &=& L_I &-& avg(L_I) = log_2{ \left( \frac{I}{avg(I)} \right)}
\end{IEEEeqnarray}

Noting the results from the previous section, the pdf for these variable can be trivially given as

\begin{IEEEeqnarray}{l l l}
pdf(D_A) &=& 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] } \\
pdf(D_I) &=& \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
pdf(D_{L^A}) &=& 2 \cdot 2^{\left[ \left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
pdf(D_{L^I}) &=& 2^{\left[ \left( D_{L^I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} \right]}
\end{IEEEeqnarray}

It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but are independent of it in the log-transformed domain.

From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider a random variable defined as the contrast between two measured samples, in the log-transformed domain:

\begin{IEEEeqnarray}{l l l l l}
C_{L^A} &=& L_1^{A_\sigma} &-& L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
C_{L^I} &=& L_1^{I_\sigma} &-& L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
\end{IEEEeqnarray}

Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is consistent in the log-domain but inconsistent in the original domain. The pdf of these variables can be given as:

\begin{IEEEeqnarray}{l l l}
pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
\end{IEEEeqnarray}

Figure \ref{fig:residual_as_noise} illustrates this, showing excellent agreement between the analytical pdf and observable histogram of deviation and contrast of the same area in a log-transformed intensity RADARSAT-2 image. 
Distance is calculated as the difference between each value point and the average value of that region, while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.

\begin{figure}[h!]
\centering
%\begin{tabular}{c}
	\subfloat[dispersion]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_dispersion_histogram.eps} 	
		 \label{amplitude}
	} 
	\hfill
	\subfloat[contrast]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_intensity_contrast_histogram.eps} 	
		 \label{intensity}
	}
%\end{tabular}
\caption{Observed and modelled pdf of deviation and contrast in homogenous log-transformed intensity images.}
\label{fig:residual_as_noise}
\end{figure}

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the measure of observable deviation in original SAR data differs, ie. is inconsistent, across different homogenous areas. 
The observable deviation in the log-transformed domain however is consistently the same across different homogenous areas. 
One possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.

\subsection{Sampling distribution of Variance in Log-Transformed domain}

From the previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as

\begin{eqnarray}
pdf(V_{L^I}) &=& 
	\ln2 \frac{ 2^{\sqrt{V_{L^I}}}}{\sqrt{V_{L^I}} \left( 1+2^{\sqrt{V_{L^I}}} \right)^2} \\
pdf(V_{L^A}) &=&
	\ln2 \frac{2^{\sqrt{4V_{L^A}}}}{\sqrt{4V_{L^A}} \left( 1+2^{\sqrt{4V_{L^A}}} \right)^2} 
\end{eqnarray}

It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance constant but the sampling distribution of this random variable is independent of $\sigma$. 
We have seen this analytically for two sample variances. 
For a larger number of samples, Monte-Carlo simulation can be used to visualise the PDF of sample variances.

In summary, a few measures of distance are shown to be consistent, which agree with the consistent sense of variance / deviation and homoskedasticity.
The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use this way is illustrated in our kMLE speckle filter.
The consistent sense of contrast can be used to test if any pair of measured data points belong to the same class of scatterer. It may also 
explain why, in the original SAR domain, the ratio based detector / classifier is prefered to differential measures, which are not consistent. 
An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
The consistent sense of contrast also gives rise to a consistent measure of variance, which can be used to test if a group of pixels can form a homogenous area.
This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.

\subsection{ Speckle Filtering Process And The Homoskedastic Log-transformed Domain}
\label{sec:schema_log_images}

\begin{figure}
 \centering
 \epsfxsize=2.4in
 \epsfysize=1.2in
 \epsffile{src/simulation_schema.eps} 	
\caption{SAR simulation, processing and filtering schema}
\label{fig:simul_process_filter_schema}
\end{figure}

Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
The ``SAR processor'' block indicates that either of the following processes is occurring.
First is the normal arrangement of transformation whieh offers several consistent measures of distance, 
	which are hypothised to be significant  in evaluating speckle filters.
	A case in point is in visual evaluation of filtered results on real captured SAR images.
Since the radiometric ground-truth is not available, %the most common 
%In real SAR captured images, the radiometric ground-truth normally is not available.
	the most common way to evaluate speckle filters is by qualitative visual evaluation. A traditional method is to investigate the ratio images between the filtered output and the noisy input data.
Since logarithmic transformation converts the ratio image into a substractive residual, which is consistent, then residual analysis can be used to analyse and evaluate the performance of speckle filters.
To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig. \ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is of course iself a subjective one.

%Our qualititative conclusion is that
%	a. it is apparently easier to notice the ``visible structure'' being removed in the residual noise pictures than the ratio mages, and
%	b. even so, the above conclusion is at best quite subjective.
%Thus to compare the filters against each other, 
%	quantitative measures are preferred.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Original Patch]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Filtered Result]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.boxcar.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Ratio: Filtered / Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Ratio: Original / Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.ratio1.eps} 	
		 \label{intensity}
	}  \\
	\subfloat[Log Residual: Filtered - Original]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual2.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Log Residual: Original - Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.residual1.eps} 	
		 \label{intensity}
	} 
\end{tabular}
\caption{Visualising Removed ``Noise'': Ratio images in the original domain vs. Residual images in the log-transformed domain}
\label{fig:real_image_ratio_vs_residual}
\end{figure}

\begin{subequations} \label{eqn:eval_metric}
\begin{align}
MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
\end{align}
\end{subequations}
%\begin{eqnarray}
%MSE_{true} = E \left[ (\hat{X} - X)^2 \right] \\
%MSE_{noise} = E \left[ (\hat{X} - \tilde{X})^2 \right] \\
%MSE_{base} = E \left[ (\tilde{X} - X)^2 \right] \\
%MSE_{benchmark} = \left| MSE_{noise} - MSE_{base} \right| 
%\end{eqnarray}

As qualititative visual evaluation is subjective by nature,
	quantitative metrics and measurements are preferred, when relevant.
Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
When ground-truth is available, 
	either in simulated experiments or over homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated and true values.

In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be estimated reasonably well.
Thus the base MSE level which is also a measure of the speckle noise level, can also be estimated.
Naturally, the speckle filter should remove as much noise as possible, 
	while it also should not remove more variations than are caused by the speckle noise.
%Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base

\section{Evaluating Speckle Filters on Homogeneous Areas}
\label{sec:eval_homo}

In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is illustrated.
Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other components, namely, variance evaluation. 
Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance methods of evaluation are shown to be mathematically related to the ENL index.
The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle over homogeneous areas.

\subsection{ Estimating ENL from MSE index in homogeneous areas }
\label{sec:homogeneous_theoretical}

In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL index. 
Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
	then the MSE evaluation reduces to variance evaluation.
That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in the log-transformed domain.

Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
%Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variables as: 
\begin{equation}
var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
\label{eqn:perf_index_theoretical}
\end{equation}

%Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
In fact, we could estimate:
\begin{equation}
  var(\hat{X}^L) = \frac{1}{(L-0.5) \ln^2(2) }
\label{eqn:perf_index_analytic}
\end{equation}
Thus the ENL, L, can be estimated as:
\begin{equation}
\hat{L}_{est} = \frac{1}{var(\hat{X}^L) \ln^2(2)} + 0.5
\label{eqn:enl_analytic}
\end{equation}

The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and corrupted with single look SAR-speckle PDF. 
Different multi-look processing filters are then applied to the image patch. 
The observable variance in the log-transformed domain is recorded, and 
	 ENL estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms of mean and standard deviation.
The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
	together with the analytical values from Eqn. \ref{eqn:perf_index_analytic}.
These experimental results evidently validate the analysis given above.
They also shows that 
	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect 
	(since ENL is supposed to be an integer), the value obtained actually corresponds very closely with the nearest correct integer result.

\begin{table}
\centering
\begin{tabular}{r|c|c|c|c}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

The finding here is not inconsistent with other authors.
	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.

\subsection{Using log-variance to evaluate speckle filters}

Fig. \ref{fig:log_consistency_model} plots the histograms of homogenous SAR data over different radiometric values.
Both single-look simulated and multi-look processed/box-car filtered data is displayed.
Specifically the plots show that the log-transformed domain is consistent while the plots from the original domain are not.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Single Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi Look (Intensity)]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/orig_inconsistency_boxcar.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Single-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_none.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Multi-Look in Log Domain]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_boxcar.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{The Inconsistency evident in the original SAR domain and the Emerged Consistency demonstrated in the log-transformed domain}
\label{fig:log_consistency_model}
\end{figure}

Fig. \ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output. Intuitively, the boxcar filter is actually similar to multi-look processing, thus it also preserve the consistency property.
This consistency will also lead to the consistent sense of distance described earlier, and is significant because it is the tell-tale indicator of the consistent contrast and variance.
This ensures applicability of various target detection/classification algorithms which employ statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Lee filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_lee.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_kuan.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_frost.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Gamma MAP filter]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/log_consistency_map.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\caption{Filtered results: consistency in log-transformed domain}
\label{fig:log_consistency_filters}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|c|r|c|r}
Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
\hline
none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
\hline
none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
\hline
none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
\end{tabular}
\caption{ Filters' Performance: Homogeneous Area }
\label{tab:homogeneous_performance_filters}
\end{table}

Table \ref{tab:homogeneous_performance_filters} provides a quantitative comparison among the filters.
It shows that the filters can all preserve the underlying radiometric values, while their speckle suppression power can be equivalently measured using either variance in the log-transformed domain, or the standard ENL index.

\section{Evaluating Speckle Filters on Heterogenous Area}
\label{sec:eval_hetero}

%For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
%First, several test patterns is created to simulate and determine the performance of various speckle filters.
%Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
%As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.

In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
From a statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
Experimentally, on clear-cut simple target-background patterns, the results that follow will indicate that
	the lower the MSE achievable by a speckle filter,
	the better the feature preservation performance recorded for its output.

%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
The general requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservation and speckle suppression.
In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of statistical estimators.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC Curve (AUC).
We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.

Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern multiple times, the histograms of the target and background areas can be reliably obtained.
%They are expected to be consistent in log-transformed domain.
The target and background can then be seperated using a simple threshold based classification model.
The separability of the two stochastic populations are judged by the standard ROC, 
	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.

The types of pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous checker board scene. 
These test patterns could, of course, be concatenated into a larger composite test image, although we will consider them as separate images to allow easier analysis of the results.
%However we would prefer to highlight the results separately for each individual area.
Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention in the radar community where the target is signified by the brighter area of the image. 
Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Line: each line is 2 pixels wide, separated by 6 pixels background]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_line2.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Edge: each stripe is 4 pixels in width]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_edge.png.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Point: each point is a $2 \times 2$ square spacing 6 pixels apart]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_point.png.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Checker board: the squares are 4 pixels wide each side]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/pattern_checker.png.eps} 	
		 \label{intensity}
	} 
\end{tabular}
%}
\centering
\caption{Example windows of ground truth patterns, each $32 \times 32$ pixels in size.}
\label{fig:hetero_patterns}
\end{figure}

Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle, and then the filters applied onto these noised images.
From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be evaluated by examining the separability of the two background and target populations.
The separability of the two histograms is visualized by plotting the ROC in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
	while subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} plot the AUC.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Simulated Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.none.fi.jpg.eps} 	
		 \label{fig:hetero_patterns_roc_auc:amplitude}
	} 
	\hfill	
	\subfloat[Kuan Filtered Image]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
		 \label{fig:hetero_patterns_roc_auc:intensity}
	} \\
	\subfloat[Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:hist_unfiltered}
	} 
	\hfill	
	\subfloat[Histograms: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:hist_kuan_filtered}
	}  \\
	\subfloat[ROC: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:roc_unfiltered}
	} 
	\hfill	
	\subfloat[ROC: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
		 \label{fig:hetero_patterns_roc_auc:roc_kuan_filtered}
	} 
\end{tabular}
%}
\caption{Target and Clutter Separability: Histograms and resulting ROC Curve visualisation}
\label{fig:hetero_patterns_roc_auc}
\end{figure}

Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' capability to seperate.
In pre-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability.

In post-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and \ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account bias error.
Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicate that the output of the Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

%Also the speckle suppression is related to the measured variance.
Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
It shows that the MSE is inversely correlated to this separability index.
The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
The results suggest that the lower MSE achivable by the filters would lead to better feature preservation in general.

\begin{figure}
\begin{tabular}{c}
	\subfloat[Error Image: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.none.gt.jpg.eps} 	
		 \label{fig:hetero_patterns_mse:amplitude}
	} 
	\hfill	
	\subfloat[Error Image: Kuan Filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
		 \label{fig:hetero_patterns_mse:intensity}
	} \\
	\subfloat[Error Histograms: Unfiltered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
		 \label{fig:hetero_patterns_mse:unfiltered}
	} 
	\hfill	
	\subfloat[Error Histograms: Kuan-filtered]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
		 \label{fig:hetero_patterns_mse:kuan_filtered}
	}  
\end{tabular}
\caption{Bias Error Investigation: Image and Histogram Visualisation}
\label{fig:hetero_patterns_mse}
\end{figure}

\begin{table}
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline
\end{tabular}

\caption{Lower MSE suggest better feature detection, measured by the AUC index}
\label{tab:mse_auc_in_log_domain}
\end{table}

\begin{table}
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$ (p-value) & AUC - $MSE_{benchmark}$ (p-value) \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
\label{tab:mse_auc_corr_coeff}
\end{table}

\section{Using MSE to find the most suitable speckle filter for practical SAR images}
\label{sec:practical_conjecture}

In this section, our conjecture of using MSE in the log-transformed domain to find the most suitable speckle filter for practical real-captured SAR images is described.
In these scenarios, the ground-truth and hence the true MSE is not available.
Therefore only the residential MSE is computable.
Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters for a captured SAR image, 
	where the ground-truth and hence true MSE is not available.
Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its removed variation being closest to the inherent speckle noise.

Experimental results are presented as empirical evidence supporting the conjecture.
The experiments in the previous sections are repeated on single-look SAR images 
	which are simulated from given ground-truth aerial images. 
%The a heuristic rule is that 
%	if the best filtered results are those with minimal MSE 
%	then just by observing the residual MSE, 
%	the observable measure of these results will also achieve 
%		being the closest to the MSE of the inherent noise.
%Besides using visual evaluation to validate the conjecture, 
%	the full justification of this conjecture is outside the scope of this paper.
%Real images however are more complex than the patterns illustrated above. 
Then the filters are applied onto the simulated SAR images. 
Fig. \ref{fig:real_simulated_images} illustrates some of the images used for our experiments.

\begin{figure}
\begin{tabular}{c}
	\subfloat[A Rural Area in Vietnam]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[A Suburb of Ha Noi]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/simulated_images.hanoi_suburb.gt.jpg.eps} 	
		 \label{intensity}
	} %\\
%	\subfloat[NTU Campus]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/Aerialcampus.eps} 	
%		 \label{amplitude}
%	} 
%	\hfill	
%	\subfloat[Chu Thap Island of Vietnam]{
%		 \epsfxsize=1.5in
%		 \epsfysize=1.5in
%		 \epsffile{src/fiery.eps} 	
%		 \label{intensity}
%	} 
\end{tabular}
\caption{Ground Truth Images for simulation}
\label{fig:real_simulated_images}
\end{figure}

With the use of MSE being validated from previous experiments, 
	the most suitable filter can be considered as the one with the lowest true MSE.
Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
	the most suitable filter is also the filter that 
		has its observable residual MSE value being closest to the noise MSE (4.1167 in the case of this example).
%We validate the idea by qualititative evaluation, an example of 
The conjecture is also validated using visual evaluation, an example of
	which is presented in Fig. \ref{fig:real_simulated_image_results}.

\begin{table}
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
Vietnam rural	& none		& 4.1174	& 4e-35\\
Vietnam rural	& pde			& 3.8022	& 0.0368\\
Vietnam rural	& lee			& 0.4984	& 3.2555\\
Vietnam rural	& frost		& 0.3490	& 4.6856\\
Vietnam rural	& kuan		& 0.3396	& 3.6877\\
Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
Hanoi suburb	& none		& 4.1321	& 4e-35\\
Hanoi suburb	& pde			& 3.8004	& 0.0391\\
Hanoi suburb	& lee			& 0.5261	& 3.2598\\
Hanoi suburb	& frost		& 0.3811	& 4.7427\\
Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
\label{tab:mse_true_noise_log_domain}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[Ground-Truth Image ]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.gt.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
		 \epsfxsize=1.6in
		 \epsfysize=1.6in
		 \epsffile{src/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Simulated Real Images: Qualititative Validation}
\label{fig:real_simulated_image_results}
\end{center}
\end{figure}
%\end{figure*}

The results from the experiments in previous sections can also be used to validate the use of residual and benchmark MSE.
The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly correlated with feature classification capability, measured by the standard AUC index.

The filters are also applied onto a real RADARSAT--2 image.
In this case, since the ground-truth is not available, 
	only visual evaluation can be used to validate our conjecture.
Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE would probably suggest a more suitable filter.
Fig. \ref{fig:real_image_results} tends to confirm this visually.
%IVMThe conclusion in this can be found through further experiments with more images, 
%IVM	which cannot be shown here due to space limitation.

\begin{table}
\centering
\begin{tabular}{c|r|r}
Filter & $MSE_{residual}$ & $MSE_{benchmark}$\\
\hline
pde & 0.2583 & 3.8584 \\
map & 2.6936 & 1.4231 \\
kuan & 3.3924 & 0.7243 \\
lee & 3.4172 & 0.6995 \\
boxcar & 3.6918 & 0.4249 \\
frost & 4.1191 & 0.0024 \\
\hline
none & $MSE_{base}$ & 4.1167 
\end{tabular}
\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
\label{tab:mse_in_real_image}
\end{table}

%\begin{figure*}
\begin{figure}
\normalsize
\begin{center}
\begin{tabular}{c}
	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.pde.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.map.jpg.eps} 	
		 \label{intensity}
	} \\
	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.lee.jpg.eps} 	
		 \label{amplitude}
	} 
	\hfill	
	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
		 \epsfxsize=1.5in
		 \epsfysize=1.5in
		 \epsffile{src/heterogenous_real.log.image.frost.jpg.eps} 	
		 \label{intensity}
	}
\end{tabular}

\caption{Filtering Real Images: Smaller $MSE_{benchmark}$ suggests visually better images}
\label{fig:real_image_results}
\end{center}
\end{figure}
%\end{figure*}

\section{Discussion and Conclusion}
\label{sec:discussion}
\subsection{Discussion}

Although it is widely known that log transformation transforms multiplicative SAR speckle into additive noise, 
	one should note that the noise is not Gaussian.
In fact, figures presented in the previous sections show that 
	they are not even centered around the origin. 
This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not work very well in practice.
To counter this, the use of maximum likelihood estimation instead of simple averaging is suggested \cite{Le_2011_ACRS}. 
Interestingly, averaging is also the MLE operator in the SAR's original domain.

%It is interesting to note that all of the standard filters' outputs exhibit consistent plots of histogram in the log-transformed domain, suggesting a consistent sense of distance. 
Log tranformation also brings about a few consistent measures of dissimilarity.
This consistency can be found not only in single-look or multi-look SAR data, 
	but can also be found in filtered data of various ``standard'' speckle filters.
This is significant probably because it ensures the applicability of various target detection/classification algorithms, 
	which exploit these consistent statistical properties, 
	into not only pre-filtered data but also post-filtered data as well.
%There are numerous

This consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
For example, in the subsequent tasks of designing target detectors or classifiers, 
	it is normally desirable to engineer the solution to not only work on single-look or multi-look SAR data,
	but also be applicable on post-filtered data.
In such cases, these consistent measures of distance in the log-transformed domain could provide a sound theoretical basis.
In fact, a number of already proposed solutions appear to make use of this feature. 
%(cite here some SAR classification papers)
An example is the ratio based discriminator in the original domain.
Looking backwards, in designing new speckle filters, by ensuring that the filtered output preserves this consistent property,
	the new speckle filters would be eligible to be used as pre-processing steps for availble classifiers / detector.

Of course, there are other speckle filters that do not preserve such consistency (e.g. the pde filter \cite{You_TIP_2000}).
One could argue that it would not be fair to the judge such filters using the MSE criteria, 
	which tend to favour the ``standard'' filters.
While we respect any other criteria that are used, we reiterate the two points that firstly
our MSE criteria is closely related to the basic ENL criteria.
The experimental results indicated that the ENL measures for such filter (i.e. the pde filter) differ depending on the radiometric values.
Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
The MSE criteria is shown to be related to feature preservation requirements.
Thus it is relevant towards subsequent target detection / classification processing, 
	which is believed to be a relatively common subsequent processing step.
For these two reasons, the MSE criteria is advocated.

In the experiments above, speckle filters with a $3 \times 3$ sliding window were used, 
	although we are aware that the normal window size used is much larger. 
The reasons for maintaining a small window is that 
	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk among adjacent targets.
Secondly, we focussed on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
	and do not wish to advocate a particular ``best'' filter in practice. 
In other words, we addressed the methodology of evaluating speckle filters, 
	and did not directly address the design of speckle filters.
However, interested filter designers are invited to download the Matlab evaluation code used in this paper to evaluate their own designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.

In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators (i.e. speckle filters).
%The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
The use of small and simple patterns allowing detailed analysis can then be done repeatedly and reliably against the stochastic nature of SAR data.% on simulated small data sets without the need of a common real large image that is somehow representative. 
This helps in the mapping of qualitative requirements for the speckle removal process into specific and quantitative requirements in the design of speckle filters.
Its use also provides an absolute ground-truth, i.e. a solid base for comparison of results across different papers.

The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.%, there is no ground-truth.
Thus the result extension towards real images is only analogical.
While the proposed rule is heuristic, 
	the experimental results presented in this paper are shown empirically to be valid.

We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
%In fact, we believe the situation is more fuzzy when it comes to classifying a given noisy captured SAR scene 
While perfect homogeneous ground truth can be defined, 
	different heterogenous patterns exhibits different levels of heterogeneity. 
Even though different measures have been proposed to evaluate scene heterogeneity levels or to test for the homogeneity hypothesis, 
	for real captured images, where the absolute ground-truth is not available, 
	there does not appears to exist any certain way to assert a given image as being perfectly homogenous or absolutely heterogenous.
Thus while the distinction helps in clarifying the concepts, 
	it is probably a leaky abstraction.
%However, without ground trutth, there appears to not exist any certain way of classifying a given captured imagary scene as homogeneous or heterogenous. 
%In fact a few different measures have been proposed to evaluate scene homogeneity / heterogeneity.

%Similarly for 
The patterns used are chosen based on our exerience and of course may affects evaluation results. 
As different patterns result in different degrees in the scale of scene homogeneity / heterogeneity, 
	and they also appear to affect the performance and ranking of each speckle filters.
One extreme case is that of perfect homogeneity, where boxcar filters would be the best performer,
	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that the boxcar would not perform well.
%Our work suggest that the performance of speckle filters is probably scene dependent, 
%	our conjecture is that it may depends on the level of scene homogeneity.
%The full justification of that, however is outside the scope of this paper.
%In fact, we do not know of any pattern that would be fair towards every possible filters.
%So the patterns should only serves as guide lines, and filter designers may not want to overly optimize their filter's performance on any single of these patterns.
%As doing so may make the filter lose out in other aspects.

%While the patterns may not be the primary evaluative criteria, we believe that the MSE measure in the log-transformed domain (particularly log-2 transformed domain) should receive serious considerations by future filter designers. Again, this is due to good reasons: that the Gauss Markov theorem is applicable in this domain (and not in the original domain). Thus, we believe an optimization for minimal MSE is likely to succeed in good real-world performance.

%IVMReaders may also find the idea of matching the most suitable speckle filter to a given scene to be foreign.
%IVMIn fact, one hope aim of this study is being able to find ``the single best'' speckle filter.
%IVMIn reality, the numbers in our experimental results however do not unanimous advocate a single best filter. 
%IVMIn hind-sight, this is probably not to be expected,
%IVM	given that the well known trade off where a power speckle-suppression filter (e.g. the boxcar filter) would likely to perform poorly in highly heterogeneous scenes, where radiometric preservation becomes more critical.
%IVMSuch insight, when coupled with the fuzzy notion of homogeneity as being the special case of generalized heterogeneity, allow us to welcome the idea.

The current scheme of finding the most suitable speckle filter requires the application of all filters before a decision is made, something that may be computationally expensive.
A possible better alternative would be to predict the choice, escaping such massive requirements of processing.
This, however, is outside the scope of this paper.

\subsection{Conclusion}

To summarize, speckle filters are generally evaluated using many different qualitative criteria.
To compare the filters against each other, a method is needed to quantify and measure these various qualitative requirements and results.
Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.

Our contribution is mainly centered around a few points. 
Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, and illustrate it's efficacy for test images.
Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find the most suitable speckle filter for any given scene. 
In short, we propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.

It should also be noted that a similar consistent sense of distance also exists in polarimetric SAR (POLSAR) data. 
Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.
%We also excited with the prospect of applying a wide variety of MSE-based or discriminator based algorithms into SAR and POLSAR values in log-transformed domain.

% references section
\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,article}

\end{document}

### 2013-03-01 paper_dev/article_vch.tex
201303_Mar01

--- 2013-03-01 paper_dev/article_ivm.tex
@@
 \author{Thanh-Hai~Le,
-        Ian~McLoughlin,~\IEEEmembership{Senior Member,~IEEE}, 
-	Brian~Quang-Huy~Nguyen,
-	Nicholas~Chan-Hua~Vun%
+        Ian~McLoughlin, 
+	    Quang-Huy~Nguyen,
+	    Chan-Hua~Vun%
 	%Ken-Yoong~Lee, 
 	%and Timo~Brestchneider % <-this % stops a space
-\thanks{Thanh-Hai~Le, Brian~Quang-Huy~Nguyen, Nicholas~Chan-Hua~Vun, and Ian~McLoughlin are with School of Computer Engineering, 
-Nanyang Technological University, Singapore,}% <-this % stops a space
-%\thanks{Ken-Yoong Lee and Timo Brestchneider are with EADS InnovationWorks Singapore.}% <-this % stops a space
+}
+\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun, are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS InnovationWorks Singapore for 
+	initial discussions and for providing RADARSAT2 images used in this paper. }% <-this % stops a space
 \thanks{Manuscript received ?, 2012; revised ?.}}
@@
 	as a single unifying performance indicator to evaluate SAR speckle filters. 
-In homogeneous areas, we determine a mathematical relationship that links the variance of log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
+In homogeneous areas, we establish a mathematical relationship that links the variance of 
+	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
 For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
-	is shown to be equivalent to the ratio-based radiometric preservation criteria usually assessed in the original domain. 
-Through experiments, and analysis, we show that lower MSE suggests better feature detection and classification ability, an important requirement for subsequent post-filtering steps in practical SAR data processing.
-Combined, we propose and describe the use of log-transformed MSE to evaluate SAR speckle filters.
+	is shown to be equivalent to the ratio-based radiometric preservation criteria that is usually assessed in the 
+	original domain. 
+Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
+	ability, which is an important requirement for subsequent post-filtering steps in practical SAR data processing.
+In this paper, we hence propose and describe the combined use of log-transformed and MSE to evaluate SAR speckle 
+	filters.
 
@@
 Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
-Then speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.
+As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.
 
 SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
-The stages in this statistical framework consist of statistical modelling, estimator development and evaluating the estimators' performance. 
+The stages in this statistical framework consist of statistical modelling, estimator development and evaluation of the estimators' performance. 
 Estimators are typically evaluated based on the bias and variance properties of their estimates; 
-	with lower bias and / or lower variance (hence lower MSE) being indicative of better accuracy.
+	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
 Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-Also, due to the stochastic nature of SAR processing, as well as simulating process, 
+In addition, due to the stochastic nature of SAR processing, as well as the simulating process, 
 	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.
@@
 Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
-	so alternative evaluation criteria are proposed.
+	prompting alternative evaluation criteria to be proposed.
 In fact, a survey of relevant literature fails to reveal 
@@
 
-The common theme is that each newly proposed speckle filter tends to be published along with a methodology for evaluating its performance.
-Many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
+Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
+	performance. 
+As such, many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
 While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
-Some papers do present quantitative measurements, 
-	however  due to the lack of a standardized performance criteria, 
+Some papers do present quantitative measurements. 
+However, due to the lack of a standardized performance criteria, 
 	the evaluation metrics can change significantly from one paper to the next.
 
-In this paper, we propose and evaluate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
+In this paper, we propose and validate the use of MSE in the homoskedastic log-transformed domain to evaluate speckle filters. 
 The paper is structured as follows.
-Section \ref{sec:lit_review} briefly surveys related work in the published literature, Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
-Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to evaluate different filters' speckle suppression power over homogeneous areas.
+Section \ref{sec:lit_review} briefly surveys related work in the published literature, 
+Section \ref{sec:log_transform} provides a brief discussion of the logarithmic transformation.
+Section \ref{sec:eval_homo} then illustrates the use of variance (an MSE component) in the log-transformed domain to 
+	evaluate different filters' speckle suppression power over homogeneous areas.
 Section \ref{sec:eval_hetero} describes the use of the same MSE to evaluate the performance of speckle filters in heterogeneous areas.
-Section \ref{sec:practical_conjecture} hypothesises the use of residual MSE in the log-transformed domain 
+Section \ref{sec:practical_conjecture} hypothesizes the use of residual MSE in the log-transformed domain 
 	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
@@
 %	related to the topic of evaluating SAR speckle filters.	
-It is customary to divide the evaluation of speckle filters into their performance across the two classes of 
+It is customary to divide the performance evaluation of speckle filters across the two classes of 
 	homogeneous and heterogeneous regions.
-Across homogeneous areas,
-	speckle filters are expected to estimate with negligible radiometric bias.
-Thus evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators' output (i.e. the speckle suppression power).
-By contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, due in part to the following difficulties.
+Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
+As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
+	output (i.e. the speckle suppression power).
+In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, 
+	due in part to the following difficulties.
 The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
-The second challenge is then to define a quantifiable metric allowing the performance of different speckle filters to be measured and compared.
+The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
+	to be measured and compared.
 %IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.
@@
 In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
-Furthermore, its application in a SAR processing framework should allow an improvement in the measurement, detection or classification of the underlying radiometric features.
+Furthermore, its application in a SAR processing framework should enable an improvement in the measurement, 
+	detection or classification of the underlying radiometric features.
 %As shown in the subsequent section, 
@@
 As shown in the subsequent sections, by applying log-transformation, 
-	this overall requirement of speckle filtering can be broken down into two smaller requirements.
-On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric preservation requirement).
+	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
+On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
+	preservation requirement).
 On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
-These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias and variance error of the output.
-The MSE evaluation is a combined evaluation of bias and variance error, and is therefore capable of evaluating the general requirement of speckle filtering.
+These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
+	and variance error of the output.
+As the MSE evaluation is a combined evaluation of bias and variance error, it is therefore capable of evaluating 
+	the general requirements of speckle filtering.
 %Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.
@@
 %Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
-From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements of speckle filters can be judged using the familiar bias and variance evaluation.
+From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
+	of speckle filters can be judged using the familiar bias and variance evaluation.
 	%are expected to estimate with no radiometry bias. 
@@
 
-One metric that can be used to detect radiometric distortion is the ratio between the estimated and the original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
+	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
 A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
-In the log-transformed domain, the equivalent index for evaluation would, of course, be a simple substraction.
-In other words, it is evident that the bias evaluation in the log-transformed domain can be used to evaluate the radiometric preservation requirement of speckle filters.
+In the log-transformed domain, the equivalent index for evaluation could be performed by a simple substraction.
+In other words, it is clear that the bias evaluation in the log-transformed domain 
+	can be used to similarily evaluate the radiometric preservation requirement of speckle filters.
 
 Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
-	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias.
+	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
+	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
+	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
 In this paper, we will also show that all of these standard filters 
-	not only preserves the expected radiometric values, 
-	but in the log-transformed domain they also preserve a few subtractive and consistent measures of distance.
+	not only preserves the expected radiometric values in the log-transformed domain,
+	they also preserve a number of subtractive and consistent measures of distance.
 
@@
 Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
-In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the log-transformed domain.
+In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the 
+	log-transformed domain.
 %However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
-Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters which is the primary criteria to evaluate speckle filters over homogeneous area.
+Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
+	which is the primary criteria used to evaluate speckle filters over homogeneous area.
 %Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
@@
 Real-life and practical images, however, are not homogeneous.
-Thus there are a few associated difficulties in evaluating speckle filters over heterogenous scenes.
+Thus there are a number of associated difficulties in evaluating speckle filters over heterogenous scenes.
 %and there are many proposed methods of evaluating speckle filters in such areas. 
@@
 The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
-It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous
-However, without simulation or access to solid ground-truth, it is practically impossible to do so for real-life images (hence, the need for speckle filters estimation).
-
-Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image, mentioned above. 
-Under a multiplicative model, the ratio image is expected to comprise the noise being removed, (i.e. it should be completely random). 
+It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
+However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
+	real-life images (hence, the need for speckle filters estimation).
+
+Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image 
+	mentioned above. 
+Under a multiplicative model, the ratio image is expected to comprise (???? comprise of data with ?)
+	the noise being removed (i.e. it should be completely random). 
 Being random, this should display as little ``visible'' structure as possible. 
 %Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
-However, when displaying such images for visual evaluation, ratios that are smaller than unity are much harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, meaning that a purely visual analysis may be insufficient.
-We therefore propose to adopt a log-transformed domain approach where multiplicative noise then resembles the familiar additive model.
-The ratio image then becomes a simple subtraction image.
-The evaluation methodology for such a proposal does not differ, but now the residual image is additive and linear and thus more natural to display and evaluate visually (see \ref{sec:schema_log_images}).
-
-Another way to evaluate speckle filters is by assessing the feature preservation characteristics of the original noised data and those of the filtered image. 
+However, when displaying such images for visual evaluation, ratios that are smaller than unity are much 
+harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, 
+meaning that a purely visual analysis may be insufficient.
+We therefore propose to adopt a log-transformed domain approach where multiplicative noise 
+would then resemble the familiar additive model, and the ratio image would then become a simple subtraction image.
+The evaluation methodology for such a proposal does not change, 
+	but now the residual image is additive and linear, 
+	and would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).
+
+Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
+of the original noised data and those of the filtered image. 
 When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
 Evaluation would then determine how closely related the two feature maps are. 
-Various methods may be applied to extract features; some that have been used are the Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} or edge map \cite{Frost_PAMI_1982}.
-While significant effort has been spent on these evaluations, serious doubts remain concerning the precision of this methodology.
-This is because feature extraction algorithms are only approximations 
-	whose accuracy is 
-		not only dependent upon the characteristics of the original image 
-		but also heavily reliant on the inherent noise.
+Various methods may be applied to extract features; examples of those that have been used are the 
+	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
+	and edge map \cite{Frost_PAMI_1982}.
+While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
+of these methodologies.
+This is because feature extraction algorithms are only approximations,
+	whose accuracy is not only dependent upon the characteristics of the original image 
+		but also heavily affected by 
+		%reliant on 
+		the inherent noise.
 Unfortunately, speckle filters invariably alter the noise characteristics.
 Thus, without a clear understanding of these dependencies and no absolute ground truth, 
-	using feature extraction algorithms to evaluate speckle filters would leave serious questions on how to interpret the results, especially its accuracy.
+	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
+	how to interpret the results, especially its accuracy.
 %is just too imprecise for us.
@@
 	as well as objectively quantified by measuring the Area Under this Curve (AUC). 
-As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of feature preservation capabilities for different speckle filters.
+As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
+	feature preservation capabilities for different speckle filters.
 
@@
 This is the second difficulty in evaluating speckle filters for heterogenous scenes.
-Under conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, normally at local or regional levels.
-In fact the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) is likely to perform poorly in terms of preserving underlying radiometric differences (such as causing excessive blurring), and vice versa.
+Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
+	normally at local or regional levels.
+In fact, the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) 
+	is likely to perform poorly in terms of preserving underlying radiometric differences 
+	(such as causing excessive blurring), and vice versa. 
 %One can relatively easily satisfy one of these criteria, but not easily satisfy both.
@@
 Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
-Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and is still subjective in nature.
+Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
+	is still subjective in nature.
 
@@
 Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
-However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, the use of MSE is not straightforward. 
-Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation.
+However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, 
+	the use of MSE is not straightforward. 
+Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, 
+	which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
 Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
@@
 	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
-Initial intitution suggests that each components of the MSE measure, 
+Initial intitution (??? intuition?)
+	suggests that each components of the MSE measure, 
 	namely bias and variance evaluation, can be mapped into 
 	the requirements of radiometric preservation and speckle suppression for speckle filters.
-Before the details of our evaluation methodology is discussed and presented, 
+Before the details of our evaluation methodology is presented and discussed, 
 	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
@@
 
-In the first portion of this section,
-    the SAR speckle model in the original domain is shown to be multiplicative and heteroskedastic.
-Next the impacts of heteroskedasticity on speckle filtering is discussed.
-Then logarithmic transformation is shown to convert original speckle data into an homoskedastic model, where the noise is not only additive, but also independent of the underlying radiometric signal.
+In 
+%the first portion of 
+this section, the SAR speckle model in the original domain is first shown to be multiplicative and heteroskedastic.
+The impacts of heteroskedasticity on speckle filtering is then discussed.
+Logarithmic transformation is then shown to convert original speckle data into an homoskedastic model, 
+	where the noise is not only additive, but also independent of the underlying radiometric signal.
 From the consistent and additive noise in log-transformed domain,
-    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and variance ($var(ln(I))$) are described.
+    the consistent measures of dispersion ($ln(I)-ln(avg(I))$), contrast ($ln(I_1)-ln(I_2)$ and 
+	variance ($var(ln(I))$) are described.
 
@@
 
-SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components, each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}.
-This interference can be considered as a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.
-The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.
-
-Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, then the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}.
-Their probability density function (pdf) is given as:
+SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
+	each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, 
+	Leith_ProcIEEE_1971}. This interference can be considered as a random walk on the 2D complex plane 
+	\cite{Goodman_JOptSocAm_76}.  The random nature of the process arises due to the unknown random location, 
+	height, distance and thus random phase of each elementary scaterer and its response.
+
+Assuming the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}, the real part $A_r$ as well as 
+the imaginary part $A_i$ of the observed SAR signal $A$ can then be considered as random variables from 
+uncorrelated Gaussian distributed stochastic processes with zero means and 
+% indentical ??? 
+identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:
 
@@
 
-It then can be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution and consequently intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential distributed random process.
+It can then be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh 
+distribution and consequently the intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of negative exponential 
+distributed random process.
 
@@
 
-It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
+It is then trivial to prove that amplitude and intensity are simply scaled versions of these unit variables, 
+ie. $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
 These relationships evidently manifest a multiplicative nature. 
-In fact, this condition has long been noted, but from different perspectives, in various SAR models including the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.
-
-If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process.
-Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.
+In fact, this condition has long been noted, but from different perspectives, in various SAR models including 
+the multiplicative model \cite{Lee_1981_CGIP} and product model \cite{Jakeman_1980_JPhysAMathGen}.
+
+If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient $\sigma$, 
+then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic 
+process. Consequently, the population expected mean and variance of the four distributions are given in Table \ref{tbl:orginal_sar_avg_var}.
 
@@
 
-From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of the mean.
-In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; estimating variance is equal to estimating the mean and is equivalent to the main problem, ie.
-estimating the unknown parameter $\sigma$.
-
-The formulas above have long been noted.
-In fact while pioneering the estimation of the equivalent number of look (ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both cases (ie.
-$snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$).
-Here, we just offer a different intepretation, which sets the stage for the discussion of logarithmic transformtion.
+From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic 
+phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional 
+expectation of the mean. 
+In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; 
+estimating variance is equal to estimating the mean and is equivalent to the main problem, 
+ie. estimating the unknown parameter $\sigma$.
+
+The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of look 
+(ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both 
+cases (ie. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$). Here, we just offer a different intepretation, 
+which sets the stage for the discussion of logarithmic transformtion.
 
@@
 %That is because: 
-Even though the statistical model within individual resolution cells is well established, the applicability of its models is restricted to homogenous areas. 
-Practical images, however, are heterogenous.
-Crucially it is this spatial variation that is of high interest.
-This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and subsequently what to do in the case of heterogeneity.
-
-Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
-Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial varition also gives rise to the heteroskedasticity phenomena.
-Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying back-scattering coefficient $(\sigma)$.
-It is believed that this heteroskedasticity give rise to serious negative impacts at various stages of speckle-filtering.
+Even though the statistical model within individual resolution cells is well established, the applicability of its 
+models is restricted to homogenous areas. 
+Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. 
+This fact gives rise to a question that seemed obvious: how to label an analysis area as being heterogenous and 
+subsequently, what to do in the case of heterogeneity.
+
+Various statistical models for heterogenous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed 
+review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous 
+original SAR data, in extending the models to heterogenous images, virtually none have noted that spatial variation 
+also gives rise to the heteroskedasticity phenomena. 
+Heteroskedasticity, as explained in the previous section, is defined as the dependence of conditional expected 
+variance of original SAR data on the conditional expectation of its mean, or equivalently its underlying 
+back-scattering coefficient $(\sigma)$.
+It is believed that this heteroskedasticity gives rise to serious negative impacts at various stages of 
+speckle-filtering.
 
@@
 In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
-This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent to estimating $\sigma$).
+This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
+to estimating $\sigma$).
 %The fact give rise to the vicious circle in SAR speckle filtering.
@@
 Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
-Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, together with the normal Mean Squared Error evaluation criteria in serious doubt. 
-If the variance is known \textit{a priori}, it has been proven, that a weighted mean estimator is the best linear unbiased estimator. 
-Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators.
-The caveat however is that in SAR speckle filtering, variance is not known a priori. 
-And eventhough variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.
+Thus it renders the efficiency of any naive Ordinary Least Square estimator \cite{Furno_1991_JStatCompSimul}, 
+together with the normal Mean Squared Error evaluation criteria in serious doubt. 
+If the variance is known \textit{a priori}, it has been proven that a weighted mean estimator is the 
+best linear unbiased estimator. 
+Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive 
+filters \cite{Lee_PAMI_1980} \cite{Kuan_1985_PAMI} \cite{Frost_PAMI_1982} does make use of weighted mean estimators. 
+However, the caveat is that in SAR speckle filtering, variance is not known \textit{a priori}. 
+And even though variance can be estimated from observable values, as the vicious circle goes, 
+estimating the variance is as good as estimating the underlying coefficient $\sigma$ itself.
 
@@
 The technique determines outlying points as being too far away from the standard deviation. 
-However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required and used. 
-It is interesting to note that the MMSE estimator used to estimate the mean in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.
-
-Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. 
-Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. 
+However, as is done in \cite{Lee_TGRS_2009}, to estimate standard deviation, an estimator of mean is required 
+and used. It is interesting to note that the MMSE estimator used to estimate the mean 
+in \cite{Lee_TGRS_2009}, itself alone, is a rather successful speckle-filter\cite{Lee_PAMI_1980}.
+
+Last, but certainly not least is the bad impact of heteroskedastic on SAR image interpretation. 
+Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, 
+target segmentation and/or target classification. 
 Each of these tasks require good similarity or discriminant functions. 
 Foundational to these is the need of a consistent measures of distance. 
-Unfortunately, by definition heteroskedasticity leads to inconsistent measures of distance. 
-This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods are
- believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods for SAR classification to underperform.
+Unfortunately, by definition, heteroskedasticity leads to inconsistent measures of distance. 
+This inconsistent measure of distance, coupled with the failure of the ordinary least square regression methods, are
+ believed to cause a large class of artificial neural networks as well as a number of other computational 
+ intelligence methods for SAR classification to underperform.
 
@@
 In this paper, we propose using a base-2 logarithmic transformtion of orignal SAR data. 
-Base-2 is chosen for implementation reasons since it can be computed faster than either natural or decimal logarithms, and yet maintains an ability to transform heterskedactic speckle into a homoskedastic relationship.
-Thus the original variables become:
+Base-2 is chosen for implementation reasons since it can be computed faster than either natural or 
+decimal logarithms, and yet maintains the ability to transform heterskedactic speckle into a 
+homoskedastic relationship. Thus the original variables become:
 
@@
 
-Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variables as follows:
+Bearing the relationship among the random variables in mind, it is then trivial to 
+show that the probability distribution of these log-transformed variables are related as follows:
 
@@
 
-Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant.
+Noting that these distributions belong to the Fisher-Tippet family, the population expected mean and variances 
+are obtained as in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma$ being the Euler-Mascheroni constant. 
 Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$
@@
 The equations above also highlight the relationships among random variables in the log-transformed domain. 
-Two conclusions become evident from these formula. 
+Two conclusions become evident from these formulae. 
 Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
-Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation is clearly manifested. 
-Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  defined as the independence of the conditional expected variance on the conditional expectation of the mean.
-
-This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. The main difference would be the use of base-2 logarithm which is prefered here for faster computation.
+Secondly, the effects of converting the multiplicative nature to an additive nature through logarithmic transformation
+is clearly manifested. 
+Table \ref{tbl:sar_log_domain_avg_var} confirms the condition of homoskedasticity,  
+defined as the independence of the conditional expected variance on the conditional expectation of the mean.
+
+This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
+The main difference would be the use of base-2 logarithm which is preferred here for more efficient computation.
 
 Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
-It can be seen that while the original data, especially intensity values, should be preferred for multi-look processing, the log-transformed domain with its homoskedastic distribution, offers consistent measures of dispersion and contrast.
-Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, additive, least squared error regression signal processing (including wavelets) and computational (including artificial neural network) techniques into SAR data.
+It can be seen that while the original data, especially intensity values, should be preferred for 
+multi-look processing, the log-transformed domain with its homoskedastic distribution offers consistent measures of 
+dispersion and contrast. 
+Thus log transformation is shown here to be a homomorphic transformation, allowing one to apply traditional linear, 
+additive, least squared error regression signal processing (including wavelets) and computational 
+(including artificial neural network) techniques on SAR data.
 
@@
 
-In order to explore this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
+To verify this experimentally, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a 
+known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
 The excellent agreement is self-evident in the graph which confirmed the log-transformed model. 
-In fact, this modelling has been used successful in explaining speckle phenomena, also verified through scientific experiments \cite{Ulaby_TGRS_1988}.
+In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
+through scientific experiments \cite{Ulaby_TGRS_1988}.
 
@@
 
-The consistent sense is explored and illustrated in this section from two different perspectives. 
-First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}.
-Consider the random variable deviation defined as the distance between an observable sample and its expected value:
+The consistent sense (??? feature?) is explored and illustrated in this section from two different perspectives. 
+First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random 
+variable deviation defined as the distance between an observable sample and its expected value:
 
@@
 
-Noting the results from the previous section, the pdf for these variable can be trivially given as
+Noting the results from the previous section, the pdf for these variable can be derived and shown to be as follows:
 
@@
 
-It is evident from the equations that these distributions are dependent on $\sigma$ in the original SAR data but are independent of it in the log-transformed domain.
-
-From a second perspective, given two adjacent resolution cells that are known to have the identical but unknown back-scattering coefficient $\sigma$, consider a random variable defined as the contrast between two measured samples, in the log-transformed domain:
+From these equations, it is clear that these distributions, which are dependent on $\sigma$ in the original SAR data, 
+are now independent of it when presented in the log-transformed domain.
+
+From a second perspective, given two adjacent resolution cells that are known to have identical but 
+unknown back-scattering coefficient $\sigma$, consider, in the log-transformed domain, a random variable defined as the contrast between two 
+measured samples:
 
@@
 
-Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is consistent in the log-domain but inconsistent in the original domain.
-The pdf of these variables can be given as:
+Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is consistent in the 
+log-domain but inconsistent in the original domain. The pdf of these variables can be expressed as:
 
@@
 
-Figure \ref{fig:residual_as_noise} illustrates this, showing excellent agreement between the analytical pdf and observable histogram of deviation and contrast of the same area in a log-transformed intensity RADARSAT-2 image.
-Distance is calculated as the difference between each value point and the average value of that region, while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.
+To illustrate this characteristic, Figure \ref{fig:residual_as_noise} is generated by using data from the RADARSAT-2 
+image. As can be seen, it shows excellent agreement between the analytical pdf and observable histogram of deviation
+(??? 'deviation', or 'dispersion' as indicated in the figure?) 
+and contrast of the same area in a log-transformed intensity RADARSAT-2 image. 
+Distance is calculated as the difference between each value point and the average value of that region, 
+while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.
 
@@
 %\end{tabular}
-\caption{Observed and modelled pdf of deviation and contrast in homogenous log-transformed intensity images.}
+\caption{Observed and modelled pdf of deviation
+and contrast in homogenous log-transformed intensity images.}
 \label{fig:residual_as_noise}
@@
 
-Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the measure of observable deviation in original SAR data differs, ie.
-is inconsistent, across different homogenous areas.
-The observable deviation in the log-transformed domain however is consistently the same across different homogenous areas. 
-One possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.
+Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that 
+the measure of observable deviation in original SAR data differs, i.e. is inconsistent, across different homogenous 
+areas. On the other hand, the observable deviation in the log-transformed domain is consistently the same across 
+different homogenous areas. As such, one possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be 
+designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.
 
@@
 
-From the previous section result, two sample variance distribution ($V_x = C_x^2$) can be given analytically as
+From the results of previous section, two sample variance distribution ($V_x = C_x^2$) can be given analytically as 
+follows:
 
@@
 
-It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance constant but the sampling distribution of this random variable is independent of $\sigma$.
-We have seen this analytically for two sample variances. 
-For a larger number of samples, Monte-Carlo simulation can be used to visualise the PDF of sample variances.
-
-In summary, a few measures of distance are shown to be consistent, which agree with the consistent sense of variance / deviation and homoskedasticity.
-The measure of disimilarity can be used to test if a pixel belong to a ``known'' scatterrer, an example of its use this way is illustrated in our kMLE speckle filter.
-The consistent sense of contrast can be used to test if any pair of measured data points belong to the same class of scatterer. It may also 
-explain why, in the original SAR domain, the ratio based detector / classifier is prefered to differential measures, which are not consistent. 
-An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
-The consistent sense of contrast also gives rise to a consistent measure of variance, which can be used to test if a group of pixels can form a homogenous area.
-This is applied in a clustering algorithm described in \cite{Le_2010_ACRS}.
+It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance 
+constant, the sampling distribution of this random variable is also independent of $\sigma$. 
+While we have observed this analytically for variances based on two samples, for a larger number of samples, 
+Monte-Carlo simulation can be used to visualise the PDF of samples' variances.
+
+In summary, measurements of distance for a number of cases are shown to agree with the 
+consistent sense of variance / deviation and homoskedasticity. The measure of disimilarity can be used to test 
+if a pixel belongs to a ``known'' scatterrer, an example of its use in this way is illustrated in our kMLE speckle 
+filter. The consistent sense of contrast can be used to test if any pair of measured data points belong to 
+the same class of scatterer. It may also explain why, in the original SAR domain, the ratio based 
+detector / classifier is preferred to differential measures, which are not consistent. 
+An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}. The consistent sense 
+of contrast also gives rise to a consistent measure of variance, which for example, can be used to test 
+if a group of pixels can form a homogenous area, as applied in a clustering 
+algorithm described in \cite{Le_2010_ACRS}.
 
@@
 
-Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and SAR speckle filtering process.
-The ``SAR processor'' block indicates that either of the following processes is occurring.
-First is the normal arrangement of transformation whieh offers several consistent measures of distance, 
-	which are hypothised to be significant  in evaluating speckle filters.
-	A case in point is in visual evaluation of filtered results on real captured SAR images.
+Fig. \ref{fig:simul_process_filter_schema} illustrates the general schema of SAR simulation / processing and 
+SAR speckle filtering process.
+The ``SAR processor'' block indicates that either one of the following processes can occur.
+First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded 
+in $\tilde{X}$. Second is the simulation process where the noisy SAR data $\tilde{X}$ is simulated from a known 
+ground-truth pattern $X$.
+%In this paper, fully developed speckle assumption is employed, which allow for easier simulation process.	
+%Eventhough different levels of noise can be simulated, in the experiments presented here, only single-look are simulated, and the similar boxcar filter is studied.
+
+The ``SAR Speckle Filter'' block indicates the speckle filtering process, 
+	which takes the noisy speckled SAR data $\tilde{X}$ as input
+	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
+The speckle filters used in this paper are: 
+	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter 
+	and PDE filter \cite{You_TIP_2000}.
+Evidently in the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
+%Thus $MSE_{residual}^{none} = MSE_{base}$
+
+Logarithmic transformation offers several consistent measures of distance, which is hypothised to be 
+significant in evaluating speckle filters.
+	A case in point is in visual evaluation of filtered results obtained from real captured SAR images.
 Since the radiometric ground-truth is not available, %the most common 
 %In real SAR captured images, the radiometric ground-truth normally is not available.
-	the most common way to evaluate speckle filters is by qualitative visual evaluation. A traditional method is to investigate the ratio images between the filtered output and the noisy input data.
-Since logarithmic transformation converts the ratio image into a substractive residual, which is consistent, then residual analysis can be used to analyse and evaluate the performance of speckle filters.
-To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, Fig.
-\ref{fig:real_image_ratio_vs_residual} shows the residual image in the log-transformed domain and the ratio images in the original domain, where a simple boxcar filter has been applied to a real RADARSAT SAR image.
-``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in the ratio images, although this conclusion is of course iself a subjective one.
+	the most common way to evaluate speckle filters then is by qualitative visual evaluation.
+A conventional method is to investigate the ratio images between the filtered output and the noisy input images.
+Since logarithmic transformation convert these ratio into substractive residual which are consistent, residual 
+analysis can be used to analyse and evaluate the performance of speckle filters.
+%To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, 
+For comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
+and the ratio images in the original domain, where a simple boxcar filter has been applied to data obtained from a 
+real RADARSAT SAR image.
+``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in 
+the ratio images, although this conclusion is of course itself a subjective one.
 
@@
 MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
-MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
+MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
 MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
@@
 As qualititative visual evaluation is subjective by nature,
-	quantitative metrics and measurements are preferred, when relevant.
-Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
+	quantitative metrics and measurements are preferred, if relevant and possible.
+Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, 
+are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
 When ground-truth is available, 
-	either in simulated experiments or over homogeneous area where it can be reasonably estimated, true MSE is the expected squared error between the estimated and true values.
-
-In real captured SAR images however, such ground truth is unknown, then evaluation can be carried out through a benchmarked MSE. 
-The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
-Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be estimated reasonably well.
-Thus the base MSE level which is also a measure of the speckle noise level, can also be estimated.
+	either in simulated experiments or over homogeneous area where it can be reasonably estimated, 
+	true MSE is the expected squared error between the estimated and true values.
+
+However, in real captured SAR images where such ground truth is unknown, the evaluation can then be carried out 
+through a benchmarked MSE. 
+The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ 
+can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
+Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be 
+estimated reasonably well.
+Thus the base MSE level, which is also a measure of the speckle noise level, can also be estimated.
 Naturally, the speckle filter should remove as much noise as possible, 
-	while it also should not remove more variations than are caused by the speckle noise.
+	while it also should not remove more variations than that caused by the speckle noise.
 %Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base
@@
 
-In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is illustrated.
-Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
+In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is 
+illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
 Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
-Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is probably insignificant in comparison to the other components, namely, variance evaluation. 
-Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance methods of evaluation are shown to be mathematically related to the ENL index.
-The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle over homogeneous areas.
+Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is 
+probably insignificant in comparison to the other components, namely, variance evaluation. 
+Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance 
+methods of evaluation are shown to be mathematically related to the ENL index.
+The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
+over homogeneous areas.
 
@@
 
-In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL index. 
-Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
+In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL 
+index. Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
 Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
-	then the MSE evaluation reduces to variance evaluation.
-That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in the log-transformed domain.
+	then the MSE evaluation is reducced to variance evaluation.
+That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered 
+output in the log-transformed domain.
 
@@
 %Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
-Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variables as: 
+Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
+variables as: 
 \begin{equation}
@@
 \end{equation}
-Thus the ENL, L, can be estimated as:
+Thus the ENL, i.e. $L$, can be estimated as:
 \begin{equation}
@@
 
-The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and corrupted with single look SAR-speckle PDF. 
+The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and 
+corrupted with single look SAR-speckle PDF. 
 Different multi-look processing filters are then applied to the image patch. 
 The observable variance in the log-transformed domain is recorded, and 
-	 ENL estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
-The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms of mean and standard deviation.
+	 ENL is then estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
+The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms 
+of mean and standard deviation.
 The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
@@
 They also shows that 
-	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect 
-	(since ENL is supposed to be an integer), the value obtained actually corresponds very closely with the nearest correct integer result.
+	while the approximation in Eqn. \ref{eqn:enl_analytic} may not be perfect, 
+	since ENL is supposed to be an integer, the value obtained actually corresponds very closely with the 
+	nearest correct integer result.
 
@@
 
-The finding here is not inconsistent with other authors.
+The finding here may also help to explain other seemingly unrelated results. For example, 
 	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
-	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ to evaluate scene heterogeneity.
+	while Lopes \cite{Lopes_TGRS_1990} proposed the use of variation co-efficient index $C_v = std(I)/avg(I)$ 
+	to evaluate scene heterogeneity.
 
@@
 Both single-look simulated and multi-look processed/box-car filtered data is displayed.
-Specifically the plots show that the log-transformed domain is consistent while the plots from the original domain are not.
+Specifically the plots show that the log-transformed domain is consistent while the plots from the original 
+domain are not.
 
@@
 
-Fig.
-\ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) preserve this consistency in their filtered output.
-Intuitively, the boxcar filter is actually similar to multi-look processing, thus it also preserve the consistency property.
-This consistency will also lead to the consistent sense of distance described earlier, and is significant because it is the tell-tale indicator of the consistent contrast and variance.
-This ensures applicability of various target detection/classification algorithms which employ statistical properties in the un-filtered data, for example the ratio based discriminator in the original domain or the differential based discriminator in the log-transformed domain.
+Fig. \ref{fig:log_consistency_filters} shows that all of the standard filters (Lee, Kuan, Frost and Gamma MAP) 
+preserve this consistency in their filtered output. Intuitively, as the boxcar filter is actually similar to 
+multi-look processing, it hence also exhibits the consistency property.
+This consistency will also lead to the consistent sense of distance described earlier, which is significant 
+because it is the tell-tale indicator of the consistent contrast and variance.
+This ensures applicability of various target detection/classification algorithms 
+which employ statistical properties in the un-filtered data, such as the ratio based discriminator 
+in the original domain or the differential based discriminator in the log-transformed domain.
 
@@
 
-%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
-The general requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservation and speckle suppression.
-In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of statistical estimators.
+%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
+log-transformed domain. 
+The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
+down into the requirements of radiometric preservation and speckle suppression.
+In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
+statistical estimators.
 Overall, while the MSE index combines the measurements of bias and variance evaluation, 
-	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC Curve (AUC).
+	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
+	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
 We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.
 
-Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern multiple times, the histograms of the target and background areas can be reliably obtained.
+Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
+multiple times, the histograms of the target and background areas can be reliably obtained.
 %They are expected to be consistent in log-transformed domain.
@@
 
-The types of pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous checker board scene. 
-These test patterns could, of course, be concatenated into a larger composite test image, although we will consider them as separate images to allow easier analysis of the results.
+The types of test pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous 
+checker board scene. 
+These test patterns could of course be concatenated into a larger composite test image, 
+although we will consider them as separate images to allow easier analysis of the results.
 %However we would prefer to highlight the results separately for each individual area.
-Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention in the radar community where the target is signified by the brighter area of the image. 
+Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention used in the 
+radar community where the target is signified by the brighter area of the image. 
 Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.
@@
 
-Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle, and then the filters applied onto these noised images.
-From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be evaluated by examining the separability of the two background and target populations.
-The separability of the two histograms is visualized by plotting the ROC in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
-	while subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} plot the AUC.
+Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle. The 
+filters are then applied onto these noised images.
+From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
+evaluated by examining the separability of the two background and target populations.
+Subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+	allows visual evaluation of target and clutter histograms and their separability.
+Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
+in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
+respectively, and is measured by computing the Area Under these Curves (AUC).
+
+%visualizes the two histograms
+%The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
+%	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
+%	and is measured by computing the Area Under these Curves (AUC).
 
@@
 	}  \\
-	\subfloat[ROC: Unfiltered]{
+	\subfloat[ROC: Unfiltered, AUC=0.738]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[ROC: Kuan Filtered]{
+	\subfloat[ROC: Kuan Filtered, AUC=0.885]{
 		 \epsfxsize=1.5in
@@
 Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
-	can help to explain how the MSE is related to the histograms' capability to seperate.
-In pre-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
-Then the seperability of clutter and target populations depends only on the variance of the additive noise. This variance is visualized as the horizontal spread of the histograms.
-Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) the better the separation capability.
-
-In post-filtered images, subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and \ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
-Here, besides the effect of the histogram spread, one also needs to take into account bias error.
-Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicate that the output of the Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), also introduce bias errors.
-Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are always over-estimated.
-This is probably due to the entropy reduction effect of the speckle filters.
+	can help to explain how the MSE is related to the histograms' separation capability.
+In pre-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
+\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
+Then the seperability of clutter and target populations depends only on the variance of the additive noise. 
+This variance is visualized as the horizontal spread of the histograms.
+Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance), 
+the better the separation capability.
+
+In post-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
+\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
+Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
+Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
+Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
+also introduce bias errors.
+Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
+always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
 Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.
@@
 %Also the speckle suppression is related to the measured variance.
-Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to evaluate the separability of the two histograms. 
-Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and patterns.
+Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
+evaluate the separability of the two histograms. 
+Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and 
+patterns.
 It shows that the MSE is inversely correlated to this separability index.
 The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
-The results suggest that the lower MSE achivable by the filters would lead to better feature preservation in general.
+The results suggest that the lower MSE achievable by the filters would, in general, lead to better feature preservation.
 
@@
 
-In this section, our conjecture of using MSE in the log-transformed domain to find the most suitable speckle filter for practical real-captured SAR images is described.
-In these scenarios, the ground-truth and hence the true MSE is not available.
-Therefore only the residential MSE is computable.
-Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark MSE is also measurable.	
+In this section, our conjecture (??? you want to emphasize this is a proposal that can't be proven mathematically ?) 
+of using MSE in the log-transformed domain to find the most suitable speckle filter 
+for practical real-captured SAR images is described.
+In these scenarios, the ground-truth, and hence the true MSE, is not available.
+Therefore, only the residential MSE is computable.
+Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark 
+MSE is also measurable.	
 Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
-This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters for a captured SAR image, 
-	where the ground-truth and hence true MSE is not available.
-Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its removed variation being closest to the inherent speckle noise.
+This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters 
+for a captured SAR image, where the ground-truth and hence true MSE is not available.
+Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its 
+removed variation being closest to the inherent speckle noise.
 
@@
 
-The results from the experiments in previous sections can also be used to validate the use of residual and benchmark MSE.
-The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly correlated with feature classification capability, measured by the standard AUC index.
-
-The filters are also applied onto a real RADARSAT--2 image.
+The results from the experiments in previous sections can also be used to validate the use of residual and 
+benchmark MSE.
+The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly 
+correlated with feature classification capability, measured by the standard AUC index.
+
+The conjecture is also validated in real SAR images.
+Different speckle filters are applied onto a real RADARSAT-2 image.
 In this case, since the ground-truth is not available, 
@@
 Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
-Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE would probably suggest a more suitable filter.
+Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE 
+would probably suggest a more suitable filter.
 Fig. \ref{fig:real_image_results} tends to confirm this visually.
@@
 Although it is widely known that log transformation transforms multiplicative SAR speckle into additive noise, 
-	one should note that the noise is not Gaussian.
-In fact, figures presented in the previous sections show that 
+	one should note that the noise is not Gaussian. In fact, figures presented in the previous sections show that 
 	they are not even centered around the origin. 
-This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not work very well in practice.
-To counter this, the use of maximum likelihood estimation instead of simple averaging is suggested \cite{Le_2011_ACRS}. 
-Interestingly, averaging is also the MLE operator in the SAR's original domain.
+This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
+	work very well in practice. To counter this, the use of maximum likelihood estimation instead of simple averaging 
+	is suggested \cite{Le_2011_ACRS}. Interestingly, averaging is also the MLE operator in the SAR's original domain.
 
@@
 	but can also be found in filtered data of various ``standard'' speckle filters.
-This is significant probably because it ensures the applicability of various target detection/classification algorithms, 
-	which exploit these consistent statistical properties, 
+This is significant probably because it ensures the applicability of various target detection/classification 
+	algorithms, which exploit these consistent statistical properties, 
 	into not only pre-filtered data but also post-filtered data as well.
@@
 
-This consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
-For example, in the subsequent tasks of designing target detectors or classifiers, 
+This consistent measures of distance in the log-transformed domain could probably have implications beyond speckle 
+filtering. For example, in the subsequent tasks of designing target detectors or classifiers, 
 	it is normally desirable to engineer the solution to not only work on single-look or multi-look SAR data,
 	but also be applicable on post-filtered data.
-In such cases, these consistent measures of distance in the log-transformed domain could provide a sound theoretical basis.
-In fact, a number of already proposed solutions appear to make use of this feature. 
+In such cases, these consistent measures of distance in the log-transformed domain could provide a sound theoretical
+	basis. In fact, a number of already proposed solutions appear to make use of this feature. 
 %(cite here some SAR classification papers)
-An example is the ratio based discriminator in the original domain.
-Looking backwards, in designing new speckle filters, by ensuring that the filtered output preserves this consistent property,
+An example is the ratio based discriminator in the original domain. Looking backwards, in designing new speckle 
+	filters, by ensuring that the filtered output preserves this consistent property,
 	the new speckle filters would be eligible to be used as pre-processing steps for availble classifiers / detector.
 
-Of course, there are other speckle filters that do not preserve such consistency (e.g. the pde filter \cite{You_TIP_2000}).
-One could argue that it would not be fair to the judge such filters using the MSE criteria, 
-	which tend to favour the ``standard'' filters.
-While we respect any other criteria that are used, we reiterate the two points that firstly
-our MSE criteria is closely related to the basic ENL criteria.
-The experimental results indicated that the ENL measures for such filter (i.e. the pde filter) differ depending on the radiometric values.
+Of course, there are other speckle filters that do not preserve such consistency 
+	(e.g. the pde filter \cite{You_TIP_2000}). One could argue that it would not be fair to the judge such filters 
+	using the MSE criteria, which tend to favour the ``standard'' filters.
+While we respect any other criteria that are used, we reiterate the two salient points of our approach. 
+Firstly, our MSE criteria is closely related to the basic ENL criteria.
+The experimental results indicated that the ENL measures for such filter (i.e. the pde filter) differ depending  
+on the radiometric values. 
 Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
@@
 The reasons for maintaining a small window is that 
-	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk among adjacent targets.
-Secondly, we focussed on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
+	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk 
+	among adjacent targets.
+In addition, we focussed on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
 	and do not wish to advocate a particular ``best'' filter in practice. 
@@
 	and did not directly address the design of speckle filters.
-However, interested filter designers are invited to download the Matlab evaluation code used in this paper to evaluate their own designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
-
-In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators (i.e. speckle filters).
+However, interested filter designers are invited to download the Matlab evaluation code used in this paper 
+to evaluate their own designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
+
+In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators 
+(i.e. speckle filters).
 %The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
-The use of small and simple patterns allowing detailed analysis can then be done repeatedly and reliably against the stochastic nature of SAR data.% on simulated small data sets without the need of a common real large image that is somehow representative.
-This helps in the mapping of qualitative requirements for the speckle removal process into specific and quantitative requirements in the design of speckle filters.
+The use of small and simple patterns allowing detailed analysis can then be done repeatedly and reliably against the 
+stochastic nature of SAR data.
+% on simulated small data sets without the need of a common real large image that is somehow representative. 
+This helps in the mapping of qualitative requirements for the speckle removal process into specific and quantitative 
+requirements in the design of speckle filters.
 Its use also provides an absolute ground-truth, i.e. a solid base for comparison of results across different papers.
 
-The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.%, there is no ground-truth.
+The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.
+%, there is no ground-truth.
 Thus the result extension towards real images is only analogical.
@@
 	different heterogenous patterns exhibits different levels of heterogeneity. 
-Even though different measures have been proposed to evaluate scene heterogeneity levels or to test for the homogeneity hypothesis, 
+Even though different measures have been proposed to evaluate scene heterogeneity levels or to test for the 
+homogeneity hypothesis, 
 	for real captured images, where the absolute ground-truth is not available, 
-	there does not appears to exist any certain way to assert a given image as being perfectly homogenous or absolutely heterogenous.
+	there does not appears to exist any certain way to assert a given image as being perfectly homogenous or 
+	absolutely heterogenous.
 Thus while the distinction helps in clarifying the concepts, 
@@
 %Similarly for 
-The patterns used are chosen based on our exerience and of course may affects evaluation results. 
+The patterns used are chosen based on our exerience, which may affects evaluation results. 
 As different patterns result in different degrees in the scale of scene homogeneity / heterogeneity, 
-	and they also appear to affect the performance and ranking of each speckle filters.
-One extreme case is that of perfect homogeneity, where boxcar filters would be the best performer,
-	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that the boxcar would not perform well.
+	they also appear to affect the performance and ranking of each speckle filters.
+One extreme example is that of perfect homogeneity, where boxcar filters would be the best performer,
+	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that the boxcar 
+	would not perform well.
 %Our work suggest that the performance of speckle filters is probably scene dependent, 
@@
 
-The current scheme of finding the most suitable speckle filter requires the application of all filters before a decision is made, something that may be computationally expensive.
+The current scheme of finding the most suitable speckle filter requires the application of all filters before 
+a decision is made, something that may be computationally expensive.
 A possible better alternative would be to predict the choice, escaping such massive requirements of processing.
@@
 To summarize, speckle filters are generally evaluated using many different qualitative criteria.
-To compare the filters against each other, a method is needed to quantify and measure these various qualitative requirements and results.
-Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
-With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.
+To compare the filters against each other, a method is needed to quantify and measure these various qualitative 
+requirements and results.
+Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the 
+original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
+With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the 
+log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.
 
 Our contribution is mainly centered around a few points. 
-Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, and illustrate it's efficacy for test images.
-Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
-Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find the most suitable speckle filter for any given scene. 
-In short, we propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation scenarios, and suggest several test images that may be useful in this regard.
+Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, 
+and illustrate it's efficacy for test images.
+Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that 
+the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
+Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
+the most suitable speckle filter for any given scene. 
+In summary, we propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation 
+scenarios, and suggest several test images that may be useful in this regard.
 

### 2013-03-01 paper_dev/detex.article.tex
201303_Mar01

[journal]IEEEtran

cite

amsmath
amsfonts

epsfig

[caption=false,font=footnotesize]subfig

	Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters.

Thanh-Hai Le,
        Ian McLoughlin, Senior Member, IEEE, 
	Brian Quang-Huy Nguyen

Thanh-Hai Le, Brian Quang-Huy Nguyen and Ian McLoughlin are with School of Computer Engineering, 
Nanyang Technological University, Singapore,

Manuscript received ?, 2012; revised ?.

Transactions on Geoscience  Remote Sensing, Vol. ?, No. ?, April 2012
 Le et al.: SLC SAR speckle filtering using Homoskedastic effects of Logarithmic Transfomation

We start off by noting the ability of Logarithmic Transformation to convert heteroskedastic SAR data into homoskedastic values. 
Under this transformed domain, the universal Gauss-Markov theorem becomes applicable suggesting that the familiar mean squared error (MSE) could become an invaluable evaluation criteria for statistical estimators (i.e. speckle filters). 
In this paper, we show, through experiments and analysis, that the MSE in log-transformed domain can serves as a reliable performance indicator to evaluate performance of SAR speckle filters.
Specifically, we give an equation that, in homogeneous area, links variance (and hence MSE) with the canonical Equivalent Number of Look index.
In heterogenous area, we note that the usual ratio-based radiometric preservation criteria is related to the standard estimator bias evaluation in log-transformed domain. 
Combine this with the fact that variance is an effective measure of speckle suppression power, it is apparent that MSE can serve as a good performance criteria to evaluate feature preservation property of SAR speckle filters.
Through experimental analysis and results, we show that lower MSE suggests better feature detection and classication in filtered images, 
	which is an important requirement property for speckle filters.

Synthetic aperture radar, speckle-filtering, homoskedasticity, mean-squared-error

Introduction

The nature of SAR speckle is stochastics over homogenous areas and heteroskedastic heterogenously. 
Statistical models are used to derive the underlying back-scattering coefficient () from the measured SAR data. 
Speckle filtering, by and large, are estimators attempting to estimate the unknown coefficient from observable SAR data.

SAR speckle-filtering can be and has been positioned within the context of estimation theory. 
The stages in this statistical framework consist of statistical modelling, estimator development and evaluating of the performance of estimators. 
Estimators are normally evaluated based on the bias and variance properties of their estimates. 
The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
Due to the stochastic nature of the simulation process, statistical summaries of repeated simulating experiments are normally preferred to a single-run result.

Our survey in the field of SAR speckle filter, however, indicates a different picture from standard practice of this framework, specifically in the stage of performance evaluation.
Due to the multiplicative nature of noise, bias and variance evaluation normally come with a twist.
Also the heteroskedastic nature of the data makes the universally standard mean-squared-error become inapplicable without some adaptation.
In fact, our survey indicates the lack of a single quantitative metric to evaluate speckle filters.

Each newly proposed filter has its own way to evaluate own results.
Some papers merely present visual qualititave comparisions on only a single or a few scenes, a methodology believed to be overly subjective.
Other papers also presents quantitative measurements. 
Unfortunately, the evaluation metrics used vary significantly from one paper to the next.

There has been a few published articles dedicated to the topic of evaluating speckle filters.
In these papers, the evaluation metrics and simulation procedures received much more thorough treatments.
However, a number of different metrics to catter for the different scenarios of imaging scenery were proposed.

In this paper, we note that log-transformation convert multiplicative and heteroskedastic SAR data into a more familiar additive and homoskedastic domain.
Thus we propose the use of MSE in the log-transformed domain as the single unifying evaluation criteria across different scenarios.

Related Work in Literature

It is customary to devide the evaluation of speckle filters in two scenarios: homogeneous area and heterogeneous scenes.
In homogeneous area where the underlying radiometry is assumed to be unchanged, the filters are expected to estimate with no radiometry bias, and the best filters achieve maximum speckle suppression power of the lot.

To evaluate estimation bias, the normal metric used is Radiometry Loss index . 
In the log-transformed domain, the equivalent index would be a simple substraction.
Shi (1994) found that all of the standard filters (boxcar, Lee, Kuan, Frost, MAP) can achieve negligible bias.
In this paper, we observes that all of these standard filters not only can preserves the expected radiometric value, 
  they also preserve the consistent sense of distance, which we will describe later, in the log-transformed domain.

There are a few metric that have been used to evaluate speckle suppression power.
The most common one is probably the Equivalent Number of Look index  proposed by Lee (cite).
Another metric is the mean to standard deviation ratio  (cite Gagnon)

Since log-transformation convert multiplcative and heteroskedastic SAR data into additive and homoskedastic model, we suggest that the variance in log-transformed domain can be used to evaluate noise suppression power of speckle filters.
In fact, Solbo used standard deviation in log-transformed domain to measure homogeneity.
We show that, in homogeneous area, ENL is equationally related to this variance.

Real-life and practical images however are not homogeneous, 
  and there are even more ways proposed to evaluate speckle filters.

Under the condition of heterogeneity, even the standard speckle filters will introduce radiometric loss, normally at local or regional level.

In fact, it is common consensus that a powerful speckle suppresion filter (says boxcar filter) is likely to perform poorly in terms of preservating underlying radiometry differences (e.g. they cause excessive blurring).
The vice versa is also commonly considered as true.

The first difficulty in evaluating speckle filters for heterogeneous scene is to find the base for comparisions.
It is trivially easy to estimate the underlying radiometric co-efficient if the area is known to be homogeneous, it is however impossible to do so without simulations and ground-truth experiments (e.g. experiments on real-life images).

Without the ground truth, one way to evaluate radiometric preservation of the filters is to compute the ratio image, which is the ratio between the orignal speckled image and the filtered image. (cite)
Under multiplicative model, the ratio images is expected to be the noise being removed, (i.e. random).
Since they are random, when displayed, the ratio images is evaluated to have as little of "visible" structure as possible.
Also its histogram / PDF are expected to match as closely as possible with the noise characteristics in the original image.
The difficulty, however is when displaying the images: the ratios that are smaller than 1 are much harder to distinguish than the ratios that are bigger than 1. (cite Merdios)

We suggest to view the procedure under the log-transformed domain. 
The multiplicative model then become the familiar additive noise.
The ratio images then become a simple substraction image. 
The evaluation methodology is the same, but now the residual image is additive and linear which is more natural to display.

Another way to evaluate speckle filter is by checking the feature preservation characteristics of the original noised data and the filtered image.
When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
Evaluation is then to see how closely related the two feature maps are.
Various methods are used to extract features, some that have been used are Hough Transform (Merdios), Sobel edge detector (cite) or edge map (Frost).
While a lot of effort has been spent in these works, we believe the methodology is overly imprecise.
This is because feature extraction algorithms are only approximations whose accuracy is dependence on noise.
Thus without a clear understanding of this dependency, using feature extraction algorithms to evaluate speckle filters, which invariably suppress the same noise, 
	leave serious questions on how to interprete those quantitative measurement results.

Since SAR statistical model are quite well understood, we strongly suggest simulation experiments with known ground-truth instead.
We also propose to use simple feature extraction algorithm (i.e. simple threshold based classifier), where the dependency between its performance and noise is well known (the Receiver Characteristics Curve (ROC) and the Area Under it (AUC)), to evaluate feature preservation capabilities of different speckle filters.

There are two main ways that ground truths are used in evaluating speckle filters. 
A simple way is to embed speckle noise into one of the optical image, and gets the filters to estimate the noise-free imagary from the speckled picture.
Normally the image is large, with a number of different features and the test is only carried out once. 
The benefit of this method is that a wide range of feature can be tested, which is probably closer to real-life situation. 
The draw back is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not giving a very representative result.
The methodology would also be applicable in log-transformed domain, however, 
	as the evaluation methodology is the same, 
		we prefer to apply the technique on investigating the residual image in log-transformed domain on real-life image instead.

Another way is to evaluate using a patterned, structured and repeated ground truth.
Since the structure is repeated many times, the combined results are going to be more representative.
Also, since the pattern can be pre-designed, analysis can be carried out a little bit easier.
The draw-back is that, only a single type of target can be tested at time.
The normal types of targets found in evaluating speckle filters are point targets, edges and lines.

Even with the known ground-truth, evaluating metrics need to be defined for quantitative measurements.
The most common way to detect a target from its back-ground is to compute their differences in intensity or amplitude domain. 
However since SAR is multiplicative, this difference is not only dependent on the noise level but also depend on the level of the signal.
Shi define the mid-point position of an edge as the intinsity value between the nominal values of the two regions, 
	and the sharpness of an edge as the slope between the two nominal intensities value, .

Lopes also proposed the variation co-efficient index  to evaluate speckle filters.
Since Lopes' underlying assumption of the scene variation may not be applicable in the designed pattern, 
	we consider the index as inapplicable for these experiments.

As we repeat a pattern multiple times,
	the histograms of target and background area can be obtained.

The target and background can then be seperated using a simple threshold based classification model.
We judge the separability of the two stochastic population by the standard ROC, and the quantitative metric of Area Under the ROC curve can then be used as an evaluation metric.

Overall, we have seen many different way and metric to evaluate speckle filters. 
And it is always advantageous to have a single metric to finally judge if a filter is better than the other.
Wang has attempted to look at the problem. 
He proposed to use fuzzy membership to weight opinions of an expert panel.
We find this suggestion to be tedious in implementation, fuzzy in concept and subjective in nature.

Another attempt is to apply the universal Mean Squared Error into the context of SAR data.
However since SAR data is heteroskedastic, the use of MSE normally comes with a twist.
Gagnon suggest the use of Signal over mean square noise removed metric, which is argued to be similar to the standard Signal to noise ratio (SNR).
Others suggest the use of normalized MSE, which essentially be the ratio between MSE and the expected mean.

We believe the use of MSE in homoskedastic log-transformed domain could be used.
This is similar to the investigation of residual image in log-transformed domain. 
This also agrees with the log-transformed variance metric in homogeneous area (assuming that the filters having no problem preserving the mean).
We also show experimentally that this MSE is inversely correlated with the AUC index mentioned earlier, suggesting that the lower the MSE index a filter can achieve, the better its feature preservation capability.

The paper is structured as follow:
Section 2 will provide a brief discussion of Log Transformation. 
Section 3 will illustrate the use of MSE in log-transformed domain to evaluate different filter's speckle suppression power in homogeneous area.
Section 4 will discuss the use of the same MSE to evaluate different filters' performance in heterogeneous area.
Section 5 will presents our discussion and our conclusion remarks.

Logarithmic Transformation

For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily (cite here some latest). That is because: eventhough, the statistical model within individual resolution cell is well established, the applicability of its corresponding estimators is restricted to homogenous areas. Practical images, however, are heterogenous. Crucially it is this spatial variation that is of high interest. This fact gives rise to the question that seemed obvious: how to call an analysis area heterogenous and subsequently what to do in the case of heterogeneity.

Various statistical models for heterogenous areas have been proposed (see  for a detailed review). Unfortunately, while most of the models highlight the multiplcative nature of sub-pixel or homogenous original SAR data, in extending the model to heterogenous images, virtually none has noted that spatial varition also gives rise to heteroskedasticity phenomena. Heteroskedastic, as explained in section ???, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean or equivalently its underlying back-scaterring coefficient . It is believed that heteroskedasticity give rise to serious negative impacts on various stages of speckle-filtering.

In modelling, heteroskedasticity has direct consequences in the central question of homogeneity or heterogeneity. In normal images, the contrast or variance among neighboring pixels have been used to measure homogeneity. Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. In SAR images, both of these measures are dependent on the underlying coefficient . This make the problem of estimating variance is equal to the problem of estimating the mean and is the same as the main problem: estimating . The fact give rise to the vicious circle in SAR speckle filtering.

Case in point can be illustrated in the recently published improved sigma filter. The technique determines outlying points as being too far away from the standard deviation. However, as is done in , to estimate standard deviation, an estimator of mean is required and used. It is interesting to note that the MMSE estimator used to estimate the mean in , itself alone, is a rather successful speckle-filter.

Heteroskedasticity also poses numerous challenges in designing and evaluating an efficient estimator. 
Heteroskedasticity directly violates Gauss-Markov theorem's homoskedastic assumption. 
Thus it renders the efficiency of any naive Ordinary Least Square estimator in serious doubt . 
If the variance is known a priori, it has been proven, cite Aitken, that a weighted mean estimator is the best linear unbiased estimator. 
Interestingly, as noted by Lopes , most known common successful adaptive filters    does make use of weighted mean estimators. 
The caveat however is that in SAR speckle filtering, variance is not known a priori. 
And eventhough variance can be estimated from observable values, as the vicious circle goes, estimating the variance is as good as estimating the underlying coefficient  itself.

Last but certainly not least, is the bad impact of heteroskedastic on SAR image interpretation. Most of the task to be carried out in intepreting SAR images almost certainly involves target detection, target segmentation and/or target classification. All of these tasks requires a good similarity or discriminant functions. Foundation to all these is the need of a consistence sense of distance. Unfortunately, by definition heteroskedasticity provided inconsistent measures of distance. This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to cause a large class of artificial neural networks as well as a number of other computational intelligence methods to underperform.

In this section, we will first discuss about the normal original SAR domain where the noise is multiplicative and heteroskedastic.
Next we will show that log transformation convert the data into additive and homoskedastic model, where the noise is not only additive but also independent of the underlying radiometric signal.
From the consistent and additive noise in log-transformed domain (i.e. given the radiometric value is known, the plots of ln(I) is fixed), we describe the consistent sense of dispersion and contrast (i.e. the plots of  and  is fixed as long as it is taken from an homogeneous area with unchanged radiometric value, regardless of its specific value).

Original Heteroskedastic Model

SAR speckle phenomena is explained as the interference of many coherent but dephased back-scaterring components, each reflecting from different and distributed elementary scaterers . These interference can be considered as a random walk on the 2D complex plane .  The random nature of the process arises due to the unknown random location, height, distance and thus random phase of each elementary scaterer and its response.

Assuming the Central Limit Theorem is applicable , then the real part  as well as the imaginary part  of the observed SAR signal  can be considered as random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances   . Their probability density function (pdf) is given as:

It then can be proved that the measurable amplitude  is a random variable of Rayleigh distributed and consequently intensity  is a random variable of negative exponential distributed random process.

l l l
pdf(A) &=& 2A^2e^ ( -A^2^2 ) 
pdf(I) &=& 1^2e^( -I^2 )

From statistical perspective, the multiplicative nature of amplitude and intensity data can be explained as follows. Consider two fixed, independent to  unit distributions given below:

l l l
pdf(A_1) &=& 2A_1 e^ ( A_1^2 ) 
pdf(I_1) &=& e^ ( -I_1 )

It is then trivial to prove that amplitude and intensity is simply a scaled version of these unit variables, ie.  and . 
These relationships evidently manifest a mutiplicative nature.

If spatial homogeneity is defined as imaging scenes having the same back-scattering coefficient , then over a homogenous area, the measured values can then be considered as samples coming from a single stochastic process. Consequently, the population expected mean and variance of the four distributions are given in table

From the above analysis, it is evident that amplitude as well as intensity SAR data suffer from hetoroskedastic phenomena, which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean. In the context of speckle filtering, table  indicates the vicious circle: estimating variance is equal to estimating the mean and is as good as main problem, ie. estimating the unknown parameter

 Homoskedastic effect of Logarithmic Transformation

We propose to consider base 2 logarithmic transformtion of SAR orignal random variables

l l l l l
L_1^A &=& _2(A_1) &=& L_1^I / 2 
L_A &=& _2(A) 	&=& L_1^A + _2
L_1^I &=& _2(I_1) 
L_I &=& _2(I) 	&=& L_1^I + 2 _2

Bearing the relationship among the random variables in mind, it is then trivial to give the probability distribution of these log-transformed variable as below:

l l l
pdf(L_1^A) &=& 2 2^[ 2 L_1^A - 2^2 L_1^A ] 
pdf(L_A) &=& 2 2^[ ( 2 L_A - 2 _2 ) - 2^( 2 L_A - 2 _2 ) ]  
pdf(L_1^I) &=& 2^[ L_1^I - 2^L_1^I ] 
pdf(L_I) &=& 2^[ ( L_I - 2 _2 ) - 2^( L_I - 2 _2 ) ]

Noting that these distributions belong to Fisher-Tippet family, the population expected mean and variances are given in table , with  being Euler-Mascheroni constant.

The equations above also highlight the relationships among random variables in log-transformed domain. 
Two conclusions become evident from these formula. 
Firstly, in log-transformed domain, working on amplitude or intensity will tend to give identical results. 
Secondly, the effects of converting multiplicative nature to additive nature of logarithmic transformation is clearly manifested. 
Table  clearly confirms the condition of homoskedastic,  defined as  the independence of conditional expected variance on the conditional expectation of mean.

This result is consistence with finding by Arsenault .  
The main difference would be the use of base 2 logarithm which is prefered here for faster computation.

Table  summarize the discussion so far. It can be seen that while original data, especially intensity values, should be prefered for multi-look processing, log-transformed domain, with its homoskedastic effects, offers consistence sense of dispersion and contrasts. Thus log transformation is proven here to be a homomorphic transformation allowing one to apply traditional linear, additive, least squared error regression signal processing (wavelet) and computational (neural networks) techniques into SAR data.

*

The result here is experimentally confirmed by inspecting measured data from a known homogenous area. Fig.  plot the histogram of observable data within a homogenous area imaged by RADARSAT2 against modelled PDF response. The excellent agreement between this model and various experiments has long been noted and undisputed. This modelling has been very successful in eplaining speckle phenomena and verified through scientific experiments .

Consistent sense of distance in Log-Transformed domain

The consistent sense is illustrated in this section from two different perspective. First, assume the back-scattering coefficient  is known a priori. Consider the random variable defined as the distance between an observable sample and its expected value.

l l l l l
D^A &=& A &-& avg(A) 
D^I &=& I &-& avg(I) 
D^L_A &=& L_A &-& avg(L_A) 
D^L_I &=& L_I &-& avg(L_I)

Noting the results from previous section, the pdf for these variable can be trivially given as

l l l
pdf(D^A) &=& 2( D^A + 2 )^2e^ ( -( D^A + 2 )^2^2 )  
pdf(D^I) &=& 1^2e^( -( D^I + ^2 )^2 )  
pdf(D^L_A) &=& 2 2^[ ( 2 D^L_A + 2 2 2 ) - 2^( 2 D^L_A + 2 2 2 ) ] 
pdf(D^L_I) &=& 2^[ ( D^L_I + 2 ) - 2^( D^L_I + 2 ) ]

It is evident from the equations that these distributions are dependent on  in the original SAR data but is independent of it in the log-transformed domain.

From another perspective, given two adjacent resolution cells that is known to have the same but unknown back-scattering coefficient , consider the random variable defined as the contrast between two measured samples, in log-transformed domain.

l l l l l
C_L^A &=& L_1^A_ &-& L_2^A_ 
C_L^I &=& L_1^I_ &-& L_2^I_

Noting that , it should come as no suprise that the sense of contrast is consistent in log-domain but in-consistent in original domain. 
The pdf of these variables can be given as:

l l l
pdf(C_L^A) &=& 2 2^(2 C_L^A )1+2^( 2 C_L^A ) 2  
pdf(C_L^I) &=& 2^( C_L^I )1+2^( C_L^I ) 2

Figure  illustrate good agreement between the analytical pdf and observable histogram of distance and contrast of the same area in log-transformed intensity RADARSAT-2 image. Distance is calculated as the difference between each value point and the average value of the patch, while contrast is calculated as the difference between two horizontally adjacent values in log-transformed domain.

Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that the sense of observable distance in original SAR data differs, ie. is inconsistent, across different homogenous areas. The observable distance in log-transformed domain however is consistently the same across different homogenous areas. One possible benefit is that should the sigma filter be designed against the , the scale estimator would no longer be required.

Evaluating Speckle Filters on Homogeneous Areas

We illustrate the concept of consistency by plotting histogram single look and multi-look simulated homogenous SAR data over different radiometric values. Specifically we shows that the plots in log-transformed domain is consistent while the plots in the original domain is not.

We shows that all the standard filters preserves this consistency in its filtered output (note: boxcar filter is actually multi-processing). 
This consistency will also leads to consistent sense of distance described earlier.
We can briefly mention that the expected mean value are also preserved by the filters.

This consistent sense of distance may explain a few phenomena that appears to be unrelated before.
First it explain why in SAR edge detector is prefered to normal differential based detectors  and . In other words, in log-transformed domain, the standard differential based detector should also work.
It leads to consistent variance in log-transformed domain, which we measured across the filtered results for different radiometric values.
It could also explains why in the origianl domain, the ratio between variance/mean that is the ENL is a robust evaluation metric (it is consistent and thus can be evaluated on homogeneous area, regardless of specific radiometric value).

Next we shows that the variance in log-transformed domain is equationally related to the universal ENL index. 
Variance computation is theoretically given by Hoek and Xie.
We show the computation can be simplified as in the confirmation report.
Thus given an known homogeneous area, the log-variance can be computed and the ENL can be evaluated as ...
We repeat the experiment in the confirmation report to confirm the agreement between theoretical analysis and experimental results.

Evaluating Speckle Filters on Heterogenous Area

Evaluating Filters over Repeating Structured Patterns

The types of pattern are: point targets, line targets, edge targets and heterogeneous scene. 
All patterns are limitted two class of ground-truth: background and target areas.
We plots histograms of filtered values on target and background populations in log-transformed domain.

From a detailed analysis point of view, we show that the radiometric preservation criteria is closely linked to the estimator's bias performance.
Also the speckle suppression is related to the measured variance.
Thus we argue that: MSE performance of the estimator, being the addition of bias and variance performance could be used as a performance metric.

From high-level perspective, we show that feature preservation can be evaluated by examine the separability of the two background and target populations.
We measure the separability of the two histograms by computing the standard Area Under the ROC Curve index.
We note that the MSE in inversely correlated to this separability index, suggesting that the lower MSE achivable by the filters would lead to better feature preservation in general.

Evaluating Filters over Practical Images

We apply the filters on a real SAR data and compute the residual image in the log-transformed domain and the ratio images in the original domain.
We plot the histogram of the derived images and evaluate how closely it matches with the noise characteristics of speckled image and show that the two methodologies are equivalent.
The distance between the histograms can be measured as the difference between its entropy.

The filters can also be applied on a speckle simulation of an aerial optical image. 
A similar evaluation methodology can be applied for this type of experiment.
As the ground-truth is available, an extra metric can be measured is the Mean-Squared-Error.
However, if this is designed as a single-run experiment, then the measured MSE may not be very representative. 
Also it should be noted that the performance of the filters may be dependent on the specific scene chosen, and designing an universal scene to comprehensively evaluate speckle filter is still an open question, as far as we know.

Discussion and Conclusion

Discussion

In the experiments above we mostly used filters with 3x3 window.
We are aware that the normal window size used is much larger, however, we insist on these value for a few reasons.
First filters with smaller size allow us to use smaller pattern without worring much about how cross talks among different targets in adjacent patterns.
Second, we want this paper to focus on advocating the use of MSE in log-transformed domain to evaluate speckle filters, and do not wish to claim or to make the decision about the "best" filters.
Interested filter designers however are wellcomed to download our evaluation code in Matlab online and we would be delighted to the central place for publishing and comparing the results of your filters on our web site.

Stochastics simulation is used extensively to evaluate the performance of statistical estimators (i.e. speckle filters). 
The use of simulation and modelling in speckle filtering allow for faster simulation and evaluation of different underlying scenarios. 
Detailed analysis can then be done repeatedly on simulated small data without the need of a real large image. 
This allow qualititative requirements of speckle removal process to be mapped into specific and quantitative requirements in designing speckle filters. 
We believe that the qualitative requirement of speckle suppression can be quantified as the variance in log-transformed domain. 
While the visual requirements of feature preservation, in the simple scenes of only targets and clutter, can be broken down into the requirements of radiometric preservations and speckle suppression.
These smaller requirements are equivalent to the bias and variance evaluation of statistical estimator.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by the standard metric for target detectability: the Area Under the ROC curve.
We show experimentally that the MSE inversely correlated with the AUC index, for all of the simulated patterns.

The patterns used is chosen based on our exeriences and they may affects evaluation results. 
In fact, we do not know of any pattern that would be fair towards every possible filters.
So the patterns should only serves as guide lines, and filter designers may not want to overly optimize their filter's performance on any single of these patterns.
As doing so may make the filter lose out in other aspects.

While the pattern should not be used as be-all end-all criteria, we believe that MSE in log-transformed domain should receive serious considerations of future filter designers.
And this is due to good reasons, that Gauss Markov theorem being applicable again in this domain.
We believe an optimization for minimal MSE is likely to succeed.
We hope and expect to see more standard image processing or signal processing algorithm being applicable to SAR images in log-transformed domain. 
Of course the advice is caveat emptor

It is widely known that log transformation converts multiplicative noise into additive noise. 
One should note that the noise is not Gaussian and not even centered around origin.
This may explain why averaging filters in log-transformed domain proposed by Arsenault does not work well in practice.
To counter this, we suggest to use Maximum Likelyhood Estimation instead of simple averaging (cite our works).
In fact, it should be noted that averaging is the MLE estimation in the original domain.

Conclusion

To summarize,

	speckle filters are evaluated using many different qualitative criteria.
To compare the filters altogether, however, we need a way to quantify and measure these.
Logarithmic transformation are shown to not only convert multiplicative and heteroskedastic noise in original SAR domain to additive and homoskedastic values, it also presents a consistent sense of distance.
Hence we describe and advocate the use of Mean Squared Error in log-transformed domain as an unifying criteria to quantitatively measure different requirements for speckle filters.

Our contributions are mainly centered around two points.
First we give an equation which links the ENL index to the variance in the log-transformed domain.
Second we shows that MSE is inversely correlated to the AUC index in heterogenous area, suggesting that the smaller MSE a filter can achieve, the better its ability to discriminate features.

Another approach in our research (cite POLSAR paper) suggest that there is also a similar consistent sense of distance in POLSAR data.
Our future work may suggest applicability of MSE approaches on POLSAR data.
We hope this would allow a wide range of developed algorithms, especially those in the fields of image processing, signal processing, machine learning or information processing, to be applicable in solving both SAR and POLSAR remote sensing problems.

IEEEtran

### 2013-03-01 paper_dev/old.article.tex
201303_Mar01

--- 2013-03-01 paper_dev/article_vch.tex
@@
 %\documentclass[a4paper,10pt]{article}
+%ifdef FINAL
 \documentclass[journal]{IEEEtran}
+%endif
+%ifdef REVIEW
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+%endif
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
@@
 	%and Timo~Brestchneider % <-this % stops a space
-}
-\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun, are with School of Computer Engineering, 
+\thanks{Thanh-Hai~Le, Quang-Huy~Nguyen and Chan-Hua~Vun are with School of Computer Engineering, 
 Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
@@
 }% <-this % stops a space
-\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS InnovationWorks Singapore for 
-	initial discussions and for providing RADARSAT2 images used in this paper. }% <-this % stops a space
+\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
 \thanks{Manuscript received ?, 2012; revised ?.}}
 
-\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, Jul~2012}%
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
 { Le \MakeLowercase{\textit{et al.}}: Using Mean-Squared-Error in Log-Transformed Domain to Evaluate Speckle Filters }
@@
 \begin{abstract}
-
 Logarithmic transformation has the potential to convert 
@@
 We show, through experiments and analysis, that 
-	the familiar mean squared error (MSE) criteria can reliably serve 
+	the familiar mean-squared-error (MSE) criteria can reliably serve 
 	as a single unifying performance indicator to evaluate SAR speckle filters. 
@@
 	log-transformed SAR data with the canonical Equivalent-Number-of-Looks index.
-For heterogenous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
-	is shown to be equivalent to the ratio-based radiometric preservation criteria that is usually assessed in the 
+For heterogeneous scenes, the standard residual-based bias evaluation, also in the log-transformed domain, 
+	is shown to be equivalent to the ratio-based radiometric preservation criteria, frequently employed in the 
 	original domain. 
 Through experiments as well as analysis, we show that lower MSE suggests better feature detection and classification
-	ability, which is an important requirement for subsequent post-filtering steps in practical SAR data processing.
-In this paper, we hence propose and describe the combined use of log-transformed and MSE to evaluate SAR speckle 
+	ability, which can be an important requirement for subsequent post-filtering steps in practical SAR data processing.
+Combining bias and variance evaluation, we propose and describe the use of MSE evaluation in log-transformed domain to evaluate SAR speckle 
 	filters.
-
 \end{abstract}
@@
 The nature of SAR speckle is that
-	it is stochastic even when the underlying radiometry is constant, 
-	and when there are spatial variation of this radiometry, not only its expected value changes, but so does its heteroskedastic variance.
+	it is stochastic even if the underlying radiometry is constant. 
+And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
 Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
@@
 SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
-The stages in this statistical framework consist of statistical modelling, estimator development and evaluation of the estimators' performance. 
-Estimators are typically evaluated based on the bias and variance properties of their estimates; 
-	with lower bias and / or lower variance (hence lower MSE) indicating better accuracy.
+The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
+%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
+%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
+Estimators are typically evaluated based on the bias and variance properties of their estimates:
+  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
 Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-In addition, due to the stochastic nature of SAR processing, as well as the simulating process, 
-	statistical summaries of repeatedly simulated experiments are normally preferred to single-run results.
+In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
+	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.
 
@@
 	prompting alternative evaluation criteria to be proposed.
-In fact, a survey of relevant literature fails to reveal 
+In fact, our survey of relevant literature fails to reveal 
 	a single universally agreed quantitative metric for the performance of speckle filters.
@@
 	performance. 
-As such, many papers lack a comparative basis beyond simple visual qualititave comparision on a few image scenes. 
-While such visual comparison is useful, as an evaluative methodology, it regretably lacks scientific objectivity. 
+As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
+While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
 Some papers do present quantitative measurements. 
@@
 	as a criteria for choosing the most suitable speckle filter for a given satellite-captured SAR image.
-%And the last section provides our discussion together with our concluding remarks.
 Finally, Section \ref{sec:discussion} discusses the findings and presents concluding remarks.
@@
 
-%Addressing this issue, 
-%There have been a few published articles dedicated to the topic of evaluating speckle filters.
-%However, our survey of SAR speckle filtering research indicates 
-%	the lack of a single universally-agreed quantitative metric to evaluate speckle filters.
-%In this section, we briefly review published work 
-%	related to the topic of evaluating SAR speckle filters.	
-It is customary to divide the performance evaluation of speckle filters across the two classes of 
-	homogeneous and heterogeneous regions.
+It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
+	homogeneous and heterogeneous region evaluation.
 Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
 As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
-	output (i.e. the speckle suppression power).
-In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complex, 
+	output (a.k.a the speckle suppression power).
+In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
 	due in part to the following difficulties.
@@
 	to be measured and compared.
-%IVMIn this section, various published work in evaluating SAR speckle filters are reviewed.
 
 In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
-Furthermore, its application in a SAR processing framework should enable an improvement in the measurement, 
+Furthermore, the application of any speckle filter in a SAR processing framework
+   should enable an improvement in the measurement, 
 	detection or classification of the underlying radiometric features.
-%As shown in the subsequent section, 
-%	one can choose to work in the original domain of SAR data where the speckle is multiplicative and heteroskedastic, or
-%	logarithmic transformation can be utilized to convert SAR data into a simpler additive and homoskedastic model.
 As shown in the subsequent sections, by applying log-transformation, 
@@
 	and variance error of the output.
-As the MSE evaluation is a combined evaluation of bias and variance error, it is therefore capable of evaluating 
+As the MSE evaluation is a combination of bias and variance error, it is therefore capable of evaluating 
 	the general requirements of speckle filtering.
-%Combined the overall general requirement of speckle filters can be evaluated using the traditional Mean-Squared-Error.
 
 For homogeneous scenes where the underlying radiometry is assumed to be constant, 
-	the filtered results, statistically speaking, are considered to be samples of 
+	the filtered results are considered, statistically speaking, to be samples of 
 	a single but complex stochastic process.
-%Statistical analysis have shown that the SAR speckle is not only multiplicative but also heterokedastic.
 From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
 	of speckle filters can be judged using the familiar bias and variance evaluation.
-	%are expected to estimate with no radiometry bias. 
-%The best filters achieve maximum speckle suppression power in such areas.
 
@@
 A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
-In the log-transformed domain, the equivalent index for evaluation could be performed by a simple substraction.
+In the log-transformed domain, the equivalent criteria for evaluation could be performed by a simple subtraction.
 In other words, it is clear that the bias evaluation in the log-transformed domain 
-	can be used to similarily evaluate the radiometric preservation requirement of speckle filters.
+	can be used to evaluate the radiometric preservation requirement of speckle filters.
 
@@
 	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
-In this paper, we will also show that all of these standard filters 
-	not only preserves the expected radiometric values in the log-transformed domain,
-	they also preserve a number of subtractive and consistent measures of distance.
+In this paper, we will also show that all of these standard filters preserve
+	not only the expected radiometric values
+	but also a number of subtractive and consistent measures of distance exhibited in the log-transformed domain.
 
@@
 Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
-In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is related to variance in the 
+In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is mathematically related to variance in the 
 	log-transformed domain.
-%However, since Lopes' underlying assumption of the scene variation may not be applicable in a designed test pattern, we do not consider the index further in these experiments.
 Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
 	which is the primary criteria used to evaluate speckle filters over homogeneous area.
-%Combined, in homogeneous area, we show that variance evaluation in log-transformed domain, 
-%	which is a component of MSE evaluation, 
-%	can be and practically has been used to evaluate speckle filters.
-%Combined, we show that Mean Squared Error in log-transformed domain can be used to evaluate speckle filters not only in homogeneous areas but also in heterogeneous scenes.
 
 Real-life and practical images, however, are not homogeneous.
-Thus there are a number of associated difficulties in evaluating speckle filters over heterogenous scenes.
-%and there are many proposed methods of evaluating speckle filters in such areas. 
-%It is here that the situation becomes less structured, and more `exciting' from a research perspective.
-%and it is here that things gets a lot more exciting and unstructured to evaluate speckle filters in heterogenous area.
-The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparision. 
+Thus there are a number of associated difficulties in evaluating speckle filters over heterogeneous scenes.
+The first difficulty in evaluating speckle filters for heterogeneous scenes is to select the basis for comparison. 
 It is trivially easy to estimate the underlying radiometric coefficient if an area is known to be homogeneous.
 However, without simulation or access to solid ground-truth, it is practically impossible to do so for 
-	real-life images (hence, the need for speckle filters estimation).
-
-Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image 
-	mentioned above. 
-Under a multiplicative model, the ratio image is expected to comprise (???? comprise of data with ?)
+	real-life images.
+And hence, the need for speckle filters estimation is warranted.
+
+Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above. 
+Under a multiplicative model, the ratio image is expected to comprise solely of
     the noise being removed (i.e. it should be completely random). 
 Being random, this should display as little ``visible'' structure as possible. 
-%Also its histogram and PDF are expected to match the noise characteristics in the original image as closely as possible.
-However, when displaying such images for visual evaluation, ratios that are smaller than unity are much 
-harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}, 
-meaning that a purely visual analysis may be insufficient.
-We therefore propose to adopt a log-transformed domain approach where multiplicative noise 
-would then resemble the familiar additive model, and the ratio image would then become a simple subtraction image.
-The evaluation methodology for such a proposal does not change, 
-	but now the residual image is additive and linear, 
-	and would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).
+However, when displaying such images for visual evaluation, the ratios that are smaller than unity are much 
+harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}. 
+We therefore propose to adopt a log-transformed domain perspective 
+  where the multiplicative noise would then be transformed into a more familiar additive model.
+More importantly, the ratio image would then become a simple subtraction image.
+The evaluation methodology for such adoption would not change. 
+Only that the residual image would become linear and additive.
+And thus it would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).
 
@@
 		but also heavily affected by 
-		%reliant on 
 		the inherent noise.
@@
 	how to interpret the results, especially its accuracy.
-%is just too imprecise for us.
 
@@
 		to evaluate speckle filters.
-		%without the need to apply feature detection. 
-In this paper, we also make use of a similar methodology discussed above with two important changes.
+In this paper, we also make use of a methodology similar to the ones discussed above with two important changes.
 Firstly, our simulated experiments offer absolute ground-truth.
@@
 This performance can be 
-	conveniently visualised by plotting the Receiver Operating Characteristics Curve (ROC) 
-	as well as objectively quantified by measuring the Area Under this Curve (AUC). 
+	conveniently visualized by plotting the Receiver Operating Characteristics Curve (ROC).   
+It can also be objectively quantified by measuring the Area Under this Curve (AUC). 
 As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
@@
 Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
-This is the second difficulty in evaluating speckle filters for heterogenous scenes.
+This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
 Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
 	normally at local or regional levels.
-In fact, the common consensus is that a powerful speckle suppresion filter (for example the boxcar filter) 
+In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
 	is likely to perform poorly in terms of preserving underlying radiometric differences 
-	(such as causing excessive blurring), and vice versa. 
-%One can relatively easily satisfy one of these criteria, but not easily satisfy both.
-%Thus, the second difficulty in evaluating speckle filters for heterogeneous scene is to find a single valid metrics to measure the performance of speckle filters.
-
-Overall, many different methods and metrics have been proposed to evaluate varios aspects of speckle filters. 
+	(e.g. causing excessive blurring).
+Furthermore, we have not found many published articles combining the evaluation
+  of these two seemingly contradicting requirements.
+
+Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
 However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
@@
 Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
-	is still subjective in nature.
+	subjective in nature.
 
@@
 Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
-However since SAR data is heteroskedastic, which violates the assumptions of the Gauss Markov theorem, 
+However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
 	the use of MSE is not straightforward. 
-Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of the signal over mean square noise removed metric, 
-	which is argued to be similar to the standard signal to noise ratio (SNR) in intrepretation. 
+Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
+  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
+The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
 Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
@@
 In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
-As the important Gauss Markov theorem becomes applicable again, 
-	the use of MSE is shown to be relevant again in evaluating statistical estimators (i.e. speckle filters).
-Initial intitution (??? intuition?)
-	suggests that each components of the MSE measure, 
+As the important Gauss-Markov theorem becomes applicable in this transformed domain, 
+	the use of MSE is shown to be again relevant for evaluating statistical estimators (i.e. speckle filters).
+Intuitively, each components of the MSE measure, 
 	namely bias and variance evaluation, can be mapped into 
@@
 
-SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
+The SAR speckle phenomena is often explained as the interference of many coherent but dephased back-scattering components,
 	each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, 
@@
 uncorrelated Gaussian distributed stochastic processes with zero means and 
-% indentical ??? 
 identical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. Their probability density function (pdf) is given as:
@@
 \begin{table}[!h]
-\caption{Both the mean and the variance of noisy SAR image data are related to the scale factor $\sigma$.}
+\caption{Both the mean and the variance of original SAR data are related to the scale factor $\sigma$.}
 \label{tbl:orginal_sar_avg_var}
@@
 expectation of the mean. 
-In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle; 
-estimating variance is equal to estimating the mean and is equivalent to the main problem, 
-ie. estimating the unknown parameter $\sigma$.
-
-The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of look 
+In the context of speckle filtering, Table \ref{tbl:orginal_sar_avg_var} indicates the vicious cycle: 
+estimating variance is equal to estimating the mean and to estimating the unknown parameter $\sigma$, 
+i.e. the main problem.
+
+The formulas above have long been noted. In fact while pioneering the estimation of the equivalent number of looks 
 (ENL) index, Lee et al commented that the ratio of expected standard deviation to mean is a constant in both 
@@
 In SAR images, both of these measures are dependent on the underlying coefficient $(\sigma)$. 
-This make the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
+This makes the problem of estimating variance to be equal to the problem of estimating the mean (i.e. equivalent 
 to estimating $\sigma$).
@@
 
-Case in point can be illustrated in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
+A case in point is the recently improved sigma filter\cite{Lee_TGRS_2009}. 
 The technique determines outlying points as being too far away from the standard deviation. 
@@
 Each of these tasks require good similarity or discriminant functions. 
-Foundational to these is the need of a consistent measures of distance. 
+Fundamental to these is the need of a consistent measures of distance. 
 Unfortunately, by definition, heteroskedasticity leads to inconsistent measures of distance. 
@@
 \subsection{ Homoskedastic effect of Logarithmic Transformation }
+
+\begin{table}[t]
+\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
+\label{tbl:sar_log_domain_avg_var}
+\normalsize
+\centering
+%\begin{center}
+
+\begin{tabular}{|l|l|}
+\hline
+Mean & Variance \\
+\hline
+$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
+$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
+$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
+$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
+\hline
+\end{tabular}
+
+%\end{center}
+\end{table}
 
@@
 Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$
-
-\begin{table}[!h]
-\caption{ Mean and Variance of Log Transformed SAR values. }
-\label{tbl:sar_log_domain_avg_var}
-\normalsize
-\centering
-%\begin{center}
-
-\begin{tabular}{|l|l|}
-\hline
-Mean & Variance \\
-\hline
-$avg(L_{1^A}) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2}$ & $var(L_{1^A}) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
-$avg(L_{1^I}) = \gamma \cdot \frac{1}{\ln2} $ & $var(L_{1^I}) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2} $ \\
-$avg(L_A) = \frac{ \gamma }{2} \cdot \frac{1}{\ln2} + \log_2{\sigma}$ & $var(L_A) = \frac{ \pi ^2}{24} \cdot \frac{1}{(\ln2)^2}$ \\
-$avg(L_I) = \gamma \cdot \frac{1}{\ln2} + 2 \log_2{\sigma}  $ & $ var(L_I) = \frac{ \pi ^2}{6} \cdot \frac{1}{(\ln2)^2}$ \\
-\hline
-\end{tabular}
-
-%\end{center}
-\end{table}
 
@@
 defined as the independence of the conditional expected variance on the conditional expectation of the mean. 
-
-This result is consistent with finding by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
+This result is consistent with findings by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
 The main difference would be the use of base-2 logarithm which is preferred here for more efficient computation.
@@
 \begin{table*}[t]
-\normalsize
+\smallsize
 %\hrulefill
@@
 
-\begin{figure}[h]
+\begin{figure}[!h]
 \centering
@@
 
-The consistent sense (??? feature?) is explored and illustrated in this section from two different perspectives. 
+The consistent feature is explored and illustrated in this section from two different perspectives. 
 First, we assume that the back-scattering coefficient $\sigma$ is known \textit{a priori}. Consider the random 
@@
 
-Noting the results from the previous section, the pdf for these variable can be derived and shown to be as follows:
+Noting the results from the previous section, the pdf for these variable can be derived as follows:
 
@@
 To illustrate this characteristic, Figure \ref{fig:residual_as_noise} is generated by using data from the RADARSAT-2 
-image. As can be seen, it shows excellent agreement between the analytical pdf and observable histogram of deviation
-(??? 'deviation', or 'dispersion' as indicated in the figure?) 
+image. As can be seen, it shows excellent agreement between the analytical pdf and observable histogram of dispersion
 and contrast of the same area in a log-transformed intensity RADARSAT-2 image. 
@@
 
-\begin{figure}[h!]
-\centering
-%\begin{tabular}{c}
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
 	\subfloat[dispersion]{
@@
 	}
-%\end{tabular}
-\caption{Observed and modelled pdf of deviation
+\end{tabular}
+\caption{Observed and modelled pdf of dispersion 
 and contrast in homogenous log-transformed intensity images.}
@@
 Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that 
-the measure of observable deviation in original SAR data differs, i.e. is inconsistent, across different homogenous 
-areas. On the other hand, the observable deviation in the log-transformed domain is consistently the same across 
+the measure of observable contrast in original SAR data differs, i.e. is inconsistent, across different homogenous 
+areas. On the other hand, the observable contrast in the log-transformed domain is consistently the same across 
 different homogenous areas. As such, one possible benefit is that should the sigma filter\cite{Lee_TGRS_2009} be 
@@
 
-From the results of previous section, two sample variance distribution ($V_x = C_x^2$) can be given analytically as 
+From the results of the previous section, two sample variance distribution ($V_x = C_x^2$) can be given analytically as 
 follows:
@@
 In summary, measurements of distance for a number of cases are shown to agree with the 
-consistent sense of variance / deviation and homoskedasticity. The measure of disimilarity can be used to test 
+consistent sense of variance / contrast and homoskedasticity. The measure of disimilarity can be used to test 
 if a pixel belongs to a ``known'' scatterrer, an example of its use in this way is illustrated in our kMLE speckle 
-filter. The consistent sense of contrast can be used to test if any pair of measured data points belong to 
+filter \cite{Le_2010_ACRS}. The consistent sense of contrast can be used to test if any pair of measured data points belong to 
 the same class of scatterer. It may also explain why, in the original SAR domain, the ratio based 
@@
 
-\begin{figure}
+\begin{figure}[h]
  \centering
@@
 	and PDE filter \cite{You_TIP_2000}.
-Evidently in the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
+Evidently for the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
 %Thus $MSE_{residual}^{none} = MSE_{base}$
@@
 A conventional method is to investigate the ratio images between the filtered output and the noisy input images.
-Since logarithmic transformation convert these ratio into substractive residual which are consistent, residual 
+Since logarithmic transformation converts these ratio into substractive residual which are consistent, residual 
 analysis can be used to analyse and evaluate the performance of speckle filters.
 %To compare the use of ratio images in the original domain and the residual image in the log-transformed domain, 
-For comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
+For visual comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
 and the ratio images in the original domain, where a simple boxcar filter has been applied to data obtained from a 
@@
 \begin{figure}
+\centering  
 \begin{tabular}{c}
@@
 
-\begin{table}
+\begin{table}[h]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[h]
+\centering  
 \begin{tabular}{c}
@@
 preserve this consistency in their filtered output. Intuitively, as the boxcar filter is actually similar to 
-multi-look processing, it hence also exhibits the consistency property.
+multi-look processing, thus its output also does exhibit the this consistency.
 This consistency will also lead to the consistent sense of distance described earlier, which is significant 
@@
 %We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
-log-transformed domain. 
+%log-transformed domain. 
 The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
@@
 
-The types of test pattern used in this paper include: point targets, line targets, edge targets and a heterogeneous 
-checker board scene. 
+The types of test pattern used in this paper include the followings:
+  point targets, line targets, edge targets and a heterogeneous checker board. 
 These test patterns could of course be concatenated into a larger composite test image, 
@@
 \begin{tabular}{c|c|c}
-Pattern  & AUC - $MSE_{true}$ (p-value) & AUC - $MSE_{benchmark}$ (p-value) \\
+Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
 \hline
@@
 
-In this section, our conjecture (??? you want to emphasize this is a proposal that can't be proven mathematically ?) 
+In this section, our conjecture
+%(??? you want to emphasize this is a proposal that can't be proven mathematically ?)
+%ans: it is true that the conclusion cannot be proved, due to lack of absolute ground truth in real SAR images
+%our conclusion however is 1. extended from a simulations which is believed to be in agreement with realities.
 of using MSE in the log-transformed domain to find the most suitable speckle filter 
@@
 This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
-	work very well in practice. To counter this, the use of maximum likelihood estimation instead of simple averaging 
+	work very well in practice.
+To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
 	is suggested \cite{Le_2011_ACRS}. Interestingly, averaging is also the MLE operator in the SAR's original domain.
 
-%It is interesting to note that all of the standard filters' outputs exhibit consistent plots of histogram in the log-transformed domain, suggesting a consistent sense of distance. 
-Log tranformation also brings about a few consistent measures of dissimilarity.
-	This consistency can be found not only in single-look or multi-look SAR data, 
-	but can also be found in filtered data of various ``standard'' speckle filters.
-This is significant probably because it ensures the applicability of various target detection/classification 
-	algorithms, which exploit these consistent statistical properties, 
-	into not only pre-filtered data but also post-filtered data as well.
-%There are numerous
-
-This consistent measures of distance in the log-transformed domain could probably have implications beyond speckle 
-filtering. For example, in the subsequent tasks of designing target detectors or classifiers, 
-	it is normally desirable to engineer the solution to not only work on single-look or multi-look SAR data,
-	but also be applicable on post-filtered data.
-In such cases, these consistent measures of distance in the log-transformed domain could provide a sound theoretical
-	basis. In fact, a number of already proposed solutions appear to make use of this feature. 
-%(cite here some SAR classification papers)
-An example is the ratio based discriminator in the original domain. Looking backwards, in designing new speckle 
-	filters, by ensuring that the filtered output preserves this consistent property,
-	the new speckle filters would be eligible to be used as pre-processing steps for availble classifiers / detector.
+Log transformation also brings about a few consistent measures of dissimilarity.
+	This consistency can be found in single-look or multi-look SAR data, 
+	as well as in filtered outputs of various ``standard'' speckle filters.
+This allows a variety of target detection/classification algorithms
+  - which exploit these consistent statistical properties -
+  to not only perform brilliantly on pre-filtered data,
+  but also be found practically working on post-filtered data.
+
+These consistent measures of distance in the log-transformed domain could probably have implications beyond speckle filtering.
+For example, in the subsequent tasks of designing target detectors or classifiers,
+  it is normally desirable for the solution to work on both unfiltered and post-filtered SAR data.
+In such cases, these consistent dissimilarity measures found in the log-transformed domain could provide a sound theoretical
+	basis. In fact, a number of proposed solutions have already appeared to exploit this feature. 
+A case in point is the simple ratio based discriminator in the original SAR domain.
+Looking backwards, in designing new speckle filters,
+  by ensuring that the filtered output preserves these consistent properties,
+	the newly designed filters would be eligible to be employed as pre-processing step for properly designed classifiers / detector.
+From a higher level perspective, the applicability of Gauss-Markov theorem and consequently a meaningful MSE 
+  predict fruitful applications for a variety of least-squared-error algorithms in the homoskedastic log-transformed domain.
 
 Of course, there are other speckle filters that do not preserve such consistency 
-	(e.g. the pde filter \cite{You_TIP_2000}). One could argue that it would not be fair to the judge such filters 
+	(e.g. the PDE filter \cite{You_TIP_2000}). One could argue that it would not be fair to judge such filters 
 	using the MSE criteria, which tend to favour the ``standard'' filters.
-While we respect any other criteria that are used, we reiterate the two salient points of our approach. 
+While we respect any other criteria that have been used, we reiterate the two salient points of our approach. 
 Firstly, our MSE criteria is closely related to the basic ENL criteria.
-The experimental results indicated that the ENL measures for such filter (i.e. the pde filter) differ depending  
-on the radiometric values. 
+As shown in previous sections, experimental results indicated that
+  the ENL measures for such filter (i.e. the PDE filter) differ depending  on the radiometric values. 
 Secondly, speckle filters need to serve a purpose, and evaluation criteria should be relevant to such purpose.
@@
 Thus it is relevant towards subsequent target detection / classification processing, 
-	which is believed to be a relatively common subsequent processing step. 
+	believed to be a common subsequent processing step. 
 For these two reasons, the MSE criteria is advocated.
 
-In the experiments above, speckle filters with a $3 \times 3$ sliding window were used, 
-	although we are aware that the normal window size used is much larger. 
-The reasons for maintaining a small window is that 
+In the experiments above, speckle filters with a $3 \times 3$ sliding window were used 
+	even though we are aware that the normal window size employed is much larger. 
+The reasons for maintaining such a small window is that 
 	smaller-sized filters facilitate the use of smaller patterns without too much concern for crosstalk 
 	among adjacent targets.
-In addition, we focussed on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
-	and do not wish to advocate a particular ``best'' filter in practice. 
+In addition, we focused on the use of MSE in the log-transformed domain for the evaluation of speckle filters, 
+	and do not wish to advocate any particular ``best'' filter. 
 In other words, we addressed the methodology of evaluating speckle filters, 
 	and did not directly address the design of speckle filters.
-However, interested filter designers are invited to download the Matlab evaluation code used in this paper 
-to evaluate their own designs\footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
+However, interested filter designers are invited to download the open Matlab source code used in this paper 
+for evaluating their own designs
+  \footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
 
@@
 (i.e. speckle filters).
-%The use of simulation and modelling in speckle filtering research allows for faster simulation and evaluation of different underlying scenarios. 
-The use of small and simple patterns allowing detailed analysis can then be done repeatedly and reliably against the 
+The use of small and simple patterns allows detailed analysis
+  which can then be done repeatedly and reliably against the 
 stochastic nature of SAR data.
-% on simulated small data sets without the need of a common real large image that is somehow representative. 
-This helps in the mapping of qualitative requirements for the speckle removal process into specific and quantitative 
+This also helps in mapping qualitative requirements for the speckle removal process into specific and quantitative 
 requirements in the design of speckle filters.
-Its use also provides an absolute ground-truth, i.e. a solid base for comparison of results across different papers.
+Its use also provides an absolute ground-truth as a solid base for comparison of results across different papers.
 
 The main drawback, of course, is that ground truth often does not exist in real-captured SAR images.
-%, there is no ground-truth.
 Thus the result extension towards real images is only analogical.
@@
 We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
-%In fact, we believe the situation is more fuzzy when it comes to classifying a given noisy captured SAR scene 
 While perfect homogeneous ground truth can be defined, 
-	different heterogenous patterns exhibits different levels of heterogeneity. 
-Even though different measures have been proposed to evaluate scene heterogeneity levels or to test for the 
-homogeneity hypothesis, 
-	for real captured images, where the absolute ground-truth is not available, 
-	there does not appears to exist any certain way to assert a given image as being perfectly homogenous or 
-	absolutely heterogenous.
+	different heterogeneous patterns exhibits different levels of heterogeneity. 
+As such, different measures have been proposed to evaluate heterogeneity levels.
+Unfortunately, for real captured images, where the absolute ground-truth is not available, 
+	there is no known and certain way to assert a given image as being perfectly homogeneous or 
+	absolutely heterogeneous.
 Thus while the distinction helps in clarifying the concepts, 
 	it is probably a leaky abstraction.
-%However, without ground trutth, there appears to not exist any certain way of classifying a given captured imagary scene as homogeneous or heterogenous. 
-%In fact a few different measures have been proposed to evaluate scene homogeneity / heterogeneity.
-
-%Similarly for 
-The patterns used are chosen based on our exerience, which may affects evaluation results. 
-As different patterns result in different degrees in the scale of scene homogeneity / heterogeneity, 
+
+The patterns used are chosen based on our experience, which may affects evaluation results. 
+As different patterns result in different homogeneity/heterogeneity degrees, 
 	they also appear to affect the performance and ranking of each speckle filters.
-One extreme example is that of perfect homogeneity, where boxcar filters would be the best performer,
-	while at the other end of the spectrum, that of high heterogeneity, it is common knowledge that the boxcar 
-	would not perform well.
-%Our work suggest that the performance of speckle filters is probably scene dependent, 
-%	our conjecture is that it may depends on the level of scene homogeneity.
-%The full justification of that, however is outside the scope of this paper.
-%In fact, we do not know of any pattern that would be fair towards every possible filters.
-%So the patterns should only serves as guide lines, and filter designers may not want to overly optimize their filter's performance on any single of these patterns.
-%As doing so may make the filter lose out in other aspects.
-
-%While the patterns may not be the primary evaluative criteria, we believe that the MSE measure in the log-transformed domain (particularly log-2 transformed domain) should receive serious considerations by future filter designers.
-Again, this is due to good reasons: that the Gauss Markov theorem is applicable in this domain (and not in the original domain).
-Thus, we believe an optimization for minimal MSE is likely to succeed in good real-world performance.
-
-%IVMReaders may also find the idea of matching the most suitable speckle filter to a given scene to be foreign.
-%IVMIn fact, one hope aim of this study is being able to find ``the single best'' speckle filter.
-%IVMIn reality, the numbers in our experimental results however do not unanimous advocate a single best filter. 
-%IVMIn hind-sight, this is probably not to be expected,
-%IVM	given that the well known trade off where a power speckle-suppression filter (e.g.
-the boxcar filter) would likely to perform poorly in highly heterogeneous scenes, where radiometric preservation becomes more critical.
-%IVMSuch insight, when coupled with the fuzzy notion of homogeneity as being the special case of generalized heterogeneity, allow us to welcome the idea.
+One extreme example is that of perfect homogeneity, where boxcar filters would exhibit a respectable performance.
+While, at the other end of the spectrum: that of high heterogeneity, it is common knowledge that the boxcar filter 
+	would not perform that well.
 
 The current scheme of finding the most suitable speckle filter requires the application of all filters before 
-a decision is made, something that may be computationally expensive.
-A possible better alternative would be to predict the choice, escaping such massive requirements of processing.
+a decision is made, which probably demands excessive processing. 
+A possibly better alternative would be to predict the choice, escaping such massive requirements of computational power.
 This, however, is outside the scope of this paper.
@@
 
-To summarize, speckle filters are generally evaluated using many different qualitative criteria.
-To compare the filters against each other, a method is needed to quantify and measure these various qualitative 
-requirements and results.
-Logarithmic transformation has been shown to not only convert multiplicative and heteroskedastic noise in the 
-original SAR domain to additive and homoskedastic values, but it also presents a consistent sense of distance.
-With the Guass-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the 
+To summarise, speckle filters are generally evaluated using many different qualitative criteria.
+To compare the filters against each other, a methodology is needed
+  to quantify these qualitative requirements,
+  and subsequently to measure, compare and evaluate these quantities in the filtered results.
+Central to all these is the need for a consistent sense of distance.
+
+Logarithmic transformation has been shown 
+  not only to convert multiplicative and heteroskedastic noise in the original SAR domain to additive and homoskedastic values,
+  but also to offer a few consistent measures of distance.
+With the Gauss-Markov theorem becoming applicable in this domain, we describe and propose the use of MSE in the 
 log-transformed domain as a unifying criteria to quantitatively measure different requirements for speckle filters.
@@
 Our contribution is mainly centered around a few points. 
-Firstly, we develop an equation to links the ENL index to the variance in the log-transformed domain, 
-and illustrate it's efficacy for test images.
-Secondly we show that MSE is inversely correlated to the AUC index for heterogenous areas, suggesting that 
-the smaller MSE a filter can achieve, the better would be its ability to discriminate features.
-Thirdly, our major practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
+Firstly, a mathematical equation is established to link the ENL index to the variance in the log-transformed domain. 
+We also illustrate the use of log-variance evaluation -
+  which is shown to be equivalent to the standard ENL evaluation -
+  in evaluating the speckle suppression effect of different speckle filters.
+Secondly we show that MSE is inversely correlated to the AUC index for simulated heterogeneous areas.
+The result suggests that the smaller MSE a filter could achieve, the better it would
+be at discriminating between the underlying radiometric features.
+%The result suggests that the smaller MSE a filter could achieve, the easier it would be discriminating the underlying radiometric features.
+Thirdly, the practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
 the most suitable speckle filter for any given scene. 
-In summary, we propose the use of log-domain MSE to evaluate speckle filter performance in a variety of evaluation 
-scenarios, and suggest several test images that may be useful in this regard.
-
-It should also be noted that a similar consistent sense of distance also exists in polarimetric SAR (POLSAR) data. 
+Combined, we propose the use of MSE in log-transformed domain in evaluating the performance of different speckle filters in a variety of evaluation scenarios, and suggest several evaluation methodologies that may be useful in this regard.
+
+It should also be noted that similar consistent measures of distance also exist in polarimetric SAR (POLSAR) data. 
 Thus future work may explore the applicability of MSE approaches to POLSAR data analysis and processing.
-%We also excited with the prospect of applying a wide variety of MSE-based or discriminator based algorithms into SAR and POLSAR values in log-transformed domain.
 

### 2013-03-01 paper_dev/test_pittetd.tex
201303_Mar01

% \iffalse meta-comment
%<*driver>
% \fi
\ProvidesFile{test_pittetd.tex}
% \iffalse
\documentclass[11pt]{ltxdoc}

\usepackage{array}
\usepackage{xspace}
\usepackage{latexsym}
\usepackage[hyperindex=false,colorlinks,bookmarks,dvipdfm,%
    citecolor=blue,urlcolor=blue,bookmarksnumbered,bookmarksopen]{hyperref}

 %this is for math typing (eg: cases)
\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{indentfirst} %to handle indenting after each section
\usepackage{mdwlist} %to handle list vertical spacing without this list will be double spaced

\usepackage{moreverb} %this is for code segments
\usepackage{float} %this is for code listing
	\floatstyle{ruled}
	\newfloat{listing}{!h}{lop}
	\floatname{listing}{Listing}

\GetFileInfo{test_pittetd.tex}
\EnableCrossrefs

\title{SAR Image Segmentation using Possibilistics Segmentation}
%\date{2004/08/17}
\author{Thanh-Hai Le}

\setcounter{IndexColumns}{2}
\CodelineIndex

\begin{document}
\maketitle
\DocInput{\filename}
\end{document}

</driver>
\fi

%\newcommand\pittetd{\textsf{pittetd}\xspace}
%{\catcode`\|=12\gdef\options#1#2{\index{options to \pittetd:>\texttt{#1}|#2}\index{pittetd=\pittetd>options}\index{#1=\texttt{#1} option|#2}}}

\tableofcontents

\section{Intro}

A stochastic process\index{stochastic process}\DescribeMacro{stochastic process}, or sometimes random process, is the counterpart to a deterministic process (or deterministic system): in the sense that instead of having only one (deterministic) output of the process for all time, stochastics process has some indeterminacy in its future outputs. To illustrate: consider a coin-tossing process, its output (head or tails) for a given observation, even though constrained, is non-deterministic.

\subsection{Statistical Distributions}

Given a random variable X which belongs to a distribution d, then
\begin{enumerate*}
 \item $f_d(u)$ is probability density function (pdf) of X iff $P [a  \leq X \leq b] = \displaystyle \int_a^b{f(u)du}$
 \item $F_d(x)$ is cumulative distribution function (cdf) of X iff $P (X \leq x) = F_d(x) = \displaystyle \int_{-\infty}^x{f(u)du}$
 \item since $F_d(x) = \displaystyle \int_{-\infty}^x{f(u)du}$ it follows that $f_d(x) =\frac{\partial{F_d(x)}}{\partial{x}}$
\end{enumerate*}

It is also taken for granted that,
\begin{enumerate*}
 \item if random variable $X_e$ follows exponential distribution then
\begin{enumerate*}
\item $P(X_e \leq x) = F_e(x) = 
				\begin{cases} 
					1 - e^{-\lambda x} & \text{if } x \geq 0 \\
					0 & \text{if } x < 0 \\
                                \end{cases}
	$
\item $f_e(x) = \frac{\partial{F_e(x)}}{\partial{x}} = 
				\begin{cases} 
					\lambda e^{-\lambda x} & \text{if } x \geq 0 \\
					0 & \text{if } x < 0 \\
				\end{cases}
	$
\end{enumerate*}
 \item  if random variable $X_r$ follows Rayleigh distribution then
\begin{enumerate*}
\item $P(X_r \leq x) = F_r(x) = 
				\begin{cases} 
					1 - \displaystyle e^{\frac{-x^2}{2\sigma^2}} & \text{if } x \geq 0 \\
					0 & \text{if } x < 0 \\
                                \end{cases}
	$
\item $f_r(x) = \frac{\partial{F_r(x)}}{\partial{x}} = 
				\begin{cases} 
					\displaystyle \frac{xe^{\frac{-x^2}{2\sigma^2}}}{\sigma^2} & \text{if } x \geq 0 \\
					0 & \text{if } x < 0 \\
				\end{cases}
	$
\end{enumerate*}
\end{enumerate*}

Next it is going to be shown a well-known result that given a random variable $X_e$ follows exponential distribution then the random variable $X_1 = \sqrt{X_e}$ will follows Rayleigh distribution. The methodology here will be used to derive the distribution of log-transformed variable $X_2 = \ln(X)$

\begin{enumerate*}
 \item CDF of $X_1$ is $P(X_1 \leq x) = F_1(x)$
 \item Since $X_1=\sqrt{X_e}$, thus with $a=\sqrt{b}$ whenever $X_e \leq b$ it holds that $X_1=\sqrt{X_e} \leq \sqrt{b} = a$ or we have $P(X_1 \leq a) = P(X_e \leq a^2) $
\item  Recall that $P(X_e \leq a^2) = 1 - e^{-\lambda a^2}$, we conclude that $P(X_1 \leq a^2) = F_1(a)=1-e^{-\lambda a^2}$
\item  PDF of $X_1$ follows $f_1(x) = \frac{\partial{F_1(x)}}{\partial{x}} = \frac{\partial{(1-e^{-\lambda x^2})}}{\partial{x}} = \frac{\partial{(-e^{-\lambda x^2})}}{\partial{(-\lambda x^2)}} \frac{\partial{(-\lambda x^2)}}{\partial{x}} = e^{-\lambda x^2} \cdot 2\lambda x$
\item Setting $\lambda = 2 \sigma^2$ it is easy to see that these results conform with standard Rayleigh distribution formula above
\end{enumerate*}

Next we are going to investigate the distribution of log-transformed variable $X_2=\ln{(X_e)}$
\begin{enumerate*}
\item CDF of $X_2$ is $P(X_2 \leq x) = F_2(x)$
\item Since $X_2=\ln{(X_e)}$, thus with $a=\ln{(b)}$ or alternatively $e^a=b$ whenever $X_e \leq b$ it holds that $X_2=\ln{(X_e)} \leq \ln{(b)} = a$ or we have $P(X_2 \leq a) = P(X_e \leq e^a) $
\item Recall that $P(X_e \leq e^a) = 1 - e^{-\lambda e^a}$, we conclude that $P(X_2 \leq a) = F_2(a)=1-e^{-\lambda e^a}$
\item PDF of $X_2$ follows $f_2(x)=\frac{\partial{F_2(x)}}{\partial{x}} = \frac{\partial{(1 - e^{-\lambda e^x})}}{\partial{x}} = \frac{\partial{(- e^{-\lambda e^x})}}{\partial{(-\lambda e^x)}} \frac{\partial{(-\lambda e^x)}}{\partial{x}} = e^{-\lambda e^x} \cdot \lambda e^x = \lambda e^{x-\lambda e^x}$
\end{enumerate*}

Next we are going to show that exponential distribution is 'multiplicative' while log-transformed version is 'addtive'. Consider random variable $X_3=\lambda X_e$
\begin{enumerate*}
\item CDF of $X_3$ is $P(X_3 \leq x) = F_3(x)$
\item Since $X_3=\lambda X_e$, thus with $a=\lambda b$ whenever $X_e \leq b$ it holds that $X_3=\lambda X_e \leq \lambda b = a$ or we have $P(X_3 \leq a) = P(X_e \leq a / \lambda) $
\item Recall that $P(X_e \leq a / \lambda) = 1 - e^{-\lambda a / \lambda} = 1-e^{-a}$, we conclude that $P(X_3 \leq a) = F_3(a)=1-e^{-a}$
\item PDF of $X_3$ follows $f_3(x)=\frac{\partial{F_3(x)}}{\partial{x}} = \frac{\partial{(1-e^{-x})}}{\partial{x}} = e^{-x} $
\end{enumerate*}

Or looking at the above result from another angle: Let's call $f^1_e(x)=e^{-x}$ as the PDF function that describe the 'unit exponential random process' $X^1_e$. Then every other exponential random process $X^{\lambda}_e$, without loss of generality being characterized as $f^{\lambda}_e(x)=\lambda e^{-\lambda x}$, can be considered as a multiplicative version of $X^1_e$ (ie. $X^{\lambda}_e=X^1_e / \lambda$)

Next we are going to show that the log-transformed distribution is additive
\begin{enumerate*}
 \item  Let’s the “unit” log-transformed random variable $X^1_l$ which have PDF $f^1_l(x)=e^{x-e^x}$
\item  Consider a additively “shifted” variable $X^{\mu_0}_l=X^1_l - \mu_0$ which has its PDF $f^{\mu_0}_l(x-\mu_0) = e^{x-\mu_0 - e^{x-\mu_0}} = e^{-\mu_0}e^{x-e^{-\mu_0}e^x}$ with $\mu_0$ is the known shifted position of the new distribution. Let $e^{-\mu_0}=\lambda$, then the shifted distribution becomes $f_s(x-\mu_0) = \lambda e^{x-\lambda e^x}$
\end{enumerate*}

To sum up what we have thus far, with an eye for application to SAR problem:
\begin{enumerate*}
 \item{Let the 'unit exponential random process' $X^1_e$ have its PDF described as $f^1_e(x)=e^{-x}$ we has 2 corraly
	\begin{enumerate*}
	\item Every other exponential random process $X^{\lambda}_e$ having PDF $f^{\lambda}_e(x)=\lambda e^{-\lambda x}$ can be can be considered as a multiplicatively scaled version of the unit-exponential process $X^1_e$ (ie. $X^{\lambda}_e=X^1_e / \lambda$)
 	\item Also the “unit” log-transformed random variable $X^1_l = \ln(X^1_e)$ will have PDF $f^1_l(x)=e^{x-e^x}$ 
	\end{enumerate*} 
 }
 \item {Log-transformation convert multiplicatively-scaling nature of exponential random process to additively-shifting of distributions
	\begin{enumerate*}
	\item Log transformation of any exponential random process $X^{\mu}_l=\ln(X^{\lambda}_e)$ will have distribution $f^{\mu}_l(x)=\lambda e^{x-\lambda e^x}$. Setting $e^{-\mu}=\lambda$ then $f^{\mu}_l(x)= e^{x-\mu - e^{x-\mu}}$
	\item The additively “shifted” variable $X^{\mu_0}_l=X^1_l - \mu_0$ will have PDF $f^{\mu_0}_l(x-\mu_0) = e^{x-\mu_0 - e^{x-\mu_0}}$
	\end{enumerate*}
 }
 \item Thus it has been shown that for any exponential distribution (any $\lambda$), its log-transformed random variable has exactly the same distribution shape function (PDF: $f(x)=e^{x-e^x}$) shifted by $\mu_0=-\ln{(\lambda)}$
 \item Or equivalently to estimate $\lambda$ (or radar-cross-section in the case of SAR) in multiplicative domain, one can instead estimate $\mu_0$ in log-transformed additive domain and set $\lambda=e^{-\mu}$
\end{enumerate*}

The extra nice thing about log-transformation is that as the shape of the distribution is unchanged, regardless of $\mu_0$ the behavior of the samples variance is the same (follows the same distribution). This allow one to form statistically test the hypothesis of a given sample data-set comes from a single or multiple exponential random processes.

\subsection{Maximum likelihood Estimation}

Given a data set $X^e=\{x^e_1,...,x^e_n\}$ which follows exponential distribution $f^e(x)=\lambda e^{-\lambda x} $. We have already proven that the derivative data set $X^l=ln(X^e)$ follows Fisher Tippet distribution $f^l(x) = e^{d-e^d}$ with $d=x^l_i-\mu_0$. Next we are going to show analytically that, in the case of single-cluster, MLE of $\lambda$ from $X^e$ will equals MLE estimate of $\mu_0$ from $X^l$

Assume that the parameter of the distributions (ie. $\lambda$ or $\mu_0$ denoted as $\rho$) is known. MLE strategy maximize the conditional (likelyhood) probability $P(X^e \| \rho )$. Product rule indicate that $P(X^e \| \rho )=\displaystyle{\prod^n_{i=1}{P(x^e_i \| \rho ) }}$. Maximize $P(X^e \| \rho )$ also maximizes $\ln(P(X^e \| \rho )) = \displaystyle{\sum^n_{i=1}{ \ln(P(x^e_i \| \rho )) }}$. The parameter $\rho_0$ which maximizes likelyhood is found by setting

\begin{equation}
   \displaystyle{ \frac{ \partial{ \ln[P( X^e \| \rho )] }  }{\partial{ \rho }} 
= \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^e_i \| \rho )) } }{ \partial{ \rho } } }} 
= 0 }   
\end{equation}

Applying to exponential distribution $X^e$ we have
\begin{enumerate*}
 \item $P(x^e_i \| \lambda) = \lambda e^{-\lambda x^e_i}$ thus $ \ln( P(x^e_i \| \lambda) ) = \ln( \lambda ) - \lambda x^e_i$
 \item thus $ \displaystyle{ \frac{ \partial{ \ln( P(x^e_i \| \lambda) ) } }{ \partial{ \lambda } } =  \frac{1}{\lambda} - x^e_i } $
 \item thus $ \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^e_i \| \lambda )) } }{ \partial{ \lambda } } } =  \frac{n}{\lambda} - \sum^n_{i=1}{x^e_i} } $
 \item MLE estimate $\lambda_0$ of $\lambda$ is found by setting $ \displaystyle{ \frac{n}{\lambda_0} - \sum^n_{i=1}{x^e_i} = 0 } $
 \item or $ \displaystyle { \lambda_0 =  \frac{n}{ \displaystyle{ \sum^n_{i=1}{x^e_i} } } } $
\end{enumerate*}

Applying to log-transformed exponential distribution $X^l = \ln( X^e )$ we have
\begin{enumerate*}
 \item $P(x^l_i \| \mu) = e^{d - e^d}$ with $d=x^l-\mu $ thus $ \ln( P(x^l_i \| \mu) ) = d - e^d$
 \item thus $ \displaystyle{ \frac{ \partial{ \ln( P(x^l_i \| \mu) ) } }{ \partial{ \mu } } =  \frac{ \partial{ (d - e^d) } }{ \partial{ d } } \frac{ \partial{d} }{ \partial{\mu} } = - (1 - e^d)  = e^{ (x^l_i - \mu) } - 1}$
 \item thus $ \displaystyle{\sum^n_{i=1}{ \frac{ \partial{ \ln(P(x^l_i \| \mu )) } }{ \partial{ \mu } } } = \sum^n_{i=1}{[ e^{ (x^l_i - \mu) } - 1 ]} } =  \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu }} } - n $
 \item MLE estimate $\mu_0$ of $\mu$ is found by setting $\displaystyle{ \sum^n_{i=1}{ \frac{ e^{ x^l_i } }{ e^{ \mu_0 }}  } - n = 0}$ Noting that $ e^{ \mu_0 }$ can be moved out of the sum, that gives us $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = e^{\mu_0} n }$
 \item Note that $ e^{ x^l_i } = x^e_i $ thus $\displaystyle{ \sum^n_{i=1}{ e^{ x^l_i } } = \sum^n_{i=1}{x^e_i} }$ or $\displaystyle{ e^{\mu_0} = \frac{ \displaystyle{ \sum^n_{i=1}{x^e_i} }}{n} }$
 \item This result consistent with the relation $\lambda_0 = e^{-\mu_0}$ (QED)
\end{enumerate*}

MLE estimation in the case of samples coming from multiple random processes however is not easy to be found analytically, instead a gradient descent learning algorithm is proposed. But before coming to this issue we need to establish enough evidence that the given samples did not come from a single random process in other word they did came from multiple random process.

\subsection{The Distribution of Log-transformed Sample Variance: the case of two samples}

Consider two samples $x_1$, $x_2$ from a random process having exponential distribution $f_e(x) =  \lambda e^{- \lambda x} $. Then the values $y_1=\frac{x_1}{x_2}$ is a random variable that follows some distribution. We are going to look at joint distribution $f(x_1,x_2)$ and work through change of variable theorem. We have $f(x_1,x_2) = \lambda^2 e^{- \lambda (x_1 + x_2)}$. We will choose $y_1=\frac{x_1}{x_2}$ and $y_2=x_1+x_2$ as two new variables to change to, then appling the variable change theorem gives us $f(y_1,y_2) = f(x_1,x_2) / J_{det}$ where $J_{det}=\begin{vmatrix} \frac{\partial y_1}{\partial x_1} & \frac{\partial y_1}{\partial x_2} \\ \frac{\partial y_2}{\partial x_1} & \frac{\partial y_2}{\partial x_2} \end{vmatrix}$.

Since $y_1=\frac{x_1}{x_2}$, we have $\frac{\partial y_1}{\partial x_1} = 1/x_2$, $\frac{\partial y_1}{\partial x_2} = - \frac{x_1}{x_2^2}$. Similarly $y_2=x_1+x_2$, thus $\frac{\partial y_2}{\partial x_1}=\frac{\partial y_2}{\partial x_2}=1$. Then $J_{det}=\begin{vmatrix} \frac{\partial y_1}{\partial x_1} & \frac{\partial y_1}{\partial x_2} \\ \frac{\partial y_2}{\partial x_1} & \frac{\partial y_2}{\partial x_2} \end{vmatrix} = \begin{vmatrix} \frac{1}{x_2} & - \frac{x_1}{x_2^2} \\ 1 & 1 \end{vmatrix} = \frac{x_1 + x_2}{x_2^2}$.

Also as $y_1=\frac{x_1}{x_2}, y_2=x_1+x_2$ then $x_1 = y_1*x_2, x_1=y_2-x_2$, then $y_1*x_2=y_2-x_2$ or $x_2=\frac{y_2}{(y_1+1)},x_1=\frac{y_2*y_1}{(y_1+1)}$

Plug these results into variable change theorem $f(y_1,y_2) = \frac{f(x_1,x_2)}{J_{det}} = \frac{\lambda^2 e^{- \lambda (x_1 + x_2)}}{\frac{x_1 + x_2}{x_2^2}} = \frac{\lambda^2 e^{- \lambda (x_1 + x_2)} x^2_2}{x_1 + x_2} = \frac{\lambda^2 e^{- \lambda y_2} \frac{y_2^2}{(1 + y_1)^2}}{y_2}=\frac{y_2 \lambda^2 e^{- \lambda y_2}}{(1 + y_1)^2}$. Then $f(y_1)=\displaystyle{ \int_0^\infty {\frac{y_2 \lambda^2 e^{- \lambda y_2}}{(1 + y_1)^2}dy_2} }= \frac{1}{(1 + y_1)^2}\int_0^\infty {y_2 \lambda^2 e^{- \lambda y_2}dy_2}$.

Note that the PDF of Gamma distribution is $f(x \| k,\theta) = x^{k-1} \frac{e^{-x/\theta}}{\theta^k \Gamma(k)}$ where $\Gamma(k)=(k-1)!$ thus $f(x \| 2,1/ \lambda) = x \lambda^2 e^{-x \lambda}$. In other words, $f(x)=x \lambda^2 e^{-x \lambda}$ is the probability distribution function of $1 / \lambda$ scaled two-shaped Gamma distribution thus $F(x) = \displaystyle{ \int{x \lambda^2 e^{-x \lambda} dx } }$ is the cummulative distribution function of said distribution. Since Gamma distribution space is $(0,\infty)$ then $F(\infty)-F(0)=1$ or alternatively $\displaystyle{ \int_0^\infty{x \lambda^2 e^{-x \lambda} dx } }=1$

Thus we have proved the random variable $y_1=x_1/x_2$ follows PDF $f(y_1)=\frac{1}{(1 + y_1)^2} \displaystyle{ \int_0^\infty {y_2 \lambda^2 e^{- \lambda y_2}dy_2} } = \frac{1}{(1+y_1)^2}$ or CDF $F(y_1)=\displaystyle{ \frac{y_1}{1+y_1} }$

Now consider the log-transformed domain, $x^l_1=\ln(x_1),x^l_2=\ln(x_2)$ then $y^l=x^l_1-x^l_2=\ln(x_1)-\ln(x_2)=\ln(x_1/x_2)=\ln(y_1)$. That is in log-transformed domain, the distance between two sample is the log-transformed of the ratio between the corresponding samples and we can calculate the distribution of such random variable. Since $y^l=\ln(y_1)$ then $P(y^l<a)=P(y_1<e^a)$ thus the PDF $f_l(a)=\frac{\partial{P(y^l<a)}}{\partial{a}}=\frac{\partial{P(y_1<e^a)}}{\partial{e^a}}\frac{\partial{e^a}}{\partial{a}}$. Since $y_1$ follows a distribution with PDF $f(x)=\frac{\partial{P(y_1<x)}}{\partial{x}}=\frac{1}{(1+x)^2}$, then PDF $f_l(a)=\frac{e^a}{(1+e^a)^2}$ or CDF $F_l(a)=\displaystyle{ \frac{e^a}{1+e^a} }$

The variance of 2 sample in log-transformed domain is $v_l=(x_1 - x_2)^2=y_l^2$ then $P(v_l<a)=P(y_l<\sqrt{a})-P(y_l<-\sqrt{a})$. Then the variance follows the PDF $f(x)=\frac{\partial{P(v_l<x)}}{\partial{x}}=\frac{\partial{P(y_l<\sqrt{x})-P(y_l<-\sqrt{x})}}{\partial{\sqrt{x}}} \frac{\partial{\sqrt{x}}}{\partial{x}}=\frac{1}{2\sqrt{x}} ( \frac{e^{\sqrt{x}}}{(1+e^{\sqrt{x}})^2} + \frac{e^{-\sqrt{x}}}{(1+e^{-\sqrt{x}})^2} )$

Since the variance of 2 sample is bounded, the variance of 3 samples should be even tighter bounded

\subsection{The Distribution of Log-transformed Sample Variance: the case of three samples}

Consider three samples $x_1$, $x_2$, $x_3$ from a random process having exponential distribution $f_e(x) =  \lambda e^{- \lambda x} $. In log-transformed domain $l_i=\ln(x_i)$ we has proven that $y_i=l_i - l_{i+1}$ follows the distribution having CDF $F_l(y)=\displaystyle{ \frac{e^y}{1+e^y} }$ and PDF $f_l(y)=\displaystyle{ \frac{e^y}{(1+e^y)^2} }$

Consider samples $l_i$ the sample mean will be $\bar{l_i}=\displaystyle{ \frac{l_1+l_2+l_3}{3} } $ and the variance

\begin{eqnarray*}
var(l_i) 
	&=& \displaystyle{ \frac{(l_1- \bar{l_i})^2 + (l_2- \bar{l_i})^2 + (l_3- \bar{l_i})^2}{3} } \\
	&=& \displaystyle{  \frac{ ( \frac{2l_1-l_2-l_3}{3}) ^2 + ( \frac{2l_2-l_1-l_3}{3}) ^2 + ( \frac{2l_3-l_2-l_1}{3}) ^2}{3} } \\
	&=& \displaystyle{ \frac{6(l_1^2+l_2^2+l_3^2-l_1l_2-l_1l_3-l_2l_3)}{27} }
\end{eqnarray*}

Choose $t=\frac{(l_1-l_2)}{2}$, $u=\frac{(l_1+l_2)}{2}$, $v=\frac{(l_1^2+l_2^2+l_3^2-l_1l_2-l_1l_3-l_2l_3)}{3}$. Then Jacobian is

\begin{eqnarray*}
J_{det}
	&=& \begin{vmatrix} 
			\frac{\partial t}{\partial l_1} & \frac{\partial t}{\partial l_2} & \frac{\partial t}{\partial l_3}\\ 
			\frac{\partial u}{\partial l_1} & \frac{\partial u}{\partial l_2} & \frac{\partial u}{\partial l_3} \\
			\frac{\partial v}{\partial l_1} & \frac{\partial v}{\partial l_2} & \frac{\partial v}{\partial l_3} 
		\end{vmatrix} \\
	&=& \begin{vmatrix} 
			1/2 & -1/2 & 0 \\ 
			1/2 &  1/2 & 0 \\
			(2l_1-l_2-l_3)/3 & (2l_2-l_1-l_3)/3 & (2l_3-l_2-l_1)/3 
		\end{vmatrix} \\
	&=& \frac{(2l_3-l_2-l_1)}{3} 
		\begin{vmatrix} 
		 	1/2 & -1/2 \\ 
			1/2 & 1/2 \\ 
		\end{vmatrix} \\
	&=& \frac{ (2l_3-l_2-l_1)}{3 \cdot 2}
\end{eqnarray*}

Since  $t=\frac{(l_1-l_2)}{2}$, $u=\frac{(l_1+l_2)}{2}$, we have $l_1=u+t$ and $l_2=u-t$

\begin{eqnarray*}
3v
	&=& l_1^2+l_2^2+l_3^2-l_1l_2-l_1l_3-l_2l_3\\
	&=& l_3^2 - l_3(l_1+l_2)+ l_1^2+l_2^2-l_1l_2 \\
	&=& l_3^2 - 2u \cdot l_3+ (u+t)^2+(u-t)^2-(u+t)(u-t) \\
	&=& l_3^2 - 2u \cdot l_3+ u^2 + 3t^2 \\
0 	&=& l_3^2 - 2u \cdot l_3+ u^2 + 3t^2 -3v \\
\Delta 	&=& 4u^2 - 4 (u^2+3t^2-3v) \\
		&=& 4 (3v-3t^2) \\
l_3	&=& \frac{2u \pm \sqrt{\Delta}}{2} \\
	&=& u \pm \sqrt{3v-3t^2}
\end{eqnarray*}

Choose $l_3 = u + \sqrt{3v-3t^2}$, then $J_{det}=\frac{ (2l_3-l_2-l_1)}{2}=\sqrt{3v-3t^2}$. Plug these results into variable change theorem, noting that $f(l_i)=e^{ \left( l_i+\mu_0 - e^{l_i+\mu_0} \right)}$

\begin{eqnarray*}
f(t,u,v)
	&=&\frac{f(l_1,l_2,l_3)}{J_{det}} \\
	&=& \frac{e^{l_1+\mu_0-e^{l_1+\mu_0}}e^{l_2+\mu_0-e^{l_2+\mu_0}}e^{l_3+\mu_0-e^{l_3+\mu_0}}}{\sqrt{3v-3t^2}} \\
	&=& \displaystyle {\frac{e^{u+t+\mu_0-e^{(u+t+\mu_0)}}e^{u-t+\mu_0-e^{(u-t+\mu_0)}}e^{u + \sqrt{3v-3t^2}+\mu_0-e^{u + \sqrt{3v-3t^2}+\mu_0}}}{\sqrt{3v-3t^2}} } \\
	&=& \displaystyle { \frac{e^{\sqrt{3v-3t^2}}e^{3\mu_0}}{\sqrt{3v-3t^2}} e^{3u-e^{(u+\mu_0)}(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})}}
\end{eqnarray*}

\begin{eqnarray*}
f(v) 
	&=& \displaystyle{ \int_{t=-\infty}^{t=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}e^{3\mu_0}} }{ \sqrt{3v-3t^2} } \int_{u=-\infty}^{u=\infty}{e^{3u-e^{(u+\mu_0)}(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})} \, du}  \right] \, dt} } \\
\text{Consider} \\
f(u) 
	&=& \int_{u=-\infty}^{u=\infty}{e^{3u-e^ue^{\mu_0}(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})} \, du} \\
\text{Set } k
	&=&-(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})e^{\mu_0} \text{, and }e^u=\upsilon \text{,  } u=\ln(\upsilon) \text{ or } \frac{ \partial u }{ \partial \upsilon} = \frac{1}{\upsilon} \\
f(\upsilon)
	&=& \int_{\upsilon=0}^{\upsilon=\infty} { \frac{\upsilon^3 \cdot e^{k \cdot \upsilon}}{\upsilon}  \, d\upsilon} \\
	&=& \int_{\upsilon=0}^{\upsilon=\infty} { \upsilon^2 \cdot e^{k \upsilon} \, d\upsilon} \\
	&=& \frac{\upsilon^2 e^{k \upsilon}}{k} - \frac{2}{k}  \int_{\upsilon=0}^{\upsilon=\infty} { \upsilon e^{k  \upsilon} \, d\upsilon} \\
	&=& \frac{\upsilon^2 e^{k \upsilon}}{k} - \frac{2}{k}  \left(\frac{\upsilon e^{k \upsilon}}{k} - \frac{1}{k} \int_{\upsilon=0}^{\upsilon=\infty} { e^{k  \upsilon} \, d\upsilon} \right)  \\
	&=&\displaystyle{ \left \vert   \frac{\upsilon^2 e^{k \upsilon}}{k} - \frac{2}{k}  \left(\frac{\upsilon e^{k \upsilon}}{k} - \frac{1}{k} \frac{ e^{k  \upsilon}}{k}   \right) \right \vert_{\upsilon=0}^{\upsilon=\infty} }  \\
	&=&\displaystyle{ \left \vert \frac{e^{k \upsilon} (\upsilon^2k^2- 2k\upsilon + 2)}{k^3}   \right \vert_{\upsilon=0}^{\upsilon=\infty} }  \\
\lim_{\upsilon \rightarrow \infty}{\frac{e^{k \upsilon} (\upsilon^2k^2- 2k\upsilon + 2)}{k^3}} 
	&=& \lim_{\upsilon \rightarrow \infty}{\frac{e^{k \upsilon}}{\upsilon}} = 0 \text{ as } k<0 \\
\lim_{\upsilon \rightarrow 0}{\frac{e^{k \upsilon} (\upsilon^2k^2- 2k\upsilon + 2)}{k^3}}  
	&=& \frac{2}{k^3} \\
f(\upsilon) &=& \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3e^{3\mu_0}} \\
f(v) 
	&=& \displaystyle{ \int_{t=-\infty}^{t=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}}e^{3\mu_0} }{ \sqrt{3v-3t^2} } \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3e^{3\mu_0}}  \right] \, dt} } \\
	&=& \displaystyle{ \int_{t=-\infty}^{t=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}} }{ \sqrt{3v-3t^2} } \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3}  \right] \, dt} }  
\end{eqnarray*}

Set $t=\sqrt{v}\sin(x)$, with $-\pi/2 \leq x \leq \pi/2$, then $\frac{\partial{t}}{\partial{x}}=\sqrt{v}\cos(x)$, and $\sqrt{v-t^2}=\sqrt{v\cos^2(x)}=\cos(x)\sqrt{v}$

\begin{eqnarray*}
f(v) 
	&=& \displaystyle{ \int_{t=-\infty}^{t=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}} }{ \sqrt{3v-3t^2} } \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3}  \right] \, dt} }  \\
	&=& \displaystyle{ \int_{x=-\pi/2}^{x=\pi/2}{ \left[  \frac{e^{\sqrt{3v}\cos(x)} }{ \sqrt{3v} \cos(x)} \frac{2}{(e^{\sqrt{v}\sin(x)}+e^{-\sqrt{v}\sin(x)}+e^{\sqrt{3v}\cos(x)})^3}  \right] \sqrt{v}\cos(x) \, dx} }  \\
	&=& \displaystyle{ \frac{2}{\sqrt{3}} \int_{-\pi/2}^{\pi/2}{\frac{1}{\left( e^{\sqrt{v}\sin(x)}+e^{-\sqrt{v}\sin(x)}+e^{\sqrt{3v}\cos(x)} \right)^3 \left( e^{-\frac{\sqrt{3v}\cos(x)}{3}} \right)^3}\, dx} } \\
	&=& \displaystyle{ \frac{2 \sqrt{v}}{\sqrt{3}} \int_{-\pi/2}^{\pi/2}{\frac{1}{\left( e^{\sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3}}+e^{-\sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3}}+e^{\sqrt{3v}\cos(x)-\frac{\sqrt{3v}\cos(x)}{3}} \right)^3 }\, dx} } \\
\end{eqnarray*}

\begin{eqnarray*}
 \sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3} 
	&=& \sqrt{v} \frac{\sqrt{3} \sin(x) - \cos(x)}{\sqrt{3}} \\
	&=& \frac{2 \sqrt{v}}{\sqrt{3}} \sin(x-\pi/6)  \\
-\sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3} 
	&=&  \frac{2 \sqrt{v}}{\sqrt{3}} \sin(-x-\pi/6) \\ 
\sqrt{3v}\cos(x)-\frac{\sqrt{3v}\cos(x)}{3}
	&=& \frac{2 \sqrt{v}}{\sqrt{3}} \cos(x) \\
\sin(a)-\cos(b) 
	&=& -2 \sin(a/2-b/2-\pi/4) \sin(a/2+b/2-\pi/4) \\
\sin(x-\pi/6) - \cos(x) 
	&=& -2 \sin(-\pi/12 -\pi/4) \sin(x-\pi/12-\pi/4) \\
	&=& \sqrt{3}\sin(x-\pi/3) \\
\sin(-x-\pi/6)  - \cos(x) 
	&=& -2 \sin(-\pi/12-\pi/4) \sin(-x-\pi/12-\pi/4) \\
	&=& \sqrt{3}\sin(-x-\pi/3) \\
	&& e^{\sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3}}+e^{-\sqrt{v}\sin(x)-\frac{\sqrt{3v}\cos(x)}{3}}+e^{\sqrt{3v}\cos(x)-\frac{\sqrt{3v}\cos(x)}{3}}  \\
	&=& e^{\frac{2 \sqrt{v}}{\sqrt{3}} \sin(x-\pi/6)}+e^{\frac{2 \sqrt{v}}{\sqrt{3}} \sin(-x-\pi/6)}+e^{\frac{2 \sqrt{v}}{\sqrt{3}} \cos(x)} \\
	&=& k^{\cos(x)} \left( k^{\sin(x-\pi/6) - \cos(x)} + k^{\sin(-x-\pi/6)  - \cos(x) } + 1 \right) \\
	&=& k^{\cos(x)} \left( k^{\sqrt{3}\sin(x-\pi/3)} + k^{\sqrt{3}\sin(-x-\pi/3) } + 1 \right)
\end{eqnarray*}

\begin{eqnarray*}
f(v) 
	&=& \displaystyle{ \int_{t=-\infty}^{t=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}} }{ \sqrt{3v-3t^2} } \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3}  \right] \, dt} } \\
f(t) 
	&=& \displaystyle{ \int_{v=0}^{v=\infty}{ \left[  \frac{e^{\sqrt{3v-3t^2}} }{ \sqrt{3v-3t^2} } \frac{2}{(e^t+e^{-t}+e^{\sqrt{3v-3t^2}})^3}  \right] \, dv} }  \\
x 
	&=& e^{\sqrt{3v-3t^2}} \\
\frac{\partial{x}}{\partial{v}}
	&=& e^{\sqrt{3v-3t^2}} \frac{\partial{\sqrt{3v-3t^2}}}{\partial{v}} \\
	&=& e^{\sqrt{3v-3t^2}} \frac{1}{2\sqrt{3v-3t^2}} \frac{\partial{3v-3t^2}}{\partial{v}} \\
	&=& e^{\sqrt{3v-3t^2}} \frac{3}{2\sqrt{3v-3t^2}} \\
f(t) 
	&=& \displaystyle{ \int_{x=0}^{x=\infty}{ \left[ \frac{2}{3}  \frac{2}{(e^t+e^{-t}+x)^3}  \right] \, dx} }  \\
	&=& \left \vert - \frac{1}{(e^t+e^{-t}+x)^2} \right \vert_0^{\infty} \\
\lim_{x \rightarrow \infty}{ \frac{1}{(e^t+e^{-t}+x)^2} }
	&=& 0 \\
\lim_{x \rightarrow 0}{ \frac{1}{(e^t+e^{-t}+x)^2} }
	&=& \frac{1}{(e^t+e^{-t})^2} \\
	&=& \frac{e^{2t}}{(e^{2t}+1)^2} \\
\end{eqnarray*}

Choose $t=\frac{l_1-l_2}{2}$, $u=\frac{l_1+l_2}{2}$, $v=\frac{(l_1^2+l_2^2+l_3^2-l_1l_2-l_1l_3-l_2l_3)}{3}$. Then Jacobian is  $J_{det}=\frac{2l_3-l_1-l_2}{3}$. Choose the branch $l_3=u+\sqrt{3v-3t^2}$, then $J_{det}=\frac{\sqrt{v-t^2}}{\sqrt{3}}$. Thus  $f(v)=\displaystyle{ \int_{t=0}^{t=\infty}{\left[ 2\frac{2\sqrt{3}}{\sqrt{v-t^2}} \int_{u \in \Re}{\left[ \varphi(u-t)\varphi(u+t)\varphi(u+\sqrt{3v-3t^2})du \right]} dt \right]} }$  Here, a factor 2 appears to take both branches into account, and an extra factor 2 appears when using symmetry to restrict the integration domain to $x \geq y$ i.e. to $t \geq 0$, and $\varphi(x)=e^{x-e^x}$ \cite{Douillet_2009}

Consider variable $u=y_1-y_2$ we are going to proof that they follow a distribution PDF $f(u)$. Set $v=y_1+y_2$, then the Jacobian determinant $J_{det} 
	= \begin{vmatrix} \frac{\partial u}{\partial y_1} & \frac{\partial u}{\partial y_2} \\ \frac{\partial v}{\partial y_1} & \frac{\partial v}{\partial y_2} \end{vmatrix} 
	= \begin{vmatrix} 1 & -1 \\ 1 & 1 \end{vmatrix} 
	= 2
$. The joint distribution $f(y_1,y_2) 
	= \displaystyle{ \frac{e^{y_1}}{(1+e^{y_1})^2} \frac{e^{y_2}}{(1+e^{y_2})^2} }
	= \displaystyle{ \frac{e^{y_1+y_2}}{(1+e^{y_1}+e^{y_2}+e^{y_1+y_2})^2} }
$ being subjected to variable change theorem gives $f(u,v) 
	= \displaystyle{ \frac{e^{v}}{(1+e^{\frac{u+v}{2}}+e^{\frac{v-u}{2}}+e^{v})^2} \frac{1}{J_{det}} }
$ thus $f(u)
	= \displaystyle{ \int_{-\infty}^{\infty}{\frac{e^{v}}{2(1+e^{\frac{u+v}{2}}+e^{\frac{v-u}{2}}+e^{v})^2} dv} }
$.

Set $e^{\frac{v}{2}}=t$ then $v=2*\ln(t)$ thus $\displaystyle{ \frac{\partial{v}}{\partial{t}} = \frac{2}{t}}$. Change variable of the integral $f(u)
	= \displaystyle{ \int_{-\infty}^{\infty}{\frac{e^{v}}{2(1+e^{\frac{u+v}{2}}+e^{\frac{v-u}{2}}+e^{v})^2}  dv} }
	= \displaystyle{ \int_0^{\infty}{ \frac{t^2}{2(1+t(e^{\frac{u}{2}}+e^{\frac{-u}{2}}) + t^2)^2} \frac{2}{t} dt } }
	= \displaystyle{ \int_0^{\infty}{ \frac{t}{(1+t(k+\frac{1}{k}) + t^2)^2} dt } }
$ with $k=e^{\frac{u}{2}}$. Or $f(u)= \displaystyle{ k^2 \int_0^{\infty}{ \frac{x}{(xk^2+kx^2+k+x)^2} } }$. We are going to proof that $\displaystyle{ \int{ \frac{x}{(xk^2+kx^2+k+x)^2} } } = \displaystyle{ \frac{ \frac{(k^2-1)(xk^2+2k+x)}{xk^2+kx^2+k+x}}{(k^2-1)^3} + \frac{(1+k^2)\ln(\frac{kx+1}{k+x})}{(k^2-1)^3} }$, thus we are able to find the PDF $f(u)$.

We have $\displaystyle{ \frac{\partial{}}{\partial{x}} (\frac{xk^2+2k+x}{xk^2+kx^2+k+x}) }
	= \displaystyle{ \frac{ \frac{\partial{(xk^2+2k+x)}}{\partial{x}} (xk^2+kx^2+k+x) - \frac{\partial{(xk^2+kx^2+k+x)}}{\partial{x}} (xk^2+2k+x) }{(xk^2+kx^2+k+x)^2} }
	= \displaystyle{ \frac{ (1+k^2)(xk^2+kx^2+k+x) -  (xk^2+2k+x)(2kx+k^2+1)}{(xk^2+kx^2+k+x)^2} } 
	= \displaystyle{ \frac{(1+k^2)(kx^2-k)-2kx(xk^2+2k+x)}{(xk^2+kx^2+k+x)^2} }
	= \displaystyle{ \frac{kx^2-k + k^3x^2-k^3 -(2x^2k^3+4k^2x+2x^2k)}{(xk^2+kx^2+k+x)^2} }
	= \displaystyle{ \frac{ -(k +k^3+x^2k^3+4k^2x+x^2k)}{(xk^2+kx^2+k+x)^2} }$

We also have $\displaystyle{ \frac{\partial{}}{\partial{x}} (\ln(\frac{kx+1}{k+x})) }
	= \displaystyle{ \frac{\partial{(\ln(\frac{kx+1}{k+x}))}}{\partial{(\frac{kx+1}{k+x})}} \frac{\partial{(\frac{kx+1}{k+x})}}{\partial{x}} }
	= \displaystyle{ \frac{k+x}{1+kx} \frac{k(k+x)-(kx+1)}{(k+x)^2}}
	= \displaystyle{ \frac{k^2-1}{(1+kx)(k+x)} }$

Thus $\displaystyle{ \frac{ \frac{(k^2-1)(xk^2+2k+x)}{xk^2+kx^2+k+x}}{(k^2-1)^3} + \frac{(1+k^2)\ln(\frac{kx+1}{k+x})}{(k^2-1)^3} }
	 = \displaystyle{ \frac{\frac{ -(k +k^3+x^2k^3+4k^2x+x^2k)}{(xk^2+kx^2+k+x)^2} (k^2-1) + \frac{k^2-1}{(1+kx)(k+x)} (1+k^2)}{(k^2-1)^3} }
	 = \displaystyle{ \frac{-(k +k^3+x^2k^3+4k^2x+x^2k) + (1+k^2)(xk^2+kx^2+k+x)}{(k^2-1)^2 (xk^2+kx^2+k+x)^2} } 
	 = \displaystyle{ \frac{-(k +k^3+x^2k^3+4k^2x+x^2k) + (xk^2+kx^2+k+x) + (xk^4+k^3x^2+k^3+xk^2)}{(k^2-1)^2 (xk^2+kx^2+k+x)^2} } 
	 = \displaystyle{ \frac{-(2k^2x) + (x) + (xk^4)}{(k^2-1)^2 (xk^2+kx^2+k+x)^2} } 
	 = \displaystyle{ \frac{x(k^2-1)^2}{(k^2-1)^2 (xk^2+kx^2+k+x)^2} } 
	 = \displaystyle{ \frac{x}{(xk^2+kx^2+k+x)^2} } $. (QED)

To find $f(u)$ we consider 
\begin{eqnarray*}
	&&\displaystyle \lim_{x \to \infty,0} {\left[ \frac{ \frac{(k^2-1)(xk^2+2k+x)}{(xk^2+kx^2+k+x)}}{(k^2-1)^3} + \frac{(1+k^2)\ln \left(\frac{kx+1}{k+x} \right)}{(k^2-1)^3} \right]}  \\
	&=& \displaystyle \lim_{x \to \infty,0} { \left[ \frac{ \frac{(k^2-1)(xk^2+2k+x)}{(xk^2+kx^2+k+x)}}{(k^2-1)^3} \right] } + \lim_{x \to \infty,0} { \left[ \frac{(1+k^2)\ln \left(\frac{kx+1}{k+x} \right) }{(k^2-1)^3} \right] } \\
	&=& \displaystyle { \frac{1}{(k^2-1)^2} \lim_{x \to \infty,0} { \left[ \frac{(xk^2+2k+x)}{(xk^2+kx^2+k+x)}  \right] } + \frac{(1+k^2)}{(k^2-1)^3} \lim_{x \to \infty,0} { \left[ \ln\left(\frac{kx+1}{k+x} \right) \right] } }
\end{eqnarray*}
We have $ \displaystyle \lim_{x \to \infty} { \frac{(xk^2+2k+x)}{(xk^2+kx^2+k+x)} } = \lim_{x \to \infty} {\frac{k^2+1}{2kx+k^2+1}} = 0$ and $ \displaystyle \lim_{x \to \infty} {\ln(\frac{kx+1}{k+x})} = \ln(k)$,  $ \displaystyle \lim_{x \to 0} { \frac{(xk^2+2k+x)}{(xk^2+kx^2+k+x)} } = \frac{2k}{k} = 2$, $ \displaystyle \lim_{x \to 0} {\ln(\frac{kx+1}{k+x})} = \ln(\frac{1}{k})$

\begin{eqnarray*}
f(u)	&=& \displaystyle{ k^2 \int_0^{\infty}{ \frac{x}{(xk^2+kx^2+k+x)^2} } } \\
	&=& \displaystyle{ k^2 \left ( \frac{1}{(k^2-1)^2} \lim_{x \to \infty} { \frac{(xk^2+2k+x)}{(xk^2+kx^2+k+x)} } + \frac{(1+k^2)}{(k^2-1)^3} \lim_{x \to \infty} { \left[ \ln \left( \frac{kx+1}{k+x} \right) \right]} \right) } \\
	& & \displaystyle{ - k^2 \left (\frac{1}{(k^2-1)^2} \lim_{x \to 0} { \frac{(xk^2+2k+x)}{(xk^2+kx^2+k+x)} } + \frac{(1+k^2)}{(k^2-1)^3} \lim_{x \to 0} {\left[ \ln \left( \frac{kx+1}{k+x} \right) \right]} \right)   } \\
	&=&  \displaystyle{ k^2 \left[ \left( \frac{0}{(k^2-1)^2} + \frac{(1+k^2)}{(k^2-1)^3} \ln(k) \right) - \left(  \frac{2}{(k^2-1)^2} + \frac{(1+k^2)}{(k^2-1)^3} \ln(\frac{1}{k})\right) \right]}  \\
	&=& \displaystyle{ 2k^2 \left( \frac{(1+k^2)}{(k^2-1)^3} \ln(k) - \frac{1}{(k^2-1)^2} \right) } 
\end{eqnarray*}
Note that $k=e^{\frac{u}{2}}$, thus 
\begin{eqnarray*}
f(u)	&=& \displaystyle{ 2e^u \left( \frac{(1+e^u)}{(e^u-1)^3} \frac{u}{2} - \frac{1}{(e^u-1)^2} \right) } \\
	&=& \displaystyle{ e^u \left( \frac{(u+ue^u)}{(e^u-1)^3} - \frac{2(e^u-1)}{(e^u-1)^3} \right) }  \\
	&=& \displaystyle{ e^u \frac{(ue^u - 2e^u+u+2)}{(e^u-1)^3}  } 
\end{eqnarray*}

This $f(u)$ is found but is not consistent with Monte-Carlo simulation, the reasons it seems is because $y_1$ and $y_2$ is not independent, (their correlation is around 0.5!)

% We have $ \displaystyle{ \frac{\partial{\tan^{-1}(x)}}{\partial{x}} = \frac{1}{1+x^2}} $ then $
% \displaystyle{ \frac{\partial{\tan^{-1}(ax+b)}}{\partial{x}} 
% 	= \frac{\partial{\tan^{-1}(ax+b)}}{\partial{(ax+b)}} \frac{\partial{(ax+b)}}{\partial{x}} }
% 	= \frac{a}{1+(ax+b)^2} 
% $ thus $
% \displaystyle{ \frac{\partial{\tan^{-1}(\frac{2x+k}{\sqrt{4-k^2}})}}{\partial{x}} } 
% 	= \frac{\frac{2}{\sqrt{4-k^2}}}{1+(\frac{2x+k}{\sqrt{4-k^2}})^2} 
% 	= \frac{2}{\sqrt{4-k^2}} \frac{1}{\frac{4-k^2+(2x+k)^2}{4-k^2}}
% 	= \frac{2}{\sqrt{4-k^2}} \frac{4-k^2}{4+4kx+4x^2}
% 	= \frac{\sqrt{4-k^2}}{2(1+kx+x^2)}
% $
% 
% We have $\displaystyle{ \frac{\partial}{\partial{x}} (\frac{kx+2}{1+kx+x^2})  } 
% 	= \displaystyle{ \frac{ \frac{\partial{(kx+2)}}{\partial{x}}(1+kx+x^2) - \frac{\partial{(1+kx+x^2)}}{\partial{x}}(kx+2) }{(1+kx+x^2)^2} }	
% 	= \displaystyle{  \frac{k(1+kx+x^2) - (2x+k)(kx+2)}{(1+kx+x^2)^2} }
% 	= \displaystyle{  \frac{ (k+xk^2+kx^2) -  (2kx^2+4x+xk^2+2k)}{(1+kx+x^2)^2} }
% 	= \displaystyle{  - \frac{ (kx^2+4x+k)}{(1+kx+x^2)^2} }
% $
% 
% $\displaystyle{ \frac{\partial}{\partial{x}} ( \frac{kx+2}{1+kx+x^2} \frac{1}{k^2-4} -  \tan^{-1}(\frac{2x+k}{\sqrt{4-k^2}}) \frac{2k\sqrt{4-k^2}}{(k^2-4)^2} )  } $ 
% $
% 	= \displaystyle{ - \frac{ (kx^2+4x+k)}{(1+kx+x^2)^2} \frac{1}{k^2-4} -  \frac{\sqrt{4-k^2}}{2(1+kx+x^2)} \frac{2k\sqrt{4-k^2}}{(k^2-4)^2} }
% $

\begin{listing}
 \caption{Monte-Carlo simulation for training }
 \label{code:training_monte_carlo}
\begin{verbatimtab}
function bdd()

[X Y] = monte_carlo_simulation(1000);
%plot(X,Y, 'r');
hold on;

P = exp(X);
Y0 = exp(X-P);
%Y0 = X .* X;
%Y0 = Y0 .* exp(X-P);
plot(X,Y0, 'b-');

%legend('Simulation','Theoretical','Location','NorthWest');

% Processing points
P = [-6 -5.8 -4 -3 -2 -0.3 -0.1 0.1 0.3 1.6 1.8 2];
for i=1:length(P)-1
    step(i)=P(i+1)-P(i);
end

%M=[1 1 1 1 1 1 1 1 1];
M = ones(1, length(P));

% partition simulated data by Processing Points
t = [X P];
t = sort(t);
t2 = ismember(t,P);
t2 = find(t2==1);

% X axis
X_Cell = cell(1, length(t2)+1);
X_Cell(1) = {t(1:t2(1)-1)};
X_Cell(length(t2)+1) = {t(t2(length(t2))+1:length(t))};
for i=2:length(t2)
    X_Cell(i)={t( t2(i-1)+1 : t2(i)-1 )};
end

% Y axis
Y_Cell = cell(1, length(X_Cell));
for i=1:length(X_Cell)
    Y_Cell(i)={Y(find(ismember(X,X_Cell{i})==1))'};
end

% Calculate membership values
Pl_cell = cell(1, length(step));
Pu_cell = cell(1, length(step));
for i=1:length(step)
    Pl_cell(i) = {1 - (X_Cell{i+1}   -  P(i))/step(i)};
    Pu_cell(i) = {1 - (P(i+1) -  X_Cell{i+1})/step(i)};
end

%M=[1 1 1];

%Calculate Output
O_Cell = cell(1, length(X_Cell));
O_Cell(1) = {M(1)};
for i=1:length(step)
    O_Cell(i+1) = {Pl_cell{i} * M(i) + Pu_cell{i} * M(i+1)};
end
O_Cell(length(X_Cell)) = {M(length(M))};

%Calculate difference & perf index
E_Cell = cell(1, length(X_Cell));
pi = 0;
for i=1:length(X_Cell)
    E_Cell(i) = {Y_Cell{i} - O_Cell{i}};
    pi = pi + sum (E_Cell{i} .* E_Cell{i});
end
pi

%back propagate error
El_cell = cell(1, length(step));
Eu_cell = cell(1, length(step));
for i=1:length(step)
    El_cell(i) = {Pl_cell{i} .* E_Cell{i+1}};
    Eu_cell(i) = {Pu_cell{i} .* E_Cell{i+1}};
end

%Caculate update rule
U(1) =  (sum(E_Cell{1}) + sum(El_cell{1})) / (length(X_Cell{1}) + length(X_Cell{2})) ;
for i=2:length(step)
    U(i) = (sum(Eu_cell{i-1}) + sum(El_cell{i})) / (length(X_Cell{i}) + length(X_Cell{i+1}));
end
U(length(M)) = (sum(Eu_cell{length(step)}) + sum(E_Cell{length(E_Cell)}))  / (length(X_Cell{length(X_Cell)-1}) + length(X_Cell{length(X_Cell)}));

M = M + U;

for i = 1:20
    O_Cell = cell(1, length(X_Cell));
    O_Cell(1) = {M(1)};
    for i=1:length(step)
        O_Cell(i+1) = {Pl_cell{i} * M(i) + Pu_cell{i} * M(i+1)};
    end
    O_Cell(length(X_Cell)) = {M(length(M))};

    E_Cell = cell(1, length(X_Cell));
    pi = 0;
    for i=1:length(X_Cell)
        E_Cell(i) = {Y_Cell{i} - O_Cell{i}};
        pi = pi + sum (E_Cell{i} .* E_Cell{i});
    end
    pi

    El_cell = cell(1, length(step));
    Eu_cell = cell(1, length(step));
    for i=1:length(step)
        El_cell(i) = {Pl_cell{i} .* E_Cell{i+1}};
        Eu_cell(i) = {Pu_cell{i} .* E_Cell{i+1}};
    end

    U(1) =  (sum(E_Cell{1}) + sum(El_cell{1})) / (length(X_Cell{1}) + length(X_Cell{2})) ;
    for i=2:length(step)
        U(i) = (sum(Eu_cell{i-1}) + sum(El_cell{i})) / (length(X_Cell{i}) + length(X_Cell{i+1}));
    end
    U(length(M)) = (sum(Eu_cell{length(step)}) + sum(E_Cell{length(E_Cell)}))  / (length(X_Cell{length(X_Cell)-1}) + length(X_Cell{length(X_Cell)}));

    M = M + U;
end

%f=figure();
hold on;

O_Cell = cell(1, length(X_Cell));
O_Cell(1) = {M(1)};
for i=1:length(step)
    O_Cell(i+1) = {Pl_cell{i} * M(i) + Pu_cell{i} * M(i+1)};
    plot(X_Cell{i+1},O_Cell{i+1},'g');
end

function [X Y] = monte_carlo_simulation(size)
%size = 100;
re = normrnd(0, 1/sqrt(2), [size*size 1]);
im = normrnd(0, 1/sqrt(2), [size*size 1]);
I = re .* re + im .* im;
L = log(I);

step = ( max(L)-min(L) ) / size;
X = [min(L):step:max(L)];
Y = histc(L,X);
Y = Y / (size * size);

%rescale among simulations Y is per unit length of X axis
Y = Y * length(X) / (max(X)-min(X));

%T = X .* X;
%Y = T .* Y';
%Y = Y';
\end{verbatimtab}
\end{listing}

\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References}
\bibitem{Douillet_2009} P.L. Douillet, \emph{Sampling Distribution Of The Variance}, Online; accessed 09-Feb-2010, available at 
\url{http://www.douillet.info/~douillet/publications/wsc09/wsc09.pdf}
\end{thebibliography}

\PrintIndex

\StopEventually

### 2013-03-01 build.sh

@@ -1,0 +1,6 @@
+latex -interaction=nonstopmode thesis.tex
+bibtex thesis
+latex -interaction=nonstopmode thesis.tex
+#makeindex thesis.nlo -s nomencl.ist -o thesis.nls
+#latex -interaction=nonstopmode thesis.tex
+

### 2013-03-01 clean.sh

@@ -1,0 +1,6 @@
+mv thesis.tex b.thesis.tex
+mv thesis.bib b.thesis.bib
+rm thesis.*
+mv b.thesis.tex thesis.tex
+mv b.thesis.bib thesis.bib
+

### 2013-03-01 paper_dev/build.sh

@@ -1,0 +1,5 @@
+latex -interaction=nonstopmode 'article.tex'
+bibtex article
+latex -interaction=nonstopmode 'article.tex'
+#xdvi article.dvi
+

### 2013-03-01 paper_dev/clean.sh

@@ -1,0 +1,6 @@
+#!/bin/bash
+cp article.tex b.article.tex
+cp article.bib b.article.bib
+rm article.*
+mv b.article.tex article.tex
+mv b.article.bib article.bib 

### 2013-04-22 0_frontmatter/abstract.tex
added 201304_Apr22

@@
 
-Put your abstract or summary in 0\_frontmatter/abstract.tex.
+In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
+As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
+POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
+Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
+
+With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
+The SAR data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
+Under this condition, it is very important to understand the statistical models for SAR data.
+It is these models that form the foundation for different SAR data processing techniques,
+  for example speckle filtering, target detection, image segmentation, and other clustering, classification techniques.
+Central to these machine learning or signal processing algorithms is the need for consistent discrimination measures which are derived from the statistical models.
+
+While the statistical models for homogeneous SAR areas have long been developed and widely used,
+  in extending the model toward heterogeneous images, the impact of the heteroskedastic property in these models has virtually been ignored.
+Specifically the concept of distance as a measure of dis-similarity is seriously flawed,
+  as it is widely known that ratio offers a better discrimination measure for SAR \cite{Rignot_1993_TGRS_896}.
+This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
+Within this log-transformed domain, a few consistent measures of distance is proposed. 
+In a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtractive distance.
+
+In extending our statistical understanding of SAR data towards multi-dimensional POLSAR data, an important issue needs to be addressed.
+The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
+While different statistical models have been developed for different POLSAR observables,
+  for a statistical model to be useful, scalar discrimination measures need to be derived from.
+Thus on the one hand, practical application for POLSAR data processing requires the measure to be scalar, consistent and preferably homoskedastic. % on the one hand.
+On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
+
+In this thesis, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
+The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario, the determinant then is transformed into the standard SAR intensity.
+Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
+And since POLSAR can be viewed as a multi-dimensional extension of SAR, the thesis describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
+%Subsequently logarithmic transformation is investigated for this generalized SAR model,
+%  which lead to the proposal for several linear and additive measures of distance for POLSAR.
+
+%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
+In short, to address the dual-problem described above,
+  this thesis proposes several scalar, additive and homoskedastic measures of distance for the multi-dimensional, multiplicative and heteroskedastic POLSAR data. 
+%The proposed statistical models and the homoskedastic measures of distance for POLSAR bring about a couple of benefits. 
+There are a couple of benefits in using these homoskedastic measures of distance for (POL)SAR.
+First, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear nature of digital imagery.
+Second, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss-Markov theorem is again applicable,
+  the use of Mean Squared Error (MSE) as universal objective function deserves to be reviewed. % as a reliable objective function / criteria for (POL)SAR estimators.
+%This may open up a number of different research directions for future studies of (POL)SAR.
+As example applications of how these statistical models and distance measures,
+  a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
 

### 2013-04-22 1_introduction/introduction.tex
added 201304_Apr22

@@
 
-% the code below specifies where the figures are stored
-%\ifpdf
-%    \graphicspath{{1_introduction/figures/PNG/}{1_introduction/figures/PDF/}{1_introduction/figures/}}
-%\else
-%    \graphicspath{{1_introduction/figures/EPS/}{1_introduction/figures/}}
-%\fi
-
-% ----------------------------------------------------------------------
-%: ----------------------- introduction content ----------------------- 
-% ----------------------------------------------------------------------
-
-Univariate SAR and multi-variate POLSAR data are multiplicative and heteroskedastic.
-By definition, heteroskedastic noised data has its variance, and correspondingly its substractive distances,
-  dependent on the main signal.
-In another line of research, log transformation has been shown
-  to convert the multiplicative nature of SAR data into a more familiar additive nature.
-We hypothesize that   
-  log-transformation also offers several consistent measures of distance in heteroskedastic SAR and POLSAR data.
-This thesis aims to investigate and validate that hypothesis.
-
-In this chapter: the main research problem and the corresponding hypothesis are explicitly stated.
-The methodology section explains how the results are obtained and analyzed.
-Contributions to advance theoretical knowledge are illustrated.
-Towards the end of the thesis, an application illustrate how the theoretical results can be applied in future research and development activities.
-
-%: ----------------------- HELP: latex document organisation
-% the commands below help you to subdivide and organise your thesis
-%    \chapter{}       = level 1, top level
-%    \section{}       = level 2
-%    \subsection{}    = level 3
-%    \subsubsection{} = level 4
-% note that everything after the percentage sign is hidden from output
-
-	\section{Background Context and the Motivation to Study}
-
-%Advantages of SAR in remote sensing paragraph (page 3)
 Synthetic Aperture Radar can soon become the preferred choice for
@@
 
-EM wave polarization and polarimetric SAR paragraph (page 3)
-
-A paragraph about partial polsar and the extension from (page 3)
-
-Problem: speckle in SAR and POLSAR, especially its heteroskedastic nature. (new)
-
-The motivation then is to provide a probably better understanding about the statistics of speckle. (new)
-
-For SAR data (page 4)
-
-For partial POLSAR data (new)
-
-For full polsar data (new)
-
-The purpose of this section is to illustrate the importance of a computational framework needed in the interpretation and processing targets' stochastic polarimetry signatures. 
-%This section start by describing the recent focus of space technology in earth observational remote sensing.
 As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
@@
 Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
-The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.
+%The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.
 
-%%TODO: SWITCH IMAGES: 24 lines
-%\begin{figure}[h!]
-%\centering
-%	\subfloat[Optical Colour Image]{
-%		 \epsfxsize=1.75in
-%		 \epsfysize=1.75in
-%		 \epsffile{images/20100502_mris_clipped.eps} 	
-%		 \label{Original}
-%	} 
-%	\hfill
-%	\subfloat[Optical Gray level image]{
-%		 \epsfxsize=1.75in
-%		 \epsfysize=1.75in
-%		\epsffile{images/20100502_mris_clipped_gray.eps}
-%		 \label{}
-%	}
-%	\hfill
-%	\subfloat[Speckled SAR image]{
-%		 \epsfxsize=1.75in
-%		 \epsfysize=1.75in
-%		 \epsffile{images/20100502_sar.eps} 	
-%		 \label{Original}
-%	} 
-%\caption{Speckle phenomena in SAR data}
-%\label{fig:sar_speckle_wrt_optical}
-%\end{figure}
+\section{The Research Question and the Motivation to Study}
+
+Univariate SAR and multi-variate POLSAR data are multiplicative and heteroskedastic.
+By definition, heteroskedastic noised data has its variance, and correspondingly its substractive distances,
+  dependent on the main signal.
+In another line of research, log transformation has been shown
+  to convert the multiplicative nature of SAR data into a more familiar additive nature.
+We hypothesize that   
+  log-transformation also offers several consistent measures of distance in heteroskedastic SAR and POLSAR data.
+This thesis aims to investigate and validate that hypothesis.
+
+In this chapter: the main research problem and the corresponding hypothesis are explicitly stated.
+The methodology section explains how the results are obtained and analyzed.
+Contributions to advance theoretical knowledge are illustrated.
+Towards the end of the thesis, an application illustrate how the theoretical results can be applied in future research and development activities.
+
+Problem: speckle in SAR and POLSAR, especially its heteroskedastic nature. (new)
+
+The motivation then is to provide a probably better understanding about the statistics of speckle. (new)
 
@@
 Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.
-As the additive noise PDF in log-domain has been worked out, we hypothesize that the true back-scattering coefficient PDF, also in log-domain, can be estimated through regularized deconvolution algorithms.
-If an algorithm could be designed to estimate such PDF, we believe this would present an improvement for a whole class of speckle filters, namely the Maximum-A-Priori (MAP) class, which up to now, still assumes the true PDF will follow certain known fixed distributions.
-%It is hoped that with the true PDF now being estimatable from the data itself, a better speckle filtering algorithm, in log-transformed domain, can be developed.
 
-For multi-channel SAR data, as reviewed in Chapter 2, speckle filtering for the off-diagonal element $S_hS_v^*$ of the covariance matrix is still an open question.
-Our observation has been that these elements are also available in dual-polarization SAR data, they specifically are part of Stokes parameters.
-As mentioned earlier, Stokes parameters have been largely ignored in polarimetric literature, until recently asserted again by Raney in 2006 \cite{Raney_2006_IGARSS}.
-Mathematically, Stokes parameters can be written as:
-\begin{equation}
-S = 
-\left(
-	\begin{array} {c}
-		S_hS_h + S_vS_v \\
-		S_hS_h - S_vS_v \\
-		2 \Re{(S_hS_v^*)} \\
-		2 \Im{(S_hS_v^*)}
-	\end{array}
-\right)
-= 
-\left(
-	\begin{array} {c}
-		S_hS_h + S_vS_v \\
-		S_hS_h - S_vS_v \\
-		S_+S_+ - S_-S_- \\
-		S_lS_l - S_rS_r
-	\end{array}
-\right)
-\end{equation}
-We have evidence, and hypothesize that $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ will have the same physical and statistical properties as the normal $S_hS_h$, $S_vS_v$.
-If our hypothesis can be proven rigorously, it may then be possible to build and validate a statistical model for all elements in the covariance matrix of Polarimetric SAR data, namely $S_hS_h$, $S_vS_v$, $\Re{( S_hS_v^*)}$, $\Im{( S_hS_v^* )}$.
-Also, speckle filtering on off-diagonal elements can be carried out using techniques, that were originally developed for single-channel SAR data, and up to now is only applicable to the diagonal elements of the covariance matrix.
+%\subsection{The Research Questions}
 
-For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
-We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
-Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
-Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
-Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
+Figure 
+	\ref{fig:residual_as_noise} 
+shows that: when compared with optical remote sensing images, SAR data suffers from serious degradation.
+%SAR data suffers from stochastic speckle phenomena, which poses numerous challenges in human capabilities of understanding SAR images.
+%Years of research in SAR signal processing has resulted in various speckle filters, all of which aims to produce better visually de-speckled gray images from the degraded SAR data.
+The degraded SAR data almost invariably requires a treatment of speckle filtering to yield more comprehensible images.
+Recent advances in Polarimetric SAR (POLSAR) have produced multiple channels of SAR data, which are conceptually similar to the multiple channels found in colourful optical images.
+However, the stochastic effects of speckle on multivariate and correlated data is ever more eminent.
+The key proposed research question is how to reconstruct clean, colorful visualization of Polarimetric Information from the new but speckled PolSAR satellites.
+Towards the end of the research project, an optional extended question shall be how this extra de-speckled polarimetric information may help in the tasks of target detection and classification.
+
+The main research question is conceptually divided into the following subsidiary questions to investigate:
+% and project phases include. 
+%1. How to simulate SAR and Polarimetric SAR data (quick pass, no lit review)
+\begin{enumerate}
+\item For single channel SAR data, the main aim would be how best to produce and quantitatively evaluate the de-speckled gray images. 
+The main contributions could be that: for the first time, the PDF for the underlying back-scattering coefficient appears to be estimate-able, at least in the log-transformed domain. 
+It is hoped this new knowledge may help in developing better speckle filters, especially those filters of \textit{Maximum a Posteriori} (MAP) nature.
+Another possible contribution could be: how the homoskedasticity in the log-transformed domain could help to consistently evaluate the performance of different speckle-filters being applied on heterogeneous spatial variations.
+%2.
+how the PDF of underlying back-scattering coefficient, in the log-domain, could be estimated and how this could help in improving the performance of the Maximum A Posteriori class of speckle-filters.
+%The topic and the concept itself is a new topic
+\item For multi-channel SAR data, the main aim would be to produce a smoothed and colourful visualisation of Polarimetric information. 
+The main contributions would be a methodology to extends the results of single-channel SAR speckle filtering towards the issue of estimating the off-diagonal elements in polarimetric covariance matrix.
+Another fundamental contribution could be: how to model, simulate and visualize the multivariate and correlated channels in POLSAR data.
+\item The third portion of this project is to investigate how full polarimetric information could be reconstructed from partial polarimetry modes. 
+The main aim of this section is to fill the gap between practical dual-polarimetric implementations and theoretical established full polarimetric results. 
+%The practical application is synchronized with current satellite hardware deployments and trade-offs.
+\item An optional collaborative portion is to investigate how the extra information in different polarimetric modes may help in the task of target detection and classification. 
+The main aim of this stage is to demonstrate the capability of (partial) polarimetric information over traditional single-channel SAR data.
+%and also to evaluate the trade-off between higher resolution offered by partial polarimetric architecture and the more complete full polarimetric mode.
+%Algorithms may have been and will also be proposed to tackle these issues, but the need to evaluate the algorithms requires rigorious ground-truthed data.
+\end{enumerate}
+
+%For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
+%We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
+%Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
+%Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
+%Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
 %Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.
@@
 
-Copy the objectives (page 6)
-
-copy the benefits (page 6)
-
-\subsection{Objectives and Contributions}
+\subsection{The Research Objectives}
 
@@
 As a testament on the effectiveness of this research, the work discussed in this report was published as two separate papers in 2010, at ISCCSP\cite{Le_2010_ISCCSP} and ACRS\cite{Le_2010_ACRS}.
-
-\subsection{The Research Questions}
-
-Figure 
-	\ref{fig:residual_as_noise} 
-shows that: when compared with optical remote sensing images, SAR data suffers from serious degradation.
-%SAR data suffers from stochastic speckle phenomena, which poses numerous challenges in human capabilities of understanding SAR images.
-%Years of research in SAR signal processing has resulted in various speckle filters, all of which aims to produce better visually de-speckled gray images from the degraded SAR data.
-The degraded SAR data almost invariably requires a treatment of speckle filtering to yield more comprehensible images.
-Recent advances in Polarimetric SAR (POLSAR) have produced multiple channels of SAR data, which are conceptually similar to the multiple channels found in colourful optical images.
-However, the stochastic effects of speckle on multivariate and correlated data is ever more eminent.
-The key proposed research question is how to reconstruct clean, colorful visualization of Polarimetric Information from the new but speckled PolSAR satellites.
-Towards the end of the research project, an optional extended question shall be how this extra de-speckled polarimetric information may help in the tasks of target detection and classification.
-
-The main research question is conceptually divided into the following subsidiary questions to investigate:
-% and project phases include. 
-%1. How to simulate SAR and Polarimetric SAR data (quick pass, no lit review)
-\begin{enumerate}
-\item For single channel SAR data, the main aim would be how best to produce and quantitatively evaluate the de-speckled gray images. 
-The main contributions could be that: for the first time, the PDF for the underlying back-scattering coefficient appears to be estimate-able, at least in the log-transformed domain. 
-It is hoped this new knowledge may help in developing better speckle filters, especially those filters of \textit{Maximum a Posteriori} (MAP) nature.
-Another possible contribution could be: how the homoskedasticity in the log-transformed domain could help to consistently evaluate the performance of different speckle-filters being applied on heterogeneous spatial variations.
-%2.
-how the PDF of underlying back-scattering coefficient, in the log-domain, could be estimated and how this could help in improving the performance of the Maximum A Posteriori class of speckle-filters.
-%The topic and the concept itself is a new topic
-\item For multi-channel SAR data, the main aim would be to produce a smoothed and colourful visualisation of Polarimetric information. 
-The main contributions would be a methodology to extends the results of single-channel SAR speckle filtering towards the issue of estimating the off-diagonal elements in polarimetric covariance matrix.
-Another fundamental contribution could be: how to model, simulate and visualize the multivariate and correlated channels in POLSAR data.
-\item The third portion of this project is to investigate how full polarimetric information could be reconstructed from partial polarimetry modes. 
-The main aim of this section is to fill the gap between practical dual-polarimetric implementations and theoretical established full polarimetric results. 
-%The practical application is synchronized with current satellite hardware deployments and trade-offs.
-\item An optional collaborative portion is to investigate how the extra information in different polarimetric modes may help in the task of target detection and classification. 
-The main aim of this stage is to demonstrate the capability of (partial) polarimetric information over traditional single-channel SAR data.
-%and also to evaluate the trade-off between higher resolution offered by partial polarimetric architecture and the more complete full polarimetric mode.
-%Algorithms may have been and will also be proposed to tackle these issues, but the need to evaluate the algorithms requires rigorious ground-truthed data.
-\end{enumerate}
 
@@
 
-\subsubsection{Theory Development and Research Strategy}
-For single channel SAR data, we propose the use of a log transform to evaluate speckle filter's performance. 
-We have proved that homoskedasticity property is indeed manifested in the log-domain.
-The traditional performance index in comparing speckle filters, i.e.
-the Equivalent Number of Looks (ENL), has also been shown to be related and calculable from the standard Mean Squared Error (MSE) inside the log-domain.
-We are working to prove that, with the homoskedastic property asserted, the universal Mean Squared Error can be a good performance indicator, even on heterogeneous spatial variations.
-
-Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able.
-In figure 
-	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
-the underlying single channel gray image histogram is presented along with the noise PDF, in the log-transformed domain. 
-As the noise is additive, it is expected that the noise PDF will act as a point spread function.
-This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
-This fact is evidenced in figure 
-	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
-where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
-We hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods.
-We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.
-
-\begin{figure}[h!]
-\centering
-	\subfloat[Original image's histogram and PSF]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
- 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
-		 \label{fig:noise_pdf_as_psf:conv_inputs}
-	} 
-	\hfill
-	\subfloat[Convoluted and speckled image histogram]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
-		 \label{fig:noise_pdf_as_psf:conv_output_observable}
-	}
-\caption{Observable convolution of PSF}
-\label{fig:noise_pdf_as_psf}
-\end{figure}
-
-For multi-channel SAR data, we focus on partial polarimetric SAR satellite data.
-Attempts have been made to model the data, especially the off-diagonal covariance matrix elements, i.e. $S_hS_v^*$.
-However, the models are overly complicated which made proposed PolSAR speckle suppression algorithms became overly complex (see polarimetric data modelling section in Chapter 2).
-We preferred an alternative approach.
-We propose to transform the polarization basis of dual-polarized SAR data to help estimate this element.
-
-We first pick up a recent revelation by Raney, 2006 \cite{Raney_2006_IGARSS}, that the back scattering waves' polarization captured in dual-pol data can be completely described using Stokes parameters.
-%From the usually given pairs of $S_h$ and $S_v$, Raney has shown that Stokes parameters can be computed.
-Furthermore, Stokes parameters can be measured in multiple polarization basis, which can also be synthesized from the given data (see polarization basis transform section in Chapter 2).
-%Both transformations, i.e. from $\{h,v\}$ to circular basis $\{l,r\}$ and from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ modes, are special cases of the transformation formula.
-That is:
-	the measured signal at $\pi/4$ linear polarizer as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
-	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
-	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
-	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
-
-The Stokes vectors, when aligned at these transformed projections are given by the following well-known equation:
-\begin{equation}
-S_t = \left(
-\begin{array}{c}
- |\xi_h|^2 + |\xi_v|^2 \\
- |\xi_h|^2 - |\xi_v|^2 \\
- 2 \Re( \xi_h \xi_v^* ) \\
- 2 \Im( \xi_h \xi_v^* ) 
-\end{array}
-\right)
-= \left(
-\begin{array}{c}
- |\xi_+|^2 + |\xi_-|^2 \\
- -2 \Re( \xi_+^* \xi_- ) \\
- |\xi_+|^2 - |\xi_-|^2 \\
- 2 \Im( \xi_+^* \xi_- ) 
-\end{array}
-\right)
-= \left(
-\begin{array}{c}
- |\xi_l|^2 + |\xi_r|^2 \\
- 2 \Re( \xi_l^* \xi_r ) \\
- -2 \Im( \xi_l^* \xi_r ) \\ 
- |\xi_l|^2 - |\xi_r|^2 
-\end{array}
-\right)  
-\end{equation}
-
-Evidently, the real and imaginary parts of $S_hS_v^*$ is closely related to Stokes Parameters.
-Specifically they may be considered as the subtraction of two random SAR intensity variables, e.g., $|S_l|^2 - |S_r|^2$. 
-%Since ShSh is exponential this can be calculated through convolutions, if each channels are independent. 
-%Laplace distribution is the difference between two identical exponential distributions. 
-For the same traditional reasoning of $|S_h|^2$ and $|S_v|^2$, we hypothesize that all the four intensities calculated from the transformation of polarization basis, i.e., $|S_+|^2$, $|S_-|^2$, $|S_l|^2$, $|S_r|^2$, follow negative exponential distributions.
-The hypothesis is supported by our preliminary experiment results, where we synthesize the basis transformed intensity from real-measured polarimetric data.
-It then follows that $S_hS_v^*$ can be despeckled by independently de-speckling the four synthesized intensities.
-Read chapter 4 for our work in progress in single-channel SAR speckle filtering.
-We hope to go further speculating that: the speckle-filtering methodologies in dual-polarization SAR data is extensible to full polarimetric SAR data.
-
 %In fact, we could build and validate statistical model for all elements of POLSAR data.
@@
 
-To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
-The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
-Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
-Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
-The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).
+%To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
+%The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
+%Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
+%Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
+%The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).
 

### 2013-04-22 2/literature_review.tex
added 201304_Apr22

@@
 
-\section{The nature of Polarimetric SAR: EM Wave Polarization}
-
-Remote sensing introduction paragraph (section 2.1.1)
-
-SAR introduction paragraph (section 2.1.2)
-
-EM Wave polarization (Maxwell law leads to wave equations section 2.1.3.1, choice of origin which leads to polarization basis change eq 2.22)
-
-SAR Polarimetry: and SAR as a special case of POLSAR (send and receive polarizations: 2.1.3.5)
-
-Full Polarimetric SAR and target polarimetric response (also 2.1.3.5)
-
-Partial Polarimetric SAR and EM wave polarization (2.1.3.4)
-
-SAR stochastics nature (new)
-
-\subsection{Representations of EM Wave Polarizations (Linear, Circular ...)}
-
-\subsubsection{Plane wave and solutions to the EM Wave equations}
-
-The general solution to the PDE EM wave equation is a linear superposition of waves each having the form
-\begin{equation}
-\vec{E}(\vec{r},t)=g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
-\end{equation} 
-and
-\begin{equation}
-\vec{B}(\vec{r},t)=g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
-\end{equation}
-where
-	$g$ is any well-behaved function of a dimensionless argument $\phi$,
-	%for virtually any well-behaved function g of dimensionless argument φ, where
-	$\omega$ is the angular frequency (in radians per second), and
-	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).
-
-%Although the function $g$ can be, and often is, a monochromatic sine wave, it does not have to be. 
-%In practice, $g$ cannot have infinite periodicity because any real electromagnetic wave must always have a finite extent in time and space. 
-%Thus based on the theory of Fourier decomposition, a real wave must consist of the superposition of an infinite set of sinusoidal frequencies.
-In addition to the relations above, the wave vector and the angular frequency are not independent; they must adhere to the dispersion relation:
-\begin{equation}
-k = |\vec{k}| = \frac{\omega}{c} = \frac{2\pi}{\lambda}
-\end{equation}
-where 
-	$k$ is the wave number and $\lambda$ is the wavelength.
-
-Since any real wave can be considered as a superpositions of several sinusoidal waves, the simplest solution to consider for the EM Wave equations is:
-\begin{equation}
-\vec{E}(\vec{r},t)= \Re \left( \vec{E}(\vec{r}) e^{i \omega t} \right)
-\end{equation}
-where
-	$\omega = 2 \pi f$ is the angular frequency,
-	$f$ is the wave frequency.
-Assuming the most common case of EM waves travelling in a planar fashion, which is a good approximation of most light waves. 
-For plane waves Maxwell's equations, specifically Gauss's laws, imposes a transversality requirement that the electric and magnetic field be perpendicular to the direction of propagation and to each other.
-Conventionally, when considering polarization, the electric field vector  is described and the magnetic field is ignored since it is perpendicular  to the electric field and proportional to it. 
-%Since the magnetic field is dependent on the electric field, 
-Thus it is sufficient to just consider electric field, which equals:
-\begin{equation}
-\vec{E}(\vec{r}) = \vec{E^0} e^{-i \vec{k} \cdot \vec{r}} %= \vec{E^0} e^{-ikz}
-\end{equation}
-
-Combining the two equations we have:
-\begin{equation}
-\vec{E}(\vec{r},t) 
-	= \vec{E^0} \Re \left( e^{i (\omega t - \vec{k} \cdot \vec{r})} \right)
-	= \vec{E^0} \cos(wt - \vec{k} \cdot \vec{r}) %\vec{E^0} \cos{ \left( wt - kz + \phi_0 \right)}
-\end{equation}
-
-If we define the $z$ direction as the travelling direction of the EM wave,
-%	and x direction is the direction of $\vec{E}$,
-%	then by Faraday's Law, the magentic field $\vec{B}$ lies in y direction, 
-%		and is related to the electric vector by $c^2 \frac{\partial B}{\partial z} = \frac{\partial E}{\partial t}$
-	and the electric field is fluctuating in the $(x,y)$ plane,
-	because the divergence of the electric and magnetic fields are zero, 
-		there will be no fields in the direction of propagation.
-Project this into $x$ and $y$ directions:
-\begin{equation}
-\vec{E}(z,t) 
-= 
-\left(
-	\begin{array} {c}
-		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
-		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
-		0
-	\end{array}
-\right)
-= 
-\left(
-	\begin{array} {c}
-		\xi_x(t) \\
-		\xi_y(t) \\
-		0
-	\end{array}
-\right)
-\end{equation}
-where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.
-
-\subsubsection{Linear, Circular and Elliptical Polarization}
-
-The shape traced out in a fixed projective plane by the electric vector as the plane wave passes over it is a description of the polarization state. 
-This shape is characterized by the formula
-\begin{equation}
- \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
-\end{equation}
-where
-	$\Delta \phi = \phi_y^0 - \phi_x^0$
-The formula characterizes what is termed as the polarization ellipse.
-
-%In the leftmost figure above, 
-When the two orthogonal components are in phase, i.e. $\phi_x^0 = \phi_y^0$, the ratio of the strengths of the two components is constant.
-Thus the direction of the electric vector (the vector sum of these two components) is constant. 
-Since the tip of the vector traces out a single line in the plane, this special case is called linear polarization. 
-The direction of this line depends on the relative amplitudes of the two components.
-%In the middle figure,
-
-When the two orthogonal components have exactly the same amplitude and are exactly ninety degrees out of phase, i.e. $E_x^0=E_y^0$ and $ | \phi_x^0 - \phi_y^0 | = \pi/2$. 
-%There are two possible phase relationships that satisfy this requirement: the x component can be ninety degrees ahead of the y  component or it can be ninety degrees behind the y component. 
-In this special case the electric vector traces out a circle in the plane, so this special case is called circular polarization. 
-The direction the field's rotation depends on the signed of the difference between the two phases. 
-These cases are called right-hand circular polarization and left-hand circular polarization, 
-	depending on which way the electric vector rotates and the chosen convention.
-
-The general case is when the two components are not in phase 
-	and either do not have the same amplitude or are not ninety degrees out of phase, 
-	though their phase offset and their amplitude ratio are constant.
-This kind of polarization is called elliptical polarization because the electric vector traces out an ellipse in the plane (the polarization ellipse). 
-%This is shown in the above figure on the right.
-
-The parameters that describe the polarization ellipse are:
-\begin{equation}
-\tan (\theta ) = \frac{E_y^0}{E_x^0}
-\end{equation}
-with
-	$0 \leq \theta \leq \pi/2$. 
-The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
-\begin{equation}
-\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
-\end{equation}
-with
-	$0 \leq \Psi < \pi$. 
-The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
-The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
-\begin{equation}
-\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
-\end{equation}
-with
-	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$
-
-Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
-Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.
-
-%The choice of basis vector used to represent horizontal and vertical directions are evidently arbitrary.
-%In general, any pair of orthogonal polarization states can be used.
-%Formally orthogonal vector pair is defined as one having a zero inner product.
-%Another common choice is left and right circular.
-%In anyway, implicit in the representations above is the orientation of the coordination frame.
-%Of the two angles frequently used in polarization ellipse analysis, one $\Psi$ is dependent on the coordination frame and the other may not $\chi$
-
-%To recap $\chi = \tan^{-1} (1/\epsilon)$, with $\epsilon$ being the ellipse's ellipticity.
-%In polarization ellipse, $\epsilon=1$ indicates circular polarization, while $\epsilon=0$ or $\epsilon=\infty$ corresponds to linear polarizations.
-%An alternative to ellipticity angle $\chi$ is the eccentricity angle.
-%However, the use of ecccentricity angle has not been widely used, as it has no obvious geometrical interpretation in Poincare Spheres.
-
-%The polarization of light can be measured with a polarimeter.
-
-\subsubsection{Mathematical representations of wave polarizations}
-
-\paragraph{ Complex polarization ratio }
-This ratio is important in explaining polarization basis changes.
-
-It is defined as:
-\begin{equation}
-\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
-\end{equation}
-
-\paragraph{Jones Vector}
-
-%Let the total wave power:
-%\begin{equation}
-%|E|^2 = (E_x^0)^2  + (E_y^0)^2
-%\end{equation}
-%and phase 
-%\begin{equation}
-%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
-%\end{equation}
-
-The Jones vector is defined as 
+\section{The Stochastics and Multivariate Nature of POLSAR data}
+
+\subsection{The Stochastic nature of SAR data}
+
+\subsubsection{ Traditional Single-Channel SAR and the Speckle phenomena}
+
+Wikipedia to be edited strongly.
+Speckle noise is a granular noise that inherently exists in and degrades the quality of the active radar and synthetic aperture radar (SAR) images.
+Speckle noise in conventional radar results from random fluctuations in the return signal from an object that is no bigger than a single image-processing element.
+It increases the mean grey level of a local area.[1]
+Speckle noise in SAR is generally more serious, causing difficulties for image interpretation.[1][2] It is caused by coherent processing of backscattered signals from multiple distributed targets.
+In SAR oceanography, for example, speckle noise is caused by signals from elementary scatterers, the gravity-capillary ripples, and manifests as a pedestal image, beneath the image of the sea waves.[3][4]
+
+\subsubsection{The Stochastic nature of SAR  and SAR speckle filtering }
+
+The stochastic nature SAR arises from the speckle phenomena.
+As SAR speckle seriously hinders the interpretation and understanding of SAR images,
+  its effect are routinely reduced through a speckle filtering process.
+SAR speckle filtering is the process to suppress the effect of speckle noise SAR images for easier intepretation.
+
+\subsection{The Multivariate Nature of POLSAR data}
+
+\subsubsection{ Partial Polarimetry and the Stokes Vector}
+
+The dual-polarization modes has been practically and operationally available for quite some time.
+However, partial polarimetry has only recently been investigated in the scientific community. 
+By comparison, 
+	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
+	while full polarimetry measures the same response for two (most of the time orthogonal) polarisation channels.
+Mathematically, the process is modelled as:
+\begin{equation}
+ \left( 
+\begin{array}{c}
+ E_h^{Rx} \\
+ E_v^{Rx}
+\end{array}
+ \right) = \frac{e^{ikr}}{r} 
+\left( 
+\begin{array}{c}
+ S_{H} \\
+ S_{V}
+\end{array}
+ \right) E^{Tx}
+\end{equation}
+
+Souyris \cite{Souyris_2005_TGRS} pioneered the field with his paper on compact polarimetry.
+Compact polarimetry is essentially a partial polarimetry mode in which the incoming pulse is of linear polarization, 
+	but is neither of the usual horizontal nor vertical angle.
+%	rather it is of an odd angle of 
+Instead its incoming polarization of linear polarisation with an odd angle of $\pi/4$.
+%The $\pi/4$ mode has not been implemented in real-hardware, but only been simulated using polarization basis change principles.
+The partial polarimetric covariance matrix then is given as
 \begin{equation}
@@
 \left(	
-\begin{array}{c}
-	\xi_x(t) \\
-	\xi_y(t) 
-\end{array}
-\right)
-= \xi_x(t)
-\left(
-\begin{array}{c}
-	1 \\
-	\rho
-\end{array}
-\right)
-\end{equation}
-
-Thus the normalized Jones vector can be given as:
-\begin{equation}
-J = 
-\left(
-\begin{array}{c}
-	\cos(\theta) \cdot e^{i \phi_x^0} \\
-	\sin(\theta) \cdot e^{i \phi_y^0}
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
-	1\\
-	\tan(\theta) \cdot e^{i \Delta \phi}
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
-	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
-	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
-\end{array}
-\right)
-\end{equation}
-
-The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
-This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
-Its bra-ket notation formula, which is normally used in quantum computation contexts is:
-\begin{equation}
-J = | \Psi \rangle 
-= 
-\left(
-\begin{array}{c}
-	\cos(\theta) \cdot e^{i \phi_x^0} \\
-	\sin(\theta) \cdot e^{i \phi_y^0}
-\end{array}
-\right)
-\end{equation}
-
-By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
-\begin{array}{c}
- 1 \\
- 0
-\end{array}
-\right)$, similarly the vertical linear polarized wave: $J_v = \left(
-\begin{array}{c}
- 0 \\
- 1
-\end{array}
-\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
-\begin{array}{c}
- 1 \\
- 1
-\end{array}
-\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
+\begin{array}{c c}
+	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
+& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
+	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
+& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
+\end{array}
+\right)
+\end{equation}
+
+Raney \cite{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
+He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
+Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
+The important parameter to choose is the use of which polarisation for the incoming pulse.
+His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
+The partial covariance matrix then become:
+\begin{equation}
+J = \frac{1}{2} \left(	
+\begin{array}{c c}
+	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
+& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
+	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
+& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
+\end{array}
+\right)
+\end{equation}
+
+The benefits of this hybrid architecture, according to Raney being:
+	this partial polarimetric measurements can measures certain physical polarimetric phenomena like odd and even bounce phenomena.
+The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
+\begin{equation}
+\Gamma_{tri} = \left(
+\begin{array}{c c}
+1 & 0 \\
+0 & -1
+\end{array}
+\right)
+\end{equation}
+Then the response will be reversed as it can be calculated as:
+\begin{equation}
+J_r = \left(
+\begin{array}{c c}
+1 & 0 \\
+0 & -1
+\end{array}
+\right) \cdot
+\left(
 \begin{array}{c}
@@
 \end{array}
-\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
+\right) = \left(
 \begin{array}{c}
@@
 \end{array}
-\right)$
-
-%Then any arbitrary state, written in R-L basis is given by:
-%\begin{equation}
-%| \Psi \rangle 
-%= 
-%a_R e^{i \phi_x - i \theta} | R \rangle 
-%+ 
-%a_L e^{i \phi_x + i \theta} | L \rangle 
-%\end{equation}
-
+\right) 
+\end{equation}
+with
+	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
+	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.
+
+For a dihedral target, whose main axis at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
+\begin{equation}
+\Gamma_{dih} = 
+\left(
+\begin{array}{c c}
+\cos(2\theta) & \sin(2\theta) \\
+\sin(2\theta) & \cos(2\theta)
+\end{array}
+\right)
+\end{equation}
+The even bounce phenomena is detectable as its polarimetric response is then:
+\begin{equation}
+J_r = \left(
+\begin{array}{c c}
+\cos(2\theta) & \sin(2\theta) \\
+\sin(2\theta) & \cos(2\theta)
+\end{array}
+\right) \cdot
+\left(
+\begin{array}{c}
+1 \\
+-i
+\end{array}
+\right) = \left(
+\begin{array}{c}
+1 \\
+-i
+\end{array}
+\right) 
+\end{equation}
+In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conviniences to hardware calibration.
+Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrate the classification power of hybrid polarimetry.
+Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
+Notably, the hybrid architectural concepts has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
+
+The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformation described above.
+Hardware realisation may not be needed until the final physical prototype stages.
+This methodology has been demonstrated and is widely used in the community.
+We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
+The focus into partial polarimetry allow analysis into a smaller matrix, while its implication can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
+Besides that, a number of research questions in this new field are still open, relevant and exciting.
+
+Souyris, in 2005, published a paper \cite{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
+The algorithm is claimed to work on natural surfaces.
+In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
+In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
+Chapter 3 reviews of this sub-topic further and introduces our work on expanding the reconstruction to urban man-made structures and surfaces.
+
+For the tasks of target detection and classification, we believe that partial dual polarization provides a unique offer.
+Compared with single-channel, dual channel provide extra polarimetric information. 
+Compared with full polarimetric data, the better spatial resolution could makes up for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
 \paragraph{ Stokes Vector }
@@
 
-\subsection{Different Modes of Polarimetric SAR}
+%In fact, this project is intended to provide help for a new project at EADS Innovation Works Singapore to investigate the use of polarimertic data in ship monitoring over the oceans.
+%It is hypothesized that using polarimetric information would improve the possibilities of detecting ships travelling in the open seas.
+%Evidently partial polarimetric modes are good candidates for better detection rates.
+%
+%The scientific application of POLSAR include: 
+%	oil slick detection \cite{Nunziata_2009_IGARSS, Gambardella_2007_ESASP}, 
+%	ship monitoring \cite{Kozai_2004_OCEANS}, 
+%	sea ice monitoring \cite{Wakabayashi_2004_TGRS, Nakamura_2005_IGARSS}, 
+%	volcano lava-flow monitoring \cite{Dierking_1998_IGARSS}, 
+%	agricultural crop monitoring \cite{Bouvet_2009_TGRS, Hajnsek_2008_IGARSS}, 
+%	planetary exploration \cite{Rosenbush_2009_JQuantSpecRadTransfer} 
+%	and other surface parameter estimations \cite{TruongLoi_2009_TGRS, Touzi_2009_TGRS, Hajnsek_Thesis_2001}. 
+%The remaining text of this chapter briefly look at recent literature in the context of ship detection and monitoring.
+%The topic of ship detection and monitoring has already been tackled quite extensively for single channel SAR data \cite{Tello_2005_IGARSS, Tello_2006_ISPRSJPhotogrammetryRemoteSensing}.
+%In fact, a number of countries have reported to implement such systems, and some uses them in everyday operations.
+%The countries includes: USA \cite{Montgomery_1998_IGARSS}, Canada \cite{Vachon_2000_JHUApplPhysics}, France \cite{Losekoot_2005_IGARSS}, Norway \cite{weydahl_2007_RemoteSenseGISGeology} and Spain \cite{Margarit_2009_RemoteSensing}.
+%The common scenarios in use are normally: 
+%	a designated area is continuously monitored through the use of some automatic ship detection algorithm.
+%If an unknown ship is detected, some manual intervention is to be applied, normally in the form of a navy ship being sent to further investigate.
+%The reports however did not elaborate about the accuracy of the detection algorithms.
+%
+%A recent trend that is reported in the literature is the use of AIS (Automatic Identification System).
+%In 2007, Vachon \cite{Vachon_2007_IGARSS} reported his study in Canada, which aimed to match ships detectable in SAR images with AIS reported locations.
+%In 2009, Grasso \cite{Grasso_2009_ISDA} evaluated the performance of ship detection algorithms using AIS as ground truth.
+%In our planned approach, we are prepared to study the performance improvement through using partial polarimetry data in comparison to normal single-channel SAR approaches.
+%Ground truth for such study will also be using synchronized AIS data.
 
@@
 
-\subsubsection{ Partial Polarimetry and the traditional SAR}
-
-The dual-polarization modes has been practically and operationally available for quite some time.
-However, partial polarimetry has only recently been investigated in the scientific community. 
-By comparison, 
-	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
-	while full polarimetry measures the same response for two (most of the time orthogonal) polarisation channels.
-Mathematically, the process is modelled as:
-\begin{equation}
- \left( 
-\begin{array}{c}
- E_h^{Rx} \\
- E_v^{Rx}
-\end{array}
- \right) = \frac{e^{ikr}}{r} 
-\left( 
-\begin{array}{c}
- S_{H} \\
- S_{V}
-\end{array}
- \right) E^{Tx}
-\end{equation}
-
-Souyris \cite{Souyris_2005_TGRS} pioneered the field with his paper on compact polarimetry.
-Compact polarimetry is essentially a partial polarimetry mode in which the incoming pulse is of linear polarization, 
-	but is neither of the usual horizontal nor vertical angle.
-%	rather it is of an odd angle of 
-Instead its incoming polarization of linear polarisation with an odd angle of $\pi/4$.
-%The $\pi/4$ mode has not been implemented in real-hardware, but only been simulated using polarization basis change principles.
-The partial polarimetric covariance matrix then is given as
-\begin{equation}
-J = 
-\left(	
-\begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
-& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
-	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
-& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
-\end{array}
-\right)
-\end{equation}
-
-Raney \cite{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
-He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
-Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
-The important parameter to choose is the use of which polarisation for the incoming pulse.
-His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
-The partial covariance matrix then become:
-\begin{equation}
-J = \frac{1}{2} \left(	
-\begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
-& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
-	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
-& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
-\end{array}
-\right)
-\end{equation}
-
-The benefits of this hybrid architecture, according to Raney being:
-	this partial polarimetric measurements can measures certain physical polarimetric phenomena like odd and even bounce phenomena.
-The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
-\begin{equation}
-\Gamma_{tri} = \left(
-\begin{array}{c c}
-1 & 0 \\
-0 & -1
-\end{array}
-\right)
-\end{equation}
-Then the response will be reversed as it can be calculated as:
-\begin{equation}
-J_r = \left(
-\begin{array}{c c}
-1 & 0 \\
-0 & -1
-\end{array}
-\right) \cdot
-\left(
-\begin{array}{c}
-1 \\
--i
-\end{array}
-\right) = \left(
-\begin{array}{c}
-1 \\
-i
-\end{array}
-\right) 
-\end{equation}
-with
-	$ \left( \begin{array}{c} 1 \\ -i \end{array} \right) $ indicating right circular polarization transmitted, and
-	$ \left( \begin{array}{c} 1 \\ i \end{array} \right) $ indicating left circular polarization received.
-
-For a dihedral target, whose main axis at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
-\begin{equation}
-\Gamma_{dih} = 
-\left(
-\begin{array}{c c}
-\cos(2\theta) & \sin(2\theta) \\
-\sin(2\theta) & \cos(2\theta)
-\end{array}
-\right)
-\end{equation}
-The even bounce phenomena is detectable as its polarimetric response is then:
-\begin{equation}
-J_r = \left(
-\begin{array}{c c}
-\cos(2\theta) & \sin(2\theta) \\
-\sin(2\theta) & \cos(2\theta)
-\end{array}
-\right) \cdot
-\left(
-\begin{array}{c}
-1 \\
--i
-\end{array}
-\right) = \left(
-\begin{array}{c}
-1 \\
--i
-\end{array}
-\right) 
-\end{equation}
-In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conviniences to hardware calibration.
-Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrate the classification power of hybrid polarimetry.
-Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
-Notably, the hybrid architectural concepts has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
-
-The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformation described above.
-Hardware realisation may not be needed until the final physical prototype stages.
-This methodology has been demonstrated and is widely used in the community.
-We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
-The focus into partial polarimetry allow analysis into a smaller matrix, while its implication can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
-Besides that, a number of research questions in this new field are still open, relevant and exciting.
-
-Souyris, in 2005, published a paper \cite{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
-The algorithm is claimed to work on natural surfaces.
-In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
-In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
-Chapter 3 reviews of this sub-topic further and introduces our work on expanding the reconstruction to urban man-made structures and surfaces.
-
-For the tasks of target detection and classification, we believe that partial dual polarization provides a unique offer.
-Compared with single-channel, dual channel provide extra polarimetric information. 
-Compared with full polarimetric data, the better spatial resolution could makes up for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
-
-In fact, this project is intended to provide help for a new project at EADS Innovation Works Singapore to investigate the use of polarimertic data in ship monitoring over the oceans.
-It is hypothesized that using polarimetric information would improve the possibilities of detecting ships travelling in the open seas.
-Evidently partial polarimetric modes are good candidates for better detection rates.
-
-The scientific application of POLSAR include: 
-	oil slick detection \cite{Nunziata_2009_IGARSS, Gambardella_2007_ESASP}, 
-	ship monitoring \cite{Kozai_2004_OCEANS}, 
-	sea ice monitoring \cite{Wakabayashi_2004_TGRS, Nakamura_2005_IGARSS}, 
-	volcano lava-flow monitoring \cite{Dierking_1998_IGARSS}, 
-	agricultural crop monitoring \cite{Bouvet_2009_TGRS, Hajnsek_2008_IGARSS}, 
-	planetary exploration \cite{Rosenbush_2009_JQuantSpecRadTransfer} 
-	and other surface parameter estimations \cite{TruongLoi_2009_TGRS, Touzi_2009_TGRS, Hajnsek_Thesis_2001}. 
-The remaining text of this chapter briefly look at recent literature in the context of ship detection and monitoring.
-The topic of ship detection and monitoring has already been tackled quite extensively for single channel SAR data \cite{Tello_2005_IGARSS, Tello_2006_ISPRSJPhotogrammetryRemoteSensing}.
-In fact, a number of countries have reported to implement such systems, and some uses them in everyday operations.
-The countries includes: USA \cite{Montgomery_1998_IGARSS}, Canada \cite{Vachon_2000_JHUApplPhysics}, France \cite{Losekoot_2005_IGARSS}, Norway \cite{weydahl_2007_RemoteSenseGISGeology} and Spain \cite{Margarit_2009_RemoteSensing}.
-The common scenarios in use are normally: 
-	a designated area is continuously monitored through the use of some automatic ship detection algorithm.
-If an unknown ship is detected, some manual intervention is to be applied, normally in the form of a navy ship being sent to further investigate.
-The reports however did not elaborate about the accuracy of the detection algorithms.
-
-A recent trend that is reported in the literature is the use of AIS (Automatic Identification System).
-In 2007, Vachon \cite{Vachon_2007_IGARSS} reported his study in Canada, which aimed to match ships detectable in SAR images with AIS reported locations.
-In 2009, Grasso \cite{Grasso_2009_ISDA} evaluated the performance of ship detection algorithms using AIS as ground truth.
-In our planned approach, we are prepared to study the performance improvement through using partial polarimetry data in comparison to normal single-channel SAR approaches.
-Ground truth for such study will also be using synchronized AIS data.
-
-\section{The Stochastics and Multivariate Nature of (POL)SAR data}
-
 %\subsection{The Stochastics Nature of SAR and POLSAR}
-\subsection{The Stochastic nature of SAR  and SAR speckle filtering }
-
+\section{Current methods in SAR and POLSAR Data Processing}
+
+\subsection{Current Statistical Models for SAR and POLSAR data}
+
+\subsection{Current Methods for SAR speckle filtering}
 This section starts with a description of the stochastic nature of SAR data. 
@@
 	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.
-
-\subsection{The Multivariate Nature and The Observables in POLSAR data}
-
-\section{Current methods in SAR and POLSAR speckle filtering}
-
-\subsection{Current Statistical Models for SAR and POLSAR data}
-
-\subsection{Current Methods for SAR speckle filtering}
-(2.2.1)
 
@@
 
-\section{Existing Measures of Distance for (POL)SAR data and their applications}
+\subsection{Existing Dis-similarity Measures for (POL)SAR data}
 
@@
 
-\section{The need for Scalar Consistent Measures of Distance}
+\subsection{The need for Scalar Consistent Measures of Distance}
 	We will show our originality and significance here!

### 2013-04-22 5/applications.tex
added 201304_Apr22

@@
 
+%SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
+The principle of many speckle filters in removing the stochastic noise is to group data into homogeneous areas.
+In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
+where 
+	$I_i$ is the intensity value of pixel \textit{i} and
+	$n$ is the total number of pixel in the surrounding areas.
+The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
+%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
+%In a filter previously proposed by the authors
+In the kMLE filter presented above and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
+where 
+	$I_i$ is the intensity value of pixel \textit{i} and
+	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.
+
 \begin{tabular}{c c}
@@
 
+%By and large,
+While it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
+  the concept of ``homogeneous area'' lacks precise definition and boundaries.
+%This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.
+In fact, the classification decisions between homogeneity and heterogeneity are probabilistic in nature.
+%the concept of “homogeneous area” lacks precise definition and boundaries. 
+This is evident in the statistical hypothesis testing used to support these decision makings.
+
+The fMLE speckle filter presented in this section follow fuzzy logic approach,
+  which, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
+  embraces truth values that range from 1 to 0.
+Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
+Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability,
+  in comparison to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.
+The benefit of this fuzzy logic approach is that: we no longer need to worry about the homogeneous / heterogeneous problem.
+
+%The idea presented in this paper is structured as follows:
+%Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
+%The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
+%Finally, Section \ref{sec:conclusion} concludes this paper.
+%The last section will offers some conclusion and finalizes the paper.
+
 \subsection{The FMLE SAR Speckle Filters}
 
-SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
-The principle of many speckle filters in removing stochastic noise is to group data into homogeneous areas.
-In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
-where 
-	$I_i$ is the intensity value of pixel \textit{i} and
-	$n$ is the total number of pixel in the surrounding areas.
-The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
-%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
-In a filter previously proposed by the authors \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
-where 
-	$I_i$ is the intensity value of pixel \textit{i} and
-	$k$ is the total number of pixels in the partitioned and homogeneous area covering the centre point.
-
-\begin{tabular}{c c}
-\begin{minipage}[c]{0.45\textwidth}
-\begin{equation}
-\label{eqn:boxcar}
-f_{boxcar} = \displaystyle{\sum_{i=1}^n{I_i}} / n 
-\end{equation}
-\end{minipage}
-\begin{minipage}[c]{0.45\textwidth}
-\begin{equation}
-\label{eqn:kmle}
-f_{kMLE }= \displaystyle{\sum_{i=1}^k{I_i} } / k 
-\end{equation}
-\end{minipage}
-\end{tabular}
-
-By and large, while it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
-  the concept of ``homogeneous area'' lacks precise definition and boundaries.
-This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.
-
-This paper presents a different approach, that of fuzzy logic.
-Fuzzy logic embraces truth values that range from 1 to 0, 
-	instead of fixing on a rigid two-member set of logical values (i.e. true and false).
-Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
-Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability, in contrast to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.
-
-The idea presented in this paper is structured as follows:
-Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
-The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
-Finally, Section \ref{sec:conclusion} concludes this paper.
-%The last section will offers some conclusion and finalizes the paper.
-
-The foundation of the approach is the consistent sense of distance found in the log-transformed domain.
-It is shown in \cite{Le_2010_ACRS} that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.
-
-Log transformation is defined as:
+The foundation of the fuzzy-estimation approach is the consistent sense of distance found in the log-transformed domain.
+%It is shown in \cite{Le_2010_ACRS}
+The consistent sense of distance states that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.
+
+The base-2 log transformation is defined as:
 ${L_I}^i = \log_2{(I^i)}$ 
@@
 %Distance in log-transformed domain is defined as:
-Log domain distance is defined as:
+The log-contrast is then defined as:
 $D= L_I^1 - L_I^2$. 
 Assumming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
-  then distance will follow the distribution 
+  then this dis-similarity distance will follow the distribution 
 $pdf(D)= \frac{2^D}{(1+2^D)^2} \ln2$,
   which is consistent.
-The analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.
+This analysis is confirmed by real-life data validations (see \cite{Le_2010_ACRS}) and visually demonstrated in Fig. \ref{fig:consistent_contrast_log_domain}.
 
@@
 
-Using a fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
+In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
 $p_i = pdf(D_i)$, with $D_i=log_2(I_i) - log_2(I_0)$.
-We then propose a new approximation given in Eqn. \ref{eqn:fmle_incl}
+The fMLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.
 
@@
 %The figures demonstrate speckle being filtering effects.
-In implementating this estimator, we noticed there are visible black dots in the filtered image.
+In implementing this statistical estimator, there are very noticable black dots in the filtered output image.
 These dots can be explained as the long-tailed nature of the intensity PDF, 
   which manifests itself in the significant existence of very small values in the population.
-In the all-inclusive scheme, this will results in 
-	a single $D_0=0$ (at $I_0$) and other very large $D_{i, (i > 0)}$, hence
+In this all-inclusive scheme, there is 
+	a single $D_0=0$ (at $I_0$) in the middle of other very large $D_{i, (i > 0)}$, which results in
 	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
 This marginalises the filtering power of surrounding pixels.
-An option is to exclude the centre point $I_0$ from its estimation (see Eqn. \ref{eqn:fmle_excl})
+One way to counter this effect is to exclude the centre point $I_0$ from its estimation,
+  which results in the exclusive scheme written in Eqn. \ref{eqn:fmle_excl}.
 
@@
 %\subsection{Comparing the two schemes}
-Both filters are applied to an simulated single-look homogeneous scene 
+For visualization and comparison purposes, both filtering schemes are applied to an simulated single-look homogeneous scene 
 and the histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original}.
-The filtering power is clearly visible.
+The speckle suppression power is clearly visible.
 %demonstrated in Figure \ref{fig:compare_filters_histograms:Original}.
-In comparing the two schemes' histogram in the same figure, it appears that 
+For comparison, the two schemes’ histogram are plotted in the same figure.
+%In comparing the two schemes' histogram in the same figure,
+And it is apparent that 
 	the filtering power of ignoring centre point scheme is at least as powerful as that of centre point included scheme and
-	the skewness in the histogram of the ignoring scheme is also appearing less than that of the included scheme.
+	the skewness in the histogram of the exclusive scheme is less than that of the inclusive estimation.
 
@@
 
-\subsubsection{Preservation of Distance Histogram Consistency}
+\subsubsection{Preservation of Log-Distance Histogram Consistency}
 
 Fig.
-\ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the distance histograms found in the outputs of applying FMLE filters on the inputs depicted in Fig.
+\ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above being applied on the inputs depicted in Fig.
 \ref{fig:compare_filters_histograms:Original}.
-They clearly demonstrate that the filtering treatment described above preserves the consistent sense of distance.
-This can be explained from the consistent histogram of the fuzzy possbilistic probabilities.
+They clearly demonstrate that the FMLE speckle filters preserves the consistent sense of distance.
+This can be explained from the consistent histogram of the input log distance PDF.
+
 Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
-This renders the task of giving analytical PDF impractical.
-However, large scale computer simulations can provide a practical histogram, from which the PDF can estimated.
+This renders the task of giving analytical PDF for the output log-distance impractical.
+However, large scale computer simulations can be used to provide an usable histogram, from which a PDF can estimated.
 %from large scale simulations. 
 %Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
-Given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.
+Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.
 
@@
 
-The preservation of consistent distance property is the enabling factor that allows the recursive use of FMLE filters.
-Additional applications of the filtering process can be expected to reduce the random noise variance even further.
-In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.
-
-In the subsequent application of the filtering algorithm, the main different when compared with the filters in initial iteration is the way the new fuzzy probabilities being calculated.
-This subsequent computation of fuzzy probabilities is based on the derived distance PDF, being computed in the previous section.
-This process is iterated iteratively, with the histogram obtained from the previous iteration serves as probabilistic distance PDF input of the subsequent application of the filter.
-This scheme allows speckle to be further depressed, as illustrated in Fig. \ref{fig:plot_incl_distance_pdf_by_iterations}
-
-\begin{figure}[h!]
+The preservation of consistent distance property is the enabling factor that allows the recursive application of FMLE filters.
+Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
+%In a sense, this scheme is similar to statistical asymptotic estimations, with the added advantage of spatial preservation.
+
+In subsequent application of the filtering algorithm, the main different when compared with the initial iteration is the way the new fuzzy probabilities being calculated.
+This subsequent computation of fuzzy probabilities is based on the output distance PDF, whose computation process is described in the previous section.
+This process is repeated iteratively, with the histogram obtained from the previous iteration serves as the input fuzzy probability PDF in subsequent application of the filter.
+%This scheme allows speckle to be further depressed, as illustrated in
+Fig. \ref{fig:plot_incl_distance_pdf_by_iterations} illustrates the extra speckle suppression power of this scheme.
+
+\begin{figure}[H]
 \centering
@@
 
-The log-transformed domain provides a consistent sense of distance.
-By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
-Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
-The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
-The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
-The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available scene and computational power, is sufficiently large.
-For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
-Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
-They also exhibit good correlation between the MSE and the AUC index.
-
 \subsection{Evaluating the FMLE SAR speckle filters}
 
-Estimators are evaluated based on the bias and variance properties of their estimates. 
-The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
-Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.
-
-The nature of SAR speckle is that
-	it is stochastic even if the underlying radiometry is constant. 
-And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
-Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
-As such, speckle filters are, by and large, estimators that attempt to determine this unknown coefficient from observable SAR data.
-
-SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
-The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
-%Estimators are typically evaluated based on the bias and variance properties of their estimates: 
-%	with lower bias and / or lower variance, hence lower MSE indicates better accuracy.
-Estimators are typically evaluated based on the bias and variance properties of their estimates:
-  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
-Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
-	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.
-
-Our survey of SAR speckle filter research, however, indicates 
-	a different picture from the standard practice of the statistical framework, 
-	specifically, in the stage of performance evaluation. 
-Due to the multiplicative and heteroskedastic nature of speckle noise, 
-	bias and variance evaluation may not be the most useful measures. 
-Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
-	prompting alternative evaluation criteria to be proposed.
-In fact, our survey of relevant literature fails to reveal 
-	a single universally agreed quantitative metric for the performance of speckle filters.
-
-Most commonly, each newly proposed speckle filter tends to be published along with its own methodology for evaluating its 
-	performance. 
-As such, many papers lack a comparative basis beyond simple visual qualitative comparison on a few image scenes. 
-While such visual comparison is useful, as an evaluative methodology, regrettably it lacks scientific objectivity. 
-Some papers do present quantitative measurements. 
-However, due to the lack of a standardized performance criteria, 
-	the evaluation metrics can change significantly from one paper to the next.
+%Estimators are evaluated based on the bias and variance properties of their estimates. 
+%The performance evaluation is usually based qualitatively on some real data and quantitatively through simulated experiments. 
+%Due to the stochastic nature of simulation process, results of repeated experiments are normally preferred.
 
@@
 In practical terms, the most common usage of speckle filtered imagery include target and feature detection and classification.
-We highlight the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs.
-We then show that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
+In this section, the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs is briefly explored.
+
+The performance of the FMLE filter is evaluated both qualitatively against real
+images and quantitatively via simulated experiments. 
+Over homogeneous regions, the speckle suppression power is
+evaluated by measuring the ubiquitous MSE on simulated and truth-grounded experiments. 
+The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
+
+For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as
+statistical evidence for better performance in the subsequent tasks of target detection
+and surface classification. 
+Experiments confirm the power of FMLE filters in various
+heterogeneously simulated areas. 
+A good correlation between the MSE and the AUC index is also exhibited. 
+The result suggests that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
+Let us start with a qualitative visual evaluation of the speckle filter on real-captured images.
+
+%We highlight the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs.
+%We then show that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
 %As is customary, we start by an visual evaluation of the filter on real-life images.
-We start with visual evaluation of the filters on real-life images.
+%We start with visual evaluation of the filters on real-life images.
 
@@
 The filtering effects are clearly visible.
-Apparently the second iteration outputs appears much better than the initial iteration, and offer roughly the same level of performance in comparision to that of boxcar filter.
-
-\begin{figure}[h!]
+Apparently the second iteration outputs appears much better than the initial application.
+Furthermore, they offer roughly the same level of speckle suppression power in comparison to that of boxcar filter.
+
+\afterpage{\clearpage}
+
+\begin{figure}
 \centering  
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering  
@@
 
-We have found that MSE in the log-transformed domain is related to the standard Equivalent Number of Look value.
-Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002}, the formula is given as:
+We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Look value.
+Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
 $MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
@@
 
-\begin{figure}[h]
-\centering
- \epsfxsize=6cm
- \epsfysize=6cm
+\begin{figure}
+\centering
+ \epsfxsize=9cm
+ \epsfysize=9cm
  \epsffile{images/verify_MSE_as_perf_index.made.eps}
-\end{figure}
-
-\begin{figure}[h]
+ \caption{MSE in the log-transformed domain is related to the ENL index}
+ \label{fig:verify_MSE_as_perf_index}
+\end{figure}
+
+\begin{figure}
 \centering
@@
 \end{figure}
+\afterpage{\clearpage}
 
@@
 
-The normal application after applying filters on SAR images is to detect the existence of certain target within its surrounding clutters.
-%Assume the 
+The normal application after applying filters on SAR images is to detect the existence of certain target within its surrounding clutters or other similar classification / discrimination tasks.
 The most common type of detector (or classifier) employs a threshold based approach in determing whether an abnormal value signifies the existence of a target.
@@
 In this experiment, we apply a simple 3x3 boxcar filter to two different homogeneous and SLC noise corrupted scenes that are known to be 3dB apart.
-And then the histograms as well as the resulting ROC curve are plotted between the pairs of target and background histogram in the two cases of unfiltered and filtered data.
+And then the histograms as well as the resulting ROC curve are plotted between the pairs of target and background histogram for both cases of unfiltered and filtered data.
 We noted that the ROC curve for the histograms in original domain matches perfectly with ROC for the histograms in the log-transformed domain (see Fig.
@@
 
-\begin{figure}[h]
+%\afterpage{\clearpage}
+
+\begin{figure}
 \centering
@@
 %\subfloat[Invariant ROC Curve]{
+%\afterpage{\clearpage}
 \begin{figure}
+\centering  
  \epsfxsize=6cm
@@
 The most common types of target to be detected in image processing are point targets, line targets, and edge targets.
-The detectability of the targets are measured using the AUC index which is tabulated against the MSE.
+The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
 Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of FMLE filters for heterogenous regions.
-Even though the relationship is probably not linear,
-  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
-Also FMLE filters apparently have better performance than boxcar filters.
-
-\begin{figure}[h!]
-\begin{minipage}[c]{0.5\textwidth}
+Aapparently the fMLE filters have better performance than boxcar filters.
+Also noticeable is the correlation between MSE and the Area Under the ROC curve criteria, 
+  which is an interesting phenomena that will be investigated further in the next section.
+%Even though the relationship is probably not linear,
+%  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
+%Also FMLE filters apparently have better performance than boxcar filters.
+
+\begin{figure}
+\begin{minipage}[c]{0.48\textwidth}
 %\captionsetup[subfigure]{labelformat=empty}
@@
 %} & 
-\begin{minipage}[c]{0.38\textwidth}
+\begin{minipage}[c]{0.4\textwidth}
 %\captionsetup[subfigure]{labelformat=empty}
@@
 %\centering
+  \footnotesize
 \begin{tabular}{|l|l|l|l|}
@@
 \end{figure}
+\afterpage{\clearpage}
 
 \subsubsection{Contribution and Conclusions}
+
+%The log-transformed domain provides a consistent sense of distance.
+%By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
+%Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
+%
+%The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
+%The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
+%The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
+%
+%For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
+%Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
+%They also exhibit good correlation between the MSE and the AUC index.
 
@@
 Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
-Various negative effects of heteroskedasticity are discussed. 
 Log-transformation is shown to provide homoskedasticity in statistical models. 
@@
 
+The log-transformed domain provides a consistent sense of distance. By embracing
+a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes
+use of this consistency. Experimental results suggest that the estimator’s output also
+exhibits this consistency property, which allows recursive application of the filter discussed above.
+
 The speckle filtering technique proposed here has been shown to work for single-look SAR images. 
 Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
-The filter is developed from an easy to understand winner-take-all clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
-Should the fuzziness be taken to a new level, an optimal fuzzy probabilistic filter which requires no clustering may be specified and designed.
+The fMLE approach is developed from an easy to understand winner-take-all kMLE clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
+With the fuzziness be taken to a new level, fuzzy probabilistic speckle filters which requires no clustering have been specified and designed.
+
+%The nature of SAR speckle is stochastic. 
+%The speckle filtering problem has been casted into a statistical estimation theory framework. 
+%Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
+%Various negative effects of heteroskedasticity are discussed. 
+%Log-transformation is shown to provide homoskedasticity in statistical models. 
+%Using speckle filtering as an applicative example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.
+%
+%The speckle filtering technique proposed here has been shown to work for single-look SAR images. 
+%Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
+%The filter is developed from an easy to understand winner-take-all clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
+%Should the fuzziness be taken to a new level, an optimal fuzzy probabilistic filter which requires no clustering may be specified and designed.
 
 \section{Evaluating SAR Speckle Filters using the consistent measures}
-
-To do quantitative evaluation of different speckle filters, it is necessary to compare a filtered image with a ground-truth one. 
-Furthermore, it is desirable that the error, i.e. the distance between the filtered output and the original input, should be consistent and independent to the particular simulated scenario. 
-Normally, the measure of choice is in the original SAR intensity or amplitude domain. 
-However owing to the homoskedastic effects of the log-transformation, the error in log-transformed domain is preferred.
-
-Homoskedasticity makes ordinary least square (OLS) approaches becomes valuable again. 
-Synonymous to OLS is the use of standard Mean Squared Error as a performance index.
-
-\begin{equation}
-\Psi = \displaystyle{ \frac{ \sum^N_{i=1}{(Y^L_i - X^L_i)^2} }{N} }
-\end{equation}
-where $Y^L_i$ indicates filtered output values and $X^L_i$ denotes the original input as ground-truth values, $N$ is the number of data points available
-
-This section will shows that in a homogeneous area, this performance index is similar to the standard Equivalent Number of Looks (ENL) measures, while investigating the value in heterogeneous areas shows how well the filter adapts to underlying spatial variations.
-
-%\section{Using MSE to evaluate SAR speckle filters}
 
@@
 
-SAR speckle-filtering can be, and has been, positioned within the context of estimation theory\cite{Touzi_2002_TGRS}. 
+SAR speckle-filtering can be, and has been, positioned within the context of estimation theory \cite{Touzi_2002_TGRS}. 
 The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
@@
 Estimators are typically evaluated based on the bias and variance properties of their estimates:
-  lower bias and/or lower variance would lead to lower MSE, which then indicates better accuracy.
-Ideally, estimator evaluation should be based both qualitatively on some real data and quantitatively through simulated experiments. 
-In addition, due to the stochastic nature of SAR-processing, and thus its simulating process, 
-	statistical summaries of repeatedly-simulated experiments are normally preferred to single-run results.
+  with lower bias and/or lower variance lead to lower MSE, which then indicates better accuracy.
+Ideally, the evaluation of SAR speckle filters should be based both qualitatively on some real data and quantitatively through simulated experiments. 
+In addition, due to the stochastic nature of SAR-processing, and its simulating process, 
+	statistical summaries of repeatedly-simulated experiments are preferred to single-run results.
 
@@
 
+To do quantitative evaluation of different speckle filters, it is necessary to compare a filtered result with a ground-truth image. 
+Furthermore, it is desirable that the error, i.e. the distance between the filtered output and the original input, should be consistent and independent to the particular simulated scenario. 
+Simplistically speaking, the measure of choice is in the original SAR intensity or amplitude domain. 
+However owing to the homoskedastic effects of the log-transformation, the error in log-transformed domain is preferred.
+%However owing to the homoskedastic effects of the log-transformation, this section shows that the error in log-transformed domain offers a better evaluation metric.  
+Homoskedasticity makes ordinary least square (OLS) approaches becomes valuable again. 
+Synonymous to OLS is the use of standard Mean Squared Error as a performance index.
+In this section, the use of MSE in the homoskedastic log-transformed domain to evaluate SAR speckle filters is proposed and validated.
+%\begin{equation}
+%\Psi = \displaystyle{ \frac{ \sum^N_{i=1}{(Y^L_i - X^L_i)^2} }{N} }
+%\end{equation}
+%where $Y^L_i$ indicates filtered output values and $X^L_i$ denotes the original input as ground-truth values, $N$ is the number of data points available
+%This section will shows that in a homogeneous area, this performance index is similar to the standard Equivalent Number of Looks (ENL) measures, while investigating the value in heterogeneous areas shows how well the filter adapts to underlying spatial variations.
+
+%\section{Using MSE to evaluate SAR speckle filters}
+
 \subsection{ Speckle Filtering Process And The Homoskedastic Log-transformed Domain}
@@
 	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
-The speckle filters used in this paper are: 
+The speckle filters used in this section are: 
 	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter 
@@
 
-Logarithmic transformation offers several consistent measures of distance, which is hypothised to be 
+Logarithmic transformation offers several consistent measures of distance, which is hypothesized to be 
 significant in evaluating speckle filters.
@@
 A conventional method is to investigate the ratio images between the filtered output and the noisy input images.
-Since logarithmic transformation converts these ratio into substractive residual which are consistent, residual 
+Since logarithmic transformation converts these ratio into subtractive residual which are consistent, residual 
 analysis can be used to analyse and evaluate the performance of speckle filters.
+The benefit of using log-residual over original-ratio is that the additive and homoskedastic nature of the log-residual signal fits better with the digital nature of imagery visualization.
 %To compare the use of ratio images in the original domain and the residual image in the log-transformed domain,
+
 For visual comparison, Fig. \ref{fig:real_image_ratio_vs_residual} depicts the residual image in the log-transformed domain 
@@
 
+\afterpage{\clearpage}
 \begin{figure}
@@
 	\subfloat[Original Patch]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.eps} 	
@@
 	\subfloat[Boxcar Filtered Result]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.boxcar.eps} 	
@@
 	\subfloat[Ratio: Filtered / Original]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.ratio2.eps} 	
@@
 	\subfloat[Ratio: Original / Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.ratio1.eps} 	
@@
 	\subfloat[Log Residual: Filtered - Original]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.residual2.eps} 	
@@
 	\subfloat[Log Residual: Original - Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.residual1.eps} 	
@@
 
-As qualititative visual evaluation is subjective by nature,
-	quantitative metrics and measurements are preferred, if relevant and possible.
+Compared to qualitative visual evaluation which is subjective by nature,
+  %quantitative metrics and measurements are preferred, if relevant and possible.
+  quantitative measurements are more objective and hence are usually preferred.
+In quantitative evaluation, it is important that the quantitative metric is computable and relevant.
 Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, 
 are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
-When ground-truth is available, 
+When the ground-truth is available, 
 	either in simulated experiments or over homogeneous area where it can be reasonably estimated, 
@@
 
-However, in real captured SAR images where such ground truth is unknown, the evaluation can then be carried out 
-through a benchmarked MSE. 
+However, in real captured SAR images where such ground truth is unknown,
+  the evaluation can only be carried out through a benchmarked MSE. 
 The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ 
@@
 Thus the base MSE level, which is also a measure of the speckle noise level, can also be estimated.
-Naturally, the speckle filter should remove as much noise as possible, 
-	while it also should not remove more variations than that caused by the speckle noise.
+Naturally, while the speckle filter should remove as much noise as possible, 
+	it also should not remove more variations than that caused by the speckle noise.
 %Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base 
+That is $MSE_{noise}$ should track the base MSE as close as possible,
+  making the $MSE_{benchmark}$ should be as close to 0 as possible.
 
@@
 
-\subsubsection{ Estimating ENL from MSE index in homogeneous areas }
+\subsubsection{ Estimating ENL from the log-variance index in homogeneous areas }
 \label{sec:homogeneous_theoretical}
@@
 In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL 
-index. Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
-Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
-	then the MSE evaluation is reducced to variance evaluation.
-That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered 
-output in the log-transformed domain.
-
-Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
+index.
+%Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
+%Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
+%	then the MSE evaluation is reducced to variance evaluation.
+%That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered 
+%output in the log-transformed domain.
+
+Let us consider the multi-look processing effect in the log-transformed domain. 
 %Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
@@
 
-The finding here may also help to explain other seemingly unrelated results. For example, 
+The relationship exposed here may also help to unite other seemingly unrelated results.
+For example, 
 	Solbo \cite{Solbo_2006_TGRS} used standard deviation in the log-transformed domain to measure homogeneity, 
@@
 
-\subsubsection{Using log-variance to evaluate speckle filters}
+\subsubsection{Using MSE criteria to evaluate speckle filters}
+
+Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
+Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
+	then the MSE evaluation is reduced to variance evaluation.
+Since the log-variance is related to the ENL, 
+  this evaluation approach is equivalent the established ENL evaluation methodology.
+In fact, a few more observations and analysis can be carried out.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
 \centering  
@@
 	\subfloat[Single Look (Intensity)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/orig_inconsistency_none.png.eps} 	
@@
 	\subfloat[Multi Look (Intensity)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/orig_inconsistency_boxcar.png.eps} 	
@@
 	\subfloat[Single-Look in Log Domain]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_none.png.eps} 	
@@
 	\subfloat[Multi-Look in Log Domain]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_boxcar.png.eps} 	
@@
 preserve this consistency in their filtered output. Intuitively, as the boxcar filter is actually similar to 
-multi-look processing, thus its output also does exhibit the this consistency.
-This consistency will also lead to the consistent sense of distance described earlier, which is significant 
-because it is the tell-tale indicator of the consistent contrast and variance.
-This ensures applicability of various target detection/classification algorithms 
-which employ statistical properties in the un-filtered data, such as the ratio based discriminator 
+multi-look processing, its output also exhibits this consistency.
+The following paragraph explains why this preservation of the consistent property is important in evaluating SAR speckle filters.
+
+%This consistency will also lead to the consistent sense of distance described earlier, which is significant 
+%because it is the tell-tale indicator of the consistent contrast and variance.
+This consistency is significant because it leads to the consistent sense of distance, contrast and variance described earlier.
+It also ensures applicability of various target detection/classification algorithms 
+which employ statistical properties in the unfiltered data, such as the ratio based discriminator 
 in the original domain or the differential based discriminator in the log-transformed domain.
+The consistent log-variance also leads to consistent and thus reliable ENL evaluation,
+  regardless of the underlying radiometric value.
 
@@
 	\subfloat[Lee filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_lee.png.eps} 	
@@
 	\subfloat[Kuan Filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_kuan.png.eps} 	
@@
 	\subfloat[Frost Filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_frost.png.eps} 	
@@
 	\subfloat[Gamma MAP filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/log_consistency_map.png.eps} 	
@@
 
-\subsubsection{ Estimating ENL from MSE index in homogeneous areas }
-
-Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
-Assuming the filters are unbiased, or the bias is already compensated, i.e. $E(Y^L)=X^L$, then the MSE becomes $\Psi = \frac{ \sum^N_{i=1}{ (Y^L_i - E(Y^L)) } }{N} = var(Y^L)$.
-That is, for known homogeneous scenes, MSE can be estimated as the observable variance of the filtered output in log-transformed domain.
-
-Let us consider the speckle suppression effect of multi-look processing in the log-transformed domain. 
-Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
-Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random variable as: $var(Y^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right)$.
-
-Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
-Taking results of the Euler proof for the Basel problem we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $\Psi= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
-Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
-In fact, we could estimate:
-\begin{equation}
-  \Psi = \frac{1}{(L-0.5) \ln^2(2) }
-\label{eqn:perf_index_analytic}
-\end{equation}
-Thus, the Equivalent Number of Look, i.e. L, can be estimated as:
-\begin{equation}
-ENL = \frac{1}{\Psi \ln^2(2)} + 0.5
-\label{eqn:enl_analytic}
-\end{equation}
-
-From the section above, it can be shown that logarithmic transformation of single-look intensity, i.e. $X^L_1$, has a speckle power MSE of $\Psi_1 = var(X^L_1)=\frac{1}{\ln2^2} \frac{\pi^2}{6}$. 
-With each additional 1-look in SAR multi-look processing, the speckle power will reduce by:  
-\begin{equation}
- \Psi_n = \Psi_{n-1} - \left( \frac{1}{\ln2(n-1)} \right)^2 
-\end{equation}
-with $n$ being the number of look being averaged.
-
-To verify the above analysis an experiment is carried out.
-In the experiment, a known $256\times256$ homogeneous area is generated and is corrupted with SAR-speckle PDF. 
-Different multi-look processing filters are repeatedly applied to the patch. 
-A performance index is calculated for each simulation with their mean and variances reported. 
-The analysis values are calculated from Equation \ref{eqn:perf_index_analytic}, together with estimated ENL from Equation \ref{eqn:enl_analytic}
-
-\begin{table}
-\centering
-
-\begin{tabular}{c|c|c|c|c}
-No  & Simulation                      &Analysis   &Est ENL       & Perf Index Improved \\% &85\%             &90\%\\
-\hline
-2   &1.3397 ($0.1036 \cdot 10^{-03}$) &1.3423	 &2.0536	& - \\
-3   &0.8201 ($0.0188 \cdot 10^{-03}$) &0.8220	 &3.0379	& 0.5196\\
-4   &0.5898 ($0.0217 \cdot 10^{-03}$) &0.5907	 &4.0287	& 0.2303\\
-5   &0.4595 ($0.0067 \cdot 10^{-03}$) &0.4607	 &5.0292	& 0.1303\\
-6   &0.3764 ($0.0013 \cdot 10^{-03}$) &0.3774	 &6.0291	& 0.0831\\
-7   &0.3195 ($0.0073 \cdot 10^{-03}$) &0.3196	 &7.0149	& 0.0569\\
-8   &0.2773 ($0.0043 \cdot 10^{-03}$) &0.2771	 &8.0056	& 0.0422\\
-9   &0.2448 ($0.0016 \cdot 10^{-03}$) &0.2446	 &9.0010	& 0.0325\\
-10  &0.2193 ($0.0015 \cdot 10^{-03}$) &0.2189	 &9.9908	& 0.0255\\
-11  &0.1975 ($0.0024 \cdot 10^{-03}$) &0.1981	 &11.0400	& 0.0218\\
-12  &0.1807 ($0.0013 \cdot 10^{-03}$) &0.1809	 &12.0157	& 0.0168\\
-13  &0.1663 ($0.0004 \cdot 10^{-03}$) &0.1664	 &13.0121	& 0.0144\\
-14  &0.1544 ($0.0004 \cdot 10^{-03}$) &0.1541	 &13.9783	& 0.0119\\
-15  &0.1435 ($0.0003 \cdot 10^{-03}$) &0.1435	 &15.0075	& 0.0109\\
-16  &0.1342 ($0.0003 \cdot 10^{-03}$) &0.1342	 &16.0071	& 0.0093\\
-17  &0.1263 ($0.0003 \cdot 10^{-03}$) &0.1261	 &16.9765	& 0.0079\\
-18  &0.1189 ($0.0004 \cdot 10^{-03}$) &0.1189	 &18.0085	& 0.0074\\
-19  &0.1126 ($0.0006 \cdot 10^{-03}$) &0.1125	 &18.9777	& 0.0063\\
-20  &0.1070 ($0.0004 \cdot 10^{-03}$) &0.1067	 &19.9528	& 0.0056\\
-21  &0.1016 ($0.0003 \cdot 10^{-03}$) &0.1015	 &20.9847	& 0.0054\\
-22  &0.0969 ($0.0004 \cdot 10^{-03}$) &0.0968	 &21.9806	& 0.0047\\
-23  &0.0924 ($0.0005 \cdot 10^{-03}$) &0.0925	 &23.0188	& 0.0045\\
-24  &0.0885 ($0.0002 \cdot 10^{-03}$) &0.0886	 &24.0214	& 0.0039\\
-25  &0.0850 ($0.0001 \cdot 10^{-03}$) &0.0849	 &24.9942	& 0.0035
-\end{tabular}
-
-\caption{ ENL: Boxcar Filter's Speckle Suppression Power }
-\label{tab:enl_in_log_domain}
-\end{table}
-
-%To evaluate the effects of number of looks on performance index, the performance index values for each ENL is computed and listed in table \ref{tab:enl_in_log_domain}. 
-%To compare our filter with boxcar filters, the error is reported not only as a single performance index value but also as the whole distribution, depicted as the histogram of error in log-domain, see figure ???.
-Homoskedastic effects should also make it possible to evaluate performance speckle filter in heterogenous scenes, however such evaluation is outside the scope of current paper.
+\afterpage{\clearpage}
 
@@
 
-Similar to the drop in variance allowing one to estimate the effect of each extra look averages being used over homogeneous areas, rises in the error variance can also be used to gauge the effects of underlying spatial variation on speckle filtering effectiveness.
-In original SAR domain, evaluating speckle filters' response to different heterogeneous areas are difficult, due to heteroskedastic conditions.
-In log-transformed domain, thanks to homoskedastic property, MSE will be shown to be relevant in evaluating speckle response to heterogeneous scenes (To be continued).
-%An simple 4x4 edge is added into the 256x256 area above, filters are applied and MSE reported.
-
-%\section{Evaluating Speckle Filters on Heterogenous Area}
-
-%For the purpose of comparative evaluation among speckle filters, the evaluation methodology needs to be quantitative and repeatable.
-%First, several test patterns is created to simulate and determine the performance of various speckle filters.
-%Then the methodology to evaluate speckle filter in heterogeneous area using the MSE criteria in log-transformed domain is described.
-%As the ground truth is available, the MSE criteria is validated by analysis and experimental results which show that lower MSE is correlated with better feature preservation.
-
-In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
+%In this section, the MSE criteria ($MSE_{true}$) is validated through experiments and analysis. 
 From a statistical estimation framework point of view, the use of MSE to evaluate statistical estimators is natural.
+In this section, the MSE criteria ($MSE_{true}$) in the log-transformed domain is validated through experiments and analysis. 
+Analytically, on clear-cut simple target-background patterns, MSE is shown to be related to the target / background separation capabilities. 
 Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
 	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
-Experimentally, on clear-cut simple target-background patterns, the results that follow will indicate that
+Experimentally, the results that follow will indicate that
 	the lower the MSE achievable by a speckle filter,
@@
 
-%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
-%log-transformed domain. 
-The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
-down into the requirements of radiometric preservation and speckle suppression.
-In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
-statistical estimators.
-Overall, while the MSE index combines the measurements of bias and variance evaluation, 
-	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
-	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
-We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.
-
-Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
-multiple times, the histograms of the target and background areas can be reliably obtained.
-%They are expected to be consistent in log-transformed domain.
-The target and background can then be seperated using a simple threshold based classification model.
-The separability of the two stochastic populations are judged by the standard ROC, 
-	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.
-
-The types of test pattern used in this paper include the followings:
+%%We believe that the qualitative requirement of speckle suppression can be quantified as the variance in 
+%%log-transformed domain. 
+%The general requirements of feature preservation, for simple scenes with only targets and clutter, can be broken 
+%down into the requirements of radiometric preservation and speckle suppression.
+%In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
+%statistical estimators.
+%Overall, while the MSE index combines the measurements of bias and variance evaluation, 
+%	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
+%	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
+%We show experimentally that MSE inversely correlates with the AUC index, for each of the simulated patterns.
+%
+%Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
+%multiple times, the histograms of the target and background areas can be reliably obtained.
+%%They are expected to be consistent in log-transformed domain.
+%The target and background can then be seperated using a simple threshold based classification model.
+%The separability of the two stochastic populations are judged by the standard ROC, 
+%	and the quantitative and normalized metric of AUC can then be used as an evaluation metric.
+
+The test patterns used in this section include:
   point targets, line targets, edge targets and a heterogeneous checker board. 
 These test patterns could of course be concatenated into a larger composite test image, 
-although we will consider them as separate images to allow easier analysis of the results.
+although they will be considered separately to allow easier analysis of the results.
 %However we would prefer to highlight the results separately for each individual area.
-Each pattern comprises two classes of ground-truth: background and target areas. We follow the convention used in the 
-radar community where the target is signified by the brighter area of the image. 
+Each pattern comprises two classes of ground-truth: background and target areas,
+with the target is signified by the brighter area of the image as conventionally used in the 
+radar community.
+%We follow the convention used in the 
+%radar community where the target is signified by the brighter area of the image. 
 Fig \ref{fig:hetero_patterns} shows a small section ($32 \times 32$ window) of each pattern.
@@
 	\subfloat[Line: each line is 2 pixels wide, separated by 6 pixels background]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/pattern_line2.png.eps} 	
@@
 	\subfloat[Edge: each stripe is 4 pixels in width]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/pattern_edge.png.eps} 	
@@
 	\subfloat[Point: each point is a $2 \times 2$ square spacing 6 pixels apart]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/pattern_point.png.eps} 	
@@
 	\subfloat[Checker board: the squares are 4 pixels wide each side]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/pattern_checker.png.eps} 	
@@
 Large patches of these patterns ($512 \times 512$) are first corrupted with single look speckle. The 
-filters are then applied onto these noised images.
-From a high-level perspective, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
+speckle filters are then applied onto these noised images.
+Since the filters are expected to be consistently behaved in the log-transformed domain, as we repeat a pattern 
+multiple times, the histograms of the target and background areas can be reliably obtained.
+The target and background can then be separated using a simple threshold based classification model.
+Using this method, the separability of the two stochastic populations are judged by the standard ROC, 
+	and the normalized metric of AUC can then be used as an evaluation criteria.
+
+%From a high-level perspective,
+Specifically, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
 evaluated by examining the separability of the two background and target populations.
@@
 
-\clearpage
+%\clearpage
 
@@
 	\subfloat[Simulated Image]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.edge.none.fi.jpg.eps} 	
@@
 	\subfloat[Kuan Filtered Image]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.edge.kuan.fi.jpg.eps} 	
@@
 	\subfloat[Histograms: Unfiltered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.histograms.edge.none.fi.png.eps} 	
@@
 	\subfloat[Histograms: Kuan Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.fi.png.eps} 	
@@
 	\subfloat[ROC: Unfiltered, AUC=0.738]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.roc_auc.edge.none.fi.png.eps} 	
@@
 	\subfloat[ROC: Kuan Filtered, AUC=0.885]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.roc_auc.edge.kuan.fi.png.eps} 	
@@
 \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
-Then the seperability of clutter and target populations depends only on the variance of the additive noise. 
+Then the separability of background and target populations depends only on the variance of the additive noise. 
 This variance is visualized as the horizontal spread of the histograms.
-Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance), 
+Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) of these sample histograms, 
 the better the separation capability.
@@
 
+Speaking in SAR domain terminology, the general requirements of feature preservation for SAR speckle filters can be broken 
+down into the requirements of radiometric preservation and speckle suppression.
+In the log-transformed domain, these smaller requirements are equivalent respectively to the bias and variance evaluation of 
+statistical estimators.
+Overall, while the MSE index combines the measurements of bias and variance evaluation, 
+	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
+	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
+%We show experimentally that MSE inversely correlates with the AUC index, for each of the %simulated patterns.
+Next the MSE is experimentally shown to be inversely correlated with the AUC index, for all simulated patterns.
+
 %Also the speckle suppression is related to the measured variance.
-Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
-evaluate the separability of the two histograms. 
+%Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
+%evaluate the separability of the two histograms. 
 Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and 
 patterns.
-It shows that the MSE is inversely correlated to this separability index.
-The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
-The results suggest that the lower MSE achievable by the filters would, in general, lead to better feature preservation.
-
+It suggests that the MSE is inversely correlated to this separability index.
+%The first column in Table \ref{tab:mse_auc_corr_coeff} quantitatively measures this statistical correlation.
+This statistical correlation is quantitatively measured in the first column of Table \ref{tab:mse_auc_corr_coeff}.
+%The results suggest that the lower MSE achievable by the filters would, in general, lead to better feature preservation.
+The results suggest that the lower MSE achievable by a SAR speckle filter would, in general, lead to better feature preservation in its filtered output.
+
+\afterpage{\clearpage}
 \begin{figure}
@@
 	\subfloat[Error Image: Unfiltered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.edge.none.gt.jpg.eps} 	
@@
 	\subfloat[Error Image: Kuan Filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
@@
 	\subfloat[Error Histograms: Unfiltered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
@@
 	\subfloat[Error Histograms: Kuan-filtered]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
@@
 In these scenarios, the ground-truth, and hence the true MSE, is not available.
-Therefore, only the residential MSE is computable.
-Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated, then the benchmark 
-MSE is also measurable.	
-Our heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
+Therefore, only the residual MSE is computable.
+Assuming the level of speckle noise (i.e. ENL or $MSE_{base}$) is known or can be estimated,
+  then the benchmark MSE, which is defined as the absolute difference between the residual and the base MSE, is also measurable.
+
+The proposed heuristic rule is that the best filtered results are those that have minimal benchmarked MSE. 
 This heuristic rule allow us to choose the ``best'' filtered results from an array of standard speckle filters 
 for a captured SAR image, where the ground-truth and hence true MSE is not available.
-Intuitively, the hypothesis is that the best speckle filter for a given scene is the one having its 
+The intuition for this conjecture is that the best speckle filter for a given scene is the one having its 
 removed variation being closest to the inherent speckle noise.
@@
 	\subfloat[A Rural Area in Vietnam]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
@@
 	\subfloat[A Suburb of Ha Noi]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.hanoi_suburb.gt.jpg.eps} 	
@@
 %	\subfloat[NTU Campus]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
 %		 \epsffile{src/Aerialcampus.eps} 	
@@
 %	\subfloat[Chu Thap Island of Vietnam]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
 %		 \epsffile{src/fiery.eps} 	
@@
 
+Then SAR speckle filters are applied onto the simulated images, and the various MSE in the log-transformed domain are computed.
 With the use of MSE being validated from previous experiments, 
-	the most suitable filter can be considered as the one with the lowest true MSE.
-Table \ref{tab:mse_true_noise_log_domain} shows that among the various filters used, 
+	the most suitable filter is deemed as the one with the lowest true MSE.
+The use of residual MSE is validated by investigating 
+Table \ref{tab:mse_true_noise_log_domain} which shows that among the various filters used, 
 	the most suitable filter is also the filter that 
@@
 
-%\begin{figure*}
 \begin{figure}
@@
 	\subfloat[Ground-Truth Image ]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
@@
 	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
@@
 	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
@@
 	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
@@
 	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
@@
 	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
-		 \epsfxsize=1.6in
-		 \epsfysize=1.6in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
@@
 \end{tabular}
-
 \caption{Filtering Simulated Real Images: Qualititative Validation}
@@
 \end{figure}
-%\end{figure*}
 
@@
 benchmark MSE.
-The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the criteria index is strongly 
+The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the evaluation index is strongly 
 correlated with feature classification capability, measured by the standard AUC index.
@@
 would probably suggest a more suitable filter.
-Fig. \ref{fig:real_image_results} tends to confirm this visually.
+Fig. \ref{fig:real_image_results} confirms this visually.
 %IVMThe conclusion in this can be found through further experiments with more images, 
@@
 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 
-\begin{figure}
+\begin{figure}[b]
 \begin{tabular}{c}
 	\subfloat[PDE Filter: $MSE_{benchmark}=3.8584$]{
-		 \epsfxsize=3cm
-		 \epsfysize=3cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.log.image.pde.jpg.eps} 	
@@
 	\subfloat[MAP Filter: $MSE_{benchmark}=1.4231$]{
-		 \epsfxsize=3cm
-		 \epsfysize=3cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.log.image.map.jpg.eps} 	
@@
 	\subfloat[Lee Filter: $MSE_{benchmark}=0.6995$]{
-		 \epsfxsize=3cm
-		 \epsfysize=3cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.log.image.lee.jpg.eps} 	
@@
 	\subfloat[Frost Filter: $MSE_{benchmark}=0.0024$]{
-		 \epsfxsize=3cm
-		 \epsfysize=3cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/heterogenous_real.log.image.frost.jpg.eps} 	
@@
 
+\afterpage{\clearpage}
 \subsection{Discussion and Conclusions}
@@
   to not only perform brilliantly on pre-filtered data,
-  but also be found practically working on post-filtered data.
+  but also practically work on post-filtered data.
 
@@
 However, interested filter designers are invited to download the open Matlab source code used in this paper 
-for evaluating their own designs
+to evaluate their own designs
   \footnote{This can be found at \texttt{http://www.lintech.org/Hai/Matlab}}.
@@
 requirements in the design of speckle filters.
-Its use also provides an absolute ground-truth as a solid base for comparison of results across different papers.
+Its use also provides an absolute ground-truth which can serves as a solid base for comparison of results across different papers.
 
@@
 While the proposed rule is heuristic, 
-	the experimental results presented in this paper are shown empirically to be valid.
-
-We distinctively divided speckle filtering into two distinct scenarios, that of homogeneity and heterogeneity.
+	the experimental results presented in this paper are shown to be valid empirically.
+
+We distinctively divided evaluation of SAR speckle filters into two distinct scenarios, that of homogeneity and heterogeneity.
 While perfect homogeneous ground truth can be defined, 
@@
 	would not perform that well.
+While the ranking of the speckle filters may change, the methodology to compare and choose the ``best’’ speckle filter should work regardless of the choice of patterns.
 
@@
 A possibly better alternative would be to predict the choice, escaping such massive requirements of computational power.
-This, however, is outside the scope of this paper.
+This, however, is outside the scope of this section.
 
@@
 
+\afterpage{\clearpage}
+
 %\section{FMLE POLSAR Speckle Filter using the consistent measures}
@@
   using the consistent measures of distance found in the homoskedastic log-transformed domain.
-The first sub-section theoretically illustrates how the consistent variance is linked to the ENL index.
-The second sub-section then demonstrate how the POLSAR speckle filters can be pratically and quantitatively evaluated over homogeneous areas by measuring the observable consistent variance after the log-transformation.
-The third sub-section finally illlustrates how POLSAR speckle filters can be visually evaluated on heterogeneous areas.
+The first subsection theoretically illustrates how the consistent variance is linked to the ENL index.
+The second sub-section then demonstrate how the POLSAR speckle filters can practically and quantitatively be evaluated over homogeneous areas.
+The third sub-section finally illustrates how POLSAR speckle filters can be visually evaluated on heterogeneous areas.
 
@@
 
-While Anfinsen solves the above equation to find ENL,
-  we took variance approach.
-Since we can ignore the constants $d\ln2 + d\ln{L} -ln|\Sigma|$ this approach might be simpler.
-
+%While Anfinsen solves the above equation to find ENL,
+%  we took variance approach.
+%Since we can ignore the constants $d\ln2 + d\ln{L} -ln|\Sigma|$ this approach might be simpler.
+
+This section discusses how ENL can be estimated using the log-variance approach in the homoskedastic, hence consistent variance, log-transformed domain.
+Specifically Eqn. TODO:REF can be rewritten as:
 \begin{equation}
@@
 \end{equation}
-
-For SAR, d=1 and $C_v=I$ then
+Theoretically speaking, the above equation can be solved for the unknown L, which would require some iterative, and hence intensive, computation.
+Extending the result in the previous sub-section for SAR, simpler estimation can be derived as:
+\begin{equation}
+  L = d \left[ \frac{1}{var(\ln|C_v|)} + 0.5 \right]
+\end{equation}
+The subsequent paragraphs details the derivation of this approximation.
+
+In the case of one-dimensional SAR, d=1 then $|C_v|=I$ and
 $var(\ln{I}) = \psi^1(L)=\sum^{\infty}_{i=L}1/i^2$.
-Since $1/L < \sum^{\infty}_{i=L}1/i^2 < 1/(L-1)$ Then an approximation is made to compute L as
-$var(\ln{I}) = 1/(L-0.5)$ or $L=1/var(\ln{I}) + 0.5 $
-
-For partial POLSAR, d=2, then
+Since $1/L < \sum^{\infty}_{i=L}1/i^2 < 1/(L-1)$, then $var(\ln{I})$ is bounded.
+Thus an approximation is made to compute L being:
+$L=1/var(\ln{I}) + 0.5 $ as $var(\ln{I}) \approx 1/(L-0.5)$.
+
+In the case of partial POLSAR, d=2, then
 \begin{equation}
@@
 \end{equation}
-That is $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
-Thus an approximation is made $var_d \left[ \ln |C_v| \right] = 2/(L-1)$
-or $L = 2/var_d \left[ \ln |C_v| \right] + 1$
-
-For full POLSAR, d=3, then
+Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
+Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
+Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$
+
+In the case of full POLSAR, d=3, then
 \begin{equation}
@@
 \end{equation}
-That is $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
-With L>3, it is trivial to prove that $3/(L-1.5)$ also is bounded by the above thresholds.
-Thus an approximation is made $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
+Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
+With $L>3$, it is trivial to prove that $3/(L-1.5)$ is also bounded by the same limits. %also is bounded by the above thresholds.
+Thus a similar approximation can be written as: $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
 or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$
 
-$L_{det}^2 = \ln{|Cv|}$
-$var(L_{det}^2)= \frac{2}{ENL-1}$
-$L_{est}=\frac{2}{var(L_{det}^2)} + 1$
-
-\begin{table}[h!]
-\centering
-\begin{tabular}{r|c|c}
- ENL & log-var(std)    & L est (enl)      \\
-\hline
-   2 & 2.2962 (0.1415) & 1.8734 (0.0509)  \\
-   3 & 1.0597 (0.0453) & 2.8899 (0.0812)  \\
-   4 & 0.6543 (0.0369) & 4.0646 (0.1831)  \\
-   5 & 0.4837 (0.0142) & 5.1373 (0.1239)  \\
-   6 & 0.3945 (0.0159) & 6.0755 (0.2129)  \\
-   7 & 0.3229 (0.0086) & 7.1966 (0.1640)  \\
-   8 & 0.2942 (0.0187) & 7.8209 (0.4616)  \\
-   9 & 0.2550 (0.0106) & 8.8517 (0.3200)  \\
-  10 & 0.2339 (0.0178) & 9.5867 (0.6273)  \\
-  11 & 0.2076 (0.0119) & 10.6565 (0.5543) \\
-  12 & 0.1839 (0.0112) & 11.9082 (0.6603) \\
-  13 & 0.1734 (0.0181) & 12.6228 (1.1593) \\
-  14 & 0.1555 (0.0085) & 13.8911 (0.6963) \\
-  15 & 0.1453 (0.0086) & 14.7963 (0.7803) \\
-  16 & 0.1316 (0.0083) & 16.2468 (0.9562) \\
-  17 & 0.1250 (0.0079) & 17.0421 (1.0042) \\
-  18 & 0.1146 (0.0035) & 18.4593 (0.5275) \\
-  19 & 0.1087 (0.0032) & 19.4153 (0.5420) \\
-  20 & 0.1056 (0.0060) & 19.9855 (1.1097) \\
-  21 & 0.0983 (0.0017) & 21.3548 (0.3492) \\
-  22 & 0.0945 (0.0056) & 22.2248 (1.2513) \\
-  23 & 0.0918 (0.0048) & 22.8346 (1.1785) \\
-  24 & 0.0845 (0.0043) & 24.7050 (1.2327) \\
-  25 & 0.0874 (0.0039) & 24.9125 (1.0243) \\
-\end{tabular}
-\caption{ POLSAR Speckle Suppression Power: ENL and Variance Log-Determinant }
-\label{tab:enl_in_log_domain}
-\end{table}
-
-Other fields in variance log-det table can include: var theory, and variance analysis
+In short, for all cases of SAR, partial-polarimetric and full-polarimetric SAR, Eqn.
+TODO:REF relates the ENL for an homogeneous POLSAR area to the variance of the log-determinant computed from POLSAR covariance matrices.
+The validation of this Eqn. has been carried out in Section TODO:REF.
+Since the ENL has routinely been used to evaluate (POL)SAR speckle filters, this mathematical relationship suggests that the same procedure applied in the log-transformed domain can, at the least, also be used to evaluate the performance of (POL)SAR speckle filters over homogeneous area.
+The next section will briefly explore this area.
+
+%\begin{table}[h!]
+%\centering
+%\begin{tabular}{r|c|c}
+% ENL & log-var(std)    & L est (enl)      \\
+%\hline
+%   2 & 2.2962 (0.1415) & 1.8734 (0.0509)  \\
+%   3 & 1.0597 (0.0453) & 2.8899 (0.0812)  \\
+%   4 & 0.6543 (0.0369) & 4.0646 (0.1831)  \\
+%   5 & 0.4837 (0.0142) & 5.1373 (0.1239)  \\
+%   6 & 0.3945 (0.0159) & 6.0755 (0.2129)  \\
+%   7 & 0.3229 (0.0086) & 7.1966 (0.1640)  \\
+%   8 & 0.2942 (0.0187) & 7.8209 (0.4616)  \\
+%   9 & 0.2550 (0.0106) & 8.8517 (0.3200)  \\
+%  10 & 0.2339 (0.0178) & 9.5867 (0.6273)  \\
+%  11 & 0.2076 (0.0119) & 10.6565 (0.5543) \\
+%  12 & 0.1839 (0.0112) & 11.9082 (0.6603) \\
+%  13 & 0.1734 (0.0181) & 12.6228 (1.1593) \\
+%  14 & 0.1555 (0.0085) & 13.8911 (0.6963) \\
+%  15 & 0.1453 (0.0086) & 14.7963 (0.7803) \\
+%  16 & 0.1316 (0.0083) & 16.2468 (0.9562) \\
+%  17 & 0.1250 (0.0079) & 17.0421 (1.0042) \\
+%  18 & 0.1146 (0.0035) & 18.4593 (0.5275) \\
+%  19 & 0.1087 (0.0032) & 19.4153 (0.5420) \\
+%  20 & 0.1056 (0.0060) & 19.9855 (1.1097) \\
+%  21 & 0.0983 (0.0017) & 21.3548 (0.3492) \\
+%  22 & 0.0945 (0.0056) & 22.2248 (1.2513) \\
+%  23 & 0.0918 (0.0048) & 22.8346 (1.1785) \\
+%  24 & 0.0845 (0.0043) & 24.7050 (1.2327) \\
+%  25 & 0.0874 (0.0039) & 24.9125 (1.0243) \\
+%\end{tabular}
+%\caption{ POLSAR Speckle Suppression Power: ENL and Variance Log-Determinant }
+%\label{tab:enl_in_log_domain}
+%\end{table}
+%
+%Other fields in variance log-det table can include: var theory, and variance analysis
 
@@
 	\subfloat[preserving consistency property: boxcar filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
                  \epsffile{images/AIRSAR_Flevoland.preserve_consistency.boxcar.eps} 
@@
 	\subfloat[preserving consistency property: fmle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/AIRSAR_Flevoland.preserve_consistency.fmle.eps} 	
@@
 
-This section describes how POLSAR filters can be evaluated
+It has also been found in \cite{Rignot_1993_TGRS_896} that for SAR dataset in its original domain: 
+   ratio offers a better dis-similarity measures than the standard substractive residual. 
+However, the ratio is not considered as being natural for digital display \cite{Medeiros_2003_IJRS}.
+Our previous work in the context of SAR speckle filtering found that
+  in log-transformed domains, this ratio is transformed into a subtractive residual that is excellent at visual evaluation.
+This section describes how the performance of POLSAR filters over homogeneous area can be evaluated
   using the consistent measures of distance found in the homoskedastic log-transformed domain.
+
 The previous section has illustrated theoretically how the variance of sample log-determinant is linked to the ENL index.
 This form the basis for evaluating POLSAR speckle filters over homogeneous areas.
-The procedure is simple.
+The procedure is simple and is described next.
 To evaluate a given POLSAR speckle filter over homogeneous areas,
@@
 The Equivant Number of Look (ENL) is then estimated
-  either by referencing the prepared graphs given by Eqn. ???
-  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. ???.
-
-In order for such a procedure to generic enough, it is important that the given POLSAR speckle filter to preserve the consistency property.
+  either by referencing the prepared graphs given by Eqn. TODO:REF
+  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. TODO:REF.
+The estimated ENL and equivalently the measured log-variance is finally used to evaluate the speckle suppression power of the filters.
+It is common concensus that the higher the ENL estimated,
+  which also means the lower the log-variance measured,
+  leads to better POLSAR speckle filters in terms of suppressing speckle noise.
+
+%In order for such a procedure to generic enough, however, it is important that the given POLSAR speckle filter to preserve the consistency property.
+%That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the dis-similarity measures presented above.
+%Fig. TODO:REF presents two example plots for such a test.
+%Experiment is carried out for the 3x3 POLSAR boxcar filter to show that it preserves the consistency property.
+%The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
+%Log-determinant and the contrast measure is computed for the inputs and outputs filtered POLSAR data,
+%  and their plots are presented in Fig. ???
+
+In order for such a procedure to be generic, however,
+  it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
 That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the dis-similarity measures presented above.
-Fig. ??? presents two example plots for such a test.
-Experiment is carried out for the 3x3 POLSAR boxcar filter to show that it preserves the consistency property.
+%Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that:
+An experiment is carried out to show that:
+  the 3x3 POLSAR boxcar filter preserves the consistency property.
 The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
 Log-determinant and the contrast measure is computed for the inputs and outputs filtered POLSAR data,
-  and their plots are presented in Fig. ???
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinants histograms of boxcar 3x3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
-		 \label{log_determinant}
-	} 
-	\hfill	
-	\subfloat[Contrast histograms of boxcar 3x3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
-		 \label{contrast}
-	}   
-\end{tabular}
-\caption{POLSAR 3x3 boxcar filter preserves the consistency property.
-Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
-\label{fig:boxcar_3x3_preserves_consistency}
-\end{figure}
-
+  and their plots are presented in Fig. \ref{fig:boxcar_3x3_preserves_consistency}.
+%In fact, the test procedure can be applied on any of the models presented above.  
 Apparently for log-determinant histograms,
-  while the location of the filtered plots differs depending on the underlysing signal $\Sigma_v$,
+  while the location of the filtered plots differs depending on the underlying signal $\Sigma_v$,
   the shape of the plots, for both pre-filtered and post-filtered data, is invariant to that underlying signal.
@@
   thus the contrast plots for the filtered output should overlap each other to show consistency.
-
+Similar procedures can also be applied using any of the models presented above.
+
+\begin{figure}
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinants histograms of boxcar 3x3 speckle filter]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+		 \label{log_determinant}
+	} 
+	\hfill	
+	\subfloat[Contrast histograms of boxcar 3x3 speckle filter]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+		 \label{contrast}
+	}   
+\end{tabular}
+\caption{POLSAR 3x3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlying signal $\Sigma_v$ the shapes of the histograms should be the same.}
+\label{fig:boxcar_3x3_preserves_consistency}
+\end{figure}
+
+%The consistency property of POLSAR speckle filter is important
+%  not only to make the estimation of ENL become general enough
+%  but also to ensure that any classification / detection algorithm
+%    which is based on the scalar and consistent measures of distance would work on both pre-filtered and post-filtered data.
 The consistency property of POLSAR speckle filter is important
-  not only to make the estimation of ENL become general enough
-  but also to ensure that any classification / detection algorithm
+  not only to make the estimation of ENL become general enough.
+It is also important in ensuring that any classification / detection algorithm
     which is based on the scalar and consistent measures of distance would work on both pre-filtered and post-filtered data.
+Otherwise if a POLSAR speckle filter gives different plots for different homogeneous areas,
+  then not only its ENL estimation will be dependent on the underlying signal, 
+  its output also shall not be consistent and homoskedastic. %follow the statistical distribution family that characterize multi-look POLSAR.
+In short, the preservation of this consistency is believed to be an important consideration for POLSAR speckle filter
+  which should also be evaluated together with the evaluation of speckle suppression power of POLSAR speckle filters.
+  %if we want a host of detection and classification algorithms to work on our filtered data output.
 
@@
 
-Over heterogeneous area, the consistent measures of distance may also be valuable tools in helping to evaluate POLSAR speckle filters.
+Over heterogeneous area, the consistent measures of distance may also be important tools in helping to evaluate POLSAR speckle filters.
 For a start, since the model for log-determinant is additive and homoskedastic,
-  log-determinant images may be better naturally suited for gray-level digital images.
+  log-determinant images is naturally more suitable for gray-level digital images.
 Especially for evaluation of statistical estimators,
   the estimators' error / residual plays an important role.
+Specifically, it is both important and convenient to investigate the estimator's error and/or residual image(s).
+
 Ideally speaking, under the context of additive model,
-  the perfect estimators' residual should be consists of only and wholly random noise.
+  the perfect estimators' residual should only consists of random noise.
 And Gauss-Markov theorem, which works under the assumption of homoskedasticity, states that the optimal estimator should have minimal Mean Squared Error.
@@
 
-Our previous work TODO:CITE explored the hypothesis context of SAR data.
-Here an experiment is carried out to illustrate the use of the consistent and homoskedastic measures of distance in evaluating the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial POLSAR data (HH-HV).
-A square 740x740 portion of the AIRSAR dataset is extracted, and the two POLSAR speckle filters is applied.
-The log-determinant images of outputs are display in Fig. ???.
-For future further analysis, the residual defined as the distance between the log-determinants of the outputs and the original input is computed for both cases and the images are also displayed in the same figure.
-Assumming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
-  the Mean Squared Error (MSE) of the filters are computed.
-Using the value of 4 as the ENL for the AIRSAR Flevoland dataset,
-  the ``optimal'' value is computed as
-%  \begin{equation}
-%    %avg(\mathbb{L})^2 + var(\mathbb{L}) = mse(\mathbb{L}) =
-%    \left[ \psi^0(4) + \psi^0(3) - 2\ln4 \right]^2 + \left[ \psi^1(4) + \psi^1(3) \right] = 1.0312 
-%  \end{equation}
-by setting $d=2,L=4$ into Eqn. (TODO:REF) making the expected MSE being $mse(\mathbb{L})=1.0132$.
+%Our previous work TODO:CITE explored the hypothesis context of SAR data.
+%Here an experiment is carried out to illustrate the use of the consistent and homoskedastic measures of distance in evaluating the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial POLSAR data (HH-HV).
+%A square 740x740 portion of the AIRSAR dataset is extracted, and the two POLSAR speckle filters is applied.
+%The log-determinant images of outputs are display in Fig. ???.
+%For future further analysis, the residual defined as the distance between the log-determinants of the outputs and the original input is computed for both cases and the images are also displayed in the same figure.
+%Assumming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+%  the Mean Squared Error (MSE) of the filters are computed.
+%Using the value of 4 as the ENL for the AIRSAR Flevoland dataset,
+%  the ``optimal'' value is computed as
+%%  \begin{equation}
+%%    %avg(\mathbb{L})^2 + var(\mathbb{L}) = mse(\mathbb{L}) =
+%%    \left[ \psi^0(4) + \psi^0(3) - 2\ln4 \right]^2 + \left[ \psi^1(4) + \psi^1(3) \right] = 1.0312 
+%%  \end{equation}
+%by setting $d=2,L=4$ into Eqn. (TODO:REF) making the expected MSE being $mse(\mathbb{L})=1.0132$.
+
+To illustrate the above analysis, an experiment is carried out to evaluate the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+A square 700x700 portion of the AIRSAR dataset is extracted,
+  and the two POLSAR speckle filters are applied on to the patch.
+Then the log-determinant images of the filtered outputs are presented in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time the residual is computed for both filters and the images are also displayed in the same figure.
+Assuming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+This optimal value is computed   
+by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
 
@@
 	\subfloat[Log-determinant Image of boxcar 3x3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
@@
 	\subfloat[Log-determinant Image of boxcar 5x5 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
@@
 	\subfloat[Image of Log-determinant Residual for 3x3 filter (MSE=1.5594)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
@@
 	\subfloat[Image of Log-determinant Residual for 5x5 filter (MSE=2.1420)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
@@
 %another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
-Visually speaking, while the worse blurring effects of the boxcar 5x5 speckle filter is quite hard to be observed in the final image of the filtered output,
-  such detection can be made relatively easier by just by visually investigating the residual image.
-And when quantified number is taken out and compared with the expected level of noise to be removed,
-  the excessive blurring effects of the 5x5 filter become crystally clear.
-In fact, even the 3x3 boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.% of the 3x3 boxcar filter suggests that   
-But a full explaination for that is outside the scope of this paper.
-
-\begin{figure}
- 	\subfloat[boxcar filter: log-determinant image]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/AIRSAR_Flevoland.boxcar.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[boxcar filter: residual image]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/AIRSAR_Flevoland.boxcar.residual.eps} 	
-		 \label{contrast_2x2}
-	}  \\
- 	\subfloat[fmle filter: log-determinant image]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/AIRSAR_Flevoland.fmle.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[fmle filter: residual image]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/AIRSAR_Flevoland.fmle.residual.eps} 	
-		 \label{contrast_2x2}
-	}   
-  \caption{AIRSAR image in log-determinant format and its variance as an edge-indicator}  
-\end{figure}
+
+In visual and qualitative evaluation, Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only the log-determinant image can offer nice visualization of the scene, 
+  the residual images also help in visualizing the distortion impact of the filter can also be made visible by the residual image.
+Specifically, while it is quite hard to observe the worsening blurring-effects of the 5x5 boxcar speckle filter as compared to the 3x3 filter
+in the additive log-determinant image of the filtered output, 
+  such a conclusion can be made relatively easier by visually investigating the residual image.
+
+And when quantified evaluation is carried out
+  where the residual MSE is compared with the expected level of noise to be removed,
+  the excessive blurring effects of the 5x5 filter become crystal clear.
+In fact, even the 3x3 boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.
+%A conclusion which is hard to make
+
+In short, while it may be hard to make such a conclusion just by looking at the filtered imagery,
+  by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer conclusive evidence.
+
+Much more detailed discussion on this topic, 
+  in the context of evaluating SAR speckle filters is given in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters.
+%This section serves more as an illustration of how the proposed theoretical model can be applied to practical scenario,
+%  as it is not as a full proposal for such an evaluation procedure for POLSAR speckle filters.
+Specifically, this is an illustration of how the proposed theoretical model can possibly be applied to a practical scenario, rather than a full evaluation procedure proposal.
+
+%Visually speaking, while the worse blurring effects of the boxcar 5x5 speckle filter is quite hard to be observed in the final image of the filtered output,
+%  such detection can be made relatively easier by just by visually investigating the residual image.
+%And when quantified number is taken out and compared with the expected level of noise to be removed,
+%  the excessive blurring effects of the 5x5 filter become crystally clear.
+%In fact, even the 3x3 boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.% of the 3x3 boxcar filter suggests that   
+%But a full explaination for that is outside the scope of this paper.
+
+%\begin{figure}
+% 	\subfloat[boxcar filter: log-determinant image]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%                 \epsffile{images/AIRSAR_Flevoland.boxcar.eps} 
+%		 \label{dispersion_2x2}
+%	} 
+%	\hfill	
+%	\subfloat[boxcar filter: residual image]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/AIRSAR_Flevoland.boxcar.residual.eps} 	
+%		 \label{contrast_2x2}
+%	}  \\
+% 	\subfloat[fmle filter: log-determinant image]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%                 \epsffile{images/AIRSAR_Flevoland.fmle.eps} 
+%		 \label{dispersion_2x2}
+%	} 
+%	\hfill	
+%	\subfloat[fmle filter: residual image]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/AIRSAR_Flevoland.fmle.residual.eps} 	
+%		 \label{contrast_2x2}
+%	}   
+%  \caption{AIRSAR image in log-determinant format and its variance as an edge-indicator}  
+%\end{figure}
+%

### 2013-04-22 6/conclusional_discussion.tex
added 201304_Apr22

@@
 
-\section{Result Evaluation and Discussion}
+In the first section of this chapter,
+  the exciting research work is reviewed and summarized.
+Then the advantages and the beneficial contributions of the polsar homoskedastic models is presented in section \ref{sec:conclusion_contribution}.
+Section \ref{sec:conclusion_future_work} will then point out a few of its probable short comings, together with several possible directions for future research work.
+Finally Section \ref{sec:conclusion_final} provides the final conclusions in wrapping up this thesis.
+
+\section{Evaluation and Discussion}
+\label{sec:conclusion_discussion}
 
@@
 \section{Contributions of the Thesis}
-
+\label{sec:conclusion_contribution}
 %\subsection{POLSAR Consistent Measures of Distance}
@@
 
-\section{Possible Future Work and Conclusion}
+%\section{Possible Future Work and Conclusion}
 
-\subsection{Possibilities for Future Work}
+\section{Possible Future Work}
+\label{sec:conclusion_future_work}
+
+As the additive noise PDF in log-domain has been worked out, we hypothesize that the true back-scattering coefficient PDF, also in log-domain, can be estimated through regularized deconvolution algorithms.
+If an algorithm could be designed to estimate such PDF, we believe this would present an improvement for a whole class of speckle filters, namely the Maximum-A-Priori (MAP) class, which up to now, still assumes the true PDF will follow certain known fixed distributions.
+%It is hoped that with the true PDF now being estimatable from the data itself, a better speckle filtering algorithm, in log-transformed domain, can be developed.
+
+For multi-channel SAR data, as reviewed in Chapter 2, speckle filtering for the off-diagonal element $S_hS_v^*$ of the covariance matrix is still an open question.
+Our observation has been that these elements are also available in dual-polarization SAR data, they specifically are part of Stokes parameters.
+As mentioned earlier, Stokes parameters have been largely ignored in polarimetric literature, until recently asserted again by Raney in 2006 \cite{Raney_2006_IGARSS}.
+Mathematically, Stokes parameters can be written as:
+\begin{equation}
+S = 
+\left(
+	\begin{array} {c}
+		S_hS_h + S_vS_v \\
+		S_hS_h - S_vS_v \\
+		2 \Re{(S_hS_v^*)} \\
+		2 \Im{(S_hS_v^*)}
+	\end{array}
+\right)
+= 
+\left(
+	\begin{array} {c}
+		S_hS_h + S_vS_v \\
+		S_hS_h - S_vS_v \\
+		S_+S_+ - S_-S_- \\
+		S_lS_l - S_rS_r
+	\end{array}
+\right)
+\end{equation}
+We have evidence, and hypothesize that $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ will have the same physical and statistical properties as the normal $S_hS_h$, $S_vS_v$.
+If our hypothesis can be proven rigorously, it may then be possible to build and validate a statistical model for all elements in the covariance matrix of Polarimetric SAR data, namely $S_hS_h$, $S_vS_v$, $\Re{( S_hS_v^*)}$, $\Im{( S_hS_v^* )}$.
+Also, speckle filtering on off-diagonal elements can be carried out using techniques, that were originally developed for single-channel SAR data, and up to now is only applicable to the diagonal elements of the covariance matrix.
+
+%\subsubsection{Theory Development and Research Strategy}
+For single channel SAR data, we propose the use of a log transform to evaluate speckle filter's performance. 
+We have proved that homoskedasticity property is indeed manifested in the log-domain.
+The traditional performance index in comparing speckle filters, i.e.
+the Equivalent Number of Looks (ENL), has also been shown to be related and calculable from the standard Mean Squared Error (MSE) inside the log-domain.
+We are working to prove that, with the homoskedastic property asserted, the universal Mean Squared Error can be a good performance indicator, even on heterogeneous spatial variations.
+
+Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able.
+In figure 
+	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
+the underlying single channel gray image histogram is presented along with the noise PDF, in the log-transformed domain. 
+As the noise is additive, it is expected that the noise PDF will act as a point spread function.
+This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
+This fact is evidenced in figure 
+	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
+where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
+We hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods.
+We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.
+
+\begin{figure}[h!]
+\centering
+	\subfloat[Original image's histogram and PSF]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+ 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
+		 \label{fig:noise_pdf_as_psf:conv_inputs}
+	} 
+	\hfill
+	\subfloat[Convoluted and speckled image histogram]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
+		 \label{fig:noise_pdf_as_psf:conv_output_observable}
+	}
+\caption{Observable convolution of PSF}
+\label{fig:noise_pdf_as_psf}
+\end{figure}
+
+For multi-channel SAR data, we focus on partial polarimetric SAR satellite data.
+Attempts have been made to model the data, especially the off-diagonal covariance matrix elements, i.e. $S_hS_v^*$.
+However, the models are overly complicated which made proposed PolSAR speckle suppression algorithms became overly complex (see polarimetric data modelling section in Chapter 2).
+We preferred an alternative approach.
+We propose to transform the polarization basis of dual-polarized SAR data to help estimate this element.
+
+We first pick up a recent revelation by Raney, 2006 \cite{Raney_2006_IGARSS}, that the back scattering waves' polarization captured in dual-pol data can be completely described using Stokes parameters.
+%From the usually given pairs of $S_h$ and $S_v$, Raney has shown that Stokes parameters can be computed.
+Furthermore, Stokes parameters can be measured in multiple polarization basis, which can also be synthesized from the given data (see polarization basis transform section in Chapter 2).
+%Both transformations, i.e. from $\{h,v\}$ to circular basis $\{l,r\}$ and from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ modes, are special cases of the transformation formula.
+That is:
+	the measured signal at $\pi/4$ linear polarizer as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
+	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
+	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
+	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
+
+The Stokes vectors, when aligned at these transformed projections are given by the following well-known equation:
+\begin{equation}
+S_t = \left(
+\begin{array}{c}
+ |\xi_h|^2 + |\xi_v|^2 \\
+ |\xi_h|^2 - |\xi_v|^2 \\
+ 2 \Re( \xi_h \xi_v^* ) \\
+ 2 \Im( \xi_h \xi_v^* ) 
+\end{array}
+\right)
+= \left(
+\begin{array}{c}
+ |\xi_+|^2 + |\xi_-|^2 \\
+ -2 \Re( \xi_+^* \xi_- ) \\
+ |\xi_+|^2 - |\xi_-|^2 \\
+ 2 \Im( \xi_+^* \xi_- ) 
+\end{array}
+\right)
+= \left(
+\begin{array}{c}
+ |\xi_l|^2 + |\xi_r|^2 \\
+ 2 \Re( \xi_l^* \xi_r ) \\
+ -2 \Im( \xi_l^* \xi_r ) \\ 
+ |\xi_l|^2 - |\xi_r|^2 
+\end{array}
+\right)  
+\end{equation}
+
+Evidently, the real and imaginary parts of $S_hS_v^*$ is closely related to Stokes Parameters.
+Specifically they may be considered as the subtraction of two random SAR intensity variables, e.g., $|S_l|^2 - |S_r|^2$. 
+%Since ShSh is exponential this can be calculated through convolutions, if each channels are independent. 
+%Laplace distribution is the difference between two identical exponential distributions. 
+For the same traditional reasoning of $|S_h|^2$ and $|S_v|^2$, we hypothesize that all the four intensities calculated from the transformation of polarization basis, i.e., $|S_+|^2$, $|S_-|^2$, $|S_l|^2$, $|S_r|^2$, follow negative exponential distributions.
+The hypothesis is supported by our preliminary experiment results, where we synthesize the basis transformed intensity from real-measured polarimetric data.
+It then follows that $S_hS_v^*$ can be despeckled by independently de-speckling the four synthesized intensities.
+Read chapter 4 for our work in progress in single-channel SAR speckle filtering.
+We hope to go further speculating that: the speckle-filtering methodologies in dual-polarization SAR data is extensible to full polarimetric SAR data.
 
@@
 
-\subsection{Conclusion}
+\section{Conclusion}
+\label{sec:conclusion_final}
 

### 2013-04-22 paper_dev/article.tex
201303_Mar01
added 201304_Apr22

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
-
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
+%\documentclass[a4paper,10pt]{article}
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{cite} %for citations
+\usepackage{url}
+
+ %this is for math typing (eg: cases)
+\usepackage{amsmath}
+   \usepackage{amsfonts}   % if you want the fonts
+   \usepackage{amssymb}    % if you want extra symbols
+\usepackage{epsfig} %for figures
+
+\usepackage[center]{caption}%for captions
+\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+
+%\nonstopmode
+
+%opening
+\title{
+  %Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
+  Scalar and Representative Models for Polarimetric SAR Data
+}
+
+%\author{Thanh-Hai Le, Ian McLoughlin}
+\author{Thanh-Hai~Le,
+        Ian~McLoughlin, 
+	and Chan-Hua~Vun%
+\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+%	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2013; revised ?.}}
+
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+  While statistical models are important in understanding the stochastic nature of Polarimetric SAR (POLSAR),
+  scalar discrimination measures are routinely used in processing this multi-dimensional data.
+  Ideally speaking, the latter should be drived from the former.
+  As far as we know, however, it has not exactly been so for the case of POLSAR.
+  In this paper, a couple of statistical models for the determinant of the POLSAR covariance matrix and its log-transformed derivations are proposed.
+  These scalar models for the determinant of the POLSAR covariance matrix are shown to be respresentative
+    since this observable is neatly transformed into the traditional SAR intensity
+    when the generic multi-dimensional polarimetry is collapsed into the case of one-dimensional SAR. %case of traditional SAR data.
+  Similar to SAR, the generic model for POLSAR is also shown to be multiplicative and heteroskedastic in the original domain 
+    and the logarithmic transformation converts this into a more familiar additve and homoskedastic model.
+  Moreover, the scalar property of these statistical models lead to the derivation of several statistical discrimination measures. %homoskedastic measures of distance.
+  All of these statistical models are validated on real-life captured data
+    and they are shown to be applicable even when the theoretical ``independent samples'' assumption is violated in practice.
+  %The paper also illustrates a couple of benefits of these models, specifically for using the homoskedastic discrimination measures.
+  %A couple of benefits for using these homoskedastic dis-similarity measures are then illustrated in this paper.
+  %These homoskedastic measures of distance
+  The combination of scalar, additive and homoskedastic properties of the derived statistical models bring about a couple of benefits, which are also described in this paper.
+  First, compared to the original multiplicative domain, %dis-criminative measure of ratio,
+    the additive log-transformed fit more naturally with the linear nature of digital imagery.
+  Second, since the Gauss-Markov theorem is again applicable in the homoskedastic log-transformed domain,
+    the use of Mean Squared Error (MSE) as an reliable objective function for POLSAR speckle filters is briefly explored.
+%This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
+%The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
+%The dissimilarity measurements, 
+%computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
+%It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+%  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
+%This puts the SAR intensity statistics to lie within the natural coverage of this new theoretical model for POLSAR.
+%Not only comprehensive theoretically, the statistical model is also robust in handling practical data. 
+%It can be validated and match reasonably well  with practical data.
+%Moreover, the match can be further improved 
+%  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
+%  instead of blind acceptance of the number of looks figure reported by the SAR processor.
+%The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+\end{abstract}
+
+\begin{IEEEkeywords}
+Polarimetric Synthetic aperture radar, Electromagnetic Modeling, Multidimensional signal processing  
+\end{IEEEkeywords}
+
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+%\section{POLSAR data: statistical analysis and logarithmic transformation}
+
+In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
+As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
+POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
+Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
+
+With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
+The complex data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
+Under this condition, it is very important to understand the statistical models for (POL)SAR data.
+
+While the statistical models for homogeneous areas of one-dimensional SAR data have been developed,
+%  in extending the model toward heterogeneous images, the impact of heteroskedasticity has virtually been ignored.
+%Specifically the concept of distance as a measure of dis-similarity is seriously flawed, as it is widely known that ratio offers a better discrimination measure TODOCITE.
+%This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
+%From this log-transformed model, a few consistent measures of distance is proposed. 
+%in a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtraction, and thus distance.
+  in extending our understanding towards multi-dimensional POLSAR data, an important issue needs to be addressed.
+The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
+While different statistical models have been developed for different POLSAR observables,
+  for a statistical model to be useful, scalar discrimination measures need to be derived from it.
+Thus practical application for POLSAR data processing requires the dis-similarity measure to be scalar, consistent and preferably homoskedastic on one hand.
+On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
+
+In this paper, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
+The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario.
+Under this transformation, the determinant of the POLSAR covariance matrix is converted into the standard SAR intensity.
+Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
+And since POLSAR can be viewed as a multi-dimensional extension of SAR, the paper describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
+
+%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
+%Firstly, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear scale nature of digital imagery.
+%Secondly, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss Markov theorem is again applicable, the universal MSE deserves to be reviewed as a reliable objective function / criteria for (POL)SAR estimators.
+%This may open up a number of different research directions for future studies of (POL)SAR.
+%As example demonstrations of how these models and distance measures can be used, a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
+
+Specifically, the rest of this paper is structured as follows.
+After the related work in literature is critically reviewed in Section \ref{sec:lit_review},
+  Section \ref{sec:theoretical_model} presents the theoretical models for both partial and full polarimetric SAR and their derived discrimination measures.
+The representative power of the scalar models are illuminated in Section \ref{sec:sar_special_case_of_polsar},
+  which details how the proposed models for the multi-variate POLSAR also includes the well-known models for the traditional SAR as its special univariate case.
+%can be used to derive the well-known models for the univariate SAR data as its special case.
+Besides being theoretically comprehensive, 
+  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+To demonstrate the application of these scalar and representative models, 
+  Section \ref{sec:evaluating_polsar_filters} explores how they can be used to evaluate POLSAR speckle filters.   
+In the end, Section \ref{sec:discussion_conclusion} provides the final conclusion of the paper.
+%critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
+%In this paper, the above results are exploited in the context of POLSAR data processing.
+In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
+The paper is structured as follows:
+%  after the preceding introduction to the basics of POLSAR statistical analysis,
+%  the second section briefly reviews related work in published literature.
+%Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+%The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+%And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+%Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+%After the model is presented for both partial and full polarimetric SAR data,
+%  section \ref{sec:sar_special_case_of_polsar} discusses
+%    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+%To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
+%  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
+%Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
+\section{Related Work in Literature}
+\label{sec:lit_review}
+
+This section critically review the related work in published literature.
+Specifically, the first sub-section shows that while many discrimination measures have been proposed for POLSAR data,
+  almost all of them depends on the likelihood statistical test for complex Wishart distribution.
+Unfortunately, in the original proposed work \cite{Conradsen_2003_TGRS_4}, while an exact distribution is to be expected, only an asymptotic distribution was given.
+The second sub-section reviews various statistical models for different POLSAR observables.
+Its purpose is to show that none of these models, as far as we know, led to statistically consistent discrimination measures.
+
+\subsection{POLSAR Discrimination Measures}
+
+This sub-section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
+In particular, a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+will be briefly reviewed.
+%specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+
+The commonly used measure of distance for matrices are either the Euclidean or the Manhattan distance,
+  which are defined in the following equations, respectively:
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
+  probably because of the multiplicative nature of the data.
+%In the context of polsar covariance matrix, however, they are not widely used 
+%  probably because of the multiplicative nature of the data.
+
+In the field of POLSAR, the Wishart Distance is probably the most widely used as part of the well-known Wishart Classifier \cite{Lee_1999_TGRS}.
+The distance is defined as \cite{Lee_1994_IJRS_2299}
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dissimilarity measures.
+These include the asymmetric and symmetric refined wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance \cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+.
+
+In comparison to these formulae, the distance measures for two covariance matrices proposed in this paper can be written as:
+\begin{equation}
+  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
+\end{equation}
+At first glance, while the propose formula may be a lot simpler, it still operates in a similar way to others in making use of the log-determinant.
+
+Closer investigation of these dis-similarity measures reveals that most of them are related to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered as the special case of the Wishart Statistical Test distance, where the two data set have the same number of look, i.e. $L_x=L_y$.
+It is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper has fixed statistical behaviour, by comparing the symmetric and asymmetric versions of the refined Wishart distance, assuming that they are shown to follow fixed distributions.
+
+The close relation among these is further supported by the fact that
+all of the papers proposing these measures referenced the statistical model developed in \cite{Conradsen_2003_TGRS_4} as their foundation.
+%Interestingly, the change detection model in \cite{Conradsen_2003_TGRS_4} also make use of determinant ratio and log determinant in its derivation.  
+%The next sub-section will illustrate how the log-determinant model presented in this paper can offer an alternative and simple derivation for the change-detection statistics.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrix is considered:  
+\begin{equation*}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation*}
+
+Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{eqnarray}
+
+To detect changes, a test statistics is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, originally in the proposed work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution is derived.
+%In this sub-section, a statistical model is developed for this measure of distance.
+Since both $Z_x$ and $Z_y$ follow a complex Wishart distribution with $L_x$ and $L_y$ degrees of freedom,
+  $Z_x+Z_y$ also follows the complex Wishart distribution with $(L_x + L_y)$ degrees of freedom.
+In view of the models for $|C_v|$ and $\ln|C_v|$ developed in this paper (Eqns. \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution}),
+  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+  but the whole statistical distribution for it can be simulated as well.
+
+\subsection{Scalar Observables and Statistical Models for POLSAR Data}
+
+Of course, discrimination measures are not the only way to carry out classification tasks in POLSAR.
+Another common approach is to carry out classification using POLSAR observables identified by different target decomposition theorems.
+In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes is evaluated.
+While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, at its conclusion, the paper indicated that ``it is impossible to indentify the best one''
+  as these ``representations ... do not show a precise trend''.
+%Instead an MLP classification approach were employed. 
+To be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
+  and thus they are not to be used individually for the purpose of single-handedly representing POLSAR data.
+
+Given the joint distribution for POLSAR is known to be the multi-variate Complex Wishart distribution,
+  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
+However, such derivations are no trivial tasks,
+  as the data is much more complex and the field is much less matured than the traditional SAR statistical modelling.
+Thus the strategy of the pioneering work is to tackle simpler versions of polarimetry.
+
+POLSAR data is commonly represented by its covariance matrix.
+For full-pol the covariance matrix has the form of
+\begin{equation*}
+C_3 = 
+\begin{bmatrix}
+S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
+\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
+S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+For part-pol, it reduces to either:
+\begin{equation*}
+  C_{2,h} =
+  \begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{hv}^* \\
+    S_{hh}^*S_{hv} & S_{hv}^2
+  \end{bmatrix};
+  C_{2,v} =
+  \begin{bmatrix}
+    S_{hv}^2 & S_{hv}S_{vv}^* \\
+    S_{hv}^*S_{vv} & S_{vv}^2
+  \end{bmatrix}
+\end{equation*}
+Obviously, the statistical behavior of $C_3$ can be understood by understanding the behavior of $C_{2h},C_{2v}$ and
+\begin{equation*}
+  C_{2,c} = 
+\begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{vv}^* \\
+    S_{hh}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+
+While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
+  $C_{2c}$ is a totally made-up mathematical term from the full-pol covariance matrix.
+In fact, in the field of Polarimetric SAR, $C_{2v}, C_{2h}$ is called cross-pol and $C_{2c}$ is called co-pol covariance matrices.
+Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
+\begin{equation*}
+  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
+\end{equation*}
+with $\phi=arg(\rho)$ is the phase difference angle.
+In $C_{2v}, C_{2h}$ of optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
+  and $\phi_v,\phi_h$ are very random, due to little correlation between orthogonal polarization in monochromatic EM waves.
+%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
+Their equivalent lie in the ``natural surface'' case of POLSAR,
+  where  it is common to consider: $|\rho_v|=|\rho_h|=0$.
+This is, however, not true in the general case of POLSAR.  
+Specifically for $C_{2c}$, since there are correlation between the two co-pol channels,
+  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.
+
+In the field of optical physics,
+  under the assumption of no correlation between cross-polarized channels,
+  \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} derived the statistical models for $C_{2h},C_{2v}$.
+The observables that have been studied are:
+\begin{enumerate}
+\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
+  \begin{enumerate}
+  \item the total power $S_0=C_{11}^2 + C_{22}^2$,
+  \item the ratio of minor to major axis of the polarization ellipse  $\epsilon=\lambda_2/\lambda_1$,
+  \item and $\psi$ the angle that the ellipse major axis makes with horizontal axis,
+  \end{enumerate}
+\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
+  \begin{enumerate}
+  \item $S_0 = C_{11}^2 + C_{22}^2$
+  \item $S_1 = C_{11}^2 - C_{22}^2$
+  \item $S_2 = \Re (C_{12})$
+  \item $S_3 = \Im (C_{12})$
+  \end{enumerate}
+\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
+\end{enumerate}
+In the field of POLSAR, under the assumption of significant correlation between polarized channels,
+  \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} derived the statistical models for note only $C_{2h},C_{2v}$ but also $C_{2c}$.
+Specifically the following observables were studied:  
+  \begin{enumerate}
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \end{enumerate}
+
+Furthermore, other studies has offered
+  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
+  the statistical model for
+  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
+While these models undoubtedly help in understanding the SAR data,
+  individually none of them statisfies the dual criteria of
+  1) resulting in statistically consistent discrimination measures and
+  2) being an representative observable for the complex POLSAR data.
+  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
+
+\section{The Scalar Statistical Models for POLSAR}  
+\label{sec:theoretical_model}
+
+In this section, several scalar statistical models for POLSAR are presented.
+After the first sub-section briefly reviews related work in published literature,
+  sub-section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+
+\subsection{The Basics of POLSAR Statistical Analysis}
+
+In this paper, the POLSAR scattering vector is denoted as $s$.
 In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
@@
 
-Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
+Let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
   where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
-Assuming all the elements in $s$ are independent
-  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
+Assuming %all the elements in $s$ are independent and
+  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
   then the probably density function (PDF) of $s$ can be written as:
@@
 \end{equation}
-where $|M|$ denotes the determinant of the matrix $M$.
-
-As covariance matrix is only defined on multiple data points,
-  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
-They are formed as the mean of Hermitian outer product of single-look scattering vectors
+where $||$ denotes the matrix determinant.
+
+As the covariance matrix is only defined on multiple data points,
+  sample POLSAR covariance matrices are commonly presented in ``ensemble'' format.
+They are formed as the mean of Hermitian outer product of single-look scattering vectors,
 \begin{equation}
@@
 \end{equation}
-with $s_i$ denotes the single-look scattering vector,
+where $s_i$ denotes the single-look scattering vector,
   which equals $s_{part}$ in the case of partial POLSAR and
@@
 
-Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
+Complex Wishart distribution statistics, however, are normally written for the scaled covariance matrix
 $Z=LC_v$, whose PDF is given as:
@@
 
-Our approach differs by applying the homoskedastic log transformation
-  on a less-than-well-known result for the deterimant of the covarinace matrix.
+The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
   %under the assumption of circular complex Gaussian distribution
   %applicable for POLSAR data.
-In \cite{Goodman_1963_AMS_178}, %Goodman
-it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
-  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
+Goodman \cite{Goodman_1963_AMS_178} proved
+that the ratio between the observable and expected values of the sample covariance matrix's determinants
+  behave like a product of $d$ chi-squared random variables with different degrees of freedom 
 \begin{equation}
@@
 
-\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
+\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
 
-In this section the multiplicative nature of POLSAR data is illustrated.
-Log-transformation is shown converting this into a more familiar additive model.
+In this section the multiplicative nature of POLSAR data is first illustrated.
+ Log-transformation is then used to  convert  the data into a more familiar additive model.
+%Log-transformation is shown converting this into a more familiar additive model.
 Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
-  is proved to be the case for the original POLSAR data.
+  is shown to be the case for the original POLSAR data.
 In log-transformed domain, the case for a homoskedastic model,
-  where  variance is fixed and be independent of the underlying mean,
+  where sample variance is fixed and thus independent of the underlying signal,
   is demonstrated.
 To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.
-
-From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
-we have:
+For more detailed derivation, Appendix \ref{chap:appendix_a} should be referred to.
+
+From Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv}
+we can deduce the following relationships:
 \begin{eqnarray}
@@
 In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
-Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
+Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that: 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
 At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
-  the logarithmic transformation converts this into a more familiar additive noise.
-
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
-\begin{equation}
-pdf(x;k) =
-  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
+  the logarithmic transformation has converted this to the more familiar additive noise.
+
+Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows a known PDF:
+\begin{equation}
+pdf(x;2L) =
+  \frac{x^{L-1} e^{-x/2}}{2^L \Gamma\left(L\right)}
 \label{eqn:chi_squared_dist_pdf:chap4}
 \end{equation}
-Applying the variable change theorem, 
+applying the variable change theorem, 
   its log-transformed variable follows the PDF of:
@@
   \end{eqnarray}
-  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma function respectively.
+  where $\psi^0()$ and $\psi^1()$ represent the digamma and trigamma functions respectively.
 
@@
 Specifically:
-\begin{eqnarray*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
+\begin{align*}
+  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
+  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+\end{align*}
 
 Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
-\begin{eqnarray}
-  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
-\end{eqnarray}
-
-Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
+%\begin{eqnarray}
+%\end{eqnarray}
+\begin{align}
+  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
+  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+\end{align}
+
+For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
+%Over a real and captured image, while the parameters $d$ and $L$ do not change for the whole image,
   the underlying $\Sigma_v$ is expected to differ from one region to the next.
 Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
-  %and it is clear that 
-  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
 In such context, Eqn.
-\ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
-At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
+\ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
+At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
   the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.
 
-\section{Consistent Measures of Distance for POLSAR data}
-
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
-  this section introduces the consistent sense of distance in a few different perspective.
-First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-the following random variables,
-  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
+\subsection{Consistent Measures of Distance for POLSAR}
+\label{sec:distance_measure}
+
+Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2010_ACRS} \cite{Le_2013_TGRS_SAR_MSE},
+  this section introduces the consistent sense of distance from a couple of different perspectives.
+Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+random variables,
+  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
   are observable according to their definitions:
 %Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
-
 \begin{eqnarray}
@@
 \end{eqnarray}
-From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
+
+On the other hand, under a more forgiving assumption %From another perspective
+  where the POLSAR is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
+  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are observable and they are defined as:
 \begin{eqnarray}
@@
 
-Taking the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
+Using the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
 \begin{eqnarray}
@@
 
-Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
+Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
   it is natural that these variables also follow fixed distributions.
-Moreover, they are independent to $\Sigma_v$.
-This serves as conclusive evidence that
-  these random variables follows consistent and fixed distributions,
+Moreover, they are independent of $\Sigma_v$.
+%This result shows how
+In short, these random variables are shown to follow consistent and fixed distributions,
   regardless of the underlying signal $\Sigma_v$.
@@
 
-The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
-In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
-Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
-Mathmatically, the sample covariance matrix is reduced to the sample variance
+The previous section has introduced the theoretical model for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+In this section, the model is shown to be also applicable for the 1-dimensional $d=1$ case.
+Physically this means the multi-dimensional POLSAR dataset is collapsed into one-dimensional conventional SAR data.
+Mathematically, the sample covariance matrix is reduced to the sample variance
+%The prevous section has validated the use of our models for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+%In this section, the focus is on the case where the dimensional number is reduced to 1 $d=1$.
+%Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
+%Mathmatically, the sample covariance matrix is reduced to the sample variance
   and the determinant equates the scalar value.
-On another hand, it is well known that for SAR data, variance equals intensity.
+On the other hand, it is well known that for SAR data, variance equals intensity.
 Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
@@
 
-The results so far for our models can be summarized as:
+%The results so far for our models can be summarized as:
+The results so far for our models can be summarized using the following equations:
 \begin{align}
@@
 
-Upon setting $d=1$ into the above models,
-  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+Upon setting $d=1$ into the above equations,
+  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
+First is the the following results obtained from the our previous works on single-look SAR \cite{Le_2010_ACRS} \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+%Upon setting $d=1$ into the above models,
+%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
+%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
 \begin{align*}
@@
 \end{align*}
-but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+%but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
   \begin{eqnarray}
@@
   \end{eqnarray}
-Furthermore, the following results for multi-look SAR data,
-  which can be thought of 
+Furthermore, the following derivations for multi-look SAR data
+   show that it can be thought of 
     either as extensions of the corresponding single-look SAR results
@@
   are also derived as:
+%  Furthermore, the following results for multi-look SAR data,
+%  which can be thought of 
+%    either as extensions of the corresponding single-look SAR results
+%    or as simple cases of the POLSAR results
+%  are also derived as:
   \begin{align*}
@@
 This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
+Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
-
-\begin{figure}[h]
+The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
+ The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
+%The ENL is set to the nominal number of 4.
+%And good visual match is apparent in the final results.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify multi-look SAR log-distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[multi-look SAR log-distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
@@
 	\hfill	
-	\subfloat[verify multi-look SAR contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[multi-look SAR contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
@@
 
-\subsection{Explaining practical data with the given Number-of-Looks}
-
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
+This section validates the theoretical models developed above against real-life practical data.
+The first sub-section provides a naive validation, where the nominal ENL is used for the model.
+While the match appears to be reasonably good, it can be further improved.
+After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
+  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
+With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
+
+\subsection{Using the nominal ENL to validate the theoretical models} 
+This sub-section describes an experiment to validate the models presented earlier against real-life captured data,
+  which can be performed in a rather straightforward manner as follows.
+The stochastic models derived in the previous sections can be graphically visualized as histogram plots of the simulated data.
+%This section describes an experiment to validate the models above against real-life captured data.
+%The validation procedure is quite straightforward.
+%Given that the stochastic models have been derived in the previous sections, 
+%  they can be graphically visualized by the histogram plots of the simulated data.
+At the same time, the form of the real-life practical data is also observable via the histogram plots of the data samples extracted from an homogeneous area.
 Therefore, the theoretical models can be validated 
@@
 
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
+For this purpose, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+Then theoretical models ar used  to explain the data.
+%As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+%Then theoretical models are employed in an attempt to explain the data.
 The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
-  assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
+  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, log-distance, dispersion and the contrast measures of distance.
+
+These models are closely related as follows.
+For  the same parameter set, the determinant and determinant ratio are simply scaled versions of each other.
+Meanwhile, the log-determinant, log-distance and dispersion are also just shifted versions of each other.
+Hence one could expect that 
+  once a model is validated, the other models in the set will follow suit, 
+  assuming that all the parameters of the image are known.% exactly.
+Nevertheless, all the models will be separately evaluated in this section.
+%The models are closely related.
+%Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
+%Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
+%Thus ideally speaking
+%  if one model is validated all the other models will also be,
+%  assuming that all the parameters of the image are known exactly.
+%Still in this section, all the models will be made subject to investigation.
 
@@
 Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
-\begin{figure}[h]
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
+
+Similarly, theoretical simulations according to Eqns.
+\ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
+$L=4$ for this study, while the dimensional number is set to either 3 or 2 depending on whether a full or partial polarimetric SAR dataset is being investigated.
+The plots are presented in Fig. 
+\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} showing an evident visual match between the model and real data, thus effectively validating the theoretical models for dispersion and contrast measures of distance.
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
@@
 	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
@@
 	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
@@
 	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
@@
 There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+The traditional way is to simply set the true signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
+Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+Both approaches will be presented in this section.
+As the log-determinant average has already been computed earlier, 
+  the second approach is hence used first for the validation of determinant-ratio and log-distance.
+%Both approaches will be explored in this section.
+%However, given that the log-determinant average has already been computed earlier, 
+%  the second approach is used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
+In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} and
+%Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
+%In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution}
+and \ref{eqn:log_determinant_distance_distribution},
   while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
   with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
-\begin{figure}[h]
+%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
+A reasonable match is again observed which validates the models for log-distance and determinant ratio.
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
@@
 	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
@@
 	} \\
-	\subfloat[full-pol 3x3 determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[full-pol (3x3) determinant ratio]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
@@
 	\hfill	
-	\subfloat[full-pol 3x3 log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[full-pol (3x3) log distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
@@
 Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
+%And if the  true signals are computed in the same manner as described before then in fact similar match can be easily observed.
+
+However, a more subtle observation phenomena occurs during the validation process for the determinant and its log-transformed model,
+%However, a more interesting  phenomena is to be described.
+%It happens in the validation process for determinant and its log-transformed model,
   where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
 %For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
+The phenomena happens when the true signal is estimated by the first approach i.e.
+equal to the average of the sample covariance matrix in its original domain (which evidently results in a different estimation for the true signal when compared with the method applied earlier).
+%Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
+
+Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small translation and scaling discrepancies -- which are
+ easier to observe in the log-determinant plots. Despite this, the curve shapes are quite similar.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[polsar (2x2) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
@@
 	\hfill	
-	\subfloat[verify polsar 2x2: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[polsar (2x2) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
@@
 	} \\ 
-	\subfloat[verify polsar 3x3: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[polsar (3x3) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
@@
 	\hfill	
-	\subfloat[verify polsar 3x3: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[polsar (3x3) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
@@
   depending on which estimation method was being used.
-The discrepancy suggests that at least one parameter for the models was wrongly employed.
-
-But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  where not only the look number is shown to be misused
-  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-For now, let us contend that:
+The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
+In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
+
+%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
+%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+%  where not only the look number is shown to be misused
+%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
+As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+  the reason is due to the inappropriate look number being used.
+Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
+For now, let us simply observe that
   using appropriate estimation of the parameters, 
@@
 
-\subsection{Comparing Theoretical Assumptions and Practical Implementations}
+%\section{Handling certain discrepancy between the theoretical model and pratical data}
+\subsection{The difference between the theoretical models and the practical data}  
 \label{sec:improve_the_match_bw_theory_practice}
 
-Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
+Even though the assumptions made in developing this theory have intentionally been kept minimal, 
+%Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
   like all other similar models, the proposed model in this paper is built upon certain presumptions.
 Practical conditions however may not always satisfy these prerequisites.
-In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
-And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
-
-There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
-The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
-Practically however high correlation is routinely observable between the POLSAR data components,
-  specifically between $S_{hh}$ and $S_{vv}$.
-This phenomena also presents in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
-Despite the mismatch,
-  astute reader would probably notice that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
+In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.
+And it is shown that: the theoretical model proposed can apply to the practical data, even when this ``imperfection'' is taken into account.
+%In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
+%And it is shown that: the theoretical model proposed can apply to the practical data, even when these ``imperfections''  are taken into account.
+%And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
+
+%There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
+%The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
+%However high correlation is routinely observed in practice between the POLSAR data components,
+%%Practically however high correlation is routinely observable between the POLSAR data components,
+%  specifically between $S_{hh}$ and $S_{vv}$.
+%This phenomena also presents in our AIRSAR dataset, where {\scriptsize $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$}.
+%Despite the mismatch,
+%  astute reader would have noticed that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
 \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
-This suggests that the proposed model is also applicable on correlated POLSAR components,
-  eventhough a full explaination for this, however, is outside the scope of this paper.
-
-Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent to each other.
-This is a reasonable assumption given that 
-  the transmission and receipt of analog signals are done independently for each radar pulse, i.e. for each resolution cell.
-Thus theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
-
-However, the actual imaging mechanism of a real-life (POL)SAR processor is that of digital nature,
-where the analog signal is to be converted into a digital data-set. 
-Specifically, the analog signal in SAR 
-  which is characterized by the pulse bandwidth measurement,
-  is fed into an analog-to-digital sampling and conversion process 
-  which is characterized by its sampling rate.
-Theoretically it is possible to define a sampling rate to ensure that each digital pixel correspond exactly to an analog physical cell resolution.
-Practically however, to ensure ``perfect reconstruction'' of the analog signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
-This results in a higher number of samples / pixels than the number of physical cells available in the scene.
-
-Stated differently, in practical data each physical radar cell is spread to more than one pixel
-  and each pixel now contains less than one physical analog cell.
+%This suggests that the proposed model is also applicable on correlated POLSAR components,
+%  although a full explanation for thisis outside the scope of this paper. 
+%%This suggests that the proposed model is also applicable on correlated POLSAR components,
+%%  eventhough a full explaination for this, however, is outside the scope of this paper.
+
+The assumption of statistical independence between samples (which applies to both SAR and POLSAR data) is reasonable given that 
+  the transmission and receipt of analogue signals is done independently for each radar pulse, i.e. for each resolution cell.
+Thus, theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
+However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
+where the analogue signal is to be converted into a digital data-set. 
+Specifically, the analogue SAR signal, 
+  which is characterised by the pulse bandwidth measurement,
+  is fed into an analogue-to-digital (ADC) sampling and conversion process 
+  which is characterised by its sampling rate.
+Theoretically it may be possible to define a sampling rate that ensures each digital pixel corresponds exactly to an separate analogue physical cell.
+Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate, resulting in a higher number of samples per pixel than the number of physical cells available in the scene.
+
+Stated differently, in practice, each physical radar cell may be spread over more than a single pixel,
+ resulting in potentially high correlation between neighbouring pixels.
 This high sampling rate also results in 
-  a significantly higher correlation between pairs of pixels that maybe related within a single physical cell resolution 
-  than the correlation found between pairs of pixels that are further away and hence having less physical relation to each other.
+  a significantly higher correlation between pairs of pixels that may be related within a single physical cell resolution. 
+  Then the correlation found between pairs of pixels that are further away and hence having less physical relation to each other will increase.
 It also results in reduced effective number of look, 
-  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
+  such as for a window of 3$\times$3 pixels, it actually contains less than 9 physical analogue cells. 
+%It also results in reduced effective number of look, 
+%  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
 The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
@@
 
-The proposed model can handle this imperfection that is available in pratical data.
-The trick is that instead of using the nominal Number of Look given by the SAR processor,
-  an ENL estimation procedure is employed. %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
+%The proposed model can handle this imperfection that is available in pratical data.
+The proposed model can handle this imperfection that is found in practical data.
+The trick is that instead of using the nominal Number of Looks given by the SAR processor,
+  an ENL estimation procedure is first undertaken, and then the obtained ENL used subsequently.
+%the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
 The first part of this section details a simple ENL estimation technique for POLSAR data.
 While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
-It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved,
-  by using ENL estimation.
-
-\subsection{Estimating the Effect Number-of-Looks (ENL)}
-
-This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
-The common approach in tackling this problem is by investigating the summary statistics of an known homogeneous area in the given data
+It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved using ENL estimation.
+
+\subsection{ENL Estimation}
+
+%This sub-section describes a few techniques that can be used to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
+%This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
+The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
   before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ has been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
-In fact Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-Recall that in carrying out validation process for AIRSAR Flevoland data using the nominal look number of 4, this relationship was broken.
-The reason for such broken relationship is believed to be an inexact look number was taken.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ is known,
-  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensure the above relationship is valid.
+The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
+  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
+Recall that in carrying out the validation process using AIRSAR Flevoland data with nominal value $L=4$, the relationship was shown to be broken.
+The reason is believed to be in the use of inexact value for $L$.
+In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
+  it is possible to estimate the ``effective'' number of look, by finding an $L$ that ensures the above relationship is valid.
 
@@
 Instead of relying on the equations for statistical mean to find ENL,
-  our approach make used variance statistics in the homoskedastic log-domain to find ENL.
-Since the determinant of POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
-  this approach can be considered as the generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} towards POLSAR data.
+  we propose an approach that makes used of variance statistics in the homoskedastic log-domain to find ENL.
+%Since the determinant of the POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
+%  this approach is a generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} for POLSAR data.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
 \end{equation}
-where $\psi^1()$ denotes tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
-Interestingly that would also require some iterative computations.
+where $\psi^1()$ again denotes the tri-gamma function.
+
+Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$,
+  which would also require some iterative computations.
 Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph.
-And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
+  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph or by using the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
+%And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
   \begin{equation}
@@
 Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  not only shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  but also illustrates the approximation power of the simplified formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-\begin{figure}[h]
+  shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
+  as well as illustrating the simplified approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/plot_enl_var_relation_1x1.eps} 
@@
 	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
@@
 
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
-The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
+\subsection{Using estimated ENL to better explain practical data}
+
+For this experiment an example RADARSAT2 dataset is used, in its Fine-Quad mode Single-Look format.
+Nine-look processing is applied before the dispersion histogram in the log-transformed domain is computed for a known homogeneous area.
+The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
+  against the theoretical models for the nominal ENL value of 9.
+The match, however, is evidently not very close.
+
+A better match can be achieved by first estimating ENL from the observable variance of the log-determinant,
+  and the theoretical model is then simulated for the estimated ENL.
 Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
-\begin{figure}[h]
+  showing a much better consistency.
+This procedure can always be carried out for a given dataset,
+  as long as a homogeneous area can be defined and extracted.
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
@@
 	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
@@
 
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
-\begin{figure}[h]
+Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
+  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
+Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
+The mis-match problem appears to depend upon how much over-sampling was used to generate the dataset as well as upon the data dimension.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
+	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
 		 \label{sar}
@@
 	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
@@
 
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
+\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+%\section{Visually Evaluating POLSAR Speckle Filters over Heterogeneous Areas}
+\label{sec:evaluating_polsar_filters}
+
+Previous sections have developed a model for POLSAR, which is also shown to be applicable to SAR.
+In this section, the use of consistent measures of distance in the context of POLSAR speckle filtering are explored briefly.
+It has been found \cite{Rignot_1993_TGRS_896} that for SAR data in its original domain,  
+   ratio is a better evaluation than standard subtractive residual. 
+However, ratio residual is argued as not being natural for digital display \cite{Medeiros_2003_IJRS}.
+Our previous work in the context of SAR speckle filtering found that
+  in the log-transformed domain, this ratio is transformed into a subtractive residual that is homoskedastic.
+
+The variance of sample log-determinant is shown to be linked to the ENL index.
+This forms the basis for evaluating POLSAR speckle filters over homogeneous areas.
+The procedure is simple:
+To evaluate a given POLSAR speckle filter over homogeneous areas,
+  the filter is applied over a known homogeneous area and the sample variance of log-determinant is measured.
+The Equivant Number of Looks (ENL) is then estimated
+  either by referencing prepared graphs from Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} 
+  or alternatively by setting the measured variance value to $var[\ln{|C_v|}]$ in Eqn. \ref{eqn:enl_estimation_formula}.
+
+In order for such a procedure to be generic,
+  it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
+That can be tested by applying the POLSAR filter into different sets of homogeneous areas and investigating the plots of the dissimilarity measures presented above.
+Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that
+  the 3$\times$3 POLSAR boxcar filter preserves the consistency property.
+In this case, the boxcar filter is applied to 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
+Log-determinant and the contrast measures are computed for the input and output filtered POLSAR data,
+  and their plots are presented.
+In fact, the test procedure can be applied on any of the models presented above.
+
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinants histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+		 \label{log_determinant}
+	} 
+	\hfill	
+	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+		 \label{contrast}
+	}   
+\end{tabular}
+\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
+\label{fig:boxcar_3x3_preserves_consistency}
+\end{figure}
+
+The consistency property of a POLSAR speckle filter is important
+  not only to make the estimation of ENL become general enough.
+It is also to ensure that any classification / detection algorithm
+    which is based on the scalar and consistent measures of distance will work on both pre-filtered and post-filtered data.
+Otherwise if a POLSAR speckle filter gives different plots for different homogeneous areas,
+  then not only its ENL estimation will be dependent on the underlying signal, 
+  but its output also shall not follow the statistical distribution family that characterises multi-look POLSAR.
+Thus the preservation of this consistency is believed to be an important consideration for POLSAR speckle filters
+  if we want many general detection and classification algorithms to work on the filtered data output.
+
+In evaluation over heterogeneous area, the consistent measures of distance may also be an invaluable tool.
+ %in helping to evaluate POLSAR speckle filters.
+Firstly, since the model for log-determinant is additive and homoskedastic,
+  log-determinant images may naturally be better suited for gray-level digital display.
+Specifically for evaluation of statistical estimators, it is both important and convenient to investigate the estimators' error / residual image. %plays an important role.
+
+For further analysis, the residual is defined here as the distance between the log-determinants of the filtered outputs and the original input. 
+Ideally speaking, under the context of an additive model,
+  a perfect estimators residual should consist only of random noise.
+And under the assumption of homoskedasticity, 
+  the Gauss Markov theorem becomes applicable.
+Thus the optimal estimator is expected to exhibit minimal Mean Squared Error (MSE).
+Over a homogeneous scene, this is reflected in the expectation of minimal bias and variance (hence maximal ENL).
+Over a heterogeneous scene, where the underlying signal is not known \textit{a priori},
+  the second best gauge is possibly to have the residual MSE being as close as possible to the MSE of the inherent noise.
+
+To illustrate the above analysis, an experiment is carried out to evaluate the performance of 3$\times$3 and5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+A square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters applied to the patch.
+Then the log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+Assuming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+This optimal value is computed   
+by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
+
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%Note if the picture does not look convincing enough
+%another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  but also the distortion impact of the filter can also be made visible by the residual image.
+In visual evaluation, while it is quite hard to observe the worsening blurring-effects of the boxcar 5$\times$5 speckle filter as compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such a conclusion can be made relatively easier by visualising the residual image.
+
+When quantified evaluation is carried out
+  where the residual MSE is compared with the expected level of noise to be removed,
+  the excessive blurring effects of the 5$\times$5 filter become clearly evident.
+%IVM: [cut this]In fact, even the 3$\times$3 boxcar filter itself might be also a bit blurry.
+%,  as suggested by its relatively high residual values.
+%A conclusion which is hard to make
+It may be hard to make such a conclusion just by looking at the filtered imagery.
+However, by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer more conclusive evidence.
+
+Further discussion on the specific topic of evaluating SAR speckle filters is given in our work that focused specifically on SAR \cite{Le_2013_TGRS_SAR_MSE}.
+However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters (i.e. extending the previous SAR approach).
+
+Specifically, this is an illustration of how the proposed theoretical model can possibly be applied to a practical scenario, rather than a full evaluation procedure and methodology.
+%IVM [cut this],  as it is not as a full proposal for such an evaluation procedure for POLSAR speckle filters.
+
+\section{Discussion and Conclusion}
+\label{sec:discussion_conclusion}
+
+%\subsection{The Likelyhood Test Statistics for POLSAR}
+
+%\begin{eqnarray}
+%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%\end{eqnarray}
+
+\subsection{Discussion}
+
+Let us begin the discussion by noting a few theoretical properties of the proposed statistical model.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
+
+Second, the model is developed for the POLSAR covariance matrix.
+However, since the POLSAR coherent matrix is related with the covariance matrix via an unitary transformation, which preserves the determinant as invariant,
+the model should also be applicable on the coherency matrix.
+
+The model is far from complete.
+ It calls for the reduction of the multi-dimensional POLSAR data into a scalar value.
+While this is probably desirable for a wide range of application where a one-dimensional number is required to represent the complex multi-dimensional data,
+  such a reduction is unlikely to be lossless.
+Thus is very similar to the way the Wishart Classifier is employed, and thus to better understand POLSAR data
+  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
+the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).
+
+However the model as presented is promising. Those presented in this paper were first developed for partial and monostatic POLSAR data.
+They were then shown to be also applicable to traditional SAR data.
+Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigations.
+%Other interesting phenomena which may warrant more study include the applicability of the model on correlated polsar channels ($S_{hh},S_{vv}$) as well as a better explanation in the use of mse to evaluate polsar speckle filters.
+
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+Since extensive examples have been shown to support the use of MSE for SAR data,
+  it is reasonable to expect the relevance of MSE to also be demonstrated for POLSAR data.
+If that is the case, a large number of existing algorithms can become applicable to the POLSAR model in this log-transformed domain,
+  which has been shown to be both additive and homoskedastic.
+
+\subsection{Conclusion}
+\label{sec:conclusion}
+
+In conclusion, a couple of statistical models for the determinant of the POLSAR covariance matrix is proposed and validated in this paper.
+Compared to other statistical models for POLSAR, the proposed models are scalar and representative for the multi-dimensional POLSAR data.
+These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
+Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
+As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
+
+%An additive and homoskedastic model, 
+%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+%  is proposed in this paper.
+%The theoretical model is shown to be comprehensive:
+%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+%
+%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+%  is gracefully transformed into traditional SAR intensity.
+%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
+
+\appendices
+\section{Homoskedastic Model for the Log-Determinant}
+\label{chap:appendix_a}
+
+\subsection{Log-Chi-Square Distribution and its Derivatives}
+%\section{Log-Chi-Square Distribution}
+\renewcommand{\theequation}{\thesection.\arabic{equation}}
+\setcounter{equation}{0}
+
+This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
 
@@
 
-From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, characteristics function can be computed.
+From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, a characteristic function can be computed.
 By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
@@
      $f_X(x)$ is the PDF function of X.
-Thus the characteristic function for log-chi-squared distribution is defined as: 
+Thus the characteristic function for the log-chi-squared distribution is defined as: 
 \begin{equation}
@@
 
-Gamma function is defined over complex domain as:
+The Gamma function is defined over the complex domain as:
 $\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
@@
 
-Consequently, the first and second derivative of log-chi-squared distribution can be computed.
+Consequently, the first and second derivative of the log-chi-squared distribution can be computed.
 The first derivative is given as:
@@
 \end{eqnarray*}
-where $\psi^0()$ denotes di-gamma function.
+where $\psi^0()$ denotes the di-gamma function.
 
@@
 \end{eqnarray*}
-with $\psi^1()$ denotes tri-gamma function.
+with $\psi^1()$ denotes the tri-gamma function.
 
@@
 \end{eqnarray*}
-That is
+That gives the result:
 \begin{equation}
@@
 
-Similarly,
+Similarly, for the second moment,
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-That is:
+That is equivalent to saying that
 \begin{equation}
@@
 
-Thus
+Thus we can state that
 \begin{equation}
@@
 
-\subsection{Summary Statistics of Some POLSAR Observables}
-
-In this section, the expected value and variance value of these mixture of random variables is derived
+\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
+
+In this section, the expected value and variance value of these mixture of random variables are derived
 \begin{eqnarray}
@@
 
-Making use of the mutual indepent property of each component $X_i$,
-  the variance and expectation of the sumation and product of random variables can be written as:
+Making use of the mutual independence property of each component $X_i$,
+  the variance and expectation of the summation and product of random variables can be written as:
 \begin{eqnarray*}
@@
 
-Thus they can be computed as:
+Thus they can be rewritten more usefully as:
 \begin{eqnarray*}
@@
 
-\subsection{The characteristic function of some dissimilarity measures for polsar}
-
-Given characteristic function (CF) of the elementary log-chi square distributions can be written as:
+\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
+\label{sec:appendix_b}
+
+Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as
 \begin{eqnarray}
@@
 \end{eqnarray}
-  the CF for the following random variables,
+  then the CF for the following random variables,
   which are combinations of the above elementary random variables, can be derived
@@
 
-Since
+Since we can state that
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-we have:
-\begin{eqnarray}
-  CF_{\chi^d_L}(t) &=& \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{L}} &=& \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{D}} &=& \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-\end{eqnarray}
+then we have:
+%\begin{eqnarray}
+%\end{eqnarray}
+\begin{align}
+  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
+\end{align}
 
@@
 \end{eqnarray*}
-we arrive at:
-\begin{eqnarray}
+then we arrive at:
+\begin{align}
   CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-\end{eqnarray}
-with $\Gamma()$ and $B()$ denotes Gamma and Beta functions respectively.
-
-\subsection{SAR intensity as the special case of the POLSAR cov-matrix determinant}
+\end{align}
+with $\Gamma()$ and $B()$ denoting Gamma and Beta functions respectively.
+
+\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
 \label{sec:appendix_sar_special_case_of_polsar}
 
-In this appendix, the following results for SAR intensity $I$ is shown to be special cases of the results given in this paper for the determinant of POLSAR's covariance matrix $det|C_v|$.
-Specifically, not only the following results from the our previous works on single-look SAR (TODO:CITE), i.e. $d=L=1$, is reviewed:
+In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
+Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
 \begin{eqnarray}
@@
 \end{eqnarray}
-but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$ is also considered:
+but also the following well-known results are considered for multi-look SAR, i.e. $d=1,L>1$:
   \begin{eqnarray}
@@
 The derivation process detailed below consists of two-phases.
-The first phase collapse the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
+The first phase collapses the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
 Mathematically this means setting the dimensional number in POLSAR to  $d=1$
@@
 
-The output of the first phase, in the general case is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplify the multi-look results into single-look results, presented in our previous work (TODO:CITE).
-Mathematically, that means setting $L=1$ in the multi-look result
-  and converting from natural logarithmic domain used in this paper to the base-2 logarithm used in (TODO:CITE).
-
-\subsubsection{Original Domain: SAR Intensity and its ratio}
+The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
+The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+Mathematically, it means setting $L=1$ in the multi-look result
+  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2013_TGRS_SAR_MSE} (base-2 was chosen in the previous paper to simplify the computation).
+
+\subsection{Original Domain: SAR Intensity and its ratio}
 
 Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
-we have:
+we find that:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-Or in PDF forms, and applying variable change theorem we have:
+Or in PDF forms, and applying the variable change theorem,:
 \begin{eqnarray*}
@@
 
-Thus we have the following results for multi-look SAR
+Thus we have the following results for multi-look SAR:
 \begin{eqnarray}
@@
 \end{eqnarray}
-which is the same as in (TODO:CITE).
-
-\subsubsection{Log-transformed domain: SAR log-intensity and the log-distance}
-
-The result for multi-look SAR data written in log-transformed domain can be derived from two different approaches.
-The first is to follow the simplification method, where the results for log-transformed POLSAR data is simplified into log-transformed multi-look SAR result.
-
-The second approach is to apply log-transformation into the results derived in the previous section.
-In this section, it is shown that both approaches would results into identical results.
+which is the same as stated in \cite{Le_2013_TGRS_SAR_MSE}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
+
+\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
+
+The result for multi-look SAR data written in the log-transformed domain can be derived from two different approaches.
+The first is to follow a simplification method, where the results for log-transformed POLSAR data are simplified into log-transformed multi-look SAR results.
+
+The second approach is to apply log-transformation to the results derived in the previous section. In this section, it is shown that both approaches would result in identical results.
 
@@
 
-Or in PDF form, and applying variable change theorem we have:
+Or in PDF form, and applying the variable change theorem we have:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-with $\bar{N} = \ln{\bar{I}}$.
-
-Thus the first approach arrives at
+with $\bar{N} = \ln{\bar{I}}$. Thus the first approach arrives at
 \begin{eqnarray}
@@
 
-In the second approach, log-transformation is applied on previous result for multi-look SAR intensity and its ratio in the original domain (Eqns.
+In the second approach, log-transformation is applied on previous results for multi-look SAR intensity and its ratio in the original domain (Eqns.
 \ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-The also arrives at the same results as above, the details working however is omitted here for brevity.
+This also arrives at the same results shown above, however the detailed working is omitted for brevity.
 
@@
 To compute summary statistics for the multi-look SAR dispersion,
-  set $d=1$ into the Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
+  set $d=1$ into Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
 we have:
@@
 \end{eqnarray*}
-with $\gamma$ denotes the Euler-Mascharoni constant.
+with $\gamma$ denoting the Euler-Mascharoni constant.
 Then to convert to base-2 logarithm from natural logarithmic transformation,
-  variable change theorem is invoked.
+  we again use the variable change theorem.
   That is:
@@
 
-\subsubsection{Deriving the PDF for SAR dispersion and contrast}
+\subsection{Deriving the PDF for SAR dispersion and contrast}
 
 The PDF for SAR dispersion can be easily derived from
-  the PDF for the Log-distance given above as:
+  the PDF for the log-distance given above as:
   \begin{equation}
@@
   \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
-\end{eqnarray*}.
+\end{eqnarray*}
 
@@
 due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
-with $\gamma$ being the Euler Mascheroni Constant which equals $0.5772$. 
-In base-2 logarithm, variable change theorem is invoked
+with $\gamma$ being the Euler Mascheroni constant (which equals $0.5772$). 
+In base-2 logarithm domain, invoking the variable change theorem:
 \begin{eqnarray*}
@@
 \end{equation}
-which is consistent to the result in our previous work (TODO:CITE).
-
-Setting $d=1$ into Eqn. for contrast result in
+which is consistent with the results found in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+
+Setting $d=1$ into Eqn. for contrast results in
 \begin{equation}
@@
 \end{equation}
-Thus PDF can be written as
+Thus the PDF can be written as
 \begin{equation}
@@
 Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
-we have the PDF for contrast of single-look SAR:
+we have the PDF for contrast of single-look SAR data:
 \begin{equation}
@@
 
-Converting to base-2 logarithm we have
+Converting to base-2 logarithm gives the following:
 \begin{eqnarray*}
@@
 \end{eqnarray*}
-which is also consistent to the result in our previous work (TODO:CITE).
-
-%\section{Simulating All Elements of POLSAR Covariance Matrix}
-%
-%Jong sen lee simulation procedures is applied and verified in 2x2 partial polsar AIRSAR Flevoland image.
-%Pipia method explicitly indicates cholesky decomposition,
-%  while the exponential notion in Lee's book appear to suggest svd decomposition
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[verify polsar 2x2 simulation: S11]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S11.eps} 
-%		 \label{S11}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S22]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S22.eps} 	
-%		 \label{S22}
-%	} \\
-%	\subfloat[verify polsar 2x2 simulation: S12r]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%                 \epsffile{images/verify_polsar_2x2_simulation.S12r.eps} 
-%		 \label{S12r}
-%	} 
-%	\hfill	
-%	\subfloat[verify polsar 2x2 simulation: S12i]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{images/verify_polsar_2x2_simulation.S12i.eps} 	
-%		 \label{S12i}
-%	}        
-%\end{tabular}
-%\caption{verifying polsar 2x2 simulation: the components}
-%\label{fig:verify_polsar_2x2_simulation_components}
-%\end{figure}
-%
-%The same procedure does not appear to work on 3x3 full polarimetric POLSAR image.
-%Despite all other elements match nicely, the ShhSvv* element does not appear to match.
-%However, the log-det still appears to be consistent
-%  and more importantly all dis-similarity measures still match.
-%  
-%\begin{figure}[h!]
-%\centering
-%\epsfxsize=6.0cm
-%\epsffile{images/verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation.eps} 
-%\caption{3x3 svd simulation: 13 element mismatch}
-%\label{fig:verify_polsar_3x3_svd_simulation.13element_on_2x2_simulation}
-%\end{figure}
-%
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[C11]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.11.eps} 
-%		 \label{11}
-%	} 
-%	\hfill	
-%	\subfloat[C22]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.22.eps} 
-%		 \label{22}
-%	} 
-%	\hfill	
-%	\subfloat[C33]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.33.eps} 
-%		 \label{33}
-%	} \\
-%	\subfloat[C12r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12r.eps} 
-%		 \label{12r}
-%	} 
-%	\hfill	
-%	\subfloat[C13r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13r.eps} 
-%		 \label{13r}
-%	} 
-%	\hfill	
-%	\subfloat[C23r]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23r.eps} 
-%		 \label{23r}
-%	}  \\
-%	\subfloat[C12i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.12i.eps} 
-%		 \label{12i}
-%	} 
-%	\hfill	
-%	\subfloat[C13i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.13i.eps} 
-%		 \label{13i}
-%	} 
-%	\hfill	
-%	\subfloat[C23i]{
-%		 \epsfxsize=2in
-%		 \epsfysize=2in
-%                 \epsffile{images/verify_polsar_simulation_3x3.23i.eps} 
-%		 \label{23i}
-%	}
-%\end{tabular}
-%\caption{verify polsar 3x3 simulation with polarization basis change}
-%\label{fig:verify_polsar_svd_3x3_simulation_polarization_basis_change}
-%\end{figure}
-%
+which is also consistent to the results shown in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+
+% references section
+\bibliographystyle{IEEEtran}
+\bibliography{IEEEabrv,article}
+
+\end{document}

### 2013-04-22 paper_dev/article_pp.tex
201303_Mar01
added 201304_Apr22

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
-
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
+%\documentclass[a4paper,10pt]{article}
+%ifdef FINAL
+\documentclass[journal]{IEEEtran}
+%endif
+%ifdef REVIEW
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+%endif
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{cite} %for citations
+\usepackage{url}
+
+ %this is for math typing (eg: cases)
+\usepackage{amsmath}
+   \usepackage{amsfonts}   % if you want the fonts
+   \usepackage{amssymb}    % if you want extra symbols
+\usepackage{epsfig} %for figures
+
+\usepackage[center]{caption}%for captions
+\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+
+%\nonstopmode
+
+%opening
+\title{
+  %Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
+  Scalar and Representative Models for Polarimetric SAR Data
+}
+
+%\author{Thanh-Hai Le, Ian McLoughlin}
+\author{Thanh-Hai~Le,
+        Ian~McLoughlin, 
+	and Chan-Hua~Vun%
+\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+%	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2013; revised ?.}}
+
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+  While statistical models are important in understanding the stochastic nature of Polarimetric SAR (POLSAR),
+  scalar discrimination measures are routinely used in processing this multi-dimensional data.
+  Ideally speaking, the latter should be drived from the former.
+  As far as we know, however, it has not exactly been so for the case of POLSAR.
+  In this paper, a couple of statistical models for the determinant of the POLSAR covariance matrix and its log-transformed derivations are proposed.
+  These scalar models for the determinant of the POLSAR covariance matrix are shown to be respresentative
+    since this observable is neatly transformed into the traditional SAR intensity
+    when the generic multi-dimensional polarimetry is collapsed into the case of one-dimensional SAR. %case of traditional SAR data.
+  Similar to SAR, the generic model for POLSAR is also shown to be multiplicative and heteroskedastic in the original domain 
+    and the logarithmic transformation converts this into a more familiar additve and homoskedastic model.
+  Moreover, the scalar property of these statistical models lead to the derivation of several statistical discrimination measures. %homoskedastic measures of distance.
+  All of these statistical models are validated on real-life captured data
+    and they are shown to be applicable even when the theoretical ``independent samples'' assumption is violated in practice.
+  %The paper also illustrates a couple of benefits of these models, specifically for using the homoskedastic discrimination measures.
+  %A couple of benefits for using these homoskedastic dis-similarity measures are then illustrated in this paper.
+  %These homoskedastic measures of distance
+  The combination of scalar, additive and homoskedastic properties of the derived statistical models bring about a couple of benefits, which are also described in this paper.
+  First, compared to the original multiplicative domain, %dis-criminative measure of ratio,
+    the additive log-transformed fit more naturally with the linear nature of digital imagery.
+  Second, since the Gauss-Markov theorem is again applicable in the homoskedastic log-transformed domain,
+    the use of Mean Squared Error (MSE) as an reliable objective function for POLSAR speckle filters is briefly explored.
+%This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
+%The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
+%The dissimilarity measurements, 
+%computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
+%It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+%  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
+%This puts the SAR intensity statistics to lie within the natural coverage of this new theoretical model for POLSAR.
+%Not only comprehensive theoretically, the statistical model is also robust in handling practical data. 
+%It can be validated and match reasonably well  with practical data.
+%Moreover, the match can be further improved 
+%  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
+%  instead of blind acceptance of the number of looks figure reported by the SAR processor.
+%The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+\end{abstract}
+
+\begin{IEEEkeywords}
+Polarimetric Synthetic aperture radar, Electromagnetic Modeling, Multidimensional signal processing  
+\end{IEEEkeywords}
+
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+%\section{POLSAR data: statistical analysis and logarithmic transformation}
+
+In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
+As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
+POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
+Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
+
+With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
+The complex data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
+Under this condition, it is very important to understand the statistical models for (POL)SAR data.
+
+While the statistical models for homogeneous areas of one-dimensional SAR data have been developed,
+%  in extending the model toward heterogeneous images, the impact of heteroskedasticity has virtually been ignored.
+%Specifically the concept of distance as a measure of dis-similarity is seriously flawed, as it is widely known that ratio offers a better discrimination measure TODOCITE.
+%This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
+%From this log-transformed model, a few consistent measures of distance is proposed. 
+%in a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtraction, and thus distance.
+  in extending our understanding towards multi-dimensional POLSAR data, an important issue needs to be addressed.
+The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
+While different statistical models have been developed for different POLSAR observables,
+  for a statistical model to be useful, scalar discrimination measures need to be derived from it.
+Thus practical application for POLSAR data processing requires the dis-similarity measure to be scalar, consistent and preferably homoskedastic on one hand.
+On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
+
+In this paper, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
+The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario.
+Under this transformation, the determinant of the POLSAR covariance matrix is converted into the standard SAR intensity.
+Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
+And since POLSAR can be viewed as a multi-dimensional extension of SAR, the paper describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
+
+%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
+%Firstly, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear scale nature of digital imagery.
+%Secondly, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss Markov theorem is again applicable, the universal MSE deserves to be reviewed as a reliable objective function / criteria for (POL)SAR estimators.
+%This may open up a number of different research directions for future studies of (POL)SAR.
+%As example demonstrations of how these models and distance measures can be used, a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
+
+Specifically, the rest of this paper is structured as follows.
+After the related work in literature is critically reviewed in Section \ref{sec:lit_review},
+  Section \ref{sec:theoretical_model} presents the theoretical models for both partial and full polarimetric SAR and their derived discrimination measures.
+The representative power of the scalar models are illuminated in Section \ref{sec:sar_special_case_of_polsar},
+  which details how the proposed models for the multi-variate POLSAR also includes the well-known models for the traditional SAR as its special univariate case.
+%can be used to derive the well-known models for the univariate SAR data as its special case.
+Besides being theoretically comprehensive, 
+  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+To demonstrate the application of these scalar and representative models, 
+  Section \ref{sec:evaluating_polsar_filters} explores how they can be used to evaluate POLSAR speckle filters.   
+In the end, Section \ref{sec:discussion_conclusion} provides the final conclusion of the paper.
+%critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
+%In this paper, the above results are exploited in the context of POLSAR data processing.
+In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
+The paper is structured as follows:
+%  after the preceding introduction to the basics of POLSAR statistical analysis,
+%  the second section briefly reviews related work in published literature.
+%Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+%The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+%And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+%Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+%After the model is presented for both partial and full polarimetric SAR data,
+%  section \ref{sec:sar_special_case_of_polsar} discusses
+%    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+%To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
+%  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
+%Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
+\section{Related Work in Literature}
+\label{sec:lit_review}
+
+This section critically review the related work in published literature.
+Specifically, the first sub-section shows that while many discrimination measures have been proposed for POLSAR data,
+  almost all of them depends on the likelihood statistical test for complex Wishart distribution.
+Unfortunately, in the original proposed work \cite{Conradsen_2003_TGRS_4}, while an exact distribution is to be expected, only an asymptotic distribution was given.
+The second sub-section reviews various statistical models for different POLSAR observables.
+Its purpose is to show that none of these models, as far as we know, led to statistically consistent discrimination measures.
+
+\subsection{POLSAR Discrimination Measures}
+
+This sub-section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
+In particular, a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+will be briefly reviewed.
+%specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+
+The commonly used measure of distance for matrices are either the Euclidean or the Manhattan distance,
+  which are defined in the following equations, respectively:
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
+  probably because of the multiplicative nature of the data.
+%In the context of polsar covariance matrix, however, they are not widely used 
+%  probably because of the multiplicative nature of the data.
+
+In the field of POLSAR, the Wishart Distance is probably the most widely used as part of the well-known Wishart Classifier \cite{Lee_1999_TGRS}.
+The distance is defined as \cite{Lee_1994_IJRS_2299}
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dissimilarity measures.
+These include the asymmetric and symmetric refined wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance \cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+.
+
+In comparison to these formulae, the distance measures for two covariance matrices proposed in this paper can be written as:
+\begin{equation}
+  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
+\end{equation}
+At first glance, while the propose formula may be a lot simpler, it still operates in a similar way to others in making use of the log-determinant.
+
+Closer investigation of these dis-similarity measures reveals that most of them are related to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered as the special case of the Wishart Statistical Test distance, where the two data set have the same number of look, i.e. $L_x=L_y$.
+It is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper has fixed statistical behaviour, by comparing the symmetric and asymmetric versions of the refined Wishart distance, assuming that they are shown to follow fixed distributions.
+
+The close relation among these is further supported by the fact that
+all of the papers proposing these measures referenced the statistical model developed in \cite{Conradsen_2003_TGRS_4} as their foundation.
+%Interestingly, the change detection model in \cite{Conradsen_2003_TGRS_4} also make use of determinant ratio and log determinant in its derivation.  
+%The next sub-section will illustrate how the log-determinant model presented in this paper can offer an alternative and simple derivation for the change-detection statistics.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrix is considered:  
+\begin{equation*}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation*}
+
+Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{eqnarray}
+
+To detect changes, a test statistics is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, originally in the proposed work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution is derived.
+%In this sub-section, a statistical model is developed for this measure of distance.
+Since both $Z_x$ and $Z_y$ follow a complex Wishart distribution with $L_x$ and $L_y$ degrees of freedom,
+  $Z_x+Z_y$ also follows the complex Wishart distribution with $(L_x + L_y)$ degrees of freedom.
+In view of the models for $|C_v|$ and $\ln|C_v|$ developed in this paper (Eqns. \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution}),
+  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+  but the whole statistical distribution for it can be simulated as well.
+
+\subsection{Scalar Observables and Statistical Models for POLSAR Data}
+
+Of course, discrimination measures are not the only way to carry out classification tasks in POLSAR.
+Another common approach is to carry out classification using POLSAR observables identified by different target decomposition theorems.
+In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes is evaluated.
+While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, at its conclusion, the paper indicated that ``it is impossible to indentify the best one''
+  as these ``representations ... do not show a precise trend''.
+%Instead an MLP classification approach were employed. 
+To be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
+  and thus they are not to be used individually for the purpose of single-handedly representing POLSAR data.
+
+Given the joint distribution for POLSAR is known to be the multi-variate Complex Wishart distribution,
+  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
+However, such derivations are no trivial tasks,
+  as the data is much more complex and the field is much less matured than the traditional SAR statistical modelling.
+Thus the strategy of the pioneering work is to tackle simpler versions of polarimetry.
+
+POLSAR data is commonly represented by its covariance matrix.
+For full-pol the covariance matrix has the form of
+\begin{equation*}
+C_3 = 
+\begin{bmatrix}
+S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
+\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
+S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+For part-pol, it reduces to either:
+\begin{equation*}
+  C_{2,h} =
+  \begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{hv}^* \\
+    S_{hh}^*S_{hv} & S_{hv}^2
+  \end{bmatrix};
+  C_{2,v} =
+  \begin{bmatrix}
+    S_{hv}^2 & S_{hv}S_{vv}^* \\
+    S_{hv}^*S_{vv} & S_{vv}^2
+  \end{bmatrix}
+\end{equation*}
+Obviously, the statistical behavior of $C_3$ can be understood by understanding the behavior of $C_{2h},C_{2v}$ and
+\begin{equation*}
+  C_{2,c} = 
+\begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{vv}^* \\
+    S_{hh}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+
+While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
+  $C_{2c}$ is a totally made-up mathematical term from the full-pol covariance matrix.
+In fact, in the field of Polarimetric SAR, $C_{2v}, C_{2h}$ is called cross-pol and $C_{2c}$ is called co-pol covariance matrices.
+Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
+\begin{equation*}
+  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
+\end{equation*}
+with $\phi=arg(\rho)$ is the phase difference angle.
+In $C_{2v}, C_{2h}$ of optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
+  and $\phi_v,\phi_h$ are very random, due to little correlation between orthogonal polarization in monochromatic EM waves.
+%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
+Their equivalent lie in the ``natural surface'' case of POLSAR,
+  where  it is common to consider: $|\rho_v|=|\rho_h|=0$.
+This is, however, not true in the general case of POLSAR.  
+Specifically for $C_{2c}$, since there are correlation between the two co-pol channels,
+  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.
+
+In the field of optical physics,
+  under the assumption of no correlation between cross-polarized channels,
+  \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} derived the statistical models for $C_{2h},C_{2v}$.
+The observables that have been studied are:
+\begin{enumerate}
+\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
+  \begin{enumerate}
+  \item the total power $S_0=C_{11}^2 + C_{22}^2$,
+  \item the ratio of minor to major axis of the polarization ellipse  $\epsilon=\lambda_2/\lambda_1$,
+  \item and $\psi$ the angle that the ellipse major axis makes with horizontal axis,
+  \end{enumerate}
+\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
+  \begin{enumerate}
+  \item $S_0 = C_{11}^2 + C_{22}^2$
+  \item $S_1 = C_{11}^2 - C_{22}^2$
+  \item $S_2 = \Re (C_{12})$
+  \item $S_3 = \Im (C_{12})$
+  \end{enumerate}
+\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
+\end{enumerate}
+In the field of POLSAR, under the assumption of significant correlation between polarized channels,
+  \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} derived the statistical models for note only $C_{2h},C_{2v}$ but also $C_{2c}$.
+Specifically the following observables were studied:  
+  \begin{enumerate}
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \end{enumerate}
+
+Furthermore, other studies has offered
+  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
+  the statistical model for
+  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
+While these models undoubtedly help in understanding the SAR data,
+  individually none of them statisfies the dual criteria of
+  1) resulting in statistically consistent discrimination measures and
+  2) being an representative observable for the complex POLSAR data.
+  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
+
+\section{The Scalar Statistical Models for POLSAR}  
+\label{sec:theoretical_model}
+
+In this section, several scalar statistical models for POLSAR are presented.
+After the first sub-section briefly reviews related work in published literature,
+  sub-section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+
+\subsection{The Basics of POLSAR Statistical Analysis}
+
+In this paper, the POLSAR scattering vector is denoted as $s$.
 In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
@@
 This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
+Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
-
+The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
+ The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
+%The ENL is set to the nominal number of 4.
+%And good visual match is apparent in the final results.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[verify multi-look SAR log-distance]{
+	\subfloat[multi-look SAR dispersion]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[verify multi-look SAR contrast]{
+	\subfloat[multi-look SAR contrast]{
 		 \epsfxsize=1.5in
@@
 \end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[multi-look SAR log-distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[multi-look SAR contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
+		 \label{multi_look_contrast}
+	}
+\end{tabular}
+\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
+\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\end{figure}
+%endif
 
@@
 Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
+
+Similarly, theoretical simulations according to Eqns.
+\ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
+$L=4$ for this study, while the dimensional number is set to either 3 or 2 depending on whether a full or partial polarimetric SAR dataset is being investigated.
+The plots are presented in Fig. 
+\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} showing an evident visual match between the model and real data, thus effectively validating the theoretical models for dispersion and contrast measures of distance.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) dispersion]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
+		 \label{dispersion_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
+		 \label{contrast_2x2}
+	} \\
+	\subfloat[full-pol (3x3) dispersion]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
+		 \label{dispersion_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
+		 \label{contrast_3x3}
+	}
+\end{tabular}
+\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
+\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\end{figure}
+%endif
 
@@
 There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+The traditional way is to simply set the true signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
+Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+Both approaches will be presented in this section.
+As the log-determinant average has already been computed earlier, 
+  the second approach is hence used first for the validation of determinant-ratio and log-distance.
+%Both approaches will be explored in this section.
+%However, given that the log-determinant average has already been computed earlier, 
+%  the second approach is used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
+In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} and
+%Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
+%In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution}
+and \ref{eqn:log_determinant_distance_distribution},
   while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
   with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
+%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
+A reasonable match is again observed which validates the models for log-distance and determinant ratio.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 	} \\
-	\subfloat[full-pol 3x3 determinant ratio]{
+	\subfloat[full-pol (3x3) determinant ratio]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[full-pol 3x3 log distance]{
+	\subfloat[full-pol (3x3) log distance]{
 		 \epsfxsize=1.5in
@@
 \end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) determinant ratio]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) log distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
+		 \label{log_distance_2x2}
+	} \\
+	\subfloat[full-pol (3x3) determinant ratio]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) log distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
+		 \label{log_distance_3x3}
+	}
+\end{tabular}
+\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
+\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\end{figure}
+%endif
 
 Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
+%And if the  true signals are computed in the same manner as described before then in fact similar match can be easily observed.
+
+However, a more subtle observation phenomena occurs during the validation process for the determinant and its log-transformed model,
+%However, a more interesting  phenomena is to be described.
+%It happens in the validation process for determinant and its log-transformed model,
   where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
 %For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
+The phenomena happens when the true signal is estimated by the first approach i.e.
+equal to the average of the sample covariance matrix in its original domain (which evidently results in a different estimation for the true signal when compared with the method applied earlier).
+%Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
+
+Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small translation and scaling discrepancies -- which are
+ easier to observe in the log-determinant plots. Despite this, the curve shapes are quite similar.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
+	\subfloat[polsar (2x2) determinant]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[verify polsar 2x2: log-determinant]{
+	\subfloat[polsar (2x2) log-determinant]{
 		 \epsfxsize=1.5in
@@
 	} \\ 
-	\subfloat[verify polsar 3x3: determinant]{
+	\subfloat[polsar (3x3) determinant]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[verify polsar 3x3: log-determinant]{
+	\subfloat[polsar (3x3) log-determinant]{
 		 \epsfxsize=1.5in
@@
 \end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[polsar (2x2) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
+		 \label{determinant_2x2}
+	} 
+	\hfill	
+	\subfloat[polsar (2x2) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
+		 \label{log_det_2x2}
+	} \\ 
+	\subfloat[polsar (3x3) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
+		 \label{determinant_3x3}
+	} 
+	\hfill	
+	\subfloat[polsar (3x3) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
+		 \label{log_det_3x3}
+	} 
+\end{tabular}
+\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
+\label{fig:verify_polsar_2x2_simulation_det}
+\end{figure}
+%endif
 
@@
 Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  not only shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  but also illustrates the approximation power of the simplified formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
+  shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
+  as well as illustrating the simplified approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{tabular}
-\caption{The relationships between ENL and the sample variance of log-determinant and log-intensity}
+\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots}
 \label{fig:plot_enl_var_relation_1x1_and_2x2}
 \end{figure}
-
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
-The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[ENL and variance log-intensity relations for SAR data]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
+		 \label{plot_enl_var_relation_1x1}
+	} 
+	\hfill	
+	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
+		 \label{plot_enl_var_relation_2x2}
+	} 
+\end{tabular}
+\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
+\label{fig:plot_enl_var_relation_1x1_and_2x2}
+\end{figure}
+%endif
+
+\subsection{Using estimated ENL to better explain practical data}
+
+For this experiment an example RADARSAT2 dataset is used, in its Fine-Quad mode Single-Look format.
+Nine-look processing is applied before the dispersion histogram in the log-transformed domain is computed for a known homogeneous area.
+The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
+  against the theoretical models for the nominal ENL value of 9.
+The match, however, is evidently not very close.
+
+A better match can be achieved by first estimating ENL from the observable variance of the log-determinant,
+  and the theoretical model is then simulated for the estimated ENL.
 Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
+  showing a much better consistency.
+This procedure can always be carried out for a given dataset,
+  as long as a homogeneous area can be defined and extracted.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
+\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics.
+However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL which matches the data much more closely.}
 \label{fig:handling_radarsat2_oversampling_practice}
 \end{figure}
-
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
+		 \label{sar}
+	} 
+	\hfill	
+	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
+		 \label{part_pol}
+	}   
+\end{tabular}
+\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
+Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then explain the data reasonably well.}
+\label{fig:handling_radarsat2_oversampling_practice}
+\end{figure}
+%endif
+
+Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
+  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
+Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
+The mis-match problem appears to depend upon how much over-sampling was used to generate the dataset as well as upon the data dimension.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
+	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
 		 \label{sar}
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}
 \end{figure}
-
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
+		 \label{sar}
+	} 
+	\hfill	
+	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
+		 \label{part_pol}
+	}   
+\end{tabular}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
+\label{fig:handling_airsar_oversampling_practice_full_pol}
+\end{figure}
+%endif
+
+\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+%\section{Visually Evaluating POLSAR Speckle Filters over Heterogeneous Areas}
+\label{sec:evaluating_polsar_filters}
+
+Previous sections have developed a model for POLSAR, which is also shown to be applicable to SAR.
+In this section, the use of consistent measures of distance in the context of POLSAR speckle filtering are explored briefly.
+It has been found \cite{Rignot_1993_TGRS_896} that for SAR data in its original domain,  
+   ratio is a better evaluation than standard subtractive residual. 
+However, ratio residual is argued as not being natural for digital display \cite{Medeiros_2003_IJRS}.
+Our previous work in the context of SAR speckle filtering found that
+  in the log-transformed domain, this ratio is transformed into a subtractive residual that is homoskedastic.
+
+The variance of sample log-determinant is shown to be linked to the ENL index.
+This forms the basis for evaluating POLSAR speckle filters over homogeneous areas.
+The procedure is simple:
+To evaluate a given POLSAR speckle filter over homogeneous areas,
+  the filter is applied over a known homogeneous area and the sample variance of log-determinant is measured.
+The Equivant Number of Looks (ENL) is then estimated
+  either by referencing prepared graphs from Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} 
+  or alternatively by setting the measured variance value to $var[\ln{|C_v|}]$ in Eqn. \ref{eqn:enl_estimation_formula}.
+
+In order for such a procedure to be generic,
+  it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
+That can be tested by applying the POLSAR filter into different sets of homogeneous areas and investigating the plots of the dissimilarity measures presented above.
+Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that
+  the 3$\times$3 POLSAR boxcar filter preserves the consistency property.
+In this case, the boxcar filter is applied to 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
+Log-determinant and the contrast measures are computed for the input and output filtered POLSAR data,
+  and their plots are presented.
+In fact, the test procedure can be applied on any of the models presented above.
+
+%ifdef FINAL
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+		 \label{log_determinant}
+	} 
+	\hfill	
+	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+		 \label{contrast}
+	}   
+\end{tabular}
+\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlying signal $\Sigma_v$, the shapes of the histograms should match.}
+\label{fig:boxcar_3x3_preserves_consistency}
+\end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinants histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+		 \label{log_determinant}
+	} 
+	\hfill	
+	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+		 \label{contrast}
+	}   
+\end{tabular}
+\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
+\label{fig:boxcar_3x3_preserves_consistency}
+\end{figure}
+%endif
+
+The consistency property of a POLSAR speckle filter is important
+  not only to make the estimation of ENL become general enough.
+It is also to ensure that any classification / detection algorithm
+    which is based on the scalar and consistent measures of distance will work on both pre-filtered and post-filtered data.
+Otherwise if a POLSAR speckle filter gives different plots for different homogeneous areas,
+  then not only its ENL estimation will be dependent on the underlying signal, 
+  but its output also shall not follow the statistical distribution family that characterises multi-look POLSAR.
+Thus the preservation of this consistency is believed to be an important consideration for POLSAR speckle filters
+  if we want many general detection and classification algorithms to work on the filtered data output.
+
+In evaluation over heterogeneous area, the consistent measures of distance may also be an invaluable tool.
+ %in helping to evaluate POLSAR speckle filters.
+Firstly, since the model for log-determinant is additive and homoskedastic,
+  log-determinant images may naturally be better suited for gray-level digital display.
+Specifically for evaluation of statistical estimators, it is both important and convenient to investigate the estimators' error / residual image. %plays an important role.
+
+For further analysis, the residual is defined here as the distance between the log-determinants of the filtered outputs and the original input. 
+Ideally speaking, under the context of an additive model,
+  a perfect estimators residual should consist only of random noise.
+And under the assumption of homoskedasticity, 
+  the Gauss Markov theorem becomes applicable.
+Thus the optimal estimator is expected to exhibit minimal Mean Squared Error (MSE).
+Over a homogeneous scene, this is reflected in the expectation of minimal bias and variance (hence maximal ENL).
+Over a heterogeneous scene, where the underlying signal is not known \textit{a priori},
+  the second best gauge is possibly to have the residual MSE being as close as possible to the MSE of the inherent noise.
+
+To illustrate the above analysis, an experiment is carried out to evaluate the performance of 3$\times$3 and5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+A square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters applied to the patch.
+Then the log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+Assuming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+This optimal value is computed   
+by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
+
+%ifdef FINAL
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+%Note if the picture does not look convincing enough
+%another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  but also the distortion impact of the filter can also be made visible by the residual image.
+In visual evaluation, while it is quite hard to observe the worsening blurring-effects of the boxcar 5$\times$5 speckle filter as compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such a conclusion can be made relatively easier by visualising the residual image.
+
+When quantified evaluation is carried out
+  where the residual MSE is compared with the expected level of noise to be removed,
+  the excessive blurring effects of the 5$\times$5 filter become clearly evident.
+%IVM: [cut this]In fact, even the 3$\times$3 boxcar filter itself might be also a bit blurry.
+%,  as suggested by its relatively high residual values.
+%A conclusion which is hard to make
+It may be hard to make such a conclusion just by looking at the filtered imagery.
+However, by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer more conclusive evidence.
+
+Further discussion on the specific topic of evaluating SAR speckle filters is given in our work that focused specifically on SAR \cite{Le_2013_TGRS_SAR_MSE}.
+However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters (i.e. extending the previous SAR approach).
+
+Specifically, this is an illustration of how the proposed theoretical model can possibly be applied to a practical scenario, rather than a full evaluation procedure and methodology.
+%IVM [cut this],  as it is not as a full proposal for such an evaluation procedure for POLSAR speckle filters.
+
+\section{Discussion and Conclusion}
+\label{sec:discussion_conclusion}
+
+%\subsection{The Likelyhood Test Statistics for POLSAR}
+
+%\begin{eqnarray}
+%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%\end{eqnarray}
+
+\subsection{Discussion}
+
+Let us begin the discussion by noting a few theoretical properties of the proposed statistical model.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
+
+Second, the model is developed for the POLSAR covariance matrix.
+However, since the POLSAR coherent matrix is related with the covariance matrix via an unitary transformation, which preserves the determinant as invariant,
+the model should also be applicable on the coherency matrix.
+
+The model is far from complete.
+ It calls for the reduction of the multi-dimensional POLSAR data into a scalar value.
+While this is probably desirable for a wide range of application where a one-dimensional number is required to represent the complex multi-dimensional data,
+  such a reduction is unlikely to be lossless.
+Thus is very similar to the way the Wishart Classifier is employed, and thus to better understand POLSAR data
+  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
+the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).
+
+However the model as presented is promising. Those presented in this paper were first developed for partial and monostatic POLSAR data.
+They were then shown to be also applicable to traditional SAR data.
+Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigations.
+%Other interesting phenomena which may warrant more study include the applicability of the model on correlated polsar channels ($S_{hh},S_{vv}$) as well as a better explanation in the use of mse to evaluate polsar speckle filters.
+
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+Since extensive examples have been shown to support the use of MSE for SAR data,
+  it is reasonable to expect the relevance of MSE to also be demonstrated for POLSAR data.
+If that is the case, a large number of existing algorithms can become applicable to the POLSAR model in this log-transformed domain,
+  which has been shown to be both additive and homoskedastic.
+
+\subsection{Conclusion}
+\label{sec:conclusion}
+
+In conclusion, a couple of statistical models for the determinant of the POLSAR covariance matrix is proposed and validated in this paper.
+Compared to other statistical models for POLSAR, the proposed models are scalar and representative for the multi-dimensional POLSAR data.
+These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
+Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
+As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
+
+%An additive and homoskedastic model, 
+%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+%  is proposed in this paper.
+%The theoretical model is shown to be comprehensive:
+%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+%
+%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+%  is gracefully transformed into traditional SAR intensity.
+%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
+
+\appendices
+\section{Homoskedastic Model for the Log-Determinant}
+\label{chap:appendix_a}
+
+\subsection{Log-Chi-Square Distribution and its Derivatives}
+%\section{Log-Chi-Square Distribution}
+\renewcommand{\theequation}{\thesection.\arabic{equation}}
+\setcounter{equation}{0}
+
+This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
 

### 2013-04-22 paper_dev/clean.sh

@@ -4,3 +4,9 @@ cp article.bib b.article.bib
 rm article.*
 mv b.article.tex article.tex
 mv b.article.bib article.bib 
+
+cp letter_to_reviewers.tex b.letter_to_reviewers.tex
+rm letter_to_reviewers.*
+mv b.letter_to_reviewers.tex letter_to_reviewers.tex
+
+

### 2013-05-17 paper_dev/article.tex
2013May_0517

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
-
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{cite} %for citations
+\usepackage{url}
+
+ %this is for math typing (eg: cases)
+\usepackage{amsmath}
+   \usepackage{amsfonts}   % if you want the fonts
+   \usepackage{amssymb}    % if you want extra symbols
+\usepackage{epsfig} %for figures
+
+\usepackage[center]{caption}%for captions
+\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+
+%opening
+\title{
+  Scalar and Representative Models for Polarimetric SAR Data
+}
+
+%\author{Thanh-Hai Le, Ian McLoughlin}
+\author{Thanh-Hai~Le,
+        Ian~McLoughlin, 
+	and Chan-Hua~Vun%
+\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2013; revised ?.}}
+
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
+Compared to other scalar statistical models for POLSAR,
+  the proposed models are highly representative of the multi-dimensional data
+  and enable useful discrimination measures to be determined easily. %consequently they lead to useful discrimination measures.
+When the multi-dimensional models are collapsed to a one-dimensional case,
+  they are shown to exactly match the traditional statistical models for SAR intensity.
+The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
+The proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
+An  example is also shown where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+\end{abstract}
+
+\begin{IEEEkeywords}
+Polarimetric Synthetic Aperture Radar, Electromagnetic Modeling, Multidimensional Signal Processing  
+\end{IEEEkeywords}
+
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+
+During the past decades, exponential growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
+technology to become a feasible and preferred technique for earth observation applications.
+SAR technology has since extended in a few directions, one of which is polarimetric SAR (POLSAR).
+POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
+  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
+
+While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
+Namely that there now exists not one but many observables quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
+The research community has responded largely by developing different statistical models for various POLSAR observables.
+However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
+Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
+On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.
+
+This paper presents novel statistical models for multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+Specifically statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domian determinant, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
+The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
+  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
+With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
+  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
+The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
+Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
+This is followed by a conclusion in Section \ref{sec:conclusion}.
+
+\section{Related Work in Literature}
+\label{sec:lit_review}
+
+This section outlines related published work.
+In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
+Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
+Section \ref{sec:lit_measures} further strengthen these findings by discussing discrimination measures that have been proposed for POLSAR,
+  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
+However, while an exact statistical distribution is needed for the test,
+  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
+
+\subsection{Investigated Scalar Observables for POLSAR Data and their Statistical Models}
+\label{sec:lit_models}
+
+Different target decomposition theorems have identified many different scalar observables for complex POLSAR data.
+In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
+While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, at its conclusion, the paper indicated that: it is impossible to identify the best representation.
+To be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
+  rather than providing a single unified representation of the POLSAR data.
+
+Given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
+  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
+This becomes an alternative approach used in the study of POLSAR data.
+However, such derivations are no trivial task, and so far, only a handful of such statistical models have been proposed, including the following:
+  \begin{enumerate}
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \end{enumerate}
+
+More recently, statistical models for
+  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been studied.
+While these models undoubtedly help in understanding POLSAR data,
+  none of these observables have been shown to meet the dual criteria of
+  1) resulting in statistically consistent discrimination measures and
+  2) being representative of the complex POLSAR data.
+
+\subsection{POLSAR Discrimination Measures}
+\label{sec:lit_measures}
+
+The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
+  probably because of the multiplicative nature of the noisy data.
+
+In the field of POLSAR, the Wishart distance is probably the most widely used as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
+It is defined as \cite{Lee_1994_IJRS_2299}
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dissimilarity measures.
+These include the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance \cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+.
+
+Closer investigation of these dis-similarity measures reveals that most are related in some way. %to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
+  when the two data sets have the same number of looks, i.e. $L_x=L_y$.
+The close relation among the measures is further supported by the fact that
+  all of their proposing papers referenced the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrix is considered:  
+\begin{equation*}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation*}
+
+Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{eqnarray}
+
+To detect changes, a test statistic is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
+
+\section{Scalar Statistical Models for POLSAR}  
+\label{sec:theoretical_model}
+
+In this section, several scalar statistical models for POLSAR are presented.
+After section \ref{sec:model_basic} briefly introduce the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
+  section \ref{sec:polsar_heterosked_model_and_log_transform}
+  presents the theoretical models together with mathematical evidence for two related points.
+The first point is that: the POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion states: log-transformation converts it into an additive and homoskedastic model.
+Several consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
+
+\subsection{Basics of POLSAR Statistical Analysis}
+\label{sec:model_basic}
+
+In this paper, the POLSAR scattering vector is denoted as $s$.
 In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
@@
 
-Let $\Sigma=E [ss^{*T}]$ denotes the population expected value of the POLSAR covariance matrix,
-  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
-Assuming all the elements in $s$ are independent
-  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
-  then the probably density function (PDF) of $s$ can be written as:
+Let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
+  where $s^{*T}$ is the complex conjugate transpose of $s$. 
+Assuming %all the elements in $s$ are independent and
+  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
+  then the probability density function (PDF) of $s$ can be written as:
 \begin{equation}
@@
 \end{equation}
-where $|M|$ denotes the determinant of the matrix $M$.
-
-As covariance matrix is only defined on multiple data points,
-  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
-They are formed as the mean of Hermitian outer product of single-look scattering vectors
+where $||$ denotes the matrix determinant.
+
+The sample POLSAR covariance matrix is formed as the mean of Hermitian outer product of independent single-look scattering vectors,
 \begin{equation}
@@
 \end{equation}
-with $s_i$ denotes the single-look scattering vector,
-  which equals $s_{part}$ in the case of partial POLSAR and
-  $s_{full}$ in the case of full polarimetry,
+where $s_i$ denotes the single-look scattering vector,
+  which equals $s_{part}$ for the case of partial POLSAR or
+  $s_{full}$ for the case of full polarimetry,
 and $L$ is the number of looks.
 
-Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
+Complex Wishart distribution statistics are normally used for the scaled covariance matrix
 $Z=LC_v$, whose PDF is given as:
@@
 
-Our approach differs by applying the homoskedastic log transformation
-  on a less-than-well-known result for the deterimant of the covarinace matrix.
-  %under the assumption of circular complex Gaussian distribution
-  %applicable for POLSAR data.
-In \cite{Goodman_1963_AMS_178}, %Goodman
-it has been proven that the ratio between the observable and the expected values of the sample covariance matrix's determinants
-  behaves like a product of $d$ chi-squared random variables with different degrees of freedom 
+The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
+Goodman \cite{Goodman_1963_AMS_178} proved
+that the ratio between the observable and expected values of the sample covariance matrix's determinants
+  behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
 \begin{equation}
@@
 
-\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
+\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
 
-In this section the multiplicative nature of POLSAR data is illustrated.
-Log-transformation is shown converting this into a more familiar additive model.
+In this section the multiplicative nature of POLSAR data is first illustrated.
+ Log-transformation is used to convert  the data into a more familiar additive model.
 Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
-  is proved to be the case for the original POLSAR data.
-In log-transformed domain, the case for a homoskedastic model,
-  where  variance is fixed and be independent of the underlying mean,
-  is demonstrated.
-To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.
-
-From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
-we have:
+  is shown to be present in the original POLSAR data.
+In the log-transformed domain, a homoskedastic model is demonstrated,
+  where sample variance is fixed and thus independent of the underlying signal.
+Several intermediate mathematical steps are not shown here, but can be found in Appendix \ref{chap:appendix_a}.
+
+From Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv}
+we can deduce the following relationships:
 \begin{eqnarray}
@@
 
-In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
-Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
+In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered constant.
+Thus Eqn. \ref{eqn:determinant_distribution} indicates that: 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
 At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
-  the logarithmic transformation converts this into a more familiar additive noise.
-
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows the PDF:
-\begin{equation}
-pdf(x;k) =
-  \frac{x^{(k/2)-1} e^{-x/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}
+  the logarithmic transformation has converted this to the more familiar additive noise.
+
+Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follow a known PDF:
+\begin{equation}
+pdf(x;2L) =
+  \frac{x^{L-1} e^{-x/2}}{2^L \Gamma\left(L\right)}
 \label{eqn:chi_squared_dist_pdf:chap4}
 \end{equation}
-Applying the variable change theorem, 
+applying the variable change theorem, 
   its log-transformed variable follows the PDF of:
@@
 
-Given the probability distribution function, the characteristic function of both the chi-squared and log-chi-squared random variables
+Using these PDFs, the characteristic functions (CF) of both the chi-squared and log-chi-squared random variables
   can be written as:
@@
   \end{eqnarray}
-Subsequently their means and variances can be computed from the given characteristic functions as:
+ Their means and variances can subsequently be computed from these  characteristic functions, leading to the following relationships:  
   \begin{eqnarray}
@@
 Specifically:
-\begin{eqnarray*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
+\begin{align*}
+  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
+  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+\end{align*}
 
 Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
-\begin{eqnarray}
-  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
-\end{eqnarray}
-
-Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
+\begin{align}
+  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
+  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+\end{align}
+
+For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
   the underlying $\Sigma_v$ is expected to differ from one region to the next.
-Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
-  %and it is clear that 
-  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
+Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ vary depending on the underlying signal $\Sigma_v$. 
 In such context, Eqn.
-\ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
-At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.
-
-\section{Consistent Measures of Distance for POLSAR data}
-
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
-  this section introduces the consistent sense of distance in a few different perspective.
-First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-the following random variables,
-  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
-  are observable according to their definitions:
-%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
-
+\ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
+At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
+  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$, exhibiting its homoskedastic nature.
+
+\subsection{Consistent Measures of Distance for POLSAR}
+\label{sec:distance_measure}
+
+Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2010_ACRS},
+  this section introduces the consistent sense of distance from different perspectives.
+Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+random variables,
+  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
+  are the observable according to the following definitions:
 \begin{eqnarray}
@@
 \end{eqnarray}
-From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
+
+On the other hand, under a looser assumption %From another perspective
+  where the POLSAR is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
+  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
 \begin{eqnarray}
@@
 
-Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
-  Appendix \ref{sec:appendix_b} derives the characteristic functions for the summative random variables as:
+Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
 \begin{align}
@@
 
-Since each elementary simulation component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
+Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
   it is natural that these variables also follow fixed distributions.
-Moreover, they are independent to $\Sigma_v$.
-This serves as conclusive evidence that
-  these random variables follows consistent and fixed distributions,
-  regardless of the underlying signal $\Sigma_v$.
-
-\section{SAR as the Special Case of Polarimetric SAR}
+Moreover, they are independent of the underlying signal $\Sigma_v$.
+
+\section{SAR as the one-dimensional case of multi-dimensional POLSAR}
 \label{sec:sar_special_case_of_polsar}
 
-The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
-In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
-Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
-Mathmatically, the sample covariance matrix is reduced to the sample variance
-  and the determinant equates the scalar value.
-On another hand, it is well known that for SAR data, variance equals intensity.
-Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
-This can be thought of 
-  either as a cross-validation evidence for the proposed POLSAR models
-  or alternatively as having SAR as the special case of POLSAR. 
-%  with well known results for SAR intensity is presented.
-
-The results so far for our models can be summarized as:
+The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
+This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
+  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into 1-dimensional conventional SAR data.
+Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
+As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
+Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
+  as well as reminding us that SAR is a special case of POLSAR.
+
+The results for our models can be summarized using the following equations:
 \begin{align}
@@
 
-Upon setting $d=1$ into the above models,
-  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+Upon setting $d=1$ into the above equations,
+  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
+First is the following results obtained from our previous works on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
 \begin{align*}
@@
 \end{align*}
-but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
   \begin{eqnarray}
@@
   \end{eqnarray}
-Furthermore, the following results for multi-look SAR data,
-  which can be thought of 
+Furthermore, the following derivations for multi-look SAR data
+   show that it can be considered 
     either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results
-  are also derived as:
+    or as simple cases of the POLSAR results:
   \begin{align*}
@@
 
-This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
+\section{Validating the proposed models against real-life data}
+\label{sec:polsar_models_validation}
+
+This section aims to verify the theoretical models against practical data.
+Since the previous section have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  which have been validated extensively, only a quick validation is needed for this case.
+
+Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
-
-\begin{figure}[h]
+The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
+ The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify multi-look SAR log-distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[multi-look SAR log-distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
 		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
@@
 
-\section{Validating the models against real-life data}
-\label{sec:polsar_models_validation}
-
-\subsection{Explaining practical data with the given Number-of-Looks}
-
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
-  assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
-
-Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
+After this quick validation, the rest of this section focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
+Specifically, section \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
+While the match appears to be reasonably good, it can be further improved.
+Section \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
+  while section \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
+With the newly estimated ENL, section \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
+
+\subsection{Using the nominal ENL to validate the theoretical models} 
+\label{sec:valid_nominal_enl}
+
+The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
+Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.
+
+For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
+Both the the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
+These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
+Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
+Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.
+
+The least-assumed stochastic processes for dispersion and contrast are validated first.
+For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
+Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
 
 At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
-\begin{figure}[h]
+Here a nominal look-number L=4 is used
+  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
+The plots, presented in Fig.
+  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
+
+\begin{figure}[h!]
 \centering
@@
 Apart from dispersion and contrast,
-the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
+  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
 There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
+Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+Both approaches will be presented in this section.
+As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
+In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
+  and \ref{eqn:log_determinant_distance_distribution},
   while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
   with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
-\begin{figure}[h]
+%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
+A close match is again observed, validating the models for log-distance and determinant ratio.
+
+\begin{figure}[h!]
 \centering
@@
 
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
-  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
+Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
+  where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
+The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
+Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[polsar (2x2) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
                  \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
@@
 
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
+In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
 The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
@@
   depending on which estimation method was being used.
-The discrepancy suggests that at least one parameter for the models was wrongly employed.
-
-But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  where not only the look number is shown to be misused
-  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-For now, let us contend that:
-  using appropriate estimation of the parameters, 
-  the proposed models match reasonably well with the practical data.
-
-\subsection{Comparing Theoretical Assumptions and Practical Implementations}
+The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
+This is discussed in the next section.
+
+\subsection{Difference between the theoretical assumptions and the conditions found in practice}  
 \label{sec:improve_the_match_bw_theory_practice}
 
-Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
+Even though the assumptions made in developing this theory have intentionally been kept minimal, 
   like all other similar models, the proposed model in this paper is built upon certain presumptions.
-Practical conditions however may not always satisfy these prerequisites.
-In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
-And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
-
-There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
-The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
-Practically however high correlation is routinely observable between the POLSAR data components,
-  specifically between $S_{hh}$ and $S_{vv}$.
-This phenomena also presents in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
-Despite the mismatch,
-  astute reader would probably notice that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
-\ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
-This suggests that the proposed model is also applicable on correlated POLSAR components,
-  eventhough a full explaination for this, however, is outside the scope of this paper.
-
-Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent to each other.
-This is a reasonable assumption given that 
-  the transmission and receipt of analog signals are done independently for each radar pulse, i.e. for each resolution cell.
-Thus theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
-
-However, the actual imaging mechanism of a real-life (POL)SAR processor is that of digital nature,
-where the analog signal is to be converted into a digital data-set. 
-Specifically, the analog signal in SAR 
-  which is characterized by the pulse bandwidth measurement,
-  is fed into an analog-to-digital sampling and conversion process 
-  which is characterized by its sampling rate.
-Theoretically it is possible to define a sampling rate to ensure that each digital pixel correspond exactly to an analog physical cell resolution.
-Practically however, to ensure ``perfect reconstruction'' of the analog signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
-This results in a higher number of samples / pixels than the number of physical cells available in the scene.
-
-Stated differently, in practical data each physical radar cell is spread to more than one pixel
-  and each pixel now contains less than one physical analog cell.
-This high sampling rate also results in 
-  a significantly higher correlation between pairs of pixels that maybe related within a single physical cell resolution 
-  than the correlation found between pairs of pixels that are further away and hence having less physical relation to each other.
-It also results in reduced effective number of look, 
-  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
-The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
-  while the later is experimental observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
+However, practical conditions may not always satisfy these prerequisites.
+In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.
+
+The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
+  the transmission and receipt of analogue signals independent for each radar pulse, i.e. for each resolution cell.
+However, the actual imaging mechanism in a real-life (POL)SAR processor is that of a digital nature,
+  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
+Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
+Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.
+
+Thus in practical images, each physical radar cell may be spread over more than a single pixel,
+resulting in both %This results in 
+  a higher correlation between neighbouring pixels \cite{Raney_1988_TGRS_666} %that may be related within a single physical cell resolution,
+  and a reduced effective number of look\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
 The oversampling practice is also documented by the producers of SAR processors.
 For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}
-
-The proposed model can handle this imperfection that is available in pratical data.
-The trick is that instead of using the nominal Number of Look given by the SAR processor,
-  an ENL estimation procedure is employed. %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
-The first part of this section details a simple ENL estimation technique for POLSAR data.
-While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
-It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved,
-  by using ENL estimation.
-
-\subsection{Estimating the Effect Number-of-Looks (ENL)}
-
-This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
-The common approach in tackling this problem is by investigating the summary statistics of an known homogeneous area in the given data
+While for RadarSat2, the pixel resolution and range - azimuth resolution combination for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
+In short, while the indepedent samples assumption is made out of necessity in theory,
+  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighboring samples. % are actually correlated
+This documented imperfection also leads to the rise of effective number-of-look concept (ENL),
+  which is almost always smaller than the nominal look-number.
+
+The proposed model apparently can handle the imperfection. %that is found in practical data.
+The handling process, however, is slightly more complex.
+Instead of adopting the nominal Number of Looks given by the SAR processor,
+  the ENL is to be estimated from the given data.
+This is discussed in the next section.
+
+\subsection{ENL Estimation for POLSAR data}
+\label{sec:valid_enl_estimation}
+
+The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
   before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ has been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
-In fact Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-Recall that in carrying out validation process for AIRSAR Flevoland data using the nominal look number of 4, this relationship was broken.
-The reason for such broken relationship is believed to be an inexact look number was taken.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ is known,
-  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensure the above relationship is valid.
-
-In fact, this approach was taken in \cite{Anfinsen_2009_TGRS_3795},
+The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
+  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
+In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
+  it is possible to estimate the ``effective'' number of look, by finding an $L$ that ensures the above relationship is valid.
+This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
   where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
-Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
-Instead of relying on the equations for statistical mean to find ENL,
-  our approach make used variance statistics in the homoskedastic log-domain to find ENL.
-Since the determinant of POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
-  this approach can be considered as the generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} towards POLSAR data.
+However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.
+
+In this section, an alternative approach making use of variance statistics in the homoskedastic log-domain to find ENL is proposed.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
 \end{equation}
-where $\psi^1()$ denotes tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
-Interestingly that would also require some iterative computations.
+where $\psi^1()$ again denotes the tri-gamma function.
+
+Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for unknown $L$,
+  although it would also require some iterative computation.
 Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph.
-And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
+  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph, or from the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
   \begin{equation}
@@
 
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
-The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
-Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
-\begin{figure}[h]
+\subsection{Using estimated ENL to better explain practical data}
+\label{sec:valid_improve_practice}
+
+To demonstrate the improvement obtained using this ENL estimation,  a sample  single-look complex fine-quad RADARSAT2 dataset is used. 
+A nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
+The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
+  against the theoretical models for the nominal ENL value of 9.
+As expected the match is evidently not very close.
+
+We now compare this to the estimated ENL approach.
+First, an ENL estimate is obtained from the observable variance of the log-determinant. 
+Then the new sample histogram is overlaid on the same figure,
+  showing a much better consistency.
+This procedure can always be carried out for a given dataset,
+  as long as a homogeneous area can be defined and extracted.
+
+\begin{figure}[h!]
 \centering
@@
 \caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
+Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
 \label{fig:handling_radarsat2_oversampling_practice}
@@
 
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
-\begin{figure}[h]
+The same approach can be applied on the AIRSAR Flevoland data to improve the validational match described earlier.
+Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
+  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
+Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
+	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
 		 \label{sar}
@@
 
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
+\section{Discussion}
+\label{sec:discussion}
+
+Let us begin by noting a few theoretical properties of the proposed statistical model.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
+
+Second, the model is developed for the POLSAR covariance matrix.
+However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+  the model should also be applicable to the coherency matrix.
+
+The model is far from complete.
+ It reduces the multi-dimensional POLSAR data to a scalar value.
+While this is probably desirable for a wide range of application,
+  such a reduction is unlikely to be lossless.
+Thus to better understand POLSAR data
+  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
+the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).
+
+However the proposed model is also promising.
+Eventhough initially developed for partial and monostatic POLSAR data,
+  it was later shown to be applicable to traditional SAR data as well.
+Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
+
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
+
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
+
+In evaluating SAR speckle filters, the intensity ratio is widely used.
+Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+Assuming a perfect filtering condition, the ratio image should only contain random noise.
+Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+
+Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+  this technique can be equally applied to evaluate POLSAR speckle filters.
+In fact better results can be achived.
+In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not very well suited for digital image presentation,
+  which is linear and additive in nature.
+Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.
+
+To evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
+  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters are then applied to the patch.
+\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  the distortion impact of the filter can also be made visible by the residual image.
+In visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such an observation can be made relatively easier by inspecting the residual image.
+
+There are many similar SAR data processing technique that may be adaptable to POLSAR.
+Examples in the same topic of evaluating speckle filters include
+  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+
+In fact, at the time of this writing, the field of SAR is much more developed than the field of POLSAR.
+The two fields however are quite separated,
+  as many techniques applicable to SAR are not directly applicable to POLSAR.
+This work may build the bridge between these two separated fields,
+  inviting potential extension of various SAR processing techniques on POLSAR data.
+Here a specific example is shown
+  where, similar to the way ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+In general, we believe there are many more unexplored possibilities for such applications
+  which is only limited by our imagination.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
+  resulting in several consistent discrimination measures for POLSAR applications.
+The theoretical models are shown to be powerful in that:
+  not only it can provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
+  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
+They are also practically useful since they lead to several consistent discrimination measures.
+Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
+Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
+
+%In conclusion, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix,
+%  which result in several consistent discrimination measures for POLSAR, are proposed and validated in this paper.
+%The theoretical model is shown to be comprehensive in that:
+%  not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
+%  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
+%Compared to other scalar statistical models for POLSAR, the proposed models are highly representative of the multi-dimensional POLSAR data.
+%%These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
+%%Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
+%%As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
+%
+
+%An additive and homoskedastic model, 
+%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+%  is proposed in this paper.
+%The theoretical model is shown to be comprehensive:
+%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+%
+%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+%  is gracefully transformed into traditional SAR intensity.
+%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+%%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+%%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+%%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.  
+%The models may also form a bridge, allowing the adaptation of many existing SAR data processing technique for POLSAR data,
+%  a quick example of this is briefly described in this paper.
+%This paper
+
+\appendices
+\section{Homoskedastic Model for the Log-Determinant}
+\label{chap:appendix_a}
+
+\subsection{Log-Chi-Square Distribution and its Derivatives}
+%\section{Log-Chi-Square Distribution}
+\renewcommand{\theequation}{\thesection.\arabic{equation}}
+\setcounter{equation}{0}
+
+This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
 

### 2013-05-17 paper_dev/article_201303_Mar06_Ian.tex
2013May_0517

--- 2013-04-22 paper_dev/article_pp.tex
@@
 \title{
-  %Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
-  Scalar and Representative Models for Polarimetric SAR Data
+  Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
+%Scalar Homoskedastic Models for POLSAR data
 }
@@
 \markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+{ Le \MakeLowercase{\textit{et al.}}:  Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data}
 
@@
 \begin{abstract}
-  While statistical models are important in understanding the stochastic nature of Polarimetric SAR (POLSAR),
-  scalar discrimination measures are routinely used in processing this multi-dimensional data.
-  Ideally speaking, the latter should be drived from the former.
-  As far as we know, however, it has not exactly been so for the case of POLSAR.
-  In this paper, a couple of statistical models for the determinant of the POLSAR covariance matrix and its log-transformed derivations are proposed.
-  These scalar models for the determinant of the POLSAR covariance matrix are shown to be respresentative
-    since this observable is neatly transformed into the traditional SAR intensity
-    when the generic multi-dimensional polarimetry is collapsed into the case of one-dimensional SAR. %case of traditional SAR data.
-  Similar to SAR, the generic model for POLSAR is also shown to be multiplicative and heteroskedastic in the original domain 
-    and the logarithmic transformation converts this into a more familiar additve and homoskedastic model.
-  Moreover, the scalar property of these statistical models lead to the derivation of several statistical discrimination measures. %homoskedastic measures of distance.
-  All of these statistical models are validated on real-life captured data
-    and they are shown to be applicable even when the theoretical ``independent samples'' assumption is violated in practice.
-  %The paper also illustrates a couple of benefits of these models, specifically for using the homoskedastic discrimination measures.
-  %A couple of benefits for using these homoskedastic dis-similarity measures are then illustrated in this paper.
-  %These homoskedastic measures of distance
-  The combination of scalar, additive and homoskedastic properties of the derived statistical models bring about a couple of benefits, which are also described in this paper.
-  First, compared to the original multiplicative domain, %dis-criminative measure of ratio,
-    the additive log-transformed fit more naturally with the linear nature of digital imagery.
-  Second, since the Gauss-Markov theorem is again applicable in the homoskedastic log-transformed domain,
-    the use of Mean Squared Error (MSE) as an reliable objective function for POLSAR speckle filters is briefly explored.
-%This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
-%The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
-%The dissimilarity measurements, 
-%computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
-%It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
+The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
+The dissimilarity measurements, 
+computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
+It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
+Thus the SAR intensity statistics can now be considered as a special case of  this new theoretical model for POLSAR.
+The statistical model is also robust, and reasonably accurate at describing practical data,
+ even  when  the supposedly independent polarimetric components are actually highly correlated (e.g. between $S_{hh}$ and $S_{vv}$).  
+Moreover, the match can be further improved 
+  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
+  instead of blind acceptance of the number of looks figure reported by the SAR processor.
+The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+%In this paper, a homoskedastic and additive model for polarimetric SAR (POLSAR) data is introduced. 
+%The statistical properties of this model subsequently lead to a few different consistent measures of distance for the POLSAR covariance matrix.
+%The dis-similarity measurements are initially developed for both partial (2x2) and full (3x3 monostatic case) polarimetric SAR data.
+%They are computed from the determinant of the POLSAR covariance matrix.
+%Interestingly, when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
 %  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
-%This puts the SAR intensity statistics to lie within the natural coverage of this new theoretical model for POLSAR.
-%Not only comprehensive theoretically, the statistical model is also robust in handling practical data. 
-%It can be validated and match reasonably well  with practical data.
-%Moreover, the match can be further improved 
-%  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
-%  instead of blind acceptance of the number of looks figure reported by the SAR processor.
-%The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+%Thus the SAR intensity statistics can now be considered as a special case of the theoretical model for POLSAR.
+%While powerful theoretically, the statistical model is also robust in handling practical data.
+%It can be validated and match reasonably well with practical data,
+% even  when  the supposedly independent polarimetric components are actually highly correlated (e.g. between $S_{hh}$ and $S_{vv}$).
+%Moreover, the match can be further improved, as better match is shown achievable, 
+%  if the model validation process include an estimation of the dataset's Effective Number of Looks (ENL) 
+%  instead of blind employment of the look number given by the SAR processor.
+%Towards the end, the practical application of these dissimilarity measures is briefly demonstrated in the context of evaluating POLSAR speckle filters.  
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Polarimetric Synthetic aperture radar, Electromagnetic Modeling, Multidimensional signal processing  
+Polarimetric, Synthetic aperture radar, speckle-filtering, homoskedasticity
 \end{IEEEkeywords}
@@
 %\section{POLSAR data: statistical analysis and logarithmic transformation}
-
-In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
-As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
-POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
-Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
-
-With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
-The complex data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
-Under this condition, it is very important to understand the statistical models for (POL)SAR data.
-
-While the statistical models for homogeneous areas of one-dimensional SAR data have been developed,
-%  in extending the model toward heterogeneous images, the impact of heteroskedasticity has virtually been ignored.
-%Specifically the concept of distance as a measure of dis-similarity is seriously flawed, as it is widely known that ratio offers a better discrimination measure TODOCITE.
-%This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
-%From this log-transformed model, a few consistent measures of distance is proposed. 
-%in a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtraction, and thus distance.
-  in extending our understanding towards multi-dimensional POLSAR data, an important issue needs to be addressed.
-The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
-While different statistical models have been developed for different POLSAR observables,
-  for a statistical model to be useful, scalar discrimination measures need to be derived from it.
-Thus practical application for POLSAR data processing requires the dis-similarity measure to be scalar, consistent and preferably homoskedastic on one hand.
-On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
-
-In this paper, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
-The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario.
-Under this transformation, the determinant of the POLSAR covariance matrix is converted into the standard SAR intensity.
-Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
-And since POLSAR can be viewed as a multi-dimensional extension of SAR, the paper describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
-
-%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
-%Firstly, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear scale nature of digital imagery.
-%Secondly, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss Markov theorem is again applicable, the universal MSE deserves to be reviewed as a reliable objective function / criteria for (POL)SAR estimators.
-%This may open up a number of different research directions for future studies of (POL)SAR.
-%As example demonstrations of how these models and distance measures can be used, a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
-
-Specifically, the rest of this paper is structured as follows.
-After the related work in literature is critically reviewed in Section \ref{sec:lit_review},
-  Section \ref{sec:theoretical_model} presents the theoretical models for both partial and full polarimetric SAR and their derived discrimination measures.
-The representative power of the scalar models are illuminated in Section \ref{sec:sar_special_case_of_polsar},
-  which details how the proposed models for the multi-variate POLSAR also includes the well-known models for the traditional SAR as its special univariate case.
-%can be used to derive the well-known models for the univariate SAR data as its special case.
-Besides being theoretically comprehensive, 
-  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
-  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
-To demonstrate the application of these scalar and representative models, 
-  Section \ref{sec:evaluating_polsar_filters} explores how they can be used to evaluate POLSAR speckle filters.   
-In the end, Section \ref{sec:discussion_conclusion} provides the final conclusion of the paper.
-%critically reviews and discusses related literature  
-%  before the paper is concluded in Section \ref{sec:conclusion}.
-
-%In this paper, the above results are exploited in the context of POLSAR data processing.
-In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
-The paper is structured as follows:
-%  after the preceding introduction to the basics of POLSAR statistical analysis,
-%  the second section briefly reviews related work in published literature.
-%Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
-%The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
-%And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
-%Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
-%After the model is presented for both partial and full polarimetric SAR data,
-%  section \ref{sec:sar_special_case_of_polsar} discusses
-%    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
-%Besides being theoretically comprehensive, 
-%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
-%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
-%To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
-%  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
-%Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
-%  before the paper is concluded in Section \ref{sec:conclusion}.
-
-\section{Related Work in Literature}
-\label{sec:lit_review}
-
-This section critically review the related work in published literature.
-Specifically, the first sub-section shows that while many discrimination measures have been proposed for POLSAR data,
-  almost all of them depends on the likelihood statistical test for complex Wishart distribution.
-Unfortunately, in the original proposed work \cite{Conradsen_2003_TGRS_4}, while an exact distribution is to be expected, only an asymptotic distribution was given.
-The second sub-section reviews various statistical models for different POLSAR observables.
-Its purpose is to show that none of these models, as far as we know, led to statistically consistent discrimination measures.
-
-\subsection{POLSAR Discrimination Measures}
-
-This sub-section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
-In particular, a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
-will be briefly reviewed.
-%specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
-
-The commonly used measure of distance for matrices are either the Euclidean or the Manhattan distance,
-  which are defined in the following equations, respectively:
-\begin{align}
-  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
-  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
-\end{align}
-where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
- $||$ denotes absolute values
-and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
-  probably because of the multiplicative nature of the data.
-%In the context of polsar covariance matrix, however, they are not widely used 
-%  probably because of the multiplicative nature of the data.
-
-In the field of POLSAR, the Wishart Distance is probably the most widely used as part of the well-known Wishart Classifier \cite{Lee_1999_TGRS}.
-The distance is defined as \cite{Lee_1994_IJRS_2299}
-\begin{equation}
-  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation}
-As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
-
-Recent works have suggested a number of other dissimilarity measures.
-These include the asymmetric and symmetric refined wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
-\begin{align}
-  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
-    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
-\end{align}
-the Bartlett distance \cite{Kersten_2005_TGRS_519},
-  \begin{align}
-  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
-  \end{align}
-the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
-\begin{equation}
-  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
-\end{equation}
-and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
-\begin{equation}
-  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
-\end{equation}
-.
-
-In comparison to these formulae, the distance measures for two covariance matrices proposed in this paper can be written as:
-\begin{equation}
-  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
-\end{equation}
-At first glance, while the propose formula may be a lot simpler, it still operates in a similar way to others in making use of the log-determinant.
-
-Closer investigation of these dis-similarity measures reveals that most of them are related to each other.
-The Bhattacharyya distance is easily shown to be related to the Barlett distance.
-At the same time the Barlett distance can be considered as the special case of the Wishart Statistical Test distance, where the two data set have the same number of look, i.e. $L_x=L_y$.
-It is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper has fixed statistical behaviour, by comparing the symmetric and asymmetric versions of the refined Wishart distance, assuming that they are shown to follow fixed distributions.
-
-The close relation among these is further supported by the fact that
-all of the papers proposing these measures referenced the statistical model developed in \cite{Conradsen_2003_TGRS_4} as their foundation.
-%Interestingly, the change detection model in \cite{Conradsen_2003_TGRS_4} also make use of determinant ratio and log determinant in its derivation.  
-%The next sub-section will illustrate how the log-determinant model presented in this paper can offer an alternative and simple derivation for the change-detection statistics.
-In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
-  which have $L_x$ and $L_y$ as the corresponding number of looks,
-  come from the same underlying stochastic process,
-the likelihood ratio statistics for POLSAR covariance matrix is considered:  
-\begin{equation*}
-  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-\end{equation*}
-
-Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
-\begin{eqnarray}
-  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
-  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
-\end{eqnarray}
-
-To detect changes, a test statistics is developed based on this measure of distance.
-This means a distribution is to be derived for the dissimilarity measure.
-However, originally in the proposed work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution is derived.
-%In this sub-section, a statistical model is developed for this measure of distance.
-Since both $Z_x$ and $Z_y$ follow a complex Wishart distribution with $L_x$ and $L_y$ degrees of freedom,
-  $Z_x+Z_y$ also follows the complex Wishart distribution with $(L_x + L_y)$ degrees of freedom.
-In view of the models for $|C_v|$ and $\ln|C_v|$ developed in this paper (Eqns. \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution}),
-  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
-  but the whole statistical distribution for it can be simulated as well.
-
-\subsection{Scalar Observables and Statistical Models for POLSAR Data}
-
-Of course, discrimination measures are not the only way to carry out classification tasks in POLSAR.
-Another common approach is to carry out classification using POLSAR observables identified by different target decomposition theorems.
-In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes is evaluated.
-While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
-Furthermore, at its conclusion, the paper indicated that ``it is impossible to indentify the best one''
-  as these ``representations ... do not show a precise trend''.
-%Instead an MLP classification approach were employed. 
-To be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
-  and thus they are not to be used individually for the purpose of single-handedly representing POLSAR data.
-
-Given the joint distribution for POLSAR is known to be the multi-variate Complex Wishart distribution,
-  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
-However, such derivations are no trivial tasks,
-  as the data is much more complex and the field is much less matured than the traditional SAR statistical modelling.
-Thus the strategy of the pioneering work is to tackle simpler versions of polarimetry.
-
-POLSAR data is commonly represented by its covariance matrix.
-For full-pol the covariance matrix has the form of
-\begin{equation*}
-C_3 = 
-\begin{bmatrix}
-S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
-\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
-S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
-\end{bmatrix}
-\end{equation*}
-For part-pol, it reduces to either:
-\begin{equation*}
-  C_{2,h} =
-  \begin{bmatrix}
-    S_{hh}^2 & S_{hh}S_{hv}^* \\
-    S_{hh}^*S_{hv} & S_{hv}^2
-  \end{bmatrix};
-  C_{2,v} =
-  \begin{bmatrix}
-    S_{hv}^2 & S_{hv}S_{vv}^* \\
-    S_{hv}^*S_{vv} & S_{vv}^2
-  \end{bmatrix}
-\end{equation*}
-Obviously, the statistical behavior of $C_3$ can be understood by understanding the behavior of $C_{2h},C_{2v}$ and
-\begin{equation*}
-  C_{2,c} = 
-\begin{bmatrix}
-    S_{hh}^2 & S_{hh}S_{vv}^* \\
-    S_{hh}^*S_{vv} & S_{vv}^2
-\end{bmatrix}
-\end{equation*}
-
-While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
-  $C_{2c}$ is a totally made-up mathematical term from the full-pol covariance matrix.
-In fact, in the field of Polarimetric SAR, $C_{2v}, C_{2h}$ is called cross-pol and $C_{2c}$ is called co-pol covariance matrices.
-Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
-\begin{equation*}
-  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
-\end{equation*}
-with $\phi=arg(\rho)$ is the phase difference angle.
-In $C_{2v}, C_{2h}$ of optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
-  and $\phi_v,\phi_h$ are very random, due to little correlation between orthogonal polarization in monochromatic EM waves.
-%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
-Their equivalent lie in the ``natural surface'' case of POLSAR,
-  where  it is common to consider: $|\rho_v|=|\rho_h|=0$.
-This is, however, not true in the general case of POLSAR.  
-Specifically for $C_{2c}$, since there are correlation between the two co-pol channels,
-  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.
-
-In the field of optical physics,
-  under the assumption of no correlation between cross-polarized channels,
-  \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} derived the statistical models for $C_{2h},C_{2v}$.
-The observables that have been studied are:
-\begin{enumerate}
-\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
-  \begin{enumerate}
-  \item the total power $S_0=C_{11}^2 + C_{22}^2$,
-  \item the ratio of minor to major axis of the polarization ellipse  $\epsilon=\lambda_2/\lambda_1$,
-  \item and $\psi$ the angle that the ellipse major axis makes with horizontal axis,
-  \end{enumerate}
-\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
-  \begin{enumerate}
-  \item $S_0 = C_{11}^2 + C_{22}^2$
-  \item $S_1 = C_{11}^2 - C_{22}^2$
-  \item $S_2 = \Re (C_{12})$
-  \item $S_3 = \Im (C_{12})$
-  \end{enumerate}
-\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
-\end{enumerate}
-In the field of POLSAR, under the assumption of significant correlation between polarized channels,
-  \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} derived the statistical models for note only $C_{2h},C_{2v}$ but also $C_{2c}$.
-Specifically the following observables were studied:  
-  \begin{enumerate}
-  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
-  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
-  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
-  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
-  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
-  \end{enumerate}
-
-Furthermore, other studies has offered
-  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
-  the statistical model for
-  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
-While these models undoubtedly help in understanding the SAR data,
-  individually none of them statisfies the dual criteria of
-  1) resulting in statistically consistent discrimination measures and
-  2) being an representative observable for the complex POLSAR data.
-  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
-
-\section{The Scalar Statistical Models for POLSAR}  
-\label{sec:theoretical_model}
-
-In this section, several scalar statistical models for POLSAR are presented.
-After the first sub-section briefly reviews related work in published literature,
-  sub-section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
-The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
-And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
-Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
-
-\subsection{The Basics of POLSAR Statistical Analysis}
 
@@
   where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
-Assuming %all the elements in $s$ are independent and
-  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
+Assuming all the elements in $s$ are independent
+  and $s$ is jointly circular complex Gaussian with the given covariance matrix $\Sigma$,
   then the probably density function (PDF) of $s$ can be written as:
@@
 \end{equation}
-where $||$ denotes the matrix determinant.
+where $|M|$ denotes the determinant of the matrix $M$.
 
@@
   %applicable for POLSAR data.
-Goodman \cite{Goodman_1963_AMS_178} proved
-that the ratio between the observable and expected values of the sample covariance matrix's determinants
-  behave like a product of $d$ chi-squared random variables with different degrees of freedom 
+Goodman \cite{Goodman_1963_AMS_178}, %Goodman
+proven that the ratio between the observable and expected values of the sample covariance matrix determinants behave like a product of $d$ chi-squared random variables with different degrees of freedom,
 \begin{equation}
@@
 
-Its log-transformed variable consequently 
-  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
+Its log-transformed variable consequently behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom,  
 \begin{equation}
@@
 
-\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
+In this paper, the above results are exploited in the context of POLSAR data processing.
+In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
+The paper is structured as follows:
+  after the preceding introduction to the basics of POLSAR statistical analysis,
+  the second section presents evidence for two related points:
+(i) POLSAR data is multiplicative and heteroskedastic in its original domain.
+(ii) log-transformation converts it into an additive and homoskedastic model.
+Consequently a few consistent measures of distance are derived and presented in Section \ref{sec:distance_measure}.
+After the model is validated against both partial and full polarimetric SAR data in Section \ref{sec:polsar_models_validation},
+  Section \ref{sec:sar_special_case_of_polsar} discusses
+    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
+Besides being theoretically comprehensive, 
+  the model is also shown, in Section \ref{sec:improve_the_match_bw_theory_practice}, to be robust in handling a few practical imperfections that violate conventional assumptions. 
+To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
+  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
+Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
+  before the paper is concluded in Section \ref{sec:conclusion}.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in section \ref{sec:improve_the_match_bw_theory_practice}, to be robust in handling a few practical imperfections that violate conventional assumptions. 
+%As an example application of the consistent and homoskedastic dis-similarity measures, 
+%  section \ref{sec:evaluating_polsar_filters} explores how they can be used in evaluating POLSAR speckle filters.   
+%Finally, section \ref{sec:discussion_conclusion} critically reviews related works in literature 
+%  before providing some conclusional discussion.
+
+\section{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
@@
   where sample variance is fixed and thus independent of the underlying signal,
-  is demonstrated.
-To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, Appendix \ref{chap:appendix_a} should be referred to.
+  is also demonstrated.
+To keep the section flowing, the mathematical derivation is only presented here in major sketches with more detailed derivation confined to Appendix \ref{chap:appendix_a}.
 
@@
 
-In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
+Within a given homogeneous POLSAR area, parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
 Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that: 
@@
 
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follows a known PDF:
+Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follow a known PDF:
 \begin{equation}
@@
 As the PDFs become available, the characteristic functions (CF) of both the chi-squared and log-chi-squared random variables
-  can be written as:
+  can be found as:
   \begin{eqnarray}
@@
   \end{eqnarray}
-Subsequently their means and variances can be computed from the given characteristic functions.
-They are:
+Subsequently their means and variances can be computed from the given characteristic functions. They are namely:
   \begin{eqnarray}
@@
 
-Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
+Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we find:
 %\begin{eqnarray}
@@
   the underlying $\Sigma_v$ is expected to differ from one region to the next.
-Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
+Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
 In such context, Eqn.
@@
 
-\subsection{Consistent Measures of Distance for POLSAR}
+\section{Consistent Measures of Distance for POLSAR}
 \label{sec:distance_measure}
 
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2010_ACRS} \cite{Le_2013_TGRS_SAR_MSE},
+Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
   this section introduces the consistent sense of distance from a couple of different perspectives.
@@
 
-Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
+Since each elementary %[IVM took out this word]simulation 
+component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
   it is natural that these variables also follow fixed distributions.
 Moreover, they are independent of $\Sigma_v$.
-%This result shows how
-In short, these random variables are shown to follow consistent and fixed distributions,
+This result shows how
+  these random variables follows consistent and fixed distributions,
   regardless of the underlying signal $\Sigma_v$.
 
-\section{SAR as the Special Case of Polarimetric SAR}
+\section{Validating the models against real-life data}
+\label{sec:polsar_models_validation}
+
+This section describes an experiment to validate the models presented earlier against real-life captured data,
+  which can be performed in a rather straightforward manner as follows.
+The stochastic models derived in the previous sections can be graphically visualized as histogram plots of the simulated data.
+%This section describes an experiment to validate the models above against real-life captured data.
+%The validation procedure is quite straightforward.
+%Given that the stochastic models have been derived in the previous sections, 
+%  they can be graphically visualized by the histogram plots of the simulated data.
+At the same time, the form of real-life practical data is also observable via the histogram plots of data samples extracted from a known homogeneous area.
+If, for the same parameters, 
+  the two plots match each other reasonably well, the theoretical models be can validated to match reality.
+
+For this purpose, a homogeneous area is chosen from the AIRSAR Flevoland POLSAR data [reference?] as experimental data samples, and theoretical models are then created and matched against this data.
+%As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+%Then theoretical models are employed in an attempt to explain the data.
+The validating models include:
+  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, log-distance, dispersion and the contrast measures of distance.
+
+These models are closely related as follows.
+For  the same parameter set, the determinant and determinant ratio are simply scaled versions of each other.
+Meanwhile, the log-determinant, log-distance and dispersion are also just shifted versions of each other.
+Hence one could expect that 
+  once a model is validated, the other models in the set will follow suit, 
+  assuming that all the parameters of the image are known.% exactly.
+Nevertheless, all the models will be separately evaluated in this section.
+%The models are closely related.
+%Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
+%Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
+%Thus ideally speaking
+%  if one model is validated all the other models will also be,
+%  assuming that all the parameters of the image are known exactly.
+%Still in this section, all the models will be made subject to investigation.
+
+Among the models, the least-assumed stochastic processes for dispersion and contrast measures of distance will be validated first.
+For each pixel in the region under test, the determinant of the covariance matrix is computed and the log-transformation is applied.
+Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
+
+Similarly, theoretical simulations according to Eqns.
+\ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
+$L=4$ for this study, while the dimensional number is set to either 3 or 2 depending on whether a full or partial polarimetric SAR dataset is being investigated.
+The plots are presented in Fig. 
+\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} showing an evident visual match between the model and real data, thus effectively validating the theoretical models for dispersion and contrast measures of distance.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) dispersion]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
+		 \label{dispersion_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) contrast]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
+		 \label{contrast_2x2}
+	} \\
+	\subfloat[full-pol (3x3) dispersion]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
+		 \label{dispersion_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) contrast]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
+		 \label{contrast_3x3}
+	}
+\end{tabular}
+\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
+\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\end{figure}
+
+Apart from dispersion and contrast,
+the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
+The traditional way to estimate this quantity over an homogeneous area is to simply set the true signal equal to the average of the POLSAR covariance matrix in its original domain, i.e.
+$\Sigma_v = avg(C_v$).
+An alternative approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e.
+$avg[ln|C_v|]$) using Eqn.
+\ref{eqn:avg_log_det}.
+For completeness, both approaches will be presented in this section.
+As the log-determinant average has already been computed earlier, 
+  the second approach will be applied first for the validation of determinant-ratio and log-distance.
+%Both approaches will be explored in this section.
+%However, given that the log-determinant average has already been computed earlier, 
+%  the second approach is used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
+In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} and
+%Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
+%In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution}
+and \ref{eqn:log_determinant_distance_distribution},
+  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
+  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
+%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
+A reasonable match is again observed which tends to validate the models for log-distance and determinant ratio.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) log distance]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
+		 \label{log_distance_2x2}
+	} \\
+	\subfloat[full-pol 3x3 determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol 3x3 log distance]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
+		 \label{log_distance_3x3}
+	}
+\end{tabular}
+\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
+\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\end{figure}
+
+Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+%And if the  true signals are computed in the same manner as described before then in fact similar match can be easily observed.
+
+However, a more subtle observation phenomena occurs during the validation process for the determinant and its log-transformed model,
+%However, a more interesting  phenomena is to be described.
+%It happens in the validation process for determinant and its log-transformed model,
+  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
+%For such simulation, an estimation of  the true signal is needed.
+The phenomena happens when the true signal is estimated by the first approach i.e.
+equal to the average of the sample covariance matrix in its original domain (which evidently results in a different estimation for the true signal when compared with the method applied earlier).
+%Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
+
+Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small translation and scaling discrepancies -- which are
+ easier to observe in the log-determinant plots. Despite this, the curve shapes are quite similar.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[verify polsar 2x2: determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
+		 \label{determinant_2x2}
+	} 
+	\hfill	
+	\subfloat[verify polsar 2x2: log-determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
+		 \label{log_det_2x2}
+	} \\ 
+	\subfloat[verify polsar 3x3: determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
+		 \label{determinant_3x3}
+	} 
+	\hfill	
+	\subfloat[verify polsar 3x3: log-determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
+		 \label{log_det_3x3}
+	} 
+\end{tabular}
+\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
+\label{fig:verify_polsar_2x2_simulation_det}
+\end{figure}
+
+In summary, the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
+The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
+  if the underlying parameters can be estimated reasonably well for the given image.   
+However as described above, a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
+  depending on which estimation method is used.
+The discrepancy suggests that at least one of the commonly used methods is slightly incorrect.%IVM - I changed this sentence... please check it!
+
+%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
+%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+%  where not only the look number is shown to be misused
+%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
+As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+  the reason is due to the inappropriate look number being used.
+Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
+For now, let us simply observe that
+  using appropriate estimation of the parameters, 
+  the proposed models match reasonably well with the practical data.
+
+\section{SAR as a Special Case of Polarimetric SAR}
 \label{sec:sar_special_case_of_polsar}
 
-The previous section has introduced the theoretical model for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+The previous section has validated the use of our models for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
 In this section, the model is shown to be also applicable for the 1-dimensional  $d=1$ case.
-Physically this means the multi-dimensional POLSAR dataset is collapsed into one-dimensional conventional SAR data.
+Physically, this means the multi-dimensional POLSAR dataset is collapsed into one-dimensional classical (conventional?) SAR data.
 Mathematically, the sample covariance matrix is reduced to the sample variance
@@
 %Mathmatically, the sample covariance matrix is reduced to the sample variance
-  and the determinant equates the scalar value.
-On the other hand, it is well known that for SAR data, variance equals intensity.
+  and the determinant equates to the scalar value.
+On the other hand, it is well known that for SAR data, variance corresponds to intensity.
 Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
@@
   either as a cross-validation evidence for the proposed POLSAR models
-  or alternatively as having SAR as the special case of POLSAR. 
+  or alternatively as SAR being simply a special case of POLSAR. 
 %  with well known results for SAR intensity is presented.
@@
 
+%******************************************************************
+%%%IVM:  Hai, you haven't introduced \mathbb{A}, \mathbb{V}, \mathbb{E} in the text, or derived them (although it's pretty simple).
+%IVM: maybe just refer the reader back to eqn. 18-21 to get this?
+%IVM: Anyway, it does need to be mentioned here and this will also help you
+%IVM: to break up the 'pile' of equations here (which is a good thing)
+%
+%
+%******************************************************************
+
 Upon setting $d=1$ into the above equations,
   Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the the following results obtained from the our previous works on single-look SAR \cite{Le_2010_ACRS} \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+First is the following results obtained from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
 %Upon setting $d=1$ into the above models,
@@
 \end{align*}
-The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+The second is the following well-known result for multi-look SAR, i.e. $d=1,L>1$:
 %but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
@@
     either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results
-  are also derived as:
+    or as simple cases of the POLSAR results, derived as:
 %  Furthermore, the following results for multi-look SAR data,
@@
 
-This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
-In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
- The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+These newly derived models for multi-look SAR data can also be validated against real-life data.
+Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} plots the results of an experiment carried out for the stated purpose.
+In this experiment, the intensity of single-channel SAR data (HH) for a known homogeneous area is extracted from the AIRSAR Flevoland dataset.
+The histograms for the log-distance and contrast are then plotted with the theoretical PDF given above. In this plot, we set $EN=4$, leading to a reasonably good visual match is apparent.
 %Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
@@
 
-%ifdef FINAL
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR dispersion]{
+	\subfloat[verify multi-look SAR log-distance]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[multi-look SAR contrast]{
+	\subfloat[verify multi-look SAR contrast]{
 		 \epsfxsize=1.5in
@@
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
+\caption{Multi-Look SAR dispersion and contrast: modelled response matches well with real-life captured data.}
 \label{fig:verify_multi_look_SAR_dispersion_contrast_models}
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[multi-look SAR log-distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
-	}
-\end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
-\end{figure}
-%endif
-
-\section{Validating the models against real-life data}
-\label{sec:polsar_models_validation}
-
-This section validates the theoretical models developed above against real-life practical data.
-The first sub-section provides a naive validation, where the nominal ENL is used for the model.
-While the match appears to be reasonably good, it can be further improved.
-After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
-  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
-With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
-
-\subsection{Using the nominal ENL to validate the theoretical models} 
-This sub-section describes an experiment to validate the models presented earlier against real-life captured data,
-  which can be performed in a rather straightforward manner as follows.
-The stochastic models derived in the previous sections can be graphically visualized as histogram plots of the simulated data.
-%This section describes an experiment to validate the models above against real-life captured data.
-%The validation procedure is quite straightforward.
-%Given that the stochastic models have been derived in the previous sections, 
-%  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via the histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-For this purpose, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models ar used  to explain the data.
-%As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-%Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, log-distance, dispersion and the contrast measures of distance.
-
-These models are closely related as follows.
-For  the same parameter set, the determinant and determinant ratio are simply scaled versions of each other.
-Meanwhile, the log-determinant, log-distance and dispersion are also just shifted versions of each other.
-Hence one could expect that 
-  once a model is validated, the other models in the set will follow suit, 
-  assuming that all the parameters of the image are known.% exactly.
-Nevertheless, all the models will be separately evaluated in this section.
-%The models are closely related.
-%Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-%Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-%Thus ideally speaking
-%  if one model is validated all the other models will also be,
-%  assuming that all the parameters of the image are known exactly.
-%Still in this section, all the models will be made subject to investigation.
-
-Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
-
-Similarly, theoretical simulations according to Eqns.
-\ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-$L=4$ for this study, while the dimensional number is set to either 3 or 2 depending on whether a full or partial polarimetric SAR dataset is being investigated.
-The plots are presented in Fig. 
-\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} showing an evident visual match between the model and real data, thus effectively validating the theoretical models for dispersion and contrast measures of distance.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
-	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
-	}
-\end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
-	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
-	}
-\end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
-\end{figure}
-%endif
-
-Apart from dispersion and contrast,
-the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be presented in this section.
-As the log-determinant average has already been computed earlier, 
-  the second approach is hence used first for the validation of determinant-ratio and log-distance.
-%Both approaches will be explored in this section.
-%However, given that the log-determinant average has already been computed earlier, 
-%  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
-In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} and
-%Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-%In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution}
-and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
-A reasonable match is again observed which validates the models for log-distance and determinant ratio.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
-	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
-	}
-\end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
-	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
-	}
-\end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
-\end{figure}
-%endif
-
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-%And if the  true signals are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more subtle observation phenomena occurs during the validation process for the determinant and its log-transformed model,
-%However, a more interesting  phenomena is to be described.
-%It happens in the validation process for determinant and its log-transformed model,
-  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The phenomena happens when the true signal is estimated by the first approach i.e.
-equal to the average of the sample covariance matrix in its original domain (which evidently results in a different estimation for the true signal when compared with the method applied earlier).
-%Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small translation and scaling discrepancies -- which are
- easier to observe in the log-determinant plots. Despite this, the curve shapes are quite similar.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
-In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
-
-%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  where not only the look number is shown to be misused
-%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  the reason is due to the inappropriate look number being used.
-Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
-For now, let us simply observe that
-  using appropriate estimation of the parameters, 
-  the proposed models match reasonably well with the practical data.
-
-%\section{Handling certain discrepancy between the theoretical model and pratical data}
-\subsection{The difference between the theoretical models and the practical data}  
+
+\section{Handling certain discrepancy between the theoretical model and pratical data}
 \label{sec:improve_the_match_bw_theory_practice}
@@
 Even though the assumptions made in developing this theory have intentionally been kept minimal, 
-%Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
-  like all other similar models, the proposed model in this paper is built upon certain presumptions.
-Practical conditions however may not always satisfy these prerequisites.
-In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.
-And it is shown that: the theoretical model proposed can apply to the practical data, even when this ``imperfection'' is taken into account.
-%In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
-%And it is shown that: the theoretical model proposed can apply to the practical data, even when these ``imperfections''  are taken into account.
+  as with other similar models, the proposed model in this paper is built upon certain presumptions and prerequisites.
+Practical conditions, however, may not always satisfy those prerequisites.
+In this section, certain gaps between the conditions found in real-life data and the theoretical assumptions are discussed.
+It is also shown that the theoretical model can apply to the practical data, even in the face of certain ``imperfections''.
 %And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
 
-%There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
-%The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
-%However high correlation is routinely observed in practice between the POLSAR data components,
-%%Practically however high correlation is routinely observable between the POLSAR data components,
-%  specifically between $S_{hh}$ and $S_{vv}$.
-%This phenomena also presents in our AIRSAR dataset, where {\scriptsize $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$}.
-%Despite the mismatch,
-%  astute reader would have noticed that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
+The two main imperfections found in practical POLSAR data are probably those related to the following assumptions:
+\begin{enumerate}
+\item Each component in the POLSAR target vector $s$ is mutually independent.
+\item The samples are statistically independent of each other.
+\end{enumerate}
+
+Regarding the first assumption of independent components, it is noted in practice that high correlation is routinely observed at times between the POLSAR data components,
+%Practically however high correlation is routinely observable between the POLSAR data components,
+  specifically between $S_{hh}$ and $S_{vv}$.
+This phenomena is also present in the AIRSAR dataset, where {\scriptsize $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$}.
+Despite the mismatch,
+the astute reader would have noticed that the proposed model is apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
 \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
+This observation suggests that the proposed model is also applicable on correlated POLSAR components, although a full explanation for this is outside the scope of this paper. 
 %This suggests that the proposed model is also applicable on correlated POLSAR components,
-%  although a full explanation for thisis outside the scope of this paper. 
-%%This suggests that the proposed model is also applicable on correlated POLSAR components,
-%%  eventhough a full explaination for this, however, is outside the scope of this paper.
-
-The assumption of statistical independence between samples (which applies to both SAR and POLSAR data) is reasonable given that 
+%  eventhough a full explaination for this, however, is outside the scope of this paper.
+
+The second assumption of statistical independence between samples (which applies to both SAR and POLSAR data) is reasonable given that 
   the transmission and receipt of analogue signals is done independently for each radar pulse, i.e. for each resolution cell.
 Thus, theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
+
 However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
@@
 
-Stated differently, in practice, each physical radar cell may be spread over more than a single pixel,
+Stated differently, each physical radar cell in practice may be spread over more than a single pixel, 
 resulting in potentially high correlation between neighbouring pixels.
-This high sampling rate also results in 
-  a significantly higher correlation between pairs of pixels that may be related within a single physical cell resolution. 
-  Then the correlation found between pairs of pixels that are further away and hence having less physical relation to each other will increase.
-It also results in reduced effective number of look, 
-  such as for a window of 3$\times$3 pixels, it actually contains less than 9 physical analogue cells. 
+This also results in a in reduction the ENL
+  such as when a window of 3$\times$3 pixels, actually contains less than 9 physical analogue cells. 
 %It also results in reduced effective number of look, 
@@
 The oversampling practice is also documented by the producers of SAR processors.
-For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}
+For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}
+while for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode are advertised as $(4.cdot \7 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
 
 %The proposed model can handle this imperfection that is available in pratical data.
-The proposed model can handle this imperfection that is found in practical data.
-The trick is that instead of using the nominal Number of Looks given by the SAR processor,
-  an ENL estimation procedure is first undertaken, and then the obtained ENL used subsequently.
+In fact, the proposed model can handle this imperfection by estimating and then adopting an ENL value rather than assuming the stated number of looks is correct.
  %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
-The first part of this section details a simple ENL estimation technique for POLSAR data.
-While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
-It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved using ENL estimation.
+To investigate further, the following subsections first present a simple ENL estimation technique for POLSAR data, then demonstrate how the practical imperfection manifests itself -- and how it can be handled with a RADARSAT2 dataset example.
+We will also illustrate how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved by the use of ENL estimation.
 
@@
 
-%This sub-section describes a few techniques that can be used to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
+%IVM: This sub-section describes a few techniques that can be used to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
 %This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
@@
 In fact, this approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
+  where an equation of the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate ENL.
 Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
@@
   we propose an approach that makes used of variance statistics in the homoskedastic log-domain to find ENL.
-%Since the determinant of the POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
-%  this approach is a generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} for POLSAR data.
+Since the determinant of the POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
+  this approach is a generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} for POLSAR data.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
 
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$,
-  which would also require some iterative computations.
+Theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could iteratively solve the above equation for the unknown $L$.
 Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph or by using the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
-%And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
+  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph or by using an approximation:
+%
+%
+% IVM:  where did you get the equation from? No reference, no derivation!!
+%
+%
   \begin{equation}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-%endif
 
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then explain the data reasonably well.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-%endif
 
@@
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
+	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
 		 \label{sar}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-%endif
-
-\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+
+\section{Evaluating POLSAR Speckle Filters using consistent measures of distance}
 %\section{Visually Evaluating POLSAR Speckle Filters over Heterogeneous Areas}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinants histograms of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
-		 \label{log_determinant}
-	} 
-	\hfill	
-	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
-		 \label{contrast}
-	}   
-\end{tabular}
-\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
-Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
-\label{fig:boxcar_3x3_preserves_consistency}
-\end{figure}
-%endif
 
@@
   the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
-This optimal value is computed   
+This optimal value is found   
 by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
 
-%ifdef FINAL
 \begin{figure}[h]
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-%endif
 %Note if the picture does not look convincing enough
@@
 
-Further discussion on the specific topic of evaluating SAR speckle filters is given in our work that focused specifically on SAR \cite{Le_2013_TGRS_SAR_MSE}.
+Further discussion on the specific topic of evaluating SAR speckle filters is given in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
 However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters (i.e. extending the previous SAR approach).
@@
 
-%\subsection{The Likelyhood Test Statistics for POLSAR}
-
+\subsection{Related Work in Literature}
+%IVM: [cut] This sub-section reviews some relevant and published works on proposing different measures of distance for POLSAR data. 
+A few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}, and these
+will be discussed in the light of the approach proposed in this paper.
+%specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+
+The commonly used measure of distance for matrices are either the Euclidean or the Manhattan distances, as follows:
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of matrix A,
+ $|.|$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR covariance matrix, they are not widely used, given the multiplicative nature of the data.
+%In the context of polsar covariance matrix, however, they are not widely used 
+%  probably because of the multiplicative nature of the data.
+
+In the field of POLSAR, the Wishart Distance is probably the most widely used as part of the well-known Wishart Classifier \cite{Lee_1999_TGRS}.
+The distance is defined as \cite{Lee_1994_IJRS_2299}:
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dissimilarity measures including
+the asymmetric and symmetric refined Wishart distances\cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance\cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance\cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance\cite{Cao_2007_TGRS_3454},
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+
+In comparison to these formula, the distance measure for two covariance matrices proposed in this paper can be summarised as:
+\begin{equation}
+  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
+\end{equation}
+At first glance, while the proposed formula may be a lot simpler, it is still very similar to others in making use of the log-determinant.
+
+Closer investigation of the dissimilarity measures mentioned reveals that most of them are related to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered as a special case of the Wishart Statistical Test distance, where the two data sets have the same number of looks $L_x=L_y$.
+It is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper have fixed statistical behaviour just by comparing the symmetric and asymmetric versions of the refined Wishart distance, assuming that they are shown to follow fixed distributions.
+
+The close relation among these is further supported by the fact that
+all of the mentioned works referenced the statistical model developed in \cite{Conradsen_2003_TGRS_4} as their foundation.
+Interestingly, the change detection model also make use of determinant ratio and log determinant in its derivation.  
+The next sub-section will illustrate how the log-determinant model presented in this paper can offer an alternative and simple derivation for the change-detection statistics.
+
+\subsection{The Likelihood Test Statistics for POLSAR}
+
+To determine if the two scaled multi-look POLSAR covariance matrices $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrices is considered \cite{Conradsen_2003_TGRS_4}:
+\begin{equation}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation}
+
+Taking the log-transformation of the above statistics, and noting that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it can be rewritten as:
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
+\end{eqnarray}
+
+To detect changes, a test statistics is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, originally in the proposed work, only an asymptotic distribution is derived.
+In this sub-section, a statistical model is developed for this measure of distance.
+
+Since both $Z_x$ and $Z_y$ follow complex Wishart distribution with $L_x$ and $L_y$ degrees of freedom,
+  $Z_x+Z_y$ also follows the complex Wishart distribution with $L_x + L_y$ degrees of freedom.
+In view of the models denoted in Eqn. \ref{eqn:log_determinant_distribution},
+  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+  but the whole statistical distribution for it can be modelled as well:
 %\begin{eqnarray}
@@
 %\end{eqnarray}
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+In the common case of $L_x = L_y$, the test statistics become
+$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
+This and the Barlett distance introduced earlier are closely related, in fact they are simply shifted versions of each other.
+Under exactly the same assumptions, 
+  the contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should provide another consistent and equivalent approach,
+  with potentially a simpler conceptual model and reduced computational requirements. 
+%a slightly simpler statistics.
 
@@
 
-The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
-In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
-  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
-can be simulated as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+Several practical applications may be developed using the model presented here and its derivatives.
+First, the model allow for the estimation and simulation of a non-natural equivalent number of looks (ENL).
+This is especially useful when real-life data is available for which the effective number of looks may not equal the nominal stated number-of-look, after multi-look-processing.
+In such cases, better-matching models can be derived
+  by estimating the effective ENL first (although this usually results in a non-integer result).
 
@@
 
-\subsection{Conclusion}
+\section{Conclusion}
 \label{sec:conclusion}
 
-In conclusion, a couple of statistical models for the determinant of the POLSAR covariance matrix is proposed and validated in this paper.
-Compared to other statistical models for POLSAR, the proposed models are scalar and representative for the multi-dimensional POLSAR data.
-These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
-Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
-As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
-
-%An additive and homoskedastic model, 
-%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
-%  is proposed in this paper.
-%The theoretical model is shown to be comprehensive:
-%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
-%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
-%
-%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
-%  is gracefully transformed into traditional SAR intensity.
-%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
-%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
-%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
+An additive and homoskedastic model, 
+  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+  is proposed in this paper.
+The theoretical model is shown to be comprehensive:
+not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+
+The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+  is gracefully transformed into traditional SAR intensity.
+Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
 

### 2013-05-17 paper_dev/article_201303_Mar20_Ian.tex
2013May_0517

--- 2013-04-22 paper_dev/article_pp.tex
@@
 \title{
-  %Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
-  Scalar and Representative Models for Polarimetric SAR Data
+  Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
+%Scalar Homoskedastic Models for POLSAR data
 }
@@
 \markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+{ Le \MakeLowercase{\textit{et al.}}:  Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data}
 
@@
 \begin{abstract}
-  While statistical models are important in understanding the stochastic nature of Polarimetric SAR (POLSAR),
-  scalar discrimination measures are routinely used in processing this multi-dimensional data.
-  Ideally speaking, the latter should be drived from the former.
-  As far as we know, however, it has not exactly been so for the case of POLSAR.
-  In this paper, a couple of statistical models for the determinant of the POLSAR covariance matrix and its log-transformed derivations are proposed.
-  These scalar models for the determinant of the POLSAR covariance matrix are shown to be respresentative
-    since this observable is neatly transformed into the traditional SAR intensity
-    when the generic multi-dimensional polarimetry is collapsed into the case of one-dimensional SAR. %case of traditional SAR data.
-  Similar to SAR, the generic model for POLSAR is also shown to be multiplicative and heteroskedastic in the original domain 
-    and the logarithmic transformation converts this into a more familiar additve and homoskedastic model.
-  Moreover, the scalar property of these statistical models lead to the derivation of several statistical discrimination measures. %homoskedastic measures of distance.
-  All of these statistical models are validated on real-life captured data
-    and they are shown to be applicable even when the theoretical ``independent samples'' assumption is violated in practice.
-  %The paper also illustrates a couple of benefits of these models, specifically for using the homoskedastic discrimination measures.
-  %A couple of benefits for using these homoskedastic dis-similarity measures are then illustrated in this paper.
-  %These homoskedastic measures of distance
-  The combination of scalar, additive and homoskedastic properties of the derived statistical models bring about a couple of benefits, which are also described in this paper.
-  First, compared to the original multiplicative domain, %dis-criminative measure of ratio,
-    the additive log-transformed fit more naturally with the linear nature of digital imagery.
-  Second, since the Gauss-Markov theorem is again applicable in the homoskedastic log-transformed domain,
-    the use of Mean Squared Error (MSE) as an reliable objective function for POLSAR speckle filters is briefly explored.
-%This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
-%The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
-%The dissimilarity measurements, 
-%computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
-%It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+This paper presents a novel homoskedastic and additive model for polarimetric SAR (POLSAR) data. 
+The statistical properties of this new model  enable a number of different consistent measures of distance for the POLSAR covariance matrix. 
+The dissimilarity measurements, 
+computed from the determinant of the POLSAR covariance matrix, are initially developed for both partial (2$\times$2) and full (3$\times$3 monostatic case) polarimetric SAR data.
+It is shown that when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
+  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
+This puts the SAR intensity statistics to lie within the natural coverage of this new theoretical model for POLSAR.
+%Thus the SAR intensity statistics can now be considered as a special case of  this new theoretical model for POLSAR.
+Not only comprehensive theoretically, the statistical model is also robust in handling practical data. 
+It can be validated and match reasonably well  with practical data.
+% even  when  the supposedly independent polarimetric components are actually highly correlated (e.g. between $S_{hh}$ and $S_{vv}$).  
+Moreover, the match can be further improved 
+  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
+  instead of blind acceptance of the number of looks figure reported by the SAR processor.
+The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+%In this paper, a homoskedastic and additive model for polarimetric SAR (POLSAR) data is introduced. 
+%The statistical properties of this model subsequently lead to a few different consistent measures of distance for the POLSAR covariance matrix.
+%The dis-similarity measurements are initially developed for both partial (2x2) and full (3x3 monostatic case) polarimetric SAR data.
+%They are computed from the determinant of the POLSAR covariance matrix.
+%Interestingly, when the multi-polarization POLSAR is collapsed into the single-polarization SAR,
 %  this covariance matrix determinant is neatly transformed into the traditional SAR intensity.
-%This puts the SAR intensity statistics to lie within the natural coverage of this new theoretical model for POLSAR.
-%Not only comprehensive theoretically, the statistical model is also robust in handling practical data. 
-%It can be validated and match reasonably well  with practical data.
-%Moreover, the match can be further improved 
-%  if the model validation process includes estimation of the dataset's Effective Number of Looks (ENL) 
-%  instead of blind acceptance of the number of looks figure reported by the SAR processor.
-%The application of these dissimilarity measures is demonstrated in this paper for evaluating the effectiveness of POLSAR speckle filters.  
+%Thus the SAR intensity statistics can now be considered as a special case of the theoretical model for POLSAR.
+%While powerful theoretically, the statistical model is also robust in handling practical data.
+%It can be validated and match reasonably well with practical data,
+% even  when  the supposedly independent polarimetric components are actually highly correlated (e.g. between $S_{hh}$ and $S_{vv}$).
+%Moreover, the match can be further improved, as better match is shown achievable, 
+%  if the model validation process include an estimation of the dataset's Effective Number of Looks (ENL) 
+%  instead of blind employment of the look number given by the SAR processor.
+%Towards the end, the practical application of these dissimilarity measures is briefly demonstrated in the context of evaluating POLSAR speckle filters.  
 \end{abstract}
@@
 
-In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
-As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
-POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
-Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
-
-With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
-The complex data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
-Under this condition, it is very important to understand the statistical models for (POL)SAR data.
-
-While the statistical models for homogeneous areas of one-dimensional SAR data have been developed,
-%  in extending the model toward heterogeneous images, the impact of heteroskedasticity has virtually been ignored.
-%Specifically the concept of distance as a measure of dis-similarity is seriously flawed, as it is widely known that ratio offers a better discrimination measure TODOCITE.
-%This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
-%From this log-transformed model, a few consistent measures of distance is proposed. 
-%in a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtraction, and thus distance.
-  in extending our understanding towards multi-dimensional POLSAR data, an important issue needs to be addressed.
-The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
-While different statistical models have been developed for different POLSAR observables,
-  for a statistical model to be useful, scalar discrimination measures need to be derived from it.
-Thus practical application for POLSAR data processing requires the dis-similarity measure to be scalar, consistent and preferably homoskedastic on one hand.
-On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
-
-In this paper, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
-The representative power of this observable is demonstrated when the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario.
-Under this transformation, the determinant of the POLSAR covariance matrix is converted into the standard SAR intensity.
-Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant are then derived.
-And since POLSAR can be viewed as a multi-dimensional extension of SAR, the paper describes how the standard statistical models for SAR can be put within the natural coverage of this generic models for POLSAR.
-
-%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
-%Firstly, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear scale nature of digital imagery.
-%Secondly, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss Markov theorem is again applicable, the universal MSE deserves to be reviewed as a reliable objective function / criteria for (POL)SAR estimators.
-%This may open up a number of different research directions for future studies of (POL)SAR.
-%As example demonstrations of how these models and distance measures can be used, a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
-
-Specifically, the rest of this paper is structured as follows.
-After the related work in literature is critically reviewed in Section \ref{sec:lit_review},
-  Section \ref{sec:theoretical_model} presents the theoretical models for both partial and full polarimetric SAR and their derived discrimination measures.
-The representative power of the scalar models are illuminated in Section \ref{sec:sar_special_case_of_polsar},
-  which details how the proposed models for the multi-variate POLSAR also includes the well-known models for the traditional SAR as its special univariate case.
-%can be used to derive the well-known models for the univariate SAR data as its special case.
+In this paper, the POLSAR scattering vector is denoted as $s$.
+In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+  the vector is two-dimensional ($d=2$) and is normally written as: 
+\begin{equation}
+s_{part}=\begin{bmatrix}
+S_h\\ 
+S_v
+\end{bmatrix}
+\end{equation}
+In the case of full and monostatic POLSAR data,
+  the vector is three-dimensional ($d=3$) and is presented as:
+\begin{equation}
+s_{full}=\begin{bmatrix}
+S_{hh}\\
+\sqrt{2}S_{hv}\\
+S_{vv}
+\end{bmatrix}
+\end{equation}
+
+Let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
+  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
+Assuming %all the elements in $s$ are independent and
+  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
+  then the probably density function (PDF) of $s$ can be written as:
+\begin{equation}
+  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
+\end{equation}
+where $||$ denotes the matrix determinant.
+
+As the covariance matrix is only defined on multiple data points,
+  sample POLSAR covariance matrices are commonly presented in ``ensemble'' format.
+They are formed as the mean of Hermitian outer product of single-look scattering vectors,
+\begin{equation}
+  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
+\end{equation}
+where $s_i$ denotes the single-look scattering vector,
+  which equals $s_{part}$ in the case of partial POLSAR and
+  $s_{full}$ in the case of full polarimetry,
+and $L$ is the number of looks.
+
+Complex Wishart distribution statistics, however, are normally written for the scaled covariance matrix
+$Z=LC_v$, whose PDF is given as:
+\begin{equation}
+  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
+\end{equation}
+with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
+and $d$ is the dimensional number of the POLSAR covariance matrix.
+
+The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
+  %under the assumption of circular complex Gaussian distribution
+  %applicable for POLSAR data.
+Goodman \cite{Goodman_1963_AMS_178} proved
+that the ratio between the observable and expected values of the sample covariance matrix's determinants
+  behave like a product of $d$ chi-squared random variables with different degrees of freedom 
+\begin{equation}
+\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
+\label{eqn:prod_chi_squared_rv}  
+\end{equation}
+
+Its log-transformed variable consequently 
+  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
+\begin{equation}
+\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
+\label{eqn:sum_log_chi_squared_rv}
+\end{equation}
+with
+  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
+
+In this paper, the above results are exploited in the context of POLSAR data processing.
+In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
+The paper is structured as follows:
+  after the preceding introduction to the basics of POLSAR statistical analysis,
+  the second section briefly reviews related work in published literature.
+Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+After the model is presented for both partial and full polarimetric SAR data,
+  section \ref{sec:sar_special_case_of_polsar} discusses
+    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
 Besides being theoretically comprehensive, 
@@
   to be robust in handling practical data. % imperfection that violate conventional assumptions. 
-To demonstrate the application of these scalar and representative models, 
-  Section \ref{sec:evaluating_polsar_filters} explores how they can be used to evaluate POLSAR speckle filters.   
-In the end, Section \ref{sec:discussion_conclusion} provides the final conclusion of the paper.
-%critically reviews and discusses related literature  
-%  before the paper is concluded in Section \ref{sec:conclusion}.
-
-%In this paper, the above results are exploited in the context of POLSAR data processing.
-In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
-The paper is structured as follows:
-%  after the preceding introduction to the basics of POLSAR statistical analysis,
-%  the second section briefly reviews related work in published literature.
-%Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
-%The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
-%And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
-%Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
-%After the model is presented for both partial and full polarimetric SAR data,
-%  section \ref{sec:sar_special_case_of_polsar} discusses
-%    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
     %Besides being theoretically comprehensive, 
-%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
-%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
-%To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
-%  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
-%Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
-%  before the paper is concluded in Section \ref{sec:conclusion}.
+%  the model is also shown, in section \ref{sec:improve_the_match_bw_theory_practice}, to be robust in handling a few practical imperfections that violate conventional assumptions. 
+To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
+  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
+Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
+  before the paper is concluded in Section \ref{sec:conclusion}.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in section \ref{sec:improve_the_match_bw_theory_practice}, to be robust in handling a few practical imperfections that violate conventional assumptions. 
+%As an example application of the consistent and homoskedastic dis-similarity measures, 
+%  section \ref{sec:evaluating_polsar_filters} explores how they can be used in evaluating POLSAR speckle filters.   
+%Finally, section \ref{sec:discussion_conclusion} critically reviews related works in literature 
+%  before providing some conclusional discussion.
 
 \section{Related Work in Literature}
-\label{sec:lit_review}
-
-This section critically review the related work in published literature.
-Specifically, the first sub-section shows that while many discrimination measures have been proposed for POLSAR data,
-  almost all of them depends on the likelihood statistical test for complex Wishart distribution.
-Unfortunately, in the original proposed work \cite{Conradsen_2003_TGRS_4}, while an exact distribution is to be expected, only an asymptotic distribution was given.
-The second sub-section reviews various statistical models for different POLSAR observables.
-Its purpose is to show that none of these models, as far as we know, led to statistically consistent discrimination measures.
-
-\subsection{POLSAR Discrimination Measures}
-
-This sub-section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
+This section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
 In particular, a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
@@
 
-Closer investigation of these dis-similarity measures reveals that most of them are related to each other.
+Closer investigation of these dissimilarity measures reveals that most of them are related to each other.
 The Bhattacharyya distance is easily shown to be related to the Barlett distance.
@@
 
-\subsection{Scalar Observables and Statistical Models for POLSAR Data}
-
-Of course, discrimination measures are not the only way to carry out classification tasks in POLSAR.
-Another common approach is to carry out classification using POLSAR observables identified by different target decomposition theorems.
-In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes is evaluated.
-While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
-Furthermore, at its conclusion, the paper indicated that ``it is impossible to indentify the best one''
-  as these ``representations ... do not show a precise trend''.
-%Instead an MLP classification approach were employed. 
-To be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
-  and thus they are not to be used individually for the purpose of single-handedly representing POLSAR data.
-
-Given the joint distribution for POLSAR is known to be the multi-variate Complex Wishart distribution,
-  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
-However, such derivations are no trivial tasks,
-  as the data is much more complex and the field is much less matured than the traditional SAR statistical modelling.
-Thus the strategy of the pioneering work is to tackle simpler versions of polarimetry.
-
-POLSAR data is commonly represented by its covariance matrix.
-For full-pol the covariance matrix has the form of
-\begin{equation*}
-C_3 = 
-\begin{bmatrix}
-S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
-\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
-S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
-\end{bmatrix}
-\end{equation*}
-For part-pol, it reduces to either:
-\begin{equation*}
-  C_{2,h} =
-  \begin{bmatrix}
-    S_{hh}^2 & S_{hh}S_{hv}^* \\
-    S_{hh}^*S_{hv} & S_{hv}^2
-  \end{bmatrix};
-  C_{2,v} =
-  \begin{bmatrix}
-    S_{hv}^2 & S_{hv}S_{vv}^* \\
-    S_{hv}^*S_{vv} & S_{vv}^2
-  \end{bmatrix}
-\end{equation*}
-Obviously, the statistical behavior of $C_3$ can be understood by understanding the behavior of $C_{2h},C_{2v}$ and
-\begin{equation*}
-  C_{2,c} = 
-\begin{bmatrix}
-    S_{hh}^2 & S_{hh}S_{vv}^* \\
-    S_{hh}^*S_{vv} & S_{vv}^2
-\end{bmatrix}
-\end{equation*}
-
-While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
-  $C_{2c}$ is a totally made-up mathematical term from the full-pol covariance matrix.
-In fact, in the field of Polarimetric SAR, $C_{2v}, C_{2h}$ is called cross-pol and $C_{2c}$ is called co-pol covariance matrices.
-Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
-\begin{equation*}
-  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
-\end{equation*}
-with $\phi=arg(\rho)$ is the phase difference angle.
-In $C_{2v}, C_{2h}$ of optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
-  and $\phi_v,\phi_h$ are very random, due to little correlation between orthogonal polarization in monochromatic EM waves.
-%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
-Their equivalent lie in the ``natural surface'' case of POLSAR,
-  where  it is common to consider: $|\rho_v|=|\rho_h|=0$.
-This is, however, not true in the general case of POLSAR.  
-Specifically for $C_{2c}$, since there are correlation between the two co-pol channels,
-  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.
-
-In the field of optical physics,
-  under the assumption of no correlation between cross-polarized channels,
-  \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} derived the statistical models for $C_{2h},C_{2v}$.
-The observables that have been studied are:
-\begin{enumerate}
-\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
-  \begin{enumerate}
-  \item the total power $S_0=C_{11}^2 + C_{22}^2$,
-  \item the ratio of minor to major axis of the polarization ellipse  $\epsilon=\lambda_2/\lambda_1$,
-  \item and $\psi$ the angle that the ellipse major axis makes with horizontal axis,
-  \end{enumerate}
-\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
-  \begin{enumerate}
-  \item $S_0 = C_{11}^2 + C_{22}^2$
-  \item $S_1 = C_{11}^2 - C_{22}^2$
-  \item $S_2 = \Re (C_{12})$
-  \item $S_3 = \Im (C_{12})$
-  \end{enumerate}
-\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
-\end{enumerate}
-In the field of POLSAR, under the assumption of significant correlation between polarized channels,
-  \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} derived the statistical models for note only $C_{2h},C_{2v}$ but also $C_{2c}$.
-Specifically the following observables were studied:  
-  \begin{enumerate}
-  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
-  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
-  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
-  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
-  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
-  \end{enumerate}
-
-Furthermore, other studies has offered
-  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
-  the statistical model for
-  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
-While these models undoubtedly help in understanding the SAR data,
-  individually none of them statisfies the dual criteria of
-  1) resulting in statistically consistent discrimination measures and
-  2) being an representative observable for the complex POLSAR data.
-  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
-
-\section{The Scalar Statistical Models for POLSAR}  
-\label{sec:theoretical_model}
-
-In this section, several scalar statistical models for POLSAR are presented.
-After the first sub-section briefly reviews related work in published literature,
-  sub-section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
-The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
-And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
-Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
-
-\subsection{The Basics of POLSAR Statistical Analysis}
-
-In this paper, the POLSAR scattering vector is denoted as $s$.
-In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
-  the vector is two-dimensional ($d=2$) and is normally written as: 
-\begin{equation}
-s_{part}=\begin{bmatrix}
-S_h\\ 
-S_v
-\end{bmatrix}
-\end{equation}
-In the case of full and monostatic POLSAR data,
-  the vector is three-dimensional ($d=3$) and is presented as:
-\begin{equation}
-s_{full}=\begin{bmatrix}
-S_{hh}\\
-\sqrt{2}S_{hv}\\
-S_{vv}
-\end{bmatrix}
-\end{equation}
-
-Let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
-  where $s^{*T}$ denotes the complex conjugate transpose of $s$. 
-Assuming %all the elements in $s$ are independent and
-  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
-  then the probably density function (PDF) of $s$ can be written as:
-\begin{equation}
-  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-\end{equation}
-where $||$ denotes the matrix determinant.
-
-As the covariance matrix is only defined on multiple data points,
-  sample POLSAR covariance matrices are commonly presented in ``ensemble'' format.
-They are formed as the mean of Hermitian outer product of single-look scattering vectors,
-\begin{equation}
-  C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
-\end{equation}
-where $s_i$ denotes the single-look scattering vector,
-  which equals $s_{part}$ in the case of partial POLSAR and
-  $s_{full}$ in the case of full polarimetry,
-and $L$ is the number of looks.
-
-Complex Wishart distribution statistics, however, are normally written for the scaled covariance matrix
-$Z=LC_v$, whose PDF is given as:
-\begin{equation}
-  pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
-\end{equation}
-with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
-and $d$ is the dimensional number of the POLSAR covariance matrix.
-
-The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
-  %under the assumption of circular complex Gaussian distribution
-  %applicable for POLSAR data.
-Goodman \cite{Goodman_1963_AMS_178} proved
-that the ratio between the observable and expected values of the sample covariance matrix's determinants
-  behave like a product of $d$ chi-squared random variables with different degrees of freedom 
-\begin{equation}
-\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
-\label{eqn:prod_chi_squared_rv}  
-\end{equation}
-
-Its log-transformed variable consequently 
-  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
-\begin{equation}
-\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
-\label{eqn:sum_log_chi_squared_rv}
-\end{equation}
-with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
-
-\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
+\section{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
@@
 Moreover, they are independent of $\Sigma_v$.
-%This result shows how
-In short, these random variables are shown to follow consistent and fixed distributions,
+This result shows how
+  these random variables follows consistent and fixed distributions,
   regardless of the underlying signal $\Sigma_v$.
@@
   Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the the following results obtained from the our previous works on single-look SAR \cite{Le_2010_ACRS} \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+First is the the following results obtained from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
 %Upon setting $d=1$ into the above models,
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR log-distance]{
+	\subfloat[verify multi-look SAR log-distance]{
 		 \epsfxsize=3in
@@
 	\hfill	
-	\subfloat[multi-look SAR contrast]{
+	\subfloat[verify multi-look SAR contrast]{
 		 \epsfxsize=3in
@@
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
+	\subfloat[full-pol 3x3 determinant ratio]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
+	\subfloat[full-pol 3x3 log distance]{
 		 \epsfxsize=1.5in
@@
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
+	\subfloat[full-pol 3x3 determinant ratio]{
 		 \epsfxsize=3in
@@
 	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
+	\subfloat[full-pol 3x3 log distance]{
 		 \epsfxsize=3in
@@
 \begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
+	\subfloat[verify polsar 2x2: determinant]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
+	\subfloat[verify polsar 2x2: log-determinant]{
 		 \epsfxsize=1.5in
@@
 	} \\ 
-	\subfloat[polsar (3x3) determinant]{
+	\subfloat[verify polsar 3x3: determinant]{
 		 \epsfxsize=1.5in
@@
 	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
+	\subfloat[verify polsar 3x3: log-determinant]{
 		 \epsfxsize=1.5in
@@
 \begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
+	\subfloat[verify polsar 2x2: determinant]{
 		 \epsfxsize=3in
@@
 	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
+	\subfloat[verify polsar 2x2: log-determinant]{
 		 \epsfxsize=3in
@@
 	} \\ 
-	\subfloat[polsar (3x3) determinant]{
+	\subfloat[verify polsar 3x3: determinant]{
 		 \epsfxsize=3in
@@
 	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
+	\subfloat[verify polsar 3x3: log-determinant]{
 		 \epsfxsize=3in
@@
 In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.
-And it is shown that: the theoretical model proposed can apply to the practical data, even when this ``imperfection'' is taken into account.
+And it is shown that: the theoretical model proposed can apply to the practical data, even when this ``imperfection''  are taken into account.
 %In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
@@
 
-The assumption of statistical independence between samples (which applies to both SAR and POLSAR data) is reasonable given that 
+The second assumption of statistical independence between samples (which applies to both SAR and POLSAR data) is reasonable given that 
   the transmission and receipt of analogue signals is done independently for each radar pulse, i.e. for each resolution cell.
 Thus, theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
+
 However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
@@
 Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph or by using the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
+  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph or by using the following equation, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
 %And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
@@
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
+	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
 		 \label{sar}
@@
 
-In conclusion, a couple of statistical models for the determinant of the POLSAR covariance matrix is proposed and validated in this paper.
-Compared to other statistical models for POLSAR, the proposed models are scalar and representative for the multi-dimensional POLSAR data.
-These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
-Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
-As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
-
-%An additive and homoskedastic model, 
-%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
-%  is proposed in this paper.
-%The theoretical model is shown to be comprehensive:
-%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
-%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
-%
-%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
-%  is gracefully transformed into traditional SAR intensity.
-%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
-%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
-%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
+An additive and homoskedastic model, 
+  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+  is proposed in this paper.
+The theoretical model is shown to be comprehensive:
+not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+
+The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+  is gracefully transformed into traditional SAR intensity.
+Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.
 

### 2013-05-17 paper_dev/article_pp.tex
2013May_0517

--- 2013-03-01 4/polsar.tex
@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
-\label{chap:polsar}
-
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
-
-\section{POLSAR statistical analysis}
-
-In this section, the POLSAR scattering vector is denoted as $s$.
+%ifdef FINAL
+\documentclass[journal]{IEEEtran}
+%endif
+%ifdef REVIEW
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+%endif
+%\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{cite} %for citations
+\usepackage{url}
+
+ %this is for math typing (eg: cases)
+\usepackage{amsmath}
+   \usepackage{amsfonts}   % if you want the fonts
+   \usepackage{amssymb}    % if you want extra symbols
+\usepackage{epsfig} %for figures
+
+\usepackage[center]{caption}%for captions
+\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+
+%opening
+\title{
+  Scalar and Representative Models for Polarimetric SAR Data
+}
+
+%\author{Thanh-Hai Le, Ian McLoughlin}
+\author{Thanh-Hai~Le,
+        Ian~McLoughlin, 
+	and Chan-Hua~Vun%
+\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
+Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+University of Science and Technology of China.
+}% <-this % stops a space
+%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
+%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+\thanks{Manuscript received ?, 2013; revised ?.}}
+
+\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+
+\begin{document}
+
+\maketitle
+
+\begin{abstract}
+This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
+Compared to other scalar statistical models for POLSAR,
+  the proposed models are highly representative of the multi-dimensional data
+  and enable useful discrimination measures to be determined easily. %consequently they lead to useful discrimination measures.
+When the multi-dimensional models are collapsed to a one-dimensional case,
+  they are shown to exactly match the traditional statistical models for SAR intensity.
+The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
+The proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
+An  example is also shown where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+\end{abstract}
+
+\begin{IEEEkeywords}
+Polarimetric Synthetic Aperture Radar, Electromagnetic Modeling, Multidimensional Signal Processing  
+\end{IEEEkeywords}
+
+\IEEEpeerreviewmaketitle
+
+\section{Introduction}
+
+During the past decades, exponential growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
+technology to become a feasible and preferred technique for earth observation applications.
+SAR technology has since extended in a few directions, one of which is polarimetric SAR (POLSAR).
+POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
+  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
+
+While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
+Namely that there now exists not one but many observables quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
+The research community has responded largely by developing different statistical models for various POLSAR observables.
+However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
+Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
+On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.
+
+This paper presents novel statistical models for multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+Specifically statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domian determinant, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
+The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
+  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
+With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
+  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
+The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
+Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
+This is followed by a conclusion in Section \ref{sec:conclusion}.
+
+\section{Related Work in Literature}
+\label{sec:lit_review}
+
+This section outlines related published work.
+In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
+Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
+Section \ref{sec:lit_measures} further strengthen these findings by discussing discrimination measures that have been proposed for POLSAR,
+  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
+However, while an exact statistical distribution is needed for the test,
+  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
+
+\subsection{Investigated Scalar Observables for POLSAR Data and their Statistical Models}
+\label{sec:lit_models}
+
+Different target decomposition theorems have identified many different scalar observables for complex POLSAR data.
+In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
+While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, at its conclusion, the paper indicated that: it is impossible to identify the best representation.
+To be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
+  rather than providing a single unified representation of the POLSAR data.
+
+Given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
+  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
+This becomes an alternative approach used in the study of POLSAR data.
+However, such derivations are no trivial task, and so far, only a handful of such statistical models have been proposed, including the following:
+  \begin{enumerate}
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \end{enumerate}
+
+More recently, statistical models for
+  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been studied.
+While these models undoubtedly help in understanding POLSAR data,
+  none of these observables have been shown to meet the dual criteria of
+  1) resulting in statistically consistent discrimination measures and
+  2) being representative of the complex POLSAR data.
+
+\subsection{POLSAR Discrimination Measures}
+\label{sec:lit_measures}
+
+The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
+\begin{align}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align}
+where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
+  probably because of the multiplicative nature of the noisy data.
+
+In the field of POLSAR, the Wishart distance is probably the most widely used as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
+It is defined as \cite{Lee_1994_IJRS_2299}
+\begin{equation}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation}
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested a number of other dissimilarity measures.
+These include the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align}
+the Bartlett distance \cite{Kersten_2005_TGRS_519},
+  \begin{align}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align}
+the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+\begin{equation}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation}
+and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+\begin{equation}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation}
+.
+
+Closer investigation of these dis-similarity measures reveals that most are related in some way. %to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
+  when the two data sets have the same number of looks, i.e. $L_x=L_y$.
+The close relation among the measures is further supported by the fact that
+  all of their proposing papers referenced the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrix is considered:  
+\begin{equation*}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation*}
+
+Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{eqnarray}
+
+To detect changes, a test statistic is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
+
+\section{Scalar Statistical Models for POLSAR}  
+\label{sec:theoretical_model}
+
+In this section, several scalar statistical models for POLSAR are presented.
+After section \ref{sec:model_basic} briefly introduce the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
+  section \ref{sec:polsar_heterosked_model_and_log_transform}
+  presents the theoretical models together with mathematical evidence for two related points.
+The first point is that: the POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion states: log-transformation converts it into an additive and homoskedastic model.
+Several consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
+
+\subsection{Basics of POLSAR Statistical Analysis}
+\label{sec:model_basic}
+
+In this paper, the POLSAR scattering vector is denoted as $s$.
 In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
@@
 
-This newly derived models for multi-look SAR data can also be validated against real-life data.
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
+\section{Validating the proposed models against real-life data}
+\label{sec:polsar_models_validation}
+
+This section aims to verify the theoretical models against practical data.
+Since the previous section have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  which have been validated extensively, only a quick validation is needed for this case.
+
+Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
-
+The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
+ The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{figure}
-
-\section{Validating the models against real-life data}
-\label{sec:polsar_models_validation}
-
-\subsection{Explaining practical data with the given Number-of-Looks}
-
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
-  assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
-
-Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[multi-look SAR log-distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[multi-look SAR contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
+		 \label{multi_look_contrast}
+	}
+\end{tabular}
+\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
+\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\end{figure}
+%endif
+
+After this quick validation, the rest of this section focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
+Specifically, section \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
+While the match appears to be reasonably good, it can be further improved.
+Section \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
+  while section \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
+With the newly estimated ENL, section \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
+
+\subsection{Using the nominal ENL to validate the theoretical models} 
+\label{sec:valid_nominal_enl}
+
+The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
+Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.
+
+For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
+Both the the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
+These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
+Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
+Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.
+
+The least-assumed stochastic processes for dispersion and contrast are validated first.
+For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
+Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
+Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
 
 At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
-
+Here a nominal look-number L=4 is used
+  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
+The plots, presented in Fig.
+  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[part-pol (2x2) dispersion]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
+		 \label{dispersion_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
+		 \label{contrast_2x2}
+	} \\
+	\subfloat[full-pol (3x3) dispersion]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
+		 \label{dispersion_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) contrast]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
+		 \label{contrast_3x3}
+	}
+\end{tabular}
+\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
+\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\end{figure}
+%endif
 
 Apart from dispersion and contrast,
-the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
+  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
 There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be explored in this section.
-However, given that the log-determinant average has already been computed earlier, 
-  the second approach is used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
+Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+Both approaches will be presented in this section.
+As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.
+
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
+In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
+  and \ref{eqn:log_determinant_distance_distribution},
   while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
   with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
+%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
+A close match is again observed, validating the models for log-distance and determinant ratio.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{figure}
-
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
-
-However, a more interesting  phenomena is to be described.
-It happens in the validation process for determinant and its log-transformed model,
-  where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
+	\subfloat[part-pol (2x2) determinant ratio]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_2x2}
+	} 
+	\hfill	
+	\subfloat[part-pol (2x2) log distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
+		 \label{log_distance_2x2}
+	} \\
+	\subfloat[full-pol (3x3) determinant ratio]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
+		 \label{determinant_ratio_3x3}
+	} 
+	\hfill	
+	\subfloat[full-pol (3x3) log distance]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
+		 \label{log_distance_3x3}
+	}
+\end{tabular}
+\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
+\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\end{figure}
+%endif
+
+Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
+  where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
+The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
+Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
+
+%ifdef FINAL
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[polsar (2x2) determinant]{
 		 \epsfxsize=1.5in
@@
 \end{figure}
-
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[polsar (2x2) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
+		 \label{determinant_2x2}
+	} 
+	\hfill	
+	\subfloat[polsar (2x2) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
+		 \label{log_det_2x2}
+	} \\ 
+	\subfloat[polsar (3x3) determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
+		 \label{determinant_3x3}
+	} 
+	\hfill	
+	\subfloat[polsar (3x3) log-determinant]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
+		 \label{log_det_3x3}
+	} 
+\end{tabular}
+\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
+\label{fig:verify_polsar_2x2_simulation_det}
+\end{figure}
+%endif
+
+In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
 The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
@@
 \end{tabular}
-\caption{The relationships between ENL and the sample variance of log-determinant and log-intensity}
+\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots}
 \label{fig:plot_enl_var_relation_1x1_and_2x2}
 \end{figure}
-
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
-The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
-Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[ENL and variance log-intensity relations for SAR data]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
+		 \label{plot_enl_var_relation_1x1}
+	} 
+	\hfill	
+	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
+		 \label{plot_enl_var_relation_2x2}
+	} 
+\end{tabular}
+\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
+\label{fig:plot_enl_var_relation_1x1_and_2x2}
+\end{figure}
+%endif
+
+\subsection{Using estimated ENL to better explain practical data}
+\label{sec:valid_improve_practice}
+
+To demonstrate the improvement obtained using this ENL estimation,  a sample  single-look complex fine-quad RADARSAT2 dataset is used. 
+A nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
+The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
+  against the theoretical models for the nominal ENL value of 9.
+As expected the match is evidently not very close.
+
+We now compare this to the estimated ENL approach.
+First, an ENL estimate is obtained from the observable variance of the log-determinant. 
+Then the new sample histogram is overlaid on the same figure,
+  showing a much better consistency.
+This procedure can always be carried out for a given dataset,
+  as long as a homogeneous area can be defined and extracted.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
+\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics.
+However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL and model the data reasonably well.}
 \label{fig:handling_radarsat2_oversampling_practice}
 \end{figure}
-
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
+		 \label{sar}
+	} 
+	\hfill	
+	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
+		 \label{part_pol}
+	}   
+\end{tabular}
+\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
+Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
+\label{fig:handling_radarsat2_oversampling_practice}
+\end{figure}
+%endif
+
+The same approach can be applied on the AIRSAR Flevoland data to improve the validational match described earlier.
+Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
+  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
+Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
+
+%ifdef FINAL
 \begin{figure}[h]
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}
 \end{figure}
-
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
+		 \label{sar}
+	} 
+	\hfill	
+	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
+		 \label{part_pol}
+	}   
+\end{tabular}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
+\label{fig:handling_airsar_oversampling_practice_full_pol}
+\end{figure}
+%endif
+
+\section{Discussion}
+\label{sec:discussion}
+
+Let us begin by noting a few theoretical properties of the proposed statistical model.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
+
+Second, the model is developed for the POLSAR covariance matrix.
+However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+  the model should also be applicable to the coherency matrix.
+
+The model is far from complete.
+ It reduces the multi-dimensional POLSAR data to a scalar value.
+While this is probably desirable for a wide range of application,
+  such a reduction is unlikely to be lossless.
+Thus to better understand POLSAR data
+  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
+the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).
+
+However the proposed model is also promising.
+Eventhough initially developed for partial and monostatic POLSAR data,
+  it was later shown to be applicable to traditional SAR data as well.
+Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
+
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
+
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
+
+In evaluating SAR speckle filters, the intensity ratio is widely used.
+Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+Assuming a perfect filtering condition, the ratio image should only contain random noise.
+Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+
+Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+  this technique can be equally applied to evaluate POLSAR speckle filters.
+In fact better results can be achived.
+In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not very well suited for digital image presentation,
+  which is linear and additive in nature.
+Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.
+
+To evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
+  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters are then applied to the patch.
+\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+
+%ifdef FINAL
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  the distortion impact of the filter can also be made visible by the residual image.
+In visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such an observation can be made relatively easier by inspecting the residual image.
+
+There are many similar SAR data processing technique that may be adaptable to POLSAR.
+Examples in the same topic of evaluating speckle filters include
+  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+
+In fact, at the time of this writing, the field of SAR is much more developed than the field of POLSAR.
+The two fields however are quite separated,
+  as many techniques applicable to SAR are not directly applicable to POLSAR.
+This work may build the bridge between these two separated fields,
+  inviting potential extension of various SAR processing techniques on POLSAR data.
+Here a specific example is shown
+  where, similar to the way ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+In general, we believe there are many more unexplored possibilities for such applications
+  which is only limited by our imagination.
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
+  resulting in several consistent discrimination measures for POLSAR applications.
+The theoretical models are shown to be powerful in that:
+  not only it can provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
+  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
+They are also practically useful since they lead to several consistent discrimination measures.
+Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
+Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
+
+%In conclusion, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix,
+%  which result in several consistent discrimination measures for POLSAR, are proposed and validated in this paper.
+%The theoretical model is shown to be comprehensive in that:
+%  not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
+%  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
+%Compared to other scalar statistical models for POLSAR, the proposed models are highly representative of the multi-dimensional POLSAR data.
+%%These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
+%%Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
+%%As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
+%
+
+%An additive and homoskedastic model, 
+%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
+%  is proposed in this paper.
+%The theoretical model is shown to be comprehensive:
+%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
+%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
+%
+%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
+%  is gracefully transformed into traditional SAR intensity.
+%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+%%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
+%%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
+%%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.  
+%The models may also form a bridge, allowing the adaptation of many existing SAR data processing technique for POLSAR data,
+%  a quick example of this is briefly described in this paper.
+%This paper
+
+\appendices
+\section{Homoskedastic Model for the Log-Determinant}
+\label{chap:appendix_a}
+
+\subsection{Log-Chi-Square Distribution and its Derivatives}
+%\section{Log-Chi-Square Distribution}
+\renewcommand{\theequation}{\thesection.\arabic{equation}}
+\setcounter{equation}{0}
+
+This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
 

### 2013-05-17 paper_dev/letter_to_reviewers.tex
2013May_0517

\documentclass{letter}
\usepackage{hyperref}
\signature{The Authors}
\address{}
\begin{document}

\begin{letter}{The Reviewers,\\IEEE Transaction on Geoscience and Remote Sensing}
\opening{Dear Reviewers,}

%\documentclass{article}
%\title{Cover letter to the Reviewers}

%\begin{document}

%\maketitle

We appreciate your time and effort in reviewing our work.
This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus provides a bridge between the two fields inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
We hope that, like us when we were faced with its results,
  you will find satisfaction as well as excitement after reading through this paper.
We appreciate your feedback in whatever way it may be in making this manuscript to become a better publication.
To facilitate your review, we enclose here a short synopsis of the paper.

We are aware that the paper is a bit too long.
Specifically, the mathematical derivations in the Appendices is presented in great details.
While this is supposed to expedite your review,
  it probably should be shortened in publication.
We would appreciate it if you can help us by pointing out which portion of this paper may be considered redundant by the TGRS readers.

Once again, we thank you for your reviewing time and effort.

\closing{Our best regards}

\encl{The Synopsis of the Paper (next page)}

\newpage
\textbf{The Research Context:}

The extension from SAR to POLSAR brings about an issue that needs to be addressed:
  there exists not one, like the intensity in SAR, but many scalar observable quantities in POLSAR. 
While different statistical models have been developed for different POLSAR observables, 
  for a model to be useful, discrimination measures need to be derived.
Many POLSAR data processing techniques requires a scalar, representative observable and statistical model.

\textbf{Problem Statement:}

Practical application for POLSAR data processing requires the measures to be scalar, consistent and preferably homoskedastic on one hand.
On the other hand, the observable quantity being modelled need to be naturally representative for the high-dimensional POLSAR data.

\textbf{Newly Proposed Technique to Handle this Situation:}

In this paper, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed.
These models are shown to be both representative and subsequently lead to statistically consistent discrimination measures.

\textbf{Shortcomings of the current POLSAR statistical models:}

There are a few published scalar statistical models for POLSAR, but none of them fit the dual criteria of being representative and at the same time lead to scalar discrimination measures.
There are also a few POLSAR discrimination measures, but all of them are based on the likelihood test statistics, which so far have only shown to be based on asymptotic distribution.

\textbf{Advantages of the newly proposed model}

Compared to other statistical models for POLSAR, the proposed models are scalar, and representative for POLSAR data.
Moreover, several multiplicative discrimination measures and additive measures of distance are derived from the proposed statistical models.
These POLSAR discrimination measures, for e.g. the determinant-ratio, can be considered as the multi-dimensional extension of the commonly used discrimination measures for the one-dimensional SAR intensity.
Compared to other discrimination measure proposals, this paper suggests an exact distribution, as opposed to asymptotic distributions, for the POLSAR likelihood statistical test.
As a by-product of this exact modeling, simpler discrimination measures, i.e. determinant-ratio and contrast, are proposed for the common case of Lx=Ly.

\textbf{High-level Summary of this work}

This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus provides a bridge between the two fields inviting the adaptation of many existing SAR data processing techniques for POLSAR data.

\end{letter}

\end{document}

### 2013-05-18 paper_dev/article.tex
201305_May18 update from last version of 201305_May17

@@
   the proposed models are highly representative of the multi-dimensional data
-  and enable useful discrimination measures to be determined easily. %consequently they lead to useful discrimination measures.
-When the multi-dimensional models are collapsed to a one-dimensional case,
+  and enable useful discrimination measures to be easily determined. %consequently they lead to useful discrimination measures.
+When the multi-dimensional models are collapsed to a single dimension,
   they are shown to exactly match the traditional statistical models for SAR intensity.
 The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
-The proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
-An  example is also shown where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+%IVMThe proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
+The intention is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
+To illstrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
 \end{abstract}
@@
 While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
-Namely that there now exists not one but many observables quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
+Namely that there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
 The research community has responded largely by developing different statistical models for various POLSAR observables.
@@
 
-This paper presents novel statistical models for multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus enables the adaptation of many existing SAR data processing techniques for POLSAR data.
-Specifically statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domian determinant, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
+This paper presents novel statistical models for multi-dimensional POLSAR data as generalisations of the commonly used one-dimensional SAR statistical model.
+This approach makes feasible the adaptation of many existing SAR processing techniques, to be applied to POLSAR data.
+Specifically, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
 The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
@@
 Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
-Section \ref{sec:lit_measures} further strengthen these findings by discussing discrimination measures that have been proposed for POLSAR,
+Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
   and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
@@
 
-Different target decomposition theorems have identified many different scalar observables for complex POLSAR data.
+Different target decomposition theorems have identified many possible scalar observables for complex POLSAR data.
 In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
 While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
-Furthermore, at its conclusion, the paper indicated that: it is impossible to identify the best representation.
-To be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
+Furthermore, at its conclusion, the paper indicated that it is impossible to identify a single best representation.
+Although, to be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
   rather than providing a single unified representation of the POLSAR data.
@@
 \end{align}
-where $A_{i,j}$ denotes the (i,j) elements of the matrix A,
+where $C_{i,j}$ denotes the (i,j) elements of the matrix C,
  $||$ denotes absolute values
 and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR covariance matrix, these dis-similarity measures are not widely used 
+However, in the context of POLSAR% covariance matrix
+, these dis-similarity measures are not widely used 
   probably because of the multiplicative nature of the noisy data.
 
-In the field of POLSAR, the Wishart distance is probably the most widely used as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
-It is defined as \cite{Lee_1994_IJRS_2299}
+In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
+It is defined \cite{Lee_1994_IJRS_2299} as:
 \begin{equation}
@@
 
-Recent works have suggested a number of other dissimilarity measures.
-These include the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+Recent works have suggested alternative dissimilarity measures including the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
 \begin{align}
@@
 .
+
+%%***IVM: Hai, you haven't introduced the notation for these!! What is tr() (in eqn. 3), what is Lx, Ly.... I changed your A_{i,j} to C_{i,j} above, just after eqn.2
 
@@
 In this section, several scalar statistical models for POLSAR are presented.
-After section \ref{sec:model_basic} briefly introduce the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
+After section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
   section \ref{sec:polsar_heterosked_model_and_log_transform}
   presents the theoretical models together with mathematical evidence for two related points.
-The first point is that: the POLSAR data is multiplicative and heteroskedastic in its original domain.
-And the second conclusion states: log-transformation converts it into an additive and homoskedastic model.
-Several consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
+The first point is that the POLSAR data is multiplicative and heteroskedastic in its original domain.
+And the second conclusion states that log-transformation converts it into an additive and homoskedastic model.
+Some consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
 
@@
 Goodman \cite{Goodman_1963_AMS_178} proved
-that the ratio between the observable and expected values of the sample covariance matrix's determinants
-  behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
+that the ratio between the observable and expected values of the sample covariance matrix determinants
+  behave like a product of $d$ chi-squared random variables with different degrees of freedom: 
 \begin{equation}
@@
 with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
+  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$.
+We will now use this result to develop the statistical models for POLSAR. %log-transformed measures of distance.
+%***IVM added the sentence above... **Please check it's true!!!!
 
@@
 Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ vary depending on the underlying signal $\Sigma_v$. 
-In such context, Eqn.
-\ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
+In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
 At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$, exhibiting its homoskedastic nature.
+  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ (i.e. it is homoskedastic).
 
@@
 
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2010_ACRS},
-  this section introduces the consistent sense of distance from different perspectives.
+Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
+  this section introduces the consistent sense of distance for POLSAR.
 Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
@@
   ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
-  are the observable according to the following definitions:
+  are observable according to the following definitions:
+%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
 \begin{eqnarray}
@@
 On the other hand, under a looser assumption %From another perspective
-  where the POLSAR is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
+  where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
   the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
@@
   it is natural that these variables also follow fixed distributions.
-Moreover, they are independent of the underlying signal $\Sigma_v$.
-
-\section{SAR as the one-dimensional case of multi-dimensional POLSAR}
+Moreover, note that they are independent of the underlying signal $\Sigma_v$.
+%This result shows how
+%In short, these random variables are shown to follow consistent and fixed distributions,
+%  regardless of the underlying signal $\Sigma_v$.
+
+\section{SAR as a one-dimensional case of POLSAR}
 \label{sec:sar_special_case_of_polsar}
@@
 This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
-  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into 1-dimensional conventional SAR data.
+  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
 Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
@@
   Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the following results obtained from our previous works on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
+First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
+%Upon setting $d=1$ into the above models,
+%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
+%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
 \begin{align*}
@@
 This section aims to verify the theoretical models against practical data.
-Since the previous section have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, only a quick validation is needed for this case.
+Since we have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  which have been validated extensively, only a simple validation is presented for this case.
 
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
-In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for the log-distance and contrast is then plotted against the theoretical PDF given above.
- The plot is obtained with ENL set to the nominal number of 4, and  good visual match is apparent in the final results.
+In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
+The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
+ The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
+%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
+%The ENL is set to the nominal number of 4.
+%And good visual match is apparent in the final results.
 
@@
 
-After this quick validation, the rest of this section focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Specifically, section \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
+The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
+Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
 While the match appears to be reasonably good, it can be further improved.
-Section \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
-  while section \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
-With the newly estimated ENL, section \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
+Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
+  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
+With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
+
+%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
+%While the match appears to be reasonably good, it can be further improved.
+%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
+%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
+%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
 
@@
 The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
-This is discussed in the next section.
+This is discussed in the next subsection.
+%The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
+%In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
+
+%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
+%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+%  where not only the look number is shown to be misused
+%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
+%As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
+%  the reason is due to the inappropriate look number being used.
+%Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
+%For now, let us simply observe that
+%  using appropriate estimation of the parameters, 
+%  the proposed models match reasonably well with the practical data.
 
@@
 Even though the assumptions made in developing this theory have intentionally been kept minimal, 
-  like all other similar models, the proposed model in this paper is built upon certain presumptions.
-However, practical conditions may not always satisfy these prerequisites.
-In this section, a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions is discussed.
+in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
+However, practical conditions may not always satisfy these prerequisites, thus we find a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions.
 
 The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
-  the transmission and receipt of analogue signals independent for each radar pulse, i.e. for each resolution cell.
-However, the actual imaging mechanism in a real-life (POL)SAR processor is that of a digital nature,
+  the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
+However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
   where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
@@
 While for RadarSat2, the pixel resolution and range - azimuth resolution combination for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
-In short, while the indepedent samples assumption is made out of necessity in theory,
-  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighboring samples. % are actually correlated
+In short, while the independent sample assumption is made out of necessity in theory,
+  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighbouring samples. % are actually correlated
 This documented imperfection also leads to the rise of effective number-of-look concept (ENL),
@@
 
-The proposed model apparently can handle the imperfection. %that is found in practical data.
+The proposed model apparently can handle this imperfection. %that is found in practical data.
 The handling process, however, is slightly more complex.
 Instead of adopting the nominal Number of Looks given by the SAR processor,
-  the ENL is to be estimated from the given data.
-This is discussed in the next section.
+  an ENL must first be estimated from the given data.
+This is discussed in the next subsection.
 
@@
 In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
-  it is possible to estimate the ``effective'' number of look, by finding an $L$ that ensures the above relationship is valid.
+  it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
 This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
@@
 
-In this section, an alternative approach making use of variance statistics in the homoskedastic log-domain to find ENL is proposed.
+We will instead propose an alternative approach making use of variance statistics in the homoskedastic log-domain.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
 \end{tabular}
-\caption{The relations between ENL and sample variance of log-determinant/log-intensity}
+\caption{The relation between ENL and sample variance of log-determinant/log-intensity.}
 \label{fig:plot_enl_var_relation_1x1_and_2x2}
@@
 
-To demonstrate the improvement obtained using this ENL estimation,  a sample  single-look complex fine-quad RADARSAT2 dataset is used. 
-A nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
+To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
+Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
 The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
@@
 
-The same approach can be applied on the AIRSAR Flevoland data to improve the validational match described earlier.
+The same approach can be applied on the AIRSAR Flevoland data to improve the validation described earlier.
 Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
-  even though it is to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
+  even though it is to a much lesser extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
 Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
@@
   such a reduction is unlikely to be lossless.
-Thus to better understand POLSAR data
-  the use of this technique can be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
-the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} ...).
-
-However the proposed model is also promising.
-Eventhough initially developed for partial and monostatic POLSAR data,
-  it was later shown to be applicable to traditional SAR data as well.
+Thus %to better understand POLSAR data
+the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
+the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar).
+
+However the proposed model is promising.
+Even though initially developed for partial and monostatic POLSAR data,
+  it was shown to be applicable to traditional SAR data as well.
 Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
@@
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
-Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
+%***IVM remove this single sentence, it detracts from the argument...
+%Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
 
@@
   this technique can be equally applied to evaluate POLSAR speckle filters.
-In fact better results can be achived.
-In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not very well suited for digital image presentation,
+In fact better results can be achieved.
+In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
   which is linear and additive in nature.
@@
 
-To evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
+To briefly evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
   a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
@@
   the distortion impact of the filter can also be made visible by the residual image.
-In visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
 in the additive log-determinant image of the filtered output, 
@@
 
-There are many similar SAR data processing technique that may be adaptable to POLSAR.
+Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
+Evidently these techniques can also be adapted for POLSAR.
+Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
+
+Hai version: (Ian have not seen this yet) There are many similar SAR data processing technique that may be adaptable to POLSAR.
 Examples in the same topic of evaluating speckle filters include
@@
   resulting in several consistent discrimination measures for POLSAR applications.
-The theoretical models are shown to be powerful in that:
-  not only it can provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
-  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
+The theoretical models are shown to be powerful in that
+  not only can they provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
+  but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
 They are also practically useful since they lead to several consistent discrimination measures.
@@
   and converting natural logarithm into base-2 logarithm.
-First, setting $L=1$ makes the above results become
+First, setting $L=1$ makes the above results become:
 \begin{eqnarray*}

### 2013-05-18 paper_dev/article_pp.tex
201305_May18 update from last version of 201305_May17

@@
 \end{tabular}
-\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots}
+\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots.}
 \label{fig:plot_enl_var_relation_1x1_and_2x2}
@@
 \caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics.
-However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL and model the data reasonably well.}
+However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL which matches the data much more closely.}
 \label{fig:handling_radarsat2_oversampling_practice}
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through to a lesser extent than the RADARSAT2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}

### 2013-07-24 0_frontmatter/abstract.tex
updated for Ian changes

--- 2013-03-01 0_frontmatter/abstract.tex
@@
 
-Put your abstract or summary in 0\_frontmatter/abstract.tex.
+On the one hand, practical application for POLSAR data processing requires the establishment of discrimination measures
+  which are to be scalar and statistically consistent.
+On the other hand, these same scalar observable quantities need to be naturally representative for the high-dimensional POLSAR data.
+At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.
+
+In this thesis, the statistical behavior of the determinant of POLSAR covariance matrix is explored.
+Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.
+
+As the result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix is proposed and validated.
+This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
+Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
+Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
+From these models, several additive measures of distance are proposed for both SAR and POLSAR data.
+
+There are several beneficial implications of the theory proposed in this thesis. 
+Since the scalar and representative model for POLSAR generalize the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+At the same time, the benefit of the homoskedastic models is multiple-folds.
+For in-experienced researchers (like this author when he started this study),
+  who attempt to process either SAR or POLSAR data using existing computation algorithms
+  which most of the time expect an additive and homoskedastic input,
+  this thesis proposes alternative and more familiar additive and homoskedastic models
+    in place of the original ones which are multiplicative and heteroskedastic.
+For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
+  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.
+
+%\newpage
+%In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
+%As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR or POLSAR.
+%POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
+%Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
+%
+%The extension from SAR to POLSAR brings about the representation issue in that:
+% there exists not one, like the intensity in SAR, but many observable quantities in POLSAR.
+%While different statistical models have been developed for different POLSAR observables,
+% for a statistical model to be useful, scalar discrimination measures need to be derived from.
+%Thus on the one hand, practical application for POLSAR data processing requires the measure to be scalar, consistent and preferably homoskedastic. 
+%On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
+%
+%Furthermore, since POLSAR can be considered as the multi-dimensional extension of the traditional SAR, a common problem exists for both SAR and POLSAR data.
+%That is: the sense of subtractive distance is seriously flawed in the original multiplicative and heteroskedastic domain of (POL)SAR data.
+%The digital technologies which ranges from image processing and presentation to artificial intelligence and machine learning algorithms that are used to process (POL)SAR data, however, are linear and additive in nature.
+%This linear and additive nature is manifested for example: in a large number of algorithms in the field of  computational intelligence which make use of the universal MSE as objective functions, as well as the extensive use of variance and contrast in digital image processing.
+%
+%Thus a solution is needed to address the dual problem of 1) figuring out scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data and 2) arriving at consistent measures of subtractive distance for both SAR and POLSAR data, which can pave the way for further applications of existing digital-based algorithms towards (POL)SAR data.
+%
+%In this thesis, scalar, representative and homoskedastic measures of distances are derived for the multi-dimensional, inter-correlated and heteroskedastic (POL)SAR data.
+%And their benefits are highlighted against well-known published work.
+%
+%Specifically, compared with other scalar statistical models for POLSAR,
+%  the proposed models are representative for POLSAR data in the sense that the observable being modelled is the generalized version of the representative one-channel SAR intensity in the multidimensional case.
+%Moreover, several multiplicative dis-similarity measures and additive measures of distance are derived from the proposed statistical models.
+%
+%And similar to the ratio in the original SAR domain, the subtractive distance in the log-transformed (POL)SAR domain is statistically consistent.
+%Compared to the subtractive distance in the original domain, the PDF of the subtractive distances are not dependent on the underlying backscattering coefficient.
+%And compared to the ratio in the original domain, the subtractive residual is linear in nature, which fits better with the digital image processing and presentation processes.
+%This has created a number of benefits, for example: the MSE is again shown to be capable of evaluating SAR speckle filters or the consistent variance is demonstrated to be instrumental in breaking the vicious circle of SAR speckle filtering.
 

### 2013-07-24 1_introduction/introduction.tex
updated for Ian changes

@@
 %: ----------------------- introduction file header -----------------------
-\chapter{Introducing The Research Question}
+\chapter{Introduction}
 
-Synthetic Aperture Radar can soon become the preferred choice for
-  continous and autonomous large-scale remote surveillance solutions.
-Compared to optical remote sensors, which is passive,
-  active SAR sensors provides weather independent and night-inclusive operational capabilities.
-Compared to other radar based active sensors, for example Real Aperture Radar (RAR),
-  SAR provides a much better resolution, and larger coverage solution.
-The once-limiting drawback of SAR is the high-demanding signal processing procedures,
-  which is needed to process SAR images, has become obsolete,
-  due to recent and quick advances in computational power  \citep{Cumming_2005_Artech}.
+%What is the situation, the background context of your research? the BIG problem!
+Synthetic Aperture Radar is a technology with many advantages.
+%Compared to optical remote sensors, which are passive, active SAR sensors provide weather independent and night-inclusive operational capabilities.
+Compared to optical remote sensors - which are passive, SAR uses active sensors to provide weather independent and night-inclusive operational capabilities. 
+Compared to other radar based active sensors,
+for example Real Aperture Radar (RAR), SAR provides state-of-the-art resolution
+and coverage.
+In the past decades, the exponential growth in computational power has made the once overly excessive computationally demanding SAR technology to become a feasible and preferred earth observation solution \cite{Cumming_2005_Artech}.
+Thus SAR has now become the preferred choice for continuous and autonomous large-scale
+remote surveillance solutions.
 
-As reviewed in the second chapter, Synthetic Aperture Radar, i.e. SAR, offers a higher resolution, large coverage, weather-independent and night-capable imaging solution.
-Recent advances in computational power has made the once-limiting high-demanding signal-processing procedures, which are needed to process SAR images, obsolete \cite{Cumming_2005_Artech}.
-Thus we believe, SAR will soon come to be the preferred choice for continuous and autonomous large-scale remote surveillance solutions.
+As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is polarimetric SAR or POLSAR. POLSAR is the natural
+extension from SAR, exploiting the natural polarization property of Electromagnetic
+(EM) waves. It extends the SAR acquisition information from the traditional single
+SAR channel to multi-channel polarimetric SAR data, corresponding to a different combination of transmitted and received polarizations.
+Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
+multi-channel POLSAR data as compared to the traditional one-channel SAR data.
 
-Electromagnetic waves have the intrinsic nature of polarization.
-Polarimetric SAR, i.e.
-POLSAR, extends the SAR acquisition information from the traditional single SAR channel to multi-channel polarimetric SAR data, corresponding to different combination of transmitted and received polarizations.
-Early works from the radar community had focused on the theoretical introduction of scattering matrix, i.e.
-Sinclair matrix or Mueller matrices, for full, i.e.
-quad, polarimetric measurements \cite{Sinclair_1950_ProcsIRE}.
-%(Sinclair, 1950), (TODO) 
-These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \cite{Zebker_1991_ProcsIEEE}.
+With both SAR and POLSAR data becoming cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. However, both SAR 
+and POLSAR suffer from speckle phenomena, which hampers the human capabilities
+to understand SAR images. Speckle arises due to the random interference of many
+de-phased but coherent backscattered waves. Thus both SAR and POLSAR data are
+stochastic by nature.
 
-Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR, and so on, were launched.
-However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes apparently as a compromise between theoretical polarimetric requirements and practical limitations.
-Initially to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.
-Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
-In his pioneer paper in 2005, Souyris\cite{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode with the suggestion that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
-Raney\cite{Raney_2006_IGARSS} showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave, via Stokes parameters, but also capable of detecting the basic target's polarimetric characters, i.e.
-odd or even bounce phenomena.
+\section{Research Motivation}
 
-The extensions from single-channel SAR to multi-channel polarimetry can be considered as analogous to the advancement towards colour TV from the black-and-white days.
-While the future is promising, both SAR and POLSAR suffer from speckle phenomena, which hampers the human capabilities to understand SAR images.
-Speckle, which arises due to the random interference of many de-phased but coherent back-scattered waves, is inherent in all channels.
-%The effects of speckle is illustrated in Figure \ref{fig:sar_speckle_wrt_optical}.
+%Given the BIG problem, Why it is important to solve this problem?
+The
+                big picture, as introduced above, is that POLSAR data is multi­dimensional,
+                stochastic, multiplicative and heteroskedastic.
+%Under
+%                this context, the motivation is to gain a better
+%                understanding of the data,
+%which
+%                hopefully will lead to better information that can be
+%                extracted from these data.
+Under this condition, it is very important to understand the statistical models for SAR
+data. It is these models that form the foundation for different SAR data processing
+techniques, for example speckle filtering, target detection, image segmentation, and
+other clustering, classification techniques.
+In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
+which comprises statistical modeling and validation, estimator design and development
+as well as evaluation of different estimators’ accuracy. And central to this statistical
+estimation theory is the need for statistically consistent discrimination measures which
+are commonly derived from the statistical models.
 
-\section{The Research Question and the Motivation to Study}
+That is, while different statistical models have been developed for different POLSAR
+observables, for a statistical model to be useful, scalar discrimination measures need to
+be derived from it. At the same time, the extension from SAR to POLSAR brings about
+a representation difficulty in that: there exists not one, like the intensity in SAR, but
+many observable quantities in POLSAR. Thus on the one hand, practical application for
+POLSAR data processing requires the measure to be scalar, consistent and preferably
+homoskedastic. On the other hand, the observable quantity being modeled needs to
+be naturally representative of the high dimensional POLSAR data.
 
-Univariate SAR and multi-variate POLSAR data are multiplicative and heteroskedastic.
-By definition, heteroskedastic noised data has its variance, and correspondingly its substractive distances,
-  dependent on the main signal.
-In another line of research, log transformation has been shown
-  to convert the multiplicative nature of SAR data into a more familiar additive nature.
-We hypothesize that   
-  log-transformation also offers several consistent measures of distance in heteroskedastic SAR and POLSAR data.
-This thesis aims to investigate and validate that hypothesis.
+%Solving these dual-problem is both important and interesting.
+%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
+%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
+In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
+In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
+This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data.
+% dear Ian I changed this back
+%of the Additive White Gaussian Noise (AWGN) model in natural processes.
+%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive.
+However this is definitely not true - your POLSAR data is digital and yet is not additive.
+Maybe you can say "or the prevalence of AWGN in the majority of sensing or sampling systems, and electronic devices."
+%OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
+It should be noted that even for the case of SAR data which is digital and not additive,
+  the above statement is still true as SAR actually has two components, real and imaginary part,
+  and all of them follows the standard Additive White Gaussian Noise model.
 
-In this chapter: the main research problem and the corresponding hypothesis are explicitly stated.
-The methodology section explains how the results are obtained and analyzed.
-Contributions to advance theoretical knowledge are illustrated.
-Towards the end of the thesis, an application illustrate how the theoretical results can be applied in future research and development activities.
+Both SAR and POLSAR data however is multiplicative and heteroskedastic by nature.
+While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
+This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility.
+An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
+Such use, however, is known to be not very robust for these so-called heavy tailed distributions.
 
-Problem: speckle in SAR and POLSAR, especially its heteroskedastic nature. (new)
+Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
+For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences.
+However for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
+Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
+For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.
 
-The motivation then is to provide a probably better understanding about the statistics of speckle. (new)
+Furthermore, since POLSAR can be considered as the multi-dimensional extension of
+traditional SAR, a common problem exists for both SAR and POLSAR data. That
+is: the sense of subtractive distance is seriously flawed in the original multiplicative
+and heteroskedastic domain of both types of data. 
+In contrast, the digital technologies which range from image processing and display to artificial intelligence and machine learning algorithms used to process (POL)SAR data are linear
+and additive in nature. 
+This linear and additive nature is manifested, for example, in a
+large number of algorithms in the field of computational intelligence which make use of
+MSE as an objective function, as well as the extensive use of variance and
+contrast in digital image processing. 
+Thus it is very exciting to derive homoskedastic models for this heteroskedastic data
+  so that the benefits of an additive and homoskedastic statistical estimation framework can be explored.
 
-The motivation for this research then is to reconstruct high-quality grey-scale images from speckled single channel SAR data, and to visualise as colourful images the despeckled multi-channel POLSAR data.
-In order to do so, the speckle effects need to be removed as much as possible from original (POL)SAR data.
+%Specifically, 
+%  this thesis focuses on providing a solution for the
+%                dual-problem of: 1) developing scalar and
+%                representative statistical models for the
+%                multi-dimensional and inter-correlated POLSAR data and
+%                2) establishing at consistent measures of distance for both
+%                SAR and POLSAR data which allow the benefits of the
+%                homoskedastic statistical estimation framework to be
+%                demonstrated.
 
-Due to the random nature of speckle, speckle filtering has been put into the context of statistical estimation theory, which comprises statistical modelling and validation, estimator design and development as well as evaluation of different estimators' accuracy.
-This proposed research project focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
+\section{Research Objective}
+
+%The research objectives 
+%helps to 1) define and focus your effort, 2) identify variables to be measured 3) identify steps to be performed 4) establish the limits of the study 5) avoid any data collection, argument development that is not necessarily needed.
+%Should be stated in action verbs specific enough to be measurable. Avoid vague, non-active verbs which is hard to evaluate if the objectives have been achieved.
+%4. Research methodologies (How the research is/was/will be conducted)
+%5. Result interpretation and evaluation (describe how the results is expected to look like, how they are going to be evaluated
+
+%How do others solve this problem?
+%Briefly What are their solution? what problems they cannot yet solve?
+While
+                the statistical model for SAR is quite well understood,
+the
+                understanding of the POLSAR statistical model trails behind.
+The
+                complex POLSAR data have been statistically modelled as
+                following the complex Wishart distribution, which
+                apparently is multi­dimensional, complex and
+                un­intuitive.
+There
+                has been a few published scalar statistical models for
+                POLSAR, but none of them fit the dual criteria of being
+                highly representative of the data and at the same time
+                lead to scalar discrimination measures.
+There
+                are also a few POLSAR discrimination measures proposed,
+                but all of them are based on the likelihood test
+                statistics, which so far have only shown to be based on an
+                asymptotic distribution.
+
+ In
+                another thread of study, to combat the negative
+                impacts caused by multiplicative and heteroskedastic
+                properties for SAR data, experienced researchers of the
+                field have developed numerous ingenious ways to tackle
+                these issues.
+For
+                example, when the sense of subtractive distance is not
+                consistent for SAR data, the ratio is proposed as its
+                discrimination measure \cite{Rignot_1993_TGRS_896}.
+Or
+                when the MMSE criteria is not very suitable to evaluate
+                SAR speckle filters, other criteria likes radiometric
+                preservation and speckle suppression power evaluation
+                are employed. 
+Unfortunately,
+                these counter­intuitive measures are not very popular
+                outside the SAR community, and newcomers to the field
+                are frequently found being trapped in these pitfalls.
+
+%In what way is your solution different ? What is the novelty in your approach and hence solution?
+Some of the problems described above have been studied using different approaches in the literature.
+However, the set of problems has not been presented in a systematic manner nor with a strong underlying foundational theory.
+In
+                this thesis, the statistical model for the determinant
+                of the POLSAR covariance matrix is proposed and
+                validated.
+Out
+                of many different possible scalar projections of the
+                multi-dimensional data, the proposed projection is
+                highly representative.
+When the dimension number is collapsed to one, the
+                special case of the proposed model matches perfectly
+                with the commonly used statistical model for SAR
+                intensity.
+Furthermore,
+                the proposed statistical model also leads to the
+                derivation of existing as well as the newly proposed
+                discrimination measure: determinant-ratio which is the
+                generalized multi dimensional version of the widely used
+                SAR intensity ratio.
+
+ Another
+                novelty of the contributions in this thesis comes from the systematic
+                treatment towards the problem of statistical estimation
+                of heteroskedastic SAR data.
+While
+                many different ways to combat the negative impacts
+                caused by multiplicative and heteroskedastic properties
+                for SAR data have been proposed over the years, they have often been
+                handled in a piecemeal manner.
+Here,
+                a systematic homoskedastic framework of statistical
+                estimation is developed, where not only homoskedastic
+                statistical models are proposed, the impacts of
+                homoskedasticity on estimator development and
+                performance evaluation of statistical estimators is also
+                studied.
+This
+                comprehensive treatment not only explains why the
+                original SAR data requires special treatment very
+                different to the common practice of computational
+                sciences, 
+it
+                also allows thorough and unique discussion, for example on
+                evaluating different evaluation criteria for statistical
+                estimators.  % ;-)).
+And
+                since the POLSAR data can be considered as the multi
+                dimensional extension of traditional SAR data, these
+                treatments are shown extensible towards POLSAR data
+                which is definitely yet another novelty.
+
+%precise problem statement
+With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
+That is
+                this thesis focuses on providing a solution for the
+                dual-problem of: 1) establishing scalar and
+                representative statistical models for the
+                multi-dimensional and inter-correlated POLSAR data and
+                2) providing consistent measures of distance for both
+                SAR and POLSAR data which allow the benefits of the
+                homoskedastic statistical estimation framework to be
+                demonstrated.
+
+\section{Research Methodology}
+%To achieve the stated objectives, what is your plan of attack? Describe How your actions are to be conducted? How your argument is developed?                
+%****IVM Hai, I removed this sentence. I don't think it adds anything useful...
+%The bottom up development of the research effort for this long-term study, admittedly is not as straightforward as the top down layout of the stated objectives.
+The
+                overall research methodology is to first focus on the
+                simpler one dimensional SAR domain, and then extend the
+                obtained insights and processing techniques 
+towards the more complex multi dimensional
+                POLSAR data domain.
+%***IVM   what OPEN LOOP??? I'm not sure that this is an open loop!! Can't you just say "This is achieved when....."
+This
+                is achieved as the theoretical models for
+                POLSAR are shown to be the multi dimensional extensions of
+                the one dimensional SAR model.
+
+The
+                development of these models are based on
+                rigorous statistical mathematics transformations. % and theory. 
+The
+                assumptions used are minimal and widely
+                acknowledged for this type of data.
+Then, the variable change theorem is applied to derive the statistical model for these transformed observables. %log-transformed SAR data.
+The
+                derived theoretical models are validated against
+                real life data.
+And
+                the imperfect conditions found in practice (in
+                comparison to the theoretical assumption) are also
+                investigated, and the models are shown to be robust, capable of
+                handling these imperfections.
+The
+                theoretical properties of these models, as well as many
+                of their benefits, are also proven using rigorous
+                mathematical principles.
+
+%The theoretical statistical models are derived from the commonly used statistical models for SAR and POLSAR.
+%Then, as mentioned above, the variable change theorem is applied to derive the statistical model for log-transformed SAR data.
+%A similar methodology is then followed for the multi-dimensional POLSAR data.
+%The POLSAR theoretical foundation used is the Complex Wishart distribution applicable on the covariance matrix.
+%In this thesis, the statistical model for the determinant of this covariance matrix,
+%  is derived from this foundation.
+%The variable change theorem is again applied to derive the discrimination measures from these derived basic models.
+
+As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering has been put into the framework of statistical estimation.
+For such application, the research methodology is based extensively on the statistical estimation framework. 
+The framework consists of three stages:
+
+%***IVM Hai, I changed your list type to make it look better
+\begin{description}
+\item{Stage 1:} data statistical analysis. 
+We propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
+The statistical models built after such a transformation are validated against real-life data.
+\item{Stage 2:} predictor and estimator development.
+Various statistics-based computational intelligence and/or signal processing methods are to be applied. 
+\item{Stage 3:} results analysis and performance evaluation.
+Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
+\end{description}
+
+\subsection{Statistical Estimation Framework for (POL)SAR data}
+
+Even though the research topic seems to spread across different sub-fields, the common framework that binds them all together is the application and development of statistical estimators.
+For speckle filtering, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
+For the problem of target detection or classification,
+  it is the estimation of the likelihood that the target belongs to a certain category.
+
+Thus a significant portion of this research effort focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
 The benefits of such a framework are many fold.
-Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for a real expensive satellite imagery.
+Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for highly expensive satellite imagery.
 Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
 Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.
+For example, allowing different authors to compare results quantitatively.
 
-For single-channel SAR images, our initial observations and experiences indicate that the community has been oblivious to many of the negative effects of statistical heteroskedasticity manifested in the original intensity and amplitude data.
-In Chapter 4, it is shown that logarithmic transformation can convert SAR's multiplicative stochastic process into a better-understood additive noise model.
-Thus, the additive-noise domain indicates homoskedasticity as well as offers a consistent sense of distance and variance.
-
-%\subsection{The Research Questions}
-
-Figure 
-	\ref{fig:residual_as_noise} 
-shows that: when compared with optical remote sensing images, SAR data suffers from serious degradation.
-%SAR data suffers from stochastic speckle phenomena, which poses numerous challenges in human capabilities of understanding SAR images.
-%Years of research in SAR signal processing has resulted in various speckle filters, all of which aims to produce better visually de-speckled gray images from the degraded SAR data.
-The degraded SAR data almost invariably requires a treatment of speckle filtering to yield more comprehensible images.
-Recent advances in Polarimetric SAR (POLSAR) have produced multiple channels of SAR data, which are conceptually similar to the multiple channels found in colourful optical images.
-However, the stochastic effects of speckle on multivariate and correlated data is ever more eminent.
-The key proposed research question is how to reconstruct clean, colorful visualization of Polarimetric Information from the new but speckled PolSAR satellites.
-Towards the end of the research project, an optional extended question shall be how this extra de-speckled polarimetric information may help in the tasks of target detection and classification.
-
-The main research question is conceptually divided into the following subsidiary questions to investigate:
-% and project phases include. 
-%1. How to simulate SAR and Polarimetric SAR data (quick pass, no lit review)
-\begin{enumerate}
-\item For single channel SAR data, the main aim would be how best to produce and quantitatively evaluate the de-speckled gray images. 
-The main contributions could be that: for the first time, the PDF for the underlying back-scattering coefficient appears to be estimate-able, at least in the log-transformed domain. 
-It is hoped this new knowledge may help in developing better speckle filters, especially those filters of \textit{Maximum a Posteriori} (MAP) nature.
-Another possible contribution could be: how the homoskedasticity in the log-transformed domain could help to consistently evaluate the performance of different speckle-filters being applied on heterogeneous spatial variations.
-%2.
-how the PDF of underlying back-scattering coefficient, in the log-domain, could be estimated and how this could help in improving the performance of the Maximum A Posteriori class of speckle-filters.
-%The topic and the concept itself is a new topic
-\item For multi-channel SAR data, the main aim would be to produce a smoothed and colourful visualisation of Polarimetric information. 
-The main contributions would be a methodology to extends the results of single-channel SAR speckle filtering towards the issue of estimating the off-diagonal elements in polarimetric covariance matrix.
-Another fundamental contribution could be: how to model, simulate and visualize the multivariate and correlated channels in POLSAR data.
-\item The third portion of this project is to investigate how full polarimetric information could be reconstructed from partial polarimetry modes. 
-The main aim of this section is to fill the gap between practical dual-polarimetric implementations and theoretical established full polarimetric results. 
-%The practical application is synchronized with current satellite hardware deployments and trade-offs.
-\item An optional collaborative portion is to investigate how the extra information in different polarimetric modes may help in the task of target detection and classification. 
-The main aim of this stage is to demonstrate the capability of (partial) polarimetric information over traditional single-channel SAR data.
-%and also to evaluate the trade-off between higher resolution offered by partial polarimetric architecture and the more complete full polarimetric mode.
-%Algorithms may have been and will also be proposed to tackle these issues, but the need to evaluate the algorithms requires rigorious ground-truthed data.
-\end{enumerate}
-
-%For the topic of target (ship) detection and classification, we notice that the use of partial polarimetry will provide extra polarimetry data without incurring loss in spatial resolution.
-%We proceed to hypothesize that: partial polarimetry will lead to improved target (ship) detection and classification accuracy in comparision to traditional SAR data.
-%Experiments can be carried out by capturing polarimetric SAR remote sensing imagery and ground truth data which is provided via the ships' locational identification data.
-%Automatic Identification System (AIS), which normally supplements marine radars, is a standard ship tracking system for identifying and locating floating vessels.
-%Empirical evidence can be obtained by applying traditional ship detection and classification on traditional and polarimetric data concurrently, and the results are to be compared.
-%Besides the empirical evidences that we plan to obtain, we hope that once our work on statistical modelling of partial polarimetry has taken shape, the hypothesis can be rigorously proven by statistical mathematics.
-
-\section{Objectives, Methodology and Contributions}
-
-\subsection{The Research Objectives}
-
-The purpose of this section is to illustrate the objectives in developing computational frameworks for Stochastic Polarimetric Data. 
-Assuming the framework will be implemented successfully, this section also describes its academic contributions as well as its projected practical benefits.
-% for the industry.
-%Also the academic contribution as well as practical benefits, assuming the frameworks is developed that meet the requirements, is to be described.
-
-%Even though the research topics appears segmentable into different sub-fields, the fact is that all of them can be considered as an application of statistical estimators.
-Even though the research topic spreads across different sub-fields, a common thread that bind them all together is the application and development of statistical estimators.
-For single channel SAR, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
-In the case of multi-channel SAR, it is the estimation of a target's polarimetric signature, being measured in multiple channels simultaneously and stochastically.
-And for the problem of target detection or classification, it is the likelihood estimation that the target belongs to a certain category.
-% which is then fed into a decision rule to make a last judgement.
-
-Thus, the main objective of this research is to derive effective statistical estimators for the reconstruction and classification of the underlying target information in speckled SAR and POLSAR data.
-
-In order to design and evaluate effective estimators, we centre our effort on developing a good computational framework. 
 The objective of such framework being:
 \begin{enumerate}
-\item To build, develop and validate statistical models for different stochastics processes that are inherent within the polarimetric SAR domain.
+\item To build, develop and validate statistical models for different stochastic processes that are inherent within the polarimetric SAR domain.
 \item To allow easy, fast and repeatable simulations and experiments of various stochastic processes in designed, focused, as well as broad-based scenarios.
@@
 \item Ultimately, to allow development of better and more accurate estimators, whose results can be verified: not only qualitatively on real life images, but also quantitatively through rigorous simulations.
-%quantitatively in rigorious simulations and qualititatively in real measured data.
 \end{enumerate}
 
-The possible benefits of the research project are:
+The possible benefits of this computational framework are:
 \begin{enumerate}
@@
 This, in turn, allows for design and development of better estimators.
-\item Our research to find evidence, and hopefully rigorous proofs, supporting the advantages of (partial) polarimetric SAR implementations over conventional SAR data also yields high practical interest.
-%Our research to find evidence, and hopefully rigorious proofs, supporting the advantanges of A over B also yields high practical interests.
-%Our intended research to address a pressing practical trade-off, between a choice of better resolution and an option of complete polarimetric information, also yields high practical interests.
-Apparently the topic has also received a fair share of attention and supports from EADS \footnote{This PhD research project is run in conjunction with EADS and has an EADS co-supervisor}.
-\item The investigative research of ship monitoring using polarimetric SAR satellites is also apparently of high interest to EADS, as evidenced by their own in-house investigations.
 \end{enumerate}
@@
 With fast and repeated experiments, the framework allows one to not only compute a single performance value on a single experiment, but also to analyze the whole behaviour of such performance measures over repeated stochastic simulations.
-\item For the sub-topic of single-channel SAR imagery, we believe an estimate for the PDF of the true underlying coefficient will be an unique research result.%is the first of such kind.
-\item For the multi-channel POLSAR sub-field, we believe our proposed approach in speckle filtering of the off-diagonal elements in the polarimetry covariance matrix is also a novelty.
-\item For the specific application of ship detection and classification, we believe our approach of evaluating the performance of higher-resolution and partial polarimetry modes using ground truth from AIS data is also unique.
+\item Thus the computational framework provides significant help in deriving new performance evaluation criteria for statistical estimators.
 \end{enumerate}
@@
 
-As a testament on the effectiveness of this research, the work discussed in this report was published as two separate papers in 2010, at ISCCSP\cite{Le_2010_ISCCSP} and ACRS\cite{Le_2010_ACRS}.
+\subsection{Data Collection}
 
-\subsection{Research Methodology}
-
-As the speckle phenomena is stochastic in nature, speckle filtering has been put into the framework of statistical estimation.
-This project's research methodology will be based extensively on a statistical estimation framework. 
-The framework consists of three stages:
-
-\begin{enumerate}
-\item Stage 1: data statistical analysis. 
-We aim to propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
-The statistical models built after such a transformation are validated against real-life data.
-\item Stage 2: predictor and estimator development.
-Various statistics based computational intelligence and/or signal processing methods are intended to be applied. 
-\item Stage 3: results analysis and performance evaluation.
-Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
-%Stochastic simulation based experiments with evaluation being both through consistent quantitative measures and visual qualititative comparisions from real captured imagery. 
-\end{enumerate}
-
-\subsubsection{Data Collection}
-
-We have used, and plan to keep using simulated data extensively. 
-There appears to have a number of advantages in using simulated experiments:
+This work has made extensive use of simulated data, which have a number of advantages listed below:
 \begin{enumerate}
@@
 This allows smaller data sets to be generated and analysis can become faster and more accurate.
-%Experiments can be carried out on smaller scale data, with validation from real images to come later
 \item Contrary to real-life images where underlying coefficients are to be estimated, ground truth is readily available in simulated experiments.
 \item Quantitative evaluation is possible not only via a single experiment on a single real-image but via repeated stochastic runs. 
-\item Thus not only single values of mean or mean-squared-error is to be evaluated. 
+\item Thus not only single values of mean or mean-squared-error are to be evaluated. 
 As the whole response PDF is available, statistical bias or heteroskedasticity can also be reported.
-%But also statistical bias or heteroskedasticity can be estimated as the whole pdf distributions are available. 
 \end{enumerate}
@@
 Besides simulated  data, we have gathered a large amount of real-life data.
-The table below lists data made available to us, courtesy of EADS Innovation Works Singapore. %(TODO:RECOLLECT)
+Table \ref{tbl:collected_data} lists data made available to us, courtesy of EADS Innovation Works Singapore.
 
@@
 \end{tabular}
-
+\caption{Collected imagery data}
 \label{tbl:collected_data}
-\caption{Collected imagery data}
 \end{table}
 
-Furthermore, for the task of ship detection and classification using polarimetric data, we intended to capture ship's location using readily available Automatic Identification System (AIS) systems. 
-The data collection strategy will be synchronized tasks of satellite imagery and AIS data capture.
-AIS data, in a close-to-port environment, will be used as ultimate ground truth to evaluate different target detection and classification algorithms.
+\subsection{Result Interpretation and Evaluation}
 
-\subsubsection{Result Interpretation and Evaluation}
+%How do you evaluate your solution? 
+The
+                achievement of the research objectives stated above not only provides
+                novel solutions to the stated problem, it also
+                illustrates the advantages and beneficial implications
+                of the proposed theory.  
+Compared
+                to existing published techniques, the advantage of the
+                proposed theory is qualitative, which does not require
+                direct quantitative comparisons.
+Instead
+                a straightforward binary evaluation would be sufficient.
+For
+                the POLSAR scalar model, its advantages are that not
+                only does it lead to consistent discrimination measures, it
+                also generalizes the traditional model for one
+                dimensional SAR intensity.
+For
+                the homoskedastic models, their advantage is that they
+                enable an additive and homoskedastic statistical
+                framework, which is not only capable of overcome various
+                negative impacts of heteroskedasticity, but also results
+                in a single better evaluation criteria that can combine
+                and represent many different existing performance
+                criteria.
 
-Simulated experiments allows evaluation of estimators against ground-truth.
-Errors can be quantitatively analyzed and methods to reduce such errors can be developed.
-Thus simulated experiments could produce quick results, which may provide faster analysis and further insights for developing more accurate estimators.
+To validate the theoretical models,  real-life data are used in this work.
+Specifically, estimated theoretical PDFs are plotted against the histogram of real data,
+  and a good visual match indicates a good validation.
+In cases where theoretical PDF cannot be derived, simulated data are then generated
+  and their histograms are matched against real-life practical data for validation.
 
-Practically in the end, all estimators would always need to be applied on real images.
-Contrary to experiments on simulated data, experiments on real images can only be compared qualitatively.
-This however, is critical and will always be used in our investigations.
-The reason is that this helps to guard against any systematic errors in the used assumptions and approximations made in developing the theoretical models.
+%***IVM This was all said before...
+%Simulated experiments allows evaluation of estimators against ground-truth.
+%Errors can be quantitatively analyzed and methods to reduce such errors can be developed.
+%Thus simulated experiments could produce quick results, which may provide faster analysis and 
+%further insights for developing more accurate estimators.
+
+To evaluate the models’ application in statistical estimation framework, a practical point of view is adopted.
+Practically, all estimators would eventually need to be applied on and work for real images.
+Contrary to experiments on simulated data, experiments on real images often can only be compared qualitatively.
+This however is critical and will always be included in our investigations.
+The reason is that this helps to guard against any systematic errors in the various assumptions and approximations made in developing the theoretical models.
 Towards that end, real-data can help to build and validate statistical models.
 
-%In fact, we could build and validate statistical model for all elements of POLSAR data.
-%One steps further and we could demonstrate the methodology for target detection and classification in dual-pol data.
-%The original results in reconstruction from CP to FP could be revised and evaluation may be on estimates of Entropy, Polarization angle, Anisotropy (Cloude).
+\section{Research Contributions}
+% How do you know if the problem is solved?   State your research objectives
+Interestingly, the dual-problem stated above are found to have a single solution.
+They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
+  which is multidimensional, inter-correlated and heteroskedastic
 
-%We could also go further and build a model for simulation of POLSAR images.
-%Stokes matrix can uniquely describe covariance matrix (CP).
-Thus dual-pol data could be visualized as a color image, and a color image could be used to simulate CP data?
-(Simulation).
-Math: stokes vector to degree of polarization, and two angles!
-map that to HSV colors.
-%This study would also help to identify pdf() rules for polarized light parameters being: degree of polarization, polarization angles.
-On way to remove speckle is multi-look processing.
-The effects of multi-look as biased estimation of these parameters will be discussed.
-The advanced way is bias-correction.
-Biasness can be investigated by simulation.
-A more prolonged study is to see the simulate pdf() (additive!) and match that with real data for model identification (ignore this!).
-Alternatively statistical analysis of off-diagonal Covariance matrix elements.
-Speckle suppression algorithms can be developed.
-Evaluation is hard at this point.
-%Should a review of target decomposition is needed see (Unal,2009,PIER).
-%One can change polarization basis to circular polarizations (see Boulbry,2007,ProcSPIE). 
-%decomposition and compact polarimetric target decomposistion
-
-%To demonstrate the use of partial polarimetry for target detection and classification tasks, we could proceed with either approach.
-%The first approach being: first full polarimetric information is to be reconstructed from partial polarimetry data.
-%Then standard full polarimetric target detection and classification techniques can be applied on synthesized data.
-%Read Chapter 3 for our published work in extending the reconstruct-ability of full polarimetric information from partial polarimetry data to urban and man-made areas.
-%The second approach would be to invent a totally new target detection algorithm making use of the fact that partial polarimetric data also contains certain basic information about the target's polarimetric signature (see partial polarimetry section in Chapter 2).
-
-\subsection{Theoretical and Practical Contributions}
-
-For SAR data, the main focus is on niches areas like evaluation of filters, estimate of PDF, new filter?
-For PolSAR data, the main focus is more fundamental: investigation and modelling of PolSAR data channels. 
-The approach is to start from simulation and ENL estimation in multi-variate extension of Gauss Markov theorem, 
-new filters can be developed, initially with limited assumptions in modelling, and is evaluated against an evaluation protocol.
-Assumptions are made and tested in the process of evaluation of PolSAR speckle filter. 
-Valid assumptions are then checked against mathematical formula and transformations.
-
-The methodology in analysing multi-channel Polarimetric SAR data is to based on target decompositions.
-The multi-variate data is decomposed into conceptually and physically independent quantities and analysis is conducted on them individually!
-Another possibility is to find a consistent distance measure from the multi variate, multi-dimensional SAR data.
-This distance measure would be useful in the task of target detection from a randomized background.
-It could also be useful in land cover classification as well as change detection fields of PolSAR
-
-We believe that the main focus of this research, partial polarimetric speckle filtering, has the following advantages:
+Specifically, the following sub-objectives are to be achieved
 \begin{enumerate}
-\item The topic and the concept itself are newly developed and have just recently being introduced into the community.
-\item Compared to full polarimetric data, partial polarimetry is much more compact.
-Yet it still exhibits the same multi-variate correctional statistics properties. 
-\item The practical application is synchronized with current satellite hardware deployments and trade-offs.
+\item                 To derive scalar and representative statistical models
+                for the multi-dimensional and inter-correlated POLSAR
+                data.
+                \begin{enumerate}
+                \item \label{itm:polsar_model} To derive a scalar statistical model for the
+                POLSAR observable, being the determinant of the
+                covariance matrix.
+                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
+                the observable being modeled 
+                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
+                that when the multi-channel POLSAR data is collapsed
+                into the traditional one-channel SAR data, this
+                determinant is transformed into the representative SAR
+                intensity.
+                \item \label{itm:polsar_validation} To validate the model against practical real-life
+                captured POLSAR data.
+                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
+                processing technique is extensible towards POLSAR data
                 \end{enumerate}
-
-The possible benefits of our proposed research project are:
+\item                To derive homoskedastic statistical models for the
+                heteroskedastic (POL)SAR data. 
                 \begin{enumerate}
-\item Practical benefits
+                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
+                the original domain and logarithmic transformation
+                can convert this into a homoskedastic model.
+                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
+                the multi dimensional POLSAR as well as for the one
+                dimensional SAR data.
+                \item \label{itm:sar_validation} To validate these statistical models against both
+                practical SAR and POLSAR data
+                \item To illustrate the beneficial applications of these
+                statistical models. Specifically:
                 \begin{enumerate}
-\item The computational frameworks allow for faster, quicker and more focused experiments.
-Often a point can be proven or rejected by designing and implementing an appropriate computational experiment.
-\item The framework allows for easier analysis and allows for more insight to be gained in an estimator's performance. This in turn allows for the development of better estimators.
-\item Our research topic for partial polarimetric SAR has high practical interest, addressing a pressing practical trade-off between the better resolution in partial modes versus the more complete but coarser resolution in theoretical full polarimetry.
-Apparently the topic also generated practical interest from industry, i.e. from EADS.
-\item The investigative research of ship monitoring using polarimetric SAR satellites is also apparently of high interest to EADS, as they are themselves working in this area.
+                \item \label{itm:filter_vicious_circle} To show how the consistent sense of variance
+                helps break the vicious cycle in the problem of SAR
+                speckle filtering: a new statistical test for
+                homogeneity and a new speckle filter is derived.
+                \item \label{itm:log_mse} To show how the consistent sense of subtractive
+                distance helps in the problem of evaluating (POL)SAR
+                speckle filters: the log-MSE is proposed to combine the
+                evaluation of radiometric preservation and speckle
+                suppression power.
                 \end{enumerate}
-\item Academic benefits
-\begin{enumerate}
-\item The computational framework allows for quantitative evaluation of estimators.
-And with fast and repeated experiments, the framework allows the computation of not only a single performance counter value on a single experiment, but also allow the full distribution of such performance over repeated stochastic simulations to be inspected.
-\item For our research topic in the SAR community, we believe that obtaining an estimate of the true underlying PDF is a first of such systems.
-\item For multi-channel POLSAR, we believe our approach to tackle speckle filtering of off-diagonal elements in polarimetric covariance matrix is also a novelty.
-\item In the topic of target (ship) detection and classification, we believe our approach of evaluating the trade off between higher-resolution and partial polarimetry using AIS as ground truth is also unique.
                 \end{enumerate}
@@
 
+In summary, the first main objective is to derive a scalar and representative statistical model for POLSAR data.
+%The theoretical foundation is the commonly agreed Circular Complex Normal distributions proposed in \cite{Goodman_JOptSocAm_76}. %***IVM you need a reference here!!
+%Theory development is based on applying the statistical variable change theorem on the proposed scalar observable.
+%The theoretical model is validated by matching the functional PDF or the simulated histogram with real-life captured data.
+The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
+This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
+%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
+%  it also results in a homoskedastic statistical model.
+%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
+%After these models are validated against practical data, their beneficial applications are further explored.
+To combine these two seemingly disconnected threads of research, the above results for SAR are extended to POLSAR,
+  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.%***IVM I changed "version" to "superset" in the sentence above.
+Please check if you are comfortable with that change, and if not, change it back!
+Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
+%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
+%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives.
+There is no need to re-emphasize the objective if the write-up is clear)
+
 \section{Organisation of the Thesis}
-The rest of this thesis is organized into 5 chapters, as follows:
+The rest of this thesis is organized into five chapters, as follows:
 The next chapter will survey the related publications
-  and state-of-the-art techniques in modeling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
+  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
 It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
-Through these discussion, the need for a homoskedatic and scalar model for the multivariate and heteroskedastic polsar is brought forward.
+Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
 
-The heart of the thesis lies in chapters \ref{chap:sar} and \ref{chap:polsar}.
-While chapter \ref{chap:sar} presents the initial homoskedastic model for SAR data, 
-chapter \ref{chap:polsar} illustrates the more recent and more generic model for POLSAR.
-Chapter \ref{chap:polsar} also specifically describes how the initial model for SAR can be considered as a special case of the POLSAR model.
+%\section{Research Contributions}
 
-Chapter \ref{chap:applications} presents several of our published techniques in handling both SAR and POLSAR data.
-Theses techniques can all be considered as applications of the theoretical model presented in chapters \ref{chap:sar} and \ref{chap:polsar}.
-Demonstrated applications include, but the possibilities are not limited to: clustering algorithms, speckle filtering techniques or a novel methodology to evaluate (POL)SAR speckle filters.
-Finally, the contribution of the thesis is discussed in the conclusional chapter \ref{chap:conclusions}.
+%1 show that the results is not only new but also useful
+%2 let the reader read the contribution and says: “gosh, if they can really deliver this, that’s exciting; I’d better read on” 
+%new theory or hypotheses, writers will need to explain shortcomings in existing theories.
+%new solution, writers will need to explain 1) existing problems and clarify how their solutions solve these problems 2) they also need to compare and contrast a range of alternative solutions and explain why their solution is the best among these alternatives.
+%new territory, writers need to make a case for why this new territory is important to study and show that it has been overlooked by previous research.
+%new methodology, then writers need to 1) critique the methods of previous studies (or characterize them as inconclusive) and 2) explain how they will address these flaws.
+
+%Show that you deliver on the objectives 
+%****IVM   Hai, again I've deleted this sentence because it is slightly negative:
+%Even
+%                though there are small differences between the bottom up
+%                development of the research efforts and the top down
+%                stated objectives, the research results of each section
+%                contribute to the achievement of the objectives.
+%Specifically,
+The heart of is thesis contains several contributions which meet the stated objectives.
+                Chapter \ref{chap:sar} begins by by highlighting that SAR
+                data are heteroskedastic in the original domain, whereas
+                logarithmic transformation converts this into a
+                homoskedastic model (Research Contribution \ref{itm:log_transform}). 
+It
+                also drives consistent and homoskedastic measures of
+                distance for the one dimensional SAR data (Research Contribution \ref{itm:sar_measures_distance}).
+These
+                models for SAR are then validated against real-life
+                practical data (Research Contribution \ref{itm:sar_validation})
+
+ Chapter
+                \ref{chap:polsar} then derives several scalar statistical models for the
+                determinant of the POLSAR covariance matrix (Research Contribution \ref{itm:polsar_model}) and
+                shows that this is heteroskedastic in the original
+                domain as well as homoskedastic in the log-transformed
+                domain (Research Contribution \ref{itm:log_transform}).
+It
+                also derives the heteroskedastic discrimination measures
+                (Research Contribution \ref{itm:polsar_discrimination_measure}) as well as several homoskedastic measures of
+                distance for the data (Research Contribution \ref{itm:sar_measures_distance}).
+Then
+                the models for SAR are shown to be a special case of
+                the proposed models for POLSAR (Research Contribution \ref{itm:polsar_include_sar}) and finally it
+                validates these proposed models (Research Contribution \ref{itm:polsar_validation})
+
+ The
+                beneficial applications of these models is presented in
+                chapter \ref{chap:applications}, where the consistent sense of variance
+                property helps to break the vicious cycle in SAR
+                speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
+It
+                also shows how MSE can be again applicable in the
+                additive and homoskedastic domain to evaluate SAR
+                speckle filters (Research Contribution \ref{itm:log_mse}).
+An
+                example of extending existing techniques from SAR to
+                POLSAR is also demonstrated in this chapter where the
+                MSE evaluation criteria is also shown capable of
+                evaluating POLSAR speckle filters (Research Contribution \ref{itm:extend_sar_to_polsar}).
+Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.
+
+%The heart of the thesis lies in chapters \ref{chap:sar} and \ref{chap:polsar}.
+%While chapter \ref{chap:sar} presents the initial homoskedastic model for SAR data, 
+%chapter \ref{chap:polsar} illustrates the more recent and more generic model for POLSAR.
+%Chapter \ref{chap:polsar} also specifically describes how the initial model for SAR can be considered as a special case of the POLSAR model.
+%
+%Chapter \ref{chap:applications} presents several of our published techniques in handling both SAR and POLSAR data.
+%Theses techniques can all be considered as applications of the theoretical model presented in chapters \ref{chap:sar} and \ref{chap:polsar}.
+%Demonstrated applications include clustering algorithms, speckle filtering techniques and a novel methodology to evaluate (POL)SAR speckle filters.

### 2013-07-24 2/literature_review.tex
updated for Ian changes

@@
 \chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2
-
-\section{The Stochastics and Multivariate Nature of POLSAR data}
-
-\subsection{The Stochastic nature of SAR data}
-
-\subsubsection{ Traditional Single-Channel SAR and the Speckle phenomena}
-
-Wikipedia to be edited strongly.
-Speckle noise is a granular noise that inherently exists in and degrades the quality of the active radar and synthetic aperture radar (SAR) images.
-Speckle noise in conventional radar results from random fluctuations in the return signal from an object that is no bigger than a single image-processing element.
-It increases the mean grey level of a local area.[1]
-Speckle noise in SAR is generally more serious, causing difficulties for image interpretation.[1][2] It is caused by coherent processing of backscattered signals from multiple distributed targets.
-In SAR oceanography, for example, speckle noise is caused by signals from elementary scatterers, the gravity-capillary ripples, and manifests as a pedestal image, beneath the image of the sea waves.[3][4]
-
-\subsubsection{The Stochastic nature of SAR  and SAR speckle filtering }
-
-The stochastic nature SAR arises from the speckle phenomena.
-As SAR speckle seriously hinders the interpretation and understanding of SAR images,
-  its effect are routinely reduced through a speckle filtering process.
-SAR speckle filtering is the process to suppress the effect of speckle noise SAR images for easier intepretation.
+\label{chap:lit_survey}
+
+This chapter 
+reviews the published literature for SAR and POLSAR data processing.
+Specifically, its first section describes the multi-dimensional and stochastic nature of the POLSAR data.
+The second section then illustrates the different approaches that have been published to address the grand challenge of modelling, processing and ultimately understanding these types of data.
+
+\section{The Stochastic and Multivariate Nature of POLSAR data}
+
+\subsection{The Stochastic Nature of SAR data}
+
+%\subsubsection{ Traditional Single-Channel SAR and the Speckle phenomena}
+
+The stochastic nature of SAR data arises due to the process of SAR image formation.
+Specifically, since one SAR resolution cell is very big in comparison to the radar wavelength, it normally consists of many elementary scatterers.
+The data point of each SAR pixel then arises from the combined interference effect of the backscattered waves from these different scatterers.
+This effect causes natural variation in SAR intensity image even when the underlying scene is highly homogeneous.
+
+SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
+  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
+The random nature of the SAR data arises
+  due to the unknown and varying location, height and thus distance of each elementary scatterer;
+  which, in turn, generates random phases in their back-scattering responses.
+Assuming the number of these elementary back scatterers is sufficiently large,
+  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
+Consequently the interference of these randomly phased responses can be considered as
+  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
+Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
+  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
+Their probability density functions (PDF) are given as:
+
+\begin{equation}
+\label{eqn:SAR Real and Imaginary Components PDF}
+\caption{eqn:SAR Real and Imaginary Components PDF}
+pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
+\end{equation}
+
+It can then be shown that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution.
+Subsequently the SAR intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of a negative exponentially distributed random process. The PDFs of these two properties can then be expressed as:
+
+%\begin{eqnarray}
+%pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
+%pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
+%\end{eqnarray}
+\begin{equation}
+\label{eqn:SAR Amplitude PDF}
+\caption{eqn:SAR Amplitude PDF}
+pdf(A) = \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Intensity PDF}
+  \caption{eqn:SAR Intensity PDF}
+pdf(I) = \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
+\end{equation}
+
+%\subsubsection{The Stochastic nature of SAR  and SAR speckle filtering }
+
+%The stochastic nature SAR arises from the speckle phenomena.
+As SAR speckle phenomena arises from the stochastic nature of SAR, it seriously hinders the interpretation and understanding of SAR images.
+Speckle noise on SAR images are hence routinely reduced through a speckle filtering process for easier human interpretation and more accurate post-processing.
+%***IVM: Hai, I added "human" before 'interpretation'. Also added the text afterwards, please check that the sense of the edited text is still correct in terms of what you wanted to say.
 
@@
 
-\subsubsection{ Partial Polarimetry and the Stokes Vector}
-
-The dual-polarization modes has been practically and operationally available for quite some time.
-However, partial polarimetry has only recently been investigated in the scientific community. 
-By comparison, 
-	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
-	while full polarimetry measures the same response for two (most of the time orthogonal) polarisation channels.
-Mathematically, the process is modelled as:
+\subsubsection{The polarization property of Electro-Magnetic waves}
+
+The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
+The general solution to these equations is a linear superposition of waves, each having the form of:
+\begin{eqnarray*}
+ \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
+ \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
+\end{eqnarray*}
+where
+	$g$ is any well-behaved function of a dimensionless argument $\phi$,
+	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
+	$\omega$ is the angular frequency (in radians per second), and
+	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).
+
+Because of the divergence between the electric and the magnetic fields, there will be no fields in the direction of wave propagation.
+Thus if we define the z direction as the travelling direction of the EM wave,
+  then both the electric and the magnetic fields are fluctuating in the x,y plane.
+Furthermore, when considering wave propagation, it is conventional that only the electric field vector is described and the magnetic field is ignored since it is perpendicular to the E field and is proportional to it.
+Projecting this vector into x,y directions, we have:
+
+\begin{equation*}
+\vec{E}(z,t) 
+= 
+\left(
+	\begin{array} {c}
+		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
+		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
+		0
+	\end{array}
+\right)
+= 
+\left(
+	\begin{array} {c}
+		\xi_x(t) \\
+		\xi_y(t) \\
+		0
+	\end{array}
+\right)
+\end{equation*}
+where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.
+
+In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
+The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
+This shape is characterized by the formula: 
+\begin{equation*}
+ \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
+\end{equation*}
+where
+	$\Delta \phi = \phi_y^0 - \phi_x^0$
+The formula characterizes what is termed as the polarization ellipse.
+
+The parameters that describe the polarization ellipse are: 
+\begin{equation*}
+\tan (\theta ) = \frac{E_y^0}{E_x^0}
+\end{equation*}
+with
+	$0 \leq \theta \leq \pi/2$. 
+The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
+\begin{equation*}
+\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
+\end{equation*}
+with
+	$0 \leq \Psi < \pi$. 
+The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
+The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
+\begin{equation*}
+\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
+\end{equation*}
+with
+	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$
+
+Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
+Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.
+
+Other parameters includes:
+\paragraph{ Complex polarization ratio }
+This ratio is important in explaining polarization basis changes.
+
+It is defined as:
 \begin{equation}
+\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
+\end{equation}
+
+\paragraph{Jones Vector}
+
+%Let the total wave power:
+%\begin{equation}
+%|E|^2 = (E_x^0)^2  + (E_y^0)^2
+%\end{equation}
+%and phase 
+%\begin{equation}
+%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
+%\end{equation}
+
+The Jones vector is defined as 
+\begin{equation}
+J = 
+\left(
+\begin{array}{c}
+	\xi_x(t) \\
+	\xi_y(t) 
+\end{array}
+\right)
+= \xi_x(t)
+\left(
+\begin{array}{c}
+	1 \\
+	\rho
+\end{array}
+\right)
+\end{equation}
+
+Thus the normalized Jones vector can be given as:
+\begin{equation}
+J = 
+\left(
+\begin{array}{c}
+	\cos(\theta) \cdot e^{i \phi_x^0} \\
+	\sin(\theta) \cdot e^{i \phi_y^0}
+\end{array}
+\right)
+=
+\left(
+\begin{array}{c}
+	1\\
+	\tan(\theta) \cdot e^{i \Delta \phi}
+\end{array}
+\right)
+=
+\left(
+\begin{array}{c}
+	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
+	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
+\end{array}
+\right)
+\end{equation}
+
+The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
+This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
+Its bra-ket notation formula, which is normally used in quantum computation contexts is:
+\begin{equation}
+J = | \Psi \rangle 
+= 
+\left(
+\begin{array}{c}
+	\cos(\theta) \cdot e^{i \phi_x^0} \\
+	\sin(\theta) \cdot e^{i \phi_y^0}
+\end{array}
+\right)
+\end{equation}
+
+By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
+\begin{array}{c}
+ 1 \\
+ 0
+\end{array}
+\right)$, similarly the vertical linear polarized wave: $J_v = \left(
+\begin{array}{c}
+ 0 \\
+ 1
+\end{array}
+\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
+\begin{array}{c}
+ 1 \\
+ 1
+\end{array}
+\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
+\begin{array}{c}
+ 1 \\
+ -i
+\end{array}
+\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
+\begin{array}{c}
+ 1 \\
+ i
+\end{array}
+\right)$
+
+\paragraph{ Stokes Vector}
+
+Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
+The wave coherency matrix is defined as:
+\begin{equation*}
+W_c = \left<
+\left(
+\begin{array}{c}
+ \xi_x \\
+ \xi_y
+\end{array}
+\right)
+\left(
+\begin{array}{c}
+ \xi_x \\
+ \xi_y
+\end{array}
+\right)^{\dagger}
+\right>
+= \left<
+\left(
+\begin{array}{c c}
+ \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
+ \xi_y \xi_x^* 	& \xi_y \xi_y^* 
+\end{array}
+\right)
+\right>
+= \left<
+\left(
+\begin{array}{c c}
+ |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
+ |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
+\end{array}
+\right)
+\right>
+\end{equation*}
+
+The Stokes vector is then defined as:
+\begin{equation*}
+S_t = 
+\left(
+\begin{array}{c}
+ S_0 \\
+ S_1 \\
+ S_2 \\
+ S_3
+\end{array}
+\right)
+=
+\left(
+\begin{array}{c}
+ |\xi_x|^2 + |\xi_y|^2 \\
+ |\xi_x|^2 - |\xi_y|^2 \\
+ 2\Re(\xi_x \xi_y^*) \\
+ 2\Im(\xi_x \xi_y^*)
+\end{array}
+\right)
+\end{equation*}
+
+In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
+\begin{equation*}
+S_t = 
+\left(
+\begin{array}{c}
+ S_0 \\
+ S_0 \cos(2\Psi) \cos(2\chi) \\
+ S_0 \sin(2\Psi) \cos(2\chi) \\
+ S_0 \sin(2\chi)
+\end{array}
+\right)
+\end{equation*}
+
+%It should be noted that: the factor of two before the polarization ellipse's angles indicate the fact that
+%	any polarization ellipse is practical indistinguishable from on rotated by $180^o$ 
+%	or with on with the axis lengths swapped accompanied by a $90^o$ rotation.
+
+At this point, a distinction needs to be highlighted. %explaination is warranted.
+%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
+%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
+In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
+The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
+In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
+As such, the polarization of the waves are normally not fully polarized.
+One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
+%The phenomena can be loosely called wave depolarization.
+%****IVM: Hai, is this your term or is it also used by others for the same thing?
+In that case, it might be good to put a reference here.
+I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.
+
+The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wavelength.
+In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.
+
+%(comment: I think it would be better if you can link the two paragraphs together, such as
+%ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )
+
+\paragraph{Degree of polarization}
+
+Closely related to the Stokes vector is the concenpt of ``Degree of polarization'' $p$, which is a quantity used to describe the portion of an EM wave which is polarized.
+A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
+A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
+Thus $0 \leq p \leq 1$.
+
+Depolarization phenomena are explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
+The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
+If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
+One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.
+
+In fully polarized wave, the following equation holds:
+\begin{equation*}
+S_0^2 = S_1^2 + S_2^2 + S_3^2
+\end{equation*}
+
+In depolarized wave, it becomes an in-equation
+\begin{equation*}
+S_0^2 > S_1^2 + S_2^2 + S_3^2
+\end{equation*}
+
+Then the degree of polarization is defined as
+\begin{equation*}
+p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
+\end{equation*}
+
+In such general case, the Stokes Vector is written as:
+\begin{align*}
+S_t &= 
+\left(
+\begin{array}{c}
+ I \\
+ I p \cos(2\Psi) \cos(2\chi) \\
+ I p \sin(2\Psi) \cos(2\chi) \\
+ I p \sin(2\chi)
+\end{array}
+\right) \\
+ &= I (1 - p)
+\left(
+\begin{array}{c}
+ 1 \\
+ 0 \\
+ 0 \\
+ 0
+\end{array}
+\right) 
++ I p
+\left(
+\begin{array}{c}
+ 1\\
+ \cos(2\Psi) \cos(2\chi) \\
+ \sin(2\Psi) \cos(2\chi) \\
+ \sin(2\chi)
+\end{array}
+\right)
+\end{align*}
+
+Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:
+$I$, the total power of the measured beam is $I=S_0$,
+$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
+$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.
+
+\subsubsection{Full Polarimetry and the Polarimetric Signatures}
+
+This section describes the core concept of POLSAR, i.e. the target's polarimetric signature, 
+	and illustrates why research into partial polarimetry is warranted.
+
+POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
+The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
+\begin{equation*}
+ E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
+\end{equation*}
+%***IVM: Hai, do you need to explain the k & r terms?
+
+Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
+\begin{equation*}
  \left( 
@@
 \left( 
+\begin{array}{c c}
+ S_{HH} & S_{HV} \\
+ S_{VH} & S_{VV}
+\end{array}
+ \right) 
+\left( 
+\begin{array}{c}
+ E_h^{Tx} \\
+ E_v^{Tx}
+\end{array}
+ \right) 
+\end{equation*}
+
+The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
+The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \cite{Sinclair_1950_ProcsIRE}.
+In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.
+
+The matrix can also be ``stratified'' to define the target scattering vector as: 
+\begin{equation}
+  \label{eqn:Covariance Target Vector of Full Polarimetric SAR}
+  \caption{eqn:Covariance Target Vector of Full Polarimetric SAR}
+T_{cv} = \left( 
+\begin{array}{c}
+ S_{HH} \\
+ \sqrt{2} S_{HV} \\
+ S_{VV}
+\end{array}
+ \right) 
+\end{equation}
+or 
+\begin{equation}
+  \label{eqn:Coherence Target Vector of Full Polarimetric SAR}
+  \caption{eqn:Coherence Target Vector of Full Polarimetric SAR}
+T_{ch} = \frac{1}{\sqrt{2}} \left( 
+\begin{array}{c}
+ S_{HH} + S_{VV}\\
+ S_{HH} - S_{VV} \\
+ S_{HV}
+\end{array}
+ \right) 
+\end{equation}
+
+Similar to the reason that Stokes vectors are preferred to Jones vector in wave polarization, 
+	second order statistics of the target scattering matrix are normally preferred.
+The covariance matrix is defined as:
+\begin{equation}
+  \label{eqn:Covariance Matrix of Full Polarimetric SAR}
+  \caption{eqn:Covariance Matrix of Full Polarimetric SAR}
+\tiny{
+C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
+\left( 
+\begin{array}{c c c}
+ S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
+ \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
+ S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
+\end{array}
+ \right) 
+}
+\end{equation}
+while the coherency matrix is defined as:
+\begin{equation}
+  \label{eqn:Coherence Matrix of Full Polarimetric SAR}
+  \caption{eqn:Coherence Matrix of Full Polarimetric SAR}
+\tiny{
+C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
+\left( 
+\begin{array}{c c c}
+ (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
+ (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
+ 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
+\end{array}
+ \right) 
+}
+\end{equation}
+
+Evidently the two matrices are related:
+\begin{equation*}
+C_h = N C_v N^T
+\end{equation*}
+where
+	$N = \frac{1}{\sqrt{2}}
+\left( 
+\begin{array}{c c c}
+ 1 & 0		& 1\\
+ 1 & 0		& -1\\
+ 0 & \sqrt{2}	& 0
+\end{array}
+\right)$
+
+The off-diagonal values in both covariance and coherence matrices are normally complex numbers. 
+Equivalent matrices with all real value entries which carry the same information are called the Mueller and the Kennaugh matrix, which are to be used in forward and backward scattering alignment respectively\cite{Guissard_1994_TGRS}.
+They are defined as the matrix that relates the Stokes matrix of sent and received signals.
+\begin{equation*}
+S_t^{Rx} = K S_t^{Tx}
+\end{equation*}
+
+Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
+\begin{equation*}
+K = 1/2 Q^* S \otimes S^* Q^{T*}
+\end{equation*}
+where
+	$\otimes$ denotes the Kronecker product, and
+	$Q = 
+\left( 
+\begin{array}{c c c c}
+ 1 & 0 & 0 &  1 \\
+ 1 & 0 & 0 & -1\\
+ 0 & 1 & 1 &  0\\
+ 0 & i & i &  0
+\end{array}
+\right)$
+
+POLSAR aims to measure the target's polarimetric response.
+%Depending on the satellite instrument and processing, either Sinclair matrix or Kennaugh matrix elements are provided.
+Typically, the radar transmitter will separately send different horizontal and vertical polarized waves, and measure the response also in horizontal and vertical polarization directions.
+The full polarimetric data, will then have four channels, i.e. $\{ S_{HH}, S_{VV}, S_{HV}, S_{VH} \}$. 
+The four channel, or quad-pol data, is considered full polarimetric data since it allows one to synthesize the target's response for any given pair of transmitted and received polarization.
+Such a process is called polarization synthesis.
+The formula is given as:
+\begin{equation}
+  \label{eqn:Polarization Synthesis Process of Full-Pol data}
+  \caption{eqn:Polarization Synthesis Process of Full-Pol data}
+I^{Rx} = 
+\left( 
+\begin{array}{c }
+ 1 \\
+ \cos(2\chi^{Rx}) \cos(2\Psi^{Rx}) \\
+ \cos(2\chi^{Rx}) \sin(2\Psi^{Rx}) \\
+ \sin(2\chi^{Rx}) 
+\end{array}
+\right)^T
+K
+\left( 
+\begin{array}{c }
+ 1 \\
+ \cos(2\chi^{Tx}) \cos(2\Psi^{Tx}) \\
+ \cos(2\chi^{Tx}) \sin(2\Psi^{Tx}) \\
+ \sin(2\chi^{Tx}) 
+\end{array}
+\right)
+\end{equation}
+where $I^{Rx}$ is the intensity of the target's response in a given combination of transmitted and received polarizations.
+
+In a full polarimetric implementation, an alternate pulsing scheme is normally used to share a single time slot for transmitting two different polarizations' pulses.
+In partial polarimetry modes only a single polarization is sent.
+Since the transmitting time-slot no longer needs to be shared in the partial polarimetry modes, higher operating frequency become possible which leads to better (almost double) resolution or coverage.
+Clearly in such cases, only two out of four data channels is available, i.e. either $\{S_{HH},S_{HV}\}$ or $\{S_{VH},S_{VV}\}$.
+%The limitation in payload is expected to be around for years to come, with new polarimetric projects being planned by various space agencies.
+This trade-off is based on limitations of physics, and hence is likely to be around for years to come.
+
+\subsubsection{Partial Polarimetry and the Stokes Vector}
+
+%***IVM: Hai your citations are wrong in this paragraph, they should be \cite (I think I've fixed them all though)
+Early works from the radar community had focused on the theoretical introduction of the scattering matrix such as the Sinclair matrix or Mueller matrices, for full, i.e.
+quad, polarimetric measurements \cite{Sinclair_1950_ProcsIRE}.
+%(Sinclair, 1950), (TODO) 
+These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \cite{Zebker_1991_ProcsIEEE}.
+
+Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR were launched.
+However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes as a compromise between theoretical polarimetric requirements and practical limitations.
+Initially, to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.
+
+Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
+In his pioneer paper in 2005, Souyris\cite{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode and suggested that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
+Raney\cite{Raney_2006_IGARSS} also showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave (via Stokes parameters), it is also capable of detecting the basic target's polarimetric characteristic, e.g.
+odd or even bounce phenomena.
+
+While the dual-polarization mode sensing has been available operationally for quite some time, partial polarimetry has only recently been investigated in the scientific community. 
+In comparison, 
+	partial polarimetry measures dual-polarized response from incoming pulses of a single polarization channel,
+	while full polarimetry measures the same response from two (generally orthogonal) polarisation channels.
+Mathematically, the process is modelled as:
+\begin{equation*}
+ \left( 
+\begin{array}{c}
+ E_h^{Rx} \\
+ E_v^{Rx}
+\end{array}
+ \right) = \frac{e^{ikr}}{r} 
+\left( 
 \begin{array}{c}
@@
  \right) E^{Tx}
-\end{equation}
-
-Souyris \cite{Souyris_2005_TGRS} pioneered the field with his paper on compact polarimetry.
-Compact polarimetry is essentially a partial polarimetry mode in which the incoming pulse is of linear polarization, 
-	but is neither of the usual horizontal nor vertical angle.
+\end{equation*}
+
+\cite{Souyris_2005_TGRS} pioneered the field with a paper on compact polarimetry.
+This essentially describes a partial polarimetry mode in which the incoming pulse is of linear polarization, 
+	but is of neither fully horizontal nor vertical angle.
 %	rather it is of an odd angle of 
-Instead its incoming polarization of linear polarisation with an odd angle of $\pi/4$.
+Instead, its incoming polarization of linear polarisationhas an odd angle of $\pi/4$.
 %The $\pi/4$ mode has not been implemented in real-hardware, but only been simulated using polarization basis change principles.
-The partial polarimetric covariance matrix then is given as
-\begin{equation}
+The partial polarimetric covariance matrix is then given as
+%\begin{equation}
+%J = 
+%\left(	
+%\begin{array}{c c}
+%	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
+%& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
+%	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
+%& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
+%\end{array}
+%\right)
+%\end{equation}
+
+%****IVM: Hai, the equation doesn't fit - can you do something like this instead? (and same for the next eqn too)-> 
+%\begin{equation}
+%J = 
+%\left(	
+%\begin{array}{c c}
+%	|s_{HH}|^2 + |s_{HV}|^2 }              		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
+%	{+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
+%\vspace{0.1}
+%	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
+%	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
+%\end{array}
+%\right)
+%\end{equation}
+
+\begin{equation*}
 J = 
@@
 \begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2 + 2 \Re{(s_{HH}s_{HV}^*)}
-& 	s_{HH}s_{VV}^* + |s_{HV}|^2 + s_{HH}s_{HV}^* + s_{HV}s_{VV}^*\\
-	s_{HH}^*s_{VV} + |s_{HV}|^2 + s_{HV}s_{HH}^* + s_{VV}s_{HV}^*
-& 	|s_{VV}|^2 + |s_{HV}|^2 + 2 \Re{(s_{VV}s_{HV}^*)}
-\end{array}
-\right)
-\end{equation}
-
-Raney \cite{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
+	|s_{HH}|^2 + |s_{HV}|^2               		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
+	+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
+        \vspace{0.01 in} & \vspace{0.01 in}\\
+	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
+	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
+\end{array}
+\right)
+\end{equation*}
+
+%*** IVM, I changed the following reference to a \citet
+In \cite{Raney_2006_IGARSS}, Raney demonstrated a different perspective by proposing a hybrid architecture.
 He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
 Thus the polarisation choice of the receiving antenna is trivial (as long as they are orthogonal).
-The important parameter to choose is the use of which polarisation for the incoming pulse.
+The important parameter is the choice of the polarisation to be used for the incoming pulse.
 His hybrid architecture is again a kind of partial polarimetry in which the incoming pulse is of circular polarisation, instead of the normally encountered linear polarisation.
-The partial covariance matrix then become:
-\begin{equation}
+The partial covariance matrix then becomes:
+\begin{equation*}
 J = \frac{1}{2} \left(	
 \begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
-& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
-	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
-& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
-\end{array}
-\right)
-\end{equation}
-
-The benefits of this hybrid architecture, according to Raney being:
-	this partial polarimetric measurements can measures certain physical polarimetric phenomena like odd and even bounce phenomena.
+	|s_{HH}|^2 + |s_{HV}|^2 
+& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* \\
+        + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
+&       - i (|s_{HV}|^2 + s_{HH}s_{VV}^*) \\ 
+        \vspace{0.01 in} & \vspace{0.01 in}\\
+	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* 
+& 	|s_{VV}|^2 + |s_{HV}|^2  \\
+        + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
+&       + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)  
+\end{array}
+\right)
+\end{equation*}
+
+The benefits of this hybrid architecture, according to Raney are that it can measure certain physical polarimetric phenomena such as the odd and even bounce phenomena.
 The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
-\begin{equation}
+\begin{equation*}
 \Gamma_{tri} = \left(
@@
 \right)
-\end{equation}
+\end{equation*}
 Then the response will be reversed as it can be calculated as:
-\begin{equation}
+\begin{equation*}
 J_r = \left(
@@
 \right) 
-\end{equation}
+\end{equation*}
 with
@@
 
-For a dihedral target, whose main axis at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
-\begin{equation}
+For a dihedral target, whose main axis is at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
+\begin{equation*}
 \Gamma_{dih} = 
@@
 \right)
-\end{equation}
-The even bounce phenomena is detectable as its polarimetric response is then:
-\begin{equation}
+\end{equation*}
+The even bounce phenomena is detectable as its polarimetric response, which is then:
+\begin{equation*}
 J_r = \left(
@@
 \right) 
-\end{equation}
-In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conviniences to hardware calibration.
-Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrate the classification power of hybrid polarimetry.
+\end{equation*}
+In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
+Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
 Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
-Notably, the hybrid architectural concepts has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
-
-The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformation described above.
+Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
+
+The research into partial polarimetry is convenient as its data can be simulated using polarisation basis transformations such as those described above.
 Hardware realisation may not be needed until the final physical prototype stages.
 This methodology has been demonstrated and is widely used in the community.
-We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
-The focus into partial polarimetry allow analysis into a smaller matrix, while its implication can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
+%We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
+The focus into partial polarimetry allows analysis with a smaller matrix, while its implications can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
 Besides that, a number of research questions in this new field are still open, relevant and exciting.
@@
 In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
+%****IVM: Hai are Nord / Ainsworth single author?
+If not, you need an "et.
+al."
 In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
-Chapter 3 reviews of this sub-topic further and introduces our work on expanding the reconstruction to urban man-made structures and surfaces.
-
-For the tasks of target detection and classification, we believe that partial dual polarization provides a unique offer.
-Compared with single-channel, dual channel provide extra polarimetric information. 
-Compared with full polarimetric data, the better spatial resolution could makes up for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
-\paragraph{ Stokes Vector }
-
-Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
-The wave coherency matrix is defined as:
-\begin{equation}
-W_c = \left<
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right)
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right)^{\dagger}
-\right>
-= \left<
-\left(
-\begin{array}{c c}
- \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
- \xi_y \xi_x^* 	& \xi_y \xi_y^* 
-\end{array}
-\right)
-\right>
-= \left<
-\left(
-\begin{array}{c c}
- |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
- |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
-\end{array}
-\right)
-\right>
-\end{equation}
-
-The Stokes vector is then defined as:
-\begin{equation}
-S_t = 
-\left(
-\begin{array}{c}
- S_0 \\
- S_1 \\
- S_2 \\
- S_3
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
- |\xi_x|^2 + |\xi_y|^2 \\
- |\xi_x|^2 - |\xi_y|^2 \\
- 2\Re(\xi_x \xi_y^*) \\
- 2\Im(\xi_x \xi_y^*)
-\end{array}
-\right)
-\end{equation}
-
-In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
-\begin{equation}
-S_t = 
-\left(
-\begin{array}{c}
- S_0 \\
- S_0 \cos(2\Psi) \cos(2\chi) \\
- S_0 \sin(2\Psi) \cos(2\chi) \\
- S_0 \sin(2\chi)
-\end{array}
-\right)
-\end{equation}
-
-%It should be noted that: the factor of two before the polarization ellipse's angles indicate the fact that
-%	any polarization ellipse is practical indistinguishable from on rotated by $180^o$ 
-%	or with on with the axis lengths swapped accompanied by a $90^o$ rotation.
-
-At this point, a distinction needs to be highlighted. %explaination is warranted.
-%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
-%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
-In comparison to the two-element Jones vector, Stokes vectors have more data, four elements. 
-Jones vector can completely describe the polarization states of an elementary wave, which formulation is based on the assumption that the wave is very well behaved.
-In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
-As such, the polarization of the waves are normally not fully polarized.
-One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
-The phenomena can be loosely called wave depolarization.
-
-The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wave length.
-In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.
-
-\paragraph{Degree of polarization}
-
-Degree of polarization $p$ is a quantity used to describe the portion of an EM wave, which is polarized.
-A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
-A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
-Thus $0 \leq p \leq 1$.
-
-In fully polarized wave, the following equation holds:
-\begin{equation}
-S_0^2 = S_1^2 + S_2^2 + S_3^2
-\end{equation}
-
-In depolarized wave, it becomes an in-equation
-\begin{equation}
-S_0^2 > S_1^2 + S_2^2 + S_3^2
-\end{equation}
-
-Then the degree of polarization is defined as
-\begin{equation}
-p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
-\end{equation}
-
-In such general case, the Stokes Vector is written as:
-\begin{equation}
-S_t = 
-\left(
-\begin{array}{c}
- I \\
- I p \cos(2\Psi) \cos(2\chi) \\
- I p \sin(2\Psi) \cos(2\chi) \\
- I p \sin(2\chi)
-\end{array}
-\right)
- = I (1 - p)
-\left(
-\begin{array}{c}
- 1 \\
- 0 \\
- 0 \\
- 0
-\end{array}
-\right) 
-+ I p
-\left(
-\begin{array}{c}
- 1\\
- \cos(2\Psi) \cos(2\chi) \\
- \sin(2\Psi) \cos(2\chi) \\
- \sin(2\chi)
-\end{array}
-\right)
-\end{equation}
-
-Or alternatively, if Stokes vector is measured and given, then the polarization characteristics of a wave is given as:
-$I$, the total power of the measured beam is $I=S_0$,
-$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
-$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.
-
-Depolarization phenomena is explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
-The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
-If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
-One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.
+Chapter 3 will review this sub-topic further and introduce our work on expanding the reconstruction to urban man-made structures and surfaces (from the original system which was relevant to natural cover only).
+
+For the tasks of target detection and classification, we believe that partial dual polarization provides a unique proposition.
+Compared with single-channel systems, the dual channel provides additional and useful polarimetric information. 
+Compared with full polarimetric data, the better spatial resolution of dual channel systems could compensate for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
 
@@
 
-\subsubsection{Full Polarimetry and the Polarimetric Signatures}
-
-This section describes the core concept of POLSAR, i.e. the target's polarimetric signature, 
-	and illustrates why research into partial polarimetry is warranted.
-
-POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
-The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
-\begin{equation}
- E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
-\end{equation}
-
-Normally, horizontal and vertical linear polarization are used, thus the scattering matrix, i.e. $S$, normally have the following expanded form:
-\begin{equation}
- \left( 
-\begin{array}{c}
- E_h^{Rx} \\
- E_v^{Rx}
-\end{array}
- \right) = \frac{e^{ikr}}{r} 
-\left( 
-\begin{array}{c c}
- S_{HH} & S_{HV} \\
- S_{VH} & S_{VV}
-\end{array}
- \right) 
-\left( 
-\begin{array}{c}
- E_h^{Tx} \\
- E_v^{Tx}
-\end{array}
- \right) 
-\end{equation}
-
-The scattering matrix can be called the Jones matrix (relating the Jones vector) in the forward scattering alignment.
-The matrix is normally called Sinclair matrix in SAR literature, as normally backward scattering alignment are normally used in SAR \cite{Sinclair_1950_ProcsIRE}.
-In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.
-
-The matrix can also be "stratified" to define the target scattering vector as: 
-\begin{equation}
-T_{cv} = \left( 
-\begin{array}{c}
- S_{HH} \\
- \sqrt{2} S_{HV} \\
- S_{VV}
-\end{array}
- \right) 
-\end{equation}
-or 
-\begin{equation}
-T_{ch} = \frac{1}{\sqrt{2}} \left( 
-\begin{array}{c}
- S_{HH} + S_{VV}\\
- S_{HH} - S_{VV} \\
- S_{HV}
-\end{array}
- \right) 
-\end{equation}
-
-Similar to the reason that Stokes vector are preferred to Jones vector in wave polarization, 
-	second order statistics of target scattering matrix are normally preferred.
-The covariance matrix is defined as:
-\begin{equation}
-\small{
-C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
-\left( 
-\begin{array}{c c c}
- S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
- \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
- S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
-\end{array}
- \right) 
-}
-\end{equation}
-while the coherency matrix is defined as:
-\begin{equation}
-\small{
-C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
-\left( 
-\begin{array}{c c c}
- (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
- (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
- 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
-\end{array}
- \right) 
-}
-\end{equation}
-
-Evidently the two matrices are related:
-\begin{equation}
-C_h = N C_v N^T
-\end{equation}
-where
-	$N = \frac{1}{\sqrt{2}}
-\left( 
-\begin{array}{c c c}
- 1 & 0		& 1\\
- 1 & 0		& -1\\
- 0 & \sqrt{2}	& 0
-\end{array}
-\right)$
-
-The off-diagonal values in both covariance and coherence matrices are normally complex. 
-The equivalent all real-valued matrices which carries the same information are called Mueller matrix and Kennaugh matrix which are to be used in forward and backward scattering alignment respectively \cite{Guissard_1994_TGRS}.
-They are defined as the matrix that relates the Stokes matrix of sent and received signals.
-\begin{equation}
-S_t^{Rx} = K S_t^{Tx}
-\end{equation}
-
-Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related and is given by:
-\begin{equation}
-K = 1/2 Q^* S \otimes S^* Q^{T*}
-\end{equation}
-where
-	$\otimes$ denotes the Kronecker product, and
-	$Q = 
-\left( 
-\begin{array}{c c c c}
- 1 & 0 & 0 &  1 \\
- 1 & 0 & 0 & -1\\
- 0 & 1 & 1 &  0\\
- 0 & i & i &  0
-\end{array}
-\right)$
-
-POLSAR aims to measure target's polarimetric response.
-%Depending on the satellite instrument and processing, either Sinclair matrix or Kennaugh matrix elements are provided.
-Typically, the radar will separately send different horizontal and vertical polarized waves, and measure the response also in horizontal and vertical polarizations.
-The full polarimetric data, will then have four channels, i.e. $\{ S_{HH}, S_{VV}, S_{HV}, S_{VH} \}$. 
-The four channel, or quad-pol data, is considered full polarimetric data since it allows one to synthesize the target's response for any given pair of transmitted and received polarization.
-Such a process is called polarization synthesis.
-The formula is given as:
-\begin{equation}
-I^{Rx} = 
-\left( 
-\begin{array}{c }
- 1 \\
- \cos(2\chi^{Rx}) \cos(2\Psi^{Rx}) \\
- \cos(2\chi^{Rx}) \sin(2\Psi^{Rx}) \\
- \sin(2\chi^{Rx}) 
-\end{array}
-\right)^T
-K
-\left( 
-\begin{array}{c }
- 1 \\
- \cos(2\chi^{Tx}) \cos(2\Psi^{Tx}) \\
- \cos(2\chi^{Tx}) \sin(2\Psi^{Tx}) \\
- \sin(2\chi^{Tx}) 
-\end{array}
-\right)
-\end{equation}
-where $I^{Rx}$ is the intensity of the target's response in a given combination of sent and receive polarizations.
-
-In full polarimetric implementation, normally an alternate pulsing scheme is used to share a single time slot for transmitting two different polarizations' pulses.
-In partial polarimetry modes only a single polarization is sent.
-Since the transmitting time-slot no longer needs to be shared, a higher frequency become possible which leads to better (almost double) resolution or coverage.
-Clearly in such cases only two out of four data channels is available, i.e. either $\{S_{HH},S_{HV}\}$ or $\{S_{VH},S_{VV}\}$.
-%The limitation in payload is expected to be around for years to come, with new polarimetric projects being planned by various space agencies.
-This trade-off is based on limitations of physics, and hence is expected to be around for years to come.
-
 \subsubsection{The Polarization Basis Transformation}
 
-Assume that the polarization states are known, the wave representation can be given as:
-\begin{equation}
+Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
+\begin{equation*}
 \left( 
@@
 \right) 
-\end{equation}
+\end{equation*}
 The representation of a wave, however, depends on the choice of orthogonal reference frame basis.
@@
 \end{array}
-\right)$
-The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by an unitary transformation matrix $U_2$.
-The transformation formula is given as:
-\begin{equation}
+\right)$ê
+.
+The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
+\begin{equation*}
 \left(
@@
 \right)
-\end{equation}
+\end{equation*}
 
 Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
-\begin{equation}
+\begin{equation*}
 U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
@@
 \right)
-\end{equation}
+\end{equation*}
 where
@@
 	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
-	and is required for the determination of the initial phase of the Jones vector in the new reference basis.
-
-In the same vein, Ferro-Famil, 2000 gives
-\begin{equation}
+	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.
+
+In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
+\begin{equation*}
 U_2 = \left(
@@
 \right)    
-\end{equation}
+\end{equation*}
 
 From these results, it is then possible to derive equations for the transformation of the scattering matrix.
-Noting that be definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
-and that $J_{xy}^*= U_2 J_{hv}^*$. 
-Noting further that $(U_2)^{-1} = (U_2)^T$.
-It is then trivial to show that:
-\begin{equation}
+Noting that by definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
+and that $J_{xy}^*= U_2 J_{hv}^*$, also that $(U_2)^{-1} = (U_2)^T$,
+it is then trivial to show that:
+\begin{equation*}
 S_{xy} = U_2 S_{hv} U_2^T
-\end{equation}.
-
+\end{equation*}
+
+%***IVM: again, I think you need to introduce some of the variables below, like delta, rho. Is rho* the complex conjugate? Better to mention that too....
 Using the result above, we then have:
-\begin{equation}
+\begin{equation*}
 S_{xx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
 S_{xy} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
 S_{yx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
 S_{yy} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
+\end{equation*}
 
 In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
-\begin{equation}
+\begin{equation*}
 S_{xx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
-\begin{equation}
+\end{equation*}
+\begin{equation*}
 S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation}
-
-The results here, together with Stokes Vector's formula, can be used to prove the following identity, which form the basis of our approach:
-\begin{equation}
+\end{equation*}
+
+The results here, together with Stokes Vector's formula, can be used to prove the following identity,
+  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
+\begin{equation*}
 S_t = 
@@
 \right)
-\end{equation}
+\end{equation*}
 where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.
@@
 
+%In practice, discrimination measures are not the only way to carry out classification tasks in POLSAR.
+%Another common approach is to use POLSAR observables identified by different target decomposition theorems.
+Different target decomposition theorems have identified many possible scalar observables for the complex POLSAR data.
+In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes are evaluated.
+While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, at its conclusion, the paper indicated that ``it is impossible to identify the best one''
+  as these ``representations ... do not show a precise trend''.
+%Instead an MLP classification approach were employed. 
+Although, to be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
+  and thus they were not precisely defined to be used individually for the purpose of single-handedly representing POLSAR data.
+
+Given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
+  it is possible to derive the scalar statistical models for some univariate POLSAR observables.
+However, such derivations are no trivial task,
+  as the data is much more complex and the field is much less mature than that of traditional SAR statistical modelling.
+Thus the strategy of the pioneering works tend to be to tackle simpler versions of polarimetry.
+
+In the literature, POLSAR data is commonly represented by its covariance matrix.
+For full polarimetric SAR data (full-pol) the covariance matrix has the form of
+\begin{equation*}
+C_3 = 
+\begin{bmatrix}
+S_{hh}^2 & \sqrt{2}S_{hh}S_{hv}^* & S_{hh}S_{vv}^* \\ 
+\sqrt{2}S_{hh}^*S_{hv} &2S_{hv}^2  & \sqrt{2}S_{hv}S_{vv}^*\\ 
+S_{hh}^*S_{vv} & \sqrt{2}S_{hv}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+For partial polarimetric SAR data (part-pol), it reduces to either of the two following equations:
+\begin{equation*}
+  C_{2,h} =
+  \begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{hv}^* \\
+    S_{hh}^*S_{hv} & S_{hv}^2
+  \end{bmatrix};
+  C_{2,v} =
+  \begin{bmatrix}
+    S_{hv}^2 & S_{hv}S_{vv}^* \\
+    S_{hv}^*S_{vv} & S_{vv}^2
+  \end{bmatrix}
+\end{equation*}
+Obviously, the statistical behaviour of $C_3$ can be understood by understanding the behaviour of $C_{2h},C_{2v}$ and
+\begin{equation*}
+  C_{2,c} = 
+\begin{bmatrix}
+    S_{hh}^2 & S_{hh}S_{vv}^* \\
+    S_{hh}^*S_{vv} & S_{vv}^2
+\end{bmatrix}
+\end{equation*}
+
+While $C_{2v}, C_{2h}$ are physically related to the Stokes parameters of EM waves,
+  $C_{2c}$ is %a totally made-up mathematical term from the full-pol covariance matrix.%***IVM changed it to:
+  an artificial term derived from the ful-pol covariance matrix.
+In fact, in the field of polarimetric SAR, $C_{2v}, C_{2h}$ are called cross-pol and $C_{2c}$ is called the co-pol covariance matrice.
+Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
+\begin{equation*}
+  \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
+\end{equation*}
+with $\phi=arg(\rho)$ is the phase difference angle.
+In $C_{2v}$ and $C_{2h}$ that are commonly used in optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
+  and $\phi_v,\phi_h$ are very random, due to little correlation existing between orthogonal polarizations in monochromatic EM waves.
+%By analogy, in POLSAR ``natural surfaces'' data, it is common to consider: $|\rho_v|=|\rho_h|=0$
+Their equivalent lies in the ``natural surface'' case of POLSAR,
+  where  it is common to assume $|\rho_v|=|\rho_h|=0$.
+This is, however, not true in the general case of POLSAR (i.e. including over built-up areas).
+Specifically for $C_{2c}$, since there is correlation between the two co-pol channels,
+  $|\rho_c|$ is almost always significant and $\phi_c$ is also not entirely random.
+
+In the field of optical physics,
+  under the assumption of no correlation between cross-polarized channels,
+  \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} derived the statistical models for $C_{2h},C_{2v}$.
+The observables that have been studied are:
+\begin{enumerate}
+\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
+  \begin{enumerate}
+  \item the total power $S_0=C_{11}^2 + C_{22}^2$,
+  \item the ratio of minor to major axis of the polarization ellipse  $\epsilon=\lambda_2/\lambda_1$,
+  \item and $\psi$ the angle that the ellipse major axis makes with horizontal axis,
+  \end{enumerate}
+\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
+  \begin{enumerate}
+  \item $S_0 = C_{11}^2 + C_{22}^2$
+  \item $S_1 = C_{11}^2 - C_{22}^2$
+  \item $S_2 = \Re (C_{12})$
+  \item $S_3 = \Im (C_{12})$
+  \end{enumerate}
+\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
+\end{enumerate}
+In the field of POLSAR, under the assumption of significant correlation between polarized channels,
+  \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} derived the statistical models for not only $C_{2h},C_{2v}$ but also $C_{2c}$.
+Specifically the following observables were studied:  
+  \begin{enumerate}
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562,Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \end{enumerate}
+
+Furthermore, other studies have offered
+  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
+  statistical model for
+  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
+While these models undoubtedly help in understanding SAR data,
+  individually none of them statisfy the dual criteria of
+  1) resulting in statistically consistent discrimination measures and
+  2) being an representative observable for the complex POLSAR data, which are the objectives of this thesis.
+  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
+
+\subsection{Existing Discrimination Measures for (POL)SAR data}
+
+The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
+\begin{align*}
+  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+\end{align*}
+where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
+ $||$ denotes absolute values
+and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+However, in the context of POLSAR% covariance matrix
+, these dis-similarity measures are not widely used 
+  mainly due to the multiplicative nature of the noisy data.
+
+In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
+It is defined \cite{Lee_1994_IJRS_2299} as:
+\begin{equation*}
+  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
+\end{equation*},
+where $tr(C)$ denotes the trace of the matrix C. 
+As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
+
+Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+\begin{align*}
+  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
+    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
+\end{align*}
+the Bartlett distance \cite{Kersten_2005_TGRS_519},
+  \begin{align*}
+  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  \end{align*}
+the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+\begin{equation*}
+  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
+\end{equation*}
+and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+\begin{equation*}
+  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+\end{equation*}
+.
+
+Closer investigation of these dis-similarity measures reveals that most are related in some ways. %to each other.
+The Bhattacharyya distance is easily shown to be related to the Barlett distance.
+At the same time the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
+  when the two data sets have the same number of looks, i.e. $L_x=L_y$.
+The close relation among the measures is further supported by the fact that
+  all of their proposing papers refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+the likelihood ratio statistics for POLSAR covariance matrix is considered:  
+\begin{equation*}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation*}
+
+Taking the log-transformation of the above equation, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
+\begin{equation}
+  \label{eqn:Complex Wishart Distribution Likelihood Test Statistics}
+  \caption{eqn:Complex Wishart Distribution Likelihood Test Statistics}
+  Q = \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}}  
+\end{equation}
+\begin{equation}
+  \label{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
+  \caption{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
+  \ln Q = L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| 
+\end{equation}
+
+To detect changes, a test statistic is developed based on this measure of distance.
+This means a distribution is to be derived for the dissimilarity measure.
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
+
 \subsection{Current Methods for SAR speckle filtering}
-This section starts with a description of the stochastic nature of SAR data. 
-SAR speckle filtering is then reviewed within a statistical estimation theory framework. 
-Various different approaches to SAR speckle filtering are reviewed, 
-	ranging from Generalized Least Squared Error algorithms
-	%ranging from a discrete cartoon like algorithm 
-	to the more convoluted Maximum A Posteriori (MAP) approaches.
-	%to recent more continous multi-resolution wavelet or partial differental equations based algorithms.
+
+%This section starts with a description of the stochastic nature of SAR data. (Comment: as mentioned ñ this should be at the beginning of the chapter)
+%SAR speckle filtering is then reviewed within a statistical estimation theory framework. 
+%Various different approaches to SAR speckle filtering are reviewed, 
+%	ranging from Generalized Least Squared Error algorithms
+%	%ranging from a discrete cartoon like algorithm 
+%	to the more convoluted Maximum A Posteriori (MAP) approaches.
+%	%to recent more continous multi-resolution wavelet or partial differental equations based algorithms.
 
 Although speckle has been extensively studied for decades, speckle reduction remains one of the major issue in SAR imaging process. 
-Many reconstruction filters have been proposed and they can be classified into two main categories: 
-	minimum mean-square error (MMSE) de-speckling using the speckle model; 
+Many reconstruction filters have been proposed, and they can be classified into two main categories: 
+	Weighted Least-Square Error de-speckling using the speckle model; 
 	and maximum a posteriori (MAP) de-speckling using the product model. 
-%The famous Lee, Kuan, and Frost ﬁlters in the ﬁrst category provide MMSE reconstructions based on measured local statistics.
-%In the second category, diﬀerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.
+In this section, various different approaches to SAR speckle filtering are reviewed.
+%The famous Lee, Kuan, and Frost ˆÄÅé‡§èÅlters in the ˆÄÅé‡§èÅrst category provide MMSE reconstructions based on measured local statistics.
+%In the second category, diˆÄÅé‡§èÄerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.
 
 In the first category the speckle random process is assumed to be stationary over the whole image. 
-Then speckle models are proposed, the multiplicative speckle model is first approximated by a linear model, then a speckle reduction filter is formulated
-The formula is as follows: 
+Then speckle models are proposed, such as the multiplicative speckle model is first approximated by a linear model.
+A class of speckle reduction filters is formulated 
+as follows: 
 \begin{equation}
+  \label{eqn:Weighted Least-Square Error}
+  \caption{eqn:Weighted Least-Square Error}
 \hat{R}(t) = I(t) \cdot W(t) + \bar{I}(t) \cdot (1 - W(t)) 
@@
 	$\hat{R}(t)$ is the filter response,
-	$I(t)$ is the intensity at the center of the moving window,
+	$I(t)$ is the intensity at the centre of the moving window,
 	$\bar{I}(t)$ is the averaged intensity for the whole processing window,
-	$W(t)$ is the weight function,
+	$W(t)$ is a weight function,
 
 For the Lee filter \cite{Lee_PAMI_1980}, the weight function is proposed to be:
-\begin{equation}
+\begin{equation*}
 W(t) = 1 - \frac{C_u^2}{C_I^2} 
-\end{equation}
+\end{equation*}
 where
@@
 In the approach of the Kuan filter \cite{Kuan_1985_PAMI}, the multiplicative speckle model is first transformed into a single-dependent additive noise model, and then the MMSE criterion is applied. 
-The speckle filter has the same form as the Lee filter but with a different weighting function 
-\begin{equation}
+The speckle filter thus has the same form as the Lee filter but with a different weighting function 
+\begin{equation*}
 W(t) = \frac{1 - \frac{C_u^2}{C_I^2} }{1+ C_u^2} 
-\end{equation} 
-The Kuan filter takes into account the dependency of noise into signal. 
+\end{equation*} 
+The Kuan filter takes into account the dependency of noise on the signal. 
 In the special case of noise being independent of the underlying signal, the Kuan filter would be exactly the same as the Lee filter.
@@
 
-The Frost filter \cite{Frost_PAMI_1982} is different from the Lee and Kuan filters with respect that the scene reflectivity is estimated by convolving the observed image with the impulse response of the SAR system.
+The Frost filter \cite{Frost_PAMI_1982} is different from the Lee and Kuan filters, where the scene reflectivity is estimated by convolving the observed image with the impulse response of the SAR system.
 The impulse response of the SAR system is obtained by minimizing the mean square error between the observed image and the scene reflectivity model which is assumed to be an autoregressive process. 
 The filter impulse response can, after some simplification, be written as:
-\begin{equation}
+\begin{equation*}
 H(t) = K_1 e^{-K_2 C_I^2(t)}
-\end{equation}
+\end{equation*}
 where
-	$K_1$ is some normalizing coefficient to allow preservation of signal mean values,
-	$K_2$ is a user chosen filter parameter.
-
-As can be seen from all the three most recognized algorithms in this field, they share the same principles:
-When the variation coefficient $C_I$ is small, the filter behaves like an low pass filter smoothing out the speckles. 
+	$K_1$ is some normalizing coefficient to allow preservation of signal mean values, and
+	$K_2$ is a user-selected filter parameter.
+
+As can be seen from these three most recognised algorithms in this field, they share similar principles.
+When the variation coefficient $C_I$ is small, the filter behaves like a low pass filter smoothing out the speckles. 
 When $C_I$ is large, it has a tendency to preserve the original observed image.
@@
 
-As discussed at length in Chapter 4, SAR data is heteroskedastic.
+As will be discussed at length in Chapter 4, SAR data is heteroskedastic.
 Our literature search yielded only a single article \cite{Amirmazlaghani_2009_TIP} tackling SAR data's heteroskedastic feature, suggesting a lack of appropriate attention within the research community about such characteristic and its effects.
-%However, the community appears to be oblivious of the fact, evidenced by the fact that we could only find very few researcher \cite{Amirmazlaghani_2009_TIP} tackling heteroskedasticity in SAR data
+%However, the community appears to be oblivious of the fact, evidenced by the fact that we could only find very few researcher (Just a comment: it could also imply that the concept is not significantly useful)  \cite{Amirmazlaghani_2009_TIP} tackling heteroskedasticity in SAR data
 Under such conditions, Ordinary Least Square methods may not provide optimal results \cite{Woods_PAMI_1984}. 
-In fact as is shown by the mathematical formula above, weighted average formula were being used.
+In fact, as is shown by Eqn. \ref{eqn:Weighted Least-Square Error}), weighted average formulae were being used.
 This is consistent with the knowledge that, when variance of heteroskedastic data is available, weighted least squares is an optimal estimator.
-As is a fact in SAR data, this variance however is not available directly and can only be estimated (note the concept of variation coefficient).
-Our analysis then shows that estimating variance is as hard as estimating the un-speckled signal itself!
-We believe that log transformation could help to break through this circle of ambiguity.
-
-In the second approach, the filters assume that speckle is not stationary globally but is only stationary locally within the moving processing window.
-The filters operate based on MAP principle, which is given as:
-\begin{equation}
+However, in SAR data, this variance is not available directly and can only be estimated. 
+Since heteroskedasticity means that this variance is dependent on the under-lying signal, thus estimating this variance is evidently as hard as estimating the un-speckled signal itself.
+%However, it will also be shown 
+% that log transformation would help to break  this circle of ambiguity.
+
+%***IVM: Hai, to be clear, when you mention "the second approach" below, do you mean "In our second approach"??? In which case, please say so!!
+In the MAP approach, the filters assume that speckle is not stationary globally but is only stationary locally within the moving processing window.
+Such filters operate based on the MAP principle, which is given as:
+\begin{equation*}
 f(x|z) = \frac{f(z|x) f(x)}{f(z)}
-\end{equation}
+\end{equation*}
 where
-	$x$ is the underlying signal that need to be estimated, and
+	$x$ is the underlying signal that needs to be estimated, and
 	$z$ is the observed signal.
 The underlying signal is found by
-\begin{equation}
+\begin{equation*}
 x = argmax \{ \log(f(z|x)) + \log(f(x))  \} 
-\end{equation}
+\end{equation*}
 
 As evidenced, these classes of filter require the knowledge of the \textit{a-priori} PDF $f(x)$. 
-Various PDFs for the underlying back-scattering coefficient have been assumed.
-
-In case Normal distribution is assumed \cite{Medeiros_1998_IAI}
-\begin{equation}
+As such, various PDFs for the underlying back-scattering coefficient have been assumed.
+
+If a normal distribution is assumed \cite{Medeiros_1998_IAI}, then:
+\begin{equation*}
 f(x) = \frac{1}{\sigma_x \sqrt{2 \pi} } e^{\frac{1}{2} \left( \frac{x-\mu}{\sigma_x} \right)^2 }
-\end{equation}
-the underlying signal is found by solving the equation
-\begin{equation}
+\end{equation*}
+and the underlying signal is found by solving the equation
+\begin{equation*}
 x^4 \Gamma^2(N) - x^3 \Gamma^2(N) \mu_x + x^2 \Gamma^2(N) 2N \sigma^2_x - 2 \sigma^2_x z^2 \Gamma^2(N+1/2) = 0
-\end{equation}
-
-In the case of Gamma distribution is assumed \cite{Lopes_1990_IGARSS} 
-\begin{equation}
+\end{equation*}
+
+If a Gamma distribution is assumed \cite{Lopes_1990_IGARSS}, then: 
+\begin{equation*}
 f(x) = \frac{\sigma_x}{\Gamma(\lambda)} (x \sigma_x )^{\lambda-1} e^{-x \sigma_x}
-\end{equation}
+\end{equation*}
 For $\lambda=1$, the Gamma distribution is identical to the exponential distribution. 
-For $\lambda=n/2$ and $\sigma=1/2$ Gamma distribution is equivalent to the chi-square distribution.
+For $\lambda=n/2$ and $\sigma=1/2$ the Gamma distribution is equivalent to the chi-square distribution.
 The underlying signal is found by solving the equation:
-\begin{equation}
+\begin{equation*}
 x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) (2N - \lambda + 1) - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation}
-
-In case exponential distribution is assumed 
-\begin{equation}
+\end{equation*}
+
+If an exponential distribution is assumed, then:
+\begin{equation*}
  f(x) = \sigma_x e^{-x \sigma_x}
-\end{equation}
-then the underlying signal is found by solving the equations
-\begin{equation}
+\end{equation*}
+and the underlying signal is found by solving the equations
+\begin{equation*}
  x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) 2N - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation}
-
-In case Chi square distribution is assumed 
-\begin{equation}
+\end{equation*}
+
+If a Chi squared distribution is assumed, then:
+\begin{equation*}
  f(x)=\frac{1}{2^{n/2} \Gamma(n/2)} x^{n/2-1} e^{(-x/2)}
-\end{equation}
-then the true signal is found by solving the equation
-\begin{equation}
+\end{equation*}
+and the true signal is found by solving the equation
+\begin{equation*}
  x^3 \Gamma^2(N) + x^2 \Gamma^2(N) (4N-n+2) - 4 z^2 \Gamma^2(N+1/2) = 0
-\end{equation}
-
-If log-normal distribution is assumed \cite{Medeiros_2003_IntJRemoteSens}
-\begin{equation}
+\end{equation*}
+
+If a log-normal distribution is assumed \cite{Medeiros_2003_IJRS}, then:
+\begin{equation*}
  f(x) = \frac{1}{\sigma_x \sqrt{2 \pi}} x^{-1} e^{\frac{-1}{2 \sigma_x} (\ln(x) - \mu_x)^2}
-\end{equation}
-\begin{equation}
+\end{equation*}
+and
+\begin{equation*}
  x^2 \Gamma^2(N) (-2N \sigma^2_x - \sigma^2_x -\log(x) + \mu_x) + 2 z^2 \Gamma^2(N+1/2)=0
-\end{equation}
+\end{equation*}
 %Some of them being: Gaussian PDF, Gamma PDF, chi square, Rayleigh, beta, log-normal ...
@@
 %Clearly should such PDF being estimatable from the data it-self, that would potentially presents an good opportunity for this class of speckle filters.
-Other distributions that has been assumed include: heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation} \dots
+Other distributions that have been proposed include the heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation} \dots
 Evidently, the performance of these filters are dependent on the underlying distribution of the back-scattering coefficient on the particular surface being imaged. 
 In this context, the community appears to focus on using Bayesian inference to choose the most suitable distributions \cite{Walessa_2000_TGRS}.
-We hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in log-transformed domain.
-
-Other approaches, that recently has been actively pursuit in the community include: 
+One of the additive and homoskedastic SAR model's benefits is the possible hypothesis that the underlying distribution of the back scattering coefficient is estimable discussed in subsequent chapters.
+%In our approach, we hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in the log-transformed domain, as will be described later.
+
+Other approaches that have recently been actively pursued in the research community and in published literature include: 
 	%recently there has been an increase publications about the applicability of
-	wavelet \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
-	curvelet \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
-	contourlet \cite{Foucher_2006_IGARSS}, 
-	ridgelet \cite{Saevarsson_2004_IGARSS},
-	fuzzy logic \cite{Cheng_ETCS_2009}, 
-	anisotropic kernels \cite{DHondt_2006_TGRS}, 
-	and autoregressive conditional heteroskedasticity \cite{Amirmazlaghani_2009_DSPWorkshop}. %techniques into SAR filtering.
-Central to wavelet techniques is the discoveries of a consistent and optimal choice for the wavelet coefficients.
-Similarly the development of kernel methods depends strongly on the discoveries of consistent predictive kernels.
+\begin{itemize}
+\item	wavelets \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
+\item	curvelets \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
+\item	contourlets \cite{Foucher_2006_IGARSS}, 
+\item	ridgelets \cite{Saevarsson_2004_IGARSS},
+\item	fuzzy logic \cite{Cheng_ETCS_2009}, 
+\item	anisotropic kernels \cite{DHondt_2006_TGRS}, 
+\item	and autoregressive conditional heteroskedasticity \cite{Amirmazlaghani_2009_DSPWorkshop}. 
+\end{itemize}
+%***IVM it might be good to make the above into an un-numbered list, I think it will look nicer!!
+
+Central to wavelet techniques is the discovery of a consistent and optimal choice for the wavelet coefficients.
+Similarly, the development of kernel methods depends strongly on the discovery of consistent predictive kernels.
 Evidently the choice of such coefficients are dependent on the underlying statistical characteristics of SAR signals.
-This further emphasizes the importance of investigating consistent statistical properties of SAR signals.
-Note only that statistical analysis is important in speckle filtering, the technique is also important in the development of information extraction \cite{Oliver_1991_JPhysDApplPhys}, target detection \cite{Luttrell_1986_JPhysDApplPhys}, classification \cite{Nyoungui_2002_IntlJRemoteSense} techniques.
-
-With different speckle filtering approaches presented, it is crucial to have a framework for 
-	(a) modelling and simulation which provide the ground-truth data in different scenarios of underlying distribution, and
-	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
-	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.
+This variety of approaches further emphasises the importance of investigating consistent statistical properties of SAR signals.
+Not only is statistical analysis important in speckle filtering, the technique is also important for  information extraction \cite{Oliver_1991_JPhysDApplPhys}, target detection \cite{Luttrell_1986_JPhysDApplPhys} and classification \cite{Nyoungui_2002_IntlJRemoteSense}.
 
@@
 
-Compared to SAR technologies, most POLSAR techniques have only recently been developed. 
-The state of POLSAR speckle filtering is reviewed and filtering the covariance matrix off-diagonal elements is shown to be an open problem.
+Compared to SAR technologies, most POLSAR techniques are relatively recent. 
+Published literatured on POLSAR speckle filtering indicate that filtering the covariance matrix off-diagonal elements is still an open problem.
 The problem can be traced back to the lack of a statistical model for the covariance matrix in polarimetry.
@@
 In the first systems that captured POLSAR data, multi-look processing was used as a method of choice for speckle filtering, at the cost of spatial resolution.
-Novak \cite{Novak_1990_TAES} pioneered the area of speckle reduction and proposed the polarimetric whitening filter (PWF) to produce a single speckle reduced intensity image. 
-The disadvantages of PWF filter is that the polarimetric information is not well-preserved.
-Multi-look processing's polarimetric result also exhibits bias and distortion \cite{Lee_2008_TGRS}.
-
-Lee \cite{Lee_1991_TGRS} proposed a new filtering algorithm which does suppress speckle for the diagonal elements, the off-diagonal elements however remain un-filtered.
-Later, Touzi \cite{Touzi_1994_TGRS} drew out the principles of speckle filtering of POLSAR data. 
-They are
+Novak \cite{Novak_1990_TAES} pioneered the concept of speckle reduction, and proposed the polarimetric whitening filter (PWF) to produce a single speckle reduced intensity image. 
+The main disadvantages of the PWF filter is that polarimetric information is not well-preserved.
+Multi-look processing polarimetric results also exhibit bias and distortion \cite{Lee_2008_TGRS}.
+
+Lee \cite{Lee_1991_TGRS} proposed a new filtering algorithm which does suppress speckle for the diagonal elements, however the off-diagonal elements remain un-filtered.
+Later, Touzi et. al. \cite{Touzi_1994_TGRS} drew out the principles of speckle filtering of POLSAR data, which they summarised as:
 \begin{enumerate}
-	\item Speckle can be filtered if ALL elements of its covariance matrix are filtered.
-	\item Single-channel SAR speckle filtering is only applicable to diagonal elements of the covariance matrix
-	\item Speckle filtering need to be performed also on off-diagonal elements, as correlation among the elements need to be exploited and the elements do not exists independently.
+	\item Speckle can be filtered if ALL elements of the covariance matrix are filtered.
+	\item Single-channel SAR speckle filtering is only applicable to diagonal elements of the covariance matrix.
+	\item Speckle filtering needs also to be performed on off-diagonal elements, as correlation among the elements needs to be exploited, and the elements do not exist independently.
 \end{enumerate}
 
-In 1999, Lee \cite{Lee_1999_TGRS} extended his refined-Lee filters on POLSAR data, and argues that all covariance matrix elements should be filtered by the same amount to preserve polarimetric properties.
-He then proposed to apply the weighted averaging on the full covariance matrix instead of single-channel intensities values. 
-\begin{equation}
+In 1999, Lee \cite{Lee_1999_TGRS} extended his refined-Lee filters to POLSAR data, and argued that all covariance matrix elements should be filtered by the same amount to preserve polarimetric properties.
+He then proposed to apply the weighted averaging on the full covariance matrix instead of single-channel intensities values:
+\begin{equation*}
 C_{out} = C_{avg} + w (C_{curr} - C_{avg})
-\end{equation}
+\end{equation*}
 where
 	$C_{out}$ is the filtered covariance matrix output,
-	$C_{avg}$ is the average covariance matrix using an edge-aligned window,
+	$C_{avg}$ is the average covariance matrix using an edge-aligned window, and
 	$C_{curr}$ is the covariance matrix of the current processing pixel.
 The weight $w$ is computed within the edge aligned window from the total power image $y$ as:
-\begin{equation}
+\begin{equation*}
 w = \frac{\sigma^2_y - \mu^2_y \sigma^2_v}{\sigma^2_y - \sigma^2_y \sigma^2_n}
-\end{equation}
+\end{equation*}
 where 
@@
 
-Further attempts has been made towards statistical modelling the off-diagonal elements but the applications of these results towards the problem of speckle suppression for off-diagonal element have been non-conclusive.
-Based on his 2003 paper \cite{Lopez_2003_TGRS} on POLSAR statistical analysis, in 2008, Martinez \cite{Lopez_2008_TGRS} proposed a model based polarimetric filter.
-He first proposed to model $S_hS_v^*$ as having both additive and multiplicative components. 
-\begin{equation}
+Further attempts have been made towards statistically modelling the off-diagonal elements but the application of these results for speckle suppression of off-diagonal element have not been conclusive.
+For instance Martinez et. al.\cite{Lopez_2008_TGRS} proposed a model based polarimetric filter.
+They first proposed to model $S_hS_v^*$ as having both additive and multiplicative components:
+\begin{equation*}
 S_pS_q^* = \psi |\rho | e^{i \theta} + \psi \bar{z}_n N_c (1-n_m) e^{i \theta} + \psi (n_{ar} + i n_{ai}) 
-\end{equation}
+\end{equation*}
 where
 	$\psi = \sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }$ represents the average joint power in the two channels, 
-	$\rho = |\rho| e^{i \theta} = \frac{E \left( S_pS_q^* \right)}{ \sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) } }$ is the complex correlation coefficient that characterize the correlation among the channels,
-	$N_c = \frac{\pi}{4} |\rho| F_{1,2} ( 1/2,1/2,2,|\rho|^2 )$ basically contains the same information as the complex correlation coefficient, and 
+	$\rho = |\rho| e^{i \theta} = \frac{E \left( S_pS_q^* \right)}{ \sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) } }$ is the complex correlation coefficient that characterises the correlation among the channels,
+	$N_c = \frac{\pi}{4} |\rho| F_{1,2} ( 1/2,1/2,2,|\rho|^2 )$ basically contains the same information as the complex correlation coefficient.
 	$F_{1,2} ( a,b,c,d )$ is the Gauss hyper-geometric function,
@@
 	$n_{ar} + i n_{ai}$ is the second additive speckle noise component with $E(n_{ar}) = E(n_{ai}) = 0$ and $var(n_{ar}) = var(n_{ai}) = \frac{1}{2} (1-|\rho|^2)^{1.32}$.
-The model is overly complicated and to do speckle filtering, various approximations has to be used.
-
-In 2009, Lee \cite{Lee_CRCPress_2009} proposed to model $S_hS_v^*$ in a different approach.
-The phase difference is defined as:
-\begin{equation}
+
+The model is overly complicated and to do speckle filtering, various approximations have to be used.
+
+Another different approach is proposed bu Lee \cite{Lee_CRCPress_2009}  to model $S_hS_v^*$.
+In this method, the phase difference is defined as:
+\begin{equation*}
 \phi = \arg{ \left( S_pS_q^* \right) }
-\end{equation}
-Lee gives the PDF for the phase difference as:
-\begin{equation}
+\end{equation*}
+and the PDF for the phase difference as:
+\begin{equation*}
 pdf(\phi) = \frac{\Gamma(3/2) (1-|\rho|^2) \beta}{2 \sqrt{\pi} \Gamma(1) (1-\beta^2)} + \frac{(1-|\rho|^2)}{2 \pi} F_{1,2}(1,1,1/2,\beta^2)
-\end{equation}
-with
+\end{equation*}
+where
 	$\beta = |\rho| cos(\phi-\theta)$ and
@@
 
-The normalized magnitude which is defined as
-\begin{equation}
+The normalized magnitude, is defined as:
+\begin{equation*}
 \xi = \frac{E \left( S_pS_q^* \right)}{\sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }}
-\end{equation}
-and the PDF is given as
-\begin{equation}
+\end{equation*}
+and the PDF is found to be:
+\begin{equation*}
 pdf(\xi) = \frac{4\xi}{\Gamma(1)(1-|\rho|^2)} I_0 \left( \frac{2 |\rho| \xi}{1-|\rho|^2} \right) K_0 \left(  \frac{2 \xi}{1-|\rho|^2} \right)
-\end{equation}
-with
+\end{equation*}
 	$I_0$ and $K_0$ are modified Bessel functions.
+
 Again the equations looks overwhelmingly complex, and as admitted by the authors themselves:
-	this do not allow for easy speckle filtering as the model is too complex and 
-	the complex correlation coefficient $\rho$ is not easy to be estimated \cite{Lee_CRCPress_2009}
-
-There are several other attempts to filter POLSAR data.
-Vasile, 2006 proposed to region growing adaptive neighborhood approach, where averaging is performed on an adaptive homogenous neighbor.
-The draw back of the approach is that only the intensity was used to determine homogeneity and primitivev averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
+	this does not allow for easy speckle filtering as the model is too complex and 
+	the complex correlation coefficient $\rho$ is not easily estimated \cite{Lee_CRCPress_2009}
+
+There have been several other attempts to filter POLSAR data.
+Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogenous neighbour.
+The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
 %J.S. Lee is also very active in POLSAR speckle filtering.
 In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogenous pixels based on their underlying scattering model. 
-While the work is interesting, it is believed that pixels having similar underlying model, says volume scattering, can still be of very different nature.
-Similar to Lee's previous work, simple weighted average filtering is applied on both diagonal and off-diagonal elements.
-Vasile, 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
+While the work is interesting, it is believed that pixels having similar underlying models, for example volume scattering, can still be of a very different nature.
+Similar to Lee's previous work, a simple weighted average filtering is applied on both diagonal and off-diagonal elements.
+Vasile, in 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
 While polarimetric information is estimated independently from the power span, its output results no longer follow established Wishart distribution.
@@
 %We will discuss our approach in the next section.
-In summary, while off-diagonal elements, which carries phase information, is important in intepreting POLSAR data \cite{Rodionova_2009_ESASP}, their estimation and filtering is under-developed.
-We will discuss our approach based on polarization basis transformation in the next section.
+In summary, while off-diagonal elements, which carry phase information, are known to be important in interpreting POLSAR data \cite{Rodionova_2009_ESASP}, their estimation and filtering is under-developed in the current research literature.
+%We will discuss our approach ??) based on polarization basis transformation in the next section.
+(comment: This chapter is about background.
+So your ìapproachî should not be included in this chapter.
+From our today conversation, I now know that the various sections are ëassembledí from the various conference papers you published.
+But you will need to re-arrange the various parts into the appropriate Chapter for the Thesis)
 
@@
 
-\subsection{Current Methods to Evaluate (POL)SAR Speckle Filters}
-
-It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
-	homogeneous and heterogeneous region evaluation.
-Across homogeneous areas, speckle filters are expected to estimate with negligible radiometric bias.
-As such, evaluating speckle filters over homogeneous areas has traditionally been focused on evaluating the variation of the estimators'
-	output (a.k.a the speckle suppression power).
-In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
-	due in part to the following difficulties.
-The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
-The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
-	to be measured and compared.
-
-In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
-Furthermore, the application of any speckle filter in a SAR processing framework
-   should enable an improvement in the measurement, 
-	detection or classification of the underlying radiometric features.
-As shown in the subsequent sections, by applying log-transformation, 
-	this overall requirement of speckle filtering can be further broken down into two smaller requirements.
+\subsection{Current Methods to Evaluate SAR Speckle Filters}
+
+Because of the variaties of  speckle filtering available, it is hence crucial to have a framework for 
+	(a) modelling and simulation, which provide the ground-truth data in different scenarios of underlying distribution, and
+	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
+	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.
+
+This section reviews the published literature for the different techniques used to evaluate SAR speckle filters.
+%In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
+%Furthermore, the application of any speckle filter in a SAR processing framework
+%   should enable an improvement in the measurement, 
+%	detection or classification of the underlying radiometric features.
+% (??? I suggest move these sections to Chapter 3 or 4, if they are really in this Chapter), 
+%.
+% (The above is your proposal. It should not appear here in Chpater 2)
+The overall requirement of speckle filtering can be broken down into two smaller requirements.
 On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
@@
 On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
-These requirements can be measured and evaluated by determining, also in the log-transformed domain, the bias 
-	and variance error of the output.
-As the MSE evaluation is a combination of bias and variance error, it is therefore capable of evaluating 
-	the general requirements of speckle filtering.
-
-For homogeneous scenes where the underlying radiometry is assumed to be constant, 
-	the filtered results are considered, statistically speaking, to be samples of 
-	a single but complex stochastic process.
-From a logarithmic transformation perspective, the radiometric preservation and speckle suppression requirements 
-	of speckle filters can be judged using the familiar bias and variance evaluation.
-
 One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
-	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech} \cite{Medeiros_2003_IJRS}.
+	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech,Medeiros_2003_IJRS}.
 A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
-In the log-transformed domain, the equivalent criteria for evaluation could be performed by a simple subtraction.
-In other words, it is clear that the bias evaluation in the log-transformed domain 
-	can be used to evaluate the radiometric preservation requirement of speckle filters.
-
-Specifically for homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
-	in the original domain the ``standard'' filters (boxcar, Lee\cite{Lee_PAMI_1980}, 
-	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
-	MAP\cite{Lopes_IGARSS_1990}) and their enhanced versions \cite{Lopes_TGRS_1990} can achieve negligible bias. 
-In this paper, we will also show that all of these standard filters preserve
-	not only the expected radiometric values
-	but also a number of subtractive and consistent measures of distance exhibited in the log-transformed domain.
-
-Several metrics have been developed to evaluate speckle suppression power.
+%For homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
+%	in the original domain the ``standard'' filters (boxcar, Lee \cite{Lee_PAMI_1980}, 
+%	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
+%	MAP\cite{Lopes_IGARSS_1990}) and the enhanced version \cite{Lopes_TGRS_1990} can achieve negligible bias. 
+%In this paper, %****IVM you need to search for the word "paper" in case you have more of these
+Several metrics have also been developed to evaluate speckle suppression power.
 The most common measure is the Equivalent Number of Looks (ENL) index 
@@
 Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
-In Section \ref{sec:eval_homo}, it will be shown that, for homogeneous areas, ENL is mathematically related to variance in the 
-	log-transformed domain.
-Subsequently, we propose the use of log-variance to evaluate the noise suppression power of speckle filters, 
-	which is the primary criteria used to evaluate speckle filters over homogeneous area.
+%****IVM: the section reference below is not found (is displayed as ??)
+
+It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
+	homogeneous and heterogeneous region evaluation.
+Across homogeneous areas, speckle filters are expected to be estimated with negligible radiometric bias.
+As such, evaluating speckle filters over homogeneous areas has traditionally focused on evaluating the variation of the estimators'
+	output (a.k.a the speckle suppression power).
+%In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
+%	due in part to the following difficulties.
+%The first obstacle is to determine an absolute ground-truth against which quantitative criteria can be measured.
+%The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
+%	to be measured and compared.
 
@@
 	real-life images.
-And hence, the need for speckle filters estimation is warranted.
+And hence, the need for speckle filter estimation is warranted.
 
@@
 harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}.
-We therefore propose to adopt a log-transformed domain perspective 
-  where the multiplicative noise would then be transformed into a more familiar additive model.
-More importantly, the ratio image would then become a simple subtraction image.
-The evaluation methodology for such adoption would not change. 
-Only that the residual image would become linear and additive.
-And thus it would be more natural to be displayed and evaluated visually (see \ref{sec:schema_log_images}).
-
-Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
+
+%There are two main ways that ground truths are used in evaluating speckle filters.
+%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
+%Normally the image is large, with a number of different features and test conducted in once. 
+%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
+%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
+%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
+%
+%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
+%Since the structure is repeated many times, the combined results become more representative.
+Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
+%The drawback is that only a single type of target can be tested per image.
+These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).
+
+Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
+This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
+Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
+	normally at local or regional levels.
+In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
+	is likely to perform poorly in terms of preserving underlying radiometric differences 
+	(e.g. causing excessive blurring).
+Furthermore, we have not found many published articles combining the evaluation
+  of these two seemingly contradicting requirements.
+
+%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
+%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
+%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
+%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
+%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
+%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
+%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
+%	where $E()$ denotes expectation operator.
+
+Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
+However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
+Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
+Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
+	subjective in nature.
+
+Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
+However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
+	the use of MSE is not straightforward. 
+Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
+  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
+The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
+Others have suggested the use of normalised MSE, which is essentially the ratio between MSE and the expected mean.
+
+In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
+Furthermore, the application of any speckle filter in a SAR processing framework
+   should enable an improvement in the measurement, 
+	detection or classification of the underlying radiometric features.
+Thus, another way to evaluate speckle filters is by comparing the feature preservation characteristics 
 of the original noised data and those of the filtered image.
+This can be applied not only whether or not the ground-truth is available precisely.
 When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
 Evaluation would then determine how closely related the two feature maps are.
+
 Various methods may be applied to extract features; examples of those that have been used are the 
@@
 	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
-	how to interpret the results, especially its accuracy.
-
-Since SAR statistical models are quite well understood, 
-	simulation experiments with known ground-truth can be employed 
-		to evaluate speckle filters.
-In this paper, we also make use of a methodology similar to the ones discussed above with two important changes.
-Firstly, our simulated experiments offer absolute ground-truth.
-Secondly, our threshold-based feature extraction algorithm is extremely simple.
-More importantly, the dependency between the performance of the algorithm and the level of noise is well established. 
-This performance can be 
-	conveniently visualized by plotting the Receiver Operating Characteristics Curve (ROC).   
-It can also be objectively quantified by measuring the Area Under this Curve (AUC). 
-As shown in section \ref{sec:eval_hetero}, this standard and normalized criteria allows a comparative evaluation of 
-	feature preservation capabilities for different speckle filters.
-
-%There are two main ways that ground truths are used in evaluating speckle filters.
-%A simple method is to embed speckle noise into an existing optical image, and then use the filters to estimate noise-free imagary from this. 
-%Normally the image is large, with a number of different features and test conducted in once. 
-%The benefit of this method is that a wide range of features can be tested, which is probably closer to the real-life situation. 
-%The main drawback is that, since the noise embedding process is stochastic in nature, reporting only a single experimental is probably not providing a very representative result. 
-%It is of course, also dependent upon the nature of the test image and noise embedded process employed.
-%
-%Another method is to evaluate using a patterned, structured and repeated ground truth which may be artificial or real.
-%Since the structure is repeated many times, the combined results become more representative.
-Also, the patterns can be pre-designed and lead to the possibility of repeatable evaluations between research groups.
-%The drawback is that only a single type of target can be tested per image.
-These types may normally be point targets, edges and lines (all features that are currently used to evaluate speckle filters).
-
-Even with known ground-truth, evaluating metrics need to be defined for quantitative measurements.
-This is the second difficulty in evaluating speckle filters for heterogeneous scenes.
-Under the conditions of heterogeneity, the standard speckle filters still introduce radiometric loss, 
-	normally at local or regional levels.
-In fact, the common consensus is that a powerful speckle suppression filter (for example the boxcar filter) 
-	is likely to perform poorly in terms of preserving underlying radiometric differences 
-	(e.g. causing excessive blurring).
-Furthermore, we have not found many published articles combining the evaluation
-  of these two seemingly contradicting requirements.
-
-Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
-However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
-Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
-Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
-	subjective in nature.
-
-%Similar to the ENL index in homogeneous area, in establishing an evaluation metric, 
-%	it is desirable that the criteria should also be scene-independent\cite{Shi_IGARSS_1994}.
-%The most common measure of difference in image processing methods is to compute some substractive distances, either in intensity or in amplitude domain. 
-%However since SAR noise is multiplicative in the original domain, these differences are not only dependent on the noise level but also on the amplitude level of the signal itself.
-%Shi \cite{Shi_IGARSS_1994} define sharpness as the ratio between
-%Shi define the mid-point position of an edge as the intensity value between the nominal values of the two regions, $M= { E(X_t) + E(X_b)}/{2}$
-%	and the sharpness of an edge as the slope between the two nominal intensities value, $S=E(X_t)-E(X_b)$, 
-%	where $E()$ denotes expectation operator.
-
-Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
-However since SAR data is heteroskedastic, which violates the assumptions of the Gauss-Markov theorem, 
-	the use of MSE is not straightforward. 
-Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
-  the ratio between the expected mean of the signal and the RMSE of the removed noise. 
-The metric is argued to be similar in interpretation to the standard signal-to-noise ratio (SNR). 
-Others have suggested the use of normalized MSE, which is essentially the ratio between MSE and the expected mean.
+	how to interpret the results, especially in terms of accuracy.
+As such, the problem of establishing an single evaluation criteria to evaluate the overall performance of speckle filters remains open for improvement.
 
@@
 
-In this paper, homoskedastic property is shown to be available after logarithmic transformation of SAR data.
-As the important Gauss-Markov theorem becomes applicable in this transformed domain, 
-	the use of MSE is shown to be again relevant for evaluating statistical estimators (i.e. speckle filters).
-Intuitively, each components of the MSE measure, 
-	namely bias and variance evaluation, can be mapped into 
-	the requirements of radiometric preservation and speckle suppression for speckle filters.
-Before the details of our evaluation methodology is presented and discussed, 
-	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
-
-\subsection{Existing Dis-similarity Measures for (POL)SAR data}
-
-to detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
-  which have $L_x$ and $L_y$ as the corresponding number of looks,
-  come from the same underlying stochastic process,
-Conradsen considered \cite{Conradsen_2003_TGRS_4} the following POLSAR statistics
-\begin{equation}
-  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-\end{equation}
-
-Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then we have
-\begin{eqnarray}
-  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
-  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
-\end{eqnarray}
-
-Since both $Z_x$ and $Z_y$ follow complex wishart distribution with $L_x$ and $L_y$ degrees of freedom,
-  $Z_x+Z_y$ also follows the complex wishart distribution with $L_x + L_y$ degrees of freedom.
-In view of the models denoted in Eqn. \ref{eqn:log_determinant_distribution},
-  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
-  but the whole statistical distribution for it can be simulated as well:
-\begin{eqnarray}
-%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
-%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
-  \ln{Q} &\sim&  q + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim& e^q \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
-\end{eqnarray}
-where $q = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-
-In the special case of $L_x = L_y$, the Conradsen statistics become
-$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
-%Our approach suggest a slightly simpler statistics which probably will work just as well: the contrast
-The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should, under exactly the same assumptions, provides another consistent and equivalent approach,
-  with probably simpler conceptual model and computational derivations. 
-%a slightly simpler statistics.
-The details application of this in edge-detection however is outside the scope of this paper.
-
-\subsection{The need for Scalar Consistent Measures of Distance}
-	We will show our originality and significance here!
-
-This section surveys recent developments in the research landscape. 
-First, the stochastic nature of SAR speckle phenomena is explained. 
-Then, the topic of SAR speckle is reviewed from the perspective of statistical estimation theory. 
-An opportunity for contribution in proposing a stochastic simulation and evaluation framework is identified. 
-Next, the applications of such a framework into the problem of POLSAR speckle filtering is described. 
-Recently, the practicality of Partial Polarimetry has been noticed and studied. 
-The need for reconstruction of Full Polarimetric signatures is highlighted and the possible application of the proposed framework is described. 
-Last but not least will be an illustration on the applicability of such a framework to the topic of target detection and classification.
-
-%\subsection{POLSAR speckle filter}
-
-	%\section{The Need for Scalar Consistent Measures of Distance}
-
-	%\section{Research Framework: Originality and Significance}
+%In this paper, 
+%	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
+%****IVM:  Hai, please be consistent in using "Section" or "section".
+My advice would be to use the capitalised form whenever you talk about a section number, and the lower case form for discussing a section.
+For example: "look at Section 1.4 or consider the previous section".
+This instance is fine, but I noticed a few above that might need to be changed.
+
+%\subsection{Existing Discrimination Measures for (POL)SAR data}
+%
+%(comment: you need to have a lead-in paragraph to link this section from the other)
+%To detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+%  which have $L_x$ and $L_y$ as the corresponding number of looks,
+%  come from the same underlying stochastic process,
+%Conradsen \cite{Conradsen_2003_TGRS_4} considered the following POLSAR statistics
+%\begin{equation*}
+%  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+%\end{equation*}
+%
+%Taking the log-transformation of the above statistics, and noting that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then we have;
+%\begin{eqnarray*}
+%  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
+%  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
+%\end{eqnarray*}
+%
+%Since both $Z_x$ and $Z_y$ follow complex Wishart distributions with $L_x$ and $L_y$ degrees of freedom,
+%  $Z_x+Z_y$ also follows the complex Wishart distribution with $L_x + L_y$ degrees of freedom.
+%In view of the models denoted later in Eqn. \ref{eqn:log_determinant_distribution},   
+%%***IVM: Hai, can you please check this equation reference (it comes out as eqn. 4.9 which I don't have in this document)
+%  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+%  but the whole statistical distribution for it can be simulated as well:
+%\begin{eqnarray*}
+%%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%  \ln{Q} &\sim&  q + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+%  Q &\sim& e^q \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
+%\end{eqnarray*}
+%where $q = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+%
+%In the special case of $L_x = L_y$, the Conradsen statistics become
+%$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
+%%Our approach suggest a slightly simpler statistics which probably will work just as well: the contrast
+%The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should, under exactly the same assumptions, provides another consistent and equivalent approach,
+%  with probably simpler conceptual model and computational derivations. 
+%%a slightly simpler statistics.
+%The detailed application of this for the task of edge-detection however is outside the scope of this thesis.%paper.
+(Commet: I suggest this section to be removed since it would not be referred to in the remainig of the thesis)
+%
+%%\subsection{The need for Scalar Representative and Homoskedastic Models}
+%%	We will show our originality and significance here!
+%
+%%This section surveys recent developments in the research landscape. 
+%%First, the stochastic nature of SAR speckle phenomena is explained. 
+%%Then, the topic of SAR speckle is reviewed from the perspective of statistical estimation theory. 
+%%An opportunity for contribution in proposing a stochastic simulation and evaluation framework is identified. 
+%%Next, the applications of such a framework into the problem of POLSAR speckle filtering is described. 
+%%Recently, the practicality of Partial Polarimetry has been noticed and studied. 
+%%The need for reconstruction of Full Polarimetric signatures is highlighted and the possible application of the proposed framework is described. 
+%%Last but not least will be an illustration on the applicability of such a framework to the topic of target detection and classification.
+%
+%%\subsection{POLSAR speckle filter}
+%        
+%	%\section{The Need for Scalar Consistent Measures of Distance}
+%
+%	%\section{Research Framework: Originality and Significance}
+
+\section{Summary }
+
+This chapter has
+  not only described the multi-dimensional and stochastic nature of the POLSAR data, but
+  also illustrates the different published approaches to address the grand challenge of modelling, processing and understanding this type of data.   
+Specifically it shows that
+while the statistical model for SAR is quite well understood,
+the understanding of the complex POLSAR statistical model trails behind.
+The complex POLSAR data have been statistically modelled as following the complex Wishart distribution, which apparently is multi-dimensional, complex and thus un-intuitive.
+There have been a few published scalar statistical models for POLSAR,
+but none of them is highly representative of the multi-dimensional data.
+None of them have so far led to published discrimination measures. 
+%but none of them fit the dual criteria of being highly representative of the data and at the same time lead to scalar discrimination measures.
+A few POLSAR discrimination measures have also been proposed, but all of them are based on likelihood test statistics, which so far have only shown to be based on an asymptotic distribution.
+
+The chapters also illustrated many different ways to combat  the negative impact caused by multiplicative and heteroskedastic properties on the statistical estimation process,
+  which includes statistical modelling of the data, estimator development and the estimator performance evaluation.
+Specifically, it showed that when the sense of subtractive distance is not consistent for SAR data, the ratio is proposed as its discrimination measure \cite{Rignot_1993_TGRS_896}.
+It also showed that while the MMSE criteria is not very suitable to evaluate SAR speckle filters, other criteria such as radiometric preservation and speckle suppression power evaluation are employed.
+Unfortunately, these counter-intuitive measures are fragmented and thus not very popular outside the SAR community.
+
+In the next chapters, theoretical models are built to form the foundation required to systematically tackle these issues.

### 2013-07-24 3/sar.tex
updated for Ian changes

@@
-\chapter{Consistent Measures of Distance for Univariate SAR Data} %chapter 3
+\chapter{Homoskedastic Models for Heteroskedastic SAR Data} %chapter 3
 \label{chap:sar}
 
-%\section{SAR speckle statistic model}
-%\label{sec:heteroskdastic_model}
-
-Useful and robust statistical estimators require un-assuming models. 
-In this chapter a homoskedastic model for the usually heteroskedastic SAR is proposed. %speckle filtering.
-In the first section the heteroskedastic nature of original amplitude and intensity SAR data will be explained. 
-Relying solely on statistical principles,
-  log-transformed SAR data is shown to be homoskedastic.
-Together with the consistent sense of variance, a few consistent measures of distance are proposed for the traditional SAR data.
+This chapter  highlights that SAR
+                data are heteroskedastic in the original domain.
+Relying solely on statistical and mathematical principles,             
+the log-transformed SAR data is shown to be homoskedastic.
+From there, the consistent sense of variance and a few consistent measures of distance are proposed and validated against real-life
+                practical SAR data.
 
@@
 
-SAR speckle phenomena are explained as the interference of many coherent but dephased back-scaterring components;
-  each reflecting from different and distributed elementary scaterers \citep{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
-The random nature of the SAR data arises
-  due to the unknown and varying location, height and thus distance of each elementary scaterer;
-  which, in turn, generates random phases in their back-scattering responses.
-Assuming the number of these elementary back scatterers is sufficiently large,
-  then the Central Limit Theorem is applicable \citep{Goodman_Springer_1975}.
-Consequently the interference of these randomly phased responses can be considered as
-  a random walk on the 2D complex plane \citep{Goodman_JOptSocAm_76}.  
-Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
-  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \citep{Lee_CRCPress_2009}. 
-Their probability density functions (PDF) are given as:
+The stochastic nature of SAR data has been illustrated earlier (see Eqns. \ref{eqn:SAR Amplitude PDF} and \ref{eqn:SAR Intensity PDF}).
+From a statistical viewpoint, the multiplicative nature of amplitude ($A$) and intensity ($I$)  data can be explained as follows. 
+Let us consider two fixed unit distributions which are independent to $\sigma$ given below:
 
 \begin{equation}
-\label{eqn:SAR Real and Imaginary Components PDF}
-\caption{eqn:SAR Real and Imaginary Components PDF}
-pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
+\label{eqn:SAR Unit Amplitude PDF}
+\caption{eqn:SAR Unit Amplitude PDF}
+pdf(A_1) = 2A_1 e^{ \left( A_1^2 \right) }
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Unit Intensity PDF}
+  \caption{eqn:SAR Unit Intensity PDF}
+pdf(I_1) = e^{ \left( -I_1 \right) }
 \end{equation}
 
-It can then be proved that the measurable amplitude $A=\sqrt{A_r^2+A_i^2}$ is a random variable of Rayleigh distribution
-  and subsequently the SAR intensity $I=A^2=(A_r^2+A_i^2)$ is a random variable of a negative exponentially distributed random process.
-That is:
-
-\begin{eqnarray}
-pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
-pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
-\end{eqnarray}
-
-From a statistical viewpoint, the multiplicative nature of amplitude and intensity data can be explained as follows. 
-Let us consider two fixed, independent to $\sigma$ unit distributions given below:
-
-\begin{eqnarray}
-pdf(A_1) &=& 2A_1 e^{ \left( A_1^2 \right) }\\
-pdf(I_1) &=& e^{ \left( -I_1 \right) }
-\end{eqnarray}
-
 Using the variable change theorem,
-%  it is then trivial to show that:
-    it can be shown that:
+    it can be shown that
     the SAR amplitude and intensity are equal to %are simply
@@
     specifically $A= \sigma A_1 $ and $I= \sigma^2 I_1 $. 
-These relationships evidently manifest a mutiplicative nature. 
+These relationships evidently display a mutiplicative nature. 
 In fact, the condition has long been noted,
@@
 
-Let us now consder the population expected mean and variance of the four distributions.
+Let us now consider the population expected mean and variance of the four statistical distributions for these observables, i.e. $A, A_1, I, I_1$.
 They are given in Table \ref{tbl:orginal_sar_avg_var}. 
-If spatial homogeneity is defined as an imaging areas having the same back-scattering coefficient $\sigma$,
+If spatial homogeneity is defined as an imaging area having the same back-scattering coefficient $\sigma$,
   then over a homogeneous scene, the measured values can then be considered as samples coming from a single stochastic process.
 However, over heterogeneous areas where $\sigma$ varies significantly,
-  it is then evidently clear that: the amplitude ($A$) as well as the intensity ($I$) of SAR data suffer from hetoroskedastic phenomena,
-  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean. 
+  it is then evidently clear that: the amplitude  as well as the intensity of SAR data suffer from hetoroskedastic phenomena. 
+%  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean.
+This means that  the conditional expected variance of SAR data is dependent on the conditional expectation of the mean.   
 In the context of speckle filtering which aims to estimate the unknown parameter $\sigma$,
-  Table \ref{tbl:orginal_sar_avg_var} also clearly indicates the ambiguous circle.
-That is, in the original domain, estimating variance is equal to estimating the mean
-  and is as hard as the main problem itself.
-  %, i.e. estimating the unknown parameter $\sigma$
+  Table \ref{tbl:orginal_sar_avg_var} also clearly indicates an ambiguous circle:
+in the original domain, estimating variance is equal to estimating the mean, but this is as hard to estimation as the variance.
 
@@
 
-The formulas above have long been noted in this research field. 
+The formulas above are extremely well known in this research field. 
 In fact while pioneering the estimation of the equivalent number of look (ENL) index, 
- it has been noted that the ratio of expected standard deviation to mean is a constant in both cases (i.e. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$) \cite{Lee_1992_IMA_298}.
-Here we just offer a different perspective,
-  one that avoids the negative effects of heteroskedasticity in SAR data processing.
+ it was noted by Lee et.al. that the ratio of expected standard deviation to mean is a constant in both cases (i.e. $snr(A)=\sqrt{\frac{4}{\pi}-1}$ and $snr(I)=1$) \cite{Lee_1992_IMA_298}.
+%Here we just offer a different perspective,
+%  one that avoids the negative effects of heteroskedasticity in SAR data processing.
 %Here, we just offer a different interpretation, which sets the stage for the discussion of logarithmic transformation.
 
-\section{The Effects of Heteroskedasticity in SAR Data Processing}
+In this thesis, a different perspective will be proposed which avoids the negative effects of heteroskedasticity in SAR data processing.
+
+\section{The Effects of Heteroskedasticity in SAR Processing}%IVM: shortened to make it look nicer
 
@@
 Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
-%For about 30 years, speckle filtering has been an active research area, with new methods being introduced steadily \cite{Lee_TGRS_2009}. 
-%That is because
-And while the statistical model within individual resolution cells is well established,
-  the applicability of these models, however, are restricted to homogeneous areas. 
-Practical images, nevertheless, are heterogeneous. 
-Crucially it is this spatial variation that is of high interest. 
-This fact gives rise to the question that seemed obvious:
+While the statistical model within individual resolution cells is well established,
+  it is only applicable to homogeneous areas.
+Practical images, however, are heterogeneous.
+Furthermore, it is precisely this spatial variation that is often of high interest.
+%And while the statistical model within individual resolution cells is well established,
+%  the applicability of these models, however, are restricted to homogeneous areas. 
+%Practical images, nevertheless, are heterogeneous. 
+%Crucially it is this spatial variation that is of high interest. 
+%This fact gives rise to the question that seemed obvious:
   %how to call an analysis area heterogeneous and subsequently
-  what to do in the case of heterogeneity.
+%  what to do in the case of heterogeneity.
 
-Various statistical models for heterogeneous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
-Unfortunately, while most of the models highlight the multiplicative nature of sub-pixel or homogeneous original SAR data, in extending the model to heterogeneous images, virtually none has noted that spatial variation also gives rise to heteroskedasticity phenomena.
+As such, various statistical models for heterogeneous areas have been proposed (see \cite{Touzi_2002_TGRS} for a detailed review). 
+However, while most of the models highlight the multiplicative nature of sub-pixel or homogeneous original SAR data, in extending the model to heterogeneous images, virtually none have noted that spatial variation also gives rise to heteroskedasticity phenomena.
 Heteroskedasticity, as explained later, is defined as the dependence of conditional expected variance of original SAR data on the conditional expectation of its mean or equivalently its underlying back-scattering coefficient $(\sigma)$.
 
-Speckle filtering, by and large, are estimators attempting to estimate the unknown coefficient $\sigma$ from the observable SAR signal $(A)$. 
-Thus, SAR speckle-filtering can be and has been positioned within the context of estimation theory \cite{Touzi_2002_TGRS}. 
-The statistical framework attempts to estimate unknown statistical parameters from the observable data. 
-The stages consist of statistical modelling, estimator development and evaluating the performance of the statistical estimators. 
+Speckle filters are effectively estimators attempting to estimate the unknown coefficient $\sigma$ from the observable SAR signal $(A)$. 
+Thus, SAR speckle-filtering can be and has been positioned within the context of estimation theory \cite{Touzi_2002_TGRS}, where
+the statistical framework is used to estimate unknown statistical parameters from the observable data. 
+The stages of this framework consist of statistical modelling, estimator development and evaluating the performance of the statistical estimators. 
 %In this section, the negative effects of heteroskedasticity on speckle filtering is analysed.
-It is believed that heteroskedasticity, in its turn, give rise to serious negative impacts on various stages of speckle-filtering.
+It is also known that heteroskedasticity gives rise to serious negative impacts on various stages of speckle-filtering.
 
 In modelling, heteroskedasticity has direct consequences in the central question of homogeneity or heterogeneity. 
-In optical images, the contrast or variance among neighboring pixels have been used to measure homogeneity. 
+In optical images, the contrast or variance among neighbouring pixels have been used to measure homogeneity. 
 Unfortunately such techniques do not appear to be effective under the heteroskedastic condition of original SAR data. 
@@
 
-A case in point can be found in the recently published improved sigma filter\cite{Lee_TGRS_2009}. 
+A case in point can be found in a recently published improved sigma filter \cite{Lee_TGRS_2009}. 
 The technique determines outlying points as being too far away from the standard deviation. 
@@
 Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations. 
-The caveat however is that in SAR speckle filtering, variance is not known \textit{a priori}. 
+The problem, however, is that in SAR speckle filtering, variance is not known \textit{a priori}. 
 And even though variance can be estimated from observable values, as the ambiguity circle goes, estimating the variance is as hard as estimating the underlying coefficient $\sigma$ itself.
 
-Heteroskedasticity also affects the performance evaluation stage of such a framework.
-Statistical estimators are routinely evaluated using their bias and variance performance,
-  which when combined normally results in MSE evaluation.
+Heteroskedasticity also affects the performance evaluation stage of the estimation framework.
+Statistical estimators are routinely evaluated using their bias and variance performance
+  which, when combined, normally result in MSE evaluation.
 Unfortunately, under heteroskedastic conditions, Least Squared Error estimation may not be optimal.   
-In other words, Minimal Squared Error can no longer serves as a reliable evaluation metric.
+In other words, Minimum Squared Error can no longer serves as a reliable evaluation metric.
 A number of different evaluation metrics have been proposed for SAR speckle filters,
   however, none have appeared capable of taking on the MSE's previous role.
-
-%Heteroskedasticity also decrease the effectiveness of estimators by increasing the variance of even the best possible estimations. 
-%This fact makes it tricky to evaluate the performance of different estimators, even if quantitative experimental results are reported.
-%In fact several quantitative simulated experiments has been carried out to compare the performance of different estimators\cite{Lee_TGRS_2009}. 
-%However only results of single experiments were reported. 
-%Due to the stochastic nature of the simulated experiment process, more experiments should be done to report the effectiveness, i.e. variance, of each estimators' results.
+%IVM: Hai, the above "Minimum Squared Error" should be Mean Squared Error???
 
@@
 All of these tasks require good discriminant functions. 
-Foundational to all of these is the need for a consistence sense of distance. 
+Fundamental to all of those is the need for a consistent measure of distance. 
 Unfortunately, by definition, heteroskedasticity provides inconsistent measures of distance. 
-This inconsistent sense of distance coupled with the failure of the ordinary least square regression methods are believed to have caused a large class of artificial neural networks as well as a number of other computational intelligence methods to under-perform on SAR data.
-
-%In our work, we aim to neutralize these various negative impacts. 
-%The paper is organized as follows. 
-%Section \ref{sec:heteroskdastic_model} will be devoted to discussion of the heteroskedastic phenomena in the original per-pixel SAR amplitude and intensity model. 
-%Logarithmic transformation is extended to the model and the homoskedastic property of it is asserted. 
-%Section \ref{sec:variance_in_log_domain} will discuss how sampling distribution of variance in the log-transformed domain can be used to model various degrees of homogeneity. 
-%Section \ref{sec:k_mle} will presents a novel speckle filtering algorithm developed from heterogenous inference made possible by statistical testing of sample variances.
-%Section \ref{sec:k_mle_result} will present evaluation of our estimator both quantitatively through simulated experiments and qualitatively on real-life images.
+This inconsistent measure of distance coupled with the failure of the ordinary least square regression methods have caused a large class of artificial neural networks as well as a number of other computational intelligence methods to under-perform for SAR data.
 
@@
 
-%\subsection{Homoskedastic effect of Logarithmic Transformation }
-
-In this chapter, a base-2 logarithmic transformtion is proposed for SAR data. 
-The choice of base-2 is due to implementation reasons
-  since base-2 logarithm can be computed faster on digital computer than either natural or decimal logarithms,
+In this section, a base-2 logarithmic transformation is proposed for SAR data. 
+The choice of base-2 is due to implementation reasons,
+  since base-2 logarithms can be computed faster by computer than either natural or decimal logarithms,
   and yet the ability to transform heterskedactic speckle into a homoskedastic relationship is still maintained.
@@
 
-\begin{eqnarray}
-L_{1}^{A} &=& \log_2(A_1) = L_{1}^{I} / 2 \\
-L_A &=& \log_2(A) 	= L_{1}^{A} + \log_2\sigma \\
-L_{1}^{I} &=& \log_2(I_1) = 2 L_{1}^{A} \\
-L_I &=& \log_2(I) 	= L_{1}^{I} + 2 \log_2\sigma
-\end{eqnarray}
+\begin{equation}
+  \label{eqn:SAR Unit Log Amplitude Observable}
+  \caption{eqn:SAR Unit Log Amplitude Observable}
+L_{1}^{A} = \log_2(A_1) = L_{1}^{I} / 2 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude Observable}
+  \caption{eqn:SAR Log Amplitude Observable}
+L_A = \log_2(A) 	= L_{1}^{A} + \log_2\sigma 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Unit Log Intensity Observable}
+  \caption{eqn:SAR Unit Log Intensity Observable}
+L_{1}^{I} = \log_2(I_1) = 2 L_{1}^{A} 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity Observable}
+  \caption{eqn:SAR Log Intensity Observable}
+L_I = \log_2(I) 	= L_{1}^{I} + 2 \log_2\sigma
+\end{equation}
 
 The equations above highlight the relationships among random variables in the log-transformed domain. 
-Two conclusions become evident from these formulae. 
+Two interesting points are evident from these formulae. 
 Firstly, in the log-transformed domain, working on either amplitude or intensity will tend to give identical results. 
@@
 is clearly manifested.
-Now, bearing the relationship among the random variables in mind, it is then trivial to 
-show that the probability distribution of these log-transformed variables are related as follows:
+Now, bearing in mind the relationship among the random variables, %it is then trivial to 
+%show that the probability distribution of these log-transformed variables are related as follows:
+application of variable change theorem leads to:
 
-\begin{eqnarray}
-pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left( 2 L_{1}^{A} \right)}e^{-2^{\left( 2 L_{1}^{A} \right) }} \\
-pdf(L_A) &=& 2 \cdot 2^{\left( 2 L_A - 2 \log_2 \sigma \right)}e^{-2^{\left( 2 L_A - 2 \log_2 \sigma \right)}} \\ 
-pdf(L_{1}^{I}) &=& 2^{L_1^I} e^{-2^{L_1^I}}  \\
-pdf(L_I) &=& 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
-%pdf(L_{1}^{A}) &=& 2 \cdot 2^{\left[ 2 L_{1}^{A} - 2^{2 L_{1}^{A}} \right]} \\
-%pdf(L_A) &=& 2 \cdot 2^{\left[ \left( 2 L_A - 2 \log_2 \sigma \right) - 2^{\left( 2 L_A - 2 \log_2 \sigma \right)} \right]} \\ 
-%pdf(L_{1}^{I}) &=& 2^{\left[ L_{1}^{I} - 2^{L_{1}^{I}} \right]} \\
-%pdf(L_I) &=& 2^{\left[ \left( L_I - 2 \log_2 \sigma \right) - 2^{\left( L_I - 2 \log_2 \sigma \right)} \right]} \label{eqn:log_intensity_base_2_dist}
-\end{eqnarray}
+\begin{equation}
+  \label{eqn:SAR Unit Log Amplitude PDF}
+  \caption{eqn:SAR Unit Log Amplitude PDF}
+pdf(L_{1}^{A}) = 2 \cdot 2^{\left( 2 L_{1}^{A} \right)}e^{-2^{\left( 2 L_{1}^{A} \right) }} 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude PDF}
+  \caption{eqn:SAR Log Amplitude PDF}
+pdf(L_A) = 2 \cdot 2^{\left( 2 L_A - 2 \log_2 \sigma \right)}e^{-2^{\left( 2 L_A - 2 \log_2 \sigma \right)}} 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Unit Log Intensity PDF}
+  \caption{eqn:SAR Unit Log Intensity PDF}
+pdf(L_{1}^{I}) = 2^{L_1^I} e^{-2^{L_1^I}}  
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity PDF}
+  \caption{eqn:SAR Log Intensity PDF}
+pdf(L_I) = 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
+\end{equation}
 
@@
 are obtained and presented in Table \ref{tbl:sar_log_domain_avg_var}, with $\gamma \approx 0.577$ being the Euler-Mascheroni constant. 
-Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$
+Most importantly, it can be seen that the means are biased and the variances are no longer related to $\sigma$.
 
@@
 
-Table \ref{tbl:sar_variables_properties} summarizes the discussion so far. 
-It can be seen that while the original data, especially intensity values, should be preferred for 
-multi-look processing, the log-transformed domain with its homoskedastic distribution offers consistent sense of variance.
+The discussion so far is further summarized in Table \ref{tbl:sar_variables_properties}.
+It shows that while the original data, especially intensity values, should be preferred for 
+multi-look processing, the log-transformed domain with its homoskedastic distribution offers a consistent sense of variance.
 
@@
 
-To experimentally validate this theoretical discussion, Fig. \ref{fig:modelled_response} plots the histogram of observable data within a 
-known homogenous area (from a RADARSAT2 image) against modelled PDF response. 
-An excellent agreement is observable in the graph which validate the log-transformed model. 
+To experimentally validate this theoretical discussion, real world data is extracted from a known  homogenous area (from within a RADARSAT2 image). The PDF histogram from this data is then plotted in 
+Fig. \ref{fig:modelled_response} along with the modelled PDF response. 
+The excellent agreement observable between the real world and modelled data tends to validate the log-transformed model. 
 %In fact, this modelling has been used successful in explaining speckle phenomena, also verified 
@@
 %}
-\caption{Observed histogram in homogenous area and modelled pdf response}
+\caption{Observed histogram of a homogenous area and modelled PDF response}
 \label{fig:modelled_response}
@@
 
-%\subsection{Consistent measures of distance in Log-Transformed domain}
-
 The consistent feature is explored and illustrated in this section from two different perspectives. 
@@
 With that, let us consider the dispersion random 
-variable defined as the distance between an observable sample and its expected value:
+variable which is defined as the distance between an observable sample and its expected value:
 
-\begin{eqnarray}
-D_A &=& A - avg(A) \\
-D_I &=& I - avg(I) \\
-D_{L^A} &=& L_A - avg(L_A) \\
-D_{L^I} &=& L_I - avg(L_I) 
-\end{eqnarray}
+\begin{equation}
+  \label{eqn:SAR Amplitude Distance Observable}
+  \caption{eqn:SAR Amplitude Distance Observable}
+D_A = A - avg(A)   
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Intensity Distance Observable}
+  \caption{eqn:SAR Intensity Distance Observable}
+D_I = I - avg(I)  
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude Distance Observable}
+  \caption{eqn:SAR Log Amplitude Distance Observable}
+D_{L^A} = L_A - avg(L_A)
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity Distance Observable}
+  \caption{eqn:SAR Log Intensity Distance Observable}
+D_{L^I} = L_I - avg(L_I) 
+\end{equation}
 
-Noting the results from the previous section, the PDF for these variable can be derived as follows:
+Noting the results from the previous section, the PDF for these variables can be derived as follows:
 
-\begin{eqnarray}
-pdf(D_A) &=& 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] } \\
-pdf(D_I) &=& \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
-pdf(D_{L^A}) &=& 2 \cdot 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} e^{-2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)}}\\
-pdf(D_{L^I}) &=& 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} e^{-2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)}}
-%pdf(D_{L^A}) &=& 2 \cdot 2^{\left[ \left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right) - 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} \right]} \\
-%pdf(D_{L^I}) &=& 2^{\left[ \left( D_{L^I} + \frac{\gamma}{\ln2} \right) - 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} \right]}
-\end{eqnarray}
+\begin{equation}
+  \label{eqn:SAR Amplitude Distance PDF}
+  \caption{eqn:SAR Amplitude Distance PDF}
+pdf(D_A) = 2 \cdot \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)}{\sigma^2}e^{ \left[ - \frac{\left( D_A + \sigma \sqrt{\pi}/2 \right)^2}{\sigma^2}   \right] }
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Intensity Distance PDF}
+  \caption{eqn:SAR Intensity Distance PDF}
+pdf(D_I) = \frac{1}{\sigma^2}e^{\left[ -\left( D_I + \sigma^2 \right) / \sigma^2 \right] } \\
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude Distance PDF}
+  \caption{eqn:SAR Log Amplitude Distance PDF}
+pdf(D_{L^A}) = 2 \cdot 2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)} e^{-2^{\left( 2 D_{L^A} + 2 \frac{\gamma}{2 \ln2} \right)}}
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity Distance PDF}
+  \caption{eqn:SAR Log Intensity Distance PDF}
+pdf(D_{L^I}) = 2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)} e^{-2^{\left( D_{L^I} + \frac{\gamma}{\ln2} \right)}}
+\end{equation}
 
-From these equations, it is clear that these distributions, which are dependent on $\sigma$ in the original domain, 
-are now independent of it when processed in the log-domain.
+It is clear that these distributions are dependent on $\sigma$ in the original domain (the upper two equations), are now independent of it when processed in the log-domain (the lower two equations).
 
-Let us investigate SAR data from the second perspective,
+Let us now investigate SAR data from the second perspective,
   where two adjacent resolution cells are known to have \textit{an identical but unknown} back-scattering coefficient $\sigma$.
@@
 
-%From a second perspective, given two adjacent resolution cells that are known to have \textit{identical but unknown} back-scattering coefficient $\sigma$,
-%  consider the contrast random variable defined, also in the log-transformed domain, as the distance between two 
-%measured samples:
+\begin{equation}
+  \label{eqn:SAR Amplitude Contrast Observable}
+  \caption{eqn:SAR Amplitude Contrast Observable}
+C_A = A_1^\sigma - A_2^\sigma 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Intensity Contrast Observable}
+  \caption{eqn:SAR Intensity Contrast Observable}
+C_I = I_1^\sigma - I_2^\sigma 
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude Contrast Observable}
+  \caption{eqn:SAR Log Amplitude Contrast Observable}
+C_{L^A} = L_1^{A_\sigma} - L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity Contrast Observable}
+  \caption{eqn:SAR Log Intensity Contrast Observable}
+C_{L^I} = L_1^{I_\sigma} - L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
+\end{equation}
 
-\begin{eqnarray}
-C_A &=& A_1^\sigma - A_2^\sigma \\
-C_I &=& I_1^\sigma - I_2^\sigma \\
-C_{L^A} &=& L_1^{A_\sigma} - L_2^{A_\sigma} = log_2 { \left( {A_1}/{A_2} \right) }\\
-C_{L^I} &=& L_1^{I_\sigma} - L_2^{I_\sigma} = log_2 { \left( {I_1}/{I_2} \right) }
-\end{eqnarray}
-
-Noting that $C_x = D_1^x - D_2^x$, it should come as no suprise that the measure of contrast is also consistent in the 
+Noting that $C_x = D_1^x - D_2^x$, it should come as no surprise that the measure of contrast is also consistent in the 
 log-domain but inconsistent in the original domain. The PDF of the log-transformed variables can be expressed as:
 
-\begin{eqnarray}
-pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{\left[ 1+2^{\left( 2 C_{L^A} \right)} \right]^2} \ln2  \\
-pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{\left[ 1+2^{\left( C_{L^I} \right)} \right]^2} \ln2 
-%pdf(C_{L^A}) &=& 2 \frac{2^{\left(2 C_{L^A} \right)}}{1+2^{\left( 2 C_{L^A} \right)}} \ln2  \\
-%pdf(C_{L^I}) &=& \frac{2^{\left( C_{L^I} \right)}}{1+2^{\left( C_{L^I} \right)}} \ln2 
-\end{eqnarray}
+\begin{equation}
+  \label{eqn:SAR Log Amplitude Contrast PDF}
+  \caption{eqn:SAR Log Amplitude Contrast PDF}
+pdf(C_{L^A}) = 2 \frac{2^{\left(2 C_{L^A} \right)}}{\left[ 1+2^{\left( 2 C_{L^A} \right)} \right]^2} \ln2
+\end{equation}
+\begin{equation}
+  \label{eqn:SAR Log Intensity Contrast PDF}
+  \caption{eqn:SAR Log Intensity Contrast PDF}
+pdf(C_{L^I}) = \frac{2^{\left( C_{L^I} \right)}}{\left[ 1+2^{\left( C_{L^I} \right)} \right]^2} \ln2 
+\end{equation}
 
@@
 As can be seen, it shows excellent agreement between the analytical PDF and the observable histogram of dispersion and contrast computed from an homogeneous area in the image.
-%To illustrate this property, Fig. \ref{fig:residual_as_noise} is generated by using data from the RADARSAT-2 
-%image. As can be seen, it shows excellent agreement between the analytical pdf and the observable histogram of dispersion
-%and contrast of an homogeneous area in the image. 
-%Distance is calculated as the difference between each value point and the average value of that region, 
-%while contrast is calculated as the difference between two horizontally adjacent values in the log-transformed domain.
 
@@
 \end{tabular}
-\caption{Observed and modelled pdf of dispersion 
-and contrast in homogenous log-transformed intensity images.}
+\caption{Observed and modelled PDF of dispersion 
+and contrast in homogeneous log-transformed intensity images.}
 \label{fig:residual_as_noise}
@@
 
-Given that real SAR images are heterogenous and the back-scattering coefficient is unknown, it is evident that 
-the measure of observable contrast in original SAR data differs, i.e. is inconsistent, across different homogenous 
+Given that real SAR images are heterogeneous and the back-scattering coefficient is unknown, it is evident that 
+the measure of observable contrast in original SAR data differs, i.e. is inconsistent, across different homogeneous 
 areas. On the other hand, the observable contrast in the log-transformed domain is consistently the same across 
-different homogenous areas. As such, one possible benefit is that should the sigma filter \cite{Lee_TGRS_2009} be 
+different homogeneous areas. As such, one possible benefit is that should the sigma filter \cite{Lee_TGRS_2009} be 
 designed against the $pdf(C_{L^I})$, then the scale estimator would probably no longer be required.
@@
 
-\begin{eqnarray}
-pdf(V_{L^I}) &=& 
-	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)\\
-pdf(V_{L^A}) &=&
+\begin{equation}
+  \label{eqn: SAR Two Samples Log Intensity Variance PDF}
+  \caption{eqn: SAR Two Samples Log Intensity Variance PDF}
+pdf(V_{L^I}) = 
+	\frac{\ln2}{2} \frac{1}{\sqrt{V_{L^I}}} \left( \frac{2^{\sqrt{V_{L^I}}}}{\left( 1+2^{\sqrt{V_{L^I}}} \right)^2} + \frac{2^{-\sqrt{V_{L^I}}}}{\left( 1+2^{-\sqrt{V_{L^I}}} \right)^2} \right)
+\end{equation}
+\begin{equation}
+  \label{eqn: SAR Two Samples Log Amplitude Variance PDF}
+  \caption{eqn: SAR Two Samples Log Amplitude Variance PDF}
+pdf(V_{L^A}) =
 	\frac{\ln2}{4} \frac{1}{\sqrt{V_{L^A}}} \left( \frac{2^{\sqrt{4 V_{L^A}}}}{\left( 1+2^{\sqrt{4 V_{L^A}}} \right)^2} + \frac{2^{-\sqrt{4 V_{L^A}}}}{\left( 1+2^{-2\sqrt{V_{L^A}}} \right)^2} \right)
-\end{eqnarray}
+\end{equation}
 
 It could be seen that, in the log-transformed domain, not only the expected value (mean) of the observable variance is constant, its distribution is also independent of $\sigma$. 
-%We have seen this analytically
 The above analysis is applicable for two sample variances. 
@@
 \begin{enumerate}
-\item A large number of input samples are generated ($n \cdot 10^6$ in the figure \ref{fig:variance}) from the PDF given in Eqn. \ref{eqn:log_intensity_base_2_dist}.
-\item The input samples are the divided into $10^6$ independent sets, each set consists of $n$ samples.
+\item A large number of input samples are generated ($n \cdot 10^6$ in the figure \ref{fig:variance}) from the PDF given in Eqn. \ref{eqn:SAR Log Intensity PDF}.
+\item The input samples are then divided into $10^6$ independent sets, each set consisting of $n$ samples.
 \item For each input set, the sample variance is calculated.
@@
 The discussion in the previous sub-section is based on the assumption of single stochastic processes, and thus homogeneity.  
-In a real given analysis area in SAR images, such condition is unknown. 
+In a given analysis window within real practical SAR images, such a perfect condition is unknown. 
 The principle of SAR speckle filtering however is to group pixels into homogeneous areas, allowing stochastic components to be removed. 
@@
   the notion that a given analysis area is heterogeneous or homogeneous can be put to test. 
-%This forms the basis of the statistical homogeneity hypothesis testing. 
-%The test statistic to be used is the sample variance. 
-%Figure \ref{fig:variance} shows the simulated CDF for sampling distribution of variance. 
-%It is clear that,
 Specifically given a pre-determined threshold-value and number of samples,
   if the observable sample variance is higher than a cut-off value, the null hypothesis can be rejected.
-%The collection of cut-off values for a certain threshold-value (a column in table \ref{tab:var_cut_off_values}) form a threshold-vector.
 
@@
 \item For each number of samples, a CDF plot is derived using the Monte-Carlo simulation described earlier.
-  \item Intrapolating from the CDF plot, a corresponding cut-off value is derived for each threshold-level.
+  \item Interpolating from the CDF plot, a corresponding cut-off value is derived for each threshold-level.
   \item The combined results form a table, similar in structure to Table \ref{tab:var_cut_off_values}.
@@
 
-Table \ref{tab:var_cut_off_values} gives the result of one such such experiment for an arbitrarily chosen set of threshold values.
+Table \ref{tab:var_cut_off_values} gives the result of one such experiment for an arbitrarily chosen set of threshold values.
 The table is useful in cases when an area is to be tested for homogeneity,
@@
 
-%\section{Chapter Conclusion}
-
-%It could be seen that, in the log-transformed domain, not only is the expected mean of the observable variance 
-%constant, the sampling distribution of this random variable is also independent of $\sigma$. 
-%While we have observed this analytically for variances based on two samples, for a larger number of samples, 
-%Monte-Carlo simulation can be used to visualise the PDF of samples' variances.
-
 \textbf{In summary}, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
 The dispersion measurement can be used to test 
-if a pixel belongs to a ``known'' class of physical scatterer \cite{Le_2010_ACRS}.
+if a pixel belongs to a ``known'' class of physical scatterer.
 The consistent sense of contrast can be used to test if any pair of measured data points belong to  the same homogeneous class.
-An example application of this is described in our fMLE speckle filter \cite{Le_2011_ACRS}.
-%It may also explain why, in the original SAR domain, the ratio based 
-%  detector / classifier is preferred to differential measures, which are not consistent. 
+An example application of this is described in our fMLE speckle filter.
 The consistent sense 
 of contrast also gives rise to consistent measures of sample variances, which for example, can be used to test 
-if a group of pixels can form a homogenous area.
-This was applied in a clustering algorithm described in  \cite{Le_2010_ACRS}.
-
-%\section{Original Heteroskedastic Model}
-
-%\section{The effects of Heteroskedasticity}
-
-%\section{The Homoskedastic effect of Logarithmic Transformation}
-
-%\section{Consistent Measures of Distance in Log-transformed domain}
-
-%\section{Consistent Measures of Variance in Log-Transformed Domain}
+if a group of pixels can form a homogeneous area.
+%All of these applications are presented in chapter \ref{chap:applications}
+Chapter \ref{chap:applications} presents several of these applications which further validates the models proposed herein.

### 2013-07-24 4/polsar.tex
updated for Ian changes

@@
-\chapter{Consistent Measures of Distance for Multivariate POLSAR Data} %chapter 4
+\chapter{Scalar Models for the Multidimensional POLSAR data} %chapter 4
 \label{chap:polsar}
 
-In this chapter, some statiscally consistent measures of distance for multi-variate POLSAR data is presented.
-The first section introduces the basics of POLSAR statiscal analysis and the log-transformation proposed in this thesis.
-The second section presents conclusive evidence that POLSAR data is multiplicative and heteroskedastic in the original domain.
-Then log-transformation is shown converting these into an additive and homoskedastic model.
-Consequently a few consistent measures of distance, namely the dispersion and the contrast measurements, is presented in the third section.
-Section (TODO:REF) illustrates how a few state-of-the-art results in POLSAR processing might be explained using the present approach.
-From another perspective, section (TODO:REF) discusses how the time-tested results for univariate SAR can also be considered as a special case for the multi-variate POLSAR results.
-Finally the last section strengthens our model showing the matching between simulation and real-life captured data
-  not only for a few dimensionally-collapsed single-dimensional measures
-  but also for all elements of the multi-dimensional POLSAR covariance matrix.
+This chapter derives several scalar statistical models for the
+                determinant of the POLSAR covariance matrix and
+                show that they are heteroskedastic in their original
+                domain as well as homoskedastic in the log-transformed
+                domain.
+It
+                also derives a heteroskedastic discrimination measures
+                 as well as several homoskedastic measures of
+                distance for the data.
+Subsequently the statistical models for SAR are shown to be a special case of
+                the proposed models for POLSAR
+And finally these proposed models are validated against real-life practical data.
+Mathematical derivations of the proposed models are presented in the Appendix. %***IVM: should say "Appendix A" or whatever it is?
+%The last section of this chapter details the mathematical derivations of these proposed models,
+%  which may only be helpful for mathematically inclined readers.
 
@@
 In this section, the POLSAR scattering vector is denoted as $s$.
-In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receive),
   the vector is two-dimensional ($d=2$) and is normally written as: 
-\begin{equation}
+%\begin{equation}
+\begin{align*}  
 s_{part}=\begin{bmatrix}
@@
 \end{bmatrix}
-\end{equation}
+%\end{equation}
+\end{align*}
+
 In the case of full and monostatic POLSAR data,
   the vector is three-dimensional ($d=3$) and is presented as:
-\begin{equation}
+\begin{align*}
 s_{full}=\begin{bmatrix}
@@
 \end{bmatrix}
-\end{equation}
+\end{align*}
 
@@
 \begin{equation}
+  \label{eqn:POLSAR Target Vector: Complex Gaussian Distribution PDF}
+  \caption{eqn:POLSAR Target Vector: Complex Gaussian Distribution PDF}
   pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
@@
 
-As covariance matrix is only defined on multiple data points,
-  sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
-They are formed as the mean of Hermitian outer product of single-look scattering vectors
-\begin{equation}
+As the covariance matrix is only defined on multiple data points,
+  the sample covariance matrix of POLSAR data is commonly presented in ``ensemble'' format.
+These are formed as the mean Hermitian outer product of single-look scattering vectors
+\begin{align*}
   C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
-\end{equation}
+\end{align*}
 with $s_i$ denotes the single-look scattering vector,
@@
 
-Complex Wishart distribution statistics, however, is normally written for the scaled covariance matrix
+Complex Wishart distribution statistics, however, are normally written for the scaled covariance matrix
 $Z=LC_v$, whose PDF is given as:
 \begin{equation}
+  \label{eqn:POLSAR Covariance Matrix: Complex Wishart Distribution PDF}
+  \caption{eqn:POLSAR Covariance Matrix: Complex Wishart Distribution PDF}
   pdf(Z;d,\Sigma,L)=\frac{|Z|^{L-d}}{|\Sigma^L|\Gamma_d(L)}e^{-tr(\Sigma^{-1}Z)}
@@
 Our approach differs by applying the homoskedastic log transformation
-  on a less-than-well-known result for the deterimant of the covarinace matrix.
-  %under the assumption of circular complex Gaussian distribution
-  %applicable for POLSAR data.
+  on the determinant of the covariance matrix.
 In \cite{Goodman_1963_AMS_178}, %Goodman
@@
 \begin{equation}
+\label{eqn:prod_chi_squared_rv}  
+\caption{eqn:Determinant Ratio and the Product of Chi-Squared Distributions}
 \chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
-\label{eqn:prod_chi_squared_rv}  
 \end{equation}
@@
 \begin{equation}
+\label{eqn:sum_log_chi_squared_rv}
+\caption{eqn:Logarithm of Determinant Ratio and the Sum of Log-Chi-Squared Distributions}
 \Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
-\label{eqn:sum_log_chi_squared_rv}
 \end{equation}
@@
 
-\section{Hetoroskedastic POLSAR data and the Homoskedastic Log-Transformation}
+\section{Heteroskedastic POLSAR data and the Homoskedastic Log-Transformation}
 \label{sec:polsar_heterosked_model_and_log_transform}
@@
 In this section the multiplicative nature of POLSAR data is illustrated.
-Log-transformation is shown converting this into a more familiar additive model.
+Log-transformation is shown able to convert this into a more familiar additive model.
 Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
@@
 In log-transformed domain, the case for a homoskedastic model,
-  where  variance is fixed and be independent of the underlying mean,
+  whose variance is fixed and be independent of the underlying mean,
   is demonstrated.
 To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, Appendix \ref{chap:appendix_a} is to be reviewed.
+For more detailed derivation, please refer to Appendix \ref{chap:appendix_a}.
 
@@
 we have:
-\begin{eqnarray}
-  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
-  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
+\begin{equation}
+  |C_v| \sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i)
+  \label{eqn:determinant_distribution}
+  \caption{eqn:POLSAR Covariance Matrix Determinant Distribution PDF}    
+\end{equation}
+\begin{equation}
+  \ln|C_v| \sim \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
   \label{eqn:log_determinant_distribution}  
-\end{eqnarray}
-
-In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constant.
-Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explaination that 
+  \caption{eqn:POLSAR Covariance Matrix Log-Determinant Distribution PDF}    
+\end{equation}
+
+Over a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered as constants.
+Thus Eqn. \ref{eqn:determinant_distribution} gives the theoretical explanation that, 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
@@
 \label{eqn:chi_squared_dist_pdf:chap4}
+\caption{eqn:Chi-Squared Distribution PDF}
 \end{equation}
@@
   pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
+\label{eqn:Log-Chi-Squared Distribution PDF}
+\caption{eqn:Log-Chi-Squared Distribution PDF}
 \end{equation}
@@
   can be written as:
-  \begin{eqnarray}
-    CF_\chi(t) &=& (1-2it)^{−L} \\ 
-    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
-  \end{eqnarray}
+  \begin{equation}
+    CF_\chi(t) = (1-2it)^{−L}  
+    \label{eqn:Log-Chi-Squared Distrbution: Characteristic Function}
+    \caption{eqn:Log-Chi-Squared Distribution: Characteristic Function}
+  \end{equation}
+  \begin{equation}
+    CF_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}
+    \label{eqn:log_chi_squared_characteristic_function}
+    \caption{eqn:Log-Chi-Squared Distribution: Characteristic Function}
+  \end{equation}
 Subsequently their means and variances can be computed from the given characteristic functions as:
-  \begin{eqnarray}
-    avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-  \end{eqnarray}
-  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma function respectively.
+  \begin{align*}
+    avg \left[ \chi(2L) \right]&= 2L \\
+var \left[ \chi(2L) \right]&= 4L \\
+avg \left[ \Lambda(2L) \right] &= \psi^0(L) + \ln2 \\
+var \left[ \Lambda(2L) \right] &= \psi^1(L)
+  \end{align*}
+  where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma functions respectively.
 
@@
 Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
-\begin{eqnarray}
-  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
-\end{eqnarray}
-
-Over a real and captured image, while the paramaters $d$ and $L$ do not change for the whole image,
+%\begin{eqnarray}
+%  avg \left[ |C_v| \right]  &=& \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+%  var \left[ |C_v| \right]  &=&   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
+%  avg \left[ \ln |C_v| \right] &=& \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} 
+%  var \left[ \ln |C_v| \right] &=&  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic} \caption{eqn:POLSAR Log Variance is independent from the underlying signal}
+%\end{eqnarray}
+\begin{equation}
+avg \left[ |C_v| \right]  = \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)
+\label{eqn:POLSAR Determinant is not biased}
+\caption{eqn:POLSAR Determinant is not biased}
+\end{equation}
+\begin{equation}
+  var \left[ |C_v| \right]  =   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}}
+  \label{eqn:var_det_is_heteroskedastic}
+  \caption{eqn:Variance of POLSAR Determinant is Heteroskedastic}
+\end{equation}
+\begin{equation}
+  \label{eqn:avg_log_det}
+  \caption{eqn:POLSAR Log-Determinant is biased}
+  avg \left[ \ln |C_v| \right] = \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i)  
+\end{equation}
+\begin{equation}
+  \label{eqn:var_log_det_is_homoskedastic}
+  \caption{eqn:The Variance of POLSAR Log-Determinant is homoskedastic}
+  var \left[ \ln |C_v| \right] =  \sum^{d-1}_{i=0} \psi^1(L-i)
+\end{equation}
+
+For a real captured image, while the parameters $d$ and $L$ do not change for the whole image,
   the underlying $\Sigma_v$ is expected to differ from one region to the next.
 Thus over an heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ varies depending on the underlying signal $\Sigma_v$. 
-  %and it is clear that 
-  %$det|C_v|$ data is multiplicative in nature and its log-transformed variable $\ln (det|C_v|)$ is additive model.
-In such context, Eqn.
+In such a context, Eqn.
 \ref{eqn:var_det_is_heteroskedastic} indicates that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$, which indicates its heteroskedastic property.
 At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} shows that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ manifesting its homoskedastic nature.
+  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$, hence exhibiting its homoskedastic nature.
 
@@
 
-Similar to the way dispersion and contrast is defined in our previous work \cite{Le_2013_TGRS_SAR_MSE},
-  this section introduces the consistent sense of distance in a few different perspective.
-First assumming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+This section introduces the consistent sense of distance from a few different perspectives.
+First assuming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
 the following random variables,
   namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
-  are observable according to their definitions:
-%Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
-
+  are observables according to their definitions:
+
+\begin{equation}
+ \label{eqn:determinant_ratio_observables}
+ \caption{eqn:POLSAR Determinant-Ratio Observable}
+ \mathbb{R} = \frac{|C_v|}{|\Sigma_v|}
+\end{equation}
+\begin{equation}
+ \label{eqn:log_distance_observables}
+ \caption{eqn:POLSAR Log-Distance Observable}
+ \mathbb{L} = \ln|C_v| - \ln|\Sigma_v|  
+\end{equation}
+
+From another perspective where the POLSAR is known as having come from an homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
 \begin{eqnarray}
-  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
-  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
 \end{eqnarray}
-From another perspective where the POLSAR is known coming from an homogeneous area but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
-\begin{eqnarray}
-  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
-  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
-\end{eqnarray}
-
-Taking the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
-\begin{eqnarray}
-\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
-\label{eqn:log_determinant_distance_distribution} \\ 
- \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
-\label{eqn:dispersion_distribution} \\ 
- \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
+\begin{equation}
+ \label{eqn:dispersion_observable}
+ \caption{eqn:POLSAR Dispersion Observable}
+ \mathbb{D} = \ln{|C_v|} - avg(\ln{|C_v|})  
+\end{equation}
+\begin{equation}
+  \label{eqn:contrast_observable}
+  \caption{eqn:POLSAR Contrast Observable}
+  \mathbb{C} = \ln(|C_{v1}|) - \ln(|C_{v2}|)
+\end{equation}
+
+Applying Eqns.
+\ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det}, Eqns \ref{eqn:determinant_ratio_observables} to \ref{eqn:contrast_observable} becomes:
+\begin{equation}
+ \label{eqn:determinant_ratio_distribution}
+ \caption{eqn:POLSAR Determinant Ratio Distribution PDF}
+ \mathbb{R} \sim \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) 
+\end{equation}
+\begin{equation}
+\mathbb{L} \sim  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
+\label{eqn:log_determinant_distance_distribution}  
+ \caption{eqn:POLSAR Log-Distance Distribution PDF}
+\end{equation}
+\begin{equation}
+ \mathbb{D} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k_D
+\label{eqn:dispersion_distribution}  
+ \caption{eqn:POLSAR Dispersion Distribution PDF}
+\end{equation}
+\begin{equation}
+ \mathbb{C} \sim \sum^{d-1}_{i=0} \Delta(2L-2i)
 \label{eqn:contrast_distribution}  
-\end{eqnarray}
+ \caption{eqn:POLSAR Contrast Distribution PDF}
+\end{equation}
 with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
-and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
+and $k_D=\sum^{d-1}_{i=0} \psi^0(L-i)$
 
 Also given the characteristic functions (CF) for the elementary components $\Lambda(2L)$ written in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
-  Appendix \ref{sec:appendix_b} derives the characteristic functions for the summative random variables as:
-\begin{align}
+  %Section \ref{sec:appendix_b} derives
+  the characteristic functions for the summative random variables can be derived as:
+\begin{align*}
   CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
@@
   CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
-\end{align}
+\end{align*}
 
@@
   it is natural that these variables also follow fixed distributions.
-Moreover, they are independent to $\Sigma_v$.
+Moreover, they are independent of $\Sigma_v$.
 This serves as conclusive evidence that
-  these random variables follows consistent and fixed distributions,
+  these random variables follow consistent and fixed distributions,
   regardless of the underlying signal $\Sigma_v$.
@@
 
-The prevous section has validated the use of our models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetric SAR cases.
-In this section, the focus is on the limit case where the dimensional number is reduced to 1, i.e. $d=1$.
-Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
-Mathmatically, the sample covariance matrix is reduced to the sample variance
-  and the determinant equates the scalar value.
-On another hand, it is well known that for SAR data, variance equals intensity.
-Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
-This can be thought of 
-  either as a cross-validation evidence for the proposed POLSAR models
-  or alternatively as having SAR as the special case of POLSAR. 
-%  with well known results for SAR intensity is presented.
+The prevous section has validated the use of our models for 3-dimensional (d = 3)
+full polarimetric and 2-dimensional (d = 2) partial polarimetric SAR cases. In this
+section, the focus is on the limit case where the dimensional number is reduced to 1,
+i.e. d = 1. Physically this means that when the multi-dimensional POLSAR dataset is collapsed
+into the one dimension, it becomes conventional  SAR data. Mathematically, the sample covariance
+matrix is reduced to the sample variance and the determinant equates the scalar value.
+Since  it is well known that, for SAR data, variance equals intensity,
+the special case of the d = 1 result should be consistent
+with previous results for SAR intensity data. This can be thought of either as a cross-validation evidence for the proposed POLSAR models, or alternatively as having SAR
+as the special case of POLSAR.
 
 The results so far for our models can be summarized as:
-\begin{align}
+\begin{align*}
   \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
@@
   \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align}
-
-Upon setting $d=1$ into the above models,
-  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) %\label{eqn:polsar_dispersion_mse} 
+\end{align*}
+
+Upon setting d = 1 into the above models,
+  Section \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results
+are consistent with not only the following results for single-look SAR derived earlier, i.e. $d =1,  L = 1$,
 \begin{align*}
@@
 but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
-  \begin{eqnarray}
-I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
-  \end{eqnarray}
-Furthermore, the following results for multi-look SAR data,
-  which can be thought of 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results
-  are also derived as:
+  \begin{align*}
+I &\sim pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
+N = \ln{I} &\sim pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
+  \end{align*}
+Furthermore, the following results for multi-look SAR data, which can be thought of
+either as extensions of the corresponding single-look SAR results or as simple cases of
+the POLSAR results can also be derived and shown to be as follows:
+
   \begin{align*}
@@
 
-This newly derived models for multi-look SAR data can also be validated against real-life data.
+This newly derived model for multi-look SAR data can also be validated against real-life data.
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
-In the experiment the intensity of a single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
+In the experiment, the intensity of a single-channel of SAR data (HH) for an homogeneous area in the AIRSAR Flevoland dataset is extracted.%***IVM do you need to give a ref to the dataset?
+Then the histograms for the log-distance and and contrast are plotted against the theoretical PDF given above.
 The ENL is set to the nominal number of 4.
-And good visual match is apparent in the final results.
+A good visual match is apparent in the final plotted results.
 
@@
 \begin{tabular}{c}
-	\subfloat[verify multi-look SAR log-distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Verification of multi-look SAR log-distance]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
@@
 	\hfill	
-	\subfloat[verify multi-look SAR contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Verification of multi-look SAR contrast]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
@@
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
+\caption{Multi-Look SAR dispersion and contrast showing that the modelled response matches very well with the histograms from real-life captured data.}
 \label{fig:verify_multi_look_SAR_dispersion_contrast_models}
@@
 
-This section describes an experiment to validate the models above against real-life captured data.
-The validation procedure is quite straightforward.
-Given that the stochastic models have been derived in the previous sections, 
-  they can be graphically visualized by the histogram plots of the simulated data.
-At the same time, the form of the real-life practical data is also observable via histogram plots of the data samples extracted from an homogeneous area.
-Therefore, the theoretical models can be validated 
-  if for the same parameters 
-  the two plots match each other reasonably well.
-
-As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
-Then theoretical models are employed in an attempt to explain the data.
-The validating models include:
-  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
-
-The models are closely related.
-Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
-Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
-Thus ideally speaking
-  if one model is validated all the other models will also be,
+This section describes the test to validate the proposed models  against real-life captured data. The validation procedure is as follows. Using the stochastic
+models  derived in the previous sections, 
+histogram plots of its simulated data are generated graphically. This is then compared against  the histogram plots of the  real-life captured data samples extracted from an homogeneous area.
+
+As such,  the theoretical models can be validated if, for the
+same parameters, the two plots match each other reasonably well.
+For this verification, an homogeneous area was chosen from the AIRSAR Flevoland POLSAR data.
+Theoretical models are then verified against the  real life data.
+The validations include the following models: the determinant and
+its log-transformed models, together with the various dissimilarity measures, namely: the determinant ratio, the log-distance, the dispersion and the contrast measures of distance.
+
+These models are also closely related.
+Given the same parameter set, the determinant and determinant ratio are just scaled versions of each other.
+Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted versions of each other.
+Thus ideally speaking,
+  if one model is validated all the other models can also be,
   assuming that all the parameters of the image are known exactly.
-Still in this section, all the models will be made subject to investigation.
+Nevertheless, all the models will be investigated separately in this section.
 
 Among all these models, the least-assumed stochastic process for dispersion and contrast measures of distance are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
-Then the average of POLSAR covariance matrix’s determinant in the log-transformed domain, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
-Then their histograms are traced out.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-The nominal value of 4 was taken as the dataset's number of look,
- while the dimensional number is set to 3 or 2 respectively depending on whether full or partial polarimetric SAR dataset is being investigated.
-All the histogram plots are presented in Fig. \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
-Apparently, a visual match is observable which verify the applicability of the theoretical models for the dispersion and contrast measures of distance.
+From the real-life data, for each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation is applied.
+The average of POLSAR covariance matrix determinants in the log-transformed domain, i.e.
+$avg(ln|C_v|)$, is then used to calculate the dispersion.
+Next, the observable samples of dispersion and contrast are computed according to Eqns.
+\ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable}.
+Finally,  their histograms are generated.
+
+Theoretical simulations of the models based on Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are also performed.
+The nominal value of 4 was taken as the dataset's number of looks, $L$, while the
+dimensional number $d$ is set to 3 for the full polarimetric SAR dataset, and 2 for the partial polarimetric SAR dataset. 
+The histogram plots of the theoretical models and the real-life dataset are presented in Fig.
+\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast}.
+A visual match is clearly observable which verifies the applicability of
+the theoretical models for the dispersion and contrast measures of distance.
 
@@
 	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
@@
 	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
@@
 	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
@@
 	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
@@
 There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the true signal equal to the average of the polsar covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
-Another approach is to estimate the true signal from the average of the log-determinant of the polsar covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+The traditional way is to simply assume that the true signal is equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
+Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
 Both approaches will be explored in this section.
@@
 
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} validate the models of determinant-ratio and log-distance against real-life data.
-In this experiment, the theoretical models is simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
+Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} shows the various plots for the models of determinant-ratio and log-distance against real-life data.
+In this test, the theoretical models are simulated from Eqns \ref{eqn:determinant_ratio_distribution} and \ref{eqn:log_determinant_distance_distribution},
   while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
   with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-Again a reasonable match is observed which validates the models for log-distance and determinant ratio.
-
-\begin{figure}[h]
+Again a reasonable match is observed, which validates the models for log-distance and determinant ratio.
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
@@
 	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
@@
 	\subfloat[full-pol 3x3 determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
@@
 	\subfloat[full-pol 3x3 log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
@@
 
-Since the models for the determinant and log-determinant are just scaled or shifted version of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-And if the  true signal are computed in the same manner as described before then in fact similar match can be easily observed.
+Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+And if the  true signals are computed in the same manner as described before then in fact a similar match can be easily observed.
 
@@
   where the theoretical response is taken from the simulated stochastic process described by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-%For such simulation, an estimation of  the true signal is needed.
-The interesting phenomena happens when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
-Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
-
-Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, exhibit some small discrepancies.
-The differences are easier to observe in the log-determinant plots, 
-  where except for some small shifted effects, the shapes of the models and the practical data exhibits certain resemblance.
-
-\begin{figure}[h]
+The phenomena occurs when the true signal is estimated by the first approach i.e. equal to the average of the sample covariance matrix in its original domain.
+Using this approach, a different estimation for the true signal arises.
+
+Subsequently the validation plots, which are presented in Fig \ref{fig:verify_polsar_2x2_simulation_det:log_det_3x3}, exhibit some small discrepancies.
+The differences are easier to observe in the log-determinant plots. 
+Except for the shifted effect, the shapes of the models and the real-life data are practically similar.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[verify polsar 2x2: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[verification of POLSAR 2x2: determinant]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
@@
 	\hfill	
-	\subfloat[verify polsar 2x2: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[verification of  POLSAR 2x2: log-determinant]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
@@
 	} \\ 
-	\subfloat[verify polsar 3x3: determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[verification of  POLSAR 3x3: determinant]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
+		 \label{fig:verify_polsar_2x2_simulation_det:determinant_3x3}
 	} 
 	\hfill	
-	\subfloat[verify polsar 3x3: log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[verification of  POLSAR 3x3: log-determinant]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
+		 \label{fig:verify_polsar_2x2_simulation_det:log_det_3x3}
 	} 
@@
 
-In short the least-assumed dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
+In summary, the dispersion and contrast measures of distance are shown to match reasonably well with the real-life data. 
 The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
@@
 However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
+  depending on which estimation method is chosen.
 The discrepancy suggests that at least one parameter for the models was wrongly employed.
-
-But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-  where not only the look number is shown to be misused
-  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-For now, let us contend that:
-  using appropriate estimation of the parameters, 
-  the proposed models match reasonably well with the practical data.
+But which model parameter was used wrongly, and even if that can be corrected, would
+a better match become observable? This question will be discussed further in the next section.
 
@@
 
-Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
-  like all other similar models, the proposed model in this paper is built upon certain presumptions.
+While the assumptions used for the proposed models are intentionally kept to the minimum, 
+  like all other similar models, they are still built upon certain presumptions.
 Practical conditions however may not always satisfy these prerequisites.
 In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
-And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
+It will be shown that the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
 
@@
 The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
-Practically however high correlation is routinely observable between the POLSAR data components,
+However, in practice, high correlation is routinely observable between the POLSAR data components,
   specifically between $S_{hh}$ and $S_{vv}$.
-This phenomena also presents in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
-Despite the mismatch,
-  astute reader would probably notice that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
-\ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
-This suggests that the proposed model is also applicable on correlated POLSAR components,
-  eventhough a full explaination for this, however, is outside the scope of this paper.
-
-Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent to each other.
+This phenomena is also present in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
+Despite the mismatch, the proposed model  is still valid under such conditions, as observed in the part-pol (HH-VV) and full-pol
+plots in Figs. \ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
+
+Another assumption of the model (for both SAR and POLSAR) is that the samples are statistically independent of each other.
 This is a reasonable assumption given that 
-  the transmission and receipt of analog signals are done independently for each radar pulse, i.e. for each resolution cell.
+  the transmission and receipt of analogue signals are done independently for each radar pulse, i.e. for each resolution cell.
 Thus theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
@@
 However, the actual imaging mechanism of a real-life (POL)SAR processor is that of digital nature,
-where the analog signal is to be converted into a digital data-set. 
-Specifically, the analog signal in SAR 
+where the analogue signal is to be converted into a digital data-set. 
+Specifically, the analogue signal in SAR 
   which is characterized by the pulse bandwidth measurement,
-  is fed into an analog-to-digital sampling and conversion process 
+  is fed into an analogue-to-digital sampling and conversion process 
   which is characterized by its sampling rate.
-Theoretically it is possible to define a sampling rate to ensure that each digital pixel correspond exactly to an analog physical cell resolution.
-Practically however, to ensure ``perfect reconstruction'' of the analog signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
+Theoretically it is possible to define a sampling rate to ensure that each digital pixel corresponds exactly to an analogue physical cell resolution.
+Practically however, to ensure ``perfect reconstruction'' of the analogue signal, the sampling rate is normally set at a slightly higher value than the theoretical mark.
 This results in a higher number of samples / pixels than the number of physical cells available in the scene.
 
-Stated differently, in practical data each physical radar cell is spread to more than one pixel
-  and each pixel now contains less than one physical analog cell.
-This high sampling rate also results in 
-  a significantly higher correlation between pairs of pixels that maybe related within a single physical cell resolution 
-  than the correlation found between pairs of pixels that are further away and hence having less physical relation to each other.
-It also results in reduced effective number of look, 
-  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
+Stated differently, in practical data, each physical radar cell influences more than one pixel,
+  and each pixel is not completely defined by one physical analogue cell.
+This high sampling rate results in 
+  a significantly higher correlation between pairs of pixels that would be found between within a single physical cell resolution, 
+  compared to the correlation between pairs of pixels that are further away and hence having less physical relation to each other.
+It also results in a reduction in the effective number of looks, 
+  which means for example that a window of 3x3 pixels actually contains less than 9 physical analogue cells.
+
 The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
-  while the later is experimental observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
+  while the later has been experimentally observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
 The oversampling practice is also documented by the producers of SAR processors.
 For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}
-
-The proposed model can handle this imperfection that is available in pratical data.
-The trick is that instead of using the nominal Number of Look given by the SAR processor,
-  an ENL estimation procedure is employed. %the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
-The first part of this section details a simple ENL estimation technique for POLSAR data.
-While the second part demonstrates how the practical imperfection manifest itself and how it can be handled in a RADARSAT2 dataset.
-It also illustrates how the match shown in Section \ref{sec:polsar_models_validation} for the AIRSAR Flevoland dataset can be improved,
-  by using ENL estimation.
+While for RadarSat2, the pixel resolution and range--azimuth resolutions for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}
+
+The proposed model in this thesis can handle this imperfection that is found in practical data through the use of an ENL estimation procedure, as will be described in the next section.
 
@@
 
-This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
-The common approach in tackling this problem is by investigating the summary statistics of an known homogeneous area in the given data
+A number of techniques are available to estimate the Effective Number of Looks (ENL) for a given POLSAR dataset.
+The common approach is by investigating the summary statistics of a known homogeneous area in the given data
   before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ has been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
+The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform}.
 In fact Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
 Recall that in carrying out validation process for AIRSAR Flevoland data using the nominal look number of 4, this relationship was broken.
-The reason for such broken relationship is believed to be an inexact look number was taken.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ is known,
-  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensure the above relationship is valid.
-
-In fact, this approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
+The reason for such broken relationship is due to an inexact look number being taken.
+In a given POLSAR dataset, since values of $|avg(C_v)|,avg(\ln|C_v|),d$ are all known,
+  it is possible to estimate the ``effective'' number of look, by finding $L$ that ensures the above relationship is valid.
+
+This approach was also used in \cite{Anfinsen_2009_TGRS_3795}, where the same equation 
+  as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
 Unfortunately, the only known way to solve the equation for the unknown $L$ requires the use of an ``iterative numerical method''.
 Instead of relying on the equations for statistical mean to find ENL,
-  our approach make used variance statistics in the homoskedastic log-domain to find ENL.
-Since the determinant of POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
-  this approach can be considered as the generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} towards POLSAR data.
+  the approach here makes use of the variance statistics in the homoskedastic log-domain to find ENL.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation}
+\begin{equation*}
   var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-  \label{eqn:expected_sample_var_log_as_function_of_enl}
-\end{equation}
+\end{equation*}
 where $\psi^1()$ denotes tri-gamma function.
@@
 Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for the unknown $L$.
-Interestingly that would also require some iterative computations.
-Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph.
-And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
+However, that would also require some iterative computations.
+%***IVM: Hai, what does this mean "var [ln|Cv |]"? Is it an equation? You show it in text mode!!!
+A more practical approach is to use a look-up graph approach
+  where for each value of $var [ln|Cv|]$, a corresponding pre-computed value for L can be found by referencing the variance value on the graph.
+An approximation can also be used  to find the L value based on a back-of-the-envelope calculation using the following equation  
   \begin{equation}
@@
     \label{eqn:enl_estimation_formula}
+    \caption{eqn:ENL Estimation Formula for POLSAR data}
   \end{equation}
 Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  not only shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  but also illustrates the approximation power of the simplified formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-\begin{figure}[h]
+  shows the shapes of the function defined in Eqn. \ref{eqn:var_log_det_is_homoskedastic} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$,
+  together with the   approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
+It can be seen that they are practically the same, hence the validity of Eqn \ref{eqn:enl_estimation_formula}.
+In the next section, the estimated ENL will hence be used to demonstrate the accuracy of the proposed model.
+
+\begin{figure}[h!]
 \centering
@@
 	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
                  \epsffile{images/plot_enl_var_relation_1x1.eps} 
@@
 	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
@@
 
-\subsection{Using the estimated ENL to better explain pratical data}
-
-For this experiment an example RADARSAT2 dataset was used.
+\subsection{Using the estimated ENL to better explain practical data}
+
+For this test a sample RADARSAT2 dataset is used. 
 The dataset is in its Fine-Quad mode Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{{fig:handling_radarsat2_oversampling_practice}}
-  against the theoretical model for the nominal ENL value of 9.
-The match however is not very good.
-
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model is simulated for the estimated ENL
-Then the new sample histogram is plotted in the same figure,
-  which indicated a much better consistency.
+  and nine-look processing is applied.
+The dispersion histogram in the log-transformed domain is computed over an homogeneous area.
+The histograms generated by the theoretical models for  nominal ENL value
+  of 9 are then plotted %for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted
+in Fig. \ref{fig:handling_radarsat2_oversampling_practice}. The nine-look histogram is the narrower and higher curve.
+As can be seen, the match is not very good between this and the observed data, displayed as points.
+
+A much better match can be achieved by estimating the ENL from the observable variance of the log-determinant, using the approximation formula given in Eqn. \ref{eqn:enl_estimation_formula}.  
+This is then used to re-calculate the histogram, which is plotted in the same figure (Fig. \ref{fig:handling_radarsat2_oversampling_practice}).
+ As can be seen, the $L=3.4241$ curve exhibits a much closer match to the real-life data.
 This procedure can always be carried out for any given dataset,
-  as long as an area of homogeneous area can be extracted.
-
-\begin{figure}[h]
+  as long as an area of homogeneous area can be identified.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Handling over-sampling consequences in Radarsat2 one-dimensional SAR data (HH)]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
@@
 	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Handling over-sampling consequences in Radarsat2 partial POLSAR data (HH-HV)]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
@@
 \end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then offer better explaination for the data.}
+\caption{9-look processed Radarsat2 data does not exactly exhibit 9-look data characteristics.
+An homoskedastic model in the log-transformed domain can be used to successfully estimate the effective ENL and thus offer a better model of the data.}
 \label{fig:handling_radarsat2_oversampling_practice}
@@
 
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in AIRSAR Flevoland dataset,
-  eventhough to a much lesser-extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-The ``corrected'' effective number-of-look offer observably better match between the model and real-life data.
-The mis-match problem appears to depend on how much over-sampling were used in the dataset
-  as well as the dimension of the data.
-
-\begin{figure}[h]
+Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol}
+  shows that the over-sampling issue is also present in AIRSAR Flevoland
+dataset, although to a much lesser extent.
+Using the  effective number-of-looks value, the reconstructed model exhibits a better match to the real-life data.
+
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset (contrast better?)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Handling over-sampling consequences in AIRSAR full-pol dataset]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_determinant_ratio.eps} 	
@@
 	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+	\subfloat[Handling over-sampling consequences in AIRSAR full-pol dataset]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
 		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though at a much smaller extend than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits the over-sampling phenomena, though to a much smaller extent than the RADARSAT 2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}
@@
 
-\section{Details of Mathematical Derivations}
-
-\subsection{The Log-Chi-Square Distribution}
-\label{sec:appendix_a}
-
-This appendix provides the mathematical proofs for the log-transformed version of chi-squared random variables.
-
-Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
-\begin{equation}
-pdf(\chi;\,k) =
-  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
-\label{eqn:chi_squared_dist_pdf:appdixA}
-\end{equation}
-
-Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
-\begin{equation}
-pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
-\end{equation}
-
-Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
-\begin{equation}
- \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
-\end{equation}
-into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
-\begin{eqnarray*}
-  d\chi &=& e^\Lambda d\Lambda \\
-  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
-\end{eqnarray*}
-In other words, we have:
-\begin{equation}
-pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
-\label{eqn:log_chi_square_dist_pdf}
-\end{equation}
-
-From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, characteristics function can be computed.
-By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
-\begin{eqnarray*}
-\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
-      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
-      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
-\end{eqnarray*}
-with $\varphi_x(t)$ is the characteristic function,
-     $F_X(x)$ is the CDF function of X and
-     $f_X(x)$ is the PDF function of X.
-Thus the characteristic function for log-chi-squared distribution is defined as: 
-\begin{equation}
-\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
-\end{equation}
-
-Gamma function is defined over complex domain as:
-$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
-Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
-Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
-%  \begin{eqnarray*}
-%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
-%  \end{eqnarray*}
-
-%Thus the characteristic function becomes
-That is:
-\begin{equation}
-\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
-\end{equation}
-
-Consequently, the first and second derivative of log-chi-squared distribution can be computed.
-The first derivative is given as:
-\begin{equation}
-  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
-\end{equation}
-due to
-\begin{eqnarray*}
-  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
-  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
-  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
-\end{eqnarray*}
-where $\psi^0()$ denotes di-gamma function.
-
-Meanwhile, the second derivative can be written as:
-\begin{equation}
-  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
-\end{equation}
-due to:
-\begin{eqnarray*}
-  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
-  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
-  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
-\end{eqnarray*}
-with $\psi^1()$ denotes tri-gamma function.
-
-The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
-\begin{equation}
-\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
-  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
-\end{equation}
-
+\section{Discussion}
+
+Let us consider the different theoretical properties of the proposed models.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
+
+Second, the models are developed for the POLSAR covariance matrix.
+However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+  the model should also be applicable to the coherency matrix.
+
+It should be noted that the models are far from complete.
+% It reduces the multi-dimensional POLSAR data to a scalar value.
+%While this is probably desirable for a wide range of application,
+%  such a reduction is unlikely to be lossless.
+While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
+  such a reduction is unlikely to be lossless.  
+Thus %to better understand POLSAR data
+the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+
+Nevertheless the proposed models are promising.
+Even though initially developed for partial and monostatic POLSAR data,
+  this was shown to be applicable to traditional SAR data as well.
+Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
+
+%If move to chapter 4, can add these paragraphs
+%The thesis also derives the homoskedastic models for both SAR and POLSAR heteroskedastic data.
+%Within this consistent variance models, several consistent sense of subtractive distance is proposed.
+%These can be thought of as the linear and subtractive versions of the commonly used ratio discrimination measure in the original multiplicative SAR model.
+%
+%Theses additive and homoskedastic models should be beneficial to all the steps of the computational and statistical estimation framework in particular as well as to many existing digital technologies and algorithms in general.
+%This thesis also includes several published studies which illustrate several of such benefits.
+%These include the use of the consistent variance to break the vicious circle of speckle filtering, as well as the use of MSE in evaluating (POL)SAR Statistical estimators within the additive and homoskedastic model.
+%
+
+ \subsection{Beneficial}
+
+%How to exploit the advantages of these new results? What
+%                are their benefit? And
+%                to whom? OK, assuming your solution is novel and it can
+%                hold water, is it useful? How is it better than the
+%                state-of-the-art? And to whom does this matter? Why
+%                should they use your solutions instead of other?
+The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
+An example is between the fields of SAR and POLSAR, where obviously SAR data processing has been studied in much further detail than the more newly derived field of POLSAR data processing.
+%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
+By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
+Another example is between the fields of computer science and SAR-based remote sensing.
+Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
+And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
+could potentially allow this currently small portion to grow larger.
+%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.
+
+%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
+%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
+The proposed homoskedastic statistical estimation framework provides a firm foundation
+to overcome the various negative impacts of heteroskedasticity on statistical estimations.
+This
+                is demonstrated in both stages of developing new
+                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
+Specifically
+                in the context of SAR speckle filters: consistent
+                variance and homoskedasticity is shown to help in
+                breaking the vicious circle of speckle filtering.
+
+At
+                the same time, a consistently meaningful sense of
+                distance leads to our proposal of using the familiar
+                MSE in the homoskedastic domain to evaluate SAR speckle
+                filters.
+Intuitively,
+                this comes about as the speckle suppression power of
+                speckle filters can be evaluated via variance estimation
+                practice, while the radiometric preservation can be
+                evaluated via the normal bias evaluation.
+Combined,
+                while there are many different evaluation criteria in
+                the heteroskedastic SAR speckle filter evaluation
+                framework, the MSE is proposed as the single unified
+                evaluation criteria for SAR speckle filters.
+%***IVM: not sure about the above paragraph... can you check it? Why the 'combined'?
+In
+                short, it is shown that in the homoskedastic domain, not
+                only it is possible to find the equivalent of existing
+                methods overcoming heteroskedastic drawbacks in the
+                original domain, it is also possible to suggest further
+                improvements based on existing techniques.
+
+The
+                proposed models for POLSAR also bring forward 
+                important benefits.
+Since
+                the models, especially those for discrimination
+                measures, can be considered as the multidimensional
+                extension of the models for SAR, it makes many existing
+                SAR processing techniques extensible towards POLSAR
+                data.
+The POLSAR determinant ratio, for example, can be considered as
+                the extension of the ubiquitous SAR intensity ratio.
+This
+                thesis also illustrates how the MSE evaluation
+                criteria can also be extended from SAR to POLSAR.
+
+From another angle, the theoretical models for POLSAR also offer several benefits.
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+As a by-product of this exact derivation, the paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.%***IVM: Hai, by "paper" in this sentence, are you referring to the Conradsen 2003 TGRS paper?
+
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.
+
+%While some of these obstacles have been overcome by various experienced researcher in the field proposing different genuine approaches, 
+%  the additive and homoskedastic transformation approach proposed in this thesis suggests that these problems also have equivalent handling techniques which usually are more familiar.
+%Furthermore competitive and even sometimes better proposal are made making use of this familiarity.
+%For example, not only it is shown that both radiometric preservation and speckle suppression evaluation of SAR speckle filters can be carried out equivalently well under both domain, 
+%  MSE is in the additive and homoskedastic domain is shown capable of combining the two evaluations, which so far have not been figured out in the original heteroskedastic domain.
+%Elsewhere, the application of wavelet in this same transformed domain has resulted in a new class of speckle filters which performs respectably in comparison to other well established filters.
+%The familiarity of this transformed domain should also be very helpful for the new comers of the field, who is much more likely to find comfort ability in this derived domain in comparison to the original multiplicative and heteroskedastic domain.
+
+\subsection{Limitations}
+
+%What are their limitations? What problems this appears
+%                to solve, but actually is not?
+
+The
+                proposed scalar models for POLSAR also have limitations.
+They
+                involve a dimensional reduction operation, which is
+                probably not lossless.
 Thus
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
-  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
-% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
-% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
-% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
-\end{eqnarray*}
-That is
-\begin{equation}
-  avg(\Lambda) = \psi^0(L) + ln(2)
-\end{equation}
-
-Similarly,
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
-  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
-% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
-% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
-% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
-\end{eqnarray*}
-That is:
-\begin{equation}
-  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
-\end{equation}
-%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
-%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.
-
-Thus
-\begin{equation}
-var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
-\end{equation}
-
-\subsection{Summary Statistics of Some POLSAR Observables}
-
-In this section, the expected value and variance value of these mixture of random variables is derived
-\begin{eqnarray}
-\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
-\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
-\end{eqnarray}
-given the averages and variances of individual components.
-\begin{eqnarray}
-avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-\end{eqnarray}
-
-Making use of the mutual indepent property of each component $X_i$,
-  the variance and expectation of the sumation and product of random variables can be written as:
-\begin{eqnarray*}
-avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
-var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
-avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
-var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
-\end{eqnarray*}
-
-Thus they can be computed as:
-\begin{eqnarray*}
-  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
-
-\subsection{The characteristic function of some dissimilarity measures for polsar}
-
-Given characteristic function (CF) of the elementary log-chi square distributions can be written as:
-\begin{eqnarray}
- CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
-\end{eqnarray}
-  the CF for the following random variables,
-  which are combinations of the above elementary random variables, can be derived
-\begin{eqnarray*}
-   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
-  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
-  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
-  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
-\end{eqnarray*}
-
-Since
-\begin{eqnarray*}
- CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
- CF_{x+k}(t) &=& e^{itk}CF_x(t)
-\end{eqnarray*}
-we have:
-\begin{eqnarray}
-  CF_{\chi^d_L}(t) &=& \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{L}} &=& \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{D}} &=& \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-\end{eqnarray}
-
-%The CF for the contrast random variable can also be written as
-Also due to
-\begin{eqnarray*}
-  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
-  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
-   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
-\end{eqnarray*}
-we arrive at:
-\begin{eqnarray}
-  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-\end{eqnarray}
-with $\Gamma()$ and $B()$ denotes Gamma and Beta functions respectively.
-
-\subsection{SAR intensity as the special case of the POLSAR cov-matrix determinant}
-\label{sec:appendix_sar_special_case_of_polsar}
-
-In this appendix, the following results for SAR intensity $I$ is shown to be special cases of the results given in this paper for the determinant of POLSAR's covariance matrix $det|C_v|$.
-Specifically, not only the following results from the our previous works on single-look SAR (TODO:CITE), i.e. $d=L=1$, is reviewed:
-\begin{eqnarray}
-  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
-  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
-  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
-  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
-  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray}
-but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$ is also considered:
-  \begin{eqnarray}
-I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
-  \end{eqnarray}
-It will be shown that all of these results are special cases of the result derived previously and rewritten below:
-\begin{eqnarray}
-  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
-  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
-\end{eqnarray}
-\begin{eqnarray}
-  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
-  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
-  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\end{eqnarray}
-\begin{eqnarray}
-  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
-  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
-  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
-\end{eqnarray}
-
-This appendix also derives new results for multi-look SAR data,
-  which can be thought of 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results presented above.
-They are:
-  \begin{eqnarray}
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
-    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
-    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
-    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{D}) &=& \psi^1(L) \\
-    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{eqnarray}
-
-The derivation process detailed below consists of two-phases.
-The first phase collapse the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
-Mathematically this means setting the dimensional number in POLSAR to  $d=1$
-  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.
-
-The output of the first phase, in the general case is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplify the multi-look results into single-look results, presented in our previous work (TODO:CITE).
-Mathematically, that means setting $L=1$ in the multi-look result
-  and converting from natural logarithmic domain used in this paper to the base-2 logarithm used in (TODO:CITE).
-
-\subsubsection{Original Domain: SAR Intensity and its ratio}
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
-we have:
-\begin{eqnarray*}
-  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
-\end{eqnarray*}
-Or in PDF forms, and applying variable change theorem we have:
-\begin{eqnarray*}
-    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
-  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
-%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
-  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
-%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
-\end{eqnarray*}
-
-Thus we have the following results for multi-look SAR
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
-\end{eqnarray}
-
-Now setting $L=1$, these results become:
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
-\end{eqnarray}
-which is the same as in (TODO:CITE).
-
-\subsubsection{Log-transformed domain: SAR log-intensity and the log-distance}
-
-The result for multi-look SAR data written in log-transformed domain can be derived from two different approaches.
-The first is to follow the simplification method, where the results for log-transformed POLSAR data is simplified into log-transformed multi-look SAR result.
-
-The second approach is to apply log-transformation into the results derived in the previous section.
-In this section, it is shown that both approaches would results into identical results.
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
-we have
-\begin{eqnarray*}
-  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
-  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
-\end{eqnarray*}
-
-Or in PDF form, and applying variable change theorem we have:
-\begin{eqnarray*}
-  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
-  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
-%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
-   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
- &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
-\end{eqnarray*}
-with $\bar{N} = \ln{\bar{I}}$.
-
-Thus the first approach arrives at
-\begin{eqnarray}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
-\end{eqnarray}
-
-In the second approach, log-transformation is applied on previous result for multi-look SAR intensity and its ratio in the original domain (Eqns.
-\ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-The also arrives at the same results as above, the details working however is omitted here for brevity.
-
-%\begin{eqnarray*}
-%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
-%\end{eqnarray*}
-%Thus
-%\begin{eqnarray*}
-%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
-%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
-%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
-%\end{eqnarray*}
-%
-%Thus the second approach also arrives at
-%\begin{eqnarray}
-%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
-%\end{eqnarray}
-
-To compute summary statistics for the multi-look SAR dispersion,
-  set $d=1$ into the Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
-we have:
-  \begin{eqnarray*}
-    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{L}) &=& \psi^1(L) \\
-    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-\end{eqnarray*}
-
-This completes the first phase of the derivation process.
-The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
-  and converting natural logarithm into base-2 logarithm.
-First, setting $L=1$ makes the above results become
-\begin{eqnarray*}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
-    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
-    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
-    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
-\end{eqnarray*}
-with $\gamma$ denotes the Euler-Mascharoni constant.
-Then to convert to base-2 logarithm from natural logarithmic transformation,
-  variable change theorem is invoked.
-  That is:
-  \begin{eqnarray*}
-   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
-   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
-       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
-  \end{eqnarray*}
-\begin{eqnarray*}
-   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
-%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
-       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
-\end{eqnarray*}
-\begin{eqnarray*}
-  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
-  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray*}
-
-\subsubsection{Deriving the PDF for SAR dispersion and contrast}
-
-The PDF for SAR dispersion can be easily derived from
-  the PDF for the Log-distance given above as:
-  \begin{equation}
-   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
-  \end{equation}
-due to $d=1$ and
-\begin{eqnarray*}
-  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
-  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
-\end{eqnarray*}.
-
-Setting $L=1$ for Single-Look SAR we have
-\begin{equation}
-  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
-\end{equation}
-due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
-with $\gamma$ being the Euler Mascheroni Constant which equals $0.5772$. 
-In base-2 logarithm, variable change theorem is invoked
-\begin{eqnarray*}
-  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
-  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
-\end{eqnarray*}
-Thus we have
-\begin{equation}
-  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
-\end{equation}
-which is consistent to the result in our previous work (TODO:CITE).
-
-Setting $d=1$ into Eqn. for contrast result in
-\begin{equation}
-  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
-\end{equation}
-The characteristic function would then be
-\begin{equation}
-  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
-\end{equation}
-Thus PDF can be written as
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
-\end{equation}
-due to
-\begin{eqnarray*}
-  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
-       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
-  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
-%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
-        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
-\end{eqnarray*}
-
-Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
-we have the PDF for contrast of single-look SAR:
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
-\end{equation}
-
-Converting to base-2 logarithm we have
-\begin{eqnarray*}
-  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
-%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
-     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
-\end{eqnarray*}
-which is also consistent to the result in our previous work (TODO:CITE).
+                while the determinant of the POLSAR covariance matrix could be described as
+                ``highly representative'', it is definitely not
+                \textit{fully representative} of the data.
+Intuitively,
+                this is similar to the use of magnitude as being
+                representative of a complex number, which also is not
+                fully representative of the two-dimensional number.
+But it is important to emphasize that,
+                just like the magnitude is invariant to the rotation of
+                the reference frame, the POLSAR determinant is also
+                invariant to polarization basis transformation.
+
+While
+                the proposed homoskedastic measures of distance have
+                their own benefits, their biggest challenge probably
+                lies in changing the hard learned lessons that
+                previous generation of researchers have experienced tackling
+                the multiplicative and heteroskedastic SAR data.
+At
+                the same time, while the logarithmic transformation has
+                the advantages of converting the multiplicative and
+                heteroskedastic model into an additive and homoskedastic
+                data, such transformation does not arrive conveniently
+                to the common additive white noise model.
+In fact, figures presented in the previous chapters show that 
+	they are not even centred around the origin. 
+This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
+	work very well in practice, as the operation is biased and statistically inconsistent.
+To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
+	is suggested \cite{Le_2011_ACRS}.
+While averaging is also the MLE operator in SAR's original domain,
+                the MLE operation in the log-transformed domain is admittedly more complex in comparison.
 
@@
 %
+
+In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
+Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
+The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
+The representative power of the observable is explained in a few different ways.
+Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
+Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
+In fact, this chapter also proposes several new discrimination measures for POLSAR,
+  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
+Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
+It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
+%Such applications are briefly explored in the next chapter. 
+The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

### 2013-07-24 5/applications.tex
updated for Ian changes

@@
-\chapter{Using the Consistent Measures of Distance} %chapter 5
+\chapter{Applications of The Proposed Models} %chapter 5
 \label{chap:applications}
 
+In this chapter, some beneficial applications of the proposed models are presented,
+  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
+filtering .
+This chapter also shows how the MSE can then be 
+applicable in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
+ POLSAR speckle filters.
+
 \section{Clustering SAR images using the consistent measures}
-%\section{SAR Image Clustering using the consistent measures}
-
-%\section{Proposed SAR speckle filter using Homoskedastic features}
 \label{sec:k_mle}
 
-Given an area of analysis, 
+Given an area to be analyzed, 
   the question of whether it is homogeneous or not can be investigated using
-%its non-homogeneity can be detected by 
-the statistical hypothesis test described above. 
-If that is decided to be the case, clustering algorithm can be applied to partition the area into smaller regions. 
+the statistical hypothesis test described in chapter \ref{chap:sar}. 
+If that is found to be the case, clustering algorithm can then be applied to partition the area into smaller regions. 
 Thus an image can be segmented into homogeneous areas by applying the process repeatedly.
 
-%Given an area of analysis, its non-homogeneity can be detected by the statistical hypothesis test described above. 
-%If that is likely to be the case, clustering algorithm can be applied to partition the area into smaller regions. 
-%The process can be applied iteratively until all partitions can be considered homogeneous (accepting the null hypothesis). 
-%This forms the basis of our proposed speckle filtering technique.
-
-\subsection{Developing kMLE clustering Algorithm}
+\subsection{Developing k-MLE clustering Algorithm}
 
@@
 
-In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given earlier. 
-Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the aim then is to estimate $\sigma$. 
-This section will show how $\sigma$ can be estimated in log-transformed domain.
+In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
+Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
+This section shows how $\sigma$ can be estimated in log-transformed domain.
 
@@
 Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
-The PDF given in Eqn. \ref{eqn:conditional_prob} then can be interpreted as
+The PDF given in Eqn. \ref{eqn:conditional_prob} can then be interpreted as
   the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.
 
-\begin{eqnarray}
-\label{eqn:conditional_prob}
-P(x^l_i | \mu ) 
-	&=& \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }
+%\begin{eqnarray}
 %\displaystyle{ \frac{ \partial }{\partial{ \mu }} P(x^l_i | \mu )  }
 %	&=& - \ln^2{2} \frac{ 2^{x^l_i - \mu} (2^{x^l_i - \mu}-1) }{ e^{2^{ x^l_i -\mu }} } 
-\end{eqnarray}
+%\end{eqnarray}
+\begin{equation}
+\label{eqn:conditional_prob}
+\caption{eqn:Conditional Probability of SAR Pixel Intensity}
+P(x^l_i | \mu ) 
+	= \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }
+\end{equation}
 
@@
 The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of value X found in the area, given the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
-Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in equation \ref{eqn:conditional_prob}.
+Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in Eqn.
+\ref{eqn:conditional_prob}.
 %$P(x^l_i | \mu ) = \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }$. 
@@
 
-\begin{eqnarray}
+\begin{eqnarray*}
 \ln[P(X^l | \mu )] 
@@
 %	&=& n \ln \ln 2 +  \displaystyle{\sum^n_{i=1}{ \ln \left( 2^{x^l_i - \mu} \right) - \ln \left( e^{2^{ x^l_i -\mu }} \right) }} 
-\end{eqnarray}
+\end{eqnarray*}
 
 The parameter $\mu$ which maximizes the likelihood is found by setting its derivatives to zero:
-\begin{eqnarray}
+\begin{eqnarray*}
 \displaystyle{ \frac{ \partial{ \ln[P( X^l | \mu )] }  }{\partial{ \mu }} }
@@
 %	&=& - \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  
-\end{eqnarray}
+\end{eqnarray*}
 
 Thus $\mu$ can be found by:
-\begin{eqnarray}
-%n \cdot \ln2	
-%	&=& \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  \\
+\begin{equation}
 2^\mu 
-	&=& \frac{ \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }} }{n}  
+	= \frac{ \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }} }{n}  
 \label{eqn:mle_log_transform}
-\end{eqnarray}
+\caption{eqn:MLE Estimation in the Log-Transformed Domain}  
+\end{equation}
 
@@
 
-In order to apply MLE into a given analysis window ($L^w$), one would need to partition the area into groups of homogeneous pixels ($G$). 
+In order to apply MLE into a given heterogeneous analysis window ($L^w$), one would need to partition the area into groups of homogeneous pixels ($G$). 
 Assuming for now that the number of homogeneous groups ($c=size(C)$) is known \textit{a priori}, this section will describe the proposed clustering algorithm. 
@@
 
-%The pseudo code for the algorithm is provided in Listing \ref{lst:k_mle_algo_cluster_centers}
-
 \lstset{language=Matlab,caption=k-MLE Clustering Algorithm Template,label=lst:k_mle_algo_template}
@@
 
-Due to the special characteristics of the log-transformed domain, we have adopted
-an MLE estimator in lieu of a standard averaging estimation for cluster centers. 
-Consequently the kMLE algorithm is presented in Listing \ref{lst:k_mle_algo_cluster_centers}.
-%a standard k-means algorithm transformed into k-mle algorithm given in Listing \ref{lst:k_mle_algo_cluster_centers}.
+Due to the special characteristics of the log-transformed domain, 
+an MLE estimator is used in lieu of the standard averaging estimation for cluster centers. 
+Consequently the k-MLE algorithm is presented in Listing \ref{lst:k_mle_algo_cluster_centers}.
 
@@
 \lstset{backgroundcolor=\color{darkgray}}
-%\begin{figure}
-%\begin{verbatimtab}
 \begin{lstlisting}[frame=tb]
@@
 \end{lstlisting}
-%\end{verbatimtab}
-%\caption{Iteratively find better cluster centers}
-%\label{src:k_mle_algo}
-%\end{figure}
-
-When compared with standard k-means the following differences are evident:
+
+Compared with using the standard k-means algorithm, the following differences are noted:
+%When compared with standard k-means the following differences are evident:
 \begin{enumerate}
@@
 In our specific situation, as the dispersion PDF is non-symmetric around the cluster center, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
-  \item The calculation of new cluster centers is different also. 
+  \item The calculation of new cluster centers is also different. 
 In k-means, new cluster centres are estimated as the average of all membered data points. 
 Here, due to the bias of the PDF, maximum likelihood estimations are preferred.
-  \item All the design decisions are made possible by the knowledge of the statistical PDF in the log-transformed domain!
+  \item All the design decisions are made possible by the knowledge of the statistical PDF in the log-transformed domain.
 \end{enumerate}
@@
 
-In the previous section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
+In the last section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
 In practice, this is not the case. This section will describe how the issue is to be tackled.
@@
 %\section{Experiment Results and Discussions}%describe analysis and compare
-\subsection{Evaluating the kMLE algorithm}
+\subsection{Evaluating the k-MLE algorithm}
 \label{sec:k_mle_result}
 
-\subsubsection{Using the kMLE clustering algorithm for speckle filtering}
-
-It should be noted there is a difference between accepting the null hypothesis and simply failing to reject it. 
+\subsubsection{Using the k-MLE clustering algorithm for speckle filtering}
+
+In the context of statistical hypothesis testing, there is a difference between accepting the null hypothesis and simply failing to reject it. 
 However, in the section that follows, the decision rule in use is that if the sample variance is lower than the cut-off value, the null hypothesis is accepted. 
-The next analysis shows that for the purpose of speckle-filtering the difference is negligible.
+This section illustrates that for the purpose of speckle-filtering the difference is negligible.
 
 The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastics noise can be removed.
-This allows the kMLE clustering algorithm to form the basis of a speckle filtering technique,
-  where the results of the clustering algorithm can be transformed into answers for the problem of speckle filter.
-Specifically the clustered areas directly serves as the grouping of pixels into homogeneous areas, and the cluster centers serves as the estimated backscattering coefficient for the analysis window.
-
-Let us now consider some extreme threshold-values used as the homogeneous criteria for grouping pixels in the kMLE speckle filter.
+Hence the k-MLE clustering algorithm can be used to form the basis of a speckle filtering technique.
+Specifically the clustered areas directly serves as the grouping of pixels into homogeneous areas, and
+the cluster centers serves as the estimated backscattering coefficient for the analysis window.
+
+Considering the case where some extreme threshold-values are used as the homogeneous criteria
 If threshold-value is set to a very high value (close to 100\%), then a given partition would almost never be broken down.
@@
 Figure \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
-Using the same moving window size, here $3\times3$, the effect of filtering is apparently proportional to the threshold values employed:
-  with sub-figures \ref{fig:k_mle_threshold_original} to \ref{fig:boxcar_filter} visualise qualitatively the effects of the kMLE speckle filter when the threshold is set at 0\% (or left untouched), 25\%, 80\% and 100\% (or equals to the boxcar filter) respectively.
-
-%	Fig. \ref{fig:k_mle_threshold_original} shows the original intensity image the speckle left untouched (0\%), 
-%	Fig. \ref{fig:k_mle_threshold_25pc} and Fig. \ref{fig:k_mle_threshold_80pc} visualise qualitatively the effects of the k-MLE filter when the threshold is set at 25\% and 80\% respectively, 
-%	while Fig. \ref{fig:boxcar_filter} shows that too much filtering (boxcar, i.e. 100\%) may lead to blurring effects.
+Using the same moving window size of $3\times3$, the effect of filtering is clearly proportional to the threshold values employed.
+This can be observed from Figs. \ref{fig:k_mle_threshold_original} to \ref{fig:boxcar_filter}
+where the  visual quality  reflects the effects of the kMLE speckle filter when its  
+threshold is set at 0\% (i.e. left untouched), 25\%, 80\% and 100\% (i.e. equals to the boxcar filter) respectively.
 
@@
 
-One way to improve the speckle suppression effect is by working on a larger window size. 
-To reduce the associated blurring effect,
-  a lower threshold-value than 100\% compared to the box-car filter would help
-    by providing an adaptive partitioning of the analysis window.
-Figure \ref{fig:k_mle_iterative_vs_boxcar} shows the visual performance of k-MLE filtering on $5 \times 5$ window.
+One way to improve the speckle filtering  performance is to use a larger window size.
+Fig. \ref{fig:boxcar_5x5} shows the visual quality performance of k-MLE filtering on $5 \times 5$ window.
+As can be seen, the blurring effect in comparison to $3 \times 3$ filters is clearly visible.
+To reduce the associated blurring effect, a threshold-value lower than 100\%  would help by providing an adaptive partitioning of the analysis
+window (via the k-MLE clustering algorithm).
 
@@
 
-Another way to improve the raw kMLE speckle filter is to apply it iteratively.
-As can be seen in figure \ref{fig:k_mle_diff_threshold}, a normal 3x3 k-mle filter would not filter as much noise as a similar boxcar filter would. 
-At the same time, a 5x5 boxcar filter while having better speckle suppression power, would lose out by the blurring effects (see Fig. \ref{fig:boxcar_5x5}). 
-To improve k-MLE filtering power while avoiding the blurring effect, the kMLE speckle filter can be used iteratively. 
+Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
+As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal 3x3 k-MLE filter would not filter as much noise as a 3x3 boxcar filter. 
+At the same time, a 5x5 boxcar filter while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
+To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
 Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a 3x3 window with 25\% threshold-value, being applied iteratively for four times. 
-%The filtering power is illustrated and the plot shows similar performance with a 5x5 boxcar filter, while the filtered image is rendered with much less blurring effect.
 From the plot, the $3 \times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5 \times 5$ boxcar filter,
-  while its visual imagary output appears much sharper, qualititatively speaking.
+  while its visual imagery output appears much sharper, qualitatively speaking.
 
@@
 
-\subsubsection{Evaluation of the kMLE speckle filter on Simulated targets}
+\subsubsection{Evaluation of the kMLE speckle filter on simulated targets}
 
 A number of point targets were simulated on a homogeneous background clutter. 
-The ground truth SNR between the target and background clutter is fixed at 9dB. 
-The original, speckled images are presented in Figure \ref{fig:sar_point_target_test_boxcar_k_mle}.
-Subsequently, the kMLE speckle filter is to be benchmarked against the standard boxcar filters.
+In this test, the SNR between the target and background clutter is fixed at 9dB. 
+%The original, speckled images are presented in Figure \ref{fig:sar_point_target_test_boxcar_k_mle}.
+Subsequently, the kMLE speckle filter is to be benchmarked against the standard boxcar filters as shown in Fig. \ref{fig:sar_point_target_test_boxcar_k_mle}.
 %Both qualitative and quantitative comparisons is done between boxcar filters and the proposed iterative k-MLE filter.
-Qualitatively speaking, it is apparent that the kMLE speckle filter delivers
+Qualitatively speaking, it is clear that the kMLE speckle filter delivers
 a resultant image with both sharper edges than the 5x5 boxcar filter and a stronger visual contrast  than the 3x3 boxcar filter.
 %a sharper image than the 5x5 boxcar filter, at the same time its result has better contrast than the 3x3 boxcar filter.
-Quantitatively, the k-MLE also appears to have the best histogram response, of all the 3 filters compared.
+Quantitatively, the k-MLE also appears to have the best histogram response among the 3 filters compared.
 
@@
 
-\subsubsection{Evaluation of the kMLE speckle filter on Real Images}
-
-The filters are applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
+\subsubsection{Evaluation of the k-MLE speckle filter on Real Images}
+
+The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
 Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
-Apparently the kMLE speckle filter delivers a significantly ``better'' image than the original data.
+It is obvious that the kMLE speckle filter delivers a significantly ``better'' image than the original data.
 
@@
 
-%SAR is stochastic and SAR speckle filtering is the removal of stochastic ``noise''.
-The principle of many speckle filters in removing the stochastic noise is to group data into homogeneous areas.
+As mentioned earlier, speckle filters removes the stochastic noise by grouping data into homogeneous areas. 
 In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
@@
 	$n$ is the total number of pixel in the surrounding areas.
-The implicit assumption is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
-%Clearly, in real-life images, the assumption in boxcar filter is too easy to get violated.
-%In a filter previously proposed by the authors
-In the kMLE filter presented above and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is given in Eqn. \ref{eqn:kmle},
+The implicit assumption for this filter is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
+In the k-MLE filter presented in the previous section and in \citep{Le_2010_ACRS}, the surrounding region is partitioned into homogeneous areas and the approximation is based on Eqn. \ref{eqn:kmle},
 where 
@@
 
-\begin{tabular}{c c}
-\begin{minipage}[c]{0.45\textwidth}
+%\begin{tabular}{c c}
+%\begin{minipage}[c]{0.45\textwidth}
 \begin{equation}
 \label{eqn:boxcar}
+\caption{eqn:Boxcar Speckle Filter Estimation}
 f_{boxcar} = \displaystyle{\sum_{i=1}^n{I_i}} / n 
 \end{equation}
-\end{minipage}
-\begin{minipage}[c]{0.45\textwidth}
+%\end{minipage}
+%\begin{minipage}[c]{0.45\textwidth}
 \begin{equation}
 \label{eqn:kmle}
+\caption{eqn:k-MLE Speckle Filter Estimation}
 f_{kMLE }= \displaystyle{\sum_{i=1}^k{I_i} } / k 
 \end{equation}
-\end{minipage}
-\end{tabular}
-
-%By and large,
-While it appears logical to classify surrounding pixels as being either in the same homogeneous area with the central point or not,
+%\end{minipage}
+%\end{tabular}
+
+While it appears logical to classify surrounding pixels as falling either inside or outside the same homogeneous area with the central point,
   the concept of ``homogeneous area'' lacks precise definition and boundaries.
-%This is self-evident in the need for a threshold on the variance measured to assert homogeneity in an ensemble of stochastic samples.
 In fact, the classification decisions between homogeneity and heterogeneity are probabilistic in nature.
-%the concept of “homogeneous area” lacks precise definition and boundaries. 
-This is evident in the statistical hypothesis testing used to support these decision makings.
-
-The fMLE speckle filter presented in this section follow fuzzy logic approach,
-  which, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
+This is evident in the statistical hypothesis testing used to support these decision makings \cite{Le_2010_ACRS}.
+
+%The f-MLE speckle filter presented
+In this section fuzzy logic approach is followed
+  where, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
   embraces truth values that range from 1 to 0.
-Thus instead of making an YES/NO decision on whether or not a data point is in the same homogeneous region with the estimating central point, a fuzzy probabilistic scale is calculated.
-Then the noise-removal impact of the surrounding data point will be scaled with this possibilistic probability,
-  in comparison to the usual scheme that proceeds with ``full impact'' or ``no impact at all''.
-The benefit of this fuzzy logic approach is that: we no longer need to worry about the homogeneous / heterogeneous problem.
-
-%The idea presented in this paper is structured as follows:
-%Section \ref{sec:fmle_estimation} will describe the FMLE estimation in details.
-%The performance of the proposed filter will be evaluated in Section \ref{sec:results_eval}.
-%Finally, Section \ref{sec:conclusion} concludes this paper.
-%The last section will offers some conclusion and finalizes the paper.
-
-\subsection{The FMLE SAR Speckle Filters}
+Thus instead of making a YES/NO decision on whether or not a data point is in the same homogeneous region with the estimated central point, a fuzzy probabilistic scale is calculated.
+Then the noise-removal impact of the surrounding data point will be scaled with this probability value.
+This fuzzy logic approach give rise to the f-MLE speckle filter presented next,
+  and its main benefit is that:  we no longer need to worry about the homogeneous / heterogeneous problem.
+
+\subsection{The F-MLE SAR Speckle Filters}
 
@@
 %It is shown in \cite{Le_2010_ACRS}
-The consistent sense of distance states that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution.
+The consistent measure of distance states that given two SAR intensity samples coming from the same background, their distance in the log transformed domain follows a fixed distribution according to Eqn.
+\ref{eqn:SAR Log Intensity Contrast PDF}.
 
@@
 	$I^i$ is the \textit{$i^{th}$} intensity sample in the originally measured domain,
-	$L_I^I$ is the value of that sample in the log-transformed domain.
+	$L_I^i$ is the value of that sample in the log-transformed domain.
 %Distance in log-transformed domain is defined as:
-The log-contrast is then defined as:
-$D= L_I^1 - L_I^2$. 
-Assumming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
+The contrast is then defined as:
+$C= L_I^1 - L_I^2$. 
+Assuming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
   then this dis-similarity distance will follow the distribution 
-$pdf(D)= \frac{2^D}{(1+2^D)^2} \ln2$,
+$pdf(C)= \frac{2^C}{(1+2^C)^2} \ln2$,
   which is consistent.
@@
 
-\subsubsection{FMLE Estimation}
+\subsubsection{F-MLE Estimation}
 
 In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
-$p_i = pdf(D_i)$, with $D_i=log_2(I_i) - log_2(I_0)$.
+$p_i = pdf(C_i)$, with $C_i=log_2(I_i) - log_2(I_0)$.
 The fMLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.
@@
 %The figures demonstrate speckle being filtering effects.
-In implementing this statistical estimator, there are very noticable black dots in the filtered output image.
+In implementing this statistical estimator, there are very noticeable black dots in the filtered output image.
 These dots can be explained as the long-tailed nature of the intensity PDF, 
@@
 In this all-inclusive scheme, there is 
-	a single $D_0=0$ (at $I_0$) in the middle of other very large $D_{i, (i > 0)}$, which results in
+	a single $C_0=0$ (at $I_0$) in the middle of other very large $C_{i, (i > 0)}$, which results in
 	a single significant $p_0$ (at $I_0$), and other probably insignificant $p_{i, (i>0)}$.
-This marginalises the filtering power of surrounding pixels.
+This marginalizes the filtering power of surrounding pixels.
 One way to counter this effect is to exclude the centre point $I_0$ from its estimation,
@@
 
-\begin{tabular}{c c}
-\begin{minipage}[c]{0.45\textwidth}
+%\begin{tabular}{c c}
+%\begin{minipage}[c]{0.45\textwidth}
 \begin{equation}
 \label{eqn:fmle_incl}
+\caption{eqn:F-MLE Estimation (Inclusive Version)}
 FMLE_{incl}= \frac{\displaystyle{\sum_{i=0}^n{p_i * I_i} } }{\displaystyle{\sum_{i=0}^n{p_i } } }
 \end{equation}
-\end{minipage}
-\begin{minipage}[c]{0.45\textwidth}
+%\end{minipage}
+%\begin{minipage}[c]{0.45\textwidth}
 \begin{equation}
 \label{eqn:fmle_excl}
+\caption{eqn:F-MLE Estimation (Exclusive Version)}
 FMLE_{excl}= \frac{\displaystyle{\sum_{i=1}^n{p_i * I_i} } }{\displaystyle{\sum_{i=1}^n{p_i } } } 
 \end{equation}
-\end{minipage}
-\end{tabular}
+%\end{minipage}
+%\end{tabular}
 
 %\subsection{Comparing the two schemes}
-For visualization and comparison purposes, both filtering schemes are applied to an simulated single-look homogeneous scene 
-and the histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original}.
-The speckle suppression power is clearly visible.
+For visualization and comparison purposes, both filtering schemes are applied to an simulated single-look homogeneous scene.
+The histogram of the filtered images are plotted in Fig. \ref{fig:compare_filters_histograms:Original} and Fig. \ref{fig:compare_filters_distance_histograms:Original},
+  where the speckle suppression power is clearly visible.
 %demonstrated in Figure \ref{fig:compare_filters_histograms:Original}.
-For comparison, the two schemes’ histogram are plotted in the same figure.
+%For comparison, the two schemes’ histogram are plotted in the same figure.
 %In comparing the two schemes' histogram in the same figure,
 And it is apparent that 
-	the filtering power of ignoring centre point scheme is at least as powerful as that of centre point included scheme and
+	the filtering performance of the excluding-centre-point scheme is at least as good as that of the centre-point-included scheme and
 	the skewness in the histogram of the exclusive scheme is less than that of the inclusive estimation.
 
-\begin{figure}[H]
+\begin{figure}[h!]
 \centering
@@
   }
-\caption{Consistent Distance Property and the FMLE Estimations}
-\end{figure}
-
-\begin{figure}[H]
+\caption{Consistent Distance Property and the F-MLE Estimations}
+\end{figure}
+
+\begin{figure}[h!]
 \centering
@@
 	}\\ 
- 	\subfloat[FMLE (incl) outputs\label{fig:compare_filters_distance_histograms:Filtered:incl}]{
+ 	\subfloat[F-MLE (incl) outputs\label{fig:compare_filters_distance_histograms:Filtered:incl}]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[FMLE (excl) outputs\label{fig:compare_filters_distance_histograms:Filtered:excl}]{
+	\subfloat[F-MLE (excl) outputs\label{fig:compare_filters_distance_histograms:Filtered:excl}]{
 		 \epsfxsize=6cm
@@
 \end{tabular}
-\caption{Consistent Distance Property and the FMLE Estimations}
+\caption{Consistent Distance Property and the F-MLE Estimations}
 \label{fig:Consistent_Distance_Property_and_the_FMLE_Estimations}
@@
 Fig.
-\ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above being applied on the inputs depicted in Fig.
+\ref{fig:compare_filters_distance_histograms:Filtered:incl} and \ref{fig:compare_filters_distance_histograms:Filtered:excl} plot the filtering treatment described above when applied on the inputs depicted in Fig.
 \ref{fig:compare_filters_histograms:Original}.
-They clearly demonstrate that the FMLE speckle filters preserves the consistent sense of distance.
+They clearly demonstrate that the F-MLE speckle filters preserves the consistent sense of distance.
 This can be explained from the consistent histogram of the input log distance PDF.
@@
 Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
-This renders the task of giving analytical PDF for the output log-distance impractical.
-However, large scale computer simulations can be used to provide an usable histogram, from which a PDF can estimated.
+%This renders the task of giving analytical PDF for the output log-distance impractical.
+This renders the task of deriving an analytical PDF expression impractical for the  log-distance output. 
+However, large scale computer simulations can be used to provide a usable histogram, from which a PDF can be estimated.
 %from large scale simulations. 
@@
 
-\subsubsection{Recursively Applying Fuzzy MLE Filter}
-
-The preservation of consistent distance property is the enabling factor that allows the recursive application of FMLE filters.
+\subsubsection{Recursively Applying The F-MLE Filters}
+
+The preservation of consistent distance property is the enabling factor that allows the recursive application of F-MLE filters.
 Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
@@
 \centering
-	\subfloat[FMLE (incl): 123]{
+	\subfloat[F-MLE (incl): 123]{
 		 \epsfxsize=3.5cm
@@
 	}
-	\subfloat[FMLE (incl): 456]{
+	\subfloat[F-MLE (incl): 456]{
 		 \epsfxsize=3.5cm
@@
 	} 
-	\subfloat[FMLE (excl): 123]{
+	\subfloat[F-MLE (excl): 123]{
 		 \epsfxsize=3.5cm
@@
 	}
-	\subfloat[FMLE (excl): 456]{          
+	\subfloat[F-MLE (excl): 456]{          
 		 \epsfxsize=3.5cm
@@
 
-\subsection{Evaluating the FMLE SAR speckle filters}
+\subsection{Evaluating the F-MLE SAR speckle filters}
 
@@
 
-The performance of speckle filters are normally evaluated based on a few criteria \citep{Nyoungui_2002_IntlJRemoteSense}.
+The performance of speckle filters are normally evaluated based on a number of criteria \citep{Nyoungui_2002_IntlJRemoteSense}.
 The most widely used criteria is speckle suppression, 
   which is often evaluated over homogeneous area.
-The other important criteria include radiometric preservation, something undeniably desirable in the filtered output.
+The other important criteria include radiometric preservation, something obviously desirable in the filtered output.
 In practical terms, the most common usage of speckle filtered imagery include target and feature detection and classification.
@@
 
-The performance of the FMLE filter is evaluated both qualitatively against real
+The performance of the F-MLE filter is evaluated both qualitatively against real
 images and quantitatively via simulated experiments. 
-Over homogeneous regions, the speckle suppression power is
-evaluated by measuring the ubiquitous MSE on simulated and truth-grounded experiments. 
-The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
-
-For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as
-statistical evidence for better performance in the subsequent tasks of target detection
-and surface classification. 
-Experiments confirm the power of FMLE filters in various
-heterogeneously simulated areas. 
-A good correlation between the MSE and the AUC index is also exhibited. 
-The result suggests that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
 Let us start with a qualitative visual evaluation of the speckle filter on real-captured images.
 
-%We highlight the use of the ROC curve and the area under it as the statistical evidence of separability between target and clutter PDFs.
-%We then show that lower MSE achievable by FMLE filters does lead to better performance in the subsequent tasks of target detection and classification.
-%As is customary, we start by an visual evaluation of the filter on real-life images.
-%We start with visual evaluation of the filters on real-life images.
-
-\subsubsection{Qualititative Evaluation on Real Images}
+\subsubsection{Qualitative Evaluation on Real Images}
 
@@
 	}\\
-	\subfloat[FMLE incl, iter 1]{
+	\subfloat[F-MLE incl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[FMLE incl, iter 2]{
+	\subfloat[F-MLE incl, iter 2]{
 		 \epsfxsize=6cm
@@
 	} \\
-	\subfloat[FMLE excl, iter 1]{
+	\subfloat[F-MLE excl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[FMLE excl, iter 2]{
+	\subfloat[F-MLE excl, iter 2]{
 		 \epsfxsize=6cm
@@
 	\end{tabular}
-\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Natural Surface}
+\caption{Qualitative Evaluation of F-MLE filter on Real Life Scene of Natural Surface}
 \label{fig:fmle.real.images}
@@
 	} \\
-	\subfloat[FMLE incl, iter 1]{
+	\subfloat[F-MLE incl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \\ 
-	\subfloat[FMLE excl, iter 1]{
+	\subfloat[F-MLE excl, iter 1]{
 		 \epsfxsize=6cm
@@
 	\end{tabular}
-\caption{Qualitative Evaluation of FMLE filter on Real Life Scene of Urban Landscape}
+\caption{Qualitative Evaluation of F-MLE filter on Real Life Scene of Urban Landscape}
 \label{fig:fmle.real.images}
@@
      \end{tabular}
-\caption{Homogeneous Area: MSE criteria and speckle suppression power of FMLE filters}
+\caption{Homogeneous Area: MSE criteria and speckle suppression power of F-MLE filters}
 \label{fig:Homogeneous_Area}
@@
 The normal application after applying filters on SAR images is to detect the existence of certain target within its surrounding clutters or other similar classification / discrimination tasks.
-The most common type of detector (or classifier) employs a threshold based approach in determing whether an abnormal value signifies the existence of a target.
+The most common type of detector (or classifier) employs a threshold based approach in determining whether an abnormal value signifies the existence of a target.
 The Receiver Characteristic Curve (ROC) and the area under it (AUC) is typically used to evaluate the detectability of target features \citep{Mazurowski_2009_IJCNN}.
@@
 The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
-Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of FMLE filters for heterogenous regions.
-Aapparently the fMLE filters have better performance than boxcar filters.
+Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of F-MLE filters for heterogenous regions.
+Apparently the f-MLE filters have better performance than boxcar filters.
 Also noticeable is the correlation between MSE and the Area Under the ROC curve criteria, 
@@
 %  the correlation between MSE and Area Under the ROC curve (AUC) is apparent,
-%Also FMLE filters apparently have better performance than boxcar filters.
-
-\begin{figure}
+
+\begin{figure}[h!]
 \begin{minipage}[c]{0.48\textwidth}
@@
 \hline
-Point Target 	& FMLE (incl, 3x3) 	& 1.38	& 0.901 \\
-Point Target 	& FMLE (excl, 3x3) 	& 1.47	& 0.893 \\
+Point Target 	& F-MLE (incl, 3x3) 	& 1.38	& 0.901 \\
+Point Target 	& F-MLE (excl, 3x3) 	& 1.47	& 0.893 \\
 Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
@@
 \hline
-Edge 	& FMLE (incl, 3x3) 	& 0.68	& 0.969 \\
-Edge 	& FMLE (excl, 3x3) 	& 0.73	& 0.964 \\
+Edge 	& F-MLE (incl, 3x3) 	& 0.68	& 0.969 \\
+Edge 	& F-MLE (excl, 3x3) 	& 0.73	& 0.964 \\
 Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
@@
 \hline
-Line 	& FMLE (incl, 3x3) 	& 1.89	& 0.791 \\
-Line 	& FMLE (excl, 3x3) 	& 2.02	& 0.767 \\
+Line 	& F-MLE (incl, 3x3) 	& 1.89	& 0.791 \\
+Line 	& F-MLE (excl, 3x3) 	& 2.02	& 0.767 \\
 Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
@@
 \hline
-Dotted 			& FMLE (incl, 3x3) 	& 2.28	& 0.639 \\
-Dotted 			& FMLE (excl, 3x3) 	& 2.32	& 0.621 \\
+Dotted 			& F-MLE (incl, 3x3) 	& 2.28	& 0.639 \\
+Dotted 			& F-MLE (excl, 3x3) 	& 2.32	& 0.621 \\
 Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
@@
 %\end{tabular}
-\caption{Heterogeneous Patterns: MSE criteria and FMLE performance}
+\caption{Heterogeneous Patterns: MSE criteria and F-MLE performance}
 \label{fig:Heterogeneous_Patterns}
 \end{figure}
-\afterpage{\clearpage}
-
-\subsubsection{Contribution and Conclusions}
-
-%The log-transformed domain provides a consistent sense of distance.
-%By embracing a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes use of this consistency.
-%Experimental results suggest that the estimator's output also exhibits this consistency property, which allows recursive application of the filter discussed above.
-%
-%The performance of the filter is evaluated both qualitatively against real images and quantitatively via simulated experiments.
-%The speckle suppression power is evaluated by measuring the ubiquitous MSE on simulated and perfectly homogeneous truth-grounded experiments.
-%The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
-%
-%For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as statistical evidence for better performance in the subsequent tasks of target detection and surface classification.
-%Experiments confirm the power of FMLE filters in various heterogeneously simulated areas.
-%They also exhibit good correlation between the MSE and the AUC index.
+
+\subsubsection{Summary}
 
@@
 With the fuzziness be taken to a new level, fuzzy probabilistic speckle filters which requires no clustering have been specified and designed.
+
+The filter is rigoriously evaluated.
+Over homogeneous regions, the speckle suppression power is
+evaluated by measuring the ubiquitous MSE on simulated and truth-grounded experiments. 
+The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
+For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as
+statistical evidence for better performance in the subsequent tasks of target detection
+and surface classification. 
+Experiments confirm the power of F-MLE filters in various
+heterogeneously simulated areas. 
+A good correlation between the MSE and the AUC index is also exhibited. 
+The result suggests that lower MSE achievable by F-MLE filters does lead to better performance in the subsequent tasks of target detection and classification.
 
@@
 
-\section{Evaluating SAR Speckle Filters using the consistent measures}
+\section{Evaluating SAR Speckle Filters using the consistent measures of distance}
 
@@
   with lower bias and/or lower variance lead to lower MSE, which then indicates better accuracy.
-Ideally, the evaluation of SAR speckle filters should be based both qualitatively on some real data and quantitatively through simulated experiments. 
+Ideally, the evaluation of SAR speckle filters' performance should be based both qualitatively on some real data and quantitatively through simulated experiments. 
 In addition, due to the stochastic nature of SAR-processing, and its simulating process, 
@@
 
-Our survey of SAR speckle filter research, however, indicates 
-	a different picture from the standard practice of the statistical framework, 
-	specifically, in the stage of performance evaluation. 
+%Our survey of SAR speckle filter research, however, indicates 
+%	a different picture from the standard practice of the statistical framework, 
+%	specifically, in the stage of performance evaluation.
+However, current SAR speckle filter performance evaluations uses a different approach
+  from the standard practice of the statistical estimation framework.        
 Due to the multiplicative and heteroskedastic nature of speckle noise, 
-	bias and variance evaluation may not be the most useful measures. 
+	bias and variance evaluation would not be the most useful measures. 
 Thus, the standard evaluation metric of mean-squared-error is not easily applicable,
 	prompting alternative evaluation criteria to be proposed.
-In fact, our survey of relevant literature fails to reveal 
-	a single universally agreed quantitative metric for the performance of speckle filters.
+Although there are alternative evaluation criteria being  proposed,
+  there is currently  no  single universally agreed quantitative metric for the performance of speckle filters.
+%In fact, our survey of relevant literature fails to reveal 
+%	a single universally agreed quantitative metric for the performance of speckle filters.
 
@@
 To do quantitative evaluation of different speckle filters, it is necessary to compare a filtered result with a ground-truth image. 
-Furthermore, it is desirable that the error, i.e. the distance between the filtered output and the original input, should be consistent and independent to the particular simulated scenario. 
-Simplistically speaking, the measure of choice is in the original SAR intensity or amplitude domain. 
-However owing to the homoskedastic effects of the log-transformation, the error in log-transformed domain is preferred.
-%However owing to the homoskedastic effects of the log-transformation, this section shows that the error in log-transformed domain offers a better evaluation metric.  
-Homoskedasticity makes ordinary least square (OLS) approaches becomes valuable again. 
-Synonymous to OLS is the use of standard Mean Squared Error as a performance index.
+Furthermore, it is desirable that the error, i.e. the difference between the filtered output and the original input, should be consistent and independent to the particular simulated scenario.
+
+In general, the measure of difference for evaluation should be based on the original SAR intensity or amplitude domain. 
+However owing to the additive and homoskedastic effects of the log-transformation,
+  the error measured in log-transformed domain is preferred here.
+This is because homoskedasticity would allow the use of standard Minimum Squared Error as a performance index.   
 In this section, the use of MSE in the homoskedastic log-transformed domain to evaluate SAR speckle filters is proposed and validated.
-%\begin{equation}
-%\Psi = \displaystyle{ \frac{ \sum^N_{i=1}{(Y^L_i - X^L_i)^2} }{N} }
-%\end{equation}
-%where $Y^L_i$ indicates filtered output values and $X^L_i$ denotes the original input as ground-truth values, $N$ is the number of data points available
-%This section will shows that in a homogeneous area, this performance index is similar to the standard Equivalent Number of Looks (ENL) measures, while investigating the value in heterogeneous areas shows how well the filter adapts to underlying spatial variations.
-
-%\section{Using MSE to evaluate SAR speckle filters}
 
@@
 SAR speckle filtering process.
-The ``SAR processor'' block indicates that either one of the following processes can occur.
+%The ``SAR processor'' block indicates that either one of the following processes can occur.
+There are two approaches that can be used to implement the  indicated ``SAR processor'' block.
 First is the normal process of SAR processing where the unknown ground radiometric attribute ($X$) is recorded 
@@
 	and outputs $\hat{X}$ as a better estimation of the ground-truth (i.e. $X$).
-The speckle filters used in this section are: 
-	boxcar filter, enhanced Lee filter, enhanced Kuan filter, enhanced Frost filter, Gamma Map filter 
-	and PDE filter \cite{You_TIP_2000}.
-Evidently for the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
+The speckle filters employed in this section include: 
+	the boxcar filter, the enhanced Lee filter, the enhanced Kuan filter, the enhanced Frost filter, the Gamma Map filter 
+	and the PDE filter \cite{You_TIP_2000}.
+%Evidently for the special case where there is no filter applied then $\hat{X}^{none} = \tilde{X}$.
 %Thus $MSE_{residual}^{none} = MSE_{base}$
@@
 real RADARSAT SAR image.
-``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in 
+``Visible'' structure appears to be more easily discerniable in the log-2 residual random pictures than in 
 the ratio images, although this conclusion is of course itself a subjective one.
@@
 \afterpage{\clearpage}
-\begin{figure}
+\begin{figure}[h!]
 \centering  
@@
 
-\begin{subequations} \label{eqn:eval_metric}
+\begin{subequations}
+  \label{eqn:eval_metric}
+  \caption{eqn:MSE Evaluation Metrics for SAR}
 \begin{align}
-MSE_{true} = E \left[ (\hat{X}^L - X^L)^2 \right] \\
-MSE_{base} = E \left[ (\tilde{X}^L - X^L)^2 \right] \\
-MSE_{noise} = MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
-MSE_{benchmark} = \left| MSE_{residual} - MSE_{base} \right| 
+MSE_{true} &= E \left[ (\hat{X}^L - X^L)^2 \right] \\
+MSE_{base} &= E \left[ (\tilde{X}^L - X^L)^2 \right] \\
+MSE_{noise} &= MSE_{residual} = E \left[ (\hat{X}^L - \tilde{X}^L)^2 \right] \\
+MSE_{benchmark} &= \left| MSE_{residual} - MSE_{base} \right| 
 \end{align}
@@
 That is $MSE_{noise}$ should track the base MSE as close as possible,
-  making the $MSE_{benchmark}$ should be as close to 0 as possible.
+  making the $MSE_{benchmark}$ as close to 0 as possible.
 
@@
 probably insignificant in comparison to the other components, namely, variance evaluation. 
-Subsection \ref{sec:homogeneous_theoretical} gives a theoretical justification for our methodology where variance 
+%Subsection \ref{sec:homogeneous_theoretical} gives
+The next section will give a theoretical justification for our methodology where variance 
 methods of evaluation are shown to be mathematically related to the ENL index.
-The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
+%The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
 over homogeneous areas.
 
-\subsubsection{ Estimating ENL from the log-variance index in homogeneous areas }
+\subsubsection{Estimating ENL from the log-variance index in homogeneous areas}
 \label{sec:homogeneous_theoretical}
 
-In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL 
-index.
+%In this subsection, we show that the variance in the log-transformed domain can be related mathematically to the ENL index.
 %Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
@@
 variables as: 
-\begin{equation}
+\begin{equation*}
 var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
 \label{eqn:perf_index_theoretical}
-\end{equation}
+\end{equation*}
 
 %Next we will be showing that the ENL, i.e. L, can be estimated from a given $var(Y^L)$. 
-Taking results of the Euler proof for the Basel problem, we have $\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
-Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
+Based on the Euler proof for the Basel problem, we have
+%$\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } $, then $var(Y^L)= \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) $.
+%Noting that $ \frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i}$, then $ \frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} $.
+%\setlength{\mathindent}{1cm}  
+\begin{align*}
+&\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } &\\
+\noindent \text{then: } \\ 
+&var(Y^L) = \frac{1}{\ln^2(2)} \left( \sum^{\infty}_{i=L}{ \frac{1}{i^2} } \right) &\\
+\noindent \text{Noting that: }  \\
+&\frac{1}{i} - \frac{1}{i+1} = \frac{1}{i(i+1)} < \frac{1}{i^2} < \frac{1}{i(i-1)} = \frac{1}{i-1} - \frac{1}{i} &\\
+\noindent \text{then: } \\
+&\frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} &
+\end{align*}
+
 In fact, we could estimate:
@@
 \label{eqn:perf_index_analytic}
+\caption{eqn:Approximation of Homoskedastic Log-Variance from given SAR ENL}
 \end{equation}
@@
 \label{eqn:enl_analytic}
+\caption{eqn:Estimation of SAR ENL from Variance in Log-Transformed Domain}
 \end{equation}
 
-The above analysis can be verified experimentally. First, a $512\times512$ homogeneous area is generated and 
+The above analysis can be verified experimentally as follows.
+First, a $512\times512$ homogeneous area is generated and 
 corrupted with single look SAR-speckle PDF. 
@@
 	 ENL is then estimated from Eqn. \ref{eqn:enl_analytic} for each simulation.
-The simulation is performed multiple times, with Table \ref{tab:enl_in_log_domain} reporting the results in terms 
-of mean and standard deviation.
+This simulation is performed multiple times. %with Table \ref{tab:enl_in_log_domain} reporting
+The results in terms of mean and standard deviation are consolidated in Table \ref{tab:enl_in_log_domain}.
 The theoretical variances are calculated from Equation \ref{eqn:perf_index_theoretical}, 
@@
 
-The relationship exposed here may also help to unite other seemingly unrelated results.
+The relationship proposed here may also help to unite other seemingly unrelated results.
 For example, 
@@
   this evaluation approach is equivalent the established ENL evaluation methodology.
-In fact, a few more observations and analysis can be carried out.
+In fact, a few more observations and analysis can be carried out as follows.
 
@@
 Both single-look simulated and multi-look processed/box-car filtered data is displayed.
-Specifically the plots show that the log-transformed domain is consistent while the plots from the original 
-domain are not.
-
-\begin{figure}
+Specifically the plots show that the log-transformed domain is consistent,
+  i.e. they retains similar shapes regardless of the underlying signal value,
+  while the plots from the original domain are not.
+
+\begin{figure}[h!]
 \centering  
@@
 multi-look processing, its output also exhibits this consistency.
-The following paragraph explains why this preservation of the consistent property is important in evaluating SAR speckle filters.
-
-%This consistency will also lead to the consistent sense of distance described earlier, which is significant 
-%because it is the tell-tale indicator of the consistent contrast and variance.
-This consistency is significant because it leads to the consistent sense of distance, contrast and variance described earlier.
+The preservation of this consistent property is important in evaluating SAR speckle filters as
+  it leads to the consistent sense of distance, contrast and variance described earlier.
 It also ensures applicability of various target detection/classification algorithms 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \centering  
@@
 
-\begin{table}
+\begin{table}[h!]
 \centering
@@
 
-\afterpage{\clearpage}
-
-\subsection{ Evaluating SAR Speckle Filters over Heterogeneous Scenes }
+\subsection{Evaluating SAR Speckle Filters over Heterogeneous Scenes }
 \label{sec:eval_hetero}
@@
 In this section, the MSE criteria ($MSE_{true}$) in the log-transformed domain is validated through experiments and analysis.
-Analytically, on clear-cut simple target-background patterns, MSE is shown to be related to the target / background separation capabilities. 
-Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
-	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
-Experimentally, the results that follow will indicate that
-	the lower the MSE achievable by a speckle filter,
-	the better the feature preservation performance recorded for its output.
 
@@
 
-The test patterns used in this section include:
+The test patterns used in this section include the following pattern:
   point targets, line targets, edge targets and a heterogeneous checker board. 
@@
 Each pattern comprises two classes of ground-truth: background and target areas,
-with the target is signified by the brighter area of the image as conventionally used in the 
+with the target signified by the brighter area of the image as conventionally used in the 
 radar community.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 \begin{tabular}{c}
@@
 
-%From a high-level perspective,
-Specifically, Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
+Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
 evaluated by examining the separability of the two background and target populations.
-Subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+Figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
 	allows visual evaluation of target and clutter histograms and their separability.
@@
 
-%visualizes the two histograms
-%The separability of the two histograms, subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered}, 
-%	is visualized by plotting the Receiver Operating Curve (ROC), subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} respectively,
-%	and is measured by computing the Area Under these Curves (AUC).
-
-%\clearpage
-
-\begin{figure}
+\afterpage{\clearpage}
+\begin{figure}[h!]
 \centering  
@@
 	can help to explain how the MSE is related to the histograms' separation capability.
-In pre-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
+In pre-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
 \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
@@
 
-In post-filtered images, shown in subfigures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
+In post-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
 \ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
 Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
-Close investigation of subfigure \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
+A closer examination of Fig. \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
 Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
@@
 
-Speaking in SAR domain terminology, the general requirements of feature preservation for SAR speckle filters can be broken 
+In SAR domain terminology, the general requirements of feature preservation for SAR speckle filters can be broken 
 down into the requirements of radiometric preservation and speckle suppression.
-In the log-transformed domain, these smaller requirements are equivalent respectively to the bias and variance evaluation of 
-statistical estimators.
+In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
+statistical estimators respectively.
 Overall, while the MSE index combines the measurements of bias and variance evaluation, 
@@
 	the standard metric for target detectability: the Area Under the ROC Curve (AUC).
-%We show experimentally that MSE inversely correlates with the AUC index, for each of the %simulated patterns.
+
 Next the MSE is experimentally shown to be inversely correlated with the AUC index, for all simulated patterns.
-
-%Also the speckle suppression is related to the measured variance.
-%Thus, the MSE performance of the estimator, which combines the effect of bias and variance error, can be used to 
-%evaluate the separability of the two histograms. 
 Table \ref{tab:mse_auc_in_log_domain} provides the measurements of MSE and AUC performance for various filters and 
@@
 
-\afterpage{\clearpage}
-\begin{figure}
+%\afterpage{\clearpage}
+\begin{figure}[h!]
 \centering  
@@
 
+Thus in this section, the MSE criteria in the log-transformed domain is validated through experiments and analysis.
+Analytically, on clear-cut simple target-background patterns, MSE is shown to be related to the target / background separation capabilities. 
+Because the log-transformation converts heteroskedastic SAR speckle into a homoskedastic distribution model, 
+	the log-transformed domains MSE is much preferred to MSE in the original SAR domain.
+Experimentally, the results that follow will indicate that
+	the lower the MSE achievable by a speckle filter,
+	the better the feature preservation performance recorded for its output.
+
 \subsection{Using MSE to find the most suitable speckle filter for practical SAR images}
@@
 In this section, our conjecture
-%(??? you want to emphasize this is a proposal that can't be proven mathematically ?)
-%ans: it is true that the conclusion cannot be proved, due to lack of absolute ground truth in real SAR images
-%our conclusion however is 1. extended from a simulations which is believed to be in agreement with realities.
 of using MSE in the log-transformed domain to find the most suitable speckle filter 
@@
 
-Then SAR speckle filters are applied onto the simulated images, and the various MSE in the log-transformed domain are computed.
+The SAR speckle filters are then applied onto the simulated images, and the various MSE in the log-transformed domain are computed.
 With the use of MSE being validated from previous experiments, 
 	the most suitable filter is deemed as the one with the lowest true MSE.
-The use of residual MSE is validated by investigating 
-Table \ref{tab:mse_true_noise_log_domain} which shows that among the various filters used, 
+The use of residual MSE is validated by examining the values shown in Table \ref{tab:mse_true_noise_log_domain}.
+It shows that among the various filters used, 
 	the most suitable filter is also the filter that 
@@
 
-\begin{figure}
-\normalsize
-\begin{center}
-\begin{tabular}{c}
-	\subfloat[Ground-Truth Image ]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
-		 \label{intensity}
-	} \\
-	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
-		 \label{intensity}
-	} \\
-	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
-		 \label{amplitude}
-	} 
-	\hfill	
-	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
-		 \label{intensity}
-	}
-\end{tabular}
-\caption{Filtering Simulated Real Images: Qualititative Validation}
-\label{fig:real_simulated_image_results}
-\end{center}
-\end{figure}
-
-The results from the experiments in previous sections can also be used to validate the use of residual and 
-benchmark MSE.
-The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the evaluation index is strongly 
-correlated with feature classification capability, measured by the standard AUC index.
-
-The conjecture is also validated in real SAR images.
-Different speckle filters are applied onto a real RADARSAT-2 image.
-In this case, since the ground-truth is not available, 
-	only visual evaluation can be used to validate our conjecture.
-Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
-Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE 
-would probably suggest a more suitable filter.
-Fig. \ref{fig:real_image_results} confirms this visually.
-%IVMThe conclusion in this can be found through further experiments with more images, 
-%IVM	which cannot be shown here due to space limitation.
-
-\begin{table}[t]
+%\afterpage{\clearpage}
+\begin{table}[h!]
 \centering
@@
 
-\begin{figure}[b]
+\afterpage{\clearpage}
+\begin{figure}[h!]
+\normalsize
+\begin{center}
+\begin{tabular}{c}
+	\subfloat[Ground-Truth Image ]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.gt.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Unfiltered Image $MSE_{true}=MSE_{base}=4.1174$]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.none.fi.jpg.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[PDE Result: $MSE_{true}=3.8022,MSE_{noise}=0.0073$]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.pde.fi.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Lee Result: $MSE_{true}=0.4984,MSE_{noise}=3.25553$]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.lee.fi.jpg.eps} 	
+		 \label{intensity}
+	} \\
+	\subfloat[Frost Result: $MSE_{true}=0.3490, MSE_{noise} = 4.6856$]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.frost.fi.jpg.eps} 	
+		 \label{amplitude}
+	} 
+	\hfill	
+	\subfloat[Boxcar Result: $MSE_{true} = 0.3107, MSE_{noise}= 4.2328$]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/simulated_images.vietnam_rural.boxcar.fi.jpg.eps} 	
+		 \label{intensity}
+	}
+\end{tabular}
+\caption{Filtering Simulated Real Images: Qualititative Validation}
+\label{fig:real_simulated_image_results}
+\end{center}
+\end{figure}
+
+The results from the experiments in previous sections can also be used to validate the use of residual and 
+benchmark MSE.
+The AUC-$MSE_{benchmark}$ column in Table \ref{tab:mse_auc_corr_coeff} shows that the evaluation index is strongly 
+correlated with feature classification capability, measured by the standard AUC index.
+
+The conjecture is also validated in real SAR images.
+Different speckle filters are applied onto a real RADARSAT-2 image.
+In this case, since the ground-truth is not available, 
+	only visual evaluation can be used to validate our conjecture.
+Table \ref{tab:mse_in_real_image} tabulates the computed MSE of the ``removed'' additive noise.
+Evidently all filters still leave some noise ``unremoved'', in which case, the higher removed noise MSE 
+would probably suggest a more suitable filter.
+Fig. \ref{fig:real_image_results} confirms this visually.
+%IVMThe conclusion in this can be found through further experiments with more images, 
+%IVM	which cannot be shown here due to space limitation.
+
+\begin{figure}[h!]
 \begin{tabular}{c}
@@
 
-\afterpage{\clearpage}
-\subsection{Discussion and Conclusions}
+\subsection{Discussion and Summary}
 
@@
 To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
-	is suggested \cite{Le_2011_ACRS}. Interestingly, averaging is also the MLE operator in the SAR's original domain.
+	is proposed in this thesis. %suggested \cite{Le_2011_ACRS}.
+        Interestingly, averaging is also the MLE operator in the SAR's original domain.
 
@@
   - which exploit these consistent statistical properties -
-  to not only perform brilliantly on pre-filtered data,
-  but also practically work on post-filtered data.
+  to perform brilliantly on pre-filtered as well as post-filtered data.
 
@@
 	basis. In fact, a number of proposed solutions have already appeared to exploit this feature. 
-A case in point is the simple ratio based discriminator in the original SAR domain.
+A case in point is the simple ratio based discriminator in the original SAR domain \cite{Rignot_1993_TGRS_896}.
 Looking backwards, in designing new speckle filters,
@@
 
-In this paper, stochastic simulation is used extensively to evaluate the performance of statistical estimators 
+In this section, stochastic simulation is used extensively to evaluate the performance of statistical estimators 
 (i.e. speckle filters).
@@
 
-\subsubsection{Conclusion}
-
-To summarise, speckle filters are generally evaluated using many different qualitative criteria.
+\subsubsection{Summary}
+
+To summarize, speckle filters are generally evaluated using many different qualitative criteria.
 To compare the filters against each other, a methodology is needed
@@
 
-\afterpage{\clearpage}
-
-%\section{FMLE POLSAR Speckle Filter using the consistent measures}
-
-%This section describes the application of one consistent measure of distance,
-%  namely contrast, in establishing a new POLSAR speckle filter.
-%The first sub-section illuminates how the principles of fuzzy logic and Maximum Liklyhood Estimation (MLE) can be employed.
-%The second sub-section illustrates that FMLE estimation preserves the consistency of contrast,
-%  and hence consistent variance and ENL can be expected.
-%The third sub-section introduces the recursive FMLE POLSAR speckle filter.
-
-%\subsection{Fuzzy MLE estimation of POLSAR covariance matrix}
-%\subsection{Preservation of the Consistency Properties in the FMLE outputs}
-%\subsection{Recursive FMLE Speckle Filters}
-%Compare increasing size FMLE vs decreasing size FMLE
-
-\section{Evaluating POLSAR Speckle Filters using the consistent measures}
+%\afterpage{\clearpage}
+
+\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
 
@@
   using the consistent measures of distance found in the homoskedastic log-transformed domain.
-The first subsection theoretically illustrates how the consistent variance is linked to the ENL index.
-The second sub-section then demonstrate how the POLSAR speckle filters can practically and quantitatively be evaluated over homogeneous areas.
-The third sub-section finally illustrates how POLSAR speckle filters can be visually evaluated on heterogeneous areas.
+The next subsection first illustrates theoretically how the consistent variance is linked to the ENL index.
+%The second sub-section then demonstrate how the POLSAR speckle filters can practically and quantitatively be evaluated over homogeneous areas.
+%The third sub-section finally illustrates how POLSAR speckle filters can be visually evaluated on heterogeneous areas.
 
@@
 
-%While Anfinsen solves the above equation to find ENL,
-%  we took variance approach.
-%Since we can ignore the constants $d\ln2 + d\ln{L} -ln|\Sigma|$ this approach might be simpler.
-
 This section discusses how ENL can be estimated using the log-variance approach in the homoskedastic, hence consistent variance, log-transformed domain.
-Specifically Eqn. TODO:REF can be rewritten as:
-\begin{equation}
-  var \left[ ln|C_v| \right] = \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{equation}
-Theoretically speaking, the above equation can be solved for the unknown L, which would require some iterative, and hence intensive, computation.
+%\begin{equation}
+%  var \left[ ln|C_v| \right] = \sum^{d-1}_{i=0} \psi^1(L-i)
+%\end{equation}
+Theoretically speaking, the Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be solved for the unknown L, which would require some iterative, and hence intensive, computation.
 Extending the result in the previous sub-section for SAR, simpler estimation can be derived as:
 \begin{equation}
+  \label{eqn:Estimate ENL from log-variance of POLSAR homogeneous areas}
+  \caption{eqn:Estimate ENL from log-variance of POLSAR homogeneous areas}
   L = d \left[ \frac{1}{var(\ln|C_v|)} + 0.5 \right]
@@
 
-In the case of one-dimensional SAR, d=1 then $|C_v|=I$ and
-$var(\ln{I}) = \psi^1(L)=\sum^{\infty}_{i=L}1/i^2$.
-Since $1/L < \sum^{\infty}_{i=L}1/i^2 < 1/(L-1)$, then $var(\ln{I})$ is bounded.
-Thus an approximation is made to compute L being:
-$L=1/var(\ln{I}) + 0.5 $ as $var(\ln{I}) \approx 1/(L-0.5)$.
+%In the case of one-dimensional SAR, d=1 then $|C_v|=I$ and
+%$var(\ln{I}) = \psi^1(L)=\sum^{\infty}_{i=L}1/i^2$.
+%Since $1/L < \sum^{\infty}_{i=L}1/i^2 < 1/(L-1)$, then $var(\ln{I})$ is bounded.
+%Thus an approximation is made to compute L being:
+%$L=1/var(\ln{I}) + 0.5 $ as $var(\ln{I}) \approx 1/(L-0.5)$.
+The previous section has discussed the one-dimensional case of SAR.
+The relation between ENL and the log-variance is depicted in Eqns. \ref{eqn:perf_index_analytic} and \ref{eqn:enl_analytic}.
+This relationship forms the special case of Eqn. \ref{eqn:Estimate ENL from log-variance of POLSAR homogeneous areas} above, where $d=1$.
 
 In the case of partial POLSAR, d=2, then
-\begin{equation}
-  var \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) \\
-    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 \\    
-\end{equation}
-Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
-Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
-Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$
+\begin{align*}
+&  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
+\noindent \text{Similar to the SAR case: } \\
+&  1/L + 1/(L-1) < var_2 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) & \\
+\noindent \text{Thus, approximately: } \\
+& var_2 \left[ \ln |C_v| \right] = 2/(L-1) & \\
+\noindent \text{Equivalently: } \\
+& L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
+\end{align*}
+%Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
+%Thus an approximation can be made: $var_d \left[ \ln |C_v| \right] = 2/(L-1)$.
+%Equivalently L can be estimated as:  $L = 2/var_d \left[ \ln |C_v| \right] + 1$
 
 In the case of full POLSAR, d=3, then
-\begin{equation}
-  var \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2) \\
-    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 \\    
-\end{equation}
-Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
-With $L>3$, it is trivial to prove that $3/(L-1.5)$ is also bounded by the same limits. %also is bounded by the above thresholds.
-Thus a similar approximation can be written as: $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
-or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$
+\begin{align*}
+&  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
+\noindent \text{Again: }  \\
+& 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
+\noindent \text{With } L>3 \\
+& var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
+\noindent \text{Or: }\\
+& L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
+\end{align*}
+%Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
+%With $L>3$, it is trivial to prove that $3/(L-1.5)$ is also bounded by the same limits. %also is bounded by the above thresholds.
+%Thus a similar approximation can be written as: $var_d \left[ \ln |C_v| \right] = 3/(L-1.5)$
+%or $L = 3/var_d \left[ \ln |C_v| \right] + 1.5$
 
 In short, for all cases of SAR, partial-polarimetric and full-polarimetric SAR, Eqn.
-TODO:REF relates the ENL for an homogeneous POLSAR area to the variance of the log-determinant computed from POLSAR covariance matrices.
-The validation of this Eqn. has been carried out in Section TODO:REF.
+\ref{eqn:Estimate ENL from log-variance of POLSAR homogeneous areas} relates the ENL for an homogeneous POLSAR area to the variance of the log-determinant computed from POLSAR covariance matrices.
+%The validation of this Eqn. has been carried out in Section TODO:REF.
 Since the ENL has routinely been used to evaluate (POL)SAR speckle filters, this mathematical relationship suggests that the same procedure applied in the log-transformed domain can, at the least, also be used to evaluate the performance of (POL)SAR speckle filters over homogeneous area.
@@
 
-\begin{figure}
+\begin{figure}[h!]
 	\subfloat[preserving consistency property: boxcar filter]{
@@
 However, the ratio is not considered as being natural for digital display \cite{Medeiros_2003_IJRS}.
-Our previous work in the context of SAR speckle filtering found that
+As shown earlier, %Our previous work in the context of SAR speckle filtering found that
   in log-transformed domains, this ratio is transformed into a subtractive residual that is excellent at visual evaluation.
@@
 
-The previous section has illustrated theoretically how the variance of sample log-determinant is linked to the ENL index.
-This form the basis for evaluating POLSAR speckle filters over homogeneous areas.
-The procedure is simple and is described next.
+%The previous section has illustrated theoretically how the variance of sample log-determinant is linked to the ENL index.
+%This form the basis for evaluating POLSAR speckle filters over homogeneous areas.
+%The procedure is simple and is described next.
 To evaluate a given POLSAR speckle filter over homogeneous areas,
@@
 The Equivant Number of Look (ENL) is then estimated
-  either by referencing the prepared graphs given by Eqn. TODO:REF
-  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. TODO:REF.
+  either by referencing the prepared graphs given by Eqn. \ref{eqn:var_log_det_is_homoskedastic}. %TODO:REF
+  or alternatively by setting the measured variance value into $var[\ln{|C_v|}]$ in Eqn. \ref{eqn:Estimate ENL from log-variance of POLSAR homogeneous areas}.
 The estimated ENL and equivalently the measured log-variance is finally used to evaluate the speckle suppression power of the filters.
-It is common concensus that the higher the ENL estimated,
-  which also means the lower the log-variance measured,
+It is common consensus that higher the ENL estimated,
+  which also means lower the log-variance measured,
   leads to better POLSAR speckle filters in terms of suppressing speckle noise.
@@
 
-In order for such a procedure to be generic, however,
+However, in order for such a procedure to be generic, 
   it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
-That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the dis-similarity measures presented above.
+That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the measures of distance presented above.
 %Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that:
-An experiment is carried out to show that:
-  the 3x3 POLSAR boxcar filter preserves the consistency property.
+An experiment is carried out as follows to show that
+  the 3x3 POLSAR boxcar speckle filter preserves the consistency property.
 The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
@@
 %In fact, the test procedure can be applied on any of the models presented above.  
-Apparently for log-determinant histograms,
+It is clear that for the log-determinant histograms,
   while the location of the filtered plots differs depending on the underlying signal $\Sigma_v$,
   the shape of the plots, for both pre-filtered and post-filtered data, is invariant to that underlying signal.
-Contrast, and similarly dispersion, measures of distance have its location independent of $\Sigma_v$,
-  thus the contrast plots for the filtered output should overlap each other to show consistency.
+Contrast, and similarly dispersion, measures of distance have its location independent of $\Sigma_v$.
+Thus, the contrast plots for the filtered output should overlap each other to show consistency.
 Similar procedures can also be applied using any of the models presented above.
 
-\begin{figure}
+\begin{figure}[h!]
 \centering
@@
 
-Over heterogeneous area, the consistent measures of distance may also be important tools in helping to evaluate POLSAR speckle filters.
+Over heterogeneous area, the consistent measures of distance may also be an important tools to help evaluating POLSAR speckle filters.
 For a start, since the model for log-determinant is additive and homoskedastic,
   log-determinant images is naturally more suitable for gray-level digital images.
-Especially for evaluation of statistical estimators,
+In particular for evaluation of statistical estimators,
   the estimators' error / residual plays an important role.
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \centering
@@
 In visual and qualitative evaluation, Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only the log-determinant image can offer nice visualization of the scene, 
-  the residual images also help in visualizing the distortion impact of the filter can also be made visible by the residual image.
+  the residual images also help in visualizing the distortion impact of the filter. % can also be made visible by the residual image.
 Specifically, while it is quite hard to observe the worsening blurring-effects of the 5x5 boxcar speckle filter as compared to the 3x3 filter
@@
 
-In short, while it may be hard to make such a conclusion just by looking at the filtered imagery,
+In summary, while it may be hard to make such a conclusion just by looking at the filtered imagery,
   by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer conclusive evidence.
 
-Much more detailed discussion on this topic, 
-  in the context of evaluating SAR speckle filters is given in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
-However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters.
+%Much more detailed discussion on this topic, 
+%  in the context of evaluating SAR speckle filters is given in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+%However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters.
 %This section serves more as an illustration of how the proposed theoretical model can be applied to practical scenario,

### 2013-07-24 6/conclusional_discussion.tex
updated for Ian changes

--- 2013-03-01 6/conclusional_discussion.tex
@@
-\chapter{Discussion and Conclusions} %chapter 7
+\chapter{Conclusions} %chapter 7
 \label{chap:conclusions}
@@
 
-\section{Result Evaluation and Discussion}
+%Small recap on what I have done
+%Then list out the results with
+%their implications
+%their limitation
+%Then introduce what may be done next
+%That is all, finally!
 
-In this thesis, a new model is developed for POLSAR data.
-The theory development is based in the principles of statistical mathematic and is visualized using computer simulations.
-The theory has shown its capabilities through a number of applications, though further studies should unearth even more interesting results.
-
-The main assumption used in this paper is the independent and circular complex Gaussian model for POLSAR data.
-While the model may not be perfectly matched with practical data,
-  it is apparently the most-widely accepted model.
-In the following paragraphs, the imperfect practice of over-sampling   data in SAR and POLSAR processing is discussed.
-
-The practice of over-sampling in SAR (and hence POLSAR) data processing may affects the choice of nominal ENL for showing the match between real-life data and the proposed model.
-Specifically, the over-sampling practice would normally be indicated a reduction of the ENL number.
-This is for example evidenced in our experiment for the RADARSAT2 dataset.
-The RADARSAT2 given to us is in its Single-Look format,
-  and nine-look processing is applied before the dispersion histogram in log-transformed domain is computed for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig ???
-  against the theoretical model for the nominal ENL value of 9.
-Even though the shapes of the histograms do look similar, the match however is not very good.
-A better match can be achieved by estimating the ENL from the observable variance of the log-determinant,
-  and the theoretical model for the estimated ENL indicated a much better consistency.
-This procedure can always be carried out for any given dataset,
-  since the sample variance of the log-determinant can always be measured
-  and hence the effective ENL can always be estimated using Eqn. ???.
-
-The use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the second order statsitics POLSAR matrices.
-In fact, the log-determinant can also be computed as the sum of log-eigen values.
-Specifically:
-\begin{eqnarray}
-  \ln{|M|} = \sum \ln{\lambda_M}
-\end{eqnarray}
-where $\lambda_M$ denotes all the eigen-values of M.
-Similar to other eigen-value based approach (e.g. Entropy/Anisotropy, ...),
-  the models presented here is roll-invariant.
-
-The methodology presented in this paper call for the reduction of the multi-dimensional POLSAR data into a scalar value.
-While this is probably desirable for a wide range of application where a one-dimensional number is required to represents the complex multi-dimensional data,
-  such reduction is probably not lossless.
-Thus similar to the way the Wishart Classifier is employed,
-  the use of this technique should be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g. Freeman Durden or entropy/anisotropy TODO:REF ...)
+This chapter concludes the work, summarizes main contributions and lists possible directions for future research.
 
 \section{Contributions of the Thesis}
+\label{sec:conclusion_contribution}
 
-%\subsection{POLSAR Consistent Measures of Distance}
+The research sets out to seek the solution for the dual-problem of 
+1) establishing scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data 
+and 
+2) developing novel additive and homoskedastic measures of distance for both SAR and POLSAR data, which allow the benefits of the homoskedastic statistical estimation framework to be demonstrated. 
+After different scalar statistical models, together with many different data processing techniques, is reviewed for both SAR and POLSAR data,
+  chapter \ref{chap:lit_survey} highlights the needs for scalar, representative and homoskedastic statistical models for the multi-dimensional, complex and heteroskedastic data.
 
-%\subsubsection{Conclusion}
+  Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
+In chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
+These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
+This combination give rise to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
+These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.
 
-In conclusion, several scalar and consistent measures-of-distance for multi-variate POLSAR data were proposed in this paper.
+%What are the results?
+Generally speaking, this thesis contributes solutions for the problem of how to interpret and process the multidimensional and stochastic (POL)SAR data.
+%One way of contribution is to derive new and better techniques to help alleviate the situation.
+%The most direct way of contributing to this problem is to
+%as well as derives new and
+%better techniques to process the data. %help alleviate the situation. 
+%An even better way, however, is to derive new theoretical models from which novel data processing technique can be derived.
+%In this thesis, new theoretical models are derived for the (POL)SAR data
+%  in addition to several novel (POL)SAR data processing techniques
+%  which are also proposed as beneficial applications of these models.
+Specifically, the
+                main theoretical results obtained in this thesis are novel statistical
+                models, which subsequently lead to derivation of
+                consistent and homoskedastic measures of distance, for
+                both SAR and POLSAR data.
+Compared
+                to other scalar models for POLSAR the proposed models
+                are highly representative of the multi dimensional data.
+Its
+                representative power is demonstrated as it lead to
+                consistent discrimination measures as well as it
+                generalizes the traditional representative model for SAR
+                intensity towards the multidimensional domain.
+
+%It is common-consensus that in the original multiplicative SAR domain,
+%  the intensity ratio serves as the best available discrimination measure.
+%Meanwhile, there are several proposed discrimination measures for POLSAR
+%  but there are no apparent link between the two fields.
+%This thesis shows that the logarithmic transformation not only converts multiplicative SAR into 
+The proposal of using the determinant ratio as a POLSAR discrimination measure is also a novel contribution.
+It can be considered as the extension of the SAR intensity ratio,
+  which have long been considered as the best discrimination measures for traditional SAR data \cite{Rignot_1993_TGRS_896}.
+It works consistently in the original multiplicative and heteroskedastic POLSAR domain,
+  and the logarithmic transformation converts this ratio into a consistent subtractive measures of distance in the transformed additive and homoskedastic domain.
+This
+                derived consistent measures of distance for SAR and
+                especially for POLSAR are also a novelty.
+With regards to other existing discrimination measures for SAR and POLSAR,
+                this thesis unite them, together with the new ones
+                proposed herein, all into a consistent theory.
+%More
+%                over the homoskedastic models and their derived
+%                consistent measures of distance bring about the benefits
+%                of homoskedastic statistical estimation framework.
+
+%The scalar POLSAR models are representative and lead to several consistent discrimination measures.
+%This should be beneficial to a range of problems where single scalar number is required to represent complex multi dimensional POLSAR.
+%These include. for example, target detection, surface cover classification, edge detection or POLSAR  speckle filters evaluations, etc
+
+%The scalar models for POLSAR are also shown to be the generic multi-dimensional models 
+%which also encompass the traditional one-dimensional SAR intensity models under its natural coverage.
+%Thus the additive and homoskedastic models initially developed for SAR are shown extensible to the generic multi-dimensional, multiplicative and heteroskedastic case of POLSAR.
+
+In \textbf{summary}, to address the dual-problem stated earlier, this thesis proposes several
+scalar, additive and homoskedastic models for the multi-dimensional, multiplicative
+and heteroskedastic POLSAR data. 
 The dis-similarity measures are computed for the determinant of the POLSAR covariance matrix,
@@
   is gracefully transformed into the traditional SAR intensity.
-Consequently, these measures of dis-similarity may be employed in a wide range of application
+The models are shown to be theoretically powerful.
+Not only they include the one-dimensional SAR under their natural coverage 
+they are also able to provide alternative and simpler explanations to a range of theoretical concepts. 
+Consequently, these measures of dis-similarity may be employed in a wide range of applications
   where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-Just like it is shown for the simpler case of SAR data processing\cite{Le_2010_ACRS},
-  when these distances are computed in the log-transformed domain,
-  their theoretical statistic models become additive and homoskedastic.
-The models are shown to be theoretically powerful.
-Not only they can provide alternative and sometimes simpler explainations to a range of theoretical concepts:
-  i.e. change detection test statistics or ENL estimation
-but also a number of results for one-dimensional SAR can be shown as special cases of the POLSAR models.
-They are also pratically versatile enough
-  capable of explaining the imperfect over-sampling practice evident in RADARSAT2 data.
-Finally, to extend our previous work in evaluating SAR speckle filters,
-  the applicaton of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored
-  with promising results reported.
+The proposed theoretical models are also versatile in practice
+  as they cope well with imperfect conditions evident in real-life captured data.
 
-\section{Possible Future Work and Conclusion}
+\section{Discussion of the proposed models}
 
-\subsection{Possibilities for Future Work}
+Let us consider the different theoretical properties of the proposed models.
+First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+  the models presented here are invariant to polarization basis transformations.
 
-A fair amount of work has been carried out, published in two conference papers in 2010.
-Still, as described in this report, the opportunities for further investigation are abundant.
+Second, the models are developed for the POLSAR covariance matrix.
+However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+  the model should also be applicable to the coherency matrix.
 
-In the field of single channel SAR, further exploitation from the results of log-transformation should be achievable and publishable.
-An immediate opportunity is identified as the estimation of the PDF of the underlying signal in SAR images. 
-The mathematical construction and conceptualization was presented earlier, with implementation under-way.
-In the medium term, a possible protocol for evaluation using homoskedastic mean squared error under various scenarios, made possible through simulation of different ground-truth PDFs is being conceptualized.
+It should be noted that the models are far from complete.
+% It reduces the multi-dimensional POLSAR data to a scalar value.
+%While this is probably desirable for a wide range of application,
+%  such a reduction is unlikely to be lossless.
+While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
+  such a reduction is unlikely to be lossless.  
+Thus %to better understand POLSAR data
+the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
 
-On the POLSAR front, the short term focus is to implement speckle filtering for the off-diagonal element in the target's covariance matrix.
-The mathematical conceptualization has been given earlier, with a presentation planned as a paper for IGARSS 2011.
-In a longer time frame, we are hoping to be able to apply log-transformation's homoskedastic features into POLSAR data to find a consistent measure of distance for one of the matrices representing the target's polarimetry signature.
-We are also prepared to render help toward EADS's in-house project investigating the problem of ship identification / classification, ground-truth using AIS data.
+Nevertheless the proposed models are promising.
+Even though initially developed for partial and monostatic POLSAR data,
+  it was shown to be applicable to traditional SAR data as well.
+Since the models assumptions are quite minimal, they may potentially applicable to bi-static and interferometric data, although that would require further study.
 
-\subsection{Conclusion}
+%If move to chapter 4, can add these paragraphs
+%The thesis also derives the homoskedastic models for both SAR and POLSAR heteroskedastic data.
+%Within this consistent variance models, several consistent sense of subtractive distance is proposed.
+%These can be thought of as the linear and subtractive versions of the commonly used ratio discrimination measure in the original multiplicative SAR model.
+%
+%Theses additive and homoskedastic models should be beneficial to all the steps of the computational and statistical estimation framework in particular as well as to many existing digital technologies and algorithms in general.
+%This thesis also includes several published studies which illustrate several of such benefits.
+%These include the use of the consistent variance to break the vicious circle of speckle filtering, as well as the use of MSE in evaluating (POL)SAR Statistical estimators within the additive and homoskedastic model.
+%
 
-In conclusion, recent advances in computational power have made SAR and multiple-channel SAR become the preferred choice for continuous and autonomous global-scale earth observation and monitoring.
-Some primitive systems have been implemented and become operational for such purposes, e.g. ship monitoring, which have show-cased the capability of the technology.
-Recent advances in multi-channels polarimetric SAR have captured attention, not only within the academic community, but also from industrial players.
+ \subsection{Beneficial implications of the proposed models}
 
-There are however certain issues need to be resolved to ensure the extra-information available in POLSAR data leads to better practical implementations.
-%Our pilot study have exposed the trade off between higher-resolution in partial polarimetry modes and lower-resolution in images of full polarimetry, which apparently will continue to be around for many years to come.
-%More importantly it exposed the need of a computational framework, to simulate, experiment and objectively evaluate the performance of different POLSAR processing techniques.
-Our studies have exposed the need for a computation framework, to simulate, experiment, carry out statistical analysis, modelling, validation and evaluation of various SAR and POLSAR processing techniques, most of which can be put within the framework of statistical estimations.
-Our work thus far has developed one such framework for the processing of single-channel SAR data.
-In the next phase of the project, we aim to develop a more elaborated framework for multi-channel POLSAR data processing.
+%How to exploit the advantages of these new results? What
+%                are their benefit? And
+%                to whom? OK, assuming your solution is novel and it can
+%                hold water, is it useful? How is it better than the
+%                state-of-the-art? And to whom does this matter? Why
+%                should they use your solutions instead of other?
+The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
+An example is between the fields of SAR and POLSAR, where obviously the SAR data is studied in much further details than the newly derived POLSAR data.
+%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
+By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
+Another example is between the fields of computer science and SAR-based remote sensing.
+Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
+And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
+could potentially allows this currently small portion to grow larger.
+%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.
 
-With the availability of such fundamental research, we can probably afford to follow a wider range of subsidiary research questions.
-For the traditional single channel SAR, one sub-topic is our hypothesis that it is possible to estimate the PDF of the true, underlying back-scattering coefficient, at least in the log-transformed domain.
-Should we succeed in such a task, the technique could be an invaluable contributions to the whole class of MAP speckle filters.
+%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
+%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
+The proposed homoskedastic statistical estimation framework provides a firm foundation
+to overcome the various negative impacts of heteroskedasticity on statistical estimations.
+This
+                is demonstrated in both stages of developing new
+                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
+Specifically
+                in the context of SAR speckle filters: consistent
+                variance and homoskedasticity is shown to help in
+                breaking the vicious circle of speckle filtering.
 
-Compared to single-channel SAR, the field of multi-channel POLSAR is much less mature. 
-Thus the application of our intended framework can be expected to bring even better impact publications.
-The first sub-topic that we aim for immediate experiment is the hypothesis that off-diagonal element in the polarimetric covariance matrix element can be speckle filtered through the application of standard SAR techniques on transformed polarization basis intensities.
-In the longer term, we hope to investigate the extension of our homoskedastic log-transformation techniques towards finding a consistent measure for the multi-variate and stochastic POLSAR data.
-%Should the experiments proved successful, an alternative and simpler way to statistically model off-diagonal element can be proposed.
+At
+                the same time, a consistently meaningful sense of
+                distance leading to our proposal of using the familiar
+                MSE in the homoskedastic domain to evaluate SAR speckle
+                filters.
+Intuitively,
+                this comes about as the speckle suppression power of
+                speckle filters can be evaluated via variance estimation
+                practice, while the radiometric preservation can be
+                evaluated via the normal bias evaluation.
+Combined,
+                while there are many different evaluation criteria in
+                the heteroskedastic SAR speckle filter evaluation
+                framework, the MSE is proposed as the single unified
+                evaluation criteria for SAR speckle filters.
+In
+                short, it is shown that in the homoskedastic domain, not
+                only it is possible to find the equivalent of existing
+                methods overcoming heteroskedastic drawbacks in the
+                original domain, it is also possible to suggests further
+                improvements based on existing techniques.
 
-%The previous chapter just elaborated a few of them, which showed the greatest potential and
-%One of such key issues is the filtering of speckle, especially on off-diagonal covariance matrix elements, which also available in partial polarimetric data.
+The
+                proposed models for POLSAR also bring forward an
+                important benefits.
+Since
+                the models, especially those for discrimination
+                measures, can be considered as the multidimensional
+                extension of the models for SAR, it makes many existing
+                SAR processing techniques extensible towards POLSAR
+                data.
+The POLSAR determinant ratio, for example, can be considered as
+                the extension of the ubiquitous SAR intensity ratio.
+This
+                thesis also illustrates how the MSE evaluation
+                criteria can also be extended from SAR to POLSAR.
 
-Presented here, and in the previous chapter, are just a few of a whole range of possibilities. 
-With such a diversity available, one of our priorities is to be focused to achieve tangible results.
-We merely choose to present only the sub-topics which showed the greatest potential and which we believe would provide the most impact and leverage for our future work.
-For such tasks, a snap-shot of the project status and the amount of remaining activities is planned and presented in the previous section.
-With continued assistance from EADS Innovation Works Singapore, who is a collaborator of this project and has provided us numerous valuable data and discussion, we believe that the remaining tasks are highly feasible.
-The academic contribution was discussed earlier while the endorsement of EADS speaks volumes about the practical contributions of our research.
-%We believe we have chosen a reasonable group of subsidiary research questions to focus, however we will be delighted to receive any feedback and suggestion from the readers.
+From another angle, the theoretical models for POLSAR also offer several benefits.
+The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
+can be simulated as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
 
-%This project, in fact, is part of a collaboration with EADS on the field.
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.
+
+%While some of these obstacles have been overcome by various experienced researcher in the field proposing different genuine approaches, 
+%  the additive and homoskedastic transformation approach proposed in this thesis suggests that these problems also have equivalent handling techniques which usually are more familiar.
+%Furthermore competitive and even sometimes better proposal are made making use of this familiarity.
+%For example, not only it is shown that both radiometric preservation and speckle suppression evaluation of SAR speckle filters can be carried out equivalently well under both domain, 
+%  MSE is in the additive and homoskedastic domain is shown capable of combining the two evaluations, which so far have not been figured out in the original heteroskedastic domain.
+%Elsewhere, the application of wavelet in this same transformed domain has resulted in a new class of speckle filters which performs respectably in comparison to other well established filters.
+%The familiarity of this transformed domain should also be very helpful for the new comers of the field, who is much more likely to find comfort ability in this derived domain in comparison to the original multiplicative and heteroskedastic domain.
+
+\subsection{Limitations of the proposed models}
+
+%What are their limitations? What problems this appears
+%                to solve, but actually is not?
+
+The
+                proposed scalar models for POLSAR also have limitations.
+It
+                calls for a dimensional reduction operation, which is
+                probably not lossless.
+Thus
+                while the determinant of POLSAR covariance matrix is
+                said to be "highly representative", it is definitely not
+                fully representative of the data.
+Intuitively,
+                this is similar to the use of magnitude as being
+                representative of a complex number, which also is not
+                fully representative of the two-dimensional number.
+But it is important to emphasize that,
+                just like the magnitude is invariant to the rotation of
+                the reference frame, the POLSAR determinant is also
+                invariant to polarization basis transformation.
+
+While
+                the proposed homoskedastic measures of distance have
+                their own benefits, their biggest challenge probably
+                lies in changing the hard learned lessons that
+                previous generation of researchers have experienced tackling
+                the multiplicative and heteroskedastic SAR data.
+At
+                the same time, while the logarithmic transformation has
+                the advantages of converting the multiplicative and
+                heteroskedastic model into an additive and homoscedastic
+                data, such transformation does not arrive conveniently
+                to the common additive white noise model.
+In fact, figures presented in the previous chapters show that 
+	they are not even centred around the origin. 
+This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
+	work very well in practice, as the operation is biased and statistically inconsistent.
+To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
+	is suggested \cite{Le_2011_ACRS}.
+While averaging is also the MLE operator in the SAR's original domain,
+                the MLE operation in the log-transformed domain is admittedly more complex in comparison.
+
+\section{Possible Future Work}
+\label{sec:conclusion_future_work}
+
+%What is still lacking to solve these problems? What is
+%                the future work to extend this theory? What can be done
+%                next?
+
+While
+                the proposed models may have certain limitations, its
+                potentials still mostly stays undiscovered.
+Since
+                the assumptions of partial and full monostatic POLSAR
+                models are quite minimal, they are probably also
+                applicable to other types of SAR-based data such as: Interferrometric SAR (InSAR), Polarimetric Interferrometric SAR (POLINSAR) 
+                or bistatic POLSAR data.
+In addition, further experiments can be done to determine whether some existing SAR data processing techniques for SAR can be equally applicable to POLSAR data.
+%                Also,
+%                it may be interesting time to choose some existing data
+%                processing techniques for SAR and showing them
+%                applicable to POLSAR data.
+
+In
+                the same vein, it is probably even more significant to
+                investigate the applicability of some certain existing
+                additive and homoskedastic based computational data
+                processing techniques towards the multiplicative and
+                heteroskedastic (POL)SAR data.
+As the additive noise PDF in log-domain has been worked out, we hypothesize that the true back-scattering coefficient PDF, also in log-domain, can be estimated through regularized deconvolution algorithms.
+If an algorithm could be designed to estimate such PDF, we believe this would present an improvement for a whole class of speckle filters, namely the Maximum-A-Priori (MAP) class, which up to now, still assumes the true PDF will follow certain known fixed distributions.
+
+Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able.
+In Fig. 
+	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
+the underlying single channel grey image histogram is presented along with the noise PDF, in the log-transformed domain. 
+As the noise is additive, it is expected that the noise PDF will act as a point spread function.
+This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
+This characteristic is reflected clearly in Fig. 
+	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
+where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
+We hence hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods,
+  such as using the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical}.
+%We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.
+
+\begin{figure}[h!]
+\centering
+	\subfloat[Original image's histogram and PSF]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
+ 		 \epsffile{images/log_PSF_NTU_gray_histogram.eps}
+		 \label{fig:noise_pdf_as_psf:conv_inputs}
+	} 
+	\hfill
+	\subfloat[Convoluted and speckled image histogram]{
+		 \epsfxsize=2.5in
+		 \epsfysize=2.5in
+		 \epsffile{images/log_convoluted_NTU_speckled_histogram.eps} 	
+		 \label{fig:noise_pdf_as_psf:conv_output_observable}
+	}
+\caption{Observable convolution of PSF}
+\label{fig:noise_pdf_as_psf}
+\end{figure}
+
+For multi-channel SAR data, the short-term focus is to extend the existing statistical estimation framework for SAR towards POLSAR.
+Specifically, the F-MLE speckle filter for SAR should be extensible towards POLSAR,
+Similarly, the study to simulate POLSAR data as well as to use MSE to evaluate POLSAR speckle filters is also highly achievable.
+Lastly, the representative models for POLSAR may also be further explored, such as to explain if the additional channels provided in POLSAR do indeed lead to improved information being captured.  
+%Another way of extension is to investigate other types of multi-channel SAR like bi-static POLSAR or InSAR.
+
+%\section{Conclusion}
+%\label{sec:conclusion_final}
+%
+%The thesis sets out to provide the solution for the dual-problem of
+%1) establishing scalar and representative statistical models for the multi-dimensional and inter-correlated POLSAR data
+%and 2) developing novel additive and homoskedastic measures of distance for both SAR and POLSAR data which allow the benefits of the homoskedastic statistical estimation framework to be demonstrated.
+%In chapter \ref{chap:sar}, this thesis presents homoskedastic models are derived for heteroskedastic SAR data.
+%Subsequently in chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated for POLSAR data.
+%These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
+%These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.
+%

### 2013-07-24 9_backmatter/appendix.tex
updated for Ian changes

@@
   \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-  \Gamma(L-it) \Gamm(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
+  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
    CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
@@
 In this appendix, the following results for SAR intensity $I$ is shown to be special cases of the results given in this paper for the determinant of POLSAR's covariance matrix $det|C_v|$.
-Specifically, not only the following results from the our previous works on single-look SAR (TODO:CITE), i.e. $d=L=1$, is reviewed:
+Specifically, not only the following results from chapter \ref{chap:sar}, i.e. $d=L=1$, is reviewed:
 \begin{eqnarray}
@@
 The output of the first phase, in the general case is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplify the multi-look results into single-look results, presented in our previous work (TODO:CITE).
+The second phase simplify the multi-look results into single-look results.
 Mathematically, that means setting $L=1$ in the multi-look result
-  and converting from natural logarithmic domain used in this paper to the base-2 logarithm used in (TODO:CITE).
+  and converting from natural logarithmic domain to the base-2 logarithm used in \ref{chap:sar}.
 
@@
 \end{eqnarray}
-which is the same as in (TODO:CITE).
+which is the same as in chapter \ref{chap:sar}.
 
@@
 \end{equation}
-which is consistent to the result in our previous work (TODO:CITE).
+which is consistent to the result in chapter \ref{chap:sar}.
 
@@
 \end{eqnarray*}
-which is also consistent to the result in our previous work (TODO:CITE).
+which is also consistent to the result in chapter \ref{chap:sar}.
+
+\chapter{Published and Under-Review Articles}

### 2013-07-24 paper_dev/article.tex
updated for Ian changes

@@
 
-\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2013}%
 { Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
@@
   and enable useful discrimination measures to be easily determined. %consequently they lead to useful discrimination measures.
-When the multi-dimensional models are collapsed to a single dimension,
-  they are shown to exactly match the traditional statistical models for SAR intensity.
-The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
+The representative power of these models is explained  
+when these multi-dimensional models are collapsed to single dimensional versions,
+  they are shown to exactly match the traditional statistical models for the representative observable of SAR intensity.
+The paper also validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
 %IVMThe proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
-The intention is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
-To illstrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+One major benefit of this paper is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
+To illustrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
 \end{abstract}
@@
 While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
-Namely that there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
+That is there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
 The research community has responded largely by developing different statistical models for various POLSAR observables.
@@
 
-This paper presents novel statistical models for multi-dimensional POLSAR data as generalisations of the commonly used one-dimensional SAR statistical model.
-This approach makes feasible the adaptation of many existing SAR processing techniques, to be applied to POLSAR data.
-Specifically, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
+This paper presents novel statistical models for multi-channel POLSAR data as generalisations of the commonly used and representative statistical models for the one-channel SAR data.
+This approach makes feasible the adaptation of many existing SAR processing techniques to be applied to POLSAR data.
+After section \ref{sec:lit_review} reviews related work in published literature, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
 The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
@@
 With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
-  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
+%  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
+  and allow many conventional SAR statistical models to stay under the umbrella of these generic POLAR models.
 The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
@@
 However, while an exact statistical distribution is needed for the test,
-  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
-
-\subsection{Investigated Scalar Observables for POLSAR Data and their Statistical Models}
+  only asymptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
+
+\subsection{Scalar Observables for POLSAR Data and their Statistical Models}
 \label{sec:lit_models}
@@
   each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been studied.
+  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been proposed.
 While these models undoubtedly help in understanding POLSAR data,
@@
 \end{align}
-where $C_{i,j}$ denotes the (i,j) elements of the matrix C,
+where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
  $||$ denotes absolute values
@@
 , these dis-similarity measures are not widely used 
-  probably because of the multiplicative nature of the noisy data.
+  mainly due to the multiplicative nature of the noisy data.
 
@@
   d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation}
+\end{equation},
+where $tr(C)$ denotes the trace of the matrix C. 
 As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
 
-Recent works have suggested alternative dissimilarity measures including the asymmetric and symmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
 \begin{align}
@@
 
-Closer investigation of these dis-similarity measures reveals that most are related in some way. %to each other.
+Closer investigation of these dis-similarity measures reveals that most are related in some ways. %to each other.
 The Bhattacharyya distance is easily shown to be related to the Barlett distance.
@@
 The close relation among the measures is further supported by the fact that
-  all of their proposing papers referenced the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
+  all of their proposing papers refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
 In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
@@
 
-Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
+Taking the log-transformation of the above equation, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
 \begin{eqnarray}
@@
 In this section, several scalar statistical models for POLSAR are presented.
-After section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
-  section \ref{sec:polsar_heterosked_model_and_log_transform}
+Section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation used in this paper, %reviews related work in published literature,
+  while section \ref{sec:polsar_heterosked_model_and_log_transform}
   presents the theoretical models together with mathematical evidence for two related points.
@@
 In this section the multiplicative nature of POLSAR data is first illustrated.
- Log-transformation is used to convert  the data into a more familiar additive model.
+ Log-transformation is then applied to convert  the data into a more familiar additive model.
 Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
@@
 In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered constant.
-Thus Eqn. \ref{eqn:determinant_distribution} indicates that: 
+Thus Eqn. \ref{eqn:determinant_distribution} indicates that 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
@@
 Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-random variables,
-  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
+then the random variables,
+  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$)
   are observable according to the following definitions:
@@
 
-The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
-This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
+The previous section  introduced  theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
+This section will show that the model is equally  applicable to the 1-dimensional ($d=1$) case,
   which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
@@
     either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results:
+    or as simpler case of the POLSAR results:
   \begin{align*}
@@
 This section aims to verify the theoretical models against practical data.
-Since we have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+Since it is shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
   which have been validated extensively, only a simple validation is presented for this case.
@@
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
+\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
+It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
 \label{fig:verify_multi_look_SAR_dispersion_contrast_models}
@@
 For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
-Both the the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
+Both the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
 These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
@@
 in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
-However, practical conditions may not always satisfy these prerequisites, thus we find a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions.
+However, practical conditions may not always satisfy these prerequisites,
+  a common and observable gap is noticed between the conditions found in practical real-life data and the theoretical assumptions.
 
@@
   where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
+In a given POLSAR dataset, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
   it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
@@
 
-We will instead propose an alternative approach making use of variance statistics in the homoskedastic log-domain.
+This paper instead proposes an alternative approach that makes use of variance statistics in the homoskedastic log-domain.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
 \end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
+\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
 \label{fig:handling_airsar_oversampling_practice_full_pol}
@@
 
-Let us begin by noting a few theoretical properties of the proposed statistical model.
+Let us begin by noting a few theoretical properties of the proposed statistical models.
 First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
@@
 
-Second, the model is developed for the POLSAR covariance matrix.
+Second, the models are developed for the POLSAR covariance matrix.
 However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
@@
 
-The model is far from complete.
- It reduces the multi-dimensional POLSAR data to a scalar value.
-While this is probably desirable for a wide range of application,
+It should be noted that the models are far from complete.
+% It reduces the multi-dimensional POLSAR data to a scalar value.
+%While this is probably desirable for a wide range of application,
+%  such a reduction is unlikely to be lossless.
+While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
   such a reduction is unlikely to be lossless.  
 Thus %to better understand POLSAR data
-the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
-the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar).
-
-However the proposed model is promising.
+the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+
+Nevertheless the proposed models are promising.
 Even though initially developed for partial and monostatic POLSAR data,
   it was shown to be applicable to traditional SAR data as well.
-Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
-
-The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+Since the models assumptions are quite minimal, they may potentially applicable to bi-static and interferometric data, although that would require further study.
+
+Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude as being representative of a complex number
+(in a sense this is also why intensity is widely considered representative of the SAR data complex).
+Similar to the determinant, the magnitude observable is also scalar and is not lossless.
+To fully represent the complex number, another observable is needed besides the magnitude.
+The magnitude however is much more widely used, as it can be shown that its is invariant to a change in the reference frame.
+Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+Thus while it is not fully representative of the POLSAR data, it can be said to be highly representative of it.
+The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
+This is also similar to the standard use of the magnitude when two or more complex numbers are to be compared. %, most of the times the magnitude is to be used.
+
+This leads to the application of the models in deriving discrimination measures.
+Besides the above properties, the theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
 In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
@@
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+These applications however are not included in this paper, but rather left as a suggestion for future investigations.
+There are a few reasons for this decision.
+The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
+  the first being a faster ENL evaluation for POLSAR data and
+  the second being the visual evaluation of POLSAR speckle filters.
+The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
+Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
+It does not, technically speaking, focuses on proposing new discrimination measures.
 %***IVM remove this single sentence, it detracts from the argument...
@@
 
+The advantages of this proposal are thus to be compared against other published models for POLSAR.
+Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
+While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
+This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
+Instead a straightforward binary evaluation would be sufficient.
+In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
+This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
+This is proven in section \ref{sec:sar_special_case_of_polsar}.
+No other existing models for POLSAR is known to have this property.
+
+Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
+This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
+There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
+  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
+%to comprehensively support the argument. 
+%To support these arguments, extensive literature surveys has been carried out for both published scalar models as well as for discrimination measures for POLSAR.
+Thus given such extensive reviews the above claims are water-tight.
+
+There may have many beneficials implications for this proposal.
+One of the main benefits is believed to be that:
+  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+This is illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+%Here a major benefit is illustrated in showing that 
 In evaluating SAR speckle filters, the intensity ratio is widely used.
@@
 
-To briefly evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
-  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
   and the two POLSAR speckle filters are then applied to the patch.
@@
 
-Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
-Evidently these techniques can also be adapted for POLSAR.
-Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
-
-Hai version: (Ian have not seen this yet) There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
+%Evidently these techniques can also be adapted for POLSAR.
+%Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
+
+%Hai version: (Ian have not seen this yet)
+There are many similar SAR data processing technique that may be adaptable to POLSAR.
 Examples in the same topic of evaluating speckle filters include
@@
 
-In fact, at the time of this writing, the field of SAR is much more developed than the field of POLSAR.
-The two fields however are quite separated,
-  as many techniques applicable to SAR are not directly applicable to POLSAR.
-This work may build the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques on POLSAR data.
-Here a specific example is shown
-  where, similar to the way ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+Currently while the field of SAR is much more developed than the field of POLSAR,
+  the two fields however are quite separated.
+Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+Under this context, the current proposal provide the bridge between these two separated fields,
+  inviting potential extension of various SAR processing techniques to POLSAR data.
+%Here a specific example is shown
+For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
   the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-In general, we believe there are many more unexplored possibilities for such applications
-  which is only limited by our imagination.
+We believe there are many more unexplored possibilities for such applications.
+%  which is only limited by our imagination.
 
@@
 A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
-  resulting in several consistent discrimination measures for POLSAR applications.
-The theoretical models are shown to be powerful in that
+  resulting in several consistent discrimination measures useful POLSAR applications.
+The theoretical models are shown to be comprehensive in that
   not only can they provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
   but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
-They are also practically useful since they lead to several consistent discrimination measures.
+The models are also practically useful since they provide several consistent discrimination measures.
 Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
@@
 In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
-Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
+Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2010_ACRS}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
 \begin{eqnarray}
@@
 The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2010_ACRS}.
 Mathematically, it means setting $L=1$ in the multi-look result
-  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2013_TGRS_SAR_MSE} (base-2 was chosen in the previous paper to simplify the computation).
+  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2010_ACRS} (base-2 was chosen in the previous paper to simplify the computation).
 
@@
 \end{eqnarray}
-which is the same as stated in \cite{Le_2013_TGRS_SAR_MSE}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
+which is the same as stated in \cite{Le_2010_ACRS}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
 
@@
 \end{equation}
-which is consistent with the results found in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+which is consistent with the results found in our previous work \cite{Le_2010_ACRS}.
 
@@
 \end{eqnarray*}
-which is also consistent to the results shown in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+which is also consistent to the results shown in our previous work \cite{Le_2010_ACRS}.
 

### 2013-07-24 paper_dev/article_pp.tex
updated for Ian changes

@@
 \title{
-  Scalar and Representative Models for Polarimetric SAR Data
+  Scalar and Representative Observables for Polarimetric SAR Data
 }
@@
 
-\markboth{Transactions on Geoscience \& Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2013}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables for Polarimetric SAR Data}
 

### 2013-07-24 paper_dev/letter_to_reviewers.tex
updated for Ian changes

@@
 \usepackage{hyperref}
-\signature{The Authors}
+\signature{Professor Ian McLoughlin, USTC}
 \address{}
@@
 
-\begin{letter}{The Reviewers,\\IEEE Transaction on Geoscience and Remote Sensing}
+\begin{letter}{The Reviewers,\\IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing (JSTAR)}
 \opening{Dear Reviewers,}
@@
 
-We appreciate your time and effort in reviewing our work.
-This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus provides a bridge between the two fields inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
-We hope that, like us when we were faced with its results,
-  you will find satisfaction as well as excitement after reading through this paper.
-We appreciate your feedback in whatever way it may be in making this manuscript to become a better publication.
-To facilitate your review, we enclose here a short synopsis of the paper.
+%We appreciate your time and effort in reviewing our work.
+This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for one-dimensional SAR data.
+The importance is that this provides a bridge between the two fields: inviting the adaptation of existing SAR data processing techniques for use with POLSAR data.
+We believe that this will serve as a useful and necessary addition to the research literature in this area.
+%We hope that, like us when we were faced with its results,
+%  you will find satisfaction as well as excitement after reading through this paper.
+%We appreciate your feedback in whatever way it may be in making this manuscript to become a better publication.
+To facilitate your review, a brief synopsis of the paper follows.
 
-We are aware that the paper is a bit too long.
-Specifically, the mathematical derivations in the Appendices is presented in great details.
-While this is supposed to expedite your review,
-  it probably should be shortened in publication.
-We would appreciate it if you can help us by pointing out which portion of this paper may be considered redundant by the TGRS readers.
+We acknowledge that the appendices are rather long (around 12 pages) due to extensive mathematical derivations.
+While we believe that this is necessary to expedite the review, perhaps the appendices could be provided online when the final version is published.
 
-Once again, we thank you for your reviewing time and effort.
+Thank you in advance for your reviewing time and effort -- we look forward to any suggestions for improvement.
 
@@
 The extension from SAR to POLSAR brings about an issue that needs to be addressed:
-  there exists not one, like the intensity in SAR, but many scalar observable quantities in POLSAR. 
-While different statistical models have been developed for different POLSAR observables, 
-  for a model to be useful, discrimination measures need to be derived.
-Many POLSAR data processing techniques requires a scalar, representative observable and statistical model.
+  there exists not one (like the intensity in SAR) but many scalar observable quantities in POLSAR. 
+Different statistical models have been developed for different POLSAR observables, 
+ but for a model to be useful, discrimination measures need to be derived.
+Many existing data processing techniques requires a scalar, representative observable and statistical model.
 
@@
 
-In this paper, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed.
+In this paper, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and explored.
 These models are shown to be both representative and subsequently lead to statistically consistent discrimination measures.
@@
 
-There are a few published scalar statistical models for POLSAR, but none of them fit the dual criteria of being representative and at the same time lead to scalar discrimination measures.
-There are also a few POLSAR discrimination measures, but all of them are based on the likelihood test statistics, which so far have only shown to be based on asymptotic distribution.
+There are a few published scalar statistical models for POLSAR (which we cite and explore), but none fit the dual criteria of being representative and at the same time serve as scalar discrimination measures.
+There are also a few POLSAR discrimination measures, but all are based on the likelihood test statistics, which so far have only shown to be based on asymptotic distribution.
 
-\textbf{Advantages of the newly proposed model}
+\textbf{Advantages of the newly proposed model:}
 
@@
 Compared to other discrimination measure proposals, this paper suggests an exact distribution, as opposed to asymptotic distributions, for the POLSAR likelihood statistical test.
-As a by-product of this exact modeling, simpler discrimination measures, i.e. determinant-ratio and contrast, are proposed for the common case of Lx=Ly.
+As a by-product of this exact modelling, simpler discrimination measures, i.e. determinant-ratio and contrast, are proposed for the common case of Lx=Ly.
 
-\textbf{High-level Summary of this work}
+\textbf{High-level Summary of this work:}
 
-This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data and thus provides a bridge between the two fields inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
+This paper presents novel statistical models for the multi-dimensional POLSAR data which generalize the commonly used statistical model for the one-dimensional SAR data, providing a bridge between the two fields.
+In consequence, inviting the adaptation of several existing SAR data processing techniques for use with POLSAR data.
 

### 2013-07-24 clean.sh

@@ -4,3 +4,6 @@ rm thesis.*
 mv b.thesis.tex thesis.tex
 mv b.thesis.bib thesis.bib
 
+rm chap*.pdf
+rm chap*.txt
+

### 2013-07-24 1_introduction/introduction_ivm.tex
updated for Ian to change

--- 2013-07-24 1_introduction/introduction.tex
@@
 %What is the situation, the background context of your research? the BIG problem!
-Synthetic Aperture Radar is a technology with many advantages.
-%Compared to optical remote sensors, which are passive, active SAR sensors provide weather independent and night-inclusive operational capabilities.
-Compared to optical remote sensors - which are passive, SAR uses active sensors to provide weather independent and night-inclusive operational capabilities. 
-Compared to other radar based active sensors,
+Synthetic Aperture Radar is a technology with many advantages. Compared to optical
+remote sensors, which are passive, active SAR sensors provide weather independent and
+night-inclusive operational capabilities. Compared to other radar based active sensors,
 for example Real Aperture Radar (RAR), SAR provides state-of-the-art resolution
 and coverage.
-In the past decades, the exponential growth in computational power has made the once overly excessive computationally demanding SAR technology to become a feasible and preferred earth observation solution \cite{Cumming_2005_Artech}.
-Thus SAR has now become the preferred choice for continuous and autonomous large-scale
+In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology to become a feasible and preferred earth observation solution \citep{Cumming_2005_Artech}.
+Thus SAR has become the preferred choice for continuous and autonomous large-scale
 remote surveillance solutions.
@@
 
-\section{Research Motivation}
-
-%Given the BIG problem, Why it is important to solve this problem?
-The
-                big picture, as introduced above, is that POLSAR data is multi­dimensional,
-                stochastic, multiplicative and heteroskedastic.
-%Under
-%                this context, the motivation is to gain a better
-%                understanding of the data,
-%which
-%                hopefully will lead to better information that can be
-%                extracted from these data.
 Under this condition, it is very important to understand the statistical models for SAR
@@
 techniques, for example speckle filtering, target detection, image segmentation, and
-other clustering, classification techniques.
-In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
-which comprises statistical modeling and validation, estimator design and development
+other clustering, classification techniques. In fact, due to the random nature of speckle,
+all of these techniques have been put into the context of statistical estimation theory,
+which comprises statistical modelling and validation, estimator design and development
 as well as evaluation of different estimators’ accuracy. And central to this statistical
@@
 POLSAR data processing requires the measure to be scalar, consistent and preferably
-homoskedastic. On the other hand, the observable quantity being modeled needs to
+homoskedastic. On the other hand, the observable quantity being modelled needs to
 be naturally representative of the high dimensional POLSAR data.
 
-%Solving these dual-problem is both important and interesting.
-%The statistical models are undoubtedly important in understanding the stochastic nature of the data. 
-%At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
-In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
+Furthermore, since POLSAR can be considered as the multi-dimensional extension of
+traditional SAR, a common problem exists for both SAR and POLSAR data. That
+is: the sense of subtractive distance is seriously flawed in the original multiplicative
+and heteroskedastic domain of both types of data. 
+In contrast, the digital technologies which range from image processing and display to artificial intelligence and machine learning algorithms used to process (POL)SAR data, are linear
+and additive in nature. 
+This linear and additive nature is manifested, for example, in a
+large number of algorithms in the field of computational intelligence which make use of
+MSE as an objective function, as well as the extensive use of variance and
+contrast in digital image processing. %***IVM Hai I removed "universal". Do you mean "common" or "ubiquitous"?
+%***IVM Hai, I don't think this next sentence adds anything
+%This is important for the foreseeable future as the enormous size of these data sets will ensure the important roles of digital and computational algorithms in (POL)SAR data processing.
+
+\section{Research Motivation}
+
+%Given the BIG problem, Why it is important to solve this problem?
+The
+                big picture, as introduced above, is that POLSAR data is multi­dimensional,
+                stochastic, multiplicative and heteroskedastic.
+Under
+                this context, the motivation is to gain a better
+                understanding of the data,
+which
+                hopefully will lead to better information that can be
+                extracted from these data.
+
+Specifically, 
+  this thesis focuses on providing a solution for the
+                dual-problem of: 1) figuring out scalar and
+                representative statistical models for the
+                multi-dimensional and inter-correlated POLSAR data and
+                2) arriving at consistent measures of distance for both
+                SAR and POLSAR data which allow the benefits of the
+                homoskedastic statistical estimation framework to be
+                demonstrated.
+
+Solving these dual-problem is both important and interesting.
+The statistical models are undoubtedly important in understand the stochastic nature of the data. 
+At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction / statistical estimation techniques.
+Traditionally, most of these data processing techniques are designed for additive and homoskedastic data.
 In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
-This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data.
-% dear Ian I changed this back
-%of the Additive White Gaussian Noise (AWGN) model in natural processes.
-%of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive.
+This is due to a number of reasons, for example the prevalence of the normal distribution which results from the central limit theorem, or the prevalence of the additive noise model which probably arises due to the linear and additive nature of digital data.%****IVM I'm not sure about this - you seem to assume (in this sentence) that digital data is linear and additive.
 However this is definitely not true - your POLSAR data is digital and yet is not additive.
@@
 %OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
-It should be noted that even for the case of SAR data which is digital and not additive,
-  the above statement is still true as SAR actually has two components, real and imaginary part,
-  and all of them follows the standard Additive White Gaussian Noise model.
 
@@
 This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility.
-An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
+An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, are also applied on multiplicative and heteroskedastic distribution, for example the gamma distribution.
 Such use, however, is known to be not very robust for these so-called heavy tailed distributions.
@@
 However for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
-Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
-For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.
+%****IVM, Hai I think you haven't introduced the abbreviation OLS.
+For another example in the normal performance evaluation stage of statistical estimators, OLS is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
+for SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.
 
-Furthermore, since POLSAR can be considered as the multi-dimensional extension of
-traditional SAR, a common problem exists for both SAR and POLSAR data. That
-is: the sense of subtractive distance is seriously flawed in the original multiplicative
-and heteroskedastic domain of both types of data. 
-In contrast, the digital technologies which range from image processing and display to artificial intelligence and machine learning algorithms used to process (POL)SAR data are linear
-and additive in nature. 
-This linear and additive nature is manifested, for example, in a
-large number of algorithms in the field of computational intelligence which make use of
-MSE as an objective function, as well as the extensive use of variance and
-contrast in digital image processing. 
-Thus it is very exciting to derive homoskedastic models for this heteroskedastic data
-  so that the benefits of an additive and homoskedastic statistical estimation framework can be explored.
-
-%Specifically, 
-%  this thesis focuses on providing a solution for the
-%                dual-problem of: 1) developing scalar and
-%                representative statistical models for the
-%                multi-dimensional and inter-correlated POLSAR data and
-%                2) establishing at consistent measures of distance for both
-%                SAR and POLSAR data which allow the benefits of the
-%                homoskedastic statistical estimation framework to be
-%                demonstrated.
-
-\section{Research Objective}
+\section{Objectives, Methodology and Contributions}
 
@@
 Some of the problems described above have been studied using different approaches in the literature.
-However, the set of problems has not been presented in a systematic manner nor with a strong underlying foundational theory.
+However, the set of problems has not been presented in a systematic manner, with a strong underlying foundational theory.
 In
-                this thesis, the statistical model for the determinant
+                this thesis, the statistical model for a the determinant
                 of the POLSAR covariance matrix is proposed and
@@
  Another
-                novelty of the contributions in this thesis comes from the systematic
+                novelty of this thesis comes from the systematic
                 treatment towards the problem of statistical estimation
@@
                 for SAR data have been proposed over the years, they have often been
-                handled in a piecemeal manner.
+                handled in a piece by piece manner.
 Here,
@@
 it
-                also allows thorough and unique discussion, for example on
+                also allows deep and unique discussion, for example on
                 evaluating different evaluation criteria for statistical
@@
 %precise problem statement
-With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
-That is
+With this approach, it is important to establish here again the focused problem statement of this thesis.
+Thus
                 this thesis focuses on providing a solution for the
-                dual-problem of: 1) establishing scalar and
+                dual-problem of: 1) figuring out scalar and
                 representative statistical models for the
                 multi-dimensional and inter-correlated POLSAR data and
-                2) providing consistent measures of distance for both
+                2) arriving at consistent measures of distance for both
                 SAR and POLSAR data which allow the benefits of the
@@
 
-\section{Research Methodology}
+\subsection{Research Objectives}
+% How do you know if the problem is solved?   State your research objectives
+Interestingly, the stated dual problems are found to have a single solution.
+They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data which is shown to be multidimensional, inter-correlated and heteroskedastic
+
+Specifically, the following sub-objectives are to be achieved
+\begin{enumerate}
+\item                 To derive scalar and representative statistical models
+                for the multi-dimensional and inter-correlated POLSAR
+                data. Specifically:
+                \begin{enumerate}
+                \item \label{itm:polsar_model} To derive a scalar statistical model for the
+                POLSAR observable, being the determinant of the
+                covariance matrix.
+                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
+                the observable being modelled 
+                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
+                that when the multi-channel POLSAR data is collapsed
+                into the traditional one-channel SAR data, this
+                determinant is transformed into the representative SAR
+                intensity.
+                \item \label{itm:polsar_validation} To validate the model against practical real-life
+                captured POLSAR data.
+                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
+                processing technique is extensible towards POLSAR data
+                \end{enumerate}
+\item                To derive homoskedastic statistical models for the
+                heteroskedastic (POL)SAR data.  Specifically:
+                \begin{enumerate}
+                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
+                the original domain and logarithmic transformation
+                can convert this into a homoskedastic model.
+                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
+                the multi dimensional POLSAR as well as for the one
+                dimensional SAR data.
+                \item \label{itm:sar_validation} To validate these statistical models against both
+                practical SAR and POLSAR data
+                \item To illustrate the beneficial applications of these
+                statistical models. Specifically:
+                \begin{enumerate}
+                \item \label{itm:filter_vicious_circle} To show how the consistent sense of variance
+                helps break the vicious cycle in the problem of SAR
+                speckle filtering: a new statistical test for
+                homogeneity and a new speckle filter is derived.
+                \item \label{itm:log_mse} To show how the consistent sense of subtractive
+                distance helps in the problem of evaluating (POL)SAR
+                speckle filters: the log-MSE is proposed to combine the
+                evaluation of radiometric preservation and speckle
+                suppression power.
+                \end{enumerate}
+                \end{enumerate}
+\end{enumerate}
+
+In summary, the first main objective is to derive a scalar and representative statistical model for POLSAR data.
+The theoretical foundation is the commonly agreed Circular Complex Normal distributions proposed by Goodman. %***IVM you need a reference here!!
+Theory development is based on applying the statistical variable change theorem on the proposed scalar observable.
+The theoretical model is validated by matching the functional PDF or the simulated histogram with real-life captured data.
+
+The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
+This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
+Here, log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
+  but it also results in a homoskedastic statistical model.
+From this consistent sense of variance, the second steps illustrate the consistent sense of contrast and distance.
+After these models are validated against practical data, their beneficial applications are further explored.
+
+To combine these two seemingly disconnected threads of research, the above results for SAR are extended to POLSAR,
+  since it is shown that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.%***IVM I changed "version" to "superset" in the sentence above.
+Please check if you are comfortable with that change, and if not, change it back!
+Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.
+
+\subsection{Research Methodology}
+%How do you evaluate your solution? 
+The
+                achievement of the above objectives not only provides
+                novel solutions to the stated problem, it also
+                illustrates the advantages and beneficial implications
+                of the proposed theory.
+Compared
+                to existing published techniques, the advantage of the
+                proposed theory is qualitative, which does not require
+                direct quantitative comparisons.
+Instead
+                a straightforward yes or no answer would be sufficient.
+%***IVM maybe this is better: "a straightforward binary evaluation would be sufficient."
+For
+                the POLSAR scalar model, its advantages are that not
+                only does it lead to consistent discrimination measures, it
+                also generalizes the traditional model for one
+                dimensional SAR intensity.
+For
+                the homoskedastic models, their advantage is that they
+                enable an additive and homoskedastic statistical
+                framework, which is not only capable of overcome various
+                negative impacts of heteroskedasticity, but also results
+                in a single better evaluation criteria that can combine
+                and represent many different existing performance
+                criteria.
+
 %To achieve the stated objectives, what is your plan of attack? Describe How your actions are to be conducted? How your argument is developed?                
@@
 This
-                is achieved as the theoretical models for
+                open loop is closed when the theoretical models for
                 POLSAR are shown to be the multi dimensional extensions of
@@
                 development of these models are based on
-                rigorous statistical mathematics transformations. % and theory. 
+                rigorous statistical mathematics and theory. 
 The
-                assumptions used are minimal and widely
+                assumptions used are also minimal and widely
                 acknowledged for this type of data.
-Then, the variable change theorem is applied to derive the statistical model for these transformed observables. %log-transformed SAR data.
 The
@@
 And
-                the imperfect conditions found in practice (in
-                comparison to the theoretical assumption) are also
-                investigated, and the models are shown to be robust, capable of
-                handling these imperfections.
+                even the imperfect conditions found in practice (in
+                comparison to the theoretical assumption) are
+                investigated, and the robust models are shown capable of
+                handling the imperfections by a simple twist.
 The
@@
 
-%The theoretical statistical models are derived from the commonly used statistical models for SAR and POLSAR.
-%Then, as mentioned above, the variable change theorem is applied to derive the statistical model for log-transformed SAR data.
-%A similar methodology is then followed for the multi-dimensional POLSAR data.
-%The POLSAR theoretical foundation used is the Complex Wishart distribution applicable on the covariance matrix.
-%In this thesis, the statistical model for the determinant of this covariance matrix,
-%  is derived from this foundation.
-%The variable change theorem is again applied to derive the discrimination measures from these derived basic models.
-
-As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering has been put into the framework of statistical estimation.
-For such application, the research methodology is based extensively on the statistical estimation framework. 
-The framework consists of three stages:
-
-%***IVM Hai, I changed your list type to make it look better
-\begin{description}
-\item{Stage 1:} data statistical analysis. 
-We propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
-The statistical models built after such a transformation are validated against real-life data.
-\item{Stage 2:} predictor and estimator development.
-Various statistics-based computational intelligence and/or signal processing methods are to be applied. 
-\item{Stage 3:} results analysis and performance evaluation.
-Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
-\end{description}
-
-\subsection{Statistical Estimation Framework for (POL)SAR data}
-
-Even though the research topic seems to spread across different sub-fields, the common framework that binds them all together is the application and development of statistical estimators.
+Even though the research topic seems to spread across different sub-fields, the common over-arching objective that binds them all together is the application and development of statistical estimators.
 For speckle filtering, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
@@
 
-\subsection{Data Collection}
+The theoretical statistical models are derived from the commonly used statistical models for SAR and POLSAR.
+Then, as mentioned above, the variable change theorem is applied to derive the statistical model for log-transformed SAR data.
+A similar methodology is then followed for the multi-dimensional POLSAR data.
+The POLSAR theoretical foundation used is the Complex Wishart distribution applicable on the covariance matrix.
+In this thesis, the statistical model for the determinant of this covariance matrix,
+  is derived from this foundation.
+The variable change theorem is again applied to derive the discrimination measures from these derived basic models.
 
-This work has made extensive use of simulated data, which have a number of advantages listed below:
+As the speckle phenomena is stochastic in nature, speckle filtering has been put into the framework of statistical estimation.
+This project's research methodology will be based extensively on a statistical estimation framework. 
+The framework consists of three stages:
+
+%***IVM Hai, I changed your list type to make it look better
+\begin{description}
+\item{Stage 1:} data statistical analysis. 
+We propose a preferred data transformation and decomposition that may allow applications of existing computer science techniques. 
+The statistical models built after such a transformation are validated against real-life data.
+\item{Stage 2:} predictor and estimator development.
+Various statistics-based computational intelligence and/or signal processing methods are to be applied. 
+\item{Stage 3:} results analysis and performance evaluation.
+Experiment results are evaluated both qualitatively on real images and quantitatively through simulated data. 
+\end{description}
+
+\subsubsection{Data Collection}
+
+This thesis has made extensive use of simulated data. 
+There appears to have a number of advantages in using simulated experiments:
 \begin{enumerate}
@@
 \end{tabular}
+
+\label{tbl:collected_data}
 \caption{Collected imagery data}
-\label{tbl:collected_data}
 \end{table}
 
-\subsection{Result Interpretation and Evaluation}
+\subsubsection{Result Interpretation and Evaluation}
 
-%How do you evaluate your solution? 
-The
-                achievement of the research objectives stated above not only provides
-                novel solutions to the stated problem, it also
-                illustrates the advantages and beneficial implications
-                of the proposed theory.  
-Compared
-                to existing published techniques, the advantage of the
-                proposed theory is qualitative, which does not require
-                direct quantitative comparisons.
-Instead
-                a straightforward binary evaluation would be sufficient.
-For
-                the POLSAR scalar model, its advantages are that not
-                only does it lead to consistent discrimination measures, it
-                also generalizes the traditional model for one
-                dimensional SAR intensity.
-For
-                the homoskedastic models, their advantage is that they
-                enable an additive and homoskedastic statistical
-                framework, which is not only capable of overcome various
-                negative impacts of heteroskedasticity, but also results
-                in a single better evaluation criteria that can combine
-                and represent many different existing performance
-                criteria.
-
-To validate the theoretical models,  real-life data are used in this work.
-Specifically, estimated theoretical PDFs are plotted against the histogram of real data,
-  and a good visual match indicates a good validation.
-In cases where theoretical PDF cannot be derived, simulated data are then generated
-  and their histograms are matched against real-life practical data for validation.
+Theoretical models derived are validated against real-life data.
+Specifically, estimated theoretical PDFs are plotted against the histogram of practical data, and a good visual match indicates a good validation.
+In cases where theoretical PDF cannot be derived, simulated data are then generated and their histogram matched against real-life practical data for validation.
 
@@
 
-To evaluate the models’ application in statistical estimation framework, a practical point of view is adopted.
 Practically, all estimators would eventually need to be applied on and work for real images.
-Contrary to experiments on simulated data, experiments on real images often can only be compared qualitatively.
+Contrary to experiments on simulated data, experiments on real images can often only be compared qualitatively.
 This however is critical and will always be included in our investigations.
@@
 
-\section{Research Contributions}
-% How do you know if the problem is solved?   State your research objectives
-Interestingly, the dual-problem stated above are found to have a single solution.
-They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
-  which is multidimensional, inter-correlated and heteroskedastic
-
-Specifically, the following sub-objectives are to be achieved
-\begin{enumerate}
-\item                 To derive scalar and representative statistical models
-                for the multi-dimensional and inter-correlated POLSAR
-                data.
-                \begin{enumerate}
-                \item \label{itm:polsar_model} To derive a scalar statistical model for the
-                POLSAR observable, being the determinant of the
-                covariance matrix.
-                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
-                the observable being modeled 
-                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
-                that when the multi-channel POLSAR data is collapsed
-                into the traditional one-channel SAR data, this
-                determinant is transformed into the representative SAR
-                intensity.
-                \item \label{itm:polsar_validation} To validate the model against practical real-life
-                captured POLSAR data.
-                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
-                processing technique is extensible towards POLSAR data
-                \end{enumerate}
-\item                To derive homoskedastic statistical models for the
-                heteroskedastic (POL)SAR data. 
-                \begin{enumerate}
-                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
-                the original domain and logarithmic transformation
-                can convert this into a homoskedastic model.
-                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
-                the multi dimensional POLSAR as well as for the one
-                dimensional SAR data.
-                \item \label{itm:sar_validation} To validate these statistical models against both
-                practical SAR and POLSAR data
-                \item To illustrate the beneficial applications of these
-                statistical models. Specifically:
-                \begin{enumerate}
-                \item \label{itm:filter_vicious_circle} To show how the consistent sense of variance
-                helps break the vicious cycle in the problem of SAR
-                speckle filtering: a new statistical test for
-                homogeneity and a new speckle filter is derived.
-                \item \label{itm:log_mse} To show how the consistent sense of subtractive
-                distance helps in the problem of evaluating (POL)SAR
-                speckle filters: the log-MSE is proposed to combine the
-                evaluation of radiometric preservation and speckle
-                suppression power.
-                \end{enumerate}
-                \end{enumerate}
-\end{enumerate}
-
-In summary, the first main objective is to derive a scalar and representative statistical model for POLSAR data.
-%The theoretical foundation is the commonly agreed Circular Complex Normal distributions proposed in \cite{Goodman_JOptSocAm_76}. %***IVM you need a reference here!!
-%Theory development is based on applying the statistical variable change theorem on the proposed scalar observable.
-%The theoretical model is validated by matching the functional PDF or the simulated histogram with real-life captured data.
-The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
-This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
-%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
-%  it also results in a homoskedastic statistical model.
-%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
-%After these models are validated against practical data, their beneficial applications are further explored.
-To combine these two seemingly disconnected threads of research, the above results for SAR are extended to POLSAR,
-  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.%***IVM I changed "version" to "superset" in the sentence above.
-Please check if you are comfortable with that change, and if not, change it back!
-Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
-%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
-%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives.
-There is no need to re-emphasize the objective if the write-up is clear)
-
-\section{Organisation of the Thesis}
-The rest of this thesis is organized into five chapters, as follows:
-The next chapter will survey the related publications
-  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
-It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
-Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
-
-%\section{Research Contributions}
+\subsection{Research Contributions}
 
@@
 %Specifically,
-The heart of is thesis contains several contributions which meet the stated objectives.
+This thesis contains several contributions which meet the stated objectives.
                 Chapter \ref{chap:sar} begins by by highlighting that SAR
@@
                 logarithmic transformation converts this into a
-                homoskedastic model (Research Contribution \ref{itm:log_transform}). 
+                homoskedastic model (see Research Objective \ref{itm:log_transform}). 
 It
                 also drives consistent and homoskedastic measures of
-                distance for the one dimensional SAR data (Research Contribution \ref{itm:sar_measures_distance}).
+                distance for the one dimensional SAR data (see Research Objective \ref{itm:sar_measures_distance}).
 These
                 models for SAR are then validated against real-life
-                practical data (Research Contribution \ref{itm:sar_validation})
+                practical data (see Research Objective \ref{itm:sar_validation})
 
  Chapter
-                \ref{chap:polsar} then derives several scalar statistical models for the
-                determinant of the POLSAR covariance matrix (Research Contribution \ref{itm:polsar_model}) and
+                \ref{chap:polsar} then derives a scalar statistical model for the
+                determinant of the POLSAR covariance matrix (see Research Objective \ref{itm:polsar_model}) and
                 shows that this is heteroskedastic in the original
                 domain as well as homoskedastic in the log-transformed
-                domain (Research Contribution \ref{itm:log_transform}).
+                domain (see Research Objective \ref{itm:log_transform}).
 It
                 also derives the heteroskedastic discrimination measures
-                (Research Contribution \ref{itm:polsar_discrimination_measure}) as well as several homoskedastic measures of
-                distance for the data (Research Contribution \ref{itm:sar_measures_distance}).
+                (see Research Objective \ref{itm:polsar_discrimination_measure}) as well as several homoskedastic measures of
+                distance for the data (see Research Objective \ref{itm:sar_measures_distance}).
 Then
                 the models for SAR are shown to be a special case of
-                the proposed models for POLSAR (Research Contribution \ref{itm:polsar_include_sar}) and finally it
-                validates these proposed models (Research Contribution \ref{itm:polsar_validation})
+                the proposed models for POLSAR (see Research Objective \ref{itm:polsar_include_sar}) and finally it
+                validates these proposed models (see Research Objective \ref{itm:polsar_validation})
 
@@
                 property helps to break the vicious cycle in SAR
-                speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
+                speckle filtering (see Research Objective \ref{itm:filter_vicious_circle}).
 It
@@
                 additive and homoskedastic domain to evaluate SAR
-                speckle filters (Research Contribution \ref{itm:log_mse}).
+                speckle filters (see Research Objective \ref{itm:log_mse}).
 An
@@
                 MSE evaluation criteria is also shown capable of
-                evaluating POLSAR speckle filters (Research Contribution \ref{itm:extend_sar_to_polsar}).
+                evaluating POLSAR speckle filters. (see Research Objective \ref{itm:extend_sar_to_polsar})
+
+	\section{Organisation of the Thesis}
+The rest of this thesis is organized into five chapters, as follows:
+The next chapter will survey the related publications
+  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
+It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
+Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
+
+The heart of the thesis lies in chapters \ref{chap:sar} and \ref{chap:polsar}.
+While chapter \ref{chap:sar} presents the initial homoskedastic model for SAR data, 
+chapter \ref{chap:polsar} illustrates the more recent and more generic model for POLSAR.
+Chapter \ref{chap:polsar} also specifically describes how the initial model for SAR can be considered as a special case of the POLSAR model.
+
+Chapter \ref{chap:applications} presents several of our published techniques in handling both SAR and POLSAR data.
+Theses techniques can all be considered as applications of the theoretical model presented in chapters \ref{chap:sar} and \ref{chap:polsar}.
+Demonstrated applications include clustering algorithms, speckle filtering techniques and a novel methodology to evaluate (POL)SAR speckle filters.
 Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.
-
-%The heart of the thesis lies in chapters \ref{chap:sar} and \ref{chap:polsar}.
-%While chapter \ref{chap:sar} presents the initial homoskedastic model for SAR data, 
-%chapter \ref{chap:polsar} illustrates the more recent and more generic model for POLSAR.
-%Chapter \ref{chap:polsar} also specifically describes how the initial model for SAR can be considered as a special case of the POLSAR model.
-%
-%Chapter \ref{chap:applications} presents several of our published techniques in handling both SAR and POLSAR data.
-%Theses techniques can all be considered as applications of the theoretical model presented in chapters \ref{chap:sar} and \ref{chap:polsar}.
-%Demonstrated applications include clustering algorithms, speckle filtering techniques and a novel methodology to evaluate (POL)SAR speckle filters.

### 2013-07-24 4/polsar_ivm.tex
updated for Ian to change

--- 2013-07-24 4/polsar.tex
@@
 To keep the section flowing, the mathematical derivation is only presented here in major sketches.
-For more detailed derivation, please refer to Appendix \ref{chap:appendix_a}.
+For more detailed derivation, please refer to Appendix \ref{sec:appendix_a}.
 
@@
 A more practical approach is to use a look-up graph approach
-  where for each value of $var [ln|Cv|]$, a corresponding pre-computed value for L can be found by referencing the variance value on the graph.
+  where for each value of var [ln|Cv |], a corresponding pre-computed value for L can be found by referencing the variance value on the graph.
 An approximation can also be used  to find the L value based on a back-of-the-envelope calculation using the following equation  
@@
 \end{figure}
+
+In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
+Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
+The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
+The representative power of the observable is explained in a few different ways.
+Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
+Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
+In fact, this chapter also proposes several new discrimination measures for POLSAR,
+  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
+Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
+It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
+Such applications are briefly explored in the next chapter.
 
@@
 %
-
-In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
-Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.
-The derived models are shown to be heteroskedastic in the original domain, and logarithmic transformation is shown to convert these into homoskedastic models.
-The representative power of the observable is explained in a few different ways.
-Firstly, the determinant observable neatly transforms into the representative and widely-used SAR intensity when the dimensional number is collapsed to one, putting the commonly-used statistical models for SAR intensity to fall within this generic proposed models.
-Secondly, this observable is also  widely used in existing discrimination measures for POLSAR.
-In fact, this chapter also proposes several new discrimination measures for POLSAR,
-  which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
-Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
-It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.
-%Such applications are briefly explored in the next chapter. 
-The next chapter will briefly explore such applications as well as presents further validation of the proposed models.

### 2013-07-24 Chap2(NV).tex
updated for Ian to change

--- 2013-07-24 2/literature_review.tex
@@
 \chapter{Current Methods in Processing SAR and POLSAR Data} %chapter 2
-\label{chap:lit_survey}
 
@@
 
-\subsection{The Stochastic Nature of SAR data}
+\subsection{The Stochastic nature of SAR data}
 
@@
 SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
-  each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
+  each reflecting from different and distributed elementary scatterers \citep{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
 The random nature of the SAR data arises
@@
 Assuming the number of these elementary back scatterers is sufficiently large,
-  then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
+  then the Central Limit Theorem is applicable \citep{Goodman_Springer_1975}.
 Consequently the interference of these randomly phased responses can be considered as
-  a random walk on the 2D complex plane \cite{Goodman_JOptSocAm_76}.  
+  a random walk on the 2D complex plane \citep{Goodman_JOptSocAm_76}.  
 Specifically the real part $A_r$ as well as the imaginary part $A_i$ of the observed SAR signal $A$ can be considered as
-  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \cite{Lee_CRCPress_2009}. 
+  random variables from uncorrelated Gaussian distributed stochastic processes with zero means and indentical variances $\sigma^2/2$  \citep{Lee_CRCPress_2009}. 
 Their probability density functions (PDF) are given as:
@@
 
-%\begin{eqnarray}
-%pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
-%pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
-%\end{eqnarray}
-\begin{equation}
-\label{eqn:SAR Amplitude PDF}
-\caption{eqn:SAR Amplitude PDF}
-pdf(A) = \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }
-\end{equation}
-\begin{equation}
-  \label{eqn:SAR Intensity PDF}
-  \caption{eqn:SAR Intensity PDF}
-pdf(I) = \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
-\end{equation}
+\begin{eqnarray}
+pdf(A) &=& \frac{2A}{\sigma^2}e^{ \left( -\frac{A^2}{\sigma^2} \right) }\\
+pdf(I) &=& \frac{1}{\sigma^2}e^{\left( -\frac{I}{\sigma^2} \right) }
+\end{eqnarray}
 
@@
 As SAR speckle phenomena arises from the stochastic nature of SAR, it seriously hinders the interpretation and understanding of SAR images.
+
 Speckle noise on SAR images are hence routinely reduced through a speckle filtering process for easier human interpretation and more accurate post-processing.
@@
 
-\subsubsection{The polarization property of Electro-Magnetic waves}
-
-The propagation of Electro-Magnetic (EM) wave in space is governed by Maxell‚Äôs equations. 
-The general solution to these equations is a linear superposition of waves, each having the form of:
-\begin{eqnarray*}
- \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
- \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
-\end{eqnarray*}
-where
-	$g$ is any well-behaved function of a dimensionless argument $\phi$,
-	%for virtually any¬†well-behaved function g¬†of dimensionless argument œÜ, where
-	$\omega$ is the angular frequency (in radians per second), and
-	$\vec{k}= (k_x,k_y,k_z)$ is the wave vector (in radians per meter).
-
-Because of the divergence between the electric and the magnetic fields, there will be no fields in the direction of wave propagation.
-Thus if we define the z direction as the travelling direction of the EM wave,
-  then both the electric and the magnetic fields are fluctuating in the x,y plane.
-Furthermore, when considering wave propagation, it is conventional that only the electric field vector is described and the magnetic field is ignored since it is perpendicular to the E field and is proportional to it.
-Projecting this vector into x,y directions, we have:
-
-\begin{equation*}
-\vec{E}(z,t) 
-= 
-\left(
-	\begin{array} {c}
-		E_x^0 \cos{ \left( wt - kz  + \phi_x^0 \right) } \\
-		E_y^0 \cos{ \left( wt - kz  + \phi_y^0 \right)} \\
-		0
-	\end{array}
-\right)
-= 
-\left(
-	\begin{array} {c}
-		\xi_x(t) \\
-		\xi_y(t) \\
-		0
-	\end{array}
-\right)
-\end{equation*}
-where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.
-
-In other words, the EM vector can oscillate in more than one orientation, and this denote the polarization property of EM wave.
-The exact shape traced out in a fixed projective plane by the tip of the electric vector as the plane propagate is a description of the polarization state.
-This shape is characterized by the formula: 
-\begin{equation*}
- \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
-\end{equation*}
-where
-	$\Delta \phi = \phi_y^0 - \phi_x^0$
-The formula characterizes what is termed as the polarization ellipse.
-
-The parameters that describe the polarization ellipse are: 
-\begin{equation*}
-\tan (\theta ) = \frac{E_y^0}{E_x^0}
-\end{equation*}
-with
-	$0 \leq \theta \leq \pi/2$. 
-The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
-\begin{equation*}
-\tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
-\end{equation*}
-with
-	$0 \leq \Psi < \pi$. 
-The ellipticity, $\epsilon$ is the major-to-minor-axis ratio.
-The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
-\begin{equation*}
-\sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
-\end{equation*}
-with
-	$0 \leq \chi \leq \pi/2$, and $0 \leq \epsilon \leq \infty$
-
-Ignoring the scale of the electrical fields, the elementary wave polarization can be completely described by two parameters, i.e. $E_y^0/E_x^0$ and $\Delta \phi = \phi_y^0 - \phi_x^0$. 
-Similarly, ignoring the scale of the ellipse, the polarization ellipse can be completely described by two angles $\Psi$ and $\chi$.
-
-Other parameters includes:
-\paragraph{ Complex polarization ratio }
-This ratio is important in explaining polarization basis changes.
-
-It is defined as:
-\begin{equation}
-\rho = \frac{E_y^0}{E_x^0} e^{i \Delta \phi} = \frac{\cos(2 \chi) + i \sin(2 \chi)}{1 - \cos(2\Psi) \cos(2\chi)}
-\end{equation}
-
-\paragraph{Jones Vector}
-
-%Let the total wave power:
-%\begin{equation}
-%|E|^2 = (E_x^0)^2  + (E_y^0)^2
-%\end{equation}
-%and phase 
-%\begin{equation}
-%\theta = \tan^{-1} \left( \frac{E_y^0}{E_x^0} \right)
-%\end{equation}
-
-The Jones vector is defined as 
-\begin{equation}
-J = 
-\left(
-\begin{array}{c}
-	\xi_x(t) \\
-	\xi_y(t) 
-\end{array}
-\right)
-= \xi_x(t)
-\left(
-\begin{array}{c}
-	1 \\
-	\rho
-\end{array}
-\right)
-\end{equation}
-
-Thus the normalized Jones vector can be given as:
-\begin{equation}
-J = 
-\left(
-\begin{array}{c}
-	\cos(\theta) \cdot e^{i \phi_x^0} \\
-	\sin(\theta) \cdot e^{i \phi_y^0}
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
-	1\\
-	\tan(\theta) \cdot e^{i \Delta \phi}
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
-	\cos(\Psi) \cos(\chi) - i \sin(\Psi) \sin(\chi) \\
-	\sin(\Psi) \cos(\chi) + i \cos(\Psi) \sin(\chi)
-\end{array}
-\right)
-\end{equation}
-
-The two parameters in the Jones vector can completely describe the polarization state (ellipse) of any elementary wave.
-This same Jones vector finds extensive use in quantum machenics, and is interpreted as quantum state vector.
-Its bra-ket notation formula, which is normally used in quantum computation contexts is:
-\begin{equation}
-J = | \Psi \rangle 
-= 
-\left(
-\begin{array}{c}
-	\cos(\theta) \cdot e^{i \phi_x^0} \\
-	\sin(\theta) \cdot e^{i \phi_y^0}
-\end{array}
-\right)
-\end{equation}
-
-By definitions, the horizontal linear polarized wave is defined as: $J_h = \left(
-\begin{array}{c}
- 1 \\
- 0
-\end{array}
-\right)$, similarly the vertical linear polarized wave: $J_v = \left(
-\begin{array}{c}
- 0 \\
- 1
-\end{array}
-\right)$, the $\pm \pi/4$ linear polarized waves $J_{\pm} = \pm \frac{1}{\sqrt{2}} \left(
-\begin{array}{c}
- 1 \\
- 1
-\end{array}
-\right)$, the left circular polarized wave: $J_l = |L\rangle = \frac{1}{\sqrt{2}} \left(
-\begin{array}{c}
- 1 \\
- -i
-\end{array}
-\right)$ and the right circular polarized wave: $J_r = |R\rangle = \frac{1}{\sqrt{2}} \left(
-\begin{array}{c}
- 1 \\
- i
-\end{array}
-\right)$
-
-\paragraph{ Stokes Vector}
-
-Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
-The wave coherency matrix is defined as:
-\begin{equation*}
-W_c = \left<
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right)
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right)^{\dagger}
-\right>
-= \left<
-\left(
-\begin{array}{c c}
- \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
- \xi_y \xi_x^* 	& \xi_y \xi_y^* 
-\end{array}
-\right)
-\right>
-= \left<
-\left(
-\begin{array}{c c}
- |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
- |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
-\end{array}
-\right)
-\right>
-\end{equation*}
-
-The Stokes vector is then defined as:
-\begin{equation*}
-S_t = 
-\left(
-\begin{array}{c}
- S_0 \\
- S_1 \\
- S_2 \\
- S_3
-\end{array}
-\right)
-=
-\left(
-\begin{array}{c}
- |\xi_x|^2 + |\xi_y|^2 \\
- |\xi_x|^2 - |\xi_y|^2 \\
- 2\Re(\xi_x \xi_y^*) \\
- 2\Im(\xi_x \xi_y^*)
-\end{array}
-\right)
-\end{equation*}
-
-In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
-\begin{equation*}
-S_t = 
-\left(
-\begin{array}{c}
- S_0 \\
- S_0 \cos(2\Psi) \cos(2\chi) \\
- S_0 \sin(2\Psi) \cos(2\chi) \\
- S_0 \sin(2\chi)
-\end{array}
-\right)
-\end{equation*}
-
-%It should be noted that: the factor of two before the polarization ellipse's angles indicate the fact that
-%	any polarization ellipse is practical indistinguishable from on rotated by $180^o$ 
-%	or with on with the axis lengths swapped accompanied by a $90^o$ rotation.
-
-At this point, a distinction needs to be highlighted. %explaination is warranted.
-%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
-%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
-In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
-The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
-In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
-As such, the polarization of the waves are normally not fully polarized.
-One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
-%The phenomena can be loosely called wave depolarization.
-%****IVM: Hai, is this your term or is it also used by others for the same thing?
-In that case, it might be good to put a reference here.
-I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.
-
-The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wavelength.
-In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.
-
-%(comment: I think it would be better if you can link the two paragraphs together, such as
-%ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )
-
-\paragraph{Degree of polarization}
-
-Closely related to the Stokes vector is the concenpt of ``Degree of polarization'' $p$, which is a quantity used to describe the portion of an EM wave which is polarized.
-A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
-A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
-Thus $0 \leq p \leq 1$.
-
-Depolarization phenomena are explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
-The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
-If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
-One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.
-
-In fully polarized wave, the following equation holds:
-\begin{equation*}
-S_0^2 = S_1^2 + S_2^2 + S_3^2
-\end{equation*}
-
-In depolarized wave, it becomes an in-equation
-\begin{equation*}
-S_0^2 > S_1^2 + S_2^2 + S_3^2
-\end{equation*}
-
-Then the degree of polarization is defined as
-\begin{equation*}
-p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
-\end{equation*}
-
-In such general case, the Stokes Vector is written as:
-\begin{align*}
-S_t &= 
-\left(
-\begin{array}{c}
- I \\
- I p \cos(2\Psi) \cos(2\chi) \\
- I p \sin(2\Psi) \cos(2\chi) \\
- I p \sin(2\chi)
-\end{array}
-\right) \\
- &= I (1 - p)
-\left(
-\begin{array}{c}
- 1 \\
- 0 \\
- 0 \\
- 0
-\end{array}
-\right) 
-+ I p
-\left(
-\begin{array}{c}
- 1\\
- \cos(2\Psi) \cos(2\chi) \\
- \sin(2\Psi) \cos(2\chi) \\
- \sin(2\chi)
-\end{array}
-\right)
-\end{align*}
-
-Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:
-$I$, the total power of the measured beam is $I=S_0$,
-$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
-$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.
-
-\subsubsection{Full Polarimetry and the Polarimetric Signatures}
-
-This section describes the core concept of POLSAR, i.e. the target's polarimetric signature, 
-	and illustrates why research into partial polarimetry is warranted.
-
-POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
-The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
-\begin{equation*}
- E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
-\end{equation*}
-%***IVM: Hai, do you need to explain the k & r terms?
-
-Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
-\begin{equation*}
- \left( 
-\begin{array}{c}
- E_h^{Rx} \\
- E_v^{Rx}
-\end{array}
- \right) = \frac{e^{ikr}}{r} 
-\left( 
-\begin{array}{c c}
- S_{HH} & S_{HV} \\
- S_{VH} & S_{VV}
-\end{array}
- \right) 
-\left( 
-\begin{array}{c}
- E_h^{Tx} \\
- E_v^{Tx}
-\end{array}
- \right) 
-\end{equation*}
-
-The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
-The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \cite{Sinclair_1950_ProcsIRE}.
-In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \cite{Nghiem_1992_RadioSci}.
-
-The matrix can also be ``stratified'' to define the target scattering vector as: 
-\begin{equation}
-  \label{eqn:Covariance Target Vector of Full Polarimetric SAR}
-  \caption{eqn:Covariance Target Vector of Full Polarimetric SAR}
-T_{cv} = \left( 
-\begin{array}{c}
- S_{HH} \\
- \sqrt{2} S_{HV} \\
- S_{VV}
-\end{array}
- \right) 
-\end{equation}
-or 
-\begin{equation}
-  \label{eqn:Coherence Target Vector of Full Polarimetric SAR}
-  \caption{eqn:Coherence Target Vector of Full Polarimetric SAR}
-T_{ch} = \frac{1}{\sqrt{2}} \left( 
-\begin{array}{c}
- S_{HH} + S_{VV}\\
- S_{HH} - S_{VV} \\
- S_{HV}
-\end{array}
- \right) 
-\end{equation}
-
-Similar to the reason that Stokes vectors are preferred to Jones vector in wave polarization, 
-	second order statistics of the target scattering matrix are normally preferred.
-The covariance matrix is defined as:
-\begin{equation}
-  \label{eqn:Covariance Matrix of Full Polarimetric SAR}
-  \caption{eqn:Covariance Matrix of Full Polarimetric SAR}
-\tiny{
-C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
-\left( 
-\begin{array}{c c c}
- S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
- \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
- S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
-\end{array}
- \right) 
-}
-\end{equation}
-while the coherency matrix is defined as:
-\begin{equation}
-  \label{eqn:Coherence Matrix of Full Polarimetric SAR}
-  \caption{eqn:Coherence Matrix of Full Polarimetric SAR}
-\tiny{
-C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
-\left( 
-\begin{array}{c c c}
- (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
- (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
- 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
-\end{array}
- \right) 
-}
-\end{equation}
-
-Evidently the two matrices are related:
-\begin{equation*}
-C_h = N C_v N^T
-\end{equation*}
-where
-	$N = \frac{1}{\sqrt{2}}
-\left( 
-\begin{array}{c c c}
- 1 & 0		& 1\\
- 1 & 0		& -1\\
- 0 & \sqrt{2}	& 0
-\end{array}
-\right)$
-
-The off-diagonal values in both covariance and coherence matrices are normally complex numbers. 
-Equivalent matrices with all real value entries which carry the same information are called the Mueller and the Kennaugh matrix, which are to be used in forward and backward scattering alignment respectively\cite{Guissard_1994_TGRS}.
-They are defined as the matrix that relates the Stokes matrix of sent and received signals.
-\begin{equation*}
-S_t^{Rx} = K S_t^{Tx}
-\end{equation*}
-
-Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
-\begin{equation*}
-K = 1/2 Q^* S \otimes S^* Q^{T*}
-\end{equation*}
-where
-	$\otimes$ denotes the Kronecker product, and
-	$Q = 
-\left( 
-\begin{array}{c c c c}
- 1 & 0 & 0 &  1 \\
- 1 & 0 & 0 & -1\\
- 0 & 1 & 1 &  0\\
- 0 & i & i &  0
-\end{array}
-\right)$
-
-POLSAR aims to measure the target's polarimetric response.
-%Depending on the satellite instrument and processing, either Sinclair matrix or Kennaugh matrix elements are provided.
-Typically, the radar transmitter will separately send different horizontal and vertical polarized waves, and measure the response also in horizontal and vertical polarization directions.
-The full polarimetric data, will then have four channels, i.e. $\{ S_{HH}, S_{VV}, S_{HV}, S_{VH} \}$. 
-The four channel, or quad-pol data, is considered full polarimetric data since it allows one to synthesize the target's response for any given pair of transmitted and received polarization.
-Such a process is called polarization synthesis.
-The formula is given as:
-\begin{equation}
-  \label{eqn:Polarization Synthesis Process of Full-Pol data}
-  \caption{eqn:Polarization Synthesis Process of Full-Pol data}
-I^{Rx} = 
-\left( 
-\begin{array}{c }
- 1 \\
- \cos(2\chi^{Rx}) \cos(2\Psi^{Rx}) \\
- \cos(2\chi^{Rx}) \sin(2\Psi^{Rx}) \\
- \sin(2\chi^{Rx}) 
-\end{array}
-\right)^T
-K
-\left( 
-\begin{array}{c }
- 1 \\
- \cos(2\chi^{Tx}) \cos(2\Psi^{Tx}) \\
- \cos(2\chi^{Tx}) \sin(2\Psi^{Tx}) \\
- \sin(2\chi^{Tx}) 
-\end{array}
-\right)
-\end{equation}
-where $I^{Rx}$ is the intensity of the target's response in a given combination of transmitted and received polarizations.
-
-In a full polarimetric implementation, an alternate pulsing scheme is normally used to share a single time slot for transmitting two different polarizations' pulses.
-In partial polarimetry modes only a single polarization is sent.
-Since the transmitting time-slot no longer needs to be shared in the partial polarimetry modes, higher operating frequency become possible which leads to better (almost double) resolution or coverage.
-Clearly in such cases, only two out of four data channels is available, i.e. either $\{S_{HH},S_{HV}\}$ or $\{S_{VH},S_{VV}\}$.
-%The limitation in payload is expected to be around for years to come, with new polarimetric projects being planned by various space agencies.
-This trade-off is based on limitations of physics, and hence is likely to be around for years to come.
-
 \subsubsection{Partial Polarimetry and the Stokes Vector}
 
-%***IVM: Hai your citations are wrong in this paragraph, they should be \cite (I think I've fixed them all though)
+%***IVM: Hai your citations are wrong in this paragraph, they should be \citep (I think I've fixed them all though)
 Early works from the radar community had focused on the theoretical introduction of the scattering matrix such as the Sinclair matrix or Mueller matrices, for full, i.e.
-quad, polarimetric measurements \cite{Sinclair_1950_ProcsIRE}.
+quad, polarimetric measurements \citep{Sinclair_1950_ProcsIRE}.
 %(Sinclair, 1950), (TODO) 
-These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \cite{Zebker_1991_ProcsIEEE}.
+These works were continued by Boerner, and the first polarimetric images were captured by NASA JPL at Caltech in 1991 \citep{Zebker_1991_ProcsIEEE}.
 
 Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR were launched.
-However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes as a compromise between theoretical polarimetric requirements and practical limitations.
+However due to operational restrictions on payload, power and data-downlink (speed?), the satellites also offer dual-channel polarimetric SAR modes as a compromise between theoretical polarimetric requirements and practical limitations.
 Initially, to the end user, while dual-channel partial polarimetry may not provide the complete polarimetric signature of the target, the loss is compensated for by either better resolutions or higher coverage and lower cost.
+(Comment - this sentence is not clear to me.
+How does the ëlossí be compensated by ëbetter resolutionsí?
+I thought loss means the resolution becomes worse to start with)
 
 Until very recently, these partial polarimetry modes were not formally taken up by scientists and academia. 
-In his pioneer paper in 2005, Souyris\cite{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode and suggested that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
-Raney\cite{Raney_2006_IGARSS} also showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave (via Stokes parameters), it is also capable of detecting the basic target's polarimetric characteristic, e.g.
+In his pioneer paper in 2005, Souyris\citep{Souyris_2005_TGRS} introduced the so-called compact polarimetry mode and suggested that it may be possible to reconstruct full polarimetric information from compact polarimetric data.
+Raney\citep{Raney_2006_IGARSS} also showed that dual-channel polarimetry is not only capable of measuring the complete polarization information of the back-scattered EM wave (via Stokes parameters), it is also capable of detecting the basic target's polarimetric characteristic, e.g.
 odd or even bounce phenomena.
@@
 Mathematically, the process is modelled as:
-\begin{equation*}
+\begin{equation}
  \left( 
@@
  \right) E^{Tx}
-\end{equation*}
+\end{equation}
 
@@
 %****IVM: Hai, the equation doesn't fit - can you do something like this instead? (and same for the next eqn too)-> 
-%\begin{equation}
-%J = 
-%\left(	
-%\begin{array}{c c}
-%	|s_{HH}|^2 + |s_{HV}|^2 }              		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
-%	{+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
-%\vspace{0.1}
-%	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
-%	{+ s_{HV}s_{HH}^* + s_{VV}s_{HV}^*} 	& { + 2 \Re{(s_{VV}s_{HV}^*)}}
-%\end{array}
-%\right)
-%\end{equation}
-
-\begin{equation*}
+\begin{equation}
 J = 
@@
 \begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2               		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
-	+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
-        \vspace{0.01 in} & \vspace{0.01 in}\\
+	|s_{HH}|^2 + |s_{HV}|^2 }              		& 	{s_{HH}s_{VV}^* + |s_{HV}|^2} \\
+	{+ 2 \Re{(s_{HH}s_{HV}^*)}          		&  {+ s_{HH}s_{HV}^* + s_{HV}s_{VV}^*}\\
+\vspace{0.1}
 	{s_{HH}^*s_{VV} + |s_{HV}|^2}         		& 	{|s_{VV}|^2 + |s_{HV}|^2}\\
@@
 \right)
-\end{equation*}
+\end{equation}
 
 %*** IVM, I changed the following reference to a \citet
-In \cite{Raney_2006_IGARSS}, Raney demonstrated a different perspective by proposing a hybrid architecture.
+\citet{Raney_2006_IGARSS} demonstrated a different perspective by proposing a hybrid architecture.
 He argued that the dual polarisation measurements effectively capture the polarisation states of the single back-scattered signal resulting from a single incoming pulse.
@@
 The partial covariance matrix then becomes:
-\begin{equation*}
+\begin{equation}
 J = \frac{1}{2} \left(	
 \begin{array}{c c}
-	|s_{HH}|^2 + |s_{HV}|^2 
-& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* \\
-        + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
-&       - i (|s_{HV}|^2 + s_{HH}s_{VV}^*) \\ 
-        \vspace{0.01 in} & \vspace{0.01 in}\\
-	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* 
-& 	|s_{VV}|^2 + |s_{HV}|^2  \\
-        + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
-&       + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)  
-\end{array}
-\right)
-\end{equation*}
+	|s_{HH}|^2 + |s_{HV}|^2 + i (s_{HH}s_{HV}^* - s_{HV}s_{VV}^*)
+& 	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* - i (|s_{HV}|^2 + s_{HH}s_{VV}^*)\\
+	s_{HH}s_{HV}^* - s_{HV}s_{VV}^* + i (|s_{HV}|^2 + s_{HH}s_{VV}^*)
+& 	|s_{VV}|^2 + |s_{HV}|^2 + i (s_{HV}s_{VV}^* - s_{VV}s_{HV}^*)
+\end{array}
+\right)
+\end{equation}
+
+(Comment: check the presentation of this equation in the pdf file)
 
@@
 The suggestion is evidenced by calculating the response of known odd-bounce trihedral and even-bounce dihedral when the incident wave is right circular polarized.
-\begin{equation*}
+\begin{equation}
 \Gamma_{tri} = \left(
@@
 \right)
-\end{equation*}
+\end{equation}
 Then the response will be reversed as it can be calculated as:
-\begin{equation*}
+\begin{equation}
 J_r = \left(
@@
 \right) 
-\end{equation*}
+\end{equation}
 with
@@
 For a dihedral target, whose main axis is at an angle $\theta$ with respect to the horizontal direction, the Sinclair matrix is given as:
-\begin{equation*}
+\begin{equation}
 \Gamma_{dih} = 
@@
 \right)
-\end{equation*}
+\end{equation}
 The even bounce phenomena is detectable as its polarimetric response, which is then:
-\begin{equation*}
+\begin{equation}
 J_r = \left(
@@
 \right) 
-\end{equation*}
-In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
-Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
-Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
-Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
+\end{equation}
+In \citep{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
+Also in a follow up study \citep{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
+Furthermore, Lardeux \citep{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
+Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \citep{Raney_2009_RadarConf}.
 
@@
 This methodology has been demonstrated and is widely used in the community.
-%We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
+We hypothesize that the partial polarimetric covariance matrix, which is essentially a variant of the Stokes vector, can be speckle filtered, using the familiar intensity speckle filtering algorithms.
 The focus into partial polarimetry allows analysis with a smaller matrix, while its implications can be extended not only to full polarimetry modes but also towards bi-static polarimetric scenarios.
@@
 
-Souyris, in 2005, published a paper \cite{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
+Souyris, in 2005, published a paper \citep{Souyris_2005_TGRS} which claimed and presented an algorithm to reconstruct full polarimetric information from the given partial compact polarimetric data.
 The algorithm is claimed to work on natural surfaces.
-In \cite{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
+In \citep{Nord_2009}, Nord reviewed the reconstruction problem for various different partial polarimetry modes, and an improved algorithm is given.
 %****IVM: Hai are Nord / Ainsworth single author?
@@
 al."
-In \cite{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
+In \citep{Ainsworth_2009_ISPRS}, Ainsworth reviewed performance of target classification on different partial modes, reconstructed pseudo-full mode and full polarimetric data.
 Chapter 3 will review this sub-topic further and introduce our work on expanding the reconstruction to urban man-made structures and surfaces (from the original system which was relevant to natural cover only).
@@
 Compared with full polarimetric data, the better spatial resolution of dual channel systems could compensate for the loss of reconstructed polarimetric information, especially for the purpose of target detection and classification.
+\paragraph{ Stokes Vector}
+
+Another way to look at polarization is through the coherency matrix, and equivalently the Stokes matrix.
+The wave coherency matrix is defined as:
+\begin{equation}
+W_c = \left<
+\left(
+\begin{array}{c}
+ \xi_x \\
+ \xi_y
+\end{array}
+\right)
+\left(
+\begin{array}{c}
+ \xi_x \\
+ \xi_y
+\end{array}
+\right)^{\dagger}
+\right>
+= \left<
+\left(
+\begin{array}{c c}
+ \xi_x \xi_x^* 	& \xi_x \xi_y^* \\
+ \xi_y \xi_x^* 	& \xi_y \xi_y^* 
+\end{array}
+\right)
+\right>
+= \left<
+\left(
+\begin{array}{c c}
+ |\xi_x|^2 	& |\xi_x| |\xi_y| e^{-i \Delta \phi} \\
+ |\xi_x| |\xi_y| e^{i \Delta \phi} 	& |\xi_y|^2
+\end{array}
+\right)
+\right>
+\end{equation}
+
+The Stokes vector is then defined as:
+\begin{equation}
+S_t = 
+\left(
+\begin{array}{c}
+ S_0 \\
+ S_1 \\
+ S_2 \\
+ S_3
+\end{array}
+\right)
+=
+\left(
+\begin{array}{c}
+ |\xi_x|^2 + |\xi_y|^2 \\
+ |\xi_x|^2 - |\xi_y|^2 \\
+ 2\Re(\xi_x \xi_y^*) \\
+ 2\Im(\xi_x \xi_y^*)
+\end{array}
+\right)
+\end{equation}
+
+In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
+\begin{equation}
+S_t = 
+\left(
+\begin{array}{c}
+ S_0 \\
+ S_0 \cos(2\Psi) \cos(2\chi) \\
+ S_0 \sin(2\Psi) \cos(2\chi) \\
+ S_0 \sin(2\chi)
+\end{array}
+\right)
+\end{equation}
+
+%It should be noted that: the factor of two before the polarization ellipse's angles indicate the fact that
+%	any polarization ellipse is practical indistinguishable from on rotated by $180^o$ 
+%	or with on with the axis lengths swapped accompanied by a $90^o$ rotation.
+
+At this point, a distinction needs to be highlighted. %explaination is warranted.
+%The naive view is that Stokes vector, which has four values are redundant in describing wave's polarization. 
+%In contrary, Stokes vector are preferred to Jones vector, as Jones vector is based on the assumption that the wave is elementary and very well behaved.
+In comparison to the two-element Jones vector, Stokes vectors have more data, namely four elements. 
+The Jones vector can completely describe the polarization states of an elementary wave, whose formulation is based on the assumption that the wave is very well behaved.
+In practice, that is not normally the case, because reflected waves are generally combinations of multiple waves which ranged over certain areas of time and frequency. 
+As such, the polarization of the waves are normally not fully polarized.
+One simple analogy is that the field ratio, i.e. $\xi_x/\xi_y$, or the phase difference, i.e. $\Delta \phi$, are not constant at all times.
+The phenomena can be loosely called wave depolarization.
+%****IVM: Hai, is this your term or is it also used by others for the same thing?
+In that case, it might be good to put a reference here.
+I think the word "loosely" is one of those trigger words that causes the examiner to sit up and read it critically.
+
+The analysis above is especially prevalent in the remote sensing community, where the area of a single resolution cell (pixel) is very large compared with the radar's wavelength.
+In such cases, the wave field is very stochastic and only statistical information about the variations and correlations between polarization components can be gathered.
+
+(comment: I think it would be better if you can link the two paragraphs together, such as
+ìClosely related to the Stoke vector is the concept of Degree of polarization p, which is a quantity used to describeÖî, or something like this )
+
+\paragraph{Degree of polarization}
+
+Degree of polarization $p$ is a quantity used to describe the portion of an EM wave which is polarized.
+A perfectly polarized wave has $p=100\%$, while a fully depolarized wave is characterized by $p=0\%$.
+A wave which is partially polarized can be represented as a superposition of a polarized and another unpolarized component.
+Thus $0 \leq p \leq 1$.
+
+Depolarization phenomena are explained from the fact that most sources of EM radiation contain a large number of ``elementary'' sources.
+The polarization of the electric fields produced by the emitters may not be correlated, which leads to depolarization effects.
+If there is partial correlation among the ``elementary'' sources, the light is partially polarized. 
+One may then describe the received EM wave polarization in terms of the degree of polarization and the parameters of the polarization ellipse.
+
+In fully polarized wave, the following equation holds:
+\begin{equation}
+S_0^2 = S_1^2 + S_2^2 + S_3^2
+\end{equation}
+
+In depolarized wave, it becomes an in-equation
+\begin{equation}
+S_0^2 > S_1^2 + S_2^2 + S_3^2
+\end{equation}
+
+Then the degree of polarization is defined as
+\begin{equation}
+p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
+\end{equation}
+
+In such general case, the Stokes Vector is written as:
+\begin{equation}
+S_t = 
+\left(
+\begin{array}{c}
+ I \\
+ I p \cos(2\Psi) \cos(2\chi) \\
+ I p \sin(2\Psi) \cos(2\chi) \\
+ I p \sin(2\chi)
+\end{array}
+\right)
+ = I (1 - p)
+\left(
+\begin{array}{c}
+ 1 \\
+ 0 \\
+ 0 \\
+ 0
+\end{array}
+\right) 
++ I p
+\left(
+\begin{array}{c}
+ 1\\
+ \cos(2\Psi) \cos(2\chi) \\
+ \sin(2\Psi) \cos(2\chi) \\
+ \sin(2\chi)
+\end{array}
+\right)
+\end{equation}
+
+Alternatively, if the Stokes vector is measured and known, then the polarization characteristics of a wave are given as:
+
+(Comment: the following should be re-aligned into multiple equations, instead of one long sentence ñ see pdf file)
+
+$I$, the total power of the measured beam is $I=S_0$,
+$p$, the degree of polarization is calculated as $p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}$,
+$2\Psi = \tan^{-1} (S_2/S_1) $ and $2 \chi = \tan^{-1} (S_3 / \sqrt{S_1^2 + S_2^2})$ are the angles that characterize the wave polarization state.
+
+(comment: you should link the following paragraph to the above discussion ñ I suggest move the following paragraph to earlier as shown here)
 
@@
 
+\subsubsection{Full Polarimetry and the Polarimetric Signatures}
+
+This section describes the core concept of POLSAR, i.e. the target's polarimetric signature, 
+	and illustrates why research into partial polarimetry is warranted.
+
+POLSAR radar measures the back-scattered echo received as the result of transmitting a signal.
+The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
+\begin{equation}
+ E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
+\end{equation}
+%***IVM: Hai, do you need to explain the k & r terms?
+
+Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
+\begin{equation}
+ \left( 
+\begin{array}{c}
+ E_h^{Rx} \\
+ E_v^{Rx}
+\end{array}
+ \right) = \frac{e^{ikr}}{r} 
+\left( 
+\begin{array}{c c}
+ S_{HH} & S_{HV} \\
+ S_{VH} & S_{VV}
+\end{array}
+ \right) 
+\left( 
+\begin{array}{c}
+ E_h^{Tx} \\
+ E_v^{Tx}
+\end{array}
+ \right) 
+\end{equation}
+
+The scattering matrix can be called the Jones matrix (relating to the Jones vector) in the forward scattering alignment.
+The matrix is normally called the Sinclair matrix in SAR literature, as backward scattering alignment is normally adopted for SAR \citep{Sinclair_1950_ProcsIRE}.
+In the case of mono-static SAR, i.e. both radar transmitter and receiver can be considered as located in a single place, physical reciprocity leads to $S_{HV}=S_{VH}$ \citep{Nghiem_1992_RadioSci}.
+
+The matrix can also be ``stratified'' to define the target scattering vector as: 
+\begin{equation}
+T_{cv} = \left( 
+\begin{array}{c}
+ S_{HH} \\
+ \sqrt{2} S_{HV} \\
+ S_{VV}
+\end{array}
+ \right) 
+\end{equation}
+or 
+\begin{equation}
+T_{ch} = \frac{1}{\sqrt{2}} \left( 
+\begin{array}{c}
+ S_{HH} + S_{VV}\\
+ S_{HH} - S_{VV} \\
+ S_{HV}
+\end{array}
+ \right) 
+\end{equation}
+
+Similar to the reason that Stokes vectors are preferred to Jones vector in wave polarization, 
+	second order statistics of the target scattering matrix are normally preferred.
+The covariance matrix is defined as:
+\begin{equation}
+\small{
+C_v = \left< T_{cv} T_{cv}^{*T} \right> = 
+\left( 
+\begin{array}{c c c}
+ S_{HH}S_{HH}^* 	& \sqrt{2}S_{HH}S_{HV}^*	& S_{HH}S_{VV}^* \\
+ \sqrt{2}S_{HV}S_{HH}^* & 2 S_{HV}S_{HV}^* 		& \sqrt{2}S_{HV}S_{VV}^* \\		
+ S_{VV}S_{HH}^*		& \sqrt{2}S_{VV}S_{HV}^*	& S_{VV}S_{VV}^*
+\end{array}
+ \right) 
+}
+\end{equation}
+while the coherency matrix is defined as:
+\begin{equation}
+\small{
+C_h = \left< T_{ch} T_{ch}^{*T} \right> = \frac{1}{2}
+\left( 
+\begin{array}{c c c}
+ (S_{HH}+S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}+S_{VV})(S_{HH}-S_{VV})^*	& (S_{HH}+S_{VV})S_{HV}^* \\
+ (S_{HH}-S_{VV})(S_{HH}+S_{VV})^* 	& (S_{HH}-S_{VV})(S_{HH}-S_{VV})^* 	& (S_{HH}-S_{VV})S_{HV}^*\\		
+ 2S_{HV}(S_{HH}+S_{VV})^*		& 2S_{HV}(S_{HH}-S_{VV})^*		& S_{HV}S_{HV}^*
+\end{array}
+ \right) 
+}
+\end{equation}
+%***IVM: Hai, maybe you can use the small maths font for this matrix... I can't remember the exact syntax, but it's something simple like \small or \mathsmall or similar....
+
+(comment: check layout of the above equation in the pdf file)
+
+Evidently the two matrices are related:
+\begin{equation}
+C_h = N C_v N^T
+\end{equation}
+where
+	$N = \frac{1}{\sqrt{2}}
+\left( 
+\begin{array}{c c c}
+ 1 & 0		& 1\\
+ 1 & 0		& -1\\
+ 0 & \sqrt{2}	& 0
+\end{array}
+\right)$
+
+The off-diagonal values in both covariance and coherence matrices are normally complex numbers. 
+Equivalent matrices with all real value entries which carry the same information are called the Mueller and the Kennaugh matrix, which are to be used in forward and backward scattering alignment respectively\citep{Guissard_1994_TGRS}.
+They are defined as the matrix that relates the Stokes matrix of sent and received signals.
+\begin{equation}
+S_t^{Rx} = K S_t^{Tx}
+\end{equation}
+
+Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
+\begin{equation}
+K = 1/2 Q^* S \otimes S^* Q^{T*}
+\end{equation}
+where
+	$\otimes$ denotes the Kronecker product, and
+	$Q = 
+\left( 
+\begin{array}{c c c c}
+ 1 & 0 & 0 &  1 \\
+ 1 & 0 & 0 & -1\\
+ 0 & 1 & 1 &  0\\
+ 0 & i & i &  0
+\end{array}
+\right)$
+
+POLSAR aims to measure the target's polarimetric response.
+%Depending on the satellite instrument and processing, either Sinclair matrix or Kennaugh matrix elements are provided.
+Typically, the radar transmitter will separately send different horizontal and vertical polarized waves, and measure the response also in horizontal and vertical polarization directions.
+The full polarimetric data, will then have four channels, i.e. $\{ S_{HH}, S_{VV}, S_{HV}, S_{VH} \}$. 
+The four channel, or quad-pol data, is considered full polarimetric data since it allows one to synthesize the target's response for any given pair of transmitted and received polarization.
+Such a process is called polarization synthesis.
+The formula is given as:
+\begin{equation}
+I^{Rx} = 
+\left( 
+\begin{array}{c }
+ 1 \\
+ \cos(2\chi^{Rx}) \cos(2\Psi^{Rx}) \\
+ \cos(2\chi^{Rx}) \sin(2\Psi^{Rx}) \\
+ \sin(2\chi^{Rx}) 
+\end{array}
+\right)^T
+K
+\left( 
+\begin{array}{c }
+ 1 \\
+ \cos(2\chi^{Tx}) \cos(2\Psi^{Tx}) \\
+ \cos(2\chi^{Tx}) \sin(2\Psi^{Tx}) \\
+ \sin(2\chi^{Tx}) 
+\end{array}
+\right)
+\end{equation}
+where $I^{Rx}$ is the intensity of the target's response in a given combination of transmitted and received polarizations.
+
+In a full polarimetric implementation, an alternate pulsing scheme is normally used to share a single time slot for transmitting two different polarizations' pulses.
+In partial polarimetry modes only a single polarization is sent.
+Since the transmitting time-slot no longer needs to be shared in the partial polarimetry modes, higher operating(?) frequency become possible which leads to better (almost double) resolution or coverage.
+Clearly in such cases, only two out of four data channels is available, i.e. either $\{S_{HH},S_{HV}\}$ or $\{S_{VH},S_{VV}\}$.
+%The limitation in payload is expected to be around for years to come, with new polarimetric projects being planned by various space agencies.
+This trade-off is based on limitations of physics, and hence is likely to be around for years to come.
+
 \subsubsection{The Polarization Basis Transformation}
@@
 Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
-\begin{equation*}
+\begin{equation}
 \left( 
@@
 \right) 
-\end{equation*}
+\end{equation}
 The representation of a wave, however, depends on the choice of orthogonal reference frame basis.
@@
 \end{array}
-\right)$ê
+\right)$¬ê
 .
 The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
-\begin{equation*}
+\begin{equation}
 \left(
@@
 \right)
-\end{equation*}
-
-Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
-\begin{equation*}
+\end{equation}
+
+Boerner \citep{Boerner_1991_ProcsIEEE} has given $U_2$ as:
+\begin{equation}
 U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
@@
 \right)
-\end{equation*}
+\end{equation}
 where
@@
 	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
-	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.
-
-In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
-\begin{equation*}
+	and is required (which one?) for the determination of the initial phase of the Jones vector in the new reference basis.
+
+(comment: the above senetence is not clear, are you referring to the ratio or the phase reference, or both?)
+
+In the same vein, Ferro-Famil, 2000 gives%****IVM pls change this to a proper \citep{}
+\begin{equation}
 U_2 = \left(
@@
 \right)    
-\end{equation*}
+\end{equation}
 
@@
 it is then trivial to show that:
-\begin{equation*}
+\begin{equation}
 S_{xy} = U_2 S_{hv} U_2^T
-\end{equation*}
+\end{equation}
 
@@
 Using the result above, we then have:
-\begin{equation*}
+\begin{equation}
 S_{xx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\end{equation}
+\begin{equation}
 S_{xy} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\end{equation}
+\begin{equation}
 S_{yx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\end{equation}
+\begin{equation}
 S_{yy} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
+\end{equation}
 
 In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
-\begin{equation*}
+\begin{equation}
 S_{xx} = \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
-\begin{equation*}
+\end{equation}
+\begin{equation}
 S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
@@
 \right)
-\end{equation*}
-
-The results here, together with Stokes Vector's formula, can be used to prove the following identity,
-  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
-\begin{equation*}
+\end{equation}
+
+The results here, together with Stokes Vector's formula, can be used to prove the following identity, which form the basis of the approach used throughout this thesis:
+\begin{equation}
 S_t = 
@@
 \right)
-\end{equation*}
+\end{equation}
 where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.
@@
 
-%In practice, discrimination measures are not the only way to carry out classification tasks in POLSAR.
-%Another common approach is to use POLSAR observables identified by different target decomposition theorems.
-Different target decomposition theorems have identified many possible scalar observables for the complex POLSAR data.
-In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes are evaluated.
+In practice, discrimination measures are not the only way to carry out classification tasks in POLSAR.
+Another common approach is to use POLSAR observables identified by different target decomposition theorems.
+In \citep{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables for classification purposes are evaluated.
 While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
@@
 %Instead an MLP classification approach were employed. 
-Although, to be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
+To be fair, these observables are identified to describe a decomposed portion of the complex POLSAR data,
   and thus they were not precisely defined to be used individually for the purpose of single-handedly representing POLSAR data.
@@
 In the literature, POLSAR data is commonly represented by its covariance matrix.
-For full polarimetric SAR data (full-pol) the covariance matrix has the form of
+For full-pol (comment ñ do you mean full-polarization? If so, should write the complete word. See further below on this) the covariance matrix has the form of
 \begin{equation*}
@@
 \end{equation*}
-For partial polarimetric SAR data (part-pol), it reduces to either of the two following equations:
+For part-pol(comment - also here may be you want to explains thesesterm first befpore using it in the text??), it reduces to either (??comment- there is no ëorí in the following equation ñ do yo mean either of the two following equations, or both ñ then no ëeitherí?):
 \begin{equation*}
@@
 with $\phi=arg(\rho)$ is the phase difference angle.
-In $C_{2v}$ and $C_{2h}$ that are commonly used in optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
+In $C_{2v} and C_{2h}$ that are commonly used in optical physics, $|\rho_v|,|\rho_h|$ are insignificant,
   and $\phi_v,\phi_h$ are very random, due to little correlation existing between orthogonal polarizations in monochromatic EM waves.
@@
 \begin{enumerate}
-\item the polarization ellipse parameters \cite{Barakat_1985_IJOptics}: i.e.
+\item the polarization ellipse parameters \citep{Barakat_1985_IJOptics}: i.e.
   \begin{enumerate}
@@
   \end{enumerate}
-\item the Stokes parameters \cite{Eliyahu_1993_PhysRevE_2881}: i.e.
+\item the Stokes parameters \citep{Eliyahu_1993_PhysRevE_2881}: i.e.
   \begin{enumerate}
@@
   \end{enumerate}
-\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \cite{Brosseau_1995_AppliedOptics_4788}
+\item and the normalized Stokes parameters $s_i=S_i/S_0, i>0$ \citep{Brosseau_1995_AppliedOptics_4788}
 \end{enumerate}
@@
   \begin{enumerate}
-  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562,Lee_1994_TGRS_1017},
-  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
-  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
-  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
-  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \citep{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \citep{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \citep{Joughin_1994_TGRS_562,Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \citep{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \citep{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \citep{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \citep{Touzi_1996_TGRS_519}. 
   \end{enumerate}
@@
   each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766}.
+  as well as the largest eigen-value of the covariance matrix $\lambda_1$ \citep{Erten_2012_Sensors_2766}.
 While these models undoubtedly help in understanding SAR data,
@@
 
-\subsection{Existing Discrimination Measures for (POL)SAR data}
-
-The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
-\begin{align*}
-  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
-  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
-\end{align*}
-where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
- $||$ denotes absolute values
-and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR% covariance matrix
-, these dis-similarity measures are not widely used 
-  mainly due to the multiplicative nature of the noisy data.
-
-In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
-It is defined \cite{Lee_1994_IJRS_2299} as:
-\begin{equation*}
-  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation*},
-where $tr(C)$ denotes the trace of the matrix C. 
-As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
-
-Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
-\begin{align*}
-  d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
-    d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
-\end{align*}
-the Bartlett distance \cite{Kersten_2005_TGRS_519},
-  \begin{align*}
-  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
-  \end{align*}
-the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
-\begin{equation*}
-  r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
-\end{equation*}
-and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
-\begin{equation*}
-  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
-\end{equation*}
-.
-
-Closer investigation of these dis-similarity measures reveals that most are related in some ways. %to each other.
-The Bhattacharyya distance is easily shown to be related to the Barlett distance.
-At the same time the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
-  when the two data sets have the same number of looks, i.e. $L_x=L_y$.
-The close relation among the measures is further supported by the fact that
-  all of their proposing papers refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
-In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
-  which have $L_x$ and $L_y$ as the corresponding number of looks,
-  come from the same underlying stochastic process,
-the likelihood ratio statistics for POLSAR covariance matrix is considered:  
-\begin{equation*}
-  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-\end{equation*}
-
-Taking the log-transformation of the above equation, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
-\begin{equation}
-  \label{eqn:Complex Wishart Distribution Likelihood Test Statistics}
-  \caption{eqn:Complex Wishart Distribution Likelihood Test Statistics}
-  Q = \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}}  
-\end{equation}
-\begin{equation}
-  \label{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
-  \caption{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
-  \ln Q = L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| 
-\end{equation}
-
-To detect changes, a test statistic is developed based on this measure of distance.
-This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
-
 \subsection{Current Methods for SAR speckle filtering}
-
-%This section starts with a description of the stochastic nature of SAR data. (Comment: as mentioned ñ this should be at the beginning of the chapter)
-%SAR speckle filtering is then reviewed within a statistical estimation theory framework. 
-%Various different approaches to SAR speckle filtering are reviewed, 
-%	ranging from Generalized Least Squared Error algorithms
-%	%ranging from a discrete cartoon like algorithm 
-%	to the more convoluted Maximum A Posteriori (MAP) approaches.
-%	%to recent more continous multi-resolution wavelet or partial differental equations based algorithms.
+This section starts with a description of the stochastic nature of SAR data. (Comment: as mentioned ñ this should be at the beginning of the chapter)
+SAR speckle filtering is then reviewed within a statistical estimation theory framework. 
+Various different approaches to SAR speckle filtering are reviewed, 
+	ranging from Generalized Least Squared Error algorithms
+	%ranging from a discrete cartoon like algorithm 
+	to the more convoluted Maximum A Posteriori (MAP) approaches.
+	%to recent more continous multi-resolution wavelet or partial differental equations based algorithms.
 
@@
 Many reconstruction filters have been proposed, and they can be classified into two main categories: 
-	Weighted Least-Square Error de-speckling using the speckle model; 
+	minimum mean-square error (MMSE) de-speckling using the speckle model; 
 	and maximum a posteriori (MAP) de-speckling using the product model. 
-In this section, various different approaches to SAR speckle filtering are reviewed.
-%The famous Lee, Kuan, and Frost ˆÄÅé‡§èÅlters in the ˆÄÅé‡§èÅrst category provide MMSE reconstructions based on measured local statistics.
-%In the second category, diˆÄÅé‡§èÄerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.
+%The famous Lee, Kuan, and Frost Ô¨Ålters in the Ô¨Årst category provide MMSE reconstructions based on measured local statistics.
+%In the second category, diÔ¨Äerent scene distributions are used: Gaussian, Gamma, and parameter-based distributions.
 
 In the first category the speckle random process is assumed to be stationary over the whole image. 
-Then speckle models are proposed, such as the multiplicative speckle model is first approximated by a linear model.
-A class of speckle reduction filters is formulated 
+Then speckle models are proposed, such as (?)the multiplicative speckle model is first approximated by a linear model. A speckle reduction filter is formulated  (Comment: This paragraph is not clear.)
 as follows: 
 \begin{equation}
-  \label{eqn:Weighted Least-Square Error}
-  \caption{eqn:Weighted Least-Square Error}
 \hat{R}(t) = I(t) \cdot W(t) + \bar{I}(t) \cdot (1 - W(t)) 
@@
 
-For the Lee filter \cite{Lee_PAMI_1980}, the weight function is proposed to be:
-\begin{equation*}
+For the Lee filter \citep{Lee_PAMI_1980}, the weight function is proposed to be:
+\begin{equation}
 W(t) = 1 - \frac{C_u^2}{C_I^2} 
-\end{equation*}
+\end{equation}
 where
@@
 
-In the approach of the Kuan filter \cite{Kuan_1985_PAMI}, the multiplicative speckle model is first transformed into a single-dependent additive noise model, and then the MMSE criterion is applied. 
+In the approach of the Kuan filter \citep{Kuan_1985_PAMI}, the multiplicative speckle model is first transformed into a single-dependent additive noise model, and then the MMSE criterion is applied. 
 The speckle filter thus has the same form as the Lee filter but with a different weighting function 
-\begin{equation*}
+\begin{equation}
 W(t) = \frac{1 - \frac{C_u^2}{C_I^2} }{1+ C_u^2} 
-\end{equation*} 
+\end{equation} 
 The Kuan filter takes into account the dependency of noise on the signal. 
@@
 
-The Frost filter \cite{Frost_PAMI_1982} is different from the Lee and Kuan filters, where the scene reflectivity is estimated by convolving the observed image with the impulse response of the SAR system.
+The Frost filter \citep{Frost_PAMI_1982} is different from the Lee and Kuan filters, where the scene reflectivity is estimated by convolving the observed image with the impulse response of the SAR system.
 The impulse response of the SAR system is obtained by minimizing the mean square error between the observed image and the scene reflectivity model which is assumed to be an autoregressive process. 
 The filter impulse response can, after some simplification, be written as:
-\begin{equation*}
+\begin{equation}
 H(t) = K_1 e^{-K_2 C_I^2(t)}
-\end{equation*}
+\end{equation}
 where
@@
 As will be discussed at length in Chapter 4, SAR data is heteroskedastic.
-Our literature search yielded only a single article \cite{Amirmazlaghani_2009_TIP} tackling SAR data's heteroskedastic feature, suggesting a lack of appropriate attention within the research community about such characteristic and its effects.
+Our literature search yielded only a single article \citep{Amirmazlaghani_2009_TIP} tackling SAR data's heteroskedastic feature, suggesting a lack of appropriate attention within the research community about such characteristic and its effects.
 %However, the community appears to be oblivious of the fact, evidenced by the fact that we could only find very few researcher (Just a comment: it could also imply that the concept is not significantly useful)  \cite{Amirmazlaghani_2009_TIP} tackling heteroskedasticity in SAR data
-Under such conditions, Ordinary Least Square methods may not provide optimal results \cite{Woods_PAMI_1984}. 
-In fact, as is shown by Eqn. \ref{eqn:Weighted Least-Square Error}), weighted average formulae were being used.
+Under such conditions, Ordinary Least Square methods may not provide optimal results \citep{Woods_PAMI_1984}. 
+In fact, as is shown by the mathematical formula above (which one?), weighted average formulae were being used.
 This is consistent with the knowledge that, when variance of heteroskedastic data is available, weighted least squares is an optimal estimator.
-However, in SAR data, this variance is not available directly and can only be estimated. 
-Since heteroskedasticity means that this variance is dependent on the under-lying signal, thus estimating this variance is evidently as hard as estimating the un-speckled signal itself.
-%However, it will also be shown 
-% that log transformation would help to break  this circle of ambiguity.
+However, in SAR data, this variance is not available directly and can only be estimated (note the concept of variation coefficient). (comment: this is mentioned the 1st time in the text?)
+Our analysis will later show that estimating variance is as hard as estimating the un-speckled signal itself. However, it will also be shown 
+ that log transformation would help to break  this circle of ambiguity.
 
 %***IVM: Hai, to be clear, when you mention "the second approach" below, do you mean "In our second approach"??? In which case, please say so!!
-In the MAP approach, the filters assume that speckle is not stationary globally but is only stationary locally within the moving processing window.
+In the second approach, (comment: it is not clear what is the first approach, so far there seems to be many approaches discussed already) the filters assume that speckle is not stationary globally but is only stationary locally within the moving processing window.
 Such filters operate based on the MAP principle, which is given as:
-\begin{equation*}
+\begin{equation}
 f(x|z) = \frac{f(z|x) f(x)}{f(z)}
-\end{equation*}
+\end{equation}
 where
@@
 The underlying signal is found by
-\begin{equation*}
+\begin{equation}
 x = argmax \{ \log(f(z|x)) + \log(f(x))  \} 
-\end{equation*}
+\end{equation}
 
@@
 
-If a normal distribution is assumed \cite{Medeiros_1998_IAI}, then:
-\begin{equation*}
+If a normal distribution is assumed \citep{Medeiros_1998_IAI}, then:
+\begin{equation}
 f(x) = \frac{1}{\sigma_x \sqrt{2 \pi} } e^{\frac{1}{2} \left( \frac{x-\mu}{\sigma_x} \right)^2 }
-\end{equation*}
+\end{equation}
 and the underlying signal is found by solving the equation
-\begin{equation*}
+\begin{equation}
 x^4 \Gamma^2(N) - x^3 \Gamma^2(N) \mu_x + x^2 \Gamma^2(N) 2N \sigma^2_x - 2 \sigma^2_x z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If a Gamma distribution is assumed \cite{Lopes_1990_IGARSS}, then: 
-\begin{equation*}
+\end{equation}
+
+If a Gamma distribution is assumed \citep{Lopes_1990_IGARSS}, then: 
+\begin{equation}
 f(x) = \frac{\sigma_x}{\Gamma(\lambda)} (x \sigma_x )^{\lambda-1} e^{-x \sigma_x}
-\end{equation*}
+\end{equation}
 For $\lambda=1$, the Gamma distribution is identical to the exponential distribution. 
@@
 The underlying signal is found by solving the equation:
-\begin{equation*}
+\begin{equation}
 x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) (2N - \lambda + 1) - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
+\end{equation}
 
 If an exponential distribution is assumed, then:
-\begin{equation*}
+\begin{equation}
  f(x) = \sigma_x e^{-x \sigma_x}
-\end{equation*}
+\end{equation}
 and the underlying signal is found by solving the equations
-\begin{equation*}
+\begin{equation}
  x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) 2N - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
+\end{equation}
 
 If a Chi squared distribution is assumed, then:
-\begin{equation*}
+\begin{equation}
  f(x)=\frac{1}{2^{n/2} \Gamma(n/2)} x^{n/2-1} e^{(-x/2)}
-\end{equation*}
+\end{equation}
 and the true signal is found by solving the equation
-\begin{equation*}
+\begin{equation}
  x^3 \Gamma^2(N) + x^2 \Gamma^2(N) (4N-n+2) - 4 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If a log-normal distribution is assumed \cite{Medeiros_2003_IJRS}, then:
-\begin{equation*}
+\end{equation}
+
+%***IVM, the reference {Medeiros_2003_IntJRemoteSens} could not be found - I got a ? in the PDF....
+If a log-normal distribution is assumed \citep{Medeiros_2003_IntJRemoteSens}, then:
+\begin{equation}
  f(x) = \frac{1}{\sigma_x \sqrt{2 \pi}} x^{-1} e^{\frac{-1}{2 \sigma_x} (\ln(x) - \mu_x)^2}
-\end{equation*}
+\end{equation}
 and
-\begin{equation*}
+\begin{equation}
  x^2 \Gamma^2(N) (-2N \sigma^2_x - \sigma^2_x -\log(x) + \mu_x) + 2 z^2 \Gamma^2(N+1/2)=0
-\end{equation*}
+\end{equation}
 %Some of them being: Gaussian PDF, Gamma PDF, chi square, Rayleigh, beta, log-normal ...
@@
 %Clearly should such PDF being estimatable from the data it-self, that would potentially presents an good opportunity for this class of speckle filters.
-Other distributions that have been proposed include the heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation} \dots
+Other distributions that have been proposed include the heavy tailed Rayleigh distribution \citep{Sun_2006_ICVES}, Weibull distribution \citep{Nezry_1997_IGARSS}, beta distribution \citep{Nezry_1997_IGARSS}, Rician distribution \citep{Lewinski_1983_TAntennaPropagation} \dots
 Evidently, the performance of these filters are dependent on the underlying distribution of the back-scattering coefficient on the particular surface being imaged. 
-In this context, the community appears to focus on using Bayesian inference to choose the most suitable distributions \cite{Walessa_2000_TGRS}.
-One of the additive and homoskedastic SAR model's benefits is the possible hypothesis that the underlying distribution of the back scattering coefficient is estimable discussed in subsequent chapters.
-%In our approach, we hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in the log-transformed domain, as will be described later.
+In this context, the community appears to focus on using Bayesian inference to choose the most suitable distributions \citep{Walessa_2000_TGRS}.
+In our approach, we hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in the log-transformed domain, as will be described later.
 
@@
 	%recently there has been an increase publications about the applicability of 
-\begin{itemize}
-\item	wavelets \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
-\item	curvelets \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
-\item	contourlets \cite{Foucher_2006_IGARSS}, 
-\item	ridgelets \cite{Saevarsson_2004_IGARSS},
-\item	fuzzy logic \cite{Cheng_ETCS_2009}, 
-\item	anisotropic kernels \cite{DHondt_2006_TGRS}, 
-\item	and autoregressive conditional heteroskedasticity \cite{Amirmazlaghani_2009_DSPWorkshop}. 
-\end{itemize}
+	wavelets \citep{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
+	curvelets \citep{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
+	contourlets \citep{Foucher_2006_IGARSS}, 
+	ridgelets \citep{Saevarsson_2004_IGARSS},
+	fuzzy logic \citep{Cheng_ETCS_2009}, 
+	anisotropic kernels \citep{DHondt_2006_TGRS}, 
+	and autoregressive conditional heteroskedasticity \citep{Amirmazlaghani_2009_DSPWorkshop}. 
 %***IVM it might be good to make the above into an un-numbered list, I think it will look nicer!!
@@
 This variety of approaches further emphasises the importance of investigating consistent statistical properties of SAR signals.
-Not only is statistical analysis important in speckle filtering, the technique is also important for  information extraction \cite{Oliver_1991_JPhysDApplPhys}, target detection \cite{Luttrell_1986_JPhysDApplPhys} and classification \cite{Nyoungui_2002_IntlJRemoteSense}.
+Not only is statistical analysis important in speckle filtering, the technique is also important for  information extraction \citep{Oliver_1991_JPhysDApplPhys}, target detection \citep{Luttrell_1986_JPhysDApplPhys} and classification \citep{Nyoungui_2002_IntlJRemoteSense}.
+
+Because of the variaties of  speckle filtering available, it is hence crucial to have a framework for 
+	(a) modelling and simulation, which provide the ground-truth data in different scenarios of underlying distribution, and
+	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
+	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.
 
@@
 In the first systems that captured POLSAR data, multi-look processing was used as a method of choice for speckle filtering, at the cost of spatial resolution.
-Novak \cite{Novak_1990_TAES} pioneered the concept of speckle reduction, and proposed the polarimetric whitening filter (PWF) to produce a single speckle reduced intensity image. 
+Novak \citep{Novak_1990_TAES} pioneered the concept of speckle reduction, and proposed the polarimetric whitening filter (PWF) to produce a single speckle reduced intensity image. 
 The main disadvantages of the PWF filter is that polarimetric information is not well-preserved.
-Multi-look processing polarimetric results also exhibit bias and distortion \cite{Lee_2008_TGRS}.
-
-Lee \cite{Lee_1991_TGRS} proposed a new filtering algorithm which does suppress speckle for the diagonal elements, however the off-diagonal elements remain un-filtered.
-Later, Touzi et. al. \cite{Touzi_1994_TGRS} drew out the principles of speckle filtering of POLSAR data, which they summarised as:
+Multi-look processing polarimetric results also exhibit bias and distortion \citep{Lee_2008_TGRS}.
+
+Lee \citep{Lee_1991_TGRS} proposed a new filtering algorithm which does suppress speckle for the diagonal elements, however the off-diagonal elements remain un-filtered.
+Later, Touzi et. al. \citep{Touzi_1994_TGRS} drew out the principles of speckle filtering of POLSAR data, which they summarised as:
 \begin{enumerate}
@@
 
-In 1999, Lee \cite{Lee_1999_TGRS} extended his refined-Lee filters to POLSAR data, and argued that all covariance matrix elements should be filtered by the same amount to preserve polarimetric properties.
+In 1999, Lee \citep{Lee_1999_TGRS} extended his refined-Lee filters to POLSAR data, and argued that all covariance matrix elements should be filtered by the same amount to preserve polarimetric properties.
 He then proposed to apply the weighted averaging on the full covariance matrix instead of single-channel intensities values:
-\begin{equation*}
+\begin{equation}
 C_{out} = C_{avg} + w (C_{curr} - C_{avg})
-\end{equation*}
+\end{equation}
 where
@@
 The weight $w$ is computed within the edge aligned window from the total power image $y$ as:
-\begin{equation*}
+\begin{equation}
 w = \frac{\sigma^2_y - \mu^2_y \sigma^2_v}{\sigma^2_y - \sigma^2_y \sigma^2_n}
-\end{equation*}
+\end{equation}
 where 
@@
 Further attempts have been made towards statistically modelling the off-diagonal elements but the application of these results for speckle suppression of off-diagonal element have not been conclusive.
-For instance Martinez et. al.\cite{Lopez_2008_TGRS} proposed a model based polarimetric filter.
+For instance Martinez et. al.\citep{Lopez_2008_TGRS} proposed a model based polarimetric filter.
+(comment: there is no need to quote the year as we are not writing historical events, but rather, should focuse on state of the art techniques)
 They first proposed to model $S_hS_v^*$ as having both additive and multiplicative components:
-\begin{equation*}
+\begin{equation}
 S_pS_q^* = \psi |\rho | e^{i \theta} + \psi \bar{z}_n N_c (1-n_m) e^{i \theta} + \psi (n_{ar} + i n_{ai}) 
-\end{equation*}
+\end{equation}
 where
@@
 
-Another different approach is proposed bu Lee \cite{Lee_CRCPress_2009}  to model $S_hS_v^*$.
+Another different approach is proposed bu Lee \citep{Lee_CRCPress_2009}  to model $S_hS_v^*$.
 In this method, the phase difference is defined as:
-\begin{equation*}
+\begin{equation}
 \phi = \arg{ \left( S_pS_q^* \right) }
-\end{equation*}
+\end{equation}
 and the PDF for the phase difference as:
-\begin{equation*}
+\begin{equation}
 pdf(\phi) = \frac{\Gamma(3/2) (1-|\rho|^2) \beta}{2 \sqrt{\pi} \Gamma(1) (1-\beta^2)} + \frac{(1-|\rho|^2)}{2 \pi} F_{1,2}(1,1,1/2,\beta^2)
-\end{equation*}
+\end{equation}
 where
@@
 The normalized magnitude, is defined as:
-\begin{equation*}
+\begin{equation}
 \xi = \frac{E \left( S_pS_q^* \right)}{\sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }}
-\end{equation*}
+\end{equation}
 and the PDF is found to be:
-\begin{equation*}
+\begin{equation}
 pdf(\xi) = \frac{4\xi}{\Gamma(1)(1-|\rho|^2)} I_0 \left( \frac{2 |\rho| \xi}{1-|\rho|^2} \right) K_0 \left(  \frac{2 \xi}{1-|\rho|^2} \right)
-\end{equation*}
+\end{equation}
 	$I_0$ and $K_0$ are modified Bessel functions.
+
+(comment:It is necessary to quote these detail if they are not really useful, and presumably wonít be refer to again in the text?
+We should try to summarise the essence and shorten the content as mush as possible by not including detail that is not relevant anymore)
 
@@
 	this does not allow for easy speckle filtering as the model is too complex and 
-	the complex correlation coefficient $\rho$ is not easily estimated \cite{Lee_CRCPress_2009}
+	the complex correlation coefficient $\rho$ is not easily estimated \citep{Lee_CRCPress_2009}
 
@@
 Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogenous neighbour.
-The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
+The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \citep{Vasile_TGRS_2006}.
 %J.S. Lee is also very active in POLSAR speckle filtering.
@@
 Similar to Lee's previous work, a simple weighted average filtering is applied on both diagonal and off-diagonal elements.
-Vasile, in 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \cite{Vasile_2010_TGRS}.
+Vasile, in 2010, published a complicated spherically invariant random vector estimation scheme to estimate the underlying target POLSAR signature \citep{Vasile_2010_TGRS}.
 While polarimetric information is estimated independently from the power span, its output results no longer follow established Wishart distribution.
@@
 %We will discuss our approach in the next section.
-In summary, while off-diagonal elements, which carry phase information, are known to be important in interpreting POLSAR data \cite{Rodionova_2009_ESASP}, their estimation and filtering is under-developed in the current research literature.
-%We will discuss our approach ??) based on polarization basis transformation in the next section.
+In summary, while off-diagonal elements, which carry phase information, are known to be important in interpreting POLSAR data \citep{Rodionova_2009_ESASP}, their estimation and filtering is under-developed in the current research literature.
+We will discuss our approach ??) based on polarization basis transformation in the next section.
 (comment: This chapter is about background.
@@
 
-\subsection{Current Methods to Evaluate SAR Speckle Filters}
-
-Because of the variaties of  speckle filtering available, it is hence crucial to have a framework for 
-	(a) modelling and simulation, which provide the ground-truth data in different scenarios of underlying distribution, and
-	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
-	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.
-
-This section reviews the published literature for the different techniques used to evaluate SAR speckle filters.
-%In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
-%Furthermore, the application of any speckle filter in a SAR processing framework
-%   should enable an improvement in the measurement, 
-%	detection or classification of the underlying radiometric features.
-% (??? I suggest move these sections to Chapter 3 or 4, if they are really in this Chapter), 
-%.
-% (The above is your proposal. It should not appear here in Chpater 2)
-The overall requirement of speckle filtering can be broken down into two smaller requirements.
-On the one hand, speckle filters should preserve the underlying radiometric signal (namely the radiometric 
-	preservation requirement).
-On the other hand, they should reduce the variation of the additive noise (i.e. speckle suppression power).
-One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
-	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech,Medeiros_2003_IJRS}.
-A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
-%For homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
-%	in the original domain the ``standard'' filters (boxcar, Lee \cite{Lee_PAMI_1980}, 
-%	Kuan \cite{Kuan_1985_PAMI}, Frost\cite{Frost_PAMI_1982}, 
-%	MAP\cite{Lopes_IGARSS_1990}) and the enhanced version \cite{Lopes_TGRS_1990} can achieve negligible bias. 
+\subsection{Current Methods to Evaluate (POL)SAR Speckle Filters}
+(comment: this section just ësuddenly pop upí here in Chapter 2.
+You should first describe how it is related to what has been mentioned so far.
+It is also not mentioned in the beginning of Chapter 2.
+Although I know what it is about and the reason behind it)
+It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
+	homogeneous and heterogeneous region evaluation.
+Across homogeneous areas, speckle filters are expected to be estimated with negligible radiometric bias.
+As such, evaluating speckle filters over homogeneous areas has traditionally focussed on evaluating the variation of the estimators'
+	output (a.k.a the speckle suppression power).
+In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
+	due in part to the following difficulties.
+The first is that of determining an absolute ground-truth against which quantitative criteria can be measured.
+The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
+	to be measured and compared.
+
+(comment: This is the problem statement of the Thesis, so it should have appeared earlier, somewhere in Chapter 1.)
+
+In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
+Furthermore, the application of any speckle filter in a SAR processing framework
+   should enable an improvement in the measurement, 
+	detection or classification of the underlying radiometric features.
+ (??? I suggest move these sections to Chapter 3 or 4, if they are really in this Chapter), 
+.
+ (The above is your proposal. It should not appear here in Chpater 2)One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
+	original value $r = X_{est} / X_{org}$ \citep{Oliver_2004_SciTech,Medeiros_2003_IJRS}.
+A somewhat similar metric is used in \citet{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
+
+For homogeneous scenes, Shi et al. \citep{Shi_IGARSS_1994} found that 
+	in the original domain the ``standard'' filters (boxcar, Lee \citep{Lee_PAMI_1980}, 
+	Kuan \citep{Kuan_1985_PAMI}, Frost\citep{Frost_PAMI_1982}, 
+	MAP\citep{Lopes_IGARSS_1990}) and the enhanced version \citep{Lopes_TGRS_1990} can achieve negligible bias. 
 %In this paper, %****IVM you need to search for the word "paper" in case you have more of these
+
 Several metrics have also been developed to evaluate speckle suppression power.
@@
 $ENL=avg(I)^2/var(I)$
-that was proposed by Lee \cite{Lee_1981_CGIP}.
-Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
+that was proposed by Lee \citep{Lee_1981_CGIP}.
+Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \citep{Gagnon_SPIEProc_1997} 
 %****IVM: the section reference below is not found (is displayed as ??)
-
-It is customary to divide the performance evaluation of speckle filters into two distinct classes of 
-	homogeneous and heterogeneous region evaluation.
-Across homogeneous areas, speckle filters are expected to be estimated with negligible radiometric bias.
-As such, evaluating speckle filters over homogeneous areas has traditionally focused on evaluating the variation of the estimators'
-	output (a.k.a the speckle suppression power).
-%In contrast, the methodologies used to evaluate speckle filters over heterogeneous areas are much more complicated, 
-%	due in part to the following difficulties.
-%The first obstacle is to determine an absolute ground-truth against which quantitative criteria can be measured.
-%The second challenge is to then define a quantifiable metric that allows the performance of different speckle filters 
-%	to be measured and compared.
 
@@
 And hence, the need for speckle filter estimation is warranted.
-
-Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above. 
+(comment: The above paragrapg should be moved to the beginning of this section to explain why there is a need to evaluate the speckle filter)
+
+Without ground truth, one way to evaluate radiometric preservation of filters is to compute the ratio image mentioned above (???). 
 Under a multiplicative model, the ratio image is expected to comprise solely of
@@
 However, when displaying such images for visual evaluation, the ratios that are smaller than unity are much 
-harder to distinguish than those that are bigger \cite{Medeiros_2003_IJRS}.
+harder to distinguish than those that are bigger \citep{Medeiros_2003_IJRS}.
+
+Another way to evaluate speckle filters is by comparing the feature preservation characteristics 
+of the original noised data and those of the filtered image. 
+When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
+Evaluation would then determine how closely related the two feature maps are.
+
+Various methods may be applied to extract features (comment: explain first why this is relevant to speckle filter evaluation??); examples of those that have been used are the 
+	Hough Transform \citep{Medeiros_2003_IJRS}, Robert gradient edge detector \citep{Gagnon_SPIEProc_1997} 
+	and edge map \citep{Frost_PAMI_1982}.
+While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
+of these methodologies.
+This is because feature extraction algorithms are only approximations,
+	whose accuracy is not only dependent upon the characteristics of the original image 
+		but also heavily affected by 
+		the inherent noise.
+Unfortunately, speckle filters invariably alter the noise characteristics.
+Thus, without a clear understanding of these dependencies and no absolute ground truth, 
+	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
+	how to interpret the results, especially in terms of accuracy.
 
@@
 
-Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
-However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
-Wang \cite{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
-Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
-	subjective in nature.
-
 Another approach is to apply a universal mean squared error criteria into the context of SAR data. 
@@
 	the use of MSE is not straightforward. 
-Thus Gagnon \cite{Gagnon_SPIEProc_1997} suggested the use of
+Thus Gagnon \citep{Gagnon_SPIEProc_1997} suggested the use of
   the ratio between the expected mean of the signal and the RMSE of the removed noise. 
@@
 
-In general, any metric to evaluate speckle filters should be relevant to the normal usage of such filters.
-Furthermore, the application of any speckle filter in a SAR processing framework
-   should enable an improvement in the measurement, 
-	detection or classification of the underlying radiometric features.
-Thus, another way to evaluate speckle filters is by comparing the feature preservation characteristics 
-of the original noised data and those of the filtered image.
-This can be applied not only whether or not the ground-truth is available precisely.
-When there is no ground-truth given, the feature are estimated in both the original noised and the filtered images.
-Evaluation would then determine how closely related the two feature maps are.
-
-Various methods may be applied to extract features; examples of those that have been used are the 
-	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
-	and edge map \cite{Frost_PAMI_1982}.
-While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
-of these methodologies.
-This is because feature extraction algorithms are only approximations,
-	whose accuracy is not only dependent upon the characteristics of the original image 
-		but also heavily affected by 
-		the inherent noise.
-Unfortunately, speckle filters invariably alter the noise characteristics.
-Thus, without a clear understanding of these dependencies and no absolute ground truth, 
-	using feature extraction algorithms to evaluate speckle filters would leave serious questions on 
-	how to interpret the results, especially in terms of accuracy.
-As such, the problem of establishing an single evaluation criteria to evaluate the overall performance of speckle filters remains open for improvement.
+Overall, many different methods and metrics have been proposed to evaluate various aspects of speckle filters. 
+However it is clearly advantageous to have a single metric that is able to judge if one filter is better than another. 
+Wang \citep{Wang_2005_MIPR} proposed using fuzzy membership to weight opinions of an expert panel. 
+Although this provides a potential solution, we consider it to be tedious in implementation, fuzzy in concept and 
+	subjective in nature.
 
@@
 %In this paper, 
-%	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
+	Section \ref{sec:log_transform} provides a brief discussion on logarithmic transformation for SAR images.
 %****IVM:  Hai, please be consistent in using "Section" or "section".
@@
 
-%\subsection{Existing Discrimination Measures for (POL)SAR data}
-%
-%(comment: you need to have a lead-in paragraph to link this section from the other)
-%To detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
-%  which have $L_x$ and $L_y$ as the corresponding number of looks,
-%  come from the same underlying stochastic process,
-%Conradsen \cite{Conradsen_2003_TGRS_4} considered the following POLSAR statistics
-%\begin{equation*}
-%  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-%\end{equation*}
-%
-%Taking the log-transformation of the above statistics, and noting that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then we have;
-%\begin{eqnarray*}
-%  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
-%  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
-%\end{eqnarray*}
-%
-%Since both $Z_x$ and $Z_y$ follow complex Wishart distributions with $L_x$ and $L_y$ degrees of freedom,
-%  $Z_x+Z_y$ also follows the complex Wishart distribution with $L_x + L_y$ degrees of freedom.
-%In view of the models denoted later in Eqn. \ref{eqn:log_determinant_distribution},   
-%%***IVM: Hai, can you please check this equation reference (it comes out as eqn. 4.9 which I don't have in this document)
-%  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
-%  but the whole statistical distribution for it can be simulated as well:
-%\begin{eqnarray*}
-%%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
-%%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
-%  \ln{Q} &\sim&  q + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-%  Q &\sim& e^q \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
-%\end{eqnarray*}
-%where $q = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-%
-%In the special case of $L_x = L_y$, the Conradsen statistics become
-%$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
-%%Our approach suggest a slightly simpler statistics which probably will work just as well: the contrast
-%The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should, under exactly the same assumptions, provides another consistent and equivalent approach,
-%  with probably simpler conceptual model and computational derivations. 
-%%a slightly simpler statistics.
-%The detailed application of this for the task of edge-detection however is outside the scope of this thesis.%paper.
+\subsection{Existing Discrimination Measures for (POL)SAR data}
+
+(comment: you need to have a lead-in paragraph to link this section from the other)
+To detect if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  which have $L_x$ and $L_y$ as the corresponding number of looks,
+  come from the same underlying stochastic process,
+Conradsen \citep{Conradsen_2003_TGRS_4} considered the following POLSAR statistics
+\begin{equation}
+  Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
+\end{equation}
+
+Taking the log-transformation of the above statistics, and noting that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then we have;
+\begin{eqnarray}
+  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \nonumber \\
+  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \nonumber
+\end{eqnarray}
+
+Since both $Z_x$ and $Z_y$ follow complex Wishart distributions with $L_x$ and $L_y$ degrees of freedom,
+  $Z_x+Z_y$ also follows the complex Wishart distribution with $L_x + L_y$ degrees of freedom.
+In view of the models denoted in Eqn. \ref{eqn:log_determinant_distribution},   
+%***IVM: Hai, can you please check this equation reference (it comes out as eqn. 4.9 which I don't have in this document)
+  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+  but the whole statistical distribution for it can be simulated as well:
+\begin{eqnarray}
+%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+  \ln{Q} &\sim&  q + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim& e^q \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}  
+\end{eqnarray}
+where $q = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+In the special case of $L_x = L_y$, the Conradsen statistics become
+$\ln Q = \ln |C_{vx}| + \ln |C_{vy}| - 2 |\ln C_{vxy}|$.
+%Our approach suggest a slightly simpler statistics which probably will work just as well: the contrast
+The contrast model which is written as $\mathbb{C} = \ln C_{vx} - \ln C_{vy}$ and presented above should, under exactly the same assumptions, provides another consistent and equivalent approach,
+  with probably simpler conceptual model and computational derivations. 
+%a slightly simpler statistics.
+The detailed application of this for the task of edge-detection however is outside the scope of this thesis.%paper.
 (Commet: I suggest this section to be removed since it would not be referred to in the remainig of the thesis)
-%
-%%\subsection{The need for Scalar Representative and Homoskedastic Models}
-%%	We will show our originality and significance here!
-%
-%%This section surveys recent developments in the research landscape. 
-%%First, the stochastic nature of SAR speckle phenomena is explained. 
-%%Then, the topic of SAR speckle is reviewed from the perspective of statistical estimation theory. 
-%%An opportunity for contribution in proposing a stochastic simulation and evaluation framework is identified. 
-%%Next, the applications of such a framework into the problem of POLSAR speckle filtering is described. 
-%%Recently, the practicality of Partial Polarimetry has been noticed and studied. 
-%%The need for reconstruction of Full Polarimetric signatures is highlighted and the possible application of the proposed framework is described. 
-%%Last but not least will be an illustration on the applicability of such a framework to the topic of target detection and classification.
-%
-%%\subsection{POLSAR speckle filter}
-%        
-%	%\section{The Need for Scalar Consistent Measures of Distance}
-%
-%	%\section{Research Framework: Originality and Significance}
+
+%\subsection{The need for Scalar Representative and Homoskedastic Models}
+%	We will show our originality and significance here!
+
+%This section surveys recent developments in the research landscape. 
+%First, the stochastic nature of SAR speckle phenomena is explained. 
+%Then, the topic of SAR speckle is reviewed from the perspective of statistical estimation theory. 
+%An opportunity for contribution in proposing a stochastic simulation and evaluation framework is identified. 
+%Next, the applications of such a framework into the problem of POLSAR speckle filtering is described. 
+%Recently, the practicality of Partial Polarimetry has been noticed and studied. 
+%The need for reconstruction of Full Polarimetric signatures is highlighted and the possible application of the proposed framework is described. 
+%Last but not least will be an illustration on the applicability of such a framework to the topic of target detection and classification.
+
+%\subsection{POLSAR speckle filter}
+
+	%\section{The Need for Scalar Consistent Measures of Distance}
+
+	%\section{Research Framework: Originality and Significance}
 
@@
   also illustrates the different published approaches to address the grand challenge of modelling, processing and understanding this type of data.
+(Comment: This ësummaryí section is too long.
+It is to SUMMARIZE the essence of the various points in this chapter, not to described what is to be done in the Thesis.
+Summary should be one or two paragraph the most.)
 Specifically it shows that
@@
   which includes statistical modelling of the data, estimator development and the estimator performance evaluation.
-Specifically, it showed that when the sense of subtractive distance is not consistent for SAR data, the ratio is proposed as its discrimination measure \cite{Rignot_1993_TGRS_896}.
+Specifically, it showed that when the sense of subtractive distance is not consistent for SAR data, the ratio is proposed as its discrimination measure \citep{Rignot_1993_TGRS_896}.
 It also showed that while the MMSE criteria is not very suitable to evaluate SAR speckle filters, other criteria such as radiometric preservation and speckle suppression power evaluation are employed.
@@
 
-In the next chapters, theoretical models are built to form the foundation required to systematically tackle these issues.
+In the next chapter, theoretical models are built to form the foundations required to systematically tackle these issues.
+
+(Comment: you would need to review the various sections in this chapter, and re-arrange them in a more coherent flow, starting with the basic of SAR and POLSAR, and then bring up the various relevant details.
+
+If you have a chance to talk to Brain, may be ask him to share with you his introductory chapter, which is written in a very clear manner that explain the issues)

### 2013-07-24 paper_dev/article_pp_ivm.tex
updated for Ian to change

--- 2013-05-18 paper_dev/article_pp.tex
@@
+%\documentclass[a4paper,10pt]{article}
 %ifdef FINAL
@@
 
+%\nonstopmode
+
 %opening
 \title{
+  %Consistent and Homoskedastic Measures of Distance for Heteroskedastic POLSAR Data
   Scalar and Representative Models for Polarimetric SAR Data
@@
 %\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
-%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
+%	their initial discussions and for providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
 \thanks{Manuscript received ?, 2013; revised ?.}}
@@
   they are shown to exactly match the traditional statistical models for SAR intensity.
+%The representative power of these multi-dimensional models is illustrated
+%  when they are collapsed into the special case of one-dimensional,
+%  the special-case statistical models then match perfectly with the traditionally used statistical models for SAR intensity.
+%These theoretical models, together with their derived discrimination measures, are then validated against practically captured POLSAR data.
 The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
@@
 To illstrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+%For example, similar to the way that the intensity ratio is routinely used to evaluate SAR speckle filters,
+%  this paper describes how the determinant-ratio and its additive version, contrast, can be used to evaluate POLSAR speckle filters.
+%  While statistical models are important in understanding the stochastic nature of Polarimetric SAR (POLSAR),
+%  scalar discrimination measures are routinely used in processing this multi-dimensional data.
+%  Ideally speaking, the latter should be drived from the former.
+%  As far as we know, however, it has not exactly been so for the case of POLSAR.
+%  In this paper, a couple of statistical models for the determinant of the POLSAR covariance matrix and its log-transformed derivations are proposed.
+%  These scalar models for the determinant of the POLSAR covariance matrix are shown to be respresentative
+%    since this observable is neatly transformed into the traditional SAR intensity
+%    when the generic multi-dimensional polarimetry is collapsed into the case of one-dimensional SAR. %case of traditional SAR data.
+%  Similar to SAR, the generic model for POLSAR is also shown to be multiplicative and heteroskedastic in the original domain 
+%    and the logarithmic transformation converts this into a more familiar additve and homoskedastic model.
+%  Moreover, the scalar property of these statistical models lead to the derivation of several statistical discrimination measures. %homoskedastic measures of distance.
+%  All of these statistical models are validated on real-life captured data
+%    and they are shown to be applicable even when the theoretical ``independent samples'' assumption is violated in practice.
+%  The combination of scalar, additive and homoskedastic properties of the derived statistical models bring about a couple of benefits, which are also described in this paper.
+%  First, compared to the original multiplicative domain, %dis-criminative measure of ratio,
+%    the additive log-transformed fit more naturally with the linear nature of digital imagery.
+%  Second, since the Gauss-Markov theorem is again applicable in the homoskedastic log-transformed domain,
+%    the use of Mean Squared Error (MSE) as an reliable objective function for POLSAR speckle filters is briefly explored.
 \end{abstract}
@@
 \section{Introduction}
+%\section{POLSAR data: statistical analysis and logarithmic transformation}
 
@@
 SAR technology has since extended in a few directions, one of which is polarimetric SAR (POLSAR).
-POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
-  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
-
+POLSAR incorporates multiple channels to represent the natural polarization properties of reflected and sensed Electro-Magnetic (EM) waves, unlike the single dimension of SAR intensity.
+
+%In the past decades, the exponential growth in computational power has made the once overly-excessive computationaly-demanding SAR technology now become a feasible and preferred earth observation solution.
+%As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is the polarimetric SAR.
+%POLSAR is the natural extension from SAR exploiting the natural polarization property of Electro-Magnetic (EM) waves.
+%Similar to the extension from black-and-white images to color photography, the polarimetric extension brought about the multi-channels POLSAR data as compared to the traditional one-channel SAR data.
+
+%With (POL)SAR data becomes cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. %it is of great important to understand the data.
+%The complex data, however is stochastic by nature, due to the interference phenomena of EM waves. %, SAR measurements are stochastic by nature.
+%Under this condition, it is very important to understand the statistical models for (POL)SAR data.
+
+%While the statistical models for homogeneous areas of one-dimensional SAR data have been developed,
+%  in extending the model toward heterogeneous images, the impact of heteroskedasticity has virtually been ignored.
+%Specifically the concept of distance as a measure of dis-similarity is seriously flawed, as it is widely known that ratio offers a better discrimination measure TODOCITE.
+%This thesis starts off by proposing the logarithmic transformation which is shown converting the SAR data into an homoskedastic model.
+%From this log-transformed model, a few consistent measures of distance is proposed. 
+%in a sense the distance concept is re-emerged, as the log-transformation converts the widely used ratio into standard subtraction, and thus distance.
 While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
@@
 On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.
+
+%While statistical models are important in understanding the stochastic nature of both SAR and POLSAR,
+%  in extending our understanding towards multi-dimensional POLSAR data, an important issue needs to be addressed.
+%The trouble that the high dimensional data bring about is that there exists not one, as the intensity in the one-channel SAR, but many observables quantities in multi-channel POLSAR.
+%While different statistical models have been developed for different POLSAR observables,
+%  for a statistical model to be useful, scalar discrimination measures need to be derived from it.
+%Thus practical application for POLSAR data processing requires the dis-similarity measure to be scalar, consistent and preferably homoskedastic on one hand.
+%On the other hand, the observable quantity being modelled needs to be naturally representative for the high dimensional POLSAR data.
+
+%In this paper, the determinant of the POLSAR covariance matrix is proposed as an observable quantity to study.
+%Statistical models for this heteroskedastic POLSAR determinant and homoskedastic log-determinant, together with several discrimination measures, are then derived in section \ref{sec:theoretical_model}.
+%The representative power of this observable is demonstrated in section \ref{sec:sar_special_case_of_polsar},
+%  where the multi-dimensional POLSAR data is collapsed into the traditional one-dimensional SAR scenario.
+%Under this transformation, the determinant of the POLSAR covariance matrix is converted into the standard SAR intensity
+%Section \ref{sec:sar_special_case_of_polsar} describes how
+%  which puts the standard statistical models for SAR to be within the natural coverage of this generic models for POLSAR.
+%All of these theoretical developments are then validated against real-life practical data in section  \ref{sec:polsar_models_validation}.
+%Finally section \ref{sec:discussion_conclusion} concludes the paper by briefly describing how an existing SAR data processing technique can be adapted for POLSAR data.
 
@@
 
+%Besides being theoretically comprehensive, 
+%  the models are also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+%shows how the statistical models for POLSAR can be considered as the generic
+%And since POLSAR can be viewed as a multi-dimensional extension of SAR, the paper
+
+%There are a few benefits of using the homoskedastic measures of distance for POLSAR.
+%Firstly, compared to the multiplicative dis-similarity measure of ratio, these additive measures of distance fit more naturally with the linear scale nature of digital imagery.
+%Secondly, within the homoskedastic log-transformed domain, where the distance concept as well as the Gauss Markov theorem is again applicable, the universal MSE deserves to be reviewed as a reliable objective function / criteria for (POL)SAR estimators.
+%This may open up a number of different research directions for future studies of (POL)SAR.
+%As example demonstrations of how these models and distance measures can be used, a novel clustering algorithm, a new speckle filter and various procedures in using MSE to evaluate speckle filters are also presented as part of the thesis.
+
+%Specifically, the rest of this paper is structured as follows.
+%After the related work in literature is critically reviewed in Section \ref{sec:lit_review},
+%  Section \ref{sec:theoretical_model} presents the theoretical models for both partial and full polarimetric SAR and their derived discrimination measures.
+%The representative power of the scalar models are illuminated in Section \ref{sec:sar_special_case_of_polsar},
+%  which details how the proposed models for the multi-variate POLSAR also includes the well-known models for the traditional SAR as its special univariate case.
+%can be used to derive the well-known models for the univariate SAR data as its special case.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+%To demonstrate the application of these scalar and representative models, 
+%  Section \ref{sec:evaluating_polsar_filters} explores how they can be used to evaluate POLSAR speckle filters.   
+%In the end, Section \ref{sec:discussion_conclusion} provides the final conclusion of the paper.
+%critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
+%In this paper, the above results are exploited in the context of POLSAR data processing.
+In particular, a few scalar, consistent and homoskedastic measures of distance are proposed.
+The paper is structured as follows:
+%  after the preceding introduction to the basics of POLSAR statistical analysis,
+%  the second section briefly reviews related work in published literature.
+%Section \ref{sec:polsar_heterosked_model_and_log_transform} presents the theoretical models together with conclusive evidence for two related points.
+%The first point is that: POLSAR data is multiplicative and heteroskedastic in its original domain.
+%And the second conclusion being: log-transformation converts it into an additive and homoskedastic model.
+%Consequently a few consistent measures of distance are presented in section \ref{sec:distance_measure}.
+%After the model is presented for both partial and full polarimetric SAR data,
+%  section \ref{sec:sar_special_case_of_polsar} discusses
+%    how the proposed models for the multi-variate POLSAR can be used to derive the well-known models for the univariate SAR data as its special case.
+%Besides being theoretically comprehensive, 
+%  the model is also shown, in Section \ref{sec:polsar_models_validation}, %in section \ref{sec:improve_the_match_bw_theory_practice},
+%  to be robust in handling practical data. % imperfection that violate conventional assumptions. 
+%To demonstrate the application of the consistent and homoskedastic dis-similarity measures, 
+%  Section \ref{sec:evaluating_polsar_filters} explores how they are used for evaluating POLSAR speckle filters.   
+%Finally, Section \ref{sec:discussion_conclusion} critically reviews and discusses related literature  
+%  before the paper is concluded in Section \ref{sec:conclusion}.
+
 \section{Related Work in Literature}
@@
 
+%it should be noted that while the original proposed work \cite{Conradsen_2003_TGRS_4}
+%  for the test requires an exact distribution, only an asymptotic distribution is used.  
+%This section critically review the related work in published literature.
+%Specifically, the first sub-section reviews various scalar statistical models for different POLSAR observables.
+%Its purpose is to show that none of the proposed models have led to statistically consistent discrimination measures.
+%%shows that while many
+%The second sub-section strengthen this findings by reviewing many different discrimination measures that have been proposed for POLSAR data.
+%It shows that almost all of them depends on the likelihood statistical test for complex Wishart distribution.
+%Unfortunately, in the original proposed work \cite{Conradsen_2003_TGRS_4} for the test,
+%  while an exact distribution is to be expected, only an asymptotic distribution was given.
+
 \subsection{Investigated Scalar Observables for POLSAR Data and their Statistical Models}
@@
 
+%Of course, discrimination measures are not the only way to carry out classification tasks in POLSAR.
+%Another common approach is to carry out classification using POLSAR observables identified by different target decomposition theorems.
 Different target decomposition theorems have identified many possible scalar observables for complex POLSAR data.
@@
 Furthermore, at its conclusion, the paper indicated that it is impossible to identify a single best representation.
+  %``it is impossible to indentify the best one''
+  %as these ``representations ... do not show a precise trend''.
+%Instead an MLP classification approach were employed. 
 Although, to be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
   rather than providing a single unified representation of the POLSAR data.
+%and thus they are not to be used individually for the purpose of single-handedly representing POLSAR data.
 
@@
 
-More recently, statistical models for
+More recently, %other studies has offered
+  %\cite{Lopez-Martinez_2003_TGRS_2232} and \cite{Erten_2012_Sensors_2766} gives
+  statistical models for
   each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
@@
   2) being representative of the complex POLSAR data.
+%While these models undoubtedly help in understanding the SAR data,
+%  individually none of these observables has been shown to statisfy the dual criteria of
+%  1) resulting in statistically consistent discrimination measures and
+%  2) being representative of the complex POLSAR data.
+  %that they model have the power to represent the multi-demensional POLSAR covariance matrix.
 
@@
 
+%This sub-section reviews some relevant and published works relating to different measures of distance for POLSAR data. 
+%In particular, a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+%will be briefly reviewed.
+%specifically a few different matrix distances have been proposed and evaluated in recent review papers\cite{Dabboor_2013_IJRS_1492}\cite{Kersten_2005_TGRS_519}
+
 The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
+%The commonly used measure of distance for matrices are either the Euclidean or the Manhattan distance,
+%  which are defined in the following equations, respectively:
 \begin{align}
@@
   probably because of the multiplicative nature of the noisy data.
+%In the context of polsar covariance matrix, however, they are not widely used 
+%  probably because of the multiplicative nature of the data.
 
 In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
-It is defined \cite{Lee_1994_IJRS_2299} as:
+It is defined \cite{Lee_1994_IJRS_2299} as;
 \begin{equation}
@@
 
+%In comparison to these formulae, the distance measures for two covariance matrices proposed in this paper can be written as:
+%\begin{equation}
+%  d(C_x,C_y) =  \ln|C_x| - \ln|C_y| 
+%\end{equation}
+%At first glance, while the propose formula may be a lot simpler, it still operates in a similar way to others in making use of the log-determinant.
+
 Closer investigation of these dis-similarity measures reveals that most are related in some way. %to each other.
@@
   when the two data sets have the same number of looks, i.e. $L_x=L_y$.
+%It is also intuitively trivial to arrive at the conclusion that the contrast measure of distance proposed in this paper has fixed statistical behaviour, by comparing the symmetric and asymmetric versions of the refined Wishart distance, assuming that they are shown to follow fixed distributions.
 The close relation among the measures is further supported by the fact that
   all of their proposing papers referenced the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
+%Interestingly, the change detection model in \cite{Conradsen_2003_TGRS_4} also make use of determinant ratio and log determinant in its derivation.  
+%The next sub-section will illustrate how the log-determinant model presented in this paper can offer an alternative and simple derivation for the change-detection statistics.
 In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
@@
 However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
+%In this sub-section, a statistical model is developed for this measure of distance.
+%Since both $Z_x$ and $Z_y$ follow a complex Wishart distribution with $L_x$ and $L_y$ degrees of freedom,
+%  $Z_x+Z_y$ also follows the complex Wishart distribution with $(L_x + L_y)$ degrees of freedom.
+%In view of the models for $|C_v|$ and $\ln|C_v|$ developed in this paper (Eqns. \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution}),
+%  it is evident that not only the bound for $\ln Q$, or equivalently $Q$, can be derived
+%  but the whole statistical distribution for it can be simulated as well.
 
@@
 
+%As the covariance matrix is only defined on multiple data points,
+%  sample POLSAR covariance matrices are commonly presented in ``ensemble'' format.
 The sample POLSAR covariance matrix is formed as the mean of Hermitian outer product of independent single-look scattering vectors,
@@
 The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
+  %under the assumption of circular complex Gaussian distribution
+  %applicable for POLSAR data.
 Goodman \cite{Goodman_1963_AMS_178} proved
@@
   $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$.
-We will now use this result to develop the statistical models for POLSAR. %log-transformed measures of distance.
+We will now use this result to develop log-transformed measures of distance.
 %***IVM added the sentence above... **Please check it's true!!!!
@@
  Log-transformation is used to convert  the data into a more familiar additive model.
+%Log-transformation is shown converting this into a more familiar additive model.
 Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
@@
   where sample variance is fixed and thus independent of the underlying signal.
+%To keep the section flowing, the mathematical derivation is only presented here in major sketches.
+%For more detailed derivation, Appendix \ref{chap:appendix_a} should be referred to.
 Several intermediate mathematical steps are not shown here, but can be found in Appendix \ref{chap:appendix_a}.
@@
   \end{eqnarray}
+%Subsequently their means and variances can be computed from the given characteristic functions.
+%They are:
  Their means and variances can subsequently be computed from these  characteristic functions, leading to the following relationships:  
@@
 Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
+%\begin{eqnarray}
+%\end{eqnarray}
 \begin{align}
@@
 For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
+%Over a real and captured image, while the parameters $d$ and $L$ do not change for the whole image,
   the underlying $\Sigma_v$ is expected to differ from one region to the next.
@@
 
-Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
-  this section introduces the consistent sense of distance for POLSAR.
+ This section introduces the consistent sense of distance from different perspectives \cite{Le_2010_ACRS}.
 Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
@@
 
+%Also using the characteristic functions for the elementary components $\Lambda(2L)$ expressed in Eqn. \ref{eqn:log_chi_squared_characteristic_function}, 
 Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
@@
 
+%The previous section has introduced the theoretical model for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+%In this section, the model is shown to be also applicable for the 1-dimensional $d=1$ case.
+%Physically this means the multi-dimensional POLSAR dataset is collapsed into one-dimensional conventional SAR data.
+%Mathematically, the sample covariance matrix is reduced to the sample variance
+%%The prevous section has validated the use of our models for 3-dimensional $d=3$ full polarimetric and two dimensional $d=2$ partial polarimetry cases.
+%%In this section, the focus is on the case where the dimensional number is reduced to 1 $d=1$.
+%%Physically this means the multi-dimensional POLSAR dataset is collapsed into the one-dimensional and classical SAR data.
+%%Mathmatically, the sample covariance matrix is reduced to the sample variance
+%  and the determinant equates the scalar value.
+%On the other hand, it is well known that for SAR data, variance equals intensity.
+%Thus the special case of our result is investigated carefully and is shown to be consistent with previous results for SAR intensity data.
+%This can be thought of 
+%  either as a cross-validation evidence for the proposed POLSAR models
+%  or alternatively as having SAR as the special case of POLSAR. 
+%%  with well known results for SAR intensity is presented.
+
 The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
@@
 
+%The results so far for our models can be summarized as:
 The results for our models can be summarized using the following equations:
@@
 The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+%but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
   \begin{eqnarray}
@@
     or as simple cases of the POLSAR results:
+%  Furthermore, the following results for multi-look SAR data,
+%  which can be thought of 
+%    either as extensions of the corresponding single-look SAR results
+%    or as simple cases of the POLSAR results
+%  are also derived as:
   \begin{align*}
@@
 Since we have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, only a simple validation is presented for this case.
-
+  only a simple validation is presented for this case.
+
+%These newly derived models for multi-look SAR data can also be validated using real-life data.
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
@@
 
+%This sub-section describes an experiment to validate the models presented earlier against real-life captured data,
+%  which can be performed in a rather straightforward manner.
+%The stochastic models derived in the previous sections can be graphically visualized as histogram plots of the simulated data.
+%%This section describes an experiment to validate the models above against real-life captured data.
+%%The validation procedure is quite straightforward.
+%%Given that the stochastic models have been derived in the previous sections, 
+%%  they can be graphically visualized by the histogram plots of the simulated data.
+%At the same time, the form of the real-life practical data is also observable via the histogram plots of the data samples extracted from an homogeneous area.
+%Therefore, the theoretical models can be validated 
+%  if for the same parameters 
+%  the two plots match each other reasonably well.
+
 For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
@@
 
+%For this purpose, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+%Then theoretical models are used  to explain the data.
+%%As a demonstration, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data as experimental data samples.
+%%Then theoretical models are employed in an attempt to explain the data.
+%All the newly proposed models is to be validated.
+%They include:
+%  the determinant and its log-transformed models, together with the dissimilarity measures namely: the determinant ratio, log-distance, dispersion and the contrast measures of distance.
+%  
+%These models are closely related.
+%For  the same parameter set, the determinant and determinant ratio are simply scaled versions of each other.
+%Meanwhile, the log-determinant, log-distance and dispersion are also just shifted versions of each other.
+%Hence one could expect that 
+%  once a model is validated, the other models in the set will follow suit, 
+%  assuming that all the parameters of the image are known.% exactly.
+%Nevertheless, all the models will be separately evaluated in this experiment to describe an interesting phenomenon.
+%%The models are closely related.
+%%Given the same parameter set, the determinant and determinant ratio are just scaled version of each other.
+%%Meanwhile, the log-determinant, the log-distance and the dispersion are also just shifted version of each other.
+%%Thus ideally speaking
+%%  if one model is validated all the other models will also be,
+%%  assuming that all the parameters of the image are known exactly.
+%%Still in this section, all the models will be made subject to investigation.
+
 The least-assumed stochastic processes for dispersion and contrast are validated first.
@@
   \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
+%Here the nominal look-number is employed $L=4$ for this experiment,
+%  while the dimensional number is set to either 3 or 2 depending on whether a full or partial polarimetric SAR dataset is being investigated.
+%The plots are presented in Fig. 
+%\ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} showing an evidentlt and visually match between the model and real data,
+%  effectively validating the theoretical models for dispersion and contrast.
 
@@
 
+%Apart from dispersion and contrast,
+%the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
+%There are two ways to estimate this quantity over an homogeneous area.
+%The traditional way is to simply set the true signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
+%Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
+%Both approaches will be presented in this section.
+%As the log-determinant average has already been computed earlier, 
+%  the second approach is hence used first for the validation of determinant-ratio and log-distance.
+%%Both approaches will be explored in this section.
+%%However, given that the log-determinant average has already been computed earlier, 
+%%  the second approach is used first for the validation of determinant-ratio and log-distance.
+
 Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
@@
 Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
+%And if the  true signals are computed in the same manner as described before then in fact similar match can be easily observed. 
 However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
+%However, a more interesting  phenomena is to be described.
+%It happens in the validation process for determinant and its log-transformed model,
   where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
+%For such simulation, an estimation of  the true signal is needed.
 The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
+%Interestingly, this approach results in a different estimation for the true signal with reference to the method described earlier.
 Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
+% easier to observe in the log-determinant plots. Despite this, the curve shapes are quite similar.
 
@@
 
+%\section{Handling certain discrepancy between the theoretical model and pratical data}
 \subsection{Difference between the theoretical assumptions and the conditions found in practice}  
@@
 Even though the assumptions made in developing this theory have intentionally been kept minimal, 
+%Even though the initial assumptions for the proposed theory is intentionally kept to minimal, 
 in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
 However, practical conditions may not always satisfy these prerequisites, thus we find a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions.
+%And it is shown that: the theoretical model proposed can apply to the practical data, even when this ``imperfection'' is taken into account.
+%In this section, certain gaps between the conditions found in practical real-life data and the theoretical assumptions are discussed.
+%And it is shown that: the theoretical model proposed can apply to the practical data, even when these ``imperfections''  are taken into account.
+%And it is shown that: the theoretical model proposed can handle the practical data, even when these ``imperfections''  are taken into account.
+
+%There are two main ``imperfections'' that are usually found in practical POLSAR data with reference to the theoretical model.
+%The first is the mutually independent assumption for each component in the POLSAR target vector $s$.
+%However high correlation is routinely observed in practice between the POLSAR data components,
+%%Practically however high correlation is routinely observable between the POLSAR data components,
+%  specifically between $S_{hh}$ and $S_{vv}$.
+%This phenomena also presents in our AIRSAR dataset, where {\scriptsize $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$}.
+%Despite the mismatch,
+%  astute reader would have noticed that the proposed model apparently still valid under such condition as evidenced by the part-pol (HH-VV) and full-pol plots in Figs.
+\ref{fig:verify_polsar_2x2_simulation_dispersion_contrast} to \ref{fig:verify_polsar_2x2_simulation_det}.
+%This suggests that the proposed model is also applicable on correlated POLSAR components,
+%  although a full explanation for thisis outside the scope of this paper. 
+%%This suggests that the proposed model is also applicable on correlated POLSAR components,
+%%  eventhough a full explaination for this, however, is outside the scope of this paper.
 
@@
   the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
+%Thus, theoretically speaking, adjacent pixels in an image can be assumed to be statistically independent.
 However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
-  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
+%where the analogue signal is to be converted into a digital data-set. 
+%Specifically, the analogue SAR signal, 
+%  which is characterised by the pulse bandwidth measurement,
+  employing an analogue-to-digital (ADC) sampling and conversion process.  
+%  which is characterised by its sampling rate.
 Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
 Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate. 
+%  resulting in a higher number of samples or pixels than the number of physical cells available in the scene.
 
 Thus in practical images, each physical radar cell may be spread over more than a single pixel,
+% resulting in potentially high correlation between neighbouring pixels.
 resulting in both %This results in 
   a higher correlation between neighbouring pixels \cite{Raney_1988_TGRS_666} %that may be related within a single physical cell resolution,
-  and a reduced effective number of look\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
+  %Then the correlation found between pairs of pixels that are further away and hence having less physical relation to each other will increase.
+%It also results in
+  and a reduced effective number of looks\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
+%  for example within a window of 3$\times$3 pixels of a single-look image, it actually contains less than 9 physical analogue cells. 
+%It also results in reduced effective number of look, 
+%  in which say a window of 3x3 pixel actually contains less than 9 physical analog cells. 
+%The former phenomena is partially explained in \cite{Raney_1988_TGRS_666} for SAR,
+%  while the later is experimental observed for POLSAR data in \cite{Lee_1994_TGRS_1017} and \cite{Anfinsen_2009_TGRS_3795}.
 The oversampling practice is also documented by the producers of SAR processors.
@@
 
+%The proposed model can handle this imperfection that is available in pratical data.
 The proposed model apparently can handle this imperfection. %that is found in practical data.
@@
 This is discussed in the next subsection.
+  %  an ENL estimation procedure is first undertaken, and subsequently the obtained ENL is then used.
+%the model validation can make use of the Effective Number of Looks that is manually estimated from a given practical dataset.
+%The next sub-section details a simple ENL estimation technique for POLSAR data.
+%While the final sub-section demonstrates how the practical imperfection can be handled in a RADARSAT2 dataset.
+%It also illustrates how the match shown in the first sub-section for the AIRSAR Flevoland dataset can be improved using ENL estimation.
 
@@
 
+%This sub-section describes a few techniques that can be used to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
+%This sub-section describes a few technique to estimate the Effective Number of Look (ENL) for a given POLSAR dataset.
 The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
@@
   where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
+%Recall that in carrying out the validation process using AIRSAR Flevoland data with nominal value $L=4$, the relationship was shown to be broken.
+%The reason is believed to be in the use of inexact value for $L$.
 In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
@@
 We will instead propose an alternative approach making use of variance statistics in the homoskedastic log-domain.
+%Instead of relying on the equations for statistical mean to find ENL,
+%  we propose an approach that makes used of variance statistics in the homoskedastic log-domain to find ENL.
+%Since the determinant of the POLSAR covariance matrix can be considered as the equivalence of the intensity in SAR data,
+%  this approach is a generic extension of our previous work on SAR ENL estimation \cite{Le_2013_TGRS_SAR_MSE} for POLSAR data.
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
@@
   and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph, or from the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
+%And if a graph is too tedious to be carried around an approximation can be made using a back-of-the-envolope calculation given as:
   \begin{equation}
@@
 To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
+%For this experiment an example single-look complex fine-quad RADARSAT2 dataset is used.
 Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
@@
 First, an ENL estimate is obtained from the observable variance of the log-determinant. 
+%A better match can be achieved by first estimating ENL from the observable variance of the log-determinant,
+%  and the theoretical model is then simulated for the estimated ENL.
 Then the new sample histogram is overlaid on the same figure,
@@
 \caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
+Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and then explain the data reasonably well.}
 \label{fig:handling_radarsat2_oversampling_practice}
@@
 Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
+%The mis-match problem appears to depend upon how much over-sampling was used to generate the dataset as well as upon the data dimension.
 
@@
 
+%\section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+%%\section{Visually Evaluating POLSAR Speckle Filters over Heterogeneous Areas}
+%\label{sec:evaluating_polsar_filters}
+%
+%Previous sections have developed a model for POLSAR, which is also shown to be applicable to SAR.
+%In this section, the use of consistent measures of distance in the context of POLSAR speckle filtering are explored briefly.
+%It has been found \cite{Rignot_1993_TGRS_896} that for SAR data in its original domain,  
+%   ratio is a better evaluation than standard subtractive residual. 
+%However, ratio residual is argued as not being natural for digital display \cite{Medeiros_2003_IJRS}.
+%Our previous work in the context of SAR speckle filtering found that
+%  in the log-transformed domain, this ratio is transformed into a subtractive residual that is homoskedastic.
+%  
+%The variance of sample log-determinant is shown to be linked to the ENL index.
+%This forms the basis for evaluating POLSAR speckle filters over homogeneous areas.
+%The procedure is simple:
+%To evaluate a given POLSAR speckle filter over homogeneous areas,
+%  the filter is applied over a known homogeneous area and the sample variance of log-determinant is measured.
+%The Equivant Number of Looks (ENL) is then estimated
+%  either by referencing prepared graphs from Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} 
+%  or alternatively by setting the measured variance value to $var[\ln{|C_v|}]$ in Eqn. \ref{eqn:enl_estimation_formula}.
+%
+%In order for such a procedure to be generic,
+%  it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
+%That can be tested by applying the POLSAR filter into different sets of homogeneous areas and investigating the plots of the dissimilarity measures presented above.
+%Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that
+%  the 3$\times$3 POLSAR boxcar filter preserves the consistency property.
+%In this case, the boxcar filter is applied to 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
+%Log-determinant and the contrast measures are computed for the input and output filtered POLSAR data,
+%  and their plots are presented.
+%In fact, the test procedure can be applied on any of the models presented above.  
+%
+%%ifdef FINAL
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant histograms of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+%		 \label{log_determinant}
+%	} 
+%	\hfill	
+%	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+%		 \label{contrast}
+%	}   
+%\end{tabular}
+%\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlying signal $\Sigma_v$, the shapes of the histograms should match.}
+%\label{fig:boxcar_3x3_preserves_consistency}
+%\end{figure}
+%%endif
+%%ifdef REVIEW
+%\begin{figure}[h!]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinants histograms of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/boxcar_3x3_preserves_consistency.log_determinant.eps} 	
+%		 \label{log_determinant}
+%	} 
+%	\hfill	
+%	\subfloat[Contrast histograms of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/boxcar_3x3_preserves_consistency.contrast.eps} 	
+%		 \label{contrast}
+%	}   
+%\end{tabular}
+%\caption{POLSAR 3$\times$3 boxcar filter preserves the consistency property.
+Consistency means: as long as the area is homogeneous, regardless of the underlysing signal $\Sigma_v$ the shapes of the histograms should be the same.}
+%\label{fig:boxcar_3x3_preserves_consistency}
+%\end{figure}
+%%endif
+%
+%The consistency property of a POLSAR speckle filter is important
+%  not only to make the estimation of ENL become general enough.
+%It is also to ensure that any classification / detection algorithm
+%    which is based on the scalar and consistent measures of distance will work on both pre-filtered and post-filtered data.
+%Otherwise if a POLSAR speckle filter gives different plots for different homogeneous areas,
+%  then not only its ENL estimation will be dependent on the underlying signal, 
+%  but its output also shall not follow the statistical distribution family that characterises multi-look POLSAR.
+%Thus the preservation of this consistency is believed to be an important consideration for POLSAR speckle filters
+%  if we want many general detection and classification algorithms to work on the filtered data output.
+%
+%In evaluation over heterogeneous area, the consistent measures of distance may also be an invaluable tool.
+% %in helping to evaluate POLSAR speckle filters.
+%Firstly, since the model for log-determinant is additive and homoskedastic,
+%  log-determinant images may naturally be better suited for gray-level digital display.
+%Specifically for evaluation of statistical estimators, it is both important and convenient to investigate the estimators' error / residual image. %plays an important role.
+%
+%For further analysis, the residual is defined here as the distance between the log-determinants of the filtered outputs and the original input. 
+%Ideally speaking, under the context of an additive model,
+%  a perfect estimators residual should consist only of random noise.
+%And under the assumption of homoskedasticity, 
+%  the Gauss Markov theorem becomes applicable.
+%Thus the optimal estimator is expected to exhibit minimal Mean Squared Error (MSE).
+%Over a homogeneous scene, this is reflected in the expectation of minimal bias and variance (hence maximal ENL).
+%Over a heterogeneous scene, where the underlying signal is not known \textit{a priori},
+%  the second best gauge is possibly to have the residual MSE being as close as possible to the MSE of the inherent noise.
+%  
+%To illustrate the above analysis, an experiment is carried out to evaluate the performance of 3$\times$3 and5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%A square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters applied to the patch.
+%Then the log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+%Assuming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+%  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+%This optimal value is computed   
+%by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
+%
+%%ifdef FINAL
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%%ifdef REVIEW
+%\begin{figure}[h!]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter (MSE=1.5594)]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter (MSE=2.1420)]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%%Note if the picture does not look convincing enough
+%%another option here is to show 7x7 filter with more pronouced blurring MSE=2.5
+%
+%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+%  but also the distortion impact of the filter can also be made visible by the residual image.
+%In visual evaluation, while it is quite hard to observe the worsening blurring-effects of the boxcar 5$\times$5 speckle filter as compared to the 3$\times$3 filter
+%in the additive log-determinant image of the filtered output, 
+%  such a conclusion can be made relatively easier by visualising the residual image.
+%
+%When quantified evaluation is carried out
+%  where the residual MSE is compared with the expected level of noise to be removed,
+%  the excessive blurring effects of the 5$\times$5 filter become clearly evident.
+%%IVM: [cut this]In fact, even the 3$\times$3 boxcar filter itself might be also a bit blurry.
+%%,  as suggested by its relatively high residual values.
+%%A conclusion which is hard to make
+%It may be hard to make such a conclusion just by looking at the filtered imagery.
+%However, by investigating the residual between the unfiltered input and the filtered results in the additive and homoskedastic model, both visual and quantitative evaluations offer more conclusive evidence.
+%
+%Further discussion on the specific topic of evaluating SAR speckle filters is given in our work that focused specifically on SAR \cite{Le_2013_TGRS_SAR_MSE}.
+%However, due to space restriction, only a brief and critical exploration is explored here for POLSAR speckle filters (i.e. extending the previous SAR approach).
+%
+%Specifically, this is an illustration of how the proposed theoretical model can possibly be applied to a practical scenario, rather than a full evaluation procedure and methodology.
+%%IVM [cut this],  as it is not as a full proposal for such an evaluation procedure for POLSAR speckle filters.
+
+%\section{Discussion and Conclusion}
+%\label{sec:discussion_conclusion}
+
+%\subsection{The Likelyhood Test Statistics for POLSAR}
+
+%\begin{eqnarray}
+%  Q &\sim& \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y} \cdot (2(L_x+L_y))^{d (L_x + L_y)}}{(2 L_x)^{d \cdot L_x} \cdot (2 L_y)^{d \cdot L_y} (\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%    &=& \frac{(L_x+L_y)^{d (L_x + L_y)}}{(L_x)^{d \cdot L_x} \cdot (L_y)^{d \cdot L_y} } \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} \\
+%\end{eqnarray}
+
 \section{Discussion}
@@
 Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
+%Other interesting phenomena which may warrant more study include the applicability of the model on correlated polsar channels ($S_{hh},S_{vv}$) as well as a better explanation in the use of mse to evaluate polsar speckle filters.
 
@@
 
+%Here a quick example is provided.
+%Since extensive examples have been shown to support the use of MSE for SAR data,
+%  it is reasonable to expect the relevance of MSE to also be demonstrated for POLSAR data.
+%If that is the case, a large number of existing algorithms can become applicable to the POLSAR model in this log-transformed domain,
+%  which has been shown to be both additive and homoskedastic.   
+%
 In evaluating SAR speckle filters, the intensity ratio is widely used.
@@
 
+%We will now show that this technique is easily applicable in the problem of evaluating POLSAR speckle filters.
+%We will now show that this technique can be equally applied for  evaluating POLSAR speckle filters.
+%Such an adaptation maps the SAR intensity ratio to the POLSAR determinant-ratio.
 Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
@@
   and the two POLSAR speckle filters are then applied to the patch. 
-\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+ \footnote{While the boxcar filters may not be the state-of-the-art POLSAR speckle filters, they are workable here since the purpose of this experiment is not to find the best POLSAR speckle filters.
+Rather its focus is to show how an existing SAR data processing technique can be adapted for POLSAR data.}
+%To illustrate the above analysis, an experiment is carried out to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR speckle filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%A square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters applied to the patch.
 The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
 At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+%Assuming the quantitative evaluation of SAR speckle filters can also be extended to POLSAR speckle filters,
+%  the Mean Squared Error (MSE) of the filters residuals are computed and compared with the ``optimal'' value.
+%This optimal value is computed   
+%by setting $d=2,L=4$ into Eqn. \ref{eqn:polsar_dispersion_mse} making the expected MSE being $mse(\mathbb{L})=1.0132$.
 
@@
 \end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
 \label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
@@
 \end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
 \label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
@@
   the distortion impact of the filter can also be made visible by the residual image.
-In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+In a visual evaluation, while it is quite hard to observe the increased blurring due to the 5$\times$5 filter compared to the 3$\times$3 filter
 in the additive log-determinant image of the filtered output, 
@@
 
-Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
+There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
 Evidently these techniques can also be adapted for POLSAR.
 Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
-
-Hai version: (Ian have not seen this yet) There are many similar SAR data processing technique that may be adaptable to POLSAR.
-Examples in the same topic of evaluating speckle filters include
-  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
-
-In fact, at the time of this writing, the field of SAR is much more developed than the field of POLSAR.
-The two fields however are quite separated,
-  as many techniques applicable to SAR are not directly applicable to POLSAR.
-This work may build the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques on POLSAR data.
-Here a specific example is shown
-  where, similar to the way ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-In general, we believe there are many more unexplored possibilities for such applications
-  which is only limited by our imagination.
+In fact, since the POLSAR models have been shown to be a multi-dimensional extension of the traditional SAR intensity models,
+many more adaptations may be possible.
+
+%There are also many algorithms developed from existing POLSAR discrimination measures which can also be adapted for the dis-similarity measures proposed in this paper.
+
+%There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Examples include the use of the mean and variance of the ratio image to quantitatively evaluate POLSAR speckle filters.
+%For example in the very same context of evaluating speckle filters,
+%  the mean and variance of the ratio image are also routinely used to provide quantitative evaluation.
+%Evidently these techniques can also be adapted to evaluate POLSAR speckle filters, without much difficulties in foresight.
+%In fact, we believe a list of such techniques would take pages.
+%Here due to space restriction, only a simple example is described to highlight the beneficial implications of the proposed models.
 
@@
   but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
-They are also practically useful since they lead to several consistent discrimination measures.
+%The theoretical model is shown to be useful in providing alternative and  simpler explanations to a range of theoretical concepts such as POLSAR test statistics and ENL estimation.
+%Furthermore, the statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix which,
+%  when converted into one-dimensional data, is gracefully transformed into traditional SAR intensity.
+They are also practically useful in that they lead to several consistent discrimination measures.
 Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
-Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
+Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
+The models may also form a bridge that allows the adaptation of many existing SAR data processing techniques for POLSAR data.
 

### 2013-07-24 build_all.sh

@@ -1,0 +1,20 @@
+pdftk A=thesis.pdf cat A3-4 output chap_abstract.pdf
+pdftotext chap_abstract.pdf
+pdftk A=thesis.pdf cat A7-20 output chap_contents.pdf
+pdftotext chap_contents.pdf
+pdftk A=thesis.pdf cat A21-32 output chap1.pdf
+pdftotext chap1.pdf
+pdftk A=thesis.pdf cat A33-62 output chap2.pdf
+pdftotext chap2.pdf
+pdftk A=thesis.pdf cat A61-74 output chap3.pdf
+pdftotext chap3.pdf
+pdftk A=thesis.pdf cat A75-98 output chap4.pdf
+pdftotext chap4.pdf
+pdftk A=thesis.pdf cat A99-150 output chap5.pdf
+pdftotext chap5.pdf
+pdftk A=thesis.pdf cat A151-158 output chap6.pdf
+pdftotext chap6.pdf
+
+#makeindex thesis.nlo -s nomencl.ist -o thesis.nls
+#latex -interaction=nonstopmode thesis.tex
+

### 2013-07-25 0_frontmatter/abstract.tex
updated Ian's abstract and acknowledgement

@@
 
-On the one hand, practical application for POLSAR data processing requires the establishment of discrimination measures
+On the one hand, practical applications for POLSAR data processing require the establishment of discrimination measures
   which are to be scalar and statistically consistent.
-On the other hand, these same scalar observable quantities need to be naturally representative for the high-dimensional POLSAR data.
+On the other hand, these same scalar observable quantities need to be naturally representative of the high-dimensional POLSAR data.
 At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.
 
-In this thesis, the statistical behavior of the determinant of POLSAR covariance matrix is explored.
+In this thesis, the statistical behaviour of the determinant of POLSAR covariance matrix is explored.
 Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.
 
-As the result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix is proposed and validated.
+As a result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix are proposed and validated.
 This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
@@
 There are several beneficial implications of the theory proposed in this thesis. 
-Since the scalar and representative model for POLSAR generalize the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
-At the same time, the benefit of the homoskedastic models is multiple-folds.
-For in-experienced researchers (like this author when he started this study),
+Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+Similarly, the homoskedastic model carries additional benefits.
+For inexperienced researchers (such as this author when he began this research),
   who attempt to process either SAR or POLSAR data using existing computation algorithms
   which most of the time expect an additive and homoskedastic input,
-  this thesis proposes alternative and more familiar additive and homoskedastic models
-    in place of the original ones which are multiplicative and heteroskedastic.
+  this thesis proposes alternative and more familiar additive and homoskedastic models. These replace
+ the original ones which are multiplicative and heteroskedastic.
 For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 

### 2013-07-25 0_frontmatter/acknowledgement.tex
updated Ian's abstract and acknowledgement

@@
   whose constant love and unconditional support I have greatly relied upon. 
-Their immeasurable sacrifices together with their continous encouragement have always been the motivation for me to follow this academic pursuit.
+Their immeasurable sacrifices together with their continuous encouragement have always been the motivation for me to follow this academic pursuit.
 %venture further. 
@@
 
-This thesis would also not have been possible without the patient and helpful guidance of Assoc. Prof. Ian McLoughlin and Assoc Prof. Nicholas Vun Chan Hua, 
-	under whose supervision I am gratefully being under. 
-The supervisors have been providing firm support, as well as spot-on guidance. 
+This thesis would also not have been possible without the patient and helpful guidance of Professor Ian McLoughlin and Associate Professor Nicholas Vun Chan Hua, 
+	under whose supervision I am gratefully under. 
+The supervisors have provided firm support, as well as spot-on guidance. 
 During all the stages of my research work, 
 	be it conceptualization or result analysis, be it writing, presentation or publishing ..
-	their kind attention and wise advices command my utmost respect and admiration.
+	their kind attention and wise advice command my utmost respect and admiration.
 
@@
 
-Special thanks go to my friends and colleagues, whose friendship and companion have made the journey a truly enjoyable one. 
-They include but not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...
+Special thanks go to my friends and colleagues, whose friendship and companionship have made the journey a truly enjoyable one. 
+They include but are not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...
 
-Last but not least I would like to give my appreciations to all NTU staffs at PDCC, SCE and GSO whose quiet but continous supporting efforts played a very important role in any measure of success this dissertation may be associated with.
+Last but not least I would like to give my appreciation to all NTU staff in PDCC, SCE and GSO whose quiet but continuous supporting efforts played a very important role in any measure of success this dissertation may be associated with.
 

### 2013-07-25 build_all.sh

@@ -1,19 +1,25 @@
-pdftk A=thesis.pdf cat A3-4 output chap_abstract.pdf
-pdftotext chap_abstract.pdf
-pdftk A=thesis.pdf cat A7-20 output chap_contents.pdf
-pdftotext chap_contents.pdf
-pdftk A=thesis.pdf cat A21-32 output chap1.pdf
+#pdftk A=thesis.pdf cat A3-4 output chap_abstract.pdf
+#pdftotext chap_abstract.pdf
+#pdftk A=thesis.pdf cat A7-20 output chap_contents.pdf
+#pdftotext chap_contents.pdf
+pdftk A=thesis.pdf cat A1-19 output chap0.pdf
+pdftotext chap0.pdf
+pdftk A=thesis.pdf cat A20-31 output chap1.pdf
 pdftotext chap1.pdf
-pdftk A=thesis.pdf cat A33-62 output chap2.pdf
+pdftk A=thesis.pdf cat A32-61 output chap2.pdf
 pdftotext chap2.pdf
-pdftk A=thesis.pdf cat A61-74 output chap3.pdf
+pdftk A=thesis.pdf cat A62-74 output chap3.pdf
 pdftotext chap3.pdf
 pdftk A=thesis.pdf cat A75-98 output chap4.pdf
 pdftotext chap4.pdf
 pdftk A=thesis.pdf cat A99-150 output chap5.pdf
 pdftotext chap5.pdf
-pdftk A=thesis.pdf cat A151-158 output chap6.pdf
+pdftk A=thesis.pdf cat A151-157 output chap6.pdf
 pdftotext chap6.pdf
+pdftk A=thesis.pdf cat A158-172 output chap9.pdf
+pdftotext chap9.pdf
+pdftk A=thesis.pdf cat A173-183 output chap_references.pdf
+pdftotext chap_references.pdf
 
 #makeindex thesis.nlo -s nomencl.ist -o thesis.nls
 #latex -interaction=nonstopmode thesis.tex

### 2013-07-27 4/polsar.tex
updated from Ian's changes

@@
 
-\section{Discussion}
-
-Let us consider the different theoretical properties of the proposed models.
-First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
-In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
-Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
-Thus similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
-  the models presented here are invariant to polarization basis transformations.
-
-Second, the models are developed for the POLSAR covariance matrix.
-However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model should also be applicable to the coherency matrix.
-
-It should be noted that the models are far from complete.
-% It reduces the multi-dimensional POLSAR data to a scalar value.
-%While this is probably desirable for a wide range of application,
+%\section{Discussion}
+%
+%Let us consider the different theoretical properties of the proposed models.
+%First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+%In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+%Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
+%Thus similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
+%  the models presented here are invariant to polarization basis transformations.
+%
+%Second, the models are developed for the POLSAR covariance matrix.
+%However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+%  the model should also be applicable to the coherency matrix.
+%
+%It should be noted that the models are far from complete.
+%% It reduces the multi-dimensional POLSAR data to a scalar value.
+%%While this is probably desirable for a wide range of application,
+%%  such a reduction is unlikely to be lossless.
+%While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
 %  such a reduction is unlikely to be lossless.  
-While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
-  such a reduction is unlikely to be lossless.  
-Thus %to better understand POLSAR data
-the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
-
-Nevertheless the proposed models are promising.
-Even though initially developed for partial and monostatic POLSAR data,
-  this was shown to be applicable to traditional SAR data as well.
-Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
-
-%If move to chapter 4, can add these paragraphs
-%The thesis also derives the homoskedastic models for both SAR and POLSAR heteroskedastic data.
-%Within this consistent variance models, several consistent sense of subtractive distance is proposed.
-%These can be thought of as the linear and subtractive versions of the commonly used ratio discrimination measure in the original multiplicative SAR model.
-%
-%Theses additive and homoskedastic models should be beneficial to all the steps of the computational and statistical estimation framework in particular as well as to many existing digital technologies and algorithms in general.
-%This thesis also includes several published studies which illustrate several of such benefits.
-%These include the use of the consistent variance to break the vicious circle of speckle filtering, as well as the use of MSE in evaluating (POL)SAR Statistical estimators within the additive and homoskedastic model.
-%
-
- \subsection{Beneficial}
-
-%How to exploit the advantages of these new results? What
-%                are their benefit? And
-%                to whom? OK, assuming your solution is novel and it can
-%                hold water, is it useful? How is it better than the
-%                state-of-the-art? And to whom does this matter? Why
-%                should they use your solutions instead of other?
-The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
-An example is between the fields of SAR and POLSAR, where obviously SAR data processing has been studied in much further detail than the more newly derived field of POLSAR data processing.
-%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
-By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
-Another example is between the fields of computer science and SAR-based remote sensing.
-Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
-And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
-could potentially allow this currently small portion to grow larger.
-%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.
-
-%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
-%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
-The proposed homoskedastic statistical estimation framework provides a firm foundation
-to overcome the various negative impacts of heteroskedasticity on statistical estimations.
-This
-                is demonstrated in both stages of developing new
-                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
-Specifically
-                in the context of SAR speckle filters: consistent
-                variance and homoskedasticity is shown to help in
-                breaking the vicious circle of speckle filtering.
-
-At
-                the same time, a consistently meaningful sense of
-                distance leads to our proposal of using the familiar
-                MSE in the homoskedastic domain to evaluate SAR speckle
-                filters.
-Intuitively,
-                this comes about as the speckle suppression power of
-                speckle filters can be evaluated via variance estimation
-                practice, while the radiometric preservation can be
-                evaluated via the normal bias evaluation.
-Combined,
-                while there are many different evaluation criteria in
-                the heteroskedastic SAR speckle filter evaluation
-                framework, the MSE is proposed as the single unified
-                evaluation criteria for SAR speckle filters.
-%***IVM: not sure about the above paragraph... can you check it? Why the 'combined'?
-In
-                short, it is shown that in the homoskedastic domain, not
-                only it is possible to find the equivalent of existing
-                methods overcoming heteroskedastic drawbacks in the
-                original domain, it is also possible to suggest further
-                improvements based on existing techniques.
-
-The
-                proposed models for POLSAR also bring forward 
-                important benefits.
-Since
-                the models, especially those for discrimination
-                measures, can be considered as the multidimensional
-                extension of the models for SAR, it makes many existing
-                SAR processing techniques extensible towards POLSAR
-                data.
-The POLSAR determinant ratio, for example, can be considered as
-                the extension of the ubiquitous SAR intensity ratio.
-This
-                thesis also illustrates how the MSE evaluation
-                criteria can also be extended from SAR to POLSAR.
-
-From another angle, the theoretical models for POLSAR also offer several benefits.
-The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
-In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
-  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
-can be simulated as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-As a by-product of this exact derivation, the paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.%***IVM: Hai, by "paper" in this sentence, are you referring to the Conradsen 2003 TGRS paper?
-
-Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
-new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.
-
-%While some of these obstacles have been overcome by various experienced researcher in the field proposing different genuine approaches, 
-%  the additive and homoskedastic transformation approach proposed in this thesis suggests that these problems also have equivalent handling techniques which usually are more familiar.
-%Furthermore competitive and even sometimes better proposal are made making use of this familiarity.
-%For example, not only it is shown that both radiometric preservation and speckle suppression evaluation of SAR speckle filters can be carried out equivalently well under both domain, 
-%  MSE is in the additive and homoskedastic domain is shown capable of combining the two evaluations, which so far have not been figured out in the original heteroskedastic domain.
-%Elsewhere, the application of wavelet in this same transformed domain has resulted in a new class of speckle filters which performs respectably in comparison to other well established filters.
-%The familiarity of this transformed domain should also be very helpful for the new comers of the field, who is much more likely to find comfort ability in this derived domain in comparison to the original multiplicative and heteroskedastic domain.
-
-\subsection{Limitations}
-
-%What are their limitations? What problems this appears
-%                to solve, but actually is not?
-
-The
-                proposed scalar models for POLSAR also have limitations.
-They
-                involve a dimensional reduction operation, which is
-                probably not lossless.
-Thus
-                while the determinant of the POLSAR covariance matrix could be described as
-                ``highly representative'', it is definitely not
-                \textit{fully representative} of the data.
-Intuitively,
-                this is similar to the use of magnitude as being
-                representative of a complex number, which also is not
-                fully representative of the two-dimensional number.
-But it is important to emphasize that,
-                just like the magnitude is invariant to the rotation of
-                the reference frame, the POLSAR determinant is also
-                invariant to polarization basis transformation.
-
-While
-                the proposed homoskedastic measures of distance have
-                their own benefits, their biggest challenge probably
-                lies in changing the hard learned lessons that
-                previous generation of researchers have experienced tackling
-                the multiplicative and heteroskedastic SAR data.
-At
-                the same time, while the logarithmic transformation has
-                the advantages of converting the multiplicative and
-                heteroskedastic model into an additive and homoskedastic
-                data, such transformation does not arrive conveniently
-                to the common additive white noise model.
-In fact, figures presented in the previous chapters show that 
-	they are not even centred around the origin. 
-This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
-	work very well in practice, as the operation is biased and statistically inconsistent.
-To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
-	is suggested \cite{Le_2011_ACRS}.
-While averaging is also the MLE operator in SAR's original domain,
-                the MLE operation in the log-transformed domain is admittedly more complex in comparison.
-
+%Thus %to better understand POLSAR data
+%the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+%
+%Nevertheless the proposed models are promising.
+%Even though initially developed for partial and monostatic POLSAR data,
+%  this was shown to be applicable to traditional SAR data as well.
+%Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
+%
+%%If move to chapter 4, can add these paragraphs
+%%The thesis also derives the homoskedastic models for both SAR and POLSAR heteroskedastic data.
+%%Within this consistent variance models, several consistent sense of subtractive distance is proposed.
+%%These can be thought of as the linear and subtractive versions of the commonly used ratio discrimination measure in the original multiplicative SAR model.
+%%
+%%Theses additive and homoskedastic models should be beneficial to all the steps of the computational and statistical estimation framework in particular as well as to many existing digital technologies and algorithms in general.
+%%This thesis also includes several published studies which illustrate several of such benefits.
+%%These include the use of the consistent variance to break the vicious circle of speckle filtering, as well as the use of MSE in evaluating (POL)SAR Statistical estimators within the additive and homoskedastic model.
+%%
+%
+% \subsection{Beneficial}
+%
+%%How to exploit the advantages of these new results? What
+%%                are their benefit? And
+%%                to whom? OK, assuming your solution is novel and it can
+%%                hold water, is it useful? How is it better than the
+%%                state-of-the-art? And to whom does this matter? Why
+%%                should they use your solutions instead of other?
+%The over-arching strategic benefit is to enable the application of existing and established techniques from one matured field into another less-than-developed new field.
+%An example is between the fields of SAR and POLSAR, where obviously SAR data processing has been studied in much further detail than the more newly derived field of POLSAR data processing.
+%%As is shown, the one-dimensional SAR neatly falls into the limit special case of the multi-dimensional POLSAR.
+%By putting both SAR and POLSAR into one consistent theory, this thesis opens up the opportunities to apply many of the existing SAR processing technique to POLSAR.
+%Another example is between the fields of computer science and SAR-based remote sensing.
+%Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
+%And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
+%could potentially allow this currently small portion to grow larger.
+%%a plethoria number of digital image processing algorithms as well as artificial intelligence and machine learning techniques to be applicable for both SAR and POLSAR data.
+%
+%%Speaking from the author's experience since he first being introduced to this field, the solution for these problem should be important for the next generation of new-comers to the field of (POL)SAR.
+%%This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
+%The proposed homoskedastic statistical estimation framework provides a firm foundation
+%to overcome the various negative impacts of heteroskedasticity on statistical estimations.
+%This
+%                is demonstrated in both stages of developing new
+%                statistical estimators (e.g. speckle filters) as well as evaluating their estimating performance.
+%Specifically
+%                in the context of SAR speckle filters: consistent
+%                variance and homoskedasticity is shown to help in
+%                breaking the vicious circle of speckle filtering.
+%
+%At
+%                the same time, a consistently meaningful sense of
+%                distance leads to our proposal of using the familiar
+%                MSE in the homoskedastic domain to evaluate SAR speckle
+%                filters.
+%Intuitively,
+%                this comes about as the speckle suppression power of
+%                speckle filters can be evaluated via variance estimation
+%                practice, while the radiometric preservation can be
+%                evaluated via the normal bias evaluation.
+%Combined,
+%                while there are many different evaluation criteria in
+%                the heteroskedastic SAR speckle filter evaluation
+%                framework, the MSE is proposed as the single unified
+%                evaluation criteria for SAR speckle filters.
+%%***IVM: not sure about the above paragraph... can you check it? Why the 'combined'?
+%In
+%                short, it is shown that in the homoskedastic domain, not
+%                only it is possible to find the equivalent of existing
+%                methods overcoming heteroskedastic drawbacks in the
+%                original domain, it is also possible to suggest further
+%                improvements based on existing techniques.
+%
+%The
+%                proposed models for POLSAR also bring forward 
+%                important benefits.
+%Since
+%                the models, especially those for discrimination
+%                measures, can be considered as the multidimensional
+%                extension of the models for SAR, it makes many existing
+%                SAR processing techniques extensible towards POLSAR
+%                data.
+%The POLSAR determinant ratio, for example, can be considered as
+%                the extension of the ubiquitous SAR intensity ratio.
+%This
+%                thesis also illustrates how the MSE evaluation
+%                criteria can also be extended from SAR to POLSAR.
+%
+%From another angle, the theoretical models for POLSAR also offer several benefits.
+%The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
+%In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
+%  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics} \& \ref{eqn:Complex Wishart Distribution Likelihood Test Statistics (Log Domain)}
+%can be simulated as:
+%\begin{align*}
+%  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+%  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+%\end{align*}
+%where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+%As a by-product of this exact derivation, the paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.%***IVM: Hai, by "paper" in this sentence, are you referring to the Conradsen 2003 TGRS paper?
+%
+%Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+%new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.
+%
+%%While some of these obstacles have been overcome by various experienced researcher in the field proposing different genuine approaches, 
+%%  the additive and homoskedastic transformation approach proposed in this thesis suggests that these problems also have equivalent handling techniques which usually are more familiar.
+%%Furthermore competitive and even sometimes better proposal are made making use of this familiarity.
+%%For example, not only it is shown that both radiometric preservation and speckle suppression evaluation of SAR speckle filters can be carried out equivalently well under both domain, 
+%%  MSE is in the additive and homoskedastic domain is shown capable of combining the two evaluations, which so far have not been figured out in the original heteroskedastic domain.
+%%Elsewhere, the application of wavelet in this same transformed domain has resulted in a new class of speckle filters which performs respectably in comparison to other well established filters.
+%%The familiarity of this transformed domain should also be very helpful for the new comers of the field, who is much more likely to find comfort ability in this derived domain in comparison to the original multiplicative and heteroskedastic domain.
+%
+%\subsection{Limitations}
+%
+%%What are their limitations? What problems this appears
+%%                to solve, but actually is not?
+%
+%The
+%                proposed scalar models for POLSAR also have limitations.
+%They
+%                involve a dimensional reduction operation, which is
+%                probably not lossless.
+%Thus
+%                while the determinant of the POLSAR covariance matrix could be described as
+%                ``highly representative'', it is definitely not
+%                \textit{fully representative} of the data.
+%Intuitively,
+%                this is similar to the use of magnitude as being
+%                representative of a complex number, which also is not
+%                fully representative of the two-dimensional number.
+%But it is important to emphasize that,
+%                just like the magnitude is invariant to the rotation of
+%                the reference frame, the POLSAR determinant is also
+%                invariant to polarization basis transformation.
+%
+%While
+%                the proposed homoskedastic measures of distance have
+%                their own benefits, their biggest challenge probably
+%                lies in changing the hard learned lessons that
+%                previous generation of researchers have experienced tackling
+%                the multiplicative and heteroskedastic SAR data.
+%At
+%                the same time, while the logarithmic transformation has
+%                the advantages of converting the multiplicative and
+%                heteroskedastic model into an additive and homoskedastic
+%                data, such transformation does not arrive conveniently
+%                to the common additive white noise model.
+%In fact, figures presented in the previous chapters show that 
+%	they are not even centred around the origin. 
+%This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
+%	work very well in practice, as the operation is biased and statistically inconsistent.
+%To counter this, the use of maximum likelihood estimation, instead of simple averaging, 
+%	is suggested \cite{Le_2011_ACRS}.
+%While averaging is also the MLE operator in SAR's original domain,
+%                the MLE operation in the log-transformed domain is admittedly more complex in comparison.
+%
 %\section{Simulating All Elements of POLSAR Covariance Matrix}

### 2013-07-27 6/conclusional_discussion.tex
updated from Ian's changes

@@
   as they cope well with imperfect conditions evident in real-life captured data.
+
+The work in this research results in the following list of articles that has been prepared for public communication:
+
+\begin{enumerate}
+\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
+  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
+  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
+\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
+  T. H. Le and I. V. McLoughlin. 
+  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
+\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
+  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
+  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
+\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
+  T. H. Le, I. V. McLoughlin, and C. H. Vun,
+  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+\item \textbf{Using MSE to evaluate SAR speckle filters.}
+  T. H. Le, I. V. McLoughlin, and C. H. Vun.
+  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing}
+\end{enumerate}
 

### 2013-07-27 paper_dev/article.tex
updated from Ian's changes

@@
 \markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Models for Polarimetric SAR Data}
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables for Polarimetric SAR Data}
 

### 2013-07-31 0_frontmatter/abstract.tex
Final changes before submission to Alan???

@@
 
-On the one hand, practical applications for POLSAR data processing require the establishment of discrimination measures
+SAR and POLSAR stochastic data are multiplicative and heteroskedastic in their natural domain.
+It is hence desirable to establish additive and homoskedastic models,
+  such that the benefits of homoskedastic statistical estimation framework can be demonstrated and realized for practical applications such as speckle filtering.
+In addition, the processing of multi-dimensional POLSAR data requires the establishment of discrimination observables
   which are to be scalar and statistically consistent.
-On the other hand, these same scalar observable quantities need to be naturally representative of the high-dimensional POLSAR data.
-At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.
+Moreover, these same scalar observable quantities also need to be naturally representative for the multidimensional POLSAR data.
 
-In this thesis, the statistical behaviour of the determinant of POLSAR covariance matrix is explored.
-Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.
+In this thesis, the effects of homoskedasticity on SAR and POLSAR speckle filtering within the framework of computational and statistical estimation are extensively studied. 
+Concurrently, the statistical behaviour of the determinant of POLSAR covariance matrix is also explored,
+  where it is shown to be the representative scalar observable for the multidimensional POLSAR, similar to the role of the intensity in SAR.
 
-As a result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix are proposed and validated.
-This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
-Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
-Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
-From these models, several additive measures of distance are proposed for both SAR and POLSAR data.
+As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix are proposed and validated.
+These generic models for POLSAR are also shown to be both multiplicative and heteroskedastic, similar to the models for SAR intensity. 
+Subsequently, logarithmic transformation is applied onto both SAR and POLSAR models
+  to convert them into additive and homoskedastic models.
+From these models, the benefits of homoskedastic statistical estimation framework are then further explored.
 
 There are several beneficial implications of the theory proposed in this thesis. 
-Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,
+  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
 Similarly, the homoskedastic model carries additional benefits.
@@
   which most of the time expect an additive and homoskedastic input,
-  this thesis proposes alternative and more familiar additive and homoskedastic models. These replace
- the original ones which are multiplicative and heteroskedastic.
+  this thesis proposes alternative and more familiar additive and homoskedastic models.
 For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
-  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.
+  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the statistical estimation framework for (POL)SAR.
 

### 2013-07-31 1_introduction/introduction.tex
Final changes before submission to Alan???

@@
 %What is the situation, the background context of your research? the BIG problem!
-Synthetic Aperture Radar is a technology with many advantages.
-%Compared to optical remote sensors, which are passive, active SAR sensors provide weather independent and night-inclusive operational capabilities.
+Synthetic Aperture Radar (SAR) is a technology with many advantages.
 Compared to optical remote sensors - which are passive, SAR uses active sensors to provide weather independent and night-inclusive operational capabilities. 
@@
 
-As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is polarimetric SAR or POLSAR. POLSAR is the natural
-extension from SAR, exploiting the natural polarization property of Electromagnetic
-(EM) waves. It extends the SAR acquisition information from the traditional single
-SAR channel to multi-channel polarimetric SAR data, corresponding to a different combination of transmitted and received polarizations.
+As state-of-the-art technology, the SAR technique has been extended in a few directions, one of which is Polarimetric SAR (POLSAR).
+POLSAR is the natural extension of SAR, exploiting the natural polarization property of Electromagnetic (EM) waves.
+It extends the SAR acquisition information from the traditional single
+SAR channel to multi-channel POLSAR data, corresponding to a different combination of transmitted and received polarizations.
 Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
@@
 
-With both SAR and POLSAR data becoming cheaper and more available, the recent research emphasis is on understanding and developing applications for the data. However, both SAR 
+With both SAR and POLSAR data becoming cheaper and more readily available, the recent research emphasis is on understanding and developing applications using these data. However, both SAR 
 and POLSAR suffer from speckle phenomena, which hampers the human capabilities
@@
 The
-                big picture, as introduced above, is that POLSAR data is multi­dimensional,
+                big picture, as introduced above, is that POLSAR data is multi-dimensional,
                 stochastic, multiplicative and heteroskedastic.
@@
 %                extracted from these data.
-Under this condition, it is very important to understand the statistical models for SAR
-data. It is these models that form the foundation for different SAR data processing
+Under this condition, it is very important to understand the statistical models for its
+data. It is these models that form the foundation for different (POL)SAR data processing
 techniques, for example speckle filtering, target detection, image segmentation, and
@@
 In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
-which comprises statistical modeling and validation, estimator design and development
-as well as evaluation of different estimators’ accuracy. And central to this statistical
+which comprises statistical modelling and validation, estimator design and development
+as well as evaluation of different estimators' accuracy. And central to this statistical
 estimation theory is the need for statistically consistent discrimination measures which
@@
 a representation difficulty in that: there exists not one, like the intensity in SAR, but
-many observable quantities in POLSAR. Thus on the one hand, practical application for
-POLSAR data processing requires the measure to be scalar, consistent and preferably
-homoskedastic. On the other hand, the observable quantity being modeled needs to
+many observable quantities in POLSAR. Thus, on the one hand, practical applications for
+POLSAR data processing require measures which are scalar, consistent and preferably
+homoskedastic. On the other hand, the observable quantity being modelled needs to
 be naturally representative of the high dimensional POLSAR data.
@@
 %OR PERHAPS THIS: "... the prevalence of AWGN in natural processes."
+%****IVM2: I'm still not sure about it, but we can put it to the examiner, see if he picks it up.
 It should be noted that even for the case of SAR data which is digital and not additive,
-  the above statement is still true as SAR actually has two components, real and imaginary part,
-  and all of them follows the standard Additive White Gaussian Noise model.
+  the above statement is still true as SAR actually has two components, the real and imaginary parts,
+  both of which follow the standard Additive White Gaussian Noise model.
+%****IVM: I really don't understand what you're trying to say here.  Are you saying that "both parts are corrupted by AWGN"?
 
-Both SAR and POLSAR data however is multiplicative and heteroskedastic by nature.
+Both SAR and POLSAR data however are multiplicative and heteroskedastic by nature.
 While there is no doubt that a number of data processing techniques have been proposed to handle certain aspects of the data, the breadth and depth of these studies trails in comparison to that of the more familiar additive and homoskedastic model.
 This leads to the fact that a lot of times, existing statistical or computational techniques initially designed for additive and homoskedastic models are applied on multiplicative and heteroskedastic data, in ignorance of the incompatibility.
-An example is the use of mean, variance and squared error criteria, which are linear by nature and works excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
+An example is the use of mean, variance and squared error criteria, which are linear by nature and work excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
 Such use, however, is known to be not very robust for these so-called heavy tailed distributions.
@@
 For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences.
-However for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
+However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
 Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
@@
 contrast in digital image processing. 
-Thus it is very exciting to derive homoskedastic models for this heteroskedastic data
+Thus it will be very useful to develop homoskedastic models for this heteroskedastic data
   so that the benefits of an additive and homoskedastic statistical estimation framework can be explored.
@@
                 following the complex Wishart distribution, which
-                apparently is multi­dimensional, complex and
-                un­intuitive.
+                apparently is multi-dimensional, complex and
+                un-intuitive.
 There
-                has been a few published scalar statistical models for
+                have been a few published scalar statistical models for
                 POLSAR, but none of them fit the dual criteria of being
@@
                 impacts caused by multiplicative and heteroskedastic
-                properties for SAR data, experienced researchers of the
+                properties for SAR data, experienced researchers in the
                 field have developed numerous ingenious ways to tackle
@@
 Unfortunately,
-                these counter­intuitive measures are not very popular
+                these counter-intuitive measures are not very popular
                 outside the SAR community, and newcomers to the field
-                are frequently found being trapped in these pitfalls.
+                are frequently found being trapped by these pitfalls.
 
@@
 Some of the problems described above have been studied using different approaches in the literature.
-However, the set of problems has not been presented in a systematic manner nor with a strong underlying foundational theory.
-In
-                this thesis, the statistical model for the determinant
-                of the POLSAR covariance matrix is proposed and
-                validated.
-Out
-                of many different possible scalar projections of the
-                multi-dimensional data, the proposed projection is
-                highly representative.
-When the dimension number is collapsed to one, the
-                special case of the proposed model matches perfectly
-                with the commonly used statistical model for SAR
-                intensity.
-Furthermore,
-                the proposed statistical model also leads to the
-                derivation of existing as well as the newly proposed
-                discrimination measure: determinant-ratio which is the
-                generalized multi dimensional version of the widely used
-                SAR intensity ratio.
-
- Another
-                novelty of the contributions in this thesis comes from the systematic
-                treatment towards the problem of statistical estimation
-                of heteroskedastic SAR data.
-While
-                many different ways to combat the negative impacts
-                caused by multiplicative and heteroskedastic properties
-                for SAR data have been proposed over the years, they have often been
-                handled in a piecemeal manner.
-Here,
-                a systematic homoskedastic framework of statistical
-                estimation is developed, where not only homoskedastic
-                statistical models are proposed, the impacts of
-                homoskedasticity on estimator development and
-                performance evaluation of statistical estimators is also
-                studied.
-This
-                comprehensive treatment not only explains why the
-                original SAR data requires special treatment very
-                different to the common practice of computational
-                sciences, 
-it
-                also allows thorough and unique discussion, for example on
-                evaluating different evaluation criteria for statistical
-                estimators.  % ;-)).
-And
-                since the POLSAR data can be considered as the multi
-                dimensional extension of traditional SAR data, these
-                treatments are shown extensible towards POLSAR data
-                which is definitely yet another novelty.
-
+However, they have not been presented in a systematic manner nor with a strong underlying foundational theory.
 %precise problem statement
-With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
-That is
+Hence the \textbf{main problem statement} of this thesis arises. %it is important to emphasize again the main problem statement of this thesis.
+That is,
                 this thesis focuses on providing a solution for the
@@
 The
-                assumptions used are minimal and widely
+                assumptions used are minimal and also widely
                 acknowledged for this type of data.
@@
                 real life data.
-And
-                the imperfect conditions found in practice (in
-                comparison to the theoretical assumption) are also
+The
+                imperfect conditions found in practice (in
+                comparison to the theoretical assumptions) are also
                 investigated, and the models are shown to be robust, capable of
@@
 Even though the research topic seems to spread across different sub-fields, the common framework that binds them all together is the application and development of statistical estimators.
-For speckle filtering, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
+For example, for speckle filtering, it is the estimation of underlying back-scattering coefficients being corrupted with stochastic noise.
 For the problem of target detection or classification,
@@
 Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.
-For example, allowing different authors to compare results quantitatively.
+For example, this would allow different authors to compare results quantitatively.
 
@@
 With fast and repeated experiments, the framework allows one to not only compute a single performance value on a single experiment, but also to analyze the whole behaviour of such performance measures over repeated stochastic simulations.
-\item Thus the computational framework provides significant help in deriving new performance evaluation criteria for statistical estimators.
+\item The computational framework provides significant help in deriving new performance evaluation criteria for statistical estimators.
 \end{enumerate}
@@
 \item Quantitative evaluation is possible not only via a single experiment on a single real-image but via repeated stochastic runs.
-\item Thus not only single values of mean or mean-squared-error are to be evaluated. 
+  Thus not only single values of mean or mean-squared-error are to be evaluated. 
 As the whole response PDF is available, statistical bias or heteroskedasticity can also be reported.
@@
                 enable an additive and homoskedastic statistical
-                framework, which is not only capable of overcome various
+                framework, which is not only capable of overcoming various
                 negative impacts of heteroskedasticity, but also results
@@
 In cases where theoretical PDF cannot be derived, simulated data are then generated
-  and their histograms are matched against real-life practical data for validation.
+  and their histograms are matched against real-life data for validation.
 
@@
 
-To evaluate the models’ application in statistical estimation framework, a practical point of view is adopted.
+To evaluate the application of these models in a statistical estimation framework, a practical point of view is adopted.
 Practically, all estimators would eventually need to be applied on and work for real images.
-Contrary to experiments on simulated data, experiments on real images often can only be compared qualitatively.
+Contrary to experiments on simulated data, experiments on real images can often only be compared qualitatively.
 This however is critical and will always be included in our investigations.
@@
 \section{Research Contributions}
+Interestingly, the dual-problems stated above are found to have a single solution.
+They are the derivation of scalar, representative and homoskedastic statistical models for the multidimensional, inter-correlated and heteroskedastic POLSAR data.
+%  which is
+
+%In what way is your solution different ? What is the novelty in your approach and hence solution?
+%In
+%                this thesis, the statistical model for the determinant
+%                of the POLSAR covariance matrix is proposed and
+%                validated.
+These theoretical models are studied and validated in this thesis.
+They are based on a highly representative observable, which is the determinant of the POLSAR covariance matrix.
+Out
+                of many different possible scalar projections of the
+                multi-dimensional data, the proposed projection is
+                highly representative.
+When the dimension number is collapsed to one, the
+                special case of the proposed model matches perfectly
+                with the commonly used statistical model for SAR
+                intensity.
+Furthermore,
+                the proposed statistical model also leads to the
+                derivation of existing as well as the newly proposed
+                discrimination measure: determinant-ratio which is the
+                generalized multi dimensional version of the widely used
+                SAR intensity ratio.
+
+ Another
+                novelty of the contributions in this thesis comes from the systematic
+                treatment towards the problem of statistical estimation
+                of heteroskedastic SAR data.
+While
+                many different ways to combat the negative impacts
+                caused by multiplicative and heteroskedastic properties
+                for SAR data have been proposed over the years, they have often been
+                handled in a piecemeal manner.
+Here,
+                a systematic homoskedastic framework of statistical
+                estimation is developed, where not only homoskedastic
+                statistical models are proposed, the impacts of
+                homoskedasticity on estimator development and
+                performance evaluation of statistical estimators is also
+                studied.
+This
+                comprehensive treatment not only explains why the
+                original SAR data requires special treatment very
+                different to the common practice of computational
+                sciences, 
+it
+                also encourages a thorough and unique discussion, for example on
+                evaluating different evaluation criteria for statistical
+                estimators.  % ;-)).
+And
+                since the POLSAR data can be considered as the multi
+                dimensional extension of traditional SAR data, these
+                treatments are shown extensible towards POLSAR data
+                which is definitely yet another novelty.
+
 % How do you know if the problem is solved?   State your research objectives
-Interestingly, the dual-problem stated above are found to have a single solution.
-They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
-  which is multidimensional, inter-correlated and heteroskedastic
-
-Specifically, the following sub-objectives are to be achieved
+Specifically, the following results are to be obtained:
 \begin{enumerate}
-\item                 To derive scalar and representative statistical models
+\item                Scalar and representative statistical models
                 for the multi-dimensional and inter-correlated POLSAR
-                data.
+                data are to be derived.
                 \begin{enumerate}
-                \item \label{itm:polsar_model} To derive a scalar statistical model for the
+                \item \label{itm:polsar_model} A scalar statistical model for the
                 POLSAR observable, being the determinant of the
-                covariance matrix.
-                \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
-                the observable being modeled 
-                \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
+                covariance matrix, is to be derived.
+                \item \label{itm:polsar_discrimination_measure} The statistical models for different discrimination measures which are based on
+                the observable are to be established together with its consistent property. %being modelled 
+                \item \label{itm:polsar_include_sar} The representation power of these observables is to be illustrated by showing
                 that when the multi-channel POLSAR data is collapsed
@@
                 intensity.
-                \item \label{itm:polsar_validation} To validate the model against practical real-life
+                \item \label{itm:polsar_validation} The model os to be validated against practical real-life
                 captured POLSAR data.
-                \item \label{itm:extend_sar_to_polsar} To demonstrate an example where an existing SAR
-                processing technique is extensible towards POLSAR data
                 \end{enumerate}
-\item                To derive homoskedastic statistical models for the
-                heteroskedastic (POL)SAR data. 
+\item                Homoskedastic statistical models for the
+                heteroskedastic (POL)SAR data are to be derived. 
                 \begin{enumerate}
-                \item \label{itm:log_transform} To show that (POL)SAR data are heteroskedastic in
+                \item \label{itm:log_transform} The fact that (POL)SAR data are heteroskedastic in
                 the original domain and logarithmic transformation
-                can convert this into a homoskedastic model.
-                \item \label{itm:sar_measures_distance} To derive homoskedastic measures of distance for
+                can convert this into a homoskedastic model are to be shown
+                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                 the multi dimensional POLSAR as well as for the one
-                dimensional SAR data.
-                \item \label{itm:sar_validation} To validate these statistical models against both
+                dimensional SAR data are to be derived.
+                \item \label{itm:sar_validation} These statistical models are to be validated against both
                 practical SAR and POLSAR data
-                \item To illustrate the beneficial applications of these
-                statistical models. Specifically:
+                \end{enumerate}
+\item The beneficial applications of these
+                statistical models are to be demonstrated. Specifically:
                 \begin{enumerate}
@@
                 suppression power.
-                \end{enumerate}
+                \item \label{itm:extend_sar_to_polsar} An example where an existing SAR
+                processing technique is extensible towards POLSAR data is to be demonstrated
                 \end{enumerate}
@@
 %After these models are validated against practical data, their beneficial applications are further explored.
-To combine these two seemingly disconnected threads of research, the above results for SAR are extended to POLSAR,
-  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.%***IVM I changed "version" to "superset" in the sentence above.
+To combine these two seemingly disconnected threads of research, the results for SAR are extended to POLSAR,
+  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.
+%***IVM I changed "version" to "superset" in the sentence above.
 Please check if you are comfortable with that change, and if not, change it back!
-Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
+%Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
 %The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
@@
 \section{Organisation of the Thesis}
-The rest of this thesis is organized into five chapters, as follows:
-The next chapter will survey the related publications
-  and state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter will be presented.
+The rest of this thesis is organized into five chapters as follows.
+
+Chapter \ref{chap:lit_survey} will survey the related publications
+  and the state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter. %will be presented.
 It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
-Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
+Through these discussions, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
 
@@
 %Specifically,
-The heart of is thesis contains several contributions which meet the stated objectives.
+
+%The heart of is thesis contains several contributions which meet the stated objectives.
                 Chapter \ref{chap:sar} begins by by highlighting that SAR
@@
                 logarithmic transformation converts this into a
-                homoskedastic model (Research Contribution \ref{itm:log_transform}). 
+                homoskedastic model. 
 It
                 also drives consistent and homoskedastic measures of
-                distance for the one dimensional SAR data (Research Contribution \ref{itm:sar_measures_distance}).
+                distance for the one dimensional SAR data.
 These
                 models for SAR are then validated against real-life
-                practical data (Research Contribution \ref{itm:sar_validation})
+                practical data. (i.e. see Research Contribution \ref{itm:log_transform} to \ref{itm:sar_validation})
 
@@
                 \ref{chap:polsar} then derives several scalar statistical models for the
-                determinant of the POLSAR covariance matrix (Research Contribution \ref{itm:polsar_model}) and
+                determinant of the POLSAR covariance matrix and
                 shows that this is heteroskedastic in the original
                 domain as well as homoskedastic in the log-transformed
-                domain (Research Contribution \ref{itm:log_transform}).
+                domain.
 It
                 also derives the heteroskedastic discrimination measures
-                (Research Contribution \ref{itm:polsar_discrimination_measure}) as well as several homoskedastic measures of
-                distance for the data (Research Contribution \ref{itm:sar_measures_distance}).
+                 as well as several homoskedastic measures of
+                distance for the data.
 Then
                 the models for SAR are shown to be a special case of
-                the proposed models for POLSAR (Research Contribution \ref{itm:polsar_include_sar}) and finally it
-                validates these proposed models (Research Contribution \ref{itm:polsar_validation})
+                the proposed models for POLSAR and finally it
+                validates these proposed models (i.e. see Research Contribution \ref{itm:polsar_model} to \ref{itm:polsar_validation})
 
@@
                 beneficial applications of these models is presented in
-                chapter \ref{chap:applications}, where the consistent sense of variance
-                property helps to break the vicious cycle in SAR
-                speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
+                chapter \ref{chap:applications}, where the property of a consistent sense of variance
+                 helps to break the vicious cycle in SAR
+                speckle filtering.
 It
-                also shows how MSE can be again applicable in the
+                also shows how MSE can again be applicable in the
                 additive and homoskedastic domain to evaluate SAR
-                speckle filters (Research Contribution \ref{itm:log_mse}).
+                speckle filters.
 An
@@
                 MSE evaluation criteria is also shown capable of
-                evaluating POLSAR speckle filters (Research Contribution \ref{itm:extend_sar_to_polsar}).
+                evaluating POLSAR speckle filters.
+(i.e. see Research Contribution \ref{itm:filter_vicious_circle} to \ref{itm:extend_sar_to_polsar})
 Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.

### 2013-07-31 1_introduction/introduction_ivm.tex
Final changes before submission to Alan???

--- 2013-07-24 1_introduction/introduction.tex
@@
 it
-                also allows thorough and unique discussion, for example on
+                also encourages a thorough and unique discussion, for example on
                 evaluating different evaluation criteria for statistical
@@
 %precise problem statement
-With this approach, the \textbf{main problem statement} of this thesis arise. %it is important to emphasize again the main problem statement of this thesis.
-That is
+With this approach, the \textbf{main problem statement} of this thesis arises. %it is important to emphasize again the main problem statement of this thesis.
+That is,
                 this thesis focuses on providing a solution for the
@@
 % How do you know if the problem is solved?   State your research objectives
-Interestingly, the dual-problem stated above are found to have a single solution.
+Interestingly, the dual-problems stated above are found to have a single solution.
 They are the derivation of scalar, representative and homoskedastic measures of distance for the POLSAR data
@@
                 \item \label{itm:polsar_discrimination_measure} To derive consistent discrimination measures for
-                the observable being modeled 
+                the observable being modelled 
                 \item \label{itm:polsar_include_sar} To illustrate its representation power by showing
@@
 It will also discuss the different measures of distance for both SAR and POLSAR data, together with their extensive applications. 
-Through these discussion, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
+Through these discussions, the need for a homoskedastic and scalar model for the multivariate and heteroskedastic POLSAR is brought forward.
 
@@
                 beneficial applications of these models is presented in
-                chapter \ref{chap:applications}, where the consistent sense of variance
-                property helps to break the vicious cycle in SAR
+                chapter \ref{chap:applications}, where the property of a consistent sense of variance
+                 helps to break the vicious cycle in SAR
                 speckle filtering (Research Contribution \ref{itm:filter_vicious_circle}).
 It
-                also shows how MSE can be again applicable in the
+                also shows how MSE can again be applicable in the
                 additive and homoskedastic domain to evaluate SAR

### 2013-07-31 2/literature_review.tex
Final changes before submission to Alan???

@@
 reviews the published literature for SAR and POLSAR data processing.
-Specifically, its first section describes the multi-dimensional and stochastic nature of the POLSAR data.
+Specifically, its first section describes the multi-dimensional and stochastic nature of the (POL)SAR data.
 The second section then illustrates the different approaches that have been published to address the grand challenge of modelling, processing and ultimately understanding these types of data.
 
-\section{The Stochastic and Multivariate Nature of POLSAR data}
+\section{The Stochastic and Multivariate Nature of (POL)SAR data}
 
@@
   d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation*},
+\end{equation*}
 where $tr(C)$ denotes the trace of the matrix C. 
@@
 \end{equation*}
-.
 
@@
 
-\subsection{Current Methods to Evaluate SAR Speckle Filters}
+\subsection{Current Techniques to Evaluate SAR Speckle Filters}
 
@@
 
-In the next chapters, theoretical models are built to form the foundation required to systematically tackle these issues.
+In the next chapter, theoretical models are developed to form the foundation required to systematically tackle these issues.

### 2013-07-31 3/sar.tex
Final changes before submission to Alan???

@@
 Relying solely on statistical and mathematical principles,             
-the log-transformed SAR data is shown to be homoskedastic.
+the log-transformed SAR data is then shown to be homoskedastic.
 From there, the consistent sense of variance and a few consistent measures of distance are proposed and validated against real-life
@@
 
-\begin{table}
+\begin{table}[H]
 \centering
-
+\small
 %awk -F"&" '{print $4}' tmp.0.txt | awk -F"(" '{print $1}'
@@
 
-\textbf{In summary}, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
+In summary, a few measurements of distance, being dispersion and contrast, are shown to agree with the consistent sense of variance and homoskedasticity.
 The dispersion measurement can be used to test 

### 2013-07-31 4/polsar.tex
Final changes before submission to Alan???

@@
 \end{equation}
-with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
+where $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$
 
@@
 Specifically:
+
 \begin{eqnarray*}
@@
 The results so far for our models can be summarized as:
+{\footnotesize
 \begin{align*}
@@
 \end{align*}
+}%
 
@@
 are consistent with not only the following results for single-look SAR derived earlier, i.e. $d =1,  L = 1$,
+
+{\footnotesize
 \begin{align*}  
@@
 \end{align*}
+}%
 but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
@@
 
-\begin{figure}[h]
+\begin{figure}[bth!]
 \centering
@@
   specifically between $S_{hh}$ and $S_{vv}$.
-This phenomena is also present in our AIRSAR dataset, where $\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}$.
+This phenomena is also present in our AIRSAR dataset, where
+${\Sigma_v = avg(C_v) = \begin{vmatrix} 0.0084 & 1 \cdot 10^{-6} + 4 \cdot 10^{-4} i & 0.0071 - 0.0017 i \\ 1 \cdot 10^{-6} - 4 \cdot 10^{-4} i & 0.0017 & -3 \cdot 10^{-4} - 2 \cdot 10^{-4} i \\ 0.0071 + 0.0017 i & -3 \cdot 10^{-4} + 2 \cdot 10^{-4} i & 0.0122 \end{vmatrix}}$.
 Despite the mismatch, the proposed model  is still valid under such conditions, as observed in the part-pol (HH-VV) and full-pol
@@
 
-In \textbf{summary}, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
+In summary, this chapter proposes the determinant of the POLSAR covariance matrix as the scalar and representative observable for the both partial and full polarimetric SAR data.
 Out of many different scalar projections of the multi-dimensional POLSAR data, this observable is proposed together with its underlying statistical model, from which consistent discriminant measures are also proposed.

### 2013-07-31 5/applications.tex
Final changes before submission to Alan???

@@
   which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
-filtering .
+filtering.
 This chapter also shows how the MSE can then be 
-applicable in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
+applied in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
  POLSAR speckle filters.
@@
 the statistical hypothesis test described in chapter \ref{chap:sar}. 
-If that is found to be the case, clustering algorithm can then be applied to partition the area into smaller regions. 
+If that is found to be the case, a clustering algorithm can then be applied to partition the area into smaller regions. 
 Thus an image can be segmented into homogeneous areas by applying the process repeatedly.
@@
 Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
-This section shows how $\sigma$ can be estimated in log-transformed domain.
+This section shows how $\sigma$ can be estimated in the log-transformed domain.
 
 It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$.
+%***IVM: Hai can you clarify the \ln 2 \frac{ 2^d }{ e^{2^d} }, is that a base 2 in there? Maybe some brackets would help....
 Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
@@
 Since log-transformed variables are biased, an MLE approach is used to estimate $\mu$. 
-The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of value X found in the area, given the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
+The MLE strategy aims to maximize the conditional (likelihood) probability of observing a set of values X found in the area, given that the underlying coefficient equals $\mu$: $P(X^l | \mu )$. 
 Assuming the values of $x^l_i$ are independent, the statistical product rule indicates that $P(X^l | \mu )=\displaystyle{\prod^n_{i=1}{P(x^l_i | \mu ) }}$, with  $P(x^l_i | \mu)$ as given in Eqn.
@@
 %$P(x^l_i | \mu ) = \ln 2 \frac{ 2^{x^l_i - \mu} }{ e^{2^{ x^l_i -\mu }} }$. 
-Maximize $P(X^e | \mu )$ also maximizes $\ln[P(X^l | \mu )]$, which can be written as:
+Maximizing $P(X^e | \mu )$ also maximizes $\ln[P(X^l | \mu )]$, which can be written as:
 
@@
 2^\mu 
-	= \frac{ \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }} }{n}  
+	= \frac{1}{n} \displaystyle{ \sum^n_{i=1}{ 2^{ x^l_i } }}  %***IVM: I edited this slightly to make it look 'nicer'. The same with the next eqn too...
 \label{eqn:mle_log_transform}
@@
 
-This result in the log-transformed domain is consistent with the analysis result in the original domain where $\sigma^2 = \frac{\sum^n_{i=1}{x^e_i}}{n} $, with $x^e_i = 2^{x^l_i}$
+This result in the log-transformed domain is consistent with the analysis result in the original domain where $\sigma^2 = \frac{1}{n}\sum^n_{i=1}{x^e_i}$, with $x^e_i = 2^{x^l_i}$
 
@@
 
-Due to the special characteristics of the log-transformed domain, 
+Due to the characteristics of the log-transformed domain, 
 an MLE estimator is used in lieu of the standard averaging estimation for cluster centers. 
@@
   for ( j = 1 to size(c) )
-    c_new[j] = maximum_likelyhood_of( l[i] with m[i,j]==1 );
+    c_new[j] = maximum_likelihood_of( l[i] with m[i,j]==1 );
   end for
@@
   \item In k-means, data points are grouped into clusters with minimum distance. 
-In our specific situation, as the dispersion PDF is non-symmetric around the cluster center, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
-  \item The calculation of new cluster centers is also different. 
+In our specific situation, as the dispersion PDF is non-symmetric around the cluster centre, log-transformed data points are assigned to the cluster that gives them highest likelihood probability.
+  \item The calculation of new cluster centres is also different. 
 In k-means, new cluster centres are estimated as the average of all membered data points. 
@@
 In the last section the algorithm was designed with the assumption that the number of clusters are known \textit{a priori}. 
-In practice, this is not the case. This section will describe how the issue is to be tackled.
+In practice, this is not the case. This section will describe how the issue can be tackled with real world data.
 
@@
 Then such an assumption is put to test using the hypothesis testing procedure described earlier. 
-If the assumption appears to be violated, the area is broken down by introducing a new cluster center. 
+If the assumption appears to be violated, the area is broken down by introducing a new cluster centre. 
 The clustering algorithm is again performed and the new clusters are again assumed to be homogeneous, and tested. 
@@
 
-\lstset{language=Matlab,caption=Homogenous partitions number growing,label=lst:k_mle_algo_partition_number}
+{\small
+\lstset{language=Matlab,caption=Homogeneous partitions number growing,label=lst:k_mle_algo_partition_number}
 \definecolor{darkgray}{rgb}{0.95,0.95,0.95}
@@
 function centers = partition_into_homogenous_groups(l, threshold)
-  c_init = maximum_likelyhood_of(l);
+  c_init = maximum_likelihood_of(l);
   [further_partition_needed, c_new] = 
@@
 \label{sec:k_mle_result}
+}%
 
@@
 
-The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastics noise can be removed.
-Hence the k-MLE clustering algorithm can be used to form the basis of a speckle filtering technique.
-Specifically the clustered areas directly serves as the grouping of pixels into homogeneous areas, and
-the cluster centers serves as the estimated backscattering coefficient for the analysis window.
-
-Considering the case where some extreme threshold-values are used as the homogeneous criteria
-If threshold-value is set to a very high value (close to 100\%), then a given partition would almost never be broken down.
+The principle of speckle filtering is to group pixels into homogeneous areas so that the stochastic noise can be removed.
+Hence the k-MLE clustering algorithm can be used to form the basis of a speckle filter.
+Specifically, the clustered areas directly serve as the grouping of pixels into homogeneous areas, and
+the cluster centres serve as the estimated backscattering coefficient for the analysis window.
+
+Considering the case where some extreme threshold-values are used as the homogeneous criteria,
+if threshold-value is set to be very high (close to 100\%), then a given partition would almost never be broken down.
 The kMLE speckle filter effect would then equals to a box-car filter. 
@@
 
-Figure \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
+Fig. \ref{fig:k_mle_diff_threshold} shows various degrees of speckle filtering controllable by using different threshold-values.
 Using the same moving window size of $3\times3$, the effect of filtering is clearly proportional to the threshold values employed.
@@
 One way to improve the speckle filtering  performance is to use a larger window size.
-Fig. \ref{fig:boxcar_5x5} shows the visual quality performance of k-MLE filtering on $5 \times 5$ window.
-As can be seen, the blurring effect in comparison to $3 \times 3$ filters is clearly visible.
+Fig. \ref{fig:boxcar_5x5} shows the visual quality performance of k-MLE filtering on $5\times5$ window.
+As can be seen, the blurring effect in comparison to the $3\times3$ filter is clearly visible.
 To reduce the associated blurring effect, a threshold-value lower than 100\%  would help by providing an adaptive partitioning of the analysis
@@
 Another way to improve the raw k-MLE speckle filter is to apply it iteratively.
-As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal 3x3 k-MLE filter would not filter as much noise as a 3x3 boxcar filter. 
-At the same time, a 5x5 boxcar filter while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
+As can be seen in Fig. \ref{fig:k_mle_diff_threshold}, a normal $3\times3$ k-MLE filter would not filter as much noise as a $3\times3$ boxcar filter. 
+At the same time, a $5\times5$ boxcar filter, while having better speckle suppression power, would lose out by its blurring effects as can be seen in Fig. \ref{fig:boxcar_5x5}. 
 To improve k-MLE filtering power while avoiding the blurring effect, the k-MLE speckle filter can be used iteratively. 
-Presented in the figure \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a 3x3 window with 25\% threshold-value, being applied iteratively for four times. 
-From the plot, the $3 \times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5 \times 5$ boxcar filter,
+Presented in the Fig. \ref{fig:k_mle_filtering_power} is the result of a k-MLE filter configured in a $3\times3$ window with 25\% threshold-value, being applied iteratively for four times. 
+From the plot, the $3\times 3$ iterative k-MLE filter appears to have similar quantitative performance with the $5\times5$ boxcar filter,
   while its visual imagery output appears much sharper, qualitatively speaking.
@@
 	\hfill
-	\subfloat[Homogenous Error in log-domain]{
+	\subfloat[Homogeneous Error in log-domain]{
 		 \epsfxsize=2.5in
@@
 \end{tabular}
-\caption{Improving Homogenous error with iterative k-MLE filter}
+\caption{Improving Homogeneous error with iterative k-MLE filter}
 \label{fig:k_mle_filtering_power}
@@
 Qualitatively speaking, it is clear that the kMLE speckle filter delivers
-a resultant image with both sharper edges than the 5x5 boxcar filter and a stronger visual contrast  than the 3x3 boxcar filter.
+a resultant image with both sharper edges than the $5\times5$ boxcar filter and a stronger visual contrast  than the $3\times3$ boxcar filter.
 %a sharper image than the 5x5 boxcar filter, at the same time its result has better contrast than the 3x3 boxcar filter.
@@
 The k-MLE filters are also applied on a SLC RadarSat 2 image covering the Muada Merbok area of Malaysia. 
-Figure \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
-It is obvious that the kMLE speckle filter delivers a significantly ``better'' image than the original data.
+Fig. \ref{fig:k_mle_on_RADARSAT2_data} shows the patches of original and filtered images of both natural and urban landscape.
+It is obvious that the k-MLE speckle filter delivers a significantly ``better'' image than the original data.
 
@@
 
-As mentioned earlier, speckle filters removes the stochastic noise by grouping data into homogeneous areas. 
+As mentioned earlier, speckle filters remove the stochastic noise by grouping data into homogeneous areas. 
 In the boxcar filter, the filtering process can be described via Eqn. \ref{eqn:boxcar}, 
@@
 	$I_i$ is the intensity value of pixel \textit{i} and
-	$n$ is the total number of pixel in the surrounding areas.
+	$n$ is the total number of pixels in the surrounding areas.
 The implicit assumption for this filter is that ALL pixels in the surrounding area belongs to the same homogeneous area with the estimating central point.
@@
 %The f-MLE speckle filter presented
-In this section fuzzy logic approach is followed
+In this section, a fuzzy logic approach is followed
   where, instead of fixing on a rigid two-member set of logical values (i.e. true and false),
-  embraces truth values that range from 1 to 0.
-Thus instead of making a YES/NO decision on whether or not a data point is in the same homogeneous region with the estimated central point, a fuzzy probabilistic scale is calculated.
-Then the noise-removal impact of the surrounding data point will be scaled with this probability value.
+the system  embraces truth values that range from 1 to 0.
+Thus instead of making a YES/NO decision on whether or not a data point is in the same homogeneous region as the estimated central point, a fuzzy probabilistic scale is calculated.
+Then the noise-removal impact of the surrounding data points will be scaled with this probability value.
 This fuzzy logic approach give rise to the f-MLE speckle filter presented next,
@@
 
-\subsection{The F-MLE SAR Speckle Filters}
+\subsection{The f-MLE SAR Speckle Filters}
 
@@
 $C= L_I^1 - L_I^2$. 
-Assuming $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
-  then this dis-similarity distance will follow the distribution 
+Assuming that $I^i$ follows a negative exponential distribution \citep{Goodman_JOptSocAm_76}, 
+  then this dissimilarity distance will follow the distribution 
 $pdf(C)= \frac{2^C}{(1+2^C)^2} \ln2$,
@@
 
-\subsubsection{F-MLE Estimation}
-
-In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the center point $I_0$ has a likelihood of being in the same homogeneous area given as: 
+\subsubsection{f-MLE Estimation}
+
+In this fuzzy logic approach, a pixel with intensity value $I_i$ in the surrounding area of the centre point $I_0$ has a likelihood of being in the same homogeneous area given as: 
 $p_i = pdf(C_i)$, with $C_i=log_2(I_i) - log_2(I_0)$.
-The fMLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.
+The f-MLE approximation is then proposed as written in Eqn. \ref{eqn:fmle_incl}.
 
@@
 In implementing this statistical estimator, there are very noticeable black dots in the filtered output image.
-These dots can be explained as the long-tailed nature of the intensity PDF, 
+These dots can be explained by the long-tailed nature of the intensity PDF, 
   which manifests itself in the significant existence of very small values in the population.
@@
 \label{eqn:fmle_incl}
-\caption{eqn:F-MLE Estimation (Inclusive Version)}
+\caption{eqn:f-MLE Estimation (Inclusive Version)}
 FMLE_{incl}= \frac{\displaystyle{\sum_{i=0}^n{p_i * I_i} } }{\displaystyle{\sum_{i=0}^n{p_i } } }
@@
 \label{eqn:fmle_excl}
-\caption{eqn:F-MLE Estimation (Exclusive Version)}
+\caption{eqn:f-MLE Estimation (Exclusive Version)}
 FMLE_{excl}= \frac{\displaystyle{\sum_{i=1}^n{p_i * I_i} } }{\displaystyle{\sum_{i=1}^n{p_i } } } 
@@
 %demonstrated in Figure \ref{fig:compare_filters_histograms:Original}.
-%For comparison, the two schemes’ histogram are plotted in the same figure.
+%For comparison, the two schemesà¥ˆ€™ histogram are plotted in the same figure.
 %In comparing the two schemes' histogram in the same figure,
@@
   }
-\caption{Consistent Distance Property and the F-MLE Estimations}
+\caption{Consistent Distance Property and the f-MLE Estimations}
 \end{figure}
@@
 	}\\ 
- 	\subfloat[F-MLE (incl) outputs\label{fig:compare_filters_distance_histograms:Filtered:incl}]{
+ 	\subfloat[f-MLE (incl) outputs\label{fig:compare_filters_distance_histograms:Filtered:incl}]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[F-MLE (excl) outputs\label{fig:compare_filters_distance_histograms:Filtered:excl}]{
+	\subfloat[f-MLE (excl) outputs\label{fig:compare_filters_distance_histograms:Filtered:excl}]{
 		 \epsfxsize=6cm
@@
 \end{tabular}
-\caption{Consistent Distance Property and the F-MLE Estimations}
+\caption{Consistent Distance Property and the f-MLE Estimations}
 \label{fig:Consistent_Distance_Property_and_the_FMLE_Estimations}
@@
 \ref{fig:compare_filters_histograms:Original}.
-They clearly demonstrate that the F-MLE speckle filters preserves the consistent sense of distance.
+They clearly demonstrate that the f-MLE speckle filters preserve the consistent sense of distance.
 This can be explained from the consistent histogram of the input log distance PDF.
 
-Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves large number of random variables.
+Unfortunately, the filtering formula given in Eqn. \ref{eqn:fmle_incl} and Eqn. \ref{eqn:fmle_excl}, especially when applied to large image areas, involves a large number of random variables.
 %This renders the task of giving analytical PDF for the output log-distance impractical.
@@
 %Simulating experiments with $10^6$ samples is carried out and the histogram information is saved.
-Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by intrapolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.
-
-\subsubsection{Recursively Applying The F-MLE Filters}
-
-The preservation of consistent distance property is the enabling factor that allows the recursive application of F-MLE filters.
+Specifically, given a distance $d$, its corresponding probability $pdf(d)$ can be simulated by interpolating from the saved histogram $y\equiv hist(x)$ at the value of $x \equiv d$.%***IVM: Hai, you had made up a word "intrapolating".
+It should be either "extrapolating" or "interpolating"...
+so I've replaced it with the latter...
+
+\subsubsection{Recursively Applying The f-MLE Filters}
+
+The preservation of consistent distance property is the enabling factor that allows the recursive application of f-MLE filters.
 Additional execution of the filtering process is be expected to further reduce the random noise power / variance even further.
@@
 \centering
-	\subfloat[F-MLE (incl): 123]{
+	\subfloat[f-MLE (incl): 123]{
 		 \epsfxsize=3.5cm
@@
 	}
-	\subfloat[F-MLE (incl): 456]{
+	\subfloat[f-MLE (incl): 456]{
 		 \epsfxsize=3.5cm
@@
 	} 
-	\subfloat[F-MLE (excl): 123]{
+	\subfloat[f-MLE (excl): 123]{
 		 \epsfxsize=3.5cm
@@
 	}
-	\subfloat[F-MLE (excl): 456]{          
+	\subfloat[f-MLE (excl): 456]{          
 		 \epsfxsize=3.5cm
@@
 
-\subsection{Evaluating the F-MLE SAR speckle filters}
+\subsection{Evaluating the f-MLE SAR speckle filters}
 
@@
 
-The performance of the F-MLE filter is evaluated both qualitatively against real
+The performance of the f-MLE filter is evaluated both qualitatively against real
 images and quantitatively via simulated experiments. 
@@
 	}\\
-	\subfloat[F-MLE incl, iter 1]{
+	\subfloat[f-MLE incl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[F-MLE incl, iter 2]{
+	\subfloat[f-MLE incl, iter 2]{
 		 \epsfxsize=6cm
@@
 	} \\
-	\subfloat[F-MLE excl, iter 1]{
+	\subfloat[f-MLE excl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \hfill
-	\subfloat[F-MLE excl, iter 2]{
+	\subfloat[f-MLE excl, iter 2]{
 		 \epsfxsize=6cm
@@
 	\end{tabular}
-\caption{Qualitative Evaluation of F-MLE filter on Real Life Scene of Natural Surface}
+\caption{Qualitative Evaluation of f-MLE filter on Real Life Scene of Natural Surface}
 \label{fig:fmle.real.images}
@@
 	} \\
-	\subfloat[F-MLE incl, iter 1]{
+	\subfloat[f-MLE incl, iter 1]{
 		 \epsfxsize=6cm
@@
 	} \\ 
-	\subfloat[F-MLE excl, iter 1]{
+	\subfloat[f-MLE excl, iter 1]{
 		 \epsfxsize=6cm
@@
 	\end{tabular}
-\caption{Qualitative Evaluation of F-MLE filter on Real Life Scene of Urban Landscape}
+\caption{Qualitative Evaluation of f-MLE filter on Real Life Scene of Urban Landscape}
 \label{fig:fmle.real.images}
@@
 
-We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Look value.
+We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Looks value.
 Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
@@
      \end{tabular}
-\caption{Homogeneous Area: MSE criteria and speckle suppression power of F-MLE filters}
+\caption{Homogeneous Area: MSE criteria and speckle suppression power of f-MLE filters}
 \label{fig:Homogeneous_Area}
@@
 The following experiment illustrates this point.
-In this experiment, we apply a simple 3x3 boxcar filter to two different homogeneous and SLC noise corrupted scenes that are known to be 3dB apart.
+In this experiment, we apply a simple $3\times3$ boxcar filter to two different homogeneous and SLC noise corrupted scenes that are known to be 3dB apart.
 And then the histograms as well as the resulting ROC curve are plotted between the pairs of target and background histogram for both cases of unfiltered and filtered data.
-We noted that the ROC curve for the histograms in original domain matches perfectly with ROC for the histograms in the log-transformed domain (see Fig.
+We note that the ROC curve for the histograms in original domain matches perfectly with the ROC for the histograms in the log-transformed domain (see Fig.
 \ref{fig:PDF_Discriminality}), as expected from theory.
@@
    \end{tabular}
-\caption{Histogram Discriminality and the ROC Curve}
+\caption{Histogram discriminality and the ROC Curve}
 \label{fig:PDF_Discriminality}
@@
 The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
-Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of F-MLE filters for heterogenous regions.
+Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of f-MLE filters for artificially-generated heterogenous test regions.
 Apparently the f-MLE filters have better performance than boxcar filters.
@@
 \hline
-Point Target 	& F-MLE (incl, 3x3) 	& 1.38	& 0.901 \\
-Point Target 	& F-MLE (excl, 3x3) 	& 1.47	& 0.893 \\
+Point Target 	& f-MLE (incl, 3x3) 	& 1.38	& 0.901 \\
+Point Target 	& f-MLE (excl, 3x3) 	& 1.47	& 0.893 \\
 Point Target 	& boxcar (3x3) 			& 1.56	& 0.826 \\
@@
 \hline
-Edge 	& F-MLE (incl, 3x3) 	& 0.68	& 0.969 \\
-Edge 	& F-MLE (excl, 3x3) 	& 0.73	& 0.964 \\
+Edge 	& f-MLE (incl, 3x3) 	& 0.68	& 0.969 \\
+Edge 	& f-MLE (excl, 3x3) 	& 0.73	& 0.964 \\
 Edge 	& boxcar (3x3) 			& 1.03	& 0.942 \\
@@
 \hline
-Line 	& F-MLE (incl, 3x3) 	& 1.89	& 0.791 \\
-Line 	& F-MLE (excl, 3x3) 	& 2.02	& 0.767 \\
+Line 	& f-MLE (incl, 3x3) 	& 1.89	& 0.791 \\
+Line 	& f-MLE (excl, 3x3) 	& 2.02	& 0.767 \\
 Line 	& boxcar (3x3) 			& 2.27	& 0.658 \\
@@
 \hline
-Dotted 			& F-MLE (incl, 3x3) 	& 2.28	& 0.639 \\
-Dotted 			& F-MLE (excl, 3x3) 	& 2.32	& 0.621 \\
+Dotted 			& f-MLE (incl, 3x3) 	& 2.28	& 0.639 \\
+Dotted 			& f-MLE (excl, 3x3) 	& 2.32	& 0.621 \\
 Dotted 			& boxcar (3x3) 			& 2.92	& 0.431 \\
@@
 %\end{tabular}
-\caption{Heterogeneous Patterns: MSE criteria and F-MLE performance}
+\caption{Heterogeneous Patterns: MSE criteria and f-MLE performance}
 \label{fig:Heterogeneous_Patterns}
@@
 The nature of SAR speckle is stochastic. 
-The speckle filtering problem has been casted into a statistical estimation theory framework. 
-Speckle filtering, by and large, means the removal of stochastic component in SAR images. 
+The speckle filtering problem has been cast into a statistical estimation theory framework. 
+Speckle filtering, by and large, means the removal of stochastic components from SAR images. 
 Log-transformation is shown to provide homoskedasticity in statistical models. 
-Using speckle filtering as an applicative example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.
+Using speckle filtering as an application example, these homoskedastic features are shown to be useful. %here to improve speckle-filtering.
 
@@
 a probabilistic approach, the proposed Fuzzy Maximum Likelihood Estimator makes
-use of this consistency. Experimental results suggest that the estimator’s output also
+use of this consistency. Experimental results suggest that the estimatorà¥ˆ output also
 exhibits this consistency property, which allows recursive application of the filter discussed above.
@@
 Multi-look processed image speckle filtering should be possible to use this technique with some minor adaptations. 
-The fMLE approach is developed from an easy to understand winner-take-all kMLE clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
+The f-MLE approach is developed from an easy to understand winner-take-all k-MLE clustering approach. %to a more fuzzy probabilistic clustering algorithm. 
 With the fuzziness be taken to a new level, fuzzy probabilistic speckle filters which requires no clustering have been specified and designed.
 
-The filter is rigoriously evaluated.
+The filter is rigorously evaluated.
 Over homogeneous regions, the speckle suppression power is
@@
 The results suggest that by applying the estimation recursively, this value can be reduced arbitrarily low, assuming that the number of iterations, and hence the available computational power, is sufficiently large.
+%***IVM: Hai, I don't like this statement "this value can be reduced arbitrarily low". Surely there is a performance floor which is data and technique-dependent, and below which you cannot go?
 For heterogeneous scenes, the robust Area Under the ROC Curve criteria is used as
@@
 and surface classification. 
-Experiments confirm the power of F-MLE filters in various
+Experiments confirm the power of f-MLE filters in various
 heterogeneously simulated areas. 
 A good correlation between the MSE and the AUC index is also exhibited. 
-The result suggests that lower MSE achievable by F-MLE filters does lead to better performance in the subsequent tasks of target detection and classification.
+The result suggests that lower MSE achievable by f-MLE filters does lead to better performance in the subsequent tasks of target detection and classification.
 
@@
 	it is stochastic even if the underlying radiometry is constant. 
-And when there are spatial radiometric variation, not only its expected value changes, its heteroskedastic variance varies as well.
+And when there is spatial radiometric variation, not only its expected value changes, but its heteroskedastic variance changes as well.
 Nevertheless, statistical models have been developed to derive the underlying back-scattering coefficient ($\sigma$) from measured SAR data. 
@@
 SAR speckle-filtering can be, and has been, positioned within the context of estimation theory \cite{Touzi_2002_TGRS}. 
-The stages in this statistical framework consist of statistical modeling, estimator development and evaluation of the estimators' performance. 
+The stages in this statistical framework consist of statistical modelling, estimator development and evaluation of the estimators' performance. 
 %Estimators are typically evaluated based on the bias and variance properties of their estimates: 
@@
 However owing to the additive and homoskedastic effects of the log-transformation,
-  the error measured in log-transformed domain is preferred here.
+  the error measured in the log-transformed domain is preferred here.
 This is because homoskedasticity would allow the use of standard Minimum Squared Error as a performance index.   
@@
  \centering
- \epsfxsize=2.4in
- \epsfysize=1.2in
+ \epsfxsize=4.8in
+ \epsfysize=2.4in
  \epsffile{images/simulation_schema.eps} 	
@@
 \end{figure}
+%***IVM: Can you make the text bigger, or just increase the figure size? A width of about 12cm would probably be OK.
 
@@
 real RADARSAT SAR image.
-``Visible'' structure appears to be more easily discerniable in the log-2 residual random pictures than in 
+``Visible'' structure appears to be more easily discernable in the log-2 residual random pictures than in 
 the ratio images, although this conclusion is of course itself a subjective one.
@@
 Different metrics to evaluate speckle filters, which will be investigated in subsequent sections, 
-are given in Eqns. \ref{eqn:eval_metric}, all in log-transformed domain.
+are given in Eqns. \ref{eqn:eval_metric}, all in the log-transformed domain.
 When the ground-truth is available, 
-	either in simulated experiments or over homogeneous area where it can be reasonably estimated, 
+	either in simulated experiments or over homogeneous areas where it can be reasonably estimated, 
 	true MSE is the expected squared error between the estimated and true values.
@@
 The idea is that since both the speckled values and the estimated values are available, the residual $MSE_{noise}$ 
-can be computed, which can be thought of as the level of noise being removed by speckle filtering process.
+can be computed, which can be thought of as the level of noise being removed by a speckle filtering process.
 Even as the ground-truth is not known in real SAR images, their speckle level (i.e. ENL) may be known or can be 
@@
 %Assumming that the speckle level of the scene is known (e.g. ENL can be reasonably estimated) then the base 
-That is $MSE_{noise}$ should track the base MSE as close as possible,
+That is, $MSE_{noise}$ should track the base MSE as close as possible,
   making the $MSE_{benchmark}$ as close to 0 as possible.
@@
 
-In this section, a methodology to evaluate speckle filters over homogeneous area in the log-transformed domain is 
+In this section, a methodology to evaluate speckle filters over homogeneous areas in the log-transformed domain is 
 illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
@@
 %Since multi-look processing is unbiased, we will take the variance of log-transformed multi-look processing output as the MSE performance index. 
-Hoek \cite{Hoekman_1991_TGRS} and Xie \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
+Hoekmen \cite{Hoekman_1991_TGRS} and Xie et. al. \cite{Xie_2002_TGRS} have given the variance for L-look log-transformed random 
 variables as: 
@@
 	to evaluate scene heterogeneity.
+	%****IVM: just check these are single authors, otherwise you need an "et al" or to name them if there are two authors.
 
@@
 
-Over homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
+Over an homogeneous area, the ground-truth is unchanged, i.e. $X^L_i=X^L \forall i$.
 Assuming the filters achieve negligible bias, i.e. $E(\hat{X}^L)=X^L$, 
@@
 
-Fig. \ref{fig:log_consistency_model} plots the histograms of homogenous SAR data over different radiometric values.
+Fig. \ref{fig:log_consistency_model} plots the histograms of homogeneous SAR data over different radiometric values.
 Both single-look simulated and multi-look processed/box-car filtered data is displayed.
@@
 \end{tabular}
-\caption{ Filters' Performance: Homogeneous Area }
+\caption{Performance of various filters over homogeneous areas}
 \label{tab:homogeneous_performance_filters}
@@
 
-Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
-evaluated by examining the separability of the two background and target populations.
-Figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
-	allows visual evaluation of target and clutter histograms and their separability.
-Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
-in subfigures \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
-respectively, and is measured by computing the Area Under these Curves (AUC).
-
 \afterpage{\clearpage}
@@
 
-Detailed examination of figures \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
+Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
+evaluated by examining the separability of the two background and target populations.
+Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+	allows visual evaluation of target and clutter histograms and their separability.
+Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
+in Figs. \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
+respectively, and is measured by computing the Area Under these Curves (AUC).
+
+%\afterpage{\clearpage}
+\begin{figure}[h!]
+\centering  
+\begin{tabular}{c}
+	\subfloat[Error Image: Unfiltered]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/heterogenous_patterns.edge.none.gt.jpg.eps} 	
+		 \label{fig:hetero_patterns_mse:amplitude}
+	} 
+	\hfill	
+	\subfloat[Error Image: Kuan Filtered]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
+		 \label{fig:hetero_patterns_mse:intensity}
+	} \\
+	\subfloat[Error Histograms: Unfiltered]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
+		 \label{fig:hetero_patterns_mse:unfiltered}
+	} 
+	\hfill	
+	\subfloat[Error Histograms: Kuan-filtered]{
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
+		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
+		 \label{fig:hetero_patterns_mse:kuan_filtered}
+	}  
+\end{tabular}
+\caption{Bias Error Investigation: Image and Histogram Visualisation}
+\label{fig:hetero_patterns_mse}
+\end{figure}
+
+Detailed examination of Figs. \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
 	can help to explain how the MSE is related to the histograms' separation capability.
-In pre-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
+In pre-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
 \ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
@@
 
-In post-filtered images, shown in figures \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
+In post-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
 \ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
@@
 The results suggest that the lower MSE achievable by a SAR speckle filter would, in general, lead to better feature preservation in its filtered output.
-
-%\afterpage{\clearpage}
-\begin{figure}[h!]
-\centering  
-\begin{tabular}{c}
-	\subfloat[Error Image: Unfiltered]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/heterogenous_patterns.edge.none.gt.jpg.eps} 	
-		 \label{fig:hetero_patterns_mse:amplitude}
-	} 
-	\hfill	
-	\subfloat[Error Image: Kuan Filtered]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/heterogenous_patterns.edge.kuan.gt.jpg.eps} 	
-		 \label{fig:hetero_patterns_mse:intensity}
-	} \\
-	\subfloat[Error Histograms: Unfiltered]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/heterogenous_patterns.histograms.edge.none.gt.png.eps} 	
-		 \label{fig:hetero_patterns_mse:unfiltered}
-	} 
-	\hfill	
-	\subfloat[Error Histograms: Kuan-filtered]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/heterogenous_patterns.histograms.edge.kuan.gt.png.eps} 	
-		 \label{fig:hetero_patterns_mse:kuan_filtered}
-	}  
-\end{tabular}
-\caption{Bias Error Investigation: Image and Histogram Visualisation}
-\label{fig:hetero_patterns_mse}
-\end{figure}
 
@@
 		 \label{intensity}
-	} %\\
+	} %\\   %****IVM: Hai, I think you need to say where (i.e.
+which satellite/agency) you got the data from, before you show the picture (or in the same page), I think you show the picture first and then mention where it's from afterwards.
 %	\subfloat[NTU Campus]{
@@
 	one should note that the noise is not Gaussian. In fact, figures presented in the previous sections show that 
-	they are not even centered around the origin. 
+	they are not even centred around the origin. 
 This may explain why averaging filters in the log-transformed domain (e.g. \cite{Arsenault_JOptSocAm_1976}) do not 
@@
 	the newly designed filters would be eligible to be employed as pre-processing step for properly designed classifiers / detector.
-From a higher level perspective, the applicability of Gauss-Markov theorem and consequently a meaningful MSE 
+From a higher level perspective, the applicability of the Gauss-Markov theorem and consequently a meaningful MSE 
   predict fruitful applications for a variety of least-squared-error algorithms in the homoskedastic log-transformed domain.
@@
 	using the MSE criteria, which tend to favour the ``standard'' filters.
-While we respect any other criteria that have been used, we reiterate the two salient points of our approach. 
+While we respect other criteria that have been used, we reiterate the two salient points of our approach: 
 Firstly, our MSE criteria is closely related to the basic ENL criteria.
@@
 
-In the experiments above, speckle filters with a $3 \times 3$ sliding window were used 
+In the experiments above, speckle filters with a $3\times3$ sliding window were used 
 	even though we are aware that the normal window size employed is much larger. 
@@
 	and did not directly address the design of speckle filters.
-However, interested filter designers are invited to download the open Matlab source code used in this paper 
+However, interested filter designers are invited to download the open Matlab source code used in this chapter 
 to evaluate their own designs
@@
 While the proposed rule is heuristic, 
-	the experimental results presented in this paper are shown to be valid empirically.
+	the experimental results presented in this chapter are shown to be valid empirically.
 
@@
 	would not perform that well.
-While the ranking of the speckle filters may change, the methodology to compare and choose the ``best’’ speckle filter should work regardless of the choice of patterns.
+While the ranking of the speckle filters may change, the methodology to compare and choose the ``best'' speckle filter should work regardless of the choice of patterns.
 
@@
 
-Our contribution is mainly centered around a few points. 
+Our contribution is mainly centred around a few points. 
 Firstly, a mathematical equation is established to link the ENL index to the variance in the log-transformed domain. 
@@
 %The result suggests that the smaller MSE a filter could achieve, the easier it would be discriminating the underlying radiometric features.
-Thirdly, the practical contribution is to suggest an heuristic rules using the benchmark MSE to find 
+Thirdly, the practical contribution is to suggest heuristic rules using the benchmark MSE to find 
 the most suitable speckle filter for any given scene. 
@@
 %\end{equation}
-Theoretically speaking, the Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be solved for the unknown L, which would require some iterative, and hence intensive, computation.
+Theoretically speaking, the Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be solved for the unknown $L$, which would require some iterative, and hence intensive, computation.
 Extending the result in the previous sub-section for SAR, simpler estimation can be derived as:
@@
 In the case of partial POLSAR, d=2, then
+{\small
 \begin{align*}
@@
 \end{align*}
+}%
 %Similar to the SAR case, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2)$.
@@
 In the case of full POLSAR, d=3, then
+{\small
 \begin{align*}
@@
 & 1/L + 1/(L-1) + 1/(L-2) < var_3 \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3) &\\
-\noindent \text{With } L>3 \\
+\noindent \text{As } L>3 \\
 & var_3 \left[ \ln |C_v| \right] = 3/(L-1.5) &\\
@@
 \end{align*}
+}%
+
 %Again, $var[ln|Cv|]$ is bounded: $1/L + 1/(L-1) + 1/(L-2) < var_d \left[ \ln |C_v| \right] < 1/(L-1) + 1/(L-2) + 1/(L-3)$.
@@
   the filter is applied over any known homogeneous areas and the sample variance of log-determinant is measured.
-The Equivant Number of Look (ENL) is then estimated
+The Equivalent Number of Looks (ENL) is then estimated
   either by referencing the prepared graphs given by Eqn. \ref{eqn:var_log_det_is_homoskedastic}. %TODO:REF
@@
 The estimated ENL and equivalently the measured log-variance is finally used to evaluate the speckle suppression power of the filters.
-It is common consensus that higher the ENL estimated,
-  which also means lower the log-variance measured,
-  leads to better POLSAR speckle filters in terms of suppressing speckle noise.
+It is common consensus that the higher the ENL estimated,
+  implies the lower the log-variance measured,
+  leading to better POLSAR speckle filters in terms of suppressing speckle noise.
 
@@
   it is important that the given POLSAR speckle filter preserve the consistency property in the log-transformed domain.
-That can be tested by applying the POLSAR filter into different sets of homogeneous area and investigate the plots of the measures of distance presented above.
+That can be tested by applying the POLSAR filter into different sets of homogeneous areas and investigating the plots of the measures of distance presented above.
 %Fig. \ref{fig:boxcar_3x3_preserves_consistency} presents two example plots to show that:
 An experiment is carried out as follows to show that
-  the 3x3 POLSAR boxcar speckle filter preserves the consistency property.
+  the $3\times3$ POLSAR boxcar speckle filter preserves the consistency property.
 The boxcar filter is applied into 2 sets of part-pol AIRSAR data over Flevoland (HH-HV and VH-VV).
@@
   while the location of the filtered plots differs depending on the underlying signal $\Sigma_v$,
-  the shape of the plots, for both pre-filtered and post-filtered data, is invariant to that underlying signal.
+  the shape of the plots, for both pre-filtered and post-filtered data, is invariant to the underlying signal.
 Contrast, and similarly dispersion, measures of distance have its location independent of $\Sigma_v$.
@@
 \begin{tabular}{c}
-	\subfloat[Log-determinants histograms of boxcar 3x3 speckle filter]{
+	\subfloat[Log-determinants histograms of boxcar $3\times3$ speckle filter]{
 		 \epsfxsize=6cm
@@
 	\hfill	
-	\subfloat[Contrast histograms of boxcar 3x3 speckle filter]{
+	\subfloat[Contrast histograms of boxcar $3\times3$ speckle filter]{
 		 \epsfxsize=6cm
@@
 \end{tabular}
-\caption{POLSAR 3x3 boxcar filter preserves the consistency property.
+\caption{POLSAR $3\times3$ boxcar filter preserves the consistency property.
 Consistency means: as long as the area is homogeneous, regardless of the underlying signal $\Sigma_v$ the shapes of the histograms should be the same.}
@@
 %    which is based on the scalar and consistent measures of distance would work on both pre-filtered and post-filtered data.
-The consistency property of POLSAR speckle filter is important
+The consistency property of POLSAR speckle filters is important
   not only to make the estimation of ENL become general enough.
@@
 
-Over heterogeneous area, the consistent measures of distance may also be an important tools to help evaluating POLSAR speckle filters.
+Over heterogeneous areas, the consistent measures of distance may also be an important tool to help evaluate POLSAR speckle filters.
 For a start, since the model for log-determinant is additive and homoskedastic,
-  log-determinant images is naturally more suitable for gray-level digital images.
+  log-determinant images is naturally more suitable for grey-level digital images.
 In particular for evaluation of statistical estimators,
@@
 
-Ideally speaking, under the context of additive model,
+Ideally speaking, under the context of an additive model,
   the perfect estimators' residual should only consists of random noise.
-And Gauss-Markov theorem, which works under the assumption of homoskedasticity, states that the optimal estimator should have minimal Mean Squared Error.
-When the underlying signal is not known apriori,
-  the second best gauge is possibly having the MSE of residual being equals or being as close as possible to the MSE of the inherent noise.
+The Gauss-Markov theorem, which works under the assumption of homoskedasticity, states that the optimal estimator should have minimal Mean Squared Error.
+When the underlying signal is not known \textit{a priori},
+  the second best gauge is possibly having the MSE of the residual being equal or being as close as possible to the MSE of the inherent noise.
 
@@
 
-To illustrate the above analysis, an experiment is carried out to evaluate the performance of boxcar 3x3 and boxcar 5x5 POLSAR filter on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-A square 700x700 portion of the AIRSAR dataset is extracted,
+To illustrate the above analysis, an experiment is carried out to evaluate the performance of boxcar $3\times3$ and boxcar $5\times5$ POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+A square $700\times700$ portion of the AIRSAR dataset is extracted,
   and the two POLSAR speckle filters are applied on to the patch.
@@
 \begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3x3 speckle filter]{
+	\subfloat[Log-determinant Image of boxcar $3\times3$ speckle filter]{
 		 \epsfxsize=6cm
@@
 	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5x5 speckle filter]{
+	\subfloat[Log-determinant Image of boxcar $5\times5$ speckle filter]{
 		 \epsfxsize=6cm
@@
 	} \\
-	\subfloat[Image of Log-determinant Residual for 3x3 filter (MSE=1.5594)]{
+	\subfloat[Image of Log-determinant Residual for $3\times3$ filter (MSE=1.5594)]{
 		 \epsfxsize=6cm
@@
 	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5x5 filter (MSE=2.1420)]{
+	\subfloat[Image of Log-determinant Residual for $5\times5$ filter (MSE=2.1420)]{
 		 \epsfxsize=6cm
@@
 \end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3x3 vs. 5x5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
+\caption{Visually Evaluating POLSAR Boxcar $3\times3$ vs. $5\times5$ Speckle Filters on AIRSA Flevoland part-pol data (HH-HV) with expected MSE=1.0312 at ENL=4. }
 \label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
@@
 
-In visual and qualitative evaluation, Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only the log-determinant image can offer nice visualization of the scene, 
+In visual and qualitative evaluation, Fig.
+\ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only can the log-determinant image offer a nice visualization of the scene, but
   the residual images also help in visualizing the distortion impact of the filter. % can also be made visible by the residual image.
-Specifically, while it is quite hard to observe the worsening blurring-effects of the 5x5 boxcar speckle filter as compared to the 3x3 filter
+Specifically, while it is quite hard to observe the worsening blurring-effects of the $5\times5$ boxcar speckle filter as compared to the $3\times3$ filter
 in the additive log-determinant image of the filtered output, 
@@
   where the residual MSE is compared with the expected level of noise to be removed,
-  the excessive blurring effects of the 5x5 filter become crystal clear.
-In fact, even the 3x3 boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.
+  the excessive blurring effects of the $5\times5$ filter become crystal clear.
+In fact, even the $3\times3$ boxcar filter itself might be also a bit blurry,  as suggested by its relatively high residual values.
 %A conclusion which is hard to make

### 2013-07-31 6/conclusional_discussion.tex
Final changes before submission to Alan???

@@
 2) developing novel additive and homoskedastic measures of distance for both SAR and POLSAR data, which allow the benefits of the homoskedastic statistical estimation framework to be demonstrated. 
-After different scalar statistical models, together with many different data processing techniques, is reviewed for both SAR and POLSAR data,
-  chapter \ref{chap:lit_survey} highlights the needs for scalar, representative and homoskedastic statistical models for the multi-dimensional, complex and heteroskedastic data.
+After different scalar statistical models, together with many different data processing techniques, are reviewed for both SAR and POLSAR data,
+  Chapter \ref{chap:lit_survey} highlights the needs for scalar, representative and homoskedastic statistical models for the multi-dimensional, complex and heteroskedastic data.
 
   Chapter \ref{chap:sar} then presents homoskedastic models that are derived for heteroskedastic SAR data. 
-In chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
+In Chapter \ref{chap:polsar}, scalar and representative statistical models are proposed for the multi-dimensional and inter-correlated POLSAR data.
 These two seemingly disconnected results are unified, when the statistical models for POLSAR are shown to be the generic multi-dimensional extension of the commonly used statistical models for SAR intensity.
-This combination give rise to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
+This combination leads to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
 These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.
@@
 
-In \textbf{summary}, to address the dual-problem stated earlier, this thesis proposes several
+In summary, to address the dual-problem stated earlier, this thesis proposes several
 scalar, additive and homoskedastic models for the multi-dimensional, multiplicative
 and heteroskedastic POLSAR data. 
-The dis-similarity measures are computed for the determinant of the POLSAR covariance matrix,
+The dis-similarity measures are based on the determinant of the POLSAR covariance matrix,
   which when converted into one-dimensional data
@@
 The models are shown to be theoretically powerful.
-Not only they include the one-dimensional SAR under their natural coverage 
+Not only they include the one-dimensional SAR under their natural coverage, 
 they are also able to provide alternative and simpler explanations to a range of theoretical concepts. 
@@
 \begin{enumerate}
+\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
+  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
+  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
 \item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
@@
   In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
-\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
-  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
-  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
 \item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
@@
 Another example is between the fields of computer science and SAR-based remote sensing.
-Evidently while the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
+Evidently the number of different digital image processing, computational intelligence or signal processing techniques for digital input data is many times higher than the number of available techniques applicable to (POL)SAR data.
 And the proposed homoskedastic models, together with the consistent measures of distance,  %a solution for the second problem
@@
 %This should also be interesting for experienced experts in the field %as it will increase our capabilities in understanding and processing of (POL)SAR data.
-The proposed homoskedastic statistical estimation framework provides a firm foundation
+The proposed homoskedastic statistical estimation framework also provides a firm foundation
 to overcome the various negative impacts of heteroskedasticity on statistical estimations.
@@
 
-Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
-new detection, classification, clustering or speckle filtering algorithms can be derived using the models proposed.
+Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS}, new algorithms can be derived using the proposed models.
 
@@
 
-While
+Although
                 the proposed models may have certain limitations, its
@@
 
-Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able.
-In Fig. 
-	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
-the underlying single channel grey image histogram is presented along with the noise PDF, in the log-transformed domain. 
-As the noise is additive, it is expected that the noise PDF will act as a point spread function.
-This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
-This characteristic is reflected clearly in Fig. 
-	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
-where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
-We hence hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods,
-  such as using the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical}.
-%We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.
-
-\begin{figure}[h!]
+\begin{figure}[ht]
 \centering
@@
 
+Furthermore, as the point spread function (PSF) is available in the log-transformed domain, it appears that, for the first time, the histogram of the underlying back-scattering coefficient may become estimate-able.
+In Fig. 
+	\ref{fig:noise_pdf_as_psf:conv_inputs}, 
+the underlying single channel grey image histogram is presented along with the noise PDF, in the log-transformed domain. 
+As the noise is additive, it is expected that the noise PDF will act as a point spread function.
+This makes the observable speckled image histogram mathematically equivalent to the convolution of the original image's histogram and the noise PDF.
+This characteristic is reflected clearly in Fig. 
+	\ref{fig:noise_pdf_as_psf:conv_output_observable}, 
+where except for the un-calibrated shifting, the shapes of theoretical convolution and observed histogram are reasonably similar.
+We hence hypothesize that: given the observable SAR data and its histogram, it should be possible to estimate the original underlying signal's histogram through some regularized deconvolution methods,
+  such as using the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical}.
+%We intended to start by applying the Richardson-Lucy algorithm \cite{Richardson_1972_JOptSocAm, Lucy_1974_JAstronomical} for such estimations.
+
 For multi-channel SAR data, the short-term focus is to extend the existing statistical estimation framework for SAR towards POLSAR.

### 2013-07-31 9_backmatter/appendix.tex
updated Ian's abstract and acknowledgement
updated from Ian's changes
Final changes before submission to Alan???

@@
 
-Given characteristic function (CF) of the elementary log-chi square distributions can be written as:
+Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as:
 \begin{eqnarray}
@@
 
-\section{SAR intensity as the special case of POLSAR covariance matrix determinant}
+\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
 \label{sec:appendix_sar_special_case_of_polsar}
 
-In this appendix, the following results for SAR intensity $I$ is shown to be special cases of the results given in this paper for the determinant of POLSAR's covariance matrix $det|C_v|$.
+In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this thesis for the determinant of POLSAR's covariance matrix $det|C_v|$.
 Specifically, not only the following results from chapter \ref{chap:sar}, i.e. $d=L=1$, is reviewed:
@@
 
-The output of the first phase, in the general case is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplify the multi-look results into single-look results.
+The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
+The second phase simplifies the multi-look results into single-look results.
 Mathematically, that means setting $L=1$ in the multi-look result
@@
 \end{eqnarray*}
-Or in PDF forms, and applying variable change theorem we have:
+Or in PDF forms, and applying the variable change theorem we have:
 \begin{eqnarray*}
@@
 The result for multi-look SAR data written in log-transformed domain can be derived from two different approaches.
-The first is to follow the simplification method, where the results for log-transformed POLSAR data is simplified into log-transformed multi-look SAR result.
+The first is to follow the simplification method, where the results for log-transformed POLSAR data are simplified into a log-transformed multi-look SAR result.
 
 The second approach is to apply log-transformation into the results derived in the previous section.
-In this section, it is shown that both approaches would results into identical results.
+In this section, it is shown that both approaches would result in identical results.
 
@@
 \ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-The also arrives at the same results as above, the details working however is omitted here for brevity.
+This also arrives at the same results as above, the detailed working however is omitted here for brevity.
 
@@
 The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
-  and converting natural logarithm into base-2 logarithm.
+  and converting natural logarithms into base-2 logarithms.
 First, setting $L=1$ makes the above results become
@@
 Then to convert to base-2 logarithm from natural logarithmic transformation,
-  variable change theorem is invoked.
+  the variable change theorem is invoked.
   That is:
@@
 with $\gamma$ being the Euler Mascheroni Constant which equals $0.5772$. 
-In base-2 logarithm, variable change theorem is invoked
+In base-2 logarithm, the variable change theorem is invoked
 \begin{eqnarray*}
@@
 
-\chapter{Published and Under-Review Articles}
+%\chapter{Articles Prepared For Public Communication}

### 2013-09-25 0_frontmatter/abstract.tex
for work in isprint

@@
 Similarly, the homoskedastic model carries additional benefits.
-For inexperienced researchers (such as this author when he began this research),
-  who attempt to process either SAR or POLSAR data using existing computation algorithms
-  which most of the time expect an additive and homoskedastic input,
-  this thesis proposes alternative and more familiar additive and homoskedastic models.
+For example, for inexperienced researchers (such as this author when he began this research),
+  this thesis proposes additive and homoskedastic models for both SAR and POLSAR data,
+  which are simpler and more familiar.
+They are helpful by keeping these inexperienced researchers from falling into several common traps in (POL)SAR data processing.
+%For inexperienced researchers (such as this author when he began this research),
+%  who attempt to process either SAR or POLSAR data using existing computation algorithms
+%  which most of the time expect an additive and homoskedastic input,
+%  this thesis proposes alternative and more familiar additive and homoskedastic models.
 For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 

### 2013-09-25 paper_dev/article.tex
for work in isprint

@@
-\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
+\documentclass[journal]{IEEEtran}
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
@@
 \begin{abstract}
-This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
-Compared to other scalar statistical models for POLSAR,
-  the proposed models are highly representative of the multi-dimensional data
-  and enable useful discrimination measures to be easily determined. %consequently they lead to useful discrimination measures.
-The representative power of these models is explained  
-when these multi-dimensional models are collapsed to single dimensional versions,
-  they are shown to exactly match the traditional statistical models for the representative observable of SAR intensity.
-The paper also validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
-%IVMThe proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
-One major benefit of this paper is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
-To illustrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+%Problem statement  
+This proposes a scalar and representative observable for the multi-dimensional POLSAR data,
+  from which statistically consistent discrimination measures can be derived.
+%What actually were done? and As the result, what is learned?
+Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
+  to derive a scalar and generic statistical model for the multi-dimensional POLSAR data,
+  which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
+As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
+  the proposed model is also shown to include the traditional model used for SAR intensity under its natural coverage.
+%What are the larger implications of the findings presented in this paper?
+Consequently, the main beneficial implication of the proposed approach is that
+  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
+  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
 \end{abstract}
@@
 
-During the past decades, exponential growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
+%What is the situation, the background context of your research? the BIG problem!
+During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
 technology to become a feasible and preferred technique for earth observation applications.
-SAR technology has since extended in a few directions, one of which is polarimetric SAR (POLSAR).
+SAR technology has since been extended in a few directions, one of which is the polarimetric SAR (POLSAR).
 POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
@@
 
-While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
-That is there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
-The research community has responded largely by developing different statistical models for various POLSAR observables.
-However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
-Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
-On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.
-
-This paper presents novel statistical models for multi-channel POLSAR data as generalisations of the commonly used and representative statistical models for the one-channel SAR data.
-This approach makes feasible the adaptation of many existing SAR processing techniques to be applied to POLSAR data.
-After section \ref{sec:lit_review} reviews related work in published literature, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
-The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
-  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
-With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
-%  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
-  and allow many conventional SAR statistical models to stay under the umbrella of these generic POLAR models.
-The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
-Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
-This is followed by a conclusion in Section \ref{sec:conclusion}.
+%Research Motivation: Why it is important to solve this problem?
+%The POLSAR data, however, is multidimensional and stochastic.
+Similar to the SAR data, POLSAR data is stochastic.
+Moreover, it is multi-dimensional.
+Under this context, it is therefore important to establish a simple and intuitive understanding of the data
+  and statistical models are undoubtedly crucial in understand the stochastic nature of the data.
+While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
+  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
+Practical POLSAR data processing, however, makes heavily uses of scalar discrimination measures,
+  which should be based on statistically consistent models for scalar yet representative observables of the multidimensional data.
+%Moreover, to provide theoretical foundation for discrimination measures proposal,
+%  statistically consistent models should be derived from this scalar observable.
+
+%How do others solve this problem?
+%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
+%  which apparently is multidimensional, complex and thus not very intuitive.
+There has been a few scalar observables with accompanying statistical models proposal for POLSAR (TODO:CITE from section II),
+  but none of them is able to provide meaningful scalar discrimination measures.
+%  but none of them has led to scalar discrimination measures proposal.
+As such no observable has been widely accepted as being highly representative of the multi-dimensional data,
+  which severely limits their applicability in practical data processing applications.
+From an alternative approach, there are also a few POLSAR discrimination measures proposed,
+  but all of them are based on the likelihood ratio statistics.
+This statistical test should be based on a statistically consistent distribution
+  but so far has only shown to be based on an asymptotic distribution.
+
+%Research Objective: Give your precise problem statement  
+This article hence present a scalar and representative observable, and its associated generic statistical model,
+  for the multi-dimensional POLSAR data that provides a consistent foundation for the derivation of POLSAR discrimination measures.
+%Now State your approach  
+%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
+%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
+%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
+%Prof Vuns: comment: the article provides the result, not the journey!
+The POLSAR data have been statistically modelled as following the complex Wishart distribution.
+As such the generic statistical model for the covariance matrix determinant, being just a scalar projection of the multidimensional data, is presented.
+%The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
+It is also shown that
+  the specific one dimensional version of the generic model proposed in this paper
+  matches perfectly with the traditional statistical model used for SAR intensity.
+Furthermore, the approach proposed in this paper
+  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
+  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.
+
+%What is the novelty of your solution? What are its advantages
+%Compared to other published scalar observables with accompanying statistical model,
+%  the proposed observable and its models are highly representative of the multidimensional data.
+%The representative power of the proposed observable is justified by the following reasons.
+%Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+%Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
+%And last but not least, this observable also leads to the determinant-ratio discrimination measure which
+%  not only is simpler in concept and computation than the existing POLSAR discrimination measures
+%  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
+% Prof Vun Comment: already mentioned above, no need to repeat
+
+%How do you know if the problem is solved? State your research contribution to be achieved
+In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
+  that is representative of the multi-dimensional data.
+Specifically the following research results are to be achieved:
+  1. The generic multi-dimensional statistical model for the POLSAR covariance matrix is to be derived, 
+  2. The generic model is also shown not only providing a staititically consistent models for newly proposed POLSAR discrimination measures, namely the determinant-ratio and the change-ratio.
+  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
+  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
+(Hai note: I kept this to keep my focus while working on this paper.
+  It can be removed before the final submission.)
+
+%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
+The rest of this article is organized as follows.
+After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR,
+  section 3? derives the generic statistical model for the determinant of the POLSAR covariance matrix.
+Section 4? then validates the specific two and three dimensional versions of the model against real-life captured data.
+After section 5? illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
+  section 6? establishes the generic determinant-ratio descrimination measure which links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
 
@@
 
-This section outlines related published work.
-In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
-Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
+%This section outlines related publication.
+Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
+  where it is shown that none of these is able to provide statistically consistent discrimination measures. 
 Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
-  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
-However, while an exact statistical distribution is needed for the test,
+  and it demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
+While an exact statistical distribution is expected for the test,
   only asymptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
@@
 Furthermore, at its conclusion, the paper indicated that it is impossible to identify a single best representation.
-Although, to be fair, those observables were identified to describe a decomposed portion of the complex POLSAR data,
-  rather than providing a single unified representation of the POLSAR data.
-
-Given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
+Although, to be fair, the observables were identified for describing a decomposed portion of the complex POLSAR data,
+  rather than providing a unified representation of the POLSAR data.
+
+Using a different approach, given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
   it is possible to derive the scalar statistical models for some univariate POLSAR observables.
-This becomes an alternative approach used in the study of POLSAR data.
-However, such derivations are no trivial task, and so far, only a handful of such statistical models have been proposed, including the following:
+%This becomes an alternative approach used in the study of POLSAR data.
+However, such derivations are not trivial tasks, and so far, only a handful of such statistical models have been proposed, including the following:
   \begin{enumerate}
@@
   \end{enumerate}
-
 More recently, statistical models for
-  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
+  each element of the POLSAR covariance matrix, i.e. $S_{pq}S_{rs}^*$, \cite{Lopez-Martinez_2003_TGRS_2232}
   as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been proposed.
-While these models undoubtedly help in understanding POLSAR data,
-  none of these observables have been shown to meet the dual criteria of
-  1) resulting in statistically consistent discrimination measures and
+
+While these models undoubtedly help to further our understandings of the POLSAR data,
+  none of the underlying observables have been shown to meet the dual criteria of
+  1) resulting in statistically consistent discrimination measures and thus 
   2) being representative of the complex POLSAR data.
@@
 
-The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
+The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined respectively as:
 \begin{align}
@@
 and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR% covariance matrix
-, these dis-similarity measures are not widely used 
+However, in the context of POLSAR, % covariance matrix
+  these dissimilarity measures are not widely used 
   mainly due to the multiplicative nature of the noisy data.
@@
 \end{equation}
-.
-
-%%***IVM: Hai, you haven't introduced the notation for these!! What is tr() (in eqn. 3), what is Lx, Ly.... I changed your A_{i,j} to C_{i,j} above, just after eqn.2
-
-Closer investigation of these dis-similarity measures reveals that most are related in some ways. %to each other.
+
+Closer examination of these dissimilarity measures reveals that most of them are related in some ways. %to each other.
 The Bhattacharyya distance is easily shown to be related to the Barlett distance.
@@
 The close relation among the measures is further supported by the fact that
-  all of their proposing papers refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
-In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  all of their publications refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as the foundation.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
   which have $L_x$ and $L_y$ as the corresponding number of looks,
@@
 
-Taking the log-transformation of the above equation, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
-\begin{eqnarray}
-  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
-  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
-\end{eqnarray}
-
-To detect changes, a test statistic is developed based on this measure of distance.
+Taking the log-transformation of the above equation, and denote $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
+{\small
+\begin{align}
+  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{align}
+}
+
+To detect changes, a test statistic is developed for this discrimination measure.
 This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
-
-\section{Scalar Statistical Models for POLSAR}  
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
+This paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
+  which is capable of providing an exact distribution for the test.
+
+\section{The Generic Scalar Statistical Model for POLSAR}  
 \label{sec:theoretical_model}
 
-In this section, several scalar statistical models for POLSAR are presented.
-Section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation used in this paper, %reviews related work in published literature,
-  while section \ref{sec:polsar_heterosked_model_and_log_transform}
-  presents the theoretical models together with mathematical evidence for two related points.
-The first point is that the POLSAR data is multiplicative and heteroskedastic in its original domain.
-And the second conclusion states that log-transformation converts it into an additive and homoskedastic model.
-Some consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
-
-\subsection{Basics of POLSAR Statistical Analysis}
-\label{sec:model_basic}
+In this section, the generic scalar statistical model for POLSAR is presented.
+After the basic foundations of POLSAR statistical analysis is introduced,
+  this section presents the theoretical model for multi-dimensional POLSAR data.
 
@@
 \begin{equation}
-\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
+\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi (2L-2i)
 \label{eqn:prod_chi_squared_rv}  
@@
 
-Its log-transformed variable consequently 
-  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
-\begin{equation}
-\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
-\label{eqn:sum_log_chi_squared_rv}
-\end{equation}
-with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$.
-We will now use this result to develop the statistical models for POLSAR. %log-transformed measures of distance.
-%***IVM added the sentence above... **Please check it's true!!!!
-
-\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
-\label{sec:polsar_heterosked_model_and_log_transform}
-
-In this section the multiplicative nature of POLSAR data is first illustrated.
- Log-transformation is then applied to convert  the data into a more familiar additive model.
-Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
-  is shown to be present in the original POLSAR data.
-In the log-transformed domain, a homoskedastic model is demonstrated,
-  where sample variance is fixed and thus independent of the underlying signal.
-Several intermediate mathematical steps are not shown here, but can be found in Appendix \ref{chap:appendix_a}.
-
-From Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv}
-we can deduce the following relationships:
+We will now use this result to develop the generic scalar statistical model for POLSAR. %log-transformed measures of distance.
+From Eqn. \ref{eqn:prod_chi_squared_rv} %and \ref{eqn:sum_log_chi_squared_rv}
+we have: %can deduce the following relationships:
 \begin{eqnarray}
-  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
-  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
-\label{eqn:log_determinant_distribution}  
+  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_distribution} %\\
+%  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
+%\label{eqn:log_determinant_distribution}  
 \end{eqnarray}
@@
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
-At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
-  the logarithmic transformation has converted this to the more familiar additive noise.
-
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follow a known PDF:
-\begin{equation}
-pdf(x;2L) =
-  \frac{x^{L-1} e^{-x/2}}{2^L \Gamma\left(L\right)}
-\label{eqn:chi_squared_dist_pdf:chap4}
-\end{equation}
-applying the variable change theorem, 
-  its log-transformed variable follows the PDF of:
-\begin{equation}
-  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
-\end{equation}
-
-Using these PDFs, the characteristic functions (CF) of both the chi-squared and log-chi-squared random variables
-  can be written as:
-  \begin{eqnarray}
-    CF_\chi(t) &=& (1-2it)^{−L} \\ 
-    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
-  \end{eqnarray}
- Their means and variances can subsequently be computed from these  characteristic functions, leading to the following relationships:  
-  \begin{eqnarray}
-    avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-  \end{eqnarray}
-  where $\psi^0()$ and $\psi^1()$ represent the digamma and trigamma functions respectively.
-
-Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
+
+Moreover, since the average and variance of these chi-squared distributions %and log-chi-squared distribution
+  are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
   the product and summation of these random variables also has fixed summary statistics.
 Specifically:
+{\footnotesize
 \begin{align*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
+%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
 \end{align*}
-
-Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
+}
+
+Combining these results with Eqn. \ref{eqn:determinant_distribution} %and \ref{eqn:log_determinant_distribution}
+  , we have:
+{\footnotesize
 \begin{align}
   avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}%\\
+%  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+%  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
 \end{align}
+}
 
@@
 In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
-At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ (i.e. it is homoskedastic).
-
-\subsection{Consistent Measures of Distance for POLSAR}
-\label{sec:distance_measure}
-
-Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
-  this section introduces the consistent sense of distance for POLSAR.
-Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-then the random variables,
-  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$)
-  are observable according to the following definitions:
+
+Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \cite{Rignot_1993_TGRS_896},
+in this article, the determinant-ratio is also proposed as a discrimination measure for the POLSAR data,
+  which also have just been shown to suffer from the multiplicative and heteroskedastic phenomena.
+%Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
+%  this section introduces the consistent sense of distance for POLSAR.
+Assuming, on the one hand,
+  that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
+%  are observable according to the following definitions:
+  is defined as:
 %Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
 \begin{eqnarray}
-  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
-  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
+  \mathbb{R}_{\Sigma} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}%\\
+%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
 \end{eqnarray}
@@
   where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
-  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
+ then random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
 \begin{eqnarray}
-  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
-  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
+  \mathbb{R}_{C} &=& \frac{|C_1|}{|C_2|} \label{eqn:determinant_ratio_samples_observables}%\\
+%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
 \end{eqnarray}
-
-Using the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
+where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
+
+%  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
+%\begin{eqnarray}
+%  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
+%  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
+%\end{eqnarray}
+
+Using the results from Eqn. \ref{eqn:determinant_distribution}, %\ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det}
+  we have
 \begin{eqnarray}
-\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
-\label{eqn:log_determinant_distance_distribution} \\ 
- \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
-\label{eqn:dispersion_distribution} \\ 
- \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\label{eqn:contrast_distribution}  
+\mathbb{R}_{\Sigma} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_ratio_distribution} \\
+\mathbb{R}_{C} &\sim& \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+%\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
+%\label{eqn:log_determinant_distance_distribution} \\ 
+% \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
+%\label{eqn:dispersion_distribution} \\ 
+% \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
+%\label{eqn:contrast_distribution}  
 \end{eqnarray}
-with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
-and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
-
-Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
-\begin{align}
-  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
-  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
-\end{align}
-
-Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
-  it is natural that these variables also follow fixed distributions.
-Moreover, note that they are independent of the underlying signal $\Sigma_v$.
+%with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
+%and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
+
+%Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
+%\begin{align}
+%  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
+%  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
+%\end{align}
+
+Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
+  it is natural that this variable also follows fixed distributions.
+Moreover, it is independent of the underlying signal $\Sigma_v$,
+  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
+  This claim is extrapolated from the widely-used intensity-ratio as SAR discrimination measure and is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case.
 %This result shows how
@@
 
-The previous section  introduced  theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
+The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
 This section will show that the model is equally  applicable to the 1-dimensional ($d=1$) case,
@@
 As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
-Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
-  as well as reminding us that SAR is a special case of POLSAR.
+Hence this derivation can be considered
+  either as cross-validation for the proposed POLSAR model
+  or as evidence showing that
+    the generic POLSAR model proposed in this article also covers the traditional model for SAR intensity in its natural coverage.
+%  as well as reminding us that SAR is a special case of POLSAR.
 
 The results for our models can be summarized using the following equations:
-\begin{align}
-  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
-  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
-  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
-  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
-  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
-  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align}
+\begin{align*}
+  |C_v| &\sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+%  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
+%  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
+%  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
+%  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
+%  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
+%  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
+\end{align*}
 
 Upon setting $d=1$ into the above equations,
-  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
-%Upon setting $d=1$ into the above models,
-%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+  the becomes:
 \begin{align*}
-  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
-  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
-  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
-  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
-  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
-  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
-  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
+  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
 \end{align*}
-The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+
+Since the PDF of chi-squared distribution can be written as:
+\begin{align*}
+\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
+\end{align*}
+, applying variable change theorem into the above equations results in:
+\begin{align*}
+  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
+\end{align*}
+These equations match exactly with the following traditional model for multi-look SAR intensity:
   \begin{eqnarray}
 I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
+\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
+  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
   \end{eqnarray}
-Furthermore, the following derivations for multi-look SAR data
-   show that it can be considered 
-    either as extensions of the corresponding single-look SAR results
-    or as simpler case of the POLSAR results:
-  \begin{align*}
-    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
-    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
-    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
-    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
-    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
-    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{align*}
-
-\section{Validating the proposed models against real-life data}
+considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.
+
+\section{Discussion}
+
+\subsection{Validating the proposed models against real-life data}
 \label{sec:polsar_models_validation}
 
-This section aims to verify the theoretical models against practical data.
-Since it is shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, only a simple validation is presented for this case.
-
+This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
+Both of these models require the estimation of two parameters from some given captured data.
+They are the dimensional number $d$ and the look number $L$.
+The dimensional number $d$ is related to the type of (POL)SAR data,
+  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
+The look-number $L$ can be taken either as nominally stated by the data provider,
+  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
+To show the robustness of the proposed models, their validation is also put to test on different types of POLSAR sensors.
+Specifically in this article, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
+  a fine-quad single-look complex RADARSAT2 image ($L=1$) are employed.
+Since the determinant of the covariance matrix is only significant on multi-look data,
+  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).
+
+Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  which have been validated extensively, the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
- The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
-%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-%The ENL is set to the nominal number of 4.
-%And good visual match is apparent in the final results.
-
-\begin{figure}[h!]
+The histograms for both the intensity and intensity ratio (TODO:Replot) %the log-distance and contrast
+  are then plotted against the theoretical PDF given above.
+The plots are obtained with ENL set to both the nominal number of 4 and the estimated number of (TODO:CALC).
+Also presented are the plots of the same experiment applied on a homogeneous patch inside the nine-look processed RADARSAT2 image (TODO:NewPlot).
+In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
+In all cases, good visual match is apparent, which validates the model proposed above. %providing us a simple validation of the result.
+
+\begin{figure}[h]
 \centering
 \begin{tabular}{c}
-	\subfloat[multi-look SAR log-distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
+	\subfloat[AIRSAR (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_determinant}
 	} 
 	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	} \\
+	\subfloat[AIRSAR (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
 	}
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
-It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_1D}
 \end{figure}
@@
 The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
-While the match appears to be reasonably good, it can be further improved.
-Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
-  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
-With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
-
-%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
-%While the match appears to be reasonably good, it can be further improved.
-%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
-%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
-%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
-
-\subsection{Using the nominal ENL to validate the theoretical models} 
-\label{sec:valid_nominal_enl}
-
-The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
-Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.
-
-For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
-Both the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
-These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
-Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
-Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.
-
-The least-assumed stochastic processes for dispersion and contrast are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
-Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-Here a nominal look-number L=4 is used
-  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
-The plots, presented in Fig.
-  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
-
-\begin{figure}[h!]
+Similar experiments like the one described for SAR data is carried out
+  for both types of polarimetric SAR
+  on both AIRSAR and RADARSAT2 datasets.
+The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.
+
+\begin{figure}[h]
 \centering
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
+	\subfloat[AIRSAR (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_determinant}
 	} 
 	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
+	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
 	} 
 	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
 	}
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_2D}
 \end{figure}
 
-Apart from dispersion and contrast,
-  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
-Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be presented in this section.
-As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
-In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
-  and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
-A close match is again observed, validating the models for log-distance and determinant ratio.
-
-\begin{figure}[h!]
+\begin{figure}[h]
 \centering
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
+	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_determinant}
 	} 
 	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
 	} 
 	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_change_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_change_ratio}
 	}
 \end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_3D}
 \end{figure}
 
-Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
-  where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
-Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
-
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-
-In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
-This is discussed in the next subsection.
-%The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
-%In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
-
-%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  where not only the look number is shown to be misused
-%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-%As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  the reason is due to the inappropriate look number being used.
-%Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
-%For now, let us simply observe that
-%  using appropriate estimation of the parameters, 
-%  the proposed models match reasonably well with the practical data.
-
-\subsection{Difference between the theoretical assumptions and the conditions found in practice}  
-\label{sec:improve_the_match_bw_theory_practice}
-
-Even though the assumptions made in developing this theory have intentionally been kept minimal, 
-in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
-However, practical conditions may not always satisfy these prerequisites,
-  a common and observable gap is noticed between the conditions found in practical real-life data and the theoretical assumptions.
-
-The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
-  the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
-However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
-  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
-Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
-Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.
-
-Thus in practical images, each physical radar cell may be spread over more than a single pixel,
-resulting in both %This results in 
-  a higher correlation between neighbouring pixels \cite{Raney_1988_TGRS_666} %that may be related within a single physical cell resolution,
-  and a reduced effective number of look\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
-The oversampling practice is also documented by the producers of SAR processors.
-For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolution combination for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
-In short, while the independent sample assumption is made out of necessity in theory,
-  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighbouring samples. % are actually correlated
-This documented imperfection also leads to the rise of effective number-of-look concept (ENL),
-  which is almost always smaller than the nominal look-number.
-
-The proposed model apparently can handle this imperfection. %that is found in practical data.
-The handling process, however, is slightly more complex.
-Instead of adopting the nominal Number of Looks given by the SAR processor,
-  an ENL must first be estimated from the given data.
-This is discussed in the next subsection.
-
-\subsection{ENL Estimation for POLSAR data}
-\label{sec:valid_enl_estimation}
-
-The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
-  before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
-  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-In a given POLSAR dataset, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
-  it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
-This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
-However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.
-
-This paper instead proposes an alternative approach that makes use of variance statistics in the homoskedastic log-domain.
-Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation}
-  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-  \label{eqn:expected_sample_var_log_as_function_of_enl}
-\end{equation}
-where $\psi^1()$ again denotes the tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for unknown $L$,
-  although it would also require some iterative computation.
-Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph, or from the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
-  \begin{equation}
-    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
-    \label{eqn:enl_estimation_formula}
-  \end{equation}
-Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  as well as illustrating the simplified approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relation between ENL and sample variance of log-determinant/log-intensity.}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-
-\subsection{Using estimated ENL to better explain practical data}
-\label{sec:valid_improve_practice}
-
-To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
-Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
-  against the theoretical models for the nominal ENL value of 9.
-As expected the match is evidently not very close.
-
-We now compare this to the estimated ENL approach.
-First, an ENL estimate is obtained from the observable variance of the log-determinant. 
-Then the new sample histogram is overlaid on the same figure,
-  showing a much better consistency.
-This procedure can always be carried out for a given dataset,
-  as long as a homogeneous area can be defined and extracted.
-
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-
-The same approach can be applied on the AIRSAR Flevoland data to improve the validation described earlier.
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
-  even though it is to a much lesser extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
-
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-
-\section{Discussion}
+\subsection{Theoretical Implications of This Proposal}
 \label{sec:discussion}
@@
 It should be noted that the models are far from complete.
-% It reduces the multi-dimensional POLSAR data to a scalar value.
-%While this is probably desirable for a wide range of application,
-%  such a reduction is unlikely to be lossless.
 While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
@@
 It does not, technically speaking, focuses on proposing new discrimination measures.
-%***IVM remove this single sentence, it detracts from the argument...
-%Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
 
@@
   existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
-%to comprehensively support the argument. 
-%To support these arguments, extensive literature surveys has been carried out for both published scalar models as well as for discrimination measures for POLSAR.
-Thus given such extensive reviews the above claims are water-tight.
 
@@
 This is illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
-%Here a major benefit is illustrated in showing that 
 In evaluating SAR speckle filters, the intensity ratio is widely used.
@@
 
-\begin{figure}[h!]
+\begin{figure}[h]
 \centering
@@
 	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
 		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
@@
 	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
 		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
@@
 	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
 		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
@@
 	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
 		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
@@
 \end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
 \label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
@@
 
-%Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
-%Evidently these techniques can also be adapted for POLSAR.
-%Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
-
-%Hai version: (Ian have not seen this yet)
 There are many similar SAR data processing technique that may be adaptable to POLSAR.
@@
   inviting potential extension of various SAR processing techniques to POLSAR data.
-%Here a specific example is shown
 For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
@@
 We believe there are many more unexplored possibilities for such applications.
-%  which is only limited by our imagination.
 
@@
 
-A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
-  resulting in several consistent discrimination measures useful POLSAR applications.
-The theoretical models are shown to be comprehensive in that
-  not only can they provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
-  but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
-The models are also practically useful since they provide several consistent discrimination measures.
-Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
-Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
-
-%In conclusion, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix,
-%  which result in several consistent discrimination measures for POLSAR, are proposed and validated in this paper.
-%The theoretical model is shown to be comprehensive in that:
-%  not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
-%  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
-%Compared to other scalar statistical models for POLSAR, the proposed models are highly representative of the multi-dimensional POLSAR data.
-%%These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
-%%Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
-%%As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
-%
-
-%An additive and homoskedastic model, 
-%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
-%  is proposed in this paper.
-%The theoretical model is shown to be comprehensive:
-%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
-%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
-%
-%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
-%  is gracefully transformed into traditional SAR intensity.
-%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-%%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
-%%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
-%%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.  
-%The models may also form a bridge, allowing the adaptation of many existing SAR data processing technique for POLSAR data,
-%  a quick example of this is briefly described in this paper.
-%This paper
-
-\appendices
-\section{Homoskedastic Model for the Log-Determinant}
-\label{chap:appendix_a}
-
-\subsection{Log-Chi-Square Distribution and its Derivatives}
-%\section{Log-Chi-Square Distribution}
-\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\setcounter{equation}{0}
-
-This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
-
-Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
-\begin{equation}
-pdf(\chi;\,k) =
-  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
-\label{eqn:chi_squared_dist_pdf:appdixA}
-\end{equation}
-
-Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
-\begin{equation}
-pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
-\end{equation}
-
-Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
-\begin{equation}
- \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
-\end{equation}
-into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
-\begin{eqnarray*}
-  d\chi &=& e^\Lambda d\Lambda \\
-  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
-\end{eqnarray*}
-In other words, we have:
-\begin{equation}
-pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
-\label{eqn:log_chi_square_dist_pdf}
-\end{equation}
-
-From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, a characteristic function can be computed.
-By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
-\begin{eqnarray*}
-\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
-      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
-      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
-\end{eqnarray*}
-with $\varphi_x(t)$ is the characteristic function,
-     $F_X(x)$ is the CDF function of X and
-     $f_X(x)$ is the PDF function of X.
-Thus the characteristic function for the log-chi-squared distribution is defined as: 
-\begin{equation}
-\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
-\end{equation}
-
-The Gamma function is defined over the complex domain as:
-$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
-Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
-Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
-%  \begin{eqnarray*}
-%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
-%  \end{eqnarray*}
-
-%Thus the characteristic function becomes
-That is:
-\begin{equation}
-\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
-\end{equation}
-
-Consequently, the first and second derivative of the log-chi-squared distribution can be computed.
-The first derivative is given as:
-\begin{equation}
-  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
-\end{equation}
-due to
-\begin{eqnarray*}
-  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
-  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
-  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
-\end{eqnarray*}
-where $\psi^0()$ denotes the di-gamma function.
-
-Meanwhile, the second derivative can be written as:
-\begin{equation}
-  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
-\end{equation}
-due to:
-\begin{eqnarray*}
-  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
-  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
-  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
-\end{eqnarray*}
-with $\psi^1()$ denotes the tri-gamma function.
-
-The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
-\begin{equation}
-\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
-  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
-\end{equation}
-
-Thus
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
-  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
-% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
-% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
-% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
-\end{eqnarray*}
-That gives the result:
-\begin{equation}
-  avg(\Lambda) = \psi^0(L) + ln(2)
-\end{equation}
-
-Similarly, for the second moment,
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
-  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
-% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
-% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
-% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
-\end{eqnarray*}
-That is equivalent to saying that
-\begin{equation}
-  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
-\end{equation}
-%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
-%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.
-
-Thus we can state that
-\begin{equation}
-var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
-\end{equation}
-
-\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
-
-In this section, the expected value and variance value of these mixture of random variables are derived
-\begin{eqnarray}
-\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
-\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
-\end{eqnarray}
-given the averages and variances of individual components.
-\begin{eqnarray}
-avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-\end{eqnarray}
-
-Making use of the mutual independence property of each component $X_i$,
-  the variance and expectation of the summation and product of random variables can be written as:
-\begin{eqnarray*}
-avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
-var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
-avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
-var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
-\end{eqnarray*}
-
-Thus they can be rewritten more usefully as:
-\begin{eqnarray*}
-  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
-
-\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
-\label{sec:appendix_b}
-
-Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as
-\begin{eqnarray}
- CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
-\end{eqnarray}
-  then the CF for the following random variables,
-  which are combinations of the above elementary random variables, can be derived
-\begin{eqnarray*}
-   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
-  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
-  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
-  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
-\end{eqnarray*}
-
-Since we can state that
-\begin{eqnarray*}
- CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
- CF_{x+k}(t) &=& e^{itk}CF_x(t)
-\end{eqnarray*}
-then we have:
+%What has been done?
+In this article,
+  based on the commonly used complex Wishart distribution for the POLSAR target vector,
+  a generic statistical model has been derived for the POLSAR covariance matrix determinant.
+Then the specific (d=2) and (d=3) versions of the derived model are respectively validated against real-life partial and full polarimetric SAR data.
+The article also shows a perfect match between the (d=1) specific model and the traditional model for SAR intensity,
+  effectively putting the existing SAR theories under the generic model's natural coverage.
+It also establish a new POLSAR discrimination measure: the determinant-ratio,
+  which essentially is the generic version of the SAR intensity ratio.
+
+%What are the results? What are their advantages over others' results?
+The result is the proposal of the POLSAR covariance matrix determinant as the scalar and representative observable for the multi-dimensional POLSAR data.
+Compared to other published scalar observable, the proposed determinant is highly representative of the multi-dimensional data.
+Its representative power is justified by the following reasons.
+Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
+And last but not least, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
+
+%What are their benefit?
+There are several beneficial implications of the proposal presented in this article.
+Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
+  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
+
+%What are their limitations? What problems this appears to solve, but actually is not?
+The theory proposed in this article also has its limitations.
+Firstly, the theoretical model proposed is based on the complex Wishart distribution.
+Thus its applicability is also limited by that of its foundation,
+  that is the proposed theoretical model is only guaranteed to work in homogeneous area.
+Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value,
+  such a reduction is unlikely to be lossless.
+Finally, in this article, the theoretical model has only been validated for partial (d=2) and full (d=3) monostatic POLSAR data,
+%and hence What can be done next?
+  leaving the test of its validity on different types of dataset like bistatic POLSAR data (d=4) or interferrometric POLSAR data (d=6) a possible future work.
+Other possible future work includes
+  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
+  as well as further studies to explore the use of this theory in conjunction with other target decomposition techniques
+    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}, etc.
+
+%\appendices
+%\section{Homoskedastic Model for the Log-Determinant}
+%\label{chap:appendix_a}
+%
+%\subsection{Log-Chi-Square Distribution and its Derivatives}
+%%\section{Log-Chi-Square Distribution}
+%\renewcommand{\theequation}{\thesection.\arabic{equation}}
+%\setcounter{equation}{0}
+%
+%This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
+%
+%Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
+%\begin{equation}
+%pdf(\chi;\,k) =
+%  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
+%\label{eqn:chi_squared_dist_pdf:appdixA}
+%\end{equation}
+%
+%Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
+%\begin{equation}
+%pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
+%\end{equation}
+%
+%Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
+%\begin{equation}
+% \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
+%\end{equation}
+%into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
+%\begin{eqnarray*}
+%  d\chi &=& e^\Lambda d\Lambda \\
+%  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
+%\end{eqnarray*}
+%In other words, we have:
+%\begin{equation}
+%pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
+%\label{eqn:log_chi_square_dist_pdf}
+%\end{equation}
+%
+%From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, a characteristic function can be computed.
+%By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
+%\begin{eqnarray*}
+%\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
+%      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
+%      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
+%\end{eqnarray*}
+%with $\varphi_x(t)$ is the characteristic function,
+%     $F_X(x)$ is the CDF function of X and
+%     $f_X(x)$ is the PDF function of X.
+%Thus the characteristic function for the log-chi-squared distribution is defined as: 
+%\begin{equation}
+%\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
+%\end{equation}
+%
+%The Gamma function is defined over the complex domain as:
+%$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
+%Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
+%Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
+%%  \begin{eqnarray*}
+%%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
+%%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
+%%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
+%%  \end{eqnarray*}
+%
+%%Thus the characteristic function becomes
+%That is:
+%\begin{equation}
+%\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
+%\end{equation}
+%
+%Consequently, the first and second derivative of the log-chi-squared distribution can be computed.
+%The first derivative is given as:
+%\begin{equation}
+%  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
+%\end{equation}
+%due to
+%\begin{eqnarray*}
+%  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
+%  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
+%  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
+%  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
+%\end{eqnarray*}
+%where $\psi^0()$ denotes the di-gamma function.
+%
+%Meanwhile, the second derivative can be written as:
+%\begin{equation}
+%  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
+%\end{equation}
+%due to:
+%\begin{eqnarray*}
+%  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
+%  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
+%  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
+%  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
+%\end{eqnarray*}
+%with $\psi^1()$ denotes the tri-gamma function.
+%
+%The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
+%\begin{equation}
+%\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
+%  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
+%\end{equation}
+%
+%Thus
+%\begin{eqnarray*}
+% \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
+%  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
+%% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
+%% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
+%% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
+%\end{eqnarray*}
+%That gives the result:
+%\begin{equation}
+%  avg(\Lambda) = \psi^0(L) + ln(2)
+%\end{equation}
+%
+%Similarly, for the second moment,
+%\begin{eqnarray*}
+% \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
+%  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
+%% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
+%% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
+%% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
+%\end{eqnarray*}
+%That is equivalent to saying that
+%\begin{equation}
+%  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
+%\end{equation}
+%%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
+%%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.
+%
+%Thus we can state that
+%\begin{equation}
+%var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
+%\end{equation}
+%
+%\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
+%
+%In this section, the expected value and variance value of these mixture of random variables are derived
 %\begin{eqnarray}
+%\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
+%\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
 %\end{eqnarray}
-\begin{align}
-  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-\end{align}
-
-%The CF for the contrast random variable can also be written as
-Also due to
-\begin{eqnarray*}
-  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
-  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
-   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
-\end{eqnarray*}
-then we arrive at:
-\begin{align}
-  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-\end{align}
-with $\Gamma()$ and $B()$ denoting Gamma and Beta functions respectively.
-
-\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
-\label{sec:appendix_sar_special_case_of_polsar}
-
-In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
-Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2010_ACRS}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
-\begin{eqnarray}
-  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
-  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
-  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
-  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
-  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray}
-but also the following well-known results are considered for multi-look SAR, i.e. $d=1,L>1$:
-  \begin{eqnarray}
-I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
-  \end{eqnarray}
-It will be shown that all of these results are special cases of the result derived previously and rewritten below:
-\begin{eqnarray}
-  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
-  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
-\end{eqnarray}
-\begin{eqnarray}
-  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
-  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
-  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\end{eqnarray}
-\begin{eqnarray}
-  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
-  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
-  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
-\end{eqnarray}
-
-This appendix also derives new results for multi-look SAR data,
-  which can be thought of 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results presented above.
-They are:
-  \begin{eqnarray}
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
-    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
-    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
-    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{D}) &=& \psi^1(L) \\
-    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{eqnarray}
-
-The derivation process detailed below consists of two-phases.
-The first phase collapses the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
-Mathematically this means setting the dimensional number in POLSAR to  $d=1$
-  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.
-
-The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2010_ACRS}.
-Mathematically, it means setting $L=1$ in the multi-look result
-  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2010_ACRS} (base-2 was chosen in the previous paper to simplify the computation).
-
-\subsection{Original Domain: SAR Intensity and its ratio}
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
-we find that:
-\begin{eqnarray*}
-  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
-\end{eqnarray*}
-Or in PDF forms, and applying the variable change theorem,:
-\begin{eqnarray*}
-    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
-  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
-%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
-  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
-%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
-\end{eqnarray*}
-
-Thus we have the following results for multi-look SAR:
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
-\end{eqnarray}
-
-Now setting $L=1$, these results become:
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
-\end{eqnarray}
-which is the same as stated in \cite{Le_2010_ACRS}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
-
-\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
-
-The result for multi-look SAR data written in the log-transformed domain can be derived from two different approaches.
-The first is to follow a simplification method, where the results for log-transformed POLSAR data are simplified into log-transformed multi-look SAR results.
-
-The second approach is to apply log-transformation to the results derived in the previous section. In this section, it is shown that both approaches would result in identical results.
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
-we have
-\begin{eqnarray*}
-  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
-  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
-\end{eqnarray*}
-
-Or in PDF form, and applying the variable change theorem we have:
-\begin{eqnarray*}
-  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
-  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
-%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
-   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
- &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
-\end{eqnarray*}
-with $\bar{N} = \ln{\bar{I}}$. Thus the first approach arrives at
-\begin{eqnarray}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
-\end{eqnarray}
-
-In the second approach, log-transformation is applied on previous results for multi-look SAR intensity and its ratio in the original domain (Eqns.
-\ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-This also arrives at the same results shown above, however the detailed working is omitted for brevity.
-
-%\begin{eqnarray*}
-%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
-%\end{eqnarray*}
-%Thus
-%\begin{eqnarray*}
-%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
-%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
-%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
-%\end{eqnarray*}
-%
-%Thus the second approach also arrives at
+%given the averages and variances of individual components.
+%\begin{eqnarray}
+%avg \left[ \chi(2L) \right]&=&2L \\
+%var \left[ \chi(2L) \right]&=&4L \\
+%avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
+%var \left[ \Lambda(2L) \right] &=& \psi^1(L)
+%\end{eqnarray}
+%
+%Making use of the mutual independence property of each component $X_i$,
+%  the variance and expectation of the summation and product of random variables can be written as:
+%\begin{eqnarray*}
+%avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
+%var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
+%avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
+%var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
+%\end{eqnarray*}
+%
+%Thus they can be rewritten more usefully as:
+%\begin{eqnarray*}
+%  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+%  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
+%  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+%  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
+%\end{eqnarray*}
+%
+%\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
+%\label{sec:appendix_b}
+%
+%Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as
+%\begin{eqnarray}
+% CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
+%\end{eqnarray}
+%  then the CF for the following random variables,
+%  which are combinations of the above elementary random variables, can be derived
+%\begin{eqnarray*}
+%   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
+%  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
+%  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
+%  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
+%\end{eqnarray*}
+%
+%Since we can state that
+%\begin{eqnarray*}
+% CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
+% CF_{x+k}(t) &=& e^{itk}CF_x(t)
+%\end{eqnarray*}
+%then we have:
+%%\begin{eqnarray}
+%%\end{eqnarray}
+%\begin{align}
+%  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
+%\end{align}
+%
+%%The CF for the contrast random variable can also be written as
+%Also due to
+%\begin{eqnarray*}
+%  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
+%  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
+%  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
+%   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
+%\end{eqnarray*}
+%then we arrive at:
+%\begin{align}
+%  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
+%\end{align}
+%with $\Gamma()$ and $B()$ denoting Gamma and Beta functions respectively.
+%
+%\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
+%\label{sec:appendix_sar_special_case_of_polsar}
+%
+%In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
+%Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2010_ACRS}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
+%\begin{eqnarray}
+%  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
+%  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
+%  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
+%  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
+%  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
+%  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
+%  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
+%  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
+%\end{eqnarray}
+%but also the following well-known results are considered for multi-look SAR, i.e. $d=1,L>1$:
+%  \begin{eqnarray}
+%I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
+%N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
+%  \end{eqnarray}
+%It will be shown that all of these results are special cases of the result derived previously and rewritten below:
+%\begin{eqnarray}
+%  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
+%  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
+%\end{eqnarray}
+%\begin{eqnarray}
+%  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
+%  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
+%  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
+%\end{eqnarray}
+%\begin{eqnarray}
+%  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
+%  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
+%  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
+%\end{eqnarray}
+%
+%This appendix also derives new results for multi-look SAR data,
+%  which can be thought of 
+%    either as extensions of the corresponding single-look SAR results
+%    or as simple cases of the POLSAR results presented above.
+%They are:
+%  \begin{eqnarray}
+%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
+%    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
+%    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
+%    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
+%    var(\mathbb{D}) &=& \psi^1(L) \\
+%    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
+%  \end{eqnarray}
+%
+%The derivation process detailed below consists of two-phases.
+%The first phase collapses the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
+%Mathematically this means setting the dimensional number in POLSAR to  $d=1$
+%  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.
+%
+%The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
+%The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2010_ACRS}.
+%Mathematically, it means setting $L=1$ in the multi-look result
+%  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2010_ACRS} (base-2 was chosen in the previous paper to simplify the computation).
+%
+%\subsection{Original Domain: SAR Intensity and its ratio}
+%
+%Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
+%we find that:
+%\begin{eqnarray*}
+%  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
+%  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
+%\end{eqnarray*}
+%Or in PDF forms, and applying the variable change theorem,:
+%\begin{eqnarray*}
+%    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
+%  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
+%%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
+%    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
+%  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
+%%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
+%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
+%\end{eqnarray*}
+%
+%Thus we have the following results for multi-look SAR:
+%\begin{eqnarray}
+%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
+%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
+%\end{eqnarray}
+%
+%Now setting $L=1$, these results become:
+%\begin{eqnarray}
+%    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
+%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
+%\end{eqnarray}
+%which is the same as stated in \cite{Le_2010_ACRS}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
+%
+%\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
+%
+%The result for multi-look SAR data written in the log-transformed domain can be derived from two different approaches.
+%The first is to follow a simplification method, where the results for log-transformed POLSAR data are simplified into log-transformed multi-look SAR results.
+%
+%The second approach is to apply log-transformation to the results derived in the previous section. In this section, it is shown that both approaches would result in identical results.
+%
+%Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
+%we have
+%\begin{eqnarray*}
+%  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
+%  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
+%\end{eqnarray*}
+%
+%Or in PDF form, and applying the variable change theorem we have:
+%\begin{eqnarray*}
+%  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
+%  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
+%%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
+%   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
+%  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
+% &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
+%\end{eqnarray*}
+%with $\bar{N} = \ln{\bar{I}}$. Thus the first approach arrives at
 %\begin{eqnarray}
 %   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
+%   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
 %\end{eqnarray}
-
-To compute summary statistics for the multi-look SAR dispersion,
-  set $d=1$ into Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
-we have:
-  \begin{eqnarray*}
-    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{L}) &=& \psi^1(L) \\
-    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-\end{eqnarray*}
-
-This completes the first phase of the derivation process.
-The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
-  and converting natural logarithm into base-2 logarithm.
-First, setting $L=1$ makes the above results become:
-\begin{eqnarray*}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
-    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
-    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
-    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
-\end{eqnarray*}
-with $\gamma$ denoting the Euler-Mascharoni constant.
-Then to convert to base-2 logarithm from natural logarithmic transformation,
-  we again use the variable change theorem.
-  That is:
-  \begin{eqnarray*}
-   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
-   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
-       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
-  \end{eqnarray*}
-\begin{eqnarray*}
-   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
-%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
-       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
-\end{eqnarray*}
-\begin{eqnarray*}
-  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
-  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray*}
-
-\subsection{Deriving the PDF for SAR dispersion and contrast}
-
-The PDF for SAR dispersion can be easily derived from
-  the PDF for the log-distance given above as:
-  \begin{equation}
-   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
-  \end{equation}
-due to $d=1$ and
-\begin{eqnarray*}
-  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
-  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
-\end{eqnarray*}
-
-Setting $L=1$ for Single-Look SAR we have
-\begin{equation}
-  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
-\end{equation}
-due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
-with $\gamma$ being the Euler Mascheroni constant (which equals $0.5772$). 
-In base-2 logarithm domain, invoking the variable change theorem:
-\begin{eqnarray*}
-  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
-  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
-\end{eqnarray*}
-Thus we have
-\begin{equation}
-  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
-\end{equation}
-which is consistent with the results found in our previous work \cite{Le_2010_ACRS}.
-
-Setting $d=1$ into Eqn. for contrast results in
-\begin{equation}
-  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
-\end{equation}
-The characteristic function would then be
-\begin{equation}
-  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
-\end{equation}
-Thus the PDF can be written as
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
-\end{equation}
-due to
-\begin{eqnarray*}
-  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
-       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
-  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
-%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
-        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
-\end{eqnarray*}
-
-Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
-we have the PDF for contrast of single-look SAR data:
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
-\end{equation}
-
-Converting to base-2 logarithm gives the following:
-\begin{eqnarray*}
-  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
-%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
-     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
-\end{eqnarray*}
-which is also consistent to the results shown in our previous work \cite{Le_2010_ACRS}.
+%
+%In the second approach, log-transformation is applied on previous results for multi-look SAR intensity and its ratio in the original domain (Eqns.
+\ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
+%This also arrives at the same results shown above, however the detailed working is omitted for brevity.
+%
+%%\begin{eqnarray*}
+%%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
+%%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
+%%\end{eqnarray*}
+%%Thus
+%%\begin{eqnarray*}
+%%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
+%%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
+%%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
+%%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
+%%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
+%%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
+%%\end{eqnarray*}
+%%
+%%Thus the second approach also arrives at
+%%\begin{eqnarray}
+%%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
+%%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
+%%\end{eqnarray}
+%
+%To compute summary statistics for the multi-look SAR dispersion,
+%  set $d=1$ into Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
+%we have:
+%  \begin{eqnarray*}
+%    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
+%    var(\mathbb{L}) &=& \psi^1(L) \\
+%    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
+%\end{eqnarray*}
+%
+%This completes the first phase of the derivation process.
+%The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
+%  and converting natural logarithm into base-2 logarithm.
+%First, setting $L=1$ makes the above results become:
+%\begin{eqnarray*}
+%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
+%   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
+%    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
+%    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
+%    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
+%\end{eqnarray*}
+%with $\gamma$ denoting the Euler-Mascharoni constant.
+%Then to convert to base-2 logarithm from natural logarithmic transformation,
+%  we again use the variable change theorem.
+%  That is:
+%  \begin{eqnarray*}
+%   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
+%   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
+%       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
+%  \end{eqnarray*}
+%\begin{eqnarray*}
+%   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
+%%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
+%       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
+%\end{eqnarray*}
+%\begin{eqnarray*}
+%  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
+%  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
+%  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
+%\end{eqnarray*}
+%
+%\subsection{Deriving the PDF for SAR dispersion and contrast}
+%
+%The PDF for SAR dispersion can be easily derived from
+%  the PDF for the log-distance given above as:
+%  \begin{equation}
+%   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
+%  \end{equation}
+%due to $d=1$ and
+%\begin{eqnarray*}
+%  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
+%  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
+%  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
+%\end{eqnarray*}
+%
+%Setting $L=1$ for Single-Look SAR we have
+%\begin{equation}
+%  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
+%\end{equation}
+%due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
+%with $\gamma$ being the Euler Mascheroni constant (which equals $0.5772$). 
+%In base-2 logarithm domain, invoking the variable change theorem:
+%\begin{eqnarray*}
+%  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
+%  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
+%\end{eqnarray*}
+%Thus we have
+%\begin{equation}
+%  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
+%\end{equation}
+%which is consistent with the results found in our previous work \cite{Le_2010_ACRS}.
+%
+%Setting $d=1$ into Eqn. for contrast results in
+%\begin{equation}
+%  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
+%\end{equation}
+%The characteristic function would then be
+%\begin{equation}
+%  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
+%\end{equation}
+%Thus the PDF can be written as
+%\begin{equation}
+%  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
+%\end{equation}
+%due to
+%\begin{eqnarray*}
+%  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
+%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
+%  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
+%%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
+%        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
+%\end{eqnarray*}
+%
+%Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
+%we have the PDF for contrast of single-look SAR data:
+%\begin{equation}
+%  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
+%\end{equation}
+%
+%Converting to base-2 logarithm gives the following:
+%\begin{eqnarray*}
+%  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
+%%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
+%     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
+%\end{eqnarray*}
+%which is also consistent to the results shown in our previous work \cite{Le_2010_ACRS}.
 

### 2013-09-25 paper_dev/article_pp.tex
for work in isprint

@@
 As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
-Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
-  as well as reminding us that SAR is a special case of POLSAR.
+Hence this derivation can be considered
+  either as cross-validation for the proposed POLSAR model
+  or as evidence showing that
+    the generic POLSAR model proposed in this article also covers the traditional model for SAR intensity in its natural coverage.
+%  as well as reminding us that SAR is a special case of POLSAR.
 
 The results for our models can be summarized using the following equations:
-\begin{align}
-  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
-  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
-  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
-  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
-  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
-  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align}
+\begin{align*}
+  |C_v| &\sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+%  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
+%  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
+%  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
+%  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
+%  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
+%  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
+\end{align*}
 
 Upon setting $d=1$ into the above equations,
-  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
-%Upon setting $d=1$ into the above models,
-%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+  the becomes:
 \begin{align*}
-  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
-  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
-  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
-  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
-  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
-  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
-  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
+  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
 \end{align*}
-The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+
+Since the PDF of chi-squared distribution can be written as:
+\begin{align*}
+\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
+\end{align*}
+, applying variable change theorem into the above equations results in:
+\begin{align*}
+  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
+\end{align*}
+These equations match exactly with the following traditional model for multi-look SAR intensity:
   \begin{eqnarray}
 I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
+\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
+  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
   \end{eqnarray}
-Furthermore, the following derivations for multi-look SAR data
-   show that it can be considered 
-    either as extensions of the corresponding single-look SAR results
-    or as simpler case of the POLSAR results:
-  \begin{align*}
-    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
-    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
-    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
-    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
-    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
-    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{align*}
-
-\section{Validating the proposed models against real-life data}
+considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.
+
+\section{Discussion}
+
+\subsection{Validating the proposed models against real-life data}
 \label{sec:polsar_models_validation}
 
-This section aims to verify the theoretical models against practical data.
-Since it is shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, only a simple validation is presented for this case.
-
+This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
+Both of these models require the estimation of two parameters from some given captured data.
+They are the dimensional number $d$ and the look number $L$.
+The dimensional number $d$ is related to the type of (POL)SAR data,
+  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
+The look-number $L$ can be taken either as nominally stated by the data provider,
+  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
+To show the robustness of the proposed models, their validation is also put to test on different types of POLSAR sensors.
+Specifically in this article, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
+  a fine-quad single-look complex RADARSAT2 image ($L=1$) are employed.
+Since the determinant of the covariance matrix is only significant on multi-look data,
+  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).
+
+Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  which have been validated extensively, the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
 In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
- The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
-%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-%The ENL is set to the nominal number of 4.
-%And good visual match is apparent in the final results.
+The histograms for both the intensity and intensity ratio (TODO:Replot) %the log-distance and contrast
+  are then plotted against the theoretical PDF given above.
+The plots are obtained with ENL set to both the nominal number of 4 and the estimated number of (TODO:CALC).
+Also presented are the plots of the same experiment applied on a homogeneous patch inside the nine-look processed RADARSAT2 image (TODO:NewPlot).
+In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
+In all cases, good visual match is apparent, which validates the model proposed above. %providing us a simple validation of the result.
 
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
+	\subfloat[AIRSAR (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	} \\
+	\subfloat[AIRSAR (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
 	}
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
-It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_1D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR log-distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
+	\subfloat[AIRSAR (HH) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}
+	\hfill	
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}  \\
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	}
+        \hfill
+        \subfloat[RADARSAT2 (HH) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	}
+        \hfill
+        \subfloat[RADARSAT2 (HH) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
 	}
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.
-It should be noted that an even better match than what is shown here is presented in Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} where a better ENL estimation is employed.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_1D}
 \end{figure}
@@
 The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
-While the match appears to be reasonably good, it can be further improved.
-Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
-  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
-With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
-
-%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
-%While the match appears to be reasonably good, it can be further improved.
-%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
-%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
-%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
-
-\subsection{Using the nominal ENL to validate the theoretical models} 
-\label{sec:valid_nominal_enl}
-
-The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
-Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.
-
-For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
-Both the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
-These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
-Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
-Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.
-
-The least-assumed stochastic processes for dispersion and contrast are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
-Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-Here a nominal look-number L=4 is used
-  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
-The plots, presented in Fig.
-  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
+Similar experiments like the one described for SAR data is carried out
+  for both types of polarimetric SAR
+  on both AIRSAR and RADARSAT2 datasets.
+The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.
 
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
+	\subfloat[AIRSAR (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
+	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
 	}
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_2D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
+	}
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	}
+ 	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
+	\subfloat[AIRSAR (HH-HV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
 	} 
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_2D}
 \end{figure}
 %endif
-
-Apart from dispersion and contrast,
-  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
-Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be presented in this section.
-As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
-In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
-  and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
-A close match is again observed, validating the models for log-distance and determinant ratio.
 
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
+	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_change_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_change_ratio}
 	}
 \end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_3D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
+	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}
+	\hfill	
+ 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_change_ratio}
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
+	}
+        \hfill
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_1D_change_ratio}
 	}
 \end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_3D}
 \end{figure}
@@
 
-Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
-  where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
-Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
-
-%ifdef FINAL
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-
-In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
-This is discussed in the next subsection.
-%The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
-%In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
-
-%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  where not only the look number is shown to be misused
-%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-%As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  the reason is due to the inappropriate look number being used.
-%Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
-%For now, let us simply observe that
-%  using appropriate estimation of the parameters, 
-%  the proposed models match reasonably well with the practical data.
-
-\subsection{Difference between the theoretical assumptions and the conditions found in practice}  
-\label{sec:improve_the_match_bw_theory_practice}
-
-Even though the assumptions made in developing this theory have intentionally been kept minimal, 
-in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
-However, practical conditions may not always satisfy these prerequisites,
-  a common and observable gap is noticed between the conditions found in practical real-life data and the theoretical assumptions.
-
-The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
-  the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
-However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
-  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
-Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
-Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.
-
-Thus in practical images, each physical radar cell may be spread over more than a single pixel,
-resulting in both %This results in 
-  a higher correlation between neighbouring pixels \cite{Raney_1988_TGRS_666} %that may be related within a single physical cell resolution,
-  and a reduced effective number of look\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
-The oversampling practice is also documented by the producers of SAR processors.
-For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolution combination for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
-In short, while the independent sample assumption is made out of necessity in theory,
-  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighbouring samples. % are actually correlated
-This documented imperfection also leads to the rise of effective number-of-look concept (ENL),
-  which is almost always smaller than the nominal look-number.
-
-The proposed model apparently can handle this imperfection. %that is found in practical data.
-The handling process, however, is slightly more complex.
-Instead of adopting the nominal Number of Looks given by the SAR processor,
-  an ENL must first be estimated from the given data.
-This is discussed in the next subsection.
-
-\subsection{ENL Estimation for POLSAR data}
-\label{sec:valid_enl_estimation}
-
-The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
-  before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
-  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-In a given POLSAR dataset, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
-  it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
-This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
-However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.
-
-This paper instead proposes an alternative approach that makes use of variance statistics in the homoskedastic log-domain.
-Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation}
-  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-  \label{eqn:expected_sample_var_log_as_function_of_enl}
-\end{equation}
-where $\psi^1()$ again denotes the tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for unknown $L$,
-  although it would also require some iterative computation.
-Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph, or from the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
-  \begin{equation}
-    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
-    \label{eqn:enl_estimation_formula}
-  \end{equation}
-Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  as well as illustrating the simplified approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots.}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relation between ENL and sample variance of log-determinant/log-intensity.}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-%endif
-
-\subsection{Using estimated ENL to better explain practical data}
-\label{sec:valid_improve_practice}
-
-To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
-Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
-  against the theoretical models for the nominal ENL value of 9.
-As expected the match is evidently not very close.
-
-We now compare this to the estimated ENL approach.
-First, an ENL estimate is obtained from the observable variance of the log-determinant. 
-Then the new sample histogram is overlaid on the same figure,
-  showing a much better consistency.
-This procedure can always be carried out for a given dataset,
-  as long as a homogeneous area can be defined and extracted.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics.
-However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL which matches the data much more closely.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-%endif
-
-The same approach can be applied on the AIRSAR Flevoland data to improve the validation described earlier.
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
-  even though it is to a much lesser extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through to a lesser extent than the RADARSAT2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extent than the RADARSAT 2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-%endif
-
-\section{Discussion}
+\subsection{Theoretical Implications of This Proposal}
 \label{sec:discussion}

### 2013-09-28 paper_dev/article.tex
simple update

@@
 %Problem statement  
-This proposes a scalar and representative observable for the multi-dimensional POLSAR data,
+This paper proposes a scalar and representative observable for the multi-dimensional POLSAR data,
   from which statistically consistent discrimination measures can be derived.
@@
 Consequently, the main beneficial implication of the proposed approach is that
-  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
-  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
+  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
+  which enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
+%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
 \end{abstract}
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-Similar to the SAR data, POLSAR data is stochastic.
-Moreover, it is multi-dimensional.
+Similar to the SAR data, the POLSAR data is stochastic.
+Moreover, it is multi-dimensional making it even harder to interpret.
 Under this context, it is therefore important to establish a simple and intuitive understanding of the data
-  and statistical models are undoubtedly crucial in understand the stochastic nature of the data.
+  and statistical models are undoubtedly crucial in understand the stochastic its nature.
 While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
   unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
-Practical POLSAR data processing, however, makes heavily uses of scalar discrimination measures,
-  which should be based on statistically consistent models for scalar yet representative observables of the multidimensional data.
+Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
+  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
+It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.
+
 %Moreover, to provide theoretical foundation for discrimination measures proposal,
@@
   but all of them are based on the likelihood ratio statistics.
-This statistical test should be based on a statistically consistent distribution
+This statistical test should be based on an exact and consistent statistical distribution
   but so far has only shown to be based on an asymptotic distribution.
@@
 The POLSAR data have been statistically modelled as following the complex Wishart distribution.
-As such the generic statistical model for the covariance matrix determinant, being just a scalar projection of the multidimensional data, is presented.
+Consequently, the generic statistical model for the covariance matrix determinant, being just a scalar projection of the multidimensional data, is presented.
+This model is then used to derive several scalar and consistent statistical models suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
+The specific two and three dimensional models of these models, 
+  which also include the derived discrimination measures,
+  are originally designed against both partial and full polarimetric SAR data.
+
 %The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
-It is also shown that
-  the specific one dimensional version of the generic model proposed in this paper
-  matches perfectly with the traditional statistical model used for SAR intensity.
-Furthermore, the approach proposed in this paper
-  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
-  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.
+Interestingly the paper also shows that %It is also shown that
+  the specific one dimensional versions of these models proposed 
+  match perfectly with the traditional statistical model used for SAR intensity.
+This effectively puts the one dimensional SAR theory to stay within the proposed scalar approach for multi dimensional POLSAR.
+With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong unifying and consistent foundation relating them all together.
+The applicability of these theoretical applications is illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+%Furthermore, the approach proposed in this paper
+%  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
+%  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.
 
@@
 % Prof Vun Comment: already mentioned above, no need to repeat
+%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
 
@@
 Specifically the following research results are to be achieved:
-  1. The generic multi-dimensional statistical model for the POLSAR covariance matrix is to be derived, 
-  2. The generic model is also shown not only providing a staititically consistent models for newly proposed POLSAR discrimination measures, namely the determinant-ratio and the change-ratio.
+  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
+  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
   3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,

### 2013-09-30 paper_dev/article.tex
update to work on Windows u

@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_3D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_3D_determinant}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_2D_change_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_2D_change_ratio}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
 		 \label{multi_look_dispersion}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
 		 \label{multi_look_contrast}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
 		 \label{multi_look_dispersion}
@@
 		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
 		 \label{multi_look_contrast}

### 2013-09-30 paper_dev/article_pp.tex
update to work on Windows u

@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{RADARSAT2_2D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_3D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_3D_change_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_3D_determinant}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 		 \epsfysize=2in
-		 \epsffile{images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_1D_change_ratio}
@@
 		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
 		 \label{multi_look_dispersion}
@@
 		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
 		 \label{multi_look_contrast}
@@
 		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
 		 \label{multi_look_dispersion}
@@
 		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
 		 \label{multi_look_contrast}

### 2013-09-30 paper_dev/article.tex
abc d

@@
 
-In this section, the generic scalar statistical model for POLSAR is presented.
-After the basic foundations of POLSAR statistical analysis is introduced,
-  this section presents the theoretical model for multi-dimensional POLSAR data.
+%In this section, the generic scalar statistical model for POLSAR is presented.
+In this section, after the basic foundations of POLSAR statistical analysis is introduced,
+  the generic scalar statistical model for the multi-dimensional POLSAR is presented.
+%  this section presents the theoretical model for multi-dimensional POLSAR data.
 
 In this paper, the POLSAR scattering vector is denoted as $s$.
-In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+For partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
   the vector is two-dimensional ($d=2$) and is normally written as: 
@@
 \end{equation}
-In the case of full and monostatic POLSAR data,
+For full and monostatic POLSAR data,
   the vector is three-dimensional ($d=3$) and is presented as:
@@
 \end{equation}
-where $s_i$ denotes the single-look scattering vector,
+where $L$ is the number of looks
+  and $s_i$ denotes the single-look scattering vector,
   which equals $s_{part}$ for the case of partial POLSAR or
-  $s_{full}$ for the case of full polarimetry,
-and $L$ is the number of looks.
+  $s_{full}$ for the case of full polarimetry.
 
@@
 that the ratio between the observable and expected values of the sample covariance matrix determinants
-  behave like a product of $d$ chi-squared random variables with different degrees of freedom: 
+  behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
 \begin{equation}
@@
 
-We will now use this result to develop the generic scalar statistical model for POLSAR. %log-transformed measures of distance.
+%We will now use 
+This result is used here to develop the generic scalar statistical model for POLSAR. %log-transformed measures of distance.
 From Eqn. \ref{eqn:prod_chi_squared_rv} %and \ref{eqn:sum_log_chi_squared_rv}
@@
 Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \cite{Rignot_1993_TGRS_896},
-in this article, the determinant-ratio is also proposed as a discrimination measure for the POLSAR data,
-  which also have just been shown to suffer from the multiplicative and heteroskedastic phenomena.
+in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data.
+  which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
 %Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
 %  this section introduces the consistent sense of distance for POLSAR.
-Assuming, on the one hand,
-  that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+
+%Assuming, on the one hand,
+For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
 then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
@@
 \end{eqnarray}
-
-On the other hand, under a looser assumption %From another perspective
-  where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
+%On the other hand, under a looser assumption %From another perspective
+For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
  then random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
@@
 \mathbb{R}_{\Sigma} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{R}_{C} &\sim& \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+\mathbb{R}_{C} &\sim& \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)} \label{eqn:change_ratio_distribution}
 %\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
@@
   indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
-  This claim is extrapolated from the widely-used intensity-ratio as SAR discrimination measure and is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case.
+This claim is extrapolated from the widely-used intensity-ratio as SAR discrimination measure
+  and will be further discussed in the next sections.
+%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
 %This result shows how
@@
 
-The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
-This section will show that the model is equally  applicable to the 1-dimensional ($d=1$) case,
+%The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
+This section shows that the proposed generic model is equally  applicable to the 1-dimensional ($d=1$) case,
   which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
-Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
-As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
+Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while the determinant $|C_v|$ is equivalent to  the scalar variance value.
+As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
 Hence this derivation can be considered
-  either as cross-validation for the proposed POLSAR model
-  or as evidence showing that
-    the generic POLSAR model proposed in this article also covers the traditional model for SAR intensity in its natural coverage.
+  both as cross-validation for the proposed POLSAR model
+  as well as evidence showing that
+    the proposed generic model for POLSAR also includes the traditional model for SAR intensity in its natural coverage.
 %  as well as reminding us that SAR is a special case of POLSAR.
@@
 Upon setting $d=1$ into the above equations,
-  the becomes:
+  the equations become:
 \begin{align*}
@@
 
-\section{Discussion}
-
-\subsection{Validating the proposed models against real-life data}
+\section{Unifying the different discrimination measures proposals for bpth SAR and POLSAR}
+
+At least for both fields of SAR and POLSAR, statistical models have always been the foundation to derive discrimination measures.
+For SAR, the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+For POLSAR, the same case should apply, 
+  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics.
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, 
+  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+
+As a matter of course, in view of the models given in Eqns \ref{eqn:determinant_distribution},
+  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be expressed as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+As a by-product of this exact derivation,
+  several discrimination measures for the common case of $L_x=L_y$ are also proposed.
+They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
+Compared to existing discrimination measures for POLSAR reviewed in section \ref{sec:lit_review}, 
+  the proposed dissimilarity measures are much simpler.
+They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.
+
+Thus the core of the proposed approach is that the determinant of the POLSAR covariance matrix is proposed as the scalar and representative observable of the complex and multi-dimensional data.
+%What is the novelty of your solution? What are its advantages
+Compared to other published scalar observables with accompanying statistical model,
+  the proposed observable and its models are highly representative of the multidimensional data.
+The representative power of the proposed observable is justified by the following reasons.
+Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
+And last but not least, this observable also leads to the determinant-ratio discrimination measure which
+  not only is simpler in concept and computation than the existing POLSAR discrimination measures
+  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
+% Prof Vun Comment: already mentioned above, no need to repeat
+%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
+However, before further discussion ensues, 
+  it is necessary to validate the models presented with practical data.
+
+\section{Validating the proposed models against real-life data}
 \label{sec:polsar_models_validation}
 
-This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
-Both of these models require the estimation of two parameters from some given captured data.
-They are the dimensional number $d$ and the look number $L$.
-The dimensional number $d$ is related to the type of (POL)SAR data,
+This section aims to verify the theoretical models given in Eqns.
+\ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
+All of these models require the estimation of two parameters from the captured data.
+These are (i) the dimensional number $d$ and (ii) the look number $L$.
+The dimensional number $d$ is related to the type of (POL)SAR data captured,
   with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
@@
   or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
-To show the robustness of the proposed models, their validation is also put to test on different types of POLSAR sensors.
-Specifically in this article, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
-  a fine-quad single-look complex RADARSAT2 image ($L=1$) are employed.
+
+To show the robustness of the proposed models, 
+  their validations are also put to test on different types of POLSAR sensors.
+Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
+  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
 Since the determinant of the covariance matrix is only significant on multi-look data,
@@
 
+\subsection{The Traditional case of SAR ($d=1$)}
+
 Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
-In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for both the intensity and intensity ratio (TODO:Replot) %the log-distance and contrast
+  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
+Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
+In the test, the intensity of single-channel SAR data (HH) for a homogeneous area in both the AIRSAR Flevoland dataset is extracted.
+The histograms for both the intensity and intensity ratio %the log-distance and contrast
   are then plotted against the theoretical PDF given above.
-The plots are obtained with ENL set to both the nominal number of 4 and the estimated number of (TODO:CALC).
-Also presented are the plots of the same experiment applied on a homogeneous patch inside the nine-look processed RADARSAT2 image (TODO:NewPlot).
-In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
-In all cases, good visual match is apparent, which validates the model proposed above. %providing us a simple validation of the result.
+Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
+The plots are obtained with ENL set an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
+%In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
+In all cases, good visual match is apparent, which hence validates the model proposed above. %providing us a simple validation of the result.
 
@@
 \caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
-\label{fig:verify_det_ratio_model_1D}
+\label{fig:verify_POLSAR_model_1D}
 \end{figure}
 
+\subsection{The Multi-dimensional case of POLSAR ($d=2,3$)}
+
 The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Similar experiments like the one described for SAR data is carried out
+Similar tests %like the one described for SAR data 
+  are carried out
   for both types of polarimetric SAR
   on both AIRSAR and RADARSAT2 datasets.
-The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.
+The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+From the plots, their visual matches again validates the proposed model.
 
@@
 
-\subsection{Theoretical Implications of This Proposal}
+%\subsection{Theoretical Implications of This Proposal}
+\section{Discussion}
 \label{sec:discussion}
 
-Let us begin by noting a few theoretical properties of the proposed statistical models.
+%Let us begin by noting
+To begin with a few theoretical properties of the proposed statistical models are discussed.
 First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
@@
 To fully represent the complex number, another observable is needed besides the magnitude.
-The magnitude however is much more widely used, as it can be shown that its is invariant to a change in the reference frame.
+The magnitude however is much more widely used, as it can be shown that it is invariant to a change in the reference frame.
 Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
@@
 The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
-This is also similar to the standard use of the magnitude when two or more complex numbers are to be compared. %, most of the times the magnitude is to be used.
-
-This leads to the application of the models in deriving discrimination measures.
-Besides the above properties, the theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
-In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
-  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
-can be simulated as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
-
+This is also similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+
+Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
 Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
@@
 
-%\appendices
-%\section{Homoskedastic Model for the Log-Determinant}
-%\label{chap:appendix_a}
-%
-%\subsection{Log-Chi-Square Distribution and its Derivatives}
-%%\section{Log-Chi-Square Distribution}
-%\renewcommand{\theequation}{\thesection.\arabic{equation}}
-%\setcounter{equation}{0}
-%
-%This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
-%
-%Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
-%\begin{equation}
-%pdf(\chi;\,k) =
-%  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
-%\label{eqn:chi_squared_dist_pdf:appdixA}
-%\end{equation}
-%
-%Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
-%\begin{equation}
-%pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
-%\end{equation}
-%
-%Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
-%\begin{equation}
-% \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
-%\end{equation}
-%into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
-%\begin{eqnarray*}
-%  d\chi &=& e^\Lambda d\Lambda \\
-%  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
-%\end{eqnarray*}
-%In other words, we have:
-%\begin{equation}
-%pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
-%\label{eqn:log_chi_square_dist_pdf}
-%\end{equation}
-%
-%From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, a characteristic function can be computed.
-%By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
-%\begin{eqnarray*}
-%\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
-%      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
-%      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
-%\end{eqnarray*}
-%with $\varphi_x(t)$ is the characteristic function,
-%     $F_X(x)$ is the CDF function of X and
-%     $f_X(x)$ is the PDF function of X.
-%Thus the characteristic function for the log-chi-squared distribution is defined as: 
-%\begin{equation}
-%\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
-%\end{equation}
-%
-%The Gamma function is defined over the complex domain as:
-%$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
-%Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
-%Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
-%%  \begin{eqnarray*}
-%%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
-%%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
-%%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
-%%  \end{eqnarray*}
-%
-%%Thus the characteristic function becomes
-%That is:
-%\begin{equation}
-%\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
-%\end{equation}
-%
-%Consequently, the first and second derivative of the log-chi-squared distribution can be computed.
-%The first derivative is given as:
-%\begin{equation}
-%  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
-%\end{equation}
-%due to
-%\begin{eqnarray*}
-%  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
-%  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
-%  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
-%  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
-%\end{eqnarray*}
-%where $\psi^0()$ denotes the di-gamma function.
-%
-%Meanwhile, the second derivative can be written as:
-%\begin{equation}
-%  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
-%\end{equation}
-%due to:
-%\begin{eqnarray*}
-%  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
-%  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
-%  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
-%  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
-%\end{eqnarray*}
-%with $\psi^1()$ denotes the tri-gamma function.
-%
-%The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
-%\begin{equation}
-%\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
-%  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
-%\end{equation}
-%
-%Thus
-%\begin{eqnarray*}
-% \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
-%  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
-%% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
-%% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
-%% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
-%\end{eqnarray*}
-%That gives the result:
-%\begin{equation}
-%  avg(\Lambda) = \psi^0(L) + ln(2)
-%\end{equation}
-%
-%Similarly, for the second moment,
-%\begin{eqnarray*}
-% \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
-%  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
-%% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
-%% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
-%% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
-%\end{eqnarray*}
-%That is equivalent to saying that
-%\begin{equation}
-%  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
-%\end{equation}
-%%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
-%%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.
-%
-%Thus we can state that
-%\begin{equation}
-%var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
-%\end{equation}
-%
-%\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
-%
-%In this section, the expected value and variance value of these mixture of random variables are derived
-%\begin{eqnarray}
-%\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
-%\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
-%\end{eqnarray}
-%given the averages and variances of individual components.
-%\begin{eqnarray}
-%avg \left[ \chi(2L) \right]&=&2L \\
-%var \left[ \chi(2L) \right]&=&4L \\
-%avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-%var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-%\end{eqnarray}
-%
-%Making use of the mutual independence property of each component $X_i$,
-%  the variance and expectation of the summation and product of random variables can be written as:
-%\begin{eqnarray*}
-%avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
-%var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
-%avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
-%var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
-%\end{eqnarray*}
-%
-%Thus they can be rewritten more usefully as:
-%\begin{eqnarray*}
-%  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-%  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-%  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-%  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-%\end{eqnarray*}
-%
-%\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
-%\label{sec:appendix_b}
-%
-%Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as
-%\begin{eqnarray}
-% CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
-%\end{eqnarray}
-%  then the CF for the following random variables,
-%  which are combinations of the above elementary random variables, can be derived
-%\begin{eqnarray*}
-%   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
-%  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
-%  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
-%  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
-%\end{eqnarray*}
-%
-%Since we can state that
-%\begin{eqnarray*}
-% CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
-% CF_{x+k}(t) &=& e^{itk}CF_x(t)
-%\end{eqnarray*}
-%then we have:
-%%\begin{eqnarray}
-%%\end{eqnarray}
-%\begin{align}
-%  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-%   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-%   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-%\end{align}
-%
-%%The CF for the contrast random variable can also be written as
-%Also due to
-%\begin{eqnarray*}
-%  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
-%  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-%  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
-%   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
-%\end{eqnarray*}
-%then we arrive at:
-%\begin{align}
-%  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-%\end{align}
-%with $\Gamma()$ and $B()$ denoting Gamma and Beta functions respectively.
-%
-%\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
-%\label{sec:appendix_sar_special_case_of_polsar}
-%
-%In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
-%Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2010_ACRS}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
-%\begin{eqnarray}
-%  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-%  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
-%  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
-%  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
-%  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
-%  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
-%  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-%  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-%\end{eqnarray}
-%but also the following well-known results are considered for multi-look SAR, i.e. $d=1,L>1$:
-%  \begin{eqnarray}
-%I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-%N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
-%  \end{eqnarray}
-%It will be shown that all of these results are special cases of the result derived previously and rewritten below:
-%\begin{eqnarray}
-%  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
-%  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
-%\end{eqnarray}
-%\begin{eqnarray}
-%  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
-%  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
-%  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-%\end{eqnarray}
-%\begin{eqnarray}
-%  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
-%  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
-%  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
-%\end{eqnarray}
-%
-%This appendix also derives new results for multi-look SAR data,
-%  which can be thought of 
-%    either as extensions of the corresponding single-look SAR results
-%    or as simple cases of the POLSAR results presented above.
-%They are:
-%  \begin{eqnarray}
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
-%    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
-%    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
-%    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
-%    var(\mathbb{D}) &=& \psi^1(L) \\
-%    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-%  \end{eqnarray}
-%
-%The derivation process detailed below consists of two-phases.
-%The first phase collapses the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
-%Mathematically this means setting the dimensional number in POLSAR to  $d=1$
-%  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.
-%
-%The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-%The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2010_ACRS}.
-%Mathematically, it means setting $L=1$ in the multi-look result
-%  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2010_ACRS} (base-2 was chosen in the previous paper to simplify the computation).
-%
-%\subsection{Original Domain: SAR Intensity and its ratio}
-%
-%Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
-%we find that:
-%\begin{eqnarray*}
-%  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
-%  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
-%\end{eqnarray*}
-%Or in PDF forms, and applying the variable change theorem,:
-%\begin{eqnarray*}
-%    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
-%  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
-%%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
-%    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
-%  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
-%%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
-%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
-%\end{eqnarray*}
-%
-%Thus we have the following results for multi-look SAR:
-%\begin{eqnarray}
-%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
-%\end{eqnarray}
-%
-%Now setting $L=1$, these results become:
-%\begin{eqnarray}
-%    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
-%\end{eqnarray}
-%which is the same as stated in \cite{Le_2010_ACRS}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
-%
-%\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
-%
-%The result for multi-look SAR data written in the log-transformed domain can be derived from two different approaches.
-%The first is to follow a simplification method, where the results for log-transformed POLSAR data are simplified into log-transformed multi-look SAR results.
-%
-%The second approach is to apply log-transformation to the results derived in the previous section. In this section, it is shown that both approaches would result in identical results.
-%
-%Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
-%we have
-%\begin{eqnarray*}
-%  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
-%  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
-%\end{eqnarray*}
-%
-%Or in PDF form, and applying the variable change theorem we have:
-%\begin{eqnarray*}
-%  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
-%  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
-%%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
-%   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-%  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
-% &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
-%\end{eqnarray*}
-%with $\bar{N} = \ln{\bar{I}}$. Thus the first approach arrives at
-%\begin{eqnarray}
-%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-%   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
-%\end{eqnarray}
-%
-%In the second approach, log-transformation is applied on previous results for multi-look SAR intensity and its ratio in the original domain (Eqns.
-\ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-%This also arrives at the same results shown above, however the detailed working is omitted for brevity.
-%
-%%\begin{eqnarray*}
-%%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
-%%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
-%%\end{eqnarray*}
-%%Thus
-%%\begin{eqnarray*}
-%%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
-%%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
-%%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
-%%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
-%%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
-%%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
-%%\end{eqnarray*}
-%%
-%%Thus the second approach also arrives at
-%%\begin{eqnarray}
-%%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-%%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
-%%\end{eqnarray}
-%
-%To compute summary statistics for the multi-look SAR dispersion,
-%  set $d=1$ into Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
-%we have:
-%  \begin{eqnarray*}
-%    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-%    var(\mathbb{L}) &=& \psi^1(L) \\
-%    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-%\end{eqnarray*}
-%
-%This completes the first phase of the derivation process.
-%The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
-%  and converting natural logarithm into base-2 logarithm.
-%First, setting $L=1$ makes the above results become:
-%\begin{eqnarray*}
-%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
-%   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
-%    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
-%    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
-%    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
-%\end{eqnarray*}
-%with $\gamma$ denoting the Euler-Mascharoni constant.
-%Then to convert to base-2 logarithm from natural logarithmic transformation,
-%  we again use the variable change theorem.
-%  That is:
-%  \begin{eqnarray*}
-%   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
-%   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
-%       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
-%  \end{eqnarray*}
-%\begin{eqnarray*}
-%   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
-%%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
-%       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
-%\end{eqnarray*}
-%\begin{eqnarray*}
-%  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
-%  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-%  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-%\end{eqnarray*}
-%
-%\subsection{Deriving the PDF for SAR dispersion and contrast}
-%
-%The PDF for SAR dispersion can be easily derived from
-%  the PDF for the log-distance given above as:
-%  \begin{equation}
-%   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
-%  \end{equation}
-%due to $d=1$ and
-%\begin{eqnarray*}
-%  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
-%  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-%  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
-%\end{eqnarray*}
-%
-%Setting $L=1$ for Single-Look SAR we have
-%\begin{equation}
-%  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
-%\end{equation}
-%due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
-%with $\gamma$ being the Euler Mascheroni constant (which equals $0.5772$). 
-%In base-2 logarithm domain, invoking the variable change theorem:
-%\begin{eqnarray*}
-%  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
-%  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
-%\end{eqnarray*}
-%Thus we have
-%\begin{equation}
-%  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
-%\end{equation}
-%which is consistent with the results found in our previous work \cite{Le_2010_ACRS}.
-%
-%Setting $d=1$ into Eqn. for contrast results in
-%\begin{equation}
-%  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
-%\end{equation}
-%The characteristic function would then be
-%\begin{equation}
-%  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
-%\end{equation}
-%Thus the PDF can be written as
-%\begin{equation}
-%  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
-%\end{equation}
-%due to
-%\begin{eqnarray*}
-%  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
-%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
-%  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
-%%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
-%        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
-%\end{eqnarray*}
-%
-%Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
-%we have the PDF for contrast of single-look SAR data:
-%\begin{equation}
-%  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
-%\end{equation}
-%
-%Converting to base-2 logarithm gives the following:
-%\begin{eqnarray*}
-%  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
-%%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
-%     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
-%\end{eqnarray*}
-%which is also consistent to the results shown in our previous work \cite{Le_2010_ACRS}.
-
 % references section

### 2013-09-30 paper_dev/article_pp.tex
abc d

@@
 
-\section{Discussion}
-
-\subsection{Validating the proposed models against real-life data}
+\section{Unifying the different discrimination measures proposals for bpth SAR and POLSAR}
+
+At least for both fields of SAR and POLSAR, statistical models have always been the foundation to derive discrimination measures.
+For SAR, the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+For POLSAR, the same case should apply, 
+  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics.
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, 
+  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+
+As a matter of course, in view of the models given in Eqns \ref{eqn:determinant_distribution},
+  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be expressed as:
+\begin{align*}
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+
+As a by-product of this exact derivation,
+  several discrimination measures for the common case of $L_x=L_y$ are further proposed.
+They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
+Compared to existing discrimination measures for POLSAR reviewed in section \ref{sec:lit_review}, 
+  the proposed dissimilarity measures are much simpler.
+They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.
+
+Thus the core of the proposed approach is that the determinant of the POLSAR covariance matrix is proposed as the scalar and representative observable of the complex and multi-dimensional data.
+%What is the novelty of your solution? What are its advantages
+Compared to other published scalar observables with accompanying statistical model,
+  the proposed observable and its models are highly representative of the multidimensional data.
+The representative power of the proposed observable is justified by the following reasons.
+Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
+And last but not least, this observable also leads to the determinant-ratio discrimination measure which
+  not only is simpler in concept and computation than the existing POLSAR discrimination measures
+  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
+% Prof Vun Comment: already mentioned above, no need to repeat
+%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
+However, before further discussion ensues, 
+  it is necessary to validate the presented theoretical model with real-life practical data.
+
+\section{Validating the proposed models against real-life data}
 \label{sec:polsar_models_validation}
 
-This section aims to verify the theoretical models given in Eqns. \ref{eqn:determinant_distribution} and \ref {eqn:determinant_ratio_distribution} against practical data.
-Both of these models require the estimation of two parameters from some given captured data.
-They are the dimensional number $d$ and the look number $L$.
-The dimensional number $d$ is related to the type of (POL)SAR data,
+This section aims to verify the theoretical models given in Eqns.
+\ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
+All of these models require the estimation of two parameters from the captured data.
+These are (i) the dimensional number $d$ and (ii) the look number $L$.
+The dimensional number $d$ is related to the type of (POL)SAR data captured,
   with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
@@
 \caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
-\label{fig:verify_det_ratio_model_1D}
+\label{fig:verify_POLSAR_model_1D}
 \end{figure}
@@
 
+\subsection{The Multi-dimensional case of POLSAR ($d=2,3$)}
+
 The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Similar experiments like the one described for SAR data is carried out
+Similar tests %like the one described for SAR data 
+  are carried out
   for both types of polarimetric SAR
   on both AIRSAR and RADARSAT2 datasets.
-The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795} and is also noted in the plots.
+The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+From the plots, their visual matches again validates the proposed model.
 
@@
 The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
-This is also similar to the standard use of the magnitude when two or more complex numbers are to be compared. %, most of the times the magnitude is to be used.
-
-This leads to the application of the models in deriving discrimination measures.
-Besides the above properties, the theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
-In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
-  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
-can be simulated as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
-
-Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+This is also similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+
+Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
+Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
 These applications however are not included in this paper, but rather left as a suggestion for future investigations.
-There are a few reasons for this decision.
-The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
-  the first being a faster ENL evaluation for POLSAR data and
-  the second being the visual evaluation of POLSAR speckle filters.
-The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
-Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
-It does not, technically speaking, focuses on proposing new discrimination measures.
-
-The advantages of this proposal are thus to be compared against other published models for POLSAR.
-Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
-While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
-This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
-Instead a straightforward binary evaluation would be sufficient.
-In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
-This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
-This is proven in section \ref{sec:sar_special_case_of_polsar}.
-No other existing models for POLSAR is known to have this property.
-
-Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
-This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
-There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
-  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
-
-There may have many beneficials implications for this proposal.
-One of the main benefits is believed to be that:
+%There are a few reasons for this decision.
+%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
+%  the first being a faster ENL evaluation for POLSAR data and
+%  the second being the visual evaluation of POLSAR speckle filters.
+%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
+%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
+%It does not, technically speaking, focuses on proposing new discrimination measures.
+
+%The advantages of this proposal are thus to be compared against other published models for POLSAR.
+%Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
+%While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
+%This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
+%Instead a straightforward binary evaluation would be sufficient.
+%In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
+%This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
+%This is proven in section \ref{sec:sar_special_case_of_polsar}.
+%No other existing models for POLSAR is known to have this property.
+%
+%Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
+%This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
+%There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
+%  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
+
+\section{Extending SAR data processing techniques towards POLSAR}
+
+Currently while the field of SAR is much more developed than the field of POLSAR,
+  the two fields however are quite separated.
+Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+With the newly gained, the current proposal provide the bridge between these two separated fields,
+  inviting potential extension of various SAR processing techniques to POLSAR data.
+%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+%We believe there are many more unexplored possibilities for such applications.
+
+There are many beneficial implications for this proposal.
+One of the main benefits is that:
   this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-This is illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+One example has already been presented in this paper, 
+  where existing SAR discrimination measures are extended towards POLSAR.
+Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.
+
 In evaluating SAR speckle filters, the intensity ratio is widely used.
@@
 Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+(TODO: shorten the above 2 paragraphs. 
+NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
 
@@
 
-Currently while the field of SAR is much more developed than the field of POLSAR,
-  the two fields however are quite separated.
-Hence many techniques applicable to SAR are not directly applicable to POLSAR.
-Under this context, the current proposal provide the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques to POLSAR data.
-For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-We believe there are many more unexplored possibilities for such applications.
-
 \section{Conclusion}

### 2013-10-01 paper_dev/article.tex
abc

@@
 As a by-product of this exact derivation,
-  several discrimination measures for the common case of $L_x=L_y$ are also proposed.
+  several discrimination measures for the common case of $L_x=L_y$ are further proposed.
 They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
@@
 However, before further discussion ensues, 
-  it is necessary to validate the models presented with practical data.
+  it is necessary to validate the presented theoretical model with real-life practical data.
 
@@
 Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
-Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
 These applications however are not included in this paper, but rather left as a suggestion for future investigations.
-There are a few reasons for this decision.
-The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
-  the first being a faster ENL evaluation for POLSAR data and
-  the second being the visual evaluation of POLSAR speckle filters.
-The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
-Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
-It does not, technically speaking, focuses on proposing new discrimination measures.
+%There are a few reasons for this decision.
+%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
+%  the first being a faster ENL evaluation for POLSAR data and
+%  the second being the visual evaluation of POLSAR speckle filters.
+%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
+%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
+%It does not, technically speaking, focuses on proposing new discrimination measures.
 
-The advantages of this proposal are thus to be compared against other published models for POLSAR.
-Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
-While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
-This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
-Instead a straightforward binary evaluation would be sufficient.
-In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
-This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
-This is proven in section \ref{sec:sar_special_case_of_polsar}.
-No other existing models for POLSAR is known to have this property.
+%The advantages of this proposal are thus to be compared against other published models for POLSAR.
+%Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
+%While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
+%This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
+%Instead a straightforward binary evaluation would be sufficient.
+%In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
+%This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
+%This is proven in section \ref{sec:sar_special_case_of_polsar}.
+%No other existing models for POLSAR is known to have this property.
+%
+%Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
+%This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
+%There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
+%  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
 
-Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
-This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
-There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
-  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
+\section{Extending SAR data processing techniques towards POLSAR}
 
-There may have many beneficials implications for this proposal.
-One of the main benefits is believed to be that:
+Currently while the field of SAR is much more developed than the field of POLSAR,
+  the two fields however are quite separated.
+Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+With the newly gained, the current proposal provide the bridge between these two separated fields,
+  inviting potential extension of various SAR processing techniques to POLSAR data.
+%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+%We believe there are many more unexplored possibilities for such applications.
+
+There are many beneficial implications for this proposal.
+One of the main benefits is that:
   this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-This is illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+One example has already been presented in this paper, 
+  where existing SAR discrimination measures are extended towards POLSAR.
+Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.
+
 In evaluating SAR speckle filters, the intensity ratio is widely used.
@@
 %What has been done?
-In this article,
+In this paper,
   based on the commonly used complex Wishart distribution for the POLSAR target vector,
-  a generic statistical model has been derived for the POLSAR covariance matrix determinant.
+  a generic statistical model has been proposed for the POLSAR covariance matrix determinant.
 Then the specific (d=2) and (d=3) versions of the derived model are respectively validated against real-life partial and full polarimetric SAR data.
-The article also shows a perfect match between the (d=1) specific model and the traditional model for SAR intensity,
-  effectively putting the existing SAR theories under the generic model's natural coverage.
-It also establish a new POLSAR discrimination measure: the determinant-ratio,
-  which essentially is the generic version of the SAR intensity ratio.
+The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,
+  which essentially are the generic version of the SAR intensity-ratio.
+At the same time, it also shows a perfect match between the (d=1) specific models and the traditional model for SAR intensity,
+  effectively encompassing the existing SAR theories within the proposed generic models' natural coverage.
 
 %What are the results? What are their advantages over others' results?
-The result is the proposal of the POLSAR covariance matrix determinant as the scalar and representative observable for the multi-dimensional POLSAR data.
-Compared to other published scalar observable, the proposed determinant is highly representative of the multi-dimensional data.
+The main result of this paper is the proposal to consider the POLSAR covariance matrix determinant as the scalar and representative observable for the multi-dimensional POLSAR data.
+Compared to other published scalar observables, the proposed determinant is highly representative of the multi-dimensional data.
 Its representative power is justified by the following reasons.
@@
 %What are their benefit?
-There are several beneficial implications of the proposal presented in this article.
+There are several beneficial implications of the proposed approach presented in this paper.
 Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
@@
 %What are their limitations? What problems this appears to solve, but actually is not?
-The theory proposed in this article also has its limitations.
-Firstly, the theoretical model proposed is based on the complex Wishart distribution.
-Thus its applicability is also limited by that of its foundation,
-  that is the proposed theoretical model is only guaranteed to work in homogeneous area.
+The models proposed in this article also has its limitations.
+Firstly, they are based on the complex Wishart distribution.
+%Thus its applicability is also limited by that of its foundation,
+%  that is the proposed theoretical model 
+  which is only guaranteed to work for homogeneous area.
 Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value,
   such a reduction is unlikely to be lossless.
-Finally, in this article, the theoretical model has only been validated for partial (d=2) and full (d=3) monostatic POLSAR data,
+
+In this paper, the theoretical model has only been validated for partial (d=2) and full (d=3) monostatic POLSAR data,
 %and hence What can be done next?
-  leaving the test of its validity on different types of dataset like bistatic POLSAR data (d=4) or interferrometric POLSAR data (d=6) a possible future work.
+  leaving the test of its validity for different types of dataset like bistatic POLSAR data (d=4) or interferrometric POLSAR data (d=6) a possible future work.
 Other possible future work includes
   an investigation on the applicability of this observables into POLSAR heterogeneous areas,
-  as well as further studies to explore the use of this theory in conjunction with other target decomposition techniques
+  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
     such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}, etc.

### 2013-10-01 paper_dev/article_pp.tex
abc

@@
   4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
-(Hai note: I kept this to keep my focus while working on this paper.
+(Hai NOTE: I kept this to keep my focus while working on this paper.
   It can be removed before the final submission.)
@@
 The plots are obtained with ENL set an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
-%In this case, even though the RADARSAT2 has a nominal look-number of 9, its ``true'' value is estimated as $L=$ (TODO:CALC).
 In all cases, good visual match is apparent, which hence validates the model proposed above. %providing us a simple validation of the result.

### 2013-10-02 paper_dev/article.tex
before going to work

@@
 This effectively puts the one dimensional SAR theory to stay within the proposed scalar approach for multi dimensional POLSAR.
-With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong unifying and consistent foundation relating them all together.
-The applicability of these theoretical applications is illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
+The applicability of these theoretical models is illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
 %Furthermore, the approach proposed in this paper
@@
 %How do you know if the problem is solved? State your research contribution to be achieved
-In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
-  that is representative of the multi-dimensional data.
-Specifically the following research results are to be achieved:
-  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
-  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
-  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
-  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
-(Hai note: I kept this to keep my focus while working on this paper.
-  It can be removed before the final submission.)
+%In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
+%  that is representative of the multi-dimensional data.
+%Specifically the following research results are to be achieved:
+%  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
+%  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
+%  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
+%  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
+%(Hai NOTE: I kept this to keep my focus while working on this paper.
+%  It can be removed before the final submission.)
 
 %Article Organization: Show that you deliver on the objectives and hence solve the stated problem
-The rest of this article is organized as follows.
-After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR,
-  section 3? derives the generic statistical model for the determinant of the POLSAR covariance matrix.
-Section 4? then validates the specific two and three dimensional versions of the model against real-life captured data.
-After section 5? illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
-  section 6? establishes the generic determinant-ratio descrimination measure which links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+Thus, the rest of this article is organized as follows.
+After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
+  derives the generic statistical model for the determinant of the POLSAR covariance matrix
+  and proposes several new discrimination measures for the multi-dimensional data.
+After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
+  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
+The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
+Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+  section \ref{sec:conclusion} finally concludes this paper.
 
@@
 
-\section{Unifying the different discrimination measures proposals for bpth SAR and POLSAR}
+\section{Unifying the different discrimination measures proposals for both SAR and POLSAR}
+\label{sec:link_sar_polsar}
 
-At least for both fields of SAR and POLSAR, statistical models have always been the foundation to derive discrimination measures.
-For SAR, the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
-For POLSAR, the same case should apply, 
-  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics.
-With the insight gained from section \ref{sec:sar_special_case_of_polsar}, 
-  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+Statistical models have always been the foundation to derive discrimination measures.
+This is true for both fields of SAR and POLSAR.
+For SAR, where the field is more or less settled on the issue,
+  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+For POLSAR, where the field is much less matured,
+  the same case should apply, 
+  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
 
-As a matter of course, in view of the models given in Eqns \ref{eqn:determinant_distribution},
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, this section presents a few results.
+%  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \cite{Rignot_1993_TGRS_896},
+  the statistical model proposed for POLSAR covariance matrix determinant is to be reviewed as providing the foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
+And second, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
+
+As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
   the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
@@
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+This, in essence, derives an exact statistical distribution for the likelyhood test statistics,
+  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.
 
@@
 They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
-Compared to existing discrimination measures for POLSAR reviewed in section \ref{sec:lit_review}, 
-  the proposed dissimilarity measures are much simpler.
+Compared to existing discrimination measures for POLSAR reviewed in Section \ref{sec:lit_review}, 
+  the proposed dissimilarity measures are simpler in both concept and computation.
 They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.
 
-Thus the core of the proposed approach is that the determinant of the POLSAR covariance matrix is proposed as the scalar and representative observable of the complex and multi-dimensional data.
-%What is the novelty of your solution? What are its advantages
-Compared to other published scalar observables with accompanying statistical model,
-  the proposed observable and its models are highly representative of the multidimensional data.
-The representative power of the proposed observable is justified by the following reasons.
-Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
-Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
-And last but not least, this observable also leads to the determinant-ratio discrimination measure which
-  not only is simpler in concept and computation than the existing POLSAR discrimination measures
-  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
-% Prof Vun Comment: already mentioned above, no need to repeat
-%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
+In short, with the newly gained insight,
+  the approach proposed in this paper provides a new bridge between the two fields of SAR and POLSAR.
+This invites the adaptation of many established SAR data processing techniques towards POLSAR data,
+  where this Section has just described a few examples.
 However, before further discussion ensues, 
@@
 
-\section{Extending SAR data processing techniques towards POLSAR}
-
-Currently while the field of SAR is much more developed than the field of POLSAR,
-  the two fields however are quite separated.
-Hence many techniques applicable to SAR are not directly applicable to POLSAR.
-With the newly gained, the current proposal provide the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques to POLSAR data.
-%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-%We believe there are many more unexplored possibilities for such applications.
-
-There are many beneficial implications for this proposal.
-One of the main benefits is that:
-  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-One example has already been presented in this paper, 
-  where existing SAR discrimination measures are extended towards POLSAR.
-Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.
-
-In evaluating SAR speckle filters, the intensity ratio is widely used.
-Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-Assuming a perfect filtering condition, the ratio image should only contain random noise.
-Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
-
-Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-  this technique can be equally applied to evaluate POLSAR speckle filters.
-In fact better results can be achieved.
-In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-  which is linear and additive in nature.
-Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-(TODO: shorten the above 2 paragraphs. 
-NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-
-To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
-  and the two POLSAR speckle filters are then applied to the patch.
-\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-
-Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-  the distortion impact of the filter can also be made visible by the residual image.
-In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-in the additive log-determinant image of the filtered output, 
-  such an observation can be made relatively easier by inspecting the residual image.
-
-There are many similar SAR data processing technique that may be adaptable to POLSAR.
-Examples in the same topic of evaluating speckle filters include
-  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+%\section{Extending SAR data processing techniques towards POLSAR}
+%
+%Currently while the field of SAR is much more developed than the field of POLSAR,
+%  the two fields however are quite separated.
+%Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+%With the newly gained, the current proposal provide the bridge between these two separated fields,
+%  inviting potential extension of various SAR processing techniques to POLSAR data.
+%%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+%%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+%%We believe there are many more unexplored possibilities for such applications.
+%  
+%There are many beneficial implications for this proposal.
+%One of the main benefits is that:
+%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+%One example has already been presented in this paper, 
+%  where existing SAR discrimination measures are extended towards POLSAR.
+%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+%
+%In evaluating SAR speckle filters, the intensity ratio is widely used.
+%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+%Assuming a perfect filtering condition, the ratio image should only contain random noise.
+%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+%
+%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+%  this technique can be equally applied to evaluate POLSAR speckle filters.
+%In fact better results can be achieved.
+%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+%  which is linear and additive in nature.
+%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+%(TODO: shorten the above 2 paragraphs. 
+%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+%
+%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters are then applied to the patch.
+%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+%
+%%ifdef FINAL
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%%ifdef REVIEW
+%\begin{figure}[h!]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%
+%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+%  the distortion impact of the filter can also be made visible by the residual image.
+%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+%in the additive log-determinant image of the filtered output, 
+%  such an observation can be made relatively easier by inspecting the residual image.
+%  
+%There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Examples in the same topic of evaluating speckle filters include
+%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 
@@
 There are several beneficial implications of the proposed approach presented in this paper.
+Currently while the field of SAR is much more developed than the field of POLSAR,
+  the two fields however are quite separated.
+Hence many techniques applicable to SAR are not directly applicable to POLSAR.
 Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
   its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+One example has already been presented in this paper, 
+  where existing SAR discrimination measures are extended towards POLSAR.
 At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.

### 2013-10-02 paper_dev/article_pp.tex
before going to work

@@
 %How do you know if the problem is solved? State your research contribution to be achieved
-In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
-  that is representative of the multi-dimensional data.
-Specifically the following research results are to be achieved:
-  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
-  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
-  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
-  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
-(Hai NOTE: I kept this to keep my focus while working on this paper.
-  It can be removed before the final submission.)
+%In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
+%  that is representative of the multi-dimensional data.
+%Specifically the following research results are to be achieved:
+%  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
+%  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
+%  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
+%  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
+%(Hai NOTE: I kept this to keep my focus while working on this paper.
+%  It can be removed before the final submission.)
 
 %Article Organization: Show that you deliver on the objectives and hence solve the stated problem
-The rest of this article is organized as follows.
-After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR,
-  section 3? derives the generic statistical model for the determinant of the POLSAR covariance matrix.
-Section 4? then validates the specific two and three dimensional versions of the model against real-life captured data.
-After section 5? illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
-  section 6? establishes the generic determinant-ratio descrimination measure which links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+Thus, the rest of this article is organized as follows.
+After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
+  derives the generic statistical model for the determinant of the POLSAR covariance matrix
+  and proposes several new discrimination measures for the multi-dimensional data.
+After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
+  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
+The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
+Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+  section \ref{sec:conclusion} finally concludes this paper.
 
@@
 
-\section{Unifying the different discrimination measures proposals for bpth SAR and POLSAR}
-
-At least for both fields of SAR and POLSAR, statistical models have always been the foundation to derive discrimination measures.
-For SAR, the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
-For POLSAR, the same case should apply, 
-  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics.
-With the insight gained from section \ref{sec:sar_special_case_of_polsar}, 
-  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
-
-As a matter of course, in view of the models given in Eqns \ref{eqn:determinant_distribution},
+\section{Unifying the different discrimination measures proposals for both SAR and POLSAR}
+\label{sec:link_sar_polsar}
+
+Statistical models have always been the foundation to derive discrimination measures.
+This is true for both fields of SAR and POLSAR.
+For SAR, where the field is more or less settled on the issue,
+  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+For POLSAR, where the field is much less matured,
+  the same case should apply, 
+  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
+
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, this section presents a few results.
+%  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \cite{Rignot_1993_TGRS_896},
+  the statistical model proposed for POLSAR covariance matrix determinant is to be reviewed as providing the foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
+And second, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
+
+As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
   the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
@@
 
-\section{Extending SAR data processing techniques towards POLSAR}
-
-Currently while the field of SAR is much more developed than the field of POLSAR,
-  the two fields however are quite separated.
-Hence many techniques applicable to SAR are not directly applicable to POLSAR.
-With the newly gained, the current proposal provide the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques to POLSAR data.
-%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-%We believe there are many more unexplored possibilities for such applications.
-
-There are many beneficial implications for this proposal.
-One of the main benefits is that:
-  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-One example has already been presented in this paper, 
-  where existing SAR discrimination measures are extended towards POLSAR.
-Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.
-
-In evaluating SAR speckle filters, the intensity ratio is widely used.
-Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-Assuming a perfect filtering condition, the ratio image should only contain random noise.
-Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
-
-Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-  this technique can be equally applied to evaluate POLSAR speckle filters.
-In fact better results can be achieved.
-In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-  which is linear and additive in nature.
-Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-(TODO: shorten the above 2 paragraphs. 
-NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-
-To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
-  and the two POLSAR speckle filters are then applied to the patch.
-\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-%endif
-
-Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-  the distortion impact of the filter can also be made visible by the residual image.
-In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-in the additive log-determinant image of the filtered output, 
-  such an observation can be made relatively easier by inspecting the residual image.
-
-There are many similar SAR data processing technique that may be adaptable to POLSAR.
-Examples in the same topic of evaluating speckle filters include
-  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+%\section{Extending SAR data processing techniques towards POLSAR}
+%
+%Currently while the field of SAR is much more developed than the field of POLSAR,
+%  the two fields however are quite separated.
+%Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+%With the newly gained, the current proposal provide the bridge between these two separated fields,
+%  inviting potential extension of various SAR processing techniques to POLSAR data.
+%%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+%%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+%%We believe there are many more unexplored possibilities for such applications.
+%  
+%There are many beneficial implications for this proposal.
+%One of the main benefits is that:
+%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+%One example has already been presented in this paper, 
+%  where existing SAR discrimination measures are extended towards POLSAR.
+%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+%
+%In evaluating SAR speckle filters, the intensity ratio is widely used.
+%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+%Assuming a perfect filtering condition, the ratio image should only contain random noise.
+%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+%
+%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+%  this technique can be equally applied to evaluate POLSAR speckle filters.
+%In fact better results can be achieved.
+%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+%  which is linear and additive in nature.
+%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+%(TODO: shorten the above 2 paragraphs. 
+%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+%
+%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters are then applied to the patch.
+%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+%
+%%ifdef FINAL
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%%ifdef REVIEW
+%\begin{figure}[h!]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%
+%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+%  the distortion impact of the filter can also be made visible by the residual image.
+%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+%in the additive log-determinant image of the filtered output, 
+%  such an observation can be made relatively easier by inspecting the residual image.
+%  
+%There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Examples in the same topic of evaluating speckle filters include
+%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 

### 2013-10-02 paper_dev/article.tex
ready to submit to ian & nick

@@
 \usepackage{cite} %for citations
+\renewcommand{\citedash}{--}
 \usepackage{url}
@@
 %  which apparently is multidimensional, complex and thus not very intuitive.
-There has been a few scalar observables with accompanying statistical models proposal for POLSAR (TODO:CITE from section II),
+There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
   but none of them is able to provide meaningful scalar discrimination measures.

### 2013-10-02 paper_dev/article_pp.tex
ready to submit to ian & nick

@@
   and statistical models are undoubtedly crucial in understand the stochastic its nature.
-While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
+While several multidimensional models have been proposed for the POLSAR data,
   unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
@@
 %Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-%(TODO: shorten the above 2 paragraphs. 
 %NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)

### 2013-10-02 paper_dev/cygwin_setup.sh

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
+  #echo $PATH
+  export MIKTEX_USERSTARTUPFILE=D:\\workspaces\\portable\\MikTex\\miktex\\config\\miktexstartup.ini
+  echo $MIKTEX_USERSTARTUPFILE
+  #D:\workspaces\portable\MikTex\miktex\config\miktexstartup.ini
+  export MIKTEX_BINDIR=/cygdrive/d/workspaces/portable/MikTex/miktex/bin/
+  export PATH=$PATH:/cygdrive/d/workspaces/portable/MikTex/miktex/bin/
+  export TEMP=/cygdrive/d/workspaces/portable/MikTex/miktex/temp/
+  export TMP=/cygdrive/d/workspaces/portable/MikTex/miktex/temp/
+  export TEMPDIR=/cygdrive/d/workspaces/portable/MikTex/miktex/temp/
+  export TMPDIR=/cygdrive/d/workspaces/portable/MikTex/miktex/temp
+
+  latex 'article.tex'
+  bibtex article
+  latex 'article.tex'
+  latex 'article.tex'
+
+fi
+

### 2013-10-07 paper_dev/article.tex
with review config 201310_Oct07

@@
-\documentclass[journal]{IEEEtran}
+\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
@@
 	\subfloat[AIRSAR (HH) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
-		 \label{RADARSAT2_1D_determinant}
-	} \\
 	\subfloat[AIRSAR (HH) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
@@
 	\hfill	
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}  \\
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	}
+        \hfill
         \subfloat[RADARSAT2 (HH) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
-	} \\
-	\subfloat[AIRSAR (HH) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
 	}
@@
         \subfloat[RADARSAT2 (HH) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
@@
 
-\begin{figure}[h]
+\begin{figure}[h!]
 \centering
 \begin{tabular}{c}
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
+	}
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	}
+ 	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
+	} \\
 	\subfloat[AIRSAR (HH-HV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_determinant}
-	} \\
 	\subfloat[AIRSAR (HH-HV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
-		 \label{AIRSAR_2D_det_ratio}
+		 \label{AIRSAR_1D_det_ratio}
 	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_det_ratio}
-	} \\
 	\subfloat[AIRSAR (HH-HV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
-		 \label{AIRSAR_2D_det_ratio}
-	} 
-	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_det_ratio}
+		 \label{AIRSAR_1D_det_ratio}
 	} 
@@
 	\subfloat[AIRSAR (HH-HV-VV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
@@
 	\hfill	
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}
+	\hfill	
+ 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_change_ratio}
+	} \\
 	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_3D_determinant}
-	} \\
-	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
-		 \label{AIRSAR_2D_det_ratio}
 	}
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_2D_det_ratio}
-	} \\
-	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
-		 \label{AIRSAR_2D_change_ratio}
+		 \label{RADARSAT2_1D_det_ratio}
 	} 
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
+		 \epsfxsize=2in
+		 \epsfysize=2in
 		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_2D_change_ratio}
+		 \label{RADARSAT2_1D_change_ratio}
 	}

### 2013-10-07 paper_dev/cygwin_setup.sh

@@ -12,10 +12,11 @@ if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
   export TEMPDIR=/cygdrive/d/workspaces/portable/MikTex/miktex/temp/
   export TMPDIR=/cygdrive/d/workspaces/portable/MikTex/miktex/temp
 
+fi
+
   latex 'article.tex'
   bibtex article
   latex 'article.tex'
   latex 'article.tex'
 
-fi
 

### 2013-10-12 paper_dev/article.tex
updated change ratio plots, before merging with Ian's changes

--- 2013-10-02 paper_dev/article.tex
@@
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
+
+\usepackage{graphicx}
+\usepackage{pstricks}
+
+\def\row{10}
+\def\column{10}
+
+\usepackage{xcolor}
+\definecolor{plot}{rgb}{1,0.652,0.1705}
+
+\newsavebox\IBox
+\savebox\IBox{\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}
+
+\psset
+{
+  xunit=\dimexpr\wd\IBox/\column,
+  yunit=\dimexpr\ht\IBox/\row,
+}
+
+\newcommand{\plotWithLegend}[1]{          
+          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
+	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
+	    \rput(5,1.5){\footnotesize{change-ratio}}
+	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
+	    \psline[linecolor=plot](5,8)(6,8)
+	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
+	    \rput(8,8){\footnotesize{model}}
+	    \rput(8,9){\footnotesize{data}}            
+          \end{pspicture}
+}
 
@@
 %Problem statement  
-This paper proposes a scalar and representative observable for the multi-dimensional POLSAR data,
+This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
   from which statistically consistent discrimination measures can be derived.
@@
 Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
-  to derive a scalar and generic statistical model for the multi-dimensional POLSAR data,
+  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
   which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
 As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
-  the proposed model is also shown to include the traditional model used for SAR intensity under its natural coverage.
+  the proposed model is also shown to include the traditional model of SAR intensity under its natural coverage.
 %What are the larger implications of the findings presented in this paper?
@@
   it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
-  which enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+  which simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
 %  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
@@
 technology to become a feasible and preferred technique for earth observation applications.
-SAR technology has since been extended in a few directions, one of which is the polarimetric SAR (POLSAR).
+SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
 POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-Similar to the SAR data, the POLSAR data is stochastic.
-Moreover, it is multi-dimensional making it even harder to interpret.
-Under this context, it is therefore important to establish a simple and intuitive understanding of the data
-  and statistical models are undoubtedly crucial in understand the stochastic its nature.
-While several multidimensional models have been proposed for the POLSAR data (TODO:CITE source thesis),
-  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
-Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
+Like SAR data, POLSAR data is stochastic.
+Moreover, it is multi-dimensional, making it even harder to interpret.
+Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
+ Statistical models are undoubtedly crucial in understanding its stochastic nature.
+While several %multidimensional 
+models have been proposed to describe POLSAR data, they
+  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
+Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
   which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
@@
 %  but none of them has led to scalar discrimination measures proposal.
-As such no observable has been widely accepted as being highly representative of the multi-dimensional data,
+As such no observable has been widely accepted as being highly representative of this multi-dimensional data,
   which severely limits their applicability in practical data processing applications.
-From an alternative approach, there are also a few POLSAR discrimination measures proposed,
-  but all of them are based on the likelihood ratio statistics.
+From an alternative approach, a few POLSAR discrimination measures have been proposed,
+  but all are based on the likelihood ratio statistics.
 This statistical test should be based on an exact and consistent statistical distribution
@@
 %Research Objective: Give your precise problem statement  
-This article hence present a scalar and representative observable, and its associated generic statistical model,
-  for the multi-dimensional POLSAR data that provides a consistent foundation for the derivation of POLSAR discrimination measures.
+This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
 %Now State your approach  
@@
 %Prof Vuns: comment: the article provides the result, not the journey!
-The POLSAR data have been statistically modelled as following the complex Wishart distribution.
-Consequently, the generic statistical model for the covariance matrix determinant, being just a scalar projection of the multidimensional data, is presented.
-This model is then used to derive several scalar and consistent statistical models suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
-The specific two and three dimensional models of these models, 
-  which also include the derived discrimination measures,
-  are originally designed against both partial and full polarimetric SAR data.
+POLSAR data have been statistically modelled as following the complex Wishart distribution.
+Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
+%
+%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
+%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.
 
@@
 Interestingly the paper also shows that %It is also shown that
-  the specific one dimensional versions of these models proposed 
+  the specific one dimensional versions of the proposed  models 
   match perfectly with the traditional statistical model used for SAR intensity.
-This effectively puts the one dimensional SAR theory to stay within the proposed scalar approach for multi dimensional POLSAR.
+This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
 With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
-The applicability of these theoretical models is illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
 %Furthermore, the approach proposed in this paper
@@
 %Article Organization: Show that you deliver on the objectives and hence solve the stated problem
-Thus, the rest of this article is organized as follows.
+The remainder of this article is organized as follows.
 After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
@@
 Section \ref{sec:discussion} presents a high-level discussion of the results presented before
-  section \ref{sec:conclusion} finally concludes this paper.
+  section \ref{sec:conclusion} finally concludes the paper.
 
@@
 Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
-  where it is shown that none of these is able to provide statistically consistent discrimination measures. 
+  where it is shown that none are able to provide statistically consistent discrimination measures. 
 Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
-  and it demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
-While an exact statistical distribution is expected for the test,
-  only asymptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
+  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
+While an exact statistical distribution is expected to be necessary for a test,
+  only an asymptotic distribution is used in the underlying approach \cite{Conradsen_2003_TGRS_4}.
 
@@
 \end{align}
-where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
+where $C_{i,j}$ denotes the $(i,j)$ elements of the POLSAR covariance matrix C,
  $||$ denotes absolute values
@@
 
-Taking the log-transformation of the above equation, and denote $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
+Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
 {\small
@@
 %In this section, the generic scalar statistical model for POLSAR is presented.
-In this section, after the basic foundations of POLSAR statistical analysis is introduced,
-  the generic scalar statistical model for the multi-dimensional POLSAR is presented.
+In this section, after the basic foundations of POLSAR statistical analysis are introduced,
+  the generic scalar statistical model for the multi-dimensional POLSAR will be presented.
 %  this section presents the theoretical model for multi-dimensional POLSAR data.
@@
   are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
-  the product and summation of these random variables also has fixed summary statistics.
+  the product and summation of these random variables also have fixed summary statistics.
 Specifically:
@@
 For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
- then random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
+ then a random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
 \begin{eqnarray}
@@
   indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
-This claim is extrapolated from the widely-used intensity-ratio as SAR discrimination measure
+This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
   and will be further discussed in the next sections.
@@
 As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
-Hence this derivation can be considered
-  both as cross-validation for the proposed POLSAR model
-  as well as evidence showing that
-    the proposed generic model for POLSAR also includes the traditional model for SAR intensity in its natural coverage.
+Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to map to the traditional model for SAR intensity in its natural coverage.
+%****IVM: Hai, by "natural coverage" above do you mean non-built-up areas, or are you using this as a figure of speech?
+Note: this sentence needs additional correction to include the word 'confidence'..
+I'll do that once you can confirm the meaning of 'natural coverage'.
 %  as well as reminding us that SAR is a special case of POLSAR.
@@
 \end{align*}
-, applying variable change theorem into the above equations results in:
+Applying variable change theorem into the above equations results in:
 \begin{align*}
@@
 
-Statistical models have always been the foundation to derive discrimination measures.
+Statistical models have always been the foundation for deriving discrimination measures.
 This is true for both fields of SAR and POLSAR.
@@
   the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
-For POLSAR, where the field is much less matured,
+For POLSAR, where the research field is much less mature,
   the same case should apply, 
-  except that so far only asymptotic distribution has been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
+  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
 
@@
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-This, in essence, derives an exact statistical distribution for the likelyhood test statistics,
+This, in essence, derives an exact statistical distribution for the likelihood test statistics,
   as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.
@@
 Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
-In the test, the intensity of single-channel SAR data (HH) for a homogeneous area in both the AIRSAR Flevoland dataset is extracted.
+In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
 The histograms for both the intensity and intensity ratio %the log-distance and contrast
   are then plotted against the theoretical PDF given above.
-Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
-The plots are obtained with ENL set an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
-In all cases, good visual match is apparent, which hence validates the model proposed above. %providing us a simple validation of the result.
+%Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
+The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
+In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
 
@@
 	\subfloat[AIRSAR (HH) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 	\subfloat[RADARSAT2 (HH) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+
+\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 \end{tabular}
-\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR dataset homogeneous patches}
 \label{fig:verify_POLSAR_model_1D}
@@
 The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
-From the plots, their visual matches again validates the proposed model.
+The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
+Fig.
+\ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
+It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
+Evidently the match is good for $d=2$.
 
+Similarly, Fig.
+\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+Again, although the histogram is much tighter, the match is visually obvious in all cases, apart from Fig.
+Fig.
+\ref{fig:verify_det_ratio_model_3D}e plotting the AIRSAR (HH-HV-VV) change ratio.
+This match is poorer becasue....
+%***IVM**** Hai, you had better find a good reason to explain this!!!
 \begin{figure}[h]
@@
 	\subfloat[AIRSAR (HH-HV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 	\subfloat[RADARSAT2 (HH-HV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}
+%\newsavebox\IBoxCRTwoR
+%\savebox\IBoxCRTwoR{\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}}
+%          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
+%	    \rput[bl](0,0){\usebox\IBoxCRTwoR}
+%	    \rput(5,1.5){\footnotesize{change-ratio}}
+%	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
+%	    \psline[linecolor=plot](5,8)(6,8)
+%	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
+%	    \rput(8,8){\footnotesize{model}}
+%	    \rput(8,9){\footnotesize{data}}
+%          \end{pspicture}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 \end{tabular}
-\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets}
 \label{fig:verify_det_ratio_model_2D}
@@
 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_2D_change_ratio}
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}
+%          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
+%	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}% \usebox\IBoxCRThreeR
+%	    \rput(5,1.5){\footnotesize{change-ratio}}
+%	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
+%	    \psline[linecolor=plot](5,8)(6,8)
+%	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
+%	    \rput(8,8){\footnotesize{model}}
+%	    \rput(8,9){\footnotesize{data}}
+%          \end{pspicture}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_2D_change_ratio}
@@
 \end{tabular}
-\caption{The specific d=3 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
 \label{fig:verify_det_ratio_model_3D}
@@
 %Let us begin by noting
-To begin with a few theoretical properties of the proposed statistical models are discussed.
+To begin, a few theoretical properties of the proposed statistical models are discussed.
 First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
 In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
-Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
-Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
+Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
   the models presented here are invariant to polarization basis transformations.
@@
 However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model should also be applicable to the coherency matrix.
+  the model is also applicable to the coherency matrix.
 
-It should be noted that the models are far from complete.
-While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
+It should be noted that despite these advantages, the model descriptions are far from complete.
+While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
   such a reduction is unlikely to be lossless.  
-Thus %to better understand POLSAR data
-the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+Ideally %to better understand POLSAR data
+the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
 
@@
   it was shown to be applicable to traditional SAR data as well.
-Since the models assumptions are quite minimal, they may potentially applicable to bi-static and interferometric data, although that would require further study.
+Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
 
-Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude as being representative of a complex number
-(in a sense this is also why intensity is widely considered representative of the SAR data complex).
-Similar to the determinant, the magnitude observable is also scalar and is not lossless.
-To fully represent the complex number, another observable is needed besides the magnitude.
-The magnitude however is much more widely used, as it can be shown that it is invariant to a change in the reference frame.
+Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
 Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-Thus while it is not fully representative of the POLSAR data, it can be said to be highly representative of it.
-The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
-This is also similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
 
@@
 %What has been done?
-In this paper,
-  based on the commonly used complex Wishart distribution for the POLSAR target vector,
-  a generic statistical model has been proposed for the POLSAR covariance matrix determinant.
-Then the specific (d=2) and (d=3) versions of the derived model are respectively validated against real-life partial and full polarimetric SAR data.
-The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,
-  which essentially are the generic version of the SAR intensity-ratio.
-At the same time, it also shows a perfect match between the (d=1) specific models and the traditional model for SAR intensity,
-  effectively encompassing the existing SAR theories within the proposed generic models' natural coverage.
+This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.%***IVM: Hai pls check this sentence!
+This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full polarimetric SAR data.
+The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
+At the same time, we have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
+  effectively bringing the existing SAR theories under the umbrella of this new model.
 
 %What are the results? What are their advantages over others' results?
-The main result of this paper is the proposal to consider the POLSAR covariance matrix determinant as the scalar and representative observable for the multi-dimensional POLSAR data.
-Compared to other published scalar observables, the proposed determinant is highly representative of the multi-dimensional data.
-Its representative power is justified by the following reasons.
+The main emphasis of this paper is the proposal to consider the POLSAR covariance matrix determinant as a scalar and representative observable for the multi-dimensional POLSAR data.
+Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
+Its representative power is justified for the following reasons.
 Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
 Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
-And last but not least, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
+Finally, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
 
@@
 There are several beneficial implications of the proposed approach presented in this paper.
-Currently while the field of SAR is much more developed than the field of POLSAR,
-  the two fields however are quite separated.
-Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
+Hence many techniques applicable to SAR can not be directly translated to POLSAR.
 Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
-  its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
+  its main benefit is that it enables the convenient adaptation of many existing SAR data processing techniques for POLSAR data.
 One example has already been presented in this paper, 
@@
 %What are their limitations? What problems this appears to solve, but actually is not?
-The models proposed in this article also has its limitations.
-Firstly, they are based on the complex Wishart distribution.
+Of course, the models proposed in this article also have their own limitations.
+Firstly, they are based on the complex Wishart distribution
 %Thus its applicability is also limited by that of its foundation,
 %  that is the proposed theoretical model 
-  which is only guaranteed to work for homogeneous area.
-Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value,
-  such a reduction is unlikely to be lossless.
+  which is only guaranteed to work for homogeneous areas.
+Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value, such a reduction is unlikely to be lossless in the general case.
 
-In this paper, the theoretical model has only been validated for partial (d=2) and full (d=3) monostatic POLSAR data,
+In this paper, the theoretical model has only been validated for partial ($d=2$) and full ($d=3$) monostatic POLSAR data,
 %and hence What can be done next?
-  leaving the test of its validity for different types of dataset like bistatic POLSAR data (d=4) or interferrometric POLSAR data (d=6) a possible future work.
+  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
 Other possible future work includes
@@
   as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
-    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}, etc.
+    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.
 

### 2013-10-12 paper_dev/article_pp.tex
updated change ratio plots, before merging with Ian's changes

@@
 %The POLSAR data, however, is multidimensional and stochastic.
-Similar to the SAR data, the POLSAR data is stochastic.
-Moreover, it is multi-dimensional making it even harder to interpret.
-Under this context, it is therefore important to establish a simple and intuitive understanding of the data
-  and statistical models are undoubtedly crucial in understand the stochastic its nature.
-While several multidimensional models have been proposed for the POLSAR data,
-  unfortunately, due to the multidimensional nature, they are complex and not very intuitive.
-Practical POLSAR data processing, however, makes heavily use of scalar discrimination measures,
+Like SAR data, POLSAR data is stochastic.
+Moreover, it is multi-dimensional, making it even harder to interpret.
+Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
+ Statistical models are undoubtedly crucial in understanding its stochastic nature.
+While several %multidimensional 
+models have been proposed to describe POLSAR data, they
+  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
+Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
   which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
@@
 \end{tabular}
-\caption{The specific d=1 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
 \label{fig:verify_POLSAR_model_1D}
@@
 The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
-From the plots, their visual matches again validates the proposed model.
-
+The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
+Fig.
+\ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
+It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
+Evidently the match is good for $d=2$.
+
+Similarly, Fig.
+\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+Again, although the histogram is much tighter, the match is visually obvious in all cases, apart from Fig.
+Fig.
+\ref{fig:verify_det_ratio_model_3D}e plotting the AIRSAR (HH-HV-VV) change ratio.
+This match is poorer becasue....
+%***IVM**** Hai, you had better find a good reason to explain this!!!
 %ifdef FINAL
@@
 \end{tabular}
-\caption{The specific d=2 models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific $d=2$ models are validated on both  RADARSAT2 and AIRSAR datasets}
 \label{fig:verify_det_ratio_model_2D}
@@
 However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model should also be applicable to the coherency matrix.
-
-It should be noted that the models are far from complete.
-While it is desirable to reduce the multi-dimensonal POLSAR data to a scalar value for many applications,
+  the model is also applicable to the coherency matrix.
+
+It should be noted that despite these advantages, the model descriptions are far from complete.
+While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
   such a reduction is unlikely to be lossless.  
-Thus %to better understand POLSAR data
-the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+Ideally %to better understand POLSAR data
+the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
 
@@
   it was shown to be applicable to traditional SAR data as well.
-Since the models assumptions are quite minimal, they may potentially applicable to bi-static and interferometric data, although that would require further study.
-
-Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude as being representative of a complex number
-(in a sense this is also why intensity is widely considered representative of the SAR data complex).
-Similar to the determinant, the magnitude observable is also scalar and is not lossless.
-To fully represent the complex number, another observable is needed besides the magnitude.
-The magnitude however is much more widely used, as it can be shown that it is invariant to a change in the reference frame.
+Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
+
+Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
 Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-Thus while it is not fully representative of the POLSAR data, it can be said to be highly representative of it.
-The important thing is that, it can be used to give a scalar comparison of the multi-dimensional data.
-This is also similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
 
@@
 %What are their limitations? What problems this appears to solve, but actually is not?
-The models proposed in this article also has its limitations.
-Firstly, they are based on the complex Wishart distribution.
+Of course, the models proposed in this article also have their own limitations.
+Firstly, they are based on the complex Wishart distribution
 %Thus its applicability is also limited by that of its foundation,
 %  that is the proposed theoretical model 
-  which is only guaranteed to work for homogeneous area.
-Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value,
-  such a reduction is unlikely to be lossless.
-
-In this paper, the theoretical model has only been validated for partial (d=2) and full (d=3) monostatic POLSAR data,
+  which is only guaranteed to work for homogeneous areas.
+Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value, such a reduction is unlikely to be lossless in the general case.
+
+In this paper, the theoretical model has only been validated for partial ($d=2$) and full ($d=3$) monostatic POLSAR data,
 %and hence What can be done next?
-  leaving the test of its validity for different types of dataset like bistatic POLSAR data (d=4) or interferrometric POLSAR data (d=6) a possible future work.
+  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
 Other possible future work includes

### 2013-10-12 paper_dev/article_pp_ivm.tex
updated change ratio plots, before merging with Ian's changes

--- 2013-05-18 paper_dev/article_pp.tex
@@
 \begin{abstract}
-This paper presents several novel scalar statistical models to represent the determinant of both partial and full polarimetric SAR (POLSAR) covariance matrices.
-Compared to other scalar statistical models for POLSAR,
-  the proposed models are highly representative of the multi-dimensional data
-  and enable useful discrimination measures to be easily determined. %consequently they lead to useful discrimination measures.
-When the multi-dimensional models are collapsed to a single dimension,
-  they are shown to exactly match the traditional statistical models for SAR intensity.
-The paper validates the theoretical models together with their derived discrimination measures using real world POLSAR data.  
-%IVMThe proposed generic models are envisioned to enable the adaptation of many existing SAR data processing techniques for use with POLSAR data.
-The intention is that these proposed generic models can facilitate the adaptation of existing SAR techniques to higher-dimensional POLSAR data.
-To illstrate, an example is given where the determinant-ratio and its additive version, contrast, are applied in the evaluation of POLSAR speckle filters.
+%Problem statement  
+This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
+  from which statistically consistent discrimination measures can be derived.
+%What actually were done? and As the result, what is learned?
+Specifically, the statistical behaviour of the POLSAR covariance matrix determinant is used
+  to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
+  which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
+As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
+  the proposed model is also shown to include the traditional model of SAR intensity under its natural coverage.
+%What are the larger implications of the findings presented in this paper?
+Consequently, the main beneficial implication of the proposed approach is that
+  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
+  which simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
+%  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
+%  and at the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
 \end{abstract}
@@
 
-During the past decades, exponential growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
+%What is the situation, the background context of your research? the BIG problem!
+During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
 technology to become a feasible and preferred technique for earth observation applications.
-SAR technology has since extended in a few directions, one of which is polarimetric SAR (POLSAR).
+SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
 POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
@@
 
-While statistical models are important in understanding the stochastic nature of both SAR and POLSAR, in extending our understanding towards multi-dimensional POLSAR, an important issue needs to be addressed.
-Namely that there now exists not one but many observable quantities in multi-channel POLSAR (as opposed to single-channel SAR intensity).
-The research community has responded largely by developing different statistical models for various POLSAR observables.
-However for a statistical model to be useful, scalar discrimination measures generally need to be derivable from it.
-Thus, practical applications for POLSAR data processing require dis-similarity measures that are scalar, consistent and preferably homoskedastic on the one hand.
-On the other hand, the observable quantity being modelled should be naturally representative of the high dimensionality POLSAR data.
-
-This paper presents novel statistical models for multi-dimensional POLSAR data as generalisations of the commonly used one-dimensional SAR statistical model.
-This approach makes feasible the adaptation of many existing SAR processing techniques, to be applied to POLSAR data.
-Specifically, statistical models for the heteroskedastic POLSAR determinant and its homoskedastic log-domain equivalent, together with several other discrimination measures are derived in section  \ref{sec:theoretical_model}.
-The representative properties of these observables are then demonstrated in section \ref{sec:sar_special_case_of_polsar}
-  where the multi-dimensional POLSAR data is collapsed to a one-dimensional SAR scenario.
-With this transformation, the determinant of the POLSAR covariance matrix is shown to be equivalent to SAR intensity,
-  which also brings many standard statistical models used with SAR  under the umbrella of these generic POLAR models.
-The proposed theoretical models are then validated against real life practical data in section \ref{sec:polsar_models_validation}.
-Section \ref{sec:discussion} briefly describes how evaluation of an existing SAR data processing technique, the speckle filter, can be extended to  POLSAR data processing using this approach.
-This is followed by a conclusion in Section \ref{sec:conclusion}.
+%Research Motivation: Why it is important to solve this problem?
+%The POLSAR data, however, is multidimensional and stochastic.
+Like SAR data, POLSAR data is stochastic.
+Moreover, it is multi-dimensional, making it even harder to interpret.
+Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
+ Statistical models are undoubtedly crucial in understanding its stochastic nature.
+While several %multidimensional 
+models have been proposed to describe POLSAR data, they
+  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
+Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
+  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
+It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.
+
+%Moreover, to provide theoretical foundation for discrimination measures proposal,
+%  statistically consistent models should be derived from this scalar observable.
+
+%How do others solve this problem?
+%The complex POLSAR data have been statistically modelled as following the complex Wishart distribution,
+%  which apparently is multidimensional, complex and thus not very intuitive.
+There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
+  but none of them is able to provide meaningful scalar discrimination measures.
+%  but none of them has led to scalar discrimination measures proposal.
+As such no observable has been widely accepted as being highly representative of this multi-dimensional data,
+  which severely limits their applicability in practical data processing applications.
+From an alternative approach, a few POLSAR discrimination measures have been proposed,
+  but all are based on the likelihood ratio statistics.
+This statistical test should be based on an exact and consistent statistical distribution
+  but so far has only shown to be based on an asymptotic distribution.
+
+%Research Objective: Give your precise problem statement  
+This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
+%Now State your approach  
+%This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
+%However, our survey of existing scalar models for POLSAR indicates that no statistical model for this observable has been published so far.
+%Consequently, in this article, the statistical behaviour of the determinant of POLSAR covariance matrix is further investigated.
+%Prof Vuns: comment: the article provides the result, not the journey!
+POLSAR data have been statistically modelled as following the complex Wishart distribution.
+Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
+%
+%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
+%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.
+
+%The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
+Interestingly the paper also shows that %It is also shown that
+  the specific one dimensional versions of the proposed  models 
+  match perfectly with the traditional statistical model used for SAR intensity.
+This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
+With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
+The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+%Furthermore, the approach proposed in this paper
+%  not only provides a consistent foundation for the different discrimination measures proposal in POLSAR
+%  but also leads to the establishment of a new discriminating measures: the determinant-ratio and the change-ratio.
+
+%What is the novelty of your solution? What are its advantages
+%Compared to other published scalar observables with accompanying statistical model,
+%  the proposed observable and its models are highly representative of the multidimensional data.
+%The representative power of the proposed observable is justified by the following reasons.
+%Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+%Secondly, the statistical model for this observable is shown as the generic multi-dimensional extension of the traditional and representative intensity model for the one dimensional SAR data.
+%And last but not least, this observable also leads to the determinant-ratio discrimination measure which
+%  not only is simpler in concept and computation than the existing POLSAR discrimination measures
+%  but also can be considered as the natural multi-dimensional extension of the commonly-used intensity-ratio discrimination measure in SAR.
+% Prof Vun Comment: already mentioned above, no need to repeat
+%hai thoughts: actually this should be included to justify our title, and our approach. It is however being moved to discussion / conclusion section
+
+%How do you know if the problem is solved? State your research contribution to be achieved
+%In summary, the main objective of this article is to propose the determinant of the POLSAR covariance matrix as a scalar observable
+%  that is representative of the multi-dimensional data.
+%Specifically the following research results are to be achieved:
+%  1. The generic scalar and representative statistical model for the determinant of the multi-dimensional POLSAR covariance matrix is to be derived, 
+%  2. This generic model is also shown leading to staititically consistent models for newly proposed POLSAR observables, namely the determinant-ratio and the change-ratio.
+%  3. The special one-dimensional version of the derived generic model is to be shown perfectly matches with the traditionally used SAR intensity model,
+%  4. All specific one, two and three dimensional versions of the derived generic model are to be validated against real-life captured data,
+%(Hai NOTE: I kept this to keep my focus while working on this paper.
+%  It can be removed before the final submission.)
+
+%Article Organization: Show that you deliver on the objectives and hence solve the stated problem
+The remainder of this article is organized as follows.
+After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
+  derives the generic statistical model for the determinant of the POLSAR covariance matrix
+  and proposes several new discrimination measures for the multi-dimensional data.
+After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
+  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
+The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
+Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+  section \ref{sec:conclusion} finally concludes the paper.
 
@@
 
-This section outlines related published work.
-In particular, section \ref{sec:lit_models} reviews various scalar statistical models used for different POLSAR observables.
-Its purpose is to show that none of those  models have led to statistically consistent discrimination measures. 
+%This section outlines related publication.
+Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
+  where it is shown that none are able to provide statistically consistent discrimination measures. 
 Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
   and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
-However, while an exact statistical distribution is needed for the test,
-  only an symptotic distribution is used in the original work \cite{Conradsen_2003_TGRS_4}.
-
-\subsection{Investigated Scalar Observables for POLSAR Data and their Statistical Models}
+While an exact statistical distribution is expected to be necessary for a test,
+  only an asymptotic distribution is used in the underlying approach \cite{Conradsen_2003_TGRS_4}.
+
+\subsection{Scalar Observables for POLSAR Data and their Statistical Models}
 \label{sec:lit_models}
@@
   \end{enumerate}
-
 More recently, statistical models for
-  each element of the POLSAR covariance matrix $S_{pq}S_{rs}^*$ \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been studied.
-While these models undoubtedly help in understanding POLSAR data,
-  none of these observables have been shown to meet the dual criteria of
-  1) resulting in statistically consistent discrimination measures and
+  each element of the POLSAR covariance matrix, i.e. $S_{pq}S_{rs}^*$, \cite{Lopez-Martinez_2003_TGRS_2232}
+  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been proposed.
+
+While these models undoubtedly help to further our understandings of the POLSAR data,
+  none of the underlying observables have been shown to meet the dual criteria of
+  1) resulting in statistically consistent discrimination measures and thus 
   2) being representative of the complex POLSAR data.
@@
 \end{align}
-where $C_{i,j}$ denotes the (i,j) elements of the matrix C,
+where $C_{i,j}$ denotes the $(i,j)$ elements of the POLSAR covariance matrix C,
  $||$ denotes absolute values
 and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR% covariance matrix
-, these dis-similarity measures are not widely used 
-  probably because of the multiplicative nature of the noisy data.
+However, in the context of POLSAR, % covariance matrix
+  these dissimilarity measures are not widely used 
+  mainly due to the multiplicative nature of the noisy data.
 
@@
 \end{equation}
-.
-
-%%***IVM: Hai, you haven't introduced the notation for these!! What is tr() (in eqn. 3), what is Lx, Ly.... I changed your A_{i,j} to C_{i,j} above, just after eqn.2
-
-Closer investigation of these dis-similarity measures reveals that most are related in some way. %to each other.
+
+Closer examination of these dissimilarity measures reveals that most of them are related in some ways. %to each other.
 The Bhattacharyya distance is easily shown to be related to the Barlett distance.
@@
 The close relation among the measures is further supported by the fact that
-  all of their proposing papers referenced the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as a foundation.
-In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrix $Z_x$ and $Z_y$,
+  all of their publications refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as the foundation.
+In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
   which have $L_x$ and $L_y$ as the corresponding number of looks,
@@
 
-Taking the log-transformation of the above statistics, and note that $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ it becomes 
-\begin{eqnarray}
-  Q &=& \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
-  \ln Q &=& L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
-\end{eqnarray}
-
-To detect changes, a test statistic is developed based on this measure of distance.
+Taking the log-transformation of the above equation, and denoting $C_{vx} = Z_x / L_x$, $C_{vy} = Z_y / L_y$ and $C_{vxy} = (Z_x + Z_y)/(L_x + L_y)$ then:
+{\small
+\begin{align}
+  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+\end{align}
+}
+
+To detect changes, a test statistic is developed for this discrimination measure.
 This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution has been proposed.
-
-\section{Scalar Statistical Models for POLSAR}  
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
+This paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
+  which is capable of providing an exact distribution for the test.
+
+\section{The Generic Scalar Statistical Model for POLSAR}  
 \label{sec:theoretical_model}
 
-In this section, several scalar statistical models for POLSAR are presented.
-After section \ref{sec:model_basic} briefly introduces the basic foundations, concepts and notation of this paper, %reviews related work in published literature,
-  section \ref{sec:polsar_heterosked_model_and_log_transform}
-  presents the theoretical models together with mathematical evidence for two related points.
-The first point is that the POLSAR data is multiplicative and heteroskedastic in its original domain.
-And the second conclusion states that log-transformation converts it into an additive and homoskedastic model.
-Some consistent measures of distance are then derived and presented in section \ref{sec:distance_measure}.
-
-\subsection{Basics of POLSAR Statistical Analysis}
-\label{sec:model_basic}
+%In this section, the generic scalar statistical model for POLSAR is presented.
+In this section, after the basic foundations of POLSAR statistical analysis are introduced,
+  the generic scalar statistical model for the multi-dimensional POLSAR will be presented.
+%  this section presents the theoretical model for multi-dimensional POLSAR data.
 
 In this paper, the POLSAR scattering vector is denoted as $s$.
-In the case of partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+For partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
   the vector is two-dimensional ($d=2$) and is normally written as: 
@@
 that the ratio between the observable and expected values of the sample covariance matrix determinants
-  behave like a product of $d$ chi-squared random variables with different degrees of freedom: 
+  behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
 \begin{equation}
-\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi^2 (2L-2i)
+\chi^d_L = (2L)^d \frac{|C_v|}{|\Sigma_v|} \sim \prod_{i=0}^{d-1} \chi (2L-2i)
 \label{eqn:prod_chi_squared_rv}  
@@
 
-Its log-transformed variable consequently 
-  behaves like a summation of $d$ log-chi-squared random variables with the same degrees of freedom  
-\begin{equation}
-\Lambda^d_L = ln \left[ (2L)^d \frac{|C_v|}{|\Sigma_v|} \right] \sim \sum_{i=0}^{d-1} \Lambda^\chi (2L-2i)
-\label{eqn:sum_log_chi_squared_rv}
-\end{equation}
-with
-  $\Lambda^\chi (k) \sim \ln \left[ \chi^2 (k) \right]$.
-We will now use this result to develop the statistical models for POLSAR. %log-transformed measures of distance.
-%***IVM added the sentence above... **Please check it's true!!!!
-
-\subsection{Original Hetoroskedastic Domain and the Homoskedastic Log-Transformation}
-\label{sec:polsar_heterosked_model_and_log_transform}
-
-In this section the multiplicative nature of POLSAR data is first illustrated.
- Log-transformation is used to convert  the data into a more familiar additive model.
-Heteroskedasticity, which is defined as the dependence of variance upon the underlying signal,
-  is shown to be present in the original POLSAR data.
-In the log-transformed domain, a homoskedastic model is demonstrated,
-  where sample variance is fixed and thus independent of the underlying signal.
-Several intermediate mathematical steps are not shown here, but can be found in Appendix \ref{chap:appendix_a}.
-
-From Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv}
-we can deduce the following relationships:
+%We will now use 
+This result is used here to develop the generic scalar statistical model for POLSAR. %log-transformed measures of distance.
+From Eqn. \ref{eqn:prod_chi_squared_rv} %and \ref{eqn:sum_log_chi_squared_rv}
+we have: %can deduce the following relationships:
 \begin{eqnarray}
-  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_distribution} \\
-  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
-\label{eqn:log_determinant_distribution}  
+  |C_v| &\sim& |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_distribution} %\\
+%  \ln|C_v| &\sim& \ln|\Sigma_v| - d \cdot \ln(2L) + \sum^{d-1}_{i=0} \Lambda(2L-2i)
+%\label{eqn:log_determinant_distribution}  
 \end{eqnarray}
@@
 In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered constant.
-Thus Eqn. \ref{eqn:determinant_distribution} indicates that: 
+Thus Eqn. \ref{eqn:determinant_distribution} indicates that 
   in the original POLSAR domain, a multiplicative speckle noise pattern is present.
-At the same time, Eqn. \ref{eqn:log_determinant_distribution} shows that
-  the logarithmic transformation has converted this to the more familiar additive noise.
-
-Since chi-squared random variables $X\ \sim\ \chi^2(k)\ $ follow a known PDF:
-\begin{equation}
-pdf(x;2L) =
-  \frac{x^{L-1} e^{-x/2}}{2^L \Gamma\left(L\right)}
-\label{eqn:chi_squared_dist_pdf:chap4}
-\end{equation}
-applying the variable change theorem, 
-  its log-transformed variable follows the PDF of:
-\begin{equation}
-  pdf(x;2L=k) = \frac{e^{Lx-e^x/2}}{2^{L}\Gamma(L)}
-\end{equation}
-
-Using these PDFs, the characteristic functions (CF) of both the chi-squared and log-chi-squared random variables
-  can be written as:
-  \begin{eqnarray}
-    CF_\chi(t) &=& (1-2it)^{−L} \\ 
-    CF_\Lambda(t) &=& 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} \label{eqn:log_chi_squared_characteristic_function}
-  \end{eqnarray}
- Their means and variances can subsequently be computed from these  characteristic functions, leading to the following relationships:  
-  \begin{eqnarray}
-    avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-  \end{eqnarray}
-  where $\psi^0()$ and $\psi^1()$ represent the digamma and trigamma functions respectively.
-
-Since the average and variance of both chi-squared distribution and log-chi-squared distribution are constant,
-  the product and summation of these random variables also has fixed summary statistics.
+
+Moreover, since the average and variance of these chi-squared distributions %and log-chi-squared distribution
+  are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
+  the product and summation of these random variables also have fixed summary statistics.
 Specifically:
+{\footnotesize
 \begin{align*}
-  avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
+%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
 \end{align*}
-
-Combining these results with Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}, we have:
+}
+
+Combining these results with Eqn. \ref{eqn:determinant_distribution} %and \ref{eqn:log_determinant_distribution}
+  , we have:
+{\footnotesize
 \begin{align}
   avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}\\
-  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
-  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}%\\
+%  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+%  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
 \end{align}
+}
 
@@
 In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
-At the same time, in the log-transformed domain, Eqn. \ref{eqn:var_log_det_is_homoskedastic} reveals that
-  the variance of $\ln |C_v|$ is invariant and independent of $\Sigma_v$ (i.e. it is homoskedastic).
-
-\subsection{Consistent Measures of Distance for POLSAR}
-\label{sec:distance_measure}
-
-Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
-  this section introduces the consistent sense of distance for POLSAR.
-Assuming, on the one hand, that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
-random variables,
-  ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
-  are observable according to the following definitions:
+
+Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \cite{Rignot_1993_TGRS_896},
+in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data.
+  which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
+%Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
+%  this section introduces the consistent sense of distance for POLSAR.
+
+%Assuming, on the one hand,
+For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
+%  are observable according to the following definitions:
+  is defined as:
 %Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
 \begin{eqnarray}
-  \mathbb{R} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}\\
-  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
+  \mathbb{R}_{\Sigma} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}%\\
+%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
 \end{eqnarray}
-
-On the other hand, under a looser assumption %From another perspective
-  where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
-  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
+%On the other hand, under a looser assumption %From another perspective
+For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
+ then a random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
 \begin{eqnarray}
-  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
-  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
+  \mathbb{R}_{C} &=& \frac{|C_1|}{|C_2|} \label{eqn:determinant_ratio_samples_observables}%\\
+%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
 \end{eqnarray}
-
-Using the results from Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det} we have
+where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
+
+%  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
+%\begin{eqnarray}
+%  \mathbb{D} &=& \ln{|C_v|} - avg(\ln{|C_v|}) \label{eqn:dispersion_observable}\\
+%  \mathbb{C} &=& \ln(|C_{v1}|) - \ln(|C_{v2}|) \label{eqn:contrast_observable}
+%\end{eqnarray}
+
+Using the results from Eqn. \ref{eqn:determinant_distribution}, %\ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det}
+  we have
 \begin{eqnarray}
-\mathbb{R} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi^2 (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
-\label{eqn:log_determinant_distance_distribution} \\ 
- \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
-\label{eqn:dispersion_distribution} \\ 
- \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\label{eqn:contrast_distribution}  
+\mathbb{R}_{\Sigma} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_ratio_distribution} \\
+\mathbb{R}_{C} &\sim& \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)} \label{eqn:change_ratio_distribution}
+%\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
+%\label{eqn:log_determinant_distance_distribution} \\ 
+% \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
+%\label{eqn:dispersion_distribution} \\ 
+% \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
+%\label{eqn:contrast_distribution}  
 \end{eqnarray}
-with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
-and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
-
-Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
-\begin{align}
-  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
-  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
-\end{align}
-
-Since each elementary component follows fixed distributions (i.e. $\chi^2(2L), \Lambda(2L), ... $),
-  it is natural that these variables also follow fixed distributions.
-Moreover, note that they are independent of the underlying signal $\Sigma_v$.
+%with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
+%and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
+
+%Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
+%\begin{align}
+%  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\mathbb{L}}(t) &= \frac{1}{L^{idt} \Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\mathbb{D}}(t) &= \frac{e^{ikt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
+%  CF_{\Delta(2L)} &= \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} \\
+%  CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
+%\end{align}
+
+Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
+  it is natural that this variable also follows fixed distributions.
+Moreover, it is independent of the underlying signal $\Sigma_v$,
+  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
+This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
+  and will be further discussed in the next sections.
+%is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
 %This result shows how
@@
 
-The previous section  introduced  theoretical models for 3-dimensional, d=3 full polarimetric and 2-dimensional, d=2 partial polarimetry, cases.
-This section will show that the model is equally  applicable to the 1-dimensional d=1 case,
+%The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
+This section shows that the proposed generic model is equally  applicable to the 1-dimensional ($d=1$) case,
   which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
-Mathematically, the sample covariance matrix is reduced to the sample variance while the determinant is equivalent to  the scalar value.
-As variance is equal to intensity for SAR data, our result is consistent with previous results for SAR intensity data.
-Hence this derivation can be considered as cross-validation evidence for the proposed POLSAR models
-  as well as reminding us that SAR is a special case of POLSAR.
+Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while the determinant $|C_v|$ is equivalent to  the scalar variance value.
+As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
+Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to map to the traditional model for SAR intensity in its natural coverage.
+%****IVM: Hai, by "natural coverage" above do you mean non-built-up areas, or are you using this as a figure of speech?
+Note: this sentence needs additional correction to include the word 'confidence'..
+I'll do that once you can confirm the meaning of 'natural coverage'.
+%  as well as reminding us that SAR is a special case of POLSAR.
 
 The results for our models can be summarized using the following equations:
-\begin{align}
-  \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
-  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
-  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
-  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
-  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
-  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align}
+\begin{align*}
+  |C_v| &\sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+%  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
+%  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
+%  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
+%  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
+%  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
+%  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
+\end{align*}
 
 Upon setting $d=1$ into the above equations,
-  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with the following two cases.
-First is the following results obtained from our previous work on single-look SAR \cite{Le_2010_ACRS} , i.e. $d=L=1$,
-%Upon setting $d=1$ into the above models,
-%  Appendix \ref{sec:appendix_sar_special_case_of_polsar} shows that the reduced results are consistent with
-%not only the following results from the our previous works on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$,
+  the equations become:
 \begin{align*}
-  I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim \log_2{\bar{I}} + pdf \left[ 2^xe^{-2^x}\ln2 \right] \\
-  \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ e^{-x} \right]  \\
-  \mathbb{L} &= \log_2{I} - \log_2{\bar{I}} \sim pdf \left[ 2^xe^{-2^x}\ln2 \right]\\
-  \mathbb{D} &= \log_2{I} - avg(\log_2{I}) \sim pdf \left[ e^{-(2^xe^{-\gamma})} 2^xe^{-\gamma} \ln2 \right] \\
-  \mathbb{C} &= \log_2{I_1} - \log_2{I_2} \sim pdf \left[ \frac{2^x}{(1+2^x)^2} \ln2 \right] \\
-  \mathbb{A} &= avg(\mathbb{L}) = -\gamma / \ln{2} \\
-  \mathbb{V} &= var(\mathbb{L}) = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
+  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
 \end{align*}
-The second is the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
+
+Since the PDF of chi-squared distribution can be written as:
+\begin{align*}
+\chi(2L) \sim pdf \left[ \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} \right]
+\end{align*}
+Applying variable change theorem into the above equations results in:
+\begin{align*}
+  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
+  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
+\end{align*}
+These equations match exactly with the following traditional model for multi-look SAR intensity:
   \begin{eqnarray}
 I &\sim& pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
+\mathbb{R}_{\bar{I}} = \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] \\
+  \mathbb{R}_{I} = \frac{I_1}{I_2} &\sim& pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
   \end{eqnarray}
-Furthermore, the following derivations for multi-look SAR data
-   show that it can be considered 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results:
+considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.
+
+\section{Unifying the different discrimination measures proposals for both SAR and POLSAR}
+\label{sec:link_sar_polsar}
+
+Statistical models have always been the foundation for deriving discrimination measures.
+This is true for both fields of SAR and POLSAR.
+For SAR, where the field is more or less settled on the issue,
+  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+For POLSAR, where the research field is much less mature,
+  the same case should apply, 
+  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
+
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, this section presents a few results.
+%  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
+First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \cite{Rignot_1993_TGRS_896},
+  the statistical model proposed for POLSAR covariance matrix determinant is to be reviewed as providing the foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
+And second, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
+
+As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
+  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+can be expressed as:
 \begin{align*}
-    \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
-    \mathbb{L} &= \ln{I} - \ln{\bar{I}} \sim pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-    \mathbb{D} &= \ln{I} - avg(\ln{I}) \sim pdf \left[ \frac{e^{L[x-\psi^0(L)]-e^{[x-\psi^0(L)]}}}{\Gamma(L)} \right] \\
-    \mathbb{C} &= \ln{I_1} - \ln{I_2} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right] \\
-    \mathbb{A} &= avg(\mathbb{L}) = \psi^0(L) - \ln{L} \\
-    \mathbb{V} &= var(\mathbb{L}) = \psi^1(L) \\
-    \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
+  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
 \end{align*}
+where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+This, in essence, derives an exact statistical distribution for the likelihood test statistics,
+  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.
+
+As a by-product of this exact derivation,
+  several discrimination measures for the common case of $L_x=L_y$ are further proposed.
+They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
+Compared to existing discrimination measures for POLSAR reviewed in Section \ref{sec:lit_review}, 
+  the proposed dissimilarity measures are simpler in both concept and computation.
+They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.
+
+In short, with the newly gained insight,
+  the approach proposed in this paper provides a new bridge between the two fields of SAR and POLSAR.
+This invites the adaptation of many established SAR data processing techniques towards POLSAR data,
+  where this Section has just described a few examples.
+However, before further discussion ensues, 
+  it is necessary to validate the presented theoretical model with real-life practical data.
 
@@
 
-This section aims to verify the theoretical models against practical data.
-Since we have shown that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  which have been validated extensively, only a simple validation is presented for this case.
-
-Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the results of an experiment carried out for the stated purpose.
-In the experiment, the intensity of single-channel SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.
-The histograms for the log-distance and contrast are then plotted against the theoretical PDF given above.
- The plot is obtained with ENL set to the nominal number of 4, and a good visual match is apparent, providing us a simple validation of the result.
-%Then the histograms for the log-distance and and contrast is plotted against the theoretical PDF given above.
-%The ENL is set to the nominal number of 4.
-%And good visual match is apparent in the final results.
+This section aims to verify the theoretical models given in Eqns.
+\ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
+All of these models require the estimation of two parameters from the captured data.
+These are (i) the dimensional number $d$ and (ii) the look number $L$.
+The dimensional number $d$ is related to the type of (POL)SAR data captured,
+  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
+The look-number $L$ can be taken either as nominally stated by the data provider,
+  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
+
+To show the robustness of the proposed models, 
+  their validations are also put to test on different types of POLSAR sensors.
+Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
+  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
+Since the determinant of the covariance matrix is only significant on multi-look data,
+  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).
+
+\subsection{The Traditional case of SAR ($d=1$)}
+
+Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
+Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
+In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
+The histograms for both the intensity and intensity ratio %the log-distance and contrast
+  are then plotted against the theoretical PDF given above.
+%Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
+The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
+In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
 
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
+	\subfloat[AIRSAR (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	} \\
+	\subfloat[AIRSAR (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
 	}
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR dataset homogeneous patches}
+\label{fig:verify_POLSAR_model_1D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[multi-look SAR log-distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_dispersion_pdf.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[multi-look SAR contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_multi_look_sar_contrast_pdf.eps} 	
-		 \label{multi_look_contrast}
+	\subfloat[AIRSAR (HH) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}
+	\hfill	
+	\subfloat[AIRSAR (HH) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}  \\
+	\subfloat[RADARSAT2 (HH) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_determinant}
+	}
+        \hfill
+        \subfloat[RADARSAT2 (HH) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	}
+        \hfill
+        \subfloat[RADARSAT2 (HH) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
 	}
 \end{tabular}
-\caption{Multi-Look SAR dispersion and contrast: modelled response matches very well with real-life captured data.}
-\label{fig:verify_multi_look_SAR_dispersion_contrast_models}
+\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_POLSAR_model_1D}
 \end{figure}
@@
 
+\subsection{The Multi-dimensional case of POLSAR ($d=2,3$)}
+
 The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Specifically, subsection \ref{sec:valid_nominal_enl} demonstrates a naive validation, where the nominal ENL is used for the model.
-While the match appears to be reasonably good, it can be further improved.
-Subsection \ref{sec:improve_the_match_bw_theory_practice} discusses why the nominal look-number given by (POL)SAR processors may not be accurate,
-  while subsection \ref{sec:valid_enl_estimation} proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in a homoskedastic model.
-With the newly estimated ENL, subsection \ref{sec:valid_improve_practice} demonstrates that the match between the theoretical model and the practical data is indeed further improved.
-
-%Specifically the first sub-section provides a naive validation, where the nominal ENL is used for the model.
-%While the match appears to be reasonably good, it can be further improved.
-%After the second sub-section discusses why the nominal look-number given by (POL)SAR processors may not be very accurate,
-%  the third sub-section proposes a new technique in estimating the Effective Number of Looks (ENL) using the consistent variance found in homoskedastic model.
-%With the newly estimated ENL, the final sub-section shows that the match between the theoretical model and the practical data is indeed further improved.
-
-\subsection{Using the nominal ENL to validate the theoretical models} 
-\label{sec:valid_nominal_enl}
-
-The stochastic models derived in the previous sections can be visualised  using histograms of the simulated data.
-Their accuracy can be verified by comparing to  histograms from real-life data samples extracted over a homogeneous area.
-
-For this purpose, a homogeneous sample area was chosen from the AIRSAR Flevoland POLSAR data.
-Both the the determinant and the log-transformed models are to be validated together with the associated dissimilarity measures, namely the determinant ratio, log-distance, dispersion and contrast.
-These are closely related in that the determinant and determinant ratio are simply scaled versions of each other.
-Meanwhile, the log-determinant, log-distance and dispersion are simply shifted versions of each other.
-Nevertheless, all will be separately evaluated in this experiment in order to reveal an interesting phenomenon.
-
-The least-assumed stochastic processes for dispersion and contrast are validated first.
-For each pixel in the region, the determinant of the covariance matrix is computed and the log-transformation applied.
-Then the average log-determinant of the POLSAR covariance matrix, i.e. $avg(ln|C_v|)$, is measured for dispersion.
-Subsequently the observable samples of dispersion and contrast are computed according to Eqns. \ref{eqn:dispersion_observable} and \ref{eqn:contrast_observable} in order to plot their histograms.
-
-At the same time, theoretical simulations according to Eqns. \ref{eqn:dispersion_distribution} and \ref{eqn:contrast_distribution} are carried out.
-Here a nominal look-number L=4 is used
-  while the dimensional number is set to either 3 or 2 for a full or partial polarimetric SAR dataset respectively.
-The plots, presented in Fig.
-  \ref {fig:verify_polsar_2x2_simulation_dispersion_contrast} show a good  visual match between the model and real data, validating the theoretical models for dispersion and contrast.
-
+Similar tests %like the one described for SAR data 
+  are carried out
+  for both types of polarimetric SAR
+  on both AIRSAR and RADARSAT2 datasets.
+The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
+Fig.
+\ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
+It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
+Evidently the match is good for $d=2$.
+
+Similarly, Fig.
+\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+Again, although the histogram is much tighter, the match is visually obvious in all cases, apart from Fig.
+Fig.
+\ref{fig:verify_det_ratio_model_3D}e plotting the AIRSAR (HH-HV-VV) change ratio.
+This match is poorer becasue....
+%***IVM**** Hai, you had better find a good reason to explain this!!!
 %ifdef FINAL
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
+	\subfloat[AIRSAR (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
+	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
 	}
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_2D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_dispersion_distribution.eps} 
-		 \label{dispersion_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_contrast_distribution.eps} 	
-		 \label{contrast_2x2}
+	\subfloat[RADARSAT2 (HH-HV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
+	}
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	}
+ 	\hfill	
+	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_dispersion_distribution.eps} 
-		 \label{dispersion_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_contrast_distribution.eps} 	
-		 \label{contrast_3x3}
+	\subfloat[AIRSAR (HH-HV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_2D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
 	} 
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
-\label{fig:verify_polsar_2x2_simulation_dispersion_contrast}
+\caption{The specific $d=2$ models are validated on both  RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_2D}
 \end{figure}
 %endif
-
-Apart from dispersion and contrast,
-  the other four models to be verified require an estimation of the ``ground truth'' underlying signal $|\Sigma_v|$.
-There are two ways to estimate this quantity over an homogeneous area.
-The traditional way is to simply set the ground truth signal equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v)$.
-Another approach is to estimate the true signal from the average of the log-determinant of the POLSAR covariance matrix (i.e. $avg[\ln|C_v|]$) using Eqn. \ref{eqn:avg_log_det}.
-Both approaches will be presented in this section.
-As the log-determinant average has already been computed, the second approach is hence used first for the validation of determinant-ratio and log-distance.
-
-Fig. \ref{fig:verify_polsar_2x2_simulation_det_ratio_log_distance} plots the determinant-ratio and log-distance models against real-life data.
-In this experiment, the theoretical models are simulated using Eqns \ref{eqn:determinant_ratio_distribution} 
-  and \ref{eqn:log_determinant_distance_distribution},
-  while the observable samples are computed using Eqns \ref{eqn:determinant_ratio_observables} and \ref{eqn:log_distance_observables}
-  with the true signal estimated from the log-determinant average, i.e. $avg(\ln|C_v|)$.
-%Again a reasonable match is observed which validates the models for log-distance and determinant ratio.  
-A close match is again observed, validating the models for log-distance and determinant ratio.
 
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
+	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_determinant}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+	} \\
+	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_2D_change_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_change_ratio}
 	}
 \end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_3D}
 \end{figure}
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_2x2}
-	} 
-	\hfill	
-	\subfloat[part-pol (2x2) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_distance_distribution.eps} 	
-		 \label{log_distance_2x2}
+	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_determinant}
+	} 
+	\hfill	
+	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+	}
+	\hfill	
+ 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
+		 \label{AIRSAR_3D_change_ratio}
 	} \\
-	\subfloat[full-pol (3x3) determinant ratio]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_ratio_distribution.eps} 
-		 \label{determinant_ratio_3x3}
-	} 
-	\hfill	
-	\subfloat[full-pol (3x3) log distance]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_distance_distribution.eps} 	
-		 \label{log_distance_3x3}
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
+	}
+        \hfill
+	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_1D_det_ratio}
+	} 
+	\hfill	
+	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+		 \epsfxsize=2in
+		 \epsfysize=2in
+		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_1D_change_ratio}
 	}
 \end{tabular}
-\caption{Validating determinant-ratio and log-distance models with $|\Sigma_v|$ is computed using $avg(\ln|C_v|)$}
-\label{fig:verify_polsar_2x2_simulation_det_ratio_log_distance}
+\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\label{fig:verify_det_ratio_model_3D}
 \end{figure}
@@
 
-Since the models for the determinant and log-determinant are just scaled or shifted versions of the models for determinant-ratio and log-distance, similar validation results are to be expected. 
-However, an interesting phenomena is observed during the validation process for the determinant and its log-transformed model,
-  where the theoretical behaviour is simulated by Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:log_determinant_distribution}.
-The phenomena occurs when the true signal is estimated using the average of the sample covariance matrix in its original domain.
-Subsequently in the validation plots presented in Fig \ref{fig:verify_polsar_2x2_simulation_det}, some small translation and scaling discrepancies are observed.% -- which are
-
-%ifdef FINAL
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[polsar (2x2) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_2x2_determinant_distribution.eps} 
-		 \label{determinant_2x2}
-	} 
-	\hfill	
-	\subfloat[polsar (2x2) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_2x2_log_det_distribution.eps} 	
-		 \label{log_det_2x2}
-	} \\ 
-	\subfloat[polsar (3x3) determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/verify_polsar_3x3_determinant_distribution.eps} 
-		 \label{determinant_3x3}
-	} 
-	\hfill	
-	\subfloat[polsar (3x3) log-determinant]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/verify_polsar_3x3_log_det_distribution.eps} 	
-		 \label{log_det_3x3}
-	} 
-\end{tabular}
-\caption{Validating determinant and log-determinant models with $\Sigma_v = avg(C_v)$}
-\label{fig:verify_polsar_2x2_simulation_det}
-\end{figure}
-%endif
-
-In summary the dispersion and contrast measures of distance are shown to match reasonably well with the practical data.
-The same can be stated for the other four models, namely: determinant, log-determinant, determinant ratio and log-distance,
-  if the underlying parameters can be estimated reasonably well for the given image.   
-However as described above a single ``true signal'' $|\Sigma_v|$ can have two different estimated values,
-  depending on which estimation method was being used.
-The discrepancy between these two values suggests that at least one parameter for the models was inaccurately estimated.
-This is discussed in the next subsection.
-%The discrepancy suggests that at least one parameter for the models was inaccurately estimated.
-%In fact, the next sub-section specifically indicates that the nominal look-number given by the (POL)SAR processor may not accurately reflect the true nature of the captured data.
-
-%But what model parameter were used wrongly, and even if that can be corrected, would a better match become observable?
-%The question is answered in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  where not only the look number is shown to be misused
-%  but also the match of between the theoretical model and the practical data is shown to improve as well once a better look number (ENL) is estimated.
-%As will be shown in Section \ref{sec:improve_the_match_bw_theory_practice}, 
-%  the reason is due to the inappropriate look number being used.
-%Furthermore, the match between the theoretical model and the practical data will also be shown to improve once a more accurate look number (ENL) is estimated.  
-%For now, let us simply observe that
-%  using appropriate estimation of the parameters, 
-%  the proposed models match reasonably well with the practical data.
-
-\subsection{Difference between the theoretical assumptions and the conditions found in practice}  
-\label{sec:improve_the_match_bw_theory_practice}
-
-Even though the assumptions made in developing this theory have intentionally been kept minimal, 
-in common with other similar derivations the proposed model in this paper is built upon certain presumptions.
-However, practical conditions may not always satisfy these prerequisites, thus we find a common and observable gap between the conditions found in practical real-life data and the theoretical assumptions.
-
-The assumption of statistical independence between samples (for both SAR and POLSAR data) is reasonable given that 
-  the transmission and receipt of analogue signals is independent for each radar pulse, i.e. for each resolution cell.
-However, the actual imaging mechanism in a real-life (POL)SAR processor is of a digital nature,
-  where the analogue signal is fed into an analogue-to-digital (ADC) sampling and conversion process.  
-Theoretically it is possible to define a sampling rate so that each digital pixel corresponds exactly to an separate analogue physical cell.
-Practically however, to ensure ``perfect reconstruction'', the sampling rate is normally set at a slightly higher value than the Nyquist rate.
-
-Thus in practical images, each physical radar cell may be spread over more than a single pixel,
-resulting in both %This results in 
-  a higher correlation between neighbouring pixels \cite{Raney_1988_TGRS_666} %that may be related within a single physical cell resolution,
-  and a reduced effective number of look\cite{Lee_1994_TGRS_1017} \cite{Anfinsen_2009_TGRS_3795}. 
-The oversampling practice is also documented by the producers of SAR processors.
-For AIRSAR, the sampling rate and pulse bandwidth combinations are either 90/40MHz or 45/20MHz \cite{JPL_2013_Web_AIRSAR_Impl}.
-While for RadarSat2, the pixel resolution and range - azimuth resolution combination for SLC fine-quad mode is advertised as $(4.7 \cdot 5.1)m^2/(5.2 \cdot 7.7)m^2$ \cite{MDA_2013_Web_RadatSat2_Description}.
-In short, while the independent sample assumption is made out of necessity in theory,
-  due to over-sampling practice in capturing systems, significant correlation is routinely observed among neighbouring samples. % are actually correlated
-This documented imperfection also leads to the rise of effective number-of-look concept (ENL),
-  which is almost always smaller than the nominal look-number.
-
-The proposed model apparently can handle this imperfection. %that is found in practical data.
-The handling process, however, is slightly more complex.
-Instead of adopting the nominal Number of Looks given by the SAR processor,
-  an ENL must first be estimated from the given data.
-This is discussed in the next subsection.
-
-\subsection{ENL Estimation for POLSAR data}
-\label{sec:valid_enl_estimation}
-
-The common approach in ENL estimation is to investigate the summary statistics of a known homogeneous area in the given data
-  before making inferences about the inherent ENL.
-The summary statistics for $|C_v|$ and $\ln|C_v|$ have been derived in Section \ref{sec:polsar_heterosked_model_and_log_transform},
-  where Eqn. \ref{eqn:avg_log_det} indicates that there is a relationship among $|avg(C_v)|,avg(\ln|C_v|),d,L$.
-In a given POLSAR datasat, since all values of $|avg(C_v)|,avg(\ln|C_v|),d$ are known,
-  it is possible to estimate the ``effective'' number of looks, by finding an $L$ that ensures the above relationship is valid.
-This approach was taken in \cite{Anfinsen_2009_TGRS_3795},
-  where an equation of exactly the same form as Eqn.  \ref{eqn:avg_log_det} was used to estimate the ENL.
-However, the only known way to solve the equation for unknown $L$ requires the use of an ``iterative numerical method''.
-
-We will instead propose an alternative approach making use of variance statistics in the homoskedastic log-domain.
-Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation}
-  var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-  \label{eqn:expected_sample_var_log_as_function_of_enl}
-\end{equation}
-where $\psi^1()$ again denotes the tri-gamma function.
-
-Thus theoretically, given some measurable value for $var  \left[ ln|C_v| \right]$, one could solve the above equation for unknown $L$,
-  although it would also require some iterative computation.
-Practically however, the shape of the right-hand-side can be pre-computed
-  and for each computed value of $var  \left[ ln|C_v| \right]$, a corresponding value for $L$ can be found by referencing the variance value on the pre-computed graph, or from the following equation:%, which is extended from a simpler SAR version \cite{Le_2013_TGRS_SAR_MSE} for POLSAR as:
-  \begin{equation}
-    \hat{L} = d \left( \frac{1}{var(\ln{|C_v|})} + 0.5 \right)
-    \label{eqn:enl_estimation_formula}
-  \end{equation}
-Fig. \ref{fig:plot_enl_var_relation_1x1_and_2x2}
-  shows the shapes of the function defined in Eqn. \ref{eqn:expected_sample_var_log_as_function_of_enl} for SAR and partial-POLSAR data $f_{d=1}(L)$ and $f_{d=2}(L)$
-  as well as illustrating the simplified approximation formula (Eqn. \ref{eqn:enl_estimation_formula}).
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relation between ENL and sample variance for log-determinant/log-intensity plots.}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[ENL and variance log-intensity relations for SAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-                 \epsffile{images/plot_enl_var_relation_1x1.eps} 
-		 \label{plot_enl_var_relation_1x1}
-	} 
-	\hfill	
-	\subfloat[ENL and var(log-det) relations for partial POLSAR data]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/plot_enl_var_relation_2x2.eps} 	
-		 \label{plot_enl_var_relation_2x2}
-	} 
-\end{tabular}
-\caption{The relation between ENL and sample variance of log-determinant/log-intensity.}
-\label{fig:plot_enl_var_relation_1x1_and_2x2}
-\end{figure}
-%endif
-
-\subsection{Using estimated ENL to better explain practical data}
-\label{sec:valid_improve_practice}
-
-To demonstrate the improvement obtained using this ENL estimation, a single-look complex fine-quad RADARSAT2 dataset is used as illustration. 
-Nine-look processing is first applied, followed by calculation of the dispersion histogram in the log-transformed domain for an homogeneous area.
-The histograms for both one-dimensional SAR and two-dimensional partial POLSAR data are plotted in Fig. \ref{fig:handling_radarsat2_oversampling_practice}
-  against the theoretical models for the nominal ENL value of 9.
-As expected the match is evidently not very close.
-
-We now compare this to the estimated ENL approach.
-First, an ENL estimate is obtained from the observable variance of the log-determinant. 
-Then the new sample histogram is overlaid on the same figure,
-  showing a much better consistency.
-This procedure can always be carried out for a given dataset,
-  as long as a homogeneous area can be defined and extracted.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{Nine-look processed Radarsat2 data does not always exhibit nine-look data characteristics.
-However the homoskedastic model in the log-transformed domain can successfully estimate an effective ENL which matches the data much more closely.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in Radarsat2 one-dimensional SAR data (HH)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.sar.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in Radarsat2 partial POLSAR data (HH-HV)]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_radarsat2_oversampling_practice.part_pol.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{9-look processed Radarsat2 data do not exactly exhibit 9-look data characteristics.
-Homoskedastic model in log-transformed domain can successfully estimate the effective ENL and model the data reasonably well.}
-\label{fig:handling_radarsat2_oversampling_practice}
-\end{figure}
-%endif
-
-The same approach can be applied on the AIRSAR Flevoland data to improve the validation described earlier.
-Fig. \ref{fig:handling_airsar_oversampling_practice_full_pol} shows that the over-sampling issue is also present in the AIRSAR Flevoland dataset,
-  even though it is to a much lesser extent. %with the nominal 4-look data actually have an effective number-of-look around 3.22 only.
-Still, the ``corrected'' ENL offers an evidently better match between the model and real-life data.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through to a lesser extent than the RADARSAT2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Handling over-sampling practice in AIRSAR part-pol dataset ]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_part_pol_log_distance.eps} 	
-		 \label{sar}
-	} 
-	\hfill	
-	\subfloat[Handling over-sampling practice in AIRSAR full-pol dataset]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/handling_airsar_oversampling_practice_full_pol_log_distance.eps} 	
-		 \label{part_pol}
-	}   
-\end{tabular}
-\caption{AIRSAR Flevoland also exhibits phenomena of over-sampling practice, through at a lesser extend than the RADARSAT 2 data.}
-\label{fig:handling_airsar_oversampling_practice_full_pol}
-\end{figure}
-%endif
-
+%\subsection{Theoretical Implications of This Proposal}
 \section{Discussion}
@@
 
-Let us begin by noting a few theoretical properties of the proposed statistical model.
+%Let us begin by noting
+To begin, a few theoretical properties of the proposed statistical models are discussed.
 First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
 In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
-Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of M.
-Thus similar to other eigenvalue based approach (e.g. entropy/anisotropy, ...),
+Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
+Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
   the models presented here are invariant to polarization basis transformations.
 
-Second, the model is developed for the POLSAR covariance matrix.
+Second, the models are developed for the POLSAR covariance matrix.
 However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model should also be applicable to the coherency matrix.
-
-The model is far from complete.
- It reduces the multi-dimensional POLSAR data to a scalar value.
-While this is probably desirable for a wide range of application,
+  the model is also applicable to the coherency matrix.
+
+It should be noted that despite these advantages, the model descriptions are far from complete.
+While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
   such a reduction is unlikely to be lossless.  
-Thus %to better understand POLSAR data
-the use of this technique could be complemented with some high-dimensional POLSAR target-decomposition techniques (e.g.
-the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar).
-
-However the proposed model is promising.
+Ideally %to better understand POLSAR data
+the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+
+Nevertheless the proposed models are promising.
 Even though initially developed for partial and monostatic POLSAR data,
   it was shown to be applicable to traditional SAR data as well.
-Since the models assumptions are quite minimal, they may also be found to apply to bi-static and interferometric data, although that would require significant further investigation.
-
-The theoretical models may also provide an alternative derivation for the widely used likelihood test statistics in POLSAR.
-In view of the models given in Eqns \ref{eqn:determinant_distribution} \& \ref{eqn:log_determinant_distribution},
-  the likelihood test statistics exposed in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
-can be simulated as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-As a by-product of this exact derivation, the current paper also proposed several simpler discrimination measures for the common case of $L_x=L_y$.
-
-Similar to the way that other measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
+
+Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
+Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+
+Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
+Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
-%***IVM remove this single sentence, it detracts from the argument...
-%Moreover many of the existing techniques in SAR may be adaptable for POLSAR data, such as visual evaluation of speckle filters.
-
-In evaluating SAR speckle filters, the intensity ratio is widely used.
-Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-Assuming a perfect filtering condition, the ratio image should only contain random noise.
-Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
-
-Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-  this technique can be equally applied to evaluate POLSAR speckle filters.
-In fact better results can be achieved.
-In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-  which is linear and additive in nature.
-Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.
-
-To briefly evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV),
-  a square 700$\times$700 pixel patch is extracted from the AIRSAR dataset,
-  and the two POLSAR speckle filters are then applied to the patch.
-\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-
-%ifdef FINAL
-\begin{figure}[h]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-		 \label{multi_look_contrast}
-	} \\
-	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-		 \label{multi_look_dispersion}
-	} 
-	\hfill	
-	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-		 \epsfxsize=3in
-		 \epsfysize=3in
-		 \epsffile{images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-		 \label{multi_look_contrast}
-	} 
-\end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
-\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-\end{figure}
-%endif
-
-Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-  the distortion impact of the filter can also be made visible by the residual image.
-In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-in the additive log-determinant image of the filtered output, 
-  such an observation can be made relatively easier by inspecting the residual image.
-
-Ian version: There are many similar SAR data processing techniques such as  the usage of  the mean and variance of the ratio image to quantitatively evaluate speckle filters.
-Evidently these techniques can also be adapted for POLSAR.
-Other examples of such techniques include existing SAR speckle filters, target detectors, land-cover classifiers and edge detectors.
-
-Hai version: (Ian have not seen this yet) There are many similar SAR data processing technique that may be adaptable to POLSAR.
-Examples in the same topic of evaluating speckle filters include
-  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
-
-In fact, at the time of this writing, the field of SAR is much more developed than the field of POLSAR.
-The two fields however are quite separated,
-  as many techniques applicable to SAR are not directly applicable to POLSAR.
-This work may build the bridge between these two separated fields,
-  inviting potential extension of various SAR processing techniques on POLSAR data.
-Here a specific example is shown
-  where, similar to the way ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-In general, we believe there are many more unexplored possibilities for such applications
-  which is only limited by our imagination.
+These applications however are not included in this paper, but rather left as a suggestion for future investigations.
+%There are a few reasons for this decision.
+%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
+%  the first being a faster ENL evaluation for POLSAR data and
+%  the second being the visual evaluation of POLSAR speckle filters.
+%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
+%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
+%It does not, technically speaking, focuses on proposing new discrimination measures.
+
+%The advantages of this proposal are thus to be compared against other published models for POLSAR.
+%Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
+%While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
+%This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
+%Instead a straightforward binary evaluation would be sufficient.
+%In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
+%This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
+%This is proven in section \ref{sec:sar_special_case_of_polsar}.
+%No other existing models for POLSAR is known to have this property.
+%
+%Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
+%This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
+%There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
+%  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
+
+%\section{Extending SAR data processing techniques towards POLSAR}
+%
+%Currently while the field of SAR is much more developed than the field of POLSAR,
+%  the two fields however are quite separated.
+%Hence many techniques applicable to SAR are not directly applicable to POLSAR.
+%With the newly gained, the current proposal provide the bridge between these two separated fields,
+%  inviting potential extension of various SAR processing techniques to POLSAR data.
+%%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
+%%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
+%%We believe there are many more unexplored possibilities for such applications.
+%  
+%There are many beneficial implications for this proposal.
+%One of the main benefits is that:
+%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+%One example has already been presented in this paper, 
+%  where existing SAR discrimination measures are extended towards POLSAR.
+%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+%
+%In evaluating SAR speckle filters, the intensity ratio is widely used.
+%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+%Assuming a perfect filtering condition, the ratio image should only contain random noise.
+%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+%
+%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+%  this technique can be equally applied to evaluate POLSAR speckle filters.
+%In fact better results can be achieved.
+%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+%  which is linear and additive in nature.
+%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+%
+%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters are then applied to the patch.
+%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+%
+%%ifdef FINAL
+%\begin{figure}[h]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%%ifdef REVIEW
+%\begin{figure}[h!]
+%\centering
+%\begin{tabular}{c}
+%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+%		 \label{multi_look_contrast}
+%	} \\
+%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+%		 \label{multi_look_dispersion}
+%	} 
+%	\hfill	
+%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+%		 \epsfxsize=3in
+%		 \epsfysize=3in
+%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+%		 \label{multi_look_contrast}
+%	} 
+%\end{tabular}
+%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+%\end{figure}
+%%endif
+%
+%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+%  the distortion impact of the filter can also be made visible by the residual image.
+%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+%in the additive log-determinant image of the filtered output, 
+%  such an observation can be made relatively easier by inspecting the residual image.
+%  
+%There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Examples in the same topic of evaluating speckle filters include
+%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 
@@
 
-A number of scalar statistical models for the determinant of the POLSAR covariance matrix are proposed and validated in this paper,
-  resulting in several consistent discrimination measures for POLSAR applications.
-The theoretical models are shown to be powerful in that
-  not only can they provide alternative and simple explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
-  but they can also be considered multi-dimensional extensions of traditional models for one-dimensional SAR data.
-They are also practically useful since they lead to several consistent discrimination measures.
-Moreover, compared to other scalar statistical models for POLSAR, the proposed models are excellent representations of the multi-dimensional POLSAR data.
-Consequently, the derived discrimination measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-Thus the models are envisioned to form a bridge inviting the adaptation of many existing SAR data processing techniques for POLSAR data.
-
-%In conclusion, a couple of scalar statistical models for the determinant of the POLSAR covariance matrix,
-%  which result in several consistent discrimination measures for POLSAR, are proposed and validated in this paper.
-%The theoretical model is shown to be comprehensive in that:
-%  not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation,
-%  it also can be considered as the multi-dimensional extension of the traditionally used models for one-dimensional SAR data.
-%Compared to other scalar statistical models for POLSAR, the proposed models are highly representative of the multi-dimensional POLSAR data.
-%%These properties lead to the derivation of several statistically consistent discrimination measures for POLSAR.
-%%Compared with other discrimination measure proposals, this paper suggests an exact distribution for the POLSAR likelihood statistical test.
-%%As a by-product of this exact modelling, simpler dis-similarity measures, i.e. contrast and determinant-ratio, are proposed for the common case of $Lx=Ly$.
-%
-
-%An additive and homoskedastic model, 
-%  which results in several scalar and consistent measures-of-distance for multi-variate POLSAR data
-%  is proposed in this paper.
-%The theoretical model is shown to be comprehensive:
-%not only it can provide alternative and sometimes simpler explanations to a range of theoretical concepts such as POLSAR test statistics or ENL estimation, 
-%it also potentially makes several well-known models for traditional SAR become applicable for POLSAR processing.  %IVM: <- changed this sentence, please check.
-%
-%The statistical model proposed in this paper is based on the determinant of the POLSAR covariance matrix  which, when converted into one-dimensional data,
-%  is gracefully transformed into traditional SAR intensity.
-%Consequently, the derived dissimilarity measures may be employed in a wide range of applications where a scalar number is required to represent the complex multi-dimensional POLSAR data.
-%%The model is also shown to be practically versatile and capable of handling two common imperfections found in practical data.   As an application of the model,
-%%  as well as an extension of our previous work on evaluating SAR speckle filters\cite{Le_2010_ACRS},
-%%  the application of these additive and homoskedastic distances in the context of evaluating POLSAR speckle filters is briefly explored with promising initial results presented.  
-%The models may also form a bridge, allowing the adaptation of many existing SAR data processing technique for POLSAR data,
-%  a quick example of this is briefly described in this paper.
-%This paper
-
-\appendices
-\section{Homoskedastic Model for the Log-Determinant}
-\label{chap:appendix_a}
-
-\subsection{Log-Chi-Square Distribution and its Derivatives}
-%\section{Log-Chi-Square Distribution}
-\renewcommand{\theequation}{\thesection.\arabic{equation}}
-\setcounter{equation}{0}
-
-This section provides the mathematical derivations for the log-transformed version of chi-squared random variables.
-
-Chi-squared random variables $\chi\ \sim\ \chi^2(k)\ $ follows the pdf:
-\begin{equation}
-pdf(\chi;\,k) =
-  \frac{\chi^{(k/2)-1} e^{-\chi/2}}{2^{k/2} \Gamma\left(\frac{k}{2}\right)}  
-\label{eqn:chi_squared_dist_pdf:appdixA}
-\end{equation}
-
-Setting L=k/2 into Eqn. \ref{eqn:chi_squared_dist_pdf:appdixA}
-\begin{equation}
-pdf(\chi) = \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)}
-\end{equation}
-
-Applying the variable change theorem, which states that: if $y=\phi(x)$ with $\phi(c)=a$ and $\phi(d)=b$, then:
-\begin{equation}
- \int_a^b \! f(y) \, dy = \int_c^d \! f[\phi(x)] \frac{d\phi}{dx} dx
-\end{equation}
-into the log-transformation, which changes the random variables $\Lambda=ln(\chi)$, we have:
-\begin{eqnarray*}
-  d\chi &=& e^\Lambda d\Lambda \\
-  \frac{\chi^{L-1}e^{-\chi/2}}{2^L\Gamma(L)} d\chi &=&  \frac{(e^\Lambda)^{L-1}e^{-e^\Lambda/2}}{2^L\Gamma(L)} e^\Lambda d\Lambda
-\end{eqnarray*}
-In other words, we have:
-\begin{equation}
-pdf(\Lambda;L) = \frac{e^{L \Lambda -e^\Lambda/2}}{2^L\Gamma(L)}
-\label{eqn:log_chi_square_dist_pdf}
-\end{equation}
-
-From the PDF given in Eqn. \ref{eqn:log_chi_square_dist_pdf}, a characteristic function can be computed.
-By definition, the characteristic function (CF) $\varphi_X(t)$ for a random variable $X$ is computed as:
-\begin{eqnarray*}
-\varphi_X(t) = \operatorname{E}\big[e^{itX}\big] 
-      &=& \int_{-\infty}^\infty e^{itx}\,dF_X(x) \\ 
-      &=& \int_{-\infty}^\infty e^{itx} f_X(x)\,dx 
-\end{eqnarray*}
-with $\varphi_x(t)$ is the characteristic function,
-     $F_X(x)$ is the CDF function of X and
-     $f_X(x)$ is the PDF function of X.
-Thus the characteristic function for the log-chi-squared distribution is defined as: 
-\begin{equation}
-\varphi_\Lambda(t)=\int_0^\infty e^{itx} \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)}\,dx 
-\end{equation}
-
-The Gamma function is defined over the complex domain as:
-$\Gamma(z) = \int_0^\infty  e^{-x} x^{z-1} dx .$
-Thus $\Gamma(L+it) = \int_0^\infty  e^{-x} x^{L+it-1} dx .$
-Set $x=e^z/2$ then $dx=e^z/2dz$, we have $\Gamma(L+it)= \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz$
-%  \begin{eqnarray*}
-%\Gamma(L+it)&=&\int_0^\infty  e^{-e^z/2} (e^z/2)^{L+it-1} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{-e^z/2} \frac{e^{z(L+it-1)}}{2^{L+it-1}} e^z/2 dz \\
-%  &=& \int_0^\infty  e^{itz} \frac{e^{Lz-e^z/2}}{2^{L+it}} dz
-%  \end{eqnarray*}
-
-%Thus the characteristic function becomes
-That is:
-\begin{equation}
-\varphi_\Lambda(t) = 2^{it} \frac{\Gamma(L+it)}{\Gamma(L)}  
-\end{equation}
-
-Consequently, the first and second derivative of the log-chi-squared distribution can be computed.
-The first derivative is given as:
-\begin{equation}
-  \frac{\partial \varphi_\Lambda(t)}{\partial t} = \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right]
-\end{equation}
-due to
-\begin{eqnarray*}
-  \frac{\partial \Gamma(x)}{\partial x} &=& \Gamma(x)\psi^0(x), \\
-  \frac{\partial \Gamma(L+it)}{\partial t} &=& i\Gamma(L+it)\psi^0(L+it), \\
-  \frac{\partial 2^{it}}{\partial t} &=& i2^{it}\ln(2), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t, 
-\end{eqnarray*}
-where $\psi^0()$ denotes the di-gamma function.
-
-Meanwhile, the second derivative can be written as:
-\begin{equation}
-  \frac{\partial ^2 \varphi_\Lambda(t)}{\partial t^2} = \frac{i^2 2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right)
-\end{equation}
-due to:
-\begin{eqnarray*}
-  \frac{d 2^{it} \Gamma(L+it)}{dt} &=& i 2^{it} \Gamma(L+it) \left[ \ln{2} + \psi^0(L+it) \right], \\
-  \frac{d \psi^0(t)}{dt} &=& \psi^1(t), \\
-  \frac{d \psi^0(L+it)}{dt} &=& i \psi^1(L+it), \\
-  \partial (u \cdot v) / \partial t &=& u \cdot \partial v /\partial t + v \cdot \partial u/\partial t,
-\end{eqnarray*}
-with $\psi^1()$ denotes the tri-gamma function.
-
-The $n^{th}$ moments of random variable $X$ can be computed from the derivatives of its characteristic function as:
-\begin{equation}
-\operatorname{E}\left(\Lambda^n\right) = i^{-n}\, \varphi_\Lambda^{(n)}(0)
-  = i^{-n}\, \left[\frac{d^n}{dt^n} \varphi_\Lambda(t)\right]_{t=0} \,\!
-\end{equation}
-
-Thus
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda\right) &=& i^{-1}\, \left[\frac{d\varphi_\Lambda(t)}{dt} \right]_{t=0} \,\! \\
-  &=& i^{-1} \left[ \frac{i 2^{it} \Gamma(L+it)}{\Gamma(L)} \left[ \ln{2} + \psi^0(L+it) \right] \right]_{t=0}
-% &=& 1/i \left[ \frac{d2^{it} \frac{\Gamma(L+it)}{\Gamma(L)} }{dt} \right]_{t=0} \\
-% &=& \frac{1}{\Gamma(L)i} \left[ \Gamma(L+it) \frac{d 2^{it}}{dt} + 2^{it}\frac{d\Gamma(L+it)}{dt} \right]_{t=0} \\
-% &=& \left[ \frac{\Gamma(L+it)}{\Gamma(L)i}i2^{it}\ln(2) \right]_{t=0} + \left[ \frac{2^{it}}{\Gamma(L)i}i\Gamma(L+it)\psi^0(L+it) \right]_{t=0} 
-\end{eqnarray*}
-That gives the result:
-\begin{equation}
-  avg(\Lambda) = \psi^0(L) + ln(2)
-\end{equation}
-
-Similarly, for the second moment,
-\begin{eqnarray*}
- \operatorname{E}\left(\Lambda^2\right) &=& i^{-2}\, \left[\frac{d^2\varphi_\Lambda(t)}{dt^2} \right]_{t=0} \,\! \\
-  &=& \left[ \frac{2^{it} \Gamma(L+it)}{\Gamma(L)} \left( \left[ \ln{2} + \psi^0(L+it) \right] ^ 2 + \psi^1(L+it) \right) \right]_{t=0}  
-% &=& -1i \left[ \frac{d \left( \frac{2^{it}\Gamma(L+it)}{\Gamma(L)} (ln2 + \psi^0(L+it)) \right) }{dt}  \right]_{t=0} \\
-% &=& \frac{-1i}{\Gamma(L)} \left[ \ln(2) \frac{d 2^{it}\Gamma(L+it)}{dt} + \frac{d 2^{it}\Gamma(L+it)\psi^0(L+it)}{dt}  \right]_{t=0} \\
-% &=& + \ln(2) (\psi^0(L)+\ln(2)) - \frac{i}{\Gamma(L)} \left[ \frac{d 2^{it}\Gamma(L+it)}{dt} \psi^0(L+it) + 2^{it}\Gamma(L+it) \frac{d \psi^0(L+it)}{dt} \right]_{t=0}
-\end{eqnarray*}
-That is equivalent to saying that
-\begin{equation}
-  E(\Lambda^2) = \left[ \psi^0(L)+\ln(2) \right]^2 + \psi^1(L)
-\end{equation}
-%since $\frac{d\psi^0(x)}{dx}=\psi^1(x)$ then
-%$E(X^2) = (\psi^0(L)+\ln(2))(\psi^0(L)+\ln(2)) + \psi^1(L)$.
-
-Thus we can state that
-\begin{equation}
-var(\Lambda)=E(\Lambda^2)-E^2(\Lambda)=\psi^1(L)
-\end{equation}
-
-\subsection{Averages and Variances of POLSAR Covariance Matrix Determinant and Log-Determinant}
-
-In this section, the expected value and variance value of these mixture of random variables are derived
-\begin{eqnarray}
-\chi^d_L &\sim& \prod_{i=0}^{d-1} \chi (2L-2i) \\
-\Lambda^d_L &\sim& \sum_{i=0}^{d-1} \Lambda (2L-2i)
-\end{eqnarray}
-given the averages and variances of individual components.
-\begin{eqnarray}
-avg \left[ \chi(2L) \right]&=&2L \\
-var \left[ \chi(2L) \right]&=&4L \\
-avg \left[ \Lambda(2L) \right] &=& \psi^0(L) + \ln2 \\
-var \left[ \Lambda(2L) \right] &=& \psi^1(L)
-\end{eqnarray}
-
-Making use of the mutual independence property of each component $X_i$,
-  the variance and expectation of the summation and product of random variables can be written as:
-\begin{eqnarray*}
-avg \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} avg(X_i), \\
-var \left( \sum^n_{i=1} X_i \right) &=& \sum^n_{i=1} var(X_i), \\
-avg \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} avg(X_i), \\ 
-var \left( \prod^n_{i=1} X_i \right) &=& \prod^n_{i=1} \left[ avg^2(X_i) + var(X_i) \right] - \prod^n_{i=1} avg^2(X_i).    
-\end{eqnarray*}
-
-Thus they can be rewritten more usefully as:
-\begin{eqnarray*}
-  avg \left[ \chi^d_L \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \chi^d_L \right] &=& \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, \\
-  avg \left[ \Lambda^d_L \right] &=& d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-  var \left[ \Lambda^d_L \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
-
-\section{Deriving the Characteristic Functions for the Consistent Measures of Distance}
-\label{sec:appendix_b}
-
-Given that the characteristic function (CF) of the elementary log-chi square distributions can be written as
-\begin{eqnarray}
- CF_{\Lambda(2L)}(t) &=& 2^{it}\Gamma(L+it)/\Gamma(L) \nonumber
-\end{eqnarray}
-  then the CF for the following random variables,
-  which are combinations of the above elementary random variables, can be derived
-\begin{eqnarray*}
-   \Lambda^d_L &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) \\
-  \mathbb{L} &\sim&  \Lambda^d_L -d \cdot \ln(2L) \\
-  \mathbb{D} &\sim& \mathbb{L} - d \cdot \ln{L} + \sum^{d-1}_{i=0} \psi^0(L-i) \\
-  \mathbb{C} &\sim&  \sum^{d-1}_{i=0} \left[ \Lambda(2L-2i) - \Lambda(2L-2i) \right]
-\end{eqnarray*}
-
-Since we can state that
-\begin{eqnarray*}
- CF_{\sum X_i}(t)   &=& \prod CF_{X_i}(t) \\
- CF_{x+k}(t) &=& e^{itk}CF_x(t)
-\end{eqnarray*}
-then we have:
-%\begin{eqnarray}
-%\end{eqnarray}
-\begin{align}
-  CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{L}} &= \frac{1}{L^{idt} \Gamma(L)^d}  \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
-   CF_{\mathbb{D}} &= \frac{ 1 }{\Gamma(L)^d} \prod^{d-1}_{j=0} e^{idt \psi^0(L-j)} \Gamma(L-j+it)  
-\end{align}
-
-%The CF for the contrast random variable can also be written as
-Also due to
-\begin{eqnarray*}
-  CF_{-\Lambda(2L)}(t) &=& 2^{-it}\frac{\Gamma(L-it)}{\Gamma(L)} \\ 
-  \Delta(2L) &\sim& \Lambda(2L) - \Lambda(2L) \\
-  \Gamma(L-it) \Gamma(L+it) &=&  \Gamma(2L)B(L-it,L+it) \\
-   CF_{\Delta(2L)}(t) &=& \frac{\Gamma(2L)B(L-it,L+it)}{\Gamma^2(L)} 
-\end{eqnarray*}
-then we arrive at:
-\begin{align}
-  CF_{\mathbb{C}} &=&  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j)B(L-j-it,L-j+it)}{\Gamma^2(L-j)} 
-\end{align}
-with $\Gamma()$ and $B()$ denoting Gamma and Beta functions respectively.
-
-\section{SAR intensity as a special case of POLSAR covariance matrix determinant}
-\label{sec:appendix_sar_special_case_of_polsar}
-
-In this appendix, the following results for SAR intensity $I$ are shown to be special cases of the results given in this paper for the determinant of the POLSAR covariance matrix $det|C_v|$.
-Specifically, the following results extend from the authors previous work on single-look SAR \cite{Le_2013_TGRS_SAR_MSE}, i.e. $d=L=1$, which is considerd a special case. We can state the following:
-\begin{eqnarray}
-  I &\sim& \bar{I} \cdot pdf \left[ e^{-R} \right] \\
-  \log_2{I} &\sim& \log_2{\bar{I}} + pdf \left[ 2^{D-2^D} \right] \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-R} \right]  \\
-  \log_2{I} - \log_2{\bar{I}} = \mathbb{D} &\sim& pdf \left[ 2^De^{-2^D}\ln2 \right]\\
-  \log_2{I_1} - \log_2{I_2} = \mathbb{C} &\sim& pdf \left[ \frac{2^c}{(1+2^c)^2} \ln2 \right] \\
-  avg(\mathbb{D}) &=& -\gamma / \ln{2} \\
-  var(\mathbb{D}) &=& \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{D}) &=& \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray}
-but also the following well-known results are considered for multi-look SAR, i.e. $d=1,L>1$:
-  \begin{eqnarray}
-I &\sim& pdf \left[ \frac{L^L I^{L-1} e^{-LI/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
-N = \ln{I} &\sim& pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(N-\bar{N})-Le^{N-\bar{N}}} \right]
-  \end{eqnarray}
-It will be shown that all of these results are special cases of the result derived previously and rewritten below:
-\begin{eqnarray}
-  |C_v| &\sim& \frac{|\Sigma_v|}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i)  \label{eqn:polsar_det_cov_dist} \\
-  \ln{|C_v|} &\sim& \ln{|\Sigma_v|} + \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_log_det_cov_dist} 
-\end{eqnarray}
-\begin{eqnarray}
-  \frac{|C_v|}{|\Sigma_v|} = \mathbb{R} &\sim& \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \label{eqn:polsar_ratio_det_cov_dist} \\
-  \ln{|C_v|} - \ln{|\Sigma_v|} = \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \label{eqn:polsar_dispersion_log_det_cov_dist} \\ 
-  \ln{|C_{1v}|} - \ln{|C_{2v}|} = \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-\end{eqnarray}
-\begin{eqnarray}
-  avg(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \label{eqn:polsar_dispersion_averages} \\
-  var(\mathbb{D}) &=& \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_variance} \\
-  mse(\mathbb{D}) &=& \left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse}
-\end{eqnarray}
-
-This appendix also derives new results for multi-look SAR data,
-  which can be thought of 
-    either as extensions of the corresponding single-look SAR results
-    or as simple cases of the POLSAR results presented above.
-They are:
-  \begin{eqnarray}
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L} \chi^2(2L) \\
-    \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& \Lambda(2L) - \ln{2L} \\
-    \ln{I_1} - \ln{I_2} = \mathbb{C} &\sim& \Delta(2L) \\
-    avg(\mathbb{D}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{D}) &=& \psi^1(L) \\
-    mse(\mathbb{D}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{eqnarray}
-
-The derivation process detailed below consists of two-phases.
-The first phase collapses the generic multi-dimensional POLSAR results into the classical one-dimensional SAR domain.
-Mathematically this means setting the dimensional number in POLSAR to  $d=1$
-  and collapsing the POLSAR covariance matrix into the variance measure in SAR, which also equals the SAR intensity i.e. $|C_v|=I,|\Sigma_v|=\bar{I}$.
-
-The output of the first phase, in the general case, is applicable to multi-look SAR data, where $d=1$ but $L>1$.
-The second phase simplifies the multi-look results into single-look results, which will match those presented in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
-Mathematically, it means setting $L=1$ in the multi-look result
-  and converting from the natural logarithmic domain used in this paper to the base-2 logarithm used in \cite{Le_2013_TGRS_SAR_MSE} (base-2 was chosen in the previous paper to simplify the computation).
-
-\subsection{Original Domain: SAR Intensity and its ratio}
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_det_cov_dist} and \ref{eqn:polsar_ratio_det_cov_dist}
-we find that:
-\begin{eqnarray*}
-  I &\sim& \frac{\bar{I}}{2L} \chi^2(2L)  \\
-  \frac{I}{\bar{I}} = \mathbb{R} &\sim& \frac{1}{2L}  \chi^2(2L)   
-\end{eqnarray*}
-Or in PDF forms, and applying the variable change theorem,:
-\begin{eqnarray*}
-    \frac{2L I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \right] \\
-  \frac{I}{\bar{I}} &\sim& pdf \left[ \frac{x^{L-1}e^{-x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=2L \cdot t} \\
-%    &\sim& pdf \left[ \frac{(2L)^{L-1} t^{L-1} e^{-Lt}}{2^L \Gamma(L)}  \cdot 2L \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \right] \\
-  I &\sim& pdf \left[ \frac{ L^{L} t^{L-1} e^{-Lt}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x/\bar{I}}  \\
-%    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L-1}\Gamma(L)} \cdot \frac{1}{\bar{I}} \right] \\
-    &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]
-\end{eqnarray*}
-
-Thus we have the following results for multi-look SAR:
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \label{eqn:multi_look_SAR_intensity_dist} \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right] 
-\end{eqnarray}
-
-Now setting $L=1$, these results become:
-\begin{eqnarray}
-    I &\sim& pdf \left[ \frac{ e^{x/\bar{I}}}{ \bar{I}} \right] \\
-    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ e^{-x} \right] 
-\end{eqnarray}
-which is the same as stated in \cite{Le_2013_TGRS_SAR_MSE}, demonstrating that the previous work is a special case of the more generic POLSAR forms.
-
-\subsection{Log-transformed domain: SAR log-intensity and the log-distance}
-
-The result for multi-look SAR data written in the log-transformed domain can be derived from two different approaches.
-The first is to follow a simplification method, where the results for log-transformed POLSAR data are simplified into log-transformed multi-look SAR results.
-
-The second approach is to apply log-transformation to the results derived in the previous section. In this section, it is shown that both approaches would result in identical results.
-
-Setting $d=1$, $|C_v|=I$ and $|\Sigma_v|=\bar{I}$ into Eqns. \ref{eqn:polsar_log_det_cov_dist} and \ref{eqn:polsar_dispersion_log_det_cov_dist}
-we have
-\begin{eqnarray*}
-  \ln{I} &\sim& \ln{\bar{I}} + \Lambda(2L) - \ln{2L}  \\
-  \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& \Lambda(2L) - \ln{2L} 
-\end{eqnarray*}
-
-Or in PDF form, and applying the variable change theorem we have:
-\begin{eqnarray*}
-  \ln{I} - \ln{\bar{I}} + \ln{2L} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \right] \\
-  \ln{I} - \ln{\bar{I}} &\sim& pdf \left[ \frac{e^{Lx-e^x/2}}{2^L \Gamma(L)} \cdot dx/dt \right]_{x=t+\ln{2L}} \\
-%   &\sim& pdf \left[ \frac{e^{L(t+\ln{2L})-e^{t+\ln{2L}}/2}}{2^L \Gamma(L)}  \right] \\ 
-   &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right] \\
-  \ln{I} &\sim&  pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)} \cdot dt/dx \right]_{t=x-\ln{\bar{I}}} \\
- &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] 
-\end{eqnarray*}
-with $\bar{N} = \ln{\bar{I}}$. Thus the first approach arrives at
-\begin{eqnarray}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]  
-\end{eqnarray}
-
-In the second approach, log-transformation is applied on previous results for multi-look SAR intensity and its ratio in the original domain (Eqns.
-\ref{eqn:multi_look_SAR_ratio_dist} and \ref{eqn:multi_look_SAR_intensity_dist}).
-This also arrives at the same results shown above, however the detailed working is omitted for brevity.
-
-%\begin{eqnarray*}
-%    I &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{x}}}{ \bar{I}^{L}\Gamma(L)} \right] \\
-%    \frac{I}{\bar{I}} = \mathbb{R} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] 
-%\end{eqnarray*}
-%Thus
-%\begin{eqnarray*}
-%  \ln{I} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t/\bar{I}}}{ \bar{I}^{L}\Gamma(L)} \cdot e^t \right]_{\bar{I}=e^{\bar{N}}} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{L(t-\bar{N})} e^{-Le^{t-\bar{N}}}}{ \Gamma(L)}  \right] \\
-%  \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \cdot dx/dt \right]_{x=e^t} \\
-%      &\sim& pdf \left[ \frac{ L^{L} e^{t(L-1)} e^{-Le^t}}{ \Gamma(L)} \cdot e^t \right] \\ 
-%      &\sim& pdf \left[ \frac{ L^{L} e^{tL-Le^t} }{ \Gamma(L)}  \right] 
-%\end{eqnarray*}
-%
-%Thus the second approach also arrives at
-%\begin{eqnarray}
-%   \ln{I} = \mathbb{N} &\sim&  pdf \left[ \frac{L^Le^{L(x-\bar{N})-Le^{x-\bar{N}}}}{ \Gamma(L)} \right] \\
-%   \ln{I} - \ln{\bar{I}} = \mathbb{D} &\sim& pdf \left[ \frac{L^Le^{Lx-Le^x}}{ \Gamma(L)}  \right]  
-%\end{eqnarray}
-
-To compute summary statistics for the multi-look SAR dispersion,
-  set $d=1$ into Eqns. \ref{eqn:polsar_dispersion_mse}, \ref{eqn:polsar_dispersion_averages} and \ref{eqn:polsar_dispersion_variance}
-we have:
-  \begin{eqnarray*}
-    avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-    var(\mathbb{L}) &=& \psi^1(L) \\
-    mse(\mathbb{L}) &=& \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-\end{eqnarray*}
-
-This completes the first phase of the derivation process.
-The second phase of simplification involves setting $L=1$ into the above results for multi-look SAR data,
-  and converting natural logarithm into base-2 logarithm.
-First, setting $L=1$ makes the above results become:
-\begin{eqnarray*}
-   \ln{I} = \mathbb{N} &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \right] \\
-   \ln{I} - \ln{\bar{I}} = \mathbb{L} &\sim& pdf \left[ e^{x-e^x}  \right] \\ 
-    avg(\mathbb{L}) &=& \psi^0(1) = -\gamma \\
-    var(\mathbb{L}) &=& \psi^1(1) = \pi^2 / 6 \\  
-    mse(\mathbb{L}) &=& \left[ \psi^0(1) \right]^2 + \psi^1(1) = \gamma^2 + \pi^2 / 6
-\end{eqnarray*}
-with $\gamma$ denoting the Euler-Mascharoni constant.
-Then to convert to base-2 logarithm from natural logarithmic transformation,
-  we again use the variable change theorem.
-  That is:
-  \begin{eqnarray*}
-   \log_2{I}  = \mathbb{N}_2    &\sim&  pdf \left[ e^{(x-\bar{N})-e^{x-\bar{N}}} \cdot dx/dt \right]_{x=t\cdot \ln{2}} \\
-   \mathbb{N} / \ln{2} = \mathbb{N}_2 &\sim&  pdf \left[ e^{(t\cdot \ln{2}-\bar{N})-e^{t\cdot \ln{2}-\bar{N}}} \ln{2} \right]_{\bar{N}_2 = \bar{N} \cdot \ln{2}} \\
-       &\sim&  pdf \left[ 2^{t-\bar{N}_2}e^{2^{t-\bar{N}_2}} \ln{2} \right] 
-  \end{eqnarray*}
-\begin{eqnarray*}
-   \log_2{I} - \log_2{\bar{I}} = \mathbb{L} / \ln{2} = \mathbb{L}_2 &\sim& pdf \left[ e^{x-e^x}  \right]_{x=t \cdot \ln{2}} \\  
-%       &\sim& pdf \left[ e^{t \cdot \ln{2}-e^{t \cdot \ln{2}}} \ln{2}  \right] \\
-       &\sim& pdf \left[ 2^t e^{2^t} \ln{2}  \right] 
-\end{eqnarray*}
-\begin{eqnarray*}
-  avg(\mathbb{L}_2) &=& avg(\mathbb{L})/ \ln{2} = -\gamma / \ln{2} \\
-  var(\mathbb{L}_2) &=& var(\mathbb{L})/ \ln^2{2} = \frac{\pi^2}{6} \frac{1}{ \ln^2{2}} \\
-  mse(\mathbb{L}_2) &=& mse(\mathbb{L})/ \ln^2{2} = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{eqnarray*}
-
-\subsection{Deriving the PDF for SAR dispersion and contrast}
-
-The PDF for SAR dispersion can be easily derived from
-  the PDF for the log-distance given above as:
-  \begin{equation}
-   \ln{I} - avg(\ln{I}) =  \mathbb{D} \sim pdf \left[ \frac{e^{L[x+\psi^0(L)]-Le^{x+\psi^0(L)-\ln{L}}}}{\Gamma(L)} \right]
-  \end{equation}
-due to $d=1$ and
-\begin{eqnarray*}
-  \mathbb{D} &\sim& \mathbb{L} - avg(\mathbb{L}) \\
-  avg(\mathbb{L}) &=& \psi^0(L) - \ln{L} \\
-  \mathbb{L} &\sim& pdf \left[ \frac{L^Le^{Lt-Le^t}}{ \Gamma(L)}  \right]
-\end{eqnarray*}
-
-Setting $L=1$ for Single-Look SAR we have
-\begin{equation}
-  \mathbb{D} \sim pdf \left[ e^{x-\gamma-e^{x-\gamma}} \right]
-\end{equation}
-due to: $\psi^0(1)=-\gamma$ and $\Gamma(1)=1$
-with $\gamma$ being the Euler Mascheroni constant (which equals $0.5772$). 
-In base-2 logarithm domain, invoking the variable change theorem:
-\begin{eqnarray*}
-  \mathbb{D}_2 &=& \log_2{I} - avg(\log_2{I}) = \mathbb{D}/\ln{2} \\
-  \mathbb{D}_2 &\sim& pdf \left[ e^{x-\gamma-e^{x-\gamma}} \cdot \frac{dx}{dt} \right]_{x=t \cdot \ln2}
-\end{eqnarray*}
-Thus we have
-\begin{equation}
-  \mathbb{D}_2 \sim pdf \left[ e^{-(2^xe^{-\gamma})} (2^xe^{-\gamma}) \ln2 \right]
-\end{equation}
-which is consistent with the results found in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
-
-Setting $d=1$ into Eqn. for contrast results in
-\begin{equation}
-  \ln{I_1} - \ln{I_2} = \mathbb{C} \sim \Delta(2L)
-\end{equation}
-The characteristic function would then be
-\begin{equation}
-  CF_\mathbb{C} =  \frac{\Gamma(2L) B(L-it,L+it)}{\Gamma(L)^2} 
-\end{equation}
-Thus the PDF can be written as
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}} \right] \label{eqn:multi_look_SAR_contrast_pdf}
-\end{equation}
-due to
-\begin{eqnarray*}
-  CF_{\mathbb{C}}(x) &=& \frac{\Gamma(2L) }{\Gamma(L)^2} B(1/(1+e^x),L-it,L+it)  \\
-       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \int^{1/(1+e^x)}_0 z^{L-it-1}(1-z)^{L+it-1} dz \\
-  \frac{\partial }{\partial x} CF_{\mathbb{C}}(x) &=&  \frac{\partial CF_{\mathbb{C}}(x) }{\partial 1/(1+e^x)} \cdot \frac{\partial 1/(1+e^x)}{\partial x} \\
-%       &=& \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{1}{(1+e^x)^{L-it-1}} \left( \frac{e^x}{1+e^x} \right)^{L+it-1} \frac{1}{(1+e^x)^2} e^x \\
-        &=&  e^{itx} \frac{\Gamma(2L) }{\Gamma(L)^2} \frac{e^{Lx}}{(1+e^x)^{2L}}   
-\end{eqnarray*}
-
-Setting $L=1$ into Eqn. \ref{eqn:multi_look_SAR_contrast_pdf} 
-we have the PDF for contrast of single-look SAR data:
-\begin{equation}
-  \mathbb{C} \sim pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \right]
-\end{equation}
-
-Converting to base-2 logarithm gives the following:
-\begin{eqnarray*}
-  \mathbb{C} / \ln{2} = \mathbb{C}_2 &\sim& pdf \left[ \frac{e^{x}}{(1+e^x)^{2}} \cdot dx/dt \right]_{x=t \cdot \ln{2}} \\
-%     &\sim& pdf \left[ \ln{2} \frac{e^{t \cdot \ln{2}}}{(1+e^{t \cdot \ln{2}})^{2}}  \right] \\
-     &\sim& pdf \left[ \ln{2} \frac{2^t}{(1+2^t)^{2}}  \right] 
-\end{eqnarray*}
-which is also consistent to the results shown in our previous work \cite{Le_2013_TGRS_SAR_MSE}.
+%What has been done?
+This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.%***IVM: Hai pls check this sentence!
+This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full polarimetric SAR data.
+The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
+At the same time, we have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
+  effectively bringing the existing SAR theories under the umbrella of this new model.
+
+%What are the results? What are their advantages over others' results?
+The main emphasis of this paper is the proposal to consider the POLSAR covariance matrix determinant as a scalar and representative observable for the multi-dimensional POLSAR data.
+Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
+Its representative power is justified for the following reasons.
+Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
+Finally, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
+
+%What are their benefit?
+There are several beneficial implications of the proposed approach presented in this paper.
+Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
+Hence many techniques applicable to SAR can not be directly translated to POLSAR.
+Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
+  its main benefit is that it enables the convenient adaptation of many existing SAR data processing techniques for POLSAR data.
+One example has already been presented in this paper, 
+  where existing SAR discrimination measures are extended towards POLSAR.
+At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
+
+%What are their limitations? What problems this appears to solve, but actually is not?
+Of course, the models proposed in this article also have their own limitations.
+Firstly, they are based on the complex Wishart distribution
+%Thus its applicability is also limited by that of its foundation,
+%  that is the proposed theoretical model 
+  which is only guaranteed to work for homogeneous areas.
+Secondly, while it is desirable for a large number of applications to reduce the multi-dimensional POLSAR data to a scalar value, such a reduction is unlikely to be lossless in the general case.
+
+In this paper, the theoretical model has only been validated for partial ($d=2$) and full ($d=3$) monostatic POLSAR data,
+%and hence What can be done next?
+  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
+Other possible future work includes
+  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
+  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
+    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.
 

### 2013-10-12 paper_dev/article.tex
put the legend of the plot into latex file

@@
 
-\newcommand{\plotWithLegend}[1]{          
+\newcommand{\plotWithLegend}[2]{          
           \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
 	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
-	    \rput(5,1.5){\footnotesize{change-ratio}}
+	    \rput(5,1.5){\footnotesize{#2}}
 	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
@@
   which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
-As the POLSAR covariance matrix determinant generalizes the SAR intensity towards the multidimensional extension,
-  the proposed model is also shown to include the traditional model of SAR intensity under its natural coverage.
+As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
+  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
 %What are the larger implications of the findings presented in this paper?
@@
 As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
-Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to map to the traditional model for SAR intensity in its natural coverage.
-%****IVM: Hai, by "natural coverage" above do you mean non-built-up areas, or are you using this as a figure of speech?
-Note: this sentence needs additional correction to include the word 'confidence'..
-I'll do that once you can confirm the meaning of 'natural coverage'.
+Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to incorporate the traditional SAR intensity as a natural case of the unified model.
 %  as well as reminding us that SAR is a special case of POLSAR.
@@
 	\subfloat[AIRSAR (HH) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_determinant}
@@
 	\subfloat[RADARSAT2 (HH) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_determinant}
@@
 	\subfloat[AIRSAR (HH) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
 		 \label{AIRSAR_1D_det_ratio}
@@
 	\subfloat[RADARSAT2 (HH) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
+          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_det_ratio}
@@
 	\subfloat[AIRSAR (HH) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
 %		 \epsfxsize=1.5in
@@
 
-\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}
+\plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
 %		 \epsfxsize=1.5in
@@
 	\subfloat[AIRSAR (HH-HV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_2d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_determinant}
@@
 	\subfloat[RADARSAT2 (HH-HV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_determinant}
@@
 	\subfloat[AIRSAR (HH-HV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
+          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_2d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 	\subfloat[AIRSAR (HH-HV) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
 %		 \epsfxsize=1.5in
@@
 	\subfloat[RADARSAT2 (HH-HV) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}
+          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}{change-ratio}
 %\newsavebox\IBoxCRTwoR
@@
 	\subfloat[AIRSAR (HH-HV-VV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_3D_determinant}
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_3D_determinant}
@@
 	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
+          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
 		 \label{RADARSAT2_2D_det_ratio}
@@
 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
 %		 \epsfxsize=1.5in
@@
 	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}
+          \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
 %          \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final

### 2013-10-12 paper_dev/article_pp_ivm.tex
put the legend of the plot into latex file

@@
 This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
-%
-%***IVM: the following sentence doesn't make sense, also, I don't think it's good to talk about 'models of a model'.  Maybe 'model variants' instead?
-%%%***IVM***The specific two and three dimensional models of these models, which %also include the derived discrimination measures, are originally designed against both partial and full polarimetric SAR data.
 

### 2013-10-14 paper_dev/article.tex
updated article file from Ian

@@
 \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
-Again, although the histogram is much tighter, the match is visually obvious in all cases, apart from Fig.
-Fig.
-\ref{fig:verify_det_ratio_model_3D}e plotting the AIRSAR (HH-HV-VV) change ratio.
-This match is poorer becasue....
-%***IVM**** Hai, you had better find a good reason to explain this!!!
+Again, although the histogram is much tighter, the match is visually obvious in all cases.
 \begin{figure}[h]
@@
 	\subfloat[AIRSAR (HH-HV) change ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+%          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}

### 2013-10-14 paper_dev/article_pp.tex
updated article file from Ian

@@
 \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
-Again, although the histogram is much tighter, the match is visually obvious in all cases, apart from Fig.
-Fig.
-\ref{fig:verify_det_ratio_model_3D}e plotting the AIRSAR (HH-HV-VV) change ratio.
-This match is poorer becasue....
-%***IVM**** Hai, you had better find a good reason to explain this!!!
+Again, although the histogram is much tighter, the match is visually obvious in all cases.
 %ifdef FINAL

### 2013-10-22 paper_dev/article.tex
changed the figures to allow better view of the axis number

@@
 	    \rput(5,1.5){\footnotesize{#2}}
-	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
+	    \rput{90}(1.5,5){\footnotesize{pdf / histogram}}
 	    \psline[linecolor=plot](5,8)(6,8)
@@
 	\subfloat[AIRSAR (HH) determinant ratio]{
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
+          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
 %		 \epsfxsize=1.5in
@@
 	\subfloat[AIRSAR (HH-HV) change ratio]{
-%          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
-		 \epsfxsize=1.5in
-		 \epsfysize=1.5in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
 		 \label{AIRSAR_2D_det_ratio}

### 2013-10-29 paper_dev/article.tex
remove x-axis, y-axis label

@@
 	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
-	    \rput(5,1.5){\footnotesize{#2}}
-	    \rput{90}(1.5,5){\footnotesize{pdf / histogram}}
+	    %\rput(5,1.5){\footnotesize{#2}}
+	    %\rput{90}(1.5,5){\footnotesize{pdf / histogram}}
 	    \psline[linecolor=plot](5,8)(6,8)
@@
 \end{tabular}
-\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR dataset homogeneous patches}
+\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
 \label{fig:verify_POLSAR_model_1D}
@@
 \end{tabular}
-\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets}
+\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
 \label{fig:verify_det_ratio_model_2D}
@@
 \end{tabular}
-\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
+\caption{The specific $d=3$ models are validated on both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
 \label{fig:verify_det_ratio_model_3D}

### 2013-10-29 paper_dev/article_pp.tex
changed the figures to allow better view of the axis number
remove x-axis, y-axis label

@@
 	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
-	    \rput(5,1.5){\footnotesize{#2}}
-	    \rput{90}(1.5,5){\footnotesize{pdf/histogram}}
+	    %\rput(5,1.5){\footnotesize{#2}}
+	    %\rput{90}(1.5,5){\footnotesize{pdf / histogram}}
 	    \psline[linecolor=plot](5,8)(6,8)

### 2013-11-03 paper_dev/article.tex
changed plot captions font size and new line

@@
 	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
-	    \rput(8,8){\footnotesize{model}}
-	    \rput(8,9){\footnotesize{data}}            
+	    \rput(8,8){\scriptsize{model}}
+	    \rput(8,9){\scriptsize{data}}            
           \end{pspicture}
@@
 \usepackage[center]{caption}%for captions
-\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+\usepackage[caption=false,font=scriptsize]{subfig} %for subfigures
 
@@
 \begin{figure}[h]
+%\captionsetup{justification=centering}
 \centering
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH) determinant]{
+	\subfloat[][AIRSAR (HH) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH) determinant]{
+	\subfloat[][RADARSAT2 (HH) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
@@
 	} \\
-	\subfloat[AIRSAR (HH) determinant ratio]{
+	\subfloat[][AIRSAR (HH) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH) determinant ratio]{
+	\subfloat[][RADARSAT2 (HH) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[AIRSAR (HH) change ratio]{
+	\subfloat[][AIRSAR (HH) \\ change ratio]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH) change ratio]{
+	\subfloat[][RADARSAT2 (HH) \\ change ratio]{
 
@@
 \end{tabular}
-\caption{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
+\caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
 \label{fig:verify_POLSAR_model_1D}
@@
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH-HV) determinant]{
+	\subfloat[][AIRSAR (HH-HV) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_2d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
@@
 	} \\
-	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+	\subfloat[][AIRSAR (HH-HV) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_2d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[AIRSAR (HH-HV) change ratio]{
+	\subfloat[][AIRSAR (HH-HV) \\ change ratio]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ change ratio]{
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}{change-ratio}
@@
 \end{tabular}
-\caption{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
+\caption{\scriptsize{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
 \label{fig:verify_det_ratio_model_2D}
@@
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
@@
 	} \\
-	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ change ratio]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ change ratio]{
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
@@
 \end{tabular}
-\caption{The specific $d=3$ models are validated on both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}
+\caption{\scriptsize{The specific $d=3$ models are validated on both RADARSAT2 and AIRSAR datasets.
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
 \label{fig:verify_det_ratio_model_3D}

### 2013-11-05 paper_dev/Remote_Sensing_Letter/tRSLguide.tex
adding Remote Sensing Letter format

% tRSLguide.tex
% v3.7 released February 2013

\documentclass[]{tRSL2e}

\begin{document}

\jvol{00} \jnum{00} \jyear{2013} \jmonth{February}

\articletype{GUIDE}

\title{{\em{Remote Sensing Letters}} \break \LaTeX\ style guide
for authors (`Own Style')}

\author{A. N. AUTHOR$^{\ast}$$\dag$\thanks{$^\ast$Corresponding
author. Email: latex.helpdesk@tandf.co.uk \vspace{6pt}} and I. T.
CONSULTANT${\ddag}$\\
\vspace{6pt} $\dag$Taylor \& Francis, 4 Park Square, Milton Park,
Abingdon, OX14 4RN, UK\\
$\ddag$ Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t,
D-79110 Freiburg, Germany\\
\vspace{6pt}\received{v3.7 released February 2013} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the Taylor \& Francis journal {\em Remote Sensing Letters} ({\it tRSL}\,) using the \LaTeX\ document preparation system and the class file {\tt
tRSL2e.cls}, which is available via the journal's homepage on the Taylor \& Francis website. Authors planning to submit their papers in \LaTeX\ are advised to use {\tt tRSL2e.cls} as
early as possible in the creation of their files.

\vspace{12pt}\centerline{\bfseries Index to information contained in this guide}\vspace{12pt}

\hbox to \textwidth{\hsize\textwidth\vbox{\hsize18pc
\hspace*{-12pt} {1.}    Introduction\\
\hspace*{7pt} {1.1.}  The {\it tRSL} document class\\
\hspace*{7pt} {1.2.}  Submission of \LaTeX\ articles\\
\hspace*{24pt}        to the journal\\
{2.}    Using the {\it tRSL} class file\\
{3.}    Additional features\\
\hspace*{10pt}{3.1.}  Footnotes to article titles\\
\hspace*{24pt}        and authors' names\\
\hspace*{10pt}{3.2.}  Abstracts\\
\hspace*{10pt}{3.3.}  Lists\\
\hspace*{10pt}{3.4.}  Landscape pages\\
{4.}    Some guidelines for using\\
\hspace*{6pt}        standard features\\
\hspace*{10pt}{4.1.}   Sections\\
\hspace*{10pt}{4.2.}   Illustrations (figures)\\
\hspace*{10pt}{4.3.}   Tables\\
\hspace*{10pt}{4.4.}   Theroem-like environments\\
\noindent \hspace*{7pt} {4.5.}   Typesetting mathematics\\
\hspace*{24pt} {4.5.1.}   Displayed mathematics\\
\hspace*{24pt} {4.5.2.}  Bold math italic symbols\\
\hspace*{24pt} {4.5.3.}   Bold Greek\\
\hspace*{24pt} {4.5.4.}   Upright Greek characters  \\
\hspace*{48pt}            and the upright partial \\
\hspace*{48pt}            derivative sign  \\}
\hspace{-24pt}\vbox{\noindent\hsize18pc
\hspace*{7pt} {4.6.}   Acknowledgements \\
\hspace*{7pt} {4.7.}   Notes \\
\hspace*{7pt} {4.8.}   References \\
\hspace*{24pt} {4.8.1.}   References cited in the\\
\hspace*{48pt}                 text  \\
\hspace*{24pt} {4.8.2.}   The list of references\\
\hspace*{7pt} {4.9.}   Appendices \\
\hspace*{7pt} {4.10.}   {\it tRSL} macros  \\
{5.}    Example of a section heading \\*
\hspace*{7pt}   including {\fontencoding{T1}\scshape{small caps}}, {\it italic}, \\*
\hspace*{7pt}   and bold Greek such as ${\bm\kappa}$ \\
{6.}   {\em tRSL} journal style \\
\hspace*{10pt}{6.1.}   Hyphens, n-rules, m-rules and\\ \hspace*{27pt}minus signs\\
\hspace*{10pt}{6.2.}   References \\
\hspace*{10pt}{6.3.}   Maths fonts\\
\noindent   {7.}   Troubleshooting\\
{8.}   Fixes for coding problems\\
{9.}   Obtaining the tRSL2e class file\\
\hspace*{10pt}{9.1}  Via the Taylor \& Francis \\
\hspace*{24pt}                 website\\
\hspace*{10pt}{9.2}   Via e-mail\\
      }}
\end{abstract}

\section{Introduction}

In order to assist authors in the process of preparing a manuscript for {\itshape Remote Sensing Letters} ({\it tRSL}), the journal's layout style has been implemented as a \LaTeXe\ class file based on the {\tt article} document class. A \textsc{Bib}\TeX\ style file is also provided to assist with the formatting of your references in a style appropriate to that of the journal.

Commands that differ from or are provided in addition to the standard \LaTeXe\ interface are explained in this guide. The guide alone is not intended as a substitute for an appropriate \LaTeXe\ manual.

The \texttt{tRSLguide.tex} file can also be used as a template for composing an article for submission by cutting, pasting, inserting and
deleting text as appropriate, using the \LaTeX\ environments provided (e.g. \verb"\begin{equation}",
\verb"\begin{enumerate}").

{\bf{Please note that the index following the abstract in this guide is provided for information only. An index is not required in submitted papers.}}

\subsection{The {\bi tRSL} document class}

The \textit{tRSL} class file preserves the standard \LaTeXe\ interface such that any document that can
be produced using {\tt article.cls} can also be produced using the {\it tRSL} document class.
However, the measure (the width of the text on a page) is narrower than the default for {\tt article.cls}, therefore line breaks
will change and some long equations may need to be reformatted accordingly.

If your article is accepted for publication in the journal, it will be typeset in Monotype Times. As most authors do not own this font, it is likely that the page make-up will alter with the change of font. For this reason, please ignore details such as slightly long lines of text, page stretching, or figures falling out of synchronization with their citations in the text: these details will be dealt with by the typesetter. Similarly, it is unnecessary to spend time addressing warnings in the log file -- if your .tex file compiles to produce a PDF file that correctly reflects how you wish your paper to appear when printed, such warnings will not prevent your source files being imported into the typesetter's program.

\subsection{Submission of \LaTeX\ articles to the journal}\label{S1.2}

Manuscripts for possible publication in the journal should be submitted to the Editors for review as directed in the journal's Instructions for Authors, which may be found at {\tt{http://www.tandf.co.uk/journals/authors/trslauth.asp}}.

Manuscripts created using \LaTeX\ should be converted to PDF format prior to submission. The \LaTeX\ source files and any graphics files will be required in addition to the final PDF version when final, revised versions of accepted manuscripts are submitted.

`Open-source' \LaTeXe\ should be used in preference to proprietary systems such as TCILaTeX or Scientific WorkPlace; similarly, class files such as REVTeX4 that produce a document in the style of a different publisher and journal should not be used for preference.

Authors who wish to incorporate Encapsulated PostScript artwork directly in their articles can do so by using
Tomas Rokicki's {\tt EPSF} macros (which are supplied with the DVIPS PostScript driver). See Section~\ref{eps},
which also demonstrates how to treat landscape pages. Please remember to supply any additional figure macros you
use with your article in the preamble before \verb"begin{document}". Authors should not attempt to use
implementation-specific \verb"\special"s directly.

Ensure that any author-defined macros are gathered together in the source file, just before the
\verb"\begin{document}" command.

Please note that, if serious problems are encountered with the coding of a paper (missing author-defined macros,
for example), it may prove necessary to divert the paper to conventional typesetting, i.e. it will be re-keyed.

\section{Using the {\bi tRSL} class file}

If the file {\tt tRSL2e.cls} is not already in the appropriate system directory for \LaTeXe\ files, either
arrange for it to be put there, or copy it to your working folder. In order to use the {\it tRSL} document class, replace
the command \verb"\documentclass{article}" at the beginning of your document with the command \verb"\documentclass{tRSL2e}".

The following document-class options should {\em not\/} be used with the {\it tRSL} class file:
%
\begin{itemize}
   \item {\tt 10pt}, {\tt 11pt}, {\tt 12pt} -- unavailable;
   \item {\tt oneside}, {\tt twoside} -- not necessary, oneside is the default;
   \item {\tt leqno} and {\tt titlepage} -- should not be used;
   \item {\tt onecolumn} -- not necessary as it is the default style.
\end{itemize}
%
The {\tt geometry} package and commands associated with it should also not be used to adjust the page dimensions.

\section{Additional features}

\subsection{Footnotes to article titles and authors' names}

The \verb"\thanks" control sequence may be used to produce a footnote to either the title or authors' names.
Footnote symbols for this purpose should be used in the order: $\dagger$ (coded as \verb"\dagger"), $\ddagger$ (\verb"\ddagger"), $\S$ (\verb"\S"), $\P$ (\verb"\P"), $\|$ (\verb"\|"),\break
$\dagger\dagger$ (\verb"\dagger\dagger"), $\ddagger\ddagger$ (\verb"\ddagger\ddagger"), $\S\S$ (\verb"\S\S"), $\P\P$ (\verb"\P\P"), $\|\|$ (\verb"\|\|").

Footnotes to the main text will automatically be assigned the superscript
 symbols 1, 2, 3,... by the class file, beginning afresh on each
page.\footnote{These symbols will be changed to the style of the journal by the
 typesetter during preparation of your proofs. If preferred, the \texttt{endnotes} package
 may be used instead to set the notes in consecutive order at the end
 of your text, before the bibliography.}

The title, author(s) and affiliation(s) should be followed by the {\verb"\maketitle"} command. If preparing an anonymized version for peer review, {\verb"\maketitle"} may follow directly after the title in order to shield the authors' identities from the reviewers.

\subsection{Abstracts}

At the beginning of your article, the title should be generated in the usual way using the {\verb"\maketitle"}
command. Immediately following the title you should include an abstract. The abstract should be enclosed within
an {\tt abstract} environment. For example, the titles for this guide were produced by the following source code:
%
\begin{verbatim}
\title{{\itshape Remote Sensing Letters}\break
\LaTeX\ style guide for authors (`Own Style')}

\author{A. N. AUTHOR$^{\ast}$$\dag$\thanks{$^\ast$Corresponding
author. Email: latex.helpdesk@tandf.co.uk \vspace{6pt}} and I. T.
CONSULTANT${\ddag}$\\
\vspace{6pt} $\dag$Taylor \& Francis, 4 Park Square, Milton Park,
Abingdon, OX14 4RN, UK\\
$\ddag$ Institut f\"{u}r Informatik, Albert-Ludwigs-Universit\"{a}t,
D-79110 Freiburg, Germany\\
\vspace{6pt}\received{v3.7 released February 2013} }

\maketitle

\begin{abstract}
This guide is for authors who are preparing papers for the Taylor
\& Francis journal {\em Remote Sensing Letters} ({\it tRSL}\,)
using the \LaTeX\ document preparation system and the class file
{\tt tRSL2e.cls}, which is available via the journal's homepage on
the Taylor \& Francis website. Authors planning to submit papers in
\LaTeX\ are advised to use {\tt tRSL2e.cls} as early as possible in
the creation of their files.
\end{abstract}
\end{verbatim}

\subsection{Lists}

The {\it tRSL} style provides numbered and unnumbered lists using the {\tt enumerate} environment and bulleted
lists  using the {\tt itemize} environment.

The enumerated list numbers each list item with roman numerals by default, for example:
%
\begin{enumerate}
   \item first item
   \item second item
   \item third item
\end{enumerate}
%
Alternative numbering styles can be achieved by inserting an optional argument in square brackets after the
\verb"\item". For example, the list
%
\begin{enumerate}
   \item[(1)] first item
   \item[(2)] second item
   \item[(3)] etc. \ldots
\end{enumerate}
%
was produced by:
%
\begin{verbatim}
\begin{enumerate}
   \item[(1)] first item
   \item[(2)] second item
   \item[(3)] etc. \ldots
\end{enumerate}
\end{verbatim}
%
Unnumbered lists are also provided using the {\tt enumerate} environment. For example,
\begin{enumerate}
   \item[] First unnumbered item which has no label and is indented from
         the left margin.
   \item[] Second unnumbered item.
   \item[] Third unnumbered item.
\end{enumerate}
was produced by:
%
\begin{verbatim}
\begin{enumerate}
  \item[] First unnumbered item...
  \item[] Second unnumbered item.
  \item[] Third unnumbered item.
\end{enumerate}
\end{verbatim}
%
Bulleted lists are provided using the {\tt itemize} environment. For example,
\begin{itemize}
\item First bulleted item
\item Second bulleted item
\item Third bulleted item
\end{itemize}
was produced by:
\begin{verbatim}
  \begin{itemize}
  \item First bulleted item
  \item Second bulleted item
  \item Third bulleted item
  \end{itemize}
\end{verbatim}

\subsection{Landscape pages}\label{eps}

If a table or illustration is too wide to fit the standard measure, it must be turned, with its caption, through
90$^{\circ}$ anticlockwise. Landscape illustrations and/or tables can be produced directly using the tRSL2e class
file using \verb"\usepackage{rotating}" after \verb"\documentclass{tRSL2e}". The following commands can be used
to produce such pages.
%
\begin{verbatim}
\setcounter{figure}{2}
\begin{sidewaysfigure}
\centerline{\epsfbox{fig1.eps}}
\caption{This is an example of a figure caption.}
\label{landfig}
\end{sidewaysfigure}
\end{verbatim}
%
\begin{verbatim}
\setcounter{table}{0}
\begin{sidewaystable}
  \tbl{The Largest Optical Telescopes.}
    \begin{tabular}{@{}llllcll}
    .
    .
    .
  \end{tabular}\label{tab1}
\end{sidewaystable}
\end{verbatim}
%
Before any float environment, use the \verb"\setcounter" command
as above to fix the numbering of the caption. Subsequent captions
will then be automatically renumbered accordingly.

\section[]{Some guidelines for using standard features}

The following notes may help you achieve the best effects with the tRSL2e Class file.

\subsection{Sections}

\LaTeXe\ provides five levels of section headings and they are all defined in the tRSL2e Class file:
\begin{enumerate}
   \item \verb"\section"
   \item \verb"\subsection"
   \item \verb"\subsubsection"
   \item \verb"\paragraph"
   \item \verb"\subparagraph"
\end{enumerate}
Numbering is automatically generated for section, subsection, subsubsection and paragraph headings.  If you need
additional text styles in the headings, see the examples in Section~5.

\subsection{Illustrations (figures)}

The {\it tRSL} class file will cope with most positioning of your illustrations and you should not normally use the optional positional qualifiers of the {\tt figure} environment, which would override these decisions. See `Instructions for Authors' in the journal's homepage on the Taylor \& Francis website for how to submit artwork (please note that requests to supply figures separately from text are addressed to authors using Microsoft Word; authors using \LaTeX\ may include illustrations at the appropriate locations in their PDF file). The original source files of any illustrations will be required when the final, revised version is submitted. Authors should ensure that their figures are suitable (in terms of lettering size, etc.) for the reductions they intend.

Figure captions should be below the figure itself, therefore the \verb"\caption" command should appear after the
figure. For example, figure~\ref{sample-figure} with caption and sub-captions is produced using the following
commands:
%
\begin{verbatim}
\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{\label{fig2} Example of a two-part figure with individual
sub-captions showing that captions are flush left and justified if
greater than one line of text, otherwise centred under the figure.}
\label{sample-figure}
\end{center}
\end{figure}
\end{verbatim}

\begin{figure}
\begin{center}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr1.eps}}}\hspace{5pt}
\subfigure[An example of an individual figure sub-caption.]{
\resizebox*{5cm}{!}{\includegraphics{senu_gr2.eps}}}
\caption{\label{fig2} Example of a two-part figure with individual
sub-captions showing that captions are flush left and justified if
greater than one line of text, otherwise centred under the figure.}
\label{sample-figure}
\end{center}
\end{figure}

To ensure that figures are correctly numbered automatically, the \verb"\label{}" command should be inserted just
after \verb"\caption{}".

\subsection{Tables}

The {\it tRSL} class file will cope with most positioning of your tables and you should not normally use the optional
positional qualifiers of the {\tt table} environment, which would override these decisions. The table caption
appears above the body of the table in {\it tRSL} style, therefore the \verb"\tbl" command should appear before
the body of the table.

The {\tt tabular} environment can be used as illustrated here to produce tables with single thick and thin horizontal rules, which
are allowed, if desired. Thick rules should be used at the head and foot only and thin rules elsewhere.

Commands to redefine quantities such as \verb"\arraystretch" should be omitted. For example, table~\ref{symbols}
is produced using the following commands. Note that \verb"\rm" will produce a roman character in math mode. There
are also \verb"\bf" and \verb"\it", which produce bold face and text italic in math mode.

\begin{table}
  \tbl{Radio-band beaming model parameters for\\ {FSRQs and BL Lacs.}}
{\begin{tabular}[l]{@{}lcccccc}
\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs &5 & 36 & 7 & $-4.0$
         & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$
         & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a long footnote is added.}
\label{symbols}
\end{table}

\begin{verbatim}
\begin{table}
  \tbl{Radio-band beaming model parameters for {FSRQs and BL Lacs.}}
{\begin{tabular}{@{}lcccccc}
\toprule
  Class$^{\rm a}$ & $\gamma _1$ & $\gamma _2$$^{\rm b}$
         & $\langle \gamma \rangle$
         & $G$ & $|{\bm f}|$ & $\theta _{c}$ \\
\colrule
  BL Lacs &5 & 36 & 7 & $-4.0$
         & $1.0\times 10^{-2}$ & 10$^\circ$ \\
  FSRQs & 5 & 40 & 11 & $-2.3$
         & $0.5\times 10^{-2}$ & 14$^\circ$ \\
\botrule
\end{tabular}}
\tabnote{$^{\rm a}$This footnote shows what footnote symbols to use.}
\tabnote{$^{\rm b}$This footnote shows the text turning over when a
 long footnote is added.}
\label{symbols}
\end{table}
\end{verbatim}

To ensure that tables are correctly numbered automatically, the \verb"\label{}" command should be inserted just before
\verb"\end{table}".

Tables produced using the {\tt booktabs} package of macros for typesetting tables are also compatible with the {\it tRSL} class file.

\subsection{Theorem-like environments}

A predefined \verb"proof" environment is provided by the \verb"amsthm" package (which is called by the class file), as follows:

\begin{proof}
More recent algorithms for solving the semidefinite programming relaxation
are particularly efficient, because they explore the structure of the
MAX-CUT problem.
\end{proof}
\noindent This was produced by simply typing:
%
\begin{verbatim}
\begin{proof}
More recent algorithms for solving the semidefinite programming
relaxation are particularly efficient, because they explore the
structure of the MAX-CUT problem.
\end{proof}
\end{verbatim}
%
Other theorem-like environments (theorem, lemma, corollary, etc.) in your document need to be defined as required, e.g. using \verb"\newtheorem{theorem}{Theorem}" in the preamble of your .tex file before \verb"begin{document}". The format of the text in these environments will be changed if necessary to match the style of the journal by the typesetter during preparation of your proofs.

\subsection{Typesetting mathematics}\label{TMth}

\subsubsection{Displayed mathematics}

The {\it tRSL} class file will set displayed mathematics centred on the measure without equation numbers, provided
that you use the \LaTeXe\ standard control sequences open (\verb"\[") and close (\verb"\]") square brackets as
delimiters. The equation
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\]
\normalfont was typeset using the commands
%
\begin{verbatim}
\[
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\].
\end{verbatim}

For those of your equations that you wish to be automatically
numbered sequentially throughout the text, use the {\tt{equation}}
environment, e.g.

\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})\qquad
  i\in {\mathbb R}
\end{equation}
%
was typeset using the commands

\begin{verbatim}
\begin{equation}
  \sum_{i=1}^p \lambda_i = {\rm trace}({\textrm{\bf S}})quad
  i\in {\mathbb R}
\end{equation}
\end{verbatim}

Part numbers for sets of equations may be generated using the
{\tt{subequations}} environment, e.g.
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
which was generated using the control sequences

\begin{verbatim}
\begin{subequations} \label{subeqnexample}
\begin{equation}
        \varepsilon \rho w_{tt}(s,t)
        =
        N[w_{s}(s,t),w_{st}(s,t)]_{s},
        \label{subeqnpart}
\end{equation}
\begin{equation}
        w_{tt}(1,t)+N[w_{s}(1,t),w_{st}(1,t)] = 0,
\end{equation}
\end{subequations}
\end{verbatim}
This is made possible by the package {\tt{subeqn}}, which is called
by the class file. If you put the \verb"\label{}" just after the
\verb"\begin{subequations}" line, references will be to the
collection of equations, `(\ref{subeqnexample})' in the example
above. Or, like the example code above, you can reference each
equation individually -- e.g. `(\ref{subeqnpart})'.

\subsubsection{Bold math italic symbols}

To get bold math italic you can use \verb"\bm", which works for
all sizes, e.g.
%
\begin{verbatim}
\sffamily
\begin{equation}
   {\rm d}({\bm s_{t_{\bm u}}) = \langle{\bm\alpha({\sf{\textbf L}})}
   [RM({\bm X}_y + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}
\normalfont
\end{verbatim}
%
produces\sffamily
\begin{equation}
   {\rm d}({\bm s_{t_{\bm u}}}) = \langle {\bm\alpha({\sf{\textbf L}})}[RM({\bm X}_y
   + {\bm s}_t) - RM({\bm x}_y)]^2 \rangle
\end{equation}\normalfont
Note that subscript, superscript, subscript to subscript, etc.
sizes will take care of themselves and are italic, not bold,
unless coded individually. \verb"\bm" produces the same effect as
\verb"\boldmath". \verb"\sffamily"...\verb"\normalfont" allows
upright sans serif fonts to be created in math mode by using the
control sequence `\verb"\sf"'.

\subsubsection{Bold Greek}\label{boldgreek}

Bold lowercase as well as uppercase Greek characters can be obtained by \verb"{\bm \gamma}", which gives ${\bm
\gamma}$, and \verb"{\bm \Gamma}", which gives ${\bm \Gamma}$.

\subsubsection{Upright lowercase Greek characters and the upright partial derivative sign}\label{upgreek}

Upright lowercase Greek characters can be obtained with the Class file by inserting the letter `u' in the
control code for the character, e.g. \verb"\umu" and \verb"\upi" produce $\umu$ (used, for example, in the
symbol for the unit microns -- $\umu{\rm m}$) and $\upi$ (the ratio of the circumference to the diameter of a
circle). Similarly, the control code for the upright partial derivative $\upartial$ is \verb"\upartial".

\subsection{Acknowledgements}

This unnumbered section, e.g. \verb"\section*{Acknowledgement(s)}", should be used for thanks, grant details, etc.
and placed before any Notes or References sections.

\subsection{Notes}

This unnumbered section, e.g. \verb"\section*{Note(s)}", may be placed before any References section.

\subsection{References}\label{refs}

\subsubsection{References cited in the text} References should be cited in the text in
author--date (Harvard) style -- e.g. `(Smith 1985, Jones 1986, Trevor {\itshape{et al.}} 1987, Bloggs
{\itshape{et al.}} 2001)' or `... see Smith (1985) ...' (note that these references have been cited in
chronological order and `{\itshape{et al.}}' has been used for two or more authors)'. References should be
listed in the references list at the end of the main text in alphabetical order, then chronologically, with no
issue numbers and full page ranges where appropriate. A smaller font than in the main body text should be used,
with a hanging indent. Each bibliographical entry has a key, which is assigned by the author and used to refer
to that entry in the text. In this document, the key \verb"ed84" in the citation form \verb"\citep{ed84}"
produces `\citep{ed84}', and the keys \verb"ed84", \verb"aiex02", \verb"glov00" and \verb"mtw73" in the citation
form \verb"\citep{ed84,aiex02,glov00,mtw73}" produce `\citep{ed84,aiex02,glov00,mtw73}'. The appropriate
citation style in the text for different situations can be produced by \verb"\citet{aiex00}" for
`\citet{aiex00}', \verb"\citealt{lam86}" for `\citealt{lam86}' and \verb"\citet{aiex00,aiex02,hk96,fzf88}" for
`\citet{aiex00,aiex02,hk96,fzf88}'. Optional notes may be included at the beginning and end of a citation by the
use of square brackets, e.g. \verb"\citep[see][and" \verb"references" \verb"therein]{aiex02}" produces
`\citep[see][and references therein]{aiex02}'. Citation of the year alone may be produced by
\verb"\citeyear{neu83}", i.e. `\citeyear{neu83}', or \verb"\citeyearpar{neu83}", i.e. `\citeyearpar{neu83}'.

\subsubsection{The list of references}

The following list shows some references prepared in the style of the journal:
%
\begin{thebibliography}{9}

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et~al.}}}{2000}]{aiex00}
\textsc{Aiex, R.M., Resende, M.G.C., Pardalos, P.M. {\normalfont and} Toraldo,
  G.}, 2000, GRASP with path-relinking for the three-index assignment problem.
  Technical report, AT\&T Labs-Research.

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et al.}}}{2002}]{aiex02}
A{\sc iex}, R.M., R{\sc esende},  M.G.C. and R{\sc ibeiro}, C.C.,
2002, Probability distribution of solution time in GRASP: an
experimental investigation. Available online at:
www.graspintime.com (accessed 23 October 2003).

\bibitem[\protect\citeauthoryear{Edwards {\itshape{et~al.}}}{1984}]{ed84}
\textsc{Edwards, D.M.F., Madden, P.A. {\normalfont and} McDonald, I.R.}, 1984,
Nanotechnology in fibrous materials -- a new perspective. {\itshape Textile Progress}, \textbf{51}, pp. 1141--1151.

\bibitem[\protect\citeauthoryear{French}{1988}]{fzf88}
\textsc{French, F.}, 1988, English title of a chapter in the translation of a
  book in a foreign language. In     {\itshape Title of a Book in Another Language
  (Quoted in that Language)}, {P.} Smith (Transl.)   (New York: Dover)
  (original work published 1923).

\bibitem[\protect\citeauthoryear{Glover}{2000}]{glov00}
\textsc{Glover, F.}, 2000, Multi-start and strategic oscillation
  methods -- principles to exploit adaptive memory. In {\itshape Computing Tools
  for Modeling, Optimization and Simulation: Interfaces in Computer Science and
  Operations Research} (2nd  edn), M.~Laguna {\normalfont and} J.L.
  Gonz\'{a}les-Velarde (Eds), pp. 1--24  (Boston, MA: Kluwer Academic).

\bibitem[\protect\citeauthoryear{Kern}{1997}]{hk96}
\textsc{Kern, H.}, 1997, The resurgent Japanese economy and a Japan--United
  States free trade agreement. In {\itshape Proceedings of the }{\itshape 4th
  International Conference on the Restructuring of the Economic and Political
  System in Japan and Europe}, 21--25 May 1996, Milan, Italy (Singapore: World
  Scientific), pp. 147--156.

\bibitem[\protect\citeauthoryear{Lamport}{1996}]{lam86}
L{\sc amport}, L., 1986, Efficient algorithms for layer assignment
problems. PhD thesis, University of Princeton, NJ.

\bibitem[\protect\citeauthoryear{Misner}{1973}]{mtw73}
\textsc{Misner, C.W.} (Ed.), 1973, Efficient algorithms for layer assignment
  problems. In {\itshape Gravitation} (2nd  edn), Einstein's Legacy Vol. 5, pp. 231--256
  (San Francisco, CA: Freeman).

\bibitem[\protect\citeauthoryear{Neumann}{1983}]{neu83}
\textsc{Neumann, M.}, 1983, Parallel GRASP with path-relinking for job
  shop scheduling. {\itshape International Journal of Geographical Information
  Science}, \textbf{50}, pp. 841--843.

\end{thebibliography}
\bigskip
\noindent This was produced by typing:
\medskip
\begin{verbatim}
\bibitem[\protect\citeauthoryear{Aiex {\itshape{et~al.}}}{2000}]{aiex00}
\textsc{Aiex, R.M., Resende, M.G.C., Pardalos, P.M. {\normalfont and}
 Toraldo, G.}, 2000, GRASP with path-relinking for the three-index
 assignment problem. Technical report, AT\&T Labs-Research.

\bibitem[\protect\citeauthoryear{Aiex {\itshape{et al.}}}{2002}]{aiex02}
A{\sc iex}, R.M., R{\sc esende},  M.G.C. and R{\sc ibeiro}, C.C.,
 2002, Probability distribution of solution time in GRASP: an
 experimental investigation. Available online at:
 www.graspintime.com (accessed 23 October 2003).

\bibitem[\protect\citeauthoryear{Edwards {\itshape{et~al.}}}{1984}]{ed84}
\textsc{Edwards, D.M.F., Madden, P.A. {\normalfont and} McDonald, I.R.},
 1984, Nanotechnology in fibrous materials -- a new perspective.
 {\itshape Textile Progress}, \textbf{51}, pp. 1141--1151.

\bibitem[\protect\citeauthoryear{French}{1988}]{fzf88}
\textsc{French, F.}, 1988, English title of a chapter in the translation
 of a book in a foreign language. In {\itshape Title of a Book in
 Another Language (Quoted in that Language)}, {P.} Smith (Transl.)
 (New York: Dover) (original work published 1923).

\bibitem[\protect\citeauthoryear{Glover}{2000}]{glov00}
\textsc{Glover, F.}, 2000, Multi-start and strategic oscillation
 methods -- principles to exploit adaptive memory. In {\itshape
 Computing Tools for Modeling, Optimization and Simulation: Interfaces
 in Computer Science and Operations Research} (2nd  edn), M.~Laguna
 {\normalfont and} J.L. Gonz\'{a}les-Velarde (Eds), pp. 1--24 (Boston,
 MA: Kluwer Academic).

\bibitem[\protect\citeauthoryear{Kern}{1997}]{hk96}
\textsc{Kern, H.}, 1997, The resurgent Japanese economy and a
 Japan--United States free trade agreement. In {\itshape Proceedings of
 the 4th International Conference on the Restructuring of the Economic
 and Political System in Japan and Europe}, 21--25 May 1996, Milan,
 Italy (Singapore: World Scientific), pp. 147--156.

\bibitem[\protect\citeauthoryear{Lamport}{1996}]{lam86}
L{\sc amport}, L., 1986, Efficient algorithms for layer assignment
 problems. PhD thesis, University of Princeton, NJ.

\bibitem[\protect\citeauthoryear{Misner}{1973}]{mtw73}
\textsc{Misner, C.W.} (Ed.), 1973, Efficient algorithms for layer
 assignment problems. In {\itshape Gravitation} (2nd  edn), Einstein's
 Legacy Vol. 5, pp. 231--256 (San Francisco, CA: Freeman).

\bibitem[\protect\citeauthoryear{Neumann}{1983}]{neu83}
\textsc{Neumann, M.}, 1983, Parallel GRASP with path-relinking for job
 shop scheduling. {\itshape International Journal of Geographical
 Information Science}, \textbf{50}, pp. 841--843.
\end{verbatim}

\medskip
\noindent Each entry takes the form:
\medskip
\begin{verbatim}
\bibitem{key} Bibliography entry
\end{verbatim}

\noindent where `{\tt key}' is the tag that is to be used as an argument for the \verb"\cite{}" command in the text of the article and `{\tt Bibliography entry}' is the material that is to appear in the list of references, suitably formatted.

Instead of typing the bibliography by hand, you may prefer to create the list of references using a B{\sc ib}\TeX\ database. Include the lines \vspace{12pt}

\noindent\verb"\bibliographystyle{tRSL}"
\newline\verb"\bibliography{tRSLguide}"
\vspace{12pt}

\noindent where the list of references should appear, where tRSL.bst is the B{\sc ib}\TeX\ style file for this journal and tRSLguide.bib is the database of bibliographic details for the references section included with the {\itshape tRSL} \LaTeX\ style package (to be replaced with the name of your own B{\sc ib}\TeX\ database). The \LaTeXe\ source file of your paper will extract from your .bib file only those references that are cited in that paper and list them in the References section of it.

Please ensure you include either a copy of your .bib file or the final generated .bbl file among your source files if your .tex file does not contain a hand-typed bibliography.

\subsection{Appendices}

Appendices should be set after the references, beginning with the command \verb"\appendices" followed by the
command \verb"\section" for each appendix title, e.g.
%
\begin{verbatim}
\appendices
\section{This is the title of the first appendix}
\section{This is the title of the second appendix}
\end{verbatim}

\noindent produces\medskip

\noindent Appendix A: This is the title of the first appendix

\noindent Appendix B: This is the title of the second appendix

\medskip
Subsections, equations, figures, tables, etc. within
appendices will then be automatically numbered as appropriate.

\subsection{{\bi tRSL} macros}

Table~\ref{macros} gives a list of macros for use with {\it tRSL}. The list displays each macro's code and a
description/demonstration of its function.

\begin{table} \tbl{{\it tRSL} macros.}{\begin{tabular}{@{}ll}
\toprule
$\backslash$thanks\{title-page footnote to article title & e.g. `Corresponding author. E-mail:\\
or author\} & A.N. Author@uiowa.edu'\\\cr
$\backslash$begin\{abstract\}...$\backslash$end\{abstract\} & for abstract on titlepage\\\\ $\backslash$bm\{math
and symbols\} & bold italic $\bm{math\;and\;symbols}$\\\cr $\backslash$bi\{text\} & bold italic \bi{text}\\\cr
$\backslash$sf\{text or upright symbols in math mode\} & sans serif \sf{text} or
$\sf{upright\;symbols\;in\;math\;mode}$\\
\botrule
\end{tabular}}
\label{macros}
\end{table}

\section{Example of a section heading including
   {\fontencoding{T1}\scshape{small caps}}, {\bi italic},
   and bold Greek such as ${\bm\kappa}$}\label{headings}

%
The following code shows how to achieve this section head:
%
\begin{verbatim}
\section{Example of a section heading including
   {\fontencoding{T1}\scshape{small caps}}, {\bi italic},
   and bold Greek such as ${\bm\kappa}$}\label{headings}
\end{verbatim}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%

\section{{\textit{tRSL}} journal style}

The notes given here relate to common style errors found in  {{\it tRSL}} manuscripts, but are {\itshape not\/}
intended to be exhaustive.

\subsection{Hyphens, N-rules, M-rules and minus signs}\label{dashes}

\begin{enumerate}
\item[(i)] Hyphens (one dash in TeX/\LaTeXe). Hyphenation should be used sparingly in {\it tRSL}. Generally, prefixes usually require hyphens: pre-, mid- (e.g. mid-1960s, pre-1978).
\item[(ii)] N-rules (also called en-rules or n-rules)(two dashes in \TeX/\LaTeXe). Spaced N-rules ( -- ) are used for parenthetical dashes, that is, to extract a part of a sentence: `The idea -- and it was her idea -- was exciting.' Otherwise, unspaced N-rules (--) are used when the first part of a compound does not modify the second, and are used in place of `and' or `to', for example, the `research--practitioner interface'; `red--green shift'; the `period 1920--1930'.
\item[(iii)] M-rules (also called em-rules or m-rules)(three dashes in \TeX/\LaTeXe). Unspaced M-rules (---) are only used to indicate the omission of a name, part of a name, or a date, for example, `Mr S--- entered the class.'
\item[(iv)] The minus sign (one dash in \TeX/\LaTeXe) is produced
automatically in math mode by use of a single dash, e.g.
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V
\end{equation}
\noindent where $|-V|=A^2+B^2$\medskip

\noindent is produced by

\begin{verbatim}
\begin{equation}
y_{i} \in \{-1, 1 \} \quad \forall i \in V
\end{equation}
\noindent where $|-V|=A^2+B^2$
\end{verbatim}

\end{enumerate}

\subsection{References}

It is important to use the correct reference style, details  of which can be found in Section~\ref{refs} above.

\subsection{Maths fonts}
Scalar  variables should be mediumface italic (e.g. $s$ for speed); vectors should be bold italic (e.g. $\bm v$
for velocity); matrices should be bold roman (upright) (e.g. $\bf A$), and tensors should be bold upright sans
serif (e.g. {\sffamily{\textbf L}}). Differential d, partial differential $\upartial$, complex i, exponential e,
superscript T for `transpose', sin, cos, tan, log, etc., should all be roman. Openface, or `blackboard', fonts
can be used, for example, for the integers $\mathbb Z$ and the reals $\mathbb R$. Sub/superscripts that are
physical variables should be italic, while those  that are labels should be roman (e.g.\ $C_p$, $T_{\rm eff}$).
Displayed equations should have end-of-line punctuation appropriate to the running text sentence of which they
form a part.

\section{Troubleshooting}

Authors may from time to time encounter problems with the  preparation
of their papers in \LaTeX. The appropriate  action  to
take will depend on the nature of the problem -- the following is
intended to act as a guide.
%
\begin{enumerate}
\item If the problem is with \LaTeX\ itself, rather than with the
actual macros, please refer to the appropriate handbooks for
initial advice.\footnote{\TeX: Knuth, D., 1986, {\it The \TeX\
book} (New York: Addison--Wesley); \LaTeXe: Lamport, L., 1994,
{\it \LaTeX: A Document Preparation System}, 2nd edn (New
York: Addison--Wesley).} If the solution cannot be found, and you
suspect that the problem lies with the macros, then please contact
Taylor \& Francis ({\tt latex.helpdesk@tandf.co.uk}).

\item Problems with page make-up (e.g.\ large spaces between paragraphs, or under headings or
figures; uneven columns; figures/tables appearing out of order):
please do {\itshape not\/} attempt to remedy these yourself using
`hard' page make-up commands -- the typesetter will correct such
problems. (You may, if you wish, draw attention to particular
problems when submitting the final version of your paper.)

\item If a required font is not available at your site, allow \TeX\
to substitute the font and specify which font you require in the
covering letter accompanying your file(s).
\end{enumerate}

\section{Fixes for coding problems}

This guide has been designed to minimize the need for user-defined macros to  create special symbols. Authors
are urged, wherever possible, to use the following coding rather than to create their own. This will minimize
the danger of author-defined macros being accidentally `overridden' when the paper is typeset (see
Section~\ref{TMth}, `Typesetting mathematics'). In cases where it is essential to create your own macros,
these should be displayed in the preamble of the source file before \verb"\begin{document}".

%
\begin{enumerate}
\item[(i)] Fonts in section headings and paper titles. The following are  examples
of styles that sometimes prove difficult to code.

\subsection*{Paper titles:}

\hsize380pt\bf{\noindent Generalized Flory theory at ${\bm\delta >
{\bf 50}^\circ}$}\\

    \noindent\normalfont is produced by
\begin{verbatim}
\title{Generalized Flory theory at
        ${\bm\delta > {\bfseries 50}^\circ}$}
\end{verbatim}
\bigskip

{\bf{\noindent Ion--ion correlations in H\,{\sc ii} regions}}\\

\noindent\normalfont is produced by
%
\begin{verbatim}
\title{Ion--ion correlations in H\,{\sc ii} regions}
\end{verbatim}

\stepcounter{enumi}

\item[(ii)] n-rules, m-rules, hyphens and minus signs (see Section~\ref{dashes} for
correct usage). To create the correct symbols in the sentence
%
\begin{quote}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{quote}
you would use the following code:
%
\begin{verbatim}
The high-resolution observations were made along a line at an
angle of $-15^\circ$ (East from North) from the axis of the
jet -- which runs North--South
\end{verbatim}

\item[(iii)] Fonts in superscripts and subscripts. Subscripts and superscripts will automatically come  out in the correct font
and size in a math environment (e.g. enclosed by `\verb"$"'
delimiters in running text or within \verb"\[...\]" or the
`equation' environment for displayed equations). You can create
the output ${\bm k_x}$ by typing \verb"${\bm k_x}$". If the
subscripts or superscripts need to be other than italic, they
should be coded individually -- see (vi) below.

\item[(iv)] Calligraphic letters (uppercase only).
%
%
Normal calligraphic can be produced with \verb"\cal" as usual (in
math mode).

\item[(v)] Automatic scaling of brackets. The codes \verb"\left" and
\verb"\right" should  be used to scale brackets automatically to
fit the equation being set. For example, to get
\[
   v = x \left( \frac{N+2}{N} \right)
\]
use the code
%
\begin{verbatim}
\[
   v = x \left( \frac{N+2}{N} \right)
\]
\end{verbatim}

\item[(vi)] Roman font in equations. It is often necessary to make some
symbols roman in an equation (e.g.\ units, non-variable
subscripts). For example, to get
\[
   \sigma \simeq (r/13~h^{-1}~{\rm Mpc})^{-0.9},
   \qquad \omega = \frac{N-N_{\rm s}}{N_{\rm R}}
\]
\noindent use the code
%
\begin{verbatim}
\[
   \sigma \simeq (r/13~h^{-1}
   ~{\rm Mpc})^{-0.9}, \qquad \omega
   =\frac{N-N_{{\rm s}}}{N_{{\rm R}}}
\]
\end{verbatim}
The {\tt siunits} package of macros for typesetting units is also compatible with the {\it tRSL} class file.
\end{enumerate}

\section{Obtaining the tRSL2e Class file}\label{FTP}

\subsection{Via the Taylor \& Francis website}

This Guide for Authors and the \verb"tRSL2e" class file may be obtained via the Instructions for Authors
on the Taylor \& Francis homepage for the journal.

Please note that the Class file calls up the following open-source \LaTeX\ packages, which will, for convenience,
unpack with the downloaded Guide for Authors and Class file: amsbsy.sty, amsfonts.sty, amsmath.sty, amssymb.sty, enumerate.sty, modsubfig.sty, natbib.sty, rotating.sty.

\subsection{Via e-mail}

This Guide for Authors, the class file and the associated open-source \LaTeX\ packages are also available by
e-mail. Requests should be addressed to {\tt latex.helpdesk@tandf.co.uk} clearly stating for which journal you
require the Guide for Authors and/or class file.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\label{lastpage}

\end{document}

### 2013-11-05 Remote_Sensing_Letter/paper.tex
RSL template applied => too long!

--- 2013-10-29 paper_dev/article_pp.tex
@@
-%ifdef FINAL
-\documentclass[journal]{IEEEtran}
-%endif
-%ifdef REVIEW
-\documentclass[journal,12pt,draftcls,onecolumn]{IEEEtran}
-%endif
+\documentclass[]{tRSL2e}
+
+%\documentclass[journal]{IEEEtran}
 %\documentclass[a4paper, 10pt, conference]{ieeeconf}
@@
 \usepackage{xcolor}
-\definecolor{plot}{rgb}{1,0.652,0.1705}
+\definecolor{plot}{rgb}{0,0.0964,1.00}
 
 \newsavebox\IBox
-\savebox\IBox{\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}
+\savebox\IBox{\includegraphics[width=2.5in,height=2.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}
 
@@
           \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
-	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
+	    \rput[bl](0,0){\includegraphics[width=2.5in,height=2.5in]{#1}}% \usebox\IBoxCRThreeR
 	    %\rput(5,1.5){\footnotesize{#2}}
@@
 	    \psline[linestyle=dashed](5,9)(6,9)%another line style: dotted
-	    \rput(8,8){\footnotesize{model}}
-	    \rput(8,9){\footnotesize{data}}            
+	    \rput(8,8){model}
+	    \rput(8,9){data}            
           \end{pspicture}
@@
 \usepackage[center]{caption}%for captions
-\usepackage[caption=false,font=footnotesize]{subfig} %for subfigures
+\usepackage{subcaption}
+%\usepackage[caption=false,font=scriptsize]{subfig} %for subfigures
 
@@
 
-%\author{Thanh-Hai Le, Ian McLoughlin}
-\author{Thanh-Hai~Le,
-        Ian~McLoughlin, 
-	and Chan-Hua~Vun%
-\thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
-Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
-University of Science and Technology of China.
-}% <-this % stops a space
-%\thanks{The authors wish to thank Dr. Ken-Yoong Lee and Dr. Timo Brestchneider of EADS Innovation-Works Singapore for 
-%	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
-\thanks{Manuscript received ?, 2013; revised ?.}}
-
-\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables for Polarimetric SAR Data}
-
 \begin{document}
+
+\author{
+  Thanh-Hai~Le$^{\ast}$$\dag$\thanks{$^\ast$Corresponding
+author. Email: le\_thanh\_hai@hotmail.com \vspace{6pt}},
+  and Ian~McLoughlin${\ddag}$, 
+  and Chan-Hua~Vun${\dag}$\\
+\vspace{6pt} $\dag$School of Computer Engineering, Nanyang Technological University, Singapore.\\
+$\ddag$ School of Information Science and Technology,
+University of Science and Technology of China.\\
+\vspace{6pt}\received{November 2013} }
 
@@
 
-\begin{IEEEkeywords}
-Polarimetric Synthetic Aperture Radar, Electromagnetic Modeling, Multidimensional Signal Processing  
-\end{IEEEkeywords}
-
-\IEEEpeerreviewmaketitle
-
 \section{Introduction}
@@
 %  which apparently is multidimensional, complex and thus not very intuitive.
-There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
+There has been a few scalar observables with accompanying statistical models proposal for POLSAR \citep{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
   but none of them is able to provide meaningful scalar discrimination measures.
@@
 While an exact statistical distribution is expected to be necessary for a test,
-  only an asymptotic distribution is used in the underlying approach \cite{Conradsen_2003_TGRS_4}.
+  only an asymptotic distribution is used in the underlying approach \citep{Conradsen_2003_TGRS_4}.
 
@@
 Different target decomposition theorems have identified many possible scalar observables for complex POLSAR data.
-In \cite{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
+In \citep{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
 While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
@@
   \begin{enumerate}
-  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \cite{Joughin_1994_TGRS_562},
-  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \cite{Joughin_1994_TGRS_562} \cite{Lee_1994_TGRS_1017},
-  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \cite{Lee_1994_TGRS_1017},
-  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \cite{Lee_1994_TGRS_1017},
-  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \cite{Lee_1994_TGRS_1017},
-  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \cite{Touzi_1996_TGRS_519}. 
+  \item cross-pol ratio $r_{HV/HH} = |S_{HV}|^2/|S_{HH}|^2$ \citep{Joughin_1994_TGRS_562},
+  \item co-pol ratio $r_{VV/HH} = |S_{VV}|^2/|S_{HH}|^2$ \citep{Joughin_1994_TGRS_562},
+  \item co-pol phase difference $\phi_{VV/HH} = arg(S_{VV}S_{HH}^*) $ \citep{Joughin_1994_TGRS_562} \citep{Lee_1994_TGRS_1017},
+  \item magnitude $g=|avg(S_{pq}S_{rs}^*)|$ \citep{Lee_1994_TGRS_1017},
+  \item normalized magnitude $\xi = \frac{|avg(S_{pq}S_{rs}^*)|}{\sqrt{avg(|S_{pq}|^2) avg(|S_{rs}|^2)}}$ \citep{Lee_1994_TGRS_1017},
+  \item intensity ratio $w = avg(|S_{pq}|^2)/avg(|S_{rs}|^2)$ \citep{Lee_1994_TGRS_1017},
+  \item and the Stokes parameters $S_i,0 \leq i \leq 3$ \citep{Touzi_1996_TGRS_519}. 
   \end{enumerate}
 More recently, statistical models for
-  each element of the POLSAR covariance matrix, i.e. $S_{pq}S_{rs}^*$, \cite{Lopez-Martinez_2003_TGRS_2232}
-  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \cite{Erten_2012_Sensors_2766} have been proposed.
+  each element of the POLSAR covariance matrix, i.e. $S_{pq}S_{rs}^*$, \citep{Lopez-Martinez_2003_TGRS_2232}
+  as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \citep{Erten_2012_Sensors_2766} have been proposed.
 
@@
 
-In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \cite{Lee_1999_TGRS}.
-It is defined \cite{Lee_1994_IJRS_2299} as:
+In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \citep{Lee_1999_TGRS}.
+It is defined \citep{Lee_1994_IJRS_2299} as:
 \begin{equation}
@@
 
-Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
+Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \citep{Anfinsen_2007_ESA_POLINSAR},
 \begin{align}
@@
 \end{align}
-the Bartlett distance \cite{Kersten_2005_TGRS_519},
+the Bartlett distance \citep{Kersten_2005_TGRS_519},
   \begin{align}
@@
   \end{align}
-the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
+the Bhattacharyya distance \citep{Lee_2011_IGARSS_3740},
 \begin{equation}
@@
 \end{equation}
-and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
+and the Wishart Statistical test distance \citep{Cao_2007_TGRS_3454}
 \begin{equation}
@@
 The close relation among the measures is further supported by the fact that
-  all of their publications refered the same statistical model developed in \cite{Conradsen_2003_TGRS_4} as the foundation.
-In \cite{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
+  all of their publications refered the same statistical model developed in \citep{Conradsen_2003_TGRS_4} as the foundation.
+In \citep{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
   which have $L_x$ and $L_y$ as the corresponding number of looks,
@@
 This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
+However, in the original work \citep{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
 This paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
@@
 The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
-Goodman \cite{Goodman_1963_AMS_178} proved
+Goodman \citep{Goodman_1963_AMS_178} proved
 that the ratio between the observable and expected values of the sample covariance matrix determinants
@@
 Specifically:
-{\footnotesize
+{
 \begin{align*}
@@
   , we have:
-{\footnotesize
+{
 \begin{align}
@@
 
-Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \cite{Rignot_1993_TGRS_896},
+Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \citep{Rignot_1993_TGRS_896},
 in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data.
   which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
-%Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
+%Similar to the way dispersion and contrast is defined for one-dimensional SAR \citep{Le_2010_ACRS},
 %  this section introduces the consistent sense of distance for POLSAR.
@@
 For SAR, where the field is more or less settled on the issue,
-  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \cite{Rignot_1993_TGRS_896}.
+  the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \citep{Rignot_1993_TGRS_896}.
 For POLSAR, where the research field is much less mature,
   the same case should apply, 
-  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \cite{Conradsen_2003_TGRS_4}.
+  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \citep{Conradsen_2003_TGRS_4}.
 
@@
 %  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
-First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \cite{Rignot_1993_TGRS_896},
+First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \citep{Rignot_1993_TGRS_896},
   the statistical model proposed for POLSAR covariance matrix determinant is to be reviewed as providing the foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
@@
 As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
-  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+  the likelihood test statistics presented in \citep{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
 can be expressed as:
@@
 This, in essence, derives an exact statistical distribution for the likelihood test statistics,
-  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.
+  as opposed to the asymptotic distribution derived in \citep{{Conradsen_2003_TGRS_4}}.
 
@@
 The look-number $L$ can be taken either as nominally stated by the data provider,
-  or it can be estimated using the technique proposed by \cite{Anfinsen_2009_TGRS_3795}.
+  or it can be estimated using the technique proposed by \citep{Anfinsen_2009_TGRS_3795}.
 
@@
 %Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
-The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
+The plots are obtained having set ENL to an estimated value obtained using the technique presented in \citep{Anfinsen_2009_TGRS_3795}.
 In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
 
-%ifdef FINAL
 \begin{figure}[h]
+%\captionsetup{justification=centering}
 \centering
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH) determinant]{
+ \begin{minipage}[b]{2.8in} 
+%	\subfloat[AIRSAR (HH) determinant]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
+%		 \epsfxsize=2.5in
+%		 \epsfysize=2.5in
 %		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps}
 		 \label{AIRSAR_1D_determinant}
-	} 
+                \subcaption{AIRSAR (HH) determinant}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH) determinant]{
+	%\subfloat[][RADARSAT2 (HH) \\ determinant]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
+%		 \epsfxsize=2.5in
+%		 \epsfysize=2.5in
 %		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
 		 \label{RADARSAT2_1D_determinant}
-	} \\
-	\subfloat[AIRSAR (HH) determinant ratio]{
+                \subcaption{RADARSAT2 (HH) determinant}
+ \end{minipage} \\                
+	%} \\
+%	\subfloat[][AIRSAR (HH) \\ determinant ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
@@
 		 \label{AIRSAR_1D_det_ratio}
-	} 
+                \subcaption{AIRSAR (HH) determinant ratio}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH) determinant ratio]{
+%	\subfloat[][RADARSAT2 (HH) \\ determinant ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
@@
 		 \label{RADARSAT2_1D_det_ratio}
-	} \\
-	\subfloat[AIRSAR (HH) change ratio]{
+                \subcaption{RADARSAT2 (HH) determinant ratio}
+ \end{minipage} \\                 
+%	} \\
+%	\subfloat[][AIRSAR (HH) \\ change ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
@@
 		 \label{AIRSAR_1D_det_ratio}
-	} 
+                \subcaption{AIRSAR (HH) change ratio}
+ \end{minipage}                 
+%	}
 	\hfill	
-	\subfloat[RADARSAT2 (HH) change ratio]{
-
+ \begin{minipage}[b]{2.8in} 
+%	\subfloat[][RADARSAT2 (HH) \\ change ratio]{
+%
 \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
@@
 %		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
-		 \label{RADARSAT2_1D_det_ratio}
-	}
+%		 \label{RADARSAT2_1D_det_ratio}
+                \subcaption{RADARSAT2 (HH) change ratio}
+ \end{minipage}                 
+%	}
 \end{tabular}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[AIRSAR (HH) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_determinant}
-	} 
-	\hfill	
-	\subfloat[AIRSAR (HH) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-	}
-	\hfill	
-	\subfloat[AIRSAR (HH) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-	}  \\
-	\subfloat[RADARSAT2 (HH) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_1d.eps} 	
-		 \label{RADARSAT2_1D_determinant}
-	}
-        \hfill
-        \subfloat[RADARSAT2 (HH) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps} 	
-		 \label{RADARSAT2_1D_det_ratio}
-	}
-        \hfill
-        \subfloat[RADARSAT2 (HH) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
-		 \label{RADARSAT2_1D_det_ratio}
-	}
-\end{tabular}
-\caption{The specific d=1 models are validated on both RADARSAT2 and AIRSAR datasets}
-\label{fig:verify_POLSAR_model_1D}
-\end{figure}
-%endif
 
@@
   on both AIRSAR and RADARSAT2 datasets.
-The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+The look-number is estimated for each type of data and for each image using the technique described in \citep{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
 The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
@@
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
-%ifdef FINAL
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH-HV) determinant]{
+%	\subfloat[][AIRSAR (HH-HV) \\ determinant]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_2d.eps}{determinant}
@@
 		 \label{AIRSAR_2D_determinant}
-	} 
+                \subcaption{AIRSAR (HH-HV) determinant}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant]{
+%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
@@
 		 \label{RADARSAT2_2D_determinant}
-	} \\
-	\subfloat[AIRSAR (HH-HV) determinant ratio]{
+                \subcaption{RADARSAT2 (HH-HV) determinant}
+ \end{minipage}                 \\
+%	} \\
+%	\subfloat[][AIRSAR (HH-HV) \\ determinant ratio]{          
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_2d.eps}{determinant-ratio}
@@
 		 \label{AIRSAR_2D_det_ratio}
-	} 
+                \subcaption{AIRSAR (HH-HV) determinant ratio}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
+%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
@@
 		 \label{RADARSAT2_2D_det_ratio}
-	} \\
-	\subfloat[AIRSAR (HH-HV) change ratio]{
+                \subcaption{RADARSAT2 (HH-HV) determinant ratio}
+ \end{minipage}                \\ 
+%	} \\
+%	\subfloat[][AIRSAR (HH-HV) \\ change ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
@@
 		 \label{AIRSAR_2D_det_ratio}
-	} 
+                \subcaption{AIRSAR (HH-HV) change ratio}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) change ratio]{
+%	\subfloat[][RADARSAT2 (HH-HV) \\ change ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}{change-ratio}
@@
 		 \label{RADARSAT2_2D_det_ratio}
-	}
+                \subcaption{RADARSAT2 (HH-HV) change ratio}
+ \end{minipage}                 
+%	}
 \end{tabular}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[RADARSAT2 (HH-HV) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_determinant}
-	}
-	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_1D_det_ratio}
-	}
- 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
-		 \label{RADARSAT2_2D_determinant}
-	} \\
-	\subfloat[AIRSAR (HH-HV) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_2d.eps} 	
-		 \label{AIRSAR_2D_determinant}
-	} 
-	\hfill	
-	\subfloat[AIRSAR (HH-HV) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_2d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-	} 
-	\hfill	
-	\subfloat[AIRSAR (HH-HV) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_2d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-	} 
-\end{tabular}
-\caption{The specific $d=2$ models are validated on both  RADARSAT2 and AIRSAR datasets}
-\label{fig:verify_det_ratio_model_2D}
-\end{figure}
-%endif
-
-%ifdef FINAL
+
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[AIRSAR (HH-HV-VV) determinant]{
+%	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
@@
 		 \label{AIRSAR_3D_determinant}
-	} 
+                \subcaption{AIRSAR (HH-HV-VV) determinant}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
+%`	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
@@
 		 \label{RADARSAT2_3D_determinant}
-	} \\
-	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
+                \subcaption{RADARSAT2 (HH-HV-VV) determinant}
+ \end{minipage}                 \\
+%	} \\
+%	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
@@
 		 \label{AIRSAR_2D_det_ratio}
-	} 
+                \subcaption{AIRSAR (HH-HV-VV) determinant ratio}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
+%	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
@@
 		 \label{RADARSAT2_2D_det_ratio}
-	} \\
-	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
+                \subcaption{RADARSAT2 (HH-HV-VV) determinant ratio}
+ \end{minipage}                \\ 
+%	} \\
+%	\subfloat[][AIRSAR (HH-HV-VV) \\ change ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
@@
 		 \label{AIRSAR_2D_change_ratio}
-	} 
+                \subcaption{AIRSAR (HH-HV-VV) change ratio}
+ \end{minipage}                 
+%	} 
 	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
+%	\subfloat[][RADARSAT2 (HH-HV-VV) \\ change ratio]{
+ \begin{minipage}[b]{2.8in} 
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
@@
 		 \label{RADARSAT2_2D_change_ratio}
-	}
+                \subcaption{RADARSAT2 (HH-HV-VV) change ratio}
+ \end{minipage}                 
+%	}
 \end{tabular}
@@
 \end{figure}
-%endif
-%ifdef REVIEW
-\begin{figure}[h!]
-\centering
-\begin{tabular}{c}
-	\subfloat[AIRSAR (HH-HV-VV) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_AIRSAR_3d.eps} 	
-		 \label{AIRSAR_3D_determinant}
-	} 
-	\hfill	
-	\subfloat[AIRSAR (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_3d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-	}
-	\hfill	
- 	\subfloat[AIRSAR (HH-HV-VV) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_3d.eps} 	
-		 \label{AIRSAR_3D_change_ratio}
-	} \\
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_3D_determinant}
-	}
-        \hfill
-	\subfloat[RADARSAT2 (HH-HV-VV) determinant ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_1D_det_ratio}
-	} 
-	\hfill	
-	\subfloat[RADARSAT2 (HH-HV-VV) change ratio]{
-		 \epsfxsize=2in
-		 \epsfysize=2in
-		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_1D_change_ratio}
-	}
-\end{tabular}
-\caption{The specific $d=3$ models are validated on both practical RADARSAT2 and AIRSAR datasets}
-\label{fig:verify_det_ratio_model_3D}
-\end{figure}
-%endif
-
-%\subsection{Theoretical Implications of This Proposal}
+
 \section{Discussion}
@@
 Ideally %to better understand POLSAR data
-the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \citep{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \citep{Cloude_1997_TGRS_68} or similar.
 
@@
 Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
-Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+Similar to the way that different measures of distance can be used to derive POLSAR classifiers \citep{Lee_1999_TGRS}, change detectors \citep{Conradsen_2003_TGRS_4}, edge detectors \citep{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \citep{Le_2010_ACRS} \citep{Le_2011_ACRS},
 new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
 These applications however are not included in this paper, but rather left as a suggestion for future investigations.
-%There are a few reasons for this decision.
-%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
-%  the first being a faster ENL evaluation for POLSAR data and
-%  the second being the visual evaluation of POLSAR speckle filters.
-%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
-%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
-%It does not, technically speaking, focuses on proposing new discrimination measures.
-
-%The advantages of this proposal are thus to be compared against other published models for POLSAR.
-%Consequently, the methodology to evaluate the result of this proposal is a bit unusual.
-%While quantitative evaluation is normally employed, in this theoretical model proposal only qualitative evaluation are shown.
-%This is because compared to existing published observables for POLSAR, the advantage of the proposed observables are qualitative which does not requires numerical quantitative comparisons.
-%Instead a straightforward binary evaluation would be sufficient.
-%In comparison to other scalar models for POLSAR, the proposed models for determinant and its log-transformed version are representative are highly representative of the POLSAR data.
-%This is because these models collapses into the representative SAR intensity when the multi-dimensional data is collapsed into the traditional one-dimensional SAR data.
-%This is proven in section \ref{sec:sar_special_case_of_polsar}.
-%No other existing models for POLSAR is known to have this property.
-%
-%Other advantage is that compared to other proposed scalar models for POLSAR, only these proposed statistical models lead to existing discrimination measures.
-%This argument is supported by an extensive literature survey in section \ref{sec:lit_review}.
-%There not only existing published scalar models for POLSAR are reviewed to show that none of them lead to discrimination measure,
-%  existing discrimination measures for POLSAR are also extensively surveyed leaving virtually no chance of there exists an existing scalar statistical model for POLSAR which leads to existing discrimination measures.
-
-%\section{Extending SAR data processing techniques towards POLSAR}
-%
-%Currently while the field of SAR is much more developed than the field of POLSAR,
-%  the two fields however are quite separated.
-%Hence many techniques applicable to SAR are not directly applicable to POLSAR.
-%With the newly gained, the current proposal provide the bridge between these two separated fields,
-%  inviting potential extension of various SAR processing techniques to POLSAR data.
-%%For instance the earlier example illustrate that while intensity ratio was commonly used to carry out visually evaluation of SAR speckle filters,
-%%  the newly proposed determinant ratio and its log-transformed version (i.e. contrast) are shown capable of visually evaluating POLSAR speckle filters.
-%%We believe there are many more unexplored possibilities for such applications.
-%  
-%There are many beneficial implications for this proposal.
-%One of the main benefits is that:
-%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-%One example has already been presented in this paper, 
-%  where existing SAR discrimination measures are extended towards POLSAR.
-%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
-%
-%In evaluating SAR speckle filters, the intensity ratio is widely used.
-%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-%Assuming a perfect filtering condition, the ratio image should only contain random noise.
-%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
-%
-%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-%  this technique can be equally applied to evaluate POLSAR speckle filters.
-%In fact better results can be achieved.
-%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-%  which is linear and additive in nature.
-%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-%
-%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
-%  and the two POLSAR speckle filters are then applied to the patch.
-%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-%
-%%ifdef FINAL
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%%ifdef REVIEW
-%\begin{figure}[h!]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%
-%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-%  the distortion impact of the filter can also be made visible by the residual image.
-%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-%in the additive log-determinant image of the filtered output, 
-%  such an observation can be made relatively easier by inspecting the residual image.
-%  
-%There are many similar SAR data processing technique that may be adaptable to POLSAR.
-%Examples in the same topic of evaluating speckle filters include
-%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 
@@
   as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
-    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.
+    such as the Freeman-Durden decomposition \citep{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \citep{Cloude_1997_TGRS_68}.
 
 % references section
-\bibliographystyle{IEEEtran}
-\bibliography{IEEEabrv,article}
+\bibliographystyle{tRSL}
+\bibliography{paper}
 

### 2013-11-06 Remote_Sensing_Letter/paper.tex
mostly include Ian's changes

@@
 \newsavebox\IBox
-\savebox\IBox{\includegraphics[width=2.5in,height=2.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}
+\savebox\IBox{\includegraphics[width=1.5in,height=1.5in]{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}}
 
@@
           \begin{pspicture}[showgrid=false](\column,\row)% set showgrid=false for the final
-	    \rput[bl](0,0){\includegraphics[width=2.5in,height=2.5in]{#1}}% \usebox\IBoxCRThreeR
+	    \rput[bl](0,0){\includegraphics[width=1.5in,height=1.5in]{#1}}% \usebox\IBoxCRThreeR
 	    %\rput(5,1.5){\footnotesize{#2}}
@@
 \vspace{6pt} $\dag$School of Computer Engineering, Nanyang Technological University, Singapore.\\
-$\ddag$ School of Information Science and Technology,
-University of Science and Technology of China.\\
+$\ddag$ University of Science and Technology of China.\\
 \vspace{6pt}\received{November 2013} }
@@
 %What is the situation, the background context of your research? the BIG problem!
-During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
-technology to become a feasible and preferred technique for earth observation applications.
-SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
-POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
-  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
+Relentless growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
+to become a feasible and preferred technique for earth observation.
+Basic SAR has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
+This exploits the natural polarization property of Electro-Magnetic (EM) waves,
+  encoded in multiple channels, compared to traditional one-channel SAR.
 
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-Like SAR data, POLSAR data is stochastic.
-Moreover, it is multi-dimensional, making it even harder to interpret.
-Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
+POLSAR data, like SAR, is stochastic but is also multi-dimensional, making it even harder to interpret.
+It is therefore important to establish a simple and intuitive understanding of the data.
  Statistical models are undoubtedly crucial in understanding its stochastic nature.
 While several %multidimensional 
-models have been proposed to describe POLSAR data, they
-  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
+models have been proposed for POLSAR data, they
+   tend to be complex and unintuitive due to the multidimensional nature of the data.
 Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
-  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
-It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.
+  which should be based on statistically consistent models %for scalar and representative observables 
+  of the multidimensional data.
+It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.
 
@@
 %  which apparently is multidimensional, complex and thus not very intuitive.
-There has been a few scalar observables with accompanying statistical models proposal for POLSAR \citep{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
-  but none of them is able to provide meaningful scalar discrimination measures.
+A few scalar POLSAR observables with accompanying statistical models have been proposal \citep{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
+  but none is able to provide meaningful scalar discrimination measures.
 %  but none of them has led to scalar discrimination measures proposal.
@@
   which severely limits their applicability in practical data processing applications.
-From an alternative approach, a few POLSAR discrimination measures have been proposed,
-  but all are based on the likelihood ratio statistics.
-This statistical test should be based on an exact and consistent statistical distribution
-  but so far has only shown to be based on an asymptotic distribution.
+Alternatively, a few POLSAR discrimination measures have been proposed,
+  but all based on likelihood ratio statistics.
+This should ideally be based on an exact and consistent distribution
+  but so far only asymptotic distributions have been demonstrated.
 
 %Research Objective: Give your precise problem statement  
-This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
+This article presents a scalar and representative observable, and its associated generic statistical model, to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.
 %Now State your approach  
@@
 Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
-This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
+This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
 %
@@
 %The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
-Interestingly the paper also shows that %It is also shown that
-  the specific one dimensional versions of the proposed  models 
-  match perfectly with the traditional statistical model used for SAR intensity.
-This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
-With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
-The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+We will also show that %It is also shown that
+  the specific one dimensional (1-D) versions of the proposed  models 
+  match %perfectly with 
+  the traditional statistical model used for SAR intensity.
+This effectively incorporates SAR theory under the umbrella of the proposed scalar approach for multi dimensional POLSAR.
+The different discrimination proposals for SAR and POLSAR are reviewed in light of this and the  proposed in this paper is shown to provide a strong, unifying and consistent foundation.
+% relating them all together.
+The applicability of these theoretical models will be illustrated by experiments where the specific 1, 2 and 3-D versions of the proposed models are validated against practical data. 
 %Furthermore, the approach proposed in this paper
@@
 %Article Organization: Show that you deliver on the objectives and hence solve the stated problem
-The remainder of this article is organized as follows.
-After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
-  derives the generic statistical model for the determinant of the POLSAR covariance matrix
-  and proposes several new discrimination measures for the multi-dimensional data.
-After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
-  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
-%Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
-The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
-Section \ref{sec:discussion} presents a high-level discussion of the results presented before
-  section \ref{sec:conclusion} finally concludes the paper.
+
+%%***IVM SKIP THIS TO SAVE SPACE - letters usually don't have this
+%The remainder of this article is organized as follows.
+%After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
+%  derives the generic statistical model for the determinant of the POLSAR covariance matrix
+ % and proposes several new discrimination measures for the multi-dimensional data.
+%After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
+ % section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+%The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
+%Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+ % section \ref{sec:conclusion} finally concludes the paper.
 
@@
 
-%This section outlines related publication.
-Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
-  where it is shown that none are able to provide statistically consistent discrimination measures. 
-Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
-  and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
-While an exact statistical distribution is expected to be necessary for a test,
-  only an asymptotic distribution is used in the underlying approach \citep{Conradsen_2003_TGRS_4}.
+%Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
+%  where it is shown that none are able to provide statistically consistent discrimination measures. 
+%Section \ref{sec:lit_measures} further strengthens those findings by discussing discrimination measures that have been proposed for POLSAR,
+ % and demonstrates that almost all of them are based on the likelihood statistical test for complex Wishart distribution.
+%While an exact statistical distribution is expected to be necessary for a test,
+ % only an asymptotic distribution is used in the underlying approach \citep{Conradsen_2003_TGRS_4}.
 
-\subsection{Scalar Observables for POLSAR Data and their Statistical Models}
-\label{sec:lit_models}
+%**IVM save space!
+%\subsection{Scalar Observables for POLSAR Data and their Statistical Models}
+%\label{sec:lit_models}
 
 Different target decomposition theorems have identified many possible scalar observables for complex POLSAR data.
-In \citep{Alberga_2008_IJRS_4129}, the performance of different scalar POLSAR observables is evaluated for classification purposes.
-While many scalar observables for POLSAR were presented, their corresponding statistical models and classifiers were not available.
-Furthermore, at its conclusion, the paper indicated that it is impossible to identify a single best representation.
+\citet{Alberga_2008_IJRS_4129} evaluated the performance of different scalar POLSAR observables for classification.
+While many were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, the paper concluded that it is impossible to identify a single best representation.
 Although, to be fair, the observables were identified for describing a decomposed portion of the complex POLSAR data,
-  rather than providing a unified representation of the POLSAR data.
-
-Using a different approach, given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart distribution,
+  rather than a unified representation.
+%
+Using a different approach, given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart,
   it is possible to derive the scalar statistical models for some univariate POLSAR observables.
 %This becomes an alternative approach used in the study of POLSAR data.
-However, such derivations are not trivial tasks, and so far, only a handful of such statistical models have been proposed, including the following:
+However, this is non-trivial -- so far, only a handful of such models have been proposed, including:
   \begin{enumerate}
@@
   as well as for the largest eigen-value of the covariance matrix $\lambda_1$ \citep{Erten_2012_Sensors_2766} have been proposed.
-
-While these models undoubtedly help to further our understandings of the POLSAR data,
-  none of the underlying observables have been shown to meet the dual criteria of
-  1) resulting in statistically consistent discrimination measures and thus 
-  2) being representative of the complex POLSAR data.
+Although useful, these have not been shown to result in statistically consistent discrimination measures or
+ be representative of the complex POLSAR data.
+%While these models undoubtedly help to further our understandings of the POLSAR data,
+ % none of the underlying observables have been shown to meet the dual criteria of
+ % 1) resulting in statistically consistent discrimination measures and thus 
+ % 2) being representative of the complex POLSAR data.
 
@@
 
-The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined respectively as:
-\begin{align}
-  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
-  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
-\end{align}
-where $C_{i,j}$ denotes the $(i,j)$ elements of the POLSAR covariance matrix C,
- $||$ denotes absolute values
-and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-However, in the context of POLSAR, % covariance matrix
-  these dissimilarity measures are not widely used 
-  mainly due to the multiplicative nature of the noisy data.
-
-In the field of POLSAR, the Wishart distance is probably the most widely used, as part of the well-known Wishart classifier \citep{Lee_1999_TGRS}.
-It is defined \citep{Lee_1994_IJRS_2299} as:
-\begin{equation}
-  d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation},
-where $tr(C)$ denotes the trace of the matrix C. 
+Euclidean or Manhattan distance measures for matrices are not widely used 
+for POLSAR due to the multiplicative nature of the noise.
+%, defined respectively as:
+%\begin{align}
+%  d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
+%  d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
+%\end{align}
+%where $C_{i,j}$ denotes the $(i,j)$ elements of the POLSAR covariance matrix C,
+% $||$ denotes absolute values
+%and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
+Instead, the Wishart distance is probably most common, as part of the well-known Wishart classifier \citep{Lee_1999_TGRS}, defined \citep{Lee_1994_IJRS_2299} as:
+$d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})$
+where $tr(C)$ denotes the trace of the POLSAR covariance matrix C. 
 As a measure of distance, its main disadvantage is that $d(C_y,C_y) = \ln|C_y| \neq 0$.
@@
 Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \citep{Anfinsen_2007_ESA_POLINSAR},
+\vspace{-2mm}
 \begin{align}
@@
 \end{align}
+\vspace{-2mm}
 the Bartlett distance \citep{Kersten_2005_TGRS_519},
+     \vspace{-2mm}
   \begin{align}
@@
   \end{align}
+     \vspace{-2mm}
 the Bhattacharyya distance \citep{Lee_2011_IGARSS_3740},
+     \vspace{-2mm}
 \begin{equation}
@@
 \end{equation}
-and the Wishart Statistical test distance \citep{Cao_2007_TGRS_3454}
+     \vspace{-2mm}
+and the Wishart Statistical test distance \citep{Cao_2007_TGRS_3454},
+     \vspace{-2mm}
 \begin{equation}
@@
 
-Closer examination of these dissimilarity measures reveals that most of them are related in some ways. %to each other.
-The Bhattacharyya distance is easily shown to be related to the Barlett distance.
-At the same time the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
+Closer examination of these reveal that most are related:
+The Bhattacharyya and Bartlett distances are easily shown to be related.
+At the same time, Barlett can be considered a special case of the Wishart Statistical Test distance,
   when the two data sets have the same number of looks, i.e. $L_x=L_y$.
-The close relation among the measures is further supported by the fact that
-  all of their publications refered the same statistical model developed in \citep{Conradsen_2003_TGRS_4} as the foundation.
+The close relation among  measures may be due to the fact that
+  all of their publications refer to, and are based on, the same statistical model in \citep{Conradsen_2003_TGRS_4}.
 In \citep{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
@@
 the likelihood ratio statistics for POLSAR covariance matrix is considered:  
-\begin{equation*}
+     \vspace{-2mm}
+\begin{equation}
   Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-\end{equation*}
+\end{equation}
 
@@
 }
+\vspace{-2mm}
 
 To detect changes, a test statistic is developed for this discrimination measure.
-This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \citep{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
-This paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
+i.e. a distribution is derived for the dissimilarity measure.
+However, \citet{Conradsen_2003_TGRS_4} only use an asymptotic distribution.
+By contrast, this paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
   which is capable of providing an exact distribution for the test.
@@
 
-%In this section, the generic scalar statistical model for POLSAR is presented.
-In this section, after the basic foundations of POLSAR statistical analysis are introduced,
-  the generic scalar statistical model for the multi-dimensional POLSAR will be presented.
+In this section, the generic scalar statistical model for POLSAR is presented.
+%In this section, after the basic foundations of POLSAR statistical analysis are introduced,
+ % the generic scalar statistical model for the multi-dimensional POLSAR will be presented.
 %  this section presents the theoretical model for multi-dimensional POLSAR data. 
-
-In this paper, the POLSAR scattering vector is denoted as $s$.
-For partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
-  the vector is two-dimensional ($d=2$) and is normally written as: 
-\begin{equation}
-s_{part}=\begin{bmatrix}
-S_h\\ 
-S_v
-\end{bmatrix}
-\end{equation}
-For full and monostatic POLSAR data,
-  the vector is three-dimensional ($d=3$) and is presented as:
-\begin{equation}
-s_{full}=\begin{bmatrix}
-S_{hh}\\
-\sqrt{2}S_{hv}\\
-S_{vv}
-\end{bmatrix}
-\end{equation}
-
-Let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
-  where $s^{*T}$ is the complex conjugate transpose of $s$. 
-Assuming %all the elements in $s$ are independent and
-  $s$ is jointly circular complex Gaussian with the expected covariance matrix $\Sigma$,
-  then the probability density function (PDF) of $s$ can be written as:
-\begin{equation}
-  pdf(s;\Sigma)=\frac{1}{\pi^d|\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-\end{equation}
+%
+%In this paper, the POLSAR scattering vector is denoted as $s$.
+%For partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+%  the vector is two-dimensional ($d=2$) and is normally written as: 
+%\begin{equation}
+%s_{part}=\begin{bmatrix}
+%S_h\\ 
+%S_v
+%\end{bmatrix}
+%\end{equation}
+%For full and monostatic POLSAR data,
+ % the vector is three-dimensional ($d=3$) and is presented as:
+%\begin{equation}
+%s_{full}=\begin{bmatrix}
+%S_{hh}\\
+%\sqrt{2}S_{hv}\\
+%S_{vv}
+%\end{bmatrix}
+%\end{equation}
+%
+First, let $\Sigma=E [ss^{*T}]$ denote the population expected value of the POLSAR covariance matrix,
+  where $s^{*T}$ is the complex conjugate transpose of the POLSAR scattering vector, $s$. 
+%Assuming 
+If this is jointly circular complex Gaussian with expected covariance matrix $\Sigma$,
+  then the PDF of $s$ can be written as
+$pdf(s;\Sigma)=\{1/{\pi^d|\Sigma|}\} exp\{-s^{*T}\Sigma^{-1}s\}$
 where $||$ denotes the matrix determinant.
-
+%
 The sample POLSAR covariance matrix is formed as the mean of Hermitian outer product of independent single-look scattering vectors,
+     \vspace{-4mm}
 \begin{equation}
@@
 where $L$ is the number of looks
-  and $s_i$ denotes the single-look scattering vector,
-  which equals $s_{part}$ for the case of partial POLSAR or
-  $s_{full}$ for the case of full polarimetry.
-
+ and $s_i$ denotes the partial or full POLSAR scattering vector respectively.
+%
 Complex Wishart distribution statistics are normally used for the scaled covariance matrix
@@
 with $\Gamma_d(L) = \pi^{d(d-1)/2} \prod^{d-1}_{i=0}\Gamma(L-i)$
-and $d$ is the dimensional number of the POLSAR covariance matrix.
-
-The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
-Goodman \citep{Goodman_1963_AMS_178} proved
-that the ratio between the observable and expected values of the sample covariance matrix determinants
+and $d$ the dimension number of the POLSAR covariance matrix.
+%
+The approach taken in this paper differs by applying a homoskedastic log transformation  on a less-than-well-known relationship.
+\citet{Goodman_1963_AMS_178} found
+that the ratio between observable and expected values of the sample covariance matrix determinants
   behaves like a product of $d$ chi-squared random variables with different degrees of freedom: 
+\vspace{-2mm}
 \begin{equation}
@@
 %We will now use 
-This result is used here to develop the generic scalar statistical model for POLSAR. %log-transformed measures of distance.
-From Eqn. \ref{eqn:prod_chi_squared_rv} %and \ref{eqn:sum_log_chi_squared_rv}
-we have: %can deduce the following relationships:
+We use this to develop a generic scalar statistical model. %log-transformed measures of distance.
+From Eqn. \ref{eqn:prod_chi_squared_rv} we have:
+\vspace{-2mm}
 \begin{eqnarray}
@@
 
-In a given homogeneous POLSAR area, the parameters $\Sigma_v$, $d$ and $L$ can be considered constant.
-Thus Eqn. \ref{eqn:determinant_distribution} indicates that 
-  in the original POLSAR domain, a multiplicative speckle noise pattern is present.
-
-Moreover, since the average and variance of these chi-squared distributions %and log-chi-squared distribution
-  are known to be constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
-  the product and summation of these random variables also have fixed summary statistics.
+Over a homogeneous area, $\Sigma_v$, $d$ and $L$ are considered constant.
+Thus Eqn. \ref{eqn:determinant_distribution} indicates that a multiplicative speckle noise pattern is present 
+  in the original POLSAR domain.
+Moreover, since the average and variance of these chi-squared distributions are %and log-chi-squared distribution
+constant, i.e. $avg \left[ \chi(2L) \right] = 2L$ and $var \left[ \chi(2L) \right] = 4L$,
+  their product and summation also have fixed summary statistics.
 Specifically:
+\vspace{-2mm}
 {
@@
   , we have:
+\vspace{-2mm}  
+%{
+%\begin{align}
+%  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+%  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}%\\
+%%  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
+%%  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+%\end{align}
+%}
 {
@@
   avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
-  var \left[ |C_v| \right]  &=   \frac{|\Sigma_v|^2 \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }{L^{2d}} \label{eqn:var_det_is_heteroskedastic}%\\
+  var \left[ |C_v| \right]  &=   {\frac{|\Sigma_v|^2}{L^{2d}}{ \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }} 
+ \label{eqn:var_det_is_heteroskedastic}%\\
 %  avg \left[ \ln |C_v| \right] &= \ln |\Sigma_v| - d \cdot \ln{L}  + \sum^{d-1}_{i=0} \psi^0(L-i) \label{eqn:avg_log_det} \\
 %  var \left[ \ln |C_v| \right] &=  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:var_log_det_is_homoskedastic}
+\vspace{-5mm}
 \end{align}
@@
 
-For a real world captured image, while the parameters $d$ and $L$ do not change for the whole image,
-  the underlying $\Sigma_v$ is expected to differ from one region to the next.
+For a real world captured image, while parameters $d$ and $L$ do not change for the whole image,
+  the underlying $\Sigma_v$ is likely to differ from one region to the next.
 Thus over a heterogeneous scene, the stochastic process for $|C_v|$ and $\ln |C_v|$ vary depending on the underlying signal $\Sigma_v$. 
-In such context, Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ also differs depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
-
+Eqn. \ref{eqn:var_det_is_heteroskedastic} implies that the variance of $|C_v|$ will also differ depending on the underlying signal $\Sigma_v$ (i.e. it is   heteroskedastic).
 Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \citep{Rignot_1993_TGRS_896},
-in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data.
-  which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
+this paper proposes the determinant-ratio and the change-ratio as discrimination measures for the POLSAR data.
+%  which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
 %Similar to the way dispersion and contrast is defined for one-dimensional SAR \citep{Le_2010_ACRS},
@@
 %Assuming, on the one hand,
-For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+If the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
 then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
@@
 %Eqns. \ref{eqn:prod_chi_squared_rv} and \ref{eqn:sum_log_chi_squared_rv} lead straight to the definition of the following random variables, which is the :
-\begin{eqnarray}
-  \mathbb{R}_{\Sigma} &=& \frac{|C_v|}{|\Sigma_v|} \label{eqn:determinant_ratio_observables}%\\
-%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
-\end{eqnarray}
+$\mathbb{R}_{\Sigma} = {|C_v|}/{|\Sigma_v|}$
 %On the other hand, under a looser assumption %From another perspective
-For cases where the POLSAR data is known to have come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown},
- then a random variable called the change-ratio ($\mathbb{R}_{C}$)  is defined as:
-\begin{eqnarray}
-  \mathbb{R}_{C} &=& \frac{|C_1|}{|C_2|} \label{eqn:determinant_ratio_samples_observables}%\\
-%  \mathbb{L} &=& \ln|C_v| - \ln|\Sigma_v| \label{eqn:log_distance_observables} 
-\end{eqnarray}
-where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
-
+For POLSAR data from a homogeneous area, but when the true value of $\Sigma_v$ is \textit{unknown},
+ then a random variable called the change-ratio $\mathbb{R}_{C}$)  is defined, $ \mathbb{R}_{C} = {|C_1|}/{|C_2|}$ where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
+%
 %  the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables are the observables defined as:
@@
 %\end{eqnarray}
-
+%
 Using the results from Eqn. \ref{eqn:determinant_distribution}, %\ref{eqn:log_determinant_distribution} and \ref{eqn:avg_log_det}
   we have
-\begin{eqnarray}
-\mathbb{R}_{\Sigma} &\sim& \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \label{eqn:determinant_ratio_distribution} \\
-\mathbb{R}_{C} &\sim& \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)} \label{eqn:change_ratio_distribution}
-%\mathbb{L} &\sim&  \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln(2L)
-%\label{eqn:log_determinant_distance_distribution} \\ 
-% \mathbb{D} &\sim& \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2} + k
-%\label{eqn:dispersion_distribution} \\ 
-% \mathbb{C} &\sim& \sum^{d-1}_{i=0} \Delta(2L-2i)
-%\label{eqn:contrast_distribution}  
-\end{eqnarray}
+\begin{equation}%\label{eqn:determinant_ratio_distribution}
+\mathbb{R}_{\Sigma} \sim \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i)  ~~and~~
+\mathbb{R}_{C} \sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)} \label{eqn:change_ratio_distribution}
+\vspace{-5mm}
+\end{equation}
+%
 %with $\Delta(2L) \sim \Lambda(2L) - \Lambda(2L)$
 %and $k=\sum^{d-1}_{i=0} \psi^0(L-i)$
-
+%
 %Thus the characteristic functions for the summative random variables is derived in Appendix \ref{sec:appendix_b} as:
@@
 %\end{align}
-
+%
 Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
-  it is natural that this variable also follows fixed distributions.
-Moreover, it is independent of the underlying signal $\Sigma_v$,
-  indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
-This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
-  and will be further discussed in the next sections.
+this variable naturally also follows fixed distributions.
+Moreover, it is independent of the underlying $\Sigma_v$,
+  indicating its statistically consistent properties (i.e. its applicability as a POLSAR discrimination measure).
+%This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
+ % and will be further discussed in the next sections.
 %is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 
@@
 %The previous sections have introduced and validated the theoretical models for 3-dimensional ($d=3$) full polarimetric and 2-dimensional ($d=2$) partial polarimetry, cases.
-This section shows that the proposed generic model is equally  applicable to the 1-dimensional ($d=1$) case,
-  which is physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into conventional single dimensional SAR data.
-Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while the determinant $|C_v|$ is equivalent to  the scalar variance value.
-As variance is equal to intensity $I$ for SAR data, our result is consistent with previous results for SAR intensity data.
-Thus the proposed generic model for POLSAR, collapsed into one dimension will be shown to incorporate the traditional SAR intensity as a natural case of the unified model.
+This section shows that the proposed generic model is  applicable to the 1-D case ($d=1$),
+physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into single dimensional SAR data.
+Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while determinant $|C_v|$ becomes the scalar variance.
+As variance is equal to intensity $I$ in SAR, our result is consistent with previous results for SAR intensity.
+Thus the proposed generic model for POLSAR, collapsed into 1-D will be shown to apply also to traditional SAR intensity.% as a natural case of the unified model.
 %  as well as reminding us that SAR is a special case of POLSAR.
 
-The results for our models can be summarized using the following equations:
-\begin{align*}
-  |C_v| &\sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) \\ %\label{eqn:determinant_distribution} %\\
-  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
-\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
-%  \mathbb{L} &= \ln{|C_v|} - \ln{|\Sigma_v|} \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \cdot \ln{2L} \\ %\label{eqn:polsar_dispersion_log_det_cov_dist} \\
-%  \mathbb{D} &= \ln{|C_v|} - avg(\ln{|C_v|}) \sim \sum^{d-1}_{i=0} \Lambda(2L-2i) - d \ln{2} + k\\
-%  \mathbb{C} &= \ln{|C_{1v}|} - \ln{|C_{2v}|} \sim \sum^{d-1}_{i=0} \Delta(2L-2i) \\
-%  \mathbb{A} &= avg(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \\ %\label{eqn:polsar_dispersion_averages} \\
-%  \mathbb{V} &= var(\mathbb{L}) = \sum^{d-1}_{i=0} \psi^1(L-i) \\ %\label{eqn:polsar_dispersion_variance} \\
-%  \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) \label{eqn:polsar_dispersion_mse} 
-\end{align*}
+The results for our models can be summarised using the following equations:
+\begin{equation}\nonumber
+  |C_v| \sim |\Sigma_v| \cdot \frac{1}{(2L)^d} \cdot \prod_{i=0}^{d-1} \chi (2L-2i) 
+\end{equation}
+\begin{eqnarray}\nonumber
+\mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi(2L-2i) ~~and~~
+\mathbb{R}_{C} = \frac{C_1}{C_2} \sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+\end{eqnarray}
 
@@
   the equations become:
-\begin{align*}
-  |C_v| &\sim  \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) \\ %\label{eqn:determinant_distribution} %\\
-  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
-\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
-\end{align*}
+\begin{equation}
+  |C_v| \sim { \frac{|\Sigma_v|}{(2L)} \cdot \chi (2L) }\\ %\label{eqn:determinant_distribution} %\\
+  \end{equation}
+\begin{equation}
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)} \cdot \chi(2L) ~~and~~
+\mathbb{R}_{C} = \frac{C_1}{C_2} \sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+\end{equation}
 
@@
 Applying variable change theorem into the above equations results in:
+\begin{equation}
+  |C_v| \sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \nonumber %
+  \end{equation}
+  \vspace{-6mm}
 \begin{align*}
-  |C_v| &\sim  pdf \left[ \frac{L^L x^{L-1} e^{-Lx/|\Sigma_v|}}{\Gamma(L) |\Sigma_v|^L} \right] \\ %\label{eqn:determinant_distribution} %\\
-  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right] \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
-  \mathbb{R}_{C} = \frac{C_1}{C_2} &\sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
+  \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \right]  ~~and~~
+  \mathbb{R}_{C} = \frac{C_1}{C_2} \sim pdf \left[ \frac{\Gamma(2L-1) x^{L-1}}{\Gamma^2(L-1) (1+x)^{2L}} \right]
 \end{align*}
+%
 These equations match exactly with the following traditional model for multi-look SAR intensity:
@@
 
-\section{Unifying the different discrimination measures proposals for both SAR and POLSAR}
+\section{Unifying different discrimination measures for SAR and POLSAR}
 \label{sec:link_sar_polsar}
 
-Statistical models have always been the foundation for deriving discrimination measures.
-This is true for both fields of SAR and POLSAR.
-For SAR, where the field is more or less settled on the issue,
+Statistical models are the foundation for discrimination measures in both SAR and POLSAR.
+For the mature SAR field, 
   the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \citep{Rignot_1993_TGRS_896}.
-For POLSAR, where the research field is much less mature,
-  the same case should apply, 
+For the less mature POLSAR field the same case should apply, 
   except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \citep{Conradsen_2003_TGRS_4}.
@@
 %  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
-First, similar to the way that the statistical model for SAR intensity has been used to provide the foundation for SAR discrimination measures, e.g. intensity-ratio \citep{Rignot_1993_TGRS_896},
-  the statistical model proposed for POLSAR covariance matrix determinant is to be reviewed as providing the foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
-And second, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
+First, similar to the way that the statistical SAR intensity models have been used as a foundation for SAR discrimination measures, e.g. intensity-ratio \citep{Rignot_1993_TGRS_896},
+  the proposed POLSAR covariance matrix determinant statistical model is to be reviewed as providing a foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
+Secondly, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
 
@@
   the likelihood test statistics presented in \citep{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
-can be expressed as:
-\begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
-  Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
+can be expressed as
+$\ln{Q} \sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)}$,
+\begin{equation}
+  Q \sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
+\end{equation}
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
@@
   the proposed dissimilarity measures are simpler in both concept and computation.
-They, at the same time, are multi-dimensional extensions of the intensity-ratio discrimination measure widely used in SAR.
+They are multi-dimensional extensions of the widely used SAR intensity-ratio discrimination measure.
 
-In short, with the newly gained insight,
-  the approach proposed in this paper provides a new bridge between the two fields of SAR and POLSAR.
-This invites the adaptation of many established SAR data processing techniques towards POLSAR data,
-  where this Section has just described a few examples.
-However, before further discussion ensues, 
-  it is necessary to validate the presented theoretical model with real-life practical data.
+%***IVM: PUT THIS IN THE CONCLUSION INSTEAD
+%In short, with the newly gained insight,
+ % the approach proposed in this paper provides a new bridge between the two fields of SAR and POLSAR.
+%This invites the adaptation of many established SAR data processing techniques towards POLSAR data,
+ % where this Section has just described a few examples.
+%However, before further discussion ensues, 
+%  it is necessary to validate the presented theoretical model with real-life practical data.
 
@@
 
-This section aims to verify the theoretical models given in Eqns.
-\ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
-All of these models require the estimation of two parameters from the captured data.
-These are (i) the dimensional number $d$ and (ii) the look number $L$.
-The dimensional number $d$ is related to the type of (POL)SAR data captured,
-  with $d=1,2,3$ corresponding to the cases of SAR, partial and full polarimetric SAR data, respectively.
-The look-number $L$ can be taken either as nominally stated by the data provider,
-  or it can be estimated using the technique proposed by \citep{Anfinsen_2009_TGRS_3795}.
+We now verify the models in Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
+Each model requires the estimation of two parameters from the captured data; 
+the dimensional number $d$, and  the look number $L$.
+$d$ is related to the type of (POL)SAR data captured,
+  with $d=1,2,3$ corresponding to the cases of SAR, partial and full POLSAR, respectively.
+$L$ is nominally stated by the data provider (or estimated using the technique proposed by \citep{Anfinsen_2009_TGRS_3795}).
 
 To show the robustness of the proposed models, 
-  their validations are also put to test on different types of POLSAR sensors.
-Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
-  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
+  their validations are tested on two different POLSAR sensors: (1) airborne four-look ($L=4$) AIRSAR Flevoland image and (2)
+fine-quad single-look ($L=1$) complex RADARSAT2 image.
 Since the determinant of the covariance matrix is only significant on multi-look data,
-  nine-look processing is first applied on the single-look RADARSAT2 data ($L=9$).
+  nine-look processing is first applied to the single-look data ($L=9$).
 
@@
 
-Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
-  the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
-Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test performed for the stated purpose.
-In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
-The histograms for both the intensity and intensity ratio %the log-distance and contrast
-  are then plotted against the theoretical PDF given above.
+%Since it has been shown in Section \ref{sec:sar_special_case_of_polsar} that the model for the case of $d=1$ matches exactly with the traditional model for SAR intensity,
+ % the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
+Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test where the intensity of single-channel SAR data (HH) for sample homogeneous areas is extracted.
+Histograms are then plotted for both the intensity and intensity ratio %the log-distance and contrast
+against the theoretical PDF.
 %Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
-The plots are obtained having set ENL to an estimated value obtained using the technique presented in \citep{Anfinsen_2009_TGRS_3795}.
+%The plots are obtained having set ENL to an estimated value obtained using the technique presented in \citep{Anfinsen_2009_TGRS_3795}.
 In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
@@
 \begin{figure}[h]
-%\captionsetup{justification=centering}
+\captionsetup{justification=centering}
 \centering
 \begin{tabular}{c}
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in}
+   \centering
 %	\subfloat[AIRSAR (HH) determinant]{
@@
 		 \label{AIRSAR_1D_determinant}
-                \subcaption{AIRSAR (HH) determinant}
+                \subcaption{AIRSAR (HH) \\ determinant}
  \end{minipage}                 
@@
  \hfill
+%	\subfloat[][AIRSAR (HH) \\ determinant ratio]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+                \subcaption{AIRSAR (HH) \\ determinant ratio}
+ \end{minipage}
+ \hfill
+%	\subfloat[][AIRSAR (HH) \\ change ratio]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
+		 \label{AIRSAR_1D_det_ratio}
+                \subcaption{AIRSAR (HH) \\ change ratio}
+ \end{minipage} \\
+
+%	}
+%	} 
 	%\subfloat[][RADARSAT2 (HH) \\ determinant]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
@@
 		 \label{RADARSAT2_1D_determinant}
-                \subcaption{RADARSAT2 (HH) determinant}
- \end{minipage} \\                
-	%} \\
-%	\subfloat[][AIRSAR (HH) \\ determinant ratio]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_det_ratio_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-                \subcaption{AIRSAR (HH) determinant ratio}
+                \subcaption{RADARSAT2 (HH) \\ determinant}
  \end{minipage}
-%	} 
  \hfill
 %	\subfloat[][RADARSAT2 (HH) \\ determinant ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
@@
 		 \label{RADARSAT2_1D_det_ratio}
-                \subcaption{RADARSAT2 (HH) determinant ratio}
- \end{minipage} \\                 
+                 \subcaption{RADARSAT2 (HH) \\ determinant ratio}
+ \end{minipage}                  
+ \hfill
 %	} \\
-%	\subfloat[][AIRSAR (HH) \\ change ratio]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_change_ratio_model_on_AIRSAR_1d.eps} 	
-		 \label{AIRSAR_1D_det_ratio}
-                \subcaption{AIRSAR (HH) change ratio}
- \end{minipage}                 
-%	}
-	\hfill	
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
 %	\subfloat[][RADARSAT2 (HH) \\ change ratio]{
-%
 \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps}{change-ratio}
@@
 %		 \epsffile{../images/verify_change_ratio_model_on_RADARSAT2_1d.eps} 	
-%		 \label{RADARSAT2_1D_det_ratio}
-                \subcaption{RADARSAT2 (HH) change ratio}
+		 \label{RADARSAT2_1D_det_ratio}
+                \subcaption{RADARSAT2 (HH) \\ change ratio}
  \end{minipage}                 
@@
 
-The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
-Similar tests %like the one described for SAR data 
-  are carried out
-  for both types of polarimetric SAR
-  on both AIRSAR and RADARSAT2 datasets.
-The look-number is estimated for each type of data and for each image using the technique described in \citep{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
-The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
-Fig.
-\ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
-It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
+%The remainder of this section now focuses on validating the models for both partial ($d=2$) and full ($d=3$) POLSAR.
+%Similar tests
+%  are carried out
+%  for both types of polarimetric SAR
+%  on both AIRSAR and RADARSAT2 datasets.
+The look-number is estimated for each dataset \citep{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+and the actual distribution plotted against the mode to yield an obvious visual match in  Fig.
+\ref{fig:verify_det_ratio_model_2D} which shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
+%It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
 Evidently the match is good for $d=2$.
@@
 Similarly, Fig.
-\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data and model parameters.
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
@@
 %	\subfloat[][AIRSAR (HH-HV) \\ determinant]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_2d.eps}{determinant}
@@
 	\hfill	
-%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_determinant}
-                \subcaption{RADARSAT2 (HH-HV) determinant}
- \end{minipage}                 \\
 %	} \\
 %	\subfloat[][AIRSAR (HH-HV) \\ determinant ratio]{          
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_2d.eps}{determinant-ratio}
@@
 	\hfill	
-%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
-		 \label{RADARSAT2_2D_det_ratio}
-                \subcaption{RADARSAT2 (HH-HV) determinant ratio}
- \end{minipage}                \\ 
-%	} \\
 %	\subfloat[][AIRSAR (HH-HV) \\ change ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
@@
  \end{minipage}
+ \\
 %	} 
+%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_determinant}
+                \subcaption{RADARSAT2 (HH-HV) determinant}
+ \end{minipage}
+ \hfill
+%	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+                \subcaption{RADARSAT2 (HH-HV) determinant ratio}
+ \end{minipage}
  \hfill
 %	\subfloat[][RADARSAT2 (HH-HV) \\ change ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}{change-ratio}
@@
 %	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
@@
 	\hfill	
-%`	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_3D_determinant}
-                \subcaption{RADARSAT2 (HH-HV-VV) determinant}
- \end{minipage}                 \\
 %	} \\
 %	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
@@
 	\hfill	
-%	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio]{
- \begin{minipage}[b]{2.8in} 
-          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
-		 \label{RADARSAT2_2D_det_ratio}
-                \subcaption{RADARSAT2 (HH-HV-VV) determinant ratio}
- \end{minipage}                \\ 
-%	} \\
 %	\subfloat[][AIRSAR (HH-HV-VV) \\ change ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
@@
 %	}
+ \\
+%`	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_determinant_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_3D_determinant}
+                \subcaption{RADARSAT2 (HH-HV-VV) determinant}
+ \end{minipage}
+ \hfill
+%	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio]{
+ \begin{minipage}[b]{1.8in} 
+   \centering
+          \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
+%		 \epsfxsize=1.5in
+%		 \epsfysize=1.5in
+%		 \epsffile{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps} 	
+		 \label{RADARSAT2_2D_det_ratio}
+                \subcaption{RADARSAT2 (HH-HV-VV) det-ratio}
+ \end{minipage}                
+%	} \\
 	\hfill	
 %	\subfloat[][RADARSAT2 (HH-HV-VV) \\ change ratio]{
- \begin{minipage}[b]{2.8in} 
+ \begin{minipage}[b]{1.8in} 
+   \centering
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
@@
 
-\section{Discussion}
-\label{sec:discussion}
-
-%Let us begin by noting
-To begin, a few theoretical properties of the proposed statistical models are discussed.
-First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
-In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
-Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
-Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
-  the models presented here are invariant to polarization basis transformations.
-
-Second, the models are developed for the POLSAR covariance matrix.
-However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model is also applicable to the coherency matrix.
-
-It should be noted that despite these advantages, the model descriptions are far from complete.
-While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
-  such a reduction is unlikely to be lossless.  
-Ideally %to better understand POLSAR data
-the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \citep{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \citep{Cloude_1997_TGRS_68} or similar.
-
-Nevertheless the proposed models are promising.
-Even though initially developed for partial and monostatic POLSAR data,
-  it was shown to be applicable to traditional SAR data as well.
-Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
-
-Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
-(in a sense this is also why intensity is widely considered representative of the complex SAR data).
-Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
-To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
-Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
-Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
-The important point is that it can provide a scalar comparison of the multi-dimensional data.
-%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
-
-Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
-Similar to the way that different measures of distance can be used to derive POLSAR classifiers \citep{Lee_1999_TGRS}, change detectors \citep{Conradsen_2003_TGRS_4}, edge detectors \citep{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \citep{Le_2010_ACRS} \citep{Le_2011_ACRS},
-new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
-These applications however are not included in this paper, but rather left as a suggestion for future investigations.
+%***IVM: SIMPLY COMMENT OUT THE DISCUSSION, MOVE ANY IMPORTANT ASPECTS TO THE CONCLUSION
+%\section{Discussion}
+%\label{sec:discussion}
+%
+%%Let us begin by noting
+%To begin, a few theoretical properties of the proposed statistical models are discussed.
+%First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+%In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+%Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
+%Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
+%  the models presented here are invariant to polarization basis transformations.
+%
+%Second, the models are developed for the POLSAR covariance matrix.
+%However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+%  the model is also applicable to the coherency matrix.
+%
+%It should be noted that despite these advantages, the model descriptions are far from complete.
+%While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
+%  such a reduction is unlikely to be lossless.  
+%Ideally %to better understand POLSAR data
+%the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \citep{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \citep{Cloude_1997_TGRS_68} or similar.
+%
+%Nevertheless the proposed models are promising.
+%Even though initially developed for partial and monostatic POLSAR data,
+%  it was shown to be applicable to traditional SAR data as well.
+%Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
+%
+%Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+%(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+%Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+%To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+%Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
+%Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+%Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+%The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used. 
+%
+%Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
+%Similar to the way that different measures of distance can be used to derive POLSAR classifiers \citep{Lee_1999_TGRS}, change detectors \citep{Conradsen_2003_TGRS_4}, edge detectors \citep{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \citep{Le_2010_ACRS} \citep{Le_2011_ACRS},
+%new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+%These applications however are not included in this paper, but rather left as a suggestion for future investigations.
 
@@
 This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.%***IVM: Hai pls check this sentence!
-This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full polarimetric SAR data.
+This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full POLSAR data.
 The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
-At the same time, we have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
+We have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
   effectively bringing the existing SAR theories under the umbrella of this new model.
@@
 Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
+It is also invariant to a change of polarization basis.
+While it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
 Its representative power is justified for the following reasons.
-Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Firstly, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
 Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
@@
 %and hence What can be done next?
-  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
-Other possible future work includes
-  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
-  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
+  leaving the test of its validity for datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) for the future.
+Other possible extensions include
+  investigating the applicability of the observables into POLSAR heterogeneous areas,
+  as well as exploring the use of these generic models in conjunction with other target decomposition techniques
     such as the Freeman-Durden decomposition \citep{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \citep{Cloude_1997_TGRS_68}.

### 2013-11-10 Remote_Sensing_Letter/paper.tex
ready for final round of edition

@@
-\documentclass[]{tRSL2e}
+\documentclass[printer]{tRSL2e}
 
@@
 \title{
-  Scalar and Representative Observables for Polarimetric SAR Data
+  Scalar and Representative Observables, and Their Associated Statistial Model, for Polarimetric SAR Data
 }
@@
 %Problem statement  
-This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
-  from which statistically consistent discrimination measures can be derived.
+This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
+  which includes several statistically consistent discrimination measures. %can be derived.
 %What actually were done? and As the result, what is learned?
@@
   to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
-  which is specifically applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
+  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
 As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
@@
 %What are the larger implications of the findings presented in this paper?
-Consequently, the main beneficial implication of the proposed approach is that
-  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
-  which simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
+Consequently, the main beneficial implications are that %of the proposed approach is that
+  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
+  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
 %  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
@@
 %What is the situation, the background context of your research? the BIG problem!
-Relentless growth in computing power has allowed once computationally-demanding Synthetic Aperture Radar (SAR)
-to become a feasible and preferred technique for earth observation.
+Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
+to become now a feasible and preferred technique for earth observation.
 Basic SAR has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
-This exploits the natural polarization property of Electro-Magnetic (EM) waves,
+POLSAR exploits the natural polarization property of Electro-Magnetic (EM) waves,
   encoded in multiple channels, compared to traditional one-channel SAR.
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-POLSAR data, like SAR, is stochastic but is also multi-dimensional, making it even harder to interpret.
+POLSAR data, like SAR, is stochastic.
+Moreover it is also multi-dimensional, making it even harder to interpret.
 It is therefore important to establish a simple and intuitive understanding of the data.
@@
 %  which apparently is multidimensional, complex and thus not very intuitive.
-A few scalar POLSAR observables with accompanying statistical models have been proposal \citep{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
+A few scalar POLSAR observables with accompanying statistical models have been proposed \citep{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
   but none is able to provide meaningful scalar discrimination measures.
@@
   which severely limits their applicability in practical data processing applications.
-Alternatively, a few POLSAR discrimination measures have been proposed,
-  but all based on likelihood ratio statistics.
-This should ideally be based on an exact and consistent distribution
-  but so far only asymptotic distributions have been demonstrated.
+Alternatively, a few POLSAR discrimination measures have been proposed \citep{Lee_1994_IJRS_2299, Anfinsen_2007_ESA_POLINSAR, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454, Conradsen_2003_TGRS_4},
+  but all are based on likelihood ratio statistics.
+These should ideally be based on an exact and consistent distribution
+  but so far only asymptotic distributions have been demonstrated \citep{Conradsen_2003_TGRS_4}.
 
 %Research Objective: Give your precise problem statement  
-This article presents a scalar and representative observable, and its associated generic statistical model, to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.
+This paper presents scalar and representative observables,
+  and one associated generic statistical model,
+  that describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.
 %Now State your approach  
@@
 %Prof Vuns: comment: the article provides the result, not the journey!
-POLSAR data have been statistically modelled as following the complex Wishart distribution.
-Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
-This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
+%Specifically POLSAR data have been statistically modelled as following the complex Wishart distribution.
+The development is based on the common assumption that POLSAR data follows the complex Wishart distribution.  
+Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+This model is then used to derive several scalar and consistent statistical distribution suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
 %
@@
 %The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
-We will also show that %It is also shown that
-  the specific one dimensional (1-D) versions of the proposed  models 
-  match %perfectly with 
+This paper also shows that %It is also shown that
+  the specific one dimensional (1-D) version of the proposed  model 
+  matches %perfectly with 
   the traditional statistical model used for SAR intensity.
-This effectively incorporates SAR theory under the umbrella of the proposed scalar approach for multi dimensional POLSAR.
-The different discrimination proposals for SAR and POLSAR are reviewed in light of this and the  proposed in this paper is shown to provide a strong, unifying and consistent foundation.
+This effectively incorporates the existing SAR theory under the umbrella of the proposed scalar approach for multi dimensional POLSAR.
+The different discrimination proposals for SAR and POLSAR are reviewed in light of this and the  proposal in this paper is shown to provide a strong, unifying and consistent foundation.
 % relating them all together.
-The applicability of these theoretical models will be illustrated by experiments where the specific 1, 2 and 3-D versions of the proposed models are validated against practical data. 
+The applicability of these theoretical models will be illustrated by experiments where the specific 1, 2 and 3-D versions of the proposed models are validated against real-life captured data. 
 %Furthermore, the approach proposed in this paper
@@
 %**IVM save space!
-%\subsection{Scalar Observables for POLSAR Data and their Statistical Models}
-%\label{sec:lit_models}
+\subsection{Scalar Observables for POLSAR Data} % and their Statistical Models}
+\label{sec:lit_models}
 
@@
 \citet{Alberga_2008_IJRS_4129} evaluated the performance of different scalar POLSAR observables for classification.
-While many were presented, their corresponding statistical models and classifiers were not available.
-Furthermore, the paper concluded that it is impossible to identify a single best representation.
-Although, to be fair, the observables were identified for describing a decomposed portion of the complex POLSAR data,
+While many observables were presented, their corresponding statistical models and classifiers were not available.
+Furthermore, the paper concluded that it is impossible to identify a single best representation,
+  although, to be fair, the observables were identified for describing a decomposed portion of the complex POLSAR data,
   rather than a unified representation.
-%
+
 Using a different approach, given that the joint distribution for POLSAR is known to be the multi-variate complex Wishart,
@@
 %This becomes an alternative approach used in the study of POLSAR data.
-However, this is non-trivial -- so far, only a handful of such models have been proposed, including:
+However, this is non-trivial -- and so far, only a handful of such models have been proposed, including:
   \begin{enumerate}
@@
 Although useful, these have not been shown to result in statistically consistent discrimination measures or
- be representative of the complex POLSAR data.
+ to be representative of the complex POLSAR data.
 %While these models undoubtedly help to further our understandings of the POLSAR data,
@@
 %and $\mathbb{R},\mathbb{I}$ denote the real and imaginary parts respectively.
-Instead, the Wishart distance is probably most common, as part of the well-known Wishart classifier \citep{Lee_1999_TGRS}, defined \citep{Lee_1994_IJRS_2299} as:
+Instead, the Wishart distance is better known, as part of the Wishart classifier \citep{Lee_1999_TGRS}, defined as \citep{Lee_1994_IJRS_2299}:
 $d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})$
@@
   \begin{align}
-  d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
+  d(C_x,C_y) &= 2 \ln |(C_x+C_y)/2| - \ln |C_x| - \ln |C_y| - 2d\ln2
   \end{align}
@@
 \begin{equation}
-  d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
+  d(C_x,C_y) = (L_x + L_y) \ln|(L_xC_x+L_yC_y)/(L_x+L_y)| - L_x \ln|C_x| - L_y\ln|C_y|
 \end{equation}
 
-Closer examination of these reveal that most are related:
-The Bhattacharyya and Bartlett distances are easily shown to be related.
-At the same time, Barlett can be considered a special case of the Wishart Statistical Test distance,
+Closer examinations reveal that most are related:
+The most obvious are the Bhattacharyya and Bartlett distances. % are easily shown to be related.
+At the same time, the Barlett distance can be considered a special case of the Wishart Statistical Test distance,
   when the two data sets have the same number of looks, i.e. $L_x=L_y$.
 The close relation among  measures may be due to the fact that
-  all of their publications refer to, and are based on, the same statistical model in \citep{Conradsen_2003_TGRS_4}.
-In \citep{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
+  all of their publications are based on the same statistical model in \citet{Conradsen_2003_TGRS_4}.
+In \citet{Conradsen_2003_TGRS_4}, to determine if the two scaled multi-look POLSAR covariance matrixes $Z_x$ and $Z_y$,
   which have $L_x$ and $L_y$ as the corresponding number of looks,
@@
 i.e. a distribution is derived for the dissimilarity measure.
-However, \citet{Conradsen_2003_TGRS_4} only use an asymptotic distribution.
+However, \citet{Conradsen_2003_TGRS_4} only used an asymptotic distribution.
 By contrast, this paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
@@
 %
-The approach taken in this paper differs by applying a homoskedastic log transformation  on a less-than-well-known relationship.
+The approach taken in this paper differs by making use of applying a less-than-well-known relationship.
 \citet{Goodman_1963_AMS_178} found
@@
 %We will now use 
-We use this to develop a generic scalar statistical model. %log-transformed measures of distance.
+This is used to develop a generic scalar statistical model. %log-transformed measures of distance.
 From Eqn. \ref{eqn:prod_chi_squared_rv} we have:
@@
   their product and summation also have fixed summary statistics.
-Specifically:
-\vspace{-2mm}
-{
-\begin{align*}
-  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
-  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
-%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
-%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{align*}
-}
-
-Combining these results with Eqn. \ref{eqn:determinant_distribution} %and \ref{eqn:log_determinant_distribution}
-  , we have:
+Specifically
+%\vspace{-2mm}
+%{
+%\begin{align*}
+%  avg \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
+%  var \left[ \prod^{d-1}_{i=0} \chi(2L-2i) \right] &= \prod^{d-1}_{i=0} 4(L-i)(L-i+1) - \prod^{d-1}_{i=0} 4(L-i)^2, %\\
+%%  avg \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= d \cdot \ln{2} + \sum^{d-1}_{i=0} \psi^0(L-i), \\
+%%  var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &= \sum^{d-1}_{i=0} \psi^1(L-i)
+%\end{align*}
+%}
+%Combining these results with
+Eqn. \ref{eqn:determinant_distribution} %and \ref{eqn:log_determinant_distribution}
+  , gives us:
 \vspace{-2mm}  
@@
 \begin{align}
-  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i)\\
+  avg \left[ |C_v| \right]  &= \frac{|\Sigma_v|}{L^d} \prod^{d-1}_{i=0} (L-i) \\
   var \left[ |C_v| \right]  &=   {\frac{|\Sigma_v|^2}{L^{2d}}{ \left[ \prod^{d-1}_{i=0} (L-i)(L-i+1) - \prod^{d-1}_{i=0} (L-i)^2 \right] }} 
@@
 
-For a real world captured image, while parameters $d$ and $L$ do not change for the whole image,
+For a real life captured image, while parameters $d$ and $L$ do not change for the whole image,
   the underlying $\Sigma_v$ is likely to differ from one region to the next.
@@
 %Assuming, on the one hand,
-If the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+If the true value of the underlying signal $\Sigma_v$ is \textit{known a priori},
 then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
@@
 %On the other hand, under a looser assumption %From another perspective
-For POLSAR data from a homogeneous area, but when the true value of $\Sigma_v$ is \textit{unknown},
- then a random variable called the change-ratio $\mathbb{R}_{C}$)  is defined, $ \mathbb{R}_{C} = {|C_1|}/{|C_2|}$ where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
+For POLSAR data from a homogeneous area, but the true value of $\Sigma_v$ is \textit{unknown},
+ then a random variable, called the change-ratio $\mathbb{R}_{C}$), is defined as: $ \mathbb{R}_{C} = {|C_1|}/{|C_2|}$ where $C_1$ and $C_2$ are samples of the covariance matrix determinant in an assumed homogeneous area.
 %
@@
 %
-Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
+Since each elementary component follows fixed distributions (i.e. $\chi(2L)$),
 this variable naturally also follows fixed distributions.
@@
 physically equivalent to  collapsing the multi-dimensional POLSAR dataset  into single dimensional SAR data.
-Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while determinant $|C_v|$ becomes the scalar variance.
-As variance is equal to intensity $I$ in SAR, our result is consistent with previous results for SAR intensity.
-Thus the proposed generic model for POLSAR, collapsed into 1-D will be shown to apply also to traditional SAR intensity.% as a natural case of the unified model.
+Mathematically, the sample covariance matrix $C_v$ is reduced to the sample variance while its determinant $|C_v|$ becomes the scalar variance.
+As variance is equal to intensity $I$ in SAR,
+  this section shows that our proposed models are consistent with the traditional models for SAR intensity.
+%Thus the proposed generic model for POLSAR, collapsed into 1-D will be shown to apply also to traditional SAR intensity.% as a natural case of the unified model.
 %  as well as reminding us that SAR is a special case of POLSAR.
@@
 Statistical models are the foundation for discrimination measures in both SAR and POLSAR.
-For the mature SAR field, 
+For the more matured SAR field, 
   the statistical model for SAR intensity has been used to derive the most widely used intensity-ratio discrimination measure \citep{Rignot_1993_TGRS_896}.
-For the less mature POLSAR field the same case should apply, 
+For the less matured POLSAR field the same case should apply, 
   except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \citep{Conradsen_2003_TGRS_4}.
 
-With the insight gained from section \ref{sec:sar_special_case_of_polsar}, this section presents a few results.
+With the insight gained from section \ref{sec:sar_special_case_of_polsar}, this section presents a few new results.
 %  it should be clear that the proposed model can also be used to derive discrimination measures for POLSAR.
 First, similar to the way that the statistical SAR intensity models have been used as a foundation for SAR discrimination measures, e.g. intensity-ratio \citep{Rignot_1993_TGRS_896},
-  the proposed POLSAR covariance matrix determinant statistical model is to be reviewed as providing a foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
+  the proposed statistical model for POLSAR covariance matrix determinant can also be viewed as providing a foundation for POLSAR discrimination measures, i.e. the likelihood test statistics.
 Secondly, new discrimination measures for POLSAR may be derived by learning from the existing SAR discrimination measures.
@@
 As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
-  the likelihood test statistics presented in \citep{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+  the likelihood test statistics presented in \citet{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
 can be expressed as
 $\ln{Q} \sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)}$,
-\begin{equation}
-  Q \sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{equation}
+ and
+%\begin{equation}
+  $Q \sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}} $
+%\end{equation}
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
 This, in essence, derives an exact statistical distribution for the likelihood test statistics,
-  as opposed to the asymptotic distribution derived in \citep{{Conradsen_2003_TGRS_4}}.
+  as opposed to the asymptotic distribution derived in \citet{{Conradsen_2003_TGRS_4}}.
 
@@
   several discrimination measures for the common case of $L_x=L_y$ are further proposed.
-They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}.
+They are the determinant-ratio and the change-ratio presented in Section \ref{sec:theoretical_model}
 Compared to existing discrimination measures for POLSAR reviewed in Section \ref{sec:lit_review}, 
   the proposed dissimilarity measures are simpler in both concept and computation.
-They are multi-dimensional extensions of the widely used SAR intensity-ratio discrimination measure.
+They are hence multi-dimensional extensions of the widely used SAR intensity-ratio discrimination measure.
 
@@
 
-\section{Validating the proposed models against real-life data}
+\section{Model Validation}
 \label{sec:polsar_models_validation}
 
-We now verify the models in Eqns. \ref{eqn:determinant_distribution}, \ref{eqn:determinant_ratio_distribution} and \ref{eqn:change_ratio_distribution} against practical data.
-Each model requires the estimation of two parameters from the captured data; 
+The models in Eqns. \ref{eqn:determinant_distribution} and \ref{eqn:change_ratio_distribution} are now validated against real-life captured data.
+Each model requires the estimation of two parameters from the data; 
 the dimensional number $d$, and  the look number $L$.
@@
   with $d=1,2,3$ corresponding to the cases of SAR, partial and full POLSAR, respectively.
-$L$ is nominally stated by the data provider (or estimated using the technique proposed by \citep{Anfinsen_2009_TGRS_3795}).
+$L$ is normally stated by the data provider,
+  but in this section it is estimated using the technique proposed by \citet{Anfinsen_2009_TGRS_3795}.
 
 To show the robustness of the proposed models, 
-  their validations are tested on two different POLSAR sensors: (1) airborne four-look ($L=4$) AIRSAR Flevoland image and (2)
+  their validations are carried out on two different POLSAR sensors: (1) airborne four-look ($L=4$) AIRSAR Flevoland image and (2)
 fine-quad single-look ($L=1$) complex RADARSAT2 image.
@@
  % the validation of the proposed $d=1$ model is quite straightforward. %only a simple validation is presented for this case.  
-Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test where the intensity of single-channel SAR data (HH) for sample homogeneous areas is extracted.
-Histograms are then plotted for both the intensity and intensity ratio %the log-distance and contrast
-against the theoretical PDF.
+Fig. \ref{fig:verify_POLSAR_model_1D} presents the results of a test where the intensity of single-channel SAR data (HH) for sample homogeneous areas are extracted.
+Histograms are then plotted for all of the proposed observables %both the intensity and intensity ratio %the log-distance and contrast
+against their theoretical models.
 %Also presented are the plots of the same test applied on a homogeneous patch inside the nine-look processed RADARSAT2 image.
 %The plots are obtained having set ENL to an estimated value obtained using the technique presented in \citep{Anfinsen_2009_TGRS_3795}.
-In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
+In all cases, the good visual match between the actual data and the respective model apparently validates the proposed model. %providing us a simple validation of the result.
 
@@
 The look-number is estimated for each dataset \citep{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
-and the actual distribution plotted against the mode to yield an obvious visual match in  Fig.
+And the actual distribution is plotted against the model yielding an obvious visual match in  Fig.
 \ref{fig:verify_det_ratio_model_2D} which shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
@@
 Similarly, Fig.
-\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data and model parameters.
+\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data and model parameter estimation.
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
@@
 This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.%***IVM: Hai pls check this sentence!
-This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full POLSAR data.
-The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
+The model has been validated for specific $d=2$ and $d=3$ cases using real-life partial and full POLSAR data.
+The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
 We have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
@@
 %What are the results? What are their advantages over others' results?
-The main emphasis of this paper is the proposal to consider the POLSAR covariance matrix determinant as a scalar and representative observable for the multi-dimensional POLSAR data.
+The main emphasis of this paper is to consider the POLSAR covariance matrix determinant as a scalar and representative observable for the multi-dimensional POLSAR data.
 Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
-It is also invariant to a change of polarization basis.
-While it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+%While it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
 Its representative power is justified for the following reasons.
@@
 Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
-Finally, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
+Thirdly, this observable also leads to the establishment of new discrimination measures for POLSAR data, which should increase the usability of this proposal.
+Finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to a change of polarization basis.
+%  due to the relation between the determinant and the eigen-values
 
 %What are their benefit?
-There are several beneficial implications of the proposed approach presented in this paper.
+%There are several beneficial implications of the proposed approach presented in this paper.
 Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
-Hence many techniques applicable to SAR can not be directly translated to POLSAR.
+Hence many techniques applicable to SAR cannot be directly extended to POLSAR.
+There lies the different beneficial implications of the proposed approach presented in this paper.
 Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,

### 2013-11-11 Remote_Sensing_Letter/paper.tex
updated prof Vun's changes

@@
 %Problem statement
-This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
-  which includes several statistically consistent discrimination measures. %can be derived.
+This paper proposes scalar and representative observables,
+  including several statistically consistent discrimination measure
+  that are vitally important in the processing of multi-dimensional POLSAR data.
+%This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
+%  which includes several statistically consistent discrimination measures. %can be derived.
 %What actually were done? and As the result, what is learned?
@@
 Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
-This model is then used to derive several scalar and consistent statistical distribution suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
+This model is then used to derive several scalar and consistent statistical distributions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
 %

### 2013-11-14 Remote_Sensing_Letter/paper.tex
ready for submission

@@
 %Problem statement
-This paper proposes scalar and representative observables,
-  including several statistically consistent discrimination measure
-  that are vitally important in the processing of multi-dimensional POLSAR data.
+This paper proposes novel scalar and representative observables,
+  including several statistically consistent discrimination measures,
+  that are particularly useful in the interpretation and processing of multi-dimensional POLSAR data.
 %This paper proposes scalar and representative observables for multi-dimensional POLSAR data,
@@
   to derive a scalar and generic statistical model for multi-dimensional POLSAR data,
-  which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
+  which is shown applicable to both two and three dimensional versions of partial and full monostatic POLSAR data.
 As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
@@
 %What are the larger implications of the findings presented in this paper?
-Consequently, the main beneficial implications are that %of the proposed approach is that
+Consequently, the main beneficial implications of the proposed approach are that
   it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
@@
 For the less matured POLSAR field the same case should apply, 
-  except that so far only asymptotic distributions have been derived for the most common foundation, i.e. the likelihood test statistics \citep{Conradsen_2003_TGRS_4}.
+  except that so far only asymptotic distributions have been derived for the most common foundation: likelihood test statistics \citep{Conradsen_2003_TGRS_4}.
 
@@
   but in this section it is estimated using the technique proposed by \citet{Anfinsen_2009_TGRS_3795}.
-
 To show the robustness of the proposed models, 

### 2014-01-25 paper_dev/article.tex
changed formatting as Nick requested
add some quantitative measure for histogram comparisons,   also bring back the application inside discussion. May need further writing in introduction / conclusion.

@@
 \usepackage{xcolor}
-\definecolor{plot}{rgb}{1,0.652,0.1705}
+\definecolor{plot}{rgb}{0,0.0964,1.00}
 
@@
 \begin{tabular}{c}
-	\subfloat[][AIRSAR (HH) \\ determinant]{
+	\subfloat[][AIRSAR (HH) \\ determinant (p-value=0.9322)]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_1d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH) \\ determinant]{
+	\subfloat[][RADARSAT2 (HH) \\ determinant (p-value=0.9994)]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_1d.eps}{determinant}
@@
 	} \\
-	\subfloat[][AIRSAR (HH) \\ determinant ratio]{
+	\subfloat[][AIRSAR (HH) \\ determinant ratio (p-value=0.9322)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_1d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH) \\ determinant ratio]{
+	\subfloat[][RADARSAT2 (HH) \\ determinant ratio (p-value=0.9994)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_1d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[][AIRSAR (HH) \\ change ratio]{
+	\subfloat[][AIRSAR (HH) \\ change ratio (p-value=0.8425)]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_1d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH) \\ change ratio]{
+	\subfloat[][RADARSAT2 (HH) \\ change ratio (p-value=0.9923)]{
 
@@
 \caption{\scriptsize{The specific d=1 models are validated for both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
+with p-value being the significant level of the Kolmogorov–Smirnov goodness-of-fit test between the two histograms}}
 \label{fig:verify_POLSAR_model_1D}
@@
 
-Similarly, Fig.
-\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
+This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
+While a good p-value does not mean automatic acceptance of the model,
+  consistently high p-value readings suggest that the proposed model should not be ignored.
+
 \begin{figure}[h]
@@
 \begin{tabular}{c}
-	\subfloat[][AIRSAR (HH-HV) \\ determinant]{
+	\subfloat[][AIRSAR (HH-HV) \\ determinant (p-value=0.9998)]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_2d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV) \\ determinant]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ determinant (p-value=0.8899)]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_2d.eps}{determinant}
@@
 	} \\
-	\subfloat[][AIRSAR (HH-HV) \\ determinant ratio]{
+	\subfloat[][AIRSAR (HH-HV) \\ determinant ratio (p-value=0.9998)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_2d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ determinant ratio (p-value=0.8899)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_2d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[][AIRSAR (HH-HV) \\ change ratio]{
+	\subfloat[][AIRSAR (HH-HV) \\ change ratio (p-value=0.9182)]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_2d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV) \\ change ratio]{
+	\subfloat[][RADARSAT2 (HH-HV) \\ change ratio (p-value=0.9824)]{
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_2d.eps}{change-ratio}
@@
 \begin{tabular}{c}
-	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant (p-value=0.8905)]{
           \plotWithLegend{../images/verify_determinant_model_on_AIRSAR_3d.eps}{determinant}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant (p-value=0.8896)]{
           \plotWithLegend{../images/verify_determinant_model_on_RADARSAT2_3d.eps}{determinant}
@@
 	} \\
-	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant ratio]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ determinant ratio (p-value=0.8905)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_AIRSAR_3d.eps}{determinant-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ determinant ratio (p-value=0.8896)]{
           \plotWithLegend{../images/verify_det_ratio_model_on_RADARSAT2_3d.eps}{determinant-ratio}
@@
 	} \\
-	\subfloat[][AIRSAR (HH-HV-VV) \\ change ratio]{
+	\subfloat[][AIRSAR (HH-HV-VV) \\ change ratio (p-value=0.9254)]{
           \plotWithLegend{../images/verify_change_ratio_model_on_AIRSAR_3d.eps}{change-ratio}
@@
 	\hfill	
-	\subfloat[][RADARSAT2 (HH-HV-VV) \\ change ratio]{
+	\subfloat[][RADARSAT2 (HH-HV-VV) \\ change ratio (p-value=0.8883)]{
           \plotWithLegend{../images/verify_change_ratio_model_on_RADARSAT2_3d.eps}{change-ratio}
@@
 %
-%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-%  this technique can be equally applied to evaluate POLSAR speckle filters.
-%In fact better results can be achieved.
-%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-%  which is linear and additive in nature.
-%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-%
-%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
-%  and the two POLSAR speckle filters are then applied to the patch.
-%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-%
-%%ifdef FINAL
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%%ifdef REVIEW
-%\begin{figure}[h!]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%
-%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-%  the distortion impact of the filter can also be made visible by the residual image.
-%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-%in the additive log-determinant image of the filtered output, 
-%  such an observation can be made relatively easier by inspecting the residual image.
-%  
-%There are many similar SAR data processing technique that may be adaptable to POLSAR.
-%Examples in the same topic of evaluating speckle filters include
-%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+  this technique can be equally applied to evaluate POLSAR speckle filters.
+In fact better results can be achieved.
+In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+  which is linear and additive in nature.
+Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+
+To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters are then applied to the patch.
+\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  the distortion impact of the filter can also be made visible by the residual image.
+In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such an observation can be made relatively easier by inspecting the residual image.
+
+There are many similar SAR data processing technique that may be adaptable to POLSAR.
+Examples in the same topic of evaluating speckle filters include
+  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 

### 2014-01-25 paper_dev/article_pp.tex
changed formatting as Nick requested
add some quantitative measure for histogram comparisons,   also bring back the application inside discussion. May need further writing in introduction / conclusion.

@@
 
-Similarly, Fig.
-\ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
+Similarly, Fig. \ref{fig:verify_det_ratio_model_3D} explores the $d=3$ case for the same data, same model parameters.
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
+This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
+While a good p-value does not mean automatic acceptance of the model,
+  consistently high p-value readings suggest that the proposed model should not be ignored.
+
 %ifdef FINAL
@@
 %
-%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
-%  this technique can be equally applied to evaluate POLSAR speckle filters.
-%In fact better results can be achieved.
-%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-%  which is linear and additive in nature.
-%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-%
-%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
-%  and the two POLSAR speckle filters are then applied to the patch.
-%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
-%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
-%
-%%ifdef FINAL
-%\begin{figure}[h]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=1.5in
-%		 \epsfysize=1.5in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%%ifdef REVIEW
-%\begin{figure}[h!]
-%\centering
-%\begin{tabular}{c}
-%	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
-%		 \label{multi_look_contrast}
-%	} \\
-%	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
-%		 \label{multi_look_dispersion}
-%	} 
-%	\hfill	
-%	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
-%		 \epsfxsize=3in
-%		 \epsfysize=3in
-%		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
-%		 \label{multi_look_contrast}
-%	} 
-%\end{tabular}
-%\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
-%\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
-%\end{figure}
-%%endif
-%
-%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-%  the distortion impact of the filter can also be made visible by the residual image.
-%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-%in the additive log-determinant image of the filtered output, 
-%  such an observation can be made relatively easier by inspecting the residual image.
-%  
-%There are many similar SAR data processing technique that may be adaptable to POLSAR.
-%Examples in the same topic of evaluating speckle filters include
-%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+  this technique can be equally applied to evaluate POLSAR speckle filters.
+In fact better results can be achieved.
+In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+  which is linear and additive in nature.
+Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+
+To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+  and the two POLSAR speckle filters are then applied to the patch.
+\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+
+%ifdef FINAL
+\begin{figure}[h]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=1.5in
+		 \epsfysize=1.5in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+%ifdef REVIEW
+\begin{figure}[h!]
+\centering
+\begin{tabular}{c}
+	\subfloat[Log-determinant Image of boxcar 3$\times$3 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.filtered.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Log-determinant Image of boxcar 5$\times$5 speckle filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.filtered.eps} 	
+		 \label{multi_look_contrast}
+	} \\
+	\subfloat[Image of Log-determinant Residual for 3$\times$3 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_3.residual.eps} 	
+		 \label{multi_look_dispersion}
+	} 
+	\hfill	
+	\subfloat[Image of Log-determinant Residual for 5$\times$5 filter]{
+		 \epsfxsize=3in
+		 \epsfysize=3in
+		 \epsffile{../images/visual_eval_part_pol_boxcar_5.residual.eps} 	
+		 \label{multi_look_contrast}
+	} 
+\end{tabular}
+\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSAR Flevoland part-pol data (HH-HV).}
+\label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
+\end{figure}
+%endif
+
+Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+  the distortion impact of the filter can also be made visible by the residual image.
+In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+in the additive log-determinant image of the filtered output, 
+  such an observation can be made relatively easier by inspecting the residual image.
+
+There are many similar SAR data processing technique that may be adaptable to POLSAR.
+Examples in the same topic of evaluating speckle filters include
+  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
 

### 2014-02-11 paper_dev/article.tex
added reference to KS test

@@
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
-This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
+This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov–Smirnov goodness-of-fit test.
 While a good p-value does not mean automatic acceptance of the model,
-  consistently high p-value readings suggest that the proposed model should not be ignored.
+  consistently high p-value readings suggest that the proposed model has excellent confidence-limit \cite{Kolmogoroff_1941_AMS_461}.
 

### 2014-02-19 answer_thesis_examiner/answer_document.tex
answer document added

\documentclass{article}

\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}

\title{Reply To Examiners}
\date{\today}
\author{Thanh-Hai Le}

\begin{document}
\maketitle

\section*{Reply to Examiner No. 1}

Some answer

\section*{Reply to Examiner No. 2}

Some answer

\section*{Reply to Examiner No. 3}

Some answer

\end{document}

### 2014-02-27 paper_dev/article.tex
first section updated

--- 2014-01-25 paper_dev/article.tex
@@
 \title{
-  Scalar and Representative Observables for Polarimetric SAR Data
+  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data
 }
@@
 \thanks{Thanh-Hai~Le and Chan-Hua~Vun are with School of Computer Engineering, 
-Nanyang Technological University, Singapore. Ian~McLoughlin is with School of Information Science and Technology,
+Nanyang Technological University, Singapore. Ian~McLoughlin is with the School of Information Science and Technology,
 University of Science and Technology of China.
@@
 %	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
-\thanks{Manuscript received ?, 2013; revised ?.}}
-
-\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2013}%
-{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables for Polarimetric SAR Data}
+\thanks{Manuscript received ?, 2014; revised ?.}}
+
+\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2014}%
+{ Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data}
 
@@
 %Problem statement  
-This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
-  from which statistically consistent discrimination measures can be derived.
+This paper proposes novel scalar and representative observables, including several statistically consistent discrimination measures, which should be useful in the interpretation and processing of multi-dimensional POLSAR data.
+% This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
+%  from which statistically consistent discrimination measures can be derived.
 %What actually were done? and As the result, what is learned?
@@
 %What are the larger implications of the findings presented in this paper?
-Consequently, the main beneficial implication of the proposed approach is that
-  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures
-  which simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
+Consequently, the main beneficial implications of the proposed approach are that
+  it provides a consistent theory unifying the currently disconnected proposals for SAR and POLSAR discrimination measures,
+  and it simplifies the adaptation of existing SAR data processing techniques for POLSAR data.
 %  it enables the adaptation of many existing SAR data processing techniques for POLSAR data,
@@
 %What is the situation, the background context of your research? the BIG problem!
-During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
-technology to become a feasible and preferred technique for earth observation applications.
-SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
-POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
-  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
+Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR) to become now a feasible and preferred technique for earth observation.
+The basic SAR technology has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
+POLSAR exploits the natural polarization property of Electro-Magnetic (EM) waves,
+   encoded in multiple channels, compared to traditional one-channel SAR.
+%During the past decades, exponential growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR)
+%technology to become a feasible and preferred technique for earth observation applications.
+%SAR technology has since been extended in a few directions, one of which is polarimetric SAR (POLSAR).
+%POLSAR extends SAR by exploiting the natural polarization property of Electro-Magnetic (EM) waves,
+%  leading to the availability of multi-channel POLSAR data, compared to traditional one-channel SAR data.
 
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-Like SAR data, POLSAR data is stochastic.
-Moreover, it is multi-dimensional, making it even harder to interpret.
-Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
+POLSAR data, like SAR, is stochastic.
+Moreover it is also multi-dimensional, making it even harder to interpret.
+It is therefore necessary to establish a simple and intuitive understanding of the data.
+%Like SAR data, POLSAR data is stochastic.
+%Moreover, it is multi-dimensional, making it even harder to interpret.
+%Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
 Statistical models are undoubtedly crucial in understanding its stochastic nature.
-While several %multidimensional 
-models have been proposed to describe POLSAR data, they
-  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
+While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional nature of the data.
+%  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
 Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
-  which should be based on statistically consistent models for scalar and representative observables of the multidimensional data.
-It is thus important to establish a scalar and representative observable for this multi-dimensional POLSAR data.
+  which should be based on statistically consistent (or signal-independent) models. %for scalar and representative observables of the multidimensional data.
+It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.
 
@@
 %  which apparently is multidimensional, complex and thus not very intuitive.
-There has been a few scalar observables with accompanying statistical models proposal for POLSAR \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
-  but none of them is able to provide meaningful scalar discrimination measures.
+%There has been a few scalar observables with accompanying statistical models proposal for POLSAR
+A few scalar POLSAR observables with accompanying statistical models have been proposed \cite{Conradsen_2003_TGRS_4, Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Lopez-Martinez_2003_TGRS_2232, Erten_2012_Sensors_2766},
+  but none of them is able to provide widely-accepted scalar discrimination measures.
 %  but none of them has led to scalar discrimination measures proposal.
-As such no observable has been widely accepted as being highly representative of this multi-dimensional data,
+As such no observable can be considered as being highly representative of this multi-dimensional data,
   which severely limits their applicability in practical data processing applications.
-From an alternative approach, a few POLSAR discrimination measures have been proposed,
-  but all are based on the likelihood ratio statistics.
-This statistical test should be based on an exact and consistent statistical distribution
-  but so far has only shown to be based on an asymptotic distribution.
+Alternatively, a few popular POLSAR discrimination measures are reviewed \cite{Lee_1994_IJRS_2299, Anfinsen_2007_ESA_POLINSAR, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454},
+%From an alternative approach, a few POLSAR discrimination measures have been proposed,
+  but all of them are shown to be based on the likelihood ratio statistics.
+This statistical test should ideally be based on an exact and consistent distribution
+   but so far only asymptotic distributions have been demonstrated \cite{Conradsen_2003_TGRS_4}.  
+%This statistical test should be based on an exact and consistent statistical distribution
+%  but so far has only shown to be based on an asymptotic distribution.
 
 %Research Objective: Give your precise problem statement
-This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
+This paper presents scalar and representative observables,
+   and one associated generic statistical model,
+   that describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.   
+%This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
 %Now State your approach
+The development is based on the common assumption that POLSAR data follows the complex Wishart distribution.  
+Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+This model is then used to derive several scalar and consistent statistical distributions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
 %This study started off with the observation that the determinant of the covariance matrix is widely used in POLSAR discrimination measures.
@@
 %Prof Vuns: comment: the article provides the result, not the journey!
-POLSAR data have been statistically modelled as following the complex Wishart distribution.
-Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
-This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
+%POLSAR data have been statistically modelled as following the complex Wishart distribution.
+%Consequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+%This model is then used to derive several scalar and consistent statistical descriptions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR data.
 %
@@
 
+This paper also shows that %It is also shown that
+   the specific one dimensional (1-D) version of the proposed  model 
+   matches %perfectly with 
+   the traditional statistical model used for SAR intensity.
+This effectively incorporates the existing SAR theory under the umbrella of the proposed scalar approach for multi dimensional POLSAR.
+The different discrimination proposals for SAR and POLSAR are reviewed in light of this and the  proposal in this paper is shown to provide a strong, unifying and consistent foundation.
+% relating them all together.
+The applicability of these theoretical models will be illustrated by experiments where the specific 1, 2 and 3-D versions of the proposed models are validated against real-life captured data.    
+The other beneficial implication of the proposed approach will also be demonstrated,
+  where the proposed theore is applied, as an example, to evaluate POLSAR speckle filters.
+
 %The specific two and three dimensional models are then validated against both partial and full polarimetric SAR data.
-Interestingly the paper also shows that %It is also shown that
-  the specific one dimensional versions of the proposed  models 
-  match perfectly with the traditional statistical model used for SAR intensity.
-This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
-With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
-The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
+%Interestingly the paper also shows that %It is also shown that
+%  the specific one dimensional versions of the proposed  models 
+%  match perfectly with the traditional statistical model used for SAR intensity.
+%This effectively incorporates the common one dimensional SAR theory under the unbrella of the proposed scalar approach for multi dimensional POLSAR.
+%With this new insight the different discrimination proposals for SAR and POLSAR are reviewed and it is shown that the approach proposed in this paper provides a strong, unifying and consistent foundation relating them all together.
+%The applicability of these theoretical models will be illustrated by experiments where the specific one, two and three dimensional versions of the proposed generic models are validated against practical data.
 %Furthermore, the approach proposed in this paper
@@
 Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
-with p-value being the significant level of the Kolmogorov–Smirnov goodness-of-fit test between the two histograms}}
+with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
 \label{fig:verify_POLSAR_model_1D}
@@
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
-This qualitative observation is further supported by high significance level (or p-value) of the standard KS goodness-of-fit test.
-While a good p-value does not mean automatic acceptance of the model,
-  consistently high p-value readings suggest that the proposed model should not be ignored.
+This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
+While a good p-value does not ensure automatic acceptance of the model,
+  consistently high p-value lend evidence the proposed model has excellent confidence\cite{Kolmogoroff_1941_AMS_461}.
 
@@
 \caption{\scriptsize{The specific $d=2$ models are validated on both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
+with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
 \label{fig:verify_det_ratio_model_2D}
@@
 \caption{\scriptsize{The specific $d=3$ models are validated on both RADARSAT2 and AIRSAR datasets.
-Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis).}}
+Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
+with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
 \label{fig:verify_det_ratio_model_3D}

### 2014-02-27 paper_dev/article.tex
done with conclusion

@@
 %What has been done?
-This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.%***IVM: Hai pls check this sentence!
-This model has been validated for specific ($d=2$) and ($d=3$) using real-life partial and full polarimetric SAR data.
-The paper also establishes a few POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
-At the same time, we have also shown a near-perfect match between the specific $d=1$ model and that for traditional SAR intensity,
+This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution. %***IVM: Hai pls check this sentence!
+The model has been validated for specific $d=2$ and $d=3$ cases using real-life partial and full POLSAR data.
+The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
+We have also shown an excellent match between the specific $d=1$ model and that for traditional SAR intensity,
   effectively bringing the existing SAR theories under the umbrella of this new model.
@@
 %What are the results? What are their advantages over others' results?
-The main emphasis of this paper is the proposal to consider the POLSAR covariance matrix determinant as a scalar and representative observable for the multi-dimensional POLSAR data.
+The main emphasis of this paper is to consider the POLSAR covariance matrix determinant, and its derivatives, as scalar and representative observables for the multi-dimensional POLSAR data.
 Compared to other published scalar observables, the determinant is highly representative of the multi-dimensional data.
 Its representative power is justified for the following reasons.
-Firstly, the covariance matrix determinant, when collapsed into one-dimensional case, transforms neatly into the representative SAR intensity.
+Firstly, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
 Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
-Finally, this observable also leads to the establishment of the determinant-ratio discrimination measure for POLSAR data, which should increase the usability of this proposal.
+Thirdly, this observable also leads to the establishment of new discrimination measures for POLSAR data, which should increase the usability of this proposal.
+Finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to a change of polarization basis.
 
@@
 Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
-Hence many techniques applicable to SAR can not be directly translated to POLSAR.
+Hence many techniques applicable to SAR cannot be directly extended to POLSAR.
+There lies the different beneficial implications of the proposed approach presented in this paper.
 Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
   its main benefit is that it enables the convenient adaptation of many existing SAR data processing techniques for POLSAR data.
-One example has already been presented in this paper, 
-  where existing SAR discrimination measures are extended towards POLSAR.
+Two example application have already been presented in this paper. 
+  In the first instance, existing SAR discrimination measures are extended towards POLSAR.
+  While in the second case, existing technique to evaluate SAR speckle filters is also shown extensible towards POLSAR.
 At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
@@
   leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
-Other possible future work includes
-  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
-  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
+Other possible extensions include
+  investigating the applicability of the observables into POLSAR heterogeneous areas,
+  as well as exploring the use of these generic models in conjunction with other target decomposition techniques
     such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.  
+%Other possible future work includes
+%  an investigation on the applicability of this observables into POLSAR heterogeneous areas,
+%  as well as further studies to explore the use of these generic models in conjunction with other target decomposition techniques
+%    such as the Freeman-Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68}.
 

### 2014-03-03 paper_dev/article.tex
ks confidence level

@@
 While a good p-value does not ensure automatic acceptance of the model,
-  consistently high p-value lend evidence the proposed model has excellent confidence\cite{Kolmogoroff_1941_AMS_461}.
+  consistently high p-values lend high level of confidence to the proposed model\cite{Kolmogoroff_1941_AMS_461}.
 

### 2014-03-03 paper_dev/article.tex
eod 201403_Mar03

@@
 The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
-Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+%Section \ref{sec:discussion} presents a high-level discussion of the results presented before
+Then section \ref{sec:application} presents a simple demonstration where an existing technique of SAR processing is extended for POLSAR data before
   section \ref{sec:conclusion} finally concludes the paper.
@@
 
+In retrospective, intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
+Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
+
 In short, with the newly gained insight,
@@
 This invites the adaptation of many established SAR data processing techniques towards POLSAR data,
-  where this Section has just described a few examples.
+  where Section \ref{sec:application} will describe an example demonstration.
 However, before further discussion ensues, 
@@
 %\subsection{Theoretical Implications of This Proposal}
-\section{Discussion}
-\label{sec:discussion}
-
-%Let us begin by noting
-To begin, a few theoretical properties of the proposed statistical models are discussed.
-First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
-In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
-Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
-Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
-  the models presented here are invariant to polarization basis transformations.
-
-Second, the models are developed for the POLSAR covariance matrix.
-However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
-  the model is also applicable to the coherency matrix.
-
-It should be noted that despite these advantages, the model descriptions are far from complete.
-While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
-  such a reduction is unlikely to be lossless.  
-Ideally %to better understand POLSAR data
-the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
-
-Nevertheless the proposed models are promising.
-Even though initially developed for partial and monostatic POLSAR data,
-  it was shown to be applicable to traditional SAR data as well.
-Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
-
-Intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
-(in a sense this is also why intensity is widely considered representative of the complex SAR data).
-Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
-To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
-Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
-Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
-The important point is that it can provide a scalar comparison of the multi-dimensional data.
-%**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
-
-Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
-Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
-new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
-These applications however are not included in this paper, but rather left as a suggestion for future investigations.
-%There are a few reasons for this decision.
-%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
-%  the first being a faster ENL evaluation for POLSAR data and
-%  the second being the visual evaluation of POLSAR speckle filters.
-%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
-%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
-%It does not, technically speaking, focuses on proposing new discrimination measures.
+%\section{Extending Existing SAR Processing Techniques To POLSAR: A Simple Demo}
+%\label{sec:discussion}
+
+%%Let us begin by noting
+%To begin, a few theoretical properties of the proposed statistical models are discussed.
+%First, the use of covariance matrix log-determinant may be related to the standard eigen-decomposition method of the POLSAR covariance matrices.
+%In fact, the log-determinant can also be computed as the sum of log-eigenvalues.
+%Specifically $\ln{|M|} = \sum \ln{\lambda_M}$ where $\lambda_M$ denotes all the eigenvalues of $M$.
+%Thus, similar to other eigenvalue based approaches (e.g. entropy/anisotropy, ...),
+%  the models presented here are invariant to polarization basis transformations.
+%
+%Second, the models are developed for the POLSAR covariance matrix.
+%However, since the POLSAR coherency matrix is related to the covariance matrix via a unitary transformation which preserves the determinant,
+%  the model is also applicable to the coherency matrix.
+%
+%It should be noted that despite these advantages, the model descriptions are far from complete.
+%While it is desirable to reduce the multi-dimensional POLSAR data to a scalar value for many applications,
+%  such a reduction is unlikely to be lossless.  
+%Ideally %to better understand POLSAR data
+%the use of this technique could be complemented by some high-dimensional POLSAR target-decomposition techniques, such as the Freeman Durden decomposition \cite{Freeman_1998_TGRS_963} or the entropy/anisotropy decomposition \cite{Cloude_1997_TGRS_68} or similar.
+%
+%Nevertheless the proposed models are promising.
+%Even though initially developed for partial and monostatic POLSAR data,
+%  it was shown to be applicable to traditional SAR data as well.
+%Since the model assumptions are quite minimal, they may potentially be applicable to bi-static and interferometric data, although that would require further study.
 
@@
 
-%\section{Extending SAR data processing techniques towards POLSAR}
-%
-%Currently while the field of SAR is much more developed than the field of POLSAR,
+\section{Extending SAR data processing techniques towards POLSAR: A Short Example}
+\label{sec:application}
+
+%5Currently while the field of SAR is much more developed than the field of POLSAR,
 %  the two fields however are quite separated.
@@
 %
-%There are many beneficial implications for this proposal.
-%One of the main benefits is that:
-%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
-%One example has already been presented in this paper, 
-%  where existing SAR discrimination measures are extended towards POLSAR.
-%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
+
+There are many beneficial implications for this proposal.
+One of the main benefits is that:
+  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+One example has already been presented in this paper, 
+  where existing SAR discrimination measures are extended towards POLSAR.
+Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
 %
-%In evaluating SAR speckle filters, the intensity ratio is widely used.
-%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-%Assuming a perfect filtering condition, the ratio image should only contain random noise.
-%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+In evaluating SAR speckle filters, the intensity ratio is widely used.
+Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+Assuming a perfect filtering condition, the ratio image should only contain random noise.
+Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
 %
@@
 
+Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
+Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+These applications however are not included in this paper, but rather left as a suggestion for future investigations.
+%There are a few reasons for this decision.
+%The first is that the advantages of the proposed models have been demonstrated through a few applications in this paper:
+%  the first being a faster ENL evaluation for POLSAR data and
+%  the second being the visual evaluation of POLSAR speckle filters.
+%The second reason is that such an application would be quite big in scope, and as such would easily distract the reader from the main proposal of this paper.
+%Last but not least, this paper focuses on the proposal of several scalar and representative statistical models for POLSAR, which results in associated statistical models and discrimination measures.
+%It does not, technically speaking, focuses on proposing new discrimination measures.
+
 \section{Conclusion}

### 2014-03-05 paper_dev/article.tex
sent out version

@@
 
-In retrospective, intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
-(in a sense this is also why intensity is widely considered representative of the complex SAR data).
-Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
-To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
-Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
-Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
-The important point is that it can provide a scalar comparison of the multi-dimensional data.
+%In retrospective, intuitively, the concept of the determinant being representative of the POLSAR data can be thought of as being similar to the concept of using the magnitude to represent a complex number
+%(in a sense this is also why intensity is widely considered representative of the complex SAR data).
+%Similar to the determinant, the magnitude observable is also scalar and is not lossless, but it is undeniably useful.
+%To fully represent the complex number, another observable would needed besides the magnitude, for example a polar representation.
+%Magnitude is, of course, widely used as it can be shown to be invariant to a change in the reference frame.
+%Similarly, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+%Thus while it may not be \textit{fully} representative of the POLSAR data, it can be said to be \textit{highly} representative of it.
+%The important point is that it can provide a scalar comparison of the multi-dimensional data.
 %**IVM removed this This is similar to the most commonly used magnitude to compare two or more complex numbers. %, most of the times the magnitude is to be used.
@@
 
-There are many beneficial implications for this proposal.
-One of the main benefits is that:
-  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+%There are many beneficial implications for this proposal.
+%One of the main benefits is that:
+%  this proposal allows the extension of many of existing SAR data processing technique toward POLSAR.
+%One example has already been presented in this paper, 
+%  where existing SAR discrimination measures are extended towards POLSAR.
+%Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.
+
+%section introduction
+One of the main beneficial implications for this proposal is that:
+  it allows the extension of many of existing SAR data processing technique toward POLSAR.
 One example has already been presented in this paper,
   where existing SAR discrimination measures are extended towards POLSAR.
-Another example can be illustrated through an example which extends the SAR speckle filters evaluation technique towards POLSAR.  
-%
-In evaluating SAR speckle filters, the intensity ratio is widely used.
-Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
-Assuming a perfect filtering condition, the ratio image should only contain random noise.
-Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
-%
+This section illustrates another example for a common technique in SAR speckle filters evaluation.
+
+%In evaluating SAR speckle filters, the intensity ratio is widely used.
+%Specifically, in its original multiplicative domain, the ratio of the filtered output and the noisy input image represents the noise being removed.
+%Assuming a perfect filtering condition, the ratio image should only contain random noise.
+%Thus a commonly used visual evaluation is to simply plot the ratio image and determine if any image features have also been removed.
+%%
+%Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
+%  this technique can be equally applied to evaluate POLSAR speckle filters.
+%In fact better results can be achieved.
+%In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
+%  which is linear and additive in nature.
+%Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
+%NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
+
+%describe the technique
+In SAR, the intensity ratio is routinely used in evaluating speckle filters.
+Specifically, the ratio of the filtered output to the noisy input image represents the amount of noise removed.
+The multiplicative ratio, however, is not well suited to digital image presentation, which is linear and additive in nature\cite{Medeiros_2003_IJRS}. 
+Thus logarithmic transformation is applied to convert the multiplicative intensity-ratio into linear subtractive residuals.  
+Apparently if the speckle filter is perfect, the ratio or residual images should only contain random noise.
+Thus the evaluation method is simply confirming that the speckle filter has not removed any image features.
+
+%To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
+%  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+%  and the two POLSAR speckle filters are then applied to the patch.
+%\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+%  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+%  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
+%The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
+%At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+
+%describe the experiment
 Since the POLSAR determinant ratio has been shown to be equivalent to the SAR intensity ratio,
   this technique can be equally applied to evaluate POLSAR speckle filters.
-In fact better results can be achieved.
-In \cite{Medeiros_2003_IJRS}, it has been shown that the multiplicative ratio is not  well suited to digital image presentation,
-  which is linear and additive in nature.
-Thus logarithmic transformation can be applied to convert the multiplicative determinant-ratio into the linear subtractive contrast.  
-NOTE: The above paragraph is long winding, should shortened it. I noted that that it is also used in the conclusion. Suggest remove it if possible)
-
-To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters on the AIRSAR Flevoland partial polarimetric data (HH-HV).
-  A square 700$\times$700 pixel patch is first extracted from the AIRSAR dataset,
+To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
+  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
+  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.}.
+  A square 700$\times$700 pixel patch is first extracted from the AIRSAR Flevoland data (partial polarimetry HH-HV),
   and the two POLSAR speckle filters are then applied to the patch.
-\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.} 
 The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
@@
 
-Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
-  the distortion impact of the filter can also be made visible by the residual image.
-In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
-in the additive log-determinant image of the filtered output, 
-  such an observation can be made relatively easier by inspecting the residual image.
-
-There are many similar SAR data processing technique that may be adaptable to POLSAR.
-Examples in the same topic of evaluating speckle filters include
-  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
-Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
-
-Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
-Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
-new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
-These applications however are not included in this paper, but rather left as a suggestion for future investigations.
+%Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that not only does the log-determinant image offer a nice visualization of the scene, 
+%  the distortion impact of the filter can also be made visible by the residual image.
+%In this visual evaluation, while it is quite hard to observe the worsen blurring-effects of the boxcar 5$\times$5 speckle filter compared to the 3$\times$3 filter
+%in the additive log-determinant image of the filtered output, 
+%  such an observation can be made relatively easier by inspecting the residual image.
+
+%describe the result
+Fig \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that the evaluation technique is also workable for POLSAR speckle filters.
+In particular, the residual images clearly show both POLSAR speckle filters'  distortion impact.
+
+%There are many similar SAR data processing technique that may be adaptable to POLSAR.
+%Examples in the same topic of evaluating speckle filters include
+%  the use of the mean and variance of the ratio image, or ENL evaluation to quantitatively evaluate POLSAR speckle filters.
+%Other topics that may also be connected include: speckle filtering, target detection, surface cover classification, edge detection ... and so on.
+%
+%Besides the above properties, the theoretical models may also provide an alternative derivation for the likelihood test statistics widely used in POLSAR.
+%Similar to the way that different measures of distance can be used to derive POLSAR classifiers \cite{Lee_1999_TGRS}, change detectors \cite{Conradsen_2003_TGRS_4}, edge detectors \cite{Schou_2003_TGRS_20} or other clustering and speckle filtering techniques \cite{Le_2010_ACRS} \cite{Le_2011_ACRS},
+%new detection, classification, clustering or speckle filtering algorithms can be derived using the models presented in this paper.
+%These applications however are not included in this paper, but rather left as a suggestion for future investigations.
 %There are a few reasons for this decision.
@@
 
+%conclude the section
+There are many similar SAR data processing techniques that may be adaptable to POLSAR. 
+Due to space constraint, these applications, however, fall outside the scope of this paper.
+
 \section{Conclusion}
@@
 Its representative power is justified for the following reasons.
-Firstly, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
-Secondly, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
-Thirdly, this observable also leads to the establishment of new discrimination measures for POLSAR data, which should increase the usability of this proposal.
-Finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to a change of polarization basis.
+First, the covariance matrix determinant, when collapsed into 1-D, transforms neatly into the representative SAR intensity.
+Second, the statistical model for this observable is shown to be the generic multi-dimensional extension of the traditional model for the one dimensional SAR intensity.
+Third, this observable also leads to the establishment of new discrimination measures for POLSAR data.
+  %, which should increase the usability of this proposal.
+And finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to any changes in polarization basis.
+
+The detailed and mathematical explanation linking the SAR intensity and the POLSAR determinant has been presented in Section \ref{sec:sar_special_case_of_polsar}.
+This paragraph offers another high-level and intuitive linkage.
+That is the scalar determinant in POLSAR can be used to represent and compare the multi-dimensonal data,
+  much in the same way that the scalar magnitude is used to represent and compare complex numbers.
+Similar to the determinant, the magnitude observable is also scalar and is not lossless.
+Besides the magnitude, another observable would be needed to fully represent a complex number.
+For example, in a polar representation, an extra angle would be requried.
+Still, to compare complex numbers, the magnitude is widely used as it can be shown to be invariant to a change in the reference frame.
+Similar to the maginute, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
+%while it may not be \textit{fully} representative of the POLSAR data, 
+Thus the scalar observable is proposed to represent and distinguish the multi-dimensional dataset.
 

### 2014-03-10 paper_dev/article.tex
integrate Ian's changes

@@
 \author{Thanh-Hai~Le,
-        Ian~McLoughlin, 
+        Ian~Vince~McLoughlin, 
 	and Chan-Hua~Vun%
@@
 %	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
-\thanks{Manuscript received ?, 2014; revised ?.}}
-
-\markboth{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing,~Vol.~?, No.~?, ?~2014}%
+\thanks{Manuscript received March, 2014; revised March, 2014.}}
+
+\markboth{IEEE Journal on Selected Topics in Applied Earth Observation and Remote Sensing,~Vol.~x, No.~x, x~2014}%
 { Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data}
@@
   which severely limits their applicability in practical data processing applications.
-Alternatively, a few popular POLSAR discrimination measures are reviewed \cite{Lee_1994_IJRS_2299, Anfinsen_2007_ESA_POLINSAR, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454},
+Alternatively, a few popular POLSAR discrimination measures have been proposed~\cite{Lee_1994_IJRS_2299, Anfinsen_2007_ESA_POLINSAR, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454},
 %From an alternative approach, a few POLSAR discrimination measures have been proposed,
-  but all of them are shown to be based on the likelihood ratio statistics.
+  but all of them are based on likelihood ratio statistics (see Subsection \ref{sec:lit_measures}).
 This statistical test should ideally be based on an exact and consistent distribution
@@
 This paper presents scalar and representative observables,
-   and one associated generic statistical model,
-   that describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of discrimination measures.   
+   and an associated generic statistical model,
+   that describes multi-dimensional POLSAR data to provide a consistent foundation for the derivation of discrimination measures.   
 %This article hence presents a scalar and representative observable, and its associated generic statistical model to describe multi-dimensional POLSAR data and provide a consistent foundation for the derivation of POLSAR discrimination measures.
@@
 The development is based on the common assumption that POLSAR data follows the complex Wishart distribution.  
-Subsquently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
+Subsequently, the generic statistical model for the covariance matrix determinant is presented as being just a scalar projection of the multidimensional data.
 This model is then used to derive several scalar and consistent statistical distributions suggesting that their associated observables are capable of being used as discrimination measures for POLSAR.
@@
 The applicability of these theoretical models will be illustrated by experiments where the specific 1, 2 and 3-D versions of the proposed models are validated against real-life captured data.    
-The other beneficial implication of the proposed approach will also be demonstrated,
-  where the proposed theore is applied, as an example, to evaluate POLSAR speckle filters.
+The other beneficial implication of the proposed approach will also be demonstrated and discussed,
+  when the proposed model is applied, as an example illustrating their effectiveness, to the evaluation of POLSAR speckle filters.
 
@@
 The remainder of this article is organized as follows.
-After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, section \ref{sec:theoretical_model}
+After the next section reviews existing discrimination measures as well as scalar observables models for POLSAR, Section \ref{sec:theoretical_model}
   derives the generic statistical model for the determinant of the POLSAR covariance matrix
   and proposes several new discrimination measures for the multi-dimensional data.
-After section \ref{sec:sar_special_case_of_polsar} illustrates the match between the specific model of one dimensional and the traditional model for SAR intensity,
-  section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for the traditional SAR and the more recent POLSAR data.
+Section \ref{sec:sar_special_case_of_polsar} then illustrates the correspondence between the specific one dimensional model, and traditional models, for SAR intensity. 
+Following this, Section \ref{sec:link_sar_polsar} links the disparate discrimination measure proposals for traditional SAR with more recent POLSAR data.
 %Section \ref{sec:polsar_models_validation} then validates the specific one, two and three dimensional versions of the proposed model against real-life captured data.
-The applicability of these models against practical data is illustrated in section \ref{sec:polsar_models_validation}.
+The applicability of these models against practical data is illustrated in Section \ref{sec:polsar_models_validation}.
 %Section \ref{sec:discussion} presents a high-level discussion of the results presented before
-Then section \ref{sec:application} presents a simple demonstration where an existing technique of SAR processing is extended for POLSAR data before
-  section \ref{sec:conclusion} finally concludes the paper.
+Section \ref{sec:application} then presents a simple demonstration where an existing technique of SAR processing is extended for POLSAR data before
+  Section \ref{sec:conclusion} finally concludes the paper.
 
@@
 %This section outlines related publication.
-Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR.
+Section \ref{sec:lit_models} reviews various statistical models used for different scalar observables for POLSAR,
   where it is shown that none are able to provide statistically consistent discrimination measures. 
@@
 While an exact statistical distribution is expected to be necessary for a test,
-  only an asymptotic distribution is used in the underlying approach \cite{Conradsen_2003_TGRS_4}.
+  only an asymptotic distribution is used in their underlying foundation \cite{Conradsen_2003_TGRS_4}.
 
@@
 
-While these models undoubtedly help to further our understandings of the POLSAR data,
+While these models undoubtedly help to further our understanding of POLSAR data,
   none of the underlying observables have been shown to meet the dual criteria of
-  1) resulting in statistically consistent discrimination measures and thus 
-  2) being representative of the complex POLSAR data.
+  (i) resulting in statistically consistent discrimination measures and thus 
+  (ii) being representative of the complex POLSAR data.
 
@@
 
-The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined respectively as:
+Commonly used measures of dissimilarity for matrices are either the Euclidean or Manhattan distances, defined respectively as:
 \begin{align}
@@
   d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation},
+\end{equation}
 where $tr(C)$ denotes the trace of the matrix C. 
@@
 This means a distribution is to be derived for the dissimilarity measure.
-However, in the original work \cite{Conradsen_2003_TGRS_4}, only an asymptotic distribution was used.
-This paper proposes a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
-  which is capable of providing an exact distribution for the test.
+However, in the original work \cite{Conradsen_2003_TGRS_4}, only an \textit{asymptotic} distribution was used.
+By contrast, this paper will propose a statistical model for the determinant of the POLSAR covariance matrix $|C_v|$
+  which is capable of providing an \textit{exact} distribution for the test.
 
@@
 
-In this paper, the POLSAR scattering vector is denoted as $s$.
-For partial polarimetric SAR (single polarization in transmit and dual polarization in receipt),
+Note that the POLSAR scattering vector is denoted as $s$ in this paper.
+For partial polarimetric SAR (single polarization in transmit and dual polarization in receive),
   the vector is two-dimensional ($d=2$) and is normally written as: 
@@
 
-The sample POLSAR covariance matrix is formed as the mean of Hermitian outer product of independent single-look scattering vectors,
+The sample POLSAR covariance matrix is formed as the mean of the Hermitian outer product of independent single-look scattering vectors,
 \begin{equation}
@@
 Similar to the way intensity-ratio is proposed as the discrimination measure for the multiplicative and heteroskedastic SAR intensity \cite{Rignot_1993_TGRS_896},
-in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data.
-  which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
+in this paper, the determinant-ratio and the change-ratio are also proposed as a discrimination measure for the POLSAR data:
+  Which is shown above to also suffer from the multiplicative and heteroskedastic phenomena.
 %Similar to the way dispersion and contrast is defined for one-dimensional SAR \cite{Le_2010_ACRS},
@@
 
-Since each elementary component follows fixed distributions (i.e. $\chi^2(2L)$),
-  it is natural that this variable also follows fixed distributions.
+Since the elementary components follow fixed distributions (i.e. $\chi^2(2L)$),
+  it is natural that this variable also follows a fixed distribution.
 Moreover, it is independent of the underlying signal $\Sigma_v$,
@@
 \end{align*}
-Applying variable change theorem into the above equations results in:
+Applying the variable change theorem into the above equations results in:
 \begin{align*}
@@
   \end{eqnarray}
-considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ as multi-dimensional POLSAR collapses into single-dimensional SAR.
+considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ when multi-dimensional POLSAR collapses into single-dimensional SAR.
 
@@
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
-This, in essence, derives an exact statistical distribution for the likelihood test statistics,
-  as opposed to the asymptotic distribution derived in \cite{{Conradsen_2003_TGRS_4}}.
+This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).
 
@@
 The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
-In all cases, the good visual match between the actual data and model distribution tends to validate the proposed model. %providing us a simple validation of the result.
+In all cases, the good match between the actual data and model distribution lends support to the proposed model. %providing us a simple validation of the result.
 
@@
 Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
-with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
+with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms}}
 \label{fig:verify_POLSAR_model_1D}
@@
   on both AIRSAR and RADARSAT2 datasets.
-The look-number is estimated for each type of data and for each image using the technique described in \cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
+The look-number is estimated for each type of data and for each image~\cite{Anfinsen_2009_TGRS_3795}. %and is also noted in the plots.
 The practical and predicted distributions are again plotted to determine whether their visual match is close in each case.
@@
 Again, although the histogram is much tighter, the match is visually obvious in all cases.
-This qualitative observation is further supported by high significance level (or p-value) of the standard Kolmogorov-Smirnov goodness-of-fit test between curves, noted under each graph.
-While a good p-value does not ensure automatic acceptance of the model,
-  consistently high p-values lend high level of confidence to the proposed model\cite{Kolmogoroff_1941_AMS_461}.
+This qualitative observation is further supported by high significance level (or p-value) in the standard Kolmogorov-Smirnov goodness-of-fit test between curves~\cite{Kolmogoroff_1941_AMS_461}, noted under each graph.
+While a good p-value may not lead to automatic acceptance of the model,
+  consistently high p-values lend a high level of confidence to the proposal.
 
@@
 Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
-with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
+with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
 \label{fig:verify_det_ratio_model_2D}
@@
 Each histogram plots the signal under investigation (along the x-axis) against its probabilistic distribution across the patch (on the y-axis),
-with p-value being the significant level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
+with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.}}
 \label{fig:verify_det_ratio_model_3D}
@@
 %section introduction
-One of the main beneficial implications for this proposal is that:
+One of the main beneficial implications for this proposal is that
   it allows the extension of many of existing SAR data processing technique toward POLSAR.
@@
   where existing SAR discrimination measures are extended towards POLSAR.
-This section illustrates another example for a common technique in SAR speckle filters evaluation.
+This section illustrates another example for a common technique in SAR, namely speckle filter evaluation.
 
@@
 %describe the technique
-In SAR, the intensity ratio is routinely used in evaluating speckle filters.
+The intensity ratio is routinely used in SAR to evaluate speckle filters.
 Specifically, the ratio of the filtered output to the noisy input image represents the amount of noise removed.
@@
   this technique can be equally applied to evaluate POLSAR speckle filters.
-To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters\footnote{While the boxcar filters may not stay in the frontier of POLSAR speckle filtering,
-  they are workable here since the focus of this experiment is not on finding the best POLSAR speckle filters available.
-  Rather its purpose is to show a quick example of how an existing technique in SAR data processing can be easily adapted for POLSAR data.}.
+To demonstrate this feature, the technique is used to evaluate the performance of 3$\times$3 and 5$\times$5 boxcar POLSAR filters\footnote{While boxcar filtering may not be the most modern POLSAR speckle filter,
+  it is chosen here because the focus of the experiment is not to find the best POLSAR speckle filter, but rather to serve as an easily reproducible example of how an existing technique in SAR data processing can be simply adapted for use with POLSAR data.}.
   A square 700$\times$700 pixel patch is first extracted from the AIRSAR Flevoland data (partial polarimetry HH-HV),
@@
 The log-determinant images of the filtered outputs are displayed in Fig. \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}.
-At the same time, the residual is computed for both filters, and the images are also displayed in the same figure.
+At the same time, the residual is computed for both filters, and the original image patches are also displayed in the same figure.
 
@@
 \end{tabular}
-\caption{Visually Evaluating POLSAR Boxcar 3$\times$3 vs. 5$\times$5 Speckle Filters on AIRSA Flevoland part-pol data (HH-HV).}
+\caption{Visual evaluation of POLSAR boxcar 3$\times$3 vs. 5$\times$5 speckle filters on AIRSAR Flevoland part-pol data (HH-HV).}
 \label{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}
@@
 %describe the result
-Fig \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5} shows that the evaluation technique is also workable for POLSAR speckle filters.
-In particular, the residual images clearly show both POLSAR speckle filters'  distortion impact.
+From a visual examination of Fig \ref{fig:visual_eval_part_pol_boxcar_speckle_filters_3x3_vs_5x5}, the evaluation technique also appears workable for POLSAR speckle filters, since the residual images clearly reveal the distortion impact of both POLSAR speckle filters.
 
@@
 %conclude the section
-There are many similar SAR data processing techniques that may be adaptable to POLSAR. 
-Due to space constraint, these applications, however, fall outside the scope of this paper.
+Many similar SAR data processing techniques may be adaptable to POLSAR in this way, however they are not explored here due to space constraints.
 
@@
 %What has been done?
-This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution. %***IVM: Hai pls check this sentence!
+This paper has proposed a generic statistical model  for the POLSAR covariance matrix determinant based on the complex Wishart POLSAR target vector distribution.
 The model has been validated for specific $d=2$ and $d=3$ cases using real-life partial and full POLSAR data.
-The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic version of the SAR intensity-ratio.
+The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic versions of the SAR intensity-ratio.
 We have also shown an excellent match between the specific $d=1$ model and that for traditional SAR intensity,
-  effectively bringing the existing SAR theories under the umbrella of this new model.
+which effectively brings the existing SAR theories under the umbrella of this new model.
 
@@
   %, which should increase the usability of this proposal.
-And finally, similar to the eigen-values, the determinant of the POLSAR covariance matrix is invariant to any changes in polarization basis.
-
-The detailed and mathematical explanation linking the SAR intensity and the POLSAR determinant has been presented in Section \ref{sec:sar_special_case_of_polsar}.
-This paragraph offers another high-level and intuitive linkage.
-That is the scalar determinant in POLSAR can be used to represent and compare the multi-dimensonal data,
+And finally, similar to eigen-values, the determinant of the POLSAR covariance matrix is invariant to any changes in polarization basis.
+
+The detailed and mathematical explanation linking the SAR intensity and the POLSAR determinant has been presented in Section \ref{sec:sar_special_case_of_polsar} but consider another high-level and intuitive linkage:
+The POLSAR scalar determinant can be used to represent and compare the multi-dimensional data,
   much in the same way that the scalar magnitude is used to represent and compare complex numbers.
@@
 Besides the magnitude, another observable would be needed to fully represent a complex number.
-For example, in a polar representation, an extra angle would be requried.
-Still, to compare complex numbers, the magnitude is widely used as it can be shown to be invariant to a change in the reference frame.
-Similar to the maginute, the determinant of the POLSAR covariance matrix is also scalar and invariant to a change of polarization basis.
-%while it may not be \textit{fully} representative of the POLSAR data, 
-Thus the scalar observable is proposed to represent and distinguish the multi-dimensional dataset.
+For example, in a polar representation, the angle would be required in addition to magnitude.
+Despite this, magnitude is still widely used when comparing two complex numbers, as it can be shown to be invariant to a change in the reference frame.
+In the same way, the determinant of the POLSAR covariance matrix, also scalar and invariant to a change of polarization basis, is useful despite not being \textit{fully} representative of the POLSAR data.
+Thus this scalar observable is proposed to represent and distinguish between multi-dimensional datasets.
 
@@
 There are several beneficial implications of the proposed approach presented in this paper.
-Currently while the field of SAR is much more developed than the field of POLSAR,  the two fields remain  quite separated.
-Hence many techniques applicable to SAR cannot be directly extended to POLSAR.
-There lies the different beneficial implications of the proposed approach presented in this paper.
-Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity,
-  its main benefit is that it enables the convenient adaptation of many existing SAR data processing techniques for POLSAR data.
-Two example application have already been presented in this paper. 
+Currently, while the field of SAR is much more developed than the field of POLSAR,  the two fields remain quite distinct.
+Hence many techniques applicable to SAR have not been directly extended to POLSAR.
+The approach of this paper, by providing a scalar and representative model for POLSAR which generalizes the traditional model for SAR intensity, enables the convenient adaptation of many existing SAR data processing techniques for used with POLSAR data.
+In fact, two example applications of the technique were presented in this paper. 
   In the first instance, existing SAR discrimination measures are extended towards POLSAR.
-  While in the second case, existing technique to evaluate SAR speckle filters is also shown extensible towards POLSAR.
-At the same time, it provides a consistent theory unifying the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
+  While in the second case, existing technique to evaluate SAR speckle filters are shown to be extensible towards POLSAR.
+At the same time, this provides a consistent theory to unify the seemingly disparate discrimination measure proposals for SAR and POLSAR data.
 
 %What are their limitations? What problems this appears to solve, but actually is not?
-Of course, the models proposed in this article also have their own limitations.
+Of course, it must be mentioned that the models proposed in this paper also have their own limitations.
 Firstly, they are based on the complex Wishart distribution
@@
 %and hence What can be done next?
-  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferrometric POLSAR data ($d=6$) as possible future work.
+  leaving the test of its validity for other datasets such as bistatic POLSAR data ($d=4$) or interferometric POLSAR data ($d=6$) as possible future work.
 Other possible extensions include

### 2014-03-13 paper_dev/article.tex
Prof Vun's changes, ready for submission?

@@
 %Problem statement  
-This paper proposes novel scalar and representative observables, including several statistically consistent discrimination measures, which should be useful in the interpretation and processing of multi-dimensional POLSAR data.
-% This paper proposes a scalar and representative observable for multi-dimensional POLSAR data,
-%  from which statistically consistent discrimination measures can be derived.
+This paper proposes novel scalar and representative observables, including several statistically consistent discrimination measures,
+  that would be useful in the interpretation and processing of multi-dimensional POLSAR data.
 %What actually were done? and As the result, what is learned?
@@
   which is shown applicable to the two and three dimensional versions of partial and full monostatic polarimetric SAR data.
-As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
-  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
+In addition, the proposed model is also able to subsume the traditional SAR intensity model under the umbrella of a unified model,
+  where the SAR intensity is shown to be a one dimension version of the multi-dimensional data.
+%As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
+%  the proposed model is able to subsume the traditional SAR intensity model under the umbrella of a unified model. 
 %What are the larger implications of the findings presented in this paper?
@@
 %What is the situation, the background context of your research? the BIG problem!
-Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR) to become now a feasible and preferred technique for earth observation.
+Relentless growth in computing power has allowed the once computationally-demanding Synthetic Aperture Radar (SAR) to now become a feasible and preferred technique for earth observation.
 The basic SAR technology has also been extended in a few directions, one of which is polarimetric SAR (POLSAR).
@@
 %The POLSAR data, however, is multidimensional and stochastic.
-POLSAR data, like SAR, is stochastic.
-Moreover it is also multi-dimensional, making it even harder to interpret.
-It is therefore necessary to establish a simple and intuitive understanding of the data.
+%POLSAR data, like SAR, is stochastic.
+%Moreover it is also multi-dimensional, making it even harder to interpret.
+%It is therefore necessary to establish a simple and intuitive understanding of the data.
 %Like SAR data, POLSAR data is stochastic.
@@
 %Under this context, it is therefore important to establish a simple and intuitive understanding of the data.
-Statistical models are undoubtedly crucial in understanding its stochastic nature.
-While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional nature of the data.
-%  unfortunately tend to be complex and not very intuitive due to the multidimensional nature of the data.
-Practical POLSAR data processing however, makes heavy use of scalar discrimination measures,
-  which should be based on statistically consistent (or signal-independent) models. %for scalar and representative observables of the multidimensional data.
+%Statistical models are undoubtedly crucial in understanding its stochastic nature.
+While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data.
+It is therefore necessary to establish a simple and intuitive model for the 
+understanding of the data, and statistical models are undoubtedly suitable due to its stochastic nature.
+Furthermore, practical POLSAR data processing also makes heavy use of scalar discrimination measures,
+  which should be based on statistically consistent (i.e. signal-independent) models. %for scalar and representative observables of the multidimensional data.
 It is thus important to establish scalar and representative observables for multi-dimensional POLSAR data.

### 2014-03-24 cygwin_setup.sh
auto commit

@@ -14,9 +14,11 @@ if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
 
 fi
 
-  latex 'article.tex'
-  bibtex article
-  latex 'article.tex'
-  latex 'article.tex'
+  latex 'thesis.tex'
+  bibtex thesis
+  latex 'thesis.tex'
+  latex 'thesis.tex'
+  yap thesis.dvi
+  #dvipdf thesis.dvi
 
 

### 2014-03-24 cygwin_setup.sh
next task: print and check format

@@ -18,7 +18,8 @@ fi
   bibtex thesis
   latex 'thesis.tex'
   latex 'thesis.tex'
-  yap thesis.dvi
-  #dvipdf thesis.dvi
+  #yap thesis.dvi
+  dvipdf thesis.dvi
+  cygstart.exe thesis.pdf
 
 

### 2014-03-28 answer_thesis_examiner/answer_document.tex
auto

@@
 
+\newenvironment{replyheader}{
+	\vspace*{10mm}
+\begin{tabular}{l l}
+\bf{Name of Student:} & Le Thanh Hai \\
+\bf{Degree:} & Doctor of Philosophy \\
+\bf{Thesis Title:} & Scalar \& Homoskedastic Models for SAR \& POLSAR data
+\end{tabular}  
+	\vspace*{10mm}
+}
+
 \section*{Reply to Examiner No. 1}
 
-Some answer
+\begin{replyheader}
+\end{replyheader}
+
+Examiner No 1 includes not only his comment but also his original thesis.
+There was no direct question in the comment, and followings are my replies to his questions in the returned thesis.
 
@@
 
-Some answer
+\begin{replyheader}
+\end{replyheader}
+
+Examiner No. 2 suggests to review Section 1.1 and Section 1.2 so that the significance of the research motivation is highlighted.
+Similarly the conclusion chapter should also include the research objectives.
+These have been updated in the revised thesis,
+  even though for the latter point I would wish to point out that the research objectives have been clearly spelled out in the Introduction chapter.
+The examiner also suggested to change the word ``theory'' to ``model'', which has also been applied through out the thesis.
+
+The second main comment is to further highlight the novelty claim, which can be splitted into two parts.
+In the first part, the examiner suggests that ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
+Our main approach actually differs slightly and in a very subtle way.
+The proposed model is derived based on a generic result for multi-dimensional random-walk in mathematics (cite Goodman), which is applicable to POLSAR.
+Subsequently we pointed out that our model is actually an extension of existing statistical models for SAR,
+  since our multi-dimensional model, when collapsed into single-dimension, matches perfectly with existing SAR models.
+In the second part, the exminer express his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria'',
+  as ``the proposed log-transform model will introduce an inevitable bias error''.
+While I have total empathy with the examiner, since it is ultimately tricky to evaluate evaluation criteria.
+Still, I wish to point out that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation,
+  which for SAR speckle filter equates to 1. radiometric preservation and 2. noise suppression capabilities.
+
+( \textbf{ Hai note: }  the examiner suggests further clarifications to support the claim of novelty in Part II of his report.
+Unfortunately I do not have it at hand.
+It would be great if I can have a look at it!)
 
@@
 
-Some answer
+\begin{replyheader}
+\end{replyheader}
 

### 2014-03-28 answer_thesis_examiner/answer_document.tex
auto

@@
 \bf{Degree:} & Doctor of Philosophy \\
-\bf{Thesis Title:} & Scalar \& Homoskedastic Models for SAR \& POLSAR data
+\bf{Thesis Title:} & Scalar \& Homoskedastic Models \\ 
+ & for SAR \& POLSAR data
 \end{tabular}  
@@
 
-Examiner No 1 includes not only his comment but also his original thesis.
-There was no direct question in the comment, and followings are my replies to his questions in the returned thesis.
+First and foremost, I would like to express my appreciation towards Examiner No. 1 for his positive overall comments.
+I also appreciate the fact that examiner No 1 includes 
+  not only his comments in the examiner's report 
+  but also his corrective suggestions inside the original thesis.
+There was no direct question in the report, 
+  and followings are my replies to his comments in the returned thesis.
 
@@
 
+The examiner also suggestion inclusion of several references into the literature review topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
+I really appreciate the examiner effort in pointing out specific references.
+They, and some other articles, have been included in the thesis.
+I would like however to seek his empathy towards a couple of points.
+First, a number of the references cited has already been included into the original thesis (e.g Touzi (TODO:CITE) or 2-11-12.). 
+Some of them (for example Argenti (TODO:CITE)) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
+Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
+While they do results in published scientific articles, 
+  they are not, however, to be considered as the main contributions of the thesis.
+Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
+As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
+
+I appreciate the fact that the examiner also shares our thoughts and put it in a very concise sentence: ``the derivation of the statistical model for POLSAR data is the main contribution of the thesis''.
+As suggested, we have tried to extract portions of this thesis as scientific articles and submitted them for review.
+
+Last but not least, I have gone through the various errata exposed by Examiner No.2 and have updated the thesis accordingly.
+Finally, I wish to express my appreciation towards Examiner No.2 for his carefully and detailed review.
+
 \section*{Reply to Examiner No. 3}
@@
 
+Since Examiner No. 3 presneted his comments and suggestions in the order of the thesis' chapters, 
+  I would follow his suite.
+
+\subsubsection*{1. Overall Organization and presentation}
+
+I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
+Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
+
+\begin{itemize}
+  \item \textbf{Page ii of Contents page is missing:} This is probably an administrative mistake and oversight from us. Please accept our appologies!
+  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
+  \item \textbf{Some page number missing: } Updated (TODO: mostlikely this is an option that has been accidently turned on in the Latex Class file.)
+  \item \textbf{List of source codes: } Updated (now called ``List of Pseudocodes'' as suggested by the Examiner.)
+\end{itemize}
+
+\subsubsection*{2. Abstract}
+
+The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.
+
+\subsubsection*{3. Chapter 1}
+
+The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
+The chapter is also updated, so that new and existing references are added to provide direct support.
+The author's publication list is now also included in this, as well as in the final conclusion, chapter.
+
+At this juncture, I would also wish to address one of Examiner No. 3's main concern.
+It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
+The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
+Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
+The model for the data in this additive domain has been derived and accepted in (TODO:CITE Arsenault).
+My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
+These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
+It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault (TODO:CITE) and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.
+
+\subsubsection*{4. Chapter 2}
+
+Chapter 2 is also updated to address Examiner No. 3's concerns.
+In a bid of not confusing other examiners, I have decided not to move the theory section into a separate chapter.
+However, this chapter is heavily updated so that 1. Section 2.1 is shortened considerably and 2. Section 2.2 is extended significantly. 
+This I believe leads to a better balance between describing the nature of the data, and reviewing the related work.
+This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
+
+\subsubsection*{5. Chapter 3}
+
+There are apparently two main concerns from Examiner No. 3's comments.
+First, page 44 line 1 should be intepreted strictly in the context of the preceeding paragraph (page 43). 
+That is mathematically  speaking $\sigma$ is just a mathematical variables, thus making the statement true. 
+Any resemblence of it with the SAR signal is established in the next paragraph.
+The third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
+It is also acknowledged in the thesis, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''
+This is the assumption used in this analysis, 
+  and a portion of subsequent work is devoted to extend this early analysis into heterogeneous area.
+The very next section (i.e. Section 3.2) starts the discussion on this very topic.
+
+In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
+Under this condition, then the variances are independent of $\sigma$, i.e. it is homoskedastic.
+In fact, if the area is heterogeneous as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
+This, of course, leads to different expression for the observable variances.
+In fact, it leads to heteroskedasticity, which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', should we consider $var(L_I)$ as the variation of the observables in an area.
+It should be noted, however, that at the level of each radar physical resolution cell, the values measured in SAR are not deterministic.
+Then if we consider $var(L_A)$ as the deviation of the observables from its true signal, we will also have $var(L_A)$ as being constant (assuming that the effective number of looks or ENL is constant across the area)!
+
+The second point concerns the models and their names.
+This chapter has been updated and model names are given for each to clarify the concepts.
+The confusion is understandable, and partially my fault, in not highlighting the following points.
+First there are different models being proposed, in Section 3.4.
+And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
+Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.
+
+\subsubsection*{6. Chapter 4}
+
 \end{document}

### 2014-03-28 answer_thesis_examiner/cygwin_setup.sh

@@ -1,0 +1,25 @@
+#!/bin/bash
+
+if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
+  #echo $PATH
+  export MIKTEX_USERSTARTUPFILE=c:\\workspaces\\isprint_desktop\\portable\\MikTex\\miktex\\config\\miktexstartup.ini
+  echo $MIKTEX_USERSTARTUPFILE
+  #D:\workspaces\portable\MikTex\miktex\config\miktexstartup.ini
+  export MIKTEX_BINDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/bin/
+  export PATH=$PATH:/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/bin/
+  export TEMP=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
+  export TMP=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
+  export TEMPDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
+  export TMPDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp
+
+fi
+
+  pdflatex 'answer_document.tex'
+  #bibtex thesis
+  #latex 'thesis.tex'
+  #latex 'thesis.tex'
+  #yap answer_document.dvi
+  #dvipdf thesis.dvi
+  #cygstart.exe thesis.pdf
+
+

### 2014-03-31 answer_thesis_examiner/answer_document.tex
auto

@@
 \usepackage{titlesec}
-\newcommand{\sectionbreak}{\clearpage}
+\newcommand{\sectionbreak}{\clearpage} %to give each section a new page
+
+\usepackage{amsmath} %to have equation with no number
 
@@
 
+Examiner No.3 expresses his doubt on two points.
+First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
+And second that $\Sigma^{-1}$ is ill-defined.
+I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
+Its form, as repeated from equation 4.1, is written as:
+
+\begin{align*}
+  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
+\end{align*}
+
+This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
+In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
+In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
+This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
+
+It is partially for the second concern that log-transformation is proposed.
+Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
+Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
+In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$.
+
+\begin{align*}
+  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
+\end{align*}
+
 \end{document}

### 2014-03-31 answer_thesis_examiner/answer_document.tex
auto

@@
 Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
-In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$.
+In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.
 
@@
 
+The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
+For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
+I believe, such a change should completely addresses his concerns.
+I also made other small updates, to addresses his other various minor concerns.
+
+\subsubsection*{7. Chapter 5}
+
+Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
+The reference for computation in the section is the ``true signal'' $\sigma$.
+
+Fig. 5.11 shows two curves that are essentially the same.
+One of them is ``simulated result'' and the other is ``analysis formula''.
+The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
+The purpose is to show that the heuristic formula given as
+
+\begin{align*}
+  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
+\end{align*}
+
+closely tracks observable values.
+Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
+
 \end{document}

### 2014-04-01 answer_thesis_examiner/answer_document.tex
auto

@@
 
+Examiner No 3 also expresses his curiosity to see ``how the f-MLE filter will compare with other state-of-the-art-filters''.
+While, I am also eager to see, and to some extend to prove, the good results of my proposed f-MLE filter,
+  I have decided not to include it in the section 5.3, where the performance of many different filters are reviewed.
+There are a few reasons for such a decision.
+First, in the section I am proposing a new way to evaluate speckle filters.
+And instead of at the same time discussing the performance of f-MLE filter, I wish to focus on that topic exclusively.
+Second, assuming the performance of f-MLE filter is included and found to be superior than others,
+  such a result can be easily refuted.
+That is because I was proposing both new speckle filters and a new approach to evaluate speckle filters,
+  which I wish to, as much as possible, keeping them independently of each other.
+Last but not least, as noted by all Examiners and myself included, speckle filtering is not the main topic of the thesis.
+It is only the avenue to demonstrate the benefits of the proposed models for SAR \& POLSAR data of the thesis.
+
+\subsubsection*{8. Chapter 6}
+
 \end{document}

### 2014-04-01 answer_thesis_examiner/answer_document.tex
auto

@@
 
+In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
+To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
+Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
+They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
+  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
+
+The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
+He went on to ask: ``What kind of eror will it cause?''.
+To this the answer is that the model inherently suffers from loss of dimension
+  where the full data is multi-dimensional and the proposed models are scalar.
+
+Besides these main points, the chapter is updated to increase its pursuasive power.
+For example: the sentence in line 1, page 133, section 6.3 is removed.
+Or a list of achievements has been included in this chapter.
+
+\subsubsection*{9. Appendix}
+
+While the conference papers have been published and the journal paper submitted,
+  their copies have been removed from this section.
+
 \end{document}

### 2014-04-06 answer_thesis_examiner/answer_document.tex
auto

--- 2014-03-31 answer_thesis_examiner/answer_document.tex
@@
 \usepackage{amsmath} %to have equation with no number
+
+\usepackage{chapterbib} %to have references in each chapter
 
@@
 	\vspace*{10mm}
+\setcounter{page}{1}
+
 \begin{tabular}{l l}
@@
 
-\section*{Reply to Examiner No. 1}
+\include{chap1}
 
-\begin{replyheader}
-\end{replyheader}
+\include{chap2}
 
-First and foremost, I would like to express my appreciation towards Examiner No. 1 for his positive overall comments.
-I also appreciate the fact that examiner No 1 includes 
-  not only his comments in the examiner's report 
-  but also his corrective suggestions inside the original thesis.
-There was no direct question in the report, 
-  and followings are my replies to his comments in the returned thesis.
-
-\section*{Reply to Examiner No. 2}
-
-\begin{replyheader}
-\end{replyheader}
-
-Examiner No. 2 suggests to review Section 1.1 and Section 1.2 so that the significance of the research motivation is highlighted.
-Similarly the conclusion chapter should also include the research objectives.
-These have been updated in the revised thesis,
-  even though for the latter point I would wish to point out that the research objectives have been clearly spelled out in the Introduction chapter.
-The examiner also suggested to change the word ``theory'' to ``model'', which has also been applied through out the thesis.
-
-The second main comment is to further highlight the novelty claim, which can be splitted into two parts.
-In the first part, the examiner suggests that ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
-Our main approach actually differs slightly and in a very subtle way.
-The proposed model is derived based on a generic result for multi-dimensional random-walk in mathematics (cite Goodman), which is applicable to POLSAR.
-Subsequently we pointed out that our model is actually an extension of existing statistical models for SAR,
-  since our multi-dimensional model, when collapsed into single-dimension, matches perfectly with existing SAR models.
-In the second part, the exminer express his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria'',
-  as ``the proposed log-transform model will introduce an inevitable bias error''.
-While I have total empathy with the examiner, since it is ultimately tricky to evaluate evaluation criteria.
-Still, I wish to point out that MSE evaluation has two components: 1. bias evaluation and 2. variance evaluation,
-  which for SAR speckle filter equates to 1. radiometric preservation and 2. noise suppression capabilities.
-
-( \textbf{ Hai note: }  the examiner suggests further clarifications to support the claim of novelty in Part II of his report.
-Unfortunately I do not have it at hand.
-It would be great if I can have a look at it!)
-
-The examiner also suggestion inclusion of several references into the literature review topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
-I really appreciate the examiner effort in pointing out specific references.
-They, and some other articles, have been included in the thesis.
-I would like however to seek his empathy towards a couple of points.
-First, a number of the references cited has already been included into the original thesis (e.g Touzi (TODO:CITE) or 2-11-12.). 
-Some of them (for example Argenti (TODO:CITE)) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
-Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
-While they do results in published scientific articles, 
-  they are not, however, to be considered as the main contributions of the thesis.
-Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
-As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
-
-I appreciate the fact that the examiner also shares our thoughts and put it in a very concise sentence: ``the derivation of the statistical model for POLSAR data is the main contribution of the thesis''.
-As suggested, we have tried to extract portions of this thesis as scientific articles and submitted them for review.
-
-Last but not least, I have gone through the various errata exposed by Examiner No.2 and have updated the thesis accordingly.
-Finally, I wish to express my appreciation towards Examiner No.2 for his carefully and detailed review.
-
-\section*{Reply to Examiner No. 3}
-
-\begin{replyheader}
-\end{replyheader}
-
-Since Examiner No. 3 presneted his comments and suggestions in the order of the thesis' chapters, 
-  I would follow his suite.
-
-\subsubsection*{1. Overall Organization and presentation}
-
-I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
-Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
-
-\begin{itemize}
-  \item \textbf{Page ii of Contents page is missing:} This is probably an administrative mistake and oversight from us. Please accept our appologies!
-  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
-  \item \textbf{Some page number missing: } Updated (TODO: mostlikely this is an option that has been accidently turned on in the Latex Class file.)
-  \item \textbf{List of source codes: } Updated (now called ``List of Pseudocodes'' as suggested by the Examiner.)
-\end{itemize}
-
-\subsubsection*{2. Abstract}
-
-The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.
-
-\subsubsection*{3. Chapter 1}
-
-The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
-The chapter is also updated, so that new and existing references are added to provide direct support.
-The author's publication list is now also included in this, as well as in the final conclusion, chapter.
-
-At this juncture, I would also wish to address one of Examiner No. 3's main concern.
-It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
-The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
-Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
-The model for the data in this additive domain has been derived and accepted in (TODO:CITE Arsenault).
-My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
-These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
-It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault (TODO:CITE) and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.
-
-\subsubsection*{4. Chapter 2}
-
-Chapter 2 is also updated to address Examiner No. 3's concerns.
-In a bid of not confusing other examiners, I have decided not to move the theory section into a separate chapter.
-However, this chapter is heavily updated so that 1. Section 2.1 is shortened considerably and 2. Section 2.2 is extended significantly. 
-This I believe leads to a better balance between describing the nature of the data, and reviewing the related work.
-This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
-
-\subsubsection*{5. Chapter 3}
-
-There are apparently two main concerns from Examiner No. 3's comments.
-First, page 44 line 1 should be intepreted strictly in the context of the preceeding paragraph (page 43). 
-That is mathematically  speaking $\sigma$ is just a mathematical variables, thus making the statement true. 
-Any resemblence of it with the SAR signal is established in the next paragraph.
-The third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
-It is also acknowledged in the thesis, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''
-This is the assumption used in this analysis, 
-  and a portion of subsequent work is devoted to extend this early analysis into heterogeneous area.
-The very next section (i.e. Section 3.2) starts the discussion on this very topic.
-
-In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
-Under this condition, then the variances are independent of $\sigma$, i.e. it is homoskedastic.
-In fact, if the area is heterogeneous as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-This, of course, leads to different expression for the observable variances.
-In fact, it leads to heteroskedasticity, which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', should we consider $var(L_I)$ as the variation of the observables in an area.
-It should be noted, however, that at the level of each radar physical resolution cell, the values measured in SAR are not deterministic.
-Then if we consider $var(L_A)$ as the deviation of the observables from its true signal, we will also have $var(L_A)$ as being constant (assuming that the effective number of looks or ENL is constant across the area)!
-
-The second point concerns the models and their names.
-This chapter has been updated and model names are given for each to clarify the concepts.
-The confusion is understandable, and partially my fault, in not highlighting the following points.
-First there are different models being proposed, in Section 3.4.
-And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
-Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.
-
-\subsubsection*{6. Chapter 4}
-
-Examiner No.3 expresses his doubt on two points.
-First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
-And second that $\Sigma^{-1}$ is ill-defined.
-I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
-Its form, as repeated from equation 4.1, is written as:
-
-\begin{align*}
-  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-\end{align*}
-
-This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
-In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
-In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
-This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
-
-It is partially for the second concern that log-transformation is proposed.
-Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
-Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
-In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.
-
-\begin{align*}
-  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
-\end{align*}
-
-The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
-For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
-I believe, such a change should completely addresses his concerns.
-I also made other small updates, to addresses his other various minor concerns.
-
-\subsubsection*{7. Chapter 5}
-
-Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
-The reference for computation in the section is the ``true signal'' $\sigma$.
-
-Fig. 5.11 shows two curves that are essentially the same.
-One of them is ``simulated result'' and the other is ``analysis formula''.
-The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
-The purpose is to show that the heuristic formula given as
-
-\begin{align*}
-  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
-\end{align*}
-
-closely tracks observable values.
-Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
+\include{chap3}
 

### 2014-04-06 answer_thesis_examiner/chap1.tex
auto

\section*{Reply to Examiner No. 1}

\begin{replyheader}
\end{replyheader}

First, I would like to express my appreciation towards Examiner No. 1 for his \textbf{over-all positive comments}.
I also appreciate the fact that Examiner No 1 includes
  not only his comments in the examiner's report
  but also helpful suggestions inside the original thesis.
There was no direct question in the report, and followings are my replies to his comments in the returned thesis.

### 2014-04-06 answer_thesis_examiner/chap2.tex
auto

\section*{Reply to Examiner No. 2}

\begin{replyheader}
\end{replyheader}

Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
In a similar fashion, the conclusion chapter should also include the research objectives.
These have been updated in the revised thesis.
Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
The examiner also suggested to change the word ``theory'' to ``model''.
That has also been applied through out the thesis.

\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.

\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
 ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
The main approach, in actuality, differs in a subtle but important way:
The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
These results are well known to be applicable to POLSAR.
Thus, the derived models by nature are multi-dimensional model.
However, when collapsed into single-dimension, they match perfectly with existing SAR models.
As such, the proposed models can be considered as an extension of existing statistical models for SAR.

\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
It is no doubt tricky to evaluate evaluation criteria.
And I can empathize with his feelings.
Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
In fact it has two components: 1. bias evaluation and 2. variance evaluation, which for SAR speckle filter evaluation translates into 1. radiometric preservation and 2. noise suppression respectively.

( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
Unfortunately I do not have it at hand.
It would be great if I can have a look at it!)

The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
I really appreciate the examiner effort in pointing out specific references.
They, and some other articles, have been included in the thesis.
I would like however to seek his empathy towards a couple of points.
First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
While they do results in published scientific articles, 
  they are not, however, to be considered as the main contributions of the thesis.
Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.

\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.

%\bibliographystyle{plainnat}
\bibliographystyle{apalike}
\bibliography{answer_document}

### 2014-04-06 answer_thesis_examiner/chap3.tex
auto

\section*{Reply to Examiner No. 3}

\begin{replyheader}
\end{replyheader}

Since Examiner No. 3 presneted his comments and suggestions in the order of the thesis' chapters, 
  I would follow his suite.

\subsubsection*{1. Overall Organization and presentation}

I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.

\begin{itemize}
  \item \textbf{Page ii of Contents page is missing:} This is probably an administrative mistake and oversight from us. Please accept our appologies!
  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
  \item \textbf{Some page number missing: } Updated (TODO: mostlikely this is an option that has been accidently turned on in the Latex Class file.)
  \item \textbf{List of source codes: } Updated (now called ``List of Pseudocodes'' as suggested by the Examiner.)
\end{itemize}

\subsubsection*{2. Abstract}

The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.

\subsubsection*{3. Chapter 1}

The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
The chapter is also updated, so that new and existing references are added to provide direct support.
The author's publication list is now also included in this, as well as in the final conclusion, chapter.

At this juncture, I would also wish to address one of Examiner No. 3's main concern.
It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
The model for the data in this additive domain has been derived and accepted in (TODO:CITE Arsenault).
My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault (TODO:CITE) and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.

\subsubsection*{4. Chapter 2}

Chapter 2 is also updated to address Examiner No. 3's concerns.
In a bid of not confusing other examiners, I have decided not to move the theory section into a separate chapter.
However, this chapter is heavily updated so that 1. Section 2.1 is shortened considerably and 2. Section 2.2 is extended significantly. 
This I believe leads to a better balance between describing the nature of the data, and reviewing the related work.
This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.

\subsubsection*{5. Chapter 3}

There are apparently two main concerns from Examiner No. 3's comments.
First, page 44 line 1 should be intepreted strictly in the context of the preceeding paragraph (page 43). 
That is mathematically  speaking $\sigma$ is just a mathematical variables, thus making the statement true. 
Any resemblence of it with the SAR signal is established in the next paragraph.
The third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
It is also acknowledged in the thesis, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''
This is the assumption used in this analysis, 
  and a portion of subsequent work is devoted to extend this early analysis into heterogeneous area.
The very next section (i.e. Section 3.2) starts the discussion on this very topic.

In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
Under this condition, then the variances are independent of $\sigma$, i.e. it is homoskedastic.
In fact, if the area is heterogeneous as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
This, of course, leads to different expression for the observable variances.
In fact, it leads to heteroskedasticity, which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', should we consider $var(L_I)$ as the variation of the observables in an area.
It should be noted, however, that at the level of each radar physical resolution cell, the values measured in SAR are not deterministic.
Then if we consider $var(L_A)$ as the deviation of the observables from its true signal, we will also have $var(L_A)$ as being constant (assuming that the effective number of looks or ENL is constant across the area)!

The second point concerns the models and their names.
This chapter has been updated and model names are given for each to clarify the concepts.
The confusion is understandable, and partially my fault, in not highlighting the following points.
First there are different models being proposed, in Section 3.4.
And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.

\subsubsection*{6. Chapter 4}

Examiner No.3 expresses his doubt on two points.
First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
And second that $\Sigma^{-1}$ is ill-defined.
I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
Its form, as repeated from equation 4.1, is written as:

\begin{align*}
  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
\end{align*}

This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.

It is partially for the second concern that log-transformation is proposed.
Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.

\begin{align*}
  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
\end{align*}

The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
I believe, such a change should completely addresses his concerns.
I also made other small updates, to addresses his other various minor concerns.

\subsubsection*{7. Chapter 5}

Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
The reference for computation in the section is the ``true signal'' $\sigma$.

Fig. 5.11 shows two curves that are essentially the same.
One of them is ``simulated result'' and the other is ``analysis formula''.
The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
The purpose is to show that the heuristic formula given as

\begin{align*}
  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
\end{align*}

closely tracks observable values.
Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.

Examiner No 3 also expresses his curiosity to see ``how the f-MLE filter will compare with other state-of-the-art-filters''.
While, I am also eager to see, and to some extend to prove, the good results of my proposed f-MLE filter,
  I have decided not to include it in the section 5.3, where the performance of many different filters are reviewed.
There are a few reasons for such a decision.
First, in the section I am proposing a new way to evaluate speckle filters.
And instead of at the same time discussing the performance of f-MLE filter, I wish to focus on that topic exclusively.
Second, assuming the performance of f-MLE filter is included and found to be superior than others,
  such a result can be easily refuted.
That is because I was proposing both new speckle filters and a new approach to evaluate speckle filters,
  which I wish to, as much as possible, keeping them independently of each other.
Last but not least, as noted by all Examiners and myself included, speckle filtering is not the main topic of the thesis.
It is only the avenue to demonstrate the benefits of the proposed models for SAR \& POLSAR data of the thesis.

\subsubsection*{8. Chapter 6}

In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...

The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
He went on to ask: ``What kind of eror will it cause?''.
To this the answer is that the model inherently suffers from loss of dimension
  where the full data is multi-dimensional and the proposed models are scalar.

Besides these main points, the chapter is updated to increase its pursuasive power.
For example: the sentence in line 1, page 133, section 6.3 is removed.
Or a list of achievements has been included in this chapter.

\subsubsection*{9. Appendix}

While the conference papers have been published and the journal paper submitted,
  their copies have been removed from this section.

### 2014-04-06 answer_thesis_examiner/build.sh

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+latex answer_document.tex
+for auxfile in chap*.aux
+do
+    bibtex `basename $auxfile .aux`
+done
+latex answer_document.tex
+latex answer_document.tex

### 2014-04-08 answer_thesis_examiner/cygwin_setup.sh
auto

@@ -2,19 +2,25 @@
 
 if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
   #echo $PATH
-  export MIKTEX_USERSTARTUPFILE=c:\\workspaces\\isprint_desktop\\portable\\MikTex\\miktex\\config\\miktexstartup.ini
+  export MIKTEX_USERSTARTUPFILE=c:\\workspaces\\portable\\MikTex\\miktex\\config\\miktexstartup.ini
   echo $MIKTEX_USERSTARTUPFILE
   #D:\workspaces\portable\MikTex\miktex\config\miktexstartup.ini
-  export MIKTEX_BINDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/bin/
-  export PATH=$PATH:/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/bin/
-  export TEMP=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
-  export TMP=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
-  export TEMPDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp/
-  export TMPDIR=/cygdrive/c/workspaces/isprint_desktop/portable/MikTex/miktex/temp
+  export MIKTEX_BINDIR=/cygdrive/c/workspaces/portable/MikTex/miktex/bin/
+  export PATH=$PATH:/cygdrive/c/workspaces/portable/MikTex/miktex/bin/
+  export TEMP=/cygdrive/c/workspaces/portable/MikTex/miktex/temp/
+  export TMP=/cygdrive/c/workspaces/portable/MikTex/miktex/temp/
+  export TEMPDIR=/cygdrive/c/workspaces/portable/MikTex/miktex/temp/
+  export TMPDIR=/cygdrive/c/workspaces/portable/MikTex/miktex/temp
 
 fi
 
-  pdflatex 'answer_document.tex'
+  latex 'answer_document.tex'
+  for auxfile in chap*.aux
+  do
+      bibtex `basename $auxfile .aux`
+  done
+  latex 'answer_document.tex'
+  latex 'answer_document.tex'
   #bibtex thesis
   #latex 'thesis.tex'
   #latex 'thesis.tex'

### 2014-04-12 answer_thesis_examiner/chap1.tex
auto

@@
 There was no direct question in the report, and followings are my replies to his comments in the returned thesis.
+
+In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
+First I would like to thank Examiner No. 2 for raising such a question.
+By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
+With that corrected, let me repeat the Equations here
+
+\begin{align}
+pdf(A_x) = \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
+pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
+pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
+\end{align}
+
+For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below
+
+\begin{align}
+pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}}
+\end{align}
+
+Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.
+
+Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:
+
+\begin{align}
+pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
+\end{align}
+
+Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:
+
+\begin{align}
+pdf(x) = \frac{e^{-x/2}}{2} 
+\end{align}
+
+Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
+Variable change theorem give us:
+
+\begin{align}
+pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
+\end{align}
+
+For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution
+
+\begin{align}
+pdf(x) = \lambda e^{- \lambda x}
+\end{align}

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

@@
 
-Since Examiner No. 3 presneted his comments and suggestions in the order of the thesis' chapters, 
+Since Examiner No. 3 presented his comments and suggestions in the order of the thesis' chapters, 
   I would follow his suite.
@@
 
-I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
-Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
+Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
+Still minor editions have been included to address his  other concerns:
+
+%I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
+%Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
 
 \begin{itemize}
-  \item \textbf{Page ii of Contents page is missing:} This is probably an administrative mistake and oversight from us. Please accept our appologies!
+  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
   \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
-  \item \textbf{Some page number missing: } Updated (TODO: mostlikely this is an option that has been accidently turned on in the Latex Class file.)
-  \item \textbf{List of source codes: } Updated (now called ``List of Pseudocodes'' as suggested by the Examiner.)
+  \item \textbf{Some page number missing: } Updated. 
+  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
 \end{itemize}
@@
 
-The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.
+The abstract has been updated so that:
+\begin{enumerate}[topsep=0pt]
+  \item Each of the proposed models have their own name and
+  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
+\end{enumerate}
 
@@
 
-The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
-The chapter is also updated, so that new and existing references are added to provide direct support.
-The author's publication list is now also included in this, as well as in the final conclusion, chapter.
+The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
+This suggestion has been updated in this chapter, as well as through out the whole thesis.
+Also references are included to increase the persuasion power of the claims.
+The list of publication is also now included in this chapter, in addition to the existing one found in the final chapter.
 
 At this juncture, I would also wish to address one of Examiner No. 3's main concern.
-It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
-The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
-Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
-The model for the data in this additive domain has been derived and accepted in (TODO:CITE Arsenault).
-My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
-These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
-It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault (TODO:CITE) and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.
+He wonders: ``What makes you think that this model is appropriate?''.
+Before the answer is laid out , I wish to make a few points.
+First, I thank the Examiner to raise this question, which no doubt is an important one. 
+Second, while it is important to judge the end result, 
+  I am not quite sure that should be done at the very first chapter.
+In fact, a large portion of the final chapter is devoted towards such a discussion.
+
+To directly address the Examiner's concern, let me iterate a few points that has been noted in the thesis.
+First the generic model proposed in this thesis is applicable to multi-dimensional POLSAR data.
+Second, when the multi-dimensional data is collapsed into one dimensional, 
+  the specific case of the proposed model matches perfectly with the model proposed for SAR by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
+Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.
+
+%It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
+%The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
+%Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
+%The model for the data in this additive domain has been derived and accepted in \cite{Arsenault_JOptSocAm_1976}.
+%My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
+%These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
+%It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault \cite{Arsenault_JOptSocAm_1976} and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.
 
@@
 
-Chapter 2 is also updated to address Examiner No. 3's concerns.
-In a bid of not confusing other examiners, I have decided not to move the theory section into a separate chapter.
-However, this chapter is heavily updated so that 1. Section 2.1 is shortened considerably and 2. Section 2.2 is extended significantly. 
-This I believe leads to a better balance between describing the nature of the data, and reviewing the related work.
-This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
+For Chapter 2, Examiner No. 3's suggests: ``Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work''.
+In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
+Still, this chapter is heavily updated so that: 
+\vspace{-3mm}
+\begin{enumerate}
+  \item Section 2.1 is shortened considerably and 
+  \item Section 2.2 is extended significantly. 
+\end{enumerate}
+
+This I believe leads to a better balance between describing the nature of the data and reviewing the related work.
+%This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
 
@@
   their copies have been removed from this section.
+
+\bibliographystyle{apalike}
+\bibliography{answer_document}

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

--- 2014-04-06 answer_thesis_examiner/chap3.tex
@@
 
-The abstract has been updated so that: 1. each of the proposed models have their own name and 2. not only the benefits are listed, but also their shortcomings.
+The abstract has been updated so that:
+
+\begin{enumerate}
+  \item each of the proposed models have their own name and
+  \item not only the benefits are listed, but also their shortcomings.
+\end{enumerate}
 

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

@@
 \begin{enumerate}
-  \item each of the proposed models have their own name and
-  \item not only the benefits are listed, but also their shortcomings.
+  \item Each of the proposed models have their own name and
+  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
 \end{enumerate}
@@
 
-The examiner suggests that ``Table captions appears at the top of a table, rather than below it'' and the chapter as well as the thesis has been updated accordingly.
+The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
+This suggestion has been updated in this chapter, as well as through out the whole thesis.
 The chapter is also updated, so that new and existing references are added to provide direct support.
-The author's publication list is now also included in this, as well as in the final conclusion, chapter.
+The author's publication list is now also included in this chapter, as well as in the final conclusion chapter.
 

### 2014-04-12 answer_thesis_examiner/clean.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+declare -a ext=('tex' 'bib');
+f_name2='chap2'
+
+function e {
+    echo $1
+    eval $1
+}
+
+
+function backup {
+    f_name=$1
+    declare -a ext=("${!2}")
+    #ext=$2
+
+    for t in ${ext[@]}
+    do
+      e "mv ${f_name}.${t} b.${f_name}.${t}"
+    done
+    
+    e "rm ${f_name}.*"
+    
+    for t in ${ext[@]}
+    do
+      e "mv b.${f_name}.${t} ${f_name}.${t}"
+    done
+}
+
+backup 'answer_document' ext[@]
+backup 'chap1' ext[@]
+backup 'chap2' ext[@]
+backup 'chap3' ext[@]
+

### 2014-04-12 answer_thesis_examiner/chap3.tex
auto

--- 2014-04-12 answer_thesis_examiner/chap3.tex
@@
 There are apparently two main concerns from Examiner No. 3's comments.
-First, page 44 line 1 should be intepreted strictly in the context of the preceeding paragraph (page 43). 
-That is mathematically  speaking $\sigma$ is just a mathematical variables, thus making the statement true. 
-Any resemblence of it with the SAR signal is established in the next paragraph.
-The third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
-It is also acknowledged in the thesis, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''
-This is the assumption used in this analysis, 
-  and a portion of subsequent work is devoted to extend this early analysis into heterogeneous area.
-The very next section (i.e. Section 3.2) starts the discussion on this very topic.
+The first is: ``how can the statement on page 44 line 1 ... be true?''.
+And second: ``why homoskedasticity is valid, and what are the assumption in this analysis?''
 
-In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
-Under this condition, then the variances are independent of $\sigma$, i.e. it is homoskedastic.
-In fact, if the area is heterogeneous as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-This, of course, leads to different expression for the observable variances.
-In fact, it leads to heteroskedasticity, which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', should we consider $var(L_I)$ as the variation of the observables in an area.
-It should be noted, however, that at the level of each radar physical resolution cell, the values measured in SAR are not deterministic.
-Then if we consider $var(L_A)$ as the deviation of the observables from its true signal, we will also have $var(L_A)$ as being constant (assuming that the effective number of looks or ENL is constant across the area)!
+First, the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
+That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
+Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
+In fact, the third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
+This is the assumption used in this analysis. 
+The assumption is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
+If $\sigma$ is not a constant, then heteroskedastic ensues.
+The next section (i.e. Section 3.2) then outlines the effects of heteroskedasticity, 
+  which explains the needs for logarithmic transformation.
+
+The assumption described above continues to hold in Section 3.3 and, of course, table 3.3.
+%In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
+Under this condition, the variances of the log-transformed variables are then independent of $\sigma$.
+The point being made in the table is that: 
+  while variances are dependent on $\sigma$ in the original domain,
+  in the log transformed domain, they are independent of this value.
+
+The assumption actually is not very restrictive.
+It should be noted that at the level of each radar physical resolution cell, 
+  the value measured in SAR is not deterministic.
+For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
+This model actually is applicable to both homogeneous and heterogeneous areas.
+
+Now, if the area is heterogeneous, then $\sigma$ is no longer a constant.
+In fact, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
+%This, of course, leads to different expression for the observable variances.
+This leads to heteroskedasticity, 
+  which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
+  should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
+However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from corresponding its ``true'' signal at each physical resolution cell level, 
+  then they will be independent of $\sigma$ (as described in Table 3.3).
+In fact they are constant, even as $sigma$ changes.
+This leads to homoskedasticity!
 

### 2014-04-16 answer_thesis_examiner/chap1.tex
auto

@@
 pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
+pdf(A_1) = 2A_1 e^{-A_1^2} \\
 pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
+\end{align}
+
+The integration of these becomes
+\begin{align}
+cdf(A_x) = \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} = 1 \\
+cdf(A) = \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{-\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} = 1\\
+cdf(A_1) = \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} = 1\\
+cdf(I) = \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} = 1
 \end{align}

### 2014-04-18 answer_thesis_examiner/chap1.tex
auto

--- 2014-04-12 answer_thesis_examiner/chap1.tex
@@
 \begin{align}
-pdf(A_x) = \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
-pdf(A) = \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
-pdf(I) = \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
+pdf(A_x) &= \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
+pdf(A)   &= \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
+pdf(A_1) &= 2A_1 e^{-A_1^2} \\
+pdf(I)   &= \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
+\end{align}
+
+The integration of these becomes
+\begin{align}
+cdf(A_x) &= \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} &= 1 \\
+cdf(A) &= \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} &= 1\\
+cdf(A_1) &= \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} &= 1\\
+cdf(I) &= \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} &= 1
 \end{align}
@@
 \begin{align}
-pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}}
+\textbf{Normal Distribution: } & pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}} \\
+\textbf{Chi-Squared Distribution (dof=2): } & pdf(x) = \frac{e^{-x/2}}{2} \\ %pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}} \\
+\textbf{Exponential Distribution: } & pdf(x) = \lambda e^{- \lambda x}
+\end{align}
+
+\begin{align}
+\textbf{Normal Distribution: } & cdf(x) = \frac{1}{2} \left[ 1 + erf \left( \frac{x-\mu}{\sqrt{2\sigma^2}} \right) \right] \\
+\textbf{Chi-Squared Distribution (dof=2): } & cdf(x) = 1 - e^{-x/2}\\
+\textbf{Exponential Distribution: } & cdf(x) = 1 - e^{- \lambda x}
 \end{align}

### 2014-04-24 answer_thesis_examiner/old.chap2.tex
auto commit

--- 2014-04-06 answer_thesis_examiner/chap2.tex
@@
 
-( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
-Unfortunately I do not have it at hand.
-It would be great if I can have a look at it!)
+%( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
+%Unfortunately I do not have it at hand.
+%It would be great if I can have a look at it!)
 
-The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
-I really appreciate the examiner effort in pointing out specific references.
+The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
+I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
 They, and some other articles, have been included in the thesis.
-I would like however to seek his empathy towards a couple of points.
-First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
-Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
-Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
-While they do results in published scientific articles, 
-  they are not, however, to be considered as the main contributions of the thesis.
-Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
-As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
+
+%The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
+%I really appreciate the examiner effort in pointing out specific references.
+%They, and some other articles, have been included in the thesis.
+%I would like however to seek his empathy towards a couple of points.
+%First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
+%Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
+%Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
+%While they do results in published scientific articles, 
+%  they are not, however, to be considered as the main contributions of the thesis.
+%Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
+%As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
 

### 2014-04-25 answer_thesis_examiner/chap2.tex
auto

@@
 \end{replyheader}
+
+\replyToComment
+    {Sec 1.1 and 1.2 should be reviewed again ... with proper citations on the background studies.}
+    {The sections were reviewed and several citations were added}
+
+\replyToComment
+    {Paragraph 1 of Sec 1.3.3 should be removed or rewritten}
+    {The paragraph were removed?}
+
+\replyToComment
+    {The achievement of objectives should (also) be stated in the conclusion chapter. }
+    {These were added into the conclusion chapter (``with proper justfications based on experimental results and findings'').}
+
+\noindent
+\begin{longtable}[c]{p{0.14\textwidth}|p{0.12\textwidth}|p{0.34\textwidth}|p{0.24\textwidth}}
+\textbf{Page No} & \textbf{Line No} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
+ \hline
+ \endhead
+ToC & - & missing page numbers & Rectified \\
+ & & & \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ & & & \\
+3 & 12 & Similarly speaking, & Similarly, \\
+3 & 19 & criteria & criterion \\ 
+4 & 14 & MMSE criteria & MMSE criterion \\
+6 & 9 & Last but certainly not least, & Thirdly, \\ 
+6 & 9 & such a framework allow & such a framework allows \\[10pt]
+ToC & - & missing page numbers & Rectified \\[10pt]
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+ToC & - & missing page numbers & Rectified \\
+1 & 13 & single SAR channel & single-channel SAR \\ 
+ToC & - & missing page numbers & Rectified \\
+\end{longtable}
+
+%\noindent
+%\begin{tabularx}{\textwidth}{X | X | X X X X}
+%  Page No & Line No & \multicolumn{2}{l|}{Comment} & \multicolumn{2}{l}{Reply} \\
+%  \hline 
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
+%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
+%          \end{tabularx}
 

### 2014-04-25 answer_thesis_examiner/chap2.tex
auto

@@
 
+\rowcolors{2}{gray!25}{white}    
 \noindent
-\begin{longtable}[c]{p{0.14\textwidth}|p{0.12\textwidth}|p{0.34\textwidth}|p{0.24\textwidth}}
-\textbf{Page No} & \textbf{Line No} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
+\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
+\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
  \hline
@@
 ToC & - & missing page numbers & Rectified \\
- & & & \\
 1 & 13 & single SAR channel & single-channel SAR \\ 
- & & & \\
 3 & 12 & Similarly speaking, & Similarly, \\
@@
 6 & 9 & Last but certainly not least, & Thirdly, \\ 
-6 & 9 & such a framework allow & such a framework allows \\[10pt]
-ToC & - & missing page numbers & Rectified \\[10pt]
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
-ToC & - & missing page numbers & Rectified \\
-1 & 13 & single SAR channel & single-channel SAR \\ 
-ToC & - & missing page numbers & Rectified \\
+6 & 9 & such a framework allow & such a framework allows \\
+9 & 7 & multidimensional & Multi-dimensional \\
+10 & 12 & The model os & The model is \\
+11 & 28 & chapter 5 & Chapter 5 \\
+12 & 6 & chapter 6 & Chapter 6 \\
+22 & 15 & RadarSat & RadarSat-2 \\
+24 & 14 & SVM & SVM (Support Vector Machine) \\
+35 & 6-7 & Rician distribution [48]... & Rician distribution [48]. \\
+35 & 11 & back scattering & backscattering \\
+36 & 10 & literatured & literatures \\
+37 & -2 & Proposed bu & proposed by \\
+39 & 4 & dependence & dependency \\
+44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
 \end{longtable}
-
-%\noindent
-%\begin{tabularx}{\textwidth}{X | X | X X X X}
-%  Page No & Line No & \multicolumn{2}{l|}{Comment} & \multicolumn{2}{l}{Reply} \\
-%  \hline 
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR} \\ 
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%  1 & 13 & \multicolumn{2}{l|}{single SAR channel } & \multicolumn{2}{l}{single-channel SAR}  \\
-%  ToC & - & \multicolumn{2}{l|}{missing page numbers} & \multicolumn{2}{l}{Rectified} \\
-%          \end{tabularx}
 

### 2014-04-26 answer_thesis_examiner/chap2.tex
auto

@@
 44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
+46 & 4 & most known common & most commonly known \\
+56 & 6 & POLSAR And & POLSAR. And \\
+65 &5,7 & an homogeneous area & a homogeneous area \\
+77 & 3 & the objective then is & the objective is \\
+77 & 5,6 & it has already been proven & it has already been proven [?] \\
+87 & -1 & Fig 5.6a & Fig 5.6. \\
+89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
+91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
+95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
+103 & 22 & related to the ENL index. over & related to the ENL index over \\
+104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
+109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
+112 & 13 & these smaller requirements & these requirements \\
+132 & 9 & evaluation criteria & evaluation criterion
 \end{longtable}
+
+\textbf{Overall Comments \& Replies}
+
+In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
+I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
+I also feel indebted to the Examiner with his suggestion to extract out and submit portions of this thesis as scientific papers for peer review.
+
+=====
 

### 2014-04-27 answer_thesis_examiner/chap1.tex
auto

@@
 There was no direct question in the report, and followings are my replies to his comments in the returned thesis.
+
+\rowcolors{2}{gray!25}{white}    
+\noindent
+\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
+\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
+ \hline
+ \endhead
+4 & 5 & missing references & citation added \\
+4 & 8 & missing references & citation added \\
+5 & 13 & techniques ... has & techniques ... have \\
+6 & 5 & many fold & manyfold \\
+14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
+\end{longtable}
+
+\rowcolors{1}{white}{}
+\replyToComment
+    {Page 14: With reference to Equations 2.1, 2.2, 2.3 what are the range of $A_x$, $A$ and $I$}
+    {The range of $A_x$ is from $(-\infty, \infty)$, and the range of both $A$ and $I$ is from $(0,\infty)$}
+
+\replyToComment
+  {Page 14: Does the integration of pdf for $A_x,A,I$ sum to 1?}
+  {With the defined range above, YES they are all sum to 1.
+This is easy to verify as they belong to the classes of Normal, Chi-Squared (2 degree-of-freedom) and Exponential Distribution respectively.}
+
+\rowcolors{2}{gray!25}{white}    
+\noindent
+\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
+\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
+ \hline
+ \endhead
+15 & 6 & missing explaination for $E,B$ & explaination added \\
+\end{longtable}
 

### 2014-04-29 answer_thesis_examiner/chap2.tex
auto

@@
     {These were added into the conclusion chapter (``with proper justfications based on experimental results and findings'').}
+
+\replyToComment
+    {Replace the word ``theory'' with ``model'' throughout the thesis}
+    {Search and replace operation done!}
+
+\replyToComment
+    {The proposed model is derived based on the existing statistical models for SAR and extended to POLSAR}
+    {The main approach, as described in the thesis, differs in a subtle but important way.
+The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
+That is: the proposed models by nature are applicable to multi-dimensional data and thus they are applicable to POLSAR data.
+To show that the proposed models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1.
+The thesis subsequently shows that they match perfectly with existing SAR models.
+}
+
+\replyToComment
+    {The proposed log-transform model will introduce an inevitable bias error, which may not be able to measure by MSE.}
+    {
+      The thesis clearly recognizes that log-transformation will introduce bias.
+      It also shows that MSE evaluation does inherently include bias evaluation.
+      In fact, the thesis argues that MSE evaluation has two components: 1.
+bias evaluation and 2.
+variance evaluation, which for evaluating the performance of SAR speckle filters translates into 1.
+radiometric preservation and 2.
+noise suppression respectively.
+}
 
@@
 \end{longtable}    
+\rowcolors{1}{white}{}
 
@@
 I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
-I also feel indebted to the Examiner with his suggestion to extract out and submit portions of this thesis as scientific papers for peer review.
+I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.
 

### 2014-05-02 answer_thesis_examiner/chap1.tex
auto

@@
 \noindent
-\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
+\begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
 \textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
@@
 6 & 5 & many fold & manyfold \\
+14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in numbers and independent in nature, \\
 14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
 \end{longtable}    
+\rowcolors{1}{white}{}
 
-\rowcolors{1}{white}{}
 \replyToComment
@@
  \endhead
-15 & 6 & missing explaination for $E,B$ & explaination added \\
+15 & 6 & missing explaination for $\vec{E},B$ & explaination added \\
+15 & 12 & x,y plane & x \& y planes \\
+15 & -2 & $2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi)$ & $2 \frac{\xi_x(t) \xi_y(t)}{E_x^0 E_y^0} \cos (\Delta \phi)$ \\
+16 & 2 & The parameters ... are: & The parameters ... are: the intensity orientation angle ($\theta$), the ellipticity angle ($\Psi$) and the orientation angle ($\chi$) \\
+17 & 4 & machenics & mechanics \\
+17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
 \end{longtable}    
+\rowcolors{1}{white}{}
 

### 2014-05-02 answer_thesis_examiner/clean.sh

@@ -1,7 +1,7 @@
 #!/bin/bash
 
 declare -a ext=('tex' 'bib');
-f_name2='chap2'
+#f_name2='chap2'
 
 function e {
     echo $1

### 2014-05-02 clean.sh

@@ -1,9 +1,45 @@
-mv thesis.tex b.thesis.tex
-mv thesis.bib b.thesis.bib
-rm thesis.*
-mv b.thesis.tex thesis.tex
-mv b.thesis.bib thesis.bib
+#!/bin/bash
 
-rm chap*.pdf
-rm chap*.txt
+declare -a ext=('tex' 'bib');
+#f_name2='chap2'
+
+function e {
+    echo $1
+    eval $1
+}
+
+
+function backup {
+    f_name=$1
+    b_name=$(basename $1)
+    p_name=${f_name%/*}
+    e "${p_name}"
+    declare -a ext=("${!2}")
+    #ext=$2
+
+    for t in ${ext[@]}
+    do
+      e "mv ${p_name}/${b_name}.${t} ${p_name}/b.${b_name}.${t}"
+    done
+    
+    e "rm ${f_name}.*"
+    
+    for t in ${ext[@]}
+    do
+      e "mv ${p_name}/b.${b_name}.${t} ${p_name}/${b_name}.${t}"
+    done
+}
+
+backup './thesis' ext[@]
+backup '0_frontmatter/dedication' ext[@]
+
+
+#mv thesis.tex b.thesis.tex
+#mv thesis.bib b.thesis.bib
+#rm thesis.*
+#mv b.thesis.tex thesis.tex
+#mv b.thesis.bib thesis.bib
+
+#rm chap*.pdf
+#rm chap*.txt
 

### 2014-05-04 answer_thesis_examiner/chap2.tex
auto

@@
 }
+
+\replyToComment
+    {A more comprehensive review of the relevant SAR/POLSAR speckle filters should be included.}
+    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}}
+
+\replyToComment
+    {Whereever possible, samples of SAR/POLSAR images with these three types of features (i.e.
+homogeneous, textured and strong scatterer) should be used to evaluate the effectiveness of the proposed models.}
+    {In the section to evaluate speckle filters, various different patterns had been studied.
+Also the MSE evaluation which includes bias and variance evaluation are shown to be able to evaluate the effectiveness of different speckle filters in terms of radiometric preservation and speckle noise reduction respectively.}
+
+%The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
+%I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
+%They, and some other articles, have been included in the thesis.
 
@@
 
-The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
-I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
-They, and some other articles, have been included in the thesis.
-
 %The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.

### 2014-05-04 clean.sh

@@ -32,7 +32,12 @@ function backup {
 
 backup './thesis' ext[@]
 backup '0_frontmatter/dedication' ext[@]
-
+backup '1_introduction/introduction' ext[@]
+backup '2/literature_review' ext[@]
+backup '3/sar' ext[@]
+backup '4/polsar' ext[@]
+backup '5/applications' ext[@]
+backup '6/conclusional_discussion' ext[@]
 
 #mv thesis.tex b.thesis.tex
 #mv thesis.bib b.thesis.bib

### 2014-05-05 answer_thesis_examiner/chap2.tex
auto

@@
 
-%The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
-%I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
-%They, and some other articles, have been included in the thesis.
+\replyToComment
+    {The work done has great potential to be published in high impact factor journals such as JSTAR, IJRS and PIER}
+    {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}
 
@@
 
-=====
-
-Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
-In a similar fashion, the conclusion chapter should also include the research objectives.
-These have been updated in the revised thesis.
-Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
-The examiner also suggested to change the word ``theory'' to ``model''.
-That has also been applied through out the thesis.
-
-\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.
-
-\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
- ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
-The main approach, in actuality, differs in a subtle but important way:
-The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
-These results are well known to be applicable to POLSAR.
-Thus, the derived models by nature are multi-dimensional model.
-However, when collapsed into single-dimension, they match perfectly with existing SAR models.
-As such, the proposed models can be considered as an extension of existing statistical models for SAR.
-
-\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
-His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
-It is no doubt tricky to evaluate evaluation criteria.
-And I can empathize with his feelings.
-Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
-In fact it has two components: 1. bias evaluation and 2. variance evaluation, which for SAR speckle filter evaluation translates into 1. radiometric preservation and 2. noise suppression respectively.
+%=====
+%
+%Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
+%In a similar fashion, the conclusion chapter should also include the research objectives.
+%These have been updated in the revised thesis.
+%Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
+%The examiner also suggested to change the word ``theory'' to ``model''.
+%That has also been applied through out the thesis.
+%
+%\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.
+%
+%\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
+% ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
+%The main approach, in actuality, differs in a subtle but important way:
+%The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
+%These results are well known to be applicable to POLSAR.
+%Thus, the derived models by nature are multi-dimensional model.
+%However, when collapsed into single-dimension, they match perfectly with existing SAR models.
+%As such, the proposed models can be considered as an extension of existing statistical models for SAR.
+%
+%\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
+%His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
+%It is no doubt tricky to evaluate evaluation criteria.
+%And I can empathize with his feelings.
+%Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
+%In fact it has two components: 1.
+bias evaluation and 2.
+variance evaluation, which for SAR speckle filter evaluation translates into 1.
+radiometric preservation and 2.
+noise suppression respectively.
 
@@
 
-\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
-Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
-Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
-Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.
+%\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
+%Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
+%Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
+%Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.
 

### 2014-05-05 answer_thesis_examiner/chap2.tex
auto

@@
     {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}
+
+\replyToComment
+    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
+    {Heteroskedastic and homoskedastic are terms defined in statistical context to respectively denote the fact that different sub-populations of a given samples can have different or similar variabilities.
+In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or the same variances.}
+
+\replyToComment
+    {Add references to the following statement: ``for example speckle filtering, target detection, image segmentation and other cluster, classification techniques''}
+    {TODO:CITE}
+
+\replyToComment
+    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
+    {TODO:CITE}
+
+\replyToComment
+    {Add references to the following statement: ``Such use, however, is known to be not very robust for these so-called heavy detailed distributions.''}
+    {TODO:CITE}
+
+\replyToComment
+    {Add references to the following statement: ``it is known that such use should be avoided in preference to a ratio-based descrimination measure.''}
+    {TODO:CITE}
+
+\replyToComment
+    {Add references to the following statement: ``The Ordinary Least Square (OLS) is widely used as the best evaluation criteria, which is probably due to the Gauss Markov theorem.''}
+    {TODO:CITE}
+
+\replyToComment
+    {Add references to the following statement: ``violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.''}
+    {TODO:CITE}
+
+\replyToComment
+    {It would be easier to read and refer if all the Equations are labelled accordingly.}
+    {All equations in the thesis has been updated with labels.}
+
+\textbf{Errata Sheet}
 

### 2014-05-05 answer_thesis_examiner/chap3.tex
auto

@@
 \subsubsection*{1. Overall Organization and presentation}
+
+\replyToComment
+    {Page ii of the Contents section is missing}
+    {Page numbers are added for Contents section}
+
+\replyToComment
+    {Usually, a Glossary is put at the end of the document}
+    {Updated (now the Glossary section stays at the end of the thesis)}
+
+\replyToComment
+    {Page xiii: List of source codes. These are actually pseudocodes and not source codes.}
+    {Updated (now called ``List of Pseudocodes'')}
 

### 2014-05-05 answer_thesis_examiner/chap3.tex
auto

@@
 
-Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
-Still minor editions have been included to address his  other concerns:
+%Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
+%Still minor editions have been included to address his  other concerns:
 
@@
 
-\begin{itemize}
-  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
-  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
-  \item \textbf{Some page number missing: } Updated. 
-  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
-\end{itemize}
+%\begin{itemize}
+%  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
+%  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
+%  \item \textbf{Some page number missing: } Updated. 
+%  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
+%\end{itemize}
 
@@
 
-The abstract has been updated so that:
-\begin{enumerate}[topsep=0pt]
-  \item Each of the proposed models have their own name and
-  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
-\end{enumerate}
+\replyToComment
+    {Since these models are the key contributions of the thesis, it would be good to give a separate name to each of these models}
+    {The models' names are added into the abstract}
+
+\replyToComment
+    {The abstract lists the benefits of these models but not the shortcomings.}
+    {The shortcomings have also been included into the abstract.}
+
+%The abstract has been updated so that:
+%\begin{enumerate}[topsep=0pt]
+%  \item Each of the proposed models have their own name and
+%  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
+%\end{enumerate}
 
@@
 
-The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
-This suggestion has been updated in this chapter, as well as through out the whole thesis.
-Also references are included to increase the persuasion power of the claims.
-The list of publication is also now included in this chapter, in addition to the existing one found in the final chapter.
+\replyToComment
+    {Table captions appears at the top of a table, rather than below it}
+    {The suggestion has been updated in this chapter, as well as through out the whole thesis}
 
-At this juncture, I would also wish to address one of Examiner No. 3's main concern.
-He wonders: ``What makes you think that this model is appropriate?''.
-Before the answer is laid out , I wish to make a few points.
+\replyToComment
+    {No references throughout this chapter.}
+    {References have been included in this chapter to increase its persuasion power.}
+
+\replyToComment
+    {you are trying to propose an additive and homoskedastic model for the data. What makes you think that thsi model is appropriate?}
+    {Before an answer is laid out, I wish to make a few points.
 First, I thank the Examiner to raise this question, which no doubt is an important one. 
@@
 Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.
+}
+
+\replyToComment
+    {In section 1.4, it may be worthwhile to mention that the author's contribution had been published in various venues, together with a list of author's publications.}
+    {The list of publication is now included in this section as well.}
+
+%The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
+%This suggestion has been updated in this chapter, as well as through out the whole thesis.
+%Also references are included to increase the persuasion power of the claims.
+%The list of publication is also now included in this chapter, in addition to the existing one found in the final chapter.
+%
+%At this juncture, I would also wish to address one of Examiner No. 3's main concern.
+%He wonders: ``What makes you think that this model is appropriate?''.
+%Before the answer is laid out , I wish to make a few points.
+%First, I thank the Examiner to raise this question, which no doubt is an important one. 
+%Second, while it is important to judge the end result, 
+%  I am not quite sure that should be done at the very first chapter.
+%In fact, a large portion of the final chapter is devoted towards such a discussion.
+%
+%To directly address the Examiner's concern, let me iterate a few points that has been noted in the thesis.
+%First the generic model proposed in this thesis is applicable to multi-dimensional POLSAR data.
+%Second, when the multi-dimensional data is collapsed into one dimensional, 
+%  the specific case of the proposed model matches perfectly with the model proposed for SAR by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
+%Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.
 
@@
 
-For Chapter 2, Examiner No. 3's suggests: ``Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work''.
-In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
+\replyToComment
+    {Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work}
+    {In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
 Still, this chapter is heavily updated so that: 
@@
 \end{enumerate}
+These editions, I believe, lead to a better balance between describing the nature of the data and reviewing the related work.
+}
 
-This I believe leads to a better balance between describing the nature of the data and reviewing the related work.
+%For Chapter 2, Examiner No. 3's suggests: ``Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work''.
+%In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
+%Still, this chapter is heavily updated so that: 
+%\vspace{-3mm}
+%\begin{enumerate}
+%  \item Section 2.1 is shortened considerably and 
+%  \item Section 2.2 is extended significantly. 
+%\end{enumerate}
+%
+%This I believe leads to a better balance between describing the nature of the data and reviewing the related work.
 %This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
@@
 
-There are apparently two main concerns from Examiner No. 3's comments.
-The first is: ``how can the statement on page 44 line 1 ... be true?''.
-And second: ``why homoskedasticity is valid, and what are the assumption in this analysis?''
-
-First, the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
+\replyToComment
+    {how can the statement on page 44 line 1 ``... intensity are equal to a scaled version of these unit variables, specifically $A=\sigma A_1$ and $I=\sigma^2 I_1$'' be true?}
+    {the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
 That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
 Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
-In fact, the third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
-This is the assumption used in this analysis. 
-The assumption is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
-If $\sigma$ is not a constant, then heteroskedastic ensues.
-The next section (i.e. Section 3.2) then outlines the effects of heteroskedasticity, 
-  which explains the needs for logarithmic transformation.
+In fact, line 7 page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area).
+}
 
-The assumption described above continues to hold in Section 3.3 and, of course, table 3.3.
-%In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
-Under this condition, the variances of the log-transformed variables are then independent of $\sigma$.
-The point being made in the table is that: 
-  while variances are dependent on $\sigma$ in the original domain,
-  in the log transformed domain, they are independent of this value.
+\replyToComment
+    {why homoskedasticity is valid, and what are the assumption in this analysis?}
+    {Spartial homogeneity is the assumption used in the analysis thus far. 
+Its limitation is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
 
-The assumption actually is not very restrictive.
+This assumption actually is not very restrictive.
 It should be noted that at the level of each radar physical resolution cell, 
@@
 For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
-This model actually is applicable to both homogeneous and heterogeneous areas.
+In that sense, the assumption is actually applicable to both homogeneous and heterogeneous areas.
+}
 
-Now, if the area is heterogeneous, then $\sigma$ is no longer a constant.
-In fact, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-%This, of course, leads to different expression for the observable variances.
-This leads to heteroskedasticity, 
-  which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
+\replyToComment
+    {If $\sigma$ is not a constant, then $var(L_A)$ and $var(L_I)$ cannot be homoskedastic}
+    {In general, the imaging area is heterogeneous, then $\sigma$ is no longer a constant from one resolution pixel to the next.
+That much is clear.
+Then, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
+This changing $\sigma$ also leads to heteroskedasticity, 
+  which the Examiner correctly pointed out in his comment
+%``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
   should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
-However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from corresponding its ``true'' signal at each physical resolution cell level, 
-  then they will be independent of $\sigma$ (as described in Table 3.3).
-In fact they are constant, even as $sigma$ changes.
-This leads to homoskedasticity!
+However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from their corresponding ``true signal'' at each physical resolution cell level, 
+  then $\sigma$ is constant at each resolution pixel!
+Consequently $var(L_A)$ and $var(L_I)$ will be independent of $\sigma$ (as described in Table 3.3).
+In fact they are constant, which leads to homoskedasticity!
+}
 
-The second point concerns the models and their names.
-This chapter has been updated and model names are given for each to clarify the concepts.
-The confusion is understandable, and partially my fault, in not highlighting the following points.
-First there are different models being proposed, in Section 3.4.
-And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
-Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.
+\replyToComment
+    {If there are different models, the author should give a name to each of his models ...}
+    {Yes there are several models proposed and the thesis is updated with names for each of them!}
+
+%There are apparently two main concerns from Examiner No. 3's comments.
+%The first is: ``how can the statement on page 44 line 1 ... be true?''.
+%And second: ``why homoskedasticity is valid, and what are the assumption in this analysis?''
+%
+%First, the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
+%That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
+%Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
+%In fact, the third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
+%This is the assumption used in this analysis. 
+%The assumption is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
+%If $\sigma$ is not a constant, then heteroskedastic ensues.
+%The next section (i.e. Section 3.2) then outlines the effects of heteroskedasticity, 
+%  which explains the needs for logarithmic transformation.  
+%
+%The assumption described above continues to hold in Section 3.3 and, of course, table 3.3.
+%%In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
+%Under this condition, the variances of the log-transformed variables are then independent of $\sigma$.
+%The point being made in the table is that: 
+%  while variances are dependent on $\sigma$ in the original domain,
+%  in the log transformed domain, they are independent of this value.
+%
+%The assumption actually is not very restrictive.
+%It should be noted that at the level of each radar physical resolution cell, 
+%  the value measured in SAR is not deterministic.
+%For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
+%This model actually is applicable to both homogeneous and heterogeneous areas.
+%
+%Now, if the area is heterogeneous, then $\sigma$ is no longer a constant.
+%In fact, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
+%%This, of course, leads to different expression for the observable variances.
+%This leads to heteroskedasticity, 
+%  which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
+%  should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
+%However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from corresponding its ``true'' signal at each physical resolution cell level, 
+%  then they will be independent of $\sigma$ (as described in Table 3.3).
+%In fact they are constant, even as $sigma$ changes.
+%This leads to homoskedasticity!
+%
+%The second point concerns the models and their names.
+%This chapter has been updated and model names are given for each to clarify the concepts.
+%The confusion is understandable, and partially my fault, in not highlighting the following points.
+%First there are different models being proposed, in Section 3.4.
+%And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
+%Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.
 
@@
 
-Examiner No.3 expresses his doubt on two points.
-First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
-And second that $\Sigma^{-1}$ is ill-defined.
-I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
+\replyToComment
+    {When you have highly correlated data (i.e. homogeneous areas), the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1.
+Also the inverse $\Sigma^{-1}$ is ill-defined, leading to large errors in your model.
+Please justify the situations, if any, your model will not work well.}
+    {Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
 Its form, as repeated from equation 4.1, is written as:
 
-\begin{align*}
-  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-\end{align*}
+%\begin{align}
+\begin{center}
+  $pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}$
+\end{center}
+%\end{align}
 
-This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
+The equation is also ill-defined where $|\Sigma|=0$, which is also the same time that $\Sigma^{-1}$ is ``ill-defined''.
 In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
@@
 
-It is partially for the second concern that log-transformation is proposed.
+It is partially for the ``narrow PDF and large errors'' concern that log-transformation is proposed.
 Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
 Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
-In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.
+In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below:
 
-\begin{align*}
-  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
-\end{align*}
+%\begin{align*}
+\begin{center}
+  $pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)$
+\end{center}
+%\end{align*}  
+}
 
-The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
-For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
-I believe, such a change should completely addresses his concerns.
-I also made other small updates, to addresses his other various minor concerns.
+\replyToComment
+    {On page 66, $3^{rd}$ paragraph, last sentence, the author declares that ``A visual match is clearly observable ...''.
+However, in Fig 4.2(a) ...}
+    {I understand that the Examiner is concerned about the subjective quality of the ``visual match'' claim. 
+For this, the section have been updated to include now a quantitative, and hence objective, measure of match.
+These objective numbers should completely addresses his concerns, I believe.}
+
+\replyToComment
+    {The section heading 4.5.3 should be ``Effective Number-of-Looks'' instead of ``Effect Number-of-Looks''}
+    {Updated accordingly!}
+
+%Examiner No.3 expresses his doubt on two points.
+%First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
+%And second that $\Sigma^{-1}$ is ill-defined.
+%I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
+%Its form, as repeated from equation 4.1, is written as:
+%
+%\begin{align*}
+%  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
+%\end{align*}  
+%
+%This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
+%In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
+%In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
+%This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
+%
+%It is partially for the second concern that log-transformation is proposed.
+%Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
+%Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
+%In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.
+%
+%\begin{align*}
+%  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
+%\end{align*}  
+%
+%The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
+%For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
+%I believe, such a change should completely addresses his concerns.
+%I also made other small updates, to addresses his other various minor concerns.
 
 \subsubsection*{7. Chapter 5}
+
+\replyToComment
+    {Page 94, section 5.2.2.2 MSE is first used here. What is MSE? Is it Mean Squared Error? If yes, what is the reference value for calculating the MSE?}
+    {MSE does stand for Mean Squared Error, and the page is updated accordingly.
+The reference for computation in the section is the ``true signal'' $\sigma$.
+}
+
+\replyToComment
+    {Fig 5.11  shows two curves that are almost, if not exactly the same. ...
+What is the difference between them?}
+    {Fig. 5.11 shows two curves that are essentially the same.
+One of them is ``simulated result'' and the other is ``analysis formula''.
+The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
+The purpose is to show that the heuristic formula given as
+
+\begin{center}
+  $MSE = \frac{1}{(ENL-0.5)\ln^2(2)}$
+\end{center}
+
+closely tracks observable values.
+The argument is presented in a much more detailed manner in Section 5.3.2.1.
+}
 

### 2014-05-06 answer_thesis_examiner/chap1.tex
auto

@@
 \begin{longtable}[c]{p{0.08\textwidth}|p{0.08\textwidth}|p{0.36\textwidth}|p{0.36\textwidth}}
-\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
+\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections \& Comments} \\
  \hline
@@
 17 & -1 & missing explaination for $\Re,\Im$ & explaination added \\
+20 & -1 & font size for Eqns 2.10 and 2.11 is different from the rest of the thesis & This is due to space restriction, where the matrix representation in the normal font size would require a larger width that that is available in one line \\
+33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
+34 & 10 & how did you get this Eqn? & References are added for each Equation \\
+35 & 10 & which distribution is more appropriate & The most appropriate distribution is the distribution of the ``true signal'', which of course, is unknown \\
+43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
 \end{longtable}    
@@
 
-In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
-First I would like to thank Examiner No. 2 for raising such a question.
-By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
-With that corrected, let me repeat the Equations here
-
-\begin{align}
-pdf(A_x) &= \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
-pdf(A)   &= \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
-pdf(A_1) &= 2A_1 e^{-A_1^2} \\
-pdf(I)   &= \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
-\end{align}
-
-The integration of these becomes
-\begin{align}
-cdf(A_x) &= \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} &= 1 \\
-cdf(A) &= \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} &= 1\\
-cdf(A_1) &= \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} &= 1\\
-cdf(I) &= \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} &= 1
-\end{align}
-
-For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below
-
-\begin{align}
-\textbf{Normal Distribution: } & pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}} \\
-\textbf{Chi-Squared Distribution (dof=2): } & pdf(x) = \frac{e^{-x/2}}{2} \\ %pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}} \\
-\textbf{Exponential Distribution: } & pdf(x) = \lambda e^{- \lambda x}
-\end{align}
-
-\begin{align}
-\textbf{Normal Distribution: } & cdf(x) = \frac{1}{2} \left[ 1 + erf \left( \frac{x-\mu}{\sqrt{2\sigma^2}} \right) \right] \\
-\textbf{Chi-Squared Distribution (dof=2): } & cdf(x) = 1 - e^{-x/2}\\
-\textbf{Exponential Distribution: } & cdf(x) = 1 - e^{- \lambda x}
-\end{align}
-
-Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.
-
-Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:
-
-\begin{align}
-pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
-\end{align}
-
-Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:
-
-\begin{align}
-pdf(x) = \frac{e^{-x/2}}{2} 
-\end{align}
-
-Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
-Variable change theorem give us:
-
-\begin{align}
-pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
-\end{align}
-
-For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution
-
-\begin{align}
-pdf(x) = \lambda e^{- \lambda x}
-\end{align}
+%In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
+%First I would like to thank Examiner No. 2 for raising such a question.
+%By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
+%With that corrected, let me repeat the Equations here
+%
+%\begin{align}
+%pdf(A_x) &= \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
+%pdf(A)   &= \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
+%pdf(A_1) &= 2A_1 e^{-A_1^2} \\
+%pdf(I)   &= \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
+%\end{align}
+%
+%The integration of these becomes
+%\begin{align}
+%cdf(A_x) &= \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} &= 1 \\
+%cdf(A) &= \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} &= 1\\
+%cdf(A_1) &= \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} &= 1\\
+%cdf(I) &= \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} &= 1
+%\end{align}
+%
+%
+%For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below
+%
+%\begin{align}
+%\textbf{Normal Distribution: } & pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}} \\
+%\textbf{Chi-Squared Distribution (dof=2): } & pdf(x) = \frac{e^{-x/2}}{2} \\ %pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}} \\
+%\textbf{Exponential Distribution: } & pdf(x) = \lambda e^{- \lambda x}
+%\end{align}
+%
+%\begin{align}
+%\textbf{Normal Distribution: } & cdf(x) = \frac{1}{2} \left[ 1 + erf \left( \frac{x-\mu}{\sqrt{2\sigma^2}} \right) \right] \\
+%\textbf{Chi-Squared Distribution (dof=2): } & cdf(x) = 1 - e^{-x/2}\\
+%\textbf{Exponential Distribution: } & cdf(x) = 1 - e^{- \lambda x}
+%\end{align}
+%
+%Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.
+%
+%Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:
+%
+%\begin{align}
+%pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
+%\end{align}
+%
+%Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:
+%
+%\begin{align}
+%pdf(x) = \frac{e^{-x/2}}{2} 
+%\end{align}
+%
+%Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
+%Variable change theorem give us:
+%
+%\begin{align}
+%pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
+%\end{align}
+%
+%
+%For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution 
+%
+%\begin{align}
+%pdf(x) = \lambda e^{- \lambda x}
+%\end{align}

### 2014-05-08 answer_thesis_examiner/chap1.tex
auto

@@
 43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\
+76 & -4 & chapter 2 & Chapter 2 \\
+129 & 1 & cahpter 5 & Chapter 5 \\
+129 & 6 & theoretical results & theoretical contributions \\
+129 & 21 & this thesis unite & this thesis unites \\
+130 & 1 & articles that has been & articles that have been \\
+132 & 14 & an important benefits & several important benefits \\
 \end{longtable}    
 \rowcolors{1}{white}{}
-
-%In page 14 of the returned thesis, Examiner No. 1 wonders ``Does the intagration of the PDF given for $A_x, A, I$ sum up to 1?''.
-%First I would like to thank Examiner No. 2 for raising such a question.
-%By going through his question, I realized that a negative sign were missed in the equation for $pdf(A_x)$.
-%With that corrected, let me repeat the Equations here
-%
-%\begin{align}
-%pdf(A_x) &= \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}} \\
-%pdf(A)   &= \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}} \\
-%pdf(A_1) &= 2A_1 e^{-A_1^2} \\
-%pdf(I)   &= \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}}
-%\end{align}
-%
-%The integration of these becomes
-%\begin{align}
-%cdf(A_x) &= \int_{-\infty}^{\infty} \frac{1}{\sqrt{\pi} \sigma} e^{- \frac{A_x^2}{\sigma^2}}  \; \mathrm{d}A_x = \frac{1}{2} erf \left( \frac{A_x}{\sigma} \right)  \Big|_{-\infty}^{\infty} &= 1 \\
-%cdf(A) &= \int_0^{\infty} \frac{2A}{\sigma^2} e^{\frac{-A^2}{\sigma^2}}  \; \mathrm{d}A = -e^{\frac{-A^2}{\sigma^2}} \Big|_0^{\infty} &= 1\\
-%cdf(A_1) &= \int_0^{\infty} 2A_1 e^{-A_1^2} \; \mathrm{d}A_1 = -e^{-A_1^2} \Big|_0^{\infty} &= 1\\
-%cdf(I) &= \int_0^{\infty} \frac{1}{\sigma^2} e^{-\frac{I}{\sigma^2}} \; \mathrm{d}A_1 = -e^{-\frac{I}{\sigma^2}}  \Big|_0^{\infty} &= 1
-%\end{align}
-%
-%
-%For the first equation, consider the standard PDF equation for normal distribution centering around $\mu$ and having variance $\sigma$ given below
-%
-%\begin{align}
-%\textbf{Normal Distribution: } & pdf(x) = \frac{1}{\sigma \sqrt{2\pi}} e^{- \frac{(x-\mu)^2}{2 \sigma^2}} \\
-%\textbf{Chi-Squared Distribution (dof=2): } & pdf(x) = \frac{e^{-x/2}}{2} \\ %pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}} \\
-%\textbf{Exponential Distribution: } & pdf(x) = \lambda e^{- \lambda x}
-%\end{align}
-%
-%\begin{align}
-%\textbf{Normal Distribution: } & cdf(x) = \frac{1}{2} \left[ 1 + erf \left( \frac{x-\mu}{\sqrt{2\sigma^2}} \right) \right] \\
-%\textbf{Chi-Squared Distribution (dof=2): } & cdf(x) = 1 - e^{-x/2}\\
-%\textbf{Exponential Distribution: } & cdf(x) = 1 - e^{- \lambda x}
-%\end{align}
-%
-%Clearly, $A_x$ follows the normal distribution with expectation $avg(A_x)=0$ and variance $var(A_x)=\frac{\sigma}{\sqrt{2}}$.
-%
-%Next consider the standard PDF equation for chi-square distribution with $k$ degree of freedom given below:
-%
-%\begin{align}
-%pdf(x) = \frac{x^{\frac{k}{2}-1}e^{-x/2}}{\Gamma(k/2)2^{k/2}}
-%\end{align}
-%
-%Set $k=2$, and thus $\Gamma(k/2)=\Gamma(1)=1$, then:
-%
-%\begin{align}
-%pdf(x) = \frac{e^{-x/2}}{2} 
-%\end{align}
-%
-%Set $\frac{x}{2} = \frac{A^2}{\sigma^2}$ or $x = \frac{2A^2}{\sigma^2}$, thus $\frac{dx}{dA} = \frac{4A}{\sigma^2}$.
-%Variable change theorem give us:
-%
-%\begin{align}
-%pdf(A) = \frac{e^{-A^2/\sigma^2}}{2} \frac{4A}{\sigma^2} = \frac{2A}{\sigma^2} e^{-\frac{A^2}{\sigma^2}}
-%\end{align}
-%
-%
-%For the $pdf(I)$, if we set $\lambda = \frac{1}{\sigma^2}$ then the equation turns out to be the standard PDF equation for the Exponential Distribution 
-%
-%\begin{align}
-%pdf(x) = \lambda e^{- \lambda x}
-%\end{align}

### 2014-05-10 answer_thesis_examiner/chap2.tex
auto

@@
     {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
-    {TODO:CITE}
+    {Reference added: most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.}
 

### 2014-05-13 answer_thesis_examiner/chap2.tex
auto

--- 2014-05-05 answer_thesis_examiner/chap2.tex
@@
     {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}
+
+\replyToComment
+    {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
+    {Heteroskedastic and homoskedastic are terms defined in statistical context to respectively denote the fact that different sub-populations of a given samples can have different or similar variabilities.
+In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or the same variances.}
+
+\replyToComment
+    {Add references to the following statement: ``for example speckle filtering, target detection, image segmentation and other cluster, classification techniques''}
+    {References added \cite{Lopez-Martinez_2003_TGRS_2232, Alberga_2008_IJRS_4129, Conradsen_2003_TGRS_4}}
+
+\replyToComment
+    {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
+    {Reference added: most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.}
+
+\replyToComment
+    {Add references to the following statement: ``Such use, however, is known to be not very robust for these so-called heavy detailed distributions.''}
+    {Reference added: \cite{McElroy_Econometric_2002}}
+
+\replyToComment
+    {Add references to the following statement: ``it is known that such use should be avoided in preference to a ratio-based descrimination measure.''}
+    {Reference added: \cite{Rignot_1993_TGRS_896}}
+
+\replyToComment
+    {Add references to the following statement: ``The Ordinary Least Square (OLS) is widely used as the best evaluation criteria, which is probably due to the Gauss Markov theorem.''}
+    {Reference added \cite{Furno_1991_JStatCompSimul}}
+
+\replyToComment
+    {Add references to the following statement: ``violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.''}
+    {References added \cite{Gagnon_SPIEProc_1997, Argenti_GRSM_2013}}
+
+\replyToComment
+    {It would be easier to read and refer if all the Equations are labelled accordingly.}
+    {All equations in the thesis has been updated with labels.}
+
+\textbf{Errata Sheet}
 

### 2014-05-13 answer_thesis_examiner/chap3.tex
auto

@@
 
-Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
-The reference for computation in the section is the ``true signal'' $\sigma$.
+\replyToComment
+    {Fig 5.12: shows the MSE and speckle suppression power of your f-MLE filters for homogeneous area. How does it compare with the other state-of-the-art speckle filters?}
+    {
+      It should be noted that the f-MLE filters are iterative filters, where the number of iteration is configurable.
+      Thus assuming prior knowledge of homogeneous area, by increasing the iteration number, the speckle suppression power can go arbitrarily better!
+      But of course, such a knowledge is only theoretical and it is impossible to hold true in real-life scenarios.
 
-Fig. 5.11 shows two curves that are essentially the same.
-One of them is ``simulated result'' and the other is ``analysis formula''.
-The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
-The purpose is to show that the heuristic formula given as
-
-\begin{align*}
-  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
-\end{align*}
-
-closely tracks observable values.
-Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
-
-Examiner No 3 also expresses his curiosity to see ``how the f-MLE filter will compare with other state-of-the-art-filters''.
-While, I am also eager to see, and to some extend to prove, the good results of my proposed f-MLE filter,
+While, I am also eager to see, and to some extend to prove, the good results of my proposed f-MLE filter in rigorious manner,
   I have decided not to include it in the section 5.3, where the performance of many different filters are reviewed.
@@
 It is only the avenue to demonstrate the benefits of the proposed models for SAR \& POLSAR data of the thesis.
+    }
+
+\replyToComment
+    {Please label the two curves in Fig. 5.13}
+    {The labels are added into the figure.}
+
+%Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
+%The reference for computation in the section is the ``true signal'' $\sigma$.
+%
+%Fig. 5.11 shows two curves that are essentially the same.
+%One of them is ``simulated result'' and the other is ``analysis formula''.
+%The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
+%The purpose is to show that the heuristic formula given as
+%
+%\begin{align*}
+%  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
+%\end{align*}  
+%
+%closely tracks observable values.
+%Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
+%
+%Examiner No 3 also expresses his curiosity to see ``how the f-MLE filter will compare with other state-of-the-art-filters''.
 

### 2014-05-14 answer_thesis_examiner/chap3.tex
auto

@@
 
-In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
-To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
+\replyToComment
+    {If the proposed models are ``far from complete'', how can it be an accurate representation of the data.}
+    {the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
 Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
@@
   for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
+}
+
+%In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
+%To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
+%Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
+%They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
+%  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
+
+\replyToComment
+    {Page 133, line 3: ``it is definitely not fully representative of the data.''.
+      So what kind of error it cause?
+      How will it affects the use of your model?
+      It is neccessary to point out what are the shortcomings and how it affects the use of your model!
+    }
+    {
+      The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
+}
 

### 2014-05-14 answer_thesis_examiner/chap3.tex
auto

@@
 \replyToComment
-    {Page 133, line 3: ``it is definitely not fully representative of the data.''.
-      So what kind of error it cause?
-      How will it affects the use of your model?
+    {
+      %Page 133, line 3: ``it is definitely not fully representative of the data.''.
+      %So what kind of error it cause?
+      %How will it affects the use of your model?
       It is neccessary to point out what are the shortcomings and how it affects the use of your model!
@@
       The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
+      This restrict the use of the model to a class of problem where a single scalar decision, probability, distance or number is required to represent the complex dataset.
     }
 
-The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
-He went on to ask: ``What kind of eror will it cause?''.
-To this the answer is that the model inherently suffers from loss of dimension
-  where the full data is multi-dimensional and the proposed models are scalar.
+\replyToComment
+    {
+      A thesis is supposed to persuade others to believe what you have proposed and to use it.
+      How can you expect others to believe in you, when you don't know what most of what it is supposed to do?
+    }
+    {
+      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
+      The thesis also includes a chapter detailing multiple different applications of the proposed models.
+      What else the proposed models can applied on, I feel, is a totally different matter.
+      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
+    }
 
-Besides these main points, the chapter is updated to increase its pursuasive power.
-For example: the sentence in line 1, page 133, section 6.3 is removed.
-Or a list of achievements has been included in this chapter.
+\replyToComment
+    {
+      On page 10, Chapter 1, the author specified a list of ``results to be obtained''.
+      However, in the conclusion chapter, there is no corresponding list of achievements ...
+    }
+    {
+      A corresponding list of achievement has been included showing that all set-out objectives are met.
+    }
+
+%The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
+%He went on to ask: ``What kind of eror will it cause?''.
+%To this the answer is that the model inherently suffers from loss of dimension
+%  where the full data is multi-dimensional and the proposed models are scalar.
+%
+%Besides these main points, the chapter is updated to increase its pursuasive power.
+%For example: the sentence in line 1, page 133, section 6.3 is removed.
+%Or a list of achievements has been included in this chapter.
 

### 2014-05-19 answer_thesis_examiner/chap3.tex
auto

@@
     {
-      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
-      The thesis also includes a chapter detailing multiple different applications of the proposed models.
-      What else the proposed models can applied on, I feel, is a totally different matter.
-      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
+     To persuade people into believing its proposed models, the thesis follows rigorous scientific methodologies. 
+     They include theoretical mathematics transformations and realistic hypothesis-testing experiments.
+      The thesis also includes a chapter detailing several different applications of the proposed models.
+      These applications, due to the various practical constraint, are unlikely to be exhaustive over all future applications.
+
+In fact, the two topics of 1) what else the proposed models can be applied on and 2) if the proposed models are to be taken as true, I feel, are not much related.
+      In the end, Einstein probably did not foresee that his theories were used to create atomic bombs and killed thousands of people.
+This lack of foresight however does not cast any doubt on his contribution to our scientific progress.
     }
@@
 
-While the conference papers have been published and the journal paper submitted,
-  their copies have been removed from this section.
+\replyToComment
+    {It is not ususal to attach copies of academic papers in the Appendix.}
+    {The attached papers were removed from the Appendix.}
+
+%While the conference papers have been published and the journal paper submitted,
+%  their copies have been removed from this section.
 

### 2014-05-21 answer_thesis_examiner/chap1.tex
Ian's changes

@@
   but also helpful suggestions inside the original thesis.
-There was no direct question in the report, and followings are my replies to his comments in the returned thesis.
+
+The examiner asked no direct question in his comments, so the following are my replies to his comments as listed in the returned thesis:
 
@@
 6 & 5 & many fold & manyfold \\
-14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in numbers and independent in nature, \\
+14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in number and independent in nature, \\
+%**IVM: the above should be 'number' (you had written 'numbers')
 14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
+%**IVM: did you mention this in the thesis? If so, it might be good to mention.
 \end{longtable}    
@@
 33 & -10 & Eqn. [2.15) & Eqn. 2.15 \\
-34 & 10 & how did you get this Eqn? & References are added for each Equation \\
-35 & 10 & which distribution is more appropriate & The most appropriate distribution is the distribution of the ``true signal'', which of course, is unknown \\
+34 & 10 & how did you get this Eqn? & References have now been added to show the source of the equation \\
+35 & 10 & which distribution is more appropriate & The most appropriate distribution is that of the ``true signal'', which of course, is unknown, so we are trying to model it \\
 43 & -3 & $pdf(A_1)=2A_1e^{A_1^2}$ & $pdf(A_1)=2A_1e^{-A_1^2}$ \\

### 2014-05-21 answer_thesis_examiner/chap2.tex
Ian's changes

@@
 
+I would like to thank Examiner 2 for examining the thesis carefully. I have listed the comments below, and responded to each one. I have also rectified all of the items in the errata.
+
 \replyToComment
     {Sec 1.1 and 1.2 should be reviewed again ... with proper citations on the background studies.}
-    {The sections were reviewed and several citations were added}
+    {This has been done: both sections have been reviewed with several new citations added}
 
@@
     {The paragraph were removed?}
-
+%**IVM: why the question mark??
 \replyToComment
     {The achievement of objectives should (also) be stated in the conclusion chapter. }
-    {These were added into the conclusion chapter (``with proper justfications based on experimental results and findings'').}
+    {These have now been added into the conclusion chapter (with proper justfications based on experimental results and findings).}
 
@@
     {Replace the word ``theory'' with ``model'' throughout the thesis}
-    {Search and replace operation done!}
+    {This has been done.}
+%**IVM better not use humour... not all examiners have a sense of humour!!    {Search and replace operation done!}
 
@@
 The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
-That is: the proposed models by nature are applicable to multi-dimensional data and thus they are applicable to POLSAR data.
-To show that the proposed models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1.
+That is: the proposed models by nature are applicable to multi-dimensional data and thus to POLSAR data.
+To show that the proposed (multidimensional) models are also applicable to SAR data, the dimension parameters in these models are collapsed into 1.
 The thesis subsequently shows that they match perfectly with existing SAR models.
@@
     {
-      The thesis clearly recognizes that log-transformation will introduce bias.
-      It also shows that MSE evaluation does inherently include bias evaluation.
+      It is true. In fact, the thesis does say that log-transformation will introduce bias. %**IVM
+      It also shows that MSE evaluation does inherently include a bias evaluation.
       In fact, the thesis argues that MSE evaluation has two components: 1.
 bias evaluation and 2.
-variance evaluation, which for evaluating the performance of SAR speckle filters translates into 1.
+variance evaluation, which, for evaluating the performance of SAR speckle filters translates into two criteria: 1.
 radiometric preservation and 2.
@@
     {A more comprehensive review of the relevant SAR/POLSAR speckle filters should be included.}
-    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}}
+    {The most recent review \cite{Argenti_GRSM_2013} has been included together with several other publications \cite{Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}, all discussed within the thesis.}
 
 \replyToComment
-    {Whereever possible, samples of SAR/POLSAR images with these three types of features (i.e.
+    {Wherever possible, samples of SAR/POLSAR images with these three types of features (i.e.
 homogeneous, textured and strong scatterer) should be used to evaluate the effectiveness of the proposed models.}
-    {In the section to evaluate speckle filters, various different patterns had been studied.
+    {In the section on evaluating speckle filters, various different patterns have been studied.
 Also the MSE evaluation which includes bias and variance evaluation are shown to be able to evaluate the effectiveness of different speckle filters in terms of radiometric preservation and speckle noise reduction respectively.}
+%**IVM: Hai - do you think that this answers the examiners question? Maybe he is looking for visual examples?
 
@@
     {The work done has great potential to be published in high impact factor journals such as JSTAR, IJRS and PIER}
-    {I appreciate the Examiner's vote of confidence. Portions of the thesis has been extracted out as academic papers and submitted for peer-review.}
+    {I appreciate the Examiner's vote of confidence. Portions of the work in this thesis have been written up as academic papers and submitted for peer-review.}
 
@@
     {Define terms heteroskedastic and homoskedastic in the context of SAR imagery.}
-    {Heteroskedastic and homoskedastic are terms defined in statistical context to respectively denote the fact that different sub-populations of a given samples can have different or similar variabilities.
-In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or the same variances.}
+    {Heteroskedastic and homoskedastic are terms defined in a statistical context to respectively denote the fact that different sub-populations of given samples can have different or similar variabilities.
+In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}  %**IVM added the word 'sample'
 
@@
     {Add references to the following statement: ``most of these data processing techniques are traditionally designed for additive and homoskedastic data.''}
-    {Reference added: most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.}
+    {Reference added: \cite{Dutch_LNCS_2004}.}
 
@@
     {It would be easier to read and refer if all the Equations are labelled accordingly.}
-    {All equations in the thesis has been updated with labels.}
+    {All equations in the thesis have been updated with labels. Originally I had used labels only for equations which were important or were referred to later.}
 
@@
 35 & 11 & back scattering & backscattering \\
-36 & 10 & literatured & literatures \\
+36 & 10 & literatured & literature \\   %**IVM: Hai, please change the thesis to "literature" instead of "literatures"
 37 & -2 & Proposed bu & proposed by \\
 39 & 4 & dependence & dependency \\
-44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence is rephrased \\
+44 & -1 & The nature of SAR is ... heteroskedastic heterogeneously & the sentence has been rephrased \\
 46 & 4 & most known common & most commonly known \\
@@
 89 & - & Figure 5.6 - subtitle (a) & (a) is removed \\
-91 & - & Figure 5.8: Legends are too small to read & They are enlarged \\
+91 & - & Figure 5.8: Legends are too small to read & They have been enlarged \\
 95 & - & Figure 5.12 & Use the same scale for  y axis (i.e MSE 0:1) across all the plots \\
 103 & 22 & related to the ENL index. over & related to the ENL index over \\
-104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\
+104 & 13 & Equation 5.3.2.1 & The number is corrected to (?) \\  %**IVM: something missing here??
 109 & 8 & Figs. 5.21c and 5.21d allows & Fig 5.21(a) and Fig 5.21(d) allow \\
@@
 In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
-I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
+%**IVM: I would skip this-> I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
 I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.

### 2014-05-21 answer_thesis_examiner/chap3.tex
Ian's changes

--- 2014-05-14 answer_thesis_examiner/chap3.tex
@@
 
-Since Examiner No. 3 presented his comments and suggestions in the order of the thesis' chapters, 
-  I would follow his suite.
+I would like to thank Examiner No. 3 for the constructive comments and suggestions. Since these were presented in the order of the thesis' chapters, I will follow this sequence in my responses below:
 
@@
     {Page ii of the Contents section is missing}
-    {Page numbers are added for Contents section}
+    {Page numbers have been added for the Contents section}
 
@@
     {Since these models are the key contributions of the thesis, it would be good to give a separate name to each of these models}
-    {The models' names are added into the abstract}
+    {The models' names have been added into the abstract}
 
@@
     {The abstract lists the benefits of these models but not the shortcomings.}
-    {The shortcomings have also been included into the abstract.}
+    {The shortcomings have also been included into the abstract now.}
 
@@
     {Table captions appears at the top of a table, rather than below it}
-    {The suggestion has been updated in this chapter, as well as through out the whole thesis}
+    {This is typical of IEEE publications, so we adopted it in the thesis. However we tried this stylistic suggestion and it looks good, so it has been adopted for the revied thesis.}
 
@@
     {No references throughout this chapter.}
-    {References have been included in this chapter to increase its persuasion power.}
+    {References have been included in this chapter, increasing its persuasive power.}
 
 \replyToComment
-    {you are trying to propose an additive and homoskedastic model for the data. What makes you think that thsi model is appropriate?}
+    {you are trying to propose an additive and homoskedastic model for the data. What makes you think that this model is appropriate?}
     {Before an answer is laid out, I wish to make a few points.
-First, I thank the Examiner to raise this question, which no doubt is an important one. 
-Second, while it is important to judge the end result, 
-  I am not quite sure that should be done at the very first chapter.
-In fact, a large portion of the final chapter is devoted towards such a discussion.
+Firstly, I do think that the Examiner has raise a good and important question here.
+However the goodness of the models are, at the end of the day, judged mainly by their performance in practice.
+In turn, the performance is found from the outcome of various experimental evaluations and after developing some mathematics.
+But the experiments and mathematics require quite a lot of theoretical explanation and background discussion before they are presented -- and this is what forms the main bulk of the thesis.
+Because of this necessary sequence, I don't think that the demonstration of the models appropriateness can be tackled in the very first chapter, although the thesis can (and does) reveal early on that the models will (later) be shown to work well.
+%**IVM: Hai, I rewrote this quite a lot.
+Can you please ensure that somewhere at the front of the thesis it says something like "this model will be shown, by experimental evaluation presented later in this thesis, to be an appropriate and useful model"
 
-To directly address the Examiner's concern, let me iterate a few points that has been noted in the thesis.
+To directly address the Examiner's concern, let me mention a few points that have been noted earlier in the thesis.
 First the generic model proposed in this thesis is applicable to multi-dimensional POLSAR data.
-Second, when the multi-dimensional data is collapsed into one dimensional, 
+Second, when the multi-dimensional data is collapsed into one dimension, 
   the specific case of the proposed model matches perfectly with the model proposed for SAR by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
-Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.
+Thus -- even before performing a detailed evaluation -- there is good evidence that the proposed generic model is at least as appropriate as the widely-accepted model cited above.
+All of this discussion is in the revised thesis.
 }
@@
     {Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work}
-    {In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
-Still, this chapter is heavily updated so that: 
+    { %In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
+    In the end I could not move the theory section away from a discussion of related work, because so much of the theory comes from the related work (i.e.
+it is not possible to cleanly separate these topics).
+    But actually I believe the examiners request is really that "more space can be dedicated to the discussion of related work".
+So instead I heavily updated the chapter to do exactly what the examiner requests.
+For example:
 \vspace{-3mm}
 \begin{enumerate}
-  \item Section 2.1 is shortened considerably and 
-  \item Section 2.2 is extended significantly. 
+  \item Section 2.1 (basic theory about the data and older related work) is shortened to 12 pages and 
+  \item Section 2.2 (newer related work and extended theory) is extended significantly to 13 pages. 
 \end{enumerate}
-These editions, I believe, lead to a better balance between describing the nature of the data and reviewing the related work.
+%**IVM: Hai, can you please check that what I wrote in the brackets () on the above 2 lines is correct?
+I believe that this rewriting leads to a better balance between describing the nature of the data and reviewing the related work.
 }
@@
     {how can the statement on page 44 line 1 ``... intensity are equal to a scaled version of these unit variables, specifically $A=\sigma A_1$ and $I=\sigma^2 I_1$'' be true?}
-    {the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
-That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
-Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
-In fact, line 7 page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area).
+    {the statement in page 44 line 1 should be interpreted strictly in the context that precedes it. 
+Mathematically speaking, $\sigma$ is just a constant, which makes the statement true.
+Any resemblance of this to the SAR signal will only established in the next paragraph onwards.
+In fact, line 7 page 44 clearly indicates under what circumstances that $\sigma$ can be considered constant (i.e. namely across spatially homogeneous areas).
 }
@@
     {Spartial homogeneity is the assumption used in the analysis thus far. 
-Its limitation is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
+Its limitation is acknowledged in the very next sentence, as the Examiner No. 3 pointed out: ``Over heterogeneous areas, ... $\sigma$ varies significantly ...''.
 
-This assumption actually is not very restrictive.
-It should be noted that at the level of each radar physical resolution cell, 
-  the value measured in SAR is not deterministic.
-For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
+This assumption is actually not very restrictive.
+It should be noted that at the level of each physical radar resolution cell, the value measured in SAR is not deterministic.
+For all practical purposes, the single measured value is considered to be the result of a stochastic process, which has one ``true'' signal, namely $\sigma$.
 In that sense, the assumption is actually applicable to both homogeneous and heterogeneous areas.
+%**IVM: Hai I'm not sure I follow your final sentence - if the assumption is homoskedacity, how can that also be applicable to heterogeneous areas?
+Or do you mean another assuption - the assumption of a stochastic process?
 }
@@
     {If $\sigma$ is not a constant, then $var(L_A)$ and $var(L_I)$ cannot be homoskedastic}
-    {In general, the imaging area is heterogeneous, then $\sigma$ is no longer a constant from one resolution pixel to the next.
+    {If the imaging area is heterogeneous, then $\sigma$ is no longer a constant from one resolution pixel to the next.
 That much is clear.
 Then, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-This changing $\sigma$ also leads to heteroskedasticity, 
-  which the Examiner correctly pointed out in his comment
+This non-constant $\sigma$ also leads to heteroskedasticity,  which the Examiner correctly pointed out in his comment
 %``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
@@
     {If there are different models, the author should give a name to each of his models ...}
-    {Yes there are several models proposed and the thesis is updated with names for each of them!}
+    {Yes there are several models proposed and the thesis has been updated with names for each of them!}
 
@@
 
-The equation is also ill-defined where $|\Sigma|=0$, which is also the same time that $\Sigma^{-1}$ is ``ill-defined''.
-In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
+The equation is also ill-defined where $|\Sigma|=0$, which is also the same time that $\Sigma^{-1}$ is ill-defined.
+In other words, the proposed model has the same assumption and validity of the widely-accepted circular complex Gaussian distribution model.
 In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
-This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
+Actually, this restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
+%**IVM: Hai, maybe you can change the sentence in the thesis to say something like ``in common with other models based on complex Gaussian distribution, the model will be ill-defined where $|\Sigma|=0$''.
 
-It is partially for the ``narrow PDF and large errors'' concern that log-transformation is proposed.
-Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
-Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
+In fact, it was partially for the ``narrow PDF and large errors'' concern that I originally proposed the use of log-transformation.
+Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found to be extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
+The log transformed domain not only changes the nature of the noise from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much wider space $(-\infty,0)$.
 In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below:
@@
     {I understand that the Examiner is concerned about the subjective quality of the ``visual match'' claim. 
-For this, the section have been updated to include now a quantitative, and hence objective, measure of match.
-These objective numbers should completely addresses his concerns, I believe.}
+Because of this, the section has now been updated so that every `visual match' also includes a quantitative, and hence objective, measure of similarity.
+These objective scores -- which do indicate good matches -- should completely addresses these concerns, I believe.}
 
@@
     {
-      It should be noted that the f-MLE filters are iterative filters, where the number of iteration is configurable.
-      Thus assuming prior knowledge of homogeneous area, by increasing the iteration number, the speckle suppression power can go arbitrarily better!
-      But of course, such a knowledge is only theoretical and it is impossible to hold true in real-life scenarios.
+      It should be noted that the f-MLE filters are iterative filters, where the number of iterations is configurable.
+      Thus assuming prior knowledge of a homogeneous area, by increasing the iteration number, the speckle suppression power can be improved.
+      But of course, such knowledge is only theoretical and may be difficult to obtain for real-life scenarios.
 
-While, I am also eager to see, and to some extend to prove, the good results of my proposed f-MLE filter in rigorious manner,
-  I have decided not to include it in the section 5.3, where the performance of many different filters are reviewed.
+While, I am also eager to see, and to some extent to prove, the good results of my proposed f-MLE filter in a rigorous manner,
+  I have decided not to include this in the section 5.3, where the performance of many different filters are reviewed.
 There are a few reasons for such a decision.
-First, in the section I am proposing a new way to evaluate speckle filters.
-And instead of at the same time discussing the performance of f-MLE filter, I wish to focus on that topic exclusively.
-Second, assuming the performance of f-MLE filter is included and found to be superior than others,
-  such a result can be easily refuted.
-That is because I was proposing both new speckle filters and a new approach to evaluate speckle filters,
-  which I wish to, as much as possible, keeping them independently of each other.
-Last but not least, as noted by all Examiners and myself included, speckle filtering is not the main topic of the thesis.
-It is only the avenue to demonstrate the benefits of the proposed models for SAR \& POLSAR data of the thesis.
+First, the focus of this section is to propose a new way to evaluate speckle filters, \textbf{not} to propose any new speckle filter.
+Instead of discussing the performance of one particular filter (f-MLE), I wish to focus more exclusively on the topic of \textit{how} to evaluate such filters.
+Second, assuming the performance of the f-MLE filter is included and found to be superior than others,
+  then such a result would be highly suspect
+because I would in effect be proposing both a speckle filter as well as a new approach to evaluate speckle filters.
+As much as possible, I would like to keep these issues independently of each other.
+Last but not least, as noted by all Examiners and myself (in the thesis abstract, introduction and conclusion), speckle filtering is not the main topic of the thesis.
+It is only one avenue to demonstrate the benefits of the proposed models for SAR \& POLSAR data.
     }
@@
     {Please label the two curves in Fig. 5.13}
-    {The labels are added into the figure.}
+    {The labels have now been added into the figure.}
 
@@
     {If the proposed models are ``far from complete'', how can it be an accurate representation of the data.}
-    {the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
-Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
-They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
-  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
+    {The proposed models in this thesis do not aim to become accurate representations of all data, or to be fully representative of all data.
+Rather, they are proposed as being highly representative (and possibly the \textit{most representative} scalar models) for the multi-dimensional POLSAR data.
+Despite not being perfect, the models are very useful, since scalar models are often needed when scalar decisions are required,
+  for example, in answering the question: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
 }
@@
       %How will it affects the use of your model?
-      It is neccessary to point out what are the shortcomings and how it affects the use of your model!
+      It is necessary to point out what are the shortcomings and how it affects the use of your model!
     }
     {
-      The thesis clearly indicated that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
-      This restrict the use of the model to a class of problem where a single scalar decision, probability, distance or number is required to represent the complex dataset.
+      The thesis very clearly states %**IVM: Hai, can you remember where? Good to put a referene here
+       that the proposed models inherently suffer from loss of dimension where the full data is multi-dimensional and the proposed models are scalar.
+      This restricts the use of the model to a class of problems where a single scalar decision, probability, distance or number is required to represent the complex dataset.
     }
@@
     {
-      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
-      The thesis also includes a chapter detailing multiple different applications of the proposed models.
-      What else the proposed models can applied on, I feel, is a totally different matter.
-      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
+     To persuade people into believing its proposed models, this thesis tries to maintain and follow a very rigorous scientific methodology. 
+     This includes theoretical mathematical transformations and realistic hypothesis-testing experiments.
+     The theory, mathematics, objective analysis and subjective evaluations all agree, and demonstrate the validity of the models.
+      The thesis also includes a chapter detailing several different applications for the proposed models, but with the disclaimer that the examiner has taken exception to.
+
+      To explain this, firstly it is completely impossible for one thesis to include a discussion on \textit{all possible uses} of something as general as a model such as this.
+Therefore, the thesis concentrates on what are likely to be the most important uses.
+These also happen to coincide with the applications that the author was working on when he originally derived the models.
+      Secondly, if other researchers find these models to be useful, they will apply them in many different situations.
+Maybe more than we can imagine at present.
+Therefore it is only being honest to acknowledge this fact in the thesis.
+
+Actually, the two questions of (1) what else can the proposed models be used for and (2) should the proposed models be taken as true, are not really related.
+%      In the end, Einstein probably did not foresee that his theories were used to create atomic bombs and killed thousands of people.
+%This lack of foresight however does not cast any doubt on his contribution to our scientific progress.
+%**IVM: Hai, best not to bring up Einstein here...
+
+In summary, the thesis contains a thorough investigation of the models, and presents results that are both consistent, positive and indicative. This should be highly persuasive.
+At the same time, the thesis makes an effort to evaluate the application of the models in the most important usage domains that the author has identified, as well as to address the use of the models beyond that.
     }
@@
     {
-      A corresponding list of achievement has been included showing that all set-out objectives are met.
+      A corresponding list of achievements has been included in the conclusion, showing that all objectives were met.
     }
@@
 
-While the conference papers have been published and the journal paper submitted,
-  their copies have been removed from this section.
+\replyToComment
+    {It is not usual to attach copies of academic papers in the Appendix.}
+    {They were included for the convenience of the examiners and other readers. They have now been removed from the Appendix.}
+
+%While the conference papers have been published and the journal paper submitted,
+%  their copies have been removed from this section.
 

### 2014-05-22 answer_thesis_examiner/chap3.tex
Auto

@@
 
-%Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
-%Still minor editions have been included to address his  other concerns:
-
-%I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
-%Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
-
-%\begin{itemize}
-%  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
-%  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
-%  \item \textbf{Some page number missing: } Updated. 
-%  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
-%\end{itemize}
-
 \subsubsection*{2. Abstract}
@@
     {The shortcomings have also been included into the abstract now.}
-
-%The abstract has been updated so that:
-%\begin{enumerate}[topsep=0pt]
-%  \item Each of the proposed models have their own name and
-%  \item Not only the benefits of the proposed models are listed, but so are their shortcomings.
-%\end{enumerate}
 
@@
 
-%The examiner suggests that ``Table captions appears at the top of a table, rather than below it''. 
-%This suggestion has been updated in this chapter, as well as through out the whole thesis.
-%Also references are included to increase the persuasion power of the claims.
-%The list of publication is also now included in this chapter, in addition to the existing one found in the final chapter.
-%
-%At this juncture, I would also wish to address one of Examiner No. 3's main concern.
-%He wonders: ``What makes you think that this model is appropriate?''.
-%Before the answer is laid out , I wish to make a few points.
-%First, I thank the Examiner to raise this question, which no doubt is an important one. 
-%Second, while it is important to judge the end result, 
-%  I am not quite sure that should be done at the very first chapter.
-%In fact, a large portion of the final chapter is devoted towards such a discussion.
-%
-%To directly address the Examiner's concern, let me iterate a few points that has been noted in the thesis.
-%First the generic model proposed in this thesis is applicable to multi-dimensional POLSAR data.
-%Second, when the multi-dimensional data is collapsed into one dimensional, 
-%  the specific case of the proposed model matches perfectly with the model proposed for SAR by Arsenault \cite{Arsenault_JOptSocAm_1976}. 
-%Thus, I believe, the proposed generic model is at least as appropriate as the widely-accepted model cited above.
-
-%It is termed as: ``it doesn't mean that by fitting a homoskedastic model to heteroskedastic data, these algorithm will give correct results''.
-%The approach described in this thesis differs slightly from ``fitting a homoskedastic model to heteroskedastic data''.
-%Here, I proposed to used log-transformation which has long been noted as converting the data from mutiplicative to additive domain.
-%The model for the data in this additive domain has been derived and accepted in \cite{Arsenault_JOptSocAm_1976}.
-%My work, in simple terms, suggests that in addition to additive properties, the transformed domain also exhibits homoskedastic properties as contrast to the heteroskedastic properties in the original domain.
-%These properties are investigated in this thesis to show that it does offers several benefits (for example: in designing and evaluating speckle filters).
-%It should be noted that the model for SAR used in this thesis is exactly the same as the additive model proposed by Arsenault \cite{Arsenault_JOptSocAm_1976} and is mathematically equivalent to the model multiplicative model for SAR data in its original domain.
-
 \subsubsection*{4. Chapter 2}
@@
     {Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work}
-    { %In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
-    In the end I could not move the theory section away from a discussion of related work, because so much of the theory comes from the related work (i.e.
+    { In the end I could not move the theory section away from a discussion of related work, because so much of the theory comes from the related work (i.e.
 it is not possible to cleanly separate these topics).
@@
 \end{enumerate}
-%**IVM: Hai, can you please check that what I wrote in the brackets () on the above 2 lines is correct?
 I believe that this rewriting leads to a better balance between describing the nature of the data and reviewing the related work.
 }
-
-%For Chapter 2, Examiner No. 3's suggests: ``Perhaps the theory section can be moved to a separate chapter, so that more space can be dedicated to the discussion of related work''.
-%In a bid of not confusing other examiners, however, I have decided not to move the theory section into a separate chapter.
-%Still, this chapter is heavily updated so that: 
-%\vspace{-3mm}
-%\begin{enumerate}
-%  \item Section 2.1 is shortened considerably and 
-%  \item Section 2.2 is extended significantly. 
-%\end{enumerate}
-%
-%This I believe leads to a better balance between describing the nature of the data and reviewing the related work.
-%This also help growing the space dedicated to the discussion of ``Other approaches that have recently been pursued in the research community (SAR speckle filters)''.
 
@@
 For all practical purposes, the single measured value is considered to be the result of a stochastic process, which has one ``true'' signal, namely $\sigma$.
-In that sense, the assumption is actually applicable to both homogeneous and heterogeneous areas.
-%**IVM: Hai I'm not sure I follow your final sentence - if the assumption is homoskedacity, how can that also be applicable to heterogeneous areas?
-Or do you mean another assuption - the assumption of a stochastic process?
+In that sense, the assumption (of a single stochastic process) is actually applicable to both homogeneous and heterogeneous areas. 
 }
@@
 Then, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-This non-constant $\sigma$ also leads to heteroskedasticity,  which the Examiner correctly pointed out in his comment
+This non-constant $\sigma$ also leads to heteroskedasticity, 
 %``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
   should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
+And the Examiner correctly pointed out in his comment. 
 However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from their corresponding ``true signal'' at each physical resolution cell level, 
@@
 
-%There are apparently two main concerns from Examiner No. 3's comments.
-%The first is: ``how can the statement on page 44 line 1 ... be true?''.
-%And second: ``why homoskedasticity is valid, and what are the assumption in this analysis?''
-%
-%First, the statement in page 44 line 1 should be intepreted strictly in the context of what preceeds it. 
-%That is mathematically  speaking $\sigma$ is just a mathematical constant, which makes the statement true. 
-%Any resemblence of it with the SAR signal is only established in the next paragraph onwards.
-%In fact, the third line of the second paragraph in page 44 clearly indicated where $\sigma$ can be considered as constant (i.e. spatial homogeneous area or at each resolution cell).
-%This is the assumption used in this analysis. 
-%The assumption is acknowledged in the very next sentence, as the Examiner No. 3 pointed out precisely: ``Over heterogeneous area, ... $\sigma$ varies significantly ...''.
-%If $\sigma$ is not a constant, then heteroskedastic ensues.
-%The next section (i.e. Section 3.2) then outlines the effects of heteroskedasticity, 
-%  which explains the needs for logarithmic transformation.  
-%
-%The assumption described above continues to hold in Section 3.3 and, of course, table 3.3.
-%%In that very same vein, table 3.3 should be viewed under the assumption that $\sigma$ is constant (either in homogeneous area or in a single resolution cell).
-%Under this condition, the variances of the log-transformed variables are then independent of $\sigma$.
-%The point being made in the table is that: 
-%  while variances are dependent on $\sigma$ in the original domain,
-%  in the log transformed domain, they are independent of this value.
-%
-%The assumption actually is not very restrictive.
-%It should be noted that at the level of each radar physical resolution cell, 
-%  the value measured in SAR is not deterministic.
-%For all practical purposes, the single measured value is to be considered as the result of a stochastic process, with one ``true'' signal $\sigma$.
-%This model actually is applicable to both homogeneous and heterogeneous areas.
-%
-%Now, if the area is heterogeneous, then $\sigma$ is no longer a constant.
-%In fact, as reviewed in Chapter 2, there are many different ways to model $\sigma$ which in turns leads to many different models for the observable magnitude.
-%%This, of course, leads to different expression for the observable variances.
-%This leads to heteroskedasticity, 
-%  which the Examiner correctly pointed out ``$var(L_A)$ and $var(L_I)$ cannot be homoskedastic'', 
-%  should we consider ``$var(L_A)$ and $var(L_I)$'' as the variation of the observables in an area.
-%However, if we consider ``$var(L_A)$ and $var(L_I)$'' as the deviation of the observables from corresponding its ``true'' signal at each physical resolution cell level, 
-%  then they will be independent of $\sigma$ (as described in Table 3.3).
-%In fact they are constant, even as $sigma$ changes.
-%This leads to homoskedasticity!
-%
-%The second point concerns the models and their names.
-%This chapter has been updated and model names are given for each to clarify the concepts.
-%The confusion is understandable, and partially my fault, in not highlighting the following points.
-%First there are different models being proposed, in Section 3.4.
-%And second, they are all however derived based on ONE basic model: the one based on ``the base-2 log-transformation of the SAR data.''
-%Finally, there are differences in each of the models, even though, whether these differences are significant or not is, to be honest, rather subjective at my current state of understanding.
-
 \subsubsection*{6. Chapter 4}
@@
 
-%\begin{align}
 \begin{center}
@@
 \end{center}
-%\end{align}
 
@@
 
-%\begin{align*}
 \begin{center}
@@
 \end{center}
-%\end{align*}  
 }
@@
     {Updated accordingly!}
-
-%Examiner No.3 expresses his doubt on two points.
-%First, that ``the determinant $|\Sigma|$ will be very small, leading to a very narrow PDF in Equation 4.1''.
-%And second that $\Sigma^{-1}$ is ill-defined.
-%I wish to highlight that Equation 4.1 is the PDF for the circular complex Gaussian distribution, which is widely used in POLSAR.
-%Its form, as repeated from equation 4.1, is written as:
-%
-%\begin{align*}
-%  pdf(s;\Sigma)=\frac{1}{\pi^d |\Sigma|} e^{-s^{*T}\Sigma^{-1}s}
-%\end{align*}  
-%
-%This equation is also ill-defined where $|\Sigma|=0$, which is also the only time that $\Sigma^{-1}$ is ``ill-defined''.
-%In other words, the models proposed has the same assumption and validity with the widely-accepted circular complex Gaussian distribution model.
-%In POLSAR, $|\Sigma|=0$ most commonly happens when the dataset is in Single-Look format.
-%This restriction is clearly stated in the sentence that follows Equation 4.1: ``the covariance matrix is only defined on multiple data-points''.
-%
-%It is partially for the second concern that log-transformation is proposed.
-%Since the original domain is multiplicative, the range of small values is, as also observed by Examiner No. 3, commonly found but extremely limited ($|\Sigma|$ ranges from $0+$ to $1$).
-%Log transformed domain not only changes the nature from multiplicative to additive, but also give this ``small'' range $(0,1)$ a much widely space $(-\infty,0)$.
-%In other words, it helps to expand the ``narrow'' distribution depicted in Equation 4.1 (when $|\Sigma|$ is small) to become another distribution whose shape does not dependent on $|\Sigma|$, as depicted by the Equation below.
-%
-%\begin{align*}
-%  pdf( \ln | \langle ss^{*T} \rangle|, \Sigma) = \ln |\Sigma| - \ln(2L)d + \sum^{d-1}_{i=0} \Lambda (2L-2i)
-%\end{align*}  
-%
-%The Examiner also expresses his concern about the quality of the ``visual match'' on page 66.
-%For this, I had updated the section to include a quantitative, and hence objective, measure of match instead of the current subjective evaluation.
-%I believe, such a change should completely addresses his concerns.
-%I also made other small updates, to addresses his other various minor concerns.
 
@@
 
-%Page 94, section 5.2.2.2 is updated to indicate MSE as ``Mean Squared Error''.
-%The reference for computation in the section is the ``true signal'' $\sigma$.
-%
-%Fig. 5.11 shows two curves that are essentially the same.
-%One of them is ``simulated result'' and the other is ``analysis formula''.
-%The difference is that the former is computed through a Monte-Carlo simulation and the other is a simple plotting of the mathematical calculated values.
-%The purpose is to show that the heuristic formula given as
-%
-%\begin{align*}
-%  MSE = \frac{1}{(ENL-0.5)\ln^2(2)}
-%\end{align*}  
-%
-%closely tracks observable values.
-%Readers should also note that this argument is presented in a much more detailed manner in Section 5.3.2.1.
-%
-%Examiner No 3 also expresses his curiosity to see ``how the f-MLE filter will compare with other state-of-the-art-filters''.
-
 \subsubsection*{8. Chapter 6}
@@
 }
-
-%In this chapter, the Examiner wonder: ``if the proposed models are far from complete, how can it be an accurate representation of the data''.
-%To clarify, the proposed models in this thesis do not aim to become accurate representation, or fully representative, of the data.
-%Rather, they are proposed as highly representative, probably the most representative scalar models, for the multi-dimensional data.
-%They are, however, useful as scalar models are needed quite often, when scalar decision are to be taken,
-%  for example: what is the best speckle filter for the given data set?, or what type of surface does the region of interest belong to? ...
 
@@
 
-%The Examiner's next question center around this very point: ``.. definitely not full representative of the data''.
-%He went on to ask: ``What kind of eror will it cause?''.
-%To this the answer is that the model inherently suffers from loss of dimension
-%  where the full data is multi-dimensional and the proposed models are scalar.
-%
-%Besides these main points, the chapter is updated to increase its pursuasive power.
-%For example: the sentence in line 1, page 133, section 6.3 is removed.
-%Or a list of achievements has been included in this chapter.
-
 \subsubsection*{9. Appendix}
@@
 
-%While the conference papers have been published and the journal paper submitted,
-%  their copies have been removed from this section.
-
 \bibliographystyle{apalike}

### 2014-06-03 answer_thesis_examiner/chap3.tex
auto

--- 2014-05-19 answer_thesis_examiner/chap3.tex
@@
 \replyToComment
+    {The presentation needs to be considerable improved.}
+    {The presentation has been improved according to the Examiners' suggestions. I greatly appreciate the Examiners' help in making this thesis its improved version!}
+
+\replyToComment
+    {Chapter 3 and 4 talks about models, but these models were not organized into sections with appropriate headings ... (see my comments in the respective chapter below).}
+    {Since the organization for the Examiner's comments as well as for my answer are based on chapters, please see my reply in the corresponding chapters below.}
+
+\replyToComment
     {Page ii of the Contents section is missing}
@@
 \replyToComment
+    {Why are some page numbers (ii,iii ... ix,xi) missing?}
+    {They were missing due to slight different in behavior in Latex systems on Windows and Linux.
+A fix has been applied to ensure consistent behavior and the page numbers should be printed out correctly now.}
+
+\replyToComment
     {Page xiii: List of source codes. These are actually pseudocodes and not source codes.}
     {Updated (now called ``List of Pseudocodes'')}
-
-%Examiner No. 3 noted: ``The overall organization of the thesis is appropriate''.
-%Still minor editions have been included to address his  other concerns:
-
-%I appreciate the fact that the examiner noted: ``The overall organization of the thesis is appropriate''.
-%Besides the issue of appropriate headings for chapter 3 and 4, which will be discussed in their respective section, minor editions have been included to address his other concerns.
-
-%\begin{itemize}
-%  \item \textbf{Page ii of the Contents section is missing:} This were probably an administrative mistake and oversight from us. Please accept our apologies!
-%  \item \textbf{Usually, a Glossary is put at the end of the document: } Updated (now the Glossary section stays at the end of the thesis)
-%  \item \textbf{Some page number missing: } Updated. 
-%  \item \textbf{List of source codes: } Updated (now ``List of Pseudocodes'' as suggested.)
-%\end{itemize}
 
@@
     {
-     To persuade people into believing its proposed models, the thesis follows rigorous scientific methodologies. 
-     They include theoretical mathematics transformations and realistic hypothesis-testing experiments.
-      The thesis also includes a chapter detailing several different applications of the proposed models.
-      These applications, due to the various practical constraint, are unlikely to be exhaustive over all future applications.
-
-In fact, the two topics of 1) what else the proposed models can be applied on and 2) if the proposed models are to be taken as true, I feel, are not much related.
-      In the end, Einstein probably did not foresee that his theories were used to create atomic bombs and killed thousands of people.
-This lack of foresight however does not cast any doubt on his contribution to our scientific progress.
+      The methodology that is employed to persuade people into believing the proposed models is to follow rigorious mathematical transformations coupled with experiments.
+      The thesis also includes a chapter detailing multiple different applications of the proposed models.
+      What else the proposed models can applied on, I feel, is a totally different matter.
+      In the end, Eistein probably did not forsee that his theory were used to create atomic bombs and killed thousands of people!
     }

### 2014-06-04 answer_thesis_examiner/chap1.tex

@@
 14 & 5 & Assuming the number of these elementary back scatterers is sufficiently large, & Assuming these elementary back scatterers are large in number and independent in nature, \\
-%**IVM: the above should be 'number' (you had written 'numbers')
 14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\

### 2014-06-04 answer_thesis_examiner/chap2.tex

@@
     {This has been done.}
-%**IVM better not use humour... not all examiners have a sense of humour!!    {Search and replace operation done!}
 
@@
     {
-      It is true. In fact, the thesis does say that log-transformation will introduce bias. %**IVM
+      It is true. In fact, the thesis does say that log-transformation will introduce bias. 
       It also shows that MSE evaluation does inherently include a bias evaluation.
@@
     {Heteroskedastic and homoskedastic are terms defined in a statistical context to respectively denote the fact that different sub-populations of given samples can have different or similar variabilities.
-In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}  %**IVM added the word 'sample'
+In the context of SAR (and POLSAR) imagery they denote the fact that different areas in a given image can have different or similar sample variance.}
 
@@
 In general, I wish to express my appreciation towards Examiner No. 2 for his careful, detailed and concise review.
-%**IVM: I would skip this-> I am amazed by the fact that the Examiner is able to precisely summarize the long thesis into a single sentence.
 I also feel encouraged by the Examiner's suggestion to extract out portions of this thesis as scientific papers for peer review, which has also been taken up and acted upon.
-
-%=====
-%
-%Examiner No. 2 suggests to further emphasize the significance of the research motivation in \textbf{Section 1.1 and Section 1.2}.
-%In a similar fashion, the conclusion chapter should also include the research objectives.
-%These have been updated in the revised thesis.
-%Even though I would wish to note that the research objectives have been spelled out in the Introduction chapter.
-%The examiner also suggested to change the word ``theory'' to ``model''.
-%That has also been applied through out the thesis.
-%
-%\textbf{The second main comment} is to further highlight the novelty claim, which can be splitted into two parts.
-%
-%\textit{In the first part}, the examiner appears to discount the novelty claim by suggesting that:
-% ``the proposed model is derived based on the existing statistical models for SAR and extended to POLSAR''.
-%The main approach, in actuality, differs in a subtle but important way:
-%The proposed model is derived based on generic mathematical results for multi-dimensional random-walk \cite{Goodman_JOptSocAm_76, Goodman_Springer_1975}.
-%These results are well known to be applicable to POLSAR.
-%Thus, the derived models by nature are multi-dimensional model.
-%However, when collapsed into single-dimension, they match perfectly with existing SAR models.
-%As such, the proposed models can be considered as an extension of existing statistical models for SAR.
-%
-%\textit{In the second part}, the Examiner expresses his doubt in ``the use of MSE (mean squared error) as the single unified evaluation criteria''.
-%His main concern: ``the proposed log-transform model will introduce an inevitable bias error''.
-%It is no doubt tricky to evaluate evaluation criteria.
-%And I can empathize with his feelings.
-%Still, I wish to point out that MSE evaluation inherently includes bias evaluation. 
-%In fact it has two components: 1.
-bias evaluation and 2.
-variance evaluation, which for SAR speckle filter evaluation translates into 1.
-radiometric preservation and 2.
-noise suppression respectively.
-
-%( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
-%Unfortunately I do not have it at hand.
-%It would be great if I can have a look at it!)
-
-%The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
-%I really appreciate the examiner effort in pointing out specific references.
-%They, and some other articles, have been included in the thesis.
-%I would like however to seek his empathy towards a couple of points.
-%First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
-%Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
-%Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
-%While they do results in published scientific articles, 
-%  they are not, however, to be considered as the main contributions of the thesis.
-%Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
-%As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
-
-%\textbf{To conclude}, I appreciate the fact that the Examiner is able to a summarize the long thesis into a single sentence.
-%Also, portions of this thesis has been extracted out as scientific articles and submitted for peer review.
-%Various errata exposed by Examiner No. 2 and have also been updated in the thesis.
-%Last but not least, I wish to express my appreciation towards Examiner No.2 for his careful and detailed review.
 

### 2014-06-04 answer_thesis_examiner/chap3.tex

--- 2014-05-22 answer_thesis_examiner/chap3.tex
@@
     {Updated (now the Glossary section stays at the end of the thesis)}
+
+\replyToComment
+    {Why are some page numbers (ii,iii ... ix,xi) missing?}
+    {They were missing due to slight different in behavior in Latex systems on Windows and Linux.
+A fix has been applied to ensure consistent behavior and the page numbers should be printed out correctly now.}
 

### 2014-06-05 answer_thesis_examiner/chap3.tex
auto

@@
 \replyToComment
-    {Since these models are the key contributions of the thesis, it would be good to give a separate name to each of these models}
-    {The models' names have been added into the abstract}
+    {
+      Since these models are the key contributions of the thesis, it would be good to give a separate name to each of these models.
+      Also a short description of what each of them is suitable for should also be included in the abstract.
+    }
+    {The models' names and descriptions have been added into the abstract}
 
 \replyToComment
-    {The abstract lists the benefits of these models but not the shortcomings.}
-    {The shortcomings have also been included into the abstract now.}
+    {The abstract lists the benefits of these models but not the shortcomings. Why?}
+    {
+      The shortcomings were discussed in the final chapters of the thesis.
+      They have also been included into the abstract now.
+    }
 
@@
 Firstly, I do think that the Examiner has raise a good and important question here.
-However the goodness of the models are, at the end of the day, judged mainly by their performance in practice.
+However %the goodness of
+the models are, at the end of the day, judged mainly by their performance in practice.
 In turn, the performance is found from the outcome of various experimental evaluations and after developing some mathematics.
@@
 \replyToComment
+    {
+      In fact, at x-axis value, the real data has a value that is a sharp dip from its neighboring values.
+      Perhaps, it is important to exaplain why the real data behaves in such a way?
+    }
+    {
+      It is observable that the chart for the real data (AIRSAR case) is not behaving as good in comparison to other dataset (e.g. RADARSAT2 or simulated data).
+      This is because the AIRSAR data set is much smaller in size than the other dataset (50x50 for AIRSAR vs. 300x300 for RADARSAT2).
+      Naturally, real data sets have natural fluctuation in comparison to perfect theoretical assumptions, (e.g.
+the area is assumed to be homogeneous while such a fact is not known for sure, in practice).
+      In small dataset (i.e. the AIRSAR dataset) these fluctuations are expected to be more pronouced than others.
+    }
+
+\replyToComment
     {The section heading 4.5.3 should be ``Effective Number-of-Looks'' instead of ``Effect Number-of-Looks''}
@@
       But of course, such knowledge is only theoretical and may be difficult to obtain for real-life scenarios.
+      Concerning the comparison with other state-of-the-art filters, please see my answer below.
+    }
 
+\replyToComment
+    {Please label the two curves in Fig. 5.13}
+    {The labels have now been added into the figure.}
+
+\replyToComment
+    {
+      In Fig 5.15 you show a comparison between f-MLE filter and the box-car filter for heterogeneous patterns ...
+      I am still curious about how f-MLE filter will compare with other state-of-the-art filters for heterogeneous area as well.
+    }
+    {
 While, I am also eager to see, and to some extent to prove, the good results of my proposed f-MLE filter in a rigorous manner,
@@
 
-\replyToComment
-    {Please label the two curves in Fig. 5.13}
-    {The labels have now been added into the figure.}
+%\replyToComment
+%    {
+%      Look at Fig 5.13 again, ... can I assume that (b) and (d) are the results of the boxcar filter for homogeneous area?
+%      Can these results be compared to the f-MLE results for homogeneous area in Fig 5.12?
+%    }
+%    {
+%      TODO:
+%    }
 
@@
     {
-      %Page 133, line 3: ``it is definitely not fully representative of the data.''.
-      %So what kind of error it cause?
-      %How will it affects the use of your model?
-      It is necessary to point out what are the shortcomings and how it affects the use of your model!
+      Page 133, line 3: ``it is definitely not fully representative of the data.''.
+      So what kind of error it cause?
+      How will it affects the use of your model?
+      %It is necessary to point out what are the shortcomings and how it affects the use of your model!
     }
@@
     {
+      Page 133, line 1: ``... its potential still mostly stays undiscovered''.
+      So what have you done with your thesis?
+      Do 10\% of the work and leave the other 90\% for other people to do it for you?
       A thesis is supposed to persuade others to believe what you have proposed and to use it.

### 2014-06-15 answer_thesis_examiner/chap3.tex
auto

@@
 
-%\replyToComment
-%    {
-%      Look at Fig 5.13 again, ... can I assume that (b) and (d) are the results of the boxcar filter for homogeneous area?
-%      Can these results be compared to the f-MLE results for homogeneous area in Fig 5.12?
-%    }
-%    {
-%      TODO:
-%    }
+\replyToComment
+    {
+      Look at Fig 5.13 again, ... can I assume that (b) and (d) are the results of the boxcar filter for homogeneous area?
+      Can these results be compared to the f-MLE results for homogeneous area in Fig 5.12?
+    }
+    {
+      Yes, Fig 5.13 shows the results of applying the boxcar filter on two homogeneous areas 3dB apart.
+      The purpose of Fig 5.13 is to illustrate how AUC (i.e. Area Under the Curve) and MSE can be used to evaluate the performance of speckle filters on heterogeneous area.
+      Thus what it shows is not to be taken for comparison with what is shown in Fig. 5.12.
+      Fig. 5.15 shows a comparison between the result between boxcar and f-MLE filters over various underlying patterns.
+    }
+
+%\begin{mylist}{Something else}
+%\item[Whatever]  \LongText 
+%\item[Something else] \LongText \LongText
+%\end{mylist}
 

### 2014-06-16 clean.sh
auto

@@ -32,12 +32,16 @@ function backup {
 
 backup './thesis' ext[@]
 backup '0_frontmatter/dedication' ext[@]
+backup '0_frontmatter/abstract' ext[@]
+backup '0_frontmatter/acknowledgement' ext[@]
 backup '1_introduction/introduction' ext[@]
 backup '2/literature_review' ext[@]
 backup '3/sar' ext[@]
 backup '4/polsar' ext[@]
 backup '5/applications' ext[@]
 backup '6/conclusional_discussion' ext[@]
+backup '9_backmatter/appendix' ext[@]
+backup 'Latex/Macros/MacroFile1' ext[@]
 
 #mv thesis.tex b.thesis.tex
 #mv thesis.bib b.thesis.bib

### 2014-06-16 paper_dev/JSTARS_Answer_Document/clean.sh

@@ -1,0 +1,34 @@
+#!/bin/bash
+
+declare -a ext=('tex' 'bib');
+#f_name2='chap2'
+
+function e {
+    echo $1
+    eval $1
+}
+
+
+function backup {
+    f_name=$1
+    declare -a ext=("${!2}")
+    #ext=$2
+
+    for t in ${ext[@]}
+    do
+      e "mv ${f_name}.${t} b.${f_name}.${t}"
+    done
+    
+    e "rm ${f_name}.*"
+    
+    for t in ${ext[@]}
+    do
+      e "mv b.${f_name}.${t} ${f_name}.${t}"
+    done
+}
+
+backup 'answer_document' ext[@]
+#backup 'chap1' ext[@]
+#backup 'chap2' ext[@]
+#backup 'chap3' ext[@]
+

### 2014-06-16 paper_dev/JSTARS_Answer_Document/cygwin_setup.sh

@@ -14,11 +14,17 @@ if [ "$(expr substr $(uname -s) 1 6)" == "CYGWIN" ]; then
 
 fi
 
-  latex 'thesis.tex'
-  bibtex thesis
-  latex 'thesis.tex'
-  latex 'thesis.tex'
-  #yap thesis.dvi
+  latex 'answer_document.tex'
+  for auxfile in chap*.aux
+  do
+      bibtex `basename $auxfile .aux`
+  done
+  latex 'answer_document.tex'
+  latex 'answer_document.tex'
+  #bibtex thesis
+  #latex 'thesis.tex'
+  #latex 'thesis.tex'
+  #yap answer_document.dvi
   #dvipdf thesis.dvi
   #cygstart.exe thesis.pdf
 

### 2014-06-17 1_introduction/introduction.tex
start changing thesis

@@
                 have been a few published scalar statistical models for
-                POLSAR, but none of them fit the dual criteria of being
+                POLSAR, \cite{Alberga_2008_IJRS_4129} \cite{Joughin_1994_TGRS_562}, \cite{Lee_1994_TGRS_1017} and \cite{Touzi_1996_TGRS_519} \cite{Barakat_1985_IJOptics}, \cite{Eliyahu_1993_PhysRevE_2881} and \cite{Brosseau_1995_AppliedOptics_4788} but none of them fit the dual criteria of being
                 highly representative of the data and at the same time

### 2014-06-17 1_introduction/introduction.tex
auto

--- 2013-07-31 1_introduction/introduction.tex
@@
                 have been a few published scalar statistical models for
-                POLSAR, but none of them fit the dual criteria of being
+                POLSAR, \cite{Alberga_2008_IJRS_4129, Joughin_1994_TGRS_562, Lee_1994_TGRS_1017, Touzi_1996_TGRS_519, Barakat_1985_IJOptics, Eliyahu_1993_PhysRevE_2881, Brosseau_1995_AppliedOptics_4788} but none of them fit the dual criteria of being
                 highly representative of the data and at the same time
@@
 There
-                are also a few POLSAR discrimination measures proposed,
+                are also a few POLSAR discrimination measures proposed \cite{Lee_1994_IJRS_2299, Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454, Conradsen_2003_TGRS_4},
                 but all of them are based on the likelihood test
@@
 
-As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering has been put into the framework of statistical estimation.
+As both the SAR and POLSAR data are stochastic in nature, many of the associated data processing techniques, such as speckle filtering have been put into the framework of statistical estimation.
 For such application, the research methodology is based extensively on the statistical estimation framework. 

### 2014-06-20 1_introduction/introduction.tex
auto

@@
 POLSAR is the natural extension of SAR, exploiting the natural polarization property of Electromagnetic (EM) waves.
-It extends the SAR acquisition information from the traditional single
-SAR channel to multi-channel POLSAR data, corresponding to a different combination of transmitted and received polarizations.
+It extends the SAR acquisition information from the traditional single-channel SAR to multi-channel POLSAR data, corresponding to a different combination of transmitted and received polarizations.
 Similar to the extension from black-and-white images to colour photography, the polarimetric extension brought about
@@
 
-Similarly speaking, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
+Similarly, heteroskedasticity poses numerous negative impacts on the usual framework of statistical estimation, which most of the time makes use of various different techniques and criteria known to work very well on the usual models.
 For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences.
 However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
-Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criteria which is probably due to the Gauss Markov theorem.
+Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem.
 For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.
@@
 Or
-                when the MMSE criteria is not very suitable to evaluate
+                when the MMSE criterion is not very suitable to evaluate
                 SAR speckle filters, other criteria likes radiometric
@@
 Some of the problems described above have been studied using different approaches in the literature.
-However, they have not been presented in a systematic manner nor with a strong underlying foundational theory.
+However, they have not been presented in a systematic manner nor with precise closed-form mathematical models.
 %precise problem statement
@@
 Thus a significant portion of this research effort focuses on developing a computational framework for simulation, evaluation, processing and classification of target polarimetric signatures.
-The benefits of such a framework are many fold.
+The benefits of such a framework are manyfold.
 Firstly, simulation allows one to quickly carry out experiments on small synthesized and well-designed scenarios, without the need for highly expensive satellite imagery.
@@
 %How do you evaluate your solution? 
-The
-                achievement of the research objectives stated above not only provides
-                novel solutions to the stated problem, it also
-                illustrates the advantages and beneficial implications
-                of the proposed theory.  
+%The
+%                achievement of the research objectives stated above not only provides
+%                novel solutions to the stated problem, it also
+%                illustrates the advantages and beneficial implications
+%                of the proposed theory.  
 Compared
                 to existing published techniques, the advantage of the
-                proposed theory is qualitative, which does not require
+                proposed models is qualitative, which does not require
                 direct quantitative comparisons.
@@
 
+The work in this research results in the following list of articles that has been prepared for public communication:
+
+\begin{enumerate}
+\item \textbf{Neural network-assisted reconstruction of full polarimetric SAR information.}
+  Thanh-Hai Le, I. McLoughlin, Ken Yoong Lee, and T. Bretschneider.
+  In \textit{Communications, Control and Signal Processing (ISCCSP), 2010 4th International Symposium on}, pages 1–5, 2010.  \cite{Le_2010_ISCCSP} 
+\item \textbf{SLC SAR speckle filtering using homoskedastic features of logarithmic transformation.}
+  T. H. Le, I. V. McLoughlin, K. Y. Lee, and T. Brestchneider.
+  In \textit{Proceedings of the 31st Asian Conference on Remote Sensing (ACRS)}, Hanoi, Vietnam, Nov 2010. \cite{Le_2010_ACRS}
+\item  \textbf{SAR Fuzzy-MLE Speckle Filter using the Distance Consistency Property in Homoskedastic Log-Transformed Domain.}
+  T. H. Le and I. V. McLoughlin. 
+  In \textit{Proceedings of the 32nd Asian Conference on Remote Sensing (ACRS)}, Taipei, Taiwan, Nov 2011 \cite{Le_2011_ACRS}
+\item \textbf{Scalar and Representative Models for Polarimetric SAR Data.}
+  T. H. Le, I. V. McLoughlin, and C. H. Vun,
+  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+\item \textbf{Using MSE to evaluate SAR speckle filters.}
+  T. H. Le, I. V. McLoughlin, and C. H. Vun.
+  submitted to \textit{IET Radar, Sonar \& Navigation}
+\end{enumerate}
+
 \section{Organisation of the Thesis}
@@
 
-Chapter \ref{chap:lit_survey} will survey the related publications
+Chapter \ref{chap:lit_survey} surveys the related publications
   and the state-of-the-art techniques in modelling, processing, filtering and evaluating (POL)SAR speckle filter. %will be presented.
@@
 %The heart of is thesis contains several contributions which meet the stated objectives.
-                Chapter \ref{chap:sar} begins by by highlighting that SAR
+                Chapter \ref{chap:sar} begins by highlighting that SAR
                 data are heteroskedastic in the original domain, whereas

### 2014-06-20 4/polsar.tex
auto

@@
   which together with the proposed statistical models help to link the existing discriminant measures for POLSAR to the widely-used intensity ratio for SAR.
-Thus this theory should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
+Thus the proposed models should help in a wide range of applications, where a single scalar observable is required to represent the complex, multi-dimensional and inter-correlated POLSAR data.
 It also builds a bridge allowing  certain existing classes of SAR data processing technique to be applicable towards POLSAR data.

### 2014-06-20 6/conclusional_discussion.tex
auto

@@
   T. H. Le, I. V. McLoughlin, and C. H. Vun,
-  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
 \item \textbf{Using MSE to evaluate SAR speckle filters.}
   T. H. Le, I. V. McLoughlin, and C. H. Vun.
-  Being finalized for submission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing}
+  submitted to \textit{IET Radar, Sonar \& Navigation}
 \end{enumerate}

### 2014-06-21 2/literature_review.tex
auto

@@
   which, in turn, generates random phases in their back-scattering responses.
-Assuming the number of these elementary back scatterers is sufficiently large,
+%Assuming the number of these elementary back scatterers is sufficiently large,
+Assuming these elementary back-scatterers are large in number and independent in nature,  
   then the Central Limit Theorem is applicable \cite{Goodman_Springer_1975}.
@@
 \caption{eqn:SAR Real and Imaginary Components PDF}
-pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{\left( \frac{A_x^2}{\sigma^2} \right) }
+pdf(A_x)=\frac{1}{\sqrt{\pi} \sigma} e^{- \left( \frac{A_x^2}{\sigma^2} \right) }
 \end{equation}
@@
 
-\subsubsection{The Polarization Basis Transformation}
-
-Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
-\begin{equation*}
-\left( 
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right) 
-= A_0 e^{-i \phi_0} \left(
-\begin{array}{c c}
- \cos(\Psi) & -\sin(\Psi) \\
- \sin(\Psi) & \cos(\Psi)
-\end{array}
-\right) 
-\left(
-\begin{array}{c}
- \cos(\chi) \\
- i \sin(\chi)
-\end{array}
-\right) 
-\end{equation*}
-The representation of a wave, however, depends on the choice of orthogonal reference frame basis.
-
-Consider two different orthogonal basis, $\{ x,y \}$ and $\{ h,v \}$.
-A given Jones vector can be measured in both basis as:
-$J_{xy}= 
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right) $ and 
-$J_{hv}
-= \left(
-\begin{array}{c}
- \xi_h \\
- \xi_v
-\end{array}
-\right)$ê
-.
-The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
-\begin{equation*}
-\left(
-\begin{array}{c}
- \xi_x \\
- \xi_y
-\end{array}
-\right)
-= U_2
-\left(
-\begin{array}{c}
- \xi_h \\
- \xi_v
-\end{array}
-\right)
-\end{equation*}
-
-Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
-\begin{equation*}
-U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
-\left(
-\begin{array}{c c}
- 1 & -\rho^* \\
- \rho & 1
-\end{array}
-\right)
-\left(
-\begin{array}{c c}
- e^{-i\delta} & 0 \\
- 0 & e^{i\delta}
-\end{array}
-\right)
-\end{equation*}
-where
-	$\rho$ is the complex polarisation ratio of the Jones vector for the first new basis, and
-	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
-	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.
-
-In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
-\begin{equation*}
-U_2 = \left(
-\begin{array}{c c}
- \cos(\Psi) & -\sin(\Psi) \\
- \sin(\Psi) & \cos(\Psi)
-\end{array}
-\right)
-\left(
-\begin{array}{c c}
- \cos(\chi) & i\sin(\chi) \\
- i\sin(\chi) & \cos(\chi)
-\end{array}
-\right)
-\left(
-\begin{array}{c c}
- e^{-i \phi_0} & 0 \\
- 0 & e^{i \phi_0}
-\end{array}
-\right)    
-\end{equation*}
-
-From these results, it is then possible to derive equations for the transformation of the scattering matrix.
-Noting that by definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
-and that $J_{xy}^*= U_2 J_{hv}^*$, also that $(U_2)^{-1} = (U_2)^T$,
-it is then trivial to show that:
-\begin{equation*}
-S_{xy} = U_2 S_{hv} U_2^T
-\end{equation*}
-
-%***IVM: again, I think you need to introduce some of the variables below, like delta, rho. Is rho* the complex conjugate? Better to mention that too....
-Using the result above, we then have:
-\begin{equation*}
-S_{xx} = \frac{1}{1+\rho \rho^*} 
-\left( 
-S_{HH} e^{-2i\delta} - \rho^* (S_{HV}+S_{VH}) + (\rho^*)^2 S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-\begin{equation*}
-S_{xy} = \frac{1}{1+\rho \rho^*} 
-\left( 
-\rho S_{HH} e^{-2i\delta} + S_{HV} -\rho \rho^* S_{VH} - \rho^* S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-\begin{equation*}
-S_{yx} = \frac{1}{1+\rho \rho^*} 
-\left( 
-\rho S_{HH} e^{-2i\delta} - \rho \rho^* S_{HV} + S_{VH} - \rho^* S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-\begin{equation*}
-S_{yy} = \frac{1}{1+\rho \rho^*} 
-\left( 
-\rho^2 S_{HH} e^{-2i\delta} + \rho (S_{HV} + S_{VH}) + S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-
-In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
-\begin{equation*}
-S_{xx} = \frac{1}{1+\rho \rho^*} 
-\left( 
-S_{HH} e^{-2i\delta} - 2 \rho^* S_{XX} + (\rho^*)^2 S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-\begin{equation*}
-S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
-\left( 
-\rho S_{HH} e^{-2i\delta} + (1-\rho \rho^*) S_{XX} - \rho^* S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-\begin{equation*}
-S_{yy} = \frac{1}{1+\rho \rho^*} 
-\left( 
-\rho^2 S_{HH} e^{-2i\delta} + 2 \rho S_{XX} +  S_{VV} e^{2i\delta}
-\right)
-\end{equation*}
-
-The results here, together with Stokes Vector's formula, can be used to prove the following identity,
-  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
-\begin{equation*}
-S_t = 
-\left(
-	\begin{array} {c}
-		S_hS_h + S_vS_v \\
-		S_hS_h - S_vS_v \\
-		2 \Re{(S_hS_v^*)} \\
-		2 \Im{(S_hS_v^*)}
-	\end{array}
-\right)
-= 
-\left(
-	\begin{array} {c}
-		S_hS_h + S_vS_v \\
-		S_hS_h - S_vS_v \\
-		S_+S_+ - S_-S_- \\
-		S_lS_l - S_rS_r
-	\end{array}
-\right)
-\end{equation*}
-where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.
-
-%The transformation from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ as well as from $\{h,v\}$ to circular basis $\{l,r\}$ are special cases of the above formula.
-%Ignoring the determination of initial phases, we have: 
-%	the measured signal at $\pi/4$ linear polarizer / projection as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
-%	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
-%	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
-%	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
-%
-%The Stokes vectors, when aligned at these transformed projections are given by the following well-known equations
-%\begin{equation}
-%S_t = \left(
+%\subsubsection{The Polarization Basis Transformation}
+%
+%Assuming that the polarization states are known, the wave representation can be given in terms of $\xi_x$ and $\xi_y$ as:%****IVM, you need to mention A_0.... as well as \phi
+%\begin{equation*}
+%\left( 
 %\begin{array}{c}
-% |\xi_h|^2 + |\xi_v|^2 \\
-% |\xi_h|^2 - |\xi_v|^2 \\
-% 2 \Re( \xi_h \xi_v^* ) \\
-% 2 \Im( \xi_h \xi_v^* ) 
+% \xi_x \\
+% \xi_y
 %\end{array}
 %\right) 
+%= A_0 e^{-i \phi_0} \left(
+%\begin{array}{c c}
+% \cos(\Psi) & -\sin(\Psi) \\
+% \sin(\Psi) & \cos(\Psi)
+%\end{array}
+%\right) 
+%\left(
+%\begin{array}{c}
+% \cos(\chi) \\
+% i \sin(\chi)
+%\end{array}
+%\right) 
+%\end{equation*}
+%The representation of a wave, however, depends on the choice of orthogonal reference frame basis.
+%
+%Consider two different orthogonal basis, $\{ x,y \}$ and $\{ h,v \}$.
+%A given Jones vector can be measured in both basis as:
+%$J_{xy}= 
+%\left(
+%\begin{array}{c}
+% \xi_x \\
+% \xi_y
+%\end{array}
+%\right) $ and 
+%$J_{hv}
 %= \left(
 %\begin{array}{c}
-% |\xi_+|^2 + |\xi_-|^2 \\
-% -2 \Re( \xi_+^* \xi_- ) \\
-% |\xi_+|^2 - |\xi_-|^2 \\
-% 2 \Im( \xi_+^* \xi_- ) 
+% \xi_h \\
+% \xi_v
 %\end{array}
-%\right)
-%= \left(
+%\right)$ê
+%.
+%The transformation from $\{h,v\}$ to $\{x,y\}$ is governed by a unitary transformation matrix $U_2$, which is given as:
+%\begin{equation*}
+%\left(
 %\begin{array}{c}
-% |\xi_l|^2 + |\xi_r|^2 \\
-% 2 \Re( \xi_l^* \xi_r ) \\
-% -2 \Im( \xi_l^* \xi_r ) \\ 
-% |\xi_l|^2 - |\xi_r|^2 
+% \xi_x \\
+% \xi_y
 %\end{array}
 %\right)
-%\end{equation}
+%= U_2
+%\left(
+%\begin{array}{c}
+% \xi_h \\
+% \xi_v
+%\end{array}
+%\right)
+%\end{equation*}
+%
+%Boerner \cite{Boerner_1991_ProcsIEEE} has given $U_2$ as:
+%\begin{equation*}
+%U_2 = \frac{1}{\sqrt{1+\rho\rho^*}}
+%\left(
+%\begin{array}{c c}
+% 1 & -\rho^* \\
+% \rho & 1
+%\end{array}
+%\right)
+%\left(
+%\begin{array}{c c}
+% e^{-i\delta} & 0 \\
+% 0 & e^{i\delta}
+%\end{array}
+%\right)
+%\end{equation*}
+%where
+%	$\rho$ is the complex polarisation ratio of the Jones vector for the first new basis, and
+%	$\delta = \tan^{-1}(\tan(\Psi) \tan(\chi)) - \phi_0$ is the phase reference for the new basis, 
+%	and $\delta$ is required for the determination of the initial phase of the Jones vector in the new reference basis.
+%
+%In the same vein, \cite{Pottier_2008_IGARSS} gives %****IVM pls change this to a proper \cite{}
+%\begin{equation*}
+%U_2 = \left(
+%\begin{array}{c c}
+% \cos(\Psi) & -\sin(\Psi) \\
+% \sin(\Psi) & \cos(\Psi)
+%\end{array}
+%\right)
+%\left(
+%\begin{array}{c c}
+% \cos(\chi) & i\sin(\chi) \\
+% i\sin(\chi) & \cos(\chi)
+%\end{array}
+%\right)
+%\left(
+%\begin{array}{c c}
+% e^{-i \phi_0} & 0 \\
+% 0 & e^{i \phi_0}
+%\end{array}
+%\right)    
+%\end{equation*}
+%
+%From these results, it is then possible to derive equations for the transformation of the scattering matrix.
+%Noting that by definition, $J_{xy}^r=S_{xy} J_{xy}^t$, $J_{hv}^r=S_{hv} J_{hv}^t$ 
+%and that $J_{xy}^*= U_2 J_{hv}^*$, also that $(U_2)^{-1} = (U_2)^T$,
+%it is then trivial to show that:
+%\begin{equation*}
+%S_{xy} = U_2 S_{hv} U_2^T
+%\end{equation*}
+%
+%%***IVM: again, I think you need to introduce some of the variables below, like delta, rho. Is rho* the complex conjugate? Better to mention that too....
+%Using the result above, we then have:
+%\begin{equation*}
+%S_{xx} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%S_{HH} e^{-2i\delta} - \rho^* (S_{HV}+S_{VH}) + (\rho^*)^2 S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%\begin{equation*}
+%S_{xy} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%\rho S_{HH} e^{-2i\delta} + S_{HV} -\rho \rho^* S_{VH} - \rho^* S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%\begin{equation*}
+%S_{yx} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%\rho S_{HH} e^{-2i\delta} - \rho \rho^* S_{HV} + S_{VH} - \rho^* S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%\begin{equation*}
+%S_{yy} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%\rho^2 S_{HH} e^{-2i\delta} + \rho (S_{HV} + S_{VH}) + S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%
+%In the case of mono-static POLSAR, i.e. $S_{HV}=S_{VH}=S_{XX}$ and $S_{xy}=S_{yx}$, the equations become
+%\begin{equation*}
+%S_{xx} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%S_{HH} e^{-2i\delta} - 2 \rho^* S_{XX} + (\rho^*)^2 S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%\begin{equation*}
+%S_{yx} = S_{xy}= \frac{1}{1+\rho \rho^*} 
+%\left( 
+%\rho S_{HH} e^{-2i\delta} + (1-\rho \rho^*) S_{XX} - \rho^* S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%\begin{equation*}
+%S_{yy} = \frac{1}{1+\rho \rho^*} 
+%\left( 
+%\rho^2 S_{HH} e^{-2i\delta} + 2 \rho S_{XX} +  S_{VV} e^{2i\delta}
+%\right)
+%\end{equation*}
+%
+%The results here, together with Stokes Vector's formula, can be used to prove the following identity,
+%  which can form the basis of a novel approach in POLSAR speckle filtering: %used throughout this thesis:
+%\begin{equation*}
+%S_t = 
+%\left(
+%	\begin{array} {c}
+%		S_hS_h + S_vS_v \\
+%		S_hS_h - S_vS_v \\
+%		2 \Re{(S_hS_v^*)} \\
+%		2 \Im{(S_hS_v^*)}
+%	\end{array}
+%\right)
+%= 
+%\left(
+%	\begin{array} {c}
+%		S_hS_h + S_vS_v \\
+%		S_hS_h - S_vS_v \\
+%		S_+S_+ - S_-S_- \\
+%		S_lS_l - S_rS_r
+%	\end{array}
+%\right)
+%\end{equation*}
+%where $S_t$ is the Stokes vector and $S_+S_+$, $S_-S_-$, $S_rS_r$, $S_lS_l$ are the intensity of received signals in $+45^o$ linear, $-45^o$ linear, right circular and left circular polarization respectively.
+%
+%%The transformation from $\{h,v\}$ to $\{+\pi/4,-\pi/4\}$ as well as from $\{h,v\}$ to circular basis $\{l,r\}$ are special cases of the above formula.
+%%Ignoring the determination of initial phases, we have: 
+%%	the measured signal at $\pi/4$ linear polarizer / projection as: $\xi_+ = \frac{\xi_h + \xi_v}{\sqrt{2}}$,
+%%	at $-\pi/4$ linear polarizer as: $\xi_- = \frac{\xi_h - \xi_v}{\sqrt{2}}$, 
+%%	at left circular polarization as: $\xi_l = \frac{\xi_h + i \xi_v}{\sqrt{2}}$, 
+%%	and at right circular polarization as $\xi_r = \frac{\xi_h - i \xi_v}{\sqrt{2}}$.
+%%
+%%The Stokes vectors, when aligned at these transformed projections are given by the following well-known equations
+%%\begin{equation}
+%%S_t = \left(
+%%\begin{array}{c}
+%% |\xi_h|^2 + |\xi_v|^2 \\
+%% |\xi_h|^2 - |\xi_v|^2 \\
+%% 2 \Re( \xi_h \xi_v^* ) \\
+%% 2 \Im( \xi_h \xi_v^* ) 
+%%\end{array}
+%%\right)
+%%= \left(
+%%\begin{array}{c}
+%% |\xi_+|^2 + |\xi_-|^2 \\
+%% -2 \Re( \xi_+^* \xi_- ) \\
+%% |\xi_+|^2 - |\xi_-|^2 \\
+%% 2 \Im( \xi_+^* \xi_- ) 
+%%\end{array}
+%%\right)
+%%= \left(
+%%\begin{array}{c}
+%% |\xi_l|^2 + |\xi_r|^2 \\
+%% 2 \Re( \xi_l^* \xi_r ) \\
+%% -2 \Im( \xi_l^* \xi_r ) \\ 
+%% |\xi_l|^2 - |\xi_r|^2 
+%%\end{array}
+%%\right)  
+%%\end{equation}
 

### 2014-06-24 2/literature_review.tex
auto

@@
 \begin{itemize}
-\item	wavelets \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS}, 
-\item	curvelets \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, 
-\item	contourlets \cite{Foucher_2006_IGARSS}, 
-\item	ridgelets \cite{Saevarsson_2004_IGARSS},
-\item	fuzzy logic \cite{Cheng_ETCS_2009}, 
-\item	anisotropic kernels \cite{DHondt_2006_TGRS}, 
-\item	and autoregressive conditional heteroskedasticity \cite{Amirmazlaghani_2009_DSPWorkshop}. 
+\item \textbf{multi-resolution methods:}
+ In this approach, speckle filtering is carried out in a scale-space representation.
+The homomorphic transformation is normally applied here.
+This transformation converts the original multiplicative model into a more familiar additive model.
+In this transformed domain, the assumption of linear-time invariant (LTI) system appears to hold.
+This simplifies the measurement and filtering of the speckle noise in each sub-band of the scale-space representation.
+\begin{itemize} 
+\item	\textbf{wavelets:} The wavelet analysis transforms a given signal / image into a new multi-resolution representation.
+The original signal / image can then be obtained using a synthesizing scheme symmetrical to that of the analysis \cite{Gagnon_SPIEProc_1997, VidalPantaleoni_2004_IJRS, Moulin_1993_JMathImageVision, Hervet_1998_SPIE, Hebar_2009_TGRS, Chen_2007_IET, Bianchi_TGRS_2008, Argenti_2006_TGRS},
+\item	\textbf{directional-lets:} Combining Laplacian pyramid decomposition and different schemes of directional filter banks results in the derivation of curvelets \cite{Wang_2007_ICWAPR, Saevarsson_2003_IGARSS, Guo_2008_ICARCV}, contourlets \cite{Foucher_2006_IGARSS} and ridgelets \cite{Saevarsson_2004_IGARSS},
+\item	\textbf{autoregressive conditional heteroskedasticity:} 
+ In this approach, the wavelet coefficient of SAR images are assumed to follow 2D GARCH models.
+GARCH is a term borrowed from the field of econometric. 
+It stands for Generalized Auto-Regressive Conditional Heteroskedasticity.
+The advantage of this approach is that it takes into account both SAR's heteroskedasticity and the relations among its wavelet coefficients \cite{Amirmazlaghani_2009_DSPWorkshop}. 
+\end{itemize}
+\item	\textbf{fuzzy logic:} The contribution of each neighboring pixel is weighed using a fuzzy probabilistic function \cite{Cheng_ETCS_2009}, 
+\item	\textbf{anisotropic kernels:} Speckle reducing anisotropic diffusion make uses of the local coefficient of variation ($C_v$). 
+In that sense, it has the same approach as that of the Frost or Lee filter.
+Yet, it has an interesting development.
+It shows that local $C_v$ is a function of the local gradient value and the applicable Laplacian operator \cite{DHondt_2006_TGRS},
+\item   \textbf{simulated annealing:} Simulated annealing (SA) is an optimization method.
+In SAR speckle filtering, it aims to find the global minimum of a multi-dimensional energy function.
+There, it is equal to finding the global MAP of a multi-variate distribution.
+The local maxima / minima is the common stumbling block of global optimization algorithms.
+SA overcomes this problem by introducing a temperature variable to control the optimization process.
+At first few iterations, the temperature is kept high allowing a  better chance of accepting configurations that results in an energy increase.
+This hopefully allows SA to get out of local minima.
+At the end of the minimization process, no further energy increases will be accepted.
+This ideally should leads to global minimal results \cite{White_ProcSPIE_1994},
 \end{itemize}
@@
 One metric that can be used to detect radiometric distortion is the ratio between the estimated and the 
-	original value $r = X_{est} / X_{org}$ \cite{Oliver_2004_SciTech,Medeiros_2003_IJRS}.
-A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (X_{est} - X_{org} )/ X_{org}$.
+	original value $r = I_{est} / I_{org}$ \cite{Oliver_2004_SciTech,Medeiros_2003_IJRS}.
+A somewhat similar metric is used in \cite{Wang_2005_MIPR} as $r_w = (I_{est} - I_{org} )/ I_{org}$.
 %For homogeneous scenes, Shi et al. \cite{Shi_IGARSS_1994} found that 
@@
 Several metrics have also been developed to evaluate speckle suppression power.
-The most common measure is the Equivalent Number of Looks (ENL) index 
-$ENL=avg(I)^2/var(I)$
-that was proposed by Lee \cite{Lee_1981_CGIP}.
+The most common measure are: the Equivalent Number of Looks (ENL) index 
+$ENL=avg(I)^2/var(I)$ \cite{Lee_1981_CGIP},
+and the Coefficient of Variation index $C_v = \frac{\sqrt{var(I)}}{avg(I)}$ \cite{Touzi_2002_TGRS}.
 Another very similar metric is the ratio of mean to standard deviation, $R=avg(I)/std(I)$ \cite{Gagnon_SPIEProc_1997} 
@@
 	Hough Transform \cite{Medeiros_2003_IJRS}, Robert gradient edge detector \cite{Gagnon_SPIEProc_1997} 
-	and edge map \cite{Frost_PAMI_1982}.
+	and edge map \cite{Frost_PAMI_1982} or edge-correlation index \cite{Sattar_TIP_1997}.
 While significant effort has been spent on these evaluations, serious doubts remain concerning the precision 
@@
 	how to interpret the results, especially in terms of accuracy.
-As such, the problem of establishing an single evaluation criteria to evaluate the overall performance of speckle filters remains open for improvement.
+
+There are also a variety of other approaches, which includes
+\begin{itemize}
+  \item The Target-To-Clutter ratio \cite{Cetin_ProcSPIE_2000}, whose applicability is limited to the special case of point-target preservation.
+  \item The Structural-Change-Index \cite{Aiazzi_ProcSPIE_2011_81790D}, whose authors also admits that it is unable to measure the overall effectiveness of SAR speckle filtering \cite{Argenti_GRSM_2013}.
+  \item The Mean Structural Similarity Index Measurement (MSSIM) \cite{Wang_TIP_2004}, where the proposed index is tuned for hypothesized overall functionalities of the Human Visual System (HVS) in a top-down manner.
+%\item the B-index \cite{}, where the proposed metric only focuses on one single evaluation of bias.
+\end{itemize}
+
+As reviewed above, the problem of establishing an single evaluation criteria to evaluate the overall performance of speckle filters remains open for improvement.
 

### 2014-06-24 5/applications.tex
auto

@@
 \end{figure}
+
+PS: During the revision of this thesis, this work \cite{Nielsen_2012_ICASSP} is brough forward to the author's attention.
+This work is quite similar and is published after the publication for the work presented in this thesis \cite{Le_2010_ACRS}.
+It excels by providing a theoretical proof for its k-MLE procedure in the case of exponential mixtures.
+Its drawback: it focuses only on the exponential distribution, which is just one special case of the work presented here.
 

### 2014-06-26 4/polsar.tex
auto

@@
 \section{Consistent Measures of Distance for POLSAR data}
+\label{sec:consistent_measures_distance_polsar}
 
@@
 the theoretical models for the dispersion and contrast measures of distance.
+This qualitative observation is further supported by high significance level (or p-value) in the standard Kolmogorov-Smirnov goodness-of-fit test between curves \cite{Kolmogoroff_1941_AMS_461}, noted under each graph.
+While a good p-value may not lead to automatic acceptance of the model, high p-values lend a high level of confidence to the proposal.
 
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
+	\subfloat[part-pol (2x2) dispersion (p-value HH-HV=0.????)]{
 		 \epsfxsize=2.5in
@@
 	\hfill	
-	\subfloat[part-pol (2x2) contrast]{
+	\subfloat[part-pol (2x2) contrast (p-value HH-HV=0.9182)]{
 		 \epsfxsize=2.5in
@@
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
+	\subfloat[full-pol (3x3) dispersion (p-value=0.????)]{
 		 \epsfxsize=2.5in
@@
 	\hfill	
-	\subfloat[full-pol (3x3) contrast]{
+	\subfloat[full-pol (3x3) contrast (p-value=0.9254)]{
 		 \epsfxsize=2.5in
@@
 \end{tabular}
-\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.}
+\caption{Validating the dispersion and contrast models against both partial and full polarimetric AIRSAR Flevoland data.
+Each histogram plots the signal(s) under investigation against its probabilistic distribution across the patch,
+  with p-value being the significance level of the Kolmogorov-Smirnov goodness-of-fit test between the two histograms.  
+}
 \label{fig:verify_polsar_2x2_simulation_dispersion_contrast}

### 2014-06-26 6/conclusional_discussion.tex
auto

@@
 This combination leads to the main result: the proposal of scalar, representative and homoskedastic models for both SAR and POLSAR data.
-These theoretical results are applied in chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.
+These theoretical results are applied in Chapter \ref{chap:applications} where a new clustering algorithm and a new SAR speckle filter are proposed together with our proposal of using MSE to evaluate both SAR and POLSAR speckle filters.
 
@@
 Specifically, the
-                main theoretical results obtained in this thesis are novel statistical
+                main theoretical contributions obtained in this thesis are novel statistical
                 models, which subsequently lead to derivation of
@@
 With regards to other existing discrimination measures for SAR and POLSAR,
-                this thesis unite them, together with the new ones
+                this thesis unites them, together with the new ones
                 proposed herein, all into a consistent theory.
@@
 %Thus the additive and homoskedastic models initially developed for SAR are shown extensible to the generic multi-dimensional, multiplicative and heteroskedastic case of POLSAR.
+
+Corresponding to the objectives outlined in Chapter 1,
+  the following results have been obtained:
+\begin{enumerate}
+\item           Several scalar and highly representative statistical models
+                for the multi-dimensional and inter-correlated POLSAR
+                data have been proposed:
+                \begin{enumerate}
+                \item The determinant statistical model is established for the determinant of POLSAR covariance matrices (Section \ref{sec:polsar_heterosked_model_and_log_transform}),
+                \item Several statistical models for different discrimination measures (namely: determinant-ratio, log-distance, dispersion and contrast) are derived together with its consistent property (Section \ref{sec:consistent_measures_distance_polsar}).
+%being modelled
+                \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
+                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
+                captured POLSAR data in Section \ref{sec:polsar_models_validation}.
+                \end{enumerate}
+\item                Homoskedastic statistical models for the
+                heteroskedastic (POL)SAR data are derived. Specifically 
+                \begin{enumerate}
+                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
+                the original domain and logarithmic transformation
+                converts this into a homoskedastic model (Sections \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
+                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
+                the multi dimensional POLSAR as well as for the one
+                dimensional SAR data are derived (Sections \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
+                \item \label{itm:sar_validation} These statistical models are validated against both
+                practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
+                \end{enumerate}
+\item The beneficial applications of these
+                statistical models have also been demonstrated. Specifically:
+                \begin{enumerate}
+                \item \label{itm:filter_vicious_circle} The consistent sense of variance
+                is shown to help breaking the vicious cycle in the problem of SAR
+                speckle filtering: with new statistical test for
+                homogeneity and new speckle filters proposed (Section \ref{sec:k_mle}, \ref{sec:f_mle}).
+                \item \label{itm:log_mse} Tconsistent sense of subtractive
+                distance also helps in the problem of evaluating SAR
+                speckle filters. Section \ref{sec:sar_filters_evaluation} proposes the use of the log-MSE to combine the
+                evaluation of radiometric preservation and speckle
+                suppression power in evaluating SAR speckle filters.
+                \item \label{itm:extend_sar_to_polsar} Section \ref{sec:polsar_models_validation} demonstrates an example where the existing SAR
+                processing technique of ENL estimation is extended towards POLSAR data.
+                \end{enumerate}
+\end{enumerate}
 
@@
 
-The work in this research results in the following list of articles that has been prepared for public communication:
+The work in this research results in the following list of articles that have been prepared for public communication:
 
@@
   T. H. Le, I. V. McLoughlin, and C. H. Vun,
-  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+  under revision for resubmission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+
 \item \textbf{Using MSE to evaluate SAR speckle filters.}

### 2014-06-26 0_frontmatter/abstract.tex
auto

@@
 \begin{abstracts}        %this creates the heading for the abstract page
+\phantomsection
+\addcontentsline{toc}{section}{Abstract Summary}
 
@@
 
-As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix are proposed and validated.
+As a result of these studies, several scalar statistical models based on the determinant of POLSAR covariance matrix, namely the determinant and the determinant-ratio models, are proposed and validated.
 These generic models for POLSAR are also shown to be both multiplicative and heteroskedastic, similar to the models for SAR intensity. 
@@
   to convert them into additive and homoskedastic models.
-From these models, the benefits of homoskedastic statistical estimation framework are then further explored.
+These models includes: the log-determinant, the log-distance, the dispersion and the contrast models.
+%From these models, the benefits of homoskedastic statistical estimation framework are then further explored.
 
-There are several beneficial implications of the theory proposed in this thesis. 
+Since the full POLSAR data is multi-dimensional and the proposed models are scalar, they are not perfect.
+Specifically, they suffers from a loss of dimension.
+Still there are several beneficial implications of the models proposed in this thesis. 
 Since the scalar and representative models for POLSAR extend the traditional models for SAR's intensity,

### 2014-06-26 1_introduction/introduction.tex
auto

@@
 techniques, for example speckle filtering, target detection, image segmentation, and
-other clustering, classification techniques.
+other clustering, classification techniques \cite{Lopez-Martinez_2003_TGRS_2232, Argenti_GRSM_2013, Conradsen_2003_TGRS_4}.
 In fact, due to the random nature of speckle, all of these techniques are essentially based on statistical estimation theory,
@@
 %At the same time, the statistical properties of the input data set greatly affect the choice and the performance of information extraction and statistical estimation techniques.
-In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data.
+In addition, most of these data processing techniques are traditionally designed for additive and homoskedastic data \cite{Dutch_LNCS_2004}.
 In fact, unless proven otherwise, it is both convenient and acceptable to assume that the additive white noise model is appropriate for any given set of data samples.
@@
 An example is the use of mean, variance and squared error criteria, which are linear by nature and work excellently on additive and homoskedastic models, being applied on multiplicative and heteroskedastic distribution such as the gamma distribution.
-Such use, however, is known to be not very robust for these so-called heavy tailed distributions.
+Such use, however, is known to be not very robust for these so-called heavy tailed distributions \cite{McElroy_Econometric_2002}.
 
@@
 For example, in modelling, it is very common to use subtractive differences to discriminate and to make decisional inferences.
-However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure.
-Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem.
-For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed.
+However, for heteroskedastic SAR, it is known that such use should be avoided in preference to a ratio-based discrimination measure \cite{Rignot_1993_TGRS_896}.
+Another example is in the normal performance evaluation stage of statistical estimators, where the Ordinary Least Square (OLS) is widely used as the best evaluation criterion which is probably due to the Gauss Markov theorem \cite{Furno_1991_JStatCompSimul}.
+For SAR data, however, its heteroskedasticity directly violates the homoskedastic assumption of the theorem and thus many different ways to evaluate SAR speckle filters were proposed \cite{Gagnon_SPIEProc_1997, Argenti_GRSM_2013}.
 
@@
   T. H. Le, I. V. McLoughlin, and C. H. Vun,
-  re-submitted to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
+  under revision for resubmission to \textit{IEEE Journal on Selected Topic in Applied Earth Observation and Remote Sensing.}
 \item \textbf{Using MSE to evaluate SAR speckle filters.}

### 2014-06-26 2/literature_review.tex
auto

@@
 The general solution to these equations is a linear superposition of waves, each having the form of:
-\begin{eqnarray*}
+\begin{eqnarray}
  \vec{E}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r}) \\
  \vec{B}(\vec{r},t) &=& g(\phi(\vec{r},t)) = g(\omega t - \vec{k} \cdot \vec{r})
-\end{eqnarray*}
+\end{eqnarray}
 where
@@
 
-\begin{equation*}
+\begin{equation}
 \vec{E}(z,t) 
@@
 \right)
-\end{equation*}
+\end{equation}
 where $\phi_0$ is the initial phase angle, that is dependent on the choice of space-time origin.
@@
 This shape is characterized by the formula: 
-\begin{equation*}
+\begin{equation}
  \frac{\xi_x^2(t)}{|E_x^0|^2} + \frac{\xi_y^2(t)}{|E_y^0|^2} - 2 \frac{\xi_x \xi_y}{E_x^0 E_y^0} \cos (\Delta \phi) = \sin^2(\Delta \phi)
-\end{equation*}
+\end{equation}
 where
@@
 The parameters that describe the polarization ellipse are: 
-\begin{equation*}
+\begin{equation}
 \tan (\theta ) = \frac{E_y^0}{E_x^0}
-\end{equation*}
+\end{equation}
 with
@@
 The orientation angle, which is the angle between the major semi-axis of the ellipse and the x-axis, is given by:
-\begin{equation*}
+\begin{equation}
 \tan (\Psi) = \tan (2 \theta) \cos(\Delta \phi)
-\end{equation*}
+\end{equation}
 with
@@
 The ellipticity angle which is defined as $\chi = \arctan (1/\epsilon)$ can be calculated as:
-\begin{equation*}
+\begin{equation}
 \sin (2 \chi) = \sin(2 \theta) \sin( \Delta \phi)
-\end{equation*}
+\end{equation}
 with
@@
 The wave coherency matrix is defined as:
-\begin{equation*}
+\begin{equation}
 W_c = \left<
@@
 \right>
-\end{equation*}
+\end{equation}
 
 The Stokes vector is then defined as:
-\begin{equation*}
+\begin{equation}
 S_t = 
@@
 \right)
-\end{equation*}
+\end{equation}
 
 In the case of elementary (or fully polarized) waves, the Stokes vector can be written as:
-\begin{equation*}
+\begin{equation}
 S_t = 
@@
 \right)
-\end{equation*}
+\end{equation}
 
@@
 In fully polarized wave, the following equation holds:
-\begin{equation*}
+\begin{equation}
 S_0^2 = S_1^2 + S_2^2 + S_3^2
-\end{equation*}
+\end{equation}
 
 In depolarized wave, it becomes an in-equation
-\begin{equation*}
+\begin{equation}
 S_0^2 > S_1^2 + S_2^2 + S_3^2
-\end{equation*}
+\end{equation}
 
 Then the degree of polarization is defined as
-\begin{equation*}
+\begin{equation}
 p = \frac{\sqrt{ S_1^2 + S_2^2 + S_3^2 }}{S_0}
-\end{equation*}
+\end{equation}
 
 In such general case, the Stokes Vector is written as:
-\begin{align*}
+\begin{align}
 S_t &= 
@@
 \end{array}
-\right) \\
+\right) \notag \\
  &= I (1 - p)
@@
 \right)
-\end{align*}
+\end{align}
 
@@
 The scattering matrix relates the received signal $E^{Rx}$ with the transmitted $E^{Tx}$ signal as:
-\begin{equation*}
+\begin{equation}
  E^{Rx} = \frac{e^{ikr}}{r} S E^{Tx}
-\end{equation*}
+\end{equation}
 %***IVM: Hai, do you need to explain the k & r terms?
@@
 Normally, horizontal and vertical linear polarization are used for transmission, and thus the scattering matrix, i.e. $S$, would normally have the following expanded form:
-\begin{equation*}
+\begin{equation}
  \left( 
@@
  \right) 
-\end{equation*}
+\end{equation}
 
@@
 Evidently the two matrices are related:
-\begin{equation*}
+\begin{equation}
 C_h = N C_v N^T
-\end{equation*}
+\end{equation}
 where
@@
 They are defined as the matrix that relates the Stokes matrix of sent and received signals.
-\begin{equation*}
+\begin{equation}
 S_t^{Rx} = K S_t^{Tx}
-\end{equation*}
+\end{equation}
 
 Since the Stokes and Jones matrices are related, the Kennaugh and Sinclair matrices are also related, and this relationship is given by:
-\begin{equation*}
+\begin{equation}
 K = 1/2 Q^* S \otimes S^* Q^{T*}
-\end{equation*}
+\end{equation}
 where
@@
 
-\begin{equation*}
+\begin{equation}
 J = 
@@
 The partial covariance matrix then becomes:
-\begin{equation*}
+\begin{equation}
 J = \frac{1}{2} \left(	
@@
 \right) 
-\end{equation*}
+\end{equation}
 In \cite{Raney_2007_IGARSS}, Raney shows that hybrid circular modes bring many conveniences to hardware calibration.
@@
 For full polarimetric SAR data (full-pol) the covariance matrix has the form of
-\begin{equation*}
+\begin{equation}
 C_3 = 
@@
 \end{bmatrix}
-\end{equation*}
+\end{equation}
 For partial polarimetric SAR data (part-pol), it reduces to either of the two following equations:
-\begin{equation*}
+\begin{equation}
   C_{2,h} =
@@
   \end{bmatrix}
-\end{equation*}
+\end{equation}
 Obviously, the statistical behaviour of $C_3$ can be understood by understanding the behaviour of $C_{2h},C_{2v}$ and
-\begin{equation*}
+\begin{equation}
   C_{2,c} = 
@@
 \end{bmatrix}
-\end{equation*}
+\end{equation}
 
@@
 Their main difference lies in investigating the so-called complex correlation coefficient, defined as:
-\begin{equation*}
+\begin{equation}
   \rho = \frac{E \left( S_{pq}S_{rs}^* \right) }{\sqrt{E \left( S^2_{pq} \right) E \left( S^2_{rs} \right) }} = |\rho| e^{j \phi}
-\end{equation*}
+\end{equation}
 with $\phi=arg(\rho)$ is the phase difference angle.
@@
 The commonly used measure of distance for matrices are either the Euclidean or Manhattan distances, defined as:
-\begin{align*}
+\begin{align}
   d(C_x,C_y) &= \sum_{i,j} |\mathbb{R} (C_x - C_y)_{i,j}| + \sum_{i,j} |\mathbb{I} (C_x - C_y)_{i,j}| \\
   d(C_x,C_y) &= \sqrt{\sum_{i,j} |C_x - C_y|_{i,j}^2 }
-\end{align*}
+\end{align}
 where $C_{i,j}$ denotes the (i,j) elements of the POLSAR covariance matrix C,
@@
 It is defined \cite{Lee_1994_IJRS_2299} as:
-\begin{equation*}
+\begin{equation}
   d(C_x,C_y) = \ln|C_y| + tr(C_xC_y^{-1})
-\end{equation*}
+\end{equation}
 where $tr(C)$ denotes the trace of the matrix C. 
@@
 Recent works have suggested alternative dissimilarity measures including the symmetric and asymmetric refined Wishart distance \cite{Anfinsen_2007_ESA_POLINSAR},
-\begin{align*}
+\begin{align}
   d(C_x,C_y) &= \frac{1}{2} tr(C_x^{-1}C_y + C_y^{-1}C_x) - d \\
     d(C_x,C_y) &= \ln|C_x| - \ln|C_y| + tr(C_xC_y^{-1}) - d
-\end{align*}
+\end{align}
 the Bartlett distance \cite{Kersten_2005_TGRS_519},
-  \begin{align*}
+  \begin{align}
   d(C_x,C_y) &= 2 \ln |C_{x+y}| - \ln |C_x| - \ln |C_y| - 2d\ln2
-  \end{align*}
+  \end{align}
 the Bhattacharyya distance \cite{Lee_2011_IGARSS_3740},
-\begin{equation*}
+\begin{equation}
   r(C_x,C_y) = \frac{|C_x|^{1/2} |C_y|^{1/2}}{|(C_x+C_y)/2|}
-\end{equation*}
+\end{equation}
 and the Wishart Statistical test distance \cite{Cao_2007_TGRS_3454}
-\begin{equation*}
+\begin{equation}
   d(C_x,C_y) = (L_x + L_y) \ln|C| - L_x \ln|C_x| - L_y\ln|C_y|
-\end{equation*}
+\end{equation}
 
@@
 the likelihood ratio statistics for POLSAR covariance matrix is considered:  
-\begin{equation*}
+\begin{equation}
   Q = \frac{(L_x+L_y)^{d \cdot (L_x+L_y)}}{L_x^{d \cdot L_x} L_y^{d \cdot L_y}} \frac{|Z_x|^{L_x} |Z_y|^{L_y} }{|Z_x+Z_y|^{(L_x+L_y)}}
-\end{equation*}
+\end{equation}
 
@@
 For the Lee filter \cite{Lee_PAMI_1980}, the weight function is proposed to be:
-\begin{equation*}
+\begin{equation}
 W(t) = 1 - \frac{C_u^2}{C_I^2} 
-\end{equation*}
+\end{equation}
 where
@@
 The speckle filter thus has the same form as the Lee filter but with a different weighting function 
-\begin{equation*}
+\begin{equation}
 W(t) = \frac{1 - \frac{C_u^2}{C_I^2} }{1+ C_u^2} 
-\end{equation*} 
+\end{equation} 
 The Kuan filter takes into account the dependency of noise on the signal. 
@@
 The filter impulse response can, after some simplification, be written as:
-\begin{equation*}
+\begin{equation}
 H(t) = K_1 e^{-K_2 C_I^2(t)}
-\end{equation*}
+\end{equation}
 where
@@
 Such filters operate based on the MAP principle, which is given as:
-\begin{equation*}
+\begin{equation}
 f(x|z) = \frac{f(z|x) f(x)}{f(z)}
-\end{equation*}
+\end{equation}
 where
@@
 
-If a normal distribution is assumed \cite{Medeiros_1998_IAI}, then:
-\begin{equation*}
+If a normal distribution is assumed, then \cite{Medeiros_1998_IAI}:
+\begin{equation}
 f(x) = \frac{1}{\sigma_x \sqrt{2 \pi} } e^{\frac{1}{2} \left( \frac{x-\mu}{\sigma_x} \right)^2 }
-\end{equation*}
+\end{equation}
 and the underlying signal is found by solving the equation
-\begin{equation*}
+\begin{equation}
 x^4 \Gamma^2(N) - x^3 \Gamma^2(N) \mu_x + x^2 \Gamma^2(N) 2N \sigma^2_x - 2 \sigma^2_x z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If a Gamma distribution is assumed \cite{Lopes_1990_IGARSS}, then: 
-\begin{equation*}
+\end{equation}
+
+If a Gamma distribution is assumed, then \cite{Lopes_1990_IGARSS}: 
+\begin{equation}
 f(x) = \frac{\sigma_x}{\Gamma(\lambda)} (x \sigma_x )^{\lambda-1} e^{-x \sigma_x}
-\end{equation*}
+\end{equation}
 For $\lambda=1$, the Gamma distribution is identical to the exponential distribution. 
@@
 The underlying signal is found by solving the equation:
-\begin{equation*}
+\begin{equation}
 x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) (2N - \lambda + 1) - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If an exponential distribution is assumed, then:
-\begin{equation*}
+\end{equation}
+
+If an exponential distribution is assumed, then \cite{Lopes_1990_IGARSS}:
+\begin{equation}
  f(x) = \sigma_x e^{-x \sigma_x}
-\end{equation*}
+\end{equation}
 and the underlying signal is found by solving the equations
-\begin{equation*}
+\begin{equation}
  x^3 \Gamma^2(N) \sigma_x + x^2 \Gamma^2(N) 2N - 2 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If a Chi squared distribution is assumed, then:
-\begin{equation*}
+\end{equation}
+
+If a Chi squared distribution is assumed, then \cite{Lopes_1990_IGARSS}:
+\begin{equation}
  f(x)=\frac{1}{2^{n/2} \Gamma(n/2)} x^{n/2-1} e^{(-x/2)}
-\end{equation*}
+\end{equation}
 and the true signal is found by solving the equation
-\begin{equation*}
+\begin{equation}
  x^3 \Gamma^2(N) + x^2 \Gamma^2(N) (4N-n+2) - 4 z^2 \Gamma^2(N+1/2) = 0
-\end{equation*}
-
-If a log-normal distribution is assumed \cite{Medeiros_2003_IJRS}, then:
-\begin{equation*}
+\end{equation}
+
+If a log-normal distribution is assumed, then \cite{Medeiros_2003_IJRS}:
+\begin{equation}
  f(x) = \frac{1}{\sigma_x \sqrt{2 \pi}} x^{-1} e^{\frac{-1}{2 \sigma_x} (\ln(x) - \mu_x)^2}
-\end{equation*}
+\end{equation}
 and
-\begin{equation*}
+\begin{equation}
  x^2 \Gamma^2(N) (-2N \sigma^2_x - \sigma^2_x -\log(x) + \mu_x) + 2 z^2 \Gamma^2(N+1/2)=0
-\end{equation*}
+\end{equation}
 %Some of them being: Gaussian PDF, Gamma PDF, chi square, Rayleigh, beta, log-normal ...
@@
 He then proposed to apply the weighted averaging on the full covariance matrix instead of single-channel intensities values:
-\begin{equation*}
+\begin{equation}
 C_{out} = C_{avg} + w (C_{curr} - C_{avg})
-\end{equation*}
+\end{equation}
 where
@@
 They first proposed to model $S_hS_v^*$ as having both additive and multiplicative components:
-\begin{equation*}
+\begin{equation}
 S_pS_q^* = \psi |\rho | e^{i \theta} + \psi \bar{z}_n N_c (1-n_m) e^{i \theta} + \psi (n_{ar} + i n_{ai}) 
-\end{equation*}
+\end{equation}
 where
@@
 In this method, the phase difference is defined as:
-\begin{equation*}
+\begin{equation}
 \phi = \arg{ \left( S_pS_q^* \right) }
-\end{equation*}
+\end{equation}
 and the PDF for the phase difference as:
-\begin{equation*}
+\begin{equation}
 pdf(\phi) = \frac{\Gamma(3/2) (1-|\rho|^2) \beta}{2 \sqrt{\pi} \Gamma(1) (1-\beta^2)} + \frac{(1-|\rho|^2)}{2 \pi} F_{1,2}(1,1,1/2,\beta^2)
-\end{equation*}
+\end{equation}
 where
@@
 The normalized magnitude, is defined as:
-\begin{equation*}
+\begin{equation}
 \xi = \frac{E \left( S_pS_q^* \right)}{\sqrt{ E \left( |S_p|^2 \right) E \left( |S_q|^2 \right) }}
-\end{equation*}
+\end{equation}
 and the PDF is found to be:
-\begin{equation*}
+\begin{equation}
 pdf(\xi) = \frac{4\xi}{\Gamma(1)(1-|\rho|^2)} I_0 \left( \frac{2 |\rho| \xi}{1-|\rho|^2} \right) K_0 \left(  \frac{2 \xi}{1-|\rho|^2} \right)
-\end{equation*}
+\end{equation}
 	$I_0$ and $K_0$ are modified Bessel functions.

### 2014-06-26 4/polsar.tex
auto

@@
 %\begin{equation}
-\begin{align*}  
+\begin{align}  
 s_{part}=\begin{bmatrix}
@@
 %\end{equation}
-\end{align*}
+\end{align}
 
@@
   the vector is three-dimensional ($d=3$) and is presented as:
-\begin{align*}
+\begin{align}
 s_{full}=\begin{bmatrix}
@@
 \end{bmatrix}
-\end{align*}
+\end{align}
 
@@
 These are formed as the mean Hermitian outer product of single-look scattering vectors
-\begin{align*}
+\begin{align}
   C_v = \langle ss^{*T} \rangle = \frac{1}{L} \sum^L_{i=1}s_is_i^{*T}
-\end{align*}
+\end{align}
 with $s_i$ denotes the single-look scattering vector,
@@
 Subsequently their means and variances can be computed from the given characteristic functions as:
-  \begin{align*}
+  \begin{align}
     avg \left[ \chi(2L) \right]&= 2L \\
@@
 var \left[ \Lambda(2L) \right] &= \psi^1(L)
-  \end{align*}
+  \end{align}
   where $\psi^0()$ and $\psi^1()$ stands for digamma and trigamma functions respectively.
@@
 
-\begin{eqnarray*}
+\begin{eqnarray}
   avg \left[ \prod^{d-1}_{i=0} \chi^2(2L-2i) \right] &=& 2^d \cdot \prod^{d-1}_{i=0} (L-i), \\
@@
   var \left[ \sum^{d-1}_{i=0} \Lambda(2L-2i) \right] &=& \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 From another perspective where the POLSAR is known as having come from an homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
-\begin{eqnarray}
-\end{eqnarray}
+%\begin{eqnarray}
+%\end{eqnarray}
 \begin{equation}
@@
   the characteristic functions for the summative random variables can be derived as:
-\begin{align*}
+\begin{align}
   CF_{\Lambda^d_L}(t) &= \frac{2^{idt}}{\Gamma(L)^d} \prod^{d-1}_{j=0} \Gamma(L-j+it) \\
@@
   CF_{\mathbb{C}}(t) &=  \prod^{d-1}_{j=0} \frac{\Gamma(2L-2j) B(L-j-it,L-j+it)}{\Gamma(L-j)^2}
-\end{align*}
+\end{align}
 
@@
 {\footnotesize
-\begin{align*}
+\begin{align}
   \mathbb{R} &= \frac{|C_v|}{|\Sigma_v|} \sim \frac{1}{(2L)^d} \prod^{d-1}_{i=0} \chi^2(2L-2i) \\% \label{eqn:polsar_ratio_det_cov_dist} \\
@@
   \mathbb{E} &= mse(\mathbb{L}) =\left[ \sum^{d-1}_{i=0} \psi^0(L-i) - d \cdot \ln{L} \right]^2 +  \sum^{d-1}_{i=0} \psi^1(L-i) %\label{eqn:polsar_dispersion_mse} 
-\end{align*}
+\end{align}
 }%
@@
 {\footnotesize
-\begin{align*}  
+\begin{align}  
   I &\sim \bar{I} \cdot pdf \left[ e^{-R} \right] \\
@@
   \mathbb{E} &= mse(\mathbb{L}) = \frac{1}{\ln^2{2}}( \gamma^2 + \pi^2/6 ) = 4.1161 
-\end{align*}
+\end{align}
 }%
 but also the following well-known results for multi-look SAR, i.e. $d=1,L>1$:
-  \begin{align*}
+  \begin{align}
 I &\sim pdf \left[ \frac{L^L x^{L-1} e^{-Lx/\bar{I}}}{\Gamma(L) \bar{I}^L} \right] \\
 N = \ln{I} &\sim pdf \left[ \frac{L^L}{\Gamma(L)} e^{L(x-\bar{N})-Le^{x-\bar{N}}} \right]
-  \end{align*}
+  \end{align}
 Furthermore, the following results for multi-look SAR data, which can be thought of
@@
 
-  \begin{align*}
+  \begin{align}
     \mathbb{R} &= \frac{I}{\bar{I}} \sim pdf \left[ \frac{ L^{L} x^{L-1} e^{-Lx}}{ \Gamma(L)} \label{eqn:multi_look_SAR_ratio_dist} \right]\\
@@
     \mathbb{E} &= mse(\mathbb{L}) = \left[ \psi^0(L) - \ln{L} \right]^2 + \psi^1(L)
-  \end{align*}
+  \end{align}
 
@@
 
+%TODO: add p-value here for 
 \begin{figure}[bth!]
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion (p-value HH-HV=0.????)]{
+	\subfloat[part-pol (2x2) dispersion]{
 		 \epsfxsize=2.5in
@@
 	} \\
-	\subfloat[full-pol (3x3) dispersion (p-value=0.????)]{
+	\subfloat[full-pol (3x3) dispersion]{
 		 \epsfxsize=2.5in

### 2014-06-26 5/applications.tex
auto

@@
 
-\section{Clustering SAR images using the consistent measures}
+\section{
+  Clustering and filtering SAR images 
+  \footnote{
+During the revision of this thesis, Nielsen's work \cite{Nielsen_2012_ICASSP} is brought forward to the author's attention.
+This work is quite similar and is published after the publication for the work presented in this thesis \cite{Le_2010_ACRS}.
+It excels by providing a theoretical proof for its k-MLE procedure in the case of exponential mixtures.
+Its drawback: it focuses only on the exponential distribution, which is just one special case of the work presented here.
+  }
+}
 \label{sec:k_mle}
@@
   the question of whether it is homogeneous or not can be investigated using
-the statistical hypothesis test described in chapter \ref{chap:sar}. 
+the statistical hypothesis test described in Chapter \ref{chap:sar}. 
 If that is found to be the case, a clustering algorithm can then be applied to partition the area into smaller regions. 
@@
 
-\begin{eqnarray*}
+\begin{eqnarray}
 \ln[P(X^l | \mu )] 
@@
 %	&=& n \ln \ln 2 +  \displaystyle{\sum^n_{i=1}{ \ln \left( 2^{x^l_i - \mu} \right) - \ln \left( e^{2^{ x^l_i -\mu }} \right) }} 
-\end{eqnarray*}
+\end{eqnarray}
 
 The parameter $\mu$ which maximizes the likelihood is found by setting its derivatives to zero:
-\begin{eqnarray*}
+\begin{eqnarray}
 \displaystyle{ \frac{ \partial{ \ln[P( X^l | \mu )] }  }{\partial{ \mu }} }
@@
 %	&=& - \ln2 \cdot \frac{ \sum^n_{i=1}{ 2^{ x^l_i } }}{2^\mu}  
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 
-PS: During the revision of this thesis, this work \cite{Nielsen_2012_ICASSP} is brough forward to the author's attention.
-This work is quite similar and is published after the publication for the work presented in this thesis \cite{Le_2010_ACRS}.
-It excels by providing a theoretical proof for its k-MLE procedure in the case of exponential mixtures.
-Its drawback: it focuses only on the exponential distribution, which is just one special case of the work presented here.
-
 \section{SAR Speckle filtering using the consistent measures}
+\label{sec:f_mle}
 
@@
 \centering
-\subfloat[Intensity histogram]{
+%\subfloat[Intensity histogram]{
   \epsfxsize=6cm
@@
   \epsffile{images/consistent_contrast_log_domain.made.eps}
+%  }
+\caption{Consistent Distance Property and the f-MLE Estimations}
 \label{fig:consistent_contrast_log_domain}
-  }
-\caption{Consistent Distance Property and the f-MLE Estimations}
 \end{figure}
@@
 	\subfloat[f-MLE (incl): 123]{
-		 \epsfxsize=3.5cm
-		 \epsfysize=3.5cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/incl_distance_pdf_by_iterations.123.made.eps} 
@@
 	\subfloat[f-MLE (incl): 456]{
-		 \epsfxsize=3.5cm
-		 \epsfysize=3.5cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/incl_distance_pdf_by_iterations.345.made.eps} 
 		 \label{fig:plot_incl_distance_pdf_by_iterations.345}
-	} 
+	} \\ 
 	\subfloat[f-MLE (excl): 123]{
-		 \epsfxsize=3.5cm
-		 \epsfysize=3.5cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/excl_distance_pdf_by_iterations.123.made.eps} 
@@
 	\subfloat[f-MLE (excl): 456]{          
-		 \epsfxsize=3.5cm
-		 \epsfysize=3.5cm
+		 \epsfxsize=6cm
+		 \epsfysize=6cm
 		 \epsffile{images/excl_distance_pdf_by_iterations.345.made.eps} 
@@
 \section{Evaluating SAR Speckle Filters using the consistent measures of distance}
+\label{sec:sar_filters_evaluation}
 
@@
 variables as: 
-\begin{equation*}
+\begin{equation}
 var(\hat{X}^L)= \frac{1}{\ln^2(2)} \left( \frac{\pi^2}{6} - \sum^{L-1}_{i=1}{\frac{1}{i^2}} \right).
 \label{eqn:perf_index_theoretical}
-\end{equation*}
+\end{equation}
 
@@
 %\setlength{\mathindent}{1cm}  
-\begin{align*}
+\begin{align}
 &\frac{\pi^2}{6} = \sum^{\infty}_{i=1}{ \frac{1}{i^2} } &\\
@@
 &\frac{1}{L} - \frac{1}{\infty} < \sum^{\infty}_{i=L}{ \frac{1}{i^2} }  < \frac{1}{L-1} - \frac{1}{\infty} &
-\end{align*}
+\end{align}
 
@@
 \section{Evaluating POLSAR Speckle Filters using the consistent measures of distance}
+\label{sec:polsar_speckle_filters_evaluation}
 
@@
 {\small
-\begin{align*}
+\begin{align}
 &  var_2 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1)     = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2 &\\
@@
 & L = 2/var_2 \left[ \ln |C_v| \right] + 1 & \\
-\end{align*}
+\end{align}
 }%
@@
 {\small
-\begin{align*}
+\begin{align}
 &  var_3 \left[ ln|C_v| \right] = \psi^1(L) + \psi^1(L-1) + \psi^1(L-2)    = \sum^{\infty}_{i=L}1/i^2 + \sum^{\infty}_{i=L-1}1/i^2  + \sum^{\infty}_{i=L-2}1/i^2 & \\
@@
 & L = 3/var_3 \left[ \ln |C_v| \right] + 1.5 &
-\end{align*}
+\end{align}
 }%

### 2014-06-26 6/conclusional_discussion.tex
auto

@@
                 the original domain and logarithmic transformation
-                converts this into a homoskedastic model (Sections \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
+                converts this into a homoskedastic model (Sections: \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
                 \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
                 the multi dimensional POLSAR as well as for the one
-                dimensional SAR data are derived (Sections \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
+                dimensional SAR data are derived (Sections: \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
                 \item \label{itm:sar_validation} These statistical models are validated against both
@@
                 speckle filtering: with new statistical test for
-                homogeneity and new speckle filters proposed (Section \ref{sec:k_mle}, \ref{sec:f_mle}).
-                \item \label{itm:log_mse} Tconsistent sense of subtractive
+                homogeneity and new speckle filters proposed (Sections: \ref{sec:k_mle}, \ref{sec:f_mle}).
+                \item \label{itm:log_mse} The consistent sense of subtractive
                 distance also helps in the problem of evaluating SAR
@@
                 suppression power in evaluating SAR speckle filters.
-                \item \label{itm:extend_sar_to_polsar} Section \ref{sec:polsar_models_validation} demonstrates an example where the existing SAR
-                processing technique of ENL estimation is extended towards POLSAR data.
+                \item \label{itm:extend_sar_to_polsar} Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
+                processing techniques are extended towards POLSAR data.
                 \end{enumerate}
@@
 The
-                proposed models for POLSAR also bring forward an
+                proposed models for POLSAR also bring forward several
                 important benefits.
@@
 can be simulated as:
-\begin{align*}
+\begin{align}
   \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
   Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
-\end{align*}
+\end{align}
 where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.

### 2014-06-26 1_introduction/introduction.tex
auto

@@
 Secondly, simulation provides ground-truth, without which quantitative evaluation of estimators would have been impossible.
-Last but certainly not least, such a framework allow one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.
+Thirdly, such a framework allows one to apply estimators repeatedly, and results from different estimators can be statistically and reliably compared.
 For example, this would allow different authors to compare results quantitatively.
@@
 \centering
+\caption{Collected imagery data}
+\label{tbl:collected_data}
 \begin{tabular}{|c|c|c|}
@@
 \end{tabular}
-\caption{Collected imagery data}
-\label{tbl:collected_data}
 \end{table}
@@
 Interestingly, the dual-problems stated above are found to have a single solution.
-They are the derivation of scalar, representative and homoskedastic statistical models for the multidimensional, inter-correlated and heteroskedastic POLSAR data.
+They are the derivation of scalar, representative and homoskedastic statistical models for the multi-dimensional, inter-correlated and heteroskedastic POLSAR data.
 %  which is
@@
                 intensity.
-                \item \label{itm:polsar_validation} The model os to be validated against practical real-life
+                \item \label{itm:polsar_validation} The model is to be validated against practical real-life
                 captured POLSAR data.
@@
                 beneficial applications of these models is presented in
-                chapter \ref{chap:applications}, where the property of a consistent sense of variance
+                Chapter \ref{chap:applications}, where the property of a consistent sense of variance
                  helps to break the vicious cycle in SAR
@@
 (i.e. see Research Contribution \ref{itm:filter_vicious_circle} to \ref{itm:extend_sar_to_polsar})
-Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding chapter \ref{chap:conclusions}.
+Finally, the contribution of the thesis with respect to the research objectives and research impact is discussed in the concluding Chapter \ref{chap:conclusions}.
 

### 2014-06-26 2/literature_review.tex
auto

@@
 Specifically, since one SAR resolution cell is very big in comparison to the radar wavelength, it normally consists of many elementary scatterers.
-The data point of each SAR pixel then arises from the combined interference effect of the backscattered waves from these different scatterers.
+The data point of each SAR pixel then arises from the combined interference effect of the back-scattered waves from these different scatterers.
 This effect causes natural variation in SAR intensity image even when the underlying scene is highly homogeneous.
 
-SAR speckle phenomena are explained as the interference of many coherent but dephased backscattering components;
+SAR speckle phenomena are explained as the interference of many coherent but dephased back-scattering components;
   each reflecting from different and distributed elementary scatterers \cite{Oliver_ProcIEEE_1963, Leith_ProcIEEE_1971}. 
@@
 
-Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat, TerraSAR, Alos-PalSAR were launched.
+Systems were then engineered and commercial POLSAR satellites, e.g. RadarSat-2, TerraSAR, Alos-PalSAR were launched.
 However due to operational restrictions on payload, power and data-downlink, the satellites also offer dual-channel polarimetric SAR modes as a compromise between theoretical polarimetric requirements and practical limitations.
@@
 Also in a follow up study \cite{Raney_2007_TGRS}, he demonstrated the classification power of hybrid polarimetry.
-Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using SVM techniques, compact polarimetry mode shows comparable results to full polarimetric data.
+Furthermore, Lardeux \cite{Lardeux_2007_ESASP} found that for target classification using Support Vector Machine (SVM) techniques, compact polarimetry mode shows comparable results to full polarimetric data.
 Notably, the hybrid architectural concept has been adopted and brought towards implementation by NASA's upcoming Desdynl satellite \cite{Raney_2009_RadarConf}.
@@
 %Clearly should such PDF being estimatable from the data it-self, that would potentially presents an good opportunity for this class of speckle filters.
-Other distributions that have been proposed include the heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation} \dots
+Other distributions that have been proposed include the heavy tailed Rayleigh distribution \cite{Sun_2006_ICVES}, Weibull distribution \cite{Nezry_1997_IGARSS}, beta distribution \cite{Nezry_1997_IGARSS}, Rician distribution \cite{Lewinski_1983_TAntennaPropagation}.
 Evidently, the performance of these filters are dependent on the underlying distribution of the back-scattering coefficient on the particular surface being imaged. 
 In this context, the community appears to focus on using Bayesian inference to choose the most suitable distributions \cite{Walessa_2000_TGRS}.
-One of the additive and homoskedastic SAR model's benefits is the possible hypothesis that the underlying distribution of the back scattering coefficient is estimable discussed in subsequent chapters.
+One of the additive and homoskedastic SAR model's benefits is the possible hypothesis that the underlying distribution of the back-scattering coefficient is estimable discussed in subsequent chapters.
 %In our approach, we hypothesize that the underlying distribution of the back scattering coefficient is estimable, at least in the log-transformed domain, as will be described later.
@@
 Compared to SAR technologies, most POLSAR techniques are relatively recent. 
-Published literatured on POLSAR speckle filtering indicate that filtering the covariance matrix off-diagonal elements is still an open problem.
+Published literature on POLSAR speckle filtering indicates that filtering the covariance matrix off-diagonal elements is still an open problem.
 The problem can be traced back to the lack of a statistical model for the covariance matrix in polarimetry.
@@
 	$n_{ar} + i n_{ai}$ is the second additive speckle noise component with $E(n_{ar}) = E(n_{ai}) = 0$ and $var(n_{ar}) = var(n_{ai}) = \frac{1}{2} (1-|\rho|^2)^{1.32}$.
-
 The model is overly complicated and to do speckle filtering, various approximations have to be used.
 
-Another different approach is proposed bu Lee \cite{Lee_CRCPress_2009}  to model $S_hS_v^*$.
+Another different approach is proposed by Lee \cite{Lee_CRCPress_2009}  to model $S_hS_v^*$.
 In this method, the phase difference is defined as:
@@
 	(a) modelling and simulation, which provide the ground-truth data in different scenarios of underlying distribution, and
-	(b) analysing the interdependency between noise and the underlying signal, as well as the dependence of each filter's performance on the different underlying distribution scenarios and
+	(b) analysing the inter-dependency between noise and the underlying signal, as well as the dependency of each filter's performance on the different underlying distribution scenarios and
 	(c) establishing consistent criteria to evaluate speckle suppression power as well as the adaptive capabilities in reconstructing the underlying signal.

### 2014-06-26 3/sar.tex
auto

@@
 \section{Original Heteroskedastic Model of SAR data}
+\label{sec:heteroskedastic_sar}
 
@@
 \caption{eqn:SAR Unit Amplitude PDF}
-pdf(A_1) = 2A_1 e^{ \left( A_1^2 \right) }
+pdf(A_1) = 2A_1 e^{ - \left( A_1^2 \right) }
 \end{equation}
@@
 \centering
+\caption{ Mean and Variance of Original SAR data }
+\label{tbl:orginal_sar_avg_var}
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
-\caption{ Mean and Variance of Original SAR data }
-\label{tbl:orginal_sar_avg_var}
 \end{table}
@@
 \section{The Effects of Heteroskedasticity in SAR Processing}%IVM: shortened to make it look nicer
+\label{sec:heteroskedastic_sar_processing}
 
@@
 
-The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously. 
+%The nature of SAR speckle is stochastic over homogeneous areas and heteroskedastic heterogeneously.
+As shown in the previous section,
+  over heterogeneous area, the stochastic SAR speckle is heteroskedastic in nature.
 Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
@@
 If the variance is known \textit{a priori}, it has been proven \cite{Aitken_1934_ProcsRoyalSocEdinburg}, that a weighted mean estimator is the best linear unbiased estimator. 
-Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most known common successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations. 
+Interestingly, as noted by Lopes \cite{Lopes_TGRS_1990}, most commonly known successful adaptive filters \cite{Lee_PAMI_1980, Kuan_1985_PAMI, Frost_PAMI_1982} do make use of weighted mean estimations.
 The problem, however, is that in SAR speckle filtering, variance is not known \textit{a priori}. 
@@
 \section{The Homoskedastic Effect of Logarithmic Transformation}
+\label{sec:homoskedastic_sar}
 
@@
 \begin{equation}
+pdf(L_{1}^{I}) = 2^{L_1^I} e^{-2^{L_1^I}}  
+  \caption{eqn:SAR Unit Log Intensity PDF}
   \label{eqn:SAR Unit Log Intensity PDF}
-  \caption{eqn:SAR Unit Log Intensity PDF}
-pdf(L_{1}^{I}) = 2^{L_1^I} e^{-2^{L_1^I}}  
 \end{equation}
 \begin{equation}
+pdf(L_I) = 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
+  \caption{eqn:SAR Log Intensity PDF}
   \label{eqn:SAR Log Intensity PDF}
-  \caption{eqn:SAR Log Intensity PDF}
-pdf(L_I) = 2^{\left( L_I - 2 \log_2 \sigma \right)} e^{-2^{\left( L_I - 2 \log_2 \sigma \right)} }  
 \end{equation}
@@
 \centering
-%\begin{center}
-
+\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
+\label{tbl:sar_log_domain_avg_var}
 \begin{tabular}{|l|l|}
@@
 \end{tabular}
-
-\caption{ Mean and Variance of Log Transformed values: here the variance is no longer dependent on $\sigma$ }
-\label{tbl:sar_log_domain_avg_var}
-%\end{center}
 \end{table}
@@
 \centering
+
+\caption{ The properties of observable SAR random variables }
+\label{tbl:sar_variables_properties}
 
@@
 \end{tabular}
-
-\caption{ The properties of observable SAR random variables }
-\label{tbl:sar_variables_properties}
 
@@
 \section{Consistent Measures of Distance in the Log-Transformed Domain}
+\label{sec:consistent_measures_distance_sar}
 
@@
 \centering
+\caption{Cut off values}
+\label{tab:var_cut_off_values}
+
 \small
@@
 
-\caption{Cut off values}
-\label{tab:var_cut_off_values}
 \end{table}

### 2014-06-26 4/polsar.tex
auto

@@
 Subsequently the statistical models for SAR are shown to be a special case of
-                the proposed models for POLSAR
+                the proposed models for POLSAR. 
 And finally these proposed models are validated against real-life practical data.
@@
 
+\subsection{The Determinant and Log-Determinant Models}
+
 From Eqn. \ref{eqn:prod_chi_squared_rv} and Eqn. \ref{eqn:sum_log_chi_squared_rv}
@@
   the logarithmic transformation converts this into a more familiar additive noise.
+
+\subsection{The Statistical Properties of the Proposed Models}
 
@@
 This section introduces the consistent sense of distance from a few different perspectives.
+
+\subsection{The Determinant-Ratio and Log-Distance Models}
+
 First assuming that the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
 the following random variables,
-  namely ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
+  namely determinat-ratio ($\mathbb{R}$) and log-distance ($\mathbb{L}$),
   are observables according to their definitions:
@@
 
-From another perspective where the POLSAR is known as having come from an homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
+\subsection{The Dispersion and Contrast Models}
+
+From another perspective where the POLSAR is known as having come from a homogeneous area, but the true value of the underlying signal $\Sigma_v$ is \textit{unknown}, consider the dispersion ($\mathbb{D}$) and contrast ($\mathbb{C}$) random variables being defined as:
 %\begin{eqnarray}
@@
 \end{equation}
+
+\subsection{The Statistical Properties of the Proposed Models}
 
@@
 Fig. \ref{fig:verify_multi_look_SAR_dispersion_contrast_models} presents the the results of an experiment carried out for the stated purpose.
-In the experiment, the intensity of a single-channel of SAR data (HH) for an homogeneous area in the AIRSAR Flevoland dataset is extracted.%***IVM do you need to give a ref to the dataset?
+In the experiment, the intensity of a single-channel of SAR data (HH) for a homogeneous area in the AIRSAR Flevoland dataset is extracted.%***IVM do you need to give a ref to the dataset?
 Then the histograms for the log-distance and and contrast are plotted against the theoretical PDF given above.
@@
 models  derived in the previous sections, 
-histogram plots of its simulated data are generated graphically. This is then compared against  the histogram plots of the  real-life captured data samples extracted from an homogeneous area.
+histogram plots of its simulated data are generated graphically. This is then compared against  the histogram plots of the  real-life captured data samples extracted from a homogeneous area.
 
@@
 same parameters, the two plots match each other reasonably well.
-For this verification, an homogeneous area was chosen from the AIRSAR Flevoland POLSAR data.
+For this verification, a homogeneous area was chosen from the AIRSAR Flevoland POLSAR data.
 Theoretical models are then verified against the  real life data.
@@
 the other four models to be investigated require an estimation of the ``true'' underlying signal $|\Sigma_v|$. 
-There are two ways to estimate this quantity over an homogeneous area.
+There are two ways to estimate this quantity over a homogeneous area.
 The traditional way is to simply assume that the true signal is equal to the average of the POLSAR covariance matrix in its original domain, i.e. $\Sigma_v = avg(C_v$).
@@
 
-\subsection{Estimating the Effect Number-of-Looks (ENL)}
+\subsection{Estimating the Effective Number-of-Looks (ENL)}
 
@@
 Specifically, Eqn. \ref{eqn:var_log_det_is_homoskedastic} can be rewritten as: 
-\begin{equation*}
+\begin{equation}
   var \left[ ln|C_v| \right] = f(L) = \sum^{d-1}_{i=0} \psi^1(L-i)
-\end{equation*}
+\end{equation}
 where $\psi^1()$ denotes tri-gamma function.
@@
   and nine-look processing is applied.
-The dispersion histogram in the log-transformed domain is computed over an homogeneous area.
+The dispersion histogram in the log-transformed domain is computed over a homogeneous area.
 The histograms generated by the theoretical models for  nominal ENL value
@@
 \caption{9-look processed Radarsat2 data does not exactly exhibit 9-look data characteristics.
-An homoskedastic model in the log-transformed domain can be used to successfully estimate the effective ENL and thus offer a better model of the data.}
+A homoskedastic model in the log-transformed domain can be used to successfully estimate the effective ENL and thus offer a better model of the data.}
 \label{fig:handling_radarsat2_oversampling_practice}

### 2014-06-26 5/applications.tex
auto

@@
 filtering.
-This chapter also shows how the MSE can then be 
+This chapter also shows how the Mean Squared Error (MSE) can then be 
 applied in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
@@
 In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
-Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
+Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective is to estimate $\sigma$. 
 This section shows how $\sigma$ can be estimated in the log-transformed domain.
 
-It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$.
+It has already been proven (see Eqn.
+\ref{eqn:SAR Log Intensity PDF}) that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$.
 %***IVM: Hai can you clarify the \ln 2 \frac{ 2^d }{ e^{2^d} }, is that a base 2 in there? Maybe some brackets would help....
@@
 The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
-This is illustrated with ``tighter'' distance histograms and reducing MSE, as plotted in Fig. \ref{fig:Homogeneous_Area}
+This is illustrated with ``tighter'' distance histograms and reducing Mean Squared Error (MSE), as plotted in Fig. \ref{fig:Homogeneous_Area}
 
@@
 %The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
-over homogeneous areas.
+%over homogeneous areas.
 
@@
 \centering
+\caption{ Speckle Suppression Power: ENL and Variance }
+\label{tab:enl_in_log_domain}
 \begin{tabular}{r|c|c|c|c}
@@
 \end{tabular}
-\caption{ Speckle Suppression Power: ENL and Variance }
-\label{tab:enl_in_log_domain}
 \end{table}
@@
 \centering
+\caption{Performance of various filters over homogeneous areas}
+\label{tab:homogeneous_performance_filters}
 \begin{tabular}{c|c|r|c|r}
@@
 \end{tabular}
-\caption{Performance of various filters over homogeneous areas}
-\label{tab:homogeneous_performance_filters}
 \end{table}
@@
 evaluated by examining the separability of the two background and target populations.
-Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
+Figs. \subref*{fig:hetero_patterns_roc_auc:hist_unfiltered} and \subref*{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
 	allows visual evaluation of target and clutter histograms and their separability.
 Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
-in Figs. \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
+in Figs. \subref*{fig:hetero_patterns_roc_auc:roc_unfiltered} and \subref*{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
 respectively, and is measured by computing the Area Under these Curves (AUC).
@@
 	can help to explain how the MSE is related to the histograms' separation capability.
-In pre-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
-\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
+In pre-filtered images, shown in Figs. \subref*{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
+\subref*{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
 Then the separability of background and target populations depends only on the variance of the additive noise. 
@@
 
-In post-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
-\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
+In post-filtered images, shown in Figs. \subref*{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
+\subref*{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
 Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
-A closer examination of Fig. \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
+A closer examination of Fig. \subref*{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
 Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
@@
 down into the requirements of radiometric preservation and speckle suppression.
-In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
+In the log-transformed domain, these requirements are equivalent to the bias and variance evaluation of 
 statistical estimators respectively.
@@
 \centering
+\caption{Lower MSE suggest better feature detection, measured by the AUC index}
+\label{tab:mse_auc_in_log_domain}
+
 \begin{tabular}{c|r|c|c|r}
@@
 
-\caption{Lower MSE suggest better feature detection, measured by the AUC index}
-\label{tab:mse_auc_in_log_domain}
 \end{table}
@@
 \centering
+\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
+\label{tab:mse_auc_corr_coeff}
 \begin{tabular}{c|c|c}
@@
 \end{tabular}
-
-\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
-\label{tab:mse_auc_corr_coeff}
 \end{table}
@@
 \centering
+\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
+\label{tab:mse_true_noise_log_domain}
 \begin{tabular}{r|r|c|c}
@@
 \end{tabular}
-
-\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
-\label{tab:mse_true_noise_log_domain}
 \end{table}
@@
 \centering
+\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
+\label{tab:mse_in_real_image}
 \begin{tabular}{c|r|r}
@@
 \end{tabular}
-\caption{Our Conjecture: Most Suitable Speckle Filter For The Scene Can Be Chosen Using The Residual MSE.}
-\label{tab:mse_in_real_image}
 \end{table}

### 2014-06-26 6/conclusional_discussion.tex
auto

@@
                 \item The proposed models for POLSAR are also shown to include the traditional SAR statistical models (Section \ref{sec:sar_special_case_of_polsar}).
-                \item \label{itm:polsar_validation} The proposed models are validated against practical real-life
+                \item The proposed models are validated against practical real-life
                 captured POLSAR data in Section \ref{sec:polsar_models_validation}.
@@
                 \begin{enumerate}
-                \item \label{itm:log_transform} The statistical model for POLSAR data are shown to be heteroskedastic in
+                \item The statistical model for POLSAR data are shown to be heteroskedastic in
                 the original domain and logarithmic transformation
                 converts this into a homoskedastic model (Sections: \ref{sec:heteroskedastic_sar}, \ref{sec:homoskedastic_sar}, \ref{sec:polsar_heterosked_model_and_log_transform}).
-                \item \label{itm:sar_measures_distance} Homoskedastic measures of distance for
+                \item Homoskedastic measures of distance for
                 the multi dimensional POLSAR as well as for the one
                 dimensional SAR data are derived (Sections: \ref{sec:consistent_measures_distance_sar}, \ref{sec:consistent_measures_distance_polsar})
-                \item \label{itm:sar_validation} These statistical models are validated against both
+                \item These statistical models are validated against both
                 practical SAR and POLSAR data (Sections: \ref{sec:sar_special_case_of_polsar}, \ref{sec:polsar_models_validation})
@@
                 \begin{enumerate}
-                \item \label{itm:filter_vicious_circle} The consistent sense of variance
+                \item The consistent sense of variance
                 is shown to help breaking the vicious cycle in the problem of SAR
@@
                 homogeneity and new speckle filters proposed (Sections: \ref{sec:k_mle}, \ref{sec:f_mle}).
-                \item \label{itm:log_mse} The consistent sense of subtractive
+                \item The consistent sense of subtractive
                 distance also helps in the problem of evaluating SAR
@@
                 suppression power in evaluating SAR speckle filters.
-                \item \label{itm:extend_sar_to_polsar} Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
+                \item  Sections \ref{sec:polsar_models_validation} and \ref{sec:polsar_speckle_filters_evaluation} demonstrate several instances where existing SAR
                 processing techniques are extended towards POLSAR data.
@@
                 framework, the MSE is proposed as the single unified
-                evaluation criteria for SAR speckle filters.
+                evaluation criterion for SAR speckle filters.
 In
@@
                 thesis also illustrates how the MSE evaluation
-                criteria can also be extended from SAR to POLSAR.
+                criterion can also be extended from SAR to POLSAR.
 

### 2014-06-27 1_introduction/introduction.tex
auto

@@
 The second main objective is to derive homoskedastic measures of distance despite its multiplicative and heteroskedastic nature.
-This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
-%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
-%  it also results in a homoskedastic statistical model.
-%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
-%After these models are validated against practical data, their beneficial applications are further explored.
-To combine these two seemingly disconnected threads of research, the results for SAR are extended to POLSAR,
-  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.
-%***IVM I changed "version" to "superset" in the sentence above.
+The proposed generic models are applicable to multi-dimensional POLSAR data.
+Moreover, when the multi-dimensional data is collapsed into one dimension, the specific case of the proposed model matches perfectly with the model proposed by Arsenault \cite{Arsenault_JOptSocAm_1976}.
+Thus - even before performing detailed evaluation - there is good evidence that the proposed generic models are at least as appropriate as the widely accepted model cited above.
+%This is first applied on the simpler case of SAR data. %devided into a few smaller objectives.
+%%For this purpose, first log transformation is shown to not only convert the multiplicative noise model into an adaptive one, 
+%%  it also results in a homoskedastic statistical model.
+%%From this consistent sense of variance, the second step illustrates the consistent sense of contrast and distance.
+%%After these models are validated against practical data, their beneficial applications are further explored.
+T%o combine these two seemingly disconnected threads of research, the results for SAR are extended to POLSAR,
+%  since the thesis also shows that the POLSAR models are a generic multi-dimensional superset of the traditional SAR data.
+%***IVM I changed "ver%sion" to "superset" in the sentence above.
 Please check if you are comfortable with that change, and if not, change it back!
-%Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
-%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
-%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives.
+%%Thus the homoskedastic theoretical models and their benefits are extended from SAR to POLSAR.   
+%%The 3 paragraphs are collapsed into 1: to address Prof Vun's comment:
+%%(comment: you are stating the objectives repetitively so far – I counted three time so far, and confuse the results obtained with the objectives.
 There is no need to re-emphasize the objective if the write-up is clear)

### 2014-06-27 3/sar.tex
auto

@@
 %  which is defined as the dependence of conditional expected variance of SAR data on the conditional expectation of mean.
-This means that  the conditional expected variance of SAR data is dependent on the conditional expectation of the mean.   
+%This means that  the conditional expected variance of SAR data is dependent on the conditional expectation of the mean.
+In statistical context, heteroskedasticity and homoskedasticity are terms defined to denote the fact that different sub-populations of a given set of samples can have different or similar variability respectively.
+In the context of SAR (and POLSAR) imagery, they respectively denote the fact that different areas in a given image can have different different or similar sample variance, depending on the underlying signal $\sigma$.
 In the context of speckle filtering which aims to estimate the unknown parameter $\sigma$,
@@
 The consistent feature is explored and illustrated in this section from two different perspectives.
+
+\subsection{The Distance and Log-Distance Models}
+
 First, the back-scattering coefficient $\sigma$ is assumed to be \textit{known a priori}.
@@
 It is clear that these distributions are dependent on $\sigma$ in the original domain (the upper two equations), are now independent of it when processed in the log-domain (the lower two equations).
+
+\subsection{The Dispersion and Contrast Models}
 

### 2014-06-27 6/conclusional_discussion.tex
auto

@@
 
-The
-                proposed scalar models for POLSAR also have limitations.
-It
-                calls for a dimensional reduction operation, which is
-                probably not lossless.
+Since the full POLSAR data is multi-dimensional and the proposed models are scalar,
+  by their own definition, they are not perfect.
+They inherently suffer from a loss of dimension.  
+%The
+%                proposed scalar models for POLSAR also have limitations.
+%It
+%                calls for a dimensional reduction operation, which is
+%                probably not lossless.
 Thus
@@
                 fully representative of the data.
+This restricts the use of the models to a class of porblem where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
+They however, are hopefully the most practical way to answer some common types of commonly asked questions such as:
+  ``what is the best speckle filter for the given data set?'' or
+  ``what type of surface does a region of interest belong to?''.
+On the other hand, the proposed models might not be very useful in applications,
+  where the relationship among each dimensional component is used to make further inferences.
+
 Intuitively,
-                this is similar to the use of magnitude as being
+                their use is similar to the use of magnitude as being
                 representative of a complex number, which also is not
@@
 
-Although
-                the proposed models may have certain limitations, its
-                potentials still mostly stays undiscovered.
+%Although
+%                the proposed models may have certain limitations, its
+%                potentials still mostly stays undiscovered.
+Building up from the proposed models, several possible future work has been identified.
 Since

### 2014-06-27 clean.sh

@@ -1,6 +1,6 @@
 #!/bin/bash
 
-declare -a ext=('tex' 'bib');
+declare -a ext=('tex' 'bib' 'pdf');
 #f_name2='chap2'
 
 function e {

### 2014-06-27 2/literature_review.tex
auto

@@
 The parameters that describe the polarization ellipse are:
+  the intensity orientation angle $\theta$,
+  the ellipticity angle $\Psi$,
+  and the orientation angle $\chi$.
+They are defined as:
 \begin{equation}
@@
 \end{equation}
+where $\Re$ and $\Im$ respectively denotes the real and imaginary parts of a complex number.
 
@@
 In this section, various different approaches to SAR speckle filtering are reviewed.
+A recent review of this topic is available in \cite{Argenti_GRSM_2013}.
 %The famous Lee, Kuan, and Frost ˆÄÅé‡§èÅlters in the ˆÄÅé‡§èÅrst category provide MMSE reconstructions based on measured local statistics.

### 2014-06-27 4/polsar.tex
auto

@@
   the logarithmic transformation converts this into a more familiar additive noise.
+\footnote{
+  As replied to the thesis' Examiners: Since the original domain is multiplicative, the range of small value is quite limited ($|C_v|$ ranges from 0 to 1).
+  The log transformed domain not only changes the nature of the noise from multiplicative to addtive,
+    it also gives this ``small'' range a much wider space ($\ln{|C_v|}$ ranges from $-\infty$ to 0).
+  In other words, it helps to expand the ``narrow'' distribution depicted in Eqn.
+\ref{eqn:determinant_distribution} to become another distribution whose shape does not depend on $\Sigma$, as depicted in Eqn.
+\ref{eqn:log_determinant_distribution}
+}
 
@@
 \begin{tabular}{c}
-	\subfloat[part-pol (2x2) dispersion]{
+	\subfloat[part-pol (2x2) dispersion (p-value HH-HV=0.8942)]{
 		 \epsfxsize=2.5in
@@
 	} \\
-	\subfloat[full-pol (3x3) dispersion]{
+	\subfloat[full-pol (3x3) dispersion (p-value=0.8806)]{
 		 \epsfxsize=2.5in

### 2014-06-27 6/conclusional_discussion.tex
auto

@@
                 fully representative of the data.
-This restricts the use of the models to a class of porblem where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
-They however, are hopefully the most practical way to answer some common types of commonly asked questions such as:
+This restricts the use of the models to a class of problems where a single scalar decision, ranking, sorting or classification answer is required from the complex dataset.
+They, however, are the most practical way to answer some commonly asked questions such as:
   ``what is the best speckle filter for the given data set?'' or

### 2014-06-29 2/literature_review.tex
auto

@@
 There have been several other attempts to filter POLSAR data.
-Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogenous neighbour.
+Vasile, proposed a region growing adaptive neighbourhood approach in 2006, where averaging is performed on an adaptive homogeneous neighbour.
 The main drawback of the approach is that only the intensity was used to determine homogeneity and a primitive averaging filter is performed on off-diagonal elements \cite{Vasile_TGRS_2006}.
 %J.S. Lee is also very active in POLSAR speckle filtering.
-In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogenous pixels based on their underlying scattering model. 
+In \cite{Lee_2006_TGRS}, J.S. Lee proposed to group homogeneous pixels based on their underlying scattering model. 
 While the work is interesting, it is believed that pixels having similar underlying models, for example volume scattering, can still be of a very different nature.

### 2014-06-29 3/sar.tex
auto

@@
 As shown in the previous section,
-  over heterogeneous area, the stochastic SAR speckle is heteroskedastic in nature.
+  the stochastic SAR speckle, over heterogeneous area, exhibits heteroskedastic properties.
 Statistical models are used to describe how the underlying back-scattering coefficient ($\sigma$) affects the distribution of the observable SAR data. 
@@
 
-To experimentally validate this theoretical discussion, real world data is extracted from a known  homogenous area (from within a RADARSAT2 image). The PDF histogram from this data is then plotted in 
+To experimentally validate this theoretical discussion, real world data is extracted from a known  homogeneous area (from within a RADARSAT2 image).
+The PDF histogram from this data is then plotted in
 Fig. \ref{fig:modelled_response} along with the modelled PDF response. 
@@
 %}
-\caption{Observed histogram of a homogenous area and modelled PDF response}
+\caption{Observed histogram of a homogeneous area and modelled PDF response}
 \label{fig:modelled_response}

### 2014-06-29 5/applications.tex
auto

@@
 \begin{lstlisting}[frame=tb]
-function centers = partition_into_homogenous_groups(l, threshold)
+function centers = partition_into_homogeneous_groups(l, threshold)
   c_init = maximum_likelihood_of(l);
@@
   end while
-  %after this: all paritions are homogenous
+  %after this: all paritions are homogeneous
 
@@
   m[i,j] = get_membership_assigments(l, c);
-  all_partitions_homogenous = true;
+  all_partitions_homogeneous = true;
   c_new = c;
@@
     g = {L[i] with m[i,j]==1};
-    this_partition_homogenous = 
+    this_partition_homogeneous = 
       (variance(g) < threshold_vector[size_of(g)]);
 
-    if (NOT this_partition_homogenous) then
-      % split non-homogenous partition
+    if (NOT this_partition_homogeneous) then
+      % split non-homogeneous partition
       c_new[j] = min(g);
@@
 
-      all_partitions_homogenous = false;
+      all_partitions_homogeneous = false;
     end if
@@
 
-  further_partition_needed = NOT all_partitions_homogenous;
+  further_partition_needed = NOT all_partitions_homogeneous;
 end function
@@
 Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
+The ``simulated result'' plot is computed through a Monte Carlo simulation.
+And the ``analysis formula'' is a straight forward plotting of the mathematical formula above.
 The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
@@
 
-\begin{figure}
-\centering
-      \begin{tabular}[h]{c}
- 	\subfloat[SLC Intensity]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
+\begin{figure}[h]
+\centering
+      \begin{tabular}{c}
+ 	\subfloat[][SLC Intensity]{
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
+%		 \epsffile{images/illustrate_ROC_curve.pdf.s.made.eps} 
+                 \plotWithLegend{images/illustrate_ROC_curve.pdf.s.made.eps}{SLC log-intensity} 
 		 \label{fig:illustrate_ROC_curve.pdf.s.made.eps}
 	} \hfill
-	\subfloat[9-Look Intensity]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
+	\subfloat[][9-Look Intensity]{
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
+%		 \epsffile{images/illustrate_ROC_curve.pdf.m.made.eps} 
+                 \plotWithLegend{images/illustrate_ROC_curve.pdf.m.made.eps}{SLC log-intensity} 
 		 \label{fig:illustrate_ROC_curve.pdf.m.made.eps}
 	} \\
- 	\subfloat[SLC log-intensity]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
+ 	\subfloat[][SLC log-intensity]{
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
+%		 \epsffile{images/log_illustrate_ROC_curve.pdf.s.made.eps} 
+                 \plotWithLegend{images/log_illustrate_ROC_curve.pdf.s.made.eps}{SLC log-intensity} 
 		 \label{fig:log_illustrate_ROC_curve.pdf.s.made.eps}
 	} \hfill
-	\subfloat[9-Look log-intensity]{
-		 \epsfxsize=6cm
-		 \epsfysize=6cm
-		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
+	\subfloat[][9-Look log-intensity]{
+%		 \epsfxsize=6cm
+%		 \epsfysize=6cm
+%		 \epsffile{images/log_illustrate_ROC_curve.pdf.m.made.eps} 
+                 \plotWithLegend{images/log_illustrate_ROC_curve.pdf.m.made.eps}{9-Look log-intensity} 
 		 \label{fig:log_illustrate_ROC_curve.pdf.m.made.eps}
@@
 The detectability of these targets are measured using the AUC index which is tabulated against the MSE.
-Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of f-MLE filters for artificially-generated heterogenous test regions.
+Fig. \ref{fig:Heterogeneous_Patterns} illustrates the evaluation result in benchmarking the performance of f-MLE filters for artificially-generated heterogeneous test regions.
 Apparently the f-MLE filters have better performance than boxcar filters.

### 2014-07-26 paper_dev/article.tex
auto

@@
 %Statistical models are undoubtedly crucial in understanding its stochastic nature.
-While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data.
+While several models have been proposed for POLSAR data, they tend to be complex and unintuitive due to the multidimensional and stochastic nature of the data \cite{Lee_1994_TGRS_1017, Lopez-Martinez_2003_TGRS_2232}.
 It is therefore necessary to establish a simple and intuitive model for the 
@@
   (ii) being representative of the complex POLSAR data.
+This will be self-evident in the next section 
+  which reviews existing scalar POLSAR discrimination measures.
 
@@
 \begin{align}
-  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
-  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} % \\
+  % \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
 \end{align}
@@
   \mathbb{R}_{\Sigma} = \frac{|C_v|}{|\Sigma_v|} &\sim \frac{1}{(2L)} \cdot \chi(2L) \\ %\label{eqn:polsar_ratio_det_cov_dist} \\
-\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \prod_{i=0}^{d-1} \frac{\chi(2L-2i)}{\chi(2L-2i)}
+\mathbb{R}_{C} = \frac{C_1}{C_2} &\sim \frac{\chi(2L)}{\chi(2L)}
 \end{align*}
@@
 \begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+  %\ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
   Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
 \end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+%where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
 This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).
@@
 Specifically in this paper, the air-borne four-look ($L=4$) AIRSAR image of Flevoland and
-  a fine-quad single-look complex RADARSAT2 image ($L=1$) are used.
+  a fine-quad single-look complex RADARSAT2 image ($L=1$) of Murda Merbok (Malaysia) are used.
 Since the determinant of the covariance matrix is only significant on multi-look data,
@@
 The plots are obtained having set ENL to an estimated value obtained using the technique presented in \cite{Anfinsen_2009_TGRS_3795}.
+The values of $L$ are $L=3.2752$ and $L=3.4241$ for the AIRSAR and RadarSat2 images respectively.   
 In all cases, the good match between the actual data and model distribution lends support to the proposed model. %providing us a simple validation of the result.

### 2014-07-28 paper_dev/article_pp.tex
auto

@@
 \begin{align}
-  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
-  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} % \\
+  % \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+%  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+%  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
 \end{align}
@@
 \begin{align*}
-  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+%  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
   Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
 \end{align*}
-where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
+%where $k = d \left[ (L_x + L_y) \ln(L_x + L_y) - L_x \ln{L_x} - L_y \ln{L_y} \right]$.
 This, in essence, derives an exact statistical distribution for the likelihood test statistics (as opposed to an asymptotic distribution \cite{{Conradsen_2003_TGRS_4}}).

### 2014-08-10 paper_dev/article.tex
auto

@@
 In addition, the proposed model is also able to subsume the traditional SAR intensity model under the umbrella of a unified model,
-  where the SAR intensity is shown to be a one dimension version of the multi-dimensional data.
+  where the SAR intensity is shown to have similar behaviour to the one dimension version of the proposed multi-dimensional models.
 %As the POLSAR covariance matrix determinant generalizes the SAR intensity towards multiple dimensions,
@@
   % \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
+%  Q &= \frac{|C_{vx}|^{L_x} \cdot |C_{vy}|^{L_y} }{|C_{vxy}|^{L_x + L_y}} \label{eqn:ori_likelyhood_stats} \\
+%  \ln Q &= L_x \ln |C_{vx}| + L_y \ln |C_{vy}| - (L_x + L_y) \ln |C_{vxy}| \label{eqn:log_likelyhood_stats}
 \end{align}
@@
 Note that the POLSAR scattering vector is denoted as $s$ in this paper.
-For partial polarimetric SAR (single polarization in transmit and dual polarization in receive),
+For partial polarimetric SAR (single polarization in transmit and dual polarization in receive), e.g. \cite{Souyris_2005_TGRS, Raney_2006_IGARSS}, 
   the vector is two-dimensional ($d=2$) and is normally written as: 
@@
 
-The approach taken in this paper differs by applying the homoskedastic log transformation  on a less-than-well-known result for the determinant of the covariance matrix.
+The approach taken in this paper differs 
+  in that it make use of 
+  %by applying the homoskedastic log transformation on 
+  a less-than-well-known result for the determinant of the covariance matrix.
 Goodman \cite{Goodman_1963_AMS_178} proved
@@
 %Assuming, on the one hand,
-For cases where the true value of the underlying signal $\Sigma_v$ is known \textit{a priori},
+Assuming the true value of the underlying signal $\Sigma_v$ is \textit{available},
 then the determinant-ratio of the signal random variable ($\mathbb{R}_{\Sigma}$) %and log-distance ($\mathbb{L}$)
@@
 Upon setting $d=1$ into the above equations,
-  the equations become:
+  they become:
 \begin{align*}
@@
   \end{eqnarray}
-considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ when multi-dimensional POLSAR collapses into single-dimensional SAR.
+considering that $|C_v| \mapsto I$ and $|\Sigma_v| \mapsto \bar{I}$ when the proposed multi-dimensional POLSAR statistical models is applied towards the case of single-dimensional SAR.
 
@@
 As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
-  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqn. \ref{eqn:ori_likelyhood_stats} %\& \ref{eqn:log_likelyhood_stats}
 can be expressed as:
 \begin{align*}
-  %\ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
+%  \ln{Q} &\sim  k + L_x \Lambda^d_{L_x} + L_y \Lambda^d_{L_y} - (L_x + L_y) \Lambda^d_{(L_x + L_y)} \\
   Q &\sim e^k \frac{(\chi^d_{L_x})^{L_x} \cdot (\chi^d_{L_y})^{L_y}}{(\chi^d_{L_x + L_y})^{L_x + L_y}}   
@@
 In the test, the intensity of single-channel SAR data (HH) for sample homogeneous areas in both datasets is extracted.
+The sizes are 300x300 and 50x50 for Radarsat2 and AIRSAR patches respectively. 
 The histograms for both the intensity and intensity ratio %the log-distance and contrast
@@
 \ref{fig:verify_det_ratio_model_2D} shows the $d=2$ plots for determinant, determinant ratio and change ratio for both datasets.
-It is very clear that the model histogram matches the data well, in fact appearing similar to a smoothed data response.
+It is clear that the model histogram matches the data well
+  %, in fact appearing similar to a smoothed data response. 
 Evidently the match is good for $d=2$.
@@
 %conclude the section
-Many similar SAR data processing techniques may be adaptable to POLSAR in this way, however they are not explored here due to space constraints.
+Many similar SAR data processing techniques may be adaptable to POLSAR in this way, however they are not explored exhaustively here due to space constraints.
 
@@
 The paper also establishes two new POLSAR discrimination measures: the determinant-ratio and the change-ratio,  which essentially are the generic versions of the SAR intensity-ratio.
-We have also shown an excellent match between the specific $d=1$ model and that for traditional SAR intensity,
+We have also shown an excellent match between the specific $d=1$ model and that of the traditional SAR intensity,
 which effectively brings the existing SAR theories under the umbrella of this new model.

### 2014-08-10 paper_dev/article_pp.tex
auto

@@
 As for the first matter, in view of the models given in Eqn \ref{eqn:determinant_distribution},
-  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqns \ref{eqn:ori_likelyhood_stats} \& \ref{eqn:log_likelyhood_stats}
+  the likelihood test statistics presented in \cite{Conradsen_2003_TGRS_4} and rewritten in Eqn. \ref{eqn:ori_likelyhood_stats} %\& \ref{eqn:log_likelyhood_stats}
 can be expressed as:

### 2014-08-10 paper_dev/cygwin_setup.sh

@@ -18,5 +18,6 @@ fi
   bibtex article
   latex 'article.tex'
   latex 'article.tex'
-
+  dvips article.dvi
+  ps2pdf article.ps
 

### 2014-08-12 paper_dev/article.tex
auto

@@
   indicating its statistically consistent properties and hence its applicability as a POLSAR discrimination measure.
-This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure
-  and will be further discussed in the next sections.
+$\mathbb{R}_C$ can be used, for example, in change detection application similar to that proposed in \cite{Conradsen_2003_TGRS_4}.
+At the same time, $\mathbb{R}_{\Sigma}$ can be used in classification or segmentation applications, similar to those proposed in \cite{Kersten_2005_TGRS_519, Lee_2011_IGARSS_3740, Cao_2007_TGRS_3454}.
+This claim is extrapolated from the widely-used intensity-ratio as a SAR discrimination measure \cite{Rignot_1993_TGRS_896}.
+This will be further discussed in the next sections.
 %is further strengthened in the next section which shows that the generic models for POLSAR presented in this paper also include the commonly-used models for SAR as its special 1-dimensional case. 

### 2014-08-17 paper_dev/JSTARS_Answer_Document/cygwin_setup.sh
auto

@@ -25,7 +25,8 @@ fi
   #latex 'thesis.tex'
   #latex 'thesis.tex'
   #yap answer_document.dvi
-  #dvipdf thesis.dvi
-  #cygstart.exe thesis.pdf
+  dvips answer_document.dvi
+  ps2pdf answer_document.ps
+  cygstart.exe answer_document.pdf
 
 

### 2014-11-22 paper_dev/article.tex
auto

@@
 %	providing us the RADAR-SAT2 imagery used in this paper. }% <-this % stops a space
-\thanks{Manuscript received March, 2014; revised March, 2014.}}
-
-\markboth{IEEE Journal on Selected Topics in Applied Earth Observation and Remote Sensing,~Vol.~x, No.~x, x~2014}%
+\thanks{Manuscript received November, 2014; revised ????, 2015.}}
+
+\markboth{IEEE Geoscience and Remote Sensing Letters,~Vol.~x, No.~x, x~2015}%
 { Le \MakeLowercase{\textit{et al.}}:  Scalar and Representative Observables, and Their Associated Statistical Model, for Polarimetric SAR Data}
